### 2022-07-28 fourmile_dataprocess.Rmd
starting fourmile

---
title: "Fourmile"
author: "Megan Sears"
date: "7/27/2022"
output:
  html_document:
    toc: true
    toc_float: true
    theme: journal
editor_options: 
  chunk_output_type: console
---

```{r open package, include=FALSE}
library(tidyverse)
library(dplyr)
library(lubridate)
library(plotly)
library(ggplot2)
library(here)
library(scales)
library(here)
```

## Load data

```{r loading data}
setwd('C:/Users/sears/Documents/Repos/fourmile/data')

#pull in all filenames with composite
filenames <- list.files('.', pattern='.csv', full.names=F)

#read all the csvs
dataframes <- lapply(filenames, read_csv)

#name all the csv
names(dataframes) <- substr(filenames, 1, 4)

#extract csvs from list to global env
lapply(names(dataframes), function(x) assign(x, dataframes[[x]], envir = .GlobalEnv))
rm(dataframes)

daily_q <- orun %>%
  select(-1) %>%
  filter(!row_number() %in% c(1:9, 11:15)) %>%
  mutate(names(.) = .[1,])

```

### 2022-07-28 fourmile_dataprocess.Rmd
plotting hydrographs

@@
   filter(!row_number() %in% c(1:9, 11:15)) %>%
-  mutate(names(.) = .[1,])
+  set_names(as.character(slice(., 1))) %>%
+  slice(-1) %>%
+  replace(.==-9999, NA) %>%
+  rename(ds3 = 2,
+         usgs1 = 3,
+         ds2 = 4,
+         usgs2 = 5,
+         us1 = 6,
+         ds1 = 7) %>%
+  mutate(date = mdy(date)) %>%
+  pivot_longer(!date, names_to = 'site', values_to = 'q_m3s') %>%
+  mutate(q_m3s = as.numeric(q_m3s))
+
+hydro <- ggplot(daily_q, aes(x=date, y=q_m3s, color=site)) + geom_line() +
+  ylim(0,8)
+
+ggplotly(hydro)
 

### 2022-07-28 fourmile_dataprocess.Rmd
knitted

--- 2022-07-28 fourmile_dataprocess.Rmd
@@
 ```{r open package, include=FALSE}
+
+knitr::opts_chunk$set(warning = FALSE, message = FALSE)
+
 library(tidyverse)
@@
 
-## Load data
-
-```{r loading data}
+```{r loading data, include=FALSE}
 setwd('C:/Users/sears/Documents/Repos/fourmile/data')
@@
 
+```
+
+## Hydrographs
+
+```{r hydrographs, echo=F}
+#daily streamflow
 daily_q <- orun %>%
@@
   filter(!row_number() %in% c(1:9, 11:15)) %>%
-  mutate(names(.) = .[1,])
+  set_names(as.character(slice(., 1))) %>%
+  slice(-1) %>%
+  replace(.==-9999, NA) %>%
+  rename(ds3 = 2,
+         usgs1 = 3,
+         ds2 = 4,
+         usgs2 = 5,
+         us1 = 6,
+         ds1 = 7) %>%
+  mutate(date = mdy(date)) %>%
+  pivot_longer(!date, names_to = 'site', values_to = 'q_m3s') %>%
+  mutate(q_m3s = as.numeric(q_m3s))
+
+hydro <- ggplot(daily_q, aes(x=date, y=q_m3s, color=site)) + geom_line() +
+  ylim(0,8) + theme_bw() + 
+  ggtitle('Daily streamflow (all)')
+
+ggplotly(hydro)
+
+#look at 2011-2013
+hydro_datelimit <- ggplot(daily_q, aes(x=date, y=q_m3s, color=site)) + geom_line() + 
+  theme_bw() + 
+  scale_x_date(limits = as.Date(c('2011-01-01', '2014-01-01'))) +
+  ylim(0,4) +
+  ggtitle('Daily streamflow (2011-2013)')
+
+ggplotly(hydro_datelimit)
 
 ```
+
+## Precip
+
+```{r precip, echo=F}
+#daily precip
+daily_p <- prec %>%
+  filter(!row_number() %in% c(1:12, 14:17)) %>%
+  set_names(as.character(slice(., 1))) %>%
+  slice(-1) %>%
+  select(-1) %>%
+  replace(.==-9999, NA) %>%
+  rename(date = 1) %>%
+  mutate(date = mdy(date)) %>%
+  pivot_longer(!date, names_to = 'site', values_to = 'precip_mm') %>%
+  mutate(precip_mm = as.numeric(precip_mm))
+
+precip <- ggplot(daily_p, aes(x=date, y=precip_mm, color=site)) + geom_line()  +
+  theme_bw() +
+  ggtitle('Daily precip')
+
+ggplotly(precip)
+
+#look at 2011-2013
+precip_datelim <- ggplot(daily_p, aes(x=date, y=precip_mm, color=site)) + geom_line() + 
+   scale_x_date(limits = as.Date(c('2011-01-01', '2014-01-01'))) +
+  theme_bw() +
+  ggtitle('Daily precip')
+
+ggplotly(precip_datelim)
+
+#monthly sums
+monthlyp <- daily_p %>%
+  group_by(site, year(date), month(date)) %>%
+  summarize(precip_mo_mm = sum(precip_mm, na.rm=T),
+            mo_yr = median(date))
+
+mo_precip <- ggplot(monthlyp, aes(mo_yr, precip_mo_mm, color=site)) + geom_col(position ='dodge') +
+  scale_x_date(limits = as.Date(c('2012-06-01', '2014-01-01'))) +
+  ggtitle('Precip - monthly sum') + theme_bw()
+
+ggplotly(mo_precip)
+
+```

### 2022-07-28 fourmile_dataprocess.Rmd
knitted again

@@
 
+library(rmdformats)
 library(tidyverse)
@@
   theme_bw() +
-  ggtitle('Daily precip')
+  ggtitle('Daily precip (all)')
 
@@
   theme_bw() +
-  ggtitle('Daily precip')
+  ggtitle('Daily precip (2011-2013)')
 

### 2022-08-02 fourmile_dataprocess.Rmd
differencing between gages

--- 2022-07-28 fourmile_dataprocess.Rmd
@@
 library(here)
+library(rgdal)
+library(sp)
+library(sf)
+library(mapview)
 ```
@@
 
+## Gage locations
+
+USGS2 and DS2 have the same coordinates. USGS1 and DS3 have the same coordinates.
+
+```{r map, echo=FALSE}
+locations <- read_csv(here('data', 'Outlets.csv'))
+
+locations <- locations %>%
+st_as_sf(., coords=c('y','x'), crs = 4326)
+
+mapview(locations, zcol = 'name')
+
+```
+
 ## Hydrographs
+
+Notes on gages: So far DS2 and DS3 have not been used. US1 and DS1 are mostly point measurements.
 
@@
 
+## Streamflow differencing from USGS1 (outlet)
+
+```{r hydrographs_diff, echo=F}
+#streamflow differencing
+q_diff <- daily_q %>%
+  pivot_wider(names_from = site, values_from = q_m3s) %>%
+  mutate(usgs2_diff = usgs1 - usgs2,
+         us1_diff = usgs1 - us1,
+         ds1_diff = usgs1 - ds1,
+         ds2_diff = usgs1 - ds2,
+         ds3_diff = usgs1 - ds3) %>%
+  select(-c(usgs2, us1, ds1, ds2, ds3, usgs1)) %>%
+  pivot_longer(!date, names_to = 'site', values_to = 'q_m3s')
+
+diff <- ggplot(q_diff, aes(x=date, y=q_m3s, color=site)) + 
+  geom_line() +
+  scale_x_date(limits = as.Date(c('2011-01-01', '2014-08-01'))) +
+  ylim(-1.1,0.6) +
+  theme_bw() + 
+  ggtitle('Daily streamflow difference from USGS1')
+
+ggplotly(diff)
+
+#streamflow percent
+# q_percent <- daily_q %>%
+#   pivot_wider(names_from = site, values_from = q_m3s) %>%
+#   mutate(usgs2_diff = usgs2 / usgs1,
+#          us1_per = us1 / usgs1,
+#          ds1_per = ds1 / usgs1,
+#          ds2_per = ds2 / usgs1,
+#          ds3_per = ds3 / usgs1) %>%
+#   select(-c(usgs2, us1, ds1, ds2, ds3, usgs1)) %>%
+#   pivot_longer(!date, names_to = 'site', values_to = 'q_m3s')
+# 
+# percent <- ggplot(q_percent, aes(x=date, y=q_m3s*100, color=site)) + 
+#   geom_line() +
+#   labs(y='percent of USGS1') +
+#   ylim(0,1125) +
+#   scale_x_date(limits = as.Date(c('2011-01-01', '2014-08-01'))) +
+#   theme_bw() + 
+#   ggtitle('Daily streamflow percent of USGS1') 
+# 
+# ggplotly(percent)
+
+```
+
+## Streamflow differencing between each gage
+
+DS1 minus US1 (uppermost)
+
+```{r DS1-US1, echo=FALSE}
+
+diff_ds1 <- daily_q %>%
+  pivot_wider(names_from = site, values_from = q_m3s) %>%
+  mutate(ds1_us1 = ds1 - us1) %>%
+  select(-c(usgs2, us1, ds1, ds2, ds3, usgs1)) %>%
+  pivot_longer(!date, names_to = 'site', values_to = 'q_m3s')
+
+diff1 <- ggplot(diff_ds1, aes(x=date, y=q_m3s)) + 
+  geom_point() +
+  scale_x_date(limits = as.Date(c('2011-01-01', '2014-08-01'))) +
+  #ylim(-1.1,0.6) +
+  theme_bw() + 
+  ggtitle('Daily streamflow DS1 - US1')
+
+ggplotly(diff1)
+
+mean(diff_ds1$q_m3s, na.rm=T)
+
+```
+
+USGS2 minus DS1
+
+```{r USGS2-DS1, echo=FALSE}
+
+diff_usgs2 <- daily_q %>%
+  pivot_wider(names_from = site, values_from = q_m3s) %>%
+  mutate(usgs2_ds1 = usgs2 - ds1) %>%
+  select(-c(usgs2, us1, ds1, ds2, ds3, usgs1)) %>%
+  pivot_longer(!date, names_to = 'site', values_to = 'q_m3s')
+
+diff2 <- ggplot(diff_usgs2, aes(x=date, y=q_m3s)) + 
+  geom_point() +
+  scale_x_date(limits = as.Date(c('2011-01-01', '2014-08-01'))) +
+  #ylim(-1.1,0.6) +
+  theme_bw() + 
+  ggtitle('Daily streamflow USGS2 - DS1')
+
+ggplotly(diff2)
+
+mean(diff_usgs2$q_m3s, na.rm=T)
+
+```
+
+USGS1 - USGS2
+
+```{r USGS1-USGS2, echo=FALSE}
+diff_usgs1 <- daily_q %>%
+  pivot_wider(names_from = site, values_from = q_m3s) %>%
+  mutate(usgs2_ds1 = usgs1 - usgs2) %>%
+  select(-c(usgs2, us1, ds1, ds2, ds3, usgs1)) %>%
+  pivot_longer(!date, names_to = 'site', values_to = 'q_m3s')
+
+diff3 <- ggplot(diff_usgs1, aes(x=date, y=q_m3s)) + 
+  geom_point() +
+  scale_x_date(limits = as.Date(c('2011-01-01', '2013-12-01'))) +
+  #ylim(-1.1,0.6) +
+  theme_bw() + 
+  ggtitle('Daily streamflow USGS1 - USGS2')
+
+ggplotly(diff3)
+
+mean(diff_usgs1$q_m3s, na.rm=T)
+
+```
+
 ## Precip
@@
   theme_bw() +
-  ggtitle('Daily precip')
+  ggtitle('Daily precip (Gordon N and S)')
 
@@
 
-#look at 2011-2013
-precip_datelim <- ggplot(daily_p, aes(x=date, y=precip_mm, color=site)) + geom_line() + 
-   scale_x_date(limits = as.Date(c('2011-01-01', '2014-01-01'))) +
-  theme_bw() +
-  ggtitle('Daily precip')
-
-ggplotly(precip_datelim)
+# #look at 2011-2013
+# precip_datelim <- ggplot(daily_p, aes(x=date, y=precip_mm, color=site)) + geom_line() + 
+#    scale_x_date(limits = as.Date(c('2011-01-01', '2014-01-01'))) +
+#   theme_bw() +
+#   ggtitle('Daily precip (2011-2013)')
+# 
+# ggplotly(precip_datelim)
 
 #monthly sums
-monthlyp <- daily_p %>%
-  group_by(site, year(date), month(date)) %>%
-  summarize(precip_mo_mm = sum(precip_mm, na.rm=T),
-            mo_yr = median(date))
-
-mo_precip <- ggplot(monthlyp, aes(mo_yr, precip_mo_mm, color=site)) + geom_col(position ='dodge') +
-  scale_x_date(limits = as.Date(c('2012-06-01', '2014-01-01'))) +
-  ggtitle('Precip - monthly sum') + theme_bw()
-
-ggplotly(mo_precip)
+# monthlyp <- daily_p %>%
+#   group_by(site, year(date), month(date)) %>%
+#   summarize(precip_mo_mm = sum(precip_mm, na.rm=T),
+#             mo_yr = median(date))
+# 
+# mo_precip <- ggplot(monthlyp, aes(mo_yr, precip_mo_mm, color=site)) + geom_col(position ='dodge') +
+#   scale_x_date(limits = as.Date(c('2012-06-01', '2014-01-01'))) +
+#   ggtitle('Precip - monthly sum') + theme_bw()
+# 
+# ggplotly(mo_precip)
 

### 2022-08-02 fourmile_dataprocess.Rmd
loss/gains per yr

@@
 library(mapview)
+library(kableExtra)
 ```
@@
 
+```
+
+Average DS1 minus US1 difference
+
+```{r DS1-US1_avg, echo=FALSE}
+
 mean(diff_ds1$q_m3s, na.rm=T)
+
+diff_ds1_yr <- diff_ds1 %>%
+  group_by(year(date)) %>%
+  summarize(mean(q_m3s, na.rm=T))
+
+kable(diff_ds1_yr, 
+      col.names = c("Year", "Avg streamflow difference (m3/s)")) %>%
+  kable_styling()
 
@@
 
+```
+
+Average USGS2 minus DS1 difference
+
+```{r USGS2-DS1_avg, echo=FALSE}
+
 mean(diff_usgs2$q_m3s, na.rm=T)
+
+diff_usgs2_yr <- diff_usgs2 %>%
+  group_by(year(date)) %>%
+  summarize(mean(q_m3s, na.rm=T))
+
+kable(diff_usgs2_yr, 
+      col.names = c("Year", "Avg streamflow difference (m3/s)")) %>%
+  kable_styling()
 
@@
 
-USGS1 - USGS2
+USGS1 minus USGS2
 
@@
 ggplotly(diff3)
+```
 
+Average USGS1 minus USGS2 difference
+
+```{r USGS1-USGS2_avg, echo=FALSE}
 mean(diff_usgs1$q_m3s, na.rm=T)
+
+diff_usgs1_yr <- diff_usgs1 %>%
+  group_by(year(date)) %>%
+  summarize(mean(q_m3s, na.rm=T))
+
+kable(diff_usgs1_yr, 
+      col.names = c("Year", "Avg streamflow difference (m3/s)")) %>%
+  kable_styling()
 

### 2022-08-02 fourmile_dataprocess.Rmd
monthly sum of loss for lower gages

@@
 
-DS1 minus US1 (uppermost)
+### DS1 minus US1 (uppermost)
 
@@
 
-Average DS1 minus US1 difference
+#### Average DS1 minus US1 difference
 
@@
 
-USGS2 minus DS1
+### USGS2 minus DS1
 
@@
 
-Average USGS2 minus DS1 difference
+#### Average USGS2 minus DS1 difference
 
@@
 
-USGS1 minus USGS2
+### USGS1 minus USGS2
 
@@
 ggplotly(diff3)
+
 ```
 
-Average USGS1 minus USGS2 difference
+#### Average USGS1 minus USGS2 difference
 
 ```{r USGS1-USGS2_avg, echo=FALSE}
+
 mean(diff_usgs1$q_m3s, na.rm=T)
@@
       col.names = c("Year", "Avg streamflow difference (m3/s)")) %>%
+  kable_styling()
+
+```
+
+#### Sum of losses between USGS1 and USGS2
+
+```{r USGS1-USGS2 sum of losses, echo=FALSE}
+
+sum_diff_usgs1 <- diff_usgs1 %>%
+  mutate(month = as.numeric(format(date, "%m")), year = as.numeric(format(date, "%Y"))) %>%
+  mutate(neg_q = if_else(q_m3s < 0, q_m3s, 0)) %>%
+  dplyr::group_by(year, month) %>%
+  dplyr::summarize(mo_loss = sum(q_m3s)) %>%
+  #distinct() %>%
+  na.omit()
+
+kable(sum_diff_usgs1, 
+      col.names = c("Year", "Month", "Monthly sum of losses (m3/s)")) %>%
   kable_styling()

### 2022-08-02 fourmile_dataprocess.Rmd
taking out usgs1 difference from all

@@
 ggplotly(hydro_datelimit)
-
-```
-
-## Streamflow differencing from USGS1 (outlet)
-
-```{r hydrographs_diff, echo=F}
-#streamflow differencing
-q_diff <- daily_q %>%
-  pivot_wider(names_from = site, values_from = q_m3s) %>%
-  mutate(usgs2_diff = usgs1 - usgs2,
-         us1_diff = usgs1 - us1,
-         ds1_diff = usgs1 - ds1,
-         ds2_diff = usgs1 - ds2,
-         ds3_diff = usgs1 - ds3) %>%
-  select(-c(usgs2, us1, ds1, ds2, ds3, usgs1)) %>%
-  pivot_longer(!date, names_to = 'site', values_to = 'q_m3s')
-
-diff <- ggplot(q_diff, aes(x=date, y=q_m3s, color=site)) + 
-  geom_line() +
-  scale_x_date(limits = as.Date(c('2011-01-01', '2014-08-01'))) +
-  ylim(-1.1,0.6) +
-  theme_bw() + 
-  ggtitle('Daily streamflow difference from USGS1')
-
-ggplotly(diff)
-
-#streamflow percent
-# q_percent <- daily_q %>%
-#   pivot_wider(names_from = site, values_from = q_m3s) %>%
-#   mutate(usgs2_diff = usgs2 / usgs1,
-#          us1_per = us1 / usgs1,
-#          ds1_per = ds1 / usgs1,
-#          ds2_per = ds2 / usgs1,
-#          ds3_per = ds3 / usgs1) %>%
-#   select(-c(usgs2, us1, ds1, ds2, ds3, usgs1)) %>%
-#   pivot_longer(!date, names_to = 'site', values_to = 'q_m3s')
-# 
-# percent <- ggplot(q_percent, aes(x=date, y=q_m3s*100, color=site)) + 
-#   geom_line() +
-#   labs(y='percent of USGS1') +
-#   ylim(0,1125) +
-#   scale_x_date(limits = as.Date(c('2011-01-01', '2014-08-01'))) +
-#   theme_bw() + 
-#   ggtitle('Daily streamflow percent of USGS1') 
-# 
-# ggplotly(percent)
 

### 2022-08-09 fourmile_dataprocess.Rmd
added pumping and precip data

@@
 library(kableExtra)
+library(dataRetrieval)
+library(raster)
+library(sf)
+
 ```
@@
 ```{r map, echo=FALSE}
-locations <- read_csv(here('data', 'Outlets.csv'))
+#locations <- read_csv(here('data', 'Outlets.csv'))
+
+#sp <- raster('MA_SP.01.18.tif')
+
+#hrus <- st_read('hrus_final.shp')
+
+#save.image(file = 'spatial.RData')
+load('C:/Users/sears/Documents/Repos/fourmile/data/spatial.RData')
 
@@
 
-mapview(locations, zcol = 'name')
+mapview(locations, zcol = 'type') + mapview(hrus)
+
+mapview(sp, col.regions = list("brown", 'purple', 'blue', 'white'), at = seq(0, 100, 25)) + 
+  mapview(locations, zcol = 'type') +
+  mapview(hrus)
 
@@
 daily_q <- orun %>%
-  select(-1) %>%
+  dplyr::select(-1) %>%
   filter(!row_number() %in% c(1:9, 11:15)) %>%
@@
   mutate(ds1_us1 = ds1 - us1) %>%
-  select(-c(usgs2, us1, ds1, ds2, ds3, usgs1)) %>%
+  dplyr::select(-c(usgs2, us1, ds1, ds2, ds3, usgs1)) %>%
   pivot_longer(!date, names_to = 'site', values_to = 'q_m3s')
@@
   mutate(usgs2_ds1 = usgs2 - ds1) %>%
-  select(-c(usgs2, us1, ds1, ds2, ds3, usgs1)) %>%
+  dplyr::select(-c(usgs2, us1, ds1, ds2, ds3, usgs1)) %>%
   pivot_longer(!date, names_to = 'site', values_to = 'q_m3s')
@@
   mutate(usgs2_ds1 = usgs1 - usgs2) %>%
-  select(-c(usgs2, us1, ds1, ds2, ds3, usgs1)) %>%
+  dplyr::select(-c(usgs2, us1, ds1, ds2, ds3, usgs1)) %>%
   pivot_longer(!date, names_to = 'site', values_to = 'q_m3s')
@@
 
+### Incorporating pumping
+
+```{r USGS1+pumping-USGS2, echo=FALSE}
+
+inlet <- inle %>%
+  replace(.==-9999, NA) %>%
+  mutate(date = mdy(date))
+
+diff_usgs1_pump <- daily_q %>%
+  pivot_wider(names_from = site, values_from = q_m3s) %>%
+  left_join(., inlet, by='date') %>%
+  mutate(usgs1_pump = (usgs1 + inflow_m3s),
+         usgs1_pump_usgs2 = (usgs1_pump - usgs2)) %>%
+  dplyr::select(-c(usgs2, us1, ds1, ds2, ds3, usgs1, inflow_m3s)) %>%
+  pivot_longer(!date, names_to = 'site', values_to = 'q_m3s')
+
+diff4 <- ggplot(diff_usgs1_pump, aes(x=date, y=q_m3s, color=site)) + 
+  geom_point() +
+  scale_x_date(limits = as.Date(c('2012-04-01', '2012-10-01'))) +
+  ylim(-0.5,0.5) +
+  theme_bw() + 
+  ggtitle('Daily streamflow: (USGS1 + pumping) - USGS2')
+
+ggplotly(diff4)
+
+```
+
 ## Precip
@@
 daily_p <- prec %>%
-  filter(!row_number() %in% c(1:12, 14:17)) %>%
-  set_names(as.character(slice(., 1))) %>%
-  slice(-1) %>%
-  select(-1) %>%
   replace(.==-9999, NA) %>%
-  rename(date = 1) %>%
-  mutate(date = mdy(date)) %>%
+  mutate(date = dmy(date)) %>%
   pivot_longer(!date, names_to = 'site', values_to = 'precip_mm') %>%
-  mutate(precip_mm = as.numeric(precip_mm))
+  mutate(precip_mm = as.numeric(precip_mm)) %>%
+  mutate(WY = calcWaterYear(date)) %>%
+  group_by(WY, site) %>%
+  mutate(dailyp_cum_mm = cumsum(precip_mm))
 
@@
   theme_bw() +
-  ggtitle('Daily precip (Gordon N and S)')
+  ggtitle('Daily precip (all)')
 
@@
 
-# #look at 2011-2013
-# precip_datelim <- ggplot(daily_p, aes(x=date, y=precip_mm, color=site)) + geom_line() + 
-#    scale_x_date(limits = as.Date(c('2011-01-01', '2014-01-01'))) +
-#   theme_bw() +
-#   ggtitle('Daily precip (2011-2013)')
-# 
-# ggplotly(precip_datelim)
+precip_cumu <- ggplot(daily_p, aes(x=date, y=dailyp_cum_mm, color=site)) + geom_line()  +
+  theme_bw() +
+  ggtitle('Daily precip cumulative sums (all)')
 
-#monthly sums
-# monthlyp <- daily_p %>%
-#   group_by(site, year(date), month(date)) %>%
-#   summarize(precip_mo_mm = sum(precip_mm, na.rm=T),
-#             mo_yr = median(date))
-# 
-# mo_precip <- ggplot(monthlyp, aes(mo_yr, precip_mo_mm, color=site)) + geom_col(position ='dodge') +
-#   scale_x_date(limits = as.Date(c('2012-06-01', '2014-01-01'))) +
-#   ggtitle('Precip - monthly sum') + theme_bw()
-# 
-# ggplotly(mo_precip)
+ggplotly(precip_cumu)
 

### 2022-09-01 fourmile_dataprocess.Rmd
filtering tipping buckets for non rain months

@@
 #daily precip
+prec_update <- prec %>%
+    replace(.==-9999, NA) %>%
+  mutate(date = dmy(date),
+         doy = yday(date)) %>%
+  mutate(Gordon_South = ifelse(!doy %in% c(152:258), 
+                               NA, Gordon_South),
+         Gordon_North = ifelse(!doy %in% c(152:258), 
+                               NA, Gordon_North),
+         GH = ifelse(!doy %in% c(152:258), 
+                               NA, GH),
+         LM = ifelse(!doy %in% c(152:258), 
+                               NA, LM),
+         SE = ifelse(!doy %in% c(152:258), 
+                               NA, SE),
+         SP = ifelse(!doy %in% c(152:258), 
+                               NA, SP),
+         ST = ifelse(!doy %in% c(152:258), 
+                               NA, ST),
+         NADP_SL = ifelse(!doy %in% c(152:258), 
+                               NA, NADP_SL))
+
 daily_p <- prec %>%
-  replace(.==-9999, NA) %>%
-  mutate(date = dmy(date)) %>%
   pivot_longer(!date, names_to = 'site', values_to = 'precip_mm') %>%
   mutate(precip_mm = as.numeric(precip_mm)) %>%
-  mutate(WY = calcWaterYear(date)) %>%
+  mutate(WY = calcWaterYear(date))
   group_by(WY, site) %>%

### 2022-09-01 fourmile_dataprocess.Rmd
comparing niwot snotel vs niwot prism pixel

@@
 ```
+
+## Compare Niwot SNOTEL pirecip to prism pixel
+
+```{r}
+niwot_prism <- read_csv(here('data', 'niwot_prism_compare.csv'))
+
+ni_prism <- niwot_prism %>%
+  filter(!row_number() %in% c(1:10)) %>%
+  rename(date = 1,
+         prism_mm = 2) %>%
+  mutate(date = ymd(date))
+
+niwot_snotel <- prec_update %>%
+  dplyr::select(c(date, Niwot_Snotel)) %>%
+  rename(snotel_mm = Niwot_Snotel)
+
+niwot_compare <- full_join(ni_prism, niwot_snotel, by = 'date')
+
+niwot_compare <- niwot_compare %>%
+  mutate(diff_mm = snotel_mm - prism_mm)
+
+summary(niwot_compare$diff_mm)
+count(niwot_compare)
+
+#filter to look at sept - june
+```

### 2022-09-02 fourmile_dataprocess.Rmd
filter out prism non winter months next

--- 2022-08-09 fourmile_dataprocess.Rmd
@@
 #daily precip
+prec_update <- prec %>%
+  mutate(date = dmy(date),
+         doy = yday(date)) %>%
+  mutate(Gordon_South = ifelse(!doy %in% c(152:258), 
+                               NA, Gordon_South),
+         Gordon_North = ifelse(!doy %in% c(152:258), 
+                               NA, Gordon_North),
+         GH = ifelse(!doy %in% c(152:258), 
+                               NA, GH),
+         LM = ifelse(!doy %in% c(152:258), 
+                               NA, LM),
+         SE = ifelse(!doy %in% c(152:258), 
+                               NA, SE),
+         SP = ifelse(!doy %in% c(152:258), 
+                               NA, SP),
+         ST = ifelse(!doy %in% c(152:258), 
+                               NA, ST),
+         NADP_SL = ifelse(!doy %in% c(152:258), 
+                               NA, NADP_SL)) %>%
+  mutate_at(c('prism_W', 'prism_M', 'prism_E'), funs(lead), n = 1) #%>%
+  mutate_at(c('prism_W', 'prism_M', 'prism_E'), )
+
 daily_p <- prec %>%
   replace(.==-9999, NA) %>%
-  mutate(date = dmy(date)) %>%
   pivot_longer(!date, names_to = 'site', values_to = 'precip_mm') %>%
   mutate(precip_mm = as.numeric(precip_mm)) %>%
-  mutate(WY = calcWaterYear(date)) %>%
+  mutate(WY = calcWaterYear(date))
   group_by(WY, site) %>%
@@
 ```
+
+## Compare Niwot SNOTEL pirecip to prism pixel
+
+```{r}
+niwot_prism <- read_csv(here('data', 'niwot_prism_compare.csv'))
+
+ni_prism <- niwot_prism %>%
+  filter(!row_number() %in% c(1:10)) %>%
+  rename(date = 1,
+         prism_mm = 2) %>%
+  mutate(date = ymd(date))
+
+niwot_snotel <- prec_update %>%
+  dplyr::select(c(date, Niwot_Snotel)) %>%
+  rename(snotel_mm = Niwot_Snotel)
+
+niwot_compare <- full_join(ni_prism, niwot_snotel, by = 'date')
+
+niwot_compare <- niwot_compare %>%
+  mutate(diff_mm = snotel_mm - prism_mm) %>%
+  na.omit()
+
+#filter to look at sept - june
+niwot_winter_comp <- niwot_compare %>%
+  mutate(month = month(date)) %>%
+  filter(!month %in% c(6:8))
+
+summary(niwot_winter_comp)
+
+niwot_prismshift <- niwot_compare %>%
+  mutate_at(c("prism_mm"), funs(lead), n = 1) %>%
+  mutate(month = month(date)) %>%
+  filter(!month %in% c(6:8)) %>%
+  mutate(diff_mm = snotel_mm - prism_mm)
+
+summary(niwot_prismshift)
+
+```

### 2022-09-06 fourmile_dataprocess.Rmd
few updates

@@
 library(sf)
+library(stringr)
 
@@
          doy = yday(date)) %>%
-  mutate(Gordon_South = ifelse(!doy %in% c(152:258), 
-                               NA, Gordon_South),
-         Gordon_North = ifelse(!doy %in% c(152:258), 
-                               NA, Gordon_North),
-         GH = ifelse(!doy %in% c(152:258), 
-                               NA, GH),
-         LM = ifelse(!doy %in% c(152:258), 
-                               NA, LM),
-         SE = ifelse(!doy %in% c(152:258), 
-                               NA, SE),
-         SP = ifelse(!doy %in% c(152:258), 
-                               NA, SP),
-         ST = ifelse(!doy %in% c(152:258), 
-                               NA, ST),
-         NADP_SL = ifelse(!doy %in% c(152:258), 
-                               NA, NADP_SL)) %>%
-  mutate_at(c('prism_W', 'prism_M', 'prism_E'), funs(lead), n = 1) #%>%
-  mutate_at(c('prism_W', 'prism_M', 'prism_E'), )
+  mutate_at(c('Gordon_South', 'Gordon_North',
+              'GH', 'LM', 'SE', 'SP', 'ST', 'NADP_SL'),
+            ~(ifelse(!doy %in% c(152:258), 
+                               NA, .))) %>%
+  mutate_at(c('prism_W', 'prism_M', 'prism_E'), list(lead), n = 1) %>%
+  mutate_at(c('prism_W', 'prism_M', 'prism_E'), ~(ifelse(doy %in% c(152:258),
+                                                         NA, .))) %>%
+  filter(date > '2009-12-31') %>%
+  dplyr::select(-c(doy)) %>%
+  mutate(date = format(as.Date(date), '%d.%m.%Y'))
+
+#write_csv(prec_update, 'precipAll_update.csv')
 
 daily_p <- prec %>%
+  mutate(date = dmy(date)) %>%
   replace(.==-9999, NA) %>%
@@
   mutate(precip_mm = as.numeric(precip_mm)) %>%
-  mutate(WY = calcWaterYear(date))
+  mutate(WY = calcWaterYear(date)) %>%
   group_by(WY, site) %>%
@@
 ```{r}
-niwot_prism <- read_csv(here('data', 'niwot_prism_compare.csv'))
-
-ni_prism <- niwot_prism %>%
+niwot_prism <- read.csv(here('data', 'niwot_prism_compare.csv')) %>% 
   filter(!row_number() %in% c(1:10)) %>%
@@
           prism_mm = 2) %>%
-  mutate(date = ymd(date))
+   mutate(date = ymd(date),
+          prism_mm = as.numeric(prism_mm))
 
@@
   dplyr::select(c(date, Niwot_Snotel)) %>%
-  rename(snotel_mm = Niwot_Snotel)
+  rename(snotel_mm = Niwot_Snotel) %>%
+  mutate(date = dmy(date))
 
-niwot_compare <- full_join(ni_prism, niwot_snotel, by = 'date')
+niwot_compare <- full_join(niwot_prism, niwot_snotel, by = 'date')
 

### 2022-09-07 fourmile_dataprocess.Rmd
next steps: clean up precip eval, get prism daily srad data

@@
 library(stringr)
-
+library(hydroGOF)
+library(Metrics)
 ```
@@
 
-## Compare Niwot SNOTEL pirecip to prism pixel
+## Compare Niwot SNOTEL precip to prism pixel
 
@@
 
+rmse(niwot_compare$prism_mm, niwot_compare$snotel_mm)
+pbias(niwot_compare$prism_mm, niwot_compare$snotel_mm)
+
+scatter <- ggplot(niwot_compare, aes(x=snotel_mm, y=prism_mm)) +
+  geom_point() +
+  geom_abline(intercept = 0, slope = 1, size=1.5, color="blue")
+
+ggplotly(scatter)
+
 #filter to look at sept - june
@@
   mutate(month = month(date)) %>%
-  filter(!month %in% c(6:8)) %>%
+  #filter(!month %in% c(6:8)) %>%
   mutate(diff_mm = snotel_mm - prism_mm)
@@
 summary(niwot_prismshift)
+rmse(niwot_prismshift$prism_mm, niwot_prismshift$snotel_mm)
+NSE(niwot_prismshift$prism_mm, niwot_prismshift$snotel_mm)
+pbias(niwot_prismshift$prism_mm, niwot_prismshift$snotel_mm)
+
+scatter_shiftday <- ggplot(niwot_prismshift, aes(x=snotel_mm, y=prism_mm)) +
+  geom_point() +
+  geom_abline(intercept = 0, slope = 1, size=1.5, color="blue")
+
+ggplotly(scatter_shiftday)
+
+niwot_prismfrac <- niwot_compare %>%
+  mutate(prism_most_mm = prism_mm * 0.974,
+         prism_little_mm = prism_mm * 0.026) %>%
+  mutate_at(c('prism_most_mm'), list(lead), n = 1) %>%
+  mutate(prism_new_mm = prism_most_mm + prism_little_mm,
+         diff_prismfrac = snotel_mm - prism_new_mm)
+
+summary(niwot_prismfrac)
+
+scatter_frac <- ggplot(niwot_prismfrac, aes(x=snotel_mm, y=prism_new_mm)) +
+  geom_point() +
+  geom_abline(intercept = 0, slope = 1, size=1.5, color="blue")
+
+ggplotly(scatter_frac)
+
+rmse(niwot_prismfrac$prism_new_mm, niwot_prismfrac$snotel_mm)
+NSE(niwot_prismfrac$prism_new_mm, niwot_prismfrac$snotel_mm)
+pbias(niwot_prismfrac$prism_new_mm, niwot_prismfrac$snotel_mm)
 
 ```
+
+## Compare prism solar rad to flux solar rad
+
+```{r}
+srad <- solr %>%
+  dplyr::select(-1) %>%
+  filter(!row_number() %in% c(1:17)) %>%
+  replace(.==-9999, NA) %>%
+  rename(date = 1,
+         prism_w = 2,
+         prism_m = 3,
+         prism_e = 4,
+         gordon_s = 5,
+         gordon_n = 6,
+         greenlake = 7) %>%
+  mutate(date = dmy(date))
+
+niwot_srad <- Niwo %>%
+  mutate(date = ymd(date))
+
+niwot_daymet <- daym %>%
+  filter(!row_number() %in% c(1:7)) %>%
+  rename(year = 1,
+         doy = 2,
+         srad_wm2 = 3)
+
+```

### 2022-09-08 fourmile_dataprocess.Rmd
added in solar radiation comparisons (prism W, daymet, and niwot flux tower)

@@
 niwot_srad <- Niwo %>%
-  mutate(date = ymd(date))
+  mutate(date = ymd(date)) %>%
+  rename(niwot_flux_mjm2 = 3) %>%
+  dplyr::select(-c(watts_per_m2)) %>%
+  replace(. == -9999, NA)
 
+## original  
+srad_compare <- full_join(srad, niwot_srad, by = 'date') %>%
+  dplyr::select(c(date, prism_w, niwot_flux_mjm2)) %>%
+  mutate(diff = niwot_flux_mjm2 - prism_w) %>%
+  na.omit()
+
+summary(srad_compare)
+
+scatter_srad_orig <- ggplot(srad_compare, aes(x=niwot_flux_mjm2, y=prism_w)) +
+  geom_point() +
+  geom_abline(intercept = 0, slope = 1, size=1.5, color="blue")
+
+ggplotly(scatter_srad_orig)
+
+## 1 day shift
+srad_shift1day <- srad_compare %>%
+  mutate_at(c("prism_w"),list(lead), n = 1) %>%
+  na.omit()
+
+scatter_srad_1day <- ggplot(srad_shift1day, aes(x=niwot_flux_mjm2, y=prism_w)) +
+  geom_point() +
+  geom_abline(intercept = 0, slope = 1, size=1.5, color="blue")
+
+ggplotly(scatter_srad_1day)
+#scatter_srad_1day
+
+summary(srad_shift1day)
+rmse(srad_shift1day$prism_w, srad_shift1day$niwot_flux_mjm2)
+pbias(srad_shift1day$prism_w, srad_shift1day$niwot_flux_mjm2)
+
+## shift by percentage
+srad_fracshift <- srad_compare %>%
+    mutate(prism_most = prism_w * 0.3,
+         prism_little = prism_w * 0.7) %>%
+  mutate_at(c('prism_most'), list(lead), n = 1) %>%
+  mutate(prism_new = prism_most + prism_little,
+         diff_prismfrac = niwot_flux_mjm2 - prism_new) %>%
+  na.omit()
+
+scatter_srad_frac <- ggplot(srad_fracshift, aes(x=niwot_flux_mjm2, y=prism_new)) +
+  geom_point() +
+  geom_abline(intercept = 0, slope = 1, size=1.5, color="blue")
+
+ggplotly(scatter_srad_frac)
+#scatter_srad_frac
+
+summary(srad_fracshift)
+rmse(srad_fracshift$prism_new, srad_fracshift$niwot_flux_mjm2)
+pbias(srad_fracshift$prism_new, srad_fracshift$niwot_flux_mjm2)
+
+## bring in daymet
+## Daily total radiation (MJ/m2/day) can be calculated as follows: ((srad (W/m2) * dayl (s/day)) / l,000,000)
 niwot_daymet <- daym %>%
@@
          doy = 2,
-         srad_wm2 = 3)
+         srad_wm2 = 3) %>%
+  mutate(date = as.Date(doy),
+         month = month(date),
+         day = day(date),
+         date = make_date(year, month, day),
+         daymet_mjm2 = (srad_wm2 * 86400) / 1000000) %>%
+  dplyr::select(-c(year, doy, month, day))
+
+niwot_daymet_comp <- full_join(niwot_srad, niwot_daymet, by = 'date') %>%
+  dplyr::select(c(date, niwot_flux_mjm2, daymet_mjm2)) %>%
+  na.omit()
+
+scatter_srad_daymet <- ggplot(niwot_daymet_comp, aes(x=niwot_flux_mjm2, y=daymet_mjm2)) +
+  geom_point() +
+  geom_abline(intercept = 0, slope = 1, size=1.5, color="blue")
+
+ggplotly(scatter_srad_daymet)
+#scatter_srad_frac
+
+#summary(srad_fracshift)
+rmse(niwot_daymet_comp$daymet_mjm2, niwot_daymet_comp$niwot_flux_mjm2)
 

### 2022-09-13 fourmile_dataprocess.Rmd
precip and solar rad prism data ready to be shared

--- 2022-09-06 fourmile_dataprocess.Rmd
@@
 
-## Compare Niwot SNOTEL pirecip to prism pixel
+## Compare Niwot SNOTEL precip to prism pixel
 
-```{r}
+### Original prism and Niwot SNOTEL precip comaprison
+
+```{r, echo = F}
 niwot_prism <- read.csv(here('data', 'niwot_prism_compare.csv')) %>% 
@@
 
+#pbias(niwot_compare$prism_mm, niwot_compare$snotel_mm)
+
+scatter <- ggplot(niwot_compare, aes(x=snotel_mm, y=prism_mm)) +
+  geom_point() +
+  geom_abline(intercept = 0, slope = 1, size=1.5, color="blue") +
+  ggtitle('Prism vs. Niwot SNOTEL precip')
+
+ggplotly(scatter)
+
+rmse(niwot_compare$prism_mm, niwot_compare$snotel_mm)
+summary(niwot_compare$diff_mm)
+
 #filter to look at sept - june
-niwot_winter_comp <- niwot_compare %>%
-  mutate(month = month(date)) %>%
-  filter(!month %in% c(6:8))
+# niwot_winter_comp <- niwot_compare %>%
+#   mutate(month = month(date)) %>%
+#   filter(!month %in% c(6:8))
+# 
+# summary(niwot_winter_comp)
+```
 
-summary(niwot_winter_comp)
+### Prism shift 1 day and Niwot SNOTEL precip
 
+```{r, echo = F}
 niwot_prismshift <- niwot_compare %>%
@@
   mutate(month = month(date)) %>%
-  filter(!month %in% c(6:8)) %>%
-  mutate(diff_mm = snotel_mm - prism_mm)
+  #filter(!month %in% c(6:8)) %>%
+  mutate(diff_mm = snotel_mm - prism_mm) %>%
+  na.omit()
 
-summary(niwot_prismshift)
+#NSE(niwot_prismshift$prism_mm, niwot_prismshift$snotel_mm)
+#pbias(niwot_prismshift$prism_mm, niwot_prismshift$snotel_mm)
+
+scatter_shiftday <- ggplot(niwot_prismshift, aes(x=snotel_mm, y=prism_mm)) +
+  geom_point() +
+  geom_abline(intercept = 0, slope = 1, size=1.5, color="blue") +
+  ggtitle('Prism shift 1 day versus Niwot SNOTEL precip')
+
+ggplotly(scatter_shiftday)
+
+rmse(niwot_prismshift$prism_mm, niwot_prismshift$snotel_mm)
+summary(niwot_prismshift$diff_mm)
+```
+
+### Prism shift by fraction and Niwot SNOTEL precip
+
+```{r, echo = F}
+niwot_prismfrac <- niwot_compare %>%
+  mutate(prism_most_mm = prism_mm * 0.974,
+         prism_little_mm = prism_mm * 0.026) %>%
+  mutate_at(c('prism_most_mm'), list(lead), n = 1) %>%
+  mutate(prism_new_mm = prism_most_mm + prism_little_mm,
+         diff_prismfrac = snotel_mm - prism_new_mm) %>%
+  na.omit()
+
+scatter_frac <- ggplot(niwot_prismfrac, aes(x=snotel_mm, y=prism_new_mm)) +
+  geom_point() +
+  geom_abline(intercept = 0, slope = 1, size=1.5, color="blue") +
+  ggtitle('Prism shift by 97.4% and Niwot SNOTEL precip')
+
+ggplotly(scatter_frac)
+
+rmse(niwot_prismfrac$prism_new_mm, niwot_prismfrac$snotel_mm)
+summary(niwot_prismfrac$diff_prismfrac)
+#NSE(niwot_prismfrac$prism_new_mm, niwot_prismfrac$snotel_mm)
+#pbias(niwot_prismfrac$prism_new_mm, niwot_prismfrac$snotel_mm)
 
 ```
+
+## Compare prism solar rad to flux solar rad
+
+### Original Prism and Niwot flux tower solar rad
+
+```{r, echo = F}
+srad <- solr %>%
+  dplyr::select(-1) %>%
+  filter(!row_number() %in% c(1:17)) %>%
+  replace(.==-9999, NA) %>%
+  rename(date = 1,
+         prism_w = 2,
+         prism_m = 3,
+         prism_e = 4,
+         gordon_s = 5,
+         gordon_n = 6,
+         greenlake = 7) %>%
+  mutate(date = dmy(date))
+
+niwot_srad <- Niwo %>%
+  mutate(date = ymd(date)) %>%
+  rename(niwot_flux_mjm2 = 3) %>%
+  dplyr::select(-c(watts_per_m2)) %>%
+  replace(. == -9999, NA)
+
+## original  
+srad_compare <- full_join(srad, niwot_srad, by = 'date') %>%
+  dplyr::select(c(date, prism_w, niwot_flux_mjm2)) %>%
+  mutate(diff = niwot_flux_mjm2 - prism_w) %>%
+  na.omit()
+
+scatter_srad_orig <- ggplot(srad_compare, aes(x=niwot_flux_mjm2, y=prism_w)) +
+  geom_point() +
+  geom_abline(intercept = 0, slope = 1, size=1.5, color="blue") +
+  ggtitle('Prism versus Niwot flux tower solar rad')
+
+ggplotly(scatter_srad_orig)
+
+rmse(srad_compare$prism_w, srad_compare$niwot_flux_mjm2)
+summary(srad_compare$diff)
+```
+
+### Prism shift by 1 day versus Niwot flux tower solar rad
+
+```{r, echo = F}
+## 1 day shift
+srad_shift1day <- srad_compare %>%
+  mutate_at(c("prism_w"),list(lead), n = 1) %>%
+  na.omit() %>%
+  mutate(diff = niwot_flux_mjm2 - prism_w)
+
+scatter_srad_1day <- ggplot(srad_shift1day, aes(x=niwot_flux_mjm2, y=prism_w)) +
+  geom_point() +
+  geom_abline(intercept = 0, slope = 1, size=1.5, color="blue") +
+  ggtitle('Prism shift 1 day vs. Niwot flux tower solar rad')
+
+ggplotly(scatter_srad_1day)
+#scatter_srad_1day
+
+rmse(srad_shift1day$prism_w, srad_shift1day$niwot_flux_mjm2)
+summary(srad_shift1day$diff)
+#pbias(srad_shift1day$prism_w, srad_shift1day$niwot_flux_mjm2)
+```
+
+### Prism shift by fraction versus Niwot flux tower solar rad
+
+```{r, echo = F}
+## shift by percentage
+srad_fracshift <- srad_compare %>%
+    mutate(prism_most = prism_w * 0.3,
+         prism_little = prism_w * 0.7) %>%
+  mutate_at(c('prism_most'), list(lead), n = 1) %>%
+  mutate(prism_new = prism_most + prism_little,
+         diff_prismfrac = niwot_flux_mjm2 - prism_new) %>%
+  na.omit()
+
+scatter_srad_frac <- ggplot(srad_fracshift, aes(x=niwot_flux_mjm2, y=prism_new)) +
+  geom_point() +
+  geom_abline(intercept = 0, slope = 1, size=1.5, color="blue") +
+  ggtitle('Prism shift by 30% vs. Niwot flux tower solar rad')
+
+ggplotly(scatter_srad_frac)
+#scatter_srad_frac
+
+rmse(srad_fracshift$prism_new, srad_fracshift$niwot_flux_mjm2)
+summary(srad_fracshift$diff_prismfrac)
+#pbias(srad_fracshift$prism_new, srad_fracshift$niwot_flux_mjm2)
+```
+
+### Daymet (original) versus Niwot flux tower solar rad
+
+```{r, echo = F}
+## bring in daymet
+## Daily total radiation (MJ/m2/day) can be calculated as follows: ((srad (W/m2) * dayl (s/day)) / l,000,000)
+niwot_daymet <- daym %>%
+  filter(!row_number() %in% c(1:7)) %>%
+  rename(year = 1,
+         doy = 2,
+         srad_wm2 = 3) %>%
+  mutate(date = as.Date(doy),
+         month = month(date),
+         day = day(date),
+         date = make_date(year, month, day),
+         daymet_mjm2 = (srad_wm2 * 86400) / 1000000) %>%
+  dplyr::select(-c(year, doy, month, day))
+
+niwot_daymet_comp <- full_join(niwot_srad, niwot_daymet, by = 'date') %>%
+  dplyr::select(c(date, niwot_flux_mjm2, daymet_mjm2)) %>%
+  na.omit() %>%
+  mutate(diff = niwot_flux_mjm2 - daymet_mjm2)
+
+scatter_srad_daymet <- ggplot(niwot_daymet_comp, aes(x=niwot_flux_mjm2, y=daymet_mjm2)) +
+  geom_point() +
+  geom_abline(intercept = 0, slope = 1, size=1.5, color="blue") +
+  ggtitle('Daymet vs. Niwot flux tower solar rad')
+
+ggplotly(scatter_srad_daymet)
+#scatter_srad_frac
+
+#summary(srad_fracshift)
+rmse(niwot_daymet_comp$daymet_mjm2, niwot_daymet_comp$niwot_flux_mjm2)
+summary(niwot_daymet_comp$diff)
+```

### 2022-09-13 fourmile_dataprocess.Rmd
not sure what I updated

@@
 rmse(niwot_compare$prism_mm, niwot_compare$snotel_mm)
+bias(niwot_compare$snotel_mm, niwot_compare$prism_mm)
 summary(niwot_compare$diff_mm)
-
 #filter to look at sept - june
@@
 rmse(niwot_prismshift$prism_mm, niwot_prismshift$snotel_mm)
+bias(niwot_prismshift$snotel_mm, niwot_prismshift$prism_mm)
 summary(niwot_prismshift$diff_mm)
@@
 rmse(niwot_prismfrac$prism_new_mm, niwot_prismfrac$snotel_mm)
+bias(niwot_prismfrac$snotel_mm, niwot_prismfrac$prism_new_mm)
 summary(niwot_prismfrac$diff_prismfrac)
@@
 rmse(srad_compare$prism_w, srad_compare$niwot_flux_mjm2)
+bias(srad_compare$niwot_flux_mjm2, srad_compare$prism_w)
 summary(srad_compare$diff)
@@
 rmse(srad_shift1day$prism_w, srad_shift1day$niwot_flux_mjm2)
+bias(srad_shift1day$niwot_flux_mjm2, srad_shift1day$prism_w)
 summary(srad_shift1day$diff)
@@
 rmse(srad_fracshift$prism_new, srad_fracshift$niwot_flux_mjm2)
+bias(srad_fracshift$niwot_flux_mjm2, srad_fracshift$prism_new)
 summary(srad_fracshift$diff_prismfrac)
@@
 rmse(niwot_daymet_comp$daymet_mjm2, niwot_daymet_comp$niwot_flux_mjm2)
+bias(niwot_daymet_comp$niwot_flux_mjm2, niwot_daymet_comp$daymet_mjm2)
 summary(niwot_daymet_comp$diff)
+
 ```

### 2022-09-19 fourmile_dataprocess.Rmd
adding in solar rad gap filling

@@
 library(Metrics)
+library(ranger)
+library(missRanger)
 ```
@@
 summary(niwot_daymet_comp$diff)
+```
+
+### Solar rad gap filling
+
+```{r}
 

### 2022-09-20 fourmile_dataprocess.Rmd
solar rad gap filling done

@@
 library(missRanger)
+library(readxl)
 ```
@@
 
-```{r}
+```{r, echo=F}
+#bring in srad and niwot_srad
+srad_gapfil <- full_join(srad, niwot_srad) %>%
+  filter(date > '2009-12-31') %>%
+  dplyr::select(-c(prism_w, prism_m, prism_e))
+
+#bat <- read_xlsx('bat_srad.xlsx')
+#save.image(file = 'bat.RData')
+load('C:/Users/sears/Documents/Repos/fourmile/data/bat.RData')
+
+bet_day <- bat %>%
+  mutate(date = as.Date(datetime)) %>%
+  group_by(date) %>%
+  summarize(sw_in_avg_wm2= mean(in_swrad_wm2)) %>%
+  filter(date > '2009-12-31') %>%
+  mutate(bet_sw_in_mjm2 = (sw_in_avg_wm2 * 86400) / 1000000) %>%
+  dplyr::select(-c(sw_in_avg_wm2))
+
+srad_gapfil_all <- full_join(srad_gapfil, bet_day, by='date') %>%
+  filter(date < '2020-12-31') %>%
+  dplyr::select(-c(bet_sw_in_mjm2.x)) %>%
+  rename(bet_sw = bet_sw_in_mjm2.y)
+
+summary(srad_gapfil_all)
+
+srad_flip_nofill <- srad_gapfil %>%
+  pivot_longer(!date, names_to = 'site', values_to = 'sw_in_mjm2')
+
+srad_nofill <- ggplot(srad_flip_nofill, aes(x=date, y=sw_in_mjm2, color=site)) +
+  geom_line() +
+  ggtitle('Solar rad, no fill')
+
+ggplotly(srad_nofill)
+
+new_srad <- missRanger(srad_gapfil_all, num.trees=100)
+summary(new_srad)
+
+srad_flip_fill <- new_srad %>%
+  pivot_longer(!date, names_to = 'site', values_to = 'sw_in_mjm2')
+
+srad_filled <- ggplot(srad_flip_fill, aes(x=date, y=sw_in_mjm2, color=site)) +
+  geom_line() +
+  ggtitle('Solar rad, fill')
+
+ggplotly(srad_filled)
 

### 2022-09-20 fourmile_dataprocess.Rmd
added doy to missRanger data gaps

@@
   dplyr::select(-c(bet_sw_in_mjm2.x)) %>%
-  rename(bet_sw = bet_sw_in_mjm2.y)
+  rename(bet_sw = bet_sw_in_mjm2.y) %>%
+  mutate(doyh = yday(date))
 
@@
 
-new_srad <- missRanger(srad_gapfil_all, num.trees=100)
+new_srad <- missRanger(srad_gapfil_all, num.trees=100000)
 summary(new_srad)
@@
 srad_flip_fill <- new_srad %>%
+  dplyr::select(-c(doyh)) %>% 
   pivot_longer(!date, names_to = 'site', values_to = 'sw_in_mjm2')

### 2022-09-26 fourmile_inputs.Rmd
lots of R issues

---
title: "Fourmile_inputs"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_float: true
    theme: journal
editor_options: 
  chunk_output_type: console
---

```{r open package, include=FALSE}

knitr::opts_chunk$set(warning = FALSE, message = FALSE)

library(rmdformats)
library(tidyverse)
library(dplyr)
library(lubridate)
library(plotly)
library(ggplot2)
library(here)
library(scales)
library(here)
library(rgdal)
library(sp)
library(sf)
library(mapview)
library(kableExtra)
library(dataRetrieval)
library(raster)
library(sf)
library(stringr)
library(hydroGOF)
library(Metrics)
library(ranger)
library(missRanger)
library(readxl)

```

```{r loading data, include = F}

setwd('C:/Users/sears/Documents/Repos/fourmile/data/files_to_edit')

#pull in all filenames with csv
filenames <- list.files('.', pattern='.csv', full.names=F)

#read all the csvs
dataframes <- lapply(filenames, read_csv)

#name all the csv
names(dataframes) <- substr(filenames, 1, 4)

#extract csvs from list to global env
lapply(names(dataframes), function(x) assign(x, dataframes[[x]], envir = .GlobalEnv))
rm(dataframes)

```

### 2022-09-26 fourmile_inputs.Rmd
just need to finish precip

@@
 
+bet_srad <- read_xlsx('bet_srad.xlsx')
+updated_prec <- read_xlsx('updated_precip_2016to20.xlsx')
+bet_airt <- read_xlsx('bt_Met1.xlsx')
+bet_met <-read_xlsx('bt_Met2.xlsx')
+
 ```
+
+# RH first
+
+```{r}
+#need to bring in Niwot and Betasso and remove prism
+rh <- rhum %>%
+  mutate(date = dmy(date)) %>%
+  dplyr::select(-c(prism_W, prism_M, prism_E))
+
+niwot_rh <- nime %>%
+  mutate(date = make_date(Year, Month, Day)) %>%
+  dplyr::select(c(date, RH_21m)) %>%
+  rename(Niwot = RH_21m) %>%
+  filter(date > '2009-12-31') %>%
+  filter(date < '2021-01-01')
+
+bet_rh <- bet_met %>%
+  rename(rh = 1,
+    datetime = 2) %>%
+  dplyr::select(c(datetime, rh)) %>%
+  mutate(date = as.Date(datetime)) %>%
+  group_by(date) %>%
+  summarize(rh = mean(rh)) %>%
+  filter(date > '2009-12-31') %>%
+  filter(date < '2021-01-01') %>%
+  rename(Betasso = rh)
+
+rhall <- full_join(rh, niwot_rh, by = 'date')
+
+rhall <- full_join(rhall, bet_rh, by = 'date') %>% 
+  mutate(date = format(as.Date(date), '%d.%m.%Y')) %>%
+  replace(is.na(.), -9999)
+
+#rh done
+write.csv(rhall, 'rh_use.csv')
+
+```
+
+# wind
+
+```{r}
+wind <- wind %>%
+  mutate(date = dmy(date))
+
+niwot_wind <- nime %>%
+  mutate(date = make_date(Year, Month, Day)) %>%
+  dplyr::select(c(date, ws_21m)) %>%
+  rename(Niwot = ws_21m) %>%
+  filter(date > '2009-12-31') %>%
+  filter(date < '2021-01-01')
+
+bet_wind <- bet_met %>%
+  rename(windspeed = 3,
+    datetime = 4) %>%
+  dplyr::select(c(datetime, windspeed)) %>%
+  mutate(date = as.Date(datetime)) %>%
+  group_by(date) %>%
+  summarize(wind = mean(windspeed)) %>%
+  filter(date > '2009-12-31') %>%
+  filter(date < '2021-01-01') %>%
+  rename(Betasso = wind)
+
+windall <- full_join(wind, niwot_wind, by = 'date')
+
+windall <- full_join(windall, bet_wind, by = 'date') %>% 
+  mutate(date = format(as.Date(date), '%d.%m.%Y')) %>%
+  replace(is.na(.), -9999)
+
+write.csv(windall, 'wind_use.csv')
+
+```
+
+# Tmax
+
+```{r}
+tmax <- tmax %>%
+  mutate(date = dmy(date)) %>%
+  dplyr::select(-c(prism_W, prism_M, prism_E))
+
+bet_tmax <- bet_airt %>%
+    rename(tmax = 3,
+    datetime = 4) %>%
+  dplyr::select(c(datetime, tmax)) %>%
+  mutate(date = as.Date(datetime)) %>%
+  group_by(date) %>%
+  summarize(tmax = max(tmax)) %>%
+  filter(date > '2009-12-31') %>%
+  filter(date < '2021-01-01') %>%
+  rename(Betasso = tmax)
+
+tmaxall <- full_join(tmax, bet_tmax, by = 'date') %>%
+  mutate(date = format(as.Date(date), '%d.%m.%Y')) %>%
+  replace(is.na(.), -9999)
+
+write.csv(tmaxall, 'tmax_use.csv')
+
+```
+
+# Tmin
+
+```{r}
+tmin <- tmin %>%
+  mutate(date = dmy(date)) %>%
+  dplyr::select(-c(prism_W, prism_M, prism_E))
+
+bet_tmin <- bet_airt %>%
+    rename(tmin = 1,
+    datetime = 2) %>%
+  dplyr::select(c(datetime, tmin)) %>%
+  mutate(date = as.Date(datetime)) %>%
+  group_by(date) %>%
+  summarize(tmin = min(tmin)) %>%
+  filter(date > '2009-12-31') %>%
+  filter(date < '2021-01-01') %>%
+  rename(Betasso = tmin)
+
+tminall <- full_join(tmin, bet_tmin, by = 'date') %>%
+  mutate(date = format(as.Date(date), '%d.%m.%Y')) %>%
+  replace(is.na(.), -9999)
+
+write.csv(tminall, 'tmin_use.csv')
+
+```
+
+# Solar rad
+
+```{r}
+solar <- solr %>%
+  mutate(date = dmy(date)) %>%
+  dplyr::select(-c(prism_W, prism_M, prism_E))
+
+niwot_solar <- niwo %>%
+  dplyr::select(c(1, 3)) %>%
+  filter(date > '2009-12-31') %>%
+  filter(date < '2021-01-01') %>%
+  rename(Niwot = 2)
+
+bet_solar <- bet_srad %>%
+  mutate(date = as.Date(datetime)) %>%
+  group_by(date) %>%
+  summarize(sw_in_avg_wm2= mean(in_swrad_wm2)) %>%
+  filter(date > '2009-12-31') %>%
+  mutate(bet_sw_in_mjm2 = (sw_in_avg_wm2 * 86400) / 1000000) %>%
+  dplyr::select(-c(sw_in_avg_wm2)) %>%
+  rename(Betasso = bet_sw_in_mjm2)
+
+solarall <- full_join(solar, niwot_solar, by = 'date')
+
+solarall <- full_join(solarall, bet_solar, by = 'date') %>% 
+  mutate(date = format(as.Date(date), '%d.%m.%Y')) %>%
+  replace(is.na(.), -9999)
+
+write.csv(solarall, 'solar_use.csv')
+
+```
+
+# Precip
+
+```{r}
+
+#daily precip
+precall <- prec %>%
+  mutate(date = dmy(date),
+         doy = yday(date)) %>%
+  mutate_at(c('Gordon_South', 'Gordon_North',
+              'GH', 'LM', 'SE', 'SP', 'ST', 'NADP_SL'),
+            ~(ifelse(!doy %in% c(152:258),
+
+  mutate_at(c('prism_W', 'prism_M', 'prism_E'), ~(ifelse(doy %in% c(152:258),
+                                                         NA, .))) %>%
+  filter(date > '2009-12-31') %>%
+  dplyr::select(-c(doy)) %>%
+  mutate(date = format(as.Date(date), '%d.%m.%Y'))
+
+  mutate(prism_most_mm = prism_mm * 0.974,
+         prism_little_mm = prism_mm * 0.026) %>%
+  mutate_at(c('prism_most_mm'), list(lead), n = 1) %>%
+  mutate(prism_new_mm = prism_most_mm + prism_little_mm
+
+```

### 2022-09-27 fourmile_inputs.Rmd
still working on precip, everything else is ready

@@
             ~(ifelse(!doy %in% c(152:258),
-
+                               NA, .))) %>%
+  mutate(prism_most_w = prism_W * 0.974,
+         prism_little_w = prism_W * 0.026,
+         prism_most_m = prism_M * 0.974,
+         prism_little_m = prism_M * 0.026,
+         prism_most_e = prism_E * 0.974,
+         prism_little_e = prism_E * 0.026) %>%
+  mutate_at(c('prism_most_w', 'prism_most_m', 'prism_most_e'), list(lead), n = 1) %>%
+  mutate(prism_W = prism_most_w + prism_little_w,
+         prism_M = prism_most_m + prism_little_m,
+         prism_E = prism_most_e + prism_little_e) %>%
+  dplyr::select(-c(prism_most_w, prism_little_w,
+                   prism_most_m, prism_little_m,
+                   prism_most_e, prism_little_e)) %>%
   mutate_at(c('prism_W', 'prism_M', 'prism_E'), ~(ifelse(doy %in% c(152:258),
                                                          NA, .))) %>%
-  filter(date > '2009-12-31') %>%
-  dplyr::select(-c(doy)) %>%
-  mutate(date = format(as.Date(date), '%d.%m.%Y'))
+  filter(date > '2009-12-31')
 
-  mutate(prism_most_mm = prism_mm * 0.974,
-         prism_little_mm = prism_mm * 0.026) %>%
-  mutate_at(c('prism_most_mm'), list(lead), n = 1) %>%
-  mutate(prism_new_mm = prism_most_mm + prism_little_mm
+bet_rain <- bet_met %>%
+  dplyr::select(c(5,6)) %>%
+  rename(Betasso_rain =1) %>%
+  mutate(date = as.Date(DATE_TIME)) %>%
+  group_by(date) %>%
+  summarize(Betasso = sum(Betasso_rain)) %>%
+  filter(date > '2009-12-31')
+
+precall <- full_join(precall, bet_rain, by = 'date')
+
+updated_prec <- updated_prec %>%
+  mutate_at(c(2,4,6,8,10), ~(.*25.4)) %>%
+  rename(GH = 2,
+         LM = 4,
+         SE = 6,
+         SP = 8,
+         ST = 10)
+
+gh <- updated_prec %>%
+  dplyr::select(c(1,2)) %>%
+  mutate(date = mdy(GH_date)) %>%
+  dplyr::select(-c(1)) %>%
+  distinct(date, .keep_all = TRUE)
+
+lm <- updated_prec %>%
+  dplyr::select(c(3,4)) %>%
+  mutate(date = mdy(LM_date)) %>%
+  dplyr::select(-c(1)) %>%
+  distinct(date, .keep_all = TRUE)
+
+se <- updated_prec %>%
+  dplyr::select(c(5,6)) %>%
+  mutate(date = mdy(SE_date)) %>%
+  dplyr::select(-c(1)) %>%
+  distinct(date, .keep_all = TRUE)
+
+sp <- updated_prec %>%
+  dplyr::select(c(7,8)) %>%
+  mutate(date = mdy(SP_date)) %>%
+  dplyr::select(-c(1)) %>%
+  distinct(date, .keep_all = TRUE)
+
+st <- updated_prec %>%
+  dplyr::select(c(9,10)) %>%
+  mutate(date = mdy(ST_date)) %>%
+  dplyr::select(-c(1)) %>%
+  distinct(date, .keep_all = TRUE)
+
+write.csv(gh, 'gh.csv')
+write.csv(lm, 'lm.csv')
+write.csv(se, 'se.csv')
+write.csv(sp, 'sp.csv')
+write.csv(st, 'st.csv')
+
+write.csv(precall, 'precall_fix.csv')
+
+# mutate(date = format(as.Date(date), '%d.%m.%Y')) %>%
+#   replace(is.na(.), -9999) %>%
+#   dplyr::select(-c(doy))
 

### 2022-09-30 fourmile_inputs.Rmd
finished input files

@@
   dplyr::select(c(5,6)) %>%
-  rename(Betasso_rain =1) %>%
+  rename(Betasso_rain = 1) %>%
   mutate(date = as.Date(DATE_TIME)) %>%
@@
 
-updated_prec <- updated_prec %>%
+updated_prec1 <- updated_prec %>%
+  mutate_at(c(2,4,6,8,10), ~(ifelse(. > 7, NA, .))) %>%
   mutate_at(c(2,4,6,8,10), ~(.*25.4)) %>%
@@
 
-gh <- updated_prec %>%
+gh <- updated_prec1 %>%
   dplyr::select(c(1,2)) %>%
@@
   dplyr::select(-c(1)) %>%
+  distinct(date, .keep_all = TRUE) %>%
+  arrange(date)
+
+gh_old <- precall %>%
+  dplyr::select(c(date, GH)) %>%
+  filter(date < '2016-01-01') %>%
+  bind_rows(gh_old, gh) %>%
   distinct(date, .keep_all = TRUE)
 
-lm <- updated_prec %>%
+precall <- precall %>%
+  dplyr::select(-c(GH))
+
+precall <- full_join(precall, gh_old, by='date')
+
+lm <- updated_prec1 %>%
   dplyr::select(c(3,4)) %>%
@@
   dplyr::select(-c(1)) %>%
+  distinct(date, .keep_all = TRUE) %>%
+  arrange(date)
+
+lm_old <- precall %>%
+  dplyr::select(c(date, LM)) %>%
+  filter(date < '2016-01-01')
+
+lm_old <- bind_rows(lm_old, lm) %>%
   distinct(date, .keep_all = TRUE)
 
-se <- updated_prec %>%
+precall <- precall %>%
+  dplyr::select(-c(LM))
+
+precall <- full_join(precall, lm_old, by='date')
+
+se <- updated_prec1 %>%
   dplyr::select(c(5,6)) %>%
@@
   dplyr::select(-c(1)) %>%
+  distinct(date, .keep_all = TRUE) %>%
+  arrange(date)
+
+se_old <- precall %>%
+  dplyr::select(c(date, SE)) %>%
+  filter(date < '2016-01-01')
+
+se_old <- bind_rows(se_old, se) %>%
   distinct(date, .keep_all = TRUE)
 
-sp <- updated_prec %>%
+precall <- precall %>%
+  dplyr::select(-c(SE))
+
+precall <- full_join(precall, se_old, by='date')
+
+sp <- updated_prec1 %>%
   dplyr::select(c(7,8)) %>%
@@
   dplyr::select(-c(1)) %>%
+  distinct(date, .keep_all = TRUE) %>%
+  arrange(date)
+
+sp_old <- precall %>%
+  dplyr::select(c(date, SP)) %>%
+  filter(date < '2016-01-01')
+
+sp_old <- bind_rows(sp_old, sp) %>%
   distinct(date, .keep_all = TRUE)
 
-st <- updated_prec %>%
+precall <- precall %>%
+  dplyr::select(-c(SP))
+
+precall <- full_join(precall, sp_old, by='date')
+
+st <- updated_prec1 %>%
   dplyr::select(c(9,10)) %>%
@@
   dplyr::select(-c(1)) %>%
+  distinct(date, .keep_all = TRUE) %>%
+  arrange(date)
+
+st_old <- precall %>%
+  dplyr::select(c(date, ST)) %>%
+  filter(date < '2016-01-01')
+
+st_old <- bind_rows(st_old, st) %>%
   distinct(date, .keep_all = TRUE)
 
-write.csv(gh, 'gh.csv')
-write.csv(lm, 'lm.csv')
-write.csv(se, 'se.csv')
-write.csv(sp, 'sp.csv')
-write.csv(st, 'st.csv')
+precall <- precall %>%
+  dplyr::select(-c(ST))
 
-write.csv(precall, 'precall_fix.csv')
+precall <- full_join(precall, st_old, by='date')
 
+prec_final <- precall %>%
+  mutate_at(c('GH', 'LM', 'SE', 'SP', 'ST'),
+            ~(ifelse(!doy %in% c(152:258),
+                               NA, .))) %>%
+  filter(date < '2021-01-01') %>%
+  mutate(date = format(as.Date(date), '%d.%m.%Y')) %>%
+  dplyr::select(-c(doy))
+
+write.csv(prec_final, 'prec_use.csv')
+
+#check the date range, make sure tip bucekts are being used at right times
 # mutate(date = format(as.Date(date), '%d.%m.%Y')) %>%

### 2022-10-03 fourmile_inputs.Rmd
added updated solar gap filling

@@
 #rh done
-write.csv(rhall, 'rh_use.csv')
+#write.csv(rhall, 'rh_use.csv')
 
@@
 
-write.csv(windall, 'wind_use.csv')
+#write.csv(windall, 'wind_use.csv')
 
@@
 
-write.csv(tmaxall, 'tmax_use.csv')
+#write.csv(tmaxall, 'tmax_use.csv')
 
@@
 
-#check the date range, make sure tip bucekts are being used at right times
-# mutate(date = format(as.Date(date), '%d.%m.%Y')) %>%
-#   replace(is.na(.), -9999) %>%
-#   dplyr::select(-c(doy))
+```
+
+# combine all met data together
+
+```{r}
+
+wind <- read_csv('wind_use.csv')
+sol <- read_csv('solar_use.csv')
+tmin <- read_csv('tmin_use.csv')
+tmax <- read_csv('tmax_use.csv')
+prec <- read_csv('prec_use.csv')
+rh <- read_csv('rh_use.csv')
+
+#put all data frames into list
+df_list <- list(prec, sol, tmin, tmax, wind, rh)
+
+#merge all data frames in list
+met_all <- df_list %>% 
+  reduce(full_join, by='date')
+
+met_all <- met_all %>%  
+  mutate(date = dmy(date),
+         doy = yday(date)) %>%
+  replace(.==-9999, NA) %>%
+  filter(date > '2009-12-31')
+
+met_fill <- missRanger(met_all, num.trees=1000)
+
+solar <- ggplot(met_fill, aes(x=date)) +
+  geom_line(aes(y=Gordon_S_mjm2), color='blue') +
+  geom_line(aes(y=Niwot_mjm2), color='red') +
+  geom_line(aes(y=Betasso_mjm2), color='orange')
+
+ggplotly(solar)
 

### 2022-10-04 fourmile_inputs.Rmd
finished solar rad gap filling, almost done w/ runoff ratios

@@
 ```
+
+# Runoff ratios
+
+```{r}
+prec_runoff <- read_csv('prec_runoff.csv')
+
+ratios_prep <- prec_runoff %>%
+  mutate(prec_12 = hru5 + hru6,
+         prec_13 = hru3 + hru11,
+         prec_10 = hru1 + hru2 + hru8 + hru9 + hru4,
+         prec_11 = hru7 + hru10,
+         date = dmy(time)) %>%
+  dplyr::select(c(date, prec_12, prec_13, prec_10, prec_11,
+                  reach10_cms, reach11_cms, reach12_cms, reach13_cms)) %>%
+  mutate_at(c('prec_12', 'prec_13', 'prec_10', 'prec_11'), ~(./1000)) %>%
+  mutate_at(c('reach10_cms', 'reach11_cms', 'reach12_cms', 'reach13_cms'), ~(.*86400)) %>%
+  mutate(prec_12_cms = prec_12 * (14378900+16275100),
+         prec_13_cms = prec_13 * (),
+         prec_10_cms = prec_10 * (),
+         prec_11_cms = prec_11 * ())
+
+```

### 2022-10-04 fourmile_inputs.Rmd
add in areas for HRUs

--- 2022-10-03 fourmile_inputs.Rmd
@@
 ```
+
+# Runoff ratios
+
+```{r}
+prec_runoff <- read_csv('prec_runoff.csv')
+
+ratios_prep <- prec_runoff %>%
+  mutate(prec_12 = hru5 + hru6,
+         prec_13 = hru3 + hru11,
+         prec_10 = hru1 + hru2 + hru8 + hru9 + hru4,
+         prec_11 = hru7 + hru10,
+         date = dmy(time)) %>%
+  dplyr::select(c(date, prec_12, prec_13, prec_10, prec_11,
+                  reach10_cms, reach11_cms, reach12_cms, reach13_cms)) %>%
+  mutate_at(c('prec_12', 'prec_13', 'prec_10', 'prec_11'), ~(./1000)) %>%
+  # mutate_at(c('reach10_cms', 'reach11_cms', 'reach12_cms', 'reach13_cms'), ~(.*86400)) %>%
+  # mutate(prec_12_cms = prec_12 * (14378900+16275100),
+  #        prec_13_cms = prec_13 * (),
+  #        prec_10_cms = prec_10 * (),
+  #        prec_11_cms = prec_11 * ())
+
+```

### 2022-10-09 fourmile_inputs.Rmd
got precip prism shift for cals, moved runoff ratios to data process Rmd

--- 2022-10-03 fourmile_inputs.Rmd
@@
 
+#####################################################################
+#get prism shift only for precip (for year round)
+prec_orig <- read_csv('precipAll.csv')
+
+prec_prismshift <- prec_orig %>%
+  dplyr::select(c(date, prism_W, prism_M, prism_E)) %>%
+  mutate(date = dmy(date)) %>%
+  mutate(prism_most_w = prism_W * 0.974,
+         prism_little_w = prism_W * 0.026,
+         prism_most_m = prism_M * 0.974,
+         prism_little_m = prism_M * 0.026,
+         prism_most_e = prism_E * 0.974,
+         prism_little_e = prism_E * 0.026) %>%
+  mutate_at(c('prism_most_w', 'prism_most_m', 'prism_most_e'), list(lead), n = 1) %>%
+  mutate(prism_W = prism_most_w + prism_little_w,
+         prism_M = prism_most_m + prism_little_m,
+         prism_E = prism_most_e + prism_little_e) %>%
+  dplyr::select(-c(prism_most_w, prism_little_w,
+                   prism_most_m, prism_little_m,
+                   prism_most_e, prism_little_e)) %>%
+  filter(date > '2009-12-31') %>%
+  mutate(date = format(as.Date(date), '%d.%m.%Y'))
+
+write.csv(prec_prismshift, 'precip_prismshift.csv')
+#####################################################
+
 bet_rain <- bet_met %>%

### 2022-10-09 fourmile_dataprocess.Rmd
added runoff ratios by WY

--- 2022-09-19 fourmile_dataprocess.Rmd
@@
 #daily precip
-prec_update <- prec %>%
-  mutate(date = dmy(date),
-         doy = yday(date)) %>%
-  mutate_at(c('Gordon_South', 'Gordon_North',
-              'GH', 'LM', 'SE', 'SP', 'ST', 'NADP_SL'),
-            ~(ifelse(!doy %in% c(152:258), 
-                               NA, .))) %>%
-  mutate_at(c('prism_W', 'prism_M', 'prism_E'), list(lead), n = 1) %>%
-  mutate_at(c('prism_W', 'prism_M', 'prism_E'), ~(ifelse(doy %in% c(152:258),
-                                                         NA, .))) %>%
-  filter(date > '2009-12-31') %>%
-  dplyr::select(-c(doy)) %>%
-  mutate(date = format(as.Date(date), '%d.%m.%Y'))
-
-#write_csv(prec_update, 'precipAll_update.csv')
-
-daily_p <- prec %>%
-  mutate(date = dmy(date)) %>%
-  replace(.==-9999, NA) %>%
-  pivot_longer(!date, names_to = 'site', values_to = 'precip_mm') %>%
-  mutate(precip_mm = as.numeric(precip_mm)) %>%
-  mutate(WY = calcWaterYear(date)) %>%
-  group_by(WY, site) %>%
-  mutate(dailyp_cum_mm = cumsum(precip_mm))
-
-precip <- ggplot(daily_p, aes(x=date, y=precip_mm, color=site)) + geom_line()  +
-  theme_bw() +
-  ggtitle('Daily precip (all)')
-
-ggplotly(precip)
-
-precip_cumu <- ggplot(daily_p, aes(x=date, y=dailyp_cum_mm, color=site)) + geom_line()  +
-  theme_bw() +
-  ggtitle('Daily precip cumulative sums (all)')
-
-ggplotly(precip_cumu)
+# prec_update <- prec %>%
+#   mutate(date = dmy(date),
+#          doy = yday(date)) %>%
+#   mutate_at(c('Gordon_South', 'Gordon_North',
+#               'GH', 'LM', 'SE', 'SP', 'ST', 'NADP_SL'),
+#             ~(ifelse(!doy %in% c(152:258), 
+#                                NA, .))) %>%
+#   mutate_at(c('prism_W', 'prism_M', 'prism_E'), list(lead), n = 1) %>%
+#   mutate_at(c('prism_W', 'prism_M', 'prism_E'), ~(ifelse(doy %in% c(152:258),
+#                                                          NA, .))) %>%
+#   filter(date > '2009-12-31') %>%
+#   dplyr::select(-c(doy)) %>%
+#   mutate(date = format(as.Date(date), '%d.%m.%Y'))
+# 
+# #write_csv(prec_update, 'precipAll_update.csv')
+# 
+# daily_p <- prec %>%
+#   mutate(date = dmy(date)) %>%
+#   replace(.==-9999, NA) %>%
+#   pivot_longer(!date, names_to = 'site', values_to = 'precip_mm') %>%
+#   mutate(precip_mm = as.numeric(precip_mm)) %>%
+#   mutate(WY = calcWaterYear(date)) %>%
+#   group_by(WY, site) %>%
+#   mutate(dailyp_cum_mm = cumsum(precip_mm))
+# 
+# precip <- ggplot(daily_p, aes(x=date, y=precip_mm, color=site)) + geom_line()  +
+#   theme_bw() +
+#   ggtitle('Daily precip (all)')
+# 
+# ggplotly(precip)
+# 
+# precip_cumu <- ggplot(daily_p, aes(x=date, y=dailyp_cum_mm, color=site)) + geom_line()  +
+#   theme_bw() +
+#   ggtitle('Daily precip cumulative sums (all)')
+# 
+# ggplotly(precip_cumu)
 
@@
 ```{r, echo = F}
-niwot_prism <- read.csv(here('data', 'niwot_prism_compare.csv')) %>% 
-  filter(!row_number() %in% c(1:10)) %>%
-   rename(date = 1,
-          prism_mm = 2) %>%
-   mutate(date = ymd(date),
-          prism_mm = as.numeric(prism_mm))
-
-niwot_snotel <- prec_update %>%
-  dplyr::select(c(date, Niwot_Snotel)) %>%
-  rename(snotel_mm = Niwot_Snotel) %>%
-  mutate(date = dmy(date))
-
-niwot_compare <- full_join(niwot_prism, niwot_snotel, by = 'date')
-
-niwot_compare <- niwot_compare %>%
-  mutate(diff_mm = snotel_mm - prism_mm) %>%
-  na.omit()
-
-#pbias(niwot_compare$prism_mm, niwot_compare$snotel_mm)
-
-scatter <- ggplot(niwot_compare, aes(x=snotel_mm, y=prism_mm)) +
-  geom_point() +
-  geom_abline(intercept = 0, slope = 1, size=1.5, color="blue") +
-  ggtitle('Prism vs. Niwot SNOTEL precip')
-
-ggplotly(scatter)
-
-rmse(niwot_compare$prism_mm, niwot_compare$snotel_mm)
-bias(niwot_compare$snotel_mm, niwot_compare$prism_mm)
-summary(niwot_compare$diff_mm)
-#filter to look at sept - june
+# niwot_prism <- read.csv(here('data', 'niwot_prism_compare.csv')) %>% 
+#   filter(!row_number() %in% c(1:10)) %>%
+#    rename(date = 1,
+#           prism_mm = 2) %>%
+#    mutate(date = ymd(date),
+#           prism_mm = as.numeric(prism_mm))
+# 
+# niwot_snotel <- prec_update %>%
+#   dplyr::select(c(date, Niwot_Snotel)) %>%
+#   rename(snotel_mm = Niwot_Snotel) %>%
+#   mutate(date = dmy(date))
+# 
+# niwot_compare <- full_join(niwot_prism, niwot_snotel, by = 'date')
+# 
+# niwot_compare <- niwot_compare %>%
+#   mutate(diff_mm = snotel_mm - prism_mm) %>%
+#   na.omit()
+# 
+# #pbias(niwot_compare$prism_mm, niwot_compare$snotel_mm)
+# 
+# scatter <- ggplot(niwot_compare, aes(x=snotel_mm, y=prism_mm)) +
+#   geom_point() +
+#   geom_abline(intercept = 0, slope = 1, size=1.5, color="blue") +
+#   ggtitle('Prism vs. Niwot SNOTEL precip')
+#   
+# ggplotly(scatter)
+# 
+# rmse(niwot_compare$prism_mm, niwot_compare$snotel_mm)
+# bias(niwot_compare$snotel_mm, niwot_compare$prism_mm)
+# summary(niwot_compare$diff_mm)
+# #filter to look at sept - june
 # niwot_winter_comp <- niwot_compare %>%
@@
 ```{r, echo = F}
-niwot_prismshift <- niwot_compare %>%
-  mutate_at(c("prism_mm"), funs(lead), n = 1) %>%
-  mutate(month = month(date)) %>%
-  #filter(!month %in% c(6:8)) %>%
-  mutate(diff_mm = snotel_mm - prism_mm) %>%
-  na.omit()
-
-#NSE(niwot_prismshift$prism_mm, niwot_prismshift$snotel_mm)
-#pbias(niwot_prismshift$prism_mm, niwot_prismshift$snotel_mm)
-
-scatter_shiftday <- ggplot(niwot_prismshift, aes(x=snotel_mm, y=prism_mm)) +
-  geom_point() +
-  geom_abline(intercept = 0, slope = 1, size=1.5, color="blue") +
-  ggtitle('Prism shift 1 day versus Niwot SNOTEL precip')
-
-ggplotly(scatter_shiftday)
-
-rmse(niwot_prismshift$prism_mm, niwot_prismshift$snotel_mm)
-bias(niwot_prismshift$snotel_mm, niwot_prismshift$prism_mm)
-summary(niwot_prismshift$diff_mm)
+# niwot_prismshift <- niwot_compare %>%
+#   mutate_at(c("prism_mm"), funs(lead), n = 1) %>%
+#   mutate(month = month(date)) %>%
+#   #filter(!month %in% c(6:8)) %>%
+#   mutate(diff_mm = snotel_mm - prism_mm) %>%
+#   na.omit()
+# 
+# #NSE(niwot_prismshift$prism_mm, niwot_prismshift$snotel_mm)
+# #pbias(niwot_prismshift$prism_mm, niwot_prismshift$snotel_mm)
+# 
+# scatter_shiftday <- ggplot(niwot_prismshift, aes(x=snotel_mm, y=prism_mm)) +
+#   geom_point() +
+#   geom_abline(intercept = 0, slope = 1, size=1.5, color="blue") +
+#   ggtitle('Prism shift 1 day versus Niwot SNOTEL precip')
+#   
+# ggplotly(scatter_shiftday)
+# 
+# rmse(niwot_prismshift$prism_mm, niwot_prismshift$snotel_mm)
+# bias(niwot_prismshift$snotel_mm, niwot_prismshift$prism_mm)
+# summary(niwot_prismshift$diff_mm)
 ```
@@
 ```{r, echo = F}
-niwot_prismfrac <- niwot_compare %>%
-  mutate(prism_most_mm = prism_mm * 0.974,
-         prism_little_mm = prism_mm * 0.026) %>%
-  mutate_at(c('prism_most_mm'), list(lead), n = 1) %>%
-  mutate(prism_new_mm = prism_most_mm + prism_little_mm,
-         diff_prismfrac = snotel_mm - prism_new_mm) %>%
-  na.omit()
-
-scatter_frac <- ggplot(niwot_prismfrac, aes(x=snotel_mm, y=prism_new_mm)) +
-  geom_point() +
-  geom_abline(intercept = 0, slope = 1, size=1.5, color="blue") +
-  ggtitle('Prism shift by 97.4% and Niwot SNOTEL precip')
-
-ggplotly(scatter_frac)
-
-rmse(niwot_prismfrac$prism_new_mm, niwot_prismfrac$snotel_mm)
-bias(niwot_prismfrac$snotel_mm, niwot_prismfrac$prism_new_mm)
-summary(niwot_prismfrac$diff_prismfrac)
+# niwot_prismfrac <- niwot_compare %>%
+#   mutate(prism_most_mm = prism_mm * 0.974,
+#          prism_little_mm = prism_mm * 0.026) %>%
+#   mutate_at(c('prism_most_mm'), list(lead), n = 1) %>%
+#   mutate(prism_new_mm = prism_most_mm + prism_little_mm,
+#          diff_prismfrac = snotel_mm - prism_new_mm) %>%
+#   na.omit()
+# 
+# scatter_frac <- ggplot(niwot_prismfrac, aes(x=snotel_mm, y=prism_new_mm)) +
+#   geom_point() +
+#   geom_abline(intercept = 0, slope = 1, size=1.5, color="blue") +
+#   ggtitle('Prism shift by 97.4% and Niwot SNOTEL precip')
+#   
+# ggplotly(scatter_frac)
+# 
+# rmse(niwot_prismfrac$prism_new_mm, niwot_prismfrac$snotel_mm)
+# bias(niwot_prismfrac$snotel_mm, niwot_prismfrac$prism_new_mm)
+# summary(niwot_prismfrac$diff_prismfrac)
 #NSE(niwot_prismfrac$prism_new_mm, niwot_prismfrac$snotel_mm)
@@
 ```{r, echo = F}
-srad <- solr %>%
-  dplyr::select(-1) %>%
-  filter(!row_number() %in% c(1:17)) %>%
-  replace(.==-9999, NA) %>%
-  rename(date = 1,
-         prism_w = 2,
-         prism_m = 3,
-         prism_e = 4,
-         gordon_s = 5,
-         gordon_n = 6,
-         greenlake = 7) %>%
-  mutate(date = dmy(date))
-
-niwot_srad <- Niwo %>%
-  mutate(date = ymd(date)) %>%
-  rename(niwot_flux_mjm2 = 3) %>%
-  dplyr::select(-c(watts_per_m2)) %>%
-  replace(. == -9999, NA)
-
-## original  
-srad_compare <- full_join(srad, niwot_srad, by = 'date') %>%
-  dplyr::select(c(date, prism_w, niwot_flux_mjm2)) %>%
-  mutate(diff = niwot_flux_mjm2 - prism_w) %>%
-  na.omit()
-
-scatter_srad_orig <- ggplot(srad_compare, aes(x=niwot_flux_mjm2, y=prism_w)) +
-  geom_point() +
-  geom_abline(intercept = 0, slope = 1, size=1.5, color="blue") +
-  ggtitle('Prism versus Niwot flux tower solar rad')
-
-ggplotly(scatter_srad_orig)
-
-rmse(srad_compare$prism_w, srad_compare$niwot_flux_mjm2)
-bias(srad_compare$niwot_flux_mjm2, srad_compare$prism_w)
-summary(srad_compare$diff)
+# srad <- solr %>%
+#   dplyr::select(-1) %>%
+#   filter(!row_number() %in% c(1:17)) %>%
+#   replace(.==-9999, NA) %>%
+#   rename(date = 1,
+#          prism_w = 2,
+#          prism_m = 3,
+#          prism_e = 4,
+#          gordon_s = 5,
+#          gordon_n = 6,
+#          greenlake = 7) %>%
+#   mutate(date = dmy(date))
+# 
+# niwot_srad <- Niwo %>%
+#   mutate(date = ymd(date)) %>%
+#   rename(niwot_flux_mjm2 = 3) %>%
+#   dplyr::select(-c(watts_per_m2)) %>%
+#   replace(. == -9999, NA)
+# 
+# ## original  
+# srad_compare <- full_join(srad, niwot_srad, by = 'date') %>%
+#   dplyr::select(c(date, prism_w, niwot_flux_mjm2)) %>%
+#   mutate(diff = niwot_flux_mjm2 - prism_w) %>%
+#   na.omit()
+# 
+# scatter_srad_orig <- ggplot(srad_compare, aes(x=niwot_flux_mjm2, y=prism_w)) +
+#   geom_point() +
+#   geom_abline(intercept = 0, slope = 1, size=1.5, color="blue") +
+#   ggtitle('Prism versus Niwot flux tower solar rad')
+#   
+# ggplotly(scatter_srad_orig)
+# 
+# rmse(srad_compare$prism_w, srad_compare$niwot_flux_mjm2)
+# bias(srad_compare$niwot_flux_mjm2, srad_compare$prism_w)
+# summary(srad_compare$diff)
 ```
@@
 ## 1 day shift
-srad_shift1day <- srad_compare %>%
-  mutate_at(c("prism_w"),list(lead), n = 1) %>%
-  na.omit() %>%
-  mutate(diff = niwot_flux_mjm2 - prism_w)
-
-scatter_srad_1day <- ggplot(srad_shift1day, aes(x=niwot_flux_mjm2, y=prism_w)) +
-  geom_point() +
-  geom_abline(intercept = 0, slope = 1, size=1.5, color="blue") +
-  ggtitle('Prism shift 1 day vs. Niwot flux tower solar rad')
-
-ggplotly(scatter_srad_1day)
-#scatter_srad_1day
-
-rmse(srad_shift1day$prism_w, srad_shift1day$niwot_flux_mjm2)
-bias(srad_shift1day$niwot_flux_mjm2, srad_shift1day$prism_w)
-summary(srad_shift1day$diff)
+# srad_shift1day <- srad_compare %>%
+#   mutate_at(c("prism_w"),list(lead), n = 1) %>%
+#   na.omit() %>%
+#   mutate(diff = niwot_flux_mjm2 - prism_w)
+# 
+# scatter_srad_1day <- ggplot(srad_shift1day, aes(x=niwot_flux_mjm2, y=prism_w)) +
+#   geom_point() +
+#   geom_abline(intercept = 0, slope = 1, size=1.5, color="blue") +
+#   ggtitle('Prism shift 1 day vs. Niwot flux tower solar rad')
+#   
+# ggplotly(scatter_srad_1day)
+# #scatter_srad_1day
+# 
+# rmse(srad_shift1day$prism_w, srad_shift1day$niwot_flux_mjm2)
+# bias(srad_shift1day$niwot_flux_mjm2, srad_shift1day$prism_w)
+# summary(srad_shift1day$diff)
 #pbias(srad_shift1day$prism_w, srad_shift1day$niwot_flux_mjm2)
@@
 ## shift by percentage
-srad_fracshift <- srad_compare %>%
-    mutate(prism_most = prism_w * 0.3,
-         prism_little = prism_w * 0.7) %>%
-  mutate_at(c('prism_most'), list(lead), n = 1) %>%
-  mutate(prism_new = prism_most + prism_little,
-         diff_prismfrac = niwot_flux_mjm2 - prism_new) %>%
-  na.omit()
-
-scatter_srad_frac <- ggplot(srad_fracshift, aes(x=niwot_flux_mjm2, y=prism_new)) +
-  geom_point() +
-  geom_abline(intercept = 0, slope = 1, size=1.5, color="blue") +
-  ggtitle('Prism shift by 30% vs. Niwot flux tower solar rad')
-
-ggplotly(scatter_srad_frac)
-#scatter_srad_frac
-
-rmse(srad_fracshift$prism_new, srad_fracshift$niwot_flux_mjm2)
-bias(srad_fracshift$niwot_flux_mjm2, srad_fracshift$prism_new)
-summary(srad_fracshift$diff_prismfrac)
+# srad_fracshift <- srad_compare %>%
+#     mutate(prism_most = prism_w * 0.3,
+#          prism_little = prism_w * 0.7) %>%
+#   mutate_at(c('prism_most'), list(lead), n = 1) %>%
+#   mutate(prism_new = prism_most + prism_little,
+#          diff_prismfrac = niwot_flux_mjm2 - prism_new) %>%
+#   na.omit()
+#   
+# scatter_srad_frac <- ggplot(srad_fracshift, aes(x=niwot_flux_mjm2, y=prism_new)) +
+#   geom_point() +
+#   geom_abline(intercept = 0, slope = 1, size=1.5, color="blue") +
+#   ggtitle('Prism shift by 30% vs. Niwot flux tower solar rad')
+#   
+# ggplotly(scatter_srad_frac)
+# #scatter_srad_frac
+# 
+# rmse(srad_fracshift$prism_new, srad_fracshift$niwot_flux_mjm2)
+# bias(srad_fracshift$niwot_flux_mjm2, srad_fracshift$prism_new)
+# summary(srad_fracshift$diff_prismfrac)
 #pbias(srad_fracshift$prism_new, srad_fracshift$niwot_flux_mjm2)
@@
 ## Daily total radiation (MJ/m2/day) can be calculated as follows: ((srad (W/m2) * dayl (s/day)) / l,000,000)
-niwot_daymet <- daym %>%
-  filter(!row_number() %in% c(1:7)) %>%
-  rename(year = 1,
-         doy = 2,
-         srad_wm2 = 3) %>%
-  mutate(date = as.Date(doy),
-         month = month(date),
-         day = day(date),
-         date = make_date(year, month, day),
-         daymet_mjm2 = (srad_wm2 * 86400) / 1000000) %>%
-  dplyr::select(-c(year, doy, month, day))
-
-niwot_daymet_comp <- full_join(niwot_srad, niwot_daymet, by = 'date') %>%
-  dplyr::select(c(date, niwot_flux_mjm2, daymet_mjm2)) %>%
-  na.omit() %>%
-  mutate(diff = niwot_flux_mjm2 - daymet_mjm2)
-
-scatter_srad_daymet <- ggplot(niwot_daymet_comp, aes(x=niwot_flux_mjm2, y=daymet_mjm2)) +
-  geom_point() +
-  geom_abline(intercept = 0, slope = 1, size=1.5, color="blue") +
-  ggtitle('Daymet vs. Niwot flux tower solar rad')
-
-ggplotly(scatter_srad_daymet)
-#scatter_srad_frac
-
-#summary(srad_fracshift)
-rmse(niwot_daymet_comp$daymet_mjm2, niwot_daymet_comp$niwot_flux_mjm2)
-bias(niwot_daymet_comp$niwot_flux_mjm2, niwot_daymet_comp$daymet_mjm2)
-summary(niwot_daymet_comp$diff)
+# niwot_daymet <- daym %>%
+#   filter(!row_number() %in% c(1:7)) %>%
+#   rename(year = 1,
+#          doy = 2,
+#          srad_wm2 = 3) %>%
+#   mutate(date = as.Date(doy),
+#          month = month(date),
+#          day = day(date),
+#          date = make_date(year, month, day),
+#          daymet_mjm2 = (srad_wm2 * 86400) / 1000000) %>%
+#   dplyr::select(-c(year, doy, month, day))
+#   
+# niwot_daymet_comp <- full_join(niwot_srad, niwot_daymet, by = 'date') %>%
+#   dplyr::select(c(date, niwot_flux_mjm2, daymet_mjm2)) %>%
+#   na.omit() %>%
+#   mutate(diff = niwot_flux_mjm2 - daymet_mjm2)
+#   
+# scatter_srad_daymet <- ggplot(niwot_daymet_comp, aes(x=niwot_flux_mjm2, y=daymet_mjm2)) +
+#   geom_point() +
+#   geom_abline(intercept = 0, slope = 1, size=1.5, color="blue") +
+#   ggtitle('Daymet vs. Niwot flux tower solar rad')
+#   
+# ggplotly(scatter_srad_daymet)
+# #scatter_srad_frac
+# 
+# #summary(srad_fracshift)
+# rmse(niwot_daymet_comp$daymet_mjm2, niwot_daymet_comp$niwot_flux_mjm2)
+# bias(niwot_daymet_comp$niwot_flux_mjm2, niwot_daymet_comp$daymet_mjm2)
+# summary(niwot_daymet_comp$diff)
 ```
@@
 
-```{r}
+```{r, echo=F}
+#bring in srad and niwot_srad
+# srad_gapfil <- full_join(srad, niwot_srad) %>%
+#   filter(date > '2009-12-31') %>%
+#   dplyr::select(-c(prism_w, prism_m, prism_e))
+# 
+# #bat <- read_xlsx('bat_srad.xlsx')
+# #save.image(file = 'bat.RData')
+# load('C:/Users/sears/Documents/Repos/fourmile/data/bat.RData')
+# 
+# bet_day <- bat %>%
+#   mutate(date = as.Date(datetime)) %>%
+#   group_by(date) %>%
+#   summarize(sw_in_avg_wm2= mean(in_swrad_wm2)) %>%
+#   filter(date > '2009-12-31') %>%
+#   mutate(bet_sw_in_mjm2 = (sw_in_avg_wm2 * 86400) / 1000000) %>%
+#   dplyr::select(-c(sw_in_avg_wm2))
+# 
+# srad_gapfil_all <- full_join(srad_gapfil, bet_day, by='date') %>%
+#   filter(date < '2020-12-31') %>%
+#   dplyr::select(-c(bet_sw_in_mjm2.x)) %>%
+#   rename(bet_sw = bet_sw_in_mjm2.y) %>%
+#   mutate(doyh = yday(date))
+# 
+# summary(srad_gapfil_all)
+# 
+# srad_flip_nofill <- srad_gapfil %>%
+#   pivot_longer(!date, names_to = 'site', values_to = 'sw_in_mjm2')
+# 
+# srad_nofill <- ggplot(srad_flip_nofill, aes(x=date, y=sw_in_mjm2, color=site)) +
+#   geom_line() +
+#   ggtitle('Solar rad, no fill')
+# 
+# ggplotly(srad_nofill)
+# 
+# new_srad <- missRanger(srad_gapfil_all, num.trees=100000)
+# summary(new_srad)
+# 
+# srad_flip_fill <- new_srad %>%
+#   dplyr::select(-c(doyh)) %>% 
+#   pivot_longer(!date, names_to = 'site', values_to = 'sw_in_mjm2')
+#   
+# 
+# srad_filled <- ggplot(srad_flip_fill, aes(x=date, y=sw_in_mjm2, color=site)) +
+#   geom_line() +
+#   ggtitle('Solar rad, fill')
+# 
+# ggplotly(srad_filled)
 
 ```
+
+## Runoff ratios
+
+```{r}
+prec_runoff <- read_csv('C:/Users/sears/Documents/Repos/fourmile/data/prec_runoff.csv')
+
+ratios_prep <- prec_runoff %>%
+  mutate(prec_12 = hru5 + hru6,
+         prec_13 = hru3 + hru11,
+         prec_10 = hru1 + hru2 + hru8 + hru9 + hru4,
+         prec_11 = hru7 + hru10,
+         date = dmy(time)) %>%
+  dplyr::select(c(date, prec_12, prec_13, prec_10, prec_11)) %>%
+  mutate_at(c('prec_12', 'prec_13', 'prec_10', 'prec_11'), ~(./1000)) %>%
+  mutate(prec_12_cmd = prec_12 * (14378900+16275100),
+         prec_13_cmd = prec_13 * (6850100+4299900),
+         prec_10_cmd = prec_10 * (4092400+2170400+2379900+1725600+1967700),
+         prec_11_cmd = prec_11 * (7092000+5834400)) %>%
+  dplyr::select(-c(prec_12, prec_13, prec_10, prec_11))
+
+obs_q <- read_csv('C:/Users/sears/Documents/Repos/fourmile/data/orun.csv')
+
+obs_q <- obs_q %>% 
+  dplyr::select(-1) %>%
+  filter(!row_number() %in% c(1:9, 11:15)) %>%
+  set_names(as.character(slice(., 1))) %>%
+  slice(-1) %>%
+  replace(.==-9999, NA) %>%
+  rename(ds3 = 2,
+         usgs1 = 3,
+         ds2 = 4,
+         usgs2 = 5,
+         us1 = 6,
+         ds1 = 7) %>%
+  mutate(date = mdy(date)) %>%
+  mutate_if(is.character, as.numeric) %>%
+  dplyr::select(-c(ds2, ds3)) %>%
+  mutate(across(where(is.numeric), ~(.*86400))) %>%
+  filter(!between(date, as.Date("2013-09-10"), as.Date("2014-04-01")))
+
+ratios <- full_join(ratios_prep, obs_q, by = 'date')
+
+summary(ratios)
+
+ratios_wy <- ratios %>%
+  mutate(wy = calcWaterYear(date)) %>%
+  group_by(wy) %>%
+  summarize_if(is.numeric, sum, na.rm=TRUE) %>%
+  slice(-c(11:12)) %>%
+  mutate(us1_rr = us1 / prec_12_cmd,
+         ds1_rr = ds1 / prec_13_cmd,
+         usgs2_rr = usgs2 / prec_10_cmd,
+         usgs1_rr = usgs1 / prec_11_cmd)
+
+kable(ratios_wy) %>%
+  kable_styling()
+
+ratios_2014 <- ratios %>%
+  mutate(wy = calcWaterYear(date)) %>%
+  filter(wy == 2014) %>%
+  mutate(usgs1_rr = usgs1 / prec_11_cmd)
+
+```

### 2022-10-09 fourmile_dataprocess.Rmd
ok done

@@
   slice(-c(11:12)) %>%
-  mutate(us1_rr = us1 / prec_12_cmd,
-         ds1_rr = ds1 / prec_13_cmd,
-         usgs2_rr = usgs2 / prec_10_cmd,
-         usgs1_rr = usgs1 / prec_11_cmd)
+  mutate(us1_rr = ifelse(is.na(us1), 
+                          NA, us1 / prec_12_cmd),
+         ds1_rr = ifelse(is.na(ds1),
+                          NA, ds1 / prec_13_cmd),
+         usgs2_rr = ifelse(is.na(usgs2), 
+                            NA, usgs2 / prec_10_cmd),
+         usgs1_rr = ifelse(is.na(usgs1),
+                            NA, usgs1 / prec_11_cmd))
 

### 2022-10-11 fourmile_dataprocess.Rmd
brought precip figs back in

@@
 #daily precip
-# prec_update <- prec %>%
-#   mutate(date = dmy(date),
-#          doy = yday(date)) %>%
-#   mutate_at(c('Gordon_South', 'Gordon_North',
-#               'GH', 'LM', 'SE', 'SP', 'ST', 'NADP_SL'),
-#             ~(ifelse(!doy %in% c(152:258), 
-#                                NA, .))) %>%
-#   mutate_at(c('prism_W', 'prism_M', 'prism_E'), list(lead), n = 1) %>%
-#   mutate_at(c('prism_W', 'prism_M', 'prism_E'), ~(ifelse(doy %in% c(152:258),
-#                                                          NA, .))) %>%
-#   filter(date > '2009-12-31') %>%
-#   dplyr::select(-c(doy)) %>%
-#   mutate(date = format(as.Date(date), '%d.%m.%Y'))
-# 
-# #write_csv(prec_update, 'precipAll_update.csv')
-# 
-# daily_p <- prec %>%
-#   mutate(date = dmy(date)) %>%
-#   replace(.==-9999, NA) %>%
-#   pivot_longer(!date, names_to = 'site', values_to = 'precip_mm') %>%
-#   mutate(precip_mm = as.numeric(precip_mm)) %>%
-#   mutate(WY = calcWaterYear(date)) %>%
-#   group_by(WY, site) %>%
-#   mutate(dailyp_cum_mm = cumsum(precip_mm))
-# 
-# precip <- ggplot(daily_p, aes(x=date, y=precip_mm, color=site)) + geom_line()  +
-#   theme_bw() +
-#   ggtitle('Daily precip (all)')
-# 
-# ggplotly(precip)
-# 
-# precip_cumu <- ggplot(daily_p, aes(x=date, y=dailyp_cum_mm, color=site)) + geom_line()  +
-#   theme_bw() +
-#   ggtitle('Daily precip cumulative sums (all)')
-# 
-# ggplotly(precip_cumu)
+prec_update <- prec %>%
+  mutate(date = dmy(date),
+         doy = yday(date)) %>%
+  mutate_at(c('Gordon_South', 'Gordon_North',
+              'GH', 'LM', 'SE', 'SP', 'ST', 'NADP_SL'),
+            ~(ifelse(!doy %in% c(152:258),
+                               NA, .))) %>%
+  mutate_at(c('prism_W', 'prism_M', 'prism_E'), list(lead), n = 1) %>%
+  mutate_at(c('prism_W', 'prism_M', 'prism_E'), ~(ifelse(doy %in% c(152:258),
+                                                         NA, .))) %>%
+  filter(date > '2009-12-31') %>%
+  dplyr::select(-c(doy)) %>%
+  mutate(date = format(as.Date(date), '%d.%m.%Y'))
+
+#write_csv(prec_update, 'precipAll_update.csv')
+
+daily_p <- prec %>%
+  mutate(date = dmy(date)) %>%
+  replace(.==-9999, NA) %>%
+  pivot_longer(!date, names_to = 'site', values_to = 'precip_mm') %>%
+  mutate(precip_mm = as.numeric(precip_mm)) %>%
+  mutate(WY = calcWaterYear(date)) %>%
+  group_by(WY, site) %>%
+  mutate(dailyp_cum_mm = cumsum(precip_mm))
+
+precip <- ggplot(daily_p, aes(x=date, y=precip_mm, color=site)) + geom_line()  +
+  theme_bw() +
+  ggtitle('Daily precip (all)')
+
+ggplotly(precip)
+
+precip_cumu <- ggplot(daily_p, aes(x=date, y=dailyp_cum_mm, color=site)) + geom_line()  +
+  theme_bw() +
+  ggtitle('Daily precip cumulative sums (all)')
+
+ggplotly(precip_cumu)
 

### 2022-10-12 fourmile_dataprocess.Rmd
reorganized files to uncomment code

@@
 author: "Megan Sears"
-date: "7/27/2022"
+date: "2022-10-12"
 output:
@@
 #save.image(file = 'spatial.RData')
-load('C:/Users/sears/Documents/Repos/fourmile/data/spatial.RData')
+load('C:/Users/sears/Documents/Repos/fourmile/data/spatial.RData') ## need to update with new locations + fire boundary ***
 
@@
 ```{r, echo = F}
-# niwot_prism <- read.csv(here('data', 'niwot_prism_compare.csv')) %>% 
-#   filter(!row_number() %in% c(1:10)) %>%
-#    rename(date = 1,
-#           prism_mm = 2) %>%
-#    mutate(date = ymd(date),
-#           prism_mm = as.numeric(prism_mm))
-# 
-# niwot_snotel <- prec_update %>%
-#   dplyr::select(c(date, Niwot_Snotel)) %>%
-#   rename(snotel_mm = Niwot_Snotel) %>%
-#   mutate(date = dmy(date))
-# 
-# niwot_compare <- full_join(niwot_prism, niwot_snotel, by = 'date')
-# 
-# niwot_compare <- niwot_compare %>%
-#   mutate(diff_mm = snotel_mm - prism_mm) %>%
-#   na.omit()
-# 
-# #pbias(niwot_compare$prism_mm, niwot_compare$snotel_mm)
-# 
-# scatter <- ggplot(niwot_compare, aes(x=snotel_mm, y=prism_mm)) +
-#   geom_point() +
-#   geom_abline(intercept = 0, slope = 1, size=1.5, color="blue") +
-#   ggtitle('Prism vs. Niwot SNOTEL precip')
-#   
-# ggplotly(scatter)
-# 
-# rmse(niwot_compare$prism_mm, niwot_compare$snotel_mm)
-# bias(niwot_compare$snotel_mm, niwot_compare$prism_mm)
-# summary(niwot_compare$diff_mm)
-# #filter to look at sept - june
-# niwot_winter_comp <- niwot_compare %>%
-#   mutate(month = month(date)) %>%
-#   filter(!month %in% c(6:8))
-# 
-# summary(niwot_winter_comp)
+niwot_prism <- read.csv(here('data', 'niwot_prism_compare.csv')) %>%
+  filter(!row_number() %in% c(1:10)) %>%
+   rename(date = 1,
+          prism_mm = 2) %>%
+   mutate(date = ymd(date),
+          prism_mm = as.numeric(prism_mm))
+
+niwot_snotel <- prec_update %>%
+  dplyr::select(c(date, Niwot_Snotel)) %>%
+  rename(snotel_mm = Niwot_Snotel) %>%
+  mutate(date = dmy(date))
+
+niwot_compare <- full_join(niwot_prism, niwot_snotel, by = 'date')
+
+niwot_compare <- niwot_compare %>%
+  mutate(diff_mm = snotel_mm - prism_mm) %>%
+  na.omit()
+
+#pbias(niwot_compare$prism_mm, niwot_compare$snotel_mm)
+
+scatter <- ggplot(niwot_compare, aes(x=snotel_mm, y=prism_mm)) +
+  geom_point() +
+  geom_abline(intercept = 0, slope = 1, size=1.5, color="blue") +
+  ggtitle('Prism vs. Niwot SNOTEL precip')
+
+ggplotly(scatter)
+
+rmse(niwot_compare$prism_mm, niwot_compare$snotel_mm)
+bias(niwot_compare$snotel_mm, niwot_compare$prism_mm)
+summary(niwot_compare$diff_mm)
+#filter to look at sept - june
+niwot_winter_comp <- niwot_compare %>%
+  mutate(month = month(date)) %>%
+  filter(!month %in% c(6:8))
+
+summary(niwot_winter_comp)
 ```
@@
 ```{r, echo = F}
-# niwot_prismshift <- niwot_compare %>%
-#   mutate_at(c("prism_mm"), funs(lead), n = 1) %>%
-#   mutate(month = month(date)) %>%
-#   #filter(!month %in% c(6:8)) %>%
-#   mutate(diff_mm = snotel_mm - prism_mm) %>%
-#   na.omit()
-# 
-# #NSE(niwot_prismshift$prism_mm, niwot_prismshift$snotel_mm)
-# #pbias(niwot_prismshift$prism_mm, niwot_prismshift$snotel_mm)
-# 
-# scatter_shiftday <- ggplot(niwot_prismshift, aes(x=snotel_mm, y=prism_mm)) +
-#   geom_point() +
-#   geom_abline(intercept = 0, slope = 1, size=1.5, color="blue") +
-#   ggtitle('Prism shift 1 day versus Niwot SNOTEL precip')
-#   
-# ggplotly(scatter_shiftday)
-# 
-# rmse(niwot_prismshift$prism_mm, niwot_prismshift$snotel_mm)
-# bias(niwot_prismshift$snotel_mm, niwot_prismshift$prism_mm)
-# summary(niwot_prismshift$diff_mm)
+niwot_prismshift <- niwot_compare %>%
+  mutate_at(c("prism_mm"), funs(lead), n = 1) %>%
+  mutate(month = month(date)) %>%
+  #filter(!month %in% c(6:8)) %>%
+  mutate(diff_mm = snotel_mm - prism_mm) %>%
+  na.omit()
+
+#NSE(niwot_prismshift$prism_mm, niwot_prismshift$snotel_mm)
+#pbias(niwot_prismshift$prism_mm, niwot_prismshift$snotel_mm)
+
+scatter_shiftday <- ggplot(niwot_prismshift, aes(x=snotel_mm, y=prism_mm)) +
+  geom_point() +
+  geom_abline(intercept = 0, slope = 1, size=1.5, color="blue") +
+  ggtitle('Prism shift 1 day versus Niwot SNOTEL precip')
+
+ggplotly(scatter_shiftday)
+
+rmse(niwot_prismshift$prism_mm, niwot_prismshift$snotel_mm)
+bias(niwot_prismshift$snotel_mm, niwot_prismshift$prism_mm)
+summary(niwot_prismshift$diff_mm)
 ```
@@
 ```{r, echo = F}
-# niwot_prismfrac <- niwot_compare %>%
-#   mutate(prism_most_mm = prism_mm * 0.974,
-#          prism_little_mm = prism_mm * 0.026) %>%
-#   mutate_at(c('prism_most_mm'), list(lead), n = 1) %>%
-#   mutate(prism_new_mm = prism_most_mm + prism_little_mm,
-#          diff_prismfrac = snotel_mm - prism_new_mm) %>%
-#   na.omit()
-# 
-# scatter_frac <- ggplot(niwot_prismfrac, aes(x=snotel_mm, y=prism_new_mm)) +
-#   geom_point() +
-#   geom_abline(intercept = 0, slope = 1, size=1.5, color="blue") +
-#   ggtitle('Prism shift by 97.4% and Niwot SNOTEL precip')
-#   
-# ggplotly(scatter_frac)
-# 
-# rmse(niwot_prismfrac$prism_new_mm, niwot_prismfrac$snotel_mm)
-# bias(niwot_prismfrac$snotel_mm, niwot_prismfrac$prism_new_mm)
-# summary(niwot_prismfrac$diff_prismfrac)
-#NSE(niwot_prismfrac$prism_new_mm, niwot_prismfrac$snotel_mm)
-#pbias(niwot_prismfrac$prism_new_mm, niwot_prismfrac$snotel_mm)
+niwot_prismfrac <- niwot_compare %>%
+  mutate(prism_most_mm = prism_mm * 0.974,
+         prism_little_mm = prism_mm * 0.026) %>%
+  mutate_at(c('prism_most_mm'), list(lead), n = 1) %>%
+  mutate(prism_new_mm = prism_most_mm + prism_little_mm,
+         diff_prismfrac = snotel_mm - prism_new_mm) %>%
+  na.omit()
+
+scatter_frac <- ggplot(niwot_prismfrac, aes(x=snotel_mm, y=prism_new_mm)) +
+  geom_point() +
+  geom_abline(intercept = 0, slope = 1, size=1.5, color="blue") +
+  ggtitle('Prism shift by 97.4% and Niwot SNOTEL precip')
+
+ggplotly(scatter_frac)
+
+rmse(niwot_prismfrac$prism_new_mm, niwot_prismfrac$snotel_mm)
+bias(niwot_prismfrac$snotel_mm, niwot_prismfrac$prism_new_mm)
+summary(niwot_prismfrac$diff_prismfrac)
+NSE(niwot_prismfrac$prism_new_mm, niwot_prismfrac$snotel_mm)
+pbias(niwot_prismfrac$prism_new_mm, niwot_prismfrac$snotel_mm)
 
@@
 ```{r, echo = F}
-# srad <- solr %>%
-#   dplyr::select(-1) %>%
-#   filter(!row_number() %in% c(1:17)) %>%
-#   replace(.==-9999, NA) %>%
-#   rename(date = 1,
-#          prism_w = 2,
-#          prism_m = 3,
-#          prism_e = 4,
-#          gordon_s = 5,
-#          gordon_n = 6,
-#          greenlake = 7) %>%
-#   mutate(date = dmy(date))
-# 
-# niwot_srad <- Niwo %>%
-#   mutate(date = ymd(date)) %>%
-#   rename(niwot_flux_mjm2 = 3) %>%
-#   dplyr::select(-c(watts_per_m2)) %>%
-#   replace(. == -9999, NA)
-# 
-# ## original  
-# srad_compare <- full_join(srad, niwot_srad, by = 'date') %>%
-#   dplyr::select(c(date, prism_w, niwot_flux_mjm2)) %>%
-#   mutate(diff = niwot_flux_mjm2 - prism_w) %>%
-#   na.omit()
-# 
-# scatter_srad_orig <- ggplot(srad_compare, aes(x=niwot_flux_mjm2, y=prism_w)) +
-#   geom_point() +
-#   geom_abline(intercept = 0, slope = 1, size=1.5, color="blue") +
-#   ggtitle('Prism versus Niwot flux tower solar rad')
-#   
-# ggplotly(scatter_srad_orig)
-# 
-# rmse(srad_compare$prism_w, srad_compare$niwot_flux_mjm2)
-# bias(srad_compare$niwot_flux_mjm2, srad_compare$prism_w)
-# summary(srad_compare$diff)
+srad <- solr %>%
+  dplyr::select(-1) %>%
+  filter(!row_number() %in% c(1:17)) %>%
+  replace(.==-9999, NA) %>%
+  rename(date = 1,
+         prism_w = 2,
+         prism_m = 3,
+         prism_e = 4,
+         gordon_s = 5,
+         gordon_n = 6,
+         greenlake = 7) %>%
+  mutate(date = dmy(date))
+
+niwot_srad <- Niwo %>%
+  mutate(date = ymd(date)) %>%
+  rename(niwot_flux_mjm2 = 3) %>%
+  dplyr::select(-c(watts_per_m2)) %>%
+  replace(. == -9999, NA)
+
+## original
+srad_compare <- full_join(srad, niwot_srad, by = 'date') %>%
+  dplyr::select(c(date, prism_w, niwot_flux_mjm2)) %>%
+  mutate(diff = niwot_flux_mjm2 - prism_w) %>%
+  na.omit()
+
+scatter_srad_orig <- ggplot(srad_compare, aes(x=niwot_flux_mjm2, y=prism_w)) +
+  geom_point() +
+  geom_abline(intercept = 0, slope = 1, size=1.5, color="blue") +
+  ggtitle('Prism versus Niwot flux tower solar rad')
+
+ggplotly(scatter_srad_orig)
+
+rmse(srad_compare$prism_w, srad_compare$niwot_flux_mjm2)
+bias(srad_compare$niwot_flux_mjm2, srad_compare$prism_w)
+summary(srad_compare$diff)
 ```
@@
 ## 1 day shift
-# srad_shift1day <- srad_compare %>%
-#   mutate_at(c("prism_w"),list(lead), n = 1) %>%
-#   na.omit() %>%
-#   mutate(diff = niwot_flux_mjm2 - prism_w)
-# 
-# scatter_srad_1day <- ggplot(srad_shift1day, aes(x=niwot_flux_mjm2, y=prism_w)) +
-#   geom_point() +
-#   geom_abline(intercept = 0, slope = 1, size=1.5, color="blue") +
-#   ggtitle('Prism shift 1 day vs. Niwot flux tower solar rad')
-#   
-# ggplotly(scatter_srad_1day)
-# #scatter_srad_1day
-# 
-# rmse(srad_shift1day$prism_w, srad_shift1day$niwot_flux_mjm2)
-# bias(srad_shift1day$niwot_flux_mjm2, srad_shift1day$prism_w)
-# summary(srad_shift1day$diff)
-#pbias(srad_shift1day$prism_w, srad_shift1day$niwot_flux_mjm2)
+srad_shift1day <- srad_compare %>%
+  mutate_at(c("prism_w"),list(lead), n = 1) %>%
+  na.omit() %>%
+  mutate(diff = niwot_flux_mjm2 - prism_w)
+
+scatter_srad_1day <- ggplot(srad_shift1day, aes(x=niwot_flux_mjm2, y=prism_w)) +
+  geom_point() +
+  geom_abline(intercept = 0, slope = 1, size=1.5, color="blue") +
+  ggtitle('Prism shift 1 day vs. Niwot flux tower solar rad')
+
+ggplotly(scatter_srad_1day)
+#scatter_srad_1day
+
+rmse(srad_shift1day$prism_w, srad_shift1day$niwot_flux_mjm2)
+bias(srad_shift1day$niwot_flux_mjm2, srad_shift1day$prism_w)
+summary(srad_shift1day$diff)
+pbias(srad_shift1day$prism_w, srad_shift1day$niwot_flux_mjm2)
 ```
@@
 ## shift by percentage
-# srad_fracshift <- srad_compare %>%
-#     mutate(prism_most = prism_w * 0.3,
-#          prism_little = prism_w * 0.7) %>%
-#   mutate_at(c('prism_most'), list(lead), n = 1) %>%
-#   mutate(prism_new = prism_most + prism_little,
-#          diff_prismfrac = niwot_flux_mjm2 - prism_new) %>%
-#   na.omit()
-#   
-# scatter_srad_frac <- ggplot(srad_fracshift, aes(x=niwot_flux_mjm2, y=prism_new)) +
-#   geom_point() +
-#   geom_abline(intercept = 0, slope = 1, size=1.5, color="blue") +
-#   ggtitle('Prism shift by 30% vs. Niwot flux tower solar rad')
-#   
-# ggplotly(scatter_srad_frac)
-# #scatter_srad_frac
-# 
-# rmse(srad_fracshift$prism_new, srad_fracshift$niwot_flux_mjm2)
-# bias(srad_fracshift$niwot_flux_mjm2, srad_fracshift$prism_new)
-# summary(srad_fracshift$diff_prismfrac)
-#pbias(srad_fracshift$prism_new, srad_fracshift$niwot_flux_mjm2)
+srad_fracshift <- srad_compare %>%
+    mutate(prism_most = prism_w * 0.3,
+         prism_little = prism_w * 0.7) %>%
+  mutate_at(c('prism_most'), list(lead), n = 1) %>%
+  mutate(prism_new = prism_most + prism_little,
+         diff_prismfrac = niwot_flux_mjm2 - prism_new) %>%
+  na.omit()
+
+scatter_srad_frac <- ggplot(srad_fracshift, aes(x=niwot_flux_mjm2, y=prism_new)) +
+  geom_point() +
+  geom_abline(intercept = 0, slope = 1, size=1.5, color="blue") +
+  ggtitle('Prism shift by 30% vs. Niwot flux tower solar rad')
+
+ggplotly(scatter_srad_frac)
+#scatter_srad_frac
+
+rmse(srad_fracshift$prism_new, srad_fracshift$niwot_flux_mjm2)
+bias(srad_fracshift$niwot_flux_mjm2, srad_fracshift$prism_new)
+summary(srad_fracshift$diff_prismfrac)
+pbias(srad_fracshift$prism_new, srad_fracshift$niwot_flux_mjm2)
 ```
@@
 ## bring in daymet
-## Daily total radiation (MJ/m2/day) can be calculated as follows: ((srad (W/m2) * dayl (s/day)) / l,000,000)
-# niwot_daymet <- daym %>%
-#   filter(!row_number() %in% c(1:7)) %>%
-#   rename(year = 1,
-#          doy = 2,
-#          srad_wm2 = 3) %>%
-#   mutate(date = as.Date(doy),
-#          month = month(date),
-#          day = day(date),
-#          date = make_date(year, month, day),
-#          daymet_mjm2 = (srad_wm2 * 86400) / 1000000) %>%
-#   dplyr::select(-c(year, doy, month, day))
-#   
-# niwot_daymet_comp <- full_join(niwot_srad, niwot_daymet, by = 'date') %>%
-#   dplyr::select(c(date, niwot_flux_mjm2, daymet_mjm2)) %>%
-#   na.omit() %>%
-#   mutate(diff = niwot_flux_mjm2 - daymet_mjm2)
-#   
-# scatter_srad_daymet <- ggplot(niwot_daymet_comp, aes(x=niwot_flux_mjm2, y=daymet_mjm2)) +
-#   geom_point() +
-#   geom_abline(intercept = 0, slope = 1, size=1.5, color="blue") +
-#   ggtitle('Daymet vs. Niwot flux tower solar rad')
-#   
-# ggplotly(scatter_srad_daymet)
-# #scatter_srad_frac
-# 
-# #summary(srad_fracshift)
-# rmse(niwot_daymet_comp$daymet_mjm2, niwot_daymet_comp$niwot_flux_mjm2)
-# bias(niwot_daymet_comp$niwot_flux_mjm2, niwot_daymet_comp$daymet_mjm2)
-# summary(niwot_daymet_comp$diff)
+# Daily total radiation (MJ/m2/day) can be calculated as follows: ((srad (W/m2) * dayl (s/day)) / l,000,000)
+niwot_daymet <- daym %>%
+  filter(!row_number() %in% c(1:7)) %>%
+  rename(year = 1,
+         doy = 2,
+         srad_wm2 = 3) %>%
+  mutate(date = as.Date(doy),
+         month = month(date),
+         day = day(date),
+         date = make_date(year, month, day),
+         daymet_mjm2 = (srad_wm2 * 86400) / 1000000) %>%
+  dplyr::select(-c(year, doy, month, day))
+
+niwot_daymet_comp <- full_join(niwot_srad, niwot_daymet, by = 'date') %>%
+  dplyr::select(c(date, niwot_flux_mjm2, daymet_mjm2)) %>%
+  na.omit() %>%
+  mutate(diff = niwot_flux_mjm2 - daymet_mjm2)
+
+scatter_srad_daymet <- ggplot(niwot_daymet_comp, aes(x=niwot_flux_mjm2, y=daymet_mjm2)) +
+  geom_point() +
+  geom_abline(intercept = 0, slope = 1, size=1.5, color="blue") +
+  ggtitle('Daymet vs. Niwot flux tower solar rad')
+
+ggplotly(scatter_srad_daymet)
+#scatter_srad_frac
+
+#summary(srad_fracshift)
+rmse(niwot_daymet_comp$daymet_mjm2, niwot_daymet_comp$niwot_flux_mjm2)
+bias(niwot_daymet_comp$niwot_flux_mjm2, niwot_daymet_comp$daymet_mjm2)
+summary(niwot_daymet_comp$diff)
 ```
@@
 #bring in srad and niwot_srad
-# srad_gapfil <- full_join(srad, niwot_srad) %>%
-#   filter(date > '2009-12-31') %>%
-#   dplyr::select(-c(prism_w, prism_m, prism_e))
-# 
-# #bat <- read_xlsx('bat_srad.xlsx')
-# #save.image(file = 'bat.RData')
-# load('C:/Users/sears/Documents/Repos/fourmile/data/bat.RData')
-# 
-# bet_day <- bat %>%
-#   mutate(date = as.Date(datetime)) %>%
-#   group_by(date) %>%
-#   summarize(sw_in_avg_wm2= mean(in_swrad_wm2)) %>%
-#   filter(date > '2009-12-31') %>%
-#   mutate(bet_sw_in_mjm2 = (sw_in_avg_wm2 * 86400) / 1000000) %>%
-#   dplyr::select(-c(sw_in_avg_wm2))
-# 
-# srad_gapfil_all <- full_join(srad_gapfil, bet_day, by='date') %>%
-#   filter(date < '2020-12-31') %>%
-#   dplyr::select(-c(bet_sw_in_mjm2.x)) %>%
-#   rename(bet_sw = bet_sw_in_mjm2.y) %>%
-#   mutate(doyh = yday(date))
-# 
-# summary(srad_gapfil_all)
-# 
-# srad_flip_nofill <- srad_gapfil %>%
-#   pivot_longer(!date, names_to = 'site', values_to = 'sw_in_mjm2')
-# 
-# srad_nofill <- ggplot(srad_flip_nofill, aes(x=date, y=sw_in_mjm2, color=site)) +
-#   geom_line() +
-#   ggtitle('Solar rad, no fill')
-# 
-# ggplotly(srad_nofill)
-# 
-# new_srad <- missRanger(srad_gapfil_all, num.trees=100000)
-# summary(new_srad)
-# 
-# srad_flip_fill <- new_srad %>%
-#   dplyr::select(-c(doyh)) %>% 
-#   pivot_longer(!date, names_to = 'site', values_to = 'sw_in_mjm2')
-#   
-# 
-# srad_filled <- ggplot(srad_flip_fill, aes(x=date, y=sw_in_mjm2, color=site)) +
-#   geom_line() +
-#   ggtitle('Solar rad, fill')
-# 
-# ggplotly(srad_filled)
+srad_gapfil <- full_join(srad, niwot_srad) %>%
+  filter(date > '2009-12-31') %>%
+  dplyr::select(-c(prism_w, prism_m, prism_e))
+
+#bat <- read_xlsx('bat_srad.xlsx')
+#save.image(file = 'bat.RData')
+load('C:/Users/sears/Documents/Repos/fourmile/data/bat.RData')
+
+bet_day <- bat %>%
+  mutate(date = as.Date(datetime)) %>%
+  group_by(date) %>%
+  summarize(sw_in_avg_wm2= mean(in_swrad_wm2)) %>%
+  filter(date > '2009-12-31') %>%
+  mutate(bet_sw_in_mjm2 = (sw_in_avg_wm2 * 86400) / 1000000) %>%
+  dplyr::select(-c(sw_in_avg_wm2))
+
+srad_gapfil_all <- full_join(srad_gapfil, bet_day, by='date') %>%
+  filter(date < '2020-12-31') %>%
+  dplyr::select(-c(bet_sw_in_mjm2.x)) %>%
+  rename(bet_sw = bet_sw_in_mjm2.y) %>%
+  mutate(doyh = yday(date))
+
+summary(srad_gapfil_all)
+
+srad_flip_nofill <- srad_gapfil %>%
+  pivot_longer(!date, names_to = 'site', values_to = 'sw_in_mjm2')
+
+srad_nofill <- ggplot(srad_flip_nofill, aes(x=date, y=sw_in_mjm2, color=site)) +
+  geom_line() +
+  ggtitle('Solar rad, no fill')
+
+ggplotly(srad_nofill)
+
+new_srad <- missRanger(srad_gapfil_all, num.trees=100000)
+summary(new_srad)
+
+srad_flip_fill <- new_srad %>%
+  dplyr::select(-c(doyh)) %>%
+  pivot_longer(!date, names_to = 'site', values_to = 'sw_in_mjm2')
+
+srad_filled <- ggplot(srad_flip_fill, aes(x=date, y=sw_in_mjm2, color=site)) +
+  geom_line() +
+  ggtitle('Solar rad, fill')
+
+ggplotly(srad_filled)
 
@@
 ```{r}
-prec_runoff <- read_csv('C:/Users/sears/Documents/Repos/fourmile/data/prec_runoff.csv')
+prec_runoff <- read_csv('C:/Users/sears/Documents/Repos/fourmile/data/runoff_prep_precip.csv')
 

### 2022-10-18 fourmile_inputs.Rmd
prism updates for tmax, tmin, precip complete

@@
 ```
+
+## Update PRISM
+
+```{r}
+#bring in all new prism data
+setwd('C:/Users/sears/Documents/Repos/fourmile/data/updated_prism')
+
+#pull in all filenames with csv
+filenames <- list.files('.', pattern='.csv', full.names=F)
+
+#read all the csvs
+dataframes <- lapply(filenames, read_csv)
+
+#name all the csv
+names(dataframes) <- substr(filenames, 1,5)
+
+#extract csvs from list to global env
+lapply(names(dataframes), function(x) assign(x, dataframes[[x]], envir = .GlobalEnv))
+rm(dataframes)
+
+prism <- list(p2010,p2011,p2012,p2013,p2014,p2015,p2016,p2017,p2018,p2019,p2020)
+
+prism_all <- bind_rows(prism) %>%
+  rename(ppt_mm = 6, 
+         tmin_c = 7,
+         tmax_c = 8) %>%
+  arrange(Date) %>%
+  filter(str_detect(Name, 'prism_7|prism_12|prism_13|prism_14|prism_15|prism_16|prism_17|prism_18|prism_28'))
+
+#break out by variable then can rotate the data
+#tmax first
+tmax <- prism_all %>%
+  dplyr::select(c(Date, Name, tmax_c)) %>%
+  pivot_wider(names_from = Name, values_from = tmax_c)
+
+write.csv(tmax, 'tmax.csv')
+write.csv(prism_all, 'prism_all.csv')
+
+#tmin
+tmin <- prism_all %>%
+  dplyr::select(c(Date, Name, tmin_c)) %>%
+  pivot_wider(names_from = Name, values_from = tmin_c)
+
+write.csv(tmin, 'tmin.csv')
+
+#prism precip 
+#best case (in winter prism is used, outside of that NA as -9999 PLUS prism shift)
+p_bestcase <- prism_all %>%
+  dplyr::select(c(Date, Name, ppt_mm)) %>%
+  pivot_wider(names_from = Name, values_from = ppt_mm) %>%
+  mutate(prism_most_7 = prism_7 * 0.974,
+         prism_little_7 = prism_7 * 0.026,
+         prism_most_12 = prism_12 * 0.974,
+         prism_little_12 = prism_12 * 0.026,
+         prism_most_13 = prism_13 * 0.974,
+         prism_little_13 = prism_13 * 0.026,
+         prism_most_14 = prism_14 * 0.974,
+         prism_little_14 = prism_14 * 0.026,
+         prism_most_15 = prism_15 * 0.974,
+         prism_little_15 = prism_15 * 0.026,
+         prism_most_16 = prism_16 * 0.974,
+         prism_little_16 = prism_16 * 0.026,
+         prism_most_17 = prism_17 * 0.974,
+         prism_little_17 = prism_17 * 0.026,
+         prism_most_18 = prism_18 * 0.974,
+         prism_little_18 = prism_18 * 0.026,
+         prism_most_28 = prism_28 * 0.974,
+         prism_little_28 = prism_28 * 0.026) %>%
+  mutate_at(c('prism_most_7', 'prism_most_12', 'prism_most_13',
+              'prism_most_14', 'prism_most_15', 'prism_most_16',
+              'prism_most_17', 'prism_most_18', 'prism_most_28'),
+            list(lead), n = 1) %>%
+  mutate(prism_7 = prism_most_7 + prism_little_7,
+         prism_12 = prism_most_12 + prism_little_12,
+         prism_13 = prism_most_13 + prism_little_13,
+         prism_14 = prism_most_14 + prism_little_14,
+         prism_15 = prism_most_15 + prism_little_15,
+         prism_16 = prism_most_16 + prism_little_16,
+         prism_17 = prism_most_17 + prism_little_17,
+         prism_18 = prism_most_18 + prism_little_18,
+         prism_28 = prism_most_28 + prism_little_28,) %>%
+  dplyr::select(-c(prism_most_7, prism_little_7,
+                   prism_most_12, prism_little_12,
+                   prism_most_13, prism_little_13,
+                   prism_most_14, prism_little_14,
+                   prism_most_15, prism_little_15,
+                   prism_most_16, prism_little_16,
+                   prism_most_17, prism_little_17,
+                   prism_most_18, prism_little_18,
+                   prism_most_28, prism_little_28)) %>%
+  mutate(doy = yday(Date)) %>%
+  mutate_at(c('prism_7', 'prism_12', 'prism_13',
+              'prism_14', 'prism_15', 'prism_16',
+              'prism_17', 'prism_18', 'prism_28'), 
+            ~(ifelse(doy %in% c(152:258), -9999, .)))
+
+write.csv(p_bestcase, 'p_bestcase.csv')
+
+p_shift <- prism_all %>%
+    dplyr::select(c(Date, Name, ppt_mm)) %>%
+  pivot_wider(names_from = Name, values_from = ppt_mm) %>%
+  mutate(prism_most_7 = prism_7 * 0.974,
+         prism_little_7 = prism_7 * 0.026,
+         prism_most_12 = prism_12 * 0.974,
+         prism_little_12 = prism_12 * 0.026,
+         prism_most_13 = prism_13 * 0.974,
+         prism_little_13 = prism_13 * 0.026,
+         prism_most_14 = prism_14 * 0.974,
+         prism_little_14 = prism_14 * 0.026,
+         prism_most_15 = prism_15 * 0.974,
+         prism_little_15 = prism_15 * 0.026,
+         prism_most_16 = prism_16 * 0.974,
+         prism_little_16 = prism_16 * 0.026,
+         prism_most_17 = prism_17 * 0.974,
+         prism_little_17 = prism_17 * 0.026,
+         prism_most_18 = prism_18 * 0.974,
+         prism_little_18 = prism_18 * 0.026,
+         prism_most_28 = prism_28 * 0.974,
+         prism_little_28 = prism_28 * 0.026) %>%
+  mutate_at(c('prism_most_7', 'prism_most_12', 'prism_most_13',
+              'prism_most_14', 'prism_most_15', 'prism_most_16',
+              'prism_most_17', 'prism_most_18', 'prism_most_28'),
+            list(lead), n = 1) %>%
+  mutate(prism_7 = prism_most_7 + prism_little_7,
+         prism_12 = prism_most_12 + prism_little_12,
+         prism_13 = prism_most_13 + prism_little_13,
+         prism_14 = prism_most_14 + prism_little_14,
+         prism_15 = prism_most_15 + prism_little_15,
+         prism_16 = prism_most_16 + prism_little_16,
+         prism_17 = prism_most_17 + prism_little_17,
+         prism_18 = prism_most_18 + prism_little_18,
+         prism_28 = prism_most_28 + prism_little_28,) %>%
+  dplyr::select(-c(prism_most_7, prism_little_7,
+                   prism_most_12, prism_little_12,
+                   prism_most_13, prism_little_13,
+                   prism_most_14, prism_little_14,
+                   prism_most_15, prism_little_15,
+                   prism_most_16, prism_little_16,
+                   prism_most_17, prism_little_17,
+                   prism_most_18, prism_little_18,
+                   prism_most_28, prism_little_28))
+
+write.csv(p_shift, 'p_shift.csv')
+
+p_noshift <- prism_all %>%
+  dplyr::select(c(Date, Name, ppt_mm)) %>%
+  pivot_wider(names_from = Name, values_from = ppt_mm)
+
+write.csv(p_noshift, 'p_noshift.csv')
+
+```

### 2022-10-18 fourmile_inputs.Rmd
added prism rh

@@
 
+#need to do RH!!!
+#RH: =100*(EXP((17.625*TD)/(243.04+TD))/EXP((17.625*T)/(243.04+T)))
+#pull in all filenames with csv
+filenames <- list.files('.', pattern='.csv', full.names=F)
+
+#read all the csvs
+dataframes <- lapply(filenames, read_csv)
+
+#name all the csv
+names(dataframes) <- substr(filenames, 1,5)
+
+#extract csvs from list to global env
+lapply(names(dataframes), function(x) assign(x, dataframes[[x]], envir = .GlobalEnv))
+rm(dataframes)
+
+prismt <- list(t2010,t2011,t2012,t2013,t2014,t2015,t2016,t2017,t2018,t2019,t2020)
+
+rh <- bind_rows(prismt) %>%
+  na.omit() %>% 
+  rename(tmean_c = 6, 
+         tdew_c = 7) %>%
+  arrange(Date) %>%
+  group_by(Name, Date) %>%
+  mutate(rh = 100*(exp((17.625*tdew_c)/(243.04+tdew_c))/exp((17.625*tmean_c)/(243.04+tmean_c)))) %>%
+  dplyr::select(c(Date, Name, rh)) %>%
+  pivot_wider(names_from = Name, values_from = rh)
+
+write.csv(rh, 'rh.csv')
+
 ```

### 2022-11-28 calibration_output.Rmd
code done for calibrations

---
title: "Fourmile Calibrations"
author: "Megan Sears"
date: "`r Sys.Date()`"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(plotly)

```

```{r load in files, include = F}

kge <- read_csv('calruns_KGE.csv')

params <- read_csv('calruns_params.csv') %>%
  drop_na()

```

# KGE

```{r look at kge, echo = F}

kge_plot <- ggplot(kge, aes(year_missing, KGE, shape = input_data, color = input_data)) + geom_point(size = 3) +
  theme_bw()

ggplotly(kge_plot)

```

# Parameters

```{r params, echo = F}

params <- params %>%
  mutate(input_data = case_when(
    grepl('station', run) ~ 'station',
    grepl('grid', run) ~ 'grid'
  )) %>%
  mutate(year_missing_almost = gsub('station_|grid_', '', run)) %>%
  mutate(year_missing = gsub('all', 'none', year_missing_almost)) %>%
  select(-c(year_missing_almost)) %>%
  filter(!param == 'locGrw',
         !param == 'tempRes') %>%
  mutate(value = as.numeric(value),
         param = as.factor(param))

plot_params <- function(param_name) {
  params %>%
    filter(param == param_name) %>%
    ggplot(aes(x = year_missing,
               y = value,
               shape = input_data, 
               color = input_data)) + 
    geom_point(size = 3) + 
    ggtitle(param_name) +
    theme_bw()
}

name <- levels(params$param)

lapply(name, plot_params)

```

### 2022-12-03 calibration_output.Rmd
grid 2012  now included
added in all streamflow (sim and obs). need to write function to compute all KGEs and pbias

@@
 
-# KGE
+## KGE for calibrations
 
@@
 
-# Parameters
+## Parameters
 
@@
 
+#function to plot all params
 plot_params <- function(param_name) {
@@
 
+write.csv(params, 'params.csv')
+
 ```
+
+## Hydrographs
+
+```{r}
+
+flow <- read_csv('discharge_all.csv') %>%
+  replace(.==-9999, NA)
+
+flow_pivot <- flow %>%
+  pivot_longer(!date, names_to = 'cal_run', values_to = 'q_m3s')
+
+q <- ggplot(flow_pivot, aes(date, q_m3s, color = cal_run)) +
+  geom_line()
+
+ggplotly(q)
+
+library(hydroGOF)
+
+KGE(flow$grid_all, flow$obs)
+KGE(flow$statn_all, flow$obs)
+
+get_kge <- function() {
+
+}
+
+```

### 2022-12-06 calibration_output.Rmd
working on hydrographs and kge

@@
 library(plotly)
+library(lubridate)
+library(knitr)
+library(kableExtra)
+library(dataRetrieval)
 
@@
 
-## Hydrographs
+## Hydrograph
 
-```{r}
-
+```{r hydrographs, echo = F}
 flow <- read_csv('discharge_all.csv') %>%
@@
 library(hydroGOF)
+```
 
-KGE(flow$grid_all, flow$obs)
-KGE(flow$statn_all, flow$obs)
+## Overall KGE
 
-get_kge <- function() {
+```{r kge overall, echo = F}
 
-}
+flow_kge_all <- flow %>%
+  summarize(grid2011 = KGE(grid_2011, obs),
+            grid2012 = KGE(grid_2012, obs),
+            grid2013 = KGE(grid_2013, obs),
+            grid2014 = KGE(grid_2014, obs),
+            grid2015 = KGE(grid_2015, obs),
+            grid2016 = KGE(grid_2016, obs),
+            grid2017 = KGE(grid_2017, obs),
+            grid2018 = KGE(grid_2018, obs),
+            grid2019 = KGE(grid_2019, obs),
+            grid2020 = KGE(grid_2020, obs),
+            gridall = KGE(grid_all, obs),
+            statn2011 = KGE(statn_2011, obs),
+            statn2012 = KGE(statn_2012, obs),
+            statn2013 = KGE(statn_2013, obs),
+            statn2014 = KGE(statn_2014, obs),
+            statn2015 = KGE(statn_2015, obs),
+            statn2016 = KGE(statn_2016, obs),
+            statn2017 = KGE(statn_2017, obs),
+            statn2018 = KGE(statn_2018, obs),
+            statn2019 = KGE(statn_2019, obs),
+            statn2020 = KGE(statn_2020, obs),
+            statnall = KGE(statn_all, obs)) %>%
+    mutate_if(is.numeric,
+            round,
+            digits = 2)
+
+flow_kge_all <- flow_kge_all %>%
+  pivot_longer(everything()) %>%
+  arrange(value)
+
+kable(flow_kge_all) %>%
+  kable_styling()
 
 ```
+
+## Model run KGE by water year
+
+```{r kge by year, echo = F}
+flow_year <- flow %>%
+  mutate(WY = addWaterYear()) %>%
+  group_by(WY) %>%
+  summarize(kge_grid2011 = KGE(grid_2011, obs),
+            kge_grid2012 = KGE(grid_2012, obs),
+            kge_grid2013 = KGE(grid_2013, obs),
+            kge_grid2014 = KGE(grid_2014, obs),
+            kge_grid2015 = KGE(grid_2015, obs),
+            kge_grid2016 = KGE(grid_2016, obs),
+            kge_grid2017 = KGE(grid_2017, obs),
+            kge_grid2018 = KGE(grid_2018, obs),
+            kge_grid2019 = KGE(grid_2019, obs),
+            kge_grid2020 = KGE(grid_2020, obs),
+            kge_gridall = KGE(grid_all, obs),
+            kge_statn2011 = KGE(statn_2011, obs),
+            kge_statn2012 = KGE(statn_2012, obs),
+            kge_statn2013 = KGE(statn_2013, obs),
+            kge_statn2014 = KGE(statn_2014, obs),
+            kge_statn2015 = KGE(statn_2015, obs),
+            kge_statn2016 = KGE(statn_2016, obs),
+            kge_statn2017 = KGE(statn_2017, obs),
+            kge_statn2018 = KGE(statn_2018, obs),
+            kge_statn2019 = KGE(statn_2019, obs),
+            kge_statn2020 = KGE(statn_2020, obs),
+            kge_statnall = KGE(statn_all, obs)) %>%
+    mutate_if(is.numeric,
+            round,
+            digits = 2)
+
+flow_kge <- flow_year %>%
+  pivot_longer(!year, names_to = 'model_run', values_to = 'kge') %>%
+  pivot_wider(names_from = 'year', values_from = 'kge')
+
+kable(flow_kge) %>%
+  kable_styling()
+
+```

### 2022-12-06 calibration_output.Rmd
added kge by water year

--- 2022-12-03 calibration_output.Rmd
@@
 date: "`r Sys.Date()`"
-output: html_document
+output:
+  html_document:
+    toc: true
+    toc_float: true
+    theme: journal
 editor_options: 
@@
 library(plotly)
+library(lubridate)
+library(knitr)
+library(kableExtra)
+library(dataRetrieval)
+library(hydroGOF)
 
@@
 
-write.csv(params, 'params.csv')
+#write.csv(params, 'params.csv')
 
@@
 
-library(hydroGOF)
+```
 
-KGE(flow$grid_all, flow$obs)
-KGE(flow$statn_all, flow$obs)
+## Overall KGE
 
-get_kge <- function() {
+```{r kge overall, echo = F}
 
+flow_kge_all <- flow %>%
+  summarize(grid2011 = KGE(grid_2011, obs),
+            grid2012 = KGE(grid_2012, obs),
+            grid2013 = KGE(grid_2013, obs),
+            grid2014 = KGE(grid_2014, obs),
+            grid2015 = KGE(grid_2015, obs),
+            grid2016 = KGE(grid_2016, obs),
+            grid2017 = KGE(grid_2017, obs),
+            grid2018 = KGE(grid_2018, obs),
+            grid2019 = KGE(grid_2019, obs),
+            grid2020 = KGE(grid_2020, obs),
+            gridall = KGE(grid_all, obs),
+            statn2011 = KGE(statn_2011, obs),
+            statn2012 = KGE(statn_2012, obs),
+            statn2013 = KGE(statn_2013, obs),
+            statn2014 = KGE(statn_2014, obs),
+            statn2015 = KGE(statn_2015, obs),
+            statn2016 = KGE(statn_2016, obs),
+            statn2017 = KGE(statn_2017, obs),
+            statn2018 = KGE(statn_2018, obs),
+            statn2019 = KGE(statn_2019, obs),
+            statn2020 = KGE(statn_2020, obs),
+            statnall = KGE(statn_all, obs)) %>%
+    mutate_if(is.numeric,
+            round,
+            digits = 2)
+
+flow_kge_all <- flow_kge_all %>%
+  pivot_longer(everything()) %>%
+  arrange(value)
+
+kable(flow_kge_all) %>%
+  kable_styling(full_width = F)
+
+```
+
+## Model run KGE by water year
+
+```{r kge by year, echo = F}
+
+flow_year <- flow %>%
+  mutate(WY = calcWaterYear(date)) %>%
+  group_by(WY) %>%
+  summarize(grid2011 = KGE(grid_2011, obs),
+            grid2012 = KGE(grid_2012, obs),
+            grid2013 = KGE(grid_2013, obs),
+            grid2014 = KGE(grid_2014, obs),
+            grid2015 = KGE(grid_2015, obs),
+            grid2016 = KGE(grid_2016, obs),
+            grid2017 = KGE(grid_2017, obs),
+            grid2018 = KGE(grid_2018, obs),
+            grid2019 = KGE(grid_2019, obs),
+            grid2020 = KGE(grid_2020, obs),
+            gridall = KGE(grid_all, obs),
+            statn2011 = KGE(statn_2011, obs),
+            statn2012 = KGE(statn_2012, obs),
+            statn2013 = KGE(statn_2013, obs),
+            statn2014 = KGE(statn_2014, obs),
+            statn2015 = KGE(statn_2015, obs),
+            statn2016 = KGE(statn_2016, obs),
+            statn2017 = KGE(statn_2017, obs),
+            statn2018 = KGE(statn_2018, obs),
+            statn2019 = KGE(statn_2019, obs),
+            statn2020 = KGE(statn_2020, obs),
+            statnall = KGE(statn_all, obs)) %>%
+    mutate_if(is.numeric,
+            round,
+            digits = 2)
+
+flow_kge <- flow_year %>%
+  pivot_longer(!WY, names_to = 'model_run', values_to = 'kge') %>%
+  pivot_wider(names_from = 'WY', values_from = 'kge')
+
+flow_kge %>%
+  kable(.) %>%
+  kable_styling()
+
+flow_plot <- flow_year %>%
+  pivot_longer(!WY, names_to = 'model_run', values_to = 'kge') %>%
+  mutate(WY = as.factor(WY))
+
+kge_plot_wy <- ggplot(flow_plot, aes(WY, kge, color = model_run)) + geom_point(size = 3) +
+  theme_bw()
+
+ggplotly(kge_plot_wy)
+
+```
+
+## Model run KGE plots by water year
+
+```{r wy plots, echo = F}
+
+plot_kge <- function(wateryear) {
+  flow_plot %>%
+    filter(WY == wateryear) %>%
+    ggplot(aes(x = model_run,
+               y = kge)) + 
+    geom_col() + 
+    ggtitle(wateryear) +
+    theme_bw() +
+    theme(axis.text.x = element_text(angle = 45, hjust=1))
 }
 
+name <- levels(flow_plot$WY)
+
+lapply(name, plot_kge)
+
 ```

### 2022-12-12 calibration_output.Rmd
finished getting kge values by reach

@@
 
+### Parameters for each calibration run
+
 ```{r params, echo = F}
@@
 
-## Hydrograph
+### Density plots: station vs. grid
+
+```{r density plots, echo = F}
+
+mean_params <- params %>%
+  group_by(param, input_data) %>%
+  summarize(mean = mean(value))
+
+plotdens_params <- function(param_name) {
+  params %>%
+    filter(param == param_name) %>%
+    ggplot(aes(x = value,
+               fill = input_data, 
+               color = input_data)) + 
+    geom_density(alpha=0.4) +
+    geom_vline(data=filter(mean_params, param == param_name), 
+               aes(xintercept=mean, color=input_data),
+             linetype="dashed", size=0.75) +
+    ggtitle(param_name) +
+    theme_bw()
+}
+
+name <- levels(params$param)
+
+lapply(name, plotdens_params)
+
+```
+
+## Outlet results
+
+### Hydrograph (outlet)
 
@@
 flow_pivot <- flow %>%
-  pivot_longer(!date, names_to = 'cal_run', values_to = 'q_m3s')
+  pivot_longer(!date, names_to = 'cal_run', values_to = 'q_m3s') %>%
+  mutate(WY = as.factor(calcWaterYear(date)))
 
@@
 
-## Overall KGE
+### Hydrograph by WY
+
+```{r wy hydrographs, echo = F}
+
+plotq_wy <- function(wateryear) {
+  {flow_pivot %>%
+    filter(WY == wateryear) %>%
+    ggplot(aes(x = date,
+               y = q_m3s,
+               color = cal_run)) + 
+    geom_line() + 
+    ggtitle(wateryear) +
+    theme_bw()} %>%
+    ggplotly()
+
+}
+
+name <- levels(flow_pivot$WY)
+
+try <- lapply(name, plotq_wy)
+
+htmltools::tagList(try)
+
+```
+
+### Overall KGE (outlet)
 
@@
 
-## Model run KGE by water year
+### Model run KGE by water year (outlet)
 
@@
 
-## Model run KGE plots by water year
+### Model run KGE plots by water year
 
@@
 ```
+
+## Reach results
+
+### Hydrograph by reach
+
+```{r reach hydrographs, echo = F}
+
+reach <- read_csv('reach_all.csv') %>%
+  mutate(reach = as.factor(reach)) %>%
+  pivot_longer(!c(date, reach, WY), names_to = 'cal', values_to = 'q_cms')
+
+plotq_reach <- function(reach_name) {
+  {reach %>%
+    filter(reach == reach_name) %>%
+    ggplot(aes(x = date,
+               y = q_cms,
+               color = cal)) + 
+    geom_line() + 
+    ggtitle(reach_name) +
+    theme_bw()} %>%
+    ggplotly()
+
+}
+
+name <- levels(reach$reach)
+
+try2 <- lapply(name, plotq_reach)
+
+htmltools::tagList(try2)
+
+```
+
+### Overall KGE by reach
+
+```{r reach kge, echo = F}
+
+reach_pivot <- reach %>%
+  pivot_wider(names_from = 'cal', values_from = 'q_cms') %>%
+  mutate(WY = as.factor(calcWaterYear(date)))
+
+reach_kge_all <- reach_pivot %>%
+  group_by(reach) %>%
+  summarize(grid2011 = KGE(grid_2011, obs),
+            grid2012 = KGE(grid_2012, obs),
+            grid2013 = KGE(grid_2013, obs),
+            grid2014 = KGE(grid_2014, obs),
+            grid2015 = KGE(grid_2015, obs),
+            grid2016 = KGE(grid_2016, obs),
+            grid2017 = KGE(grid_2017, obs),
+            grid2018 = KGE(grid_2018, obs),
+            grid2019 = KGE(grid_2019, obs),
+            grid2020 = KGE(grid_2020, obs),
+            gridall = KGE(grid_all, obs),
+            statn2011 = KGE(statn_2011, obs),
+            statn2012 = KGE(statn_2012, obs),
+            statn2013 = KGE(statn_2013, obs),
+            statn2014 = KGE(statn_2014, obs),
+            statn2015 = KGE(statn_2015, obs),
+            statn2016 = KGE(statn_2016, obs),
+            statn2017 = KGE(statn_2017, obs),
+            statn2018 = KGE(statn_2018, obs),
+            statn2019 = KGE(statn_2019, obs),
+            statn2020 = KGE(statn_2020, obs),
+            statnall = KGE(statn_all, obs)) %>%
+    mutate_if(is.numeric,
+            round,
+            digits = 2)
+
+reach_kge_all <- reach_kge_all %>%
+  pivot_longer(!reach, names_to = 'cal_runs', values_to = 'KGE') %>%
+  pivot_wider(names_from = 'reach', values_from = 'KGE')
+
+kable(reach_kge_all) %>%
+  kable_styling(full_width = F)
+
+obs_count <- reach_pivot %>%
+  select(obs, reach) %>%
+  drop_na() %>%
+  group_by(reach) %>%
+  summarize(count_obs = n())
+
+kable(obs_count, caption = 'Streamflow observation count') %>%
+  kable_styling(full_width = F)
+
+```

### 2022-12-28 calibration_output.Rmd
updating cal results for outlet only

--- 2022-12-06 calibration_output.Rmd
@@
 
-params <- read_csv('calruns_params.csv') %>%
-  drop_na()
+# params <- read_csv('calruns_params.csv') %>%
+#   drop_na()
 
@@
 
+### Parameters for each calibration run
+
 ```{r params, echo = F}
 
-params <- params %>%
-  mutate(input_data = case_when(
-    grepl('station', run) ~ 'station',
-    grepl('grid', run) ~ 'grid'
-  )) %>%
-  mutate(year_missing_almost = gsub('station_|grid_', '', run)) %>%
-  mutate(year_missing = gsub('all', 'none', year_missing_almost)) %>%
-  select(-c(year_missing_almost)) %>%
-  filter(!param == 'locGrw',
-         !param == 'tempRes') %>%
+# params <- params %>%
+#   mutate(input_data = case_when(
+#     grepl('station', run) ~ 'station',
+#     grepl('grid', run) ~ 'grid'
+#   )) %>%
+#   mutate(year_missing_almost = gsub('station_|grid_', '', run)) %>%
+#   mutate(year_missing = gsub('all', 'none', year_missing_almost)) %>%
+#   select(-c(year_missing_almost)) %>%
+#   filter(!param == 'locGrw',
+#          !param == 'tempRes') %>%
+#   mutate(value = as.numeric(value),
+#          param = as.factor(param))
+
+# write_csv(params, 'paramsnew.csv')
+
+params <- read_csv('paramsnew.csv') %>%
   mutate(value = as.numeric(value),
@@
 
-## Hydrograph
+### Density plots: station vs. grid
 
-```{r hydrographs, echo = F}
-flow <- read_csv('discharge_all.csv') %>%
-  replace(.==-9999, NA)
+```{r density plots, echo = F}
 
-flow_pivot <- flow %>%
-  pivot_longer(!date, names_to = 'cal_run', values_to = 'q_m3s')
+mean_params <- params %>%
+  group_by(param, input_data) %>%
+  summarize(mean = mean(value))
 
-q <- ggplot(flow_pivot, aes(date, q_m3s, color = cal_run)) +
-  geom_line()
+plotdens_params <- function(param_name) {
+  params %>%
+    filter(param == param_name) %>%
+    ggplot(aes(x = value,
+               fill = input_data, 
+               color = input_data)) + 
+    geom_density(alpha=0.4) +
+    geom_vline(data=filter(mean_params, param == param_name), 
+               aes(xintercept=mean, color=input_data),
+             linetype="dashed", size=0.75) +
+    ggtitle(param_name) +
+    theme_bw()
+}
 
-ggplotly(q)
+name <- levels(params$param)
+
+lapply(name, plotdens_params)
 
@@
 
-## Overall KGE
+## Outlet results
+
+### Hydrograph (outlet)
+
+```{r hydrographs, echo = F}
+# flow <- read_csv('discharge_all.csv') %>%
+#   replace(.==-9999, NA)
+# 
+# 
+# flow_pivot <- flow %>%
+#   pivot_longer(!date, names_to = 'cal_run', values_to = 'q_m3s') %>%
+#   mutate(WY = as.factor(calcWaterYear(date)))
+#   
+# 
+# q <- ggplot(flow_pivot, aes(date, q_m3s, color = cal_run)) +
+#   geom_line()
+# 
+# ggplotly(q)
+
+```
+
+### Hydrograph by WY
+
+```{r wy hydrographs, echo = F}
+
+# plotq_wy <- function(wateryear) {
+#   {flow_pivot %>%
+#     filter(WY == wateryear) %>%
+#     ggplot(aes(x = date,
+#                y = q_m3s,
+#                color = cal_run)) + 
+#     geom_line() + 
+#     ggtitle(wateryear) +
+#     theme_bw()} %>%
+#     ggplotly()
+#   
+# }
+# 
+# name <- levels(flow_pivot$WY)
+# 
+# try <- lapply(name, plotq_wy)
+# 
+# htmltools::tagList(try)
+
+```
+
+### Overall KGE (outlet)
 
@@
 
-flow_kge_all <- flow %>%
-  summarize(grid2011 = KGE(grid_2011, obs),
-            grid2012 = KGE(grid_2012, obs),
-            grid2013 = KGE(grid_2013, obs),
-            grid2014 = KGE(grid_2014, obs),
-            grid2015 = KGE(grid_2015, obs),
-            grid2016 = KGE(grid_2016, obs),
-            grid2017 = KGE(grid_2017, obs),
-            grid2018 = KGE(grid_2018, obs),
-            grid2019 = KGE(grid_2019, obs),
-            grid2020 = KGE(grid_2020, obs),
-            gridall = KGE(grid_all, obs),
-            statn2011 = KGE(statn_2011, obs),
-            statn2012 = KGE(statn_2012, obs),
-            statn2013 = KGE(statn_2013, obs),
-            statn2014 = KGE(statn_2014, obs),
-            statn2015 = KGE(statn_2015, obs),
-            statn2016 = KGE(statn_2016, obs),
-            statn2017 = KGE(statn_2017, obs),
-            statn2018 = KGE(statn_2018, obs),
-            statn2019 = KGE(statn_2019, obs),
-            statn2020 = KGE(statn_2020, obs),
-            statnall = KGE(statn_all, obs)) %>%
-    mutate_if(is.numeric,
-            round,
-            digits = 2)
-
-flow_kge_all <- flow_kge_all %>%
-  pivot_longer(everything()) %>%
-  arrange(value)
-
-kable(flow_kge_all) %>%
-  kable_styling(full_width = F)
+# flow_kge_all <- flow %>%
+#   summarize(grid2011 = KGE(grid_2011, obs),
+#             grid2012 = KGE(grid_2012, obs),
+#             grid2013 = KGE(grid_2013, obs),
+#             grid2014 = KGE(grid_2014, obs),
+#             grid2015 = KGE(grid_2015, obs),
+#             grid2016 = KGE(grid_2016, obs),
+#             grid2017 = KGE(grid_2017, obs),
+#             grid2018 = KGE(grid_2018, obs),
+#             grid2019 = KGE(grid_2019, obs),
+#             grid2020 = KGE(grid_2020, obs),
+#             gridall = KGE(grid_all, obs),
+#             statn2011 = KGE(statn_2011, obs),
+#             statn2012 = KGE(statn_2012, obs),
+#             statn2013 = KGE(statn_2013, obs),
+#             statn2014 = KGE(statn_2014, obs),
+#             statn2015 = KGE(statn_2015, obs),
+#             statn2016 = KGE(statn_2016, obs),
+#             statn2017 = KGE(statn_2017, obs),
+#             statn2018 = KGE(statn_2018, obs),
+#             statn2019 = KGE(statn_2019, obs),
+#             statn2020 = KGE(statn_2020, obs),
+#             statnall = KGE(statn_all, obs)) %>%
+#     mutate_if(is.numeric,
+#             round,
+#             digits = 2)
+# 
+# flow_kge_all <- flow_kge_all %>%
+#   pivot_longer(everything()) %>%
+#   arrange(value)
+# 
+# kable(flow_kge_all) %>%
+#   kable_styling(full_width = F)
 
@@
 
-flow_year <- flow %>%
-  mutate(WY = calcWaterYear(date)) %>%
-  group_by(WY) %>%
-  summarize(grid2011 = KGE(grid_2011, obs),
-            grid2012 = KGE(grid_2012, obs),
-            grid2013 = KGE(grid_2013, obs),
-            grid2014 = KGE(grid_2014, obs),
-            grid2015 = KGE(grid_2015, obs),
-            grid2016 = KGE(grid_2016, obs),
-            grid2017 = KGE(grid_2017, obs),
-            grid2018 = KGE(grid_2018, obs),
-            grid2019 = KGE(grid_2019, obs),
-            grid2020 = KGE(grid_2020, obs),
-            gridall = KGE(grid_all, obs),
-            statn2011 = KGE(statn_2011, obs),
-            statn2012 = KGE(statn_2012, obs),
-            statn2013 = KGE(statn_2013, obs),
-            statn2014 = KGE(statn_2014, obs),
-            statn2015 = KGE(statn_2015, obs),
-            statn2016 = KGE(statn_2016, obs),
-            statn2017 = KGE(statn_2017, obs),
-            statn2018 = KGE(statn_2018, obs),
-            statn2019 = KGE(statn_2019, obs),
-            statn2020 = KGE(statn_2020, obs),
-            statnall = KGE(statn_all, obs)) %>%
-    mutate_if(is.numeric,
-            round,
-            digits = 2)
-
-flow_kge <- flow_year %>%
-  pivot_longer(!WY, names_to = 'model_run', values_to = 'kge') %>%
-  pivot_wider(names_from = 'WY', values_from = 'kge')
-
-flow_kge %>%
-  kable(.) %>%
-  kable_styling()
-
-flow_plot <- flow_year %>%
-  pivot_longer(!WY, names_to = 'model_run', values_to = 'kge') %>%
-  mutate(WY = as.factor(WY))
-
-kge_plot_wy <- ggplot(flow_plot, aes(WY, kge, color = model_run)) + geom_point(size = 3) +
-  theme_bw()
-
-ggplotly(kge_plot_wy)
+# flow_year <- flow %>%
+#   mutate(WY = calcWaterYear(date)) %>%
+#   group_by(WY) %>%
+#   summarize(grid2011 = KGE(grid_2011, obs),
+#             grid2012 = KGE(grid_2012, obs),
+#             grid2013 = KGE(grid_2013, obs),
+#             grid2014 = KGE(grid_2014, obs),
+#             grid2015 = KGE(grid_2015, obs),
+#             grid2016 = KGE(grid_2016, obs),
+#             grid2017 = KGE(grid_2017, obs),
+#             grid2018 = KGE(grid_2018, obs),
+#             grid2019 = KGE(grid_2019, obs),
+#             grid2020 = KGE(grid_2020, obs),
+#             gridall = KGE(grid_all, obs),
+#             statn2011 = KGE(statn_2011, obs),
+#             statn2012 = KGE(statn_2012, obs),
+#             statn2013 = KGE(statn_2013, obs),
+#             statn2014 = KGE(statn_2014, obs),
+#             statn2015 = KGE(statn_2015, obs),
+#             statn2016 = KGE(statn_2016, obs),
+#             statn2017 = KGE(statn_2017, obs),
+#             statn2018 = KGE(statn_2018, obs),
+#             statn2019 = KGE(statn_2019, obs),
+#             statn2020 = KGE(statn_2020, obs),
+#             statnall = KGE(statn_all, obs)) %>%
+#     mutate_if(is.numeric,
+#             round,
+#             digits = 2)
+# 
+# flow_kge <- flow_year %>%
+#   pivot_longer(!WY, names_to = 'model_run', values_to = 'kge') %>%
+#   pivot_wider(names_from = 'WY', values_from = 'kge')
+# 
+# flow_kge %>%
+#   kable(.) %>%
+#   kable_styling()
+# 
+# 
+# flow_plot <- flow_year %>%
+#   pivot_longer(!WY, names_to = 'model_run', values_to = 'kge') %>%
+#   mutate(WY = as.factor(WY))
+# 
+# 
+# kge_plot_wy <- ggplot(flow_plot, aes(WY, kge, color = model_run)) + geom_point(size = 3) +
+#   theme_bw()
+# 
+# ggplotly(kge_plot_wy)
 
@@
 
-plot_kge <- function(wateryear) {
-  flow_plot %>%
-    filter(WY == wateryear) %>%
-    ggplot(aes(x = model_run,
-               y = kge)) + 
-    geom_col() + 
-    ggtitle(wateryear) +
-    theme_bw() +
-    theme(axis.text.x = element_text(angle = 45, hjust=1))
-}
-
-name <- levels(flow_plot$WY)
-
-lapply(name, plot_kge)
+# plot_kge <- function(wateryear) {
+#   flow_plot %>%
+#     filter(WY == wateryear) %>%
+#     ggplot(aes(x = model_run,
+#                y = kge)) + 
+#     geom_col() + 
+#     ggtitle(wateryear) +
+#     theme_bw() +
+#     theme(axis.text.x = element_text(angle = 45, hjust=1))
+# }
+# 
+# name <- levels(flow_plot$WY)
+# 
+# lapply(name, plot_kge)
 
 ```
+
+## Reach results
+
+### Hydrograph by reach
+
+```{r reach hydrographs, echo = F}
+
+# reach <- read_csv('reach_all.csv') %>%
+#   mutate(reach = as.factor(reach)) %>%
+#   pivot_longer(!c(date, reach, WY), names_to = 'cal', values_to = 'q_cms')
+# 
+#   
+# plotq_reach <- function(reach_name) {
+#   {reach %>%
+#     filter(reach == reach_name) %>%
+#     ggplot(aes(x = date,
+#                y = q_cms,
+#                color = cal)) + 
+#     geom_line() + 
+#     ggtitle(reach_name) +
+#     theme_bw()} %>%
+#     ggplotly()
+#   
+# }
+# 
+# name <- levels(reach$reach)
+# 
+# try2 <- lapply(name, plotq_reach)
+# 
+# htmltools::tagList(try2)
+# 
+# ```
+# 
+# ### Overall KGE by reach
+# 
+# ```{r reach kge, echo = F}
+# 
+# reach_pivot <- reach %>%
+#   pivot_wider(names_from = 'cal', values_from = 'q_cms') %>%
+#   mutate(WY = as.factor(calcWaterYear(date)))
+# 
+# reach_kge_all <- reach_pivot %>%
+#   group_by(reach) %>%
+#   summarize(grid2011 = KGE(grid_2011, obs),
+#             grid2012 = KGE(grid_2012, obs),
+#             grid2013 = KGE(grid_2013, obs),
+#             grid2014 = KGE(grid_2014, obs),
+#             grid2015 = KGE(grid_2015, obs),
+#             grid2016 = KGE(grid_2016, obs),
+#             grid2017 = KGE(grid_2017, obs),
+#             grid2018 = KGE(grid_2018, obs),
+#             grid2019 = KGE(grid_2019, obs),
+#             grid2020 = KGE(grid_2020, obs),
+#             gridall = KGE(grid_all, obs),
+#             statn2011 = KGE(statn_2011, obs),
+#             statn2012 = KGE(statn_2012, obs),
+#             statn2013 = KGE(statn_2013, obs),
+#             statn2014 = KGE(statn_2014, obs),
+#             statn2015 = KGE(statn_2015, obs),
+#             statn2016 = KGE(statn_2016, obs),
+#             statn2017 = KGE(statn_2017, obs),
+#             statn2018 = KGE(statn_2018, obs),
+#             statn2019 = KGE(statn_2019, obs),
+#             statn2020 = KGE(statn_2020, obs),
+#             statnall = KGE(statn_all, obs)) %>%
+#     mutate_if(is.numeric,
+#             round,
+#             digits = 2)
+# 
+# 
+# reach_kge_all <- reach_kge_all %>%
+#   pivot_longer(!reach, names_to = 'cal_runs', values_to = 'KGE') %>%
+#   pivot_wider(names_from = 'reach', values_from = 'KGE')
+# 
+# 
+# kable(reach_kge_all) %>%
+#   kable_styling(full_width = F)
+# 
+# 
+# obs_count <- reach_pivot %>%
+#   select(obs, reach) %>%
+#   drop_na() %>%
+#   group_by(reach) %>%
+#   summarize(count_obs = n())
+# 
+# kable(obs_count, caption = 'Streamflow observation count') %>%
+#   kable_styling(full_width = F)
+
+```

### 2022-12-29 calibration_output.Rmd
new model results using outlet only

@@
 ```{r hydrographs, echo = F}
-# flow <- read_csv('discharge_all.csv') %>%
-#   replace(.==-9999, NA)
-# 
-# 
-# flow_pivot <- flow %>%
-#   pivot_longer(!date, names_to = 'cal_run', values_to = 'q_m3s') %>%
-#   mutate(WY = as.factor(calcWaterYear(date)))
-#   
-# 
-# q <- ggplot(flow_pivot, aes(date, q_m3s, color = cal_run)) +
-#   geom_line()
-# 
-# ggplotly(q)
+flow <- read_csv('discharge_all.csv') %>%
+  replace(.==-9999, NA)
+
+flow_pivot <- flow %>%
+  pivot_longer(!date, names_to = 'cal_run', values_to = 'q_m3s') %>%
+  mutate(year = as.factor(year(date)))
+
+q <- ggplot(flow_pivot, aes(date, q_m3s, color = cal_run)) +
+  geom_line()
+
+ggplotly(q)
 
@@
 
-### Hydrograph by WY
+### Hydrograph by calendar year
 
@@
 
-# plotq_wy <- function(wateryear) {
-#   {flow_pivot %>%
-#     filter(WY == wateryear) %>%
-#     ggplot(aes(x = date,
-#                y = q_m3s,
-#                color = cal_run)) + 
-#     geom_line() + 
-#     ggtitle(wateryear) +
-#     theme_bw()} %>%
-#     ggplotly()
-#   
-# }
-# 
-# name <- levels(flow_pivot$WY)
-# 
-# try <- lapply(name, plotq_wy)
-# 
-# htmltools::tagList(try)
+plotq_cy <- function(calyear) {
+  {flow_pivot %>%
+    filter(year == calyear) %>%
+    ggplot(aes(x = date,
+               y = q_m3s,
+               color = cal_run)) +
+    geom_line() +
+    ggtitle(calyear) +
+    theme_bw()} %>%
+    ggplotly()
+
+}
+
+name <- levels(flow_pivot$year)
+
+try <- lapply(name, plotq_cy)
+
+htmltools::tagList(try)
+
+#try
 
@@
 
-# flow_kge_all <- flow %>%
-#   summarize(grid2011 = KGE(grid_2011, obs),
-#             grid2012 = KGE(grid_2012, obs),
-#             grid2013 = KGE(grid_2013, obs),
-#             grid2014 = KGE(grid_2014, obs),
-#             grid2015 = KGE(grid_2015, obs),
-#             grid2016 = KGE(grid_2016, obs),
-#             grid2017 = KGE(grid_2017, obs),
-#             grid2018 = KGE(grid_2018, obs),
-#             grid2019 = KGE(grid_2019, obs),
-#             grid2020 = KGE(grid_2020, obs),
-#             gridall = KGE(grid_all, obs),
-#             statn2011 = KGE(statn_2011, obs),
-#             statn2012 = KGE(statn_2012, obs),
-#             statn2013 = KGE(statn_2013, obs),
-#             statn2014 = KGE(statn_2014, obs),
-#             statn2015 = KGE(statn_2015, obs),
-#             statn2016 = KGE(statn_2016, obs),
-#             statn2017 = KGE(statn_2017, obs),
-#             statn2018 = KGE(statn_2018, obs),
-#             statn2019 = KGE(statn_2019, obs),
-#             statn2020 = KGE(statn_2020, obs),
-#             statnall = KGE(statn_all, obs)) %>%
-#     mutate_if(is.numeric,
-#             round,
-#             digits = 2)
-# 
-# flow_kge_all <- flow_kge_all %>%
-#   pivot_longer(everything()) %>%
-#   arrange(value)
-# 
-# kable(flow_kge_all) %>%
-#   kable_styling(full_width = F)
+flow_kge_all <- flow %>%
+  summarize(grid2011 = KGE(grid_2011, obs),
+            grid2012 = KGE(grid_2012, obs),
+            grid2013 = KGE(grid_2013, obs),
+            grid2014 = KGE(grid_2014, obs),
+            grid2015 = KGE(grid_2015, obs),
+            grid2016 = KGE(grid_2016, obs),
+            grid2017 = KGE(grid_2017, obs),
+            grid2018 = KGE(grid_2018, obs),
+            grid2019 = KGE(grid_2019, obs),
+            grid2020 = KGE(grid_2020, obs),
+            gridall = KGE(grid_all, obs),
+            statn2011 = KGE(statn_2011, obs),
+            statn2012 = KGE(statn_2012, obs),
+            statn2013 = KGE(statn_2013, obs),
+            statn2014 = KGE(statn_2014, obs),
+            statn2015 = KGE(statn_2015, obs),
+            statn2016 = KGE(statn_2016, obs),
+            statn2017 = KGE(statn_2017, obs),
+            statn2018 = KGE(statn_2018, obs),
+            statn2019 = KGE(statn_2019, obs),
+            statn2020 = KGE(statn_2020, obs),
+            statnall = KGE(statn_all, obs)) %>%
+    mutate_if(is.numeric,
+            round,
+            digits = 2)
+
+flow_kge_all <- flow_kge_all %>%
+  pivot_longer(everything()) %>%
+  arrange(value)
+
+kable(flow_kge_all) %>%
+  kable_styling(full_width = F)
 
@@
 
-### Model run KGE by water year (outlet)
+### Model run KGE by calendar year (outlet)
 
@@
 
-# flow_year <- flow %>%
-#   mutate(WY = calcWaterYear(date)) %>%
-#   group_by(WY) %>%
-#   summarize(grid2011 = KGE(grid_2011, obs),
-#             grid2012 = KGE(grid_2012, obs),
-#             grid2013 = KGE(grid_2013, obs),
-#             grid2014 = KGE(grid_2014, obs),
-#             grid2015 = KGE(grid_2015, obs),
-#             grid2016 = KGE(grid_2016, obs),
-#             grid2017 = KGE(grid_2017, obs),
-#             grid2018 = KGE(grid_2018, obs),
-#             grid2019 = KGE(grid_2019, obs),
-#             grid2020 = KGE(grid_2020, obs),
-#             gridall = KGE(grid_all, obs),
-#             statn2011 = KGE(statn_2011, obs),
-#             statn2012 = KGE(statn_2012, obs),
-#             statn2013 = KGE(statn_2013, obs),
-#             statn2014 = KGE(statn_2014, obs),
-#             statn2015 = KGE(statn_2015, obs),
-#             statn2016 = KGE(statn_2016, obs),
-#             statn2017 = KGE(statn_2017, obs),
-#             statn2018 = KGE(statn_2018, obs),
-#             statn2019 = KGE(statn_2019, obs),
-#             statn2020 = KGE(statn_2020, obs),
-#             statnall = KGE(statn_all, obs)) %>%
-#     mutate_if(is.numeric,
-#             round,
-#             digits = 2)
-# 
-# flow_kge <- flow_year %>%
-#   pivot_longer(!WY, names_to = 'model_run', values_to = 'kge') %>%
-#   pivot_wider(names_from = 'WY', values_from = 'kge')
-# 
-# flow_kge %>%
-#   kable(.) %>%
-#   kable_styling()
-# 
-# 
-# flow_plot <- flow_year %>%
-#   pivot_longer(!WY, names_to = 'model_run', values_to = 'kge') %>%
-#   mutate(WY = as.factor(WY))
-# 
-# 
-# kge_plot_wy <- ggplot(flow_plot, aes(WY, kge, color = model_run)) + geom_point(size = 3) +
-#   theme_bw()
-# 
-# ggplotly(kge_plot_wy)
+flow_year <- flow %>%
+  mutate(year = year(date)) %>%
+  group_by(year) %>%
+  summarize(grid2011 = KGE(grid_2011, obs),
+            grid2012 = KGE(grid_2012, obs),
+            grid2013 = KGE(grid_2013, obs),
+            grid2014 = KGE(grid_2014, obs),
+            grid2015 = KGE(grid_2015, obs),
+            grid2016 = KGE(grid_2016, obs),
+            grid2017 = KGE(grid_2017, obs),
+            grid2018 = KGE(grid_2018, obs),
+            grid2019 = KGE(grid_2019, obs),
+            grid2020 = KGE(grid_2020, obs),
+            gridall = KGE(grid_all, obs),
+            statn2011 = KGE(statn_2011, obs),
+            statn2012 = KGE(statn_2012, obs),
+            statn2013 = KGE(statn_2013, obs),
+            statn2014 = KGE(statn_2014, obs),
+            statn2015 = KGE(statn_2015, obs),
+            statn2016 = KGE(statn_2016, obs),
+            statn2017 = KGE(statn_2017, obs),
+            statn2018 = KGE(statn_2018, obs),
+            statn2019 = KGE(statn_2019, obs),
+            statn2020 = KGE(statn_2020, obs),
+            statnall = KGE(statn_all, obs)) %>%
+    mutate_if(is.numeric,
+            round,
+            digits = 2)
+
+flow_kge <- flow_year %>%
+  pivot_longer(!year, names_to = 'model_run', values_to = 'kge') %>%
+  pivot_wider(names_from = 'year', values_from = 'kge')
+
+flow_kge %>%
+  kable(.) %>%
+  kable_styling()
+
+flow_plot <- flow_year %>%
+  pivot_longer(!year, names_to = 'model_run', values_to = 'kge') %>%
+  mutate(year = as.factor(year))
+
+kge_plot_cy <- ggplot(flow_plot, aes(year, kge, color = model_run)) + geom_point(size = 3) +
+  theme_bw()
+
+ggplotly(kge_plot_cy)
 
@@
 
-### Model run KGE plots by water year
+### Model run KGE plots by calendar year
 
@@
 
-# plot_kge <- function(wateryear) {
-#   flow_plot %>%
-#     filter(WY == wateryear) %>%
-#     ggplot(aes(x = model_run,
-#                y = kge)) + 
-#     geom_col() + 
-#     ggtitle(wateryear) +
-#     theme_bw() +
-#     theme(axis.text.x = element_text(angle = 45, hjust=1))
-# }
-# 
-# name <- levels(flow_plot$WY)
-# 
-# lapply(name, plot_kge)
+plot_kge <- function(calyear) {
+  flow_plot %>%
+    filter(year == calyear) %>%
+    ggplot(aes(x = model_run,
+               y = kge)) +
+    geom_col() +
+    ggtitle(calyear) +
+    theme_bw() +
+    theme(axis.text.x = element_text(angle = 45, hjust=1))
+}
+
+name <- levels(flow_plot$year)
+
+lapply(name, plot_kge)
 
 ```
-
-## Reach results
-
-### Hydrograph by reach
 

### 2023-01-12 calibration_output.Rmd
updated ensemble stuff including rmse and kge

@@
 
+# #these are old -- no longer in use
 # params <- read_csv('calruns_params.csv') %>%
@@
 
-## KGE for calibrations
+# KGE for calibrations
 
@@
 
-## Parameters
+# Parameters
 
-### Parameters for each calibration run
+## Scatter plots
 
@@
 
-### Density plots: station vs. grid
+## Histograms
 
@@
                color = input_data)) + 
-    geom_density(alpha=0.4) +
+    geom_histogram(position="identity", alpha=0.5) +
     geom_vline(data=filter(mean_params, param == param_name), 
@@
 
-## Outlet results
+# Outlet results
 
-### Hydrograph (outlet)
+## Hydrograph
 
@@
 
-### Hydrograph by calendar year
+## Annual hydrographs
 
-```{r wy hydrographs, echo = F}
+```{r cy hydrographs, echo = F}
 
@@
 
-#try
-
 ```
 
-### Overall KGE (outlet)
+## KGE
+
+### Overall KGE
 
@@
 
-### Model run KGE by calendar year (outlet)
+### KGE by year
 
@@
 
-### Model run KGE plots by calendar year
+### Annual KGE plots
 
@@
 lapply(name, plot_kge)
+
+```
+
+# Ensembles
+
+## Hydrograph
+
+```{r ensemble hydrographs, echo = F}
+
+ensem <- flow %>%
+  rowwise() %>%
+  mutate(grid_ensemble = mean(c(grid_2011, grid_2012,
+                                grid_2013, grid_2014,
+                                grid_2015, grid_2016,
+                                grid_2017, grid_2018,
+                                grid_2019, grid_2020)),
+         statn_ensemble = mean(c(statn_2011, statn_2012,
+                                 statn_2013, statn_2014,
+                                 statn_2015, statn_2016,
+                                 statn_2017, statn_2018,
+                                 statn_2019, statn_2020)),
+         all_ensemble = mean(c(grid_2011, grid_2012,
+                               grid_2013, grid_2014,
+                               grid_2015, grid_2016,
+                               grid_2017, grid_2018,
+                               grid_2019, grid_2020,
+                               statn_2011, statn_2012,
+                               statn_2013, statn_2014,
+                               statn_2015, statn_2016,
+                               statn_2017, statn_2018,
+                               statn_2019, statn_2020,
+                               grid_all, statn_all))) %>%
+  select(date, grid_ensemble, statn_ensemble, 
+         all_ensemble, grid_all, 
+         statn_all, obs)
+
+ensem_pivot <- ensem %>%
+  pivot_longer(!date, names_to = 'cal_run', values_to = 'q_m3s') %>%
+  mutate(year = as.factor(year(date)))
+
+q_ensemble <- ggplot(ensem_pivot, aes(date, q_m3s, color = cal_run)) +
+  geom_line()
+
+ggplotly(q_ensemble)
+
+```
+
+## Annual hydrographs
+
+```{r hydrogs by cy, echo = F}
+
+plotqensem_cy <- function(calyear) {
+  {ensem_pivot %>%
+    filter(year == calyear) %>%
+    ggplot(aes(x = date,
+               y = q_m3s,
+               color = cal_run)) +
+    geom_line() +
+    ggtitle(calyear) +
+    theme_bw()} %>%
+    ggplotly()
+
+}
+
+name <- levels(ensem_pivot$year)
+
+try <- lapply(name, plotqensem_cy)
+
+htmltools::tagList(try)
+
+```
+
+## KGE
+
+### KGE for ensembles (entire period)
+
+```{r ensemble kge, echo = F}
+
+ensem_kge_all <- ensem %>%
+  ungroup() %>%
+  summarize(grid_ensemble = KGE(grid_ensemble, obs),
+            statn_ensemble = KGE(statn_ensemble, obs),
+            all_ensemble = KGE(all_ensemble, obs),
+            grid_all = KGE(grid_all, obs),
+            statn_all = KGE(statn_all, obs)) %>%
+    mutate_if(is.numeric,
+            round,
+            digits = 2)
+
+kable(ensem_kge_all) %>%
+  kable_styling(full_width = F)
+
+```
+
+### Annual KGEs for ensembles
+
+```{r annual kge ensemble, echo = F}
+
+yr_kge_ensem <- ensem %>%
+  ungroup() %>%
+  mutate(year = year(date)) %>%
+  group_by(year) %>%
+  summarize(grid_ensemble = KGE(grid_ensemble, obs),
+            statn_ensemble = KGE(statn_ensemble, obs),
+            all_ensemble = KGE(all_ensemble, obs),
+            grid_all = KGE(grid_all, obs),
+            statn_all = KGE(statn_all, obs)) %>%
+    mutate_if(is.numeric,
+            round,
+            digits = 2)
+
+yr_kge_table <- yr_kge_ensem %>%
+  pivot_longer(!year, names_to = 'model_run', values_to = 'kge') %>%
+  pivot_wider(names_from = 'year', values_from = 'kge')
+
+yr_kge_table %>%
+  kable(.) %>%
+  kable_styling()
+
+yr_kge_plot <- yr_kge_ensem %>%
+  pivot_longer(!year, names_to = 'model_run', values_to = 'kge') %>%
+  mutate(year = as.factor(year))
+
+#plot annual kge vals for ensembles
+plot_kge_yr_ensem <- function(calyear) {
+  yr_kge_plot %>%
+    filter(year == calyear) %>%
+    ggplot(aes(x = model_run,
+               y = kge)) +
+    geom_col() +
+    ggtitle(calyear) +
+    theme_bw() +
+    theme(axis.text.x = element_text(angle = 45, hjust=1))
+}
+
+name <- levels(yr_kge_plot$year)
+
+lapply(name, plot_kge_yr_ensem)
+
+```
+
+### Monthly KGEs for ensembles
+
+```{r monthly kge ensemble, echo = F}
+
+mo_kge <- ensem %>%
+  ungroup() %>%
+  drop_na() %>% 
+  mutate(month = month(date)) %>%
+  group_by(month) %>%
+  summarize(grid_ensemble = KGE(grid_ensemble, obs),
+            statn_ensemble = KGE(statn_ensemble, obs),
+            all_ensemble = KGE(all_ensemble, obs),
+            grid_all = KGE(grid_all, obs),
+            statn_all = KGE(statn_all, obs)) %>%
+    mutate_if(is.numeric,
+            round,
+            digits = 2)
+
+kable(mo_kge) %>%
+  kable_styling(full_width = F)
+
+mo_pivot <- mo_kge %>%
+  pivot_longer(!month, names_to = 'cal_run', values_to = 'KGE') %>%
+  drop_na()
+
+kge_plot_mo <- ggplot(mo_pivot, aes(month, KGE, color = cal_run)) + geom_point(size = 3) +
+  theme_bw()
+
+ggplotly(kge_plot_mo)
+
+```
+
+## RMSE
+
+### Ensemble RMSE for entire period
+
+```{r ensemble rmse, echo = F}
+
+ensem_rmse_all <- ensem %>%
+  ungroup() %>%
+  summarize(grid_ensemble = rmse(grid_ensemble, obs),
+            statn_ensemble = rmse(statn_ensemble, obs),
+            all_ensemble = rmse(all_ensemble, obs),
+            grid_all = rmse(grid_all, obs),
+            statn_all = rmse(statn_all, obs)) %>%
+    mutate_if(is.numeric,
+            round,
+            digits = 2)
+
+kable(ensem_rmse_all) %>%
+  kable_styling(full_width = F)
+
+```
+
+### Annual RMSE for ensembles
+
+```{r annual rmse ensem, echo = F}
+
+yr_rmse_ensem <- ensem %>%
+  ungroup() %>%
+  mutate(year = year(date)) %>%
+  group_by(year) %>%
+  summarize(grid_ensemble = rmse(grid_ensemble, obs),
+            statn_ensemble = rmse(statn_ensemble, obs),
+            all_ensemble = rmse(all_ensemble, obs),
+            grid_all = rmse(grid_all, obs),
+            statn_all = rmse(statn_all, obs)) %>%
+    mutate_if(is.numeric,
+            round,
+            digits = 2)
+
+yr_rmse_table <- yr_rmse_ensem %>%
+  pivot_longer(!year, names_to = 'model_run', values_to = 'rmse') %>%
+  pivot_wider(names_from = 'year', values_from = 'rmse')
+
+yr_rmse_table %>%
+  kable(.) %>%
+  kable_styling()
+
+yr_rmse_plot <- yr_rmse_ensem %>%
+  pivot_longer(!year, names_to = 'model_run', values_to = 'rmse') %>%
+  mutate(year = as.factor(year))
+
+#plot annual rmse vals for ensembles
+plot_rmse_yr_ensem <- function(calyear) {
+  yr_rmse_plot %>%
+    filter(year == calyear) %>%
+    ggplot(aes(x = model_run,
+               y = rmse)) +
+    geom_col() +
+    ggtitle(calyear) +
+    theme_bw() +
+    theme(axis.text.x = element_text(angle = 45, hjust=1))
+}
+
+name <- levels(yr_rmse_plot$year)
+
+lapply(name, plot_rmse_yr_ensem)
+
+```
+
+### Monthly RMSEs for ensembles
+
+```{r month ensem rmse, echo = F}
+
+mo_rmse <- ensem %>%
+  ungroup() %>%
+  mutate(month = month(date)) %>%
+  group_by(month) %>%
+  summarize(grid_ensemble = rmse(grid_ensemble, obs),
+            statn_ensemble = rmse(statn_ensemble, obs),
+            all_ensemble = rmse(all_ensemble, obs),
+            grid_all = rmse(grid_all, obs),
+            statn_all = rmse(statn_all, obs)) %>%
+    mutate_if(is.numeric,
+            round,
+            digits = 2)
+
+kable(mo_rmse) %>%
+  kable_styling(full_width = F)
+
+mo_pivot2 <- mo_rmse %>%
+  pivot_longer(!month, names_to = 'cal_run', values_to = 'RMSE') %>%
+  drop_na()
+
+rmse_plot_mo <- ggplot(mo_pivot2, aes(month, RMSE, color = cal_run)) + geom_point(size = 3) +
+  theme_bw()
+
+ggplotly(rmse_plot_mo)
 

### 2023-01-20 calibration_output.Rmd
added NSE, pbias, and cumulative Q plots. Need to make obs lines black

@@
             round,
-            digits = 2)
+            digits = 4)
 
@@
 ggplotly(rmse_plot_mo)
+
+```
+
+## NSE
+
+### Ensemble NSE for entire period
+
+```{r nse all, echo = F}
+
+ensem_nse_all <- ensem %>%
+  ungroup() %>%
+  summarize(grid_ensemble = NSE(grid_ensemble, obs),
+            statn_ensemble = NSE(statn_ensemble, obs),
+            all_ensemble = NSE(all_ensemble, obs),
+            grid_all = NSE(grid_all, obs),
+            statn_all = NSE(statn_all, obs)) %>%
+    mutate_if(is.numeric,
+            round,
+            digits = 2)
+
+kable(ensem_nse_all) %>%
+  kable_styling(full_width = F)
+
+```
+
+### Annual NSE for ensembles
+
+```{r annual nse, echo = F}
+
+yr_nse_ensem <- ensem %>%
+  ungroup() %>%
+  mutate(year = year(date)) %>%
+  group_by(year) %>%
+  summarize(grid_ensemble = NSE(grid_ensemble, obs),
+            statn_ensemble = NSE(statn_ensemble, obs),
+            all_ensemble = NSE(all_ensemble, obs),
+            grid_all = NSE(grid_all, obs),
+            statn_all = NSE(statn_all, obs)) %>%
+    mutate_if(is.numeric,
+            round,
+            digits = 4)
+
+yr_nse_table <- yr_nse_ensem %>%
+  pivot_longer(!year, names_to = 'model_run', values_to = 'nse') %>%
+  pivot_wider(names_from = 'year', values_from = 'nse')
+
+yr_nse_table %>%
+  kable(.) %>%
+  kable_styling()
+
+yr_nse_plot <- yr_nse_ensem %>%
+  pivot_longer(!year, names_to = 'model_run', values_to = 'nse') %>%
+  mutate(year = as.factor(year))
+
+#plot annual nse vals for ensembles
+plot_nse_yr_ensem <- function(calyear) {
+  yr_nse_plot %>%
+    filter(year == calyear) %>%
+    ggplot(aes(x = model_run,
+               y = nse)) +
+    geom_col() +
+    ggtitle(calyear) +
+    theme_bw() +
+    theme(axis.text.x = element_text(angle = 45, hjust=1))
+}
+
+name <- levels(yr_nse_plot$year)
+
+lapply(name, plot_nse_yr_ensem)
+
+```
+
+### Monthly NSE for ensembles
+
+```{r monthly rmse, echo =F}
+
+mo_nse <- ensem %>%
+  ungroup() %>%
+  mutate(month = month(date)) %>%
+  group_by(month) %>%
+  summarize(grid_ensemble = NSE(grid_ensemble, obs),
+            statn_ensemble = NSE(statn_ensemble, obs),
+            all_ensemble = NSE(all_ensemble, obs),
+            grid_all = NSE(grid_all, obs),
+            statn_all = NSE(statn_all, obs)) %>%
+    mutate_if(is.numeric,
+            round,
+            digits = 4)
+
+kable(mo_nse) %>%
+  kable_styling(full_width = F)
+
+mo_pivot2 <- mo_nse %>%
+  pivot_longer(!month, names_to = 'cal_run', values_to = 'nse') %>%
+  drop_na()
+
+nse_plot_mo <- ggplot(mo_pivot2, aes(month, nse, color = cal_run)) + geom_point(size = 3) +
+  theme_bw()
+
+ggplotly(nse_plot_mo)
+
+```
+
+## Percent bias
+
+Positive values indicate model overestimation and negative values model underestimation.
+
+### Ensemble pbias for entire period
+
+```{r nse all, echo = F}
+
+ensem_pbias_all <- ensem %>%
+  ungroup() %>%
+  summarize(grid_ensemble = pbias(grid_ensemble, obs),
+            statn_ensemble = pbias(statn_ensemble, obs),
+            all_ensemble = pbias(all_ensemble, obs),
+            grid_all = pbias(grid_all, obs),
+            statn_all = pbias(statn_all, obs))
+
+kable(ensem_pbias_all) %>%
+  kable_styling(full_width = F)
+
+```
+
+### Annual pbias for ensembles
+
+```{r annual nse, echo = F}
+
+yr_pbias_ensem <- ensem %>%
+  ungroup() %>%
+  mutate(year = year(date)) %>%
+  group_by(year) %>%
+  summarize(grid_ensemble = pbias(grid_ensemble, obs),
+            statn_ensemble = pbias(statn_ensemble, obs),
+            all_ensemble = pbias(all_ensemble, obs),
+            grid_all = pbias(grid_all, obs),
+            statn_all = pbias(statn_all, obs))
+
+yr_pbias_table <- yr_pbias_ensem %>%
+  pivot_longer(!year, names_to = 'model_run', values_to = 'pbias') %>%
+  pivot_wider(names_from = 'year', values_from = 'pbias')
+
+yr_pbias_table %>%
+  kable(.) %>%
+  kable_styling()
+
+yr_pbias_plot <- yr_pbias_ensem %>%
+  pivot_longer(!year, names_to = 'model_run', values_to = 'pbias') %>%
+  mutate(year = as.factor(year))
+
+#plot annual pbias vals for ensembles
+plot_pbias_yr_ensem <- function(calyear) {
+  yr_pbias_plot %>%
+    filter(year == calyear) %>%
+    ggplot(aes(x = model_run,
+               y = pbias)) +
+    geom_col() +
+    ggtitle(calyear) +
+    theme_bw() +
+    theme(axis.text.x = element_text(angle = 45, hjust=1))
+}
+
+name <- levels(yr_pbias_plot$year)
+
+lapply(name, plot_pbias_yr_ensem)
+
+```
+
+### Monthly pbias for ensembles
+
+```{r monthly rmse, echo =F}
+
+mo_pbias <- ensem %>%
+  ungroup() %>%
+  mutate(month = month(date)) %>%
+  group_by(month) %>%
+  summarize(grid_ensemble = pbias(grid_ensemble, obs),
+            statn_ensemble = pbias(statn_ensemble, obs),
+            all_ensemble = pbias(all_ensemble, obs),
+            grid_all = pbias(grid_all, obs),
+            statn_all = pbias(statn_all, obs)) %>%
+    mutate_if(is.numeric,
+            round,
+            digits = 4)
+
+kable(mo_pbias) %>%
+  kable_styling(full_width = F)
+
+mo_pivot2 <- mo_pbias %>%
+  pivot_longer(!month, names_to = 'cal_run', values_to = 'pbias') %>%
+  drop_na()
+
+pbias_plot_mo <- ggplot(mo_pivot2, aes(month, pbias, color = cal_run)) + geom_point(size = 3) +
+  theme_bw()
+
+ggplotly(pbias_plot_mo)
+
+```
+
+## Cumulative Q
+
+```{r}
+
+ensem_cumq <- ensem %>%
+  mutate(month = month(date)) %>%
+  filter(month %in% c(4:9)) %>%
+  select(-month) %>% 
+  pivot_longer(!date, names_to = 'cal_run', values_to = 'q_m3s') %>%
+  group_by(cal_run, year(date)) %>%
+  mutate(cumsum = cumsum(replace_na(q_m3s, 0))) %>%
+  rename(year = 4) %>%
+  mutate(year = as.factor(year))
+
+#plot annual cumulative Q vals for ensembles
+plot_cumulq_yr_ensem <- function(calyear) {
+  {ensem_cumq %>%
+    filter(year == calyear) %>%
+    ggplot(aes(x = date,
+               y = cumsum,
+               color = cal_run)) +
+    geom_line() +
+    geom_line(data=ensem_cumq[ensem_cumq$cal_run=='obs',], aes(group=cal_run), color = "black") +
+    ggtitle(calyear) +
+    theme_bw() +
+    labs(y = 'cumulative Q (m3s)')} %>%
+    ggplotly()
+}
+
+name <- levels(ensem_cumq$year)
+
+cumulative_plots <- lapply(name, plot_cumulq_yr_ensem)
+
+htmltools::tagList(cumulative_plots)
+
+cumulative_plots
 

### 2023-01-24 calibration_output.Rmd
added cumulative flows, percentiles, catchment precip & tmean

@@
 q <- ggplot(flow_pivot, aes(date, q_m3s, color = cal_run)) +
-  geom_line()
+  geom_line() +
+  scale_color_manual(name="cal_run", values=c('obs' = 'black',
+                                            "grid_2011"="seagreen", 
+                                            "grid_2012"="seagreen2", 
+                                            "grid_2013"="steelblue",
+                                            "grid_2014"='dodgerblue', 
+                                            "grid_2015" = "cyan3",
+                                            'grid_2016' = 'blue',
+                                            'grid_2017' = 'blue4',
+                                            'grid_2018' = 'cadetblue',
+                                            'grid_2019' = 'lightgreen',
+                                            'grid_2020' = 'olivedrab',
+                                            'grid_all' = 'steelblue3',
+                                            "statn_2011"="maroon", 
+                                            "statn_2012"="deeppink4", 
+                                            "statn_2013"="deeppink",
+                                            "statn_2014"='purple', 
+                                            "statn_2015" = "mediumorchid1",
+                                            'statn_2016' = 'indianred',
+                                            'statn_2017' = 'sienna',
+                                            'statn_2018' = 'salmon2',
+                                            'statn_2019' = 'mediumpurple1',
+                                            'statn_2020' = 'violetred',
+                                            'statn_all' = 'red'))
 
@@
     geom_line() +
+        scale_color_manual(name="cal_run", values=c('obs' = 'black',
+                                            "grid_2011"="seagreen", 
+                                            "grid_2012"="seagreen2", 
+                                            "grid_2013"="steelblue",
+                                            "grid_2014"='dodgerblue', 
+                                            "grid_2015" = "cyan3",
+                                            'grid_2016' = 'blue',
+                                            'grid_2017' = 'blue4',
+                                            'grid_2018' = 'cadetblue',
+                                            'grid_2019' = 'lightgreen',
+                                            'grid_2020' = 'olivedrab',
+                                            'grid_all' = 'steelblue3',
+                                            "statn_2011"="maroon", 
+                                            "statn_2012"="deeppink4", 
+                                            "statn_2013"="deeppink",
+                                            "statn_2014"='purple', 
+                                            "statn_2015" = "mediumorchid1",
+                                            'statn_2016' = 'indianred',
+                                            'statn_2017' = 'sienna',
+                                            'statn_2018' = 'salmon2',
+                                            'statn_2019' = 'mediumpurple1',
+                                            'statn_2020' = 'violetred',
+                                            'statn_all' = 'red')) +
     ggtitle(calyear) +
@@
 
+try
 ```
@@
 
-kge_plot_cy <- ggplot(flow_plot, aes(year, kge, color = model_run)) + geom_point(size = 3) +
+kge_plot_cy <- ggplot(flow_plot, aes(year, kge, color = model_run)) + 
+  geom_point(size = 3) +
+  scale_color_manual(name="model_run", values=c("grid2011"="seagreen", 
+                                            "grid2012"="seagreen2", 
+                                            "grid2013"="steelblue",
+                                            "grid2014"='dodgerblue', 
+                                            "grid2015" = "cyan3",
+                                            'grid2016' = 'blue',
+                                            'grid2017' = 'blue4',
+                                            'grid2018' = 'cadetblue',
+                                            'grid2019' = 'lightgreen',
+                                            'grid2020' = 'olivedrab',
+                                            'gridall' = 'steelblue3',
+                                            "statn2011"="maroon", 
+                                            "statn2012"="deeppink4", 
+                                            "statn2013"="deeppink",
+                                            "statn2014"='purple', 
+                                            "statn2015" = "mediumorchid1",
+                                            'statn2016' = 'indianred',
+                                            'statn2017' = 'sienna',
+                                            'statn2018' = 'salmon2',
+                                            'statn2019' = 'mediumpurple1',
+                                            'statn2020' = 'violetred',
+                                            'statnall' = 'red')) +
   theme_bw()
@@
 q_ensemble <- ggplot(ensem_pivot, aes(date, q_m3s, color = cal_run)) +
-  geom_line()
+  geom_line() +
+  scale_color_manual(name="cal_run", values=c('obs'='black',
+                                            "grid_ensemble"="maroon", 
+                                            "statn_ensemble"="darkturquoise", 
+                                            "grid_all"="purple1",
+                                            "statn_all"='springgreen4', 
+                                            "all_ensemble" = "orange"))
 
@@
     geom_line() +
+    scale_color_manual(name="cal_run", values=c('obs' = 'black',
+                                            "grid_ensemble"="maroon", 
+                                            "statn_ensemble"="darkturquoise", 
+                                            "grid_all"="purple1",
+                                            "statn_all"='springgreen4', 
+                                            "all_ensemble" = "orange")) +
     ggtitle(calyear) +
@@
 htmltools::tagList(try)
+
+try
 
@@
 kge_plot_mo <- ggplot(mo_pivot, aes(month, KGE, color = cal_run)) + geom_point(size = 3) +
+    scale_color_manual(name="cal_run", values=c("grid_ensemble"="maroon", 
+                                            "statn_ensemble"="darkturquoise", 
+                                            "grid_all"="purple1",
+                                            "statn_all"='springgreen4', 
+                                            "all_ensemble" = "orange")) +
   theme_bw()
@@
 rmse_plot_mo <- ggplot(mo_pivot2, aes(month, RMSE, color = cal_run)) + geom_point(size = 3) +
+    scale_color_manual(name="cal_run", values=c("grid_ensemble"="maroon", 
+                                            "statn_ensemble"="darkturquoise", 
+                                            "grid_all"="purple1",
+                                            "statn_all"='springgreen4', 
+                                            "all_ensemble" = "orange")) +
   theme_bw()
@@
   ungroup() %>%
+  drop_na() %>% 
   mutate(month = month(date)) %>%
@@
 nse_plot_mo <- ggplot(mo_pivot2, aes(month, nse, color = cal_run)) + geom_point(size = 3) +
-  theme_bw()
+  theme_bw() +
+  scale_color_manual(name="cal_run", values=c("grid_ensemble"="maroon", 
+                                            "statn_ensemble"="darkturquoise", 
+                                            "grid_all"="purple1",
+                                            "statn_all"='springgreen4', 
+                                            "all_ensemble" = "orange"))
 
@@
 
-```{r nse all, echo = F}
+```{r pbias all, echo = F}
 
@@
 
-```{r annual nse, echo = F}
+```{r annualpbias, echo = F}
 
@@
 
-```{r monthly rmse, echo =F}
+```{r monthly pbias, echo =F}
 
@@
 
-pbias_plot_mo <- ggplot(mo_pivot2, aes(month, pbias, color = cal_run)) + geom_point(size = 3) +
+pbias_plot_mo <- ggplot(mo_pivot2, aes(month, pbias, color = cal_run)) + 
+  geom_point(size = 3) +
+  scale_color_manual(name="cal_run", values=c("grid_ensemble"="maroon", 
+                                            "statn_ensemble"="darkturquoise", 
+                                            "grid_all"="purple1",
+                                            "statn_all"='springgreen4', 
+                                            "all_ensemble" = "orange")) +
   theme_bw()
@@
 
-```{r}
+```{r cumq, echo = F}
 
@@
   rename(year = 4) %>%
-  mutate(year = as.factor(year))
+  mutate(year = as.factor(year)) %>%
+  ungroup()
 
@@
     geom_line() +
-    geom_line(data=ensem_cumq[ensem_cumq$cal_run=='obs',], aes(group=cal_run), color = "black") +
+    scale_color_manual(name="cal_run", values=c("obs"="black",
+                                             "grid_ensemble"="maroon", 
+                                            "statn_ensemble"="darkturquoise", 
+                                            "grid_all"="purple1",
+                                            "statn_all"='springgreen4', 
+                                            "all_ensemble" = "orange")) +
     ggtitle(calyear) +
@@
 cumulative_plots
+
+```
+
+## Percentiles
+
+```{r percentiles, echo = F}
+
+quantile_calc <- function(x, probs, date) {
+  tibble(x = quantile(x, probs), probs = probs,
+         date = date[x = quantile(x, probs)])
+}
+
+percent <- ensem_cumq %>%
+  group_by(year, cal_run) %>%
+  summarize(quantile_calc(cumsum, c(0.25, 0.5, 0.75), date)) %>%
+  mutate(date = as.Date(date)) %>%
+  mutate(probs = as.factor(probs))
+
+###
+# quantile_cal <- function(data, prob) {
+#   data %>%
+#     dplyr::group_by(cal_run, year) %>%
+#     mutate(quantile = paste0(prob),
+#            value = quantile(cumsum, prob)) %>%
+#     filter(cumsum >= value) %>%
+#     filter(date == min(date))
+#   }
+# 
+# quantiles <- c(0.25, 0.5, 0.75)
+# 
+# quants <- quantiles %>% 
+#   map(~ quantile_cal(data = ensem_cumq, prob = .)) %>%
+#   bind_rows()
+####
+
+#plot percentiles
+plot_perc_ensem <- function(perc) {
+  {percent %>%
+    filter(probs == perc) %>%
+    ggplot(aes(x = year,
+               y = x,
+               color = cal_run)) +
+    geom_point(size=3) +
+    scale_color_manual(name="cal_run", values=c("obs"="black",
+                                             "grid_ensemble"="maroon", 
+                                            "statn_ensemble"="darkturquoise", 
+                                            "grid_all"="purple1",
+                                            "statn_all"='springgreen4', 
+                                            "all_ensemble" = "orange")) +
+    ggtitle(perc) +
+    ylab('Streamflow (cms)') +
+    theme_bw()} %>%
+    ggplotly()
+}
+
+name <- levels(percent$probs)
+
+perc_plots <- lapply(name, perc_plots)
+
+htmltools::tagList(plot_perc_ensem)
+
+perc_plots
+
+```
+
+# Catchment results
+
+```{r catch, echo = F}
+
+setwd("C:/Users/sears/Documents/Repos/fourmile/catchments")
+
+statn <- read_csv('statnall.csv')
+grid <- read_csv('gridall.csv')
+
+grid <- grid %>% mutate(site = 'grid')
+statn <- statn %>% mutate(site = 'statn')
+
+catchment <- bind_rows(grid, statn) %>%
+  mutate(year = as.factor(year(time))) %>%
+  group_by(year, site) %>%
+  mutate(cumulative_p = cumsum(precip))
+
+#plot cumulative precip by year
+plot_cumprecip <- function(calyear) {
+  {catchment %>%
+    filter(year == calyear) %>%
+    ggplot(aes(x = time,
+               y = cumulative_p, color = site)) +
+    geom_line(size=1) +
+    ggtitle(calyear) +
+    ylab('Cumulative precip (mm)') +
+    theme_bw() +
+    theme(axis.text.x = element_text(angle = 45, hjust=1))} %>%
+    ggplotly()
+}
+
+name <- levels(catchment$year)
+
+precip_plots <- lapply(name, plot_cumprecip)
+
+htmltools::tagList(precip_plots)
+
+precip_plots
+
+## total P
+max_cumulativep <- catchment %>%
+  group_by(year, site) %>%
+  summarize(total_cumulativep = max(cumulative_p))
+
+ggplot(max_cumulativep, aes(x=year, y=total_cumulativep, color=site)) + 
+  geom_point(size=3) +
+  ggtitle('Total cumulative precip (mm) by year')
+
+##tmean 
+tmean <- catchment %>%
+  group_by(year, site) %>%
+  summarize(tmean = mean(tmean)) %>%
+  ggplot(aes(x = year, y=tmean, color = site)) +
+  geom_point(size=3) +
+  ggtitle('Average temp by year')
+
+tmean
 

### 2023-01-24 calibration_output.Rmd
ready for meeting. Still need to figure out dates of percentiles and SWE comparison for Niwot

@@
 ###
-# quantile_cal <- function(data, prob) {
-#   data %>%
-#     dplyr::group_by(cal_run, year) %>%
-#     mutate(quantile = paste0(prob),
-#            value = quantile(cumsum, prob)) %>%
-#     filter(cumsum >= value) %>%
-#     filter(date == min(date))
-#   }
-# 
-# quantiles <- c(0.25, 0.5, 0.75)
-# 
-# quants <- quantiles %>% 
-#   map(~ quantile_cal(data = ensem_cumq, prob = .)) %>%
-#   bind_rows()
+quantile_cal <- function(data, prob) {
+  data %>%
+    dplyr::group_by(cal_run, year) %>%
+    mutate(quantile = paste0(prob),
+           value = quantile(cumsum, prob)) %>%
+    group_by(cal_run, year, quantile) %>% 
+    filter(cumsum >= value) %>%
+    filter(date == min(date))
+  }
+
+quantiles <- c(0.25, 0.5, 0.75)
+
+quants <- quantiles %>%
+  map(~ quantile_cal(data = ensem_cumq, prob = .)) %>%
+  bind_rows()
 ####
@@
 
-perc_plots <- lapply(name, perc_plots)
-
-htmltools::tagList(plot_perc_ensem)
+perc_plots <- lapply(name, plot_perc_ensem)
+
+htmltools::tagList(perc_plots)
 
@@
 
-##tmean 
+## tmean 
 tmean <- catchment %>%
@@
 tmean
+
+```
+
+## Niwot
+
+### SWE
+
+-Look at SWE dataframe as a group
+
+```{r niwot, echo = F}
+library(snotelr)
+
+niwot_snotel <- snotel_download(site_id = 663, internal = T)
+
+niwot_snotel <- niwot_snotel %>%
+  select(date, snow_water_equivalent, precipitation) %>%
+  mutate(date = as.Date(date)) %>%
+  rename(swe_mm_snotel = snow_water_equivalent,
+         precip_mm_snotel = precipitation) %>%
+  #mutate(swe_mm_snotel = swe_mm_snotel*25.4,
+         #precip_mm_snotel = precip_mm_snotel*25.4) %>%
+  filter(date > '2010-12-31' & date < '2020-10-01')
+
+hru7_grid <- read_csv('C:/Users/sears/Documents/Repos/fourmile/HRU_output/HRU_7_grid.csv') %>%
+  select(date, precip_mm, swe_mm) %>%
+  rename(precip_mm_hrugrid = precip_mm,
+         swe_mm_hrugrid = swe_mm)
+
+hru7_statn <- read_csv('C:/Users/sears/Documents/Repos/fourmile/HRU_output/HRU_7_statn.csv') %>%
+  select(date, precip_mm, swe_mm) %>%
+  rename(precip_mm_hrustatn = precip_mm,
+         swe_mm_hrustatn = swe_mm)
+
+niwot <- niwot_snotel %>%
+  left_join(hru7_grid, by = 'date') %>%
+  left_join(hru7_statn, by = 'date')
+
+#look at swe -- ****** ask about this
+niwot_swe <- niwot %>%
+  dplyr::select(date, swe_mm_snotel, swe_mm_hrugrid, swe_mm_hrustatn) %>%
+  mutate(swe_mm_snotel2 = swe_mm_snotel - lag(swe_mm_snotel))
+
+kable(niwot_swe) %>%
+  kable_styling(full_width = F) %>% 
+  scroll_box(width = "100%", height = "500px")
+
+# niwot_swe <- niwot_swe %>% 
+#   pivot_longer(!date, names_to = 'source', values_to = 'swe_mm')
+
+```
+
+### ET
+
+```{r ET, echo = F}
+
+niwot_et <- read_csv('C:/Users/sears/Documents/Repos/fourmile/HRU_output/Niwot_daily_et.csv') %>%
+  filter(year > 2010) %>%
+  mutate(date = make_date(year = year, month = month, day = day)) %>%
+  select(date, et) %>%
+  rename(et_niwot = et)
+
+hru7_grid <- read_csv('C:/Users/sears/Documents/Repos/fourmile/HRU_output/HRU_7_grid.csv') %>%
+  select(date, AET_mm) %>%
+  rename(et_hru7grid = AET_mm)
+
+hru7_statn <- read_csv('C:/Users/sears/Documents/Repos/fourmile/HRU_output/HRU_7_statn.csv') %>%
+  select(date, AET_mm) %>%
+  rename(et_hru7statn = AET_mm)
+
+niwot_et_compare <- niwot_et %>%
+  left_join(hru7_grid, by = 'date') %>%
+  left_join(hru7_statn, by = 'date') %>%
+  mutate(year = year(date)) %>%
+  filter(year < 2021) %>% 
+  pivot_longer(!c(date, year), names_to= 'source', values_to = 'et_mm') %>%
+  mutate(year = as.factor(year))
+
+#plot ET by year
+plot_ET <- function(calyear) {
+  {niwot_et_compare %>%
+    filter(year == calyear) %>%
+    ggplot(aes(x = date,
+               y = et_mm, color = source)) +
+    geom_line(size=1) +
+    ggtitle(calyear) +
+    ylab('ET (mm/day)') +
+    theme_bw() +
+    theme(axis.text.x = element_text(angle = 45, hjust=1))} %>%
+    ggplotly()
+}
+
+name <- levels(niwot_et_compare$year)
+
+ET_plots <- lapply(name, plot_ET)
+
+htmltools::tagList(ET_plots)
+
+ET_plots
 

### 2023-01-30 calibration_output.Rmd
added: map, boulder creek n75th gage, maxQ prior to Apr1, compairson of niwot & hru7 precip, comparison of niwot % hru7 ET

@@
 library(hydroGOF)
+library(sp)
+library(raster)
+library(sf)
+library(mapview)
+library(here)
+library(scales)
+library(dataRetrieval)
 
@@
 # Outlet results
+
+```{r map, echo = F}
+
+locations <- read_csv(here('data/GIS', 'fourmile_sensors.csv'))
+
+hrus <- st_read(here('data/GIS', 'hrus_final.shp'))
+
+locations <- locations %>%
+  st_as_sf(., coords=c('y','x'), crs = 4326)
+
+mapviewOptions(basemaps = c("Esri.WorldShadedRelief", "OpenStreetMap.DE"),
+               layers.control.pos = "topright")
+
+mapview(locations, zcol = 'type') + mapview(hrus)
+
+```
 
@@
 
+```{r boulder cr gage, echo = F}
+
+#pull in Boulder Creek @ N 75th gage
+
+bouldcr <- readNWISdv(siteNumbers = "06730200",
+                          parameterCd = "00060", 
+                          startDate = "2011-01-01", 
+                          endDate = "2020-12-31")  %>%
+  select(date = Date,
+         q_cfs = X_00060_00003) %>%
+  mutate(bouldcr = q_cfs/35.3146662) %>%
+  select(-q_cfs) %>%
+  mutate(year = year(date))
+
+```
+
 ```{r ensemble hydrographs, echo = F}
@@
                                             "statn_all"='springgreen4', 
-                                            "all_ensemble" = "orange"))
-
-ggplotly(q_ensemble)
+                                            "all_ensemble" = "orange")) +
+  geom_line(data = bouldcr, aes(date, bouldcr/10), color = 'darkgrey') +
+  scale_y_continuous(name = 'Q_m3s',
+                    sec.axis = sec_axis(~.*10, name='BoulderCr_cms')) +
+  theme_bw()
+
+ggplotly(q_ensemble) %>%
+  add_lines(data=bouldcr, x=~date, y=~bouldcr, colors=NULL, yaxis="y2", 
+              inherit=FALSE, showlegend = FALSE) %>%
+  layout(yaxis2 = list(overlaying = "y", side = "right",
+                       color = 'darkgray',
+                       title = "BoulderCr_cms"),
+         legend = list(x = 1.1, y = 0.95))
 
@@
     ggtitle(calyear) +
-    theme_bw()} %>%
+    theme_bw()
+    } %>%
     ggplotly()
-
 }
@@
 
+## Max Q prior to April 1
+
+```{r}
+
+ensem_bould <- left_join(ensem, bouldcr, by = 'date') %>%
+  pivot_longer(!c(date, year), names_to = 'source', values_to = 'q_m3s') %>%
+  mutate(month = month(date)) %>%
+  filter(month %in% 1:3) %>%
+  group_by(source, year) %>%
+  slice_max(q_m3s, n=1)
+
+early_peakq <- ensem_bould %>%
+  mutate(doy = yday(date)) %>%
+  select(c(doy, source, q_m3s, year)) %>%
+  pivot_wider(names_from = 'source', values_from = c('q_m3s', 'doy'))
+
+ggplot(early_peakq, aes(doy_bouldcr, doy_all_ensemble)) +
+  geom_point(size=2.5) +
+  geom_abline(intercept = 0, slope = 1, size=1, color='red') +
+  theme_bw() +
+  ggtitle('DOY of peak Q prior to April 1st - All Ensemble')
+
+ggplot(early_peakq, aes(doy_bouldcr, doy_grid_all)) +
+  geom_point(size=2.5) +
+  geom_abline(intercept = 0, slope = 1, size=1, color='red') +
+  theme_bw() +
+  ggtitle('DOY of peak Q prior to April 1st - Grid All')
+
+ggplot(early_peakq, aes(doy_bouldcr, doy_grid_ensemble)) +
+  geom_point(size=2.5) +
+  geom_abline(intercept = 0, slope = 1, size=1, color='red') +
+  theme_bw() +
+  ggtitle('DOY of peak Q prior to April 1st - Grid Ensemble')
+
+ggplot(early_peakq, aes(doy_bouldcr, doy_statn_all)) +
+  geom_point(size=2.5) +
+  geom_abline(intercept = 0, slope = 1, size=1, color='red') +
+  theme_bw() +
+  ggtitle('DOY of peak Q prior to April 1st - Station All')
+
+ggplot(early_peakq, aes(doy_bouldcr, doy_statn_ensemble)) +
+  geom_point(size=2.5) +
+  geom_abline(intercept = 0, slope = 1, size=1, color='red') +
+  theme_bw() +
+  ggtitle('DOY of peak Q prior to April 1st - Station Ensemble')
+
+early_peakq_table <- ensem_bould %>%
+  mutate(doy = yday(date)) %>%
+  dplyr::arrange(date)
+
+kable(early_peakq_table) %>%
+  kable_styling(full_width = F) %>% 
+  scroll_box(width = "100%", height = "500px")
+
+```
+
 # Catchment results
 
-```{r catch, echo = F}
-
-setwd("C:/Users/sears/Documents/Repos/fourmile/catchments")
+## Precip
+
+```{r catch precip, echo = F}
+setwd("C:/Users/sears/Documents/Repos/fourmile/catchment_output")
 
@@
 
+```
+
+## Tmean
+
+```{r tmean catch, echo = F}
 ## tmean 
@@
 
-## Niwot
-
-### SWE
-
--Look at SWE dataframe as a group
+# Niwot and HRU7
+
+## SWE and precip
 
@@
 
-#look at swe -- ****** ask about this
+# look at swe
 niwot_swe <- niwot %>%
-  dplyr::select(date, swe_mm_snotel, swe_mm_hrugrid, swe_mm_hrustatn) %>%
-  mutate(swe_mm_snotel2 = swe_mm_snotel - lag(swe_mm_snotel))
+  dplyr::select(date, swe_mm_snotel, swe_mm_hrugrid, swe_mm_hrustatn)
 
@@
 
-# niwot_swe <- niwot_swe %>% 
-#   pivot_longer(!date, names_to = 'source', values_to = 'swe_mm')
-
-```
-
-### ET
+# cumulative swe
+niwot_swe2 <- niwot_swe %>%
+  mutate(year = year(date)) %>%
+  pivot_longer(!c(date,year), names_to = 'source', values_to = 'swe_mm') %>%
+  group_by(year, source) %>%
+  mutate(swe_cumsum_mm = cumsum(swe_mm))
+
+cum_swe_niwot <- ggplot(niwot_swe2, aes(date, swe_cumsum_mm, color = source)) +
+  geom_line() +
+  scale_x_date(labels = date_format("%b")) +
+  facet_wrap(~year, scales = 'free')
+
+ggplotly(cum_swe_niwot)
+
+#look at precip
+niwot_p <- niwot %>%
+  dplyr::select(date, precip_mm_snotel, precip_mm_hrugrid, precip_mm_hrustatn)
+
+kable(niwot_p) %>%
+  kable_styling(full_width = F) %>% 
+  scroll_box(width = "100%", height = "500px")
+
+# cumulative precip
+niwot_p2 <- niwot_p %>%
+  mutate(year = year(date)) %>%
+  pivot_longer(!c(date,year), names_to = 'source', values_to = 'precip_mm') %>%
+  group_by(year, source) %>%
+  mutate(p_cumsum_mm = cumsum(precip_mm))
+
+cum_precip_niwot <- ggplot(niwot_p2, aes(date, p_cumsum_mm, color = source)) +
+  geom_line() +
+  scale_x_date(labels = date_format("%b")) +
+  facet_wrap(~year, scales = 'free')
+
+ggplotly(cum_precip_niwot)
+
+```
+
+## ET
 
@@
 ET_plots
+
+# 1:1 scatter plots for Niwot vs grid and Niwot vs station
+niwot_et_scatter <- niwot_et_compare %>%
+  filter(et_mm > 0)
+
+# Niwot vs grid
+et_grid_obs <- niwot_et_scatter %>%
+  filter(source == c('et_niwot','et_hru7grid')) %>%
+  pivot_wider(names_from = 'source', values_from = 'et_mm')
+
+#scatter of grid vs niwot
+et_scatter_grid_obs <- ggplot(et_grid_obs, aes(x = et_niwot, y = et_hru7grid)) +
+  geom_point() +
+  geom_abline(intercept = 0, slope = 1, size=1, color='red') + 
+  ggtitle('Niwot ET vs. HRU7 grid ET')
+
+et_scatter_grid_obs
+
+# Niwot vs statn inputs
+et_statn_obs <- niwot_et_scatter %>%
+  filter(source == c('et_niwot','et_hru7statn')) %>%
+  pivot_wider(names_from = 'source', values_from = 'et_mm')
+
+#scatter of grid vs niwot
+et_scatter_statn_obs <- ggplot(et_statn_obs, aes(x = et_niwot, y = et_hru7statn)) +
+  geom_point() +
+  geom_abline(intercept = 0, slope = 1, size=1, color='red') + 
+  ggtitle('Niwot ET vs. HRU7 station ET')
+
+et_scatter_statn_obs
 

### 2023-01-30 sp_mean.R

@@ -1,37 +1,0 @@
-library(raster)
-library(sp)
-library(tidyverse)
-library(rgdal)
-library(osmdata)
-library(sf)
-library(mapview)
-
-
-setwd('D:/CPF/snowpersistence_2010_2020')
-
-#pull in all filenames with .tif
-names <- list.files('.', pattern='.tif', full.names=F)
-
-#stack, stack, stack it up
-allrasties <- stack(names)
-
-meanrastie <- calc(allrasties, fun = mean, na.rm=T)
-
-#clip to CO
-states <- raster::getData("GADM", country = "United States", level = 1)
-states
-
-state_proj <- spTransform(states, crs(meanrastie)) %>%
-  st_as_sf(state_proj)
-
-co <- state_proj %>%
-  filter(NAME_1 == 'Colorado')
-
-co_sp <- crop(meanrastie, extent(co))
-
-plot(co_sp)
-
-writeRaster(co_sp, filename = 'co_sp_2020to2020.tif')
-
-
-mapview(co_sp, col.regions = list("brown", 'purple', 'blue', 'white'), at = seq(0, 100, 25))

### 2023-01-31 calibration_output.Rmd
push html

@@
                           endDate = "2020-12-31")  %>%
-  select(date = Date,
+  dplyr::select(date = Date,
          q_cfs = X_00060_00003) %>%
   mutate(bouldcr = q_cfs/35.3146662) %>%
-  select(-q_cfs) %>%
+  dplyr::select(-q_cfs) %>%
   mutate(year = year(date))
@@
                                grid_all, statn_all))) %>%
-  select(date, grid_ensemble, statn_ensemble, 
+  dplyr::select(date, grid_ensemble, statn_ensemble, 
          all_ensemble, grid_all, 
@@
   filter(month %in% c(4:9)) %>%
-  select(-month) %>% 
+  dplyr::select(-month) %>% 
   pivot_longer(!date, names_to = 'cal_run', values_to = 'q_m3s') %>%
@@
 
-```{r}
+```{r early max q, echo = F}
 
@@
   mutate(doy = yday(date)) %>%
-  select(c(doy, source, q_m3s, year)) %>%
+  dplyr::select(c(doy, source, q_m3s, year)) %>%
   pivot_wider(names_from = 'source', values_from = c('q_m3s', 'doy'))
@@
 niwot_snotel <- niwot_snotel %>%
-  select(date, snow_water_equivalent, precipitation) %>%
+  dplyr::select(date, snow_water_equivalent, precipitation) %>%
   mutate(date = as.Date(date)) %>%
@@
 hru7_grid <- read_csv('C:/Users/sears/Documents/Repos/fourmile/HRU_output/HRU_7_grid.csv') %>%
-  select(date, precip_mm, swe_mm) %>%
+  dplyr::select(date, precip_mm, swe_mm) %>%
   rename(precip_mm_hrugrid = precip_mm,
@@
 hru7_statn <- read_csv('C:/Users/sears/Documents/Repos/fourmile/HRU_output/HRU_7_statn.csv') %>%
-  select(date, precip_mm, swe_mm) %>%
+  dplyr::select(date, precip_mm, swe_mm) %>%
   rename(precip_mm_hrustatn = precip_mm,
@@
 
-ggplotly(cum_swe_niwot)
+cum_swe_niwot
 
@@
 
-ggplotly(cum_precip_niwot)
+cum_precip_niwot
 
@@
   mutate(date = make_date(year = year, month = month, day = day)) %>%
-  select(date, et) %>%
+  dplyr::select(date, et) %>%
   rename(et_niwot = et)
@@
 hru7_grid <- read_csv('C:/Users/sears/Documents/Repos/fourmile/HRU_output/HRU_7_grid.csv') %>%
-  select(date, AET_mm) %>%
+  dplyr::select(date, AET_mm) %>%
   rename(et_hru7grid = AET_mm)
@@
 hru7_statn <- read_csv('C:/Users/sears/Documents/Repos/fourmile/HRU_output/HRU_7_statn.csv') %>%
-  select(date, AET_mm) %>%
+  dplyr::select(date, AET_mm) %>%
   rename(et_hru7statn = AET_mm)

### 2023-01-31 calibration_output.Rmd
finished for meeting

@@
 # Outlet results
-
-```{r map, echo = F}
-
-locations <- read_csv(here('data/GIS', 'fourmile_sensors.csv'))
-
-hrus <- st_read(here('data/GIS', 'hrus_final.shp'))
-
-locations <- locations %>%
-  st_as_sf(., coords=c('y','x'), crs = 4326)
-
-mapviewOptions(basemaps = c("Esri.WorldShadedRelief", "OpenStreetMap.DE"),
-               layers.control.pos = "topright")
-
-mapview(locations, zcol = 'type') + mapview(hrus)
-
-```
 
@@
 
+## RD and RG
+
+```{r rd and rg, echo = F}
+
+gw_grid <- grid %>%
+  dplyr::select(time, genRD1, genRD2, genRG1, genRG2) %>%
+  mutate(source = 'grid')
+
+gw_statn <- statn %>%
+  dplyr::select(time, genRD1, genRD2, genRG1, genRG2) %>%
+  mutate(source = 'statn')
+
+gw <- bind_rows(gw_grid, gw_statn) %>%
+  mutate(year = year(time)) %>%
+  rename(date = time)
+
+ggplot(gw, aes(x=date, color = source)) +
+  geom_line(aes(y=genRD1)) +
+  facet_wrap(~year, scales = 'free') +
+  scale_x_date(labels = date_format("%b")) +
+  ggtitle('genRD1')
+
+ggplot(gw, aes(x=date, color = source)) +
+  geom_line(aes(y=genRD2)) +
+  facet_wrap(~year, scales = 'free') +
+  scale_x_date(labels = date_format("%b")) +
+  ggtitle('genRD2')
+
+ggplot(gw, aes(x=date, color = source)) +
+  geom_line(aes(y=genRG1)) +
+  facet_wrap(~year, scales = 'free') +
+  scale_x_date(labels = date_format("%b")) +
+  ggtitle('genRG1')
+
+ggplot(gw, aes(x=date, color = source)) +
+  geom_line(aes(y=genRG2)) +
+  facet_wrap(~year, scales = 'free') +
+  scale_x_date(labels = date_format("%b")) +
+  ggtitle('genRG2')
+
+gw <- gw %>%
+  group_by(year, source) %>%
+  mutate(RD1cumsum = cumsum(genRD1),
+         RD2cumsum = cumsum(genRD2),
+         RG1cumsum = cumsum(genRG1),
+         RG2cumsum = cumsum(genRG2))
+
+ggplot(gw, aes(x=date, color = source)) +
+  geom_line(aes(y=RD1cumsum)) +
+  facet_wrap(~year, scales = 'free') +
+  scale_x_date(labels = date_format("%b")) +
+  ggtitle('Cumulative genRD1')
+
+ggplot(gw, aes(x=date, color = source)) +
+  geom_line(aes(y=RD2cumsum)) +
+  facet_wrap(~year, scales = 'free') +
+  scale_x_date(labels = date_format("%b")) +
+  ggtitle('Cumulative genRD2')
+
+ggplot(gw, aes(x=date, color = source)) +
+  geom_line(aes(y=RG1cumsum)) +
+  facet_wrap(~year, scales = 'free') +
+  scale_x_date(labels = date_format("%b")) +
+  ggtitle('Cumulative genRG1')
+
+ggplot(gw, aes(x=date, color = source)) +
+  geom_line(aes(y=RG2cumsum)) +
+  facet_wrap(~year, scales = 'free') +
+  scale_x_date(labels = date_format("%b")) +
+  ggtitle('Cumulative genRG2')
+
+```
+
+# HRU Map
+
+```{r map, echo = F}
+
+locations <- read_csv(here('data/GIS', 'fourmile_sensors.csv'))
+
+hrus <- st_read(here('data/GIS', 'hrus_final.shp'))
+
+locations <- locations %>%
+  st_as_sf(., coords=c('y','x'), crs = 4326)
+
+mapviewOptions(basemaps = c("Esri.WorldShadedRelief", "OpenStreetMap.DE"),
+               layers.control.pos = "topright")
+
+mapview(locations, zcol = 'type') + mapview(hrus)
+
+```
+
 # Niwot and HRU7
@@
 et_scatter_statn_obs
+
+```
+
+# Tmean for HRUs 7, 9, 22, 36
+
+```{r hru7 temp, echo = F}
+
+tmean7_grid <- read_csv('C:/Users/sears/Documents/Repos/fourmile/HRU_output/HRU_7_grid.csv') %>%
+  dplyr::select(date, tmean) %>%
+  rename(t7_grid = tmean)
+
+tmean7_statn <- read_csv('C:/Users/sears/Documents/Repos/fourmile/HRU_output/HRU_7_statn.csv') %>%
+  dplyr::select(date, tmean) %>%
+  rename(t7_statn = tmean)
+
+tmean9_grid <- read_csv('C:/Users/sears/Documents/Repos/fourmile/HRU_output/HRU_9_grid.csv') %>%
+  dplyr::select(date, tmean) %>%
+  rename(t9_grid = tmean)
+
+tmean9_statn <- read_csv('C:/Users/sears/Documents/Repos/fourmile/HRU_output/HRU_9_statn.csv') %>%
+  dplyr::select(date, tmean) %>%
+  rename(t9_statn = tmean)
+
+tmean22_grid <- read_csv('C:/Users/sears/Documents/Repos/fourmile/HRU_output/HRU_22_grid.csv') %>%
+  dplyr::select(date, tmean) %>%
+  rename(t22_grid = tmean)
+
+tmean22_statn <- read_csv('C:/Users/sears/Documents/Repos/fourmile/HRU_output/HRU_22_statn.csv') %>%
+  dplyr::select(date, tmean) %>%
+  rename(t22_statn = tmean)
+
+tmean36_grid <- read_csv('C:/Users/sears/Documents/Repos/fourmile/HRU_output/HRU_36_grid.csv') %>%
+  dplyr::select(date, tmean) %>%
+  rename(t36_grid = tmean)
+
+tmean36_statn <- read_csv('C:/Users/sears/Documents/Repos/fourmile/HRU_output/HRU_36_statn.csv') %>%
+  dplyr::select(date, tmean) %>%
+  rename(t36_statn = tmean)
+
+tmean_hrus <- list(tmean7_grid, tmean7_statn, tmean9_grid, 
+     tmean9_statn, tmean22_grid, tmean22_statn,
+     tmean36_grid, tmean36_statn)
+
+t_hrus <- tmean_hrus %>% reduce(left_join, by='date')
+
+t_hrus <- t_hrus %>%
+  mutate(year = year(date)) %>%
+  mutate(t7_diff = t7_statn - t7_grid,
+         t9_diff = t9_statn - t9_grid,
+         t22_diff = t22_statn - t22_grid,
+         t36_diff = t36_statn - t36_grid) %>%
+  group_by(year) %>%
+  mutate(t7_cumdiff = cumsum(t7_diff),
+         t9_cumdiff = cumsum(t9_diff),
+         t22_cumdiff = cumsum(t22_diff),
+         t36_cumdiff = cumsum(t36_diff))
+
+tmean_cumdiff_plot <- ggplot(t_hrus, aes(x = date)) +
+  geom_line(aes(y = t7_cumdiff, color = 'HRU7'), size =1) + 
+  geom_line(aes(y = t9_cumdiff, color = 'HRU9'), size =1) + 
+  geom_line(aes(y = t22_cumdiff, color = 'HRU22'), size =1) + 
+  geom_line(aes(y = t36_cumdiff, color = 'HRU36'), size =1) + 
+  facet_wrap(~year, scales = 'free') +
+  scale_x_date(labels = date_format("%b")) +
+  labs(y = 'Tmean cumulative difference (deg C)') +
+  ggtitle('Tmean station and grid cumulative difference (Station - Grid)')
+
+tmean_cumdiff_plot
 

### 2023-02-06 calibration_output.Rmd
facet plots are small..
updated max Q prior to Apr 1 to be for March only, fixed teh facet wrap small plots

@@
 ```{r setup, include=FALSE}
-knitr::opts_chunk$set(echo = TRUE)
+knitr::opts_chunk$set(
+  echo = F)
 
@@
   mutate(month = month(date)) %>%
-  filter(month %in% 1:3) %>%
+  filter(month %in% 3) %>%
   group_by(source, year) %>%
@@
 
-ggplot(early_peakq, aes(doy_bouldcr, doy_all_ensemble)) +
-  geom_point(size=2.5) +
+marpeakq <- ggplot(early_peakq, aes(x = doy_bouldcr)) +
+  geom_point(aes(y = doy_all_ensemble, shape = "all_ensemble"), size=2.5) +
+  geom_point(aes(y = doy_grid_all, shape = 'grid_all'), size=2.5) +
+  geom_point(aes(y = doy_grid_ensemble, shape = 'grid_ensemble'), size=2.5) +
+  geom_point(aes(y = doy_statn_all, shape = 'statn_all'), size=2.5) +
+  geom_point(aes(y = doy_statn_ensemble, shape = 'statn_ensemble'), size=2.5) +
   geom_abline(intercept = 0, slope = 1, size=1, color='red') +
+  labs(x = "Boulder Creek DOY for March Peak Q", y = 'DOY for March Peak Q') +
   theme_bw() +
-  ggtitle('DOY of peak Q prior to April 1st - All Ensemble')
-
-ggplot(early_peakq, aes(doy_bouldcr, doy_grid_all)) +
-  geom_point(size=2.5) +
-  geom_abline(intercept = 0, slope = 1, size=1, color='red') +
-  theme_bw() +
-  ggtitle('DOY of peak Q prior to April 1st - Grid All')
-
-ggplot(early_peakq, aes(doy_bouldcr, doy_grid_ensemble)) +
-  geom_point(size=2.5) +
-  geom_abline(intercept = 0, slope = 1, size=1, color='red') +
-  theme_bw() +
-  ggtitle('DOY of peak Q prior to April 1st - Grid Ensemble')
-
-ggplot(early_peakq, aes(doy_bouldcr, doy_statn_all)) +
-  geom_point(size=2.5) +
-  geom_abline(intercept = 0, slope = 1, size=1, color='red') +
-  theme_bw() +
-  ggtitle('DOY of peak Q prior to April 1st - Station All')
-
-ggplot(early_peakq, aes(doy_bouldcr, doy_statn_ensemble)) +
-  geom_point(size=2.5) +
-  geom_abline(intercept = 0, slope = 1, size=1, color='red') +
-  theme_bw() +
-  ggtitle('DOY of peak Q prior to April 1st - Station Ensemble')
+  scale_shape_manual(name="source", values=c("all_ensemble"=15, 
+                                            "grid_all"=16, 
+                                            "grid_ensemble"=17,
+                                            "statn_all"=18, 
+                                            "statn_ensemble" = 8))+
+  ggtitle('DOY of peak Q in March')
+
+ggplotly(marpeakq)
+
+# ggplot(early_peakq, aes(doy_bouldcr, doy_grid_all)) +
+#   geom_point(size=2.5) +
+#   geom_abline(intercept = 0, slope = 1, size=1, color='red') +
+#   theme_bw() +
+#   ggtitle('DOY of peak Q prior to April 1st - Grid All')
+# 
+# 
+# ggplot(early_peakq, aes(doy_bouldcr, doy_grid_ensemble)) +
+#   geom_point(size=2.5) +
+#   geom_abline(intercept = 0, slope = 1, size=1, color='red') +
+#   theme_bw() +
+#   ggtitle('DOY of peak Q prior to April 1st - Grid Ensemble')
+# 
+# 
+# ggplot(early_peakq, aes(doy_bouldcr, doy_statn_all)) +
+#   geom_point(size=2.5) +
+#   geom_abline(intercept = 0, slope = 1, size=1, color='red') +
+#   theme_bw() +
+#   ggtitle('DOY of peak Q prior to April 1st - Station All')
+# 
+# 
+# ggplot(early_peakq, aes(doy_bouldcr, doy_statn_ensemble)) +
+#   geom_point(size=2.5) +
+#   geom_abline(intercept = 0, slope = 1, size=1, color='red') +
+#   theme_bw() +
+#   ggtitle('DOY of peak Q prior to April 1st - Station Ensemble')
 
@@
 
-```{r rd and rg, echo = F}
+```{r rd and rg, echo = F, fig.width = 14, fig.asp = 1, out.width = "100%"}
 
@@
 ggplot(gw, aes(x=date, color = source)) +
-  geom_line(aes(y=genRD1)) +
-  facet_wrap(~year, scales = 'free') +
+  geom_line(aes(y=genRD1), size =1) +
+  facet_wrap(~year, scales = 'free', ncol = 2) +
   scale_x_date(labels = date_format("%b")) +
-  ggtitle('genRD1')
+  ggtitle('genRD1') +
+  theme(text = element_text(size = 20))
 
 ggplot(gw, aes(x=date, color = source)) +
-  geom_line(aes(y=genRD2)) +
-  facet_wrap(~year, scales = 'free') +
+  geom_line(aes(y=genRD2), size =1) +
+  facet_wrap(~year, scales = 'free', ncol = 2) +
   scale_x_date(labels = date_format("%b")) +
-  ggtitle('genRD2')
+  ggtitle('genRD2') +
+  theme(text = element_text(size = 20))
 
 ggplot(gw, aes(x=date, color = source)) +
-  geom_line(aes(y=genRG1)) +
-  facet_wrap(~year, scales = 'free') +
+  geom_line(aes(y=genRG1), size =1) +
+  facet_wrap(~year, scales = 'free', ncol = 2) +
   scale_x_date(labels = date_format("%b")) +
-  ggtitle('genRG1')
+  ggtitle('genRG1') +
+  theme(text = element_text(size = 20))
 
 ggplot(gw, aes(x=date, color = source)) +
-  geom_line(aes(y=genRG2)) +
-  facet_wrap(~year, scales = 'free') +
+  geom_line(aes(y=genRG2), size =1) +
+  facet_wrap(~year, scales = 'free', ncol=2) +
   scale_x_date(labels = date_format("%b")) +
-  ggtitle('genRG2')
+  ggtitle('genRG2') +
+  theme(text = element_text(size = 20))
 
@@
 ggplot(gw, aes(x=date, color = source)) +
-  geom_line(aes(y=RD1cumsum)) +
-  facet_wrap(~year, scales = 'free') +
+  geom_line(aes(y=RD1cumsum), size =1) +
+  facet_wrap(~year, scales = 'free', ncol=2) +
   scale_x_date(labels = date_format("%b")) +
-  ggtitle('Cumulative genRD1')
+  ggtitle('Cumulative genRD1') +
+  theme(text = element_text(size = 20))
 
 ggplot(gw, aes(x=date, color = source)) +
-  geom_line(aes(y=RD2cumsum)) +
-  facet_wrap(~year, scales = 'free') +
+  geom_line(aes(y=RD2cumsum), size = 1) +
+  facet_wrap(~year, scales = 'free', ncol=2) +
   scale_x_date(labels = date_format("%b")) +
-  ggtitle('Cumulative genRD2')
+  ggtitle('Cumulative genRD2') +
+  theme(text = element_text(size = 20))
 
 ggplot(gw, aes(x=date, color = source)) +
-  geom_line(aes(y=RG1cumsum)) +
-  facet_wrap(~year, scales = 'free') +
+  geom_line(aes(y=RG1cumsum), size  = 1) +
+  facet_wrap(~year, scales = 'free', ncol = 2) +
   scale_x_date(labels = date_format("%b")) +
-  ggtitle('Cumulative genRG1')
+  ggtitle('Cumulative genRG1') +
+  theme(text = element_text(size = 20))
 
 ggplot(gw, aes(x=date, color = source)) +
-  geom_line(aes(y=RG2cumsum)) +
-  facet_wrap(~year, scales = 'free') +
+  geom_line(aes(y=RG2cumsum), size =1) +
+  facet_wrap(~year, scales = 'free', ncol = 2) +
   scale_x_date(labels = date_format("%b")) +
-  ggtitle('Cumulative genRG2')
-
-```
-
-# HRU Map
+  ggtitle('Cumulative genRG2') +
+  theme(text = element_text(size = 20))
+
+```
+
+# HRU results
+
+## HRU Map
 
@@
 
-# Niwot and HRU7
-
-## SWE and precip
-
-```{r niwot, echo = F}
+## Niwot and HRU7
+
+### SWE and precip
+
+```{r niwot, echo = F, fig.width = 14, fig.asp = 1, out.width = "100%"}
 library(snotelr)
@@
 cum_swe_niwot <- ggplot(niwot_swe2, aes(date, swe_cumsum_mm, color = source)) +
-  geom_line() +
+  geom_line(size =1) +
   scale_x_date(labels = date_format("%b")) +
-  facet_wrap(~year, scales = 'free')
+  facet_wrap(~year, scales = 'free', ncol=2) +
+  theme(text = element_text(size = 20))
 
@@
 cum_precip_niwot <- ggplot(niwot_p2, aes(date, p_cumsum_mm, color = source)) +
-  geom_line() +
+  geom_line(size=1) +
   scale_x_date(labels = date_format("%b")) +
-  facet_wrap(~year, scales = 'free')
+  facet_wrap(~year, scales = 'free', ncol=2) +
+  theme(text = element_text(size = 20))
 
@@
 
-## ET
+### ET
 
@@
 
-# Tmean for HRUs 7, 9, 22, 36
-
-```{r hru7 temp, echo = F}
+## Tmean for HRUs 7, 9, 22, 36
+
+```{r hru7 temp, echo = F, fig.width = 14, fig.asp = 1, out.width = "100%"}
 
@@
   geom_line(aes(y = t36_cumdiff, color = 'HRU36'), size =1) + 
-  facet_wrap(~year, scales = 'free') +
+  facet_wrap(~year, scales = 'free',ncol=2) +
   scale_x_date(labels = date_format("%b")) +
   labs(y = 'Tmean cumulative difference (deg C)') +
-  ggtitle('Tmean station and grid cumulative difference (Station - Grid)')
+  ggtitle('Tmean station and grid cumulative difference (Station - Grid)') +
+  theme(text = element_text(size = 20))
 

### 2023-02-07 calibration_output.Rmd
added precip and tmean average cumulative diff maps.

@@
 knitr::opts_chunk$set(
-  echo = F)
+  echo = F,
+  message = F)
 
@@
 library(dataRetrieval)
+library(tmap)
 
@@
 ```{r rd and rg, echo = F, fig.width = 14, fig.asp = 1, out.width = "100%"}
-
-gw_grid <- grid %>%
-  dplyr::select(time, genRD1, genRD2, genRG1, genRG2) %>%
+setwd("C:/Users/sears/Documents/Repos/fourmile/catchment_output")
+
+gw_grid <- read_csv('gridall_outlet.csv') %>%
+  dplyr::select(time, catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w) %>%
   mutate(source = 'grid')
 
-gw_statn <- statn %>%
-  dplyr::select(time, genRD1, genRD2, genRG1, genRG2) %>%
+gw_statn <- read_csv('statnall_outlet.csv') %>%
+  dplyr::select(time, catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w) %>%
   mutate(source = 'statn')
@@
 ggplot(gw, aes(x=date, color = source)) +
-  geom_line(aes(y=genRD1), size =1) +
+  geom_line(aes(y=catchmentRD1_w), size =1) +
   facet_wrap(~year, scales = 'free', ncol = 2) +
   scale_x_date(labels = date_format("%b")) +
-  ggtitle('genRD1') +
+  ggtitle('RD1') +
   theme(text = element_text(size = 20))
@@
 ggplot(gw, aes(x=date, color = source)) +
-  geom_line(aes(y=genRD2), size =1) +
+  geom_line(aes(y=catchmentRD2_w), size =1) +
   facet_wrap(~year, scales = 'free', ncol = 2) +
   scale_x_date(labels = date_format("%b")) +
-  ggtitle('genRD2') +
+  ggtitle('RD2') +
   theme(text = element_text(size = 20))
@@
 ggplot(gw, aes(x=date, color = source)) +
-  geom_line(aes(y=genRG1), size =1) +
+  geom_line(aes(y=catchmentRG1_w), size =1) +
   facet_wrap(~year, scales = 'free', ncol = 2) +
   scale_x_date(labels = date_format("%b")) +
-  ggtitle('genRG1') +
+  ggtitle('RG1') +
   theme(text = element_text(size = 20))
@@
 ggplot(gw, aes(x=date, color = source)) +
-  geom_line(aes(y=genRG2), size =1) +
+  geom_line(aes(y=catchmentRG2_w), size =1) +
   facet_wrap(~year, scales = 'free', ncol=2) +
   scale_x_date(labels = date_format("%b")) +
-  ggtitle('genRG2') +
+  ggtitle('RG2') +
   theme(text = element_text(size = 20))
@@
   group_by(year, source) %>%
-  mutate(RD1cumsum = cumsum(genRD1),
-         RD2cumsum = cumsum(genRD2),
-         RG1cumsum = cumsum(genRG1),
-         RG2cumsum = cumsum(genRG2))
+  mutate(RD1cumsum = cumsum(catchmentRD1_w),
+         RD2cumsum = cumsum(catchmentRD2_w),
+         RG1cumsum = cumsum(catchmentRG1_w),
+         RG2cumsum = cumsum(catchmentRG2_w))
 
@@
   scale_x_date(labels = date_format("%b")) +
-  ggtitle('Cumulative genRD1') +
+  ggtitle('Cumulative RD1') +
   theme(text = element_text(size = 20))
@@
   scale_x_date(labels = date_format("%b")) +
-  ggtitle('Cumulative genRD2') +
+  ggtitle('Cumulative RD2') +
   theme(text = element_text(size = 20))
@@
   scale_x_date(labels = date_format("%b")) +
-  ggtitle('Cumulative genRG1') +
+  ggtitle('Cumulative RG1') +
   theme(text = element_text(size = 20))
@@
   scale_x_date(labels = date_format("%b")) +
-  ggtitle('Cumulative genRG2') +
+  ggtitle('Cumulative RG2') +
   theme(text = element_text(size = 20))
@@
 tmean_cumdiff_plot
+
+```
+
+## Cumulative Tmean difference
+
+2011-2020 average of daily station-grid Tmean for DOY 365 (or 366)
+
+```{r cumulative tmean for HRUs, echo = F}
+#grid first
+setwd("C:/Users/sears/Documents/Repos/fourmile/HRU_output/grid")
+
+read_ages_grid <- function(dataframe){
+  read_csv(dataframe, skip = 3) %>%
+  slice(3:n()) %>%
+  dplyr::select(-starts_with('@'),
+                -1) %>%
+  mutate(time = ymd(time)) %>%
+  mutate_if(is.character, as.numeric) %>%
+  mutate(source = 'grid')
+
+}
+
+#pull in all filenames with HRU in the name
+filenames <- list.files(".", pattern="HRU", full.names=F)
+
+#read all the csvs using read_ages function
+dataframes <- lapply(filenames, read_ages_grid)
+
+#name all the csvs based on first 6 characters
+names(dataframes) <- substr(filenames, 1, 6)
+
+#bind all and make 1 df
+hru_grids <- dataframes %>%
+  bind_rows()
+
+#statn next
+setwd("C:/Users/sears/Documents/Repos/fourmile/HRU_output/statn")
+
+read_ages_statn <- function(dataframe){
+  read_csv(dataframe, skip = 3) %>%
+  slice(3:n()) %>%
+  dplyr::select(-starts_with('@'),
+                -1) %>%
+  mutate(time = ymd(time)) %>%
+  mutate_if(is.character, as.numeric) %>%
+  mutate(source = 'statn')
+
+}
+
+#pull in all filenames with HRU in the name
+filenames <- list.files(".", pattern="HRU", full.names=F)
+
+#read all the csvs using read_ages function
+dataframes <- lapply(filenames, read_ages_statn)
+
+#name all the csvs based on first 6 characters
+names(dataframes) <- substr(filenames, 1, 6)
+
+#bind all and make 1 df
+hru_statn <- dataframes %>%
+  bind_rows()
+
+#get rid of a bunch of data
+hru_grid_tmean <- hru_grids %>%
+  dplyr::select(c(time, ID, tmean)) %>%
+  rename(tmean_grid = tmean)
+
+hru_statn_tmean <- hru_statn %>%
+  dplyr::select(c(time, ID, tmean)) %>%
+  rename(tmean_statn = tmean)
+
+tmean_hrus <- left_join(hru_grid_tmean, hru_statn_tmean, by = c('time', 'ID')) %>%
+  mutate(diff = tmean_statn - tmean_grid,
+         year = year(time)) %>%
+  group_by(year, ID) %>%
+  mutate(total_diff = cumsum(diff)) %>% 
+  filter(time == max(time)) %>%
+  group_by(ID) %>%
+  summarize(tmean_avg_cumdiff = mean(total_diff)) %>%
+  rename(value = ID)
+
+hrus_map_tmean <- left_join(hrus, tmean_hrus, by = 'value')
+
+tmap_mode('view')
+
+tm_shape(hrus_map_tmean) +
+  tm_polygons('tmean_avg_cumdiff') +
+tm_shape(locations) +
+  tm_symbols(col='blue', size=4)
+
+```
+
+## Cumulative Precip difference
+
+2011-2020 average of daily station-grid precip for DOY 365 (or 366)
+
+```{r cum precip, echo = F}
+#get rid of a bunch of data
+hru_grid_precip <- hru_grids %>%
+  dplyr::select(c(time, ID, precip)) %>%
+  rename(precip_grid = precip)
+
+hru_statn_precip <- hru_statn %>%
+  dplyr::select(c(time, ID, precip)) %>%
+  rename(precip_statn = precip)
+
+precip_hrus <- left_join(hru_grid_precip, hru_statn_precip, by = c('time', 'ID')) %>%
+  mutate(diff = precip_statn - precip_grid,
+         year = year(time)) %>%
+  group_by(year, ID) %>%
+  mutate(total_diff = cumsum(diff)) %>% 
+  filter(time == max(time)) %>%
+  group_by(ID) %>%
+  summarize(precip_avg_cumdiff = mean(total_diff)) %>%
+  rename(value = ID)
+
+hrus_map_precip <- left_join(hrus, precip_hrus, by = 'value')
+
+tmap_mode('view')
+
+tm_shape(hrus_map_precip) +
+  tm_polygons('precip_avg_cumdiff', midpoint = NA, palette = 'YlGnBu') +
+tm_shape(locations) +
+  tm_symbols(col='blue', size=4)
 

### 2023-02-07 calibration_output.Rmd
added solar rad map

@@
 
+## Cumulative solar radiation difference
+
+2011-2020 average of daily station-grid solar rad for DOY 365 (or 366)
+
+```{r cum sol rad, echo = F}
+
+#get rid of a bunch of data
+hru_grid_solrad <- hru_grids %>%
+  dplyr::select(c(time, ID, solRad)) %>%
+  rename(solrad_grid = solRad)
+
+hru_statn_solrad <- hru_statn %>%
+  dplyr::select(c(time, ID, solRad)) %>%
+  rename(solrad_statn = solRad)
+
+solrad_hrus <- left_join(hru_grid_solrad, hru_statn_solrad, by = c('time', 'ID')) %>%
+  mutate(diff = solrad_statn - solrad_grid,
+         year = year(time)) %>%
+  group_by(year, ID) %>%
+  mutate(total_diff = cumsum(diff)) %>% 
+  filter(time == max(time)) %>%
+  group_by(ID) %>%
+  summarize(solrad_avg_cumdiff = mean(total_diff)) %>%
+  rename(value = ID)
+
+hrus_map_solrad <- left_join(hrus, solrad_hrus, by = 'value')
+
+tmap_mode('view')
+
+tm_shape(hrus_map_solrad) +
+  tm_polygons('solrad_avg_cumdiff', midpoint = NA, palette = 'YlOrRd') +
+tm_shape(locations) +
+  tm_symbols(col='blue', size=4)
+
+```
+
 ```{r reach hydrographs, echo = F}

### 2023-02-07 calibration_output.Rmd
updated march peak q plot

@@
 marpeakq <- ggplot(early_peakq, aes(x = doy_bouldcr)) +
-  geom_point(aes(y = doy_all_ensemble, shape = "all_ensemble"), size=2.5) +
-  geom_point(aes(y = doy_grid_all, shape = 'grid_all'), size=2.5) +
-  geom_point(aes(y = doy_grid_ensemble, shape = 'grid_ensemble'), size=2.5) +
-  geom_point(aes(y = doy_statn_all, shape = 'statn_all'), size=2.5) +
-  geom_point(aes(y = doy_statn_ensemble, shape = 'statn_ensemble'), size=2.5) +
-  geom_abline(intercept = 0, slope = 1, size=1, color='red') +
-  labs(x = "Boulder Creek DOY for March Peak Q", y = 'DOY for March Peak Q') +
+  geom_point(aes(y = doy_all_ensemble, shape = "all_ensemble", 
+                 color = 'all_ensemble'), size=2.5) +
+  geom_point(aes(y = doy_grid_all, shape = 'grid_all', 
+                 color = 'grid_all'), size=2.5) +
+  geom_point(aes(y = doy_grid_ensemble, shape = 'grid_ensemble', 
+                 color = 'grid_ensemble'), size=2.5) +
+  geom_point(aes(y = doy_statn_all, shape = 'statn_all', 
+                 color = 'statn_all'), size=2.5) +
+  geom_point(aes(y = doy_statn_ensemble, shape = 'statn_ensemble', 
+                 color = 'statn_ensemble'), size=2.5) +
+  geom_abline(intercept = 0, slope = 1, size=1, color='black') +
+  labs(x = "Boulder Creek DOY for March Peak Q", 
+       y = 'DOY for March Peak Q') +
   theme_bw() +
@@
                                             "statn_all"=18, 
-                                            "statn_ensemble" = 8))+
+                                            "statn_ensemble" = 8)) +
+    scale_color_manual(name="source", values=c("all_ensemble"='orange', 
+                                            "grid_all"='purple1', 
+                                            "grid_ensemble"='maroon',
+                                            "statn_all"='springgreen4', 
+                                            "statn_ensemble" = 'darkturquoise')) +
   ggtitle('DOY of peak Q in March')

### 2023-02-09 calibration_output.Rmd
updating

@@
 output:
+  word_document:
+    toc: yes
   html_document:
-    toc: true
-    toc_float: true
+    toc: yes
+    toc_float: yes
     theme: journal
@@
   chunk_output_type: console
+  always_allow_html: true
 ---

### 2023-02-14 calibration_output.Rmd
everything done on the list except adding relative maps

--- 2023-02-07 calibration_output.Rmd
@@
   html_document:
-    toc: true
-    toc_float: true
+    toc: yes
+    toc_float: yes
     theme: journal
@@
 
+bouldcr3 <- bouldcr %>%
+  mutate(month = month(date)) %>%
+  filter(month == 3, year == 2011)
+
+test1 <- ensem_pivot %>%
+  mutate(month = month(date)) %>%
+  filter(year == 2011,
+         month == 3) %>% 
+  ggplot(aes(date, q_m3s, color = cal_run)) +
+  geom_line() +
+  scale_color_manual(name="cal_run", values=c('obs'='black',
+                                            "grid_ensemble"="maroon", 
+                                            "statn_ensemble"="darkturquoise", 
+                                            "grid_all"="purple1",
+                                            "statn_all"='springgreen4', 
+                                            "all_ensemble" = "orange")) +
+  geom_line(data = bouldcr3, aes(date, bouldcr/10), color = 'darkgrey') +
+  scale_y_continuous(name = 'Q_m3s',
+                    sec.axis = sec_axis(~.*10, name='BoulderCr_cms')) +
+  theme_bw() +
+  ggtitle('March 2011')
+
+ggplotly(test1) %>%
+  add_lines(data=bouldcr, x=~date, y=~bouldcr, colors=NULL, yaxis="y2", 
+              inherit=FALSE, showlegend = FALSE) %>%
+  layout(yaxis2 = list(overlaying = "y", side = "right",
+                       color = 'darkgray',
+                       title = "BoulderCr_cms"),
+         legend = list(x = 1.1, y = 0.95))
+
+################################################
+
+bouldcr3_2 <- bouldcr %>%
+  mutate(month = month(date)) %>%
+  filter(month == 3, year == 2019)
+
+test2 <- ensem_pivot %>%
+  mutate(month = month(date)) %>%
+  filter(year == 2019,
+         month == 3) %>% 
+  ggplot(aes(date, q_m3s, color = cal_run)) +
+  geom_line() +
+  scale_color_manual(name="cal_run", values=c('obs'='black',
+                                            "grid_ensemble"="maroon", 
+                                            "statn_ensemble"="darkturquoise", 
+                                            "grid_all"="purple1",
+                                            "statn_all"='springgreen4', 
+                                            "all_ensemble" = "orange")) +
+  geom_line(data = bouldcr3_2, aes(date, bouldcr/10), color = 'darkgrey') +
+  scale_y_continuous(name = 'Q_m3s',
+                    sec.axis = sec_axis(~.*10, name='BoulderCr_cms')) +
+  theme_bw() +
+  ggtitle('March 2019')
+
+ggplotly(test2) %>%
+  add_lines(data=bouldcr, x=~date, y=~bouldcr, colors=NULL, yaxis="y2", 
+              inherit=FALSE, showlegend = FALSE) %>%
+  layout(yaxis2 = list(overlaying = "y", side = "right",
+                       color = 'darkgray',
+                       title = "BoulderCr_cms"),
+         legend = list(x = 1.1, y = 0.95))
+
 ```
@@
 
+```{r rd and rg sums, echo = F, fig.width = 22, fig.asp = 1.5, out.width = "100%"}
+
+##################
+# all 4 with facets
+
+ggplot(gw, aes(x=date)) +
+  geom_line(aes(y=RG2cumsum, color = 'cumulative RG2'), size =1) +
+  geom_line(aes(y=RG1cumsum, color = 'cumulative RG1'), size =1) +
+  geom_line(aes(y=RD1cumsum, color = 'cumulative RD1'), size =1) +
+  geom_line(aes(y=RD2cumsum, color = 'cumulative RD2'), size =1) +
+  scale_x_date(labels = date_format("%b")) +
+  facet_wrap(~year + source, scales = 'free_x', ncol=2) +
+  ggtitle('Cumulative RD and RG') +
+  theme(text = element_text(size = 24))
+
+```
+
 # HRU results
@@
 
+locations_t <- locations %>% 
+  dplyr::filter(name %in% c('Gordon_South', 'Gordon_North',
+                        'Betasso', 'Niwot_Snotel',
+                        'University Camp SNTL'))
+
 tm_shape(hrus_map_tmean) +
-  tm_polygons('tmean_avg_cumdiff') +
-tm_shape(locations) +
+  tm_polygons('tmean_avg_cumdiff', id = 'value') +
+tm_shape(locations_t) +
   tm_symbols(col='blue', size=4)
@@
 
+locations_p <- locations %>%
+  filter(type == 'precip')
+
 tm_shape(hrus_map_precip) +
-  tm_polygons('precip_avg_cumdiff', midpoint = NA, palette = 'YlGnBu') +
-tm_shape(locations) +
+  tm_polygons('precip_avg_cumdiff', midpoint = NA, palette = 'YlGnBu', id = 'value') +
+tm_shape(locations_p) +
   tm_symbols(col='blue', size=4)
@@
 
+locations_solrad <- locations %>% 
+  dplyr::filter(name %in% c('Gordon_South',
+                        'Betasso', 'Niwot_Snotel'))
+
 tm_shape(hrus_map_solrad) +
-  tm_polygons('solrad_avg_cumdiff', midpoint = NA, palette = 'YlOrRd') +
-tm_shape(locations) +
+  tm_polygons('solrad_avg_cumdiff', midpoint = NA, palette = 'YlOrRd', id = 'value') +
+tm_shape(locations_solrad) +
+  tm_symbols(col='blue', size=4)
+
+```
+
+## Cumulative RH difference
+
+```{r rh, echo = F}
+
+#get rid of a bunch of data
+hru_grid_rh <- hru_grids %>%
+  dplyr::select(c(time, ID, rhum)) %>%
+  rename(rh_grid = rhum)
+
+hru_statn_rh <- hru_statn %>%
+  dplyr::select(c(time, ID, rhum)) %>%
+  rename(rh_statn = rhum)
+
+rh_hrus <- left_join(hru_grid_rh, hru_statn_rh, by = c('time', 'ID')) %>%
+  mutate(diff = rh_statn - rh_grid,
+         year = year(time)) %>%
+  group_by(year, ID) %>%
+  mutate(total_diff = cumsum(diff)) %>% 
+  filter(time == max(time)) %>%
+  group_by(ID) %>%
+  summarize(rh_avg_cumdiff = mean(total_diff)) %>%
+  rename(value = ID)
+
+hrus_map_rh <- left_join(hrus, rh_hrus, by = 'value')
+
+tmap_mode('view')
+
+locations_rh <- locations %>% 
+  dplyr::filter(name %in% c('Gordon_South', 'Gordon_North',
+                        'Betasso', 'Niwot_Snotel'))
+
+tm_shape(hrus_map_rh) +
+  tm_polygons('rh_avg_cumdiff', midpoint = NA, id = 'value') +
+tm_shape(locations_rh) +
+  tm_symbols(col='blue', size=4)
+
+```
+
+## Cumulative wind difference
+
+```{r wind, echo = F}
+
+#get rid of a bunch of data
+hru_grid_wind <- hru_grids %>%
+  dplyr::select(c(time, ID, wind)) %>%
+  rename(wind_grid = wind)
+
+hru_statn_wind <- hru_statn %>%
+  dplyr::select(c(time, ID, wind)) %>%
+  rename(wind_statn = wind)
+
+wind_hrus <- left_join(hru_grid_wind, hru_statn_wind, by = c('time', 'ID')) %>%
+  mutate(diff = wind_statn - wind_grid,
+         year = year(time)) %>%
+  group_by(year, ID) %>%
+  mutate(total_diff = cumsum(diff)) %>% 
+  filter(time == max(time)) %>%
+  group_by(ID) %>%
+  summarize(wind_avg_cumdiff = mean(total_diff)) %>%
+  rename(value = ID)
+
+hrus_map_wind <- left_join(hrus, wind_hrus, by = 'value')
+
+tmap_mode('view')
+
+locations_w <- locations %>% 
+  dplyr::filter(name %in% c('Gordon_South', 'Gordon_North',
+                        'Betasso', 'Niwot_Snotel'))
+
+tm_shape(hrus_map_wind) +
+  tm_polygons('wind_avg_cumdiff', midpoint = NA, id = 'value') +
+tm_shape(locations_w) +
   tm_symbols(col='blue', size=4)

### 2023-02-14 calibration_output.Rmd
updated relative map figs

@@
 
+Relative Tmean difference
+
+```{r relative tmean, echo = F}
+
+reg_tmean <- read_csv('C:/Users/sears/Documents/Repos/fourmile/HRU_output/reg_tmean.csv',
+                      skip = 13) %>%
+  dplyr::select(-starts_with('@')) %>%
+  mutate(time = dmy(time)) %>%
+  summarize(across(`3`:`19`, ~ mean(.))) %>%
+  pivot_longer(cols = `3`:`19`,
+               names_to = 'value', 
+               values_to = 'tmean_avg') %>%
+  mutate(value = as.numeric(value))
+
+hrus_map_tmean <- left_join(hrus_map_tmean, reg_tmean, by = 'value')
+
+hrus_map_tmean <- hrus_map_tmean%>%
+  mutate(relative_avgcum_diff = tmean_avg_cumdiff / tmean_avg)
+
+tm_shape(hrus_map_tmean) +
+  tm_polygons('relative_avgcum_diff', id = 'value') +
+tm_shape(locations_t) +
+  tm_symbols(col='blue', size=4)
+
+```
+
 ## Cumulative Precip difference
@@
 
+Relative Precip difference
+
+```{r relative p, echo = F}
+
+reg_p <- read_csv('C:/Users/sears/Documents/Repos/fourmile/HRU_output/reg_precipAll.csv',
+                      skip = 21) %>%
+  dplyr::select(-starts_with('@')) %>%
+  mutate(time = dmy(time)) %>%
+  summarize(across(`3`:`19`, ~ mean(.))) %>%
+  pivot_longer(cols = `3`:`19`,
+               names_to = 'value', 
+               values_to = 'precip_avg') %>%
+  mutate(value = as.numeric(value))
+
+hrus_map_precip <- left_join(hrus_map_precip, reg_p, by = 'value')
+
+hrus_map_precip <- hrus_map_precip %>%
+  mutate(relative_avgcum_diff = precip_avg_cumdiff / precip_avg)
+
+tm_shape(hrus_map_precip) +
+  tm_polygons('relative_avgcum_diff', midpoint = NA, palette = 'YlGnBu', id = 'value') +
+tm_shape(locations_p) +
+  tm_symbols(col='blue', size=4)
+
+```
+
 ## Cumulative solar radiation difference
@@
 
+Relative solar rad difference
+
+```{r relative solrad, echo = F}
+
+reg_solrad <- read_csv('C:/Users/sears/Documents/Repos/fourmile/HRU_output/reg_solradAll.csv',
+                      skip = 14) %>%
+  dplyr::select(-starts_with('@')) %>%
+  mutate(time = dmy(time)) %>%
+  summarize(across(`3`:`19`, ~ mean(.))) %>%
+  pivot_longer(cols = `3`:`19`,
+               names_to = 'value', 
+               values_to = 'solrad_avg') %>%
+  mutate(value = as.numeric(value))
+
+hrus_map_solrad <- left_join(hrus_map_solrad, reg_solrad, by = 'value')
+
+hrus_map_solrad <- hrus_map_solrad %>%
+  mutate(relative_avgcum_diff = solrad_avg_cumdiff / solrad_avg)
+
+tm_shape(hrus_map_solrad) +
+  tm_polygons('relative_avgcum_diff', midpoint = NA, palette = 'YlOrRd', id = 'value') +
+tm_shape(locations_solrad) +
+  tm_symbols(col='blue', size=4)
+
+```
+
 ## Cumulative RH difference
@@
   tm_symbols(col='blue', size=4)
+
+```
+
+Relative RH difference
+
+```{r relative rh, echo = F}
+
+reg_rh <- read_csv('C:/Users/sears/Documents/Repos/fourmile/HRU_output/reg_rhumAll.csv',
+                      skip = 14) %>%
+  dplyr::select(-starts_with('@')) %>%
+  mutate(time = dmy(time)) %>%
+  summarize(across(`3`:`19`, ~ mean(.))) %>%
+  pivot_longer(cols = `3`:`19`,
+               names_to = 'value', 
+               values_to = 'rh_avg') %>%
+  mutate(value = as.numeric(value))
+
+hrus_map_rh <- left_join(hrus_map_rh, reg_rh, by = 'value')
+
+hrus_map_rh <- hrus_map_rh %>%
+  mutate(relative_avgcum_diff = rh_avg_cumdiff / rh_avg)
+
+tm_shape(hrus_map_rh) +
+  tm_polygons('relative_avgcum_diff', midpoint = NA, id = 'value') +
+tm_shape(locations_rh) +
+  tm_symbols(col='blue', size=4)
+
+```
+
+## Cumulative soil sat difference
+
+```{r soilsat, echo = F}
+
+#get rid of a bunch of data
+hru_grid_soilSat <- hru_grids %>%
+  dplyr::select(c(time, ID, soilSat)) %>%
+  rename(soilSat_grid = soilSat)
+
+hru_statn_soilSat <- hru_statn %>%
+  dplyr::select(c(time, ID, soilSat)) %>%
+  rename(soilSat_statn = soilSat)
+
+soilSat_hrus <- left_join(hru_grid_soilSat, hru_statn_soilSat, by = c('time', 'ID')) %>%
+  mutate(diff = soilSat_statn - soilSat_grid,
+         year = year(time)) %>%
+  group_by(year, ID) %>%
+  mutate(total_diff = cumsum(diff)) %>% 
+  filter(time == max(time)) %>%
+  group_by(ID) %>%
+  summarize(soilSat_avg_cumdiff = mean(total_diff)) %>%
+  rename(value = ID)
+
+hrus_map_soilSat <- left_join(hrus, soilSat_hrus, by = 'value')
+
+tmap_mode('view')
+
+tm_shape(hrus_map_soilSat) +
+  tm_polygons('soilSat_avg_cumdiff', midpoint = NA, id = 'value')
+
+```
+
+## Cumulative ET
+
+```{r et, echo = F}
+
+#get rid of a bunch of data
+hru_grid_ET <- hru_grids %>%
+  dplyr::select(c(time, ID, actET)) %>%
+  rename(ET_grid = actET)
+
+hru_statn_ET <- hru_statn %>%
+  dplyr::select(c(time, ID, actET)) %>%
+  rename(ET_statn = actET)
+
+ET_hrus <- left_join(hru_grid_ET, hru_statn_ET, by = c('time', 'ID')) %>%
+  mutate(diff = ET_statn - ET_grid,
+         year = year(time)) %>%
+  group_by(year, ID) %>%
+  mutate(total_diff = cumsum(diff)) %>% 
+  filter(time == max(time)) %>%
+  group_by(ID) %>%
+  summarize(ET_avg_cumdiff = mean(total_diff)) %>%
+  rename(value = ID)
+
+hrus_map_ET <- left_join(hrus, ET_hrus, by = 'value')
+
+tmap_mode('view')
+
+tm_shape(hrus_map_ET) +
+  tm_polygons('ET_avg_cumdiff', midpoint = NA, id = 'value')
 

### 2023-02-20 calibration_output.Rmd
update spatial figs

--- 2023-02-14 calibration_output.Rmd
@@
 
+gw_maxcumsum <- gw %>%
+  group_by(source, year) %>%
+  summarize(yr_max_RD1 = max(RD1cumsum),
+            yr_max_RD2 = max(RD2cumsum),
+            yr_max_RG1 = max(RG1cumsum),
+            yr_max_RG2 = max(RG2cumsum)) %>%
+  mutate(year = as.factor(year)) %>%
+  pivot_longer(!c(year, source), names_to = 'flow_type', values_to = 'flow_cms')
+
+ggplot(gw_maxcumsum, aes(x = flow_type, y = flow_cms, fill = source)) +
+  geom_boxplot(position = position_dodge(1)) + 
+  ggtitle('Max annual cumulative sums')
+
+ggplot(gw_maxcumsum, aes(x = flow_type, y = flow_cms, fill = source)) +
+  geom_boxplot(position = position_dodge(1)) +
+  facet_wrap(~flow_type, scales = 'free') +
+  ggtitle('Max annual cumulative sums')
+
 ```
@@
 
-## Cumulative Tmean difference
-
-2011-2020 average of daily station-grid Tmean for DOY 365 (or 366)
+## Tmean difference
+
+2011-2020 average of daily station-grid Tmean
 
@@
   dplyr::select(c(time, ID, tmean)) %>%
-  rename(tmean_grid = tmean)
+  rename(tmean_grid = tmean)  %>%
+  group_by(ID) %>%
+  summarize(tmean_all_grid = mean(tmean_grid))
 
@@
   dplyr::select(c(time, ID, tmean)) %>%
-  rename(tmean_statn = tmean)
-
-tmean_hrus <- left_join(hru_grid_tmean, hru_statn_tmean, by = c('time', 'ID')) %>%
-  mutate(diff = tmean_statn - tmean_grid,
-         year = year(time)) %>%
-  group_by(year, ID) %>%
-  mutate(total_diff = cumsum(diff)) %>% 
-  filter(time == max(time)) %>%
+  rename(tmean_statn = tmean) %>%
   group_by(ID) %>%
-  summarize(tmean_avg_cumdiff = mean(total_diff)) %>%
+  summarize(tmean_all_statn = mean(tmean_statn))
+
+tmean_hrus <- left_join(hru_grid_tmean, hru_statn_tmean, by = c('ID')) %>%
+  mutate(diff = tmean_all_statn - tmean_all_grid) %>%
   rename(value = ID)
@@
 tm_shape(hrus_map_tmean) +
-  tm_polygons('tmean_avg_cumdiff', id = 'value') +
+  tm_polygons('diff', id = 'value') +
+tm_shape(locations_t) +
+  tm_symbols(col='blue', size=4)
+
+```
+
+## Tmax difference
+
+```{r tmax, echo = F}
+
+tmax_grid <- read_csv('C:/Users/sears/Documents/Repos/fourmile/HRU_output/reg_tmaxAll_prism.csv') %>% 
+  pivot_longer(cols = `3`:`19`,
+               names_to = 'value', 
+               values_to = 'tmax_grid') %>%
+  mutate(time = dmy(time)) %>%
+  group_by(value) %>%
+  summarize(Tmax_mean_grid = mean(tmax_grid))
+
+tmax_statn <- read_csv('C:/Users/sears/Documents/Repos/fourmile/HRU_output/reg_tmaxAll.csv') %>% 
+  pivot_longer(cols = `3`:`19`,
+               names_to = 'value', 
+               values_to = 'tmax_statn') %>%
+  mutate(time = dmy(time)) %>%
+  group_by(value) %>%
+  summarize(Tmax_mean_statn = mean(tmax_statn))
+
+tmax_hrus <- left_join(tmax_grid, tmax_statn, by = c('value')) %>%
+  mutate(diff = Tmax_mean_statn - Tmax_mean_grid,
+         value = as.numeric(value))
+
+hrus_map_tmax <- left_join(hrus, tmax_hrus, by = 'value')
+
+tmap_mode('view')
+
+tm_shape(hrus_map_tmax) +
+  tm_polygons('diff', id = 'value') +
+tm_shape(locations_t) +
+  tm_symbols(col='blue', size=4)
+
+```
+
+## Tmax monthly average
+
+```{r tmax month, echo = F}
+
+tmax_grid_mo <- read_csv('C:/Users/sears/Documents/Repos/fourmile/HRU_output/reg_tmaxAll_prism.csv') %>% 
+  pivot_longer(cols = `3`:`19`,
+               names_to = 'value', 
+               values_to = 'tmax_grid') %>%
+  mutate(time = dmy(time),
+         month = month(time)) %>%
+  filter(month %in% c(3:6)) %>%
+  group_by(value, month) %>%
+  summarize(avg_tmax_grid = mean(tmax_grid))
+
+tmax_statn_mo <- read_csv('C:/Users/sears/Documents/Repos/fourmile/HRU_output/reg_tmaxAll.csv') %>% 
+  pivot_longer(cols = `3`:`19`,
+               names_to = 'value', 
+               values_to = 'tmax_statn') %>%
+  mutate(time = dmy(time),
+         month = month(time)) %>%
+  filter(month %in% c(3:6)) %>%
+  group_by(value, month) %>%
+  summarize(avg_tmax_statn = mean(tmax_statn))
+
+tmax_hrus_mo <- left_join(tmax_grid_mo, tmax_statn_mo, by = c('value', 'month')) %>%
+  mutate(mo_tmax_diff = avg_tmax_statn - avg_tmax_grid,
+         value = as.numeric(value))
+
+tmap_mode('plot')
+
+#march
+tmax_hrus_mar<- tmax_hrus_mo %>%
+  filter(month == 3)
+
+hrus_map_tmax_mar <- left_join(hrus, tmax_hrus_mar, by = 'value')
+
+mar_tmax <- tm_shape(hrus_map_tmax_mar) +
+  tm_polygons('mo_tmax_diff', id = 'value') +
+tm_shape(locations_t) +
+  tm_symbols(col='blue', size=1) +
+  tm_layout(title = 'March avg tmax')
+
+#april
+tmax_hrus_apr<- tmax_hrus_mo %>%
+  filter(month == 4)
+
+hrus_map_tmax_apr <- left_join(hrus, tmax_hrus_apr, by = 'value')
+
+apr_tmax <- tm_shape(hrus_map_tmax_apr) +
+  tm_polygons('mo_tmax_diff', id = 'value') +
+tm_shape(locations_t) +
+  tm_symbols(col='blue', size=1) +
+  tm_layout(title = 'April avg tmax')
+
+#may
+tmax_hrus_may<- tmax_hrus_mo %>%
+  filter(month == 5)
+
+hrus_map_tmax_may <- left_join(hrus, tmax_hrus_may, by = 'value')
+
+may_tmax <- tm_shape(hrus_map_tmax_may) +
+  tm_polygons('mo_tmax_diff', id = 'value') +
+tm_shape(locations_t) +
+  tm_symbols(col='blue', size=1) +
+  tm_layout(title = 'May avg tmax')
+
+#june
+tmax_hrus_jun<- tmax_hrus_mo %>%
+  filter(month == 6)
+
+hrus_map_tmax_jun <- left_join(hrus, tmax_hrus_jun, by = 'value')
+
+jun_tmax <- tm_shape(hrus_map_tmax_jun) +
+  tm_polygons('mo_tmax_diff', id = 'value') +
+tm_shape(locations_t) +
+  tm_symbols(col='blue', size=1) +
+  tm_layout(title = 'June avg tmax')
+
+tmap_arrange(mar_tmax, apr_tmax, may_tmax, jun_tmax)
+
+```
+
+## Tmin difference
+
+```{r tmin, echo = F}
+
+tmin_grid <- read_csv('C:/Users/sears/Documents/Repos/fourmile/HRU_output/reg_tminAll_prism.csv') %>% 
+  pivot_longer(cols = `3`:`19`,
+               names_to = 'value', 
+               values_to = 'tmin_grid') %>%
+  mutate(time = dmy(time)) %>%
+  group_by(value) %>%
+  summarize(Tmin_mean_grid = mean(tmin_grid))
+
+tmin_statn <- read_csv('C:/Users/sears/Documents/Repos/fourmile/HRU_output/reg_tminAll.csv') %>% 
+  pivot_longer(cols = `3`:`19`,
+               names_to = 'value', 
+               values_to = 'tmin_statn') %>%
+  mutate(time = dmy(time)) %>%
+  group_by(value) %>%
+  summarize(Tmin_mean_statn = mean(tmin_statn))
+
+tmin_hrus <- left_join(tmin_grid, tmin_statn, by = c('value')) %>%
+  mutate(diff = Tmin_mean_statn - Tmin_mean_grid,
+         value = as.numeric(value))
+
+hrus_map_tmin <- left_join(hrus, tmin_hrus, by = 'value')
+
+tmap_mode('view')
+
+tm_shape(hrus_map_tmin) +
+  tm_polygons('diff', id = 'value') +
 tm_shape(locations_t) +
@@
 
-## Cumulative solar radiation difference
-
-2011-2020 average of daily station-grid solar rad for DOY 365 (or 366)
+Relative Precip difference
+
+```{r relative p, echo = F}
+
+reg_p <- read_csv('C:/Users/sears/Documents/Repos/fourmile/HRU_output/reg_precipAll.csv',
+                      skip = 21) %>%
+  dplyr::select(-starts_with('@')) %>%
+  mutate(time = dmy(time)) %>%
+  summarize(across(`3`:`19`, ~ mean(.))) %>%
+  pivot_longer(cols = `3`:`19`,
+               names_to = 'value', 
+               values_to = 'precip_avg') %>%
+  mutate(value = as.numeric(value))
+
+hrus_map_precip <- left_join(hrus_map_precip, reg_p, by = 'value')
+
+hrus_map_precip <- hrus_map_precip %>%
+  mutate(relative_avgcum_diff = precip_avg_cumdiff / precip_avg)
+
+tm_shape(hrus_map_precip) +
+  tm_polygons('relative_avgcum_diff', midpoint = NA, palette = 'YlGnBu', id = 'value') +
+tm_shape(locations_p) +
+  tm_symbols(col='blue', size=4)
+
+```
+
+## Solar radiation difference
+
+2011-2020 average of daily station-grid solar rad
 
@@
   dplyr::select(c(time, ID, solRad)) %>%
-  rename(solrad_grid = solRad)
+  rename(solrad_grid = solRad)  %>%
+  group_by(ID) %>%
+  summarize(solrad_all_grid = mean(solrad_grid))
 
@@
   dplyr::select(c(time, ID, solRad)) %>%
-  rename(solrad_statn = solRad)
-
-solrad_hrus <- left_join(hru_grid_solrad, hru_statn_solrad, by = c('time', 'ID')) %>%
-  mutate(diff = solrad_statn - solrad_grid,
-         year = year(time)) %>%
-  group_by(year, ID) %>%
-  mutate(total_diff = cumsum(diff)) %>% 
-  filter(time == max(time)) %>%
+  rename(solrad_statn = solRad) %>%
   group_by(ID) %>%
-  summarize(solrad_avg_cumdiff = mean(total_diff)) %>%
+  summarize(solrad_all_statn = mean(solrad_statn))
+
+solrad_hrus <- left_join(hru_grid_solrad, hru_statn_solrad, by = c('ID')) %>%
+  mutate(diff = solrad_all_statn - solrad_all_grid) %>%
   rename(value = ID)
@@
 tm_shape(hrus_map_solrad) +
-  tm_polygons('solrad_avg_cumdiff', midpoint = NA, palette = 'YlOrRd', id = 'value') +
+  tm_polygons('diff', midpoint = NA, palette = 'YlOrRd', id = 'value') +
 tm_shape(locations_solrad) +
@@
 
-## Cumulative RH difference
+## RH difference
 
@@
   dplyr::select(c(time, ID, rhum)) %>%
-  rename(rh_grid = rhum)
+  rename(rh_grid = rhum)  %>%
+  group_by(ID) %>%
+  summarize(rh_all_grid = mean(rh_grid))
 
@@
   dplyr::select(c(time, ID, rhum)) %>%
-  rename(rh_statn = rhum)
-
-rh_hrus <- left_join(hru_grid_rh, hru_statn_rh, by = c('time', 'ID')) %>%
-  mutate(diff = rh_statn - rh_grid,
-         year = year(time)) %>%
-  group_by(year, ID) %>%
-  mutate(total_diff = cumsum(diff)) %>% 
-  filter(time == max(time)) %>%
+  rename(rh_statn = rhum) %>%
   group_by(ID) %>%
-  summarize(rh_avg_cumdiff = mean(total_diff)) %>%
+  summarize(rh_all_statn = mean(rh_statn))
+
+rh_hrus <- left_join(hru_grid_rh, hru_statn_rh, by = c('ID')) %>%
+  mutate(diff = rh_all_statn - rh_all_grid) %>%
   rename(value = ID)
@@
 tm_shape(hrus_map_rh) +
-  tm_polygons('rh_avg_cumdiff', midpoint = NA, id = 'value') +
+  tm_polygons('diff', midpoint = NA, id = 'value') +
 tm_shape(locations_rh) +
@@
 
-## Cumulative wind difference
-
-```{r wind, echo = F}
+## Average soil sat difference comparison
+
+```{r soilsat, echo = F}
 
 #get rid of a bunch of data
-hru_grid_wind <- hru_grids %>%
-  dplyr::select(c(time, ID, wind)) %>%
-  rename(wind_grid = wind)
-
-hru_statn_wind <- hru_statn %>%
-  dplyr::select(c(time, ID, wind)) %>%
-  rename(wind_statn = wind)
-
-wind_hrus <- left_join(hru_grid_wind, hru_statn_wind, by = c('time', 'ID')) %>%
-  mutate(diff = wind_statn - wind_grid,
-         year = year(time)) %>%
-  group_by(year, ID) %>%
-  mutate(total_diff = cumsum(diff)) %>% 
-  filter(time == max(time)) %>%
+hru_grid_soilsat <- hru_grids %>%
+  dplyr::select(c(time, ID, soilSat)) %>%
+  rename(soilsat_grid = soilSat)  %>%
   group_by(ID) %>%
-  summarize(wind_avg_cumdiff = mean(total_diff)) %>%
+  summarize(soilsat_all_grid = mean(soilsat_grid))
+
+hru_statn_soilsat <- hru_statn %>%
+  dplyr::select(c(time, ID, soilSat)) %>%
+  rename(soilsat_statn = soilSat) %>%
+  group_by(ID) %>%
+  summarize(soilsat_all_statn = mean(soilsat_statn))
+
+soilsat_hrus <- left_join(hru_grid_soilsat, hru_statn_soilsat, by = c('ID')) %>%
   rename(value = ID)
 
-hrus_map_wind <- left_join(hrus, wind_hrus, by = 'value')
-
-tmap_mode('view')
-
-locations_w <- locations %>% 
-  dplyr::filter(name %in% c('Gordon_South', 'Gordon_North',
-                        'Betasso', 'Niwot_Snotel'))
-
-tm_shape(hrus_map_wind) +
-  tm_polygons('wind_avg_cumdiff', midpoint = NA, id = 'value') +
-tm_shape(locations_w) +
-  tm_symbols(col='blue', size=4)
+hrus_map_soilsat <- left_join(hrus, soilsat_hrus, by = 'value')
+
+tmap_mode('plot')
+
+soilavg_grid <- tm_shape(hrus_map_soilsat) +
+  tm_polygons('soilsat_all_grid', midpoint = NA, id = 'value') +
+  tm_legend(legend.outside = T) +
+  tm_layout(main.title = 'Average soil sat')
+
+soilavg_statn <- tm_shape(hrus_map_soilsat) +
+  tm_polygons('soilsat_all_statn', midpoint = NA, id = 'value') +
+  tm_legend(legend.outside = T)
+
+tmap_arrange(soilavg_grid, soilavg_statn)
+
+```
+
+## Average max soil sat comparison
+
+```{r max soilsat, echo = F}
+
+#get rid of a bunch of data
+hru_grid_soilsat_max <- hru_grids %>%
+  dplyr::select(c(time, ID, soilSat)) %>%
+  rename(soilsat_grid = soilSat)  %>%
+  mutate(year = year(time)) %>% 
+  group_by(ID, year) %>%
+  summarize(soilsat_yrmax_grid = max(soilsat_grid)) %>%
+  summarize(avg_max_grid = mean(soilsat_yrmax_grid))
+
+hru_statn_soilsat_max <- hru_statn %>%
+  dplyr::select(c(time, ID, soilSat)) %>%
+  rename(soilsat_statn = soilSat) %>%
+  mutate(year = year(time)) %>% 
+  group_by(ID, year) %>%
+  summarize(soilsat_yrmax_statn = max(soilsat_statn)) %>%
+  summarize(avg_max_statn = mean(soilsat_yrmax_statn))
+
+soilsat_hrus_max <- left_join(hru_grid_soilsat_max, hru_statn_soilsat_max, by = c('ID')) %>%
+  rename(value = ID)
+
+hrus_map_soilsat_max <- left_join(hrus, soilsat_hrus_max, by = 'value')
+
+tmap_mode('plot')
+
+soilavg_grid_max <- tm_shape(hrus_map_soilsat_max) +
+  tm_polygons('avg_max_grid', midpoint = NA, id = 'value') +
+  tm_legend(legend.outside = T) +
+  tm_layout(title = 'Average max soil sat',
+            title.position = c('left', 'top'))
+
+soilavg_statn_max <- tm_shape(hrus_map_soilsat_max) +
+  tm_polygons('avg_max_statn', midpoint = NA, id = 'value') +
+  tm_legend(legend.outside = T)
+
+tmap_arrange(soilavg_grid_max, soilavg_statn_max)
+
+```
+
+## Average ET comparison
+
+```{r et, echo = F}
+#get rid of a bunch of data
+hru_grid_ET <- hru_grids %>%
+  dplyr::select(c(time, ID, actET)) %>%
+  rename(ET_grid = actET)  %>%
+  group_by(ID) %>%
+  summarize(ET_all_grid = mean(ET_grid))
+
+hru_statn_ET <- hru_statn %>%
+  dplyr::select(c(time, ID, actET)) %>%
+  rename(ET_statn = actET) %>%
+  group_by(ID) %>%
+  summarize(ET_all_statn = mean(ET_statn))
+
+ET_hrus <- left_join(hru_grid_ET, hru_statn_ET, by = c('ID')) %>%
+  rename(value = ID)
+
+hrus_map_ET <- left_join(hrus, ET_hrus, by = 'value')
+
+tmap_mode('plot')
+
+ETavg_grid <- tm_shape(hrus_map_ET) +
+  tm_polygons('ET_all_grid', midpoint = NA, id = 'value') +
+  tm_legend(legend.outside = T) +
+  tm_layout(main.title = 'Average ET')
+
+ETavg_statn <- tm_shape(hrus_map_ET) +
+  tm_polygons('ET_all_statn', midpoint = NA, id = 'value') +
+  tm_legend(legend.outside = T)
+
+tmap_arrange(ETavg_grid, ETavg_statn)
 

### 2023-02-21 calibration_output.Rmd
tmin and tmax monthly HRU vals

@@
 mar_tmax <- tm_shape(hrus_map_tmax_mar) +
-  tm_polygons('mo_tmax_diff', id = 'value') +
+  #tm_polygons('mo_tmax_diff', id = 'value') +
+  tm_fill('mo_tmax_diff', id = 'value',
+          breaks = c(-6,-3,0,3,6)) +
+  tm_borders() +
   tm_shape(locations_t) +
-  tm_symbols(col='blue', size=1) +
-  tm_layout(title = 'March avg tmax')
+  tm_symbols(col='blue', size = 0.25) +
+  tm_layout(title = 'March avg tmax',
+            legend.outside = T)
 
@@
 apr_tmax <- tm_shape(hrus_map_tmax_apr) +
-  tm_polygons('mo_tmax_diff', id = 'value') +
+  tm_fill('mo_tmax_diff', id = 'value',
+          breaks = c(-6,-3,0,3,6)) +
+  tm_borders() +
   tm_shape(locations_t) +
-  tm_symbols(col='blue', size=1) +
-  tm_layout(title = 'April avg tmax')
+  tm_symbols(col='blue', size = 0.25) +
+  tm_layout(title = 'April avg tmax',
+            legend.outside = T)
 
@@
 may_tmax <- tm_shape(hrus_map_tmax_may) +
-  tm_polygons('mo_tmax_diff', id = 'value') +
+  tm_fill('mo_tmax_diff', id = 'value',
+         breaks = c(-6,-3,0,3,6)) +
+  tm_borders() +
 tm_shape(locations_t) +
-  tm_symbols(col='blue', size=1) +
-  tm_layout(title = 'May avg tmax')
+  tm_symbols(col='blue', size = 0.25) +
+  tm_layout(title = 'May avg tmax',
+            legend.outside = T)
 
@@
 jun_tmax <- tm_shape(hrus_map_tmax_jun) +
-  tm_polygons('mo_tmax_diff', id = 'value') +
+  tm_fill('mo_tmax_diff', id = 'value',
+          breaks = c(-6,-3,0,3,6)) +
+  tm_borders() +
 tm_shape(locations_t) +
-  tm_symbols(col='blue', size=1) +
-  tm_layout(title = 'June avg tmax')
+  tm_symbols(col='blue', size = 0.25) +
+  tm_layout(title = 'June avg tmax',
+            legend.outside = T)
 
@@
 
+## Tmin monthly average
+
+```{r tmin month, echo = F}
+tmin_grid_mo <- read_csv('C:/Users/sears/Documents/Repos/fourmile/HRU_output/reg_tminAll_prism.csv') %>% 
+  pivot_longer(cols = `3`:`19`,
+               names_to = 'value', 
+               values_to = 'tmin_grid') %>%
+  mutate(time = dmy(time),
+         month = month(time)) %>%
+  filter(month %in% c(3:6)) %>%
+  group_by(value, month) %>%
+  summarize(avg_tmin_grid = mean(tmin_grid))
+
+tmin_statn_mo <- read_csv('C:/Users/sears/Documents/Repos/fourmile/HRU_output/reg_tminAll.csv') %>% 
+  pivot_longer(cols = `3`:`19`,
+               names_to = 'value', 
+               values_to = 'tmin_statn') %>%
+  mutate(time = dmy(time),
+         month = month(time)) %>%
+  filter(month %in% c(3:6)) %>%
+  group_by(value, month) %>%
+  summarize(avg_tmin_statn = mean(tmin_statn))
+
+tmin_hrus_mo <- left_join(tmin_grid_mo, tmin_statn_mo, by = c('value', 'month')) %>%
+  mutate(mo_tmin_diff = avg_tmin_statn - avg_tmin_grid,
+         value = as.numeric(value))
+
+tmap_mode('plot')
+
+#march
+tmin_hrus_mar<- tmin_hrus_mo %>%
+  filter(month == 3)
+
+hrus_map_tmin_mar <- left_join(hrus, tmin_hrus_mar, by = 'value')
+
+mar_tmin <- tm_shape(hrus_map_tmin_mar) +
+  #tm_polygons('mo_tmin_diff', id = 'value') +
+  tm_fill('mo_tmin_diff', id = 'value',
+          breaks = c(-5,-2.5,0,2.5,5)) +
+  tm_borders() +
+  tm_shape(locations_t) +
+  tm_symbols(col='blue', size = 0.25) +
+  tm_layout(title = 'March avg tmin',
+            legend.outside = T)
+
+#april
+tmin_hrus_apr<- tmin_hrus_mo %>%
+  filter(month == 4)
+
+hrus_map_tmin_apr <- left_join(hrus, tmin_hrus_apr, by = 'value')
+
+apr_tmin <- tm_shape(hrus_map_tmin_apr) +
+  tm_fill('mo_tmin_diff', id = 'value',
+          breaks = c(-5,-2.5,0,2.5,5)) +
+  tm_borders() +
+  tm_shape(locations_t) +
+  tm_symbols(col='blue', size = 0.25) +
+  tm_layout(title = 'April avg tmin',
+            legend.outside = T)
+
+#may
+tmin_hrus_may<- tmin_hrus_mo %>%
+  filter(month == 5)
+
+hrus_map_tmin_may <- left_join(hrus, tmin_hrus_may, by = 'value')
+
+may_tmin <- tm_shape(hrus_map_tmin_may) +
+  tm_fill('mo_tmin_diff', id = 'value',
+         breaks = c(-5,-2.5,0,2.5,5)) +
+  tm_borders() +
+tm_shape(locations_t) +
+  tm_symbols(col='blue', size = 0.25) +
+  tm_layout(title = 'May avg tmin',
+            legend.outside = T)
+
+#june
+tmin_hrus_jun<- tmin_hrus_mo %>%
+  filter(month == 6)
+
+hrus_map_tmin_jun <- left_join(hrus, tmin_hrus_jun, by = 'value')
+
+jun_tmin <- tm_shape(hrus_map_tmin_jun) +
+  tm_fill('mo_tmin_diff', id = 'value',
+          breaks = c(-5,-2.5,0,2.5,5)) +
+  tm_borders() +
+tm_shape(locations_t) +
+  tm_symbols(col='blue', size = 0.25) +
+  tm_layout(title = 'June avg tmin',
+            legend.outside = T)
+
+tmap_arrange(mar_tmin, apr_tmin, may_tmin, jun_tmin)
+
+```
+
+```{r tmax month, echo = F}
 ## Cumulative Precip difference
@@
   tm_legend(legend.outside = T) +
-  tm_layout(title = 'Average max soil sat',
+  tm_layout(main.title = 'Average max soil sat',
             title.position = c('left', 'top'))

### 2023-02-28 calibration_output.Rmd
updated for meeting
updated rd and rg plot sizes
things got weird
added LAI and fixed WDs

@@
   dplyr::select(c(doy, source, q_m3s, year)) %>%
+  drop_na() %>% 
   pivot_wider(names_from = 'source', values_from = c('q_m3s', 'doy'))
@@
 ```{r catch precip, echo = F}
-setwd("C:/Users/sears/Documents/Repos/fourmile/catchment_output")
+setwd("./catchment_output")
 
@@
 ```{r rd and rg, echo = F, fig.width = 14, fig.asp = 1, out.width = "100%"}
-setwd("C:/Users/sears/Documents/Repos/fourmile/catchment_output")
-
-gw_grid <- read_csv('gridall_outlet.csv') %>%
+
+gw_grid <- read_csv(here('catchment_output/gridall_outlet.csv')) %>%
   dplyr::select(time, catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w) %>%
@@
 
-gw_statn <- read_csv('statnall_outlet.csv') %>%
+gw_statn <- read_csv(here('catchment_output/statnall_outlet.csv')) %>%
   dplyr::select(time, catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w) %>%
@@
 
+```
+
+```{r gw boxplot, echo = F}
+
 gw_maxcumsum <- gw %>%
@@
 
-hru7_grid <- read_csv('C:/Users/sears/Documents/Repos/fourmile/HRU_output/HRU_7_grid.csv') %>%
+hru7_grid <- read_csv(here('HRU_output/HRU_7_grid.csv')) %>%
   dplyr::select(date, precip_mm, swe_mm) %>%
@@
 
-hru7_statn <- read_csv('C:/Users/sears/Documents/Repos/fourmile/HRU_output/HRU_7_statn.csv') %>%
+hru7_statn <- read_csv(here('HRU_output/HRU_7_statn.csv')) %>%
   dplyr::select(date, precip_mm, swe_mm) %>%
@@
 
-niwot_et <- read_csv('C:/Users/sears/Documents/Repos/fourmile/HRU_output/Niwot_daily_et.csv') %>%
+niwot_et <- read_csv(here('HRU_output/Niwot_daily_et.csv')) %>%
   filter(year > 2010) %>%
@@
 
-hru7_grid <- read_csv('C:/Users/sears/Documents/Repos/fourmile/HRU_output/HRU_7_grid.csv') %>%
+hru7_grid <- read_csv(here('HRU_output/HRU_7_grid.csv')) %>%
   dplyr::select(date, AET_mm) %>%
@@
 
-hru7_statn <- read_csv('C:/Users/sears/Documents/Repos/fourmile/HRU_output/HRU_7_statn.csv') %>%
+hru7_statn <- read_csv(here('HRU_output/HRU_7_statn.csv')) %>%
   dplyr::select(date, AET_mm) %>%
@@
 
-tmean7_grid <- read_csv('C:/Users/sears/Documents/Repos/fourmile/HRU_output/HRU_7_grid.csv') %>%
+tmean7_grid <- read_csv(here('HRU_output/HRU_7_grid.csv')) %>%
   dplyr::select(date, tmean) %>%
@@
 
-tmean7_statn <- read_csv('C:/Users/sears/Documents/Repos/fourmile/HRU_output/HRU_7_statn.csv') %>%
+tmean7_statn <- read_csv(here('HRU_output/HRU_7_statn.csv')) %>%
   dplyr::select(date, tmean) %>%
@@
 
-tmean9_grid <- read_csv('C:/Users/sears/Documents/Repos/fourmile/HRU_output/HRU_9_grid.csv') %>%
+tmean9_grid <- read_csv(here('HRU_output/HRU_9_grid.csv')) %>%
   dplyr::select(date, tmean) %>%
@@
 
-tmean9_statn <- read_csv('C:/Users/sears/Documents/Repos/fourmile/HRU_output/HRU_9_statn.csv') %>%
+tmean9_statn <- read_csv(here('HRU_output/HRU_9_statn.csv')) %>%
   dplyr::select(date, tmean) %>%
@@
 
-tmean22_grid <- read_csv('C:/Users/sears/Documents/Repos/fourmile/HRU_output/HRU_22_grid.csv') %>%
+tmean22_grid <- read_csv(here('HRU_output/HRU_22_grid.csv')) %>%
   dplyr::select(date, tmean) %>%
@@
 
-tmean22_statn <- read_csv('C:/Users/sears/Documents/Repos/fourmile/HRU_output/HRU_22_statn.csv') %>%
+tmean22_statn <- read_csv(here('HRU_output/HRU_22_statn.csv')) %>%
   dplyr::select(date, tmean) %>%
@@
 
-tmean36_grid <- read_csv('C:/Users/sears/Documents/Repos/fourmile/HRU_output/HRU_36_grid.csv') %>%
+tmean36_grid <- read_csv(here('HRU_output/HRU_36_grid.csv')) %>%
   dplyr::select(date, tmean) %>%
@@
 
-tmean36_statn <- read_csv('C:/Users/sears/Documents/Repos/fourmile/HRU_output/HRU_36_statn.csv') %>%
+tmean36_statn <- read_csv(here('HRU_output/HRU_36_statn.csv')) %>%
   dplyr::select(date, tmean) %>%
@@
 #grid first
-setwd("C:/Users/sears/Documents/Repos/fourmile/HRU_output/grid")
+setwd(here("HRU_output/grid"))
 
@@
 #statn next
-setwd("C:/Users/sears/Documents/Repos/fourmile/HRU_output/statn")
+setwd(here("HRU_output/statn"))
 
@@
 
-tmax_grid <- read_csv('C:/Users/sears/Documents/Repos/fourmile/HRU_output/reg_tmaxAll_prism.csv') %>% 
+tmax_grid <- read_csv(here('HRU_output/reg_tmaxAll_prism.csv'))%>% 
   pivot_longer(cols = `3`:`19`,
@@
 
-tmax_statn <- read_csv('C:/Users/sears/Documents/Repos/fourmile/HRU_output/reg_tmaxAll.csv') %>% 
+tmax_statn <- read_csv(here('HRU_output/reg_tmaxAll.csv')) %>% 
   pivot_longer(cols = `3`:`19`,
@@
 
-tmax_grid_mo <- read_csv('C:/Users/sears/Documents/Repos/fourmile/HRU_output/reg_tmaxAll_prism.csv') %>% 
+tmax_grid_mo <- read_csv(here('HRU_output/reg_tmaxAll_prism.csv')) %>% 
   pivot_longer(cols = `3`:`19`,
@@
 
-tmax_statn_mo <- read_csv('C:/Users/sears/Documents/Repos/fourmile/HRU_output/reg_tmaxAll.csv') %>% 
+tmax_statn_mo <- read_csv(here('HRU_output/reg_tmaxAll.csv')) %>% 
   pivot_longer(cols = `3`:`19`,
@@
 
-tmin_grid <- read_csv('C:/Users/sears/Documents/Repos/fourmile/HRU_output/reg_tminAll_prism.csv') %>% 
+tmin_grid <- read_csv(here('HRU_output/reg_tminAll_prism.csv')) %>% 
   pivot_longer(cols = `3`:`19`,
@@
 
-tmin_statn <- read_csv('C:/Users/sears/Documents/Repos/fourmile/HRU_output/reg_tminAll.csv') %>% 
+tmin_statn <- read_csv(here('HRU_output/reg_tminAll.csv')) %>% 
   pivot_longer(cols = `3`:`19`,
@@
 ```{r tmin month, echo = F}
-tmin_grid_mo <- read_csv('C:/Users/sears/Documents/Repos/fourmile/HRU_output/reg_tminAll_prism.csv') %>% 
+tmin_grid_mo <- read_csv(here('HRU_output/reg_tminAll_prism.csv')) %>% 
   pivot_longer(cols = `3`:`19`,
@@
 
-tmin_statn_mo <- read_csv('C:/Users/sears/Documents/Repos/fourmile/HRU_output/reg_tminAll.csv') %>% 
+tmin_statn_mo <- read_csv(here('HRU_output/reg_tminAll.csv')) %>% 
   pivot_longer(cols = `3`:`19`,
@@
 
-```{r tmax month, echo = F}
 ## Cumulative Precip difference
@@
 
-reg_p <- read_csv('C:/Users/sears/Documents/Repos/fourmile/HRU_output/reg_precipAll.csv',
+reg_p <- read_csv(here('HRU_output/reg_precipAll.csv'),
                       skip = 21) %>%
@@
 tmap_arrange(ETavg_grid, ETavg_statn)
+
+```
+
+## Average LAI comparison
+
+```{r lai, echo = F}
+
+#get rid of a bunch of data
+hru_grid_LAI <- hru_grids %>%
+  dplyr::select(c(time, ID, LAI)) %>%
+  rename(LAI_grid = LAI)  %>%
+  group_by(ID) %>%
+  summarize(LAI_all_grid = mean(LAI_grid))
+
+hru_statn_LAI <- hru_statn %>%
+  dplyr::select(c(time, ID, LAI)) %>%
+  rename(LAI_statn = LAI) %>%
+  group_by(ID) %>%
+  summarize(LAI_all_statn = mean(LAI_statn))
+
+LAI_hrus <- left_join(hru_grid_LAI, hru_statn_LAI, by = c('ID')) %>%
+  rename(value = ID)
+
+hrus_map_LAI <- left_join(hrus, LAI_hrus, by = 'value')
+
+tmap_mode('plot')
+
+LAIavg_grid <- tm_shape(hrus_map_LAI) +
+  tm_polygons('LAI_all_grid', midpoint = NA, id = 'value',
+              breaks = c(1,2,3,4,5)) +
+  tm_legend(legend.outside = T) +
+  tm_layout(main.title = 'Average LAI')
+
+LAIavg_statn <- tm_shape(hrus_map_LAI) +
+  tm_polygons('LAI_all_statn', midpoint = NA, id = 'value',
+              breaks = c(1,2,3,4,5)) +
+  tm_legend(legend.outside = T)
+
+tmap_arrange(LAIavg_grid, LAIavg_statn)
 

### 2023-02-28 calibration_output.Rmd
updates ready for meeting

@@
   echo = F,
-  message = F)
+  message = F, 
+  warning  = F)
 
@@
   geom_boxplot(position = position_dodge(1)) + 
+  geom_point(position=position_jitterdodge(),alpha=0.3) +
   ggtitle('Max annual cumulative sums')
@@
   geom_boxplot(position = position_dodge(1)) +
+  geom_point(position=position_jitterdodge(),alpha=0.3) +
+  #geom_point(aes(color = source)) +
   facet_wrap(~flow_type, scales = 'free') +
   ggtitle('Max annual cumulative sums')
+
+```
+
+### RD and RG by season
+
+```{r flow season, echo = F, fig.width = 12, fig.asp = 0.75, out.width = "100%"}
+
+#group by season and get max sums by season
+flow_season <- gw %>%
+  dplyr::select(RD1cumsum, RD2cumsum, RG1cumsum, RG2cumsum, date, year, source) %>%
+  mutate(month = month(date)) %>%
+  mutate(season = case_when(month %in% c(3,4,5,6) ~ 'snowmelt',
+                            month %in% c(7,8,9,10) ~ 'monsoon',
+                            month %in% c(11,12,1,2) ~ 'baseflow')) %>%
+  group_by(source, year, season) %>%
+  summarize(yr_season_RD1 = max(RD1cumsum),
+            yr_season_RD2 = max(RD2cumsum),
+            yr_season_RG1 = max(RG1cumsum),
+            yr_season_RG2 = max(RG2cumsum)) %>%
+            pivot_longer(!c(year, source, season), names_to = 'flow_type', values_to = 'flow_cms')
+
+flow_season %>%
+  ggplot(aes(x = flow_type, y = flow_cms, fill = source)) +
+  geom_boxplot(position = position_dodge(1)) +
+  geom_point(position=position_jitterdodge(),alpha=0.3) +
+  #geom_point(aes(color = source)) +
+  facet_wrap(~season, scales = 'free') +
+  ggtitle('Max annual season cumulative sums') +
+  theme_bw() +
+  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
+  theme(text = element_text(size = 20))
+
+flow_season %>%
+  ggplot(aes(x = flow_type, y = flow_cms, fill = source)) +
+  geom_boxplot(position = position_dodge(1)) +
+  geom_point(position=position_jitterdodge(),alpha=0.3) +
+  #geom_point(aes(color = source)) +
+  facet_wrap(~season + flow_type, scales = 'free') +
+  ggtitle('Max annual season cumulative sums') +
+  theme_bw() +
+  theme(text = element_text(size = 20))
 
@@
 tm_shape(hrus_map_tmean) +
-  tm_polygons('diff', id = 'value') +
+  tm_polygons('diff', id = 'value',
+              breaks = c(-6,-4,-2,0,2,4,6)) +
 tm_shape(locations_t) +
@@
 tm_shape(hrus_map_tmax) +
-  tm_polygons('diff', id = 'value') +
+  tm_polygons('diff', id = 'value',
+              breaks = c(-6,-4,-2,0,2,4,6)) +
 tm_shape(locations_t) +
@@
   tm_fill('mo_tmax_diff', id = 'value',
-          breaks = c(-6,-3,0,3,6)) +
+          breaks = c(-6,-4,-2,0,2,4,6)) +
   tm_borders() +
@@
   tm_fill('mo_tmax_diff', id = 'value',
-         breaks = c(-6,-3,0,3,6)) +
+         breaks = c(-6,-4,-2,0,2,4,6)) +
   tm_borders() +
@@
   tm_fill('mo_tmax_diff', id = 'value',
-          breaks = c(-6,-3,0,3,6)) +
+         breaks = c(-6,-4,-2,0,2,4,6)) +
   tm_borders() +
@@
 tm_shape(hrus_map_tmin) +
-  tm_polygons('diff', id = 'value') +
+  tm_polygons('diff', id = 'value',
+              breaks = c(-6,-4,-2,0,2,4,6)) +
 tm_shape(locations_t) +
@@
 
-Relative Precip difference
-
 ```{r relative p, echo = F}
 
-reg_p <- read_csv(here('HRU_output/reg_precipAll.csv'),
-                      skip = 21) %>%
-  dplyr::select(-starts_with('@')) %>%
-  mutate(time = dmy(time)) %>%
-  summarize(across(`3`:`19`, ~ mean(.))) %>%
-  pivot_longer(cols = `3`:`19`,
-               names_to = 'value', 
-               values_to = 'precip_avg') %>%
-  mutate(value = as.numeric(value))
-
-hrus_map_precip <- left_join(hrus_map_precip, reg_p, by = 'value')
-
-hrus_map_precip <- hrus_map_precip %>%
-  mutate(relative_avgcum_diff = precip_avg_cumdiff / precip_avg)
-
-tm_shape(hrus_map_precip) +
-  tm_polygons('relative_avgcum_diff', midpoint = NA, palette = 'YlGnBu', id = 'value') +
-tm_shape(locations_p) +
-  tm_symbols(col='blue', size=4)
+# reg_p <- read_csv(here('HRU_output/reg_precipAll.csv'),
+#                       skip = 21) %>%
+#   dplyr::select(-starts_with('@')) %>%
+#   mutate(time = dmy(time)) %>%
+#   summarize(across(`3`:`19`, ~ mean(.))) %>%
+#   pivot_longer(cols = `3`:`19`,
+#                names_to = 'value', 
+#                values_to = 'precip_avg') %>%
+#   mutate(value = as.numeric(value))
+# 
+# 
+# hrus_map_precip <- left_join(hrus_map_precip, reg_p, by = 'value') 
+# 
+# hrus_map_precip <- hrus_map_precip %>%
+#   mutate(relative_avgcum_diff = precip_avg_cumdiff / precip_avg)
+# 
+# tm_shape(hrus_map_precip) +
+#   tm_polygons('relative_avgcum_diff', midpoint = NA, palette = 'YlGnBu', id = 'value') +
+# tm_shape(locations_p) +
+#   tm_symbols(col='blue', size=4)
 
@@
 
-## Average soil sat difference comparison
+## Average soil sat comparison
 
@@
 soilavg_grid <- tm_shape(hrus_map_soilsat) +
-  tm_polygons('soilsat_all_grid', midpoint = NA, id = 'value') +
+  tm_polygons('soilsat_all_grid', midpoint = NA, id = 'value',
+              breaks = c(0.0, 0.05, 0.1, 0.15, 0.2, 0.25, 0.3)) +
   tm_legend(legend.outside = T) +
@@
 soilavg_statn <- tm_shape(hrus_map_soilsat) +
-  tm_polygons('soilsat_all_statn', midpoint = NA, id = 'value') +
+  tm_polygons('soilsat_all_statn', midpoint = NA, id = 'value',
+              breaks = c(0.0, 0.05, 0.1, 0.15, 0.2, 0.25, 0.3)) +
   tm_legend(legend.outside = T)
@@
 soilavg_grid_max <- tm_shape(hrus_map_soilsat_max) +
-  tm_polygons('avg_max_grid', midpoint = NA, id = 'value') +
+  tm_polygons('avg_max_grid', midpoint = NA, id = 'value',
+              breaks = c(0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.7)) +
   tm_legend(legend.outside = T) +
@@
 soilavg_statn_max <- tm_shape(hrus_map_soilsat_max) +
-  tm_polygons('avg_max_statn', midpoint = NA, id = 'value') +
+  tm_polygons('avg_max_statn', midpoint = NA, id = 'value',
+              breaks = c(0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.7)) +
   tm_legend(legend.outside = T)
@@
 ETavg_grid <- tm_shape(hrus_map_ET) +
-  tm_polygons('ET_all_grid', midpoint = NA, id = 'value') +
+  tm_polygons('ET_all_grid', midpoint = NA, id = 'value',
+              breaks = c(0.2, 0.4, 0.6, 0.8, 1.0, 1.2)) +
   tm_legend(legend.outside = T) +
@@
 ETavg_statn <- tm_shape(hrus_map_ET) +
-  tm_polygons('ET_all_statn', midpoint = NA, id = 'value') +
+  tm_polygons('ET_all_statn', midpoint = NA, id = 'value',
+             breaks = c(0.2, 0.4, 0.6, 0.8, 1.0, 1.2)) +
   tm_legend(legend.outside = T)
@@
 tmap_arrange(ETavg_grid, ETavg_statn)
+
+```
+
+## Average ET difference
+
+```{r et diff, echo = F}
+
+ET_hrus <- ET_hrus %>%
+  mutate(diff = ET_all_statn - ET_all_grid)
+
+hrus_map_et_diff <- left_join(hrus, ET_hrus, by = 'value')
+
+tmap_mode('plot')
+
+tm_shape(hrus_map_et_diff) +
+  tm_polygons('diff', midpoint = NA, id = 'value')  +
+  tm_legend(legend.outside = T) +
+  tm_layout(main.title = 'Average ET difference')
 
@@
 
-tmap_mode('plot')
+tmap_mode('view')
 
@@
 tmap_arrange(LAIavg_grid, LAIavg_statn)
+
+```
+
+## LAI over time
+
+```{r lai over time, echo = F}
+
+# plot time series of LAI over for HRU 1 and HRU 12
+hru_grid_select <- hru_grids %>%
+  filter(ID == 1 | ID == 12) %>%
+  dplyr::select(time, ID, LAI_grid = LAI)
+
+hru_statn_select <- hru_statn %>%
+  filter(ID == 1 | ID == 12) %>%
+  dplyr::select(time, ID, LAI_statn = LAI)
+
+hru_select <- left_join(hru_grid_select, hru_statn_select, by = c('time', 'ID')) %>%
+  rename(value = ID)
+
+# plot time series of LAI over for HRU 1
+hru_select %>%
+  mutate(year = year(time)) %>% 
+  filter(value == 1) %>% 
+ggplot(aes(x = time)) +
+  geom_line(aes(y = LAI_grid, color = "HRU1_burn_grid"), size = 1) +
+  geom_line(aes(y = LAI_statn, color = 'HRU1_burn_statn'), size = 1) +
+  ggtitle('LAI over time for HRU 1 (burned)') +
+  scale_color_manual(name = 'HRU' , values=c("HRU1_burn_grid"='orange', 
+                                            "HRU1_burn_statn"='springgreen4')) +
+  theme_bw()
+
+# plot time series of LAI over for HRU 12
+hru_select %>%
+  mutate(year = year(time)) %>% 
+  filter(value == 12) %>% 
+ggplot(aes(x = time)) +
+  geom_line(aes(y = LAI_grid, color = "HRU12_unburn_grid"), size = 1) +
+  geom_line(aes(y = LAI_statn, color = 'HRU12_unburn_statn'), size = 1) +
+  ggtitle('LAI over time for HRU 12 (unburned)') +
+  scale_color_manual(name = 'HRU' , values=c("HRU12_unburn_grid"='orange', 
+                                            "HRU12_unburn_statn"='springgreen4')) +
+  theme_bw()
 

### 2023-03-07 calibration_output.Rmd
some updates

@@
 library(tmap)
+library(ggpubr)
+library(gridExtra)
 
@@
 # plot time series of LAI over for HRU 12
-hru_select %>%
+{hru_select %>%
   mutate(year = year(time)) %>% 
@@
                                             "HRU12_unburn_statn"='springgreen4')) +
-  theme_bw()
-
-```
-
-```{r reach hydrographs, echo = F}
-
-# reach <- read_csv('reach_all.csv') %>%
-#   mutate(reach = as.factor(reach)) %>%
-#   pivot_longer(!c(date, reach, WY), names_to = 'cal', values_to = 'q_cms')
-# 
-#   
-# plotq_reach <- function(reach_name) {
-#   {reach %>%
-#     filter(reach == reach_name) %>%
-#     ggplot(aes(x = date,
-#                y = q_cms,
-#                color = cal)) + 
-#     geom_line() + 
-#     ggtitle(reach_name) +
-#     theme_bw()} %>%
-#     ggplotly()
-#   
-# }
-# 
-# name <- levels(reach$reach)
-# 
-# try2 <- lapply(name, plotq_reach)
-# 
-# htmltools::tagList(try2)
-# 
-# ```
-# 
-# ### Overall KGE by reach
-# 
-# ```{r reach kge, echo = F}
-# 
-# reach_pivot <- reach %>%
-#   pivot_wider(names_from = 'cal', values_from = 'q_cms') %>%
-#   mutate(WY = as.factor(calcWaterYear(date)))
-# 
-# reach_kge_all <- reach_pivot %>%
-#   group_by(reach) %>%
-#   summarize(grid2011 = KGE(grid_2011, obs),
-#             grid2012 = KGE(grid_2012, obs),
-#             grid2013 = KGE(grid_2013, obs),
-#             grid2014 = KGE(grid_2014, obs),
-#             grid2015 = KGE(grid_2015, obs),
-#             grid2016 = KGE(grid_2016, obs),
-#             grid2017 = KGE(grid_2017, obs),
-#             grid2018 = KGE(grid_2018, obs),
-#             grid2019 = KGE(grid_2019, obs),
-#             grid2020 = KGE(grid_2020, obs),
-#             gridall = KGE(grid_all, obs),
-#             statn2011 = KGE(statn_2011, obs),
-#             statn2012 = KGE(statn_2012, obs),
-#             statn2013 = KGE(statn_2013, obs),
-#             statn2014 = KGE(statn_2014, obs),
-#             statn2015 = KGE(statn_2015, obs),
-#             statn2016 = KGE(statn_2016, obs),
-#             statn2017 = KGE(statn_2017, obs),
-#             statn2018 = KGE(statn_2018, obs),
-#             statn2019 = KGE(statn_2019, obs),
-#             statn2020 = KGE(statn_2020, obs),
-#             statnall = KGE(statn_all, obs)) %>%
-#     mutate_if(is.numeric,
-#             round,
-#             digits = 2)
-# 
-# 
-# reach_kge_all <- reach_kge_all %>%
-#   pivot_longer(!reach, names_to = 'cal_runs', values_to = 'KGE') %>%
-#   pivot_wider(names_from = 'reach', values_from = 'KGE')
-# 
-# 
-# kable(reach_kge_all) %>%
-#   kable_styling(full_width = F)
-# 
-# 
-# obs_count <- reach_pivot %>%
-#   select(obs, reach) %>%
-#   drop_na() %>%
-#   group_by(reach) %>%
-#   summarize(count_obs = n())
-# 
-# kable(obs_count, caption = 'Streamflow observation count') %>%
-#   kable_styling(full_width = F)
-
-```
+  theme_bw()} %>%
+  ggplotly()
+
+```
+
+## HRU 29 LAI and biomass
+
+```{r hru29 lai and biomass}
+
+# plot time series of LAI 29
+hru_grid29 <- hru_grids %>%
+  filter(ID == 29) %>%
+  dplyr::select(time, ID, LAI_grid = LAI)
+
+hru_statn29 <- hru_statn %>%
+  filter(ID == 29) %>%
+  dplyr::select(time, ID, LAI_statn = LAI)
+
+hru_29 <- left_join(hru_grid29, hru_statn29, by = c('time', 'ID'))
+
+# plot time series of LAI over for HRU 29
+{hru_29 %>%
+  ggplot(aes(x = time)) +
+  geom_line(aes(y = LAI_grid, color = "HRU29_grid"), size = 1) +
+  geom_line(aes(y = LAI_statn, color = 'HRU29_statn'), size = 1) +
+  ggtitle('LAI - HRU 29') +
+  scale_color_manual(name = 'HRU' , values=c("HRU29_grid"='orange', 
+                                            "HRU29_statn"='springgreen4')) +
+  theme_bw()} %>%
+  ggplotly()
+
+hru29grid_bio <- read_csv('/Users/megansears/Documents/Repos/fourmile/HRU_output/HRU_29_grid.csv') %>%
+  mutate(time = mdy(time)) %>%
+  dplyr::select(time, BioAct_grid = BioAct_kgha)
+
+hru29statn_bio <- read_csv('/Users/megansears/Documents/Repos/fourmile/HRU_output/HRU_29_statn.csv') %>%
+  mutate(time = mdy(time)) %>%
+  dplyr::select(time, BioAct_statn= BioAct_kgha)
+
+hru_29_bio <- left_join(hru29grid_bio, hru29statn_bio, by = c('time'))
+
+#plot time series of biomass over time for HRU 29
+{hru_29_bio %>%
+  ggplot(aes(x = time)) +
+  geom_line(aes(y = BioAct_grid, color = "HRU29_grid"), size = 1) +
+  geom_line(aes(y = BioAct_statn, color = 'HRU29_statn'), size = 1) +
+  ggtitle('Biomass') +
+  scale_color_manual(name = 'HRU' , values=c("HRU29_grid"='orange', 
+                                            "HRU29_statn"='springgreen4')) +
+  theme_bw()} %>%
+  ggplotly()
+
+```
+
+# Mauscript figs
+
+## Figure 1
+
+```{r fig1}
+
+library(usmap)
+
+dem <- raster('/Users/megansears/Documents/Repos/fourmile/data/GIS/cutDEM.tif')
+
+hru_bnds <- st_read('/Users/megansears/Documents/Repos/fourmile/data/GIS/hrus_final.shp')
+
+tmap_mode('plot')
+
+tm_shape(dem) +
+  tm_raster(palette = terrain.colors(5)) +
+  tm_shape(hru_bnds) +
+  tm_polygons(alpha =0, col = 'black') +
+  tm_compass() +
+  tm_scale_bar() +
+  tm_layout(legend.outside = T,
+            main.title = 'A')
+
+dem2 <- as.data.frame(dem, xy = TRUE)
+
+# ggplot() +
+#  geom_polygon(data = hru_bnds, aes(x = x, y = y, fill = value)) +
+#   geom_raster(data = dem2, aes(x = x, y = y,
+#                                       fill = cutDEM)) +
+#   theme_bw() +
+#   coord_quickmap()
+
+###################################################
+
+catchment_mo_mean <- catchment %>%
+  mutate(month = month(time)) %>%
+  group_by(site, month) %>%
+  summarise(across(precip:solRad, ~ mean(.x, na.rm = TRUE))) %>%
+  dplyr::select(site, month,
+                precip_mean = precip, tmean_mean = tmean, 
+                solrad_mean = solRad, rh_mean = rhum)
+
+catchment_mo_max <- catchment %>%
+  mutate(month = month(time)) %>%
+  group_by(site, month) %>%
+  summarise(across(precip:solRad, ~ max(.x, na.rm = TRUE))) %>%
+  dplyr::select(site, month,
+                precip_max = precip, tmax_max = tmean, 
+                solrad_max = solRad, rh_max = rhum)
+
+catchment_mo_min <- catchment %>%
+  mutate(month = month(time)) %>%
+  group_by(site, month) %>%
+  summarise(across(precip:solRad, ~ min(.x, na.rm = TRUE))) %>%
+  dplyr::select(site, month,
+                precip_min = precip, tmin_min = tmean, 
+                solrad_min = solRad, rh_min = rhum)
+
+catchment_mo <- left_join(catchment_mo_mean, catchment_mo_max, 
+                          by = c('month', 'site'))
+
+catchment_mo2 <- left_join(catchment_mo, catchment_mo_min, 
+                          by = c('month', 'site')) %>%
+  mutate(month_name = month.abb[month]) %>%
+  mutate(month_name = factor(month_name, 
+                             levels = c('Jan', 'Feb', 'Mar',
+                                        'Apr', 'May', 'Jun',
+                                        'Jul', 'Aug', 'Sep',
+                                        'Oct', 'Nov', 'Dec')))
+
+p_moplot <- ggplot(catchment_mo2, aes(x = month_name, y = precip_mean, 
+                                      color = site, group = site)) +
+  geom_ribbon(aes(ymin = precip_min, ymax = precip_max, fill = site), alpha = 0.2) +
+  geom_line() +
+  geom_point() +
+  theme_bw() +
+  labs(y = 'Precipitation (mm)') +
+  ggtitle('B')
+
+p_moplot
+
+t_moplot <- ggplot(catchment_mo2, aes(x = month_name, y = tmean_mean, 
+                                      color = site, group = site)) +
+  geom_ribbon(aes(ymin = tmin_min, ymax = tmax_max, fill = site), alpha = 0.2) +
+  geom_line() +
+  geom_point() +
+  theme_bw() +
+  labs(y = expression("Mean temperature " ( degree~C)))+
+  ggtitle('C')
+
+t_moplot
+
+sol_moplot <- ggplot(catchment_mo2, aes(x = month_name, y = solrad_mean, 
+                                      color = site, group = site)) +
+  geom_ribbon(aes(ymin = solrad_min, ymax = solrad_max, fill = site), alpha = 0.2) +
+  geom_line() +
+  geom_point() +
+  theme_bw() +
+  labs(y = 'Solar Radiation (unit)') +
+  ggtitle('D')
+
+sol_moplot
+
+rh_moplot <- ggplot(catchment_mo2, aes(x = month_name, y = rh_mean, 
+                                      color = site, group = site)) +
+  geom_ribbon(aes(ymin = rh_min, ymax = rh_max, fill = site), alpha = 0.2) +
+  geom_line() +
+  geom_point() +
+  theme_bw() +
+  labs(y = 'RH (%)', x= 'Month') +
+  ggtitle('E')
+
+rh_moplot
+
+ggarrange(p_moplot+ rremove("x.text") +
+               rremove("x.title") +
+               rremove('x.ticks'),
+             t_moplot+ rremove("x.text") +
+               rremove("x.title")+
+               rremove('x.ticks'), 
+             sol_moplot + rremove("x.text") +
+               rremove("x.title")+
+               rremove('x.ticks'),
+             rh_moplot,
+          common.legend = T,
+          legend = 'bottom',
+             nrow = 4)
+
+```

### 2023-03-16 calibration_output.Rmd
hd fig updates

@@
 ```{r catch precip, echo = F}
-setwd("./catchment_output")
+setwd("/Users/megansears/Documents/Repos/fourmile/catchment_output")
 
@@
 
-catchment_mo_max <- catchment %>%
+catchment_mo_sd <- catchment %>%
   mutate(month = month(time)) %>%
   group_by(site, month) %>%
-  summarise(across(precip:solRad, ~ max(.x, na.rm = TRUE))) %>%
+  summarise(across(precip:solRad, ~ sd(.x, na.rm = TRUE))) %>%
   dplyr::select(site, month,
-                precip_max = precip, tmax_max = tmean, 
-                solrad_max = solRad, rh_max = rhum)
-
-catchment_mo_min <- catchment %>%
-  mutate(month = month(time)) %>%
-  group_by(site, month) %>%
-  summarise(across(precip:solRad, ~ min(.x, na.rm = TRUE))) %>%
-  dplyr::select(site, month,
-                precip_min = precip, tmin_min = tmean, 
-                solrad_min = solRad, rh_min = rhum)
-
-catchment_mo <- left_join(catchment_mo_mean, catchment_mo_max, 
+                precip_sd = precip, tmean_sd = tmean, 
+                solrad_sd = solRad, rh_sd = rhum)
+
+catchment_mo <- left_join(catchment_mo_mean, catchment_mo_sd, 
                           by = c('month', 'site'))
 
-catchment_mo2 <- left_join(catchment_mo, catchment_mo_min, 
-                          by = c('month', 'site')) %>%
+catchment_mo2 <- catchment_mo %>%
   mutate(month_name = month.abb[month]) %>%
@@
 
-p_moplot <- ggplot(catchment_mo2, aes(x = month_name, y = precip_mean, 
+p_cols <- ggplot(catchment_mo2, aes(x = month_name, y = precip_mean,
+                          color = site, fill = site)) +
+  geom_col(position='dodge') +
+  geom_errorbar(aes(ymin = 0, ymax = precip_mean + precip_sd), 
+                position = position_dodge(width = 0.6), width = 0.2) +
+  theme_bw(base_size = 14) +
+  labs(y = 'Precipitation (mm)',
+       x = element_blank())
+
+ggsave("P.png", plot = p_cols, width = 8, height = 6, dpi = 300)
+
+t_moplot <- ggplot(catchment_mo2, aes(x = month_name, y = tmean_mean, 
                                       color = site, group = site)) +
-  geom_ribbon(aes(ymin = precip_min, ymax = precip_max, fill = site), alpha = 0.2) +
+  geom_ribbon(aes(ymin = tmean_mean - tmean_sd, ymax = tmean_mean + tmean_sd, fill = site), alpha = 0.2) +
   geom_line() +
   geom_point() +
-  theme_bw() +
-  labs(y = 'Precipitation (mm)') +
-  ggtitle('B')
-
-p_moplot
-
-t_moplot <- ggplot(catchment_mo2, aes(x = month_name, y = tmean_mean, 
+  theme_bw(base_size=14) +
+  labs(y = expression("Mean temperature " ( degree~C)),
+       x = element_blank())
+
+t_moplot
+
+sol_moplot <- ggplot(catchment_mo2, aes(x = month_name, y = solrad_mean, 
                                       color = site, group = site)) +
-  geom_ribbon(aes(ymin = tmin_min, ymax = tmax_max, fill = site), alpha = 0.2) +
+  geom_ribbon(aes(ymin = solrad_mean - solrad_sd, ymax = solrad_mean + solrad_sd, fill = site), alpha = 0.2) +
   geom_line() +
   geom_point() +
-  theme_bw() +
-  labs(y = expression("Mean temperature " ( degree~C)))+
-  ggtitle('C')
-
-t_moplot
-
-sol_moplot <- ggplot(catchment_mo2, aes(x = month_name, y = solrad_mean, 
+  theme_bw(base_size = 14) +
+  labs(y = expression("Solar radiation (MJ/m"^"2" * ")"),
+       x = element_blank())
+
+sol_moplot
+
+rh_moplot <- ggplot(catchment_mo2, aes(x = month_name, y = rh_mean, 
                                       color = site, group = site)) +
-  geom_ribbon(aes(ymin = solrad_min, ymax = solrad_max, fill = site), alpha = 0.2) +
+  geom_ribbon(aes(ymin = rh_mean - rh_sd, ymax = rh_mean + rh_sd, fill = site), alpha = 0.2) +
   geom_line() +
   geom_point() +
-  theme_bw() +
-  labs(y = 'Solar Radiation (unit)') +
-  ggtitle('D')
-
-sol_moplot
-
-rh_moplot <- ggplot(catchment_mo2, aes(x = month_name, y = rh_mean, 
-                                      color = site, group = site)) +
-  geom_ribbon(aes(ymin = rh_min, ymax = rh_max, fill = site), alpha = 0.2) +
-  geom_line() +
-  geom_point() +
-  theme_bw() +
-  labs(y = 'RH (%)', x= 'Month') +
-  ggtitle('E')
-
+  theme_bw(base_size = 14) +
+  labs(y = 'RH (%)', x= element_blank()) 
 rh_moplot
 
-ggarrange(p_moplot+ rremove("x.text") +
-               rremove("x.title") +
-               rremove('x.ticks'),
-             t_moplot+ rremove("x.text") +
-               rremove("x.title")+
-               rremove('x.ticks'), 
-             sol_moplot + rremove("x.text") +
-               rremove("x.title")+
-               rremove('x.ticks'),
+quad <- ggarrange(p_cols, 
+          t_moplot,
+          sol_moplot,
           rh_moplot,
@@
           legend = 'bottom',
-             nrow = 4)
-
-```
+             nrow = 2,
+          ncol= 2)
+
+ggsave("quad.png", plot = quad, width = 8, height = 6, dpi = 300)
+
+```

### 2023-04-25 38HRU_model/fourmile_model_outputs.Rmd
messed up

---
title: "Fourmile Calibrations and Output"
author: "Megan Sears"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: yes
    toc_float: yes
    theme: journal
editor_options:
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = F,
  message = F, 
  warning  = F)

library(tidyverse)
library(plotly)
library(lubridate)
library(knitr)
library(kableExtra)
library(dataRetrieval)
library(hydroGOF)
library(sp)
library(raster)
library(sf)
library(mapview)
library(here)
library(scales)
library(dataRetrieval)
library(tmap)
library(ggpubr)
library(gridExtra)

```

```{r load in files, include = F}

kge <- read_csv('calruns_KGE.csv')

```

# KGE for calibrations

```{r look at kge, echo = F}

kge_plot <- ggplot(kge, aes(year_missing, KGE, shape = input_data, color = input_data)) + geom_point(size = 3) +
  theme_bw()

ggplotly(kge_plot)

```

# Parameters

## Scatter plots

```{r read in params, echo = FALSE, message = FALSE, warning = FALSE, include = F}
setwd("/Users/megansears/Documents/Repos/fourmile/38HRU_model/cals")

#pull in all filenames with composite
filenames <- list.files('.', pattern=".csv", full.names=F)

#read all the csvs
dataframes <- lapply(filenames, read_csv)

#name all the csv
names(dataframes) <- substr(filenames, 1, 9)

#extract csvs from list to global env
lapply(names(dataframes), function(x) assign(x, dataframes[[x]], envir = .GlobalEnv))
rm(dataframes) #remove dataframes list

```

```{r params, echo = FALSE, message = FALSE, warning = FALSE}

# function to read files, remove top rows, paste site name
read_cals <- function(df, name){
    df <- df %>%
      slice(-c(1:9, 146:277)) %>%
      separate(Parameter, c("Parameter", "value"), sep = ",") %>%
      drop_na() %>%
      dplyr::select(-1) %>% 
      mutate(cal = name)

}

grid_2011 <- read_cals(grid2011., name = 'grid_2011')
grid_2012 <- read_cals(grid2012., name = 'grid_2012')
grid_2013 <- read_cals(grid2013., name = 'grid_2013')
grid_2014 <- read_cals(grid2014., name = 'grid_2014')
grid_2015 <- read_cals(grid2015., name = 'grid_2015')
grid_2016 <- read_cals(grid2016., name = 'grid_2016')
grid_2017 <- read_cals(grid2017., name = 'grid_2017')
grid_2018 <- read_cals(grid2018., name = 'grid_2018')
grid_2019 <- read_cals(grid2019., name = 'grid_2019')
grid_2020 <- read_cals(grid2020., name = 'grid_2020')
grid_all <- read_cals(gridall.c, name = 'grid_all')

grid <- bind_rows(grid_2011, grid_2012, grid_2013, grid_2014, grid_2015,
                  grid_2016, grid_2017, grid_2018, grid_2019, grid_2020,
                  grid_all) %>%
  mutate(input_data = 'grid') %>%
  mutate(year_missing_almost = gsub('grid_', '', cal)) %>%
  mutate(year_missing = gsub('all', 'none', year_missing_almost)) %>%
  dplyr::select(-c(year_missing_almost)) %>%
  rename(param = Parameter) %>%
  filter(!param == 'locGrw',
         !param == 'tempRes')

statn_2011 <- read_cals(statn2011, name = 'statn_2011')
statn_2012 <- read_cals(statn2012, name = 'statn_2012')
statn_2013 <- read_cals(statn2013, name = 'statn_2013')
statn_2014 <- read_cals(statn2014, name = 'statn_2014')
statn_2015 <- read_cals(statn2015, name = 'statn_2015')
statn_2016 <- read_cals(statn2016, name = 'statn_2016')
statn_2017 <- read_cals(statn2017, name = 'statn_2017')
statn_2018 <- read_cals(statn2018, name = 'statn_2018')
statn_2019 <- read_cals(statn2019, name = 'statn_2019')
statn_2020 <- read_cals(statn2020, name = 'statn_2020')
statn_all <- read_cals(statnall., name = 'statn_all')

statn <- bind_rows(statn_2011, statn_2012, statn_2013, statn_2014, statn_2015,
                  statn_2016, statn_2017, statn_2018, statn_2019, statn_2020,
                  statn_all) %>%
  mutate(input_data = 'statn') %>%
  mutate(year_missing_almost = gsub('statn_', '', cal)) %>%
  mutate(year_missing = gsub('all', 'none', year_missing_almost)) %>%
  dplyr::select(-c(year_missing_almost)) %>%
  rename(param = Parameter) %>%
  filter(!param == 'locGrw',
         !param == 'tempRes')

params <- bind_rows(statn, grid)

params <- params %>%
  filter(!param %in% c('angstrom_a', 'angstrom_b', 
                      'Beta_min', 
                      'Beta_rsd', "Beta_trans", 'clat', 
                      'delayNitrification',
                      'denitrificationRateCoefficient', 
                      'denitrificationSoilSaturationThreshold',
                      'deposition_factor', 'drrad', 
                      'drspac', 'initLPS', 'initRG1',
                      'initRG2', 'Ksink', 'LExCoef', 
                      'longTZ', 'N_concRG1', 'N_concRG2', 'N_delay_RG1',
                      'N_delay_RG2', 
                      'nitrificationSoilTemperatureThreshold', 
                      'nitrificationSurfaceTemperatureThreshold',
                      'opti', 'piadin', 'rootfactor', 'sceno', 
                      'soilImpGT80', 'soilImpLT80',
                      'soilLinRed', 'soilMaxPerc', 'temp_lag')) %>%
    mutate(value = as.numeric(value),
         param = as.factor(param))

#function to plot all params
plot_params <- function(param_name) {
  params %>%
    filter(param == param_name) %>%
    ggplot(aes(x = year_missing,
               y = value,
               shape = input_data, 
               color = input_data)) + 
    geom_point(size = 3) + 
    ggtitle(param_name) +
    theme_bw()
}

name <- levels(params$param)

lapply(name, plot_params)

#write.csv(params, 'params.csv')

```

## Density plots

```{r density plots, echo = F, message = F}

mean_params <- params %>%
  group_by(param, input_data) %>%
  summarize(mean = mean(value))

plotdens_params <- function(param_name) {
  params %>%
    filter(param == param_name) %>%
    ggplot(aes(x = value,
               fill = input_data, 
               color = input_data)) + 
    geom_density(alpha=0.5) +
    geom_vline(data=filter(mean_params, param == param_name), 
               aes(xintercept=mean, color=input_data),
             linetype="dashed", linewidth=0.75) +
    ggtitle(param_name) +
    theme_bw()
}

name <- levels(params$param)

lapply(name, plotdens_params)

```

<!-- # Outlet results -->

<!-- ## Hydrograph -->

<!-- ```{r hydrographs, echo = F} -->
<!-- flow <- read_csv('discharge_all.csv') %>% -->
<!--   replace(.==-9999, NA) -->

<!-- flow_pivot <- flow %>% -->
<!--   pivot_longer(!date, names_to = 'cal_run', values_to = 'q_m3s') %>% -->
<!--   mutate(year = as.factor(year(date))) -->

<!-- q <- ggplot(flow_pivot, aes(date, q_m3s, color = cal_run)) + -->
<!--   geom_line() + -->
<!--   scale_color_manual(name="cal_run", values=c('obs' = 'black', -->
<!--                                             "grid_2011"="seagreen", -->
<!--                                             "grid_2012"="seagreen2", -->
<!--                                             "grid_2013"="steelblue", -->
<!--                                             "grid_2014"='dodgerblue', -->
<!--                                             "grid_2015" = "cyan3", -->
<!--                                             'grid_2016' = 'blue', -->
<!--                                             'grid_2017' = 'blue4', -->
<!--                                             'grid_2018' = 'cadetblue', -->
<!--                                             'grid_2019' = 'lightgreen', -->
<!--                                             'grid_2020' = 'olivedrab', -->
<!--                                             'grid_all' = 'steelblue3', -->
<!--                                             "statn_2011"="maroon", -->
<!--                                             "statn_2012"="deeppink4", -->
<!--                                             "statn_2013"="deeppink", -->
<!--                                             "statn_2014"='purple', -->
<!--                                             "statn_2015" = "mediumorchid1", -->
<!--                                             'statn_2016' = 'indianred', -->
<!--                                             'statn_2017' = 'sienna', -->
<!--                                             'statn_2018' = 'salmon2', -->
<!--                                             'statn_2019' = 'mediumpurple1', -->
<!--                                             'statn_2020' = 'violetred', -->
<!--                                             'statn_all' = 'red')) -->

<!-- ggplotly(q) -->

<!-- ``` -->

<!-- ## Annual hydrographs -->

<!-- ```{r cy hydrographs, echo = F} -->

<!-- plotq_cy <- function(calyear) { -->
<!--   {flow_pivot %>% -->
<!--     filter(year == calyear) %>% -->
<!--     ggplot(aes(x = date, -->
<!--                y = q_m3s, -->
<!--                color = cal_run)) + -->
<!--     geom_line() + -->
<!--         scale_color_manual(name="cal_run", values=c('obs' = 'black', -->
<!--                                             "grid_2011"="seagreen",  -->
<!--                                             "grid_2012"="seagreen2",  -->
<!--                                             "grid_2013"="steelblue", -->
<!--                                             "grid_2014"='dodgerblue',  -->
<!--                                             "grid_2015" = "cyan3", -->
<!--                                             'grid_2016' = 'blue', -->
<!--                                             'grid_2017' = 'blue4', -->
<!--                                             'grid_2018' = 'cadetblue', -->
<!--                                             'grid_2019' = 'lightgreen', -->
<!--                                             'grid_2020' = 'olivedrab', -->
<!--                                             'grid_all' = 'steelblue3', -->
<!--                                             "statn_2011"="maroon",  -->
<!--                                             "statn_2012"="deeppink4",  -->
<!--                                             "statn_2013"="deeppink", -->
<!--                                             "statn_2014"='purple',  -->
<!--                                             "statn_2015" = "mediumorchid1", -->
<!--                                             'statn_2016' = 'indianred', -->
<!--                                             'statn_2017' = 'sienna', -->
<!--                                             'statn_2018' = 'salmon2', -->
<!--                                             'statn_2019' = 'mediumpurple1', -->
<!--                                             'statn_2020' = 'violetred', -->
<!--                                             'statn_all' = 'red')) + -->
<!--     ggtitle(calyear) + -->
<!--     theme_bw()} %>% -->
<!--     ggplotly() -->

<!-- } -->

<!-- name <- levels(flow_pivot$year) -->

<!-- try <- lapply(name, plotq_cy) -->

<!-- htmltools::tagList(try) -->

<!-- try -->
<!-- ``` -->

<!-- ## KGE -->

<!-- ### Overall KGE -->

<!-- ```{r kge overall, echo = F} -->

<!-- flow_kge_all <- flow %>% -->
<!--   summarize(grid2011 = KGE(grid_2011, obs), -->
<!--             grid2012 = KGE(grid_2012, obs), -->
<!--             grid2013 = KGE(grid_2013, obs), -->
<!--             grid2014 = KGE(grid_2014, obs), -->
<!--             grid2015 = KGE(grid_2015, obs), -->
<!--             grid2016 = KGE(grid_2016, obs), -->
<!--             grid2017 = KGE(grid_2017, obs), -->
<!--             grid2018 = KGE(grid_2018, obs), -->
<!--             grid2019 = KGE(grid_2019, obs), -->
<!--             grid2020 = KGE(grid_2020, obs), -->
<!--             gridall = KGE(grid_all, obs), -->
<!--             statn2011 = KGE(statn_2011, obs), -->
<!--             statn2012 = KGE(statn_2012, obs), -->
<!--             statn2013 = KGE(statn_2013, obs), -->
<!--             statn2014 = KGE(statn_2014, obs), -->
<!--             statn2015 = KGE(statn_2015, obs), -->
<!--             statn2016 = KGE(statn_2016, obs), -->
<!--             statn2017 = KGE(statn_2017, obs), -->
<!--             statn2018 = KGE(statn_2018, obs), -->
<!--             statn2019 = KGE(statn_2019, obs), -->
<!--             statn2020 = KGE(statn_2020, obs), -->
<!--             statnall = KGE(statn_all, obs)) %>% -->
<!--     mutate_if(is.numeric, -->
<!--             round, -->
<!--             digits = 2) -->

<!-- flow_kge_all <- flow_kge_all %>% -->
<!--   pivot_longer(everything()) %>% -->
<!--   arrange(value) -->

<!-- kable(flow_kge_all) %>% -->
<!--   kable_styling(full_width = F) -->

<!-- ``` -->

<!-- ### KGE by year -->

<!-- ```{r kge by year, echo = F} -->

<!-- flow_year <- flow %>% -->
<!--   mutate(year = year(date)) %>% -->
<!--   group_by(year) %>% -->
<!--   summarize(grid2011 = KGE(grid_2011, obs), -->
<!--             grid2012 = KGE(grid_2012, obs), -->
<!--             grid2013 = KGE(grid_2013, obs), -->
<!--             grid2014 = KGE(grid_2014, obs), -->
<!--             grid2015 = KGE(grid_2015, obs), -->
<!--             grid2016 = KGE(grid_2016, obs), -->
<!--             grid2017 = KGE(grid_2017, obs), -->
<!--             grid2018 = KGE(grid_2018, obs), -->
<!--             grid2019 = KGE(grid_2019, obs), -->
<!--             grid2020 = KGE(grid_2020, obs), -->
<!--             gridall = KGE(grid_all, obs), -->
<!--             statn2011 = KGE(statn_2011, obs), -->
<!--             statn2012 = KGE(statn_2012, obs), -->
<!--             statn2013 = KGE(statn_2013, obs), -->
<!--             statn2014 = KGE(statn_2014, obs), -->
<!--             statn2015 = KGE(statn_2015, obs), -->
<!--             statn2016 = KGE(statn_2016, obs), -->
<!--             statn2017 = KGE(statn_2017, obs), -->
<!--             statn2018 = KGE(statn_2018, obs), -->
<!--             statn2019 = KGE(statn_2019, obs), -->
<!--             statn2020 = KGE(statn_2020, obs), -->
<!--             statnall = KGE(statn_all, obs)) %>% -->
<!--     mutate_if(is.numeric, -->
<!--             round, -->
<!--             digits = 2) -->

<!-- flow_kge <- flow_year %>% -->
<!--   pivot_longer(!year, names_to = 'model_run', values_to = 'kge') %>% -->
<!--   pivot_wider(names_from = 'year', values_from = 'kge') -->

<!-- flow_kge %>% -->
<!--   kable(.) %>% -->
<!--   kable_styling() -->

<!-- flow_plot <- flow_year %>% -->
<!--   pivot_longer(!year, names_to = 'model_run', values_to = 'kge') %>% -->
<!--   mutate(year = as.factor(year)) -->

<!-- kge_plot_cy <- ggplot(flow_plot, aes(year, kge, color = model_run)) +  -->
<!--   geom_point(size = 3) + -->
<!--   scale_color_manual(name="model_run", values=c("grid2011"="seagreen",  -->
<!--                                             "grid2012"="seagreen2",  -->
<!--                                             "grid2013"="steelblue", -->
<!--                                             "grid2014"='dodgerblue',  -->
<!--                                             "grid2015" = "cyan3", -->
<!--                                             'grid2016' = 'blue', -->
<!--                                             'grid2017' = 'blue4', -->
<!--                                             'grid2018' = 'cadetblue', -->
<!--                                             'grid2019' = 'lightgreen', -->
<!--                                             'grid2020' = 'olivedrab', -->
<!--                                             'gridall' = 'steelblue3', -->
<!--                                             "statn2011"="maroon",  -->
<!--                                             "statn2012"="deeppink4",  -->
<!--                                             "statn2013"="deeppink", -->
<!--                                             "statn2014"='purple',  -->
<!--                                             "statn2015" = "mediumorchid1", -->
<!--                                             'statn2016' = 'indianred', -->
<!--                                             'statn2017' = 'sienna', -->
<!--                                             'statn2018' = 'salmon2', -->
<!--                                             'statn2019' = 'mediumpurple1', -->
<!--                                             'statn2020' = 'violetred', -->
<!--                                             'statnall' = 'red')) + -->
<!--   theme_bw() -->

<!-- ggplotly(kge_plot_cy) -->

<!-- ``` -->

<!-- ### Annual KGE plots -->

<!-- ```{r wy plots, echo = F} -->

<!-- plot_kge <- function(calyear) { -->
<!--   flow_plot %>% -->
<!--     filter(year == calyear) %>% -->
<!--     ggplot(aes(x = model_run, -->
<!--                y = kge)) + -->
<!--     geom_col() + -->
<!--     ggtitle(calyear) + -->
<!--     theme_bw() + -->
<!--     theme(axis.text.x = element_text(angle = 45, hjust=1)) -->
<!-- } -->

<!-- name <- levels(flow_plot$year) -->

<!-- lapply(name, plot_kge) -->

<!-- ``` -->

<!-- # Ensembles -->

<!-- ## Hydrograph -->

<!-- ```{r boulder cr gage, echo = F} -->

<!-- #pull in Boulder Creek @ N 75th gage -->

<!-- bouldcr <- readNWISdv(siteNumbers = "06730200", -->
<!--                           parameterCd = "00060",  -->
<!--                           startDate = "2011-01-01",  -->
<!--                           endDate = "2020-12-31")  %>% -->
<!--   dplyr::select(date = Date, -->
<!--          q_cfs = X_00060_00003) %>% -->
<!--   mutate(bouldcr = q_cfs/35.3146662) %>% -->
<!--   dplyr::select(-q_cfs) %>% -->
<!--   mutate(year = year(date)) -->

<!-- ``` -->

<!-- ```{r ensemble hydrographs, echo = F} -->

<!-- ensem <- flow %>% -->
<!--   rowwise() %>% -->
<!--   mutate(grid_ensemble = mean(c(grid_2011, grid_2012, -->
<!--                                 grid_2013, grid_2014, -->
<!--                                 grid_2015, grid_2016, -->
<!--                                 grid_2017, grid_2018, -->
<!--                                 grid_2019, grid_2020)), -->
<!--          statn_ensemble = mean(c(statn_2011, statn_2012, -->
<!--                                  statn_2013, statn_2014, -->
<!--                                  statn_2015, statn_2016, -->
<!--                                  statn_2017, statn_2018, -->
<!--                                  statn_2019, statn_2020)), -->
<!--          all_ensemble = mean(c(grid_2011, grid_2012, -->
<!--                                grid_2013, grid_2014, -->
<!--                                grid_2015, grid_2016, -->
<!--                                grid_2017, grid_2018, -->
<!--                                grid_2019, grid_2020, -->
<!--                                statn_2011, statn_2012, -->
<!--                                statn_2013, statn_2014, -->
<!--                                statn_2015, statn_2016, -->
<!--                                statn_2017, statn_2018, -->
<!--                                statn_2019, statn_2020, -->
<!--                                grid_all, statn_all))) %>% -->
<!--   dplyr::select(date, grid_ensemble, statn_ensemble,  -->
<!--          all_ensemble, grid_all,  -->
<!--          statn_all, obs)  -->

<!-- ensem_pivot <- ensem %>% -->
<!--   pivot_longer(!date, names_to = 'cal_run', values_to = 'q_m3s') %>% -->
<!--   mutate(year = as.factor(year(date))) -->

<!-- q_ensemble <- ggplot(ensem_pivot, aes(date, q_m3s, color = cal_run)) + -->
<!--   geom_line() + -->
<!--   scale_color_manual(name="cal_run", values=c('obs'='black', -->
<!--                                             "grid_ensemble"="maroon",  -->
<!--                                             "statn_ensemble"="darkturquoise",  -->
<!--                                             "grid_all"="purple1", -->
<!--                                             "statn_all"='springgreen4',  -->
<!--                                             "all_ensemble" = "orange")) + -->
<!--   geom_line(data = bouldcr, aes(date, bouldcr/10), color = 'darkgrey') + -->
<!--   scale_y_continuous(name = 'Q_m3s', -->
<!--                     sec.axis = sec_axis(~.*10, name='BoulderCr_cms')) + -->
<!--   theme_bw() -->

<!-- ggplotly(q_ensemble) %>% -->
<!--   add_lines(data=bouldcr, x=~date, y=~bouldcr, colors=NULL, yaxis="y2",  -->
<!--               inherit=FALSE, showlegend = FALSE) %>% -->
<!--   layout(yaxis2 = list(overlaying = "y", side = "right", -->
<!--                        color = 'darkgray', -->
<!--                        title = "BoulderCr_cms"), -->
<!--          legend = list(x = 1.1, y = 0.95)) -->

<!-- ``` -->

<!-- ## Annual hydrographs -->

<!-- ```{r hydrogs by cy, echo = F} -->

<!-- plotqensem_cy <- function(calyear) { -->
<!--   {ensem_pivot %>% -->
<!--     filter(year == calyear) %>% -->
<!--     ggplot(aes(x = date, -->
<!--                y = q_m3s, -->
<!--                color = cal_run)) + -->
<!--     geom_line() + -->
<!--     scale_color_manual(name="cal_run", values=c('obs' = 'black', -->
<!--                                             "grid_ensemble"="maroon",  -->
<!--                                             "statn_ensemble"="darkturquoise",  -->
<!--                                             "grid_all"="purple1", -->
<!--                                             "statn_all"='springgreen4',  -->
<!--                                             "all_ensemble" = "orange")) + -->
<!--     ggtitle(calyear) + -->
<!--     theme_bw() -->
<!--     } %>% -->
<!--     ggplotly() -->
<!-- } -->

<!-- name <- levels(ensem_pivot$year) -->

<!-- try <- lapply(name, plotqensem_cy) -->

<!-- htmltools::tagList(try) -->

<!-- try -->

<!-- ``` -->

<!-- ## KGE -->

<!-- ### KGE for ensembles (entire period) -->

<!-- ```{r ensemble kge, echo = F} -->

<!-- ensem_kge_all <- ensem %>% -->
<!--   ungroup() %>% -->
<!--   summarize(grid_ensemble = KGE(grid_ensemble, obs), -->
<!--             statn_ensemble = KGE(statn_ensemble, obs), -->
<!--             all_ensemble = KGE(all_ensemble, obs), -->
<!--             grid_all = KGE(grid_all, obs), -->
<!--             statn_all = KGE(statn_all, obs)) %>% -->
<!--     mutate_if(is.numeric, -->
<!--             round, -->
<!--             digits = 2) -->

<!-- kable(ensem_kge_all) %>% -->
<!--   kable_styling(full_width = F) -->

<!-- ``` -->

<!-- ### Annual KGEs for ensembles -->

<!-- ```{r annual kge ensemble, echo = F} -->

<!-- yr_kge_ensem <- ensem %>% -->
<!--   ungroup() %>% -->
<!--   mutate(year = year(date)) %>% -->
<!--   group_by(year) %>% -->
<!--   summarize(grid_ensemble = KGE(grid_ensemble, obs), -->
<!--             statn_ensemble = KGE(statn_ensemble, obs), -->
<!--             all_ensemble = KGE(all_ensemble, obs), -->
<!--             grid_all = KGE(grid_all, obs), -->
<!--             statn_all = KGE(statn_all, obs)) %>% -->
<!--     mutate_if(is.numeric, -->
<!--             round, -->
<!--             digits = 2) -->

<!-- yr_kge_table <- yr_kge_ensem %>% -->
<!--   pivot_longer(!year, names_to = 'model_run', values_to = 'kge') %>% -->
<!--   pivot_wider(names_from = 'year', values_from = 'kge') -->

<!-- yr_kge_table %>% -->
<!--   kable(.) %>% -->
<!--   kable_styling() -->

<!-- yr_kge_plot <- yr_kge_ensem %>% -->
<!--   pivot_longer(!year, names_to = 'model_run', values_to = 'kge') %>% -->
<!--   mutate(year = as.factor(year)) -->

<!-- #plot annual kge vals for ensembles -->
<!-- plot_kge_yr_ensem <- function(calyear) { -->
<!--   yr_kge_plot %>% -->
<!--     filter(year == calyear) %>% -->
<!--     ggplot(aes(x = model_run, -->
<!--                y = kge)) + -->
<!--     geom_col() + -->
<!--     ggtitle(calyear) + -->
<!--     theme_bw() + -->
<!--     theme(axis.text.x = element_text(angle = 45, hjust=1)) -->
<!-- } -->

<!-- name <- levels(yr_kge_plot$year) -->

<!-- lapply(name, plot_kge_yr_ensem) -->

<!-- ``` -->

<!-- ### Monthly KGEs for ensembles -->

<!-- ```{r monthly kge ensemble, echo = F} -->

<!-- mo_kge <- ensem %>% -->
<!--   ungroup() %>% -->
<!--   drop_na() %>%  -->
<!--   mutate(month = month(date)) %>% -->
<!--   group_by(month) %>% -->
<!--   summarize(grid_ensemble = KGE(grid_ensemble, obs), -->
<!--             statn_ensemble = KGE(statn_ensemble, obs), -->
<!--             all_ensemble = KGE(all_ensemble, obs), -->
<!--             grid_all = KGE(grid_all, obs), -->
<!--             statn_all = KGE(statn_all, obs)) %>% -->
<!--     mutate_if(is.numeric, -->
<!--             round, -->
<!--             digits = 2) -->

<!-- kable(mo_kge) %>% -->
<!--   kable_styling(full_width = F) -->

<!-- mo_pivot <- mo_kge %>% -->
<!--   pivot_longer(!month, names_to = 'cal_run', values_to = 'KGE') %>% -->
<!--   drop_na() -->

<!-- kge_plot_mo <- ggplot(mo_pivot, aes(month, KGE, color = cal_run)) + geom_point(size = 3) + -->
<!--     scale_color_manual(name="cal_run", values=c("grid_ensemble"="maroon",  -->
<!--                                             "statn_ensemble"="darkturquoise",  -->
<!--                                             "grid_all"="purple1", -->
<!--                                             "statn_all"='springgreen4',  -->
<!--                                             "all_ensemble" = "orange")) + -->
<!--   theme_bw() -->

<!-- ggplotly(kge_plot_mo) -->

<!-- ``` -->

<!-- ## RMSE -->

<!-- ### Ensemble RMSE for entire period -->

<!-- ```{r ensemble rmse, echo = F} -->

<!-- ensem_rmse_all <- ensem %>% -->
<!--   ungroup() %>% -->
<!--   summarize(grid_ensemble = rmse(grid_ensemble, obs), -->
<!--             statn_ensemble = rmse(statn_ensemble, obs), -->
<!--             all_ensemble = rmse(all_ensemble, obs), -->
<!--             grid_all = rmse(grid_all, obs), -->
<!--             statn_all = rmse(statn_all, obs)) %>% -->
<!--     mutate_if(is.numeric, -->
<!--             round, -->
<!--             digits = 4) -->

<!-- kable(ensem_rmse_all) %>% -->
<!--   kable_styling(full_width = F) -->

<!-- ``` -->

<!-- ### Annual RMSE for ensembles -->

<!-- ```{r annual rmse ensem, echo = F} -->

<!-- yr_rmse_ensem <- ensem %>% -->
<!--   ungroup() %>% -->
<!--   mutate(year = year(date)) %>% -->
<!--   group_by(year) %>% -->
<!--   summarize(grid_ensemble = rmse(grid_ensemble, obs), -->
<!--             statn_ensemble = rmse(statn_ensemble, obs), -->
<!--             all_ensemble = rmse(all_ensemble, obs), -->
<!--             grid_all = rmse(grid_all, obs), -->
<!--             statn_all = rmse(statn_all, obs)) %>% -->
<!--     mutate_if(is.numeric, -->
<!--             round, -->
<!--             digits = 4) -->

<!-- yr_rmse_table <- yr_rmse_ensem %>% -->
<!--   pivot_longer(!year, names_to = 'model_run', values_to = 'rmse') %>% -->
<!--   pivot_wider(names_from = 'year', values_from = 'rmse') -->

<!-- yr_rmse_table %>% -->
<!--   kable(.) %>% -->
<!--   kable_styling() -->

<!-- yr_rmse_plot <- yr_rmse_ensem %>% -->
<!--   pivot_longer(!year, names_to = 'model_run', values_to = 'rmse') %>% -->
<!--   mutate(year = as.factor(year)) -->

<!-- #plot annual rmse vals for ensembles -->
<!-- plot_rmse_yr_ensem <- function(calyear) { -->
<!--   yr_rmse_plot %>% -->
<!--     filter(year == calyear) %>% -->
<!--     ggplot(aes(x = model_run, -->
<!--                y = rmse)) + -->
<!--     geom_col() + -->
<!--     ggtitle(calyear) + -->
<!--     theme_bw() + -->
<!--     theme(axis.text.x = element_text(angle = 45, hjust=1)) -->
<!-- } -->

<!-- name <- levels(yr_rmse_plot$year) -->

<!-- lapply(name, plot_rmse_yr_ensem) -->

<!-- ``` -->

<!-- ### Monthly RMSEs for ensembles -->

<!-- ```{r month ensem rmse, echo = F} -->

<!-- mo_rmse <- ensem %>% -->
<!--   ungroup() %>% -->
<!--   drop_na() %>%  -->
<!--   mutate(month = month(date)) %>% -->
<!--   group_by(month) %>% -->
<!--   summarize(grid_ensemble = rmse(grid_ensemble, obs), -->
<!--             statn_ensemble = rmse(statn_ensemble, obs), -->
<!--             all_ensemble = rmse(all_ensemble, obs), -->
<!--             grid_all = rmse(grid_all, obs), -->
<!--             statn_all = rmse(statn_all, obs)) %>% -->
<!--     mutate_if(is.numeric, -->
<!--             round, -->
<!--             digits = 4) -->

<!-- kable(mo_rmse) %>% -->
<!--   kable_styling(full_width = F) -->

<!-- mo_pivot2 <- mo_rmse %>% -->
<!--   pivot_longer(!month, names_to = 'cal_run', values_to = 'RMSE') %>% -->
<!--   drop_na() -->

<!-- rmse_plot_mo <- ggplot(mo_pivot2, aes(month, RMSE, color = cal_run)) + geom_point(size = 3) + -->
<!--     scale_color_manual(name="cal_run", values=c("grid_ensemble"="maroon",  -->
<!--                                             "statn_ensemble"="darkturquoise",  -->
<!--                                             "grid_all"="purple1", -->
<!--                                             "statn_all"='springgreen4',  -->
<!--                                             "all_ensemble" = "orange")) + -->
<!--   theme_bw() -->

<!-- ggplotly(rmse_plot_mo) -->

<!-- ``` -->

<!-- ## NSE -->

<!-- ### Ensemble NSE for entire period -->

<!-- ```{r nse all, echo = F} -->

<!-- ensem_nse_all <- ensem %>% -->
<!--   ungroup() %>% -->
<!--   summarize(grid_ensemble = NSE(grid_ensemble, obs), -->
<!--             statn_ensemble = NSE(statn_ensemble, obs), -->
<!--             all_ensemble = NSE(all_ensemble, obs), -->
<!--             grid_all = NSE(grid_all, obs), -->
<!--             statn_all = NSE(statn_all, obs)) %>% -->
<!--     mutate_if(is.numeric, -->
<!--             round, -->
<!--             digits = 2) -->

<!-- kable(ensem_nse_all) %>% -->
<!--   kable_styling(full_width = F) -->

<!-- ``` -->

<!-- ### Annual NSE for ensembles -->

<!-- ```{r annual nse, echo = F} -->

<!-- yr_nse_ensem <- ensem %>% -->
<!--   ungroup() %>% -->
<!--   mutate(year = year(date)) %>% -->
<!--   group_by(year) %>% -->
<!--   summarize(grid_ensemble = NSE(grid_ensemble, obs), -->
<!--             statn_ensemble = NSE(statn_ensemble, obs), -->
<!--             all_ensemble = NSE(all_ensemble, obs), -->
<!--             grid_all = NSE(grid_all, obs), -->
<!--             statn_all = NSE(statn_all, obs)) %>% -->
<!--     mutate_if(is.numeric, -->
<!--             round, -->
<!--             digits = 4) -->

<!-- yr_nse_table <- yr_nse_ensem %>% -->
<!--   pivot_longer(!year, names_to = 'model_run', values_to = 'nse') %>% -->
<!--   pivot_wider(names_from = 'year', values_from = 'nse') -->

<!-- yr_nse_table %>% -->
<!--   kable(.) %>% -->
<!--   kable_styling() -->

<!-- yr_nse_plot <- yr_nse_ensem %>% -->
<!--   pivot_longer(!year, names_to = 'model_run', values_to = 'nse') %>% -->
<!--   mutate(year = as.factor(year)) -->

<!-- #plot annual nse vals for ensembles -->
<!-- plot_nse_yr_ensem <- function(calyear) { -->
<!--   yr_nse_plot %>% -->
<!--     filter(year == calyear) %>% -->
<!--     ggplot(aes(x = model_run, -->
<!--                y = nse)) + -->
<!--     geom_col() + -->
<!--     ggtitle(calyear) + -->
<!--     theme_bw() + -->
<!--     theme(axis.text.x = element_text(angle = 45, hjust=1)) -->
<!-- } -->

<!-- name <- levels(yr_nse_plot$year) -->

<!-- lapply(name, plot_nse_yr_ensem) -->

<!-- ``` -->

<!-- ### Monthly NSE for ensembles -->

<!-- ```{r monthly rmse, echo =F} -->

<!-- mo_nse <- ensem %>% -->
<!--   ungroup() %>% -->
<!--   drop_na() %>%  -->
<!--   mutate(month = month(date)) %>% -->
<!--   group_by(month) %>% -->
<!--   summarize(grid_ensemble = NSE(grid_ensemble, obs), -->
<!--             statn_ensemble = NSE(statn_ensemble, obs), -->
<!--             all_ensemble = NSE(all_ensemble, obs), -->
<!--             grid_all = NSE(grid_all, obs), -->
<!--             statn_all = NSE(statn_all, obs)) %>% -->
<!--     mutate_if(is.numeric, -->
<!--             round, -->
<!--             digits = 4) -->

<!-- kable(mo_nse) %>% -->
<!--   kable_styling(full_width = F) -->

<!-- mo_pivot2 <- mo_nse %>% -->
<!--   pivot_longer(!month, names_to = 'cal_run', values_to = 'nse') %>% -->
<!--   drop_na() -->

<!-- nse_plot_mo <- ggplot(mo_pivot2, aes(month, nse, color = cal_run)) + geom_point(size = 3) + -->
<!--   theme_bw() + -->
<!--   scale_color_manual(name="cal_run", values=c("grid_ensemble"="maroon",  -->
<!--                                             "statn_ensemble"="darkturquoise",  -->
<!--                                             "grid_all"="purple1", -->
<!--                                             "statn_all"='springgreen4',  -->
<!--                                             "all_ensemble" = "orange"))  -->

<!-- ggplotly(nse_plot_mo) -->

<!-- ``` -->

<!-- ## Percent bias -->

<!-- Positive values indicate model overestimation and negative values model underestimation. -->

<!-- ### Ensemble pbias for entire period -->

<!-- ```{r pbias all, echo = F} -->

<!-- ensem_pbias_all <- ensem %>% -->
<!--   ungroup() %>% -->
<!--   summarize(grid_ensemble = pbias(grid_ensemble, obs), -->
<!--             statn_ensemble = pbias(statn_ensemble, obs), -->
<!--             all_ensemble = pbias(all_ensemble, obs), -->
<!--             grid_all = pbias(grid_all, obs), -->
<!--             statn_all = pbias(statn_all, obs)) -->

<!-- kable(ensem_pbias_all) %>% -->
<!--   kable_styling(full_width = F) -->

<!-- ``` -->

<!-- ### Annual pbias for ensembles -->

<!-- ```{r annualpbias, echo = F} -->

<!-- yr_pbias_ensem <- ensem %>% -->
<!--   ungroup() %>% -->
<!--   mutate(year = year(date)) %>% -->
<!--   group_by(year) %>% -->
<!--   summarize(grid_ensemble = pbias(grid_ensemble, obs), -->
<!--             statn_ensemble = pbias(statn_ensemble, obs), -->
<!--             all_ensemble = pbias(all_ensemble, obs), -->
<!--             grid_all = pbias(grid_all, obs), -->
<!--             statn_all = pbias(statn_all, obs)) -->

<!-- yr_pbias_table <- yr_pbias_ensem %>% -->
<!--   pivot_longer(!year, names_to = 'model_run', values_to = 'pbias') %>% -->
<!--   pivot_wider(names_from = 'year', values_from = 'pbias') -->

<!-- yr_pbias_table %>% -->
<!--   kable(.) %>% -->
<!--   kable_styling() -->

<!-- yr_pbias_plot <- yr_pbias_ensem %>% -->
<!--   pivot_longer(!year, names_to = 'model_run', values_to = 'pbias') %>% -->
<!--   mutate(year = as.factor(year)) -->

<!-- #plot annual pbias vals for ensembles -->
<!-- plot_pbias_yr_ensem <- function(calyear) { -->
<!--   yr_pbias_plot %>% -->
<!--     filter(year == calyear) %>% -->
<!--     ggplot(aes(x = model_run, -->
<!--                y = pbias)) + -->
<!--     geom_col() + -->
<!--     ggtitle(calyear) + -->
<!--     theme_bw() + -->
<!--     theme(axis.text.x = element_text(angle = 45, hjust=1)) -->
<!-- } -->

<!-- name <- levels(yr_pbias_plot$year) -->

<!-- lapply(name, plot_pbias_yr_ensem) -->

<!-- ``` -->

<!-- ### Monthly pbias for ensembles -->

<!-- ```{r monthly pbias, echo =F} -->

<!-- mo_pbias <- ensem %>% -->
<!--   ungroup() %>% -->
<!--   drop_na() %>%  -->
<!--   mutate(month = month(date)) %>% -->
<!--   group_by(month) %>% -->
<!--   summarize(grid_ensemble = pbias(grid_ensemble, obs), -->
<!--             statn_ensemble = pbias(statn_ensemble, obs), -->
<!--             all_ensemble = pbias(all_ensemble, obs), -->
<!--             grid_all = pbias(grid_all, obs), -->
<!--             statn_all = pbias(statn_all, obs)) %>% -->
<!--     mutate_if(is.numeric, -->
<!--             round, -->
<!--             digits = 4) -->

<!-- kable(mo_pbias) %>% -->
<!--   kable_styling(full_width = F) -->

<!-- mo_pivot2 <- mo_pbias %>% -->
<!--   pivot_longer(!month, names_to = 'cal_run', values_to = 'pbias') %>% -->
<!--   drop_na() -->

<!-- pbias_plot_mo <- ggplot(mo_pivot2, aes(month, pbias, color = cal_run)) +  -->
<!--   geom_point(size = 3) + -->
<!--   scale_color_manual(name="cal_run", values=c("grid_ensemble"="maroon",  -->
<!--                                             "statn_ensemble"="darkturquoise",  -->
<!--                                             "grid_all"="purple1", -->
<!--                                             "statn_all"='springgreen4',  -->
<!--                                             "all_ensemble" = "orange")) + -->
<!--   theme_bw() -->

<!-- ggplotly(pbias_plot_mo) -->

<!-- ``` -->

<!-- ## Cumulative Q -->

<!-- ```{r cumq, echo = F} -->

<!-- ensem_cumq <- ensem %>% -->
<!--   mutate(month = month(date)) %>% -->
<!--   filter(month %in% c(4:9)) %>% -->
<!--   dplyr::select(-month) %>%  -->
<!--   pivot_longer(!date, names_to = 'cal_run', values_to = 'q_m3s') %>% -->
<!--   group_by(cal_run, year(date)) %>% -->
<!--   mutate(cumsum = cumsum(replace_na(q_m3s, 0))) %>% -->
<!--   rename(year = 4) %>% -->
<!--   mutate(year = as.factor(year)) %>% -->
<!--   ungroup() -->

<!-- #plot annual cumulative Q vals for ensembles -->
<!-- plot_cumulq_yr_ensem <- function(calyear) { -->
<!--   {ensem_cumq %>% -->
<!--     filter(year == calyear) %>% -->
<!--     ggplot(aes(x = date, -->
<!--                y = cumsum, -->
<!--                color = cal_run)) + -->
<!--     geom_line() + -->
<!--     scale_color_manual(name="cal_run", values=c("obs"="black", -->
<!--                                              "grid_ensemble"="maroon",  -->
<!--                                             "statn_ensemble"="darkturquoise",  -->
<!--                                             "grid_all"="purple1", -->
<!--                                             "statn_all"='springgreen4',  -->
<!--                                             "all_ensemble" = "orange")) + -->
<!--     ggtitle(calyear) + -->
<!--     theme_bw() + -->
<!--     labs(y = 'cumulative Q (m3s)')} %>% -->
<!--     ggplotly() -->
<!-- } -->

<!-- name <- levels(ensem_cumq$year) -->

<!-- cumulative_plots <- lapply(name, plot_cumulq_yr_ensem) -->

<!-- htmltools::tagList(cumulative_plots) -->

<!-- cumulative_plots -->

<!-- ``` -->

<!-- ## Percentiles -->

<!-- ```{r percentiles, echo = F} -->

<!-- quantile_calc <- function(x, probs, date) { -->
<!--   tibble(x = quantile(x, probs), probs = probs, -->
<!--          date = date[x = quantile(x, probs)]) -->
<!-- } -->

<!-- percent <- ensem_cumq %>% -->
<!--   group_by(year, cal_run) %>% -->
<!--   summarize(quantile_calc(cumsum, c(0.25, 0.5, 0.75), date)) %>% -->
<!--   mutate(date = as.Date(date)) %>% -->
<!--   mutate(probs = as.factor(probs)) -->

<!-- ### -->
<!-- quantile_cal <- function(data, prob) { -->
<!--   data %>% -->
<!--     dplyr::group_by(cal_run, year) %>% -->
<!--     mutate(quantile = paste0(prob), -->
<!--            value = quantile(cumsum, prob)) %>% -->
<!--     group_by(cal_run, year, quantile) %>%  -->
<!--     filter(cumsum >= value) %>% -->
<!--     filter(date == min(date)) -->
<!--   } -->

<!-- quantiles <- c(0.25, 0.5, 0.75) -->

<!-- quants <- quantiles %>% -->
<!--   map(~ quantile_cal(data = ensem_cumq, prob = .)) %>% -->
<!--   bind_rows() -->
<!-- #### -->

<!-- #plot percentiles -->
<!-- plot_perc_ensem <- function(perc) { -->
<!--   {percent %>% -->
<!--     filter(probs == perc) %>% -->
<!--     ggplot(aes(x = year, -->
<!--                y = x, -->
<!--                color = cal_run)) + -->
<!--     geom_point(size=3) + -->
<!--     scale_color_manual(name="cal_run", values=c("obs"="black", -->
<!--                                              "grid_ensemble"="maroon",  -->
<!--                                             "statn_ensemble"="darkturquoise",  -->
<!--                                             "grid_all"="purple1", -->
<!--                                             "statn_all"='springgreen4',  -->
<!--                                             "all_ensemble" = "orange")) + -->
<!--     ggtitle(perc) + -->
<!--     ylab('Streamflow (cms)') + -->
<!--     theme_bw()} %>% -->
<!--     ggplotly() -->
<!-- } -->

<!-- name <- levels(percent$probs) -->

<!-- perc_plots <- lapply(name, plot_perc_ensem) -->

<!-- htmltools::tagList(perc_plots) -->

<!-- perc_plots -->

<!-- ``` -->

<!-- ## Max Q prior to April 1 -->

<!-- ```{r early max q, echo = F} -->

<!-- ensem_bould <- left_join(ensem, bouldcr, by = 'date') %>% -->
<!--   pivot_longer(!c(date, year), names_to = 'source', values_to = 'q_m3s') %>% -->
<!--   mutate(month = month(date)) %>% -->
<!--   filter(month %in% 3) %>% -->
<!--   group_by(source, year) %>% -->
<!--   slice_max(q_m3s, n=1) -->

<!-- early_peakq <- ensem_bould %>% -->
<!--   mutate(doy = yday(date)) %>% -->
<!--   dplyr::select(c(doy, source, q_m3s, year)) %>% -->
<!--   drop_na() %>%  -->
<!--   pivot_wider(names_from = 'source', values_from = c('q_m3s', 'doy')) -->

<!-- marpeakq <- ggplot(early_peakq, aes(x = doy_bouldcr)) + -->
<!--   geom_point(aes(y = doy_all_ensemble, shape = "all_ensemble",  -->
<!--                  color = 'all_ensemble'), size=2.5) + -->
<!--   geom_point(aes(y = doy_grid_all, shape = 'grid_all',  -->
<!--                  color = 'grid_all'), size=2.5) + -->
<!--   geom_point(aes(y = doy_grid_ensemble, shape = 'grid_ensemble',  -->
<!--                  color = 'grid_ensemble'), size=2.5) + -->
<!--   geom_point(aes(y = doy_statn_all, shape = 'statn_all',  -->
<!--                  color = 'statn_all'), size=2.5) + -->
<!--   geom_point(aes(y = doy_statn_ensemble, shape = 'statn_ensemble',  -->
<!--                  color = 'statn_ensemble'), size=2.5) + -->
<!--   geom_abline(intercept = 0, slope = 1, size=1, color='black') + -->
<!--   labs(x = "Boulder Creek DOY for March Peak Q",  -->
<!--        y = 'DOY for March Peak Q') + -->
<!--   theme_bw() + -->
<!--   scale_shape_manual(name="source", values=c("all_ensemble"=15,  -->
<!--                                             "grid_all"=16,  -->
<!--                                             "grid_ensemble"=17, -->
<!--                                             "statn_all"=18,  -->
<!--                                             "statn_ensemble" = 8)) + -->
<!--     scale_color_manual(name="source", values=c("all_ensemble"='orange',  -->
<!--                                             "grid_all"='purple1',  -->
<!--                                             "grid_ensemble"='maroon', -->
<!--                                             "statn_all"='springgreen4',  -->
<!--                                             "statn_ensemble" = 'darkturquoise')) + -->
<!--   ggtitle('DOY of peak Q in March') -->

<!-- ggplotly(marpeakq) -->

<!-- # ggplot(early_peakq, aes(doy_bouldcr, doy_grid_all)) + -->
<!-- #   geom_point(size=2.5) + -->
<!-- #   geom_abline(intercept = 0, slope = 1, size=1, color='red') + -->
<!-- #   theme_bw() + -->
<!-- #   ggtitle('DOY of peak Q prior to April 1st - Grid All') -->
<!-- #  -->
<!-- #  -->
<!-- # ggplot(early_peakq, aes(doy_bouldcr, doy_grid_ensemble)) + -->
<!-- #   geom_point(size=2.5) + -->
<!-- #   geom_abline(intercept = 0, slope = 1, size=1, color='red') + -->
<!-- #   theme_bw() + -->
<!-- #   ggtitle('DOY of peak Q prior to April 1st - Grid Ensemble') -->
<!-- #  -->
<!-- #  -->
<!-- # ggplot(early_peakq, aes(doy_bouldcr, doy_statn_all)) + -->
<!-- #   geom_point(size=2.5) + -->
<!-- #   geom_abline(intercept = 0, slope = 1, size=1, color='red') + -->
<!-- #   theme_bw() + -->
<!-- #   ggtitle('DOY of peak Q prior to April 1st - Station All') -->
<!-- #  -->
<!-- #  -->
<!-- # ggplot(early_peakq, aes(doy_bouldcr, doy_statn_ensemble)) + -->
<!-- #   geom_point(size=2.5) + -->
<!-- #   geom_abline(intercept = 0, slope = 1, size=1, color='red') + -->
<!-- #   theme_bw() + -->
<!-- #   ggtitle('DOY of peak Q prior to April 1st - Station Ensemble') -->

<!-- early_peakq_table <- ensem_bould %>% -->
<!--   mutate(doy = yday(date)) %>% -->
<!--   dplyr::arrange(date) -->

<!-- kable(early_peakq_table) %>% -->
<!--   kable_styling(full_width = F) %>%  -->
<!--   scroll_box(width = "100%", height = "500px") -->

<!-- bouldcr3 <- bouldcr %>% -->
<!--   mutate(month = month(date)) %>% -->
<!--   filter(month == 3, year == 2011) -->

<!-- test1 <- ensem_pivot %>% -->
<!--   mutate(month = month(date)) %>% -->
<!--   filter(year == 2011, -->
<!--          month == 3) %>%  -->
<!--   ggplot(aes(date, q_m3s, color = cal_run)) + -->
<!--   geom_line() + -->
<!--   scale_color_manual(name="cal_run", values=c('obs'='black', -->
<!--                                             "grid_ensemble"="maroon",  -->
<!--                                             "statn_ensemble"="darkturquoise",  -->
<!--                                             "grid_all"="purple1", -->
<!--                                             "statn_all"='springgreen4',  -->
<!--                                             "all_ensemble" = "orange")) + -->
<!--   geom_line(data = bouldcr3, aes(date, bouldcr/10), color = 'darkgrey') + -->
<!--   scale_y_continuous(name = 'Q_m3s', -->
<!--                     sec.axis = sec_axis(~.*10, name='BoulderCr_cms')) + -->
<!--   theme_bw() + -->
<!--   ggtitle('March 2011') -->

<!-- ggplotly(test1) %>% -->
<!--   add_lines(data=bouldcr, x=~date, y=~bouldcr, colors=NULL, yaxis="y2",  -->
<!--               inherit=FALSE, showlegend = FALSE) %>% -->
<!--   layout(yaxis2 = list(overlaying = "y", side = "right", -->
<!--                        color = 'darkgray', -->
<!--                        title = "BoulderCr_cms"), -->
<!--          legend = list(x = 1.1, y = 0.95)) -->

<!-- ################################################ -->

<!-- bouldcr3_2 <- bouldcr %>% -->
<!--   mutate(month = month(date)) %>% -->
<!--   filter(month == 3, year == 2019) -->

<!-- test2 <- ensem_pivot %>% -->
<!--   mutate(month = month(date)) %>% -->
<!--   filter(year == 2019, -->
<!--          month == 3) %>%  -->
<!--   ggplot(aes(date, q_m3s, color = cal_run)) + -->
<!--   geom_line() + -->
<!--   scale_color_manual(name="cal_run", values=c('obs'='black', -->
<!--                                             "grid_ensemble"="maroon",  -->
<!--                                             "statn_ensemble"="darkturquoise",  -->
<!--                                             "grid_all"="purple1", -->
<!--                                             "statn_all"='springgreen4',  -->
<!--                                             "all_ensemble" = "orange")) + -->
<!--   geom_line(data = bouldcr3_2, aes(date, bouldcr/10), color = 'darkgrey') + -->
<!--   scale_y_continuous(name = 'Q_m3s', -->
<!--                     sec.axis = sec_axis(~.*10, name='BoulderCr_cms')) + -->
<!--   theme_bw() + -->
<!--   ggtitle('March 2019') -->

<!-- ggplotly(test2) %>% -->
<!--   add_lines(data=bouldcr, x=~date, y=~bouldcr, colors=NULL, yaxis="y2",  -->
<!--               inherit=FALSE, showlegend = FALSE) %>% -->
<!--   layout(yaxis2 = list(overlaying = "y", side = "right", -->
<!--                        color = 'darkgray', -->
<!--                        title = "BoulderCr_cms"), -->
<!--          legend = list(x = 1.1, y = 0.95)) -->

<!-- ``` -->

<!-- # Catchment results -->

<!-- ## Precip -->

<!-- ```{r catch precip, echo = F} -->
<!-- setwd("/Users/megansears/Documents/Repos/fourmile/catchment_output") -->

<!-- statn <- read_csv('statnall.csv') -->
<!-- grid <- read_csv('gridall.csv') -->

<!-- grid <- grid %>% mutate(site = 'grid') -->
<!-- statn <- statn %>% mutate(site = 'statn') -->

<!-- catchment <- bind_rows(grid, statn) %>% -->
<!--   mutate(year = as.factor(year(time))) %>% -->
<!--   group_by(year, site) %>% -->
<!--   mutate(cumulative_p = cumsum(precip)) -->

<!-- #plot cumulative precip by year -->
<!-- plot_cumprecip <- function(calyear) { -->
<!--   {catchment %>% -->
<!--     filter(year == calyear) %>% -->
<!--     ggplot(aes(x = time, -->
<!--                y = cumulative_p, color = site)) + -->
<!--     geom_line(size=1) + -->
<!--     ggtitle(calyear) + -->
<!--     ylab('Cumulative precip (mm)') + -->
<!--     theme_bw() + -->
<!--     theme(axis.text.x = element_text(angle = 45, hjust=1))} %>% -->
<!--     ggplotly() -->
<!-- } -->

<!-- name <- levels(catchment$year) -->

<!-- precip_plots <- lapply(name, plot_cumprecip) -->

<!-- htmltools::tagList(precip_plots) -->

<!-- precip_plots -->

<!-- ## total P -->
<!-- max_cumulativep <- catchment %>% -->
<!--   group_by(year, site) %>% -->
<!--   summarize(total_cumulativep = max(cumulative_p)) -->

<!-- ggplot(max_cumulativep, aes(x=year, y=total_cumulativep, color=site)) +  -->
<!--   geom_point(size=3) + -->
<!--   ggtitle('Total cumulative precip (mm) by year') -->

<!-- ``` -->

<!-- ## Tmean -->

<!-- ```{r tmean catch, echo = F} -->
<!-- ## tmean  -->
<!-- tmean <- catchment %>% -->
<!--   group_by(year, site) %>% -->
<!--   summarize(tmean = mean(tmean)) %>% -->
<!--   ggplot(aes(x = year, y=tmean, color = site)) + -->
<!--   geom_point(size=3) + -->
<!--   ggtitle('Average temp by year') -->

<!-- tmean -->

<!-- ``` -->

<!-- ## RD and RG -->

<!-- ```{r rd and rg, echo = F, fig.width = 14, fig.asp = 1, out.width = "100%"} -->

<!-- gw_grid <- read_csv(here('catchment_output/gridall_outlet.csv')) %>% -->
<!--   dplyr::select(time, catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w) %>% -->
<!--   mutate(source = 'grid') -->

<!-- gw_statn <- read_csv(here('catchment_output/statnall_outlet.csv')) %>% -->
<!--   dplyr::select(time, catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w) %>% -->
<!--   mutate(source = 'statn') -->

<!-- gw <- bind_rows(gw_grid, gw_statn) %>% -->
<!--   mutate(year = year(time)) %>% -->
<!--   rename(date = time) -->

<!-- ggplot(gw, aes(x=date, color = source)) + -->
<!--   geom_line(aes(y=catchmentRD1_w), size =1) + -->
<!--   facet_wrap(~year, scales = 'free', ncol = 2) + -->
<!--   scale_x_date(labels = date_format("%b")) + -->
<!--   ggtitle('RD1') + -->
<!--   theme(text = element_text(size = 20))    -->

<!-- ggplot(gw, aes(x=date, color = source)) + -->
<!--   geom_line(aes(y=catchmentRD2_w), size =1) + -->
<!--   facet_wrap(~year, scales = 'free', ncol = 2) + -->
<!--   scale_x_date(labels = date_format("%b")) + -->
<!--   ggtitle('RD2') + -->
<!--   theme(text = element_text(size = 20))    -->

<!-- ggplot(gw, aes(x=date, color = source)) + -->
<!--   geom_line(aes(y=catchmentRG1_w), size =1) + -->
<!--   facet_wrap(~year, scales = 'free', ncol = 2) + -->
<!--   scale_x_date(labels = date_format("%b")) + -->
<!--   ggtitle('RG1') + -->
<!--   theme(text = element_text(size = 20))    -->

<!-- ggplot(gw, aes(x=date, color = source)) + -->
<!--   geom_line(aes(y=catchmentRG2_w), size =1) + -->
<!--   facet_wrap(~year, scales = 'free', ncol=2) + -->
<!--   scale_x_date(labels = date_format("%b")) + -->
<!--   ggtitle('RG2') + -->
<!--   theme(text = element_text(size = 20))    -->

<!-- gw <- gw %>% -->
<!--   group_by(year, source) %>% -->
<!--   mutate(RD1cumsum = cumsum(catchmentRD1_w), -->
<!--          RD2cumsum = cumsum(catchmentRD2_w), -->
<!--          RG1cumsum = cumsum(catchmentRG1_w), -->
<!--          RG2cumsum = cumsum(catchmentRG2_w)) -->

<!-- ggplot(gw, aes(x=date, color = source)) + -->
<!--   geom_line(aes(y=RD1cumsum), size =1) + -->
<!--   facet_wrap(~year, scales = 'free', ncol=2) + -->
<!--   scale_x_date(labels = date_format("%b")) + -->
<!--   ggtitle('Cumulative RD1') + -->
<!--   theme(text = element_text(size = 20))    -->

<!-- ggplot(gw, aes(x=date, color = source)) + -->
<!--   geom_line(aes(y=RD2cumsum), size = 1) + -->
<!--   facet_wrap(~year, scales = 'free', ncol=2) + -->
<!--   scale_x_date(labels = date_format("%b")) + -->
<!--   ggtitle('Cumulative RD2') + -->
<!--   theme(text = element_text(size = 20))    -->

<!-- ggplot(gw, aes(x=date, color = source)) + -->
<!--   geom_line(aes(y=RG1cumsum), size  = 1) + -->
<!--   facet_wrap(~year, scales = 'free', ncol = 2) + -->
<!--   scale_x_date(labels = date_format("%b")) + -->
<!--   ggtitle('Cumulative RG1') + -->
<!--   theme(text = element_text(size = 20))    -->

<!-- ggplot(gw, aes(x=date, color = source)) + -->
<!--   geom_line(aes(y=RG2cumsum), size =1) + -->
<!--   facet_wrap(~year, scales = 'free', ncol = 2) + -->
<!--   scale_x_date(labels = date_format("%b")) + -->
<!--   ggtitle('Cumulative RG2') + -->
<!--   theme(text = element_text(size = 20))    -->

<!-- ``` -->

<!-- ```{r rd and rg sums, echo = F, fig.width = 22, fig.asp = 1.5, out.width = "100%"} -->

<!-- ################## -->
<!-- # all 4 with facets -->

<!-- ggplot(gw, aes(x=date)) + -->
<!--   geom_line(aes(y=RG2cumsum, color = 'cumulative RG2'), size =1) + -->
<!--   geom_line(aes(y=RG1cumsum, color = 'cumulative RG1'), size =1) + -->
<!--   geom_line(aes(y=RD1cumsum, color = 'cumulative RD1'), size =1) + -->
<!--   geom_line(aes(y=RD2cumsum, color = 'cumulative RD2'), size =1) + -->
<!--   scale_x_date(labels = date_format("%b")) + -->
<!--   facet_wrap(~year + source, scales = 'free_x', ncol=2) + -->
<!--   ggtitle('Cumulative RD and RG') + -->
<!--   theme(text = element_text(size = 24))    -->

<!-- ``` -->

<!-- ```{r gw boxplot, echo = F} -->

<!-- gw_maxcumsum <- gw %>% -->
<!--   group_by(source, year) %>% -->
<!--   summarize(yr_max_RD1 = max(RD1cumsum), -->
<!--             yr_max_RD2 = max(RD2cumsum), -->
<!--             yr_max_RG1 = max(RG1cumsum), -->
<!--             yr_max_RG2 = max(RG2cumsum)) %>% -->
<!--   mutate(year = as.factor(year)) %>% -->
<!--   pivot_longer(!c(year, source), names_to = 'flow_type', values_to = 'flow_cms') -->

<!-- ggplot(gw_maxcumsum, aes(x = flow_type, y = flow_cms, fill = source)) + -->
<!--   geom_boxplot(position = position_dodge(1)) +  -->
<!--   geom_point(position=position_jitterdodge(),alpha=0.3) + -->
<!--   ggtitle('Max annual cumulative sums') -->

<!-- ggplot(gw_maxcumsum, aes(x = flow_type, y = flow_cms, fill = source)) + -->
<!--   geom_boxplot(position = position_dodge(1)) + -->
<!--   geom_point(position=position_jitterdodge(),alpha=0.3) + -->
<!--   #geom_point(aes(color = source)) + -->
<!--   facet_wrap(~flow_type, scales = 'free') + -->
<!--   ggtitle('Max annual cumulative sums') -->

<!-- ``` -->

<!-- ### RD and RG by season -->

<!-- ```{r flow season, echo = F, fig.width = 12, fig.asp = 0.75, out.width = "100%"} -->

<!-- #group by season and get max sums by season -->
<!-- flow_season <- gw %>% -->
<!--   dplyr::select(RD1cumsum, RD2cumsum, RG1cumsum, RG2cumsum, date, year, source) %>% -->
<!--   mutate(month = month(date)) %>% -->
<!--   mutate(season = case_when(month %in% c(3,4,5,6) ~ 'snowmelt', -->
<!--                             month %in% c(7,8,9,10) ~ 'monsoon', -->
<!--                             month %in% c(11,12,1,2) ~ 'baseflow')) %>% -->
<!--   group_by(source, year, season) %>% -->
<!--   summarize(yr_season_RD1 = max(RD1cumsum), -->
<!--             yr_season_RD2 = max(RD2cumsum), -->
<!--             yr_season_RG1 = max(RG1cumsum), -->
<!--             yr_season_RG2 = max(RG2cumsum)) %>% -->
<!--             pivot_longer(!c(year, source, season), names_to = 'flow_type', values_to = 'flow_cms') -->

<!-- flow_season %>% -->
<!--   ggplot(aes(x = flow_type, y = flow_cms, fill = source)) + -->
<!--   geom_boxplot(position = position_dodge(1)) + -->
<!--   geom_point(position=position_jitterdodge(),alpha=0.3) + -->
<!--   #geom_point(aes(color = source)) + -->
<!--   facet_wrap(~season, scales = 'free') + -->
<!--   ggtitle('Max annual season cumulative sums') + -->
<!--   theme_bw() + -->
<!--   theme(axis.text.x = element_text(angle = 45, hjust = 1)) + -->
<!--   theme(text = element_text(size = 20))  -->

<!-- flow_season %>% -->
<!--   ggplot(aes(x = flow_type, y = flow_cms, fill = source)) + -->
<!--   geom_boxplot(position = position_dodge(1)) + -->
<!--   geom_point(position=position_jitterdodge(),alpha=0.3) + -->
<!--   #geom_point(aes(color = source)) + -->
<!--   facet_wrap(~season + flow_type, scales = 'free') + -->
<!--   ggtitle('Max annual season cumulative sums') + -->
<!--   theme_bw() + -->
<!--   theme(text = element_text(size = 20)) -->

<!-- ``` -->

<!-- # HRU results -->

<!-- ## HRU Map -->

<!-- ```{r map, echo = F} -->

<!-- locations <- read_csv(here('data/GIS', 'fourmile_sensors.csv')) -->

<!-- hrus <- st_read(here('data/GIS', 'hrus_final.shp')) -->

<!-- locations <- locations %>% -->
<!--   st_as_sf(., coords=c('y','x'), crs = 4326) -->

<!-- mapviewOptions(basemaps = c("Esri.WorldShadedRelief", "OpenStreetMap.DE"), -->
<!--                layers.control.pos = "topright") -->

<!-- mapview(locations, zcol = 'type') + mapview(hrus) -->

<!-- ``` -->

<!-- ## Niwot and HRU7 -->

<!-- ### SWE and precip -->

<!-- ```{r niwot, echo = F, fig.width = 14, fig.asp = 1, out.width = "100%"} -->
<!-- library(snotelr) -->

<!-- niwot_snotel <- snotel_download(site_id = 663, internal = T) -->

<!-- niwot_snotel <- niwot_snotel %>% -->
<!--   dplyr::select(date, snow_water_equivalent, precipitation) %>% -->
<!--   mutate(date = as.Date(date)) %>% -->
<!--   rename(swe_mm_snotel = snow_water_equivalent, -->
<!--          precip_mm_snotel = precipitation) %>% -->
<!--   #mutate(swe_mm_snotel = swe_mm_snotel*25.4, -->
<!--          #precip_mm_snotel = precip_mm_snotel*25.4) %>% -->
<!--   filter(date > '2010-12-31' & date < '2020-10-01') -->

<!-- hru7_grid <- read_csv(here('HRU_output/HRU_7_grid.csv')) %>% -->
<!--   dplyr::select(date, precip_mm, swe_mm) %>% -->
<!--   rename(precip_mm_hrugrid = precip_mm, -->
<!--          swe_mm_hrugrid = swe_mm) -->

<!-- hru7_statn <- read_csv(here('HRU_output/HRU_7_statn.csv')) %>% -->
<!--   dplyr::select(date, precip_mm, swe_mm) %>% -->
<!--   rename(precip_mm_hrustatn = precip_mm, -->
<!--          swe_mm_hrustatn = swe_mm) -->

<!-- niwot <- niwot_snotel %>% -->
<!--   left_join(hru7_grid, by = 'date') %>% -->
<!--   left_join(hru7_statn, by = 'date') -->

<!-- # look at swe -->
<!-- niwot_swe <- niwot %>% -->
<!--   dplyr::select(date, swe_mm_snotel, swe_mm_hrugrid, swe_mm_hrustatn) -->

<!-- kable(niwot_swe) %>% -->
<!--   kable_styling(full_width = F) %>%  -->
<!--   scroll_box(width = "100%", height = "500px") -->

<!-- # cumulative swe -->
<!-- niwot_swe2 <- niwot_swe %>% -->
<!--   mutate(year = year(date)) %>% -->
<!--   pivot_longer(!c(date,year), names_to = 'source', values_to = 'swe_mm') %>% -->
<!--   group_by(year, source) %>% -->
<!--   mutate(swe_cumsum_mm = cumsum(swe_mm)) -->

<!-- cum_swe_niwot <- ggplot(niwot_swe2, aes(date, swe_cumsum_mm, color = source)) + -->
<!--   geom_line(size =1) + -->
<!--   scale_x_date(labels = date_format("%b")) + -->
<!--   facet_wrap(~year, scales = 'free', ncol=2) + -->
<!--   theme(text = element_text(size = 20))   -->

<!-- cum_swe_niwot -->

<!-- #look at precip -->
<!-- niwot_p <- niwot %>% -->
<!--   dplyr::select(date, precip_mm_snotel, precip_mm_hrugrid, precip_mm_hrustatn) -->

<!-- kable(niwot_p) %>% -->
<!--   kable_styling(full_width = F) %>%  -->
<!--   scroll_box(width = "100%", height = "500px") -->

<!-- # cumulative precip -->
<!-- niwot_p2 <- niwot_p %>% -->
<!--   mutate(year = year(date)) %>% -->
<!--   pivot_longer(!c(date,year), names_to = 'source', values_to = 'precip_mm') %>% -->
<!--   group_by(year, source) %>% -->
<!--   mutate(p_cumsum_mm = cumsum(precip_mm)) -->

<!-- cum_precip_niwot <- ggplot(niwot_p2, aes(date, p_cumsum_mm, color = source)) + -->
<!--   geom_line(size=1) + -->
<!--   scale_x_date(labels = date_format("%b")) + -->
<!--   facet_wrap(~year, scales = 'free', ncol=2) + -->
<!--   theme(text = element_text(size = 20))   -->

<!-- cum_precip_niwot -->

<!-- ``` -->

<!-- ### ET -->

<!-- ```{r ET, echo = F} -->

<!-- niwot_et <- read_csv(here('HRU_output/Niwot_daily_et.csv')) %>% -->
<!--   filter(year > 2010) %>% -->
<!--   mutate(date = make_date(year = year, month = month, day = day)) %>% -->
<!--   dplyr::select(date, et) %>% -->
<!--   rename(et_niwot = et) -->

<!-- hru7_grid <- read_csv(here('HRU_output/HRU_7_grid.csv')) %>% -->
<!--   dplyr::select(date, AET_mm) %>% -->
<!--   rename(et_hru7grid = AET_mm) -->

<!-- hru7_statn <- read_csv(here('HRU_output/HRU_7_statn.csv')) %>% -->
<!--   dplyr::select(date, AET_mm) %>% -->
<!--   rename(et_hru7statn = AET_mm) -->

<!-- niwot_et_compare <- niwot_et %>% -->
<!--   left_join(hru7_grid, by = 'date') %>% -->
<!--   left_join(hru7_statn, by = 'date') %>% -->
<!--   mutate(year = year(date)) %>% -->
<!--   filter(year < 2021) %>%  -->
<!--   pivot_longer(!c(date, year), names_to= 'source', values_to = 'et_mm') %>% -->
<!--   mutate(year = as.factor(year)) -->

<!-- #plot ET by year -->
<!-- plot_ET <- function(calyear) { -->
<!--   {niwot_et_compare %>% -->
<!--     filter(year == calyear) %>% -->
<!--     ggplot(aes(x = date, -->
<!--                y = et_mm, color = source)) + -->
<!--     geom_line(size=1) + -->
<!--     ggtitle(calyear) + -->
<!--     ylab('ET (mm/day)') + -->
<!--     theme_bw() + -->
<!--     theme(axis.text.x = element_text(angle = 45, hjust=1))} %>% -->
<!--     ggplotly() -->
<!-- } -->

<!-- name <- levels(niwot_et_compare$year) -->

<!-- ET_plots <- lapply(name, plot_ET) -->

<!-- htmltools::tagList(ET_plots) -->

<!-- ET_plots -->

<!-- # 1:1 scatter plots for Niwot vs grid and Niwot vs station -->
<!-- niwot_et_scatter <- niwot_et_compare %>% -->
<!--   filter(et_mm > 0) -->

<!-- # Niwot vs grid -->
<!-- et_grid_obs <- niwot_et_scatter %>% -->
<!--   filter(source == c('et_niwot','et_hru7grid')) %>% -->
<!--   pivot_wider(names_from = 'source', values_from = 'et_mm') -->

<!-- #scatter of grid vs niwot -->
<!-- et_scatter_grid_obs <- ggplot(et_grid_obs, aes(x = et_niwot, y = et_hru7grid)) + -->
<!--   geom_point() + -->
<!--   geom_abline(intercept = 0, slope = 1, size=1, color='red') +  -->
<!--   ggtitle('Niwot ET vs. HRU7 grid ET') -->

<!-- et_scatter_grid_obs -->

<!-- # Niwot vs statn inputs -->
<!-- et_statn_obs <- niwot_et_scatter %>% -->
<!--   filter(source == c('et_niwot','et_hru7statn')) %>% -->
<!--   pivot_wider(names_from = 'source', values_from = 'et_mm') -->

<!-- #scatter of grid vs niwot -->
<!-- et_scatter_statn_obs <- ggplot(et_statn_obs, aes(x = et_niwot, y = et_hru7statn)) + -->
<!--   geom_point() + -->
<!--   geom_abline(intercept = 0, slope = 1, size=1, color='red') +  -->
<!--   ggtitle('Niwot ET vs. HRU7 station ET') -->

<!-- et_scatter_statn_obs -->

<!-- ``` -->

<!-- ## Tmean for HRUs 7, 9, 22, 36 -->

<!-- ```{r hru7 temp, echo = F, fig.width = 14, fig.asp = 1, out.width = "100%"} -->

<!-- tmean7_grid <- read_csv(here('HRU_output/HRU_7_grid.csv')) %>% -->
<!--   dplyr::select(date, tmean) %>% -->
<!--   rename(t7_grid = tmean) -->

<!-- tmean7_statn <- read_csv(here('HRU_output/HRU_7_statn.csv')) %>% -->
<!--   dplyr::select(date, tmean) %>% -->
<!--   rename(t7_statn = tmean) -->

<!-- tmean9_grid <- read_csv(here('HRU_output/HRU_9_grid.csv')) %>% -->
<!--   dplyr::select(date, tmean) %>% -->
<!--   rename(t9_grid = tmean) -->

<!-- tmean9_statn <- read_csv(here('HRU_output/HRU_9_statn.csv')) %>% -->
<!--   dplyr::select(date, tmean) %>% -->
<!--   rename(t9_statn = tmean) -->

<!-- tmean22_grid <- read_csv(here('HRU_output/HRU_22_grid.csv')) %>% -->
<!--   dplyr::select(date, tmean) %>% -->
<!--   rename(t22_grid = tmean) -->

<!-- tmean22_statn <- read_csv(here('HRU_output/HRU_22_statn.csv')) %>% -->
<!--   dplyr::select(date, tmean) %>% -->
<!--   rename(t22_statn = tmean) -->

<!-- tmean36_grid <- read_csv(here('HRU_output/HRU_36_grid.csv')) %>% -->
<!--   dplyr::select(date, tmean) %>% -->
<!--   rename(t36_grid = tmean) -->

<!-- tmean36_statn <- read_csv(here('HRU_output/HRU_36_statn.csv')) %>% -->
<!--   dplyr::select(date, tmean) %>% -->
<!--   rename(t36_statn = tmean) -->

<!-- tmean_hrus <- list(tmean7_grid, tmean7_statn, tmean9_grid,  -->
<!--      tmean9_statn, tmean22_grid, tmean22_statn, -->
<!--      tmean36_grid, tmean36_statn) -->

<!-- t_hrus <- tmean_hrus %>% reduce(left_join, by='date') -->

<!-- t_hrus <- t_hrus %>% -->
<!--   mutate(year = year(date)) %>% -->
<!--   mutate(t7_diff = t7_statn - t7_grid, -->
<!--          t9_diff = t9_statn - t9_grid, -->
<!--          t22_diff = t22_statn - t22_grid, -->
<!--          t36_diff = t36_statn - t36_grid) %>% -->
<!--   group_by(year) %>% -->
<!--   mutate(t7_cumdiff = cumsum(t7_diff), -->
<!--          t9_cumdiff = cumsum(t9_diff), -->
<!--          t22_cumdiff = cumsum(t22_diff), -->
<!--          t36_cumdiff = cumsum(t36_diff)) -->

<!-- tmean_cumdiff_plot <- ggplot(t_hrus, aes(x = date)) + -->
<!--   geom_line(aes(y = t7_cumdiff, color = 'HRU7'), size =1) +  -->
<!--   geom_line(aes(y = t9_cumdiff, color = 'HRU9'), size =1) +  -->
<!--   geom_line(aes(y = t22_cumdiff, color = 'HRU22'), size =1) +  -->
<!--   geom_line(aes(y = t36_cumdiff, color = 'HRU36'), size =1) +  -->
<!--   facet_wrap(~year, scales = 'free',ncol=2) + -->
<!--   scale_x_date(labels = date_format("%b")) + -->
<!--   labs(y = 'Tmean cumulative difference (deg C)') + -->
<!--   ggtitle('Tmean station and grid cumulative difference (Station - Grid)') + -->
<!--   theme(text = element_text(size = 20))   -->

<!-- tmean_cumdiff_plot -->

<!-- ``` -->

<!-- ## Tmean difference -->

<!-- 2011-2020 average of daily station-grid Tmean  -->

<!-- ```{r cumulative tmean for HRUs, echo = F} -->
<!-- #grid first -->
<!-- setwd(here("HRU_output/grid")) -->

<!-- read_ages_grid <- function(dataframe){ -->
<!--   read_csv(dataframe, skip = 3) %>% -->
<!--   slice(3:n()) %>% -->
<!--   dplyr::select(-starts_with('@'), -->
<!--                 -1) %>% -->
<!--   mutate(time = ymd(time)) %>% -->
<!--   mutate_if(is.character, as.numeric) %>% -->
<!--   mutate(source = 'grid') -->

<!-- } -->

<!-- #pull in all filenames with HRU in the name -->
<!-- filenames <- list.files(".", pattern="HRU", full.names=F) -->

<!-- #read all the csvs using read_ages function -->
<!-- dataframes <- lapply(filenames, read_ages_grid)  -->

<!-- #name all the csvs based on first 6 characters -->
<!-- names(dataframes) <- substr(filenames, 1, 6) -->

<!-- #bind all and make 1 df -->
<!-- hru_grids <- dataframes %>% -->
<!--   bind_rows()  -->

<!-- #statn next -->
<!-- setwd(here("HRU_output/statn")) -->

<!-- read_ages_statn <- function(dataframe){ -->
<!--   read_csv(dataframe, skip = 3) %>% -->
<!--   slice(3:n()) %>% -->
<!--   dplyr::select(-starts_with('@'), -->
<!--                 -1) %>% -->
<!--   mutate(time = ymd(time)) %>% -->
<!--   mutate_if(is.character, as.numeric) %>% -->
<!--   mutate(source = 'statn') -->

<!-- } -->

<!-- #pull in all filenames with HRU in the name -->
<!-- filenames <- list.files(".", pattern="HRU", full.names=F) -->

<!-- #read all the csvs using read_ages function -->
<!-- dataframes <- lapply(filenames, read_ages_statn)  -->

<!-- #name all the csvs based on first 6 characters -->
<!-- names(dataframes) <- substr(filenames, 1, 6) -->

<!-- #bind all and make 1 df -->
<!-- hru_statn <- dataframes %>% -->
<!--   bind_rows()  -->

<!-- #get rid of a bunch of data -->
<!-- hru_grid_tmean <- hru_grids %>% -->
<!--   dplyr::select(c(time, ID, tmean)) %>% -->
<!--   rename(tmean_grid = tmean)  %>% -->
<!--   group_by(ID) %>% -->
<!--   summarize(tmean_all_grid = mean(tmean_grid)) -->

<!-- hru_statn_tmean <- hru_statn %>% -->
<!--   dplyr::select(c(time, ID, tmean)) %>% -->
<!--   rename(tmean_statn = tmean) %>% -->
<!--   group_by(ID) %>% -->
<!--   summarize(tmean_all_statn = mean(tmean_statn)) -->

<!-- tmean_hrus <- left_join(hru_grid_tmean, hru_statn_tmean, by = c('ID')) %>% -->
<!--   mutate(diff = tmean_all_statn - tmean_all_grid) %>% -->
<!--   rename(value = ID) -->

<!-- hrus_map_tmean <- left_join(hrus, tmean_hrus, by = 'value') -->

<!-- tmap_mode('view') -->

<!-- locations_t <- locations %>%  -->
<!--   dplyr::filter(name %in% c('Gordon_South', 'Gordon_North', -->
<!--                         'Betasso', 'Niwot_Snotel', -->
<!--                         'University Camp SNTL')) -->

<!-- tm_shape(hrus_map_tmean) + -->
<!--   tm_polygons('diff', id = 'value', -->
<!--               breaks = c(-6,-4,-2,0,2,4,6)) + -->
<!-- tm_shape(locations_t) + -->
<!--   tm_symbols(col='blue', size=4) -->

<!-- ``` -->

<!-- ## Tmax difference -->

<!-- ```{r tmax, echo = F} -->

<!-- tmax_grid <- read_csv(here('HRU_output/reg_tmaxAll_prism.csv'))%>%  -->
<!--   pivot_longer(cols = `3`:`19`, -->
<!--                names_to = 'value',  -->
<!--                values_to = 'tmax_grid') %>% -->
<!--   mutate(time = dmy(time)) %>% -->
<!--   group_by(value) %>% -->
<!--   summarize(Tmax_mean_grid = mean(tmax_grid)) -->

<!-- tmax_statn <- read_csv(here('HRU_output/reg_tmaxAll.csv')) %>%  -->
<!--   pivot_longer(cols = `3`:`19`, -->
<!--                names_to = 'value',  -->
<!--                values_to = 'tmax_statn') %>% -->
<!--   mutate(time = dmy(time)) %>% -->
<!--   group_by(value) %>% -->
<!--   summarize(Tmax_mean_statn = mean(tmax_statn)) -->

<!-- tmax_hrus <- left_join(tmax_grid, tmax_statn, by = c('value')) %>% -->
<!--   mutate(diff = Tmax_mean_statn - Tmax_mean_grid, -->
<!--          value = as.numeric(value)) -->

<!-- hrus_map_tmax <- left_join(hrus, tmax_hrus, by = 'value') -->

<!-- tmap_mode('view') -->

<!-- tm_shape(hrus_map_tmax) + -->
<!--   tm_polygons('diff', id = 'value', -->
<!--               breaks = c(-6,-4,-2,0,2,4,6)) + -->
<!-- tm_shape(locations_t) + -->
<!--   tm_symbols(col='blue', size=4) -->

<!-- ``` -->

<!-- ## Tmax monthly average -->

<!-- ```{r tmax month, echo = F} -->

<!-- tmax_grid_mo <- read_csv(here('HRU_output/reg_tmaxAll_prism.csv')) %>%  -->
<!--   pivot_longer(cols = `3`:`19`, -->
<!--                names_to = 'value',  -->
<!--                values_to = 'tmax_grid') %>% -->
<!--   mutate(time = dmy(time), -->
<!--          month = month(time)) %>% -->
<!--   filter(month %in% c(3:6)) %>% -->
<!--   group_by(value, month) %>% -->
<!--   summarize(avg_tmax_grid = mean(tmax_grid)) -->

<!-- tmax_statn_mo <- read_csv(here('HRU_output/reg_tmaxAll.csv')) %>%  -->
<!--   pivot_longer(cols = `3`:`19`, -->
<!--                names_to = 'value',  -->
<!--                values_to = 'tmax_statn') %>% -->
<!--   mutate(time = dmy(time), -->
<!--          month = month(time)) %>% -->
<!--   filter(month %in% c(3:6)) %>% -->
<!--   group_by(value, month) %>% -->
<!--   summarize(avg_tmax_statn = mean(tmax_statn)) -->

<!-- tmax_hrus_mo <- left_join(tmax_grid_mo, tmax_statn_mo, by = c('value', 'month')) %>% -->
<!--   mutate(mo_tmax_diff = avg_tmax_statn - avg_tmax_grid, -->
<!--          value = as.numeric(value)) -->

<!-- tmap_mode('plot') -->

<!-- #march -->
<!-- tmax_hrus_mar<- tmax_hrus_mo %>% -->
<!--   filter(month == 3) -->

<!-- hrus_map_tmax_mar <- left_join(hrus, tmax_hrus_mar, by = 'value') -->

<!-- mar_tmax <- tm_shape(hrus_map_tmax_mar) + -->
<!--   #tm_polygons('mo_tmax_diff', id = 'value') + -->
<!--   tm_fill('mo_tmax_diff', id = 'value', -->
<!--           breaks = c(-6,-4,-2,0,2,4,6)) + -->
<!--   tm_borders() + -->
<!--   tm_shape(locations_t) + -->
<!--   tm_symbols(col='blue', size = 0.25) + -->
<!--   tm_layout(title = 'March avg tmax', -->
<!--             legend.outside = T) -->

<!-- #april -->
<!-- tmax_hrus_apr<- tmax_hrus_mo %>% -->
<!--   filter(month == 4) -->

<!-- hrus_map_tmax_apr <- left_join(hrus, tmax_hrus_apr, by = 'value') -->

<!-- apr_tmax <- tm_shape(hrus_map_tmax_apr) + -->
<!--   tm_fill('mo_tmax_diff', id = 'value', -->
<!--           breaks = c(-6,-4,-2,0,2,4,6)) + -->
<!--   tm_borders() + -->
<!--   tm_shape(locations_t) + -->
<!--   tm_symbols(col='blue', size = 0.25) + -->
<!--   tm_layout(title = 'April avg tmax', -->
<!--             legend.outside = T) -->

<!-- #may -->
<!-- tmax_hrus_may<- tmax_hrus_mo %>% -->
<!--   filter(month == 5) -->

<!-- hrus_map_tmax_may <- left_join(hrus, tmax_hrus_may, by = 'value') -->

<!-- may_tmax <- tm_shape(hrus_map_tmax_may) + -->
<!--   tm_fill('mo_tmax_diff', id = 'value', -->
<!--          breaks = c(-6,-4,-2,0,2,4,6)) + -->
<!--   tm_borders() + -->
<!-- tm_shape(locations_t) + -->
<!--   tm_symbols(col='blue', size = 0.25) + -->
<!--   tm_layout(title = 'May avg tmax', -->
<!--             legend.outside = T) -->

<!-- #june -->
<!-- tmax_hrus_jun<- tmax_hrus_mo %>% -->
<!--   filter(month == 6) -->

<!-- hrus_map_tmax_jun <- left_join(hrus, tmax_hrus_jun, by = 'value') -->

<!-- jun_tmax <- tm_shape(hrus_map_tmax_jun) + -->
<!--   tm_fill('mo_tmax_diff', id = 'value', -->
<!--          breaks = c(-6,-4,-2,0,2,4,6)) + -->
<!--   tm_borders() + -->
<!-- tm_shape(locations_t) + -->
<!--   tm_symbols(col='blue', size = 0.25) + -->
<!--   tm_layout(title = 'June avg tmax', -->
<!--             legend.outside = T) -->

<!-- tmap_arrange(mar_tmax, apr_tmax, may_tmax, jun_tmax) -->

<!-- ``` -->

<!-- ## Tmin difference -->

<!-- ```{r tmin, echo = F} -->

<!-- tmin_grid <- read_csv(here('HRU_output/reg_tminAll_prism.csv')) %>%  -->
<!--   pivot_longer(cols = `3`:`19`, -->
<!--                names_to = 'value',  -->
<!--                values_to = 'tmin_grid') %>% -->
<!--   mutate(time = dmy(time)) %>% -->
<!--   group_by(value) %>% -->
<!--   summarize(Tmin_mean_grid = mean(tmin_grid)) -->

<!-- tmin_statn <- read_csv(here('HRU_output/reg_tminAll.csv')) %>%  -->
<!--   pivot_longer(cols = `3`:`19`, -->
<!--                names_to = 'value',  -->
<!--                values_to = 'tmin_statn') %>% -->
<!--   mutate(time = dmy(time)) %>% -->
<!--   group_by(value) %>% -->
<!--   summarize(Tmin_mean_statn = mean(tmin_statn)) -->

<!-- tmin_hrus <- left_join(tmin_grid, tmin_statn, by = c('value')) %>% -->
<!--   mutate(diff = Tmin_mean_statn - Tmin_mean_grid, -->
<!--          value = as.numeric(value)) -->

<!-- hrus_map_tmin <- left_join(hrus, tmin_hrus, by = 'value') -->

<!-- tmap_mode('view') -->

<!-- tm_shape(hrus_map_tmin) + -->
<!--   tm_polygons('diff', id = 'value', -->
<!--               breaks = c(-6,-4,-2,0,2,4,6)) + -->
<!-- tm_shape(locations_t) + -->
<!--   tm_symbols(col='blue', size=4) -->

<!-- ``` -->

<!-- ## Tmin monthly average -->

<!-- ```{r tmin month, echo = F} -->
<!-- tmin_grid_mo <- read_csv(here('HRU_output/reg_tminAll_prism.csv')) %>%  -->
<!--   pivot_longer(cols = `3`:`19`, -->
<!--                names_to = 'value',  -->
<!--                values_to = 'tmin_grid') %>% -->
<!--   mutate(time = dmy(time), -->
<!--          month = month(time)) %>% -->
<!--   filter(month %in% c(3:6)) %>% -->
<!--   group_by(value, month) %>% -->
<!--   summarize(avg_tmin_grid = mean(tmin_grid)) -->

<!-- tmin_statn_mo <- read_csv(here('HRU_output/reg_tminAll.csv')) %>%  -->
<!--   pivot_longer(cols = `3`:`19`, -->
<!--                names_to = 'value',  -->
<!--                values_to = 'tmin_statn') %>% -->
<!--   mutate(time = dmy(time), -->
<!--          month = month(time)) %>% -->
<!--   filter(month %in% c(3:6)) %>% -->
<!--   group_by(value, month) %>% -->
<!--   summarize(avg_tmin_statn = mean(tmin_statn)) -->

<!-- tmin_hrus_mo <- left_join(tmin_grid_mo, tmin_statn_mo, by = c('value', 'month')) %>% -->
<!--   mutate(mo_tmin_diff = avg_tmin_statn - avg_tmin_grid, -->
<!--          value = as.numeric(value)) -->

<!-- tmap_mode('plot') -->

<!-- #march -->
<!-- tmin_hrus_mar<- tmin_hrus_mo %>% -->
<!--   filter(month == 3) -->

<!-- hrus_map_tmin_mar <- left_join(hrus, tmin_hrus_mar, by = 'value') -->

<!-- mar_tmin <- tm_shape(hrus_map_tmin_mar) + -->
<!--   #tm_polygons('mo_tmin_diff', id = 'value') + -->
<!--   tm_fill('mo_tmin_diff', id = 'value', -->
<!--           breaks = c(-5,-2.5,0,2.5,5)) + -->
<!--   tm_borders() + -->
<!--   tm_shape(locations_t) + -->
<!--   tm_symbols(col='blue', size = 0.25) + -->
<!--   tm_layout(title = 'March avg tmin', -->
<!--             legend.outside = T) -->

<!-- #april -->
<!-- tmin_hrus_apr<- tmin_hrus_mo %>% -->
<!--   filter(month == 4) -->

<!-- hrus_map_tmin_apr <- left_join(hrus, tmin_hrus_apr, by = 'value') -->

<!-- apr_tmin <- tm_shape(hrus_map_tmin_apr) + -->
<!--   tm_fill('mo_tmin_diff', id = 'value', -->
<!--           breaks = c(-5,-2.5,0,2.5,5)) + -->
<!--   tm_borders() + -->
<!--   tm_shape(locations_t) + -->
<!--   tm_symbols(col='blue', size = 0.25) + -->
<!--   tm_layout(title = 'April avg tmin', -->
<!--             legend.outside = T) -->

<!-- #may -->
<!-- tmin_hrus_may<- tmin_hrus_mo %>% -->
<!--   filter(month == 5) -->

<!-- hrus_map_tmin_may <- left_join(hrus, tmin_hrus_may, by = 'value') -->

<!-- may_tmin <- tm_shape(hrus_map_tmin_may) + -->
<!--   tm_fill('mo_tmin_diff', id = 'value', -->
<!--          breaks = c(-5,-2.5,0,2.5,5)) + -->
<!--   tm_borders() + -->
<!-- tm_shape(locations_t) + -->
<!--   tm_symbols(col='blue', size = 0.25) + -->
<!--   tm_layout(title = 'May avg tmin', -->
<!--             legend.outside = T) -->

<!-- #june -->
<!-- tmin_hrus_jun<- tmin_hrus_mo %>% -->
<!--   filter(month == 6) -->

<!-- hrus_map_tmin_jun <- left_join(hrus, tmin_hrus_jun, by = 'value') -->

<!-- jun_tmin <- tm_shape(hrus_map_tmin_jun) + -->
<!--   tm_fill('mo_tmin_diff', id = 'value', -->
<!--           breaks = c(-5,-2.5,0,2.5,5)) + -->
<!--   tm_borders() + -->
<!-- tm_shape(locations_t) + -->
<!--   tm_symbols(col='blue', size = 0.25) + -->
<!--   tm_layout(title = 'June avg tmin', -->
<!--             legend.outside = T) -->

<!-- tmap_arrange(mar_tmin, apr_tmin, may_tmin, jun_tmin) -->

<!-- ``` -->

<!-- ## Cumulative Precip difference -->

<!-- 2011-2020 average of daily station-grid precip for DOY 365 (or 366) -->

<!-- ```{r cum precip, echo = F} -->
<!-- #get rid of a bunch of data -->
<!-- hru_grid_precip <- hru_grids %>% -->
<!--   dplyr::select(c(time, ID, precip)) %>% -->
<!--   rename(precip_grid = precip) -->

<!-- hru_statn_precip <- hru_statn %>% -->
<!--   dplyr::select(c(time, ID, precip)) %>% -->
<!--   rename(precip_statn = precip) -->

<!-- precip_hrus <- left_join(hru_grid_precip, hru_statn_precip, by = c('time', 'ID')) %>% -->
<!--   mutate(diff = precip_statn - precip_grid, -->
<!--          year = year(time)) %>% -->
<!--   group_by(year, ID) %>% -->
<!--   mutate(total_diff = cumsum(diff)) %>%  -->
<!--   filter(time == max(time)) %>% -->
<!--   group_by(ID) %>% -->
<!--   summarize(precip_avg_cumdiff = mean(total_diff)) %>% -->
<!--   rename(value = ID) -->

<!-- hrus_map_precip <- left_join(hrus, precip_hrus, by = 'value') -->

<!-- tmap_mode('view') -->

<!-- locations_p <- locations %>% -->
<!--   filter(type == 'precip') -->

<!-- tm_shape(hrus_map_precip) + -->
<!--   tm_polygons('precip_avg_cumdiff', midpoint = NA, palette = 'YlGnBu', id = 'value') + -->
<!-- tm_shape(locations_p) + -->
<!--   tm_symbols(col='blue', size=4) -->

<!-- ``` -->

<!-- ```{r relative p, echo = F} -->

<!-- # reg_p <- read_csv(here('HRU_output/reg_precipAll.csv'), -->
<!-- #                       skip = 21) %>% -->
<!-- #   dplyr::select(-starts_with('@')) %>% -->
<!-- #   mutate(time = dmy(time)) %>% -->
<!-- #   summarize(across(`3`:`19`, ~ mean(.))) %>% -->
<!-- #   pivot_longer(cols = `3`:`19`, -->
<!-- #                names_to = 'value',  -->
<!-- #                values_to = 'precip_avg') %>% -->
<!-- #   mutate(value = as.numeric(value)) -->
<!-- #  -->
<!-- #  -->
<!-- # hrus_map_precip <- left_join(hrus_map_precip, reg_p, by = 'value')  -->
<!-- #  -->
<!-- # hrus_map_precip <- hrus_map_precip %>% -->
<!-- #   mutate(relative_avgcum_diff = precip_avg_cumdiff / precip_avg) -->
<!-- #  -->
<!-- # tm_shape(hrus_map_precip) + -->
<!-- #   tm_polygons('relative_avgcum_diff', midpoint = NA, palette = 'YlGnBu', id = 'value') + -->
<!-- # tm_shape(locations_p) + -->
<!-- #   tm_symbols(col='blue', size=4) -->

<!-- ``` -->

<!-- ## Solar radiation difference -->

<!-- 2011-2020 average of daily station-grid solar rad -->

<!-- ```{r cum sol rad, echo = F} -->

<!-- #get rid of a bunch of data -->
<!-- hru_grid_solrad <- hru_grids %>% -->
<!--   dplyr::select(c(time, ID, solRad)) %>% -->
<!--   rename(solrad_grid = solRad)  %>% -->
<!--   group_by(ID) %>% -->
<!--   summarize(solrad_all_grid = mean(solrad_grid)) -->

<!-- hru_statn_solrad <- hru_statn %>% -->
<!--   dplyr::select(c(time, ID, solRad)) %>% -->
<!--   rename(solrad_statn = solRad) %>% -->
<!--   group_by(ID) %>% -->
<!--   summarize(solrad_all_statn = mean(solrad_statn)) -->

<!-- solrad_hrus <- left_join(hru_grid_solrad, hru_statn_solrad, by = c('ID')) %>% -->
<!--   mutate(diff = solrad_all_statn - solrad_all_grid) %>% -->
<!--   rename(value = ID) -->

<!-- hrus_map_solrad <- left_join(hrus, solrad_hrus, by = 'value') -->

<!-- tmap_mode('view') -->

<!-- locations_solrad <- locations %>%  -->
<!--   dplyr::filter(name %in% c('Gordon_South', -->
<!--                         'Betasso', 'Niwot_Snotel')) -->

<!-- tm_shape(hrus_map_solrad) + -->
<!--   tm_polygons('diff', midpoint = NA, palette = 'YlOrRd', id = 'value') + -->
<!-- tm_shape(locations_solrad) + -->
<!--   tm_symbols(col='blue', size=4) -->

<!-- ``` -->

<!-- ## RH difference -->

<!-- ```{r rh, echo = F} -->

<!-- #get rid of a bunch of data -->
<!-- hru_grid_rh <- hru_grids %>% -->
<!--   dplyr::select(c(time, ID, rhum)) %>% -->
<!--   rename(rh_grid = rhum)  %>% -->
<!--   group_by(ID) %>% -->
<!--   summarize(rh_all_grid = mean(rh_grid)) -->

<!-- hru_statn_rh <- hru_statn %>% -->
<!--   dplyr::select(c(time, ID, rhum)) %>% -->
<!--   rename(rh_statn = rhum) %>% -->
<!--   group_by(ID) %>% -->
<!--   summarize(rh_all_statn = mean(rh_statn)) -->

<!-- rh_hrus <- left_join(hru_grid_rh, hru_statn_rh, by = c('ID')) %>% -->
<!--   mutate(diff = rh_all_statn - rh_all_grid) %>% -->
<!--   rename(value = ID) -->

<!-- hrus_map_rh <- left_join(hrus, rh_hrus, by = 'value') -->

<!-- tmap_mode('view') -->

<!-- locations_rh <- locations %>%  -->
<!--   dplyr::filter(name %in% c('Gordon_South', 'Gordon_North', -->
<!--                         'Betasso', 'Niwot_Snotel')) -->

<!-- tm_shape(hrus_map_rh) + -->
<!--   tm_polygons('diff', midpoint = NA, id = 'value') + -->
<!-- tm_shape(locations_rh) + -->
<!--   tm_symbols(col='blue', size=4) -->

<!-- ``` -->

<!-- ## Average soil sat comparison -->

<!-- ```{r soilsat, echo = F} -->

<!-- #get rid of a bunch of data -->
<!-- hru_grid_soilsat <- hru_grids %>% -->
<!--   dplyr::select(c(time, ID, soilSat)) %>% -->
<!--   rename(soilsat_grid = soilSat)  %>% -->
<!--   group_by(ID) %>% -->
<!--   summarize(soilsat_all_grid = mean(soilsat_grid)) -->

<!-- hru_statn_soilsat <- hru_statn %>% -->
<!--   dplyr::select(c(time, ID, soilSat)) %>% -->
<!--   rename(soilsat_statn = soilSat) %>% -->
<!--   group_by(ID) %>% -->
<!--   summarize(soilsat_all_statn = mean(soilsat_statn)) -->

<!-- soilsat_hrus <- left_join(hru_grid_soilsat, hru_statn_soilsat, by = c('ID')) %>% -->
<!--   rename(value = ID) -->

<!-- hrus_map_soilsat <- left_join(hrus, soilsat_hrus, by = 'value') -->

<!-- tmap_mode('plot') -->

<!-- soilavg_grid <- tm_shape(hrus_map_soilsat) + -->
<!--   tm_polygons('soilsat_all_grid', midpoint = NA, id = 'value', -->
<!--               breaks = c(0.0, 0.05, 0.1, 0.15, 0.2, 0.25, 0.3)) + -->
<!--   tm_legend(legend.outside = T) + -->
<!--   tm_layout(main.title = 'Average soil sat') -->

<!-- soilavg_statn <- tm_shape(hrus_map_soilsat) + -->
<!--   tm_polygons('soilsat_all_statn', midpoint = NA, id = 'value', -->
<!--               breaks = c(0.0, 0.05, 0.1, 0.15, 0.2, 0.25, 0.3)) + -->
<!--   tm_legend(legend.outside = T) -->

<!-- tmap_arrange(soilavg_grid, soilavg_statn)  -->

<!-- ``` -->

<!-- ## Average max soil sat comparison -->

<!-- ```{r max soilsat, echo = F} -->

<!-- #get rid of a bunch of data -->
<!-- hru_grid_soilsat_max <- hru_grids %>% -->
<!--   dplyr::select(c(time, ID, soilSat)) %>% -->
<!--   rename(soilsat_grid = soilSat)  %>% -->
<!--   mutate(year = year(time)) %>%  -->
<!--   group_by(ID, year) %>% -->
<!--   summarize(soilsat_yrmax_grid = max(soilsat_grid)) %>% -->
<!--   summarize(avg_max_grid = mean(soilsat_yrmax_grid)) -->

<!-- hru_statn_soilsat_max <- hru_statn %>% -->
<!--   dplyr::select(c(time, ID, soilSat)) %>% -->
<!--   rename(soilsat_statn = soilSat) %>% -->
<!--   mutate(year = year(time)) %>%  -->
<!--   group_by(ID, year) %>% -->
<!--   summarize(soilsat_yrmax_statn = max(soilsat_statn)) %>% -->
<!--   summarize(avg_max_statn = mean(soilsat_yrmax_statn)) -->

<!-- soilsat_hrus_max <- left_join(hru_grid_soilsat_max, hru_statn_soilsat_max, by = c('ID')) %>% -->
<!--   rename(value = ID) -->

<!-- hrus_map_soilsat_max <- left_join(hrus, soilsat_hrus_max, by = 'value') -->

<!-- tmap_mode('plot') -->

<!-- soilavg_grid_max <- tm_shape(hrus_map_soilsat_max) + -->
<!--   tm_polygons('avg_max_grid', midpoint = NA, id = 'value', -->
<!--               breaks = c(0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.7)) + -->
<!--   tm_legend(legend.outside = T) + -->
<!--   tm_layout(main.title = 'Average max soil sat', -->
<!--             title.position = c('left', 'top')) -->

<!-- soilavg_statn_max <- tm_shape(hrus_map_soilsat_max) + -->
<!--   tm_polygons('avg_max_statn', midpoint = NA, id = 'value', -->
<!--               breaks = c(0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.7)) + -->
<!--   tm_legend(legend.outside = T) -->

<!-- tmap_arrange(soilavg_grid_max, soilavg_statn_max)  -->

<!-- ``` -->

<!-- ## Average ET comparison -->

<!-- ```{r et, echo = F} -->
<!-- #get rid of a bunch of data -->
<!-- hru_grid_ET <- hru_grids %>% -->
<!--   dplyr::select(c(time, ID, actET)) %>% -->
<!--   rename(ET_grid = actET)  %>% -->
<!--   group_by(ID) %>% -->
<!--   summarize(ET_all_grid = mean(ET_grid)) -->

<!-- hru_statn_ET <- hru_statn %>% -->
<!--   dplyr::select(c(time, ID, actET)) %>% -->
<!--   rename(ET_statn = actET) %>% -->
<!--   group_by(ID) %>% -->
<!--   summarize(ET_all_statn = mean(ET_statn)) -->

<!-- ET_hrus <- left_join(hru_grid_ET, hru_statn_ET, by = c('ID')) %>% -->
<!--   rename(value = ID) -->

<!-- hrus_map_ET <- left_join(hrus, ET_hrus, by = 'value') -->

<!-- tmap_mode('plot') -->

<!-- ETavg_grid <- tm_shape(hrus_map_ET) + -->
<!--   tm_polygons('ET_all_grid', midpoint = NA, id = 'value', -->
<!--               breaks = c(0.2, 0.4, 0.6, 0.8, 1.0, 1.2)) + -->
<!--   tm_legend(legend.outside = T) + -->
<!--   tm_layout(main.title = 'Average ET') -->

<!-- ETavg_statn <- tm_shape(hrus_map_ET) + -->
<!--   tm_polygons('ET_all_statn', midpoint = NA, id = 'value', -->
<!--              breaks = c(0.2, 0.4, 0.6, 0.8, 1.0, 1.2)) + -->
<!--   tm_legend(legend.outside = T) -->

<!-- tmap_arrange(ETavg_grid, ETavg_statn) -->

<!-- ``` -->

<!-- ## Average ET difference -->

<!-- ```{r et diff, echo = F} -->

<!-- ET_hrus <- ET_hrus %>% -->
<!--   mutate(diff = ET_all_statn - ET_all_grid) -->

<!-- hrus_map_et_diff <- left_join(hrus, ET_hrus, by = 'value') -->

<!-- tmap_mode('plot') -->

<!-- tm_shape(hrus_map_et_diff) + -->
<!--   tm_polygons('diff', midpoint = NA, id = 'value')  + -->
<!--   tm_legend(legend.outside = T) + -->
<!--   tm_layout(main.title = 'Average ET difference') -->

<!-- ``` -->

<!-- ## Average LAI comparison -->

<!-- ```{r lai, echo = F} -->

<!-- #get rid of a bunch of data -->
<!-- hru_grid_LAI <- hru_grids %>% -->
<!--   dplyr::select(c(time, ID, LAI)) %>% -->
<!--   rename(LAI_grid = LAI)  %>% -->
<!--   group_by(ID) %>% -->
<!--   summarize(LAI_all_grid = mean(LAI_grid)) -->

<!-- hru_statn_LAI <- hru_statn %>% -->
<!--   dplyr::select(c(time, ID, LAI)) %>% -->
<!--   rename(LAI_statn = LAI) %>% -->
<!--   group_by(ID) %>% -->
<!--   summarize(LAI_all_statn = mean(LAI_statn)) -->

<!-- LAI_hrus <- left_join(hru_grid_LAI, hru_statn_LAI, by = c('ID')) %>% -->
<!--   rename(value = ID) -->

<!-- hrus_map_LAI <- left_join(hrus, LAI_hrus, by = 'value') -->

<!-- tmap_mode('view') -->

<!-- LAIavg_grid <- tm_shape(hrus_map_LAI) + -->
<!--   tm_polygons('LAI_all_grid', midpoint = NA, id = 'value', -->
<!--               breaks = c(1,2,3,4,5)) + -->
<!--   tm_legend(legend.outside = T) + -->
<!--   tm_layout(main.title = 'Average LAI') -->

<!-- LAIavg_statn <- tm_shape(hrus_map_LAI) + -->
<!--   tm_polygons('LAI_all_statn', midpoint = NA, id = 'value', -->
<!--               breaks = c(1,2,3,4,5)) + -->
<!--   tm_legend(legend.outside = T) -->

<!-- tmap_arrange(LAIavg_grid, LAIavg_statn) -->

<!-- ``` -->

<!-- ## LAI over time  -->

<!-- ```{r lai over time, echo = F} -->

<!-- # plot time series of LAI over for HRU 1 and HRU 12 -->
<!-- hru_grid_select <- hru_grids %>% -->
<!--   filter(ID == 1 | ID == 12) %>% -->
<!--   dplyr::select(time, ID, LAI_grid = LAI) -->

<!-- hru_statn_select <- hru_statn %>% -->
<!--   filter(ID == 1 | ID == 12) %>% -->
<!--   dplyr::select(time, ID, LAI_statn = LAI) -->

<!-- hru_select <- left_join(hru_grid_select, hru_statn_select, by = c('time', 'ID')) %>% -->
<!--   rename(value = ID) -->

<!-- # plot time series of LAI over for HRU 1 -->
<!-- hru_select %>% -->
<!--   mutate(year = year(time)) %>%  -->
<!--   filter(value == 1) %>%  -->
<!-- ggplot(aes(x = time)) + -->
<!--   geom_line(aes(y = LAI_grid, color = "HRU1_burn_grid"), size = 1) + -->
<!--   geom_line(aes(y = LAI_statn, color = 'HRU1_burn_statn'), size = 1) + -->
<!--   ggtitle('LAI over time for HRU 1 (burned)') + -->
<!--   scale_color_manual(name = 'HRU' , values=c("HRU1_burn_grid"='orange',  -->
<!--                                             "HRU1_burn_statn"='springgreen4')) + -->
<!--   theme_bw() -->

<!-- # plot time series of LAI over for HRU 12 -->
<!-- {hru_select %>% -->
<!--   mutate(year = year(time)) %>%  -->
<!--   filter(value == 12) %>%  -->
<!-- ggplot(aes(x = time)) + -->
<!--   geom_line(aes(y = LAI_grid, color = "HRU12_unburn_grid"), size = 1) + -->
<!--   geom_line(aes(y = LAI_statn, color = 'HRU12_unburn_statn'), size = 1) + -->
<!--   ggtitle('LAI over time for HRU 12 (unburned)') + -->
<!--   scale_color_manual(name = 'HRU' , values=c("HRU12_unburn_grid"='orange',  -->
<!--                                             "HRU12_unburn_statn"='springgreen4')) + -->
<!--   theme_bw()} %>% -->
<!--   ggplotly() -->

<!-- ``` -->

<!-- ## HRU 29 LAI and biomass -->

<!-- ```{r hru29 lai and biomass} -->

<!-- # plot time series of LAI 29 -->
<!-- hru_grid29 <- hru_grids %>% -->
<!--   filter(ID == 29) %>% -->
<!--   dplyr::select(time, ID, LAI_grid = LAI) -->

<!-- hru_statn29 <- hru_statn %>% -->
<!--   filter(ID == 29) %>% -->
<!--   dplyr::select(time, ID, LAI_statn = LAI) -->

<!-- hru_29 <- left_join(hru_grid29, hru_statn29, by = c('time', 'ID'))  -->

<!-- # plot time series of LAI over for HRU 29 -->
<!-- {hru_29 %>% -->
<!--   ggplot(aes(x = time)) + -->
<!--   geom_line(aes(y = LAI_grid, color = "HRU29_grid"), size = 1) + -->
<!--   geom_line(aes(y = LAI_statn, color = 'HRU29_statn'), size = 1) + -->
<!--   ggtitle('LAI - HRU 29') + -->
<!--   scale_color_manual(name = 'HRU' , values=c("HRU29_grid"='orange',  -->
<!--                                             "HRU29_statn"='springgreen4')) + -->
<!--   theme_bw()} %>% -->
<!--   ggplotly() -->

<!-- hru29grid_bio <- read_csv('/Users/megansears/Documents/Repos/fourmile/HRU_output/HRU_29_grid.csv') %>% -->
<!--   mutate(time = mdy(time)) %>% -->
<!--   dplyr::select(time, BioAct_grid = BioAct_kgha) -->

<!-- hru29statn_bio <- read_csv('/Users/megansears/Documents/Repos/fourmile/HRU_output/HRU_29_statn.csv') %>% -->
<!--   mutate(time = mdy(time)) %>% -->
<!--   dplyr::select(time, BioAct_statn= BioAct_kgha) -->

<!-- hru_29_bio <- left_join(hru29grid_bio, hru29statn_bio, by = c('time'))  -->

<!-- #plot time series of biomass over time for HRU 29 -->
<!-- {hru_29_bio %>% -->
<!--   ggplot(aes(x = time)) + -->
<!--   geom_line(aes(y = BioAct_grid, color = "HRU29_grid"), size = 1) + -->
<!--   geom_line(aes(y = BioAct_statn, color = 'HRU29_statn'), size = 1) + -->
<!--   ggtitle('Biomass') + -->
<!--   scale_color_manual(name = 'HRU' , values=c("HRU29_grid"='orange',  -->
<!--                                             "HRU29_statn"='springgreen4')) + -->
<!--   theme_bw()} %>% -->
<!--   ggplotly() -->

<!-- ``` -->

<!-- # Mauscript figs -->

<!-- ## Figure 1 -->

<!-- ```{r fig1} -->

<!-- library(usmap) -->

<!-- dem <- raster('/Users/megansears/Documents/Repos/fourmile/data/GIS/cutDEM.tif') -->

<!-- hru_bnds <- st_read('/Users/megansears/Documents/Repos/fourmile/data/GIS/hrus_final.shp') -->

<!-- tmap_mode('plot') -->

<!-- tm_shape(dem) + -->
<!--   tm_raster(palette = terrain.colors(5)) + -->
<!--   tm_shape(hru_bnds) + -->
<!--   tm_polygons(alpha =0, col = 'black') + -->
<!--   tm_compass() + -->
<!--   tm_scale_bar() + -->
<!--   tm_layout(legend.outside = T, -->
<!--             main.title = 'A') -->

<!-- dem2 <- as.data.frame(dem, xy = TRUE) -->

<!-- # ggplot() + -->
<!-- #  geom_polygon(data = hru_bnds, aes(x = x, y = y, fill = value)) + -->
<!-- #   geom_raster(data = dem2, aes(x = x, y = y, -->
<!-- #                                       fill = cutDEM)) + -->
<!-- #   theme_bw() + -->
<!-- #   coord_quickmap() -->

<!-- ################################################### -->

<!-- catchment_mo_mean <- catchment %>% -->
<!--   mutate(month = month(time)) %>% -->
<!--   group_by(site, month) %>% -->
<!--   summarise(across(precip:solRad, ~ mean(.x, na.rm = TRUE))) %>% -->
<!--   dplyr::select(site, month, -->
<!--                 precip_mean = precip, tmean_mean = tmean,  -->
<!--                 solrad_mean = solRad, rh_mean = rhum) -->

<!-- catchment_mo_sd <- catchment %>% -->
<!--   mutate(month = month(time)) %>% -->
<!--   group_by(site, month) %>% -->
<!--   summarise(across(precip:solRad, ~ sd(.x, na.rm = TRUE))) %>% -->
<!--   dplyr::select(site, month, -->
<!--                 precip_sd = precip, tmean_sd = tmean,  -->
<!--                 solrad_sd = solRad, rh_sd = rhum) -->

<!-- catchment_mo <- left_join(catchment_mo_mean, catchment_mo_sd,  -->
<!--                           by = c('month', 'site')) -->

<!-- catchment_mo2 <- catchment_mo %>% -->
<!--   mutate(month_name = month.abb[month]) %>% -->
<!--   mutate(month_name = factor(month_name,  -->
<!--                              levels = c('Jan', 'Feb', 'Mar', -->
<!--                                         'Apr', 'May', 'Jun', -->
<!--                                         'Jul', 'Aug', 'Sep', -->
<!--                                         'Oct', 'Nov', 'Dec'))) -->

<!-- p_cols <- ggplot(catchment_mo2, aes(x = month_name, y = precip_mean, -->
<!--                           color = site, fill = site)) + -->
<!--   geom_col(position='dodge') + -->
<!--   geom_errorbar(aes(ymin = 0, ymax = precip_mean + precip_sd),  -->
<!--                 position = position_dodge(width = 0.6), width = 0.2) + -->
<!--   theme_bw(base_size = 14) + -->
<!--   labs(y = 'Precipitation (mm)', -->
<!--        x = element_blank())  -->

<!-- ggsave("P.png", plot = p_cols, width = 8, height = 6, dpi = 300) -->

<!-- t_moplot <- ggplot(catchment_mo2, aes(x = month_name, y = tmean_mean,  -->
<!--                                       color = site, group = site)) + -->
<!--   geom_ribbon(aes(ymin = tmean_mean - tmean_sd, ymax = tmean_mean + tmean_sd, fill = site), alpha = 0.2) + -->
<!--   geom_line() + -->
<!--   geom_point() + -->
<!--   theme_bw(base_size=14) + -->
<!--   labs(y = expression("Mean temperature " ( degree~C)), -->
<!--        x = element_blank()) -->

<!-- t_moplot -->

<!-- sol_moplot <- ggplot(catchment_mo2, aes(x = month_name, y = solrad_mean,  -->
<!--                                       color = site, group = site)) + -->
<!--   geom_ribbon(aes(ymin = solrad_mean - solrad_sd, ymax = solrad_mean + solrad_sd, fill = site), alpha = 0.2) + -->
<!--   geom_line() + -->
<!--   geom_point() + -->
<!--   theme_bw(base_size = 14) + -->
<!--   labs(y = expression("Solar radiation (MJ/m"^"2" * ")"), -->
<!--        x = element_blank())  -->

<!-- sol_moplot -->

<!-- rh_moplot <- ggplot(catchment_mo2, aes(x = month_name, y = rh_mean,  -->
<!--                                       color = site, group = site)) + -->
<!--   geom_ribbon(aes(ymin = rh_mean - rh_sd, ymax = rh_mean + rh_sd, fill = site), alpha = 0.2) + -->
<!--   geom_line() + -->
<!--   geom_point() + -->
<!--   theme_bw(base_size = 14) + -->
<!--   labs(y = 'RH (%)', x= element_blank())  -->
<!-- rh_moplot -->

<!-- quad <- ggarrange(p_cols,  -->
<!--           t_moplot, -->
<!--           sol_moplot, -->
<!--           rh_moplot, -->
<!--           common.legend = T, -->
<!--           legend = 'bottom', -->
<!--              nrow = 2, -->
<!--           ncol= 2) -->

<!-- ggsave("quad.png", plot = quad, width = 8, height = 6, dpi = 300) -->

<!-- ``` -->

### 2023-05-02 38HRU_model/fourmile_model_outputs.Rmd
updates
NEED TO RERUN CALS!
adding burn stuff

@@
 
+setwd('/Users/megansears/Documents/Repos/fourmile/38HRU_model')
+
 kge <- read_csv('calruns_KGE.csv')
@@
 #name all the csv
-names(dataframes) <- substr(filenames, 1, 9)
+names(dataframes) <- substr(filenames, 1, 10)
 
@@
 
-grid_2011 <- read_cals(grid2011., name = 'grid_2011')
-grid_2012 <- read_cals(grid2012., name = 'grid_2012')
-grid_2013 <- read_cals(grid2013., name = 'grid_2013')
-grid_2014 <- read_cals(grid2014., name = 'grid_2014')
-grid_2015 <- read_cals(grid2015., name = 'grid_2015')
-grid_2016 <- read_cals(grid2016., name = 'grid_2016')
-grid_2017 <- read_cals(grid2017., name = 'grid_2017')
-grid_2018 <- read_cals(grid2018., name = 'grid_2018')
-grid_2019 <- read_cals(grid2019., name = 'grid_2019')
-grid_2020 <- read_cals(grid2020., name = 'grid_2020')
-grid_all <- read_cals(gridall.c, name = 'grid_all')
+grid_2011 <- read_cals(grid_2011., name = 'grid_2011')
+grid_2012 <- read_cals(grid_2012., name = 'grid_2012')
+grid_2013 <- read_cals(grid_2013., name = 'grid_2013')
+grid_2014 <- read_cals(grid_2014., name = 'grid_2014')
+grid_2015 <- read_cals(grid_2015., name = 'grid_2015')
+grid_2016 <- read_cals(grid_2016., name = 'grid_2016')
+grid_2017 <- read_cals(grid_2017., name = 'grid_2017')
+grid_2018 <- read_cals(grid_2018., name = 'grid_2018')
+grid_2019 <- read_cals(grid_2019., name = 'grid_2019')
+grid_2020 <- read_cals(grid_2020., name = 'grid_2020')
+grid_all <- read_cals(grid_all.c, name = 'grid_all')
 
@@
 
-statn_2011 <- read_cals(statn2011, name = 'statn_2011')
-statn_2012 <- read_cals(statn2012, name = 'statn_2012')
-statn_2013 <- read_cals(statn2013, name = 'statn_2013')
-statn_2014 <- read_cals(statn2014, name = 'statn_2014')
-statn_2015 <- read_cals(statn2015, name = 'statn_2015')
-statn_2016 <- read_cals(statn2016, name = 'statn_2016')
-statn_2017 <- read_cals(statn2017, name = 'statn_2017')
-statn_2018 <- read_cals(statn2018, name = 'statn_2018')
-statn_2019 <- read_cals(statn2019, name = 'statn_2019')
-statn_2020 <- read_cals(statn2020, name = 'statn_2020')
-statn_all <- read_cals(statnall., name = 'statn_all')
+statn_2011 <- read_cals(statn_2011, name = 'statn_2011')
+statn_2012 <- read_cals(statn_2012, name = 'statn_2012')
+statn_2013 <- read_cals(statn_2013, name = 'statn_2013')
+statn_2014 <- read_cals(statn_2014, name = 'statn_2014')
+statn_2015 <- read_cals(statn_2015, name = 'statn_2015')
+statn_2016 <- read_cals(statn_2016, name = 'statn_2016')
+statn_2017 <- read_cals(statn_2017, name = 'statn_2017')
+statn_2018 <- read_cals(statn_2018, name = 'statn_2018')
+statn_2019 <- read_cals(statn_2019, name = 'statn_2019')
+statn_2020 <- read_cals(statn_2020, name = 'statn_2020')
+statn_all <- read_cals(statn_all., name = 'statn_all')
 
@@
 lapply(name, plotdens_params)
+
+```
+
+## Burn params
+
+```{echo = FALSE, message = FALSE, warning = FALSE, include = F}
+
+#pull in all filenames with composite
+filenames <- list.files('.', pattern=".csv", full.names=TRUE)
+
+#read all the csvs
+dataframes <- lapply(filenames, read_csv)
+
+#name all the csv
+names(dataframes) <- substr(filenames, 1, 10)
+
+#extract csvs from list to global env
+lapply(names(dataframes), function(x) assign(x, dataframes[[x]], envir = .GlobalEnv))
+rm(dataframes) #remove dataframes list
+
+# read in all the grid burn params
+read_cals_burn <- function(df, name){
+    df <- df %>%
+      slice(-c(1:274)) %>%
+      separate_wider_delim(Parameter, 
+                       delim = ',',
+                       names = c('soilID',
+                                 'luca_a_rain',
+                                 'luca_a_snow',
+                                 'luca_soilMaxInfSummer',
+                                 'luca_soilMaxDPS',
+                                 'luca_lagSurfaceRunoff',
+                                 'luca_soilDistMPSLPS')) %>%
+      slice(-1) %>%
+      dplyr::select(-1) %>% 
+      mutate(cal = name)
+}
+
+grid_2011_burn <- read_cals_burn(grid_2011., name = 'grid_2011')
+grid_2012_burn <- read_cals_burn(grid_2012., name = 'grid_2012')
+grid_2013_burn <- read_cals_burn(grid_2013., name = 'grid_2013')
+grid_2014_burn <- read_cals_burn(grid_2014., name = 'grid_2014')
+grid_2015_burn <- read_cals_burn(grid_2015., name = 'grid_2015')
+grid_2016_burn <- read_cals_burn(grid_2016., name = 'grid_2016')
+grid_2017_burn <- read_cals_burn(grid_2017., name = 'grid_2017')
+grid_2018_burn <- read_cals_burn(grid_2018., name = 'grid_2018')
+grid_2019_burn <- read_cals_burn(grid_2019., name = 'grid_2019')
+grid_2020_burn <- read_cals_burn(grid_2020., name = 'grid_2020')
+grid_all_burn <- read_cals_burn(grid_all.c, name = 'grid_all')
+
+grid_burn <- bind_rows(grid_2011_burn, 
+                  grid_2012_burn, 
+                  grid_2013_burn, 
+                  grid_2014_burn, 
+                  grid_2015_burn,
+                  grid_2016_burn, 
+                  grid_2017_burn, 
+                  grid_2018_burn, 
+                  grid_2019_burn, 
+                  grid_2020_burn,
+                  grid_all_burn) %>%
+  mutate(input_data = 'grid') %>%
+  mutate(year_missing_almost = gsub('grid_', '', cal)) %>%
+  mutate(year_missing = gsub('all', 'none', year_missing_almost)) %>%
+  dplyr::select(-c(year_missing_almost))
+
+# now do statn burn params
+statn_2011_burn <- read_cals_burn(statn_2011, name = 'statn_2011')
+statn_2012_burn <- read_cals_burn(statn_2012, name = 'statn_2012')
+statn_2013_burn <- read_cals_burn(statn_2013, name = 'statn_2013')
+statn_2014_burn <- read_cals_burn(statn_2014, name = 'statn_2014')
+statn_2015_burn <- read_cals_burn(statn_2015, name = 'statn_2015')
+statn_2016_burn <- read_cals_burn(statn_2016, name = 'statn_2016')
+statn_2017_burn <- read_cals_burn(statn_2017, name = 'statn_2017')
+statn_2018_burn <- read_cals_burn(statn_2018, name = 'statn_2018')
+statn_2019_burn <- read_cals_burn(statn_2019, name = 'statn_2019')
+statn_2020_burn <- read_cals_burn(statn_2020, name = 'statn_2020')
+statn_all_burn <- read_cals_burn(statn_all., name = 'statn_all')
+
+statn_burn <- bind_rows(statn_2011_burn, 
+                  statn_2012_burn, 
+                  statn_2013_burn, 
+                  statn_2014_burn, 
+                  statn_2015_burn,
+                  statn_2016_burn, 
+                  statn_2017_burn, 
+                  statn_2018_burn, 
+                  statn_2019_burn, 
+                  statn_2020_burn,
+                  statn_all_burn) %>%
+  mutate(input_data = 'statn') %>%
+  mutate(year_missing_almost = gsub('statn_', '', cal)) %>%
+  mutate(year_missing = gsub('all', 'none', year_missing_almost)) %>%
+  dplyr::select(-c(year_missing_almost))
+
+burn_params <- bind_rows(grid_burn, statn_burn) %>%
+  ungroup() %>%
+  mutate(across(c(luca_a_rain:luca_soilDistMPSLPS), as.numeric)) %>%
+  group_by(cal) %>%
+  summarise(across(c(luca_a_rain:luca_soilDistMPSLPS), mean)) %>%
+  pivot_longer(!cal, 
+               names_to = 'params',
+               values_to = 'value')
+
+```
+
+```{r}
+
+# plot_burnparams <- function(param_name) {
+#   params %>%
+#     filter(params == param_name) %>%
+#     ggplot(aes(x = value,
+#                y = cal)) + 
+#     geom_point() +
+#     ggtitle(param_name) +
+#     theme_bw()
+# }
+# 
+# name <- levels(burn_params$params)
+# 
+# lapply(name, plot_burnparams)
 

### 2023-05-03 38HRU_model/fourmile_model_outputs.Rmd
added in burn params

@@
 library(gridExtra)
+library(stringr)
 
@@
 
-## Burn params
+## Burn parameters
 
@@
   group_by(cal) %>%
-  summarise(across(c(luca_a_rain:luca_soilDistMPSLPS), mean)) %>%
-  pivot_longer(!cal, 
+  mutate(across(c(luca_a_rain:luca_soilDistMPSLPS), mean)) %>%
+  filter(soilID == 22) %>%
+  dplyr::select(-soilID) %>% 
+  pivot_longer(!c(cal, input_data, year_missing), 
                names_to = 'params',
-               values_to = 'value')
+               values_to = 'value') %>% 
+  mutate(params = str_remove(params, 'luca_')) %>%
+  mutate(params = as.factor(params),
+         burn = 'yes')
 
@@
 
-# plot_burnparams <- function(param_name) {
-#   params %>%
-#     filter(params == param_name) %>%
-#     ggplot(aes(x = value,
-#                y = cal)) + 
-#     geom_point() +
-#     ggtitle(param_name) +
-#     theme_bw()
-# }
-# 
-# name <- levels(burn_params$params)
-# 
-# lapply(name, plot_burnparams)
-
-```
-
-<!-- # Outlet results -->
-
-<!-- ## Hydrograph -->
-
-<!-- ```{r hydrographs, echo = F} -->
-<!-- flow <- read_csv('discharge_all.csv') %>% -->
-<!--   replace(.==-9999, NA) -->
-
-<!-- flow_pivot <- flow %>% -->
-<!--   pivot_longer(!date, names_to = 'cal_run', values_to = 'q_m3s') %>% -->
-<!--   mutate(year = as.factor(year(date))) -->
-
-<!-- q <- ggplot(flow_pivot, aes(date, q_m3s, color = cal_run)) + -->
-<!--   geom_line() + -->
-<!--   scale_color_manual(name="cal_run", values=c('obs' = 'black', -->
-<!--                                             "grid_2011"="seagreen", -->
-<!--                                             "grid_2012"="seagreen2", -->
-<!--                                             "grid_2013"="steelblue", -->
-<!--                                             "grid_2014"='dodgerblue', -->
-<!--                                             "grid_2015" = "cyan3", -->
-<!--                                             'grid_2016' = 'blue', -->
-<!--                                             'grid_2017' = 'blue4', -->
-<!--                                             'grid_2018' = 'cadetblue', -->
-<!--                                             'grid_2019' = 'lightgreen', -->
-<!--                                             'grid_2020' = 'olivedrab', -->
-<!--                                             'grid_all' = 'steelblue3', -->
-<!--                                             "statn_2011"="maroon", -->
-<!--                                             "statn_2012"="deeppink4", -->
-<!--                                             "statn_2013"="deeppink", -->
-<!--                                             "statn_2014"='purple', -->
-<!--                                             "statn_2015" = "mediumorchid1", -->
-<!--                                             'statn_2016' = 'indianred', -->
-<!--                                             'statn_2017' = 'sienna', -->
-<!--                                             'statn_2018' = 'salmon2', -->
-<!--                                             'statn_2019' = 'mediumpurple1', -->
-<!--                                             'statn_2020' = 'violetred', -->
-<!--                                             'statn_all' = 'red')) -->
-
-<!-- ggplotly(q) -->
-
-<!-- ``` -->
-
-<!-- ## Annual hydrographs -->
-
-<!-- ```{r cy hydrographs, echo = F} -->
-
-<!-- plotq_cy <- function(calyear) { -->
-<!--   {flow_pivot %>% -->
-<!--     filter(year == calyear) %>% -->
-<!--     ggplot(aes(x = date, -->
-<!--                y = q_m3s, -->
-<!--                color = cal_run)) + -->
-<!--     geom_line() + -->
-<!--         scale_color_manual(name="cal_run", values=c('obs' = 'black', -->
-<!--                                             "grid_2011"="seagreen",  -->
-<!--                                             "grid_2012"="seagreen2",  -->
-<!--                                             "grid_2013"="steelblue", -->
-<!--                                             "grid_2014"='dodgerblue',  -->
-<!--                                             "grid_2015" = "cyan3", -->
-<!--                                             'grid_2016' = 'blue', -->
-<!--                                             'grid_2017' = 'blue4', -->
-<!--                                             'grid_2018' = 'cadetblue', -->
-<!--                                             'grid_2019' = 'lightgreen', -->
-<!--                                             'grid_2020' = 'olivedrab', -->
-<!--                                             'grid_all' = 'steelblue3', -->
-<!--                                             "statn_2011"="maroon",  -->
-<!--                                             "statn_2012"="deeppink4",  -->
-<!--                                             "statn_2013"="deeppink", -->
-<!--                                             "statn_2014"='purple',  -->
-<!--                                             "statn_2015" = "mediumorchid1", -->
-<!--                                             'statn_2016' = 'indianred', -->
-<!--                                             'statn_2017' = 'sienna', -->
-<!--                                             'statn_2018' = 'salmon2', -->
-<!--                                             'statn_2019' = 'mediumpurple1', -->
-<!--                                             'statn_2020' = 'violetred', -->
-<!--                                             'statn_all' = 'red')) + -->
-<!--     ggtitle(calyear) + -->
-<!--     theme_bw()} %>% -->
-<!--     ggplotly() -->
-
-<!-- } -->
-
-<!-- name <- levels(flow_pivot$year) -->
-
-<!-- try <- lapply(name, plotq_cy) -->
-
-<!-- htmltools::tagList(try) -->
-
-<!-- try -->
-<!-- ``` -->
-
-<!-- ## KGE -->
-
-<!-- ### Overall KGE -->
-
-<!-- ```{r kge overall, echo = F} -->
-
-<!-- flow_kge_all <- flow %>% -->
-<!--   summarize(grid2011 = KGE(grid_2011, obs), -->
-<!--             grid2012 = KGE(grid_2012, obs), -->
-<!--             grid2013 = KGE(grid_2013, obs), -->
-<!--             grid2014 = KGE(grid_2014, obs), -->
-<!--             grid2015 = KGE(grid_2015, obs), -->
-<!--             grid2016 = KGE(grid_2016, obs), -->
-<!--             grid2017 = KGE(grid_2017, obs), -->
-<!--             grid2018 = KGE(grid_2018, obs), -->
-<!--             grid2019 = KGE(grid_2019, obs), -->
-<!--             grid2020 = KGE(grid_2020, obs), -->
-<!--             gridall = KGE(grid_all, obs), -->
-<!--             statn2011 = KGE(statn_2011, obs), -->
-<!--             statn2012 = KGE(statn_2012, obs), -->
-<!--             statn2013 = KGE(statn_2013, obs), -->
-<!--             statn2014 = KGE(statn_2014, obs), -->
-<!--             statn2015 = KGE(statn_2015, obs), -->
-<!--             statn2016 = KGE(statn_2016, obs), -->
-<!--             statn2017 = KGE(statn_2017, obs), -->
-<!--             statn2018 = KGE(statn_2018, obs), -->
-<!--             statn2019 = KGE(statn_2019, obs), -->
-<!--             statn2020 = KGE(statn_2020, obs), -->
-<!--             statnall = KGE(statn_all, obs)) %>% -->
-<!--     mutate_if(is.numeric, -->
-<!--             round, -->
-<!--             digits = 2) -->
-
-<!-- flow_kge_all <- flow_kge_all %>% -->
-<!--   pivot_longer(everything()) %>% -->
-<!--   arrange(value) -->
-
-<!-- kable(flow_kge_all) %>% -->
-<!--   kable_styling(full_width = F) -->
-
-<!-- ``` -->
-
-<!-- ### KGE by year -->
-
-<!-- ```{r kge by year, echo = F} -->
-
-<!-- flow_year <- flow %>% -->
-<!--   mutate(year = year(date)) %>% -->
-<!--   group_by(year) %>% -->
-<!--   summarize(grid2011 = KGE(grid_2011, obs), -->
-<!--             grid2012 = KGE(grid_2012, obs), -->
-<!--             grid2013 = KGE(grid_2013, obs), -->
-<!--             grid2014 = KGE(grid_2014, obs), -->
-<!--             grid2015 = KGE(grid_2015, obs), -->
-<!--             grid2016 = KGE(grid_2016, obs), -->
-<!--             grid2017 = KGE(grid_2017, obs), -->
-<!--             grid2018 = KGE(grid_2018, obs), -->
-<!--             grid2019 = KGE(grid_2019, obs), -->
-<!--             grid2020 = KGE(grid_2020, obs), -->
-<!--             gridall = KGE(grid_all, obs), -->
-<!--             statn2011 = KGE(statn_2011, obs), -->
-<!--             statn2012 = KGE(statn_2012, obs), -->
-<!--             statn2013 = KGE(statn_2013, obs), -->
-<!--             statn2014 = KGE(statn_2014, obs), -->
-<!--             statn2015 = KGE(statn_2015, obs), -->
-<!--             statn2016 = KGE(statn_2016, obs), -->
-<!--             statn2017 = KGE(statn_2017, obs), -->
-<!--             statn2018 = KGE(statn_2018, obs), -->
-<!--             statn2019 = KGE(statn_2019, obs), -->
-<!--             statn2020 = KGE(statn_2020, obs), -->
-<!--             statnall = KGE(statn_all, obs)) %>% -->
-<!--     mutate_if(is.numeric, -->
-<!--             round, -->
-<!--             digits = 2) -->
-
-<!-- flow_kge <- flow_year %>% -->
-<!--   pivot_longer(!year, names_to = 'model_run', values_to = 'kge') %>% -->
-<!--   pivot_wider(names_from = 'year', values_from = 'kge') -->
-
-<!-- flow_kge %>% -->
-<!--   kable(.) %>% -->
-<!--   kable_styling() -->
-
-<!-- flow_plot <- flow_year %>% -->
-<!--   pivot_longer(!year, names_to = 'model_run', values_to = 'kge') %>% -->
-<!--   mutate(year = as.factor(year)) -->
-
-<!-- kge_plot_cy <- ggplot(flow_plot, aes(year, kge, color = model_run)) +  -->
-<!--   geom_point(size = 3) + -->
-<!--   scale_color_manual(name="model_run", values=c("grid2011"="seagreen",  -->
-<!--                                             "grid2012"="seagreen2",  -->
-<!--                                             "grid2013"="steelblue", -->
-<!--                                             "grid2014"='dodgerblue',  -->
-<!--                                             "grid2015" = "cyan3", -->
-<!--                                             'grid2016' = 'blue', -->
-<!--                                             'grid2017' = 'blue4', -->
-<!--                                             'grid2018' = 'cadetblue', -->
-<!--                                             'grid2019' = 'lightgreen', -->
-<!--                                             'grid2020' = 'olivedrab', -->
-<!--                                             'gridall' = 'steelblue3', -->
-<!--                                             "statn2011"="maroon",  -->
-<!--                                             "statn2012"="deeppink4",  -->
-<!--                                             "statn2013"="deeppink", -->
-<!--                                             "statn2014"='purple',  -->
-<!--                                             "statn2015" = "mediumorchid1", -->
-<!--                                             'statn2016' = 'indianred', -->
-<!--                                             'statn2017' = 'sienna', -->
-<!--                                             'statn2018' = 'salmon2', -->
-<!--                                             'statn2019' = 'mediumpurple1', -->
-<!--                                             'statn2020' = 'violetred', -->
-<!--                                             'statnall' = 'red')) + -->
-<!--   theme_bw() -->
-
-<!-- ggplotly(kge_plot_cy) -->
-
-<!-- ``` -->
-
-<!-- ### Annual KGE plots -->
-
-<!-- ```{r wy plots, echo = F} -->
-
-<!-- plot_kge <- function(calyear) { -->
-<!--   flow_plot %>% -->
-<!--     filter(year == calyear) %>% -->
-<!--     ggplot(aes(x = model_run, -->
-<!--                y = kge)) + -->
-<!--     geom_col() + -->
-<!--     ggtitle(calyear) + -->
-<!--     theme_bw() + -->
-<!--     theme(axis.text.x = element_text(angle = 45, hjust=1)) -->
-<!-- } -->
-
-<!-- name <- levels(flow_plot$year) -->
-
-<!-- lapply(name, plot_kge) -->
-
-<!-- ``` -->
-
-<!-- # Ensembles -->
-
-<!-- ## Hydrograph -->
-
-<!-- ```{r boulder cr gage, echo = F} -->
-
-<!-- #pull in Boulder Creek @ N 75th gage -->
-
-<!-- bouldcr <- readNWISdv(siteNumbers = "06730200", -->
-<!--                           parameterCd = "00060",  -->
-<!--                           startDate = "2011-01-01",  -->
-<!--                           endDate = "2020-12-31")  %>% -->
-<!--   dplyr::select(date = Date, -->
-<!--          q_cfs = X_00060_00003) %>% -->
-<!--   mutate(bouldcr = q_cfs/35.3146662) %>% -->
-<!--   dplyr::select(-q_cfs) %>% -->
-<!--   mutate(year = year(date)) -->
-
-<!-- ``` -->
-
-<!-- ```{r ensemble hydrographs, echo = F} -->
-
-<!-- ensem <- flow %>% -->
-<!--   rowwise() %>% -->
-<!--   mutate(grid_ensemble = mean(c(grid_2011, grid_2012, -->
-<!--                                 grid_2013, grid_2014, -->
-<!--                                 grid_2015, grid_2016, -->
-<!--                                 grid_2017, grid_2018, -->
-<!--                                 grid_2019, grid_2020)), -->
-<!--          statn_ensemble = mean(c(statn_2011, statn_2012, -->
-<!--                                  statn_2013, statn_2014, -->
-<!--                                  statn_2015, statn_2016, -->
-<!--                                  statn_2017, statn_2018, -->
-<!--                                  statn_2019, statn_2020)), -->
-<!--          all_ensemble = mean(c(grid_2011, grid_2012, -->
-<!--                                grid_2013, grid_2014, -->
-<!--                                grid_2015, grid_2016, -->
-<!--                                grid_2017, grid_2018, -->
-<!--                                grid_2019, grid_2020, -->
-<!--                                statn_2011, statn_2012, -->
-<!--                                statn_2013, statn_2014, -->
-<!--                                statn_2015, statn_2016, -->
-<!--                                statn_2017, statn_2018, -->
-<!--                                statn_2019, statn_2020, -->
-<!--                                grid_all, statn_all))) %>% -->
-<!--   dplyr::select(date, grid_ensemble, statn_ensemble,  -->
-<!--          all_ensemble, grid_all,  -->
-<!--          statn_all, obs)  -->
-
-<!-- ensem_pivot <- ensem %>% -->
-<!--   pivot_longer(!date, names_to = 'cal_run', values_to = 'q_m3s') %>% -->
-<!--   mutate(year = as.factor(year(date))) -->
-
-<!-- q_ensemble <- ggplot(ensem_pivot, aes(date, q_m3s, color = cal_run)) + -->
-<!--   geom_line() + -->
-<!--   scale_color_manual(name="cal_run", values=c('obs'='black', -->
-<!--                                             "grid_ensemble"="maroon",  -->
-<!--                                             "statn_ensemble"="darkturquoise",  -->
-<!--                                             "grid_all"="purple1", -->
-<!--                                             "statn_all"='springgreen4',  -->
-<!--                                             "all_ensemble" = "orange")) + -->
-<!--   geom_line(data = bouldcr, aes(date, bouldcr/10), color = 'darkgrey') + -->
-<!--   scale_y_continuous(name = 'Q_m3s', -->
-<!--                     sec.axis = sec_axis(~.*10, name='BoulderCr_cms')) + -->
-<!--   theme_bw() -->
-
-<!-- ggplotly(q_ensemble) %>% -->
-<!--   add_lines(data=bouldcr, x=~date, y=~bouldcr, colors=NULL, yaxis="y2",  -->
-<!--               inherit=FALSE, showlegend = FALSE) %>% -->
-<!--   layout(yaxis2 = list(overlaying = "y", side = "right", -->
-<!--                        color = 'darkgray', -->
-<!--                        title = "BoulderCr_cms"), -->
-<!--          legend = list(x = 1.1, y = 0.95)) -->
-
-<!-- ``` -->
-
-<!-- ## Annual hydrographs -->
-
-<!-- ```{r hydrogs by cy, echo = F} -->
-
-<!-- plotqensem_cy <- function(calyear) { -->
-<!--   {ensem_pivot %>% -->
-<!--     filter(year == calyear) %>% -->
-<!--     ggplot(aes(x = date, -->
-<!--                y = q_m3s, -->
-<!--                color = cal_run)) + -->
-<!--     geom_line() + -->
-<!--     scale_color_manual(name="cal_run", values=c('obs' = 'black', -->
-<!--                                             "grid_ensemble"="maroon",  -->
-<!--                                             "statn_ensemble"="darkturquoise",  -->
-<!--                                             "grid_all"="purple1", -->
-<!--                                             "statn_all"='springgreen4',  -->
-<!--                                             "all_ensemble" = "orange")) + -->
-<!--     ggtitle(calyear) + -->
-<!--     theme_bw() -->
-<!--     } %>% -->
-<!--     ggplotly() -->
-<!-- } -->
-
-<!-- name <- levels(ensem_pivot$year) -->
-
-<!-- try <- lapply(name, plotqensem_cy) -->
-
-<!-- htmltools::tagList(try) -->
-
-<!-- try -->
-
-<!-- ``` -->
-
-<!-- ## KGE -->
-
-<!-- ### KGE for ensembles (entire period) -->
-
-<!-- ```{r ensemble kge, echo = F} -->
-
-<!-- ensem_kge_all <- ensem %>% -->
-<!--   ungroup() %>% -->
-<!--   summarize(grid_ensemble = KGE(grid_ensemble, obs), -->
-<!--             statn_ensemble = KGE(statn_ensemble, obs), -->
-<!--             all_ensemble = KGE(all_ensemble, obs), -->
-<!--             grid_all = KGE(grid_all, obs), -->
-<!--             statn_all = KGE(statn_all, obs)) %>% -->
-<!--     mutate_if(is.numeric, -->
-<!--             round, -->
-<!--             digits = 2) -->
-
-<!-- kable(ensem_kge_all) %>% -->
-<!--   kable_styling(full_width = F) -->
-
-<!-- ``` -->
-
-<!-- ### Annual KGEs for ensembles -->
-
-<!-- ```{r annual kge ensemble, echo = F} -->
-
-<!-- yr_kge_ensem <- ensem %>% -->
-<!--   ungroup() %>% -->
-<!--   mutate(year = year(date)) %>% -->
-<!--   group_by(year) %>% -->
-<!--   summarize(grid_ensemble = KGE(grid_ensemble, obs), -->
-<!--             statn_ensemble = KGE(statn_ensemble, obs), -->
-<!--             all_ensemble = KGE(all_ensemble, obs), -->
-<!--             grid_all = KGE(grid_all, obs), -->
-<!--             statn_all = KGE(statn_all, obs)) %>% -->
-<!--     mutate_if(is.numeric, -->
-<!--             round, -->
-<!--             digits = 2) -->
-
-<!-- yr_kge_table <- yr_kge_ensem %>% -->
-<!--   pivot_longer(!year, names_to = 'model_run', values_to = 'kge') %>% -->
-<!--   pivot_wider(names_from = 'year', values_from = 'kge') -->
-
-<!-- yr_kge_table %>% -->
-<!--   kable(.) %>% -->
-<!--   kable_styling() -->
-
-<!-- yr_kge_plot <- yr_kge_ensem %>% -->
-<!--   pivot_longer(!year, names_to = 'model_run', values_to = 'kge') %>% -->
-<!--   mutate(year = as.factor(year)) -->
-
-<!-- #plot annual kge vals for ensembles -->
-<!-- plot_kge_yr_ensem <- function(calyear) { -->
-<!--   yr_kge_plot %>% -->
-<!--     filter(year == calyear) %>% -->
-<!--     ggplot(aes(x = model_run, -->
-<!--                y = kge)) + -->
-<!--     geom_col() + -->
-<!--     ggtitle(calyear) + -->
-<!--     theme_bw() + -->
-<!--     theme(axis.text.x = element_text(angle = 45, hjust=1)) -->
-<!-- } -->
-
-<!-- name <- levels(yr_kge_plot$year) -->
-
-<!-- lapply(name, plot_kge_yr_ensem) -->
-
-<!-- ``` -->
-
-<!-- ### Monthly KGEs for ensembles -->
-
-<!-- ```{r monthly kge ensemble, echo = F} -->
-
-<!-- mo_kge <- ensem %>% -->
-<!--   ungroup() %>% -->
-<!--   drop_na() %>%  -->
-<!--   mutate(month = month(date)) %>% -->
-<!--   group_by(month) %>% -->
-<!--   summarize(grid_ensemble = KGE(grid_ensemble, obs), -->
-<!--             statn_ensemble = KGE(statn_ensemble, obs), -->
-<!--             all_ensemble = KGE(all_ensemble, obs), -->
-<!--             grid_all = KGE(grid_all, obs), -->
-<!--             statn_all = KGE(statn_all, obs)) %>% -->
-<!--     mutate_if(is.numeric, -->
-<!--             round, -->
-<!--             digits = 2) -->
-
-<!-- kable(mo_kge) %>% -->
-<!--   kable_styling(full_width = F) -->
-
-<!-- mo_pivot <- mo_kge %>% -->
-<!--   pivot_longer(!month, names_to = 'cal_run', values_to = 'KGE') %>% -->
-<!--   drop_na() -->
-
-<!-- kge_plot_mo <- ggplot(mo_pivot, aes(month, KGE, color = cal_run)) + geom_point(size = 3) + -->
-<!--     scale_color_manual(name="cal_run", values=c("grid_ensemble"="maroon",  -->
-<!--                                             "statn_ensemble"="darkturquoise",  -->
-<!--                                             "grid_all"="purple1", -->
-<!--                                             "statn_all"='springgreen4',  -->
-<!--                                             "all_ensemble" = "orange")) + -->
-<!--   theme_bw() -->
-
-<!-- ggplotly(kge_plot_mo) -->
-
-<!-- ``` -->
-
-<!-- ## RMSE -->
-
-<!-- ### Ensemble RMSE for entire period -->
-
-<!-- ```{r ensemble rmse, echo = F} -->
-
-<!-- ensem_rmse_all <- ensem %>% -->
-<!--   ungroup() %>% -->
-<!--   summarize(grid_ensemble = rmse(grid_ensemble, obs), -->
-<!--             statn_ensemble = rmse(statn_ensemble, obs), -->
-<!--             all_ensemble = rmse(all_ensemble, obs), -->
-<!--             grid_all = rmse(grid_all, obs), -->
-<!--             statn_all = rmse(statn_all, obs)) %>% -->
-<!--     mutate_if(is.numeric, -->
-<!--             round, -->
-<!--             digits = 4) -->
-
-<!-- kable(ensem_rmse_all) %>% -->
-<!--   kable_styling(full_width = F) -->
-
-<!-- ``` -->
-
-<!-- ### Annual RMSE for ensembles -->
-
-<!-- ```{r annual rmse ensem, echo = F} -->
-
-<!-- yr_rmse_ensem <- ensem %>% -->
-<!--   ungroup() %>% -->
-<!--   mutate(year = year(date)) %>% -->
-<!--   group_by(year) %>% -->
-<!--   summarize(grid_ensemble = rmse(grid_ensemble, obs), -->
-<!--             statn_ensemble = rmse(statn_ensemble, obs), -->
-<!--             all_ensemble = rmse(all_ensemble, obs), -->
-<!--             grid_all = rmse(grid_all, obs), -->
-<!--             statn_all = rmse(statn_all, obs)) %>% -->
-<!--     mutate_if(is.numeric, -->
-<!--             round, -->
-<!--             digits = 4) -->
-
-<!-- yr_rmse_table <- yr_rmse_ensem %>% -->
-<!--   pivot_longer(!year, names_to = 'model_run', values_to = 'rmse') %>% -->
-<!--   pivot_wider(names_from = 'year', values_from = 'rmse') -->
-
-<!-- yr_rmse_table %>% -->
-<!--   kable(.) %>% -->
-<!--   kable_styling() -->
-
-<!-- yr_rmse_plot <- yr_rmse_ensem %>% -->
-<!--   pivot_longer(!year, names_to = 'model_run', values_to = 'rmse') %>% -->
-<!--   mutate(year = as.factor(year)) -->
-
-<!-- #plot annual rmse vals for ensembles -->
-<!-- plot_rmse_yr_ensem <- function(calyear) { -->
-<!--   yr_rmse_plot %>% -->
-<!--     filter(year == calyear) %>% -->
-<!--     ggplot(aes(x = model_run, -->
-<!--                y = rmse)) + -->
-<!--     geom_col() + -->
-<!--     ggtitle(calyear) + -->
-<!--     theme_bw() + -->
-<!--     theme(axis.text.x = element_text(angle = 45, hjust=1)) -->
-<!-- } -->
-
-<!-- name <- levels(yr_rmse_plot$year) -->
-
-<!-- lapply(name, plot_rmse_yr_ensem) -->
-
-<!-- ``` -->
-
-<!-- ### Monthly RMSEs for ensembles -->
-
-<!-- ```{r month ensem rmse, echo = F} -->
-
-<!-- mo_rmse <- ensem %>% -->
-<!--   ungroup() %>% -->
-<!--   drop_na() %>%  -->
-<!--   mutate(month = month(date)) %>% -->
-<!--   group_by(month) %>% -->
-<!--   summarize(grid_ensemble = rmse(grid_ensemble, obs), -->
-<!--             statn_ensemble = rmse(statn_ensemble, obs), -->
-<!--             all_ensemble = rmse(all_ensemble, obs), -->
-<!--             grid_all = rmse(grid_all, obs), -->
-<!--             statn_all = rmse(statn_all, obs)) %>% -->
-<!--     mutate_if(is.numeric, -->
-<!--             round, -->
-<!--             digits = 4) -->
-
-<!-- kable(mo_rmse) %>% -->
-<!--   kable_styling(full_width = F) -->
-
-<!-- mo_pivot2 <- mo_rmse %>% -->
-<!--   pivot_longer(!month, names_to = 'cal_run', values_to = 'RMSE') %>% -->
-<!--   drop_na() -->
-
-<!-- rmse_plot_mo <- ggplot(mo_pivot2, aes(month, RMSE, color = cal_run)) + geom_point(size = 3) + -->
-<!--     scale_color_manual(name="cal_run", values=c("grid_ensemble"="maroon",  -->
-<!--                                             "statn_ensemble"="darkturquoise",  -->
-<!--                                             "grid_all"="purple1", -->
-<!--                                             "statn_all"='springgreen4',  -->
-<!--                                             "all_ensemble" = "orange")) + -->
-<!--   theme_bw() -->
-
-<!-- ggplotly(rmse_plot_mo) -->
-
-<!-- ``` -->
-
-<!-- ## NSE -->
-
-<!-- ### Ensemble NSE for entire period -->
-
-<!-- ```{r nse all, echo = F} -->
-
-<!-- ensem_nse_all <- ensem %>% -->
-<!--   ungroup() %>% -->
-<!--   summarize(grid_ensemble = NSE(grid_ensemble, obs), -->
-<!--             statn_ensemble = NSE(statn_ensemble, obs), -->
-<!--             all_ensemble = NSE(all_ensemble, obs), -->
-<!--             grid_all = NSE(grid_all, obs), -->
-<!--             statn_all = NSE(statn_all, obs)) %>% -->
-<!--     mutate_if(is.numeric, -->
-<!--             round, -->
-<!--             digits = 2) -->
-
-<!-- kable(ensem_nse_all) %>% -->
-<!--   kable_styling(full_width = F) -->
-
-<!-- ``` -->
-
-<!-- ### Annual NSE for ensembles -->
-
-<!-- ```{r annual nse, echo = F} -->
-
-<!-- yr_nse_ensem <- ensem %>% -->
-<!--   ungroup() %>% -->
-<!--   mutate(year = year(date)) %>% -->
-<!--   group_by(year) %>% -->
-<!--   summarize(grid_ensemble = NSE(grid_ensemble, obs), -->
-<!--             statn_ensemble = NSE(statn_ensemble, obs), -->
-<!--             all_ensemble = NSE(all_ensemble, obs), -->
-<!--             grid_all = NSE(grid_all, obs), -->
-<!--             statn_all = NSE(statn_all, obs)) %>% -->
-<!--     mutate_if(is.numeric, -->
-<!--             round, -->
-<!--             digits = 4) -->
-
-<!-- yr_nse_table <- yr_nse_ensem %>% -->
-<!--   pivot_longer(!year, names_to = 'model_run', values_to = 'nse') %>% -->
-<!--   pivot_wider(names_from = 'year', values_from = 'nse') -->
-
-<!-- yr_nse_table %>% -->
-<!--   kable(.) %>% -->
-<!--   kable_styling() -->
-
-<!-- yr_nse_plot <- yr_nse_ensem %>% -->
-<!--   pivot_longer(!year, names_to = 'model_run', values_to = 'nse') %>% -->
-<!--   mutate(year = as.factor(year)) -->
-
-<!-- #plot annual nse vals for ensembles -->
-<!-- plot_nse_yr_ensem <- function(calyear) { -->
-<!--   yr_nse_plot %>% -->
-<!--     filter(year == calyear) %>% -->
-<!--     ggplot(aes(x = model_run, -->
-<!--                y = nse)) + -->
-<!--     geom_col() + -->
-<!--     ggtitle(calyear) + -->
-<!--     theme_bw() + -->
-<!--     theme(axis.text.x = element_text(angle = 45, hjust=1)) -->
-<!-- } -->
-
-<!-- name <- levels(yr_nse_plot$year) -->
-
-<!-- lapply(name, plot_nse_yr_ensem) -->
-
-<!-- ``` -->
-
-<!-- ### Monthly NSE for ensembles -->
-
-<!-- ```{r monthly rmse, echo =F} -->
-
-<!-- mo_nse <- ensem %>% -->
-<!--   ungroup() %>% -->
-<!--   drop_na() %>%  -->
-<!--   mutate(month = month(date)) %>% -->
-<!--   group_by(month) %>% -->
-<!--   summarize(grid_ensemble = NSE(grid_ensemble, obs), -->
-<!--             statn_ensemble = NSE(statn_ensemble, obs), -->
-<!--             all_ensemble = NSE(all_ensemble, obs), -->
-<!--             grid_all = NSE(grid_all, obs), -->
-<!--             statn_all = NSE(statn_all, obs)) %>% -->
-<!--     mutate_if(is.numeric, -->
-<!--             round, -->
-<!--             digits = 4) -->
-
-<!-- kable(mo_nse) %>% -->
-<!--   kable_styling(full_width = F) -->
-
-<!-- mo_pivot2 <- mo_nse %>% -->
-<!--   pivot_longer(!month, names_to = 'cal_run', values_to = 'nse') %>% -->
-<!--   drop_na() -->
-
-<!-- nse_plot_mo <- ggplot(mo_pivot2, aes(month, nse, color = cal_run)) + geom_point(size = 3) + -->
-<!--   theme_bw() + -->
-<!--   scale_color_manual(name="cal_run", values=c("grid_ensemble"="maroon",  -->
-<!--                                             "statn_ensemble"="darkturquoise",  -->
-<!--                                             "grid_all"="purple1", -->
-<!--                                             "statn_all"='springgreen4',  -->
-<!--                                             "all_ensemble" = "orange"))  -->
-
-<!-- ggplotly(nse_plot_mo) -->
-
-<!-- ``` -->
-
-<!-- ## Percent bias -->
-
-<!-- Positive values indicate model overestimation and negative values model underestimation. -->
-
-<!-- ### Ensemble pbias for entire period -->
-
-<!-- ```{r pbias all, echo = F} -->
-
-<!-- ensem_pbias_all <- ensem %>% -->
-<!--   ungroup() %>% -->
-<!--   summarize(grid_ensemble = pbias(grid_ensemble, obs), -->
-<!--             statn_ensemble = pbias(statn_ensemble, obs), -->
-<!--             all_ensemble = pbias(all_ensemble, obs), -->
-<!--             grid_all = pbias(grid_all, obs), -->
-<!--             statn_all = pbias(statn_all, obs)) -->
-
-<!-- kable(ensem_pbias_all) %>% -->
-<!--   kable_styling(full_width = F) -->
-
-<!-- ``` -->
-
-<!-- ### Annual pbias for ensembles -->
-
-<!-- ```{r annualpbias, echo = F} -->
-
-<!-- yr_pbias_ensem <- ensem %>% -->
-<!--   ungroup() %>% -->
-<!--   mutate(year = year(date)) %>% -->
-<!--   group_by(year) %>% -->
-<!--   summarize(grid_ensemble = pbias(grid_ensemble, obs), -->
-<!--             statn_ensemble = pbias(statn_ensemble, obs), -->
-<!--             all_ensemble = pbias(all_ensemble, obs), -->
-<!--             grid_all = pbias(grid_all, obs), -->
-<!--             statn_all = pbias(statn_all, obs)) -->
-
-<!-- yr_pbias_table <- yr_pbias_ensem %>% -->
-<!--   pivot_longer(!year, names_to = 'model_run', values_to = 'pbias') %>% -->
-<!--   pivot_wider(names_from = 'year', values_from = 'pbias') -->
-
-<!-- yr_pbias_table %>% -->
-<!--   kable(.) %>% -->
-<!--   kable_styling() -->
-
-<!-- yr_pbias_plot <- yr_pbias_ensem %>% -->
-<!--   pivot_longer(!year, names_to = 'model_run', values_to = 'pbias') %>% -->
-<!--   mutate(year = as.factor(year)) -->
-
-<!-- #plot annual pbias vals for ensembles -->
-<!-- plot_pbias_yr_ensem <- function(calyear) { -->
-<!--   yr_pbias_plot %>% -->
-<!--     filter(year == calyear) %>% -->
-<!--     ggplot(aes(x = model_run, -->
-<!--                y = pbias)) + -->
-<!--     geom_col() + -->
-<!--     ggtitle(calyear) + -->
-<!--     theme_bw() + -->
-<!--     theme(axis.text.x = element_text(angle = 45, hjust=1)) -->
-<!-- } -->
-
-<!-- name <- levels(yr_pbias_plot$year) -->
-
-<!-- lapply(name, plot_pbias_yr_ensem) -->
-
-<!-- ``` -->
-
-<!-- ### Monthly pbias for ensembles -->
-
-<!-- ```{r monthly pbias, echo =F} -->
-
-<!-- mo_pbias <- ensem %>% -->
-<!--   ungroup() %>% -->
-<!--   drop_na() %>%  -->
-<!--   mutate(month = month(date)) %>% -->
-<!--   group_by(month) %>% -->
-<!--   summarize(grid_ensemble = pbias(grid_ensemble, obs), -->
-<!--             statn_ensemble = pbias(statn_ensemble, obs), -->
-<!--             all_ensemble = pbias(all_ensemble, obs), -->
-<!--             grid_all = pbias(grid_all, obs), -->
-<!--             statn_all = pbias(statn_all, obs)) %>% -->
-<!--     mutate_if(is.numeric, -->
-<!--             round, -->
-<!--             digits = 4) -->
-
-<!-- kable(mo_pbias) %>% -->
-<!--   kable_styling(full_width = F) -->
-
-<!-- mo_pivot2 <- mo_pbias %>% -->
-<!--   pivot_longer(!month, names_to = 'cal_run', values_to = 'pbias') %>% -->
-<!--   drop_na() -->
-
-<!-- pbias_plot_mo <- ggplot(mo_pivot2, aes(month, pbias, color = cal_run)) +  -->
-<!--   geom_point(size = 3) + -->
-<!--   scale_color_manual(name="cal_run", values=c("grid_ensemble"="maroon",  -->
-<!--                                             "statn_ensemble"="darkturquoise",  -->
-<!--                                             "grid_all"="purple1", -->
-<!--                                             "statn_all"='springgreen4',  -->
-<!--                                             "all_ensemble" = "orange")) + -->
-<!--   theme_bw() -->
-
-<!-- ggplotly(pbias_plot_mo) -->
-
-<!-- ``` -->
-
-<!-- ## Cumulative Q -->
-
-<!-- ```{r cumq, echo = F} -->
-
-<!-- ensem_cumq <- ensem %>% -->
-<!--   mutate(month = month(date)) %>% -->
-<!--   filter(month %in% c(4:9)) %>% -->
-<!--   dplyr::select(-month) %>%  -->
-<!--   pivot_longer(!date, names_to = 'cal_run', values_to = 'q_m3s') %>% -->
-<!--   group_by(cal_run, year(date)) %>% -->
-<!--   mutate(cumsum = cumsum(replace_na(q_m3s, 0))) %>% -->
-<!--   rename(year = 4) %>% -->
-<!--   mutate(year = as.factor(year)) %>% -->
-<!--   ungroup() -->
-
-<!-- #plot annual cumulative Q vals for ensembles -->
-<!-- plot_cumulq_yr_ensem <- function(calyear) { -->
-<!--   {ensem_cumq %>% -->
-<!--     filter(year == calyear) %>% -->
-<!--     ggplot(aes(x = date, -->
-<!--                y = cumsum, -->
-<!--                color = cal_run)) + -->
-<!--     geom_line() + -->
-<!--     scale_color_manual(name="cal_run", values=c("obs"="black", -->
-<!--                                              "grid_ensemble"="maroon",  -->
-<!--                                             "statn_ensemble"="darkturquoise",  -->
-<!--                                             "grid_all"="purple1", -->
-<!--                                             "statn_all"='springgreen4',  -->
-<!--                                             "all_ensemble" = "orange")) + -->
-<!--     ggtitle(calyear) + -->
-<!--     theme_bw() + -->
-<!--     labs(y = 'cumulative Q (m3s)')} %>% -->
-<!--     ggplotly() -->
-<!-- } -->
-
-<!-- name <- levels(ensem_cumq$year) -->
-
-<!-- cumulative_plots <- lapply(name, plot_cumulq_yr_ensem) -->
-
-<!-- htmltools::tagList(cumulative_plots) -->
-
-<!-- cumulative_plots -->
-
-<!-- ``` -->
-
-<!-- ## Percentiles -->
-
-<!-- ```{r percentiles, echo = F} -->
-
-<!-- quantile_calc <- function(x, probs, date) { -->
-<!--   tibble(x = quantile(x, probs), probs = probs, -->
-<!--          date = date[x = quantile(x, probs)]) -->
-<!-- } -->
-
-<!-- percent <- ensem_cumq %>% -->
-<!--   group_by(year, cal_run) %>% -->
-<!--   summarize(quantile_calc(cumsum, c(0.25, 0.5, 0.75), date)) %>% -->
-<!--   mutate(date = as.Date(date)) %>% -->
-<!--   mutate(probs = as.factor(probs)) -->
-
-<!-- ### -->
-<!-- quantile_cal <- function(data, prob) { -->
-<!--   data %>% -->
-<!--     dplyr::group_by(cal_run, year) %>% -->
-<!--     mutate(quantile = paste0(prob), -->
-<!--            value = quantile(cumsum, prob)) %>% -->
-<!--     group_by(cal_run, year, quantile) %>%  -->
-<!--     filter(cumsum >= value) %>% -->
-<!--     filter(date == min(date)) -->
-<!--   } -->
-
-<!-- quantiles <- c(0.25, 0.5, 0.75) -->
-
-<!-- quants <- quantiles %>% -->
-<!--   map(~ quantile_cal(data = ensem_cumq, prob = .)) %>% -->
-<!--   bind_rows() -->
-<!-- #### -->
-
-<!-- #plot percentiles -->
-<!-- plot_perc_ensem <- function(perc) { -->
-<!--   {percent %>% -->
-<!--     filter(probs == perc) %>% -->
-<!--     ggplot(aes(x = year, -->
-<!--                y = x, -->
-<!--                color = cal_run)) + -->
-<!--     geom_point(size=3) + -->
-<!--     scale_color_manual(name="cal_run", values=c("obs"="black", -->
-<!--                                              "grid_ensemble"="maroon",  -->
-<!--                                             "statn_ensemble"="darkturquoise",  -->
-<!--                                             "grid_all"="purple1", -->
-<!--                                             "statn_all"='springgreen4',  -->
-<!--                                             "all_ensemble" = "orange")) + -->
-<!--     ggtitle(perc) + -->
-<!--     ylab('Streamflow (cms)') + -->
-<!--     theme_bw()} %>% -->
-<!--     ggplotly() -->
-<!-- } -->
-
-<!-- name <- levels(percent$probs) -->
-
-<!-- perc_plots <- lapply(name, plot_perc_ensem) -->
-
-<!-- htmltools::tagList(perc_plots) -->
-
-<!-- perc_plots -->
-
-<!-- ``` -->
-
-<!-- ## Max Q prior to April 1 -->
-
-<!-- ```{r early max q, echo = F} -->
-
-<!-- ensem_bould <- left_join(ensem, bouldcr, by = 'date') %>% -->
-<!--   pivot_longer(!c(date, year), names_to = 'source', values_to = 'q_m3s') %>% -->
-<!--   mutate(month = month(date)) %>% -->
-<!--   filter(month %in% 3) %>% -->
-<!--   group_by(source, year) %>% -->
-<!--   slice_max(q_m3s, n=1) -->
-
-<!-- early_peakq <- ensem_bould %>% -->
-<!--   mutate(doy = yday(date)) %>% -->
-<!--   dplyr::select(c(doy, source, q_m3s, year)) %>% -->
-<!--   drop_na() %>%  -->
-<!--   pivot_wider(names_from = 'source', values_from = c('q_m3s', 'doy')) -->
-
-<!-- marpeakq <- ggplot(early_peakq, aes(x = doy_bouldcr)) + -->
-<!--   geom_point(aes(y = doy_all_ensemble, shape = "all_ensemble",  -->
-<!--                  color = 'all_ensemble'), size=2.5) + -->
-<!--   geom_point(aes(y = doy_grid_all, shape = 'grid_all',  -->
-<!--                  color = 'grid_all'), size=2.5) + -->
-<!--   geom_point(aes(y = doy_grid_ensemble, shape = 'grid_ensemble',  -->
-<!--                  color = 'grid_ensemble'), size=2.5) + -->
-<!--   geom_point(aes(y = doy_statn_all, shape = 'statn_all',  -->
-<!--                  color = 'statn_all'), size=2.5) + -->
-<!--   geom_point(aes(y = doy_statn_ensemble, shape = 'statn_ensemble',  -->
-<!--                  color = 'statn_ensemble'), size=2.5) + -->
-<!--   geom_abline(intercept = 0, slope = 1, size=1, color='black') + -->
-<!--   labs(x = "Boulder Creek DOY for March Peak Q",  -->
-<!--        y = 'DOY for March Peak Q') + -->
-<!--   theme_bw() + -->
-<!--   scale_shape_manual(name="source", values=c("all_ensemble"=15,  -->
-<!--                                             "grid_all"=16,  -->
-<!--                                             "grid_ensemble"=17, -->
-<!--                                             "statn_all"=18,  -->
-<!--                                             "statn_ensemble" = 8)) + -->
-<!--     scale_color_manual(name="source", values=c("all_ensemble"='orange',  -->
-<!--                                             "grid_all"='purple1',  -->
-<!--                                             "grid_ensemble"='maroon', -->
-<!--                                             "statn_all"='springgreen4',  -->
-<!--                                             "statn_ensemble" = 'darkturquoise')) + -->
-<!--   ggtitle('DOY of peak Q in March') -->
-
-<!-- ggplotly(marpeakq) -->
-
-<!-- # ggplot(early_peakq, aes(doy_bouldcr, doy_grid_all)) + -->
-<!-- #   geom_point(size=2.5) + -->
-<!-- #   geom_abline(intercept = 0, slope = 1, size=1, color='red') + -->
-<!-- #   theme_bw() + -->
-<!-- #   ggtitle('DOY of peak Q prior to April 1st - Grid All') -->
-<!-- #  -->
-<!-- #  -->
-<!-- # ggplot(early_peakq, aes(doy_bouldcr, doy_grid_ensemble)) + -->
-<!-- #   geom_point(size=2.5) + -->
-<!-- #   geom_abline(intercept = 0, slope = 1, size=1, color='red') + -->
-<!-- #   theme_bw() + -->
-<!-- #   ggtitle('DOY of peak Q prior to April 1st - Grid Ensemble') -->
-<!-- #  -->
-<!-- #  -->
-<!-- # ggplot(early_peakq, aes(doy_bouldcr, doy_statn_all)) + -->
-<!-- #   geom_point(size=2.5) + -->
-<!-- #   geom_abline(intercept = 0, slope = 1, size=1, color='red') + -->
-<!-- #   theme_bw() + -->
-<!-- #   ggtitle('DOY of peak Q prior to April 1st - Station All') -->
-<!-- #  -->
-<!-- #  -->
-<!-- # ggplot(early_peakq, aes(doy_bouldcr, doy_statn_ensemble)) + -->
-<!-- #   geom_point(size=2.5) + -->
-<!-- #   geom_abline(intercept = 0, slope = 1, size=1, color='red') + -->
-<!-- #   theme_bw() + -->
-<!-- #   ggtitle('DOY of peak Q prior to April 1st - Station Ensemble') -->
-
-<!-- early_peakq_table <- ensem_bould %>% -->
-<!--   mutate(doy = yday(date)) %>% -->
-<!--   dplyr::arrange(date) -->
-
-<!-- kable(early_peakq_table) %>% -->
-<!--   kable_styling(full_width = F) %>%  -->
-<!--   scroll_box(width = "100%", height = "500px") -->
-
-<!-- bouldcr3 <- bouldcr %>% -->
-<!--   mutate(month = month(date)) %>% -->
-<!--   filter(month == 3, year == 2011) -->
-
-<!-- test1 <- ensem_pivot %>% -->
-<!--   mutate(month = month(date)) %>% -->
-<!--   filter(year == 2011, -->
-<!--          month == 3) %>%  -->
-<!--   ggplot(aes(date, q_m3s, color = cal_run)) + -->
-<!--   geom_line() + -->
-<!--   scale_color_manual(name="cal_run", values=c('obs'='black', -->
-<!--                                             "grid_ensemble"="maroon",  -->
-<!--                                             "statn_ensemble"="darkturquoise",  -->
-<!--                                             "grid_all"="purple1", -->
-<!--                                             "statn_all"='springgreen4',  -->
-<!--                                             "all_ensemble" = "orange")) + -->
-<!--   geom_line(data = bouldcr3, aes(date, bouldcr/10), color = 'darkgrey') + -->
-<!--   scale_y_continuous(name = 'Q_m3s', -->
-<!--                     sec.axis = sec_axis(~.*10, name='BoulderCr_cms')) + -->
-<!--   theme_bw() + -->
-<!--   ggtitle('March 2011') -->
-
-<!-- ggplotly(test1) %>% -->
-<!--   add_lines(data=bouldcr, x=~date, y=~bouldcr, colors=NULL, yaxis="y2",  -->
-<!--               inherit=FALSE, showlegend = FALSE) %>% -->
-<!--   layout(yaxis2 = list(overlaying = "y", side = "right", -->
-<!--                        color = 'darkgray', -->
-<!--                        title = "BoulderCr_cms"), -->
-<!--          legend = list(x = 1.1, y = 0.95)) -->
-
-<!-- ################################################ -->
-
-<!-- bouldcr3_2 <- bouldcr %>% -->
-<!--   mutate(month = month(date)) %>% -->
-<!--   filter(month == 3, year == 2019) -->
-
-<!-- test2 <- ensem_pivot %>% -->
-<!--   mutate(month = month(date)) %>% -->
-<!--   filter(year == 2019, -->
-<!--          month == 3) %>%  -->
-<!--   ggplot(aes(date, q_m3s, color = cal_run)) + -->
-<!--   geom_line() + -->
-<!--   scale_color_manual(name="cal_run", values=c('obs'='black', -->
-<!--                                             "grid_ensemble"="maroon",  -->
-<!--                                             "statn_ensemble"="darkturquoise",  -->
-<!--                                             "grid_all"="purple1", -->
-<!--                                             "statn_all"='springgreen4',  -->
-<!--                                             "all_ensemble" = "orange")) + -->
-<!--   geom_line(data = bouldcr3_2, aes(date, bouldcr/10), color = 'darkgrey') + -->
-<!--   scale_y_continuous(name = 'Q_m3s', -->
-<!--                     sec.axis = sec_axis(~.*10, name='BoulderCr_cms')) + -->
-<!--   theme_bw() + -->
-<!--   ggtitle('March 2019') -->
-
-<!-- ggplotly(test2) %>% -->
-<!--   add_lines(data=bouldcr, x=~date, y=~bouldcr, colors=NULL, yaxis="y2",  -->
-<!--               inherit=FALSE, showlegend = FALSE) %>% -->
-<!--   layout(yaxis2 = list(overlaying = "y", side = "right", -->
-<!--                        color = 'darkgray', -->
-<!--                        title = "BoulderCr_cms"), -->
-<!--          legend = list(x = 1.1, y = 0.95)) -->
-
-<!-- ``` -->
-
-<!-- # Catchment results -->
-
-<!-- ## Precip -->
-
-<!-- ```{r catch precip, echo = F} -->
-<!-- setwd("/Users/megansears/Documents/Repos/fourmile/catchment_output") -->
-
-<!-- statn <- read_csv('statnall.csv') -->
-<!-- grid <- read_csv('gridall.csv') -->
-
-<!-- grid <- grid %>% mutate(site = 'grid') -->
-<!-- statn <- statn %>% mutate(site = 'statn') -->
-
-<!-- catchment <- bind_rows(grid, statn) %>% -->
-<!--   mutate(year = as.factor(year(time))) %>% -->
-<!--   group_by(year, site) %>% -->
-<!--   mutate(cumulative_p = cumsum(precip)) -->
-
-<!-- #plot cumulative precip by year -->
-<!-- plot_cumprecip <- function(calyear) { -->
-<!--   {catchment %>% -->
-<!--     filter(year == calyear) %>% -->
-<!--     ggplot(aes(x = time, -->
-<!--                y = cumulative_p, color = site)) + -->
-<!--     geom_line(size=1) + -->
-<!--     ggtitle(calyear) + -->
-<!--     ylab('Cumulative precip (mm)') + -->
-<!--     theme_bw() + -->
-<!--     theme(axis.text.x = element_text(angle = 45, hjust=1))} %>% -->
-<!--     ggplotly() -->
-<!-- } -->
-
-<!-- name <- levels(catchment$year) -->
-
-<!-- precip_plots <- lapply(name, plot_cumprecip) -->
-
-<!-- htmltools::tagList(precip_plots) -->
-
-<!-- precip_plots -->
-
-<!-- ## total P -->
-<!-- max_cumulativep <- catchment %>% -->
-<!--   group_by(year, site) %>% -->
-<!--   summarize(total_cumulativep = max(cumulative_p)) -->
-
-<!-- ggplot(max_cumulativep, aes(x=year, y=total_cumulativep, color=site)) +  -->
-<!--   geom_point(size=3) + -->
-<!--   ggtitle('Total cumulative precip (mm) by year') -->
-
-<!-- ``` -->
-
-<!-- ## Tmean -->
-
-<!-- ```{r tmean catch, echo = F} -->
-<!-- ## tmean  -->
-<!-- tmean <- catchment %>% -->
-<!--   group_by(year, site) %>% -->
-<!--   summarize(tmean = mean(tmean)) %>% -->
-<!--   ggplot(aes(x = year, y=tmean, color = site)) + -->
-<!--   geom_point(size=3) + -->
-<!--   ggtitle('Average temp by year') -->
-
-<!-- tmean -->
-
-<!-- ``` -->
-
-<!-- ## RD and RG -->
-
-<!-- ```{r rd and rg, echo = F, fig.width = 14, fig.asp = 1, out.width = "100%"} -->
-
-<!-- gw_grid <- read_csv(here('catchment_output/gridall_outlet.csv')) %>% -->
-<!--   dplyr::select(time, catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w) %>% -->
-<!--   mutate(source = 'grid') -->
-
-<!-- gw_statn <- read_csv(here('catchment_output/statnall_outlet.csv')) %>% -->
-<!--   dplyr::select(time, catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w) %>% -->
-<!--   mutate(source = 'statn') -->
-
-<!-- gw <- bind_rows(gw_grid, gw_statn) %>% -->
-<!--   mutate(year = year(time)) %>% -->
-<!--   rename(date = time) -->
-
-<!-- ggplot(gw, aes(x=date, color = source)) + -->
-<!--   geom_line(aes(y=catchmentRD1_w), size =1) + -->
-<!--   facet_wrap(~year, scales = 'free', ncol = 2) + -->
-<!--   scale_x_date(labels = date_format("%b")) + -->
-<!--   ggtitle('RD1') + -->
-<!--   theme(text = element_text(size = 20))    -->
-
-<!-- ggplot(gw, aes(x=date, color = source)) + -->
-<!--   geom_line(aes(y=catchmentRD2_w), size =1) + -->
-<!--   facet_wrap(~year, scales = 'free', ncol = 2) + -->
-<!--   scale_x_date(labels = date_format("%b")) + -->
-<!--   ggtitle('RD2') + -->
-<!--   theme(text = element_text(size = 20))    -->
-
-<!-- ggplot(gw, aes(x=date, color = source)) + -->
-<!--   geom_line(aes(y=catchmentRG1_w), size =1) + -->
-<!--   facet_wrap(~year, scales = 'free', ncol = 2) + -->
-<!--   scale_x_date(labels = date_format("%b")) + -->
-<!--   ggtitle('RG1') + -->
-<!--   theme(text = element_text(size = 20))    -->
-
-<!-- ggplot(gw, aes(x=date, color = source)) + -->
-<!--   geom_line(aes(y=catchmentRG2_w), size =1) + -->
-<!--   facet_wrap(~year, scales = 'free', ncol=2) + -->
-<!--   scale_x_date(labels = date_format("%b")) + -->
-<!--   ggtitle('RG2') + -->
-<!--   theme(text = element_text(size = 20))    -->
-
-<!-- gw <- gw %>% -->
-<!--   group_by(year, source) %>% -->
-<!--   mutate(RD1cumsum = cumsum(catchmentRD1_w), -->
-<!--          RD2cumsum = cumsum(catchmentRD2_w), -->
-<!--          RG1cumsum = cumsum(catchmentRG1_w), -->
-<!--          RG2cumsum = cumsum(catchmentRG2_w)) -->
-
-<!-- ggplot(gw, aes(x=date, color = source)) + -->
-<!--   geom_line(aes(y=RD1cumsum), size =1) + -->
-<!--   facet_wrap(~year, scales = 'free', ncol=2) + -->
-<!--   scale_x_date(labels = date_format("%b")) + -->
-<!--   ggtitle('Cumulative RD1') + -->
-<!--   theme(text = element_text(size = 20))    -->
-
-<!-- ggplot(gw, aes(x=date, color = source)) + -->
-<!--   geom_line(aes(y=RD2cumsum), size = 1) + -->
-<!--   facet_wrap(~year, scales = 'free', ncol=2) + -->
-<!--   scale_x_date(labels = date_format("%b")) + -->
-<!--   ggtitle('Cumulative RD2') + -->
-<!--   theme(text = element_text(size = 20))    -->
-
-<!-- ggplot(gw, aes(x=date, color = source)) + -->
-<!--   geom_line(aes(y=RG1cumsum), size  = 1) + -->
-<!--   facet_wrap(~year, scales = 'free', ncol = 2) + -->
-<!--   scale_x_date(labels = date_format("%b")) + -->
-<!--   ggtitle('Cumulative RG1') + -->
-<!--   theme(text = element_text(size = 20))    -->
-
-<!-- ggplot(gw, aes(x=date, color = source)) + -->
-<!--   geom_line(aes(y=RG2cumsum), size =1) + -->
-<!--   facet_wrap(~year, scales = 'free', ncol = 2) + -->
-<!--   scale_x_date(labels = date_format("%b")) + -->
-<!--   ggtitle('Cumulative RG2') + -->
-<!--   theme(text = element_text(size = 20))    -->
-
-<!-- ``` -->
-
-<!-- ```{r rd and rg sums, echo = F, fig.width = 22, fig.asp = 1.5, out.width = "100%"} -->
-
-<!-- ################## -->
-<!-- # all 4 with facets -->
-
-<!-- ggplot(gw, aes(x=date)) + -->
-<!--   geom_line(aes(y=RG2cumsum, color = 'cumulative RG2'), size =1) + -->
-<!--   geom_line(aes(y=RG1cumsum, color = 'cumulative RG1'), size =1) + -->
-<!--   geom_line(aes(y=RD1cumsum, color = 'cumulative RD1'), size =1) + -->
-<!--   geom_line(aes(y=RD2cumsum, color = 'cumulative RD2'), size =1) + -->
-<!--   scale_x_date(labels = date_format("%b")) + -->
-<!--   facet_wrap(~year + source, scales = 'free_x', ncol=2) + -->
-<!--   ggtitle('Cumulative RD and RG') + -->
-<!--   theme(text = element_text(size = 24))    -->
-
-<!-- ``` -->
-
-<!-- ```{r gw boxplot, echo = F} -->
-
-<!-- gw_maxcumsum <- gw %>% -->
-<!--   group_by(source, year) %>% -->
-<!--   summarize(yr_max_RD1 = max(RD1cumsum), -->
-<!--             yr_max_RD2 = max(RD2cumsum), -->
-<!--             yr_max_RG1 = max(RG1cumsum), -->
-<!--             yr_max_RG2 = max(RG2cumsum)) %>% -->
-<!--   mutate(year = as.factor(year)) %>% -->
-<!--   pivot_longer(!c(year, source), names_to = 'flow_type', values_to = 'flow_cms') -->
-
-<!-- ggplot(gw_maxcumsum, aes(x = flow_type, y = flow_cms, fill = source)) + -->
-<!--   geom_boxplot(position = position_dodge(1)) +  -->
-<!--   geom_point(position=position_jitterdodge(),alpha=0.3) + -->
-<!--   ggtitle('Max annual cumulative sums') -->
-
-<!-- ggplot(gw_maxcumsum, aes(x = flow_type, y = flow_cms, fill = source)) + -->
-<!--   geom_boxplot(position = position_dodge(1)) + -->
-<!--   geom_point(position=position_jitterdodge(),alpha=0.3) + -->
-<!--   #geom_point(aes(color = source)) + -->
-<!--   facet_wrap(~flow_type, scales = 'free') + -->
-<!--   ggtitle('Max annual cumulative sums') -->
-
-<!-- ``` -->
-
-<!-- ### RD and RG by season -->
-
-<!-- ```{r flow season, echo = F, fig.width = 12, fig.asp = 0.75, out.width = "100%"} -->
-
-<!-- #group by season and get max sums by season -->
-<!-- flow_season <- gw %>% -->
-<!--   dplyr::select(RD1cumsum, RD2cumsum, RG1cumsum, RG2cumsum, date, year, source) %>% -->
-<!--   mutate(month = month(date)) %>% -->
-<!--   mutate(season = case_when(month %in% c(3,4,5,6) ~ 'snowmelt', -->
-<!--                             month %in% c(7,8,9,10) ~ 'monsoon', -->
-<!--                             month %in% c(11,12,1,2) ~ 'baseflow')) %>% -->
-<!--   group_by(source, year, season) %>% -->
-<!--   summarize(yr_season_RD1 = max(RD1cumsum), -->
-<!--             yr_season_RD2 = max(RD2cumsum), -->
-<!--             yr_season_RG1 = max(RG1cumsum), -->
-<!--             yr_season_RG2 = max(RG2cumsum)) %>% -->
-<!--             pivot_longer(!c(year, source, season), names_to = 'flow_type', values_to = 'flow_cms') -->
-
-<!-- flow_season %>% -->
-<!--   ggplot(aes(x = flow_type, y = flow_cms, fill = source)) + -->
-<!--   geom_boxplot(position = position_dodge(1)) + -->
-<!--   geom_point(position=position_jitterdodge(),alpha=0.3) + -->
-<!--   #geom_point(aes(color = source)) + -->
-<!--   facet_wrap(~season, scales = 'free') + -->
-<!--   ggtitle('Max annual season cumulative sums') + -->
-<!--   theme_bw() + -->
-<!--   theme(axis.text.x = element_text(angle = 45, hjust = 1)) + -->
-<!--   theme(text = element_text(size = 20))  -->
-
-<!-- flow_season %>% -->
-<!--   ggplot(aes(x = flow_type, y = flow_cms, fill = source)) + -->
-<!--   geom_boxplot(position = position_dodge(1)) + -->
-<!--   geom_point(position=position_jitterdodge(),alpha=0.3) + -->
-<!--   #geom_point(aes(color = source)) + -->
-<!--   facet_wrap(~season + flow_type, scales = 'free') + -->
-<!--   ggtitle('Max annual season cumulative sums') + -->
-<!--   theme_bw() + -->
-<!--   theme(text = element_text(size = 20)) -->
-
-<!-- ``` -->
-
-<!-- # HRU results -->
-
-<!-- ## HRU Map -->
-
-<!-- ```{r map, echo = F} -->
-
-<!-- locations <- read_csv(here('data/GIS', 'fourmile_sensors.csv')) -->
-
-<!-- hrus <- st_read(here('data/GIS', 'hrus_final.shp')) -->
-
-<!-- locations <- locations %>% -->
-<!--   st_as_sf(., coords=c('y','x'), crs = 4326) -->
-
-<!-- mapviewOptions(basemaps = c("Esri.WorldShadedRelief", "OpenStreetMap.DE"), -->
-<!--                layers.control.pos = "topright") -->
-
-<!-- mapview(locations, zcol = 'type') + mapview(hrus) -->
-
-<!-- ``` -->
-
-<!-- ## Niwot and HRU7 -->
-
-<!-- ### SWE and precip -->
-
-<!-- ```{r niwot, echo = F, fig.width = 14, fig.asp = 1, out.width = "100%"} -->
-<!-- library(snotelr) -->
-
-<!-- niwot_snotel <- snotel_download(site_id = 663, internal = T) -->
-
-<!-- niwot_snotel <- niwot_snotel %>% -->
-<!--   dplyr::select(date, snow_water_equivalent, precipitation) %>% -->
-<!--   mutate(date = as.Date(date)) %>% -->
-<!--   rename(swe_mm_snotel = snow_water_equivalent, -->
-<!--          precip_mm_snotel = precipitation) %>% -->
-<!--   #mutate(swe_mm_snotel = swe_mm_snotel*25.4, -->
-<!--          #precip_mm_snotel = precip_mm_snotel*25.4) %>% -->
-<!--   filter(date > '2010-12-31' & date < '2020-10-01') -->
-
-<!-- hru7_grid <- read_csv(here('HRU_output/HRU_7_grid.csv')) %>% -->
-<!--   dplyr::select(date, precip_mm, swe_mm) %>% -->
-<!--   rename(precip_mm_hrugrid = precip_mm, -->
-<!--          swe_mm_hrugrid = swe_mm) -->
-
-<!-- hru7_statn <- read_csv(here('HRU_output/HRU_7_statn.csv')) %>% -->
-<!--   dplyr::select(date, precip_mm, swe_mm) %>% -->
-<!--   rename(precip_mm_hrustatn = precip_mm, -->
-<!--          swe_mm_hrustatn = swe_mm) -->
-
-<!-- niwot <- niwot_snotel %>% -->
-<!--   left_join(hru7_grid, by = 'date') %>% -->
-<!--   left_join(hru7_statn, by = 'date') -->
-
-<!-- # look at swe -->
-<!-- niwot_swe <- niwot %>% -->
-<!--   dplyr::select(date, swe_mm_snotel, swe_mm_hrugrid, swe_mm_hrustatn) -->
-
-<!-- kable(niwot_swe) %>% -->
-<!--   kable_styling(full_width = F) %>%  -->
-<!--   scroll_box(width = "100%", height = "500px") -->
-
-<!-- # cumulative swe -->
-<!-- niwot_swe2 <- niwot_swe %>% -->
-<!--   mutate(year = year(date)) %>% -->
-<!--   pivot_longer(!c(date,year), names_to = 'source', values_to = 'swe_mm') %>% -->
-<!--   group_by(year, source) %>% -->
-<!--   mutate(swe_cumsum_mm = cumsum(swe_mm)) -->
-
-<!-- cum_swe_niwot <- ggplot(niwot_swe2, aes(date, swe_cumsum_mm, color = source)) + -->
-<!--   geom_line(size =1) + -->
-<!--   scale_x_date(labels = date_format("%b")) + -->
-<!--   facet_wrap(~year, scales = 'free', ncol=2) + -->
-<!--   theme(text = element_text(size = 20))   -->
-
-<!-- cum_swe_niwot -->
-
-<!-- #look at precip -->
-<!-- niwot_p <- niwot %>% -->
-<!--   dplyr::select(date, precip_mm_snotel, precip_mm_hrugrid, precip_mm_hrustatn) -->
-
-<!-- kable(niwot_p) %>% -->
-<!--   kable_styling(full_width = F) %>%  -->
-<!--   scroll_box(width = "100%", height = "500px") -->
-
-<!-- # cumulative precip -->
-<!-- niwot_p2 <- niwot_p %>% -->
-<!--   mutate(year = year(date)) %>% -->
-<!--   pivot_longer(!c(date,year), names_to = 'source', values_to = 'precip_mm') %>% -->
-<!--   group_by(year, source) %>% -->
-<!--   mutate(p_cumsum_mm = cumsum(precip_mm)) -->
-
-<!-- cum_precip_niwot <- ggplot(niwot_p2, aes(date, p_cumsum_mm, color = source)) + -->
-<!--   geom_line(size=1) + -->
-<!--   scale_x_date(labels = date_format("%b")) + -->
-<!--   facet_wrap(~year, scales = 'free', ncol=2) + -->
-<!--   theme(text = element_text(size = 20))   -->
-
-<!-- cum_precip_niwot -->
-
-<!-- ``` -->
-
-<!-- ### ET -->
-
-<!-- ```{r ET, echo = F} -->
-
-<!-- niwot_et <- read_csv(here('HRU_output/Niwot_daily_et.csv')) %>% -->
-<!--   filter(year > 2010) %>% -->
-<!--   mutate(date = make_date(year = year, month = month, day = day)) %>% -->
-<!--   dplyr::select(date, et) %>% -->
-<!--   rename(et_niwot = et) -->
-
-<!-- hru7_grid <- read_csv(here('HRU_output/HRU_7_grid.csv')) %>% -->
-<!--   dplyr::select(date, AET_mm) %>% -->
-<!--   rename(et_hru7grid = AET_mm) -->
-
-<!-- hru7_statn <- read_csv(here('HRU_output/HRU_7_statn.csv')) %>% -->
-<!--   dplyr::select(date, AET_mm) %>% -->
-<!--   rename(et_hru7statn = AET_mm) -->
-
-<!-- niwot_et_compare <- niwot_et %>% -->
-<!--   left_join(hru7_grid, by = 'date') %>% -->
-<!--   left_join(hru7_statn, by = 'date') %>% -->
-<!--   mutate(year = year(date)) %>% -->
-<!--   filter(year < 2021) %>%  -->
-<!--   pivot_longer(!c(date, year), names_to= 'source', values_to = 'et_mm') %>% -->
-<!--   mutate(year = as.factor(year)) -->
-
-<!-- #plot ET by year -->
-<!-- plot_ET <- function(calyear) { -->
-<!--   {niwot_et_compare %>% -->
-<!--     filter(year == calyear) %>% -->
-<!--     ggplot(aes(x = date, -->
-<!--                y = et_mm, color = source)) + -->
-<!--     geom_line(size=1) + -->
-<!--     ggtitle(calyear) + -->
-<!--     ylab('ET (mm/day)') + -->
-<!--     theme_bw() + -->
-<!--     theme(axis.text.x = element_text(angle = 45, hjust=1))} %>% -->
-<!--     ggplotly() -->
-<!-- } -->
-
-<!-- name <- levels(niwot_et_compare$year) -->
-
-<!-- ET_plots <- lapply(name, plot_ET) -->
-
-<!-- htmltools::tagList(ET_plots) -->
-
-<!-- ET_plots -->
-
-<!-- # 1:1 scatter plots for Niwot vs grid and Niwot vs station -->
-<!-- niwot_et_scatter <- niwot_et_compare %>% -->
-<!--   filter(et_mm > 0) -->
-
-<!-- # Niwot vs grid -->
-<!-- et_grid_obs <- niwot_et_scatter %>% -->
-<!--   filter(source == c('et_niwot','et_hru7grid')) %>% -->
-<!--   pivot_wider(names_from = 'source', values_from = 'et_mm') -->
-
-<!-- #scatter of grid vs niwot -->
-<!-- et_scatter_grid_obs <- ggplot(et_grid_obs, aes(x = et_niwot, y = et_hru7grid)) + -->
-<!--   geom_point() + -->
-<!--   geom_abline(intercept = 0, slope = 1, size=1, color='red') +  -->
-<!--   ggtitle('Niwot ET vs. HRU7 grid ET') -->
-
-<!-- et_scatter_grid_obs -->
-
-<!-- # Niwot vs statn inputs -->
-<!-- et_statn_obs <- niwot_et_scatter %>% -->
-<!--   filter(source == c('et_niwot','et_hru7statn')) %>% -->
-<!--   pivot_wider(names_from = 'source', values_from = 'et_mm') -->
-
-<!-- #scatter of grid vs niwot -->
-<!-- et_scatter_statn_obs <- ggplot(et_statn_obs, aes(x = et_niwot, y = et_hru7statn)) + -->
-<!--   geom_point() + -->
-<!--   geom_abline(intercept = 0, slope = 1, size=1, color='red') +  -->
-<!--   ggtitle('Niwot ET vs. HRU7 station ET') -->
-
-<!-- et_scatter_statn_obs -->
-
-<!-- ``` -->
-
-<!-- ## Tmean for HRUs 7, 9, 22, 36 -->
-
-<!-- ```{r hru7 temp, echo = F, fig.width = 14, fig.asp = 1, out.width = "100%"} -->
-
-<!-- tmean7_grid <- read_csv(here('HRU_output/HRU_7_grid.csv')) %>% -->
-<!--   dplyr::select(date, tmean) %>% -->
-<!--   rename(t7_grid = tmean) -->
-
-<!-- tmean7_statn <- read_csv(here('HRU_output/HRU_7_statn.csv')) %>% -->
-<!--   dplyr::select(date, tmean) %>% -->
-<!--   rename(t7_statn = tmean) -->
-
-<!-- tmean9_grid <- read_csv(here('HRU_output/HRU_9_grid.csv')) %>% -->
-<!--   dplyr::select(date, tmean) %>% -->
-<!--   rename(t9_grid = tmean) -->
-
-<!-- tmean9_statn <- read_csv(here('HRU_output/HRU_9_statn.csv')) %>% -->
-<!--   dplyr::select(date, tmean) %>% -->
-<!--   rename(t9_statn = tmean) -->
-
-<!-- tmean22_grid <- read_csv(here('HRU_output/HRU_22_grid.csv')) %>% -->
-<!--   dplyr::select(date, tmean) %>% -->
-<!--   rename(t22_grid = tmean) -->
-
-<!-- tmean22_statn <- read_csv(here('HRU_output/HRU_22_statn.csv')) %>% -->
-<!--   dplyr::select(date, tmean) %>% -->
-<!--   rename(t22_statn = tmean) -->
-
-<!-- tmean36_grid <- read_csv(here('HRU_output/HRU_36_grid.csv')) %>% -->
-<!--   dplyr::select(date, tmean) %>% -->
-<!--   rename(t36_grid = tmean) -->
-
-<!-- tmean36_statn <- read_csv(here('HRU_output/HRU_36_statn.csv')) %>% -->
-<!--   dplyr::select(date, tmean) %>% -->
-<!--   rename(t36_statn = tmean) -->
-
-<!-- tmean_hrus <- list(tmean7_grid, tmean7_statn, tmean9_grid,  -->
-<!--      tmean9_statn, tmean22_grid, tmean22_statn, -->
-<!--      tmean36_grid, tmean36_statn) -->
-
-<!-- t_hrus <- tmean_hrus %>% reduce(left_join, by='date') -->
-
-<!-- t_hrus <- t_hrus %>% -->
-<!--   mutate(year = year(date)) %>% -->
-<!--   mutate(t7_diff = t7_statn - t7_grid, -->
-<!--          t9_diff = t9_statn - t9_grid, -->
-<!--          t22_diff = t22_statn - t22_grid, -->
-<!--          t36_diff = t36_statn - t36_grid) %>% -->
-<!--   group_by(year) %>% -->
-<!--   mutate(t7_cumdiff = cumsum(t7_diff), -->
-<!--          t9_cumdiff = cumsum(t9_diff), -->
-<!--          t22_cumdiff = cumsum(t22_diff), -->
-<!--          t36_cumdiff = cumsum(t36_diff)) -->
-
-<!-- tmean_cumdiff_plot <- ggplot(t_hrus, aes(x = date)) + -->
-<!--   geom_line(aes(y = t7_cumdiff, color = 'HRU7'), size =1) +  -->
-<!--   geom_line(aes(y = t9_cumdiff, color = 'HRU9'), size =1) +  -->
-<!--   geom_line(aes(y = t22_cumdiff, color = 'HRU22'), size =1) +  -->
-<!--   geom_line(aes(y = t36_cumdiff, color = 'HRU36'), size =1) +  -->
-<!--   facet_wrap(~year, scales = 'free',ncol=2) + -->
-<!--   scale_x_date(labels = date_format("%b")) + -->
-<!--   labs(y = 'Tmean cumulative difference (deg C)') + -->
-<!--   ggtitle('Tmean station and grid cumulative difference (Station - Grid)') + -->
-<!--   theme(text = element_text(size = 20))   -->
-
-<!-- tmean_cumdiff_plot -->
-
-<!-- ``` -->
-
-<!-- ## Tmean difference -->
-
-<!-- 2011-2020 average of daily station-grid Tmean  -->
-
-<!-- ```{r cumulative tmean for HRUs, echo = F} -->
-<!-- #grid first -->
-<!-- setwd(here("HRU_output/grid")) -->
-
-<!-- read_ages_grid <- function(dataframe){ -->
-<!--   read_csv(dataframe, skip = 3) %>% -->
-<!--   slice(3:n()) %>% -->
-<!--   dplyr::select(-starts_with('@'), -->
-<!--                 -1) %>% -->
-<!--   mutate(time = ymd(time)) %>% -->
-<!--   mutate_if(is.character, as.numeric) %>% -->
-<!--   mutate(source = 'grid') -->
-
-<!-- } -->
-
-<!-- #pull in all filenames with HRU in the name -->
-<!-- filenames <- list.files(".", pattern="HRU", full.names=F) -->
-
-<!-- #read all the csvs using read_ages function -->
-<!-- dataframes <- lapply(filenames, read_ages_grid)  -->
-
-<!-- #name all the csvs based on first 6 characters -->
-<!-- names(dataframes) <- substr(filenames, 1, 6) -->
-
-<!-- #bind all and make 1 df -->
-<!-- hru_grids <- dataframes %>% -->
-<!--   bind_rows()  -->
-
-<!-- #statn next -->
-<!-- setwd(here("HRU_output/statn")) -->
-
-<!-- read_ages_statn <- function(dataframe){ -->
-<!--   read_csv(dataframe, skip = 3) %>% -->
-<!--   slice(3:n()) %>% -->
-<!--   dplyr::select(-starts_with('@'), -->
-<!--                 -1) %>% -->
-<!--   mutate(time = ymd(time)) %>% -->
-<!--   mutate_if(is.character, as.numeric) %>% -->
-<!--   mutate(source = 'statn') -->
-
-<!-- } -->
-
-<!-- #pull in all filenames with HRU in the name -->
-<!-- filenames <- list.files(".", pattern="HRU", full.names=F) -->
-
-<!-- #read all the csvs using read_ages function -->
-<!-- dataframes <- lapply(filenames, read_ages_statn)  -->
-
-<!-- #name all the csvs based on first 6 characters -->
-<!-- names(dataframes) <- substr(filenames, 1, 6) -->
-
-<!-- #bind all and make 1 df -->
-<!-- hru_statn <- dataframes %>% -->
-<!--   bind_rows()  -->
-
-<!-- #get rid of a bunch of data -->
-<!-- hru_grid_tmean <- hru_grids %>% -->
-<!--   dplyr::select(c(time, ID, tmean)) %>% -->
-<!--   rename(tmean_grid = tmean)  %>% -->
-<!--   group_by(ID) %>% -->
-<!--   summarize(tmean_all_grid = mean(tmean_grid)) -->
-
-<!-- hru_statn_tmean <- hru_statn %>% -->
-<!--   dplyr::select(c(time, ID, tmean)) %>% -->
-<!--   rename(tmean_statn = tmean) %>% -->
-<!--   group_by(ID) %>% -->
-<!--   summarize(tmean_all_statn = mean(tmean_statn)) -->
-
-<!-- tmean_hrus <- left_join(hru_grid_tmean, hru_statn_tmean, by = c('ID')) %>% -->
-<!--   mutate(diff = tmean_all_statn - tmean_all_grid) %>% -->
-<!--   rename(value = ID) -->
-
-<!-- hrus_map_tmean <- left_join(hrus, tmean_hrus, by = 'value') -->
-
-<!-- tmap_mode('view') -->
-
-<!-- locations_t <- locations %>%  -->
-<!--   dplyr::filter(name %in% c('Gordon_South', 'Gordon_North', -->
-<!--                         'Betasso', 'Niwot_Snotel', -->
-<!--                         'University Camp SNTL')) -->
-
-<!-- tm_shape(hrus_map_tmean) + -->
-<!--   tm_polygons('diff', id = 'value', -->
-<!--               breaks = c(-6,-4,-2,0,2,4,6)) + -->
-<!-- tm_shape(locations_t) + -->
-<!--   tm_symbols(col='blue', size=4) -->
-
-<!-- ``` -->
-
-<!-- ## Tmax difference -->
-
-<!-- ```{r tmax, echo = F} -->
-
-<!-- tmax_grid <- read_csv(here('HRU_output/reg_tmaxAll_prism.csv'))%>%  -->
-<!--   pivot_longer(cols = `3`:`19`, -->
-<!--                names_to = 'value',  -->
-<!--                values_to = 'tmax_grid') %>% -->
-<!--   mutate(time = dmy(time)) %>% -->
-<!--   group_by(value) %>% -->
-<!--   summarize(Tmax_mean_grid = mean(tmax_grid)) -->
-
-<!-- tmax_statn <- read_csv(here('HRU_output/reg_tmaxAll.csv')) %>%  -->
-<!--   pivot_longer(cols = `3`:`19`, -->
-<!--                names_to = 'value',  -->
-<!--                values_to = 'tmax_statn') %>% -->
-<!--   mutate(time = dmy(time)) %>% -->
-<!--   group_by(value) %>% -->
-<!--   summarize(Tmax_mean_statn = mean(tmax_statn)) -->
-
-<!-- tmax_hrus <- left_join(tmax_grid, tmax_statn, by = c('value')) %>% -->
-<!--   mutate(diff = Tmax_mean_statn - Tmax_mean_grid, -->
-<!--          value = as.numeric(value)) -->
-
-<!-- hrus_map_tmax <- left_join(hrus, tmax_hrus, by = 'value') -->
-
-<!-- tmap_mode('view') -->
-
-<!-- tm_shape(hrus_map_tmax) + -->
-<!--   tm_polygons('diff', id = 'value', -->
-<!--               breaks = c(-6,-4,-2,0,2,4,6)) + -->
-<!-- tm_shape(locations_t) + -->
-<!--   tm_symbols(col='blue', size=4) -->
-
-<!-- ``` -->
-
-<!-- ## Tmax monthly average -->
-
-<!-- ```{r tmax month, echo = F} -->
-
-<!-- tmax_grid_mo <- read_csv(here('HRU_output/reg_tmaxAll_prism.csv')) %>%  -->
-<!--   pivot_longer(cols = `3`:`19`, -->
-<!--                names_to = 'value',  -->
-<!--                values_to = 'tmax_grid') %>% -->
-<!--   mutate(time = dmy(time), -->
-<!--          month = month(time)) %>% -->
-<!--   filter(month %in% c(3:6)) %>% -->
-<!--   group_by(value, month) %>% -->
-<!--   summarize(avg_tmax_grid = mean(tmax_grid)) -->
-
-<!-- tmax_statn_mo <- read_csv(here('HRU_output/reg_tmaxAll.csv')) %>%  -->
-<!--   pivot_longer(cols = `3`:`19`, -->
-<!--                names_to = 'value',  -->
-<!--                values_to = 'tmax_statn') %>% -->
-<!--   mutate(time = dmy(time), -->
-<!--          month = month(time)) %>% -->
-<!--   filter(month %in% c(3:6)) %>% -->
-<!--   group_by(value, month) %>% -->
-<!--   summarize(avg_tmax_statn = mean(tmax_statn)) -->
-
-<!-- tmax_hrus_mo <- left_join(tmax_grid_mo, tmax_statn_mo, by = c('value', 'month')) %>% -->
-<!--   mutate(mo_tmax_diff = avg_tmax_statn - avg_tmax_grid, -->
-<!--          value = as.numeric(value)) -->
-
-<!-- tmap_mode('plot') -->
-
-<!-- #march -->
-<!-- tmax_hrus_mar<- tmax_hrus_mo %>% -->
-<!--   filter(month == 3) -->
-
-<!-- hrus_map_tmax_mar <- left_join(hrus, tmax_hrus_mar, by = 'value') -->
-
-<!-- mar_tmax <- tm_shape(hrus_map_tmax_mar) + -->
-<!--   #tm_polygons('mo_tmax_diff', id = 'value') + -->
-<!--   tm_fill('mo_tmax_diff', id = 'value', -->
-<!--           breaks = c(-6,-4,-2,0,2,4,6)) + -->
-<!--   tm_borders() + -->
-<!--   tm_shape(locations_t) + -->
-<!--   tm_symbols(col='blue', size = 0.25) + -->
-<!--   tm_layout(title = 'March avg tmax', -->
-<!--             legend.outside = T) -->
-
-<!-- #april -->
-<!-- tmax_hrus_apr<- tmax_hrus_mo %>% -->
-<!--   filter(month == 4) -->
-
-<!-- hrus_map_tmax_apr <- left_join(hrus, tmax_hrus_apr, by = 'value') -->
-
-<!-- apr_tmax <- tm_shape(hrus_map_tmax_apr) + -->
-<!--   tm_fill('mo_tmax_diff', id = 'value', -->
-<!--           breaks = c(-6,-4,-2,0,2,4,6)) + -->
-<!--   tm_borders() + -->
-<!--   tm_shape(locations_t) + -->
-<!--   tm_symbols(col='blue', size = 0.25) + -->
-<!--   tm_layout(title = 'April avg tmax', -->
-<!--             legend.outside = T) -->
-
-<!-- #may -->
-<!-- tmax_hrus_may<- tmax_hrus_mo %>% -->
-<!--   filter(month == 5) -->
-
-<!-- hrus_map_tmax_may <- left_join(hrus, tmax_hrus_may, by = 'value') -->
-
-<!-- may_tmax <- tm_shape(hrus_map_tmax_may) + -->
-<!--   tm_fill('mo_tmax_diff', id = 'value', -->
-<!--          breaks = c(-6,-4,-2,0,2,4,6)) + -->
-<!--   tm_borders() + -->
-<!-- tm_shape(locations_t) + -->
-<!--   tm_symbols(col='blue', size = 0.25) + -->
-<!--   tm_layout(title = 'May avg tmax', -->
-<!--             legend.outside = T) -->
-
-<!-- #june -->
-<!-- tmax_hrus_jun<- tmax_hrus_mo %>% -->
-<!--   filter(month == 6) -->
-
-<!-- hrus_map_tmax_jun <- left_join(hrus, tmax_hrus_jun, by = 'value') -->
-
-<!-- jun_tmax <- tm_shape(hrus_map_tmax_jun) + -->
-<!--   tm_fill('mo_tmax_diff', id = 'value', -->
-<!--          breaks = c(-6,-4,-2,0,2,4,6)) + -->
-<!--   tm_borders() + -->
-<!-- tm_shape(locations_t) + -->
-<!--   tm_symbols(col='blue', size = 0.25) + -->
-<!--   tm_layout(title = 'June avg tmax', -->
-<!--             legend.outside = T) -->
-
-<!-- tmap_arrange(mar_tmax, apr_tmax, may_tmax, jun_tmax) -->
-
-<!-- ``` -->
-
-<!-- ## Tmin difference -->
-
-<!-- ```{r tmin, echo = F} -->
-
-<!-- tmin_grid <- read_csv(here('HRU_output/reg_tminAll_prism.csv')) %>%  -->
-<!--   pivot_longer(cols = `3`:`19`, -->
-<!--                names_to = 'value',  -->
-<!--                values_to = 'tmin_grid') %>% -->
-<!--   mutate(time = dmy(time)) %>% -->
-<!--   group_by(value) %>% -->
-<!--   summarize(Tmin_mean_grid = mean(tmin_grid)) -->
-
-<!-- tmin_statn <- read_csv(here('HRU_output/reg_tminAll.csv')) %>%  -->
-<!--   pivot_longer(cols = `3`:`19`, -->
-<!--                names_to = 'value',  -->
-<!--                values_to = 'tmin_statn') %>% -->
-<!--   mutate(time = dmy(time)) %>% -->
-<!--   group_by(value) %>% -->
-<!--   summarize(Tmin_mean_statn = mean(tmin_statn)) -->
-
-<!-- tmin_hrus <- left_join(tmin_grid, tmin_statn, by = c('value')) %>% -->
-<!--   mutate(diff = Tmin_mean_statn - Tmin_mean_grid, -->
-<!--          value = as.numeric(value)) -->
-
-<!-- hrus_map_tmin <- left_join(hrus, tmin_hrus, by = 'value') -->
-
-<!-- tmap_mode('view') -->
-
-<!-- tm_shape(hrus_map_tmin) + -->
-<!--   tm_polygons('diff', id = 'value', -->
-<!--               breaks = c(-6,-4,-2,0,2,4,6)) + -->
-<!-- tm_shape(locations_t) + -->
-<!--   tm_symbols(col='blue', size=4) -->
-
-<!-- ``` -->
-
-<!-- ## Tmin monthly average -->
-
-<!-- ```{r tmin month, echo = F} -->
-<!-- tmin_grid_mo <- read_csv(here('HRU_output/reg_tminAll_prism.csv')) %>%  -->
-<!--   pivot_longer(cols = `3`:`19`, -->
-<!--                names_to = 'value',  -->
-<!--                values_to = 'tmin_grid') %>% -->
-<!--   mutate(time = dmy(time), -->
-<!--          month = month(time)) %>% -->
-<!--   filter(month %in% c(3:6)) %>% -->
-<!--   group_by(value, month) %>% -->
-<!--   summarize(avg_tmin_grid = mean(tmin_grid)) -->
-
-<!-- tmin_statn_mo <- read_csv(here('HRU_output/reg_tminAll.csv')) %>%  -->
-<!--   pivot_longer(cols = `3`:`19`, -->
-<!--                names_to = 'value',  -->
-<!--                values_to = 'tmin_statn') %>% -->
-<!--   mutate(time = dmy(time), -->
-<!--          month = month(time)) %>% -->
-<!--   filter(month %in% c(3:6)) %>% -->
-<!--   group_by(value, month) %>% -->
-<!--   summarize(avg_tmin_statn = mean(tmin_statn)) -->
-
-<!-- tmin_hrus_mo <- left_join(tmin_grid_mo, tmin_statn_mo, by = c('value', 'month')) %>% -->
-<!--   mutate(mo_tmin_diff = avg_tmin_statn - avg_tmin_grid, -->
-<!--          value = as.numeric(value)) -->
-
-<!-- tmap_mode('plot') -->
-
-<!-- #march -->
-<!-- tmin_hrus_mar<- tmin_hrus_mo %>% -->
-<!--   filter(month == 3) -->
-
-<!-- hrus_map_tmin_mar <- left_join(hrus, tmin_hrus_mar, by = 'value') -->
-
-<!-- mar_tmin <- tm_shape(hrus_map_tmin_mar) + -->
-<!--   #tm_polygons('mo_tmin_diff', id = 'value') + -->
-<!--   tm_fill('mo_tmin_diff', id = 'value', -->
-<!--           breaks = c(-5,-2.5,0,2.5,5)) + -->
-<!--   tm_borders() + -->
-<!--   tm_shape(locations_t) + -->
-<!--   tm_symbols(col='blue', size = 0.25) + -->
-<!--   tm_layout(title = 'March avg tmin', -->
-<!--             legend.outside = T) -->
-
-<!-- #april -->
-<!-- tmin_hrus_apr<- tmin_hrus_mo %>% -->
-<!--   filter(month == 4) -->
-
-<!-- hrus_map_tmin_apr <- left_join(hrus, tmin_hrus_apr, by = 'value') -->
-
-<!-- apr_tmin <- tm_shape(hrus_map_tmin_apr) + -->
-<!--   tm_fill('mo_tmin_diff', id = 'value', -->
-<!--           breaks = c(-5,-2.5,0,2.5,5)) + -->
-<!--   tm_borders() + -->
-<!--   tm_shape(locations_t) + -->
-<!--   tm_symbols(col='blue', size = 0.25) + -->
-<!--   tm_layout(title = 'April avg tmin', -->
-<!--             legend.outside = T) -->
-
-<!-- #may -->
-<!-- tmin_hrus_may<- tmin_hrus_mo %>% -->
-<!--   filter(month == 5) -->
-
-<!-- hrus_map_tmin_may <- left_join(hrus, tmin_hrus_may, by = 'value') -->
-
-<!-- may_tmin <- tm_shape(hrus_map_tmin_may) + -->
-<!--   tm_fill('mo_tmin_diff', id = 'value', -->
-<!--          breaks = c(-5,-2.5,0,2.5,5)) + -->
-<!--   tm_borders() + -->
-<!-- tm_shape(locations_t) + -->
-<!--   tm_symbols(col='blue', size = 0.25) + -->
-<!--   tm_layout(title = 'May avg tmin', -->
-<!--             legend.outside = T) -->
-
-<!-- #june -->
-<!-- tmin_hrus_jun<- tmin_hrus_mo %>% -->
-<!--   filter(month == 6) -->
-
-<!-- hrus_map_tmin_jun <- left_join(hrus, tmin_hrus_jun, by = 'value') -->
-
-<!-- jun_tmin <- tm_shape(hrus_map_tmin_jun) + -->
-<!--   tm_fill('mo_tmin_diff', id = 'value', -->
-<!--           breaks = c(-5,-2.5,0,2.5,5)) + -->
-<!--   tm_borders() + -->
-<!-- tm_shape(locations_t) + -->
-<!--   tm_symbols(col='blue', size = 0.25) + -->
-<!--   tm_layout(title = 'June avg tmin', -->
-<!--             legend.outside = T) -->
-
-<!-- tmap_arrange(mar_tmin, apr_tmin, may_tmin, jun_tmin) -->
-
-<!-- ``` -->
-
-<!-- ## Cumulative Precip difference -->
-
-<!-- 2011-2020 average of daily station-grid precip for DOY 365 (or 366) -->
-
-<!-- ```{r cum precip, echo = F} -->
-<!-- #get rid of a bunch of data -->
-<!-- hru_grid_precip <- hru_grids %>% -->
-<!--   dplyr::select(c(time, ID, precip)) %>% -->
-<!--   rename(precip_grid = precip) -->
-
-<!-- hru_statn_precip <- hru_statn %>% -->
-<!--   dplyr::select(c(time, ID, precip)) %>% -->
-<!--   rename(precip_statn = precip) -->
-
-<!-- precip_hrus <- left_join(hru_grid_precip, hru_statn_precip, by = c('time', 'ID')) %>% -->
-<!--   mutate(diff = precip_statn - precip_grid, -->
-<!--          year = year(time)) %>% -->
-<!--   group_by(year, ID) %>% -->
-<!--   mutate(total_diff = cumsum(diff)) %>%  -->
-<!--   filter(time == max(time)) %>% -->
-<!--   group_by(ID) %>% -->
-<!--   summarize(precip_avg_cumdiff = mean(total_diff)) %>% -->
-<!--   rename(value = ID) -->
-
-<!-- hrus_map_precip <- left_join(hrus, precip_hrus, by = 'value') -->
-
-<!-- tmap_mode('view') -->
-
-<!-- locations_p <- locations %>% -->
-<!--   filter(type == 'precip') -->
-
-<!-- tm_shape(hrus_map_precip) + -->
-<!--   tm_polygons('precip_avg_cumdiff', midpoint = NA, palette = 'YlGnBu', id = 'value') + -->
-<!-- tm_shape(locations_p) + -->
-<!--   tm_symbols(col='blue', size=4) -->
-
-<!-- ``` -->
-
-<!-- ```{r relative p, echo = F} -->
-
-<!-- # reg_p <- read_csv(here('HRU_output/reg_precipAll.csv'), -->
-<!-- #                       skip = 21) %>% -->
-<!-- #   dplyr::select(-starts_with('@')) %>% -->
-<!-- #   mutate(time = dmy(time)) %>% -->
-<!-- #   summarize(across(`3`:`19`, ~ mean(.))) %>% -->
-<!-- #   pivot_longer(cols = `3`:`19`, -->
-<!-- #                names_to = 'value',  -->
-<!-- #                values_to = 'precip_avg') %>% -->
-<!-- #   mutate(value = as.numeric(value)) -->
-<!-- #  -->
-<!-- #  -->
-<!-- # hrus_map_precip <- left_join(hrus_map_precip, reg_p, by = 'value')  -->
-<!-- #  -->
-<!-- # hrus_map_precip <- hrus_map_precip %>% -->
-<!-- #   mutate(relative_avgcum_diff = precip_avg_cumdiff / precip_avg) -->
-<!-- #  -->
-<!-- # tm_shape(hrus_map_precip) + -->
-<!-- #   tm_polygons('relative_avgcum_diff', midpoint = NA, palette = 'YlGnBu', id = 'value') + -->
-<!-- # tm_shape(locations_p) + -->
-<!-- #   tm_symbols(col='blue', size=4) -->
-
-<!-- ``` -->
-
-<!-- ## Solar radiation difference -->
-
-<!-- 2011-2020 average of daily station-grid solar rad -->
-
-<!-- ```{r cum sol rad, echo = F} -->
-
-<!-- #get rid of a bunch of data -->
-<!-- hru_grid_solrad <- hru_grids %>% -->
-<!--   dplyr::select(c(time, ID, solRad)) %>% -->
-<!--   rename(solrad_grid = solRad)  %>% -->
-<!--   group_by(ID) %>% -->
-<!--   summarize(solrad_all_grid = mean(solrad_grid)) -->
-
-<!-- hru_statn_solrad <- hru_statn %>% -->
-<!--   dplyr::select(c(time, ID, solRad)) %>% -->
-<!--   rename(solrad_statn = solRad) %>% -->
-<!--   group_by(ID) %>% -->
-<!--   summarize(solrad_all_statn = mean(solrad_statn)) -->
-
-<!-- solrad_hrus <- left_join(hru_grid_solrad, hru_statn_solrad, by = c('ID')) %>% -->
-<!--   mutate(diff = solrad_all_statn - solrad_all_grid) %>% -->
-<!--   rename(value = ID) -->
-
-<!-- hrus_map_solrad <- left_join(hrus, solrad_hrus, by = 'value') -->
-
-<!-- tmap_mode('view') -->
-
-<!-- locations_solrad <- locations %>%  -->
-<!--   dplyr::filter(name %in% c('Gordon_South', -->
-<!--                         'Betasso', 'Niwot_Snotel')) -->
-
-<!-- tm_shape(hrus_map_solrad) + -->
-<!--   tm_polygons('diff', midpoint = NA, palette = 'YlOrRd', id = 'value') + -->
-<!-- tm_shape(locations_solrad) + -->
-<!--   tm_symbols(col='blue', size=4) -->
-
-<!-- ``` -->
-
-<!-- ## RH difference -->
-
-<!-- ```{r rh, echo = F} -->
-
-<!-- #get rid of a bunch of data -->
-<!-- hru_grid_rh <- hru_grids %>% -->
-<!--   dplyr::select(c(time, ID, rhum)) %>% -->
-<!--   rename(rh_grid = rhum)  %>% -->
-<!--   group_by(ID) %>% -->
-<!--   summarize(rh_all_grid = mean(rh_grid)) -->
-
-<!-- hru_statn_rh <- hru_statn %>% -->
-<!--   dplyr::select(c(time, ID, rhum)) %>% -->
-<!--   rename(rh_statn = rhum) %>% -->
-<!--   group_by(ID) %>% -->
-<!--   summarize(rh_all_statn = mean(rh_statn)) -->
-
-<!-- rh_hrus <- left_join(hru_grid_rh, hru_statn_rh, by = c('ID')) %>% -->
-<!--   mutate(diff = rh_all_statn - rh_all_grid) %>% -->
-<!--   rename(value = ID) -->
-
-<!-- hrus_map_rh <- left_join(hrus, rh_hrus, by = 'value') -->
-
-<!-- tmap_mode('view') -->
-
-<!-- locations_rh <- locations %>%  -->
-<!--   dplyr::filter(name %in% c('Gordon_South', 'Gordon_North', -->
-<!--                         'Betasso', 'Niwot_Snotel')) -->
-
-<!-- tm_shape(hrus_map_rh) + -->
-<!--   tm_polygons('diff', midpoint = NA, id = 'value') + -->
-<!-- tm_shape(locations_rh) + -->
-<!--   tm_symbols(col='blue', size=4) -->
-
-<!-- ``` -->
-
-<!-- ## Average soil sat comparison -->
-
-<!-- ```{r soilsat, echo = F} -->
-
-<!-- #get rid of a bunch of data -->
-<!-- hru_grid_soilsat <- hru_grids %>% -->
-<!--   dplyr::select(c(time, ID, soilSat)) %>% -->
-<!--   rename(soilsat_grid = soilSat)  %>% -->
-<!--   group_by(ID) %>% -->
-<!--   summarize(soilsat_all_grid = mean(soilsat_grid)) -->
-
-<!-- hru_statn_soilsat <- hru_statn %>% -->
-<!--   dplyr::select(c(time, ID, soilSat)) %>% -->
-<!--   rename(soilsat_statn = soilSat) %>% -->
-<!--   group_by(ID) %>% -->
-<!--   summarize(soilsat_all_statn = mean(soilsat_statn)) -->
-
-<!-- soilsat_hrus <- left_join(hru_grid_soilsat, hru_statn_soilsat, by = c('ID')) %>% -->
-<!--   rename(value = ID) -->
-
-<!-- hrus_map_soilsat <- left_join(hrus, soilsat_hrus, by = 'value') -->
-
-<!-- tmap_mode('plot') -->
-
-<!-- soilavg_grid <- tm_shape(hrus_map_soilsat) + -->
-<!--   tm_polygons('soilsat_all_grid', midpoint = NA, id = 'value', -->
-<!--               breaks = c(0.0, 0.05, 0.1, 0.15, 0.2, 0.25, 0.3)) + -->
-<!--   tm_legend(legend.outside = T) + -->
-<!--   tm_layout(main.title = 'Average soil sat') -->
-
-<!-- soilavg_statn <- tm_shape(hrus_map_soilsat) + -->
-<!--   tm_polygons('soilsat_all_statn', midpoint = NA, id = 'value', -->
-<!--               breaks = c(0.0, 0.05, 0.1, 0.15, 0.2, 0.25, 0.3)) + -->
-<!--   tm_legend(legend.outside = T) -->
-
-<!-- tmap_arrange(soilavg_grid, soilavg_statn)  -->
-
-<!-- ``` -->
-
-<!-- ## Average max soil sat comparison -->
-
-<!-- ```{r max soilsat, echo = F} -->
-
-<!-- #get rid of a bunch of data -->
-<!-- hru_grid_soilsat_max <- hru_grids %>% -->
-<!--   dplyr::select(c(time, ID, soilSat)) %>% -->
-<!--   rename(soilsat_grid = soilSat)  %>% -->
-<!--   mutate(year = year(time)) %>%  -->
-<!--   group_by(ID, year) %>% -->
-<!--   summarize(soilsat_yrmax_grid = max(soilsat_grid)) %>% -->
-<!--   summarize(avg_max_grid = mean(soilsat_yrmax_grid)) -->
-
-<!-- hru_statn_soilsat_max <- hru_statn %>% -->
-<!--   dplyr::select(c(time, ID, soilSat)) %>% -->
-<!--   rename(soilsat_statn = soilSat) %>% -->
-<!--   mutate(year = year(time)) %>%  -->
-<!--   group_by(ID, year) %>% -->
-<!--   summarize(soilsat_yrmax_statn = max(soilsat_statn)) %>% -->
-<!--   summarize(avg_max_statn = mean(soilsat_yrmax_statn)) -->
-
-<!-- soilsat_hrus_max <- left_join(hru_grid_soilsat_max, hru_statn_soilsat_max, by = c('ID')) %>% -->
-<!--   rename(value = ID) -->
-
-<!-- hrus_map_soilsat_max <- left_join(hrus, soilsat_hrus_max, by = 'value') -->
-
-<!-- tmap_mode('plot') -->
-
-<!-- soilavg_grid_max <- tm_shape(hrus_map_soilsat_max) + -->
-<!--   tm_polygons('avg_max_grid', midpoint = NA, id = 'value', -->
-<!--               breaks = c(0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.7)) + -->
-<!--   tm_legend(legend.outside = T) + -->
-<!--   tm_layout(main.title = 'Average max soil sat', -->
-<!--             title.position = c('left', 'top')) -->
-
-<!-- soilavg_statn_max <- tm_shape(hrus_map_soilsat_max) + -->
-<!--   tm_polygons('avg_max_statn', midpoint = NA, id = 'value', -->
-<!--               breaks = c(0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.7)) + -->
-<!--   tm_legend(legend.outside = T) -->
-
-<!-- tmap_arrange(soilavg_grid_max, soilavg_statn_max)  -->
-
-<!-- ``` -->
-
-<!-- ## Average ET comparison -->
-
-<!-- ```{r et, echo = F} -->
-<!-- #get rid of a bunch of data -->
-<!-- hru_grid_ET <- hru_grids %>% -->
-<!--   dplyr::select(c(time, ID, actET)) %>% -->
-<!--   rename(ET_grid = actET)  %>% -->
-<!--   group_by(ID) %>% -->
-<!--   summarize(ET_all_grid = mean(ET_grid)) -->
-
-<!-- hru_statn_ET <- hru_statn %>% -->
-<!--   dplyr::select(c(time, ID, actET)) %>% -->
-<!--   rename(ET_statn = actET) %>% -->
-<!--   group_by(ID) %>% -->
-<!--   summarize(ET_all_statn = mean(ET_statn)) -->
-
-<!-- ET_hrus <- left_join(hru_grid_ET, hru_statn_ET, by = c('ID')) %>% -->
-<!--   rename(value = ID) -->
-
-<!-- hrus_map_ET <- left_join(hrus, ET_hrus, by = 'value') -->
-
-<!-- tmap_mode('plot') -->
-
-<!-- ETavg_grid <- tm_shape(hrus_map_ET) + -->
-<!--   tm_polygons('ET_all_grid', midpoint = NA, id = 'value', -->
-<!--               breaks = c(0.2, 0.4, 0.6, 0.8, 1.0, 1.2)) + -->
-<!--   tm_legend(legend.outside = T) + -->
-<!--   tm_layout(main.title = 'Average ET') -->
-
-<!-- ETavg_statn <- tm_shape(hrus_map_ET) + -->
-<!--   tm_polygons('ET_all_statn', midpoint = NA, id = 'value', -->
-<!--              breaks = c(0.2, 0.4, 0.6, 0.8, 1.0, 1.2)) + -->
-<!--   tm_legend(legend.outside = T) -->
-
-<!-- tmap_arrange(ETavg_grid, ETavg_statn) -->
-
-<!-- ``` -->
-
-<!-- ## Average ET difference -->
-
-<!-- ```{r et diff, echo = F} -->
-
-<!-- ET_hrus <- ET_hrus %>% -->
-<!--   mutate(diff = ET_all_statn - ET_all_grid) -->
-
-<!-- hrus_map_et_diff <- left_join(hrus, ET_hrus, by = 'value') -->
-
-<!-- tmap_mode('plot') -->
-
-<!-- tm_shape(hrus_map_et_diff) + -->
-<!--   tm_polygons('diff', midpoint = NA, id = 'value')  + -->
-<!--   tm_legend(legend.outside = T) + -->
-<!--   tm_layout(main.title = 'Average ET difference') -->
-
-<!-- ``` -->
-
-<!-- ## Average LAI comparison -->
-
-<!-- ```{r lai, echo = F} -->
-
-<!-- #get rid of a bunch of data -->
-<!-- hru_grid_LAI <- hru_grids %>% -->
-<!--   dplyr::select(c(time, ID, LAI)) %>% -->
-<!--   rename(LAI_grid = LAI)  %>% -->
-<!--   group_by(ID) %>% -->
-<!--   summarize(LAI_all_grid = mean(LAI_grid)) -->
-
-<!-- hru_statn_LAI <- hru_statn %>% -->
-<!--   dplyr::select(c(time, ID, LAI)) %>% -->
-<!--   rename(LAI_statn = LAI) %>% -->
-<!--   group_by(ID) %>% -->
-<!--   summarize(LAI_all_statn = mean(LAI_statn)) -->
-
-<!-- LAI_hrus <- left_join(hru_grid_LAI, hru_statn_LAI, by = c('ID')) %>% -->
-<!--   rename(value = ID) -->
-
-<!-- hrus_map_LAI <- left_join(hrus, LAI_hrus, by = 'value') -->
-
-<!-- tmap_mode('view') -->
-
-<!-- LAIavg_grid <- tm_shape(hrus_map_LAI) + -->
-<!--   tm_polygons('LAI_all_grid', midpoint = NA, id = 'value', -->
-<!--               breaks = c(1,2,3,4,5)) + -->
-<!--   tm_legend(legend.outside = T) + -->
-<!--   tm_layout(main.title = 'Average LAI') -->
-
-<!-- LAIavg_statn <- tm_shape(hrus_map_LAI) + -->
-<!--   tm_polygons('LAI_all_statn', midpoint = NA, id = 'value', -->
-<!--               breaks = c(1,2,3,4,5)) + -->
-<!--   tm_legend(legend.outside = T) -->
-
-<!-- tmap_arrange(LAIavg_grid, LAIavg_statn) -->
-
-<!-- ``` -->
-
-<!-- ## LAI over time  -->
-
-<!-- ```{r lai over time, echo = F} -->
-
-<!-- # plot time series of LAI over for HRU 1 and HRU 12 -->
-<!-- hru_grid_select <- hru_grids %>% -->
-<!--   filter(ID == 1 | ID == 12) %>% -->
-<!--   dplyr::select(time, ID, LAI_grid = LAI) -->
-
-<!-- hru_statn_select <- hru_statn %>% -->
-<!--   filter(ID == 1 | ID == 12) %>% -->
-<!--   dplyr::select(time, ID, LAI_statn = LAI) -->
-
-<!-- hru_select <- left_join(hru_grid_select, hru_statn_select, by = c('time', 'ID')) %>% -->
-<!--   rename(value = ID) -->
-
-<!-- # plot time series of LAI over for HRU 1 -->
-<!-- hru_select %>% -->
-<!--   mutate(year = year(time)) %>%  -->
-<!--   filter(value == 1) %>%  -->
-<!-- ggplot(aes(x = time)) + -->
-<!--   geom_line(aes(y = LAI_grid, color = "HRU1_burn_grid"), size = 1) + -->
-<!--   geom_line(aes(y = LAI_statn, color = 'HRU1_burn_statn'), size = 1) + -->
-<!--   ggtitle('LAI over time for HRU 1 (burned)') + -->
-<!--   scale_color_manual(name = 'HRU' , values=c("HRU1_burn_grid"='orange',  -->
-<!--                                             "HRU1_burn_statn"='springgreen4')) + -->
-<!--   theme_bw() -->
-
-<!-- # plot time series of LAI over for HRU 12 -->
-<!-- {hru_select %>% -->
-<!--   mutate(year = year(time)) %>%  -->
-<!--   filter(value == 12) %>%  -->
-<!-- ggplot(aes(x = time)) + -->
-<!--   geom_line(aes(y = LAI_grid, color = "HRU12_unburn_grid"), size = 1) + -->
-<!--   geom_line(aes(y = LAI_statn, color = 'HRU12_unburn_statn'), size = 1) + -->
-<!--   ggtitle('LAI over time for HRU 12 (unburned)') + -->
-<!--   scale_color_manual(name = 'HRU' , values=c("HRU12_unburn_grid"='orange',  -->
-<!--                                             "HRU12_unburn_statn"='springgreen4')) + -->
-<!--   theme_bw()} %>% -->
-<!--   ggplotly() -->
-
-<!-- ``` -->
-
-<!-- ## HRU 29 LAI and biomass -->
-
-<!-- ```{r hru29 lai and biomass} -->
-
-<!-- # plot time series of LAI 29 -->
-<!-- hru_grid29 <- hru_grids %>% -->
-<!--   filter(ID == 29) %>% -->
-<!--   dplyr::select(time, ID, LAI_grid = LAI) -->
-
-<!-- hru_statn29 <- hru_statn %>% -->
-<!--   filter(ID == 29) %>% -->
-<!--   dplyr::select(time, ID, LAI_statn = LAI) -->
-
-<!-- hru_29 <- left_join(hru_grid29, hru_statn29, by = c('time', 'ID'))  -->
-
-<!-- # plot time series of LAI over for HRU 29 -->
-<!-- {hru_29 %>% -->
-<!--   ggplot(aes(x = time)) + -->
-<!--   geom_line(aes(y = LAI_grid, color = "HRU29_grid"), size = 1) + -->
-<!--   geom_line(aes(y = LAI_statn, color = 'HRU29_statn'), size = 1) + -->
-<!--   ggtitle('LAI - HRU 29') + -->
-<!--   scale_color_manual(name = 'HRU' , values=c("HRU29_grid"='orange',  -->
-<!--                                             "HRU29_statn"='springgreen4')) + -->
-<!--   theme_bw()} %>% -->
-<!--   ggplotly() -->
-
-<!-- hru29grid_bio <- read_csv('/Users/megansears/Documents/Repos/fourmile/HRU_output/HRU_29_grid.csv') %>% -->
-<!--   mutate(time = mdy(time)) %>% -->
-<!--   dplyr::select(time, BioAct_grid = BioAct_kgha) -->
-
-<!-- hru29statn_bio <- read_csv('/Users/megansears/Documents/Repos/fourmile/HRU_output/HRU_29_statn.csv') %>% -->
-<!--   mutate(time = mdy(time)) %>% -->
-<!--   dplyr::select(time, BioAct_statn= BioAct_kgha) -->
-
-<!-- hru_29_bio <- left_join(hru29grid_bio, hru29statn_bio, by = c('time'))  -->
-
-<!-- #plot time series of biomass over time for HRU 29 -->
-<!-- {hru_29_bio %>% -->
-<!--   ggplot(aes(x = time)) + -->
-<!--   geom_line(aes(y = BioAct_grid, color = "HRU29_grid"), size = 1) + -->
-<!--   geom_line(aes(y = BioAct_statn, color = 'HRU29_statn'), size = 1) + -->
-<!--   ggtitle('Biomass') + -->
-<!--   scale_color_manual(name = 'HRU' , values=c("HRU29_grid"='orange',  -->
-<!--                                             "HRU29_statn"='springgreen4')) + -->
-<!--   theme_bw()} %>% -->
-<!--   ggplotly() -->
-
-<!-- ``` -->
-
-<!-- # Mauscript figs -->
-
-<!-- ## Figure 1 -->
-
-<!-- ```{r fig1} -->
-
-<!-- library(usmap) -->
-
-<!-- dem <- raster('/Users/megansears/Documents/Repos/fourmile/data/GIS/cutDEM.tif') -->
-
-<!-- hru_bnds <- st_read('/Users/megansears/Documents/Repos/fourmile/data/GIS/hrus_final.shp') -->
-
-<!-- tmap_mode('plot') -->
-
-<!-- tm_shape(dem) + -->
-<!--   tm_raster(palette = terrain.colors(5)) + -->
-<!--   tm_shape(hru_bnds) + -->
-<!--   tm_polygons(alpha =0, col = 'black') + -->
-<!--   tm_compass() + -->
-<!--   tm_scale_bar() + -->
-<!--   tm_layout(legend.outside = T, -->
-<!--             main.title = 'A') -->
-
-<!-- dem2 <- as.data.frame(dem, xy = TRUE) -->
-
-<!-- # ggplot() + -->
-<!-- #  geom_polygon(data = hru_bnds, aes(x = x, y = y, fill = value)) + -->
-<!-- #   geom_raster(data = dem2, aes(x = x, y = y, -->
-<!-- #                                       fill = cutDEM)) + -->
-<!-- #   theme_bw() + -->
-<!-- #   coord_quickmap() -->
-
-<!-- ################################################### -->
-
-<!-- catchment_mo_mean <- catchment %>% -->
-<!--   mutate(month = month(time)) %>% -->
-<!--   group_by(site, month) %>% -->
-<!--   summarise(across(precip:solRad, ~ mean(.x, na.rm = TRUE))) %>% -->
-<!--   dplyr::select(site, month, -->
-<!--                 precip_mean = precip, tmean_mean = tmean,  -->
-<!--                 solrad_mean = solRad, rh_mean = rhum) -->
-
-<!-- catchment_mo_sd <- catchment %>% -->
-<!--   mutate(month = month(time)) %>% -->
-<!--   group_by(site, month) %>% -->
-<!--   summarise(across(precip:solRad, ~ sd(.x, na.rm = TRUE))) %>% -->
-<!--   dplyr::select(site, month, -->
-<!--                 precip_sd = precip, tmean_sd = tmean,  -->
-<!--                 solrad_sd = solRad, rh_sd = rhum) -->
-
-<!-- catchment_mo <- left_join(catchment_mo_mean, catchment_mo_sd,  -->
-<!--                           by = c('month', 'site')) -->
-
-<!-- catchment_mo2 <- catchment_mo %>% -->
-<!--   mutate(month_name = month.abb[month]) %>% -->
-<!--   mutate(month_name = factor(month_name,  -->
-<!--                              levels = c('Jan', 'Feb', 'Mar', -->
-<!--                                         'Apr', 'May', 'Jun', -->
-<!--                                         'Jul', 'Aug', 'Sep', -->
-<!--                                         'Oct', 'Nov', 'Dec'))) -->
-
-<!-- p_cols <- ggplot(catchment_mo2, aes(x = month_name, y = precip_mean, -->
-<!--                           color = site, fill = site)) + -->
-<!--   geom_col(position='dodge') + -->
-<!--   geom_errorbar(aes(ymin = 0, ymax = precip_mean + precip_sd),  -->
-<!--                 position = position_dodge(width = 0.6), width = 0.2) + -->
-<!--   theme_bw(base_size = 14) + -->
-<!--   labs(y = 'Precipitation (mm)', -->
-<!--        x = element_blank())  -->
-
-<!-- ggsave("P.png", plot = p_cols, width = 8, height = 6, dpi = 300) -->
-
-<!-- t_moplot <- ggplot(catchment_mo2, aes(x = month_name, y = tmean_mean,  -->
-<!--                                       color = site, group = site)) + -->
-<!--   geom_ribbon(aes(ymin = tmean_mean - tmean_sd, ymax = tmean_mean + tmean_sd, fill = site), alpha = 0.2) + -->
-<!--   geom_line() + -->
-<!--   geom_point() + -->
-<!--   theme_bw(base_size=14) + -->
-<!--   labs(y = expression("Mean temperature " ( degree~C)), -->
-<!--        x = element_blank()) -->
-
-<!-- t_moplot -->
-
-<!-- sol_moplot <- ggplot(catchment_mo2, aes(x = month_name, y = solrad_mean,  -->
-<!--                                       color = site, group = site)) + -->
-<!--   geom_ribbon(aes(ymin = solrad_mean - solrad_sd, ymax = solrad_mean + solrad_sd, fill = site), alpha = 0.2) + -->
-<!--   geom_line() + -->
-<!--   geom_point() + -->
-<!--   theme_bw(base_size = 14) + -->
-<!--   labs(y = expression("Solar radiation (MJ/m"^"2" * ")"), -->
-<!--        x = element_blank())  -->
-
-<!-- sol_moplot -->
-
-<!-- rh_moplot <- ggplot(catchment_mo2, aes(x = month_name, y = rh_mean,  -->
-<!--                                       color = site, group = site)) + -->
-<!--   geom_ribbon(aes(ymin = rh_mean - rh_sd, ymax = rh_mean + rh_sd, fill = site), alpha = 0.2) + -->
-<!--   geom_line() + -->
-<!--   geom_point() + -->
-<!--   theme_bw(base_size = 14) + -->
-<!--   labs(y = 'RH (%)', x= element_blank())  -->
-<!-- rh_moplot -->
-
-<!-- quad <- ggarrange(p_cols,  -->
-<!--           t_moplot, -->
-<!--           sol_moplot, -->
-<!--           rh_moplot, -->
-<!--           common.legend = T, -->
-<!--           legend = 'bottom', -->
-<!--              nrow = 2, -->
-<!--           ncol= 2) -->
-
-<!-- ggsave("quad.png", plot = quad, width = 8, height = 6, dpi = 300) -->
-
-<!-- ``` -->
+plot_burnparams <- function(param_name) {
+  burn_params %>%
+    filter(params == param_name) %>%
+    ggplot(aes(y = value,
+               x = year_missing,
+               color = input_data)) +
+    geom_point(size = 3) +
+    ggtitle(param_name) +
+    theme_bw()
+}
+
+name <- levels(burn_params$params)
+
+lapply(name, plot_burnparams)
+
+```
+
+## Combined parameters
+
+The two burned HRU parameters were averaged together.
+
+```{r}
+params <- params %>%
+  mutate(burn = 'no')
+
+params_combo <- bind_rows(params,
+                          burn_params %>%
+                            rename(param = params))
+
+#function to plot all params
+plot_params <- function(param_name) {
+  params_combo %>%
+    filter(param == param_name) %>%
+    ggplot(aes(x = year_missing,
+               y = value,
+               shape = burn, 
+               color = input_data)) + 
+    geom_point(size = 3) + 
+    ggtitle(param_name) +
+    theme_bw()
+}
+
+name <- levels(params_combo$param)
+
+lapply(name, plot_params)
+
+```
+
+# Outlet results
+
+## Hydrograph
+
+```{r hydrographs, echo = F}
+flow <- read_csv('discharge_all.csv') %>%
+  replace(.==-9999, NA)
+
+flow_pivot <- flow %>%
+  pivot_longer(!date, names_to = 'cal_run', values_to = 'q_m3s') %>%
+  mutate(year = as.factor(year(date)))
+
+q <- ggplot(flow_pivot, aes(date, q_m3s, color = cal_run)) +
+  geom_line() +
+  scale_color_manual(name="cal_run", values=c('obs' = 'black',
+                                            "grid_2011"="seagreen",
+                                            "grid_2012"="seagreen2",
+                                            "grid_2013"="steelblue",
+                                            "grid_2014"='dodgerblue',
+                                            "grid_2015" = "cyan3",
+                                            'grid_2016' = 'blue',
+                                            'grid_2017' = 'blue4',
+                                            'grid_2018' = 'cadetblue',
+                                            'grid_2019' = 'lightgreen',
+                                            'grid_2020' = 'olivedrab',
+                                            'grid_all' = 'steelblue3',
+                                            "statn_2011"="maroon",
+                                            "statn_2012"="deeppink4",
+                                            "statn_2013"="deeppink",
+                                            "statn_2014"='purple',
+                                            "statn_2015" = "mediumorchid1",
+                                            'statn_2016' = 'indianred',
+                                            'statn_2017' = 'sienna',
+                                            'statn_2018' = 'salmon2',
+                                            'statn_2019' = 'mediumpurple1',
+                                            'statn_2020' = 'violetred',
+                                            'statn_all' = 'red'))
+
+ggplotly(q)
+
+```
+
+## KGE
+
+### Overall KGE
+
+```{r kge overall, echo = F}
+
+flow_kge_all <- flow %>%
+  summarize(grid2011 = KGE(grid_2011, obs),
+            grid2012 = KGE(grid_2012, obs),
+            grid2013 = KGE(grid_2013, obs),
+            grid2014 = KGE(grid_2014, obs),
+            grid2015 = KGE(grid_2015, obs),
+            grid2016 = KGE(grid_2016, obs),
+            grid2017 = KGE(grid_2017, obs),
+            grid2018 = KGE(grid_2018, obs),
+            grid2019 = KGE(grid_2019, obs),
+            grid2020 = KGE(grid_2020, obs),
+            gridall = KGE(grid_all, obs),
+            statn2011 = KGE(statn_2011, obs),
+            statn2012 = KGE(statn_2012, obs),
+            statn2013 = KGE(statn_2013, obs),
+            statn2014 = KGE(statn_2014, obs),
+            statn2015 = KGE(statn_2015, obs),
+            statn2016 = KGE(statn_2016, obs),
+            statn2017 = KGE(statn_2017, obs),
+            statn2018 = KGE(statn_2018, obs),
+            statn2019 = KGE(statn_2019, obs),
+            statn2020 = KGE(statn_2020, obs),
+            statnall = KGE(statn_all, obs)) %>%
+    mutate_if(is.numeric,
+            round,
+            digits = 2)
+
+flow_kge_all <- flow_kge_all %>%
+  pivot_longer(everything()) %>%
+  arrange(value)
+
+kable(flow_kge_all) %>%
+  kable_styling(full_width = F)
+
+```
+
+### KGE by year
+
+```{r kge by year, echo = F}
+
+flow_year <- flow %>%
+  mutate(year = year(date)) %>%
+  group_by(year) %>%
+  summarize(grid2011 = KGE(grid_2011, obs),
+            grid2012 = KGE(grid_2012, obs),
+            grid2013 = KGE(grid_2013, obs),
+            grid2014 = KGE(grid_2014, obs),
+            grid2015 = KGE(grid_2015, obs),
+            grid2016 = KGE(grid_2016, obs),
+            grid2017 = KGE(grid_2017, obs),
+            grid2018 = KGE(grid_2018, obs),
+            grid2019 = KGE(grid_2019, obs),
+            grid2020 = KGE(grid_2020, obs),
+            gridall = KGE(grid_all, obs),
+            statn2011 = KGE(statn_2011, obs),
+            statn2012 = KGE(statn_2012, obs),
+            statn2013 = KGE(statn_2013, obs),
+            statn2014 = KGE(statn_2014, obs),
+            statn2015 = KGE(statn_2015, obs),
+            statn2016 = KGE(statn_2016, obs),
+            statn2017 = KGE(statn_2017, obs),
+            statn2018 = KGE(statn_2018, obs),
+            statn2019 = KGE(statn_2019, obs),
+            statn2020 = KGE(statn_2020, obs),
+            statnall = KGE(statn_all, obs)) %>%
+    mutate_if(is.numeric,
+            round,
+            digits = 2)
+
+flow_kge <- flow_year %>%
+  pivot_longer(!year, names_to = 'model_run', values_to = 'kge') %>%
+  pivot_wider(names_from = 'year', values_from = 'kge')
+
+flow_kge %>%
+  kable(.) %>%
+  kable_styling()
+
+flow_plot <- flow_year %>%
+  pivot_longer(!year, names_to = 'model_run', values_to = 'kge') %>%
+  mutate(year = as.factor(year))
+
+kge_plot_cy <- ggplot(flow_plot, aes(year, kge, color = model_run)) +
+  geom_point(size = 3) +
+  scale_color_manual(name="model_run", values=c("grid2011"="seagreen",
+                                            "grid2012"="seagreen2",
+                                            "grid2013"="steelblue",
+                                            "grid2014"='dodgerblue',
+                                            "grid2015" = "cyan3",
+                                            'grid2016' = 'blue',
+                                            'grid2017' = 'blue4',
+                                            'grid2018' = 'cadetblue',
+                                            'grid2019' = 'lightgreen',
+                                            'grid2020' = 'olivedrab',
+                                            'gridall' = 'steelblue3',
+                                            "statn2011"="maroon",
+                                            "statn2012"="deeppink4",
+                                            "statn2013"="deeppink",
+                                            "statn2014"='purple',
+                                            "statn2015" = "mediumorchid1",
+                                            'statn2016' = 'indianred',
+                                            'statn2017' = 'sienna',
+                                            'statn2018' = 'salmon2',
+                                            'statn2019' = 'mediumpurple1',
+                                            'statn2020' = 'violetred',
+                                            'statnall' = 'red')) +
+  theme_bw()
+
+ggplotly(kge_plot_cy)
+
+```
+
+### Annual KGE plots
+
+```{r wy plots, echo = F}
+
+plot_kge <- function(calyear) {
+  flow_plot %>%
+    filter(year == calyear) %>%
+    ggplot(aes(x = model_run,
+               y = kge)) +
+    geom_col() +
+    ggtitle(calyear) +
+    theme_bw() +
+    theme(axis.text.x = element_text(angle = 45, hjust=1))
+}
+
+name <- levels(flow_plot$year)
+
+lapply(name, plot_kge)
+
+```
+
+# Ensembles
+
+## Hydrograph
+
+```{r ensemble hydrographs, echo = F}
+
+ensem <- flow %>%
+  rowwise() %>%
+  mutate(grid_ensemble = mean(c(grid_2011, grid_2012,
+                                grid_2013, grid_2014,
+                                grid_2015, grid_2016,
+                                grid_2017, grid_2018,
+                                grid_2019, grid_2020)),
+         statn_ensemble = mean(c(statn_2011, statn_2012,
+                                 statn_2013, statn_2014,
+                                 statn_2015, statn_2016,
+                                 statn_2017, statn_2018,
+                                 statn_2019, statn_2020)),
+         all_ensemble = mean(c(grid_2011, grid_2012,
+                               grid_2013, grid_2014,
+                               grid_2015, grid_2016,
+                               grid_2017, grid_2018,
+                               grid_2019, grid_2020,
+                               statn_2011, statn_2012,
+                               statn_2013, statn_2014,
+                               statn_2015, statn_2016,
+                               statn_2017, statn_2018,
+                               statn_2019, statn_2020,
+                               grid_all, statn_all))) %>%
+  dplyr::select(date, grid_ensemble, statn_ensemble,
+         all_ensemble, grid_all,
+         statn_all, obs)
+
+ensem_pivot <- ensem %>%
+  pivot_longer(!date, names_to = 'cal_run', values_to = 'q_m3s') %>%
+  mutate(year = as.factor(year(date)))
+
+q_ensemble <- ggplot(ensem_pivot, aes(date, q_m3s, color = cal_run)) +
+  geom_line() +
+  scale_color_manual(name="cal_run", values=c('obs'='black',
+                                            "grid_ensemble"="maroon",
+                                            "statn_ensemble"="darkturquoise",
+                                            "grid_all"="purple1",
+                                            "statn_all"='springgreen4',
+                                            "all_ensemble" = "orange")) +
+  geom_line(data = bouldcr, aes(date, bouldcr/10), color = 'darkgrey') +
+  scale_y_continuous(name = 'Q_m3s',
+                    sec.axis = sec_axis(~.*10, name='BoulderCr_cms')) +
+  theme_bw()
+
+ggplotly(q_ensemble) %>%
+  add_lines(data=bouldcr, x=~date, y=~bouldcr, colors=NULL, yaxis="y2",
+              inherit=FALSE, showlegend = FALSE) %>%
+  layout(yaxis2 = list(overlaying = "y", side = "right",
+                       color = 'darkgray',
+                       title = "BoulderCr_cms"),
+         legend = list(x = 1.1, y = 0.95))
+
+```
+
+## KGE
+
+### KGE for ensembles (entire period)
+
+```{r ensemble kge, echo = F}
+
+ensem_kge_all <- ensem %>%
+  ungroup() %>%
+  summarize(grid_ensemble = KGE(grid_ensemble, obs),
+            statn_ensemble = KGE(statn_ensemble, obs),
+            all_ensemble = KGE(all_ensemble, obs),
+            grid_all = KGE(grid_all, obs),
+            statn_all = KGE(statn_all, obs)) %>%
+    mutate_if(is.numeric,
+            round,
+            digits = 2)
+
+kable(ensem_kge_all) %>%
+  kable_styling(full_width = F)
+
+```
+
+### Annual KGEs for ensembles
+
+```{r annual kge ensemble, echo = F}
+
+yr_kge_ensem <- ensem %>%
+  ungroup() %>%
+  mutate(year = year(date)) %>%
+  group_by(year) %>%
+  summarize(grid_ensemble = KGE(grid_ensemble, obs),
+            statn_ensemble = KGE(statn_ensemble, obs),
+            all_ensemble = KGE(all_ensemble, obs),
+            grid_all = KGE(grid_all, obs),
+            statn_all = KGE(statn_all, obs)) %>%
+    mutate_if(is.numeric,
+            round,
+            digits = 2)
+
+yr_kge_table <- yr_kge_ensem %>%
+  pivot_longer(!year, names_to = 'model_run', values_to = 'kge') %>%
+  pivot_wider(names_from = 'year', values_from = 'kge')
+
+yr_kge_table %>%
+  kable(.) %>%
+  kable_styling()
+
+yr_kge_plot <- yr_kge_ensem %>%
+  pivot_longer(!year, names_to = 'model_run', values_to = 'kge') %>%
+  mutate(year = as.factor(year))
+
+#plot annual kge vals for ensembles
+plot_kge_yr_ensem <- function(calyear) {
+  yr_kge_plot %>%
+    filter(year == calyear) %>%
+    ggplot(aes(x = model_run,
+               y = kge)) +
+    geom_col() +
+    ggtitle(calyear) +
+    theme_bw() +
+    theme(axis.text.x = element_text(angle = 45, hjust=1))
+}
+
+name <- levels(yr_kge_plot$year)
+
+lapply(name, plot_kge_yr_ensem)
+
+```
+
+### Monthly KGEs for ensembles
+
+```{r monthly kge ensemble, echo = F}
+
+mo_kge <- ensem %>%
+  ungroup() %>%
+  drop_na() %>%
+  mutate(month = month(date)) %>%
+  group_by(month) %>%
+  summarize(grid_ensemble = KGE(grid_ensemble, obs),
+            statn_ensemble = KGE(statn_ensemble, obs),
+            all_ensemble = KGE(all_ensemble, obs),
+            grid_all = KGE(grid_all, obs),
+            statn_all = KGE(statn_all, obs)) %>%
+    mutate_if(is.numeric,
+            round,
+            digits = 2)
+
+kable(mo_kge) %>%
+  kable_styling(full_width = F)
+
+mo_pivot <- mo_kge %>%
+  pivot_longer(!month, names_to = 'cal_run', values_to = 'KGE') %>%
+  drop_na()
+
+kge_plot_mo <- ggplot(mo_pivot, aes(month, KGE, color = cal_run)) + geom_point(size = 3) +
+    scale_color_manual(name="cal_run", values=c("grid_ensemble"="maroon",
+                                            "statn_ensemble"="darkturquoise",
+                                            "grid_all"="purple1",
+                                            "statn_all"='springgreen4',
+                                            "all_ensemble" = "orange")) +
+  theme_bw()
+
+ggplotly(kge_plot_mo)
+
+```
+
+## RMSE
+
+### Ensemble RMSE for entire period
+
+```{r ensemble rmse, echo = F}
+
+ensem_rmse_all <- ensem %>%
+  ungroup() %>%
+  summarize(grid_ensemble = rmse(grid_ensemble, obs),
+            statn_ensemble = rmse(statn_ensemble, obs),
+            all_ensemble = rmse(all_ensemble, obs),
+            grid_all = rmse(grid_all, obs),
+            statn_all = rmse(statn_all, obs)) %>%
+    mutate_if(is.numeric,
+            round,
+            digits = 4)
+
+kable(ensem_rmse_all) %>%
+  kable_styling(full_width = F)
+
+```
+
+### Annual RMSE for ensembles
+
+```{r annual rmse ensem, echo = F}
+
+yr_rmse_ensem <- ensem %>%
+  ungroup() %>%
+  mutate(year = year(date)) %>%
+  group_by(year) %>%
+  summarize(grid_ensemble = rmse(grid_ensemble, obs),
+            statn_ensemble = rmse(statn_ensemble, obs),
+            all_ensemble = rmse(all_ensemble, obs),
+            grid_all = rmse(grid_all, obs),
+            statn_all = rmse(statn_all, obs)) %>%
+    mutate_if(is.numeric,
+            round,
+            digits = 4)
+
+yr_rmse_table <- yr_rmse_ensem %>%
+  pivot_longer(!year, names_to = 'model_run', values_to = 'rmse') %>%
+  pivot_wider(names_from = 'year', values_from = 'rmse')
+
+yr_rmse_table %>%
+  kable(.) %>%
+  kable_styling()
+
+yr_rmse_plot <- yr_rmse_ensem %>%
+  pivot_longer(!year, names_to = 'model_run', values_to = 'rmse') %>%
+  mutate(year = as.factor(year))
+
+#plot annual rmse vals for ensembles
+plot_rmse_yr_ensem <- function(calyear) {
+  yr_rmse_plot %>%
+    filter(year == calyear) %>%
+    ggplot(aes(x = model_run,
+               y = rmse)) +
+    geom_col() +
+    ggtitle(calyear) +
+    theme_bw() +
+    theme(axis.text.x = element_text(angle = 45, hjust=1))
+}
+
+name <- levels(yr_rmse_plot$year)
+
+lapply(name, plot_rmse_yr_ensem)
+
+```
+
+### Monthly RMSEs for ensembles
+
+```{r month ensem rmse, echo = F}
+
+mo_rmse <- ensem %>%
+  ungroup() %>%
+  drop_na() %>%
+  mutate(month = month(date)) %>%
+  group_by(month) %>%
+  summarize(grid_ensemble = rmse(grid_ensemble, obs),
+            statn_ensemble = rmse(statn_ensemble, obs),
+            all_ensemble = rmse(all_ensemble, obs),
+            grid_all = rmse(grid_all, obs),
+            statn_all = rmse(statn_all, obs)) %>%
+    mutate_if(is.numeric,
+            round,
+            digits = 4)
+
+kable(mo_rmse) %>%
+  kable_styling(full_width = F)
+
+mo_pivot2 <- mo_rmse %>%
+  pivot_longer(!month, names_to = 'cal_run', values_to = 'RMSE') %>%
+  drop_na()
+
+rmse_plot_mo <- ggplot(mo_pivot2, aes(month, RMSE, color = cal_run)) + geom_point(size = 3) +
+    scale_color_manual(name="cal_run", values=c("grid_ensemble"="maroon",
+                                            "statn_ensemble"="darkturquoise",
+                                            "grid_all"="purple1",
+                                            "statn_all"='springgreen4',
+                                            "all_ensemble" = "orange")) +
+  theme_bw()
+
+ggplotly(rmse_plot_mo)
+
+```
+
+## NSE
+
+### Ensemble NSE for entire period
+
+```{r nse all, echo = F}
+
+ensem_nse_all <- ensem %>%
+  ungroup() %>%
+  summarize(grid_ensemble = NSE(grid_ensemble, obs),
+            statn_ensemble = NSE(statn_ensemble, obs),
+            all_ensemble = NSE(all_ensemble, obs),
+            grid_all = NSE(grid_all, obs),
+            statn_all = NSE(statn_all, obs)) %>%
+    mutate_if(is.numeric,
+            round,
+            digits = 2)
+
+kable(ensem_nse_all) %>%
+  kable_styling(full_width = F)
+
+```
+
+### Annual NSE for ensembles
+
+```{r annual nse, echo = F}
+
+yr_nse_ensem <- ensem %>%
+  ungroup() %>%
+  mutate(year = year(date)) %>%
+  group_by(year) %>%
+  summarize(grid_ensemble = NSE(grid_ensemble, obs),
+            statn_ensemble = NSE(statn_ensemble, obs),
+            all_ensemble = NSE(all_ensemble, obs),
+            grid_all = NSE(grid_all, obs),
+            statn_all = NSE(statn_all, obs)) %>%
+    mutate_if(is.numeric,
+            round,
+            digits = 4)
+
+yr_nse_table <- yr_nse_ensem %>%
+  pivot_longer(!year, names_to = 'model_run', values_to = 'nse') %>%
+  pivot_wider(names_from = 'year', values_from = 'nse')
+
+yr_nse_table %>%
+  kable(.) %>%
+  kable_styling()
+
+yr_nse_plot <- yr_nse_ensem %>%
+  pivot_longer(!year, names_to = 'model_run', values_to = 'nse') %>%
+  mutate(year = as.factor(year))
+
+#plot annual nse vals for ensembles
+plot_nse_yr_ensem <- function(calyear) {
+  yr_nse_plot %>%
+    filter(year == calyear) %>%
+    ggplot(aes(x = model_run,
+               y = nse)) +
+    geom_col() +
+    ggtitle(calyear) +
+    theme_bw() +
+    theme(axis.text.x = element_text(angle = 45, hjust=1))
+}
+
+name <- levels(yr_nse_plot$year)
+
+lapply(name, plot_nse_yr_ensem)
+
+```
+
+### Monthly NSE for ensembles
+
+```{r monthly rmse, echo =F}
+
+mo_nse <- ensem %>%
+  ungroup() %>%
+  drop_na() %>%
+  mutate(month = month(date)) %>%
+  group_by(month) %>%
+  summarize(grid_ensemble = NSE(grid_ensemble, obs),
+            statn_ensemble = NSE(statn_ensemble, obs),
+            all_ensemble = NSE(all_ensemble, obs),
+            grid_all = NSE(grid_all, obs),
+            statn_all = NSE(statn_all, obs)) %>%
+    mutate_if(is.numeric,
+            round,
+            digits = 4)
+
+kable(mo_nse) %>%
+  kable_styling(full_width = F)
+
+mo_pivot2 <- mo_nse %>%
+  pivot_longer(!month, names_to = 'cal_run', values_to = 'nse') %>%
+  drop_na()
+
+nse_plot_mo <- ggplot(mo_pivot2, aes(month, nse, color = cal_run)) + geom_point(size = 3) +
+  theme_bw() +
+  scale_color_manual(name="cal_run", values=c("grid_ensemble"="maroon",
+                                            "statn_ensemble"="darkturquoise",
+                                            "grid_all"="purple1",
+                                            "statn_all"='springgreen4',
+                                            "all_ensemble" = "orange"))
+
+ggplotly(nse_plot_mo)
+
+```
+
+## Cumulative Q
+
+```{r cumq, echo = F}
+
+ensem_cumq <- ensem %>%
+  mutate(month = month(date)) %>%
+  filter(month %in% c(4:9)) %>%
+  dplyr::select(-month) %>%
+  pivot_longer(!date, names_to = 'cal_run', values_to = 'q_m3s') %>%
+  group_by(cal_run, year(date)) %>%
+  mutate(cumsum = cumsum(replace_na(q_m3s, 0))) %>%
+  rename(year = 4) %>%
+  mutate(year = as.factor(year)) %>%
+  ungroup()
+
+#plot annual cumulative Q vals for ensembles
+plot_cumulq_yr_ensem <- function(calyear) {
+  {ensem_cumq %>%
+    filter(year == calyear) %>%
+    ggplot(aes(x = date,
+               y = cumsum,
+               color = cal_run)) +
+    geom_line() +
+    scale_color_manual(name="cal_run", values=c("obs"="black",
+                                             "grid_ensemble"="maroon",
+                                            "statn_ensemble"="darkturquoise",
+                                            "grid_all"="purple1",
+                                            "statn_all"='springgreen4',
+                                            "all_ensemble" = "orange")) +
+    ggtitle(calyear) +
+    theme_bw() +
+    labs(y = 'cumulative Q (m3s)')} %>%
+    ggplotly()
+}
+
+name <- levels(ensem_cumq$year)
+
+cumulative_plots <- lapply(name, plot_cumulq_yr_ensem)
+
+htmltools::tagList(cumulative_plots)
+
+cumulative_plots
+
+```
+
+# Catchment results
+
+## Precip
+
+```{r catch precip, echo = F}
+setwd("/Users/megansears/Documents/Repos/fourmile/catchment_output")
+
+statn <- read_csv('statnall.csv')
+grid <- read_csv('gridall.csv')
+
+grid <- grid %>% mutate(site = 'grid')
+statn <- statn %>% mutate(site = 'statn')
+
+catchment <- bind_rows(grid, statn) %>%
+  mutate(year = as.factor(year(time))) %>%
+  group_by(year, site) %>%
+  mutate(cumulative_p = cumsum(precip))
+
+#plot cumulative precip by year
+plot_cumprecip <- function(calyear) {
+  {catchment %>%
+    filter(year == calyear) %>%
+    ggplot(aes(x = time,
+               y = cumulative_p, color = site)) +
+    geom_line(size=1) +
+    ggtitle(calyear) +
+    ylab('Cumulative precip (mm)') +
+    theme_bw() +
+    theme(axis.text.x = element_text(angle = 45, hjust=1))} %>%
+    ggplotly()
+}
+
+name <- levels(catchment$year)
+
+precip_plots <- lapply(name, plot_cumprecip)
+
+htmltools::tagList(precip_plots)
+
+precip_plots
+
+## total P
+max_cumulativep <- catchment %>%
+  group_by(year, site) %>%
+  summarize(total_cumulativep = max(cumulative_p))
+
+ggplot(max_cumulativep, aes(x=year, y=total_cumulativep, color=site)) +
+  geom_point(size=3) +
+  ggtitle('Total cumulative precip (mm) by year')
+
+```
+
+## Tmean
+
+```{r tmean catch, echo = F}
+## tmean
+tmean <- catchment %>%
+  group_by(year, site) %>%
+  summarize(tmean = mean(tmean)) %>%
+  ggplot(aes(x = year, y=tmean, color = site)) +
+  geom_point(size=3) +
+  ggtitle('Average temp by year')
+
+tmean
+
+```
+
+## RD and RG
+
+```{r rd and rg, echo = F, fig.width = 14, fig.asp = 1, out.width = "100%"}
+
+gw_grid <- read_csv(here('catchment_output/gridall_outlet.csv')) %>%
+  dplyr::select(time, catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w) %>%
+  mutate(source = 'grid')
+
+gw_statn <- read_csv(here('catchment_output/statnall_outlet.csv')) %>%
+  dplyr::select(time, catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w) %>%
+  mutate(source = 'statn')
+
+gw <- bind_rows(gw_grid, gw_statn) %>%
+  mutate(year = year(time)) %>%
+  rename(date = time)
+
+ggplot(gw, aes(x=date, color = source)) +
+  geom_line(aes(y=catchmentRD1_w), size =1) +
+  facet_wrap(~year, scales = 'free', ncol = 2) +
+  scale_x_date(labels = date_format("%b")) +
+  ggtitle('RD1') +
+  theme(text = element_text(size = 20))
+
+ggplot(gw, aes(x=date, color = source)) +
+  geom_line(aes(y=catchmentRD2_w), size =1) +
+  facet_wrap(~year, scales = 'free', ncol = 2) +
+  scale_x_date(labels = date_format("%b")) +
+  ggtitle('RD2') +
+  theme(text = element_text(size = 20))
+
+ggplot(gw, aes(x=date, color = source)) +
+  geom_line(aes(y=catchmentRG1_w), size =1) +
+  facet_wrap(~year, scales = 'free', ncol = 2) +
+  scale_x_date(labels = date_format("%b")) +
+  ggtitle('RG1') +
+  theme(text = element_text(size = 20))
+
+ggplot(gw, aes(x=date, color = source)) +
+  geom_line(aes(y=catchmentRG2_w), size =1) +
+  facet_wrap(~year, scales = 'free', ncol=2) +
+  scale_x_date(labels = date_format("%b")) +
+  ggtitle('RG2') +
+  theme(text = element_text(size = 20))
+
+gw <- gw %>%
+  group_by(year, source) %>%
+  mutate(RD1cumsum = cumsum(catchmentRD1_w),
+         RD2cumsum = cumsum(catchmentRD2_w),
+         RG1cumsum = cumsum(catchmentRG1_w),
+         RG2cumsum = cumsum(catchmentRG2_w))
+
+ggplot(gw, aes(x=date, color = source)) +
+  geom_line(aes(y=RD1cumsum), size =1) +
+  facet_wrap(~year, scales = 'free', ncol=2) +
+  scale_x_date(labels = date_format("%b")) +
+  ggtitle('Cumulative RD1') +
+  theme(text = element_text(size = 20))
+
+ggplot(gw, aes(x=date, color = source)) +
+  geom_line(aes(y=RD2cumsum), size = 1) +
+  facet_wrap(~year, scales = 'free', ncol=2) +
+  scale_x_date(labels = date_format("%b")) +
+  ggtitle('Cumulative RD2') +
+  theme(text = element_text(size = 20))
+
+ggplot(gw, aes(x=date, color = source)) +
+  geom_line(aes(y=RG1cumsum), size  = 1) +
+  facet_wrap(~year, scales = 'free', ncol = 2) +
+  scale_x_date(labels = date_format("%b")) +
+  ggtitle('Cumulative RG1') +
+  theme(text = element_text(size = 20))
+
+ggplot(gw, aes(x=date, color = source)) +
+  geom_line(aes(y=RG2cumsum), size =1) +
+  facet_wrap(~year, scales = 'free', ncol = 2) +
+  scale_x_date(labels = date_format("%b")) +
+  ggtitle('Cumulative RG2') +
+  theme(text = element_text(size = 20))
+
+```
+
+```{r rd and rg sums, echo = F, fig.width = 22, fig.asp = 1.5, out.width = "100%"}
+
+##################
+# all 4 with facets
+
+ggplot(gw, aes(x=date)) +
+  geom_line(aes(y=RG2cumsum, color = 'cumulative RG2'), size =1) +
+  geom_line(aes(y=RG1cumsum, color = 'cumulative RG1'), size =1) +
+  geom_line(aes(y=RD1cumsum, color = 'cumulative RD1'), size =1) +
+  geom_line(aes(y=RD2cumsum, color = 'cumulative RD2'), size =1) +
+  scale_x_date(labels = date_format("%b")) +
+  facet_wrap(~year + source, scales = 'free_x', ncol=2) +
+  ggtitle('Cumulative RD and RG') +
+  theme(text = element_text(size = 24))
+
+```
+
+```{r gw boxplot, echo = F}
+
+gw_maxcumsum <- gw %>%
+  group_by(source, year) %>%
+  summarize(yr_max_RD1 = max(RD1cumsum),
+            yr_max_RD2 = max(RD2cumsum),
+            yr_max_RG1 = max(RG1cumsum),
+            yr_max_RG2 = max(RG2cumsum)) %>%
+  mutate(year = as.factor(year)) %>%
+  pivot_longer(!c(year, source), names_to = 'flow_type', values_to = 'flow_cms')
+
+ggplot(gw_maxcumsum, aes(x = flow_type, y = flow_cms, fill = source)) +
+  geom_boxplot(position = position_dodge(1)) +
+  geom_point(position=position_jitterdodge(),alpha=0.3) +
+  ggtitle('Max annual cumulative sums')
+
+ggplot(gw_maxcumsum, aes(x = flow_type, y = flow_cms, fill = source)) +
+  geom_boxplot(position = position_dodge(1)) +
+  geom_point(position=position_jitterdodge(),alpha=0.3) +
+  #geom_point(aes(color = source)) +
+  facet_wrap(~flow_type, scales = 'free') +
+  ggtitle('Max annual cumulative sums')
+
+```
+
+### RD and RG by season
+
+```{r flow season, echo = F, fig.width = 12, fig.asp = 0.75, out.width = "100%"}
+
+#group by season and get max sums by season
+flow_season <- gw %>%
+  dplyr::select(RD1cumsum, RD2cumsum, RG1cumsum, RG2cumsum, date, year, source) %>%
+  mutate(month = month(date)) %>%
+  mutate(season = case_when(month %in% c(3,4,5,6) ~ 'snowmelt',
+                            month %in% c(7,8,9,10) ~ 'monsoon',
+                            month %in% c(11,12,1,2) ~ 'baseflow')) %>%
+  group_by(source, year, season) %>%
+  summarize(yr_season_RD1 = max(RD1cumsum),
+            yr_season_RD2 = max(RD2cumsum),
+            yr_season_RG1 = max(RG1cumsum),
+            yr_season_RG2 = max(RG2cumsum)) %>%
+            pivot_longer(!c(year, source, season), names_to = 'flow_type', values_to = 'flow_cms')
+
+flow_season %>%
+  ggplot(aes(x = flow_type, y = flow_cms, fill = source)) +
+  geom_boxplot(position = position_dodge(1)) +
+  geom_point(position=position_jitterdodge(),alpha=0.3) +
+  #geom_point(aes(color = source)) +
+  facet_wrap(~season, scales = 'free') +
+  ggtitle('Max annual season cumulative sums') +
+  theme_bw() +
+  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
+  theme(text = element_text(size = 20))
+
+flow_season %>%
+  ggplot(aes(x = flow_type, y = flow_cms, fill = source)) +
+  geom_boxplot(position = position_dodge(1)) +
+  geom_point(position=position_jitterdodge(),alpha=0.3) +
+  #geom_point(aes(color = source)) +
+  facet_wrap(~season + flow_type, scales = 'free') +
+  ggtitle('Max annual season cumulative sums') +
+  theme_bw() +
+  theme(text = element_text(size = 20))
+
+```
+
+# HRU results
+
+## Tmean difference
+
+2011-2020 average of daily station-grid Tmean
+
+```{r cumulative tmean for HRUs, echo = F}
+#grid first
+setwd(here("HRU_output/grid"))
+
+read_ages_grid <- function(dataframe){
+  read_csv(dataframe, skip = 3) %>%
+  slice(3:n()) %>%
+  dplyr::select(-starts_with('@'),
+                -1) %>%
+  mutate(time = ymd(time)) %>%
+  mutate_if(is.character, as.numeric) %>%
+  mutate(source = 'grid')
+
+}
+
+#pull in all filenames with HRU in the name
+filenames <- list.files(".", pattern="HRU", full.names=F)
+
+#read all the csvs using read_ages function
+dataframes <- lapply(filenames, read_ages_grid)
+
+#name all the csvs based on first 6 characters
+names(dataframes) <- substr(filenames, 1, 6)
+
+#bind all and make 1 df
+hru_grids <- dataframes %>%
+  bind_rows()
+
+#statn next
+setwd(here("HRU_output/statn"))
+
+read_ages_statn <- function(dataframe){
+  read_csv(dataframe, skip = 3) %>%
+  slice(3:n()) %>%
+  dplyr::select(-starts_with('@'),
+                -1) %>%
+  mutate(time = ymd(time)) %>%
+  mutate_if(is.character, as.numeric) %>%
+  mutate(source = 'statn')
+
+}
+
+#pull in all filenames with HRU in the name
+filenames <- list.files(".", pattern="HRU", full.names=F)
+
+#read all the csvs using read_ages function
+dataframes <- lapply(filenames, read_ages_statn)
+
+#name all the csvs based on first 6 characters
+names(dataframes) <- substr(filenames, 1, 6)
+
+#bind all and make 1 df
+hru_statn <- dataframes %>%
+  bind_rows()
+
+#get rid of a bunch of data
+hru_grid_tmean <- hru_grids %>%
+  dplyr::select(c(time, ID, tmean)) %>%
+  rename(tmean_grid = tmean)  %>%
+  group_by(ID) %>%
+  summarize(tmean_all_grid = mean(tmean_grid))
+
+hru_statn_tmean <- hru_statn %>%
+  dplyr::select(c(time, ID, tmean)) %>%
+  rename(tmean_statn = tmean) %>%
+  group_by(ID) %>%
+  summarize(tmean_all_statn = mean(tmean_statn))
+
+tmean_hrus <- left_join(hru_grid_tmean, hru_statn_tmean, by = c('ID')) %>%
+  mutate(diff = tmean_all_statn - tmean_all_grid) %>%
+  rename(value = ID)
+
+hrus_map_tmean <- left_join(hrus, tmean_hrus, by = 'value')
+
+tmap_mode('view')
+
+locations_t <- locations %>%
+  dplyr::filter(name %in% c('Gordon_South', 'Gordon_North',
+                        'Betasso', 'Niwot_Snotel',
+                        'University Camp SNTL'))
+
+tm_shape(hrus_map_tmean) +
+  tm_polygons('diff', id = 'value',
+              breaks = c(-6,-4,-2,0,2,4,6)) +
+tm_shape(locations_t) +
+  tm_symbols(col='blue', size=4)
+
+```
+
+## Tmax difference
+
+```{r tmax, echo = F}
+
+tmax_grid <- read_csv(here('HRU_output/reg_tmaxAll_prism.csv'))%>%
+  pivot_longer(cols = `3`:`19`,
+               names_to = 'value',
+               values_to = 'tmax_grid') %>%
+  mutate(time = dmy(time)) %>%
+  group_by(value) %>%
+  summarize(Tmax_mean_grid = mean(tmax_grid))
+
+tmax_statn <- read_csv(here('HRU_output/reg_tmaxAll.csv')) %>%
+  pivot_longer(cols = `3`:`19`,
+               names_to = 'value',
+               values_to = 'tmax_statn') %>%
+  mutate(time = dmy(time)) %>%
+  group_by(value) %>%
+  summarize(Tmax_mean_statn = mean(tmax_statn))
+
+tmax_hrus <- left_join(tmax_grid, tmax_statn, by = c('value')) %>%
+  mutate(diff = Tmax_mean_statn - Tmax_mean_grid,
+         value = as.numeric(value))
+
+hrus_map_tmax <- left_join(hrus, tmax_hrus, by = 'value')
+
+tmap_mode('view')
+
+tm_shape(hrus_map_tmax) +
+  tm_polygons('diff', id = 'value',
+              breaks = c(-6,-4,-2,0,2,4,6)) +
+tm_shape(locations_t) +
+  tm_symbols(col='blue', size=4)
+
+```
+
+## Tmax monthly average
+
+```{r tmax month, echo = F}
+
+tmax_grid_mo <- read_csv(here('HRU_output/reg_tmaxAll_prism.csv')) %>%
+  pivot_longer(cols = `3`:`19`,
+               names_to = 'value',
+               values_to = 'tmax_grid') %>%
+  mutate(time = dmy(time),
+         month = month(time)) %>%
+  filter(month %in% c(3:6)) %>%
+  group_by(value, month) %>%
+  summarize(avg_tmax_grid = mean(tmax_grid))
+
+tmax_statn_mo <- read_csv(here('HRU_output/reg_tmaxAll.csv')) %>%
+  pivot_longer(cols = `3`:`19`,
+               names_to = 'value',
+               values_to = 'tmax_statn') %>%
+  mutate(time = dmy(time),
+         month = month(time)) %>%
+  filter(month %in% c(3:6)) %>%
+  group_by(value, month) %>%
+  summarize(avg_tmax_statn = mean(tmax_statn))
+
+tmax_hrus_mo <- left_join(tmax_grid_mo, tmax_statn_mo, by = c('value', 'month')) %>%
+  mutate(mo_tmax_diff = avg_tmax_statn - avg_tmax_grid,
+         value = as.numeric(value))
+
+tmap_mode('plot')
+
+#march
+tmax_hrus_mar<- tmax_hrus_mo %>%
+  filter(month == 3)
+
+hrus_map_tmax_mar <- left_join(hrus, tmax_hrus_mar, by = 'value')
+
+mar_tmax <- tm_shape(hrus_map_tmax_mar) +
+  #tm_polygons('mo_tmax_diff', id = 'value') +
+  tm_fill('mo_tmax_diff', id = 'value',
+          breaks = c(-6,-4,-2,0,2,4,6)) +
+  tm_borders() +
+  tm_shape(locations_t) +
+  tm_symbols(col='blue', size = 0.25) +
+  tm_layout(title = 'March avg tmax',
+            legend.outside = T)
+
+#april
+tmax_hrus_apr<- tmax_hrus_mo %>%
+  filter(month == 4)
+
+hrus_map_tmax_apr <- left_join(hrus, tmax_hrus_apr, by = 'value')
+
+apr_tmax <- tm_shape(hrus_map_tmax_apr) +
+  tm_fill('mo_tmax_diff', id = 'value',
+          breaks = c(-6,-4,-2,0,2,4,6)) +
+  tm_borders() +
+  tm_shape(locations_t) +
+  tm_symbols(col='blue', size = 0.25) +
+  tm_layout(title = 'April avg tmax',
+            legend.outside = T)
+
+#may
+tmax_hrus_may<- tmax_hrus_mo %>%
+  filter(month == 5)
+
+hrus_map_tmax_may <- left_join(hrus, tmax_hrus_may, by = 'value')
+
+may_tmax <- tm_shape(hrus_map_tmax_may) +
+  tm_fill('mo_tmax_diff', id = 'value',
+         breaks = c(-6,-4,-2,0,2,4,6)) +
+  tm_borders() +
+tm_shape(locations_t) +
+  tm_symbols(col='blue', size = 0.25) +
+  tm_layout(title = 'May avg tmax',
+            legend.outside = T)
+
+#june
+tmax_hrus_jun<- tmax_hrus_mo %>%
+  filter(month == 6)
+
+hrus_map_tmax_jun <- left_join(hrus, tmax_hrus_jun, by = 'value')
+
+jun_tmax <- tm_shape(hrus_map_tmax_jun) +
+  tm_fill('mo_tmax_diff', id = 'value',
+         breaks = c(-6,-4,-2,0,2,4,6)) +
+  tm_borders() +
+tm_shape(locations_t) +
+  tm_symbols(col='blue', size = 0.25) +
+  tm_layout(title = 'June avg tmax',
+            legend.outside = T)
+
+tmap_arrange(mar_tmax, apr_tmax, may_tmax, jun_tmax)
+
+```
+
+## Tmin difference
+
+```{r tmin, echo = F}
+
+tmin_grid <- read_csv(here('HRU_output/reg_tminAll_prism.csv')) %>%
+  pivot_longer(cols = `3`:`19`,
+               names_to = 'value',
+               values_to = 'tmin_grid') %>%
+  mutate(time = dmy(time)) %>%
+  group_by(value) %>%
+  summarize(Tmin_mean_grid = mean(tmin_grid))
+
+tmin_statn <- read_csv(here('HRU_output/reg_tminAll.csv')) %>%
+  pivot_longer(cols = `3`:`19`,
+               names_to = 'value',
+               values_to = 'tmin_statn') %>%
+  mutate(time = dmy(time)) %>%
+  group_by(value) %>%
+  summarize(Tmin_mean_statn = mean(tmin_statn))
+
+tmin_hrus <- left_join(tmin_grid, tmin_statn, by = c('value')) %>%
+  mutate(diff = Tmin_mean_statn - Tmin_mean_grid,
+         value = as.numeric(value))
+
+hrus_map_tmin <- left_join(hrus, tmin_hrus, by = 'value')
+
+tmap_mode('view')
+
+tm_shape(hrus_map_tmin) +
+  tm_polygons('diff', id = 'value',
+              breaks = c(-6,-4,-2,0,2,4,6)) +
+tm_shape(locations_t) +
+  tm_symbols(col='blue', size=4)
+
+```
+
+## Tmin monthly average
+
+```{r tmin month, echo = F}
+tmin_grid_mo <- read_csv(here('HRU_output/reg_tminAll_prism.csv')) %>%
+  pivot_longer(cols = `3`:`19`,
+               names_to = 'value',
+               values_to = 'tmin_grid') %>%
+  mutate(time = dmy(time),
+         month = month(time)) %>%
+  filter(month %in% c(3:6)) %>%
+  group_by(value, month) %>%
+  summarize(avg_tmin_grid = mean(tmin_grid))
+
+tmin_statn_mo <- read_csv(here('HRU_output/reg_tminAll.csv')) %>%
+  pivot_longer(cols = `3`:`19`,
+               names_to = 'value',
+               values_to = 'tmin_statn') %>%
+  mutate(time = dmy(time),
+         month = month(time)) %>%
+  filter(month %in% c(3:6)) %>%
+  group_by(value, month) %>%
+  summarize(avg_tmin_statn = mean(tmin_statn))
+
+tmin_hrus_mo <- left_join(tmin_grid_mo, tmin_statn_mo, by = c('value', 'month')) %>%
+  mutate(mo_tmin_diff = avg_tmin_statn - avg_tmin_grid,
+         value = as.numeric(value))
+
+tmap_mode('plot')
+
+#march
+tmin_hrus_mar<- tmin_hrus_mo %>%
+  filter(month == 3)
+
+hrus_map_tmin_mar <- left_join(hrus, tmin_hrus_mar, by = 'value')
+
+mar_tmin <- tm_shape(hrus_map_tmin_mar) +
+  #tm_polygons('mo_tmin_diff', id = 'value') +
+  tm_fill('mo_tmin_diff', id = 'value',
+          breaks = c(-5,-2.5,0,2.5,5)) +
+  tm_borders() +
+  tm_shape(locations_t) +
+  tm_symbols(col='blue', size = 0.25) +
+  tm_layout(title = 'March avg tmin',
+            legend.outside = T)
+
+#april
+tmin_hrus_apr<- tmin_hrus_mo %>%
+  filter(month == 4)
+
+hrus_map_tmin_apr <- left_join(hrus, tmin_hrus_apr, by = 'value')
+
+apr_tmin <- tm_shape(hrus_map_tmin_apr) +
+  tm_fill('mo_tmin_diff', id = 'value',
+          breaks = c(-5,-2.5,0,2.5,5)) +
+  tm_borders() +
+  tm_shape(locations_t) +
+  tm_symbols(col='blue', size = 0.25) +
+  tm_layout(title = 'April avg tmin',
+            legend.outside = T)
+
+#may
+tmin_hrus_may<- tmin_hrus_mo %>%
+  filter(month == 5)
+
+hrus_map_tmin_may <- left_join(hrus, tmin_hrus_may, by = 'value')
+
+may_tmin <- tm_shape(hrus_map_tmin_may) +
+  tm_fill('mo_tmin_diff', id = 'value',
+         breaks = c(-5,-2.5,0,2.5,5)) +
+  tm_borders() +
+tm_shape(locations_t) +
+  tm_symbols(col='blue', size = 0.25) +
+  tm_layout(title = 'May avg tmin',
+            legend.outside = T)
+
+#june
+tmin_hrus_jun<- tmin_hrus_mo %>%
+  filter(month == 6)
+
+hrus_map_tmin_jun <- left_join(hrus, tmin_hrus_jun, by = 'value')
+
+jun_tmin <- tm_shape(hrus_map_tmin_jun) +
+  tm_fill('mo_tmin_diff', id = 'value',
+          breaks = c(-5,-2.5,0,2.5,5)) +
+  tm_borders() +
+tm_shape(locations_t) +
+  tm_symbols(col='blue', size = 0.25) +
+  tm_layout(title = 'June avg tmin',
+            legend.outside = T)
+
+tmap_arrange(mar_tmin, apr_tmin, may_tmin, jun_tmin)
+
+```
+
+## Cumulative Precip difference
+
+2011-2020 average of daily station-grid precip for DOY 365 (or 366)
+
+```{r cum precip, echo = F}
+#get rid of a bunch of data
+hru_grid_precip <- hru_grids %>%
+  dplyr::select(c(time, ID, precip)) %>%
+  rename(precip_grid = precip)
+
+hru_statn_precip <- hru_statn %>%
+  dplyr::select(c(time, ID, precip)) %>%
+  rename(precip_statn = precip)
+
+precip_hrus <- left_join(hru_grid_precip, hru_statn_precip, by = c('time', 'ID')) %>%
+  mutate(diff = precip_statn - precip_grid,
+         year = year(time)) %>%
+  group_by(year, ID) %>%
+  mutate(total_diff = cumsum(diff)) %>%
+  filter(time == max(time)) %>%
+  group_by(ID) %>%
+  summarize(precip_avg_cumdiff = mean(total_diff)) %>%
+  rename(value = ID)
+
+hrus_map_precip <- left_join(hrus, precip_hrus, by = 'value')
+
+tmap_mode('view')
+
+locations_p <- locations %>%
+  filter(type == 'precip')
+
+tm_shape(hrus_map_precip) +
+  tm_polygons('precip_avg_cumdiff', midpoint = NA, palette = 'YlGnBu', id = 'value') +
+tm_shape(locations_p) +
+  tm_symbols(col='blue', size=4)
+
+```
+
+## Solar radiation difference
+
+2011-2020 average of daily station-grid solar rad
+
+```{r cum sol rad, echo = F}
+
+#get rid of a bunch of data
+hru_grid_solrad <- hru_grids %>%
+  dplyr::select(c(time, ID, solRad)) %>%
+  rename(solrad_grid = solRad)  %>%
+  group_by(ID) %>%
+  summarize(solrad_all_grid = mean(solrad_grid))
+
+hru_statn_solrad <- hru_statn %>%
+  dplyr::select(c(time, ID, solRad)) %>%
+  rename(solrad_statn = solRad) %>%
+  group_by(ID) %>%
+  summarize(solrad_all_statn = mean(solrad_statn))
+
+solrad_hrus <- left_join(hru_grid_solrad, hru_statn_solrad, by = c('ID')) %>%
+  mutate(diff = solrad_all_statn - solrad_all_grid) %>%
+  rename(value = ID)
+
+hrus_map_solrad <- left_join(hrus, solrad_hrus, by = 'value')
+
+tmap_mode('view')
+
+locations_solrad <- locations %>%
+  dplyr::filter(name %in% c('Gordon_South',
+                        'Betasso', 'Niwot_Snotel'))
+
+tm_shape(hrus_map_solrad) +
+  tm_polygons('diff', midpoint = NA, palette = 'YlOrRd', id = 'value') +
+tm_shape(locations_solrad) +
+  tm_symbols(col='blue', size=4)
+
+```
+
+## RH difference
+
+```{r rh, echo = F}
+
+#get rid of a bunch of data
+hru_grid_rh <- hru_grids %>%
+  dplyr::select(c(time, ID, rhum)) %>%
+  rename(rh_grid = rhum)  %>%
+  group_by(ID) %>%
+  summarize(rh_all_grid = mean(rh_grid))
+
+hru_statn_rh <- hru_statn %>%
+  dplyr::select(c(time, ID, rhum)) %>%
+  rename(rh_statn = rhum) %>%
+  group_by(ID) %>%
+  summarize(rh_all_statn = mean(rh_statn))
+
+rh_hrus <- left_join(hru_grid_rh, hru_statn_rh, by = c('ID')) %>%
+  mutate(diff = rh_all_statn - rh_all_grid) %>%
+  rename(value = ID)
+
+hrus_map_rh <- left_join(hrus, rh_hrus, by = 'value')
+
+tmap_mode('view')
+
+locations_rh <- locations %>%
+  dplyr::filter(name %in% c('Gordon_South', 'Gordon_North',
+                        'Betasso', 'Niwot_Snotel'))
+
+tm_shape(hrus_map_rh) +
+  tm_polygons('diff', midpoint = NA, id = 'value') +
+tm_shape(locations_rh) +
+  tm_symbols(col='blue', size=4)
+
+```
+
+## Average soil sat comparison
+
+```{r soilsat, echo = F}
+
+#get rid of a bunch of data
+hru_grid_soilsat <- hru_grids %>%
+  dplyr::select(c(time, ID, soilSat)) %>%
+  rename(soilsat_grid = soilSat)  %>%
+  group_by(ID) %>%
+  summarize(soilsat_all_grid = mean(soilsat_grid))
+
+hru_statn_soilsat <- hru_statn %>%
+  dplyr::select(c(time, ID, soilSat)) %>%
+  rename(soilsat_statn = soilSat) %>%
+  group_by(ID) %>%
+  summarize(soilsat_all_statn = mean(soilsat_statn))
+
+soilsat_hrus <- left_join(hru_grid_soilsat, hru_statn_soilsat, by = c('ID')) %>%
+  rename(value = ID)
+
+hrus_map_soilsat <- left_join(hrus, soilsat_hrus, by = 'value')
+
+tmap_mode('plot')
+
+soilavg_grid <- tm_shape(hrus_map_soilsat) +
+  tm_polygons('soilsat_all_grid', midpoint = NA, id = 'value',
+              breaks = c(0.0, 0.05, 0.1, 0.15, 0.2, 0.25, 0.3)) +
+  tm_legend(legend.outside = T) +
+  tm_layout(main.title = 'Average soil sat')
+
+soilavg_statn <- tm_shape(hrus_map_soilsat) +
+  tm_polygons('soilsat_all_statn', midpoint = NA, id = 'value',
+              breaks = c(0.0, 0.05, 0.1, 0.15, 0.2, 0.25, 0.3)) +
+  tm_legend(legend.outside = T)
+
+tmap_arrange(soilavg_grid, soilavg_statn)
+
+```
+
+## Average max soil sat comparison
+
+```{r max soilsat, echo = F}
+
+#get rid of a bunch of data
+hru_grid_soilsat_max <- hru_grids %>%
+  dplyr::select(c(time, ID, soilSat)) %>%
+  rename(soilsat_grid = soilSat)  %>%
+  mutate(year = year(time)) %>%
+  group_by(ID, year) %>%
+  summarize(soilsat_yrmax_grid = max(soilsat_grid)) %>%
+  summarize(avg_max_grid = mean(soilsat_yrmax_grid))
+
+hru_statn_soilsat_max <- hru_statn %>%
+  dplyr::select(c(time, ID, soilSat)) %>%
+  rename(soilsat_statn = soilSat) %>%
+  mutate(year = year(time)) %>%
+  group_by(ID, year) %>%
+  summarize(soilsat_yrmax_statn = max(soilsat_statn)) %>%
+  summarize(avg_max_statn = mean(soilsat_yrmax_statn))
+
+soilsat_hrus_max <- left_join(hru_grid_soilsat_max, hru_statn_soilsat_max, by = c('ID')) %>%
+  rename(value = ID)
+
+hrus_map_soilsat_max <- left_join(hrus, soilsat_hrus_max, by = 'value')
+
+tmap_mode('plot')
+
+soilavg_grid_max <- tm_shape(hrus_map_soilsat_max) +
+  tm_polygons('avg_max_grid', midpoint = NA, id = 'value',
+              breaks = c(0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.7)) +
+  tm_legend(legend.outside = T) +
+  tm_layout(main.title = 'Average max soil sat',
+            title.position = c('left', 'top'))
+
+soilavg_statn_max <- tm_shape(hrus_map_soilsat_max) +
+  tm_polygons('avg_max_statn', midpoint = NA, id = 'value',
+              breaks = c(0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.7)) +
+  tm_legend(legend.outside = T)
+
+tmap_arrange(soilavg_grid_max, soilavg_statn_max)
+
+```
+
+## Average ET comparison
+
+```{r et, echo = F}
+#get rid of a bunch of data
+hru_grid_ET <- hru_grids %>%
+  dplyr::select(c(time, ID, actET)) %>%
+  rename(ET_grid = actET)  %>%
+  group_by(ID) %>%
+  summarize(ET_all_grid = mean(ET_grid))
+
+hru_statn_ET <- hru_statn %>%
+  dplyr::select(c(time, ID, actET)) %>%
+  rename(ET_statn = actET) %>%
+  group_by(ID) %>%
+  summarize(ET_all_statn = mean(ET_statn))
+
+ET_hrus <- left_join(hru_grid_ET, hru_statn_ET, by = c('ID')) %>%
+  rename(value = ID)
+
+hrus_map_ET <- left_join(hrus, ET_hrus, by = 'value')
+
+tmap_mode('plot')
+
+ETavg_grid <- tm_shape(hrus_map_ET) +
+  tm_polygons('ET_all_grid', midpoint = NA, id = 'value',
+              breaks = c(0.2, 0.4, 0.6, 0.8, 1.0, 1.2)) +
+  tm_legend(legend.outside = T) +
+  tm_layout(main.title = 'Average ET')
+
+ETavg_statn <- tm_shape(hrus_map_ET) +
+  tm_polygons('ET_all_statn', midpoint = NA, id = 'value',
+             breaks = c(0.2, 0.4, 0.6, 0.8, 1.0, 1.2)) +
+  tm_legend(legend.outside = T)
+
+tmap_arrange(ETavg_grid, ETavg_statn)
+
+```
+
+## Average ET difference
+
+```{r et diff, echo = F}
+
+ET_hrus <- ET_hrus %>%
+  mutate(diff = ET_all_statn - ET_all_grid)
+
+hrus_map_et_diff <- left_join(hrus, ET_hrus, by = 'value')
+
+tmap_mode('plot')
+
+tm_shape(hrus_map_et_diff) +
+  tm_polygons('diff', midpoint = NA, id = 'value')  +
+  tm_legend(legend.outside = T) +
+  tm_layout(main.title = 'Average ET difference')
+
+```
+
+## Average LAI comparison
+
+```{r lai, echo = F}
+
+#get rid of a bunch of data
+hru_grid_LAI <- hru_grids %>%
+  dplyr::select(c(time, ID, LAI)) %>%
+  rename(LAI_grid = LAI)  %>%
+  group_by(ID) %>%
+  summarize(LAI_all_grid = mean(LAI_grid))
+
+hru_statn_LAI <- hru_statn %>%
+  dplyr::select(c(time, ID, LAI)) %>%
+  rename(LAI_statn = LAI) %>%
+  group_by(ID) %>%
+  summarize(LAI_all_statn = mean(LAI_statn))
+
+LAI_hrus <- left_join(hru_grid_LAI, hru_statn_LAI, by = c('ID')) %>%
+  rename(value = ID)
+
+hrus_map_LAI <- left_join(hrus, LAI_hrus, by = 'value')
+
+tmap_mode('view')
+
+LAIavg_grid <- tm_shape(hrus_map_LAI) +
+  tm_polygons('LAI_all_grid', midpoint = NA, id = 'value',
+              breaks = c(1,2,3,4,5)) +
+  tm_legend(legend.outside = T) +
+  tm_layout(main.title = 'Average LAI')
+
+LAIavg_statn <- tm_shape(hrus_map_LAI) +
+  tm_polygons('LAI_all_statn', midpoint = NA, id = 'value',
+              breaks = c(1,2,3,4,5)) +
+  tm_legend(legend.outside = T)
+
+tmap_arrange(LAIavg_grid, LAIavg_statn)
+
+```

### 2023-05-03 38HRU_model/fourmile_model_outputs.Rmd
added Q!

@@
 
-```{echo = FALSE, message = FALSE, warning = FALSE, include = F}
+```{r echo = FALSE, message = FALSE, warning = FALSE, include = F}
+
+rm(statn_2011, statn_2012, statn_2013, statn_2014, statn_2015,
+                  statn_2016, statn_2017, statn_2018, statn_2019, statn_2020,
+                  statn_all., statn_all)
+
+setwd("/Users/megansears/Documents/Repos/fourmile/38HRU_model/cals")
 
 #pull in all filenames with composite
-filenames <- list.files('.', pattern=".csv", full.names=TRUE)
+filenames <- list.files('.', pattern=".csv", full.names=F)
 
@@
 rm(dataframes) #remove dataframes list
+
+```
+
+```{r}
 
@@
 
-name <- levels(burn_params$params)
-
-lapply(name, plot_burnparams)
+name2 <- levels(burn_params$params)
+
+lapply(name2, plot_burnparams)
 
@@
 ```{r hydrographs, echo = F}
+setwd('/Users/megansears/Documents/Repos/fourmile/38HRU_model')
+
 flow <- read_csv('discharge_all.csv') %>%
-  replace(.==-9999, NA)
+  replace(.==-9999, NA) %>%
+  rename(date = time) %>%
+  mutate(date = mdy(date))
 
@@
                                             "all_ensemble" = "orange")) +
-  geom_line(data = bouldcr, aes(date, bouldcr/10), color = 'darkgrey') +
-  scale_y_continuous(name = 'Q_m3s',
-                    sec.axis = sec_axis(~.*10, name='BoulderCr_cms')) +
+  scale_y_continuous(name = 'Q_m3s') +
   theme_bw()
 
-ggplotly(q_ensemble) %>%
-  add_lines(data=bouldcr, x=~date, y=~bouldcr, colors=NULL, yaxis="y2",
-              inherit=FALSE, showlegend = FALSE) %>%
-  layout(yaxis2 = list(overlaying = "y", side = "right",
-                       color = 'darkgray',
-                       title = "BoulderCr_cms"),
-         legend = list(x = 1.1, y = 0.95))
+q_ensemble
 
@@
 
-# Catchment results
-
-## Precip
-
-```{r catch precip, echo = F}
-setwd("/Users/megansears/Documents/Repos/fourmile/catchment_output")
-
-statn <- read_csv('statnall.csv')
-grid <- read_csv('gridall.csv')
-
-grid <- grid %>% mutate(site = 'grid')
-statn <- statn %>% mutate(site = 'statn')
-
-catchment <- bind_rows(grid, statn) %>%
-  mutate(year = as.factor(year(time))) %>%
-  group_by(year, site) %>%
-  mutate(cumulative_p = cumsum(precip))
-
-#plot cumulative precip by year
-plot_cumprecip <- function(calyear) {
-  {catchment %>%
-    filter(year == calyear) %>%
-    ggplot(aes(x = time,
-               y = cumulative_p, color = site)) +
-    geom_line(size=1) +
-    ggtitle(calyear) +
-    ylab('Cumulative precip (mm)') +
-    theme_bw() +
-    theme(axis.text.x = element_text(angle = 45, hjust=1))} %>%
-    ggplotly()
-}
-
-name <- levels(catchment$year)
-
-precip_plots <- lapply(name, plot_cumprecip)
-
-htmltools::tagList(precip_plots)
-
-precip_plots
-
-## total P
-max_cumulativep <- catchment %>%
-  group_by(year, site) %>%
-  summarize(total_cumulativep = max(cumulative_p))
-
-ggplot(max_cumulativep, aes(x=year, y=total_cumulativep, color=site)) +
-  geom_point(size=3) +
-  ggtitle('Total cumulative precip (mm) by year')
-
-```
-
-## Tmean
-
-```{r tmean catch, echo = F}
-## tmean
-tmean <- catchment %>%
-  group_by(year, site) %>%
-  summarize(tmean = mean(tmean)) %>%
-  ggplot(aes(x = year, y=tmean, color = site)) +
-  geom_point(size=3) +
-  ggtitle('Average temp by year')
-
-tmean
-
-```
-
-## RD and RG
-
-```{r rd and rg, echo = F, fig.width = 14, fig.asp = 1, out.width = "100%"}
-
-gw_grid <- read_csv(here('catchment_output/gridall_outlet.csv')) %>%
-  dplyr::select(time, catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w) %>%
-  mutate(source = 'grid')
-
-gw_statn <- read_csv(here('catchment_output/statnall_outlet.csv')) %>%
-  dplyr::select(time, catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w) %>%
-  mutate(source = 'statn')
-
-gw <- bind_rows(gw_grid, gw_statn) %>%
-  mutate(year = year(time)) %>%
-  rename(date = time)
-
-ggplot(gw, aes(x=date, color = source)) +
-  geom_line(aes(y=catchmentRD1_w), size =1) +
-  facet_wrap(~year, scales = 'free', ncol = 2) +
-  scale_x_date(labels = date_format("%b")) +
-  ggtitle('RD1') +
-  theme(text = element_text(size = 20))
-
-ggplot(gw, aes(x=date, color = source)) +
-  geom_line(aes(y=catchmentRD2_w), size =1) +
-  facet_wrap(~year, scales = 'free', ncol = 2) +
-  scale_x_date(labels = date_format("%b")) +
-  ggtitle('RD2') +
-  theme(text = element_text(size = 20))
-
-ggplot(gw, aes(x=date, color = source)) +
-  geom_line(aes(y=catchmentRG1_w), size =1) +
-  facet_wrap(~year, scales = 'free', ncol = 2) +
-  scale_x_date(labels = date_format("%b")) +
-  ggtitle('RG1') +
-  theme(text = element_text(size = 20))
-
-ggplot(gw, aes(x=date, color = source)) +
-  geom_line(aes(y=catchmentRG2_w), size =1) +
-  facet_wrap(~year, scales = 'free', ncol=2) +
-  scale_x_date(labels = date_format("%b")) +
-  ggtitle('RG2') +
-  theme(text = element_text(size = 20))
-
-gw <- gw %>%
-  group_by(year, source) %>%
-  mutate(RD1cumsum = cumsum(catchmentRD1_w),
-         RD2cumsum = cumsum(catchmentRD2_w),
-         RG1cumsum = cumsum(catchmentRG1_w),
-         RG2cumsum = cumsum(catchmentRG2_w))
-
-ggplot(gw, aes(x=date, color = source)) +
-  geom_line(aes(y=RD1cumsum), size =1) +
-  facet_wrap(~year, scales = 'free', ncol=2) +
-  scale_x_date(labels = date_format("%b")) +
-  ggtitle('Cumulative RD1') +
-  theme(text = element_text(size = 20))
-
-ggplot(gw, aes(x=date, color = source)) +
-  geom_line(aes(y=RD2cumsum), size = 1) +
-  facet_wrap(~year, scales = 'free', ncol=2) +
-  scale_x_date(labels = date_format("%b")) +
-  ggtitle('Cumulative RD2') +
-  theme(text = element_text(size = 20))
-
-ggplot(gw, aes(x=date, color = source)) +
-  geom_line(aes(y=RG1cumsum), size  = 1) +
-  facet_wrap(~year, scales = 'free', ncol = 2) +
-  scale_x_date(labels = date_format("%b")) +
-  ggtitle('Cumulative RG1') +
-  theme(text = element_text(size = 20))
-
-ggplot(gw, aes(x=date, color = source)) +
-  geom_line(aes(y=RG2cumsum), size =1) +
-  facet_wrap(~year, scales = 'free', ncol = 2) +
-  scale_x_date(labels = date_format("%b")) +
-  ggtitle('Cumulative RG2') +
-  theme(text = element_text(size = 20))
-
-```
-
-```{r rd and rg sums, echo = F, fig.width = 22, fig.asp = 1.5, out.width = "100%"}
-
-##################
-# all 4 with facets
-
-ggplot(gw, aes(x=date)) +
-  geom_line(aes(y=RG2cumsum, color = 'cumulative RG2'), size =1) +
-  geom_line(aes(y=RG1cumsum, color = 'cumulative RG1'), size =1) +
-  geom_line(aes(y=RD1cumsum, color = 'cumulative RD1'), size =1) +
-  geom_line(aes(y=RD2cumsum, color = 'cumulative RD2'), size =1) +
-  scale_x_date(labels = date_format("%b")) +
-  facet_wrap(~year + source, scales = 'free_x', ncol=2) +
-  ggtitle('Cumulative RD and RG') +
-  theme(text = element_text(size = 24))
-
-```
-
-```{r gw boxplot, echo = F}
-
-gw_maxcumsum <- gw %>%
-  group_by(source, year) %>%
-  summarize(yr_max_RD1 = max(RD1cumsum),
-            yr_max_RD2 = max(RD2cumsum),
-            yr_max_RG1 = max(RG1cumsum),
-            yr_max_RG2 = max(RG2cumsum)) %>%
-  mutate(year = as.factor(year)) %>%
-  pivot_longer(!c(year, source), names_to = 'flow_type', values_to = 'flow_cms')
-
-ggplot(gw_maxcumsum, aes(x = flow_type, y = flow_cms, fill = source)) +
-  geom_boxplot(position = position_dodge(1)) +
-  geom_point(position=position_jitterdodge(),alpha=0.3) +
-  ggtitle('Max annual cumulative sums')
-
-ggplot(gw_maxcumsum, aes(x = flow_type, y = flow_cms, fill = source)) +
-  geom_boxplot(position = position_dodge(1)) +
-  geom_point(position=position_jitterdodge(),alpha=0.3) +
-  #geom_point(aes(color = source)) +
-  facet_wrap(~flow_type, scales = 'free') +
-  ggtitle('Max annual cumulative sums')
-
-```
-
-### RD and RG by season
-
-```{r flow season, echo = F, fig.width = 12, fig.asp = 0.75, out.width = "100%"}
-
-#group by season and get max sums by season
-flow_season <- gw %>%
-  dplyr::select(RD1cumsum, RD2cumsum, RG1cumsum, RG2cumsum, date, year, source) %>%
-  mutate(month = month(date)) %>%
-  mutate(season = case_when(month %in% c(3,4,5,6) ~ 'snowmelt',
-                            month %in% c(7,8,9,10) ~ 'monsoon',
-                            month %in% c(11,12,1,2) ~ 'baseflow')) %>%
-  group_by(source, year, season) %>%
-  summarize(yr_season_RD1 = max(RD1cumsum),
-            yr_season_RD2 = max(RD2cumsum),
-            yr_season_RG1 = max(RG1cumsum),
-            yr_season_RG2 = max(RG2cumsum)) %>%
-            pivot_longer(!c(year, source, season), names_to = 'flow_type', values_to = 'flow_cms')
-
-flow_season %>%
-  ggplot(aes(x = flow_type, y = flow_cms, fill = source)) +
-  geom_boxplot(position = position_dodge(1)) +
-  geom_point(position=position_jitterdodge(),alpha=0.3) +
-  #geom_point(aes(color = source)) +
-  facet_wrap(~season, scales = 'free') +
-  ggtitle('Max annual season cumulative sums') +
-  theme_bw() +
-  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
-  theme(text = element_text(size = 20))
-
-flow_season %>%
-  ggplot(aes(x = flow_type, y = flow_cms, fill = source)) +
-  geom_boxplot(position = position_dodge(1)) +
-  geom_point(position=position_jitterdodge(),alpha=0.3) +
-  #geom_point(aes(color = source)) +
-  facet_wrap(~season + flow_type, scales = 'free') +
-  ggtitle('Max annual season cumulative sums') +
-  theme_bw() +
-  theme(text = element_text(size = 20))
-
-```
-
-# HRU results
-
-## Tmean difference
-
-2011-2020 average of daily station-grid Tmean
-
-```{r cumulative tmean for HRUs, echo = F}
-#grid first
-setwd(here("HRU_output/grid"))
-
-read_ages_grid <- function(dataframe){
-  read_csv(dataframe, skip = 3) %>%
-  slice(3:n()) %>%
-  dplyr::select(-starts_with('@'),
-                -1) %>%
-  mutate(time = ymd(time)) %>%
-  mutate_if(is.character, as.numeric) %>%
-  mutate(source = 'grid')
-
-}
-
-#pull in all filenames with HRU in the name
-filenames <- list.files(".", pattern="HRU", full.names=F)
-
-#read all the csvs using read_ages function
-dataframes <- lapply(filenames, read_ages_grid)
-
-#name all the csvs based on first 6 characters
-names(dataframes) <- substr(filenames, 1, 6)
-
-#bind all and make 1 df
-hru_grids <- dataframes %>%
-  bind_rows()
-
-#statn next
-setwd(here("HRU_output/statn"))
-
-read_ages_statn <- function(dataframe){
-  read_csv(dataframe, skip = 3) %>%
-  slice(3:n()) %>%
-  dplyr::select(-starts_with('@'),
-                -1) %>%
-  mutate(time = ymd(time)) %>%
-  mutate_if(is.character, as.numeric) %>%
-  mutate(source = 'statn')
-
-}
-
-#pull in all filenames with HRU in the name
-filenames <- list.files(".", pattern="HRU", full.names=F)
-
-#read all the csvs using read_ages function
-dataframes <- lapply(filenames, read_ages_statn)
-
-#name all the csvs based on first 6 characters
-names(dataframes) <- substr(filenames, 1, 6)
-
-#bind all and make 1 df
-hru_statn <- dataframes %>%
-  bind_rows()
-
-#get rid of a bunch of data
-hru_grid_tmean <- hru_grids %>%
-  dplyr::select(c(time, ID, tmean)) %>%
-  rename(tmean_grid = tmean)  %>%
-  group_by(ID) %>%
-  summarize(tmean_all_grid = mean(tmean_grid))
-
-hru_statn_tmean <- hru_statn %>%
-  dplyr::select(c(time, ID, tmean)) %>%
-  rename(tmean_statn = tmean) %>%
-  group_by(ID) %>%
-  summarize(tmean_all_statn = mean(tmean_statn))
-
-tmean_hrus <- left_join(hru_grid_tmean, hru_statn_tmean, by = c('ID')) %>%
-  mutate(diff = tmean_all_statn - tmean_all_grid) %>%
-  rename(value = ID)
-
-hrus_map_tmean <- left_join(hrus, tmean_hrus, by = 'value')
-
-tmap_mode('view')
-
-locations_t <- locations %>%
-  dplyr::filter(name %in% c('Gordon_South', 'Gordon_North',
-                        'Betasso', 'Niwot_Snotel',
-                        'University Camp SNTL'))
-
-tm_shape(hrus_map_tmean) +
-  tm_polygons('diff', id = 'value',
-              breaks = c(-6,-4,-2,0,2,4,6)) +
-tm_shape(locations_t) +
-  tm_symbols(col='blue', size=4)
-
-```
-
-## Tmax difference
-
-```{r tmax, echo = F}
-
-tmax_grid <- read_csv(here('HRU_output/reg_tmaxAll_prism.csv'))%>%
-  pivot_longer(cols = `3`:`19`,
-               names_to = 'value',
-               values_to = 'tmax_grid') %>%
-  mutate(time = dmy(time)) %>%
-  group_by(value) %>%
-  summarize(Tmax_mean_grid = mean(tmax_grid))
-
-tmax_statn <- read_csv(here('HRU_output/reg_tmaxAll.csv')) %>%
-  pivot_longer(cols = `3`:`19`,
-               names_to = 'value',
-               values_to = 'tmax_statn') %>%
-  mutate(time = dmy(time)) %>%
-  group_by(value) %>%
-  summarize(Tmax_mean_statn = mean(tmax_statn))
-
-tmax_hrus <- left_join(tmax_grid, tmax_statn, by = c('value')) %>%
-  mutate(diff = Tmax_mean_statn - Tmax_mean_grid,
-         value = as.numeric(value))
-
-hrus_map_tmax <- left_join(hrus, tmax_hrus, by = 'value')
-
-tmap_mode('view')
-
-tm_shape(hrus_map_tmax) +
-  tm_polygons('diff', id = 'value',
-              breaks = c(-6,-4,-2,0,2,4,6)) +
-tm_shape(locations_t) +
-  tm_symbols(col='blue', size=4)
-
-```
-
-## Tmax monthly average
-
-```{r tmax month, echo = F}
-
-tmax_grid_mo <- read_csv(here('HRU_output/reg_tmaxAll_prism.csv')) %>%
-  pivot_longer(cols = `3`:`19`,
-               names_to = 'value',
-               values_to = 'tmax_grid') %>%
-  mutate(time = dmy(time),
-         month = month(time)) %>%
-  filter(month %in% c(3:6)) %>%
-  group_by(value, month) %>%
-  summarize(avg_tmax_grid = mean(tmax_grid))
-
-tmax_statn_mo <- read_csv(here('HRU_output/reg_tmaxAll.csv')) %>%
-  pivot_longer(cols = `3`:`19`,
-               names_to = 'value',
-               values_to = 'tmax_statn') %>%
-  mutate(time = dmy(time),
-         month = month(time)) %>%
-  filter(month %in% c(3:6)) %>%
-  group_by(value, month) %>%
-  summarize(avg_tmax_statn = mean(tmax_statn))
-
-tmax_hrus_mo <- left_join(tmax_grid_mo, tmax_statn_mo, by = c('value', 'month')) %>%
-  mutate(mo_tmax_diff = avg_tmax_statn - avg_tmax_grid,
-         value = as.numeric(value))
-
-tmap_mode('plot')
-
-#march
-tmax_hrus_mar<- tmax_hrus_mo %>%
-  filter(month == 3)
-
-hrus_map_tmax_mar <- left_join(hrus, tmax_hrus_mar, by = 'value')
-
-mar_tmax <- tm_shape(hrus_map_tmax_mar) +
-  #tm_polygons('mo_tmax_diff', id = 'value') +
-  tm_fill('mo_tmax_diff', id = 'value',
-          breaks = c(-6,-4,-2,0,2,4,6)) +
-  tm_borders() +
-  tm_shape(locations_t) +
-  tm_symbols(col='blue', size = 0.25) +
-  tm_layout(title = 'March avg tmax',
-            legend.outside = T)
-
-#april
-tmax_hrus_apr<- tmax_hrus_mo %>%
-  filter(month == 4)
-
-hrus_map_tmax_apr <- left_join(hrus, tmax_hrus_apr, by = 'value')
-
-apr_tmax <- tm_shape(hrus_map_tmax_apr) +
-  tm_fill('mo_tmax_diff', id = 'value',
-          breaks = c(-6,-4,-2,0,2,4,6)) +
-  tm_borders() +
-  tm_shape(locations_t) +
-  tm_symbols(col='blue', size = 0.25) +
-  tm_layout(title = 'April avg tmax',
-            legend.outside = T)
-
-#may
-tmax_hrus_may<- tmax_hrus_mo %>%
-  filter(month == 5)
-
-hrus_map_tmax_may <- left_join(hrus, tmax_hrus_may, by = 'value')
-
-may_tmax <- tm_shape(hrus_map_tmax_may) +
-  tm_fill('mo_tmax_diff', id = 'value',
-         breaks = c(-6,-4,-2,0,2,4,6)) +
-  tm_borders() +
-tm_shape(locations_t) +
-  tm_symbols(col='blue', size = 0.25) +
-  tm_layout(title = 'May avg tmax',
-            legend.outside = T)
-
-#june
-tmax_hrus_jun<- tmax_hrus_mo %>%
-  filter(month == 6)
-
-hrus_map_tmax_jun <- left_join(hrus, tmax_hrus_jun, by = 'value')
-
-jun_tmax <- tm_shape(hrus_map_tmax_jun) +
-  tm_fill('mo_tmax_diff', id = 'value',
-         breaks = c(-6,-4,-2,0,2,4,6)) +
-  tm_borders() +
-tm_shape(locations_t) +
-  tm_symbols(col='blue', size = 0.25) +
-  tm_layout(title = 'June avg tmax',
-            legend.outside = T)
-
-tmap_arrange(mar_tmax, apr_tmax, may_tmax, jun_tmax)
-
-```
-
-## Tmin difference
-
-```{r tmin, echo = F}
-
-tmin_grid <- read_csv(here('HRU_output/reg_tminAll_prism.csv')) %>%
-  pivot_longer(cols = `3`:`19`,
-               names_to = 'value',
-               values_to = 'tmin_grid') %>%
-  mutate(time = dmy(time)) %>%
-  group_by(value) %>%
-  summarize(Tmin_mean_grid = mean(tmin_grid))
-
-tmin_statn <- read_csv(here('HRU_output/reg_tminAll.csv')) %>%
-  pivot_longer(cols = `3`:`19`,
-               names_to = 'value',
-               values_to = 'tmin_statn') %>%
-  mutate(time = dmy(time)) %>%
-  group_by(value) %>%
-  summarize(Tmin_mean_statn = mean(tmin_statn))
-
-tmin_hrus <- left_join(tmin_grid, tmin_statn, by = c('value')) %>%
-  mutate(diff = Tmin_mean_statn - Tmin_mean_grid,
-         value = as.numeric(value))
-
-hrus_map_tmin <- left_join(hrus, tmin_hrus, by = 'value')
-
-tmap_mode('view')
-
-tm_shape(hrus_map_tmin) +
-  tm_polygons('diff', id = 'value',
-              breaks = c(-6,-4,-2,0,2,4,6)) +
-tm_shape(locations_t) +
-  tm_symbols(col='blue', size=4)
-
-```
-
-## Tmin monthly average
-
-```{r tmin month, echo = F}
-tmin_grid_mo <- read_csv(here('HRU_output/reg_tminAll_prism.csv')) %>%
-  pivot_longer(cols = `3`:`19`,
-               names_to = 'value',
-               values_to = 'tmin_grid') %>%
-  mutate(time = dmy(time),
-         month = month(time)) %>%
-  filter(month %in% c(3:6)) %>%
-  group_by(value, month) %>%
-  summarize(avg_tmin_grid = mean(tmin_grid))
-
-tmin_statn_mo <- read_csv(here('HRU_output/reg_tminAll.csv')) %>%
-  pivot_longer(cols = `3`:`19`,
-               names_to = 'value',
-               values_to = 'tmin_statn') %>%
-  mutate(time = dmy(time),
-         month = month(time)) %>%
-  filter(month %in% c(3:6)) %>%
-  group_by(value, month) %>%
-  summarize(avg_tmin_statn = mean(tmin_statn))
-
-tmin_hrus_mo <- left_join(tmin_grid_mo, tmin_statn_mo, by = c('value', 'month')) %>%
-  mutate(mo_tmin_diff = avg_tmin_statn - avg_tmin_grid,
-         value = as.numeric(value))
-
-tmap_mode('plot')
-
-#march
-tmin_hrus_mar<- tmin_hrus_mo %>%
-  filter(month == 3)
-
-hrus_map_tmin_mar <- left_join(hrus, tmin_hrus_mar, by = 'value')
-
-mar_tmin <- tm_shape(hrus_map_tmin_mar) +
-  #tm_polygons('mo_tmin_diff', id = 'value') +
-  tm_fill('mo_tmin_diff', id = 'value',
-          breaks = c(-5,-2.5,0,2.5,5)) +
-  tm_borders() +
-  tm_shape(locations_t) +
-  tm_symbols(col='blue', size = 0.25) +
-  tm_layout(title = 'March avg tmin',
-            legend.outside = T)
-
-#april
-tmin_hrus_apr<- tmin_hrus_mo %>%
-  filter(month == 4)
-
-hrus_map_tmin_apr <- left_join(hrus, tmin_hrus_apr, by = 'value')
-
-apr_tmin <- tm_shape(hrus_map_tmin_apr) +
-  tm_fill('mo_tmin_diff', id = 'value',
-          breaks = c(-5,-2.5,0,2.5,5)) +
-  tm_borders() +
-  tm_shape(locations_t) +
-  tm_symbols(col='blue', size = 0.25) +
-  tm_layout(title = 'April avg tmin',
-            legend.outside = T)
-
-#may
-tmin_hrus_may<- tmin_hrus_mo %>%
-  filter(month == 5)
-
-hrus_map_tmin_may <- left_join(hrus, tmin_hrus_may, by = 'value')
-
-may_tmin <- tm_shape(hrus_map_tmin_may) +
-  tm_fill('mo_tmin_diff', id = 'value',
-         breaks = c(-5,-2.5,0,2.5,5)) +
-  tm_borders() +
-tm_shape(locations_t) +
-  tm_symbols(col='blue', size = 0.25) +
-  tm_layout(title = 'May avg tmin',
-            legend.outside = T)
-
-#june
-tmin_hrus_jun<- tmin_hrus_mo %>%
-  filter(month == 6)
-
-hrus_map_tmin_jun <- left_join(hrus, tmin_hrus_jun, by = 'value')
-
-jun_tmin <- tm_shape(hrus_map_tmin_jun) +
-  tm_fill('mo_tmin_diff', id = 'value',
-          breaks = c(-5,-2.5,0,2.5,5)) +
-  tm_borders() +
-tm_shape(locations_t) +
-  tm_symbols(col='blue', size = 0.25) +
-  tm_layout(title = 'June avg tmin',
-            legend.outside = T)
-
-tmap_arrange(mar_tmin, apr_tmin, may_tmin, jun_tmin)
-
-```
-
-## Cumulative Precip difference
-
-2011-2020 average of daily station-grid precip for DOY 365 (or 366)
-
-```{r cum precip, echo = F}
-#get rid of a bunch of data
-hru_grid_precip <- hru_grids %>%
-  dplyr::select(c(time, ID, precip)) %>%
-  rename(precip_grid = precip)
-
-hru_statn_precip <- hru_statn %>%
-  dplyr::select(c(time, ID, precip)) %>%
-  rename(precip_statn = precip)
-
-precip_hrus <- left_join(hru_grid_precip, hru_statn_precip, by = c('time', 'ID')) %>%
-  mutate(diff = precip_statn - precip_grid,
-         year = year(time)) %>%
-  group_by(year, ID) %>%
-  mutate(total_diff = cumsum(diff)) %>%
-  filter(time == max(time)) %>%
-  group_by(ID) %>%
-  summarize(precip_avg_cumdiff = mean(total_diff)) %>%
-  rename(value = ID)
-
-hrus_map_precip <- left_join(hrus, precip_hrus, by = 'value')
-
-tmap_mode('view')
-
-locations_p <- locations %>%
-  filter(type == 'precip')
-
-tm_shape(hrus_map_precip) +
-  tm_polygons('precip_avg_cumdiff', midpoint = NA, palette = 'YlGnBu', id = 'value') +
-tm_shape(locations_p) +
-  tm_symbols(col='blue', size=4)
-
-```
-
-## Solar radiation difference
-
-2011-2020 average of daily station-grid solar rad
-
-```{r cum sol rad, echo = F}
-
-#get rid of a bunch of data
-hru_grid_solrad <- hru_grids %>%
-  dplyr::select(c(time, ID, solRad)) %>%
-  rename(solrad_grid = solRad)  %>%
-  group_by(ID) %>%
-  summarize(solrad_all_grid = mean(solrad_grid))
-
-hru_statn_solrad <- hru_statn %>%
-  dplyr::select(c(time, ID, solRad)) %>%
-  rename(solrad_statn = solRad) %>%
-  group_by(ID) %>%
-  summarize(solrad_all_statn = mean(solrad_statn))
-
-solrad_hrus <- left_join(hru_grid_solrad, hru_statn_solrad, by = c('ID')) %>%
-  mutate(diff = solrad_all_statn - solrad_all_grid) %>%
-  rename(value = ID)
-
-hrus_map_solrad <- left_join(hrus, solrad_hrus, by = 'value')
-
-tmap_mode('view')
-
-locations_solrad <- locations %>%
-  dplyr::filter(name %in% c('Gordon_South',
-                        'Betasso', 'Niwot_Snotel'))
-
-tm_shape(hrus_map_solrad) +
-  tm_polygons('diff', midpoint = NA, palette = 'YlOrRd', id = 'value') +
-tm_shape(locations_solrad) +
-  tm_symbols(col='blue', size=4)
-
-```
-
-## RH difference
-
-```{r rh, echo = F}
-
-#get rid of a bunch of data
-hru_grid_rh <- hru_grids %>%
-  dplyr::select(c(time, ID, rhum)) %>%
-  rename(rh_grid = rhum)  %>%
-  group_by(ID) %>%
-  summarize(rh_all_grid = mean(rh_grid))
-
-hru_statn_rh <- hru_statn %>%
-  dplyr::select(c(time, ID, rhum)) %>%
-  rename(rh_statn = rhum) %>%
-  group_by(ID) %>%
-  summarize(rh_all_statn = mean(rh_statn))
-
-rh_hrus <- left_join(hru_grid_rh, hru_statn_rh, by = c('ID')) %>%
-  mutate(diff = rh_all_statn - rh_all_grid) %>%
-  rename(value = ID)
-
-hrus_map_rh <- left_join(hrus, rh_hrus, by = 'value')
-
-tmap_mode('view')
-
-locations_rh <- locations %>%
-  dplyr::filter(name %in% c('Gordon_South', 'Gordon_North',
-                        'Betasso', 'Niwot_Snotel'))
-
-tm_shape(hrus_map_rh) +
-  tm_polygons('diff', midpoint = NA, id = 'value') +
-tm_shape(locations_rh) +
-  tm_symbols(col='blue', size=4)
-
-```
-
-## Average soil sat comparison
-
-```{r soilsat, echo = F}
-
-#get rid of a bunch of data
-hru_grid_soilsat <- hru_grids %>%
-  dplyr::select(c(time, ID, soilSat)) %>%
-  rename(soilsat_grid = soilSat)  %>%
-  group_by(ID) %>%
-  summarize(soilsat_all_grid = mean(soilsat_grid))
-
-hru_statn_soilsat <- hru_statn %>%
-  dplyr::select(c(time, ID, soilSat)) %>%
-  rename(soilsat_statn = soilSat) %>%
-  group_by(ID) %>%
-  summarize(soilsat_all_statn = mean(soilsat_statn))
-
-soilsat_hrus <- left_join(hru_grid_soilsat, hru_statn_soilsat, by = c('ID')) %>%
-  rename(value = ID)
-
-hrus_map_soilsat <- left_join(hrus, soilsat_hrus, by = 'value')
-
-tmap_mode('plot')
-
-soilavg_grid <- tm_shape(hrus_map_soilsat) +
-  tm_polygons('soilsat_all_grid', midpoint = NA, id = 'value',
-              breaks = c(0.0, 0.05, 0.1, 0.15, 0.2, 0.25, 0.3)) +
-  tm_legend(legend.outside = T) +
-  tm_layout(main.title = 'Average soil sat')
-
-soilavg_statn <- tm_shape(hrus_map_soilsat) +
-  tm_polygons('soilsat_all_statn', midpoint = NA, id = 'value',
-              breaks = c(0.0, 0.05, 0.1, 0.15, 0.2, 0.25, 0.3)) +
-  tm_legend(legend.outside = T)
-
-tmap_arrange(soilavg_grid, soilavg_statn)
-
-```
-
-## Average max soil sat comparison
-
-```{r max soilsat, echo = F}
-
-#get rid of a bunch of data
-hru_grid_soilsat_max <- hru_grids %>%
-  dplyr::select(c(time, ID, soilSat)) %>%
-  rename(soilsat_grid = soilSat)  %>%
-  mutate(year = year(time)) %>%
-  group_by(ID, year) %>%
-  summarize(soilsat_yrmax_grid = max(soilsat_grid)) %>%
-  summarize(avg_max_grid = mean(soilsat_yrmax_grid))
-
-hru_statn_soilsat_max <- hru_statn %>%
-  dplyr::select(c(time, ID, soilSat)) %>%
-  rename(soilsat_statn = soilSat) %>%
-  mutate(year = year(time)) %>%
-  group_by(ID, year) %>%
-  summarize(soilsat_yrmax_statn = max(soilsat_statn)) %>%
-  summarize(avg_max_statn = mean(soilsat_yrmax_statn))
-
-soilsat_hrus_max <- left_join(hru_grid_soilsat_max, hru_statn_soilsat_max, by = c('ID')) %>%
-  rename(value = ID)
-
-hrus_map_soilsat_max <- left_join(hrus, soilsat_hrus_max, by = 'value')
-
-tmap_mode('plot')
-
-soilavg_grid_max <- tm_shape(hrus_map_soilsat_max) +
-  tm_polygons('avg_max_grid', midpoint = NA, id = 'value',
-              breaks = c(0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.7)) +
-  tm_legend(legend.outside = T) +
-  tm_layout(main.title = 'Average max soil sat',
-            title.position = c('left', 'top'))
-
-soilavg_statn_max <- tm_shape(hrus_map_soilsat_max) +
-  tm_polygons('avg_max_statn', midpoint = NA, id = 'value',
-              breaks = c(0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.7)) +
-  tm_legend(legend.outside = T)
-
-tmap_arrange(soilavg_grid_max, soilavg_statn_max)
-
-```
-
-## Average ET comparison
-
-```{r et, echo = F}
-#get rid of a bunch of data
-hru_grid_ET <- hru_grids %>%
-  dplyr::select(c(time, ID, actET)) %>%
-  rename(ET_grid = actET)  %>%
-  group_by(ID) %>%
-  summarize(ET_all_grid = mean(ET_grid))
-
-hru_statn_ET <- hru_statn %>%
-  dplyr::select(c(time, ID, actET)) %>%
-  rename(ET_statn = actET) %>%
-  group_by(ID) %>%
-  summarize(ET_all_statn = mean(ET_statn))
-
-ET_hrus <- left_join(hru_grid_ET, hru_statn_ET, by = c('ID')) %>%
-  rename(value = ID)
-
-hrus_map_ET <- left_join(hrus, ET_hrus, by = 'value')
-
-tmap_mode('plot')
-
-ETavg_grid <- tm_shape(hrus_map_ET) +
-  tm_polygons('ET_all_grid', midpoint = NA, id = 'value',
-              breaks = c(0.2, 0.4, 0.6, 0.8, 1.0, 1.2)) +
-  tm_legend(legend.outside = T) +
-  tm_layout(main.title = 'Average ET')
-
-ETavg_statn <- tm_shape(hrus_map_ET) +
-  tm_polygons('ET_all_statn', midpoint = NA, id = 'value',
-             breaks = c(0.2, 0.4, 0.6, 0.8, 1.0, 1.2)) +
-  tm_legend(legend.outside = T)
-
-tmap_arrange(ETavg_grid, ETavg_statn)
-
-```
-
-## Average ET difference
-
-```{r et diff, echo = F}
-
-ET_hrus <- ET_hrus %>%
-  mutate(diff = ET_all_statn - ET_all_grid)
-
-hrus_map_et_diff <- left_join(hrus, ET_hrus, by = 'value')
-
-tmap_mode('plot')
-
-tm_shape(hrus_map_et_diff) +
-  tm_polygons('diff', midpoint = NA, id = 'value')  +
-  tm_legend(legend.outside = T) +
-  tm_layout(main.title = 'Average ET difference')
-
-```
-
-## Average LAI comparison
-
-```{r lai, echo = F}
-
-#get rid of a bunch of data
-hru_grid_LAI <- hru_grids %>%
-  dplyr::select(c(time, ID, LAI)) %>%
-  rename(LAI_grid = LAI)  %>%
-  group_by(ID) %>%
-  summarize(LAI_all_grid = mean(LAI_grid))
-
-hru_statn_LAI <- hru_statn %>%
-  dplyr::select(c(time, ID, LAI)) %>%
-  rename(LAI_statn = LAI) %>%
-  group_by(ID) %>%
-  summarize(LAI_all_statn = mean(LAI_statn))
-
-LAI_hrus <- left_join(hru_grid_LAI, hru_statn_LAI, by = c('ID')) %>%
-  rename(value = ID)
-
-hrus_map_LAI <- left_join(hrus, LAI_hrus, by = 'value')
-
-tmap_mode('view')
-
-LAIavg_grid <- tm_shape(hrus_map_LAI) +
-  tm_polygons('LAI_all_grid', midpoint = NA, id = 'value',
-              breaks = c(1,2,3,4,5)) +
-  tm_legend(legend.outside = T) +
-  tm_layout(main.title = 'Average LAI')
-
-LAIavg_statn <- tm_shape(hrus_map_LAI) +
-  tm_polygons('LAI_all_statn', midpoint = NA, id = 'value',
-              breaks = c(1,2,3,4,5)) +
-  tm_legend(legend.outside = T)
-
-tmap_arrange(LAIavg_grid, LAIavg_statn)
-
-```
+<!-- # Catchment results -->
+
+<!-- ## Precip -->
+
+<!-- ```{r catch precip, echo = F} -->
+<!-- setwd("/Users/megansears/Documents/Repos/fourmile/catchment_output") -->
+
+<!-- statn <- read_csv('statnall.csv') -->
+<!-- grid <- read_csv('gridall.csv') -->
+
+<!-- grid <- grid %>% mutate(site = 'grid') -->
+<!-- statn <- statn %>% mutate(site = 'statn') -->
+
+<!-- catchment <- bind_rows(grid, statn) %>% -->
+<!--   mutate(year = as.factor(year(time))) %>% -->
+<!--   group_by(year, site) %>% -->
+<!--   mutate(cumulative_p = cumsum(precip)) -->
+
+<!-- #plot cumulative precip by year -->
+<!-- plot_cumprecip <- function(calyear) { -->
+<!--   {catchment %>% -->
+<!--     filter(year == calyear) %>% -->
+<!--     ggplot(aes(x = time, -->
+<!--                y = cumulative_p, color = site)) + -->
+<!--     geom_line(size=1) + -->
+<!--     ggtitle(calyear) + -->
+<!--     ylab('Cumulative precip (mm)') + -->
+<!--     theme_bw() + -->
+<!--     theme(axis.text.x = element_text(angle = 45, hjust=1))} %>% -->
+<!--     ggplotly() -->
+<!-- } -->
+
+<!-- name <- levels(catchment$year) -->
+
+<!-- precip_plots <- lapply(name, plot_cumprecip) -->
+
+<!-- htmltools::tagList(precip_plots) -->
+
+<!-- precip_plots -->
+
+<!-- ## total P -->
+<!-- max_cumulativep <- catchment %>% -->
+<!--   group_by(year, site) %>% -->
+<!--   summarize(total_cumulativep = max(cumulative_p)) -->
+
+<!-- ggplot(max_cumulativep, aes(x=year, y=total_cumulativep, color=site)) + -->
+<!--   geom_point(size=3) + -->
+<!--   ggtitle('Total cumulative precip (mm) by year') -->
+
+<!-- ``` -->
+
+<!-- ## Tmean -->
+
+<!-- ```{r tmean catch, echo = F} -->
+<!-- ## tmean -->
+<!-- tmean <- catchment %>% -->
+<!--   group_by(year, site) %>% -->
+<!--   summarize(tmean = mean(tmean)) %>% -->
+<!--   ggplot(aes(x = year, y=tmean, color = site)) + -->
+<!--   geom_point(size=3) + -->
+<!--   ggtitle('Average temp by year') -->
+
+<!-- tmean -->
+
+<!-- ``` -->
+
+<!-- ## RD and RG -->
+
+<!-- ```{r rd and rg, echo = F, fig.width = 14, fig.asp = 1, out.width = "100%"} -->
+
+<!-- gw_grid <- read_csv(here('catchment_output/gridall_outlet.csv')) %>% -->
+<!--   dplyr::select(time, catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w) %>% -->
+<!--   mutate(source = 'grid') -->
+
+<!-- gw_statn <- read_csv(here('catchment_output/statnall_outlet.csv')) %>% -->
+<!--   dplyr::select(time, catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w) %>% -->
+<!--   mutate(source = 'statn') -->
+
+<!-- gw <- bind_rows(gw_grid, gw_statn) %>% -->
+<!--   mutate(year = year(time)) %>% -->
+<!--   rename(date = time) -->
+
+<!-- ggplot(gw, aes(x=date, color = source)) + -->
+<!--   geom_line(aes(y=catchmentRD1_w), size =1) + -->
+<!--   facet_wrap(~year, scales = 'free', ncol = 2) + -->
+<!--   scale_x_date(labels = date_format("%b")) + -->
+<!--   ggtitle('RD1') + -->
+<!--   theme(text = element_text(size = 20)) -->
+
+<!-- ggplot(gw, aes(x=date, color = source)) + -->
+<!--   geom_line(aes(y=catchmentRD2_w), size =1) + -->
+<!--   facet_wrap(~year, scales = 'free', ncol = 2) + -->
+<!--   scale_x_date(labels = date_format("%b")) + -->
+<!--   ggtitle('RD2') + -->
+<!--   theme(text = element_text(size = 20)) -->
+
+<!-- ggplot(gw, aes(x=date, color = source)) + -->
+<!--   geom_line(aes(y=catchmentRG1_w), size =1) + -->
+<!--   facet_wrap(~year, scales = 'free', ncol = 2) + -->
+<!--   scale_x_date(labels = date_format("%b")) + -->
+<!--   ggtitle('RG1') + -->
+<!--   theme(text = element_text(size = 20)) -->
+
+<!-- ggplot(gw, aes(x=date, color = source)) + -->
+<!--   geom_line(aes(y=catchmentRG2_w), size =1) + -->
+<!--   facet_wrap(~year, scales = 'free', ncol=2) + -->
+<!--   scale_x_date(labels = date_format("%b")) + -->
+<!--   ggtitle('RG2') + -->
+<!--   theme(text = element_text(size = 20)) -->
+
+<!-- gw <- gw %>% -->
+<!--   group_by(year, source) %>% -->
+<!--   mutate(RD1cumsum = cumsum(catchmentRD1_w), -->
+<!--          RD2cumsum = cumsum(catchmentRD2_w), -->
+<!--          RG1cumsum = cumsum(catchmentRG1_w), -->
+<!--          RG2cumsum = cumsum(catchmentRG2_w)) -->
+
+<!-- ggplot(gw, aes(x=date, color = source)) + -->
+<!--   geom_line(aes(y=RD1cumsum), size =1) + -->
+<!--   facet_wrap(~year, scales = 'free', ncol=2) + -->
+<!--   scale_x_date(labels = date_format("%b")) + -->
+<!--   ggtitle('Cumulative RD1') + -->
+<!--   theme(text = element_text(size = 20)) -->
+
+<!-- ggplot(gw, aes(x=date, color = source)) + -->
+<!--   geom_line(aes(y=RD2cumsum), size = 1) + -->
+<!--   facet_wrap(~year, scales = 'free', ncol=2) + -->
+<!--   scale_x_date(labels = date_format("%b")) + -->
+<!--   ggtitle('Cumulative RD2') + -->
+<!--   theme(text = element_text(size = 20)) -->
+
+<!-- ggplot(gw, aes(x=date, color = source)) + -->
+<!--   geom_line(aes(y=RG1cumsum), size  = 1) + -->
+<!--   facet_wrap(~year, scales = 'free', ncol = 2) + -->
+<!--   scale_x_date(labels = date_format("%b")) + -->
+<!--   ggtitle('Cumulative RG1') + -->
+<!--   theme(text = element_text(size = 20)) -->
+
+<!-- ggplot(gw, aes(x=date, color = source)) + -->
+<!--   geom_line(aes(y=RG2cumsum), size =1) + -->
+<!--   facet_wrap(~year, scales = 'free', ncol = 2) + -->
+<!--   scale_x_date(labels = date_format("%b")) + -->
+<!--   ggtitle('Cumulative RG2') + -->
+<!--   theme(text = element_text(size = 20)) -->
+
+<!-- ``` -->
+
+<!-- ```{r rd and rg sums, echo = F, fig.width = 22, fig.asp = 1.5, out.width = "100%"} -->
+
+<!-- ################## -->
+<!-- # all 4 with facets -->
+
+<!-- ggplot(gw, aes(x=date)) + -->
+<!--   geom_line(aes(y=RG2cumsum, color = 'cumulative RG2'), size =1) + -->
+<!--   geom_line(aes(y=RG1cumsum, color = 'cumulative RG1'), size =1) + -->
+<!--   geom_line(aes(y=RD1cumsum, color = 'cumulative RD1'), size =1) + -->
+<!--   geom_line(aes(y=RD2cumsum, color = 'cumulative RD2'), size =1) + -->
+<!--   scale_x_date(labels = date_format("%b")) + -->
+<!--   facet_wrap(~year + source, scales = 'free_x', ncol=2) + -->
+<!--   ggtitle('Cumulative RD and RG') + -->
+<!--   theme(text = element_text(size = 24)) -->
+
+<!-- ``` -->
+
+<!-- ```{r gw boxplot, echo = F} -->
+
+<!-- gw_maxcumsum <- gw %>% -->
+<!--   group_by(source, year) %>% -->
+<!--   summarize(yr_max_RD1 = max(RD1cumsum), -->
+<!--             yr_max_RD2 = max(RD2cumsum), -->
+<!--             yr_max_RG1 = max(RG1cumsum), -->
+<!--             yr_max_RG2 = max(RG2cumsum)) %>% -->
+<!--   mutate(year = as.factor(year)) %>% -->
+<!--   pivot_longer(!c(year, source), names_to = 'flow_type', values_to = 'flow_cms') -->
+
+<!-- ggplot(gw_maxcumsum, aes(x = flow_type, y = flow_cms, fill = source)) + -->
+<!--   geom_boxplot(position = position_dodge(1)) + -->
+<!--   geom_point(position=position_jitterdodge(),alpha=0.3) + -->
+<!--   ggtitle('Max annual cumulative sums') -->
+
+<!-- ggplot(gw_maxcumsum, aes(x = flow_type, y = flow_cms, fill = source)) + -->
+<!--   geom_boxplot(position = position_dodge(1)) + -->
+<!--   geom_point(position=position_jitterdodge(),alpha=0.3) + -->
+<!--   #geom_point(aes(color = source)) + -->
+<!--   facet_wrap(~flow_type, scales = 'free') + -->
+<!--   ggtitle('Max annual cumulative sums') -->
+
+<!-- ``` -->
+
+<!-- ### RD and RG by season -->
+
+<!-- ```{r flow season, echo = F, fig.width = 12, fig.asp = 0.75, out.width = "100%"} -->
+
+<!-- #group by season and get max sums by season -->
+<!-- flow_season <- gw %>% -->
+<!--   dplyr::select(RD1cumsum, RD2cumsum, RG1cumsum, RG2cumsum, date, year, source) %>% -->
+<!--   mutate(month = month(date)) %>% -->
+<!--   mutate(season = case_when(month %in% c(3,4,5,6) ~ 'snowmelt', -->
+<!--                             month %in% c(7,8,9,10) ~ 'monsoon', -->
+<!--                             month %in% c(11,12,1,2) ~ 'baseflow')) %>% -->
+<!--   group_by(source, year, season) %>% -->
+<!--   summarize(yr_season_RD1 = max(RD1cumsum), -->
+<!--             yr_season_RD2 = max(RD2cumsum), -->
+<!--             yr_season_RG1 = max(RG1cumsum), -->
+<!--             yr_season_RG2 = max(RG2cumsum)) %>% -->
+<!--             pivot_longer(!c(year, source, season), names_to = 'flow_type', values_to = 'flow_cms') -->
+
+<!-- flow_season %>% -->
+<!--   ggplot(aes(x = flow_type, y = flow_cms, fill = source)) + -->
+<!--   geom_boxplot(position = position_dodge(1)) + -->
+<!--   geom_point(position=position_jitterdodge(),alpha=0.3) + -->
+<!--   #geom_point(aes(color = source)) + -->
+<!--   facet_wrap(~season, scales = 'free') + -->
+<!--   ggtitle('Max annual season cumulative sums') + -->
+<!--   theme_bw() + -->
+<!--   theme(axis.text.x = element_text(angle = 45, hjust = 1)) + -->
+<!--   theme(text = element_text(size = 20)) -->
+
+<!-- flow_season %>% -->
+<!--   ggplot(aes(x = flow_type, y = flow_cms, fill = source)) + -->
+<!--   geom_boxplot(position = position_dodge(1)) + -->
+<!--   geom_point(position=position_jitterdodge(),alpha=0.3) + -->
+<!--   #geom_point(aes(color = source)) + -->
+<!--   facet_wrap(~season + flow_type, scales = 'free') + -->
+<!--   ggtitle('Max annual season cumulative sums') + -->
+<!--   theme_bw() + -->
+<!--   theme(text = element_text(size = 20)) -->
+
+<!-- ``` -->
+
+<!-- # HRU results -->
+
+<!-- ## Tmean difference -->
+
+<!-- 2011-2020 average of daily station-grid Tmean -->
+
+<!-- ```{r cumulative tmean for HRUs, echo = F} -->
+<!-- #grid first -->
+<!-- setwd(here("HRU_output/grid")) -->
+
+<!-- read_ages_grid <- function(dataframe){ -->
+<!--   read_csv(dataframe, skip = 3) %>% -->
+<!--   slice(3:n()) %>% -->
+<!--   dplyr::select(-starts_with('@'), -->
+<!--                 -1) %>% -->
+<!--   mutate(time = ymd(time)) %>% -->
+<!--   mutate_if(is.character, as.numeric) %>% -->
+<!--   mutate(source = 'grid') -->
+
+<!-- } -->
+
+<!-- #pull in all filenames with HRU in the name -->
+<!-- filenames <- list.files(".", pattern="HRU", full.names=F) -->
+
+<!-- #read all the csvs using read_ages function -->
+<!-- dataframes <- lapply(filenames, read_ages_grid) -->
+
+<!-- #name all the csvs based on first 6 characters -->
+<!-- names(dataframes) <- substr(filenames, 1, 6) -->
+
+<!-- #bind all and make 1 df -->
+<!-- hru_grids <- dataframes %>% -->
+<!--   bind_rows() -->
+
+<!-- #statn next -->
+<!-- setwd(here("HRU_output/statn")) -->
+
+<!-- read_ages_statn <- function(dataframe){ -->
+<!--   read_csv(dataframe, skip = 3) %>% -->
+<!--   slice(3:n()) %>% -->
+<!--   dplyr::select(-starts_with('@'), -->
+<!--                 -1) %>% -->
+<!--   mutate(time = ymd(time)) %>% -->
+<!--   mutate_if(is.character, as.numeric) %>% -->
+<!--   mutate(source = 'statn') -->
+
+<!-- } -->
+
+<!-- #pull in all filenames with HRU in the name -->
+<!-- filenames <- list.files(".", pattern="HRU", full.names=F) -->
+
+<!-- #read all the csvs using read_ages function -->
+<!-- dataframes <- lapply(filenames, read_ages_statn) -->
+
+<!-- #name all the csvs based on first 6 characters -->
+<!-- names(dataframes) <- substr(filenames, 1, 6) -->
+
+<!-- #bind all and make 1 df -->
+<!-- hru_statn <- dataframes %>% -->
+<!--   bind_rows() -->
+
+<!-- #get rid of a bunch of data -->
+<!-- hru_grid_tmean <- hru_grids %>% -->
+<!--   dplyr::select(c(time, ID, tmean)) %>% -->
+<!--   rename(tmean_grid = tmean)  %>% -->
+<!--   group_by(ID) %>% -->
+<!--   summarize(tmean_all_grid = mean(tmean_grid)) -->
+
+<!-- hru_statn_tmean <- hru_statn %>% -->
+<!--   dplyr::select(c(time, ID, tmean)) %>% -->
+<!--   rename(tmean_statn = tmean) %>% -->
+<!--   group_by(ID) %>% -->
+<!--   summarize(tmean_all_statn = mean(tmean_statn)) -->
+
+<!-- tmean_hrus <- left_join(hru_grid_tmean, hru_statn_tmean, by = c('ID')) %>% -->
+<!--   mutate(diff = tmean_all_statn - tmean_all_grid) %>% -->
+<!--   rename(value = ID) -->
+
+<!-- hrus_map_tmean <- left_join(hrus, tmean_hrus, by = 'value') -->
+
+<!-- tmap_mode('view') -->
+
+<!-- locations_t <- locations %>% -->
+<!--   dplyr::filter(name %in% c('Gordon_South', 'Gordon_North', -->
+<!--                         'Betasso', 'Niwot_Snotel', -->
+<!--                         'University Camp SNTL')) -->
+
+<!-- tm_shape(hrus_map_tmean) + -->
+<!--   tm_polygons('diff', id = 'value', -->
+<!--               breaks = c(-6,-4,-2,0,2,4,6)) + -->
+<!-- tm_shape(locations_t) + -->
+<!--   tm_symbols(col='blue', size=4) -->
+
+<!-- ``` -->
+
+<!-- ## Tmax difference -->
+
+<!-- ```{r tmax, echo = F} -->
+
+<!-- tmax_grid <- read_csv(here('HRU_output/reg_tmaxAll_prism.csv'))%>% -->
+<!--   pivot_longer(cols = `3`:`19`, -->
+<!--                names_to = 'value', -->
+<!--                values_to = 'tmax_grid') %>% -->
+<!--   mutate(time = dmy(time)) %>% -->
+<!--   group_by(value) %>% -->
+<!--   summarize(Tmax_mean_grid = mean(tmax_grid)) -->
+
+<!-- tmax_statn <- read_csv(here('HRU_output/reg_tmaxAll.csv')) %>% -->
+<!--   pivot_longer(cols = `3`:`19`, -->
+<!--                names_to = 'value', -->
+<!--                values_to = 'tmax_statn') %>% -->
+<!--   mutate(time = dmy(time)) %>% -->
+<!--   group_by(value) %>% -->
+<!--   summarize(Tmax_mean_statn = mean(tmax_statn)) -->
+
+<!-- tmax_hrus <- left_join(tmax_grid, tmax_statn, by = c('value')) %>% -->
+<!--   mutate(diff = Tmax_mean_statn - Tmax_mean_grid, -->
+<!--          value = as.numeric(value)) -->
+
+<!-- hrus_map_tmax <- left_join(hrus, tmax_hrus, by = 'value') -->
+
+<!-- tmap_mode('view') -->
+
+<!-- tm_shape(hrus_map_tmax) + -->
+<!--   tm_polygons('diff', id = 'value', -->
+<!--               breaks = c(-6,-4,-2,0,2,4,6)) + -->
+<!-- tm_shape(locations_t) + -->
+<!--   tm_symbols(col='blue', size=4) -->
+
+<!-- ``` -->
+
+<!-- ## Tmax monthly average -->
+
+<!-- ```{r tmax month, echo = F} -->
+
+<!-- tmax_grid_mo <- read_csv(here('HRU_output/reg_tmaxAll_prism.csv')) %>% -->
+<!--   pivot_longer(cols = `3`:`19`, -->
+<!--                names_to = 'value', -->
+<!--                values_to = 'tmax_grid') %>% -->
+<!--   mutate(time = dmy(time), -->
+<!--          month = month(time)) %>% -->
+<!--   filter(month %in% c(3:6)) %>% -->
+<!--   group_by(value, month) %>% -->
+<!--   summarize(avg_tmax_grid = mean(tmax_grid)) -->
+
+<!-- tmax_statn_mo <- read_csv(here('HRU_output/reg_tmaxAll.csv')) %>% -->
+<!--   pivot_longer(cols = `3`:`19`, -->
+<!--                names_to = 'value', -->
+<!--                values_to = 'tmax_statn') %>% -->
+<!--   mutate(time = dmy(time), -->
+<!--          month = month(time)) %>% -->
+<!--   filter(month %in% c(3:6)) %>% -->
+<!--   group_by(value, month) %>% -->
+<!--   summarize(avg_tmax_statn = mean(tmax_statn)) -->
+
+<!-- tmax_hrus_mo <- left_join(tmax_grid_mo, tmax_statn_mo, by = c('value', 'month')) %>% -->
+<!--   mutate(mo_tmax_diff = avg_tmax_statn - avg_tmax_grid, -->
+<!--          value = as.numeric(value)) -->
+
+<!-- tmap_mode('plot') -->
+
+<!-- #march -->
+<!-- tmax_hrus_mar<- tmax_hrus_mo %>% -->
+<!--   filter(month == 3) -->
+
+<!-- hrus_map_tmax_mar <- left_join(hrus, tmax_hrus_mar, by = 'value') -->
+
+<!-- mar_tmax <- tm_shape(hrus_map_tmax_mar) + -->
+<!--   #tm_polygons('mo_tmax_diff', id = 'value') + -->
+<!--   tm_fill('mo_tmax_diff', id = 'value', -->
+<!--           breaks = c(-6,-4,-2,0,2,4,6)) + -->
+<!--   tm_borders() + -->
+<!--   tm_shape(locations_t) + -->
+<!--   tm_symbols(col='blue', size = 0.25) + -->
+<!--   tm_layout(title = 'March avg tmax', -->
+<!--             legend.outside = T) -->
+
+<!-- #april -->
+<!-- tmax_hrus_apr<- tmax_hrus_mo %>% -->
+<!--   filter(month == 4) -->
+
+<!-- hrus_map_tmax_apr <- left_join(hrus, tmax_hrus_apr, by = 'value') -->
+
+<!-- apr_tmax <- tm_shape(hrus_map_tmax_apr) + -->
+<!--   tm_fill('mo_tmax_diff', id = 'value', -->
+<!--           breaks = c(-6,-4,-2,0,2,4,6)) + -->
+<!--   tm_borders() + -->
+<!--   tm_shape(locations_t) + -->
+<!--   tm_symbols(col='blue', size = 0.25) + -->
+<!--   tm_layout(title = 'April avg tmax', -->
+<!--             legend.outside = T) -->
+
+<!-- #may -->
+<!-- tmax_hrus_may<- tmax_hrus_mo %>% -->
+<!--   filter(month == 5) -->
+
+<!-- hrus_map_tmax_may <- left_join(hrus, tmax_hrus_may, by = 'value') -->
+
+<!-- may_tmax <- tm_shape(hrus_map_tmax_may) + -->
+<!--   tm_fill('mo_tmax_diff', id = 'value', -->
+<!--          breaks = c(-6,-4,-2,0,2,4,6)) + -->
+<!--   tm_borders() + -->
+<!-- tm_shape(locations_t) + -->
+<!--   tm_symbols(col='blue', size = 0.25) + -->
+<!--   tm_layout(title = 'May avg tmax', -->
+<!--             legend.outside = T) -->
+
+<!-- #june -->
+<!-- tmax_hrus_jun<- tmax_hrus_mo %>% -->
+<!--   filter(month == 6) -->
+
+<!-- hrus_map_tmax_jun <- left_join(hrus, tmax_hrus_jun, by = 'value') -->
+
+<!-- jun_tmax <- tm_shape(hrus_map_tmax_jun) + -->
+<!--   tm_fill('mo_tmax_diff', id = 'value', -->
+<!--          breaks = c(-6,-4,-2,0,2,4,6)) + -->
+<!--   tm_borders() + -->
+<!-- tm_shape(locations_t) + -->
+<!--   tm_symbols(col='blue', size = 0.25) + -->
+<!--   tm_layout(title = 'June avg tmax', -->
+<!--             legend.outside = T) -->
+
+<!-- tmap_arrange(mar_tmax, apr_tmax, may_tmax, jun_tmax) -->
+
+<!-- ``` -->
+
+<!-- ## Tmin difference -->
+
+<!-- ```{r tmin, echo = F} -->
+
+<!-- tmin_grid <- read_csv(here('HRU_output/reg_tminAll_prism.csv')) %>% -->
+<!--   pivot_longer(cols = `3`:`19`, -->
+<!--                names_to = 'value', -->
+<!--                values_to = 'tmin_grid') %>% -->
+<!--   mutate(time = dmy(time)) %>% -->
+<!--   group_by(value) %>% -->
+<!--   summarize(Tmin_mean_grid = mean(tmin_grid)) -->
+
+<!-- tmin_statn <- read_csv(here('HRU_output/reg_tminAll.csv')) %>% -->
+<!--   pivot_longer(cols = `3`:`19`, -->
+<!--                names_to = 'value', -->
+<!--                values_to = 'tmin_statn') %>% -->
+<!--   mutate(time = dmy(time)) %>% -->
+<!--   group_by(value) %>% -->
+<!--   summarize(Tmin_mean_statn = mean(tmin_statn)) -->
+
+<!-- tmin_hrus <- left_join(tmin_grid, tmin_statn, by = c('value')) %>% -->
+<!--   mutate(diff = Tmin_mean_statn - Tmin_mean_grid, -->
+<!--          value = as.numeric(value)) -->
+
+<!-- hrus_map_tmin <- left_join(hrus, tmin_hrus, by = 'value') -->
+
+<!-- tmap_mode('view') -->
+
+<!-- tm_shape(hrus_map_tmin) + -->
+<!--   tm_polygons('diff', id = 'value', -->
+<!--               breaks = c(-6,-4,-2,0,2,4,6)) + -->
+<!-- tm_shape(locations_t) + -->
+<!--   tm_symbols(col='blue', size=4) -->
+
+<!-- ``` -->
+
+<!-- ## Tmin monthly average -->
+
+<!-- ```{r tmin month, echo = F} -->
+<!-- tmin_grid_mo <- read_csv(here('HRU_output/reg_tminAll_prism.csv')) %>% -->
+<!--   pivot_longer(cols = `3`:`19`, -->
+<!--                names_to = 'value', -->
+<!--                values_to = 'tmin_grid') %>% -->
+<!--   mutate(time = dmy(time), -->
+<!--          month = month(time)) %>% -->
+<!--   filter(month %in% c(3:6)) %>% -->
+<!--   group_by(value, month) %>% -->
+<!--   summarize(avg_tmin_grid = mean(tmin_grid)) -->
+
+<!-- tmin_statn_mo <- read_csv(here('HRU_output/reg_tminAll.csv')) %>% -->
+<!--   pivot_longer(cols = `3`:`19`, -->
+<!--                names_to = 'value', -->
+<!--                values_to = 'tmin_statn') %>% -->
+<!--   mutate(time = dmy(time), -->
+<!--          month = month(time)) %>% -->
+<!--   filter(month %in% c(3:6)) %>% -->
+<!--   group_by(value, month) %>% -->
+<!--   summarize(avg_tmin_statn = mean(tmin_statn)) -->
+
+<!-- tmin_hrus_mo <- left_join(tmin_grid_mo, tmin_statn_mo, by = c('value', 'month')) %>% -->
+<!--   mutate(mo_tmin_diff = avg_tmin_statn - avg_tmin_grid, -->
+<!--          value = as.numeric(value)) -->
+
+<!-- tmap_mode('plot') -->
+
+<!-- #march -->
+<!-- tmin_hrus_mar<- tmin_hrus_mo %>% -->
+<!--   filter(month == 3) -->
+
+<!-- hrus_map_tmin_mar <- left_join(hrus, tmin_hrus_mar, by = 'value') -->
+
+<!-- mar_tmin <- tm_shape(hrus_map_tmin_mar) + -->
+<!--   #tm_polygons('mo_tmin_diff', id = 'value') + -->
+<!--   tm_fill('mo_tmin_diff', id = 'value', -->
+<!--           breaks = c(-5,-2.5,0,2.5,5)) + -->
+<!--   tm_borders() + -->
+<!--   tm_shape(locations_t) + -->
+<!--   tm_symbols(col='blue', size = 0.25) + -->
+<!--   tm_layout(title = 'March avg tmin', -->
+<!--             legend.outside = T) -->
+
+<!-- #april -->
+<!-- tmin_hrus_apr<- tmin_hrus_mo %>% -->
+<!--   filter(month == 4) -->
+
+<!-- hrus_map_tmin_apr <- left_join(hrus, tmin_hrus_apr, by = 'value') -->
+
+<!-- apr_tmin <- tm_shape(hrus_map_tmin_apr) + -->
+<!--   tm_fill('mo_tmin_diff', id = 'value', -->
+<!--           breaks = c(-5,-2.5,0,2.5,5)) + -->
+<!--   tm_borders() + -->
+<!--   tm_shape(locations_t) + -->
+<!--   tm_symbols(col='blue', size = 0.25) + -->
+<!--   tm_layout(title = 'April avg tmin', -->
+<!--             legend.outside = T) -->
+
+<!-- #may -->
+<!-- tmin_hrus_may<- tmin_hrus_mo %>% -->
+<!--   filter(month == 5) -->
+
+<!-- hrus_map_tmin_may <- left_join(hrus, tmin_hrus_may, by = 'value') -->
+
+<!-- may_tmin <- tm_shape(hrus_map_tmin_may) + -->
+<!--   tm_fill('mo_tmin_diff', id = 'value', -->
+<!--          breaks = c(-5,-2.5,0,2.5,5)) + -->
+<!--   tm_borders() + -->
+<!-- tm_shape(locations_t) + -->
+<!--   tm_symbols(col='blue', size = 0.25) + -->
+<!--   tm_layout(title = 'May avg tmin', -->
+<!--             legend.outside = T) -->
+
+<!-- #june -->
+<!-- tmin_hrus_jun<- tmin_hrus_mo %>% -->
+<!--   filter(month == 6) -->
+
+<!-- hrus_map_tmin_jun <- left_join(hrus, tmin_hrus_jun, by = 'value') -->
+
+<!-- jun_tmin <- tm_shape(hrus_map_tmin_jun) + -->
+<!--   tm_fill('mo_tmin_diff', id = 'value', -->
+<!--           breaks = c(-5,-2.5,0,2.5,5)) + -->
+<!--   tm_borders() + -->
+<!-- tm_shape(locations_t) + -->
+<!--   tm_symbols(col='blue', size = 0.25) + -->
+<!--   tm_layout(title = 'June avg tmin', -->
+<!--             legend.outside = T) -->
+
+<!-- tmap_arrange(mar_tmin, apr_tmin, may_tmin, jun_tmin) -->
+
+<!-- ``` -->
+
+<!-- ## Cumulative Precip difference -->
+
+<!-- 2011-2020 average of daily station-grid precip for DOY 365 (or 366) -->
+
+<!-- ```{r cum precip, echo = F} -->
+<!-- #get rid of a bunch of data -->
+<!-- hru_grid_precip <- hru_grids %>% -->
+<!--   dplyr::select(c(time, ID, precip)) %>% -->
+<!--   rename(precip_grid = precip) -->
+
+<!-- hru_statn_precip <- hru_statn %>% -->
+<!--   dplyr::select(c(time, ID, precip)) %>% -->
+<!--   rename(precip_statn = precip) -->
+
+<!-- precip_hrus <- left_join(hru_grid_precip, hru_statn_precip, by = c('time', 'ID')) %>% -->
+<!--   mutate(diff = precip_statn - precip_grid, -->
+<!--          year = year(time)) %>% -->
+<!--   group_by(year, ID) %>% -->
+<!--   mutate(total_diff = cumsum(diff)) %>% -->
+<!--   filter(time == max(time)) %>% -->
+<!--   group_by(ID) %>% -->
+<!--   summarize(precip_avg_cumdiff = mean(total_diff)) %>% -->
+<!--   rename(value = ID) -->
+
+<!-- hrus_map_precip <- left_join(hrus, precip_hrus, by = 'value') -->
+
+<!-- tmap_mode('view') -->
+
+<!-- locations_p <- locations %>% -->
+<!--   filter(type == 'precip') -->
+
+<!-- tm_shape(hrus_map_precip) + -->
+<!--   tm_polygons('precip_avg_cumdiff', midpoint = NA, palette = 'YlGnBu', id = 'value') + -->
+<!-- tm_shape(locations_p) + -->
+<!--   tm_symbols(col='blue', size=4) -->
+
+<!-- ``` -->
+
+<!-- ## Solar radiation difference -->
+
+<!-- 2011-2020 average of daily station-grid solar rad -->
+
+<!-- ```{r cum sol rad, echo = F} -->
+
+<!-- #get rid of a bunch of data -->
+<!-- hru_grid_solrad <- hru_grids %>% -->
+<!--   dplyr::select(c(time, ID, solRad)) %>% -->
+<!--   rename(solrad_grid = solRad)  %>% -->
+<!--   group_by(ID) %>% -->
+<!--   summarize(solrad_all_grid = mean(solrad_grid)) -->
+
+<!-- hru_statn_solrad <- hru_statn %>% -->
+<!--   dplyr::select(c(time, ID, solRad)) %>% -->
+<!--   rename(solrad_statn = solRad) %>% -->
+<!--   group_by(ID) %>% -->
+<!--   summarize(solrad_all_statn = mean(solrad_statn)) -->
+
+<!-- solrad_hrus <- left_join(hru_grid_solrad, hru_statn_solrad, by = c('ID')) %>% -->
+<!--   mutate(diff = solrad_all_statn - solrad_all_grid) %>% -->
+<!--   rename(value = ID) -->
+
+<!-- hrus_map_solrad <- left_join(hrus, solrad_hrus, by = 'value') -->
+
+<!-- tmap_mode('view') -->
+
+<!-- locations_solrad <- locations %>% -->
+<!--   dplyr::filter(name %in% c('Gordon_South', -->
+<!--                         'Betasso', 'Niwot_Snotel')) -->
+
+<!-- tm_shape(hrus_map_solrad) + -->
+<!--   tm_polygons('diff', midpoint = NA, palette = 'YlOrRd', id = 'value') + -->
+<!-- tm_shape(locations_solrad) + -->
+<!--   tm_symbols(col='blue', size=4) -->
+
+<!-- ``` -->
+
+<!-- ## RH difference -->
+
+<!-- ```{r rh, echo = F} -->
+
+<!-- #get rid of a bunch of data -->
+<!-- hru_grid_rh <- hru_grids %>% -->
+<!--   dplyr::select(c(time, ID, rhum)) %>% -->
+<!--   rename(rh_grid = rhum)  %>% -->
+<!--   group_by(ID) %>% -->
+<!--   summarize(rh_all_grid = mean(rh_grid)) -->
+
+<!-- hru_statn_rh <- hru_statn %>% -->
+<!--   dplyr::select(c(time, ID, rhum)) %>% -->
+<!--   rename(rh_statn = rhum) %>% -->
+<!--   group_by(ID) %>% -->
+<!--   summarize(rh_all_statn = mean(rh_statn)) -->
+
+<!-- rh_hrus <- left_join(hru_grid_rh, hru_statn_rh, by = c('ID')) %>% -->
+<!--   mutate(diff = rh_all_statn - rh_all_grid) %>% -->
+<!--   rename(value = ID) -->
+
+<!-- hrus_map_rh <- left_join(hrus, rh_hrus, by = 'value') -->
+
+<!-- tmap_mode('view') -->
+
+<!-- locations_rh <- locations %>% -->
+<!--   dplyr::filter(name %in% c('Gordon_South', 'Gordon_North', -->
+<!--                         'Betasso', 'Niwot_Snotel')) -->
+
+<!-- tm_shape(hrus_map_rh) + -->
+<!--   tm_polygons('diff', midpoint = NA, id = 'value') + -->
+<!-- tm_shape(locations_rh) + -->
+<!--   tm_symbols(col='blue', size=4) -->
+
+<!-- ``` -->
+
+<!-- ## Average soil sat comparison -->
+
+<!-- ```{r soilsat, echo = F} -->
+
+<!-- #get rid of a bunch of data -->
+<!-- hru_grid_soilsat <- hru_grids %>% -->
+<!--   dplyr::select(c(time, ID, soilSat)) %>% -->
+<!--   rename(soilsat_grid = soilSat)  %>% -->
+<!--   group_by(ID) %>% -->
+<!--   summarize(soilsat_all_grid = mean(soilsat_grid)) -->
+
+<!-- hru_statn_soilsat <- hru_statn %>% -->
+<!--   dplyr::select(c(time, ID, soilSat)) %>% -->
+<!--   rename(soilsat_statn = soilSat) %>% -->
+<!--   group_by(ID) %>% -->
+<!--   summarize(soilsat_all_statn = mean(soilsat_statn)) -->
+
+<!-- soilsat_hrus <- left_join(hru_grid_soilsat, hru_statn_soilsat, by = c('ID')) %>% -->
+<!--   rename(value = ID) -->
+
+<!-- hrus_map_soilsat <- left_join(hrus, soilsat_hrus, by = 'value') -->
+
+<!-- tmap_mode('plot') -->
+
+<!-- soilavg_grid <- tm_shape(hrus_map_soilsat) + -->
+<!--   tm_polygons('soilsat_all_grid', midpoint = NA, id = 'value', -->
+<!--               breaks = c(0.0, 0.05, 0.1, 0.15, 0.2, 0.25, 0.3)) + -->
+<!--   tm_legend(legend.outside = T) + -->
+<!--   tm_layout(main.title = 'Average soil sat') -->
+
+<!-- soilavg_statn <- tm_shape(hrus_map_soilsat) + -->
+<!--   tm_polygons('soilsat_all_statn', midpoint = NA, id = 'value', -->
+<!--               breaks = c(0.0, 0.05, 0.1, 0.15, 0.2, 0.25, 0.3)) + -->
+<!--   tm_legend(legend.outside = T) -->
+
+<!-- tmap_arrange(soilavg_grid, soilavg_statn) -->
+
+<!-- ``` -->
+
+<!-- ## Average max soil sat comparison -->
+
+<!-- ```{r max soilsat, echo = F} -->
+
+<!-- #get rid of a bunch of data -->
+<!-- hru_grid_soilsat_max <- hru_grids %>% -->
+<!--   dplyr::select(c(time, ID, soilSat)) %>% -->
+<!--   rename(soilsat_grid = soilSat)  %>% -->
+<!--   mutate(year = year(time)) %>% -->
+<!--   group_by(ID, year) %>% -->
+<!--   summarize(soilsat_yrmax_grid = max(soilsat_grid)) %>% -->
+<!--   summarize(avg_max_grid = mean(soilsat_yrmax_grid)) -->
+
+<!-- hru_statn_soilsat_max <- hru_statn %>% -->
+<!--   dplyr::select(c(time, ID, soilSat)) %>% -->
+<!--   rename(soilsat_statn = soilSat) %>% -->
+<!--   mutate(year = year(time)) %>% -->
+<!--   group_by(ID, year) %>% -->
+<!--   summarize(soilsat_yrmax_statn = max(soilsat_statn)) %>% -->
+<!--   summarize(avg_max_statn = mean(soilsat_yrmax_statn)) -->
+
+<!-- soilsat_hrus_max <- left_join(hru_grid_soilsat_max, hru_statn_soilsat_max, by = c('ID')) %>% -->
+<!--   rename(value = ID) -->
+
+<!-- hrus_map_soilsat_max <- left_join(hrus, soilsat_hrus_max, by = 'value') -->
+
+<!-- tmap_mode('plot') -->
+
+<!-- soilavg_grid_max <- tm_shape(hrus_map_soilsat_max) + -->
+<!--   tm_polygons('avg_max_grid', midpoint = NA, id = 'value', -->
+<!--               breaks = c(0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.7)) + -->
+<!--   tm_legend(legend.outside = T) + -->
+<!--   tm_layout(main.title = 'Average max soil sat', -->
+<!--             title.position = c('left', 'top')) -->
+
+<!-- soilavg_statn_max <- tm_shape(hrus_map_soilsat_max) + -->
+<!--   tm_polygons('avg_max_statn', midpoint = NA, id = 'value', -->
+<!--               breaks = c(0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.7)) + -->
+<!--   tm_legend(legend.outside = T) -->
+
+<!-- tmap_arrange(soilavg_grid_max, soilavg_statn_max) -->
+
+<!-- ``` -->
+
+<!-- ## Average ET comparison -->
+
+<!-- ```{r et, echo = F} -->
+<!-- #get rid of a bunch of data -->
+<!-- hru_grid_ET <- hru_grids %>% -->
+<!--   dplyr::select(c(time, ID, actET)) %>% -->
+<!--   rename(ET_grid = actET)  %>% -->
+<!--   group_by(ID) %>% -->
+<!--   summarize(ET_all_grid = mean(ET_grid)) -->
+
+<!-- hru_statn_ET <- hru_statn %>% -->
+<!--   dplyr::select(c(time, ID, actET)) %>% -->
+<!--   rename(ET_statn = actET) %>% -->
+<!--   group_by(ID) %>% -->
+<!--   summarize(ET_all_statn = mean(ET_statn)) -->
+
+<!-- ET_hrus <- left_join(hru_grid_ET, hru_statn_ET, by = c('ID')) %>% -->
+<!--   rename(value = ID) -->
+
+<!-- hrus_map_ET <- left_join(hrus, ET_hrus, by = 'value') -->
+
+<!-- tmap_mode('plot') -->
+
+<!-- ETavg_grid <- tm_shape(hrus_map_ET) + -->
+<!--   tm_polygons('ET_all_grid', midpoint = NA, id = 'value', -->
+<!--               breaks = c(0.2, 0.4, 0.6, 0.8, 1.0, 1.2)) + -->
+<!--   tm_legend(legend.outside = T) + -->
+<!--   tm_layout(main.title = 'Average ET') -->
+
+<!-- ETavg_statn <- tm_shape(hrus_map_ET) + -->
+<!--   tm_polygons('ET_all_statn', midpoint = NA, id = 'value', -->
+<!--              breaks = c(0.2, 0.4, 0.6, 0.8, 1.0, 1.2)) + -->
+<!--   tm_legend(legend.outside = T) -->
+
+<!-- tmap_arrange(ETavg_grid, ETavg_statn) -->
+
+<!-- ``` -->
+
+<!-- ## Average ET difference -->
+
+<!-- ```{r et diff, echo = F} -->
+
+<!-- ET_hrus <- ET_hrus %>% -->
+<!--   mutate(diff = ET_all_statn - ET_all_grid) -->
+
+<!-- hrus_map_et_diff <- left_join(hrus, ET_hrus, by = 'value') -->
+
+<!-- tmap_mode('plot') -->
+
+<!-- tm_shape(hrus_map_et_diff) + -->
+<!--   tm_polygons('diff', midpoint = NA, id = 'value')  + -->
+<!--   tm_legend(legend.outside = T) + -->
+<!--   tm_layout(main.title = 'Average ET difference') -->
+
+<!-- ``` -->
+
+<!-- ## Average LAI comparison -->
+
+<!-- ```{r lai, echo = F} -->
+
+<!-- #get rid of a bunch of data -->
+<!-- hru_grid_LAI <- hru_grids %>% -->
+<!--   dplyr::select(c(time, ID, LAI)) %>% -->
+<!--   rename(LAI_grid = LAI)  %>% -->
+<!--   group_by(ID) %>% -->
+<!--   summarize(LAI_all_grid = mean(LAI_grid)) -->
+
+<!-- hru_statn_LAI <- hru_statn %>% -->
+<!--   dplyr::select(c(time, ID, LAI)) %>% -->
+<!--   rename(LAI_statn = LAI) %>% -->
+<!--   group_by(ID) %>% -->
+<!--   summarize(LAI_all_statn = mean(LAI_statn)) -->
+
+<!-- LAI_hrus <- left_join(hru_grid_LAI, hru_statn_LAI, by = c('ID')) %>% -->
+<!--   rename(value = ID) -->
+
+<!-- hrus_map_LAI <- left_join(hrus, LAI_hrus, by = 'value') -->
+
+<!-- tmap_mode('view') -->
+
+<!-- LAIavg_grid <- tm_shape(hrus_map_LAI) + -->
+<!--   tm_polygons('LAI_all_grid', midpoint = NA, id = 'value', -->
+<!--               breaks = c(1,2,3,4,5)) + -->
+<!--   tm_legend(legend.outside = T) + -->
+<!--   tm_layout(main.title = 'Average LAI') -->
+
+<!-- LAIavg_statn <- tm_shape(hrus_map_LAI) + -->
+<!--   tm_polygons('LAI_all_statn', midpoint = NA, id = 'value', -->
+<!--               breaks = c(1,2,3,4,5)) + -->
+<!--   tm_legend(legend.outside = T) -->
+
+<!-- tmap_arrange(LAIavg_grid, LAIavg_statn) -->
+
+<!-- ``` -->

### 2023-05-05 38HRU_model/fourmile_model_outputs.Rmd
flow added, burn params edited

@@
 ```{r}
-params <- params %>%
-  mutate(burn = 'no')
-
-params_combo <- bind_rows(params,
+params2 <- params %>%
+  mutate(burn = 'no') %>%
+  filter(param %in% c('a_rain',
+                        'a_snow',
+                        'soilMaxInfSummer',
+                        'soilMaxDPS',
+                        'lagSurfaceRunoff',
+                        'soilDistMPSLPS'))
+
+params_combo <- bind_rows(params2,
                           burn_params %>%
@@
 
-name <- levels(params_combo$param)
-
-lapply(name, plot_params)
+#name <- levels(params_combo$param)
+
+lapply(name2, plot_params)
 

### 2023-05-05 38HRU_model/fourmile_model_outputs.Rmd
added rd and rg

@@
 
-<!-- ## RD and RG -->
-
-<!-- ```{r rd and rg, echo = F, fig.width = 14, fig.asp = 1, out.width = "100%"} -->
-
-<!-- gw_grid <- read_csv(here('catchment_output/gridall_outlet.csv')) %>% -->
-<!--   dplyr::select(time, catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w) %>% -->
-<!--   mutate(source = 'grid') -->
-
-<!-- gw_statn <- read_csv(here('catchment_output/statnall_outlet.csv')) %>% -->
-<!--   dplyr::select(time, catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w) %>% -->
-<!--   mutate(source = 'statn') -->
-
-<!-- gw <- bind_rows(gw_grid, gw_statn) %>% -->
-<!--   mutate(year = year(time)) %>% -->
-<!--   rename(date = time) -->
-
-<!-- ggplot(gw, aes(x=date, color = source)) + -->
-<!--   geom_line(aes(y=catchmentRD1_w), size =1) + -->
-<!--   facet_wrap(~year, scales = 'free', ncol = 2) + -->
-<!--   scale_x_date(labels = date_format("%b")) + -->
-<!--   ggtitle('RD1') + -->
-<!--   theme(text = element_text(size = 20)) -->
-
-<!-- ggplot(gw, aes(x=date, color = source)) + -->
-<!--   geom_line(aes(y=catchmentRD2_w), size =1) + -->
-<!--   facet_wrap(~year, scales = 'free', ncol = 2) + -->
-<!--   scale_x_date(labels = date_format("%b")) + -->
-<!--   ggtitle('RD2') + -->
-<!--   theme(text = element_text(size = 20)) -->
-
-<!-- ggplot(gw, aes(x=date, color = source)) + -->
-<!--   geom_line(aes(y=catchmentRG1_w), size =1) + -->
-<!--   facet_wrap(~year, scales = 'free', ncol = 2) + -->
-<!--   scale_x_date(labels = date_format("%b")) + -->
-<!--   ggtitle('RG1') + -->
-<!--   theme(text = element_text(size = 20)) -->
-
-<!-- ggplot(gw, aes(x=date, color = source)) + -->
-<!--   geom_line(aes(y=catchmentRG2_w), size =1) + -->
-<!--   facet_wrap(~year, scales = 'free', ncol=2) + -->
-<!--   scale_x_date(labels = date_format("%b")) + -->
-<!--   ggtitle('RG2') + -->
-<!--   theme(text = element_text(size = 20)) -->
-
-<!-- gw <- gw %>% -->
-<!--   group_by(year, source) %>% -->
-<!--   mutate(RD1cumsum = cumsum(catchmentRD1_w), -->
-<!--          RD2cumsum = cumsum(catchmentRD2_w), -->
-<!--          RG1cumsum = cumsum(catchmentRG1_w), -->
-<!--          RG2cumsum = cumsum(catchmentRG2_w)) -->
-
-<!-- ggplot(gw, aes(x=date, color = source)) + -->
-<!--   geom_line(aes(y=RD1cumsum), size =1) + -->
-<!--   facet_wrap(~year, scales = 'free', ncol=2) + -->
-<!--   scale_x_date(labels = date_format("%b")) + -->
-<!--   ggtitle('Cumulative RD1') + -->
-<!--   theme(text = element_text(size = 20)) -->
-
-<!-- ggplot(gw, aes(x=date, color = source)) + -->
-<!--   geom_line(aes(y=RD2cumsum), size = 1) + -->
-<!--   facet_wrap(~year, scales = 'free', ncol=2) + -->
-<!--   scale_x_date(labels = date_format("%b")) + -->
-<!--   ggtitle('Cumulative RD2') + -->
-<!--   theme(text = element_text(size = 20)) -->
-
-<!-- ggplot(gw, aes(x=date, color = source)) + -->
-<!--   geom_line(aes(y=RG1cumsum), size  = 1) + -->
-<!--   facet_wrap(~year, scales = 'free', ncol = 2) + -->
-<!--   scale_x_date(labels = date_format("%b")) + -->
-<!--   ggtitle('Cumulative RG1') + -->
-<!--   theme(text = element_text(size = 20)) -->
-
-<!-- ggplot(gw, aes(x=date, color = source)) + -->
-<!--   geom_line(aes(y=RG2cumsum), size =1) + -->
-<!--   facet_wrap(~year, scales = 'free', ncol = 2) + -->
-<!--   scale_x_date(labels = date_format("%b")) + -->
-<!--   ggtitle('Cumulative RG2') + -->
-<!--   theme(text = element_text(size = 20)) -->
-
-<!-- ``` -->
-
-<!-- ```{r rd and rg sums, echo = F, fig.width = 22, fig.asp = 1.5, out.width = "100%"} -->
-
-<!-- ################## -->
-<!-- # all 4 with facets -->
-
-<!-- ggplot(gw, aes(x=date)) + -->
-<!--   geom_line(aes(y=RG2cumsum, color = 'cumulative RG2'), size =1) + -->
-<!--   geom_line(aes(y=RG1cumsum, color = 'cumulative RG1'), size =1) + -->
-<!--   geom_line(aes(y=RD1cumsum, color = 'cumulative RD1'), size =1) + -->
-<!--   geom_line(aes(y=RD2cumsum, color = 'cumulative RD2'), size =1) + -->
-<!--   scale_x_date(labels = date_format("%b")) + -->
-<!--   facet_wrap(~year + source, scales = 'free_x', ncol=2) + -->
-<!--   ggtitle('Cumulative RD and RG') + -->
-<!--   theme(text = element_text(size = 24)) -->
-
-<!-- ``` -->
-
-<!-- ```{r gw boxplot, echo = F} -->
-
-<!-- gw_maxcumsum <- gw %>% -->
-<!--   group_by(source, year) %>% -->
-<!--   summarize(yr_max_RD1 = max(RD1cumsum), -->
-<!--             yr_max_RD2 = max(RD2cumsum), -->
-<!--             yr_max_RG1 = max(RG1cumsum), -->
-<!--             yr_max_RG2 = max(RG2cumsum)) %>% -->
-<!--   mutate(year = as.factor(year)) %>% -->
-<!--   pivot_longer(!c(year, source), names_to = 'flow_type', values_to = 'flow_cms') -->
-
-<!-- ggplot(gw_maxcumsum, aes(x = flow_type, y = flow_cms, fill = source)) + -->
-<!--   geom_boxplot(position = position_dodge(1)) + -->
-<!--   geom_point(position=position_jitterdodge(),alpha=0.3) + -->
-<!--   ggtitle('Max annual cumulative sums') -->
-
-<!-- ggplot(gw_maxcumsum, aes(x = flow_type, y = flow_cms, fill = source)) + -->
-<!--   geom_boxplot(position = position_dodge(1)) + -->
-<!--   geom_point(position=position_jitterdodge(),alpha=0.3) + -->
-<!--   #geom_point(aes(color = source)) + -->
-<!--   facet_wrap(~flow_type, scales = 'free') + -->
-<!--   ggtitle('Max annual cumulative sums') -->
-
-<!-- ``` -->
-
-<!-- ### RD and RG by season -->
-
-<!-- ```{r flow season, echo = F, fig.width = 12, fig.asp = 0.75, out.width = "100%"} -->
-
-<!-- #group by season and get max sums by season -->
-<!-- flow_season <- gw %>% -->
-<!--   dplyr::select(RD1cumsum, RD2cumsum, RG1cumsum, RG2cumsum, date, year, source) %>% -->
-<!--   mutate(month = month(date)) %>% -->
-<!--   mutate(season = case_when(month %in% c(3,4,5,6) ~ 'snowmelt', -->
-<!--                             month %in% c(7,8,9,10) ~ 'monsoon', -->
-<!--                             month %in% c(11,12,1,2) ~ 'baseflow')) %>% -->
-<!--   group_by(source, year, season) %>% -->
-<!--   summarize(yr_season_RD1 = max(RD1cumsum), -->
-<!--             yr_season_RD2 = max(RD2cumsum), -->
-<!--             yr_season_RG1 = max(RG1cumsum), -->
-<!--             yr_season_RG2 = max(RG2cumsum)) %>% -->
-<!--             pivot_longer(!c(year, source, season), names_to = 'flow_type', values_to = 'flow_cms') -->
-
-<!-- flow_season %>% -->
-<!--   ggplot(aes(x = flow_type, y = flow_cms, fill = source)) + -->
-<!--   geom_boxplot(position = position_dodge(1)) + -->
-<!--   geom_point(position=position_jitterdodge(),alpha=0.3) + -->
-<!--   #geom_point(aes(color = source)) + -->
-<!--   facet_wrap(~season, scales = 'free') + -->
-<!--   ggtitle('Max annual season cumulative sums') + -->
-<!--   theme_bw() + -->
-<!--   theme(axis.text.x = element_text(angle = 45, hjust = 1)) + -->
-<!--   theme(text = element_text(size = 20)) -->
-
-<!-- flow_season %>% -->
-<!--   ggplot(aes(x = flow_type, y = flow_cms, fill = source)) + -->
-<!--   geom_boxplot(position = position_dodge(1)) + -->
-<!--   geom_point(position=position_jitterdodge(),alpha=0.3) + -->
-<!--   #geom_point(aes(color = source)) + -->
-<!--   facet_wrap(~season + flow_type, scales = 'free') + -->
-<!--   ggtitle('Max annual season cumulative sums') + -->
-<!--   theme_bw() + -->
-<!--   theme(text = element_text(size = 20)) -->
-
-<!-- ``` -->
+# RD and RG
+
+```{r rd and rg, echo = F, fig.width = 14, fig.asp = 1, out.width = "100%"}
+
+gw_grid <- read_csv(here('catchment_output/gridall_outlet.csv')) %>%
+  dplyr::select(time, catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w) %>%
+  mutate(source = 'grid')
+
+gw_statn <- read_csv(here('catchment_output/statnall_outlet.csv')) %>%
+  dplyr::select(time, catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w) %>%
+  mutate(source = 'statn')
+
+gw <- bind_rows(gw_grid, gw_statn) %>%
+  mutate(year = year(time)) %>%
+  rename(date = time)
+
+ggplot(gw, aes(x=date, color = source)) +
+  geom_line(aes(y=catchmentRD1_w), size =1) +
+  facet_wrap(~year, scales = 'free', ncol = 2) +
+  scale_x_date(labels = date_format("%b")) +
+  ggtitle('RD1') +
+  theme(text = element_text(size = 20))
+
+ggplot(gw, aes(x=date, color = source)) +
+  geom_line(aes(y=catchmentRD2_w), size =1) +
+  facet_wrap(~year, scales = 'free', ncol = 2) +
+  scale_x_date(labels = date_format("%b")) +
+  ggtitle('RD2') +
+  theme(text = element_text(size = 20))
+
+ggplot(gw, aes(x=date, color = source)) +
+  geom_line(aes(y=catchmentRG1_w), size =1) +
+  facet_wrap(~year, scales = 'free', ncol = 2) +
+  scale_x_date(labels = date_format("%b")) +
+  ggtitle('RG1') +
+  theme(text = element_text(size = 20))
+
+ggplot(gw, aes(x=date, color = source)) +
+  geom_line(aes(y=catchmentRG2_w), size =1) +
+  facet_wrap(~year, scales = 'free', ncol=2) +
+  scale_x_date(labels = date_format("%b")) +
+  ggtitle('RG2') +
+  theme(text = element_text(size = 20))
+
+gw <- gw %>%
+  group_by(year, source) %>%
+  mutate(RD1cumsum = cumsum(catchmentRD1_w),
+         RD2cumsum = cumsum(catchmentRD2_w),
+         RG1cumsum = cumsum(catchmentRG1_w),
+         RG2cumsum = cumsum(catchmentRG2_w))
+
+ggplot(gw, aes(x=date, color = source)) +
+  geom_line(aes(y=RD1cumsum), size =1) +
+  facet_wrap(~year, scales = 'free', ncol=2) +
+  scale_x_date(labels = date_format("%b")) +
+  ggtitle('Cumulative RD1') +
+  theme(text = element_text(size = 20))
+
+ggplot(gw, aes(x=date, color = source)) +
+  geom_line(aes(y=RD2cumsum), size = 1) +
+  facet_wrap(~year, scales = 'free', ncol=2) +
+  scale_x_date(labels = date_format("%b")) +
+  ggtitle('Cumulative RD2') +
+  theme(text = element_text(size = 20))
+
+ggplot(gw, aes(x=date, color = source)) +
+  geom_line(aes(y=RG1cumsum), size  = 1) +
+  facet_wrap(~year, scales = 'free', ncol = 2) +
+  scale_x_date(labels = date_format("%b")) +
+  ggtitle('Cumulative RG1') +
+  theme(text = element_text(size = 20))
+
+ggplot(gw, aes(x=date, color = source)) +
+  geom_line(aes(y=RG2cumsum), size =1) +
+  facet_wrap(~year, scales = 'free', ncol = 2) +
+  scale_x_date(labels = date_format("%b")) +
+  ggtitle('Cumulative RG2') +
+  theme(text = element_text(size = 20))
+
+```
+
+```{r rd and rg sums, echo = F, fig.width = 22, fig.asp = 1.5, out.width = "100%"}
+
+##################
+# all 4 with facets
+
+ggplot(gw, aes(x=date)) +
+  geom_line(aes(y=RG2cumsum, color = 'cumulative RG2'), size =1) +
+  geom_line(aes(y=RG1cumsum, color = 'cumulative RG1'), size =1) +
+  geom_line(aes(y=RD1cumsum, color = 'cumulative RD1'), size =1) +
+  geom_line(aes(y=RD2cumsum, color = 'cumulative RD2'), size =1) +
+  scale_x_date(labels = date_format("%b")) +
+  facet_wrap(~year + source, scales = 'free_x', ncol=2) +
+  ggtitle('Cumulative RD and RG') +
+  theme(text = element_text(size = 24))
+
+```
+
+```{r gw boxplot, echo = F}
+
+gw_maxcumsum <- gw %>%
+  group_by(source, year) %>%
+  summarize(yr_max_RD1 = max(RD1cumsum),
+            yr_max_RD2 = max(RD2cumsum),
+            yr_max_RG1 = max(RG1cumsum),
+            yr_max_RG2 = max(RG2cumsum)) %>%
+  mutate(year = as.factor(year)) %>%
+  pivot_longer(!c(year, source), names_to = 'flow_type', values_to = 'flow_cms')
+
+ggplot(gw_maxcumsum, aes(x = flow_type, y = flow_cms, fill = source)) +
+  geom_boxplot(position = position_dodge(1)) +
+  geom_point(position=position_jitterdodge(),alpha=0.3) +
+  ggtitle('Max annual cumulative sums')
+
+ggplot(gw_maxcumsum, aes(x = flow_type, y = flow_cms, fill = source)) +
+  geom_boxplot(position = position_dodge(1)) +
+  geom_point(position=position_jitterdodge(),alpha=0.3) +
+  #geom_point(aes(color = source)) +
+  facet_wrap(~flow_type, scales = 'free') +
+  ggtitle('Max annual cumulative sums')
+
+```
+
+### RD and RG by season
+
+```{r flow season, echo = F, fig.width = 12, fig.asp = 0.75, out.width = "100%"}
+
+#group by season and get max sums by season
+flow_season <- gw %>%
+  dplyr::select(RD1cumsum, RD2cumsum, RG1cumsum, RG2cumsum, date, year, source) %>%
+  mutate(month = month(date)) %>%
+  mutate(season = case_when(month %in% c(3,4,5,6) ~ 'snowmelt',
+                            month %in% c(7,8,9,10) ~ 'monsoon',
+                            month %in% c(11,12,1,2) ~ 'baseflow')) %>%
+  group_by(source, year, season) %>%
+  summarize(yr_season_RD1 = max(RD1cumsum),
+            yr_season_RD2 = max(RD2cumsum),
+            yr_season_RG1 = max(RG1cumsum),
+            yr_season_RG2 = max(RG2cumsum)) %>%
+            pivot_longer(!c(year, source, season), names_to = 'flow_type', values_to = 'flow_cms')
+
+flow_season %>%
+  ggplot(aes(x = flow_type, y = flow_cms, fill = source)) +
+  geom_boxplot(position = position_dodge(1)) +
+  geom_point(position=position_jitterdodge(),alpha=0.3) +
+  #geom_point(aes(color = source)) +
+  facet_wrap(~season, scales = 'free') +
+  ggtitle('Max annual season cumulative sums') +
+  theme_bw() +
+  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
+  theme(text = element_text(size = 20))
+
+flow_season %>%
+  ggplot(aes(x = flow_type, y = flow_cms, fill = source)) +
+  geom_boxplot(position = position_dodge(1)) +
+  geom_point(position=position_jitterdodge(),alpha=0.3) +
+  #geom_point(aes(color = source)) +
+  facet_wrap(~season + flow_type, scales = 'free') +
+  ggtitle('Max annual season cumulative sums') +
+  theme_bw() +
+  theme(text = element_text(size = 20))
+
+```
 

### 2023-05-15 38HRU_model/fourmile_model_outputs.Rmd
added hru shp, sensor locations, and HRU outputs

@@
 
-<!-- # HRU results -->
-
-<!-- ## Tmean difference -->
-
-<!-- 2011-2020 average of daily station-grid Tmean -->
-
-<!-- ```{r cumulative tmean for HRUs, echo = F} -->
-<!-- #grid first -->
-<!-- setwd(here("HRU_output/grid")) -->
-
-<!-- read_ages_grid <- function(dataframe){ -->
-<!--   read_csv(dataframe, skip = 3) %>% -->
-<!--   slice(3:n()) %>% -->
-<!--   dplyr::select(-starts_with('@'), -->
-<!--                 -1) %>% -->
-<!--   mutate(time = ymd(time)) %>% -->
-<!--   mutate_if(is.character, as.numeric) %>% -->
-<!--   mutate(source = 'grid') -->
-
-<!-- } -->
-
-<!-- #pull in all filenames with HRU in the name -->
-<!-- filenames <- list.files(".", pattern="HRU", full.names=F) -->
-
-<!-- #read all the csvs using read_ages function -->
-<!-- dataframes <- lapply(filenames, read_ages_grid) -->
-
-<!-- #name all the csvs based on first 6 characters -->
-<!-- names(dataframes) <- substr(filenames, 1, 6) -->
-
-<!-- #bind all and make 1 df -->
-<!-- hru_grids <- dataframes %>% -->
-<!--   bind_rows() -->
-
-<!-- #statn next -->
-<!-- setwd(here("HRU_output/statn")) -->
-
-<!-- read_ages_statn <- function(dataframe){ -->
-<!--   read_csv(dataframe, skip = 3) %>% -->
-<!--   slice(3:n()) %>% -->
-<!--   dplyr::select(-starts_with('@'), -->
-<!--                 -1) %>% -->
-<!--   mutate(time = ymd(time)) %>% -->
-<!--   mutate_if(is.character, as.numeric) %>% -->
-<!--   mutate(source = 'statn') -->
-
-<!-- } -->
-
-<!-- #pull in all filenames with HRU in the name -->
-<!-- filenames <- list.files(".", pattern="HRU", full.names=F) -->
-
-<!-- #read all the csvs using read_ages function -->
-<!-- dataframes <- lapply(filenames, read_ages_statn) -->
-
-<!-- #name all the csvs based on first 6 characters -->
-<!-- names(dataframes) <- substr(filenames, 1, 6) -->
-
-<!-- #bind all and make 1 df -->
-<!-- hru_statn <- dataframes %>% -->
-<!--   bind_rows() -->
-
-<!-- #get rid of a bunch of data -->
-<!-- hru_grid_tmean <- hru_grids %>% -->
-<!--   dplyr::select(c(time, ID, tmean)) %>% -->
-<!--   rename(tmean_grid = tmean)  %>% -->
-<!--   group_by(ID) %>% -->
-<!--   summarize(tmean_all_grid = mean(tmean_grid)) -->
-
-<!-- hru_statn_tmean <- hru_statn %>% -->
-<!--   dplyr::select(c(time, ID, tmean)) %>% -->
-<!--   rename(tmean_statn = tmean) %>% -->
-<!--   group_by(ID) %>% -->
-<!--   summarize(tmean_all_statn = mean(tmean_statn)) -->
-
-<!-- tmean_hrus <- left_join(hru_grid_tmean, hru_statn_tmean, by = c('ID')) %>% -->
-<!--   mutate(diff = tmean_all_statn - tmean_all_grid) %>% -->
-<!--   rename(value = ID) -->
-
-<!-- hrus_map_tmean <- left_join(hrus, tmean_hrus, by = 'value') -->
-
-<!-- tmap_mode('view') -->
-
-<!-- locations_t <- locations %>% -->
-<!--   dplyr::filter(name %in% c('Gordon_South', 'Gordon_North', -->
-<!--                         'Betasso', 'Niwot_Snotel', -->
-<!--                         'University Camp SNTL')) -->
-
-<!-- tm_shape(hrus_map_tmean) + -->
-<!--   tm_polygons('diff', id = 'value', -->
-<!--               breaks = c(-6,-4,-2,0,2,4,6)) + -->
-<!-- tm_shape(locations_t) + -->
-<!--   tm_symbols(col='blue', size=4) -->
-
-<!-- ``` -->
-
-<!-- ## Tmax difference -->
-
-<!-- ```{r tmax, echo = F} -->
-
-<!-- tmax_grid <- read_csv(here('HRU_output/reg_tmaxAll_prism.csv'))%>% -->
-<!--   pivot_longer(cols = `3`:`19`, -->
-<!--                names_to = 'value', -->
-<!--                values_to = 'tmax_grid') %>% -->
-<!--   mutate(time = dmy(time)) %>% -->
-<!--   group_by(value) %>% -->
-<!--   summarize(Tmax_mean_grid = mean(tmax_grid)) -->
-
-<!-- tmax_statn <- read_csv(here('HRU_output/reg_tmaxAll.csv')) %>% -->
-<!--   pivot_longer(cols = `3`:`19`, -->
-<!--                names_to = 'value', -->
-<!--                values_to = 'tmax_statn') %>% -->
-<!--   mutate(time = dmy(time)) %>% -->
-<!--   group_by(value) %>% -->
-<!--   summarize(Tmax_mean_statn = mean(tmax_statn)) -->
-
-<!-- tmax_hrus <- left_join(tmax_grid, tmax_statn, by = c('value')) %>% -->
-<!--   mutate(diff = Tmax_mean_statn - Tmax_mean_grid, -->
-<!--          value = as.numeric(value)) -->
-
-<!-- hrus_map_tmax <- left_join(hrus, tmax_hrus, by = 'value') -->
-
-<!-- tmap_mode('view') -->
-
-<!-- tm_shape(hrus_map_tmax) + -->
-<!--   tm_polygons('diff', id = 'value', -->
-<!--               breaks = c(-6,-4,-2,0,2,4,6)) + -->
-<!-- tm_shape(locations_t) + -->
-<!--   tm_symbols(col='blue', size=4) -->
-
-<!-- ``` -->
-
-<!-- ## Tmax monthly average -->
-
-<!-- ```{r tmax month, echo = F} -->
-
-<!-- tmax_grid_mo <- read_csv(here('HRU_output/reg_tmaxAll_prism.csv')) %>% -->
-<!--   pivot_longer(cols = `3`:`19`, -->
-<!--                names_to = 'value', -->
-<!--                values_to = 'tmax_grid') %>% -->
-<!--   mutate(time = dmy(time), -->
-<!--          month = month(time)) %>% -->
-<!--   filter(month %in% c(3:6)) %>% -->
-<!--   group_by(value, month) %>% -->
-<!--   summarize(avg_tmax_grid = mean(tmax_grid)) -->
-
-<!-- tmax_statn_mo <- read_csv(here('HRU_output/reg_tmaxAll.csv')) %>% -->
-<!--   pivot_longer(cols = `3`:`19`, -->
-<!--                names_to = 'value', -->
-<!--                values_to = 'tmax_statn') %>% -->
-<!--   mutate(time = dmy(time), -->
-<!--          month = month(time)) %>% -->
-<!--   filter(month %in% c(3:6)) %>% -->
-<!--   group_by(value, month) %>% -->
-<!--   summarize(avg_tmax_statn = mean(tmax_statn)) -->
-
-<!-- tmax_hrus_mo <- left_join(tmax_grid_mo, tmax_statn_mo, by = c('value', 'month')) %>% -->
-<!--   mutate(mo_tmax_diff = avg_tmax_statn - avg_tmax_grid, -->
-<!--          value = as.numeric(value)) -->
-
-<!-- tmap_mode('plot') -->
-
-<!-- #march -->
-<!-- tmax_hrus_mar<- tmax_hrus_mo %>% -->
-<!--   filter(month == 3) -->
-
-<!-- hrus_map_tmax_mar <- left_join(hrus, tmax_hrus_mar, by = 'value') -->
-
-<!-- mar_tmax <- tm_shape(hrus_map_tmax_mar) + -->
-<!--   #tm_polygons('mo_tmax_diff', id = 'value') + -->
-<!--   tm_fill('mo_tmax_diff', id = 'value', -->
-<!--           breaks = c(-6,-4,-2,0,2,4,6)) + -->
-<!--   tm_borders() + -->
-<!--   tm_shape(locations_t) + -->
-<!--   tm_symbols(col='blue', size = 0.25) + -->
-<!--   tm_layout(title = 'March avg tmax', -->
-<!--             legend.outside = T) -->
-
-<!-- #april -->
-<!-- tmax_hrus_apr<- tmax_hrus_mo %>% -->
-<!--   filter(month == 4) -->
-
-<!-- hrus_map_tmax_apr <- left_join(hrus, tmax_hrus_apr, by = 'value') -->
-
-<!-- apr_tmax <- tm_shape(hrus_map_tmax_apr) + -->
-<!--   tm_fill('mo_tmax_diff', id = 'value', -->
-<!--           breaks = c(-6,-4,-2,0,2,4,6)) + -->
-<!--   tm_borders() + -->
-<!--   tm_shape(locations_t) + -->
-<!--   tm_symbols(col='blue', size = 0.25) + -->
-<!--   tm_layout(title = 'April avg tmax', -->
-<!--             legend.outside = T) -->
-
-<!-- #may -->
-<!-- tmax_hrus_may<- tmax_hrus_mo %>% -->
-<!--   filter(month == 5) -->
-
-<!-- hrus_map_tmax_may <- left_join(hrus, tmax_hrus_may, by = 'value') -->
-
-<!-- may_tmax <- tm_shape(hrus_map_tmax_may) + -->
-<!--   tm_fill('mo_tmax_diff', id = 'value', -->
-<!--          breaks = c(-6,-4,-2,0,2,4,6)) + -->
-<!--   tm_borders() + -->
-<!-- tm_shape(locations_t) + -->
-<!--   tm_symbols(col='blue', size = 0.25) + -->
-<!--   tm_layout(title = 'May avg tmax', -->
-<!--             legend.outside = T) -->
-
-<!-- #june -->
-<!-- tmax_hrus_jun<- tmax_hrus_mo %>% -->
-<!--   filter(month == 6) -->
-
-<!-- hrus_map_tmax_jun <- left_join(hrus, tmax_hrus_jun, by = 'value') -->
-
-<!-- jun_tmax <- tm_shape(hrus_map_tmax_jun) + -->
-<!--   tm_fill('mo_tmax_diff', id = 'value', -->
-<!--          breaks = c(-6,-4,-2,0,2,4,6)) + -->
-<!--   tm_borders() + -->
-<!-- tm_shape(locations_t) + -->
-<!--   tm_symbols(col='blue', size = 0.25) + -->
-<!--   tm_layout(title = 'June avg tmax', -->
-<!--             legend.outside = T) -->
-
-<!-- tmap_arrange(mar_tmax, apr_tmax, may_tmax, jun_tmax) -->
-
-<!-- ``` -->
-
-<!-- ## Tmin difference -->
-
-<!-- ```{r tmin, echo = F} -->
-
-<!-- tmin_grid <- read_csv(here('HRU_output/reg_tminAll_prism.csv')) %>% -->
-<!--   pivot_longer(cols = `3`:`19`, -->
-<!--                names_to = 'value', -->
-<!--                values_to = 'tmin_grid') %>% -->
-<!--   mutate(time = dmy(time)) %>% -->
-<!--   group_by(value) %>% -->
-<!--   summarize(Tmin_mean_grid = mean(tmin_grid)) -->
-
-<!-- tmin_statn <- read_csv(here('HRU_output/reg_tminAll.csv')) %>% -->
-<!--   pivot_longer(cols = `3`:`19`, -->
-<!--                names_to = 'value', -->
-<!--                values_to = 'tmin_statn') %>% -->
-<!--   mutate(time = dmy(time)) %>% -->
-<!--   group_by(value) %>% -->
-<!--   summarize(Tmin_mean_statn = mean(tmin_statn)) -->
-
-<!-- tmin_hrus <- left_join(tmin_grid, tmin_statn, by = c('value')) %>% -->
-<!--   mutate(diff = Tmin_mean_statn - Tmin_mean_grid, -->
-<!--          value = as.numeric(value)) -->
-
-<!-- hrus_map_tmin <- left_join(hrus, tmin_hrus, by = 'value') -->
-
-<!-- tmap_mode('view') -->
-
-<!-- tm_shape(hrus_map_tmin) + -->
-<!--   tm_polygons('diff', id = 'value', -->
-<!--               breaks = c(-6,-4,-2,0,2,4,6)) + -->
-<!-- tm_shape(locations_t) + -->
-<!--   tm_symbols(col='blue', size=4) -->
-
-<!-- ``` -->
-
-<!-- ## Tmin monthly average -->
-
-<!-- ```{r tmin month, echo = F} -->
-<!-- tmin_grid_mo <- read_csv(here('HRU_output/reg_tminAll_prism.csv')) %>% -->
-<!--   pivot_longer(cols = `3`:`19`, -->
-<!--                names_to = 'value', -->
-<!--                values_to = 'tmin_grid') %>% -->
-<!--   mutate(time = dmy(time), -->
-<!--          month = month(time)) %>% -->
-<!--   filter(month %in% c(3:6)) %>% -->
-<!--   group_by(value, month) %>% -->
-<!--   summarize(avg_tmin_grid = mean(tmin_grid)) -->
-
-<!-- tmin_statn_mo <- read_csv(here('HRU_output/reg_tminAll.csv')) %>% -->
-<!--   pivot_longer(cols = `3`:`19`, -->
-<!--                names_to = 'value', -->
-<!--                values_to = 'tmin_statn') %>% -->
-<!--   mutate(time = dmy(time), -->
-<!--          month = month(time)) %>% -->
-<!--   filter(month %in% c(3:6)) %>% -->
-<!--   group_by(value, month) %>% -->
-<!--   summarize(avg_tmin_statn = mean(tmin_statn)) -->
-
-<!-- tmin_hrus_mo <- left_join(tmin_grid_mo, tmin_statn_mo, by = c('value', 'month')) %>% -->
-<!--   mutate(mo_tmin_diff = avg_tmin_statn - avg_tmin_grid, -->
-<!--          value = as.numeric(value)) -->
-
-<!-- tmap_mode('plot') -->
-
-<!-- #march -->
-<!-- tmin_hrus_mar<- tmin_hrus_mo %>% -->
-<!--   filter(month == 3) -->
-
-<!-- hrus_map_tmin_mar <- left_join(hrus, tmin_hrus_mar, by = 'value') -->
-
-<!-- mar_tmin <- tm_shape(hrus_map_tmin_mar) + -->
-<!--   #tm_polygons('mo_tmin_diff', id = 'value') + -->
-<!--   tm_fill('mo_tmin_diff', id = 'value', -->
-<!--           breaks = c(-5,-2.5,0,2.5,5)) + -->
-<!--   tm_borders() + -->
-<!--   tm_shape(locations_t) + -->
-<!--   tm_symbols(col='blue', size = 0.25) + -->
-<!--   tm_layout(title = 'March avg tmin', -->
-<!--             legend.outside = T) -->
-
-<!-- #april -->
-<!-- tmin_hrus_apr<- tmin_hrus_mo %>% -->
-<!--   filter(month == 4) -->
-
-<!-- hrus_map_tmin_apr <- left_join(hrus, tmin_hrus_apr, by = 'value') -->
-
-<!-- apr_tmin <- tm_shape(hrus_map_tmin_apr) + -->
-<!--   tm_fill('mo_tmin_diff', id = 'value', -->
-<!--           breaks = c(-5,-2.5,0,2.5,5)) + -->
-<!--   tm_borders() + -->
-<!--   tm_shape(locations_t) + -->
-<!--   tm_symbols(col='blue', size = 0.25) + -->
-<!--   tm_layout(title = 'April avg tmin', -->
-<!--             legend.outside = T) -->
-
-<!-- #may -->
-<!-- tmin_hrus_may<- tmin_hrus_mo %>% -->
-<!--   filter(month == 5) -->
-
-<!-- hrus_map_tmin_may <- left_join(hrus, tmin_hrus_may, by = 'value') -->
-
-<!-- may_tmin <- tm_shape(hrus_map_tmin_may) + -->
-<!--   tm_fill('mo_tmin_diff', id = 'value', -->
-<!--          breaks = c(-5,-2.5,0,2.5,5)) + -->
-<!--   tm_borders() + -->
-<!-- tm_shape(locations_t) + -->
-<!--   tm_symbols(col='blue', size = 0.25) + -->
-<!--   tm_layout(title = 'May avg tmin', -->
-<!--             legend.outside = T) -->
-
-<!-- #june -->
-<!-- tmin_hrus_jun<- tmin_hrus_mo %>% -->
-<!--   filter(month == 6) -->
-
-<!-- hrus_map_tmin_jun <- left_join(hrus, tmin_hrus_jun, by = 'value') -->
-
-<!-- jun_tmin <- tm_shape(hrus_map_tmin_jun) + -->
-<!--   tm_fill('mo_tmin_diff', id = 'value', -->
-<!--           breaks = c(-5,-2.5,0,2.5,5)) + -->
-<!--   tm_borders() + -->
-<!-- tm_shape(locations_t) + -->
-<!--   tm_symbols(col='blue', size = 0.25) + -->
-<!--   tm_layout(title = 'June avg tmin', -->
-<!--             legend.outside = T) -->
-
-<!-- tmap_arrange(mar_tmin, apr_tmin, may_tmin, jun_tmin) -->
-
-<!-- ``` -->
-
-<!-- ## Cumulative Precip difference -->
-
-<!-- 2011-2020 average of daily station-grid precip for DOY 365 (or 366) -->
-
-<!-- ```{r cum precip, echo = F} -->
-<!-- #get rid of a bunch of data -->
-<!-- hru_grid_precip <- hru_grids %>% -->
-<!--   dplyr::select(c(time, ID, precip)) %>% -->
-<!--   rename(precip_grid = precip) -->
-
-<!-- hru_statn_precip <- hru_statn %>% -->
-<!--   dplyr::select(c(time, ID, precip)) %>% -->
-<!--   rename(precip_statn = precip) -->
-
-<!-- precip_hrus <- left_join(hru_grid_precip, hru_statn_precip, by = c('time', 'ID')) %>% -->
-<!--   mutate(diff = precip_statn - precip_grid, -->
-<!--          year = year(time)) %>% -->
-<!--   group_by(year, ID) %>% -->
-<!--   mutate(total_diff = cumsum(diff)) %>% -->
-<!--   filter(time == max(time)) %>% -->
-<!--   group_by(ID) %>% -->
-<!--   summarize(precip_avg_cumdiff = mean(total_diff)) %>% -->
-<!--   rename(value = ID) -->
-
-<!-- hrus_map_precip <- left_join(hrus, precip_hrus, by = 'value') -->
-
-<!-- tmap_mode('view') -->
-
-<!-- locations_p <- locations %>% -->
-<!--   filter(type == 'precip') -->
-
-<!-- tm_shape(hrus_map_precip) + -->
-<!--   tm_polygons('precip_avg_cumdiff', midpoint = NA, palette = 'YlGnBu', id = 'value') + -->
-<!-- tm_shape(locations_p) + -->
-<!--   tm_symbols(col='blue', size=4) -->
-
-<!-- ``` -->
-
-<!-- ## Solar radiation difference -->
-
-<!-- 2011-2020 average of daily station-grid solar rad -->
-
-<!-- ```{r cum sol rad, echo = F} -->
-
-<!-- #get rid of a bunch of data -->
-<!-- hru_grid_solrad <- hru_grids %>% -->
-<!--   dplyr::select(c(time, ID, solRad)) %>% -->
-<!--   rename(solrad_grid = solRad)  %>% -->
-<!--   group_by(ID) %>% -->
-<!--   summarize(solrad_all_grid = mean(solrad_grid)) -->
-
-<!-- hru_statn_solrad <- hru_statn %>% -->
-<!--   dplyr::select(c(time, ID, solRad)) %>% -->
-<!--   rename(solrad_statn = solRad) %>% -->
-<!--   group_by(ID) %>% -->
-<!--   summarize(solrad_all_statn = mean(solrad_statn)) -->
-
-<!-- solrad_hrus <- left_join(hru_grid_solrad, hru_statn_solrad, by = c('ID')) %>% -->
-<!--   mutate(diff = solrad_all_statn - solrad_all_grid) %>% -->
-<!--   rename(value = ID) -->
-
-<!-- hrus_map_solrad <- left_join(hrus, solrad_hrus, by = 'value') -->
-
-<!-- tmap_mode('view') -->
-
-<!-- locations_solrad <- locations %>% -->
-<!--   dplyr::filter(name %in% c('Gordon_South', -->
-<!--                         'Betasso', 'Niwot_Snotel')) -->
-
-<!-- tm_shape(hrus_map_solrad) + -->
-<!--   tm_polygons('diff', midpoint = NA, palette = 'YlOrRd', id = 'value') + -->
-<!-- tm_shape(locations_solrad) + -->
-<!--   tm_symbols(col='blue', size=4) -->
-
-<!-- ``` -->
-
-<!-- ## RH difference -->
-
-<!-- ```{r rh, echo = F} -->
-
-<!-- #get rid of a bunch of data -->
-<!-- hru_grid_rh <- hru_grids %>% -->
-<!--   dplyr::select(c(time, ID, rhum)) %>% -->
-<!--   rename(rh_grid = rhum)  %>% -->
-<!--   group_by(ID) %>% -->
-<!--   summarize(rh_all_grid = mean(rh_grid)) -->
-
-<!-- hru_statn_rh <- hru_statn %>% -->
-<!--   dplyr::select(c(time, ID, rhum)) %>% -->
-<!--   rename(rh_statn = rhum) %>% -->
-<!--   group_by(ID) %>% -->
-<!--   summarize(rh_all_statn = mean(rh_statn)) -->
-
-<!-- rh_hrus <- left_join(hru_grid_rh, hru_statn_rh, by = c('ID')) %>% -->
-<!--   mutate(diff = rh_all_statn - rh_all_grid) %>% -->
-<!--   rename(value = ID) -->
-
-<!-- hrus_map_rh <- left_join(hrus, rh_hrus, by = 'value') -->
-
-<!-- tmap_mode('view') -->
-
-<!-- locations_rh <- locations %>% -->
-<!--   dplyr::filter(name %in% c('Gordon_South', 'Gordon_North', -->
-<!--                         'Betasso', 'Niwot_Snotel')) -->
-
-<!-- tm_shape(hrus_map_rh) + -->
-<!--   tm_polygons('diff', midpoint = NA, id = 'value') + -->
-<!-- tm_shape(locations_rh) + -->
-<!--   tm_symbols(col='blue', size=4) -->
-
-<!-- ``` -->
-
-<!-- ## Average soil sat comparison -->
-
-<!-- ```{r soilsat, echo = F} -->
-
-<!-- #get rid of a bunch of data -->
-<!-- hru_grid_soilsat <- hru_grids %>% -->
-<!--   dplyr::select(c(time, ID, soilSat)) %>% -->
-<!--   rename(soilsat_grid = soilSat)  %>% -->
-<!--   group_by(ID) %>% -->
-<!--   summarize(soilsat_all_grid = mean(soilsat_grid)) -->
-
-<!-- hru_statn_soilsat <- hru_statn %>% -->
-<!--   dplyr::select(c(time, ID, soilSat)) %>% -->
-<!--   rename(soilsat_statn = soilSat) %>% -->
-<!--   group_by(ID) %>% -->
-<!--   summarize(soilsat_all_statn = mean(soilsat_statn)) -->
-
-<!-- soilsat_hrus <- left_join(hru_grid_soilsat, hru_statn_soilsat, by = c('ID')) %>% -->
-<!--   rename(value = ID) -->
-
-<!-- hrus_map_soilsat <- left_join(hrus, soilsat_hrus, by = 'value') -->
-
-<!-- tmap_mode('plot') -->
-
-<!-- soilavg_grid <- tm_shape(hrus_map_soilsat) + -->
-<!--   tm_polygons('soilsat_all_grid', midpoint = NA, id = 'value', -->
-<!--               breaks = c(0.0, 0.05, 0.1, 0.15, 0.2, 0.25, 0.3)) + -->
-<!--   tm_legend(legend.outside = T) + -->
-<!--   tm_layout(main.title = 'Average soil sat') -->
-
-<!-- soilavg_statn <- tm_shape(hrus_map_soilsat) + -->
-<!--   tm_polygons('soilsat_all_statn', midpoint = NA, id = 'value', -->
-<!--               breaks = c(0.0, 0.05, 0.1, 0.15, 0.2, 0.25, 0.3)) + -->
-<!--   tm_legend(legend.outside = T) -->
-
-<!-- tmap_arrange(soilavg_grid, soilavg_statn) -->
-
-<!-- ``` -->
-
-<!-- ## Average max soil sat comparison -->
-
-<!-- ```{r max soilsat, echo = F} -->
-
-<!-- #get rid of a bunch of data -->
-<!-- hru_grid_soilsat_max <- hru_grids %>% -->
-<!--   dplyr::select(c(time, ID, soilSat)) %>% -->
-<!--   rename(soilsat_grid = soilSat)  %>% -->
-<!--   mutate(year = year(time)) %>% -->
-<!--   group_by(ID, year) %>% -->
-<!--   summarize(soilsat_yrmax_grid = max(soilsat_grid)) %>% -->
-<!--   summarize(avg_max_grid = mean(soilsat_yrmax_grid)) -->
-
-<!-- hru_statn_soilsat_max <- hru_statn %>% -->
-<!--   dplyr::select(c(time, ID, soilSat)) %>% -->
-<!--   rename(soilsat_statn = soilSat) %>% -->
-<!--   mutate(year = year(time)) %>% -->
-<!--   group_by(ID, year) %>% -->
-<!--   summarize(soilsat_yrmax_statn = max(soilsat_statn)) %>% -->
-<!--   summarize(avg_max_statn = mean(soilsat_yrmax_statn)) -->
-
-<!-- soilsat_hrus_max <- left_join(hru_grid_soilsat_max, hru_statn_soilsat_max, by = c('ID')) %>% -->
-<!--   rename(value = ID) -->
-
-<!-- hrus_map_soilsat_max <- left_join(hrus, soilsat_hrus_max, by = 'value') -->
-
-<!-- tmap_mode('plot') -->
-
-<!-- soilavg_grid_max <- tm_shape(hrus_map_soilsat_max) + -->
-<!--   tm_polygons('avg_max_grid', midpoint = NA, id = 'value', -->
-<!--               breaks = c(0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.7)) + -->
-<!--   tm_legend(legend.outside = T) + -->
-<!--   tm_layout(main.title = 'Average max soil sat', -->
-<!--             title.position = c('left', 'top')) -->
-
-<!-- soilavg_statn_max <- tm_shape(hrus_map_soilsat_max) + -->
-<!--   tm_polygons('avg_max_statn', midpoint = NA, id = 'value', -->
-<!--               breaks = c(0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.7)) + -->
-<!--   tm_legend(legend.outside = T) -->
-
-<!-- tmap_arrange(soilavg_grid_max, soilavg_statn_max) -->
-
-<!-- ``` -->
-
-<!-- ## Average ET comparison -->
-
-<!-- ```{r et, echo = F} -->
-<!-- #get rid of a bunch of data -->
-<!-- hru_grid_ET <- hru_grids %>% -->
-<!--   dplyr::select(c(time, ID, actET)) %>% -->
-<!--   rename(ET_grid = actET)  %>% -->
-<!--   group_by(ID) %>% -->
-<!--   summarize(ET_all_grid = mean(ET_grid)) -->
-
-<!-- hru_statn_ET <- hru_statn %>% -->
-<!--   dplyr::select(c(time, ID, actET)) %>% -->
-<!--   rename(ET_statn = actET) %>% -->
-<!--   group_by(ID) %>% -->
-<!--   summarize(ET_all_statn = mean(ET_statn)) -->
-
-<!-- ET_hrus <- left_join(hru_grid_ET, hru_statn_ET, by = c('ID')) %>% -->
-<!--   rename(value = ID) -->
-
-<!-- hrus_map_ET <- left_join(hrus, ET_hrus, by = 'value') -->
-
-<!-- tmap_mode('plot') -->
-
-<!-- ETavg_grid <- tm_shape(hrus_map_ET) + -->
-<!--   tm_polygons('ET_all_grid', midpoint = NA, id = 'value', -->
-<!--               breaks = c(0.2, 0.4, 0.6, 0.8, 1.0, 1.2)) + -->
-<!--   tm_legend(legend.outside = T) + -->
-<!--   tm_layout(main.title = 'Average ET') -->
-
-<!-- ETavg_statn <- tm_shape(hrus_map_ET) + -->
-<!--   tm_polygons('ET_all_statn', midpoint = NA, id = 'value', -->
-<!--              breaks = c(0.2, 0.4, 0.6, 0.8, 1.0, 1.2)) + -->
-<!--   tm_legend(legend.outside = T) -->
-
-<!-- tmap_arrange(ETavg_grid, ETavg_statn) -->
-
-<!-- ``` -->
-
-<!-- ## Average ET difference -->
-
-<!-- ```{r et diff, echo = F} -->
-
-<!-- ET_hrus <- ET_hrus %>% -->
-<!--   mutate(diff = ET_all_statn - ET_all_grid) -->
-
-<!-- hrus_map_et_diff <- left_join(hrus, ET_hrus, by = 'value') -->
-
-<!-- tmap_mode('plot') -->
-
-<!-- tm_shape(hrus_map_et_diff) + -->
-<!--   tm_polygons('diff', midpoint = NA, id = 'value')  + -->
-<!--   tm_legend(legend.outside = T) + -->
-<!--   tm_layout(main.title = 'Average ET difference') -->
-
-<!-- ``` -->
-
-<!-- ## Average LAI comparison -->
-
-<!-- ```{r lai, echo = F} -->
-
-<!-- #get rid of a bunch of data -->
-<!-- hru_grid_LAI <- hru_grids %>% -->
-<!--   dplyr::select(c(time, ID, LAI)) %>% -->
-<!--   rename(LAI_grid = LAI)  %>% -->
-<!--   group_by(ID) %>% -->
-<!--   summarize(LAI_all_grid = mean(LAI_grid)) -->
-
-<!-- hru_statn_LAI <- hru_statn %>% -->
-<!--   dplyr::select(c(time, ID, LAI)) %>% -->
-<!--   rename(LAI_statn = LAI) %>% -->
-<!--   group_by(ID) %>% -->
-<!--   summarize(LAI_all_statn = mean(LAI_statn)) -->
-
-<!-- LAI_hrus <- left_join(hru_grid_LAI, hru_statn_LAI, by = c('ID')) %>% -->
-<!--   rename(value = ID) -->
-
-<!-- hrus_map_LAI <- left_join(hrus, LAI_hrus, by = 'value') -->
-
-<!-- tmap_mode('view') -->
-
-<!-- LAIavg_grid <- tm_shape(hrus_map_LAI) + -->
-<!--   tm_polygons('LAI_all_grid', midpoint = NA, id = 'value', -->
-<!--               breaks = c(1,2,3,4,5)) + -->
-<!--   tm_legend(legend.outside = T) + -->
-<!--   tm_layout(main.title = 'Average LAI') -->
-
-<!-- LAIavg_statn <- tm_shape(hrus_map_LAI) + -->
-<!--   tm_polygons('LAI_all_statn', midpoint = NA, id = 'value', -->
-<!--               breaks = c(1,2,3,4,5)) + -->
-<!--   tm_legend(legend.outside = T) -->
-
-<!-- tmap_arrange(LAIavg_grid, LAIavg_statn) -->
-
-<!-- ``` -->
+# HRU results
+
+## Tmean difference
+
+2011-2020 average of daily station-grid Tmean
+
+```{r cumulative tmean for HRUs, echo = F}
+hrus <- st_read('/Users/megansears/Documents/Repos/fourmile/38HRU_model/hrus_final.shp')
+
+locations <- read_csv('/Users/megansears/Documents/Repos/fourmile/38HRU_model/fourmile_sensors.csv')
+
+locations <- locations %>%
+  st_as_sf(., coords=c('y','x'), crs = 4326)
+
+#grid first
+setwd("/Users/megansears/Documents/Repos/fourmile/38HRU_model/HRU_output/grid_all")
+
+read_ages_grid <- function(dataframe){
+  read_csv(dataframe, skip = 3) %>%
+  slice(3:n()) %>%
+  dplyr::select(-starts_with('@'),
+                -1) %>%
+  mutate(time = ymd(time)) %>%
+  mutate_if(is.character, as.numeric) %>%
+  mutate(source = 'grid')
+
+}
+
+#pull in all filenames with HRU in the name
+filenames <- list.files(".", pattern="HRU", full.names=F)
+
+#read all the csvs using read_ages function
+dataframes <- lapply(filenames, read_ages_grid)
+
+#name all the csvs based on first 6 characters
+names(dataframes) <- substr(filenames, 1, 6)
+
+#bind all and make 1 df
+hru_grids <- dataframes %>%
+  bind_rows()
+
+#statn next
+setwd("/Users/megansears/Documents/Repos/fourmile/38HRU_model/HRU_output/statn_all")
+
+read_ages_statn <- function(dataframe){
+  read_csv(dataframe, skip = 3) %>%
+  slice(3:n()) %>%
+  dplyr::select(-starts_with('@'),
+                -1) %>%
+  mutate(time = ymd(time)) %>%
+  mutate_if(is.character, as.numeric) %>%
+  mutate(source = 'statn')
+
+}
+
+#pull in all filenames with HRU in the name
+filenames <- list.files(".", pattern="HRU", full.names=F)
+
+#read all the csvs using read_ages function
+dataframes <- lapply(filenames, read_ages_statn)
+
+#name all the csvs based on first 6 characters
+names(dataframes) <- substr(filenames, 1, 6)
+
+#bind all and make 1 df
+hru_statn <- dataframes %>%
+  bind_rows()
+
+#get rid of a bunch of data
+hru_grid_tmean <- hru_grids %>%
+  dplyr::select(c(time, ID, tmean)) %>%
+  rename(tmean_grid = tmean)  %>%
+  group_by(ID) %>%
+  summarize(tmean_all_grid = mean(tmean_grid))
+
+hru_statn_tmean <- hru_statn %>%
+  dplyr::select(c(time, ID, tmean)) %>%
+  rename(tmean_statn = tmean) %>%
+  group_by(ID) %>%
+  summarize(tmean_all_statn = mean(tmean_statn))
+
+tmean_hrus <- left_join(hru_grid_tmean, hru_statn_tmean, by = c('ID')) %>%
+  mutate(diff = tmean_all_statn - tmean_all_grid) %>%
+  rename(value = ID)
+
+hrus_map_tmean <- left_join(hrus, tmean_hrus, by = 'value')
+
+tmap_mode('view')
+
+locations_t <- locations %>%
+  dplyr::filter(name %in% c('Gordon_South', 'Gordon_North',
+                        'Betasso', 'Niwot_Snotel',
+                        'University Camp SNTL'))
+
+tm_shape(hrus_map_tmean) +
+  tm_polygons('diff', id = 'value',
+              breaks = c(-6,-4,-2,0,2,4,6)) +
+tm_shape(locations_t) +
+  tm_symbols(col='blue', size=4)
+
+```
+
+## Tmax difference
+
+```{r tmax, echo = F}
+
+#get rid of a bunch of data
+hru_grid_tmax <- hru_grids %>%
+  dplyr::select(c(time, ID, tmax)) %>%
+  rename(tmax_grid = tmax)  %>%
+  group_by(ID) %>%
+  summarize(tmax_all_grid = mean(tmax_grid))
+
+hru_statn_tmax <- hru_statn %>%
+  dplyr::select(c(time, ID, tmax)) %>%
+  rename(tmax_statn = tmax) %>%
+  group_by(ID) %>%
+  summarize(tmax_all_statn = mean(tmax_statn))
+
+tmax_hrus <- left_join(hru_grid_tmax, hru_statn_tmax, by = c('ID')) %>%
+  mutate(diff = tmax_all_statn - tmax_all_grid) %>%
+  rename(value = ID)
+
+hrus_map_tmax <- left_join(hrus, tmax_hrus, by = 'value')
+
+tmap_mode('view')
+
+locations_t <- locations %>%
+  dplyr::filter(name %in% c('Gordon_South', 'Gordon_North',
+                        'Betasso', 'Niwot_Snotel',
+                        'University Camp SNTL'))
+
+tm_shape(hrus_map_tmax) +
+  tm_polygons('diff', id = 'value',
+              breaks = c(-6,-4,-2,0,2,4,6)) +
+tm_shape(locations_t) +
+  tm_symbols(col='blue', size=4)
+
+```
+
+## Tmin difference
+
+```{r tmin, echo = F}
+
+#get rid of a bunch of data
+hru_grid_tmin <- hru_grids %>%
+  dplyr::select(c(time, ID, tmin)) %>%
+  rename(tmin_grid = tmin)  %>%
+  group_by(ID) %>%
+  summarize(tmin_all_grid = mean(tmin_grid))
+
+hru_statn_tmin <- hru_statn %>%
+  dplyr::select(c(time, ID, tmin)) %>%
+  rename(tmin_statn = tmin) %>%
+  group_by(ID) %>%
+  summarize(tmin_all_statn = mean(tmin_statn))
+
+tmin_hrus <- left_join(hru_grid_tmin, hru_statn_tmin, by = c('ID')) %>%
+  mutate(diff = tmin_all_statn - tmin_all_grid) %>%
+  rename(value = ID)
+
+hrus_map_tmin <- left_join(hrus, tmin_hrus, by = 'value')
+
+tmap_mode('view')
+
+locations_t <- locations %>%
+  dplyr::filter(name %in% c('Gordon_South', 'Gordon_North',
+                        'Betasso', 'Niwot_Snotel',
+                        'University Camp SNTL'))
+
+tm_shape(hrus_map_tmin) +
+  tm_polygons('diff', id = 'value',
+              breaks = c(-6,-4,-2,0,2,4,6)) +
+tm_shape(locations_t) +
+  tm_symbols(col='blue', size=4)
+
+```
+
+## Cumulative Precip difference
+
+2011-2020 average of daily station-grid precip for DOY 365 (or 366)
+
+```{r cum precip, echo = F}
+#get rid of a bunch of data
+hru_grid_precip <- hru_grids %>%
+  dplyr::select(c(time, ID, precip)) %>%
+  rename(precip_grid = precip)
+
+hru_statn_precip <- hru_statn %>%
+  dplyr::select(c(time, ID, precip)) %>%
+  rename(precip_statn = precip)
+
+precip_hrus <- left_join(hru_grid_precip, hru_statn_precip, by = c('time', 'ID')) %>%
+  mutate(diff = precip_statn - precip_grid,
+         year = year(time)) %>%
+  group_by(year, ID) %>%
+  mutate(total_diff = cumsum(diff)) %>%
+  filter(time == max(time)) %>%
+  group_by(ID) %>%
+  summarize(precip_avg_cumdiff = mean(total_diff)) %>%
+  rename(value = ID)
+
+hrus_map_precip <- left_join(hrus, precip_hrus, by = 'value')
+
+tmap_mode('view')
+
+locations_p <- locations %>%
+  filter(type == 'precip')
+
+tm_shape(hrus_map_precip) +
+  tm_polygons('precip_avg_cumdiff', midpoint = NA, palette = 'YlGnBu', id = 'value') +
+tm_shape(locations_p) +
+  tm_symbols(col='blue', size=4)
+
+```
+
+## Solar radiation difference
+
+2011-2020 average of daily station-grid solar rad
+
+```{r cum sol rad, echo = F}
+
+#get rid of a bunch of data
+hru_grid_solrad <- hru_grids %>%
+  dplyr::select(c(time, ID, solRad)) %>%
+  rename(solrad_grid = solRad)  %>%
+  group_by(ID) %>%
+  summarize(solrad_all_grid = mean(solrad_grid))
+
+hru_statn_solrad <- hru_statn %>%
+  dplyr::select(c(time, ID, solRad)) %>%
+  rename(solrad_statn = solRad) %>%
+  group_by(ID) %>%
+  summarize(solrad_all_statn = mean(solrad_statn))
+
+solrad_hrus <- left_join(hru_grid_solrad, hru_statn_solrad, by = c('ID')) %>%
+  mutate(diff = solrad_all_statn - solrad_all_grid) %>%
+  rename(value = ID)
+
+hrus_map_solrad <- left_join(hrus, solrad_hrus, by = 'value')
+
+tmap_mode('view')
+
+locations_solrad <- locations %>%
+  dplyr::filter(name %in% c('Gordon_South',
+                        'Betasso', 'Niwot_Snotel'))
+
+tm_shape(hrus_map_solrad) +
+  tm_polygons('diff', midpoint = NA, palette = 'YlOrRd', id = 'value') +
+tm_shape(locations_solrad) +
+  tm_symbols(col='blue', size=4)
+
+```
+
+## RH difference
+
+```{r rh, echo = F}
+
+#get rid of a bunch of data
+hru_grid_rh <- hru_grids %>%
+  dplyr::select(c(time, ID, rhum)) %>%
+  rename(rh_grid = rhum)  %>%
+  group_by(ID) %>%
+  summarize(rh_all_grid = mean(rh_grid))
+
+hru_statn_rh <- hru_statn %>%
+  dplyr::select(c(time, ID, rhum)) %>%
+  rename(rh_statn = rhum) %>%
+  group_by(ID) %>%
+  summarize(rh_all_statn = mean(rh_statn))
+
+rh_hrus <- left_join(hru_grid_rh, hru_statn_rh, by = c('ID')) %>%
+  mutate(diff = rh_all_statn - rh_all_grid) %>%
+  rename(value = ID)
+
+hrus_map_rh <- left_join(hrus, rh_hrus, by = 'value')
+
+tmap_mode('view')
+
+locations_rh <- locations %>%
+  dplyr::filter(name %in% c('Gordon_South', 'Gordon_North',
+                        'Betasso', 'Niwot_Snotel'))
+
+tm_shape(hrus_map_rh) +
+  tm_polygons('diff', midpoint = NA, id = 'value') +
+tm_shape(locations_rh) +
+  tm_symbols(col='blue', size=4)
+
+```
+
+## Average soil sat comparison
+
+```{r soilsat, echo = F}
+
+#get rid of a bunch of data
+hru_grid_soilsat <- hru_grids %>%
+  dplyr::select(c(time, ID, soilSat)) %>%
+  rename(soilsat_grid = soilSat)  %>%
+  group_by(ID) %>%
+  summarize(soilsat_all_grid = mean(soilsat_grid))
+
+hru_statn_soilsat <- hru_statn %>%
+  dplyr::select(c(time, ID, soilSat)) %>%
+  rename(soilsat_statn = soilSat) %>%
+  group_by(ID) %>%
+  summarize(soilsat_all_statn = mean(soilsat_statn))
+
+soilsat_hrus <- left_join(hru_grid_soilsat, hru_statn_soilsat, by = c('ID')) %>%
+  rename(value = ID)
+
+hrus_map_soilsat <- left_join(hrus, soilsat_hrus, by = 'value')
+
+tmap_mode('plot')
+
+soilavg_grid <- tm_shape(hrus_map_soilsat) +
+  tm_polygons('soilsat_all_grid', midpoint = NA, id = 'value',
+              breaks = c(0.0, 0.05, 0.1, 0.15, 0.2, 0.25, 0.3, 0.35, 0.4)) +
+  tm_legend(legend.outside = T) +
+  tm_layout(main.title = 'Average soil sat')
+
+soilavg_statn <- tm_shape(hrus_map_soilsat) +
+  tm_polygons('soilsat_all_statn', midpoint = NA, id = 'value',
+              breaks = c(0.0, 0.05, 0.1, 0.15, 0.2, 0.25, 0.3, 0.35, 0.4)) +
+  tm_legend(legend.outside = T)
+
+tmap_arrange(soilavg_grid, soilavg_statn)
+
+```
+
+## Average max soil sat comparison
+
+```{r max soilsat, echo = F}
+
+#get rid of a bunch of data
+hru_grid_soilsat_max <- hru_grids %>%
+  dplyr::select(c(time, ID, soilSat)) %>%
+  rename(soilsat_grid = soilSat)  %>%
+  mutate(year = year(time)) %>%
+  group_by(ID, year) %>%
+  summarize(soilsat_yrmax_grid = max(soilsat_grid)) %>%
+  summarize(avg_max_grid = mean(soilsat_yrmax_grid))
+
+hru_statn_soilsat_max <- hru_statn %>%
+  dplyr::select(c(time, ID, soilSat)) %>%
+  rename(soilsat_statn = soilSat) %>%
+  mutate(year = year(time)) %>%
+  group_by(ID, year) %>%
+  summarize(soilsat_yrmax_statn = max(soilsat_statn)) %>%
+  summarize(avg_max_statn = mean(soilsat_yrmax_statn))
+
+soilsat_hrus_max <- left_join(hru_grid_soilsat_max, hru_statn_soilsat_max, by = c('ID')) %>%
+  rename(value = ID)
+
+hrus_map_soilsat_max <- left_join(hrus, soilsat_hrus_max, by = 'value')
+
+tmap_mode('plot')
+
+soilavg_grid_max <- tm_shape(hrus_map_soilsat_max) +
+  tm_polygons('avg_max_grid', midpoint = NA, id = 'value',
+              breaks = c(0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.7, 0.8)) +
+  tm_legend(legend.outside = T) +
+  tm_layout(main.title = 'Average max soil sat',
+            title.position = c('left', 'top'))
+
+soilavg_statn_max <- tm_shape(hrus_map_soilsat_max) +
+  tm_polygons('avg_max_statn', midpoint = NA, id = 'value',
+              breaks = c(0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.7, 0.8)) +
+  tm_legend(legend.outside = T)
+
+tmap_arrange(soilavg_grid_max, soilavg_statn_max)
+
+```
+
+## Average ET comparison
+
+```{r et, echo = F}
+#get rid of a bunch of data
+hru_grid_ET <- hru_grids %>%
+  dplyr::select(c(time, ID, actET)) %>%
+  rename(ET_grid = actET)  %>%
+  group_by(ID) %>%
+  summarize(ET_all_grid = mean(ET_grid))
+
+hru_statn_ET <- hru_statn %>%
+  dplyr::select(c(time, ID, actET)) %>%
+  rename(ET_statn = actET) %>%
+  group_by(ID) %>%
+  summarize(ET_all_statn = mean(ET_statn))
+
+ET_hrus <- left_join(hru_grid_ET, hru_statn_ET, by = c('ID')) %>%
+  rename(value = ID)
+
+hrus_map_ET <- left_join(hrus, ET_hrus, by = 'value')
+
+tmap_mode('plot')
+
+ETavg_grid <- tm_shape(hrus_map_ET) +
+  tm_polygons('ET_all_grid', midpoint = NA, id = 'value',
+              breaks = c(0.0,0.2, 0.4, 0.6, 0.8, 1.0, 1.2)) +
+  tm_legend(legend.outside = T) +
+  tm_layout(main.title = 'Average ET')
+
+ETavg_statn <- tm_shape(hrus_map_ET) +
+  tm_polygons('ET_all_statn', midpoint = NA, id = 'value',
+             breaks = c(0.0, 0.1, 0.2, 0.4, 0.6, 0.8, 1.0, 1.2)) +
+  tm_legend(legend.outside = T)
+
+tmap_arrange(ETavg_grid, ETavg_statn)
+
+```
+
+## Average ET difference
+
+```{r et diff, echo = F}
+
+ET_hrus <- ET_hrus %>%
+  mutate(diff = ET_all_statn - ET_all_grid)
+
+hrus_map_et_diff <- left_join(hrus, ET_hrus, by = 'value')
+
+tmap_mode('plot')
+
+tm_shape(hrus_map_et_diff) +
+  tm_polygons('diff', midpoint = NA, id = 'value')  +
+  tm_legend(legend.outside = T) +
+  tm_layout(main.title = 'Average ET difference')
+
+```
+
+## Average LAI comparison
+
+```{r lai, echo = F}
+
+#get rid of a bunch of data
+hru_grid_LAI <- hru_grids %>%
+  dplyr::select(c(time, ID, LAI)) %>%
+  rename(LAI_grid = LAI)  %>%
+  group_by(ID) %>%
+  summarize(LAI_all_grid = mean(LAI_grid))
+
+hru_statn_LAI <- hru_statn %>%
+  dplyr::select(c(time, ID, LAI)) %>%
+  rename(LAI_statn = LAI) %>%
+  group_by(ID) %>%
+  summarize(LAI_all_statn = mean(LAI_statn))
+
+LAI_hrus <- left_join(hru_grid_LAI, hru_statn_LAI, by = c('ID')) %>%
+  rename(value = ID)
+
+hrus_map_LAI <- left_join(hrus, LAI_hrus, by = 'value')
+
+tmap_mode('view')
+
+LAIavg_grid <- tm_shape(hrus_map_LAI) +
+  tm_polygons('LAI_all_grid', midpoint = NA, id = 'value',
+              breaks = c(1,2,3,4,5)) +
+  tm_legend(legend.outside = T) +
+  tm_layout(main.title = 'Average LAI')
+
+LAIavg_statn <- tm_shape(hrus_map_LAI) +
+  tm_polygons('LAI_all_statn', midpoint = NA, id = 'value',
+              breaks = c(1,2,3,4,5)) +
+  tm_legend(legend.outside = T)
+
+tmap_arrange(LAIavg_grid, LAIavg_statn)
+
+```

### 2024-06-14 38HRU_model/fourmile_model_outputs.Rmd
added in burned vs unburned param boxplots
updating git ignore

@@
 
+# find min and max of grid and statn param for sensitivity analysis
+# grid_minmax <- grid %>%
+#   group_by(param) %>%
+#   summarize(min = as.numeric(min(value)),
+#             max = as.numeric(max(value))) %>%
+#   mutate(input = 'grid_unburn')
+# 
+# statn_minmax <- statn %>%
+#   group_by(param) %>%
+#   summarize(min = as.numeric(min(value)),
+#             max = as.numeric(max(value))) %>%
+#   mutate(input = 'statn_unburn')
+# 
+# minmax_burn <- burn_params %>%
+#   group_by(params, input_data) %>%
+#   summarize(min = min(value),
+#             max = max(value)) %>%
+#   mutate(input = paste(input_data, '_burn')) %>%
+#   dplyr::select(-input_data) %>%
+#   rename(param = params) %>%
+#   mutate(param = as.character(param))
+# 
+# minmax_params <- bind_rows(grid_minmax, statn_minmax, minmax_burn)
+# write.csv(minmax_params, 'min_max_params.csv')
+
 ```
@@
 lapply(name2, plot_params)
+
+# boxplots of burned and unburned
+
+ggplot(params_combo, aes(x=burn, y=value, fill=input_data)) +
+  geom_boxplot() +
+  facet_wrap(~param, scales = 'free_y')
 
@@
 
-gw_grid <- read_csv(here('catchment_output/gridall_outlet.csv')) %>%
-  dplyr::select(time, catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w) %>%
-  mutate(source = 'grid')
-
-gw_statn <- read_csv(here('catchment_output/statnall_outlet.csv')) %>%
-  dplyr::select(time, catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w) %>%
-  mutate(source = 'statn')
-
-gw <- bind_rows(gw_grid, gw_statn) %>%
-  mutate(year = year(time)) %>%
-  rename(date = time)
+gw_gridall <- read_csv(here('catchment_output/gridall_outlet.csv')) %>%
+  dplyr::select(time, catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w) %>%
+  mutate(source = 'grid_all')
+
+gw_statnall <- read_csv(here('catchment_output/statnall_outlet.csv')) %>%
+  dplyr::select(time, catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w) %>%
+  mutate(source = 'statn_all')
+
+gw_grid2011 <- read_csv(here('catchment_output/grid2011_outlet.csv')) %>%
+  dplyr::select(time, catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w) %>%
+  mutate(source = 'grid_2011')
+
+gw_grid2012 <- read_csv(here('catchment_output/grid2012_outlet.csv')) %>%
+  dplyr::select(time, catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w) %>%
+  mutate(source = 'grid_2012')
+
+gw_grid2013 <- read_csv(here('catchment_output/grid2013_outlet.csv')) %>%
+  dplyr::select(time, catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w) %>%
+  mutate(source = 'grid_2013')
+
+gw_grid2014 <- read_csv(here('catchment_output/grid2014_outlet.csv')) %>%
+  dplyr::select(time, catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w) %>%
+  mutate(source = 'grid_2014')
+
+gw_grid2015 <- read_csv(here('catchment_output/grid2015_outlet.csv')) %>%
+  dplyr::select(time, catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w) %>%
+  mutate(source = 'grid_2015')
+
+gw_grid2016 <- read_csv(here('catchment_output/grid2016_outlet.csv')) %>%
+  dplyr::select(time, catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w) %>%
+  mutate(source = 'grid_2016')
+
+gw_grid2017 <- read_csv(here('catchment_output/grid2017_outlet.csv')) %>%
+  dplyr::select(time, catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w) %>%
+  mutate(source = 'grid_2017')
+
+gw_grid2018 <- read_csv(here('catchment_output/grid2018_outlet.csv')) %>%
+  dplyr::select(time, catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w) %>%
+  mutate(source = 'grid_2018')
+
+gw_grid2019 <- read_csv(here('catchment_output/grid2019_outlet.csv')) %>%
+  dplyr::select(time, catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w) %>%
+  mutate(source = 'grid_2019')
+
+gw_grid2020 <- read_csv(here('catchment_output/grid2020_outlet.csv')) %>%
+  dplyr::select(time, catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w) %>%
+  mutate(source = 'grid_2020')
+
+gw_statn2011 <- read_csv(here('catchment_output/statn2011_outlet.csv')) %>%
+  dplyr::select(time, catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w) %>%
+  mutate(source = 'statn_2011')
+
+gw_statn2012 <- read_csv(here('catchment_output/statn2012_outlet.csv')) %>%
+  dplyr::select(time, catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w) %>%
+  mutate(source = 'statn_2012')
+
+gw_statn2013 <- read_csv(here('catchment_output/statn2013_outlet.csv')) %>%
+  dplyr::select(time, catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w) %>%
+  mutate(source = 'statn_2013')
+
+gw_statn2014 <- read_csv(here('catchment_output/statn2014_outlet.csv')) %>%
+  dplyr::select(time, catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w) %>%
+  mutate(source = 'statn_2014')
+
+gw_statn2015 <- read_csv(here('catchment_output/statn2015_outlet.csv')) %>%
+  dplyr::select(time, catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w) %>%
+  mutate(source = 'statn_2015')
+
+gw_statn2016 <- read_csv(here('catchment_output/statn2016_outlet.csv')) %>%
+  dplyr::select(time, catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w) %>%
+  mutate(source = 'statn_2016')
+
+gw_statn2017 <- read_csv(here('catchment_output/statn2017_outlet.csv')) %>%
+  dplyr::select(time, catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w) %>%
+  mutate(source = 'statn_2017')
+
+gw_statn2018 <- read_csv(here('catchment_output/statn2018_outlet.csv')) %>%
+  dplyr::select(time, catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w) %>%
+  mutate(source = 'statn_2018')
+
+gw_statn2019 <- read_csv(here('catchment_output/statn2019_outlet.csv')) %>%
+  dplyr::select(time, catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w) %>%
+  mutate(source = 'statn_2019')
+
+gw_statn2020 <- read_csv(here('catchment_output/statn2020_outlet.csv')) %>%
+  dplyr::select(time, catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w) %>%
+  mutate(source = 'statn_2020')
+
+gw <- bind_rows(
+  gw_gridall, gw_statnall,
+  gw_grid2011, gw_grid2012,
+  gw_grid2013, gw_grid2014,
+  gw_grid2015, gw_grid2016,
+  gw_grid2017, gw_grid2018,
+  gw_grid2019, gw_grid2020,
+  gw_statn2011, gw_statn2012,
+  gw_statn2013, gw_statn2014,
+  gw_statn2015, gw_statn2016,
+  gw_statn2017, gw_statn2018,
+  gw_statn2019, gw_statn2020
+) %>%
+  mutate(date = mdy(time),
+         year = year(date))
 
@@
 gw <- gw %>%
+  arrange(date) %>%
   group_by(year, source) %>%
@@
   group_by(source, year) %>%
-  summarize(yr_max_RD1 = max(RD1cumsum),
-            yr_max_RD2 = max(RD2cumsum),
-            yr_max_RG1 = max(RG1cumsum),
-            yr_max_RG2 = max(RG2cumsum)) %>%
+  summarize(yr_cum_RD1 = max(RD1cumsum),
+            yr_cum_RD2 = max(RD2cumsum),
+            yr_cum_RG1 = max(RG1cumsum),
+            yr_cum_RG2 = max(RG2cumsum)) %>%
   mutate(year = as.factor(year)) %>%
@@
 ```
+
+# Join param & RD/RG
+
+```{r}
+
+join <- gw_maxcumsum %>%
+  rename(input_data = source)
+
+params1 <- params %>%
+  dplyr::select(-input_data) %>%
+  rename(input_data = cal) %>%
+  dplyr::select(-c(year_missing))
+
+join <- left_join(join, params1, by = c('input_data')) %>%
+  pivot_wider(., names_from='param', values_from='value') %>%
+  pivot_wider(., names_from = 'flow_type', values_from = 'flow_cms')
+
+write_csv(join, 'flow_params.csv')
+
+```

### 2024-06-14 fourmile_dataprocess.Rmd
things got weird
looking at ds3

@@
 ```{r loading data, include=FALSE}
-setwd('C:/Users/sears/Documents/Repos/fourmile/data')
+setwd('/Users/megansears/Documents/Repos/fourmile/data')
 
@@
 #save.image(file = 'spatial.RData')
-load('C:/Users/sears/Documents/Repos/fourmile/data/spatial.RData') ## need to update with new locations + fire boundary ***
+load('/Users/megansears/Documents/Repos/fourmile/data/GIS/spatial.Rdata') ## need to update with new locations + fire boundary ***
 
@@
 hydro <- ggplot(daily_q, aes(x=date, y=q_m3s, color=site)) + geom_line() +
-  ylim(0,8) + theme_bw() + 
+  geom_point() +
+  ylim(0,8) + 
+  theme_bw() + 
   ggtitle('Daily streamflow (all)')
@@
 ggplotly(hydro)
+
+daily_q_ds3 <- daily_q %>%
+  filter(site %in% c('ds3', 'usgs1')) %>%
+  mutate(year = year(date)) %>%
+  filter(year %in% c(2011:2015)) %>%
+  drop_na()
 

### 2024-06-14 spatial_figs.Rmd
creating spatial figures

---
title: "spatial_figures"
author: "Megan Sears"
date: "`r Sys.Date()`"
output: html_document
---

```{r open package, include=FALSE}

knitr::opts_chunk$set(warning = FALSE, message = FALSE)

library(tidyverse)
library(dplyr)
library(lubridate)
library(plotly)
library(ggplot2)
library(here)
library(sf)
library(mapview)
library(raster)
library(sf)
library(terra)
library(viridis)

```

# Figure 1a

```{r}

# update the HRUs
hru_new <- vect('/Users/megansears/Documents/Repos/fourmile/data/GIS/hrus_final.shp')
plot(hru_new)

hru_new <- st_read('/Users/megansears/Documents/Repos/fourmile/data/GIS/hrus_final.shp')

mapview(hru_new)

locations <- read_csv('/Users/megansears/Documents/Repos/fourmile/data/GIS/locations_all.csv')

locations <- locations %>%
  st_as_sf(., coords=c('lon','lat'), crs = 4326)

mapview(locations) + mapview(hru_new)

# Read the DEM raster file
dem_raster <- raster('/Users/megansears/Documents/Repos/fourmile/data/GIS/USGS_13_n41w106_20230314 (1).tif')
dem_raster2 <- raster('/Users/megansears/Documents/Repos/fourmile/data/GIS/USGS_13_n40w106_20230602.tif')

dem_raster <- merge(dem_raster, dem_raster2)

mapview(dem_raster) + mapview(hru_new) + mapview(locations)

#######
bbox <- st_bbox(locations)

# # Bounding box cuts off some points so expand it
xrange <- bbox$xmax - bbox$xmin # range of x values
yrange <- bbox$ymax - bbox$ymin # range of y values
# Expand the extent
bbox[1] <- bbox[1] - (0.1 * xrange) # xmin - left
bbox[3] <- bbox[3] + (0.1 * xrange) # xmax - right
bbox[2] <- bbox[2] - (0.1 * yrange) # ymin - bottom
bbox[4] <- bbox[4] + (0.1 * yrange) # ymax - top
# 
#######

hru_new <- st_transform(hru_new, crs(dem_raster))

dem_cropped <- crop(dem_raster, extent(bbox))

mapview(dem_cropped) + mapview(hru_new) + mapview(locations)

# Convert the raster to a data frame
dem_df <- as.data.frame(dem_cropped, xy = TRUE)

fire <- st_read('/Users/megansears/Documents/Repos/fourmile/data/GIS/co4005110538520100906_20100621_20110624_burn_bndy.shp')
mapview(fire) + mapview(hru_new)

fire <- st_transform(fire, crs(dem_raster))

## inset data

library(spData)
data("us_states", package = "spData")

# Extract the geometry of Colorado
wus <- us_states[us_states$REGION == "West", ]

point <- locations[locations$source == 'USGS1',]

# Create a ggplot with western US states and the bounding box
ggm1 <- ggplot() + 
  geom_sf(data = wus, fill = "white") + 
  geom_sf(data = point, shape = 8, size = 3, color = "red", fill = "red") +  # Add star point
  theme_void()

ggm1

##

library(ggspatial)

# Define custom shapes for each value of 'display_use'
custom_shapes <- c("Daymet" = 15, "Prism" = 16, "Precip" = 17, "Multi-sensor" = 18, "Streamflow" = 7)  # Replace "Type1", "Type2", etc. with actual values

terrain <- ggplot() +
  geom_raster(data = dem_df, 
              aes(x = x, y = y, fill = layer)) +  
  scale_fill_gradientn(colors = terrain.colors(200),  
    name = "Elevation (m)") +
   geom_sf(data = fire, 
          aes(color = "Fire"), 
          fill = NA, 
          lwd = 0.75) +
  geom_sf(data = hru_new, 
          aes(color = "HRU"), 
          fill = NA, 
          lwd = 0.5) +
  geom_sf(data = locations, 
          aes(shape = factor(display_use)), 
          size = 4) + 
  scale_shape_manual(values = custom_shapes) +
   scale_color_manual(name = NULL,
                      values = c(Fire = "red", HRU = "black"), 
                     labels = c(Fire = "Fourmile Canyon fire", HRU = "HRUs")) + 
  labs(shape = element_blank()) +
  theme_bw(base_size = 25) +
  theme(axis.title.x = element_blank(),
    axis.title.y = element_blank(),
    legend.spacing.y = unit(0.01, "cm"))

terrain

ggsave('./figures/fig1a.png', dpi=600)

ggplot() +
  geom_raster(data = dem_df, aes(x = x, y = y, fill = layer)) +
  scale_fill_viridis_c(name = "Elevation (m)", 
                       option = "viridis",direction=-1) +
  geom_sf(data = fire, 
          aes(color = "Fire"), 
          fill = NA, 
          lwd = 0.75) +
  geom_sf(data = hru_new, 
          aes(color = "HRU"), 
          fill = NA, 
          lwd = 0.5) +
  geom_sf(data = locations, 
          aes(shape = factor(display_use)), 
          size = 4) + 
  scale_shape_manual(values = custom_shapes) +
   scale_color_manual(name = NULL,
                      values = c(Fire = "red", HRU = "black"), 
                     labels = c(Fire = "Fourmile Canyon fire", HRU = "HRUs")) + 
  labs(shape = element_blank()) +
  theme_bw(base_size = 25) +
  theme(axis.title.x = element_blank(),
    axis.title.y = element_blank(),
    legend.spacing.y = unit(0.01, "cm"))

ggsave('./figures/fig1a_2.png', dpi=600)

###
library(cowplot)

ggdraw() +
  draw_plot(terrain) +
  draw_plot(ggm1, x = 0.042, y = 0.63, width = 0.16, height = 0.16)
  #draw_plot(ggm1, x = 0.585, y = 0.56, width = 0.25, height = 0.25)

ggsave('./figures/fig1a.png', dpi=600)

```

# Figure 1b-e

```{r}
grid <- read_csv("/Users/megansears/Documents/Repos/fourmile/38HRU_model/HRU_gridall.csv") %>%
  mutate(date = mdy(time),
         site = 'grid')

statn <- read_csv('/Users/megansears/Documents/Repos/fourmile/38HRU_model/HRU_statnall.csv') %>%
  mutate(date = mdy(time),
         site = 'statn')

all <- bind_rows(grid, statn) %>%
  arrange(date)

catchment_mo_mean <- all %>%
  mutate(month = month(date)) %>%
  group_by(site, month) %>%
  summarise(across(precip:solRad, ~ mean(.x, na.rm = TRUE))) %>%
  dplyr::select(site, month,
                precip_mean = precip, tmean_mean = tmean, 
                solrad_mean = solRad, rh_mean = rhum)

catchment_mo_sd <- all %>%
  mutate(month = month(date)) %>%
  group_by(site, month) %>%
  summarise(across(precip:solRad, ~ sd(.x, na.rm = TRUE))) %>%
  dplyr::select(site, month,
                precip_sd = precip, tmean_sd = tmean, 
                solrad_sd = solRad, rh_sd = rhum)

catchment_mo <- left_join(catchment_mo_mean, catchment_mo_sd, 
                          by = c('month', 'site'))

catchment_mo2 <- catchment_mo %>%
  mutate(month_name = month.abb[month]) %>%
  mutate(month_name = factor(month_name, 
                             levels = c('Jan', 'Feb', 'Mar',
                                        'Apr', 'May', 'Jun',
                                        'Jul', 'Aug', 'Sep',
                                        'Oct', 'Nov', 'Dec')))

p_cols <- ggplot(catchment_mo2, aes(x = month_name, y = precip_mean,
                                    color = site, fill = site)) +
  geom_col(position = 'dodge') +
  geom_errorbar(aes(ymin = 0, ymax = precip_mean + precip_sd), 
                position = position_dodge(width = 0.6), width = 0.2) +
  scale_color_manual(values = c("blue", "orange"),
                     labels = c("Gridded", "Observed")) +  # Rename color legend items
  scale_fill_manual(values = c("blue", "orange"),
                    labels = c("Gridded", "Observed")) +   # Rename fill legend items
  theme_bw(base_size = 12) +
  labs(y = 'Precipitation (mm)',
       x = element_blank()) +
  guides(color = guide_legend(title = NULL),
         fill = guide_legend(title = NULL))

p_cols

ggsave("P.png", plot = p_cols, width = 8, height = 6, dpi = 300)

# Temperature plot
t_moplot <- ggplot(catchment_mo2, aes(x = month_name, y = tmean_mean, 
                                      color = site, group = site)) +
  geom_ribbon(aes(ymin = tmean_mean - tmean_sd, ymax = tmean_mean + tmean_sd, fill = site), alpha = 0.2) +
  geom_line() +
  geom_point() +
  scale_color_manual(values = c("blue", "orange"),
                     labels = c("Gridded", "Observed")) +  # Set line color to blue and orange and rename
  scale_fill_manual(values = c("blue", "orange"),
                    labels = c("Gridded", "Observed")) +   # Set ribbon fill color to blue and orange and rename
  theme_bw(base_size=12) +
  labs(y = expression("Mean temperature " ( degree~C)),
       x = element_blank()) +
  labs(color = NULL, fill = NULL)

# Solar radiation plot
sol_moplot <- ggplot(catchment_mo2, aes(x = month_name, y = solrad_mean, 
                                         color = site, group = site)) +
  geom_ribbon(aes(ymin = solrad_mean - solrad_sd, ymax = solrad_mean + solrad_sd, fill = site), alpha = 0.2) +
  geom_line() +
  geom_point() +
  scale_color_manual(values = c("blue", "orange"),
                     labels = c("Gridded", "Observed")) +  # Set line color to blue and orange and rename
  scale_fill_manual(values = c("blue", "orange"),
                    labels = c("Gridded", "Observed")) +   # Set ribbon fill color to blue and orange and rename
  theme_bw(base_size = 12) +
  labs(y = expression("Solar radiation (MJ/m"^"2" * ")"),
       x = element_blank()) +
  labs(color = NULL, fill = NULL)

# Relative humidity plot
rh_moplot <- ggplot(catchment_mo2, aes(x = month_name, y = rh_mean, 
                                        color = site, group = site)) +
  geom_ribbon(aes(ymin = rh_mean - rh_sd, ymax = rh_mean + rh_sd, fill = site), alpha = 0.2) +
  geom_line() +
  geom_point() +
  scale_color_manual(values = c("blue", "orange"),
                     labels = c("Gridded", "Observed")) +  # Set line color to blue and orange and rename
  scale_fill_manual(values = c("blue", "orange"),
                    labels = c("Gridded", "Observed")) +   # Set ribbon fill color to blue and orange and rename
  theme_bw(base_size = 12) +
  labs(y = 'RH (%)', x= element_blank()) +
  labs(color = NULL, fill = NULL)

# Print the plots
t_moplot
sol_moplot
rh_moplot

# t_moplot <- ggplot(catchment_mo2, aes(x = month_name, y = tmean_mean, 
#                                       color = site, group = site)) +
#   geom_ribbon(aes(ymin = tmean_mean - tmean_sd, ymax = tmean_mean + tmean_sd, fill = site), alpha = 0.2) +
#   geom_line() +
#   geom_point() +
#   theme_bw(base_size=14) +
#   labs(y = expression("Mean temperature " ( degree~C)),
#        x = element_blank())
# 
# t_moplot
# 
# sol_moplot <- ggplot(catchment_mo2, aes(x = month_name, y = solrad_mean, 
#                                       color = site, group = site)) +
#   geom_ribbon(aes(ymin = solrad_mean - solrad_sd, ymax = solrad_mean + solrad_sd, fill = site), alpha = 0.2) +
#   geom_line() +
#   geom_point() +
#   theme_bw(base_size = 14) +
#   labs(y = expression("Solar radiation (MJ/m"^"2" * ")"),
#        x = element_blank()) 
# 
# sol_moplot
# 
# 
# rh_moplot <- ggplot(catchment_mo2, aes(x = month_name, y = rh_mean, 
#                                       color = site, group = site)) +
#   geom_ribbon(aes(ymin = rh_mean - rh_sd, ymax = rh_mean + rh_sd, fill = site), alpha = 0.2) +
#   geom_line() +
#   geom_point() +
#   theme_bw(base_size = 14) +
#   labs(y = 'RH (%)', x= element_blank()) 
# rh_moplot
library(ggpubr)

quad <- ggarrange(p_cols, 
          t_moplot,
          sol_moplot,
          rh_moplot,
          common.legend = T,
          legend = 'bottom',
          ncol=4) 
          #nrow = 4)
          #ncol= 0)
quad

ggsave("./figures/quad.png", plot = quad, dpi = 600)

```

# difference

```{r}

#grid first
setwd("/Users/megansears/Documents/Repos/fourmile/38HRU_model/HRU_output/grid_all")

read_ages_grid <- function(dataframe){
  read_csv(dataframe, skip = 3) %>%
  slice(3:n()) %>%
  dplyr::select(-starts_with('@'),
                -1) %>%
  mutate(time = ymd(time)) %>%
  mutate_if(is.character, as.numeric) %>%
  mutate(source = 'grid')

}

#pull in all filenames with HRU in the name
filenames <- list.files(".", pattern="HRU", full.names=F)

#read all the csvs using read_ages function
dataframes <- lapply(filenames, read_ages_grid)

#name all the csvs based on first 6 characters
names(dataframes) <- substr(filenames, 1, 6)

#bind all and make 1 df
hru_grids <- dataframes %>%
  bind_rows()

#statn next
setwd("/Users/megansears/Documents/Repos/fourmile/38HRU_model/HRU_output/statn_all")

read_ages_statn <- function(dataframe){
  read_csv(dataframe, skip = 3) %>%
  slice(3:n()) %>%
  dplyr::select(-starts_with('@'),
                -1) %>%
  mutate(time = ymd(time)) %>%
  mutate_if(is.character, as.numeric) %>%
  mutate(source = 'statn')

}

#pull in all filenames with HRU in the name
filenames <- list.files(".", pattern="HRU", full.names=F)

#read all the csvs using read_ages function
dataframes <- lapply(filenames, read_ages_statn)

#name all the csvs based on first 6 characters
names(dataframes) <- substr(filenames, 1, 6)

#bind all and make 1 df
hru_statn <- dataframes %>%
  bind_rows()

#get rid of a bunch of data
hru_grid_tmean <- hru_grids %>%
  dplyr::select(c(time, ID, tmean)) %>%
  rename(tmean_grid = tmean)  %>%
  group_by(ID) %>%
  summarize(tmean_all_grid = mean(tmean_grid))

hru_statn_tmean <- hru_statn %>%
  dplyr::select(c(time, ID, tmean)) %>%
  rename(tmean_statn = tmean) %>%
  group_by(ID) %>%
  summarize(tmean_all_statn = mean(tmean_statn))

tmean_hrus <- left_join(hru_grid_tmean, hru_statn_tmean, by = c('ID')) %>%
  mutate(diff = tmean_all_statn - tmean_all_grid) %>%
  rename(value = ID)

hrus_map_tmean <- left_join(hru_new, tmean_hrus, by = 'value')

# T max
#get rid of a bunch of data
hru_grid_tmax <- hru_grids %>%
  dplyr::select(c(time, ID, tmax)) %>%
  rename(tmax_grid = tmax)  %>%
  group_by(ID) %>%
  summarize(tmax_all_grid = mean(tmax_grid))

hru_statn_tmax <- hru_statn %>%
  dplyr::select(c(time, ID, tmax)) %>%
  rename(tmax_statn = tmax) %>%
  group_by(ID) %>%
  summarize(tmax_all_statn = mean(tmax_statn))

tmax_hrus <- left_join(hru_grid_tmax, hru_statn_tmax, by = c('ID')) %>%
  mutate(diff = tmax_all_statn - tmax_all_grid) %>%
  rename(value = ID)

hrus_map_tmax <- left_join(hru_new, tmax_hrus, by = 'value')

# Tmin
#get rid of a bunch of data
hru_grid_tmin <- hru_grids %>%
  dplyr::select(c(time, ID, tmin)) %>%
  rename(tmin_grid = tmin)  %>%
  group_by(ID) %>%
  summarize(tmin_all_grid = mean(tmin_grid))

hru_statn_tmin <- hru_statn %>%
  dplyr::select(c(time, ID, tmin)) %>%
  rename(tmin_statn = tmin) %>%
  group_by(ID) %>%
  summarize(tmin_all_statn = mean(tmin_statn))

tmin_hrus <- left_join(hru_grid_tmin, hru_statn_tmin, by = c('ID')) %>%
  mutate(diff = tmin_all_statn - tmin_all_grid) %>%
  rename(value = ID)

hrus_map_tmin <- left_join(hru_new, tmin_hrus, by = 'value')

# Cumulative p
hru_grid_precip <- hru_grids %>%
  dplyr::select(c(time, ID, precip)) %>%
  rename(precip_grid = precip)

hru_statn_precip <- hru_statn %>%
  dplyr::select(c(time, ID, precip)) %>%
  rename(precip_statn = precip)

precip_hrus <- left_join(hru_grid_precip, hru_statn_precip, by = c('time', 'ID')) %>%
  mutate(diff = precip_statn - precip_grid,
         year = year(time)) %>%
  group_by(year, ID) %>%
  mutate(total_diff = cumsum(diff)) %>%
  filter(time == max(time)) %>%
  group_by(ID) %>%
  summarize(precip_avg_cumdiff = mean(total_diff)) %>%
  rename(value = ID)

hrus_map_precip <- left_join(hru_new, precip_hrus, by = 'value')

# solar rad
hru_grid_solrad <- hru_grids %>%
  dplyr::select(c(time, ID, solRad)) %>%
  rename(solrad_grid = solRad)  %>%
  group_by(ID) %>%
  summarize(solrad_all_grid = mean(solrad_grid))

hru_statn_solrad <- hru_statn %>%
  dplyr::select(c(time, ID, solRad)) %>%
  rename(solrad_statn = solRad) %>%
  group_by(ID) %>%
  summarize(solrad_all_statn = mean(solrad_statn))

solrad_hrus <- left_join(hru_grid_solrad, hru_statn_solrad, by = c('ID')) %>%
  mutate(diff = solrad_all_statn - solrad_all_grid) %>%
  rename(value = ID)

hrus_map_solrad <- left_join(hru_new, solrad_hrus, by = 'value')

# RH
#get rid of a bunch of data
hru_grid_rh <- hru_grids %>%
  dplyr::select(c(time, ID, rhum)) %>%
  rename(rh_grid = rhum)  %>%
  group_by(ID) %>%
  summarize(rh_all_grid = mean(rh_grid))

hru_statn_rh <- hru_statn %>%
  dplyr::select(c(time, ID, rhum)) %>%
  rename(rh_statn = rhum) %>%
  group_by(ID) %>%
  summarize(rh_all_statn = mean(rh_statn))

rh_hrus <- left_join(hru_grid_rh, hru_statn_rh, by = c('ID')) %>%
  mutate(diff = rh_all_statn - rh_all_grid) %>%
  rename(value = ID)

hrus_map_rh <- left_join(hru_new, rh_hrus, by = 'value')

rh <- ggplot() +
  geom_sf(data = hrus_map_rh, aes(fill = diff), color = "black", lwd = 0.2) +
  scale_fill_viridis_c(option = "viridis", name = "RH difference (%)") +
  theme_bw(base_size=13.5) +
  theme(
    legend.position = "bottom",
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    axis.title.x = element_blank(),
    axis.title.y = element_blank())

rh

sr <- ggplot() +
  geom_sf(data = hrus_map_solrad, aes(fill = diff), color = "black", lwd = 0.2) +
  scale_fill_viridis_c(option = "cividis", name = expression("Solar rad difference (MJ/m"^"2" * ")")) +
  theme_bw(base_size=13.5) +
  theme(
    legend.position = "bottom",
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    axis.title.x = element_blank(),
    axis.title.y = element_blank()) +
  guides(
    fill = guide_colorbar(
      label.theme = element_text(size = 10)))

sr

precip <- ggplot() +
  geom_sf(data = hrus_map_precip, aes(fill = precip_avg_cumdiff), color = "black", lwd = 0.2) +
  scale_fill_viridis_c(option = "mako", name = "Cumulative P Difference (mm)") +
  theme_bw(base_size=13.5) +
  theme(
    legend.position = "bottom",
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    axis.title.x = element_blank(),
    axis.title.y = element_blank())

precip

tmean <- ggplot() +
  geom_sf(data = hrus_map_tmean, aes(fill = diff), color = "black", lwd = 0.2) +
  scale_fill_viridis_c(option = "plasma", name = "Tmean difference (°C)") +
  theme_bw(base_size=13.5) +
  theme(
    legend.position = "bottom",
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    axis.title.x = element_blank(),
    axis.title.y = element_blank())

tmin <- ggplot() +
  geom_sf(data = hrus_map_tmin, aes(fill = diff), color = "black", lwd = 0.2) +
  scale_fill_viridis_c(option = "mako", name = "Tmin difference (°C)") +
  theme_bw(base_size=13.5) +
  theme(
    legend.position = "bottom",
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    axis.title.x = element_blank(),
    axis.title.y = element_blank())

tmax <- ggplot() +
  geom_sf(data = hrus_map_tmax, aes(fill = diff), color = "black", lwd = 0.2) +
  scale_fill_viridis_c(option = "inferno", name = "Tmax difference (°C)") +
  theme_bw(base_size=13.5) +
  theme(
    legend.position = "bottom",
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    axis.title.x = element_blank(),
    axis.title.y = element_blank())

lots <- ggarrange(precip,
                  sr,
                  rh,
                  tmean,
                  tmax,
                  tmin) 
          #nrow = 4)
          #ncol= 0)
lots

ggsave("./figures/diff.png", plot = lots, dpi = 600)

```

### 2024-06-17 38HRU_model/fourmile_model_outputs.Rmd
update

@@
   gw_gridall, gw_statnall,
-  gw_grid2011, gw_grid2012,
-  gw_grid2013, gw_grid2014,
-  gw_grid2015, gw_grid2016,
-  gw_grid2017, gw_grid2018,
-  gw_grid2019, gw_grid2020,
-  gw_statn2011, gw_statn2012,
-  gw_statn2013, gw_statn2014,
-  gw_statn2015, gw_statn2016,
-  gw_statn2017, gw_statn2018,
-  gw_statn2019, gw_statn2020
+  # gw_grid2011, gw_grid2012,
+  # gw_grid2013, gw_grid2014,
+  # gw_grid2015, gw_grid2016,
+  # gw_grid2017, gw_grid2018,
+  # gw_grid2019, gw_grid2020,
+  # gw_statn2011, gw_statn2012,
+  # gw_statn2013, gw_statn2014,
+  # gw_statn2015, gw_statn2016,
+  # gw_statn2017, gw_statn2018,
+  # gw_statn2019, gw_statn2020
 ) %>%

### 2024-06-25 spatial_figs.Rmd
updated manuscript figs

@@
 
-hru_new <- st_read('/Users/megansears/Documents/Repos/fourmile/data/GIS/hrus_final.shp')
+hru_new <- st_read('/Users/megansears/Documents/Repos/fourmile/data/GIS/hrus_final.shp') %>%
 
@@
 
-# Figure 1b-e
+# Figure 1b-e -- NEED TO REDO WITH WHOLE CATCHMENT DATA
 
 ```{r}
-grid <- read_csv("/Users/megansears/Documents/Repos/fourmile/38HRU_model/HRU_gridall.csv") %>%
-  mutate(date = mdy(time),
-         site = 'grid')
+grid <- read_csv("/Users/megansears/Documents/Repos/fourmile/38HRU_model/output/4milecreek38HRUs-gridall_#1/out/Catchment.csv",
+                 skip=3) %>%
+   slice(3:n()) %>%
+  dplyr::select(-starts_with('@'),
+                -1) %>%
+  mutate(date = ymd(time)) %>%
+  dplyr::select(-time) %>%
+  mutate_if(is.character, as.numeric) %>% 
+  mutate(site = 'grid')
 
-statn <- read_csv('/Users/megansears/Documents/Repos/fourmile/38HRU_model/HRU_statnall.csv') %>%
-  mutate(date = mdy(time),
-         site = 'statn')
+statn <- read_csv('/Users/megansears/Documents/Repos/fourmile/38HRU_model/output/4milecreek38HRUs-statnall_#1/out/Catchment.csv',
+                 skip=3) %>%
+   slice(3:n()) %>%
+  dplyr::select(-starts_with('@'),
+                -1) %>%
+  mutate(date = ymd(time)) %>%
+  dplyr::select(-time) %>%
+  mutate_if(is.character, as.numeric) %>% 
+  mutate(site = 'statn')
 
@@
 
+setwd("~/Documents/Repos/fourmile")
+
 # Cumulative p
@@
   theme_bw(base_size=13.5) +
+  theme_void() +
   theme(
@@
   geom_sf(data = hrus_map_tmean, aes(fill = diff), color = "black", lwd = 0.2) +
-  scale_fill_viridis_c(option = "plasma", name = "Tmean difference (°C)") +
+  scale_fill_viridis_c(option = "plasma", name = "Tmean difference (°C)",
+                       limits = c(-5, 2)) +
   theme_bw(base_size=13.5) +
+  theme_void() +
   theme(
@@
 
+tmean
+
 tmin <- ggplot() +
   geom_sf(data = hrus_map_tmin, aes(fill = diff), color = "black", lwd = 0.2) +
-  scale_fill_viridis_c(option = "mako", name = "Tmin difference (°C)") +
+  scale_fill_viridis_c(option = "plasma", name = "Tmin difference (°C)",
+                       limits = c(-5, 2)) +
   theme_bw(base_size=13.5) +
+  theme_void() +
   theme(
@@
 
+tmin
+
 tmax <- ggplot() +
   geom_sf(data = hrus_map_tmax, aes(fill = diff), color = "black", lwd = 0.2) +
-  scale_fill_viridis_c(option = "inferno", name = "Tmax difference (°C)") +
+  scale_fill_viridis_c(option = "plasma", name = "Tmax difference (°C)",
+                       limits = c(-5, 2)) +
   theme_bw(base_size=13.5) +
+  theme_void() +
   theme(
@@
     axis.title.y = element_blank())
+
+tmin
 
@@
 ```
+
+# Pgrid vs Pstatn
+
+```{r}
+
+statn_catch <- read_csv('/Users/megansears/Documents/Repos/fourmile/38HRU_model/output/4milecreek38HRUs-statnall_#1/out/Catchment.csv',
+                        skip=3) %>%
+  slice(3:n()) %>%
+  dplyr::select(-starts_with('@'),
+                -1) %>%
+  mutate(time = ymd(time)) %>%
+  mutate_if(is.character, as.numeric) %>%
+  mutate(source = 'statn')
+
+grid_catch <- read_csv('/Users/megansears/Documents/Repos/fourmile/38HRU_model/output/4milecreek38HRUs-gridall_#1/out/Catchment.csv',
+                       skip=3) %>%
+  slice(3:n()) %>%
+  dplyr::select(-starts_with('@'),
+                -1) %>%
+  mutate(time = ymd(time)) %>%
+  mutate_if(is.character, as.numeric) %>%
+  mutate(source = 'grid')
+
+catchment_p <- bind_rows(statn_catch, grid_catch) %>%
+  dplyr::select(precip, time, source) %>%
+  pivot_wider(., names_from=source, values_from=precip)
+
+p_comp <- ggplot(catchment_p, aes(x=statn, y=grid)) + geom_point(size = 3) +
+  theme_bw(base_size=25) +
+  labs(x = 'Station precip (mm)',
+       y = 'Grid precip (mm)') +
+  geom_abline(slope = 1, intercept = 0, linetype = "dashed", color = "red")
+
+p_comp
+ggsave("./figures/p_compare.png", plot = p_comp, dpi = 600)
+
+```

### 2024-06-25 38HRU_model/fourmile_model_outputs.Rmd
params weighted code added

--- 2024-06-14 38HRU_model/fourmile_model_outputs.Rmd
@@
   facet_wrap(~param, scales = 'free_y')
+
+# add area weights to params combo
+params_weighted <- params_combo %>%
+  mutate(area = if_else(burn == 'no', 48243400,
+                        18823000)) %>%
+  group_by(param, cal) %>%
+  summarize(numerator = sum(value * area),
+    denominator = sum(area)) %>%
+  mutate(area_weighted_average = numerator / denominator) %>%
+  dplyr::select(-c(numerator, denominator))
+
+write_csv(params_weighted, './params_weighted.csv')
 
@@
 
+#
+params_weighted1 <- params_weighted %>%
+  rename(input_data = cal) %>%
+  pivot_wider(names_from = 'param',
+              values_from = 'area_weighted_average') %>%
+  rename_with(~ paste0(., '_weighted'), 2:7)
+
 join <- left_join(join, params1, by = c('input_data')) %>%
@@
 
+join <- left_join(join, params_weighted1, by = 'input_data')
+
 write_csv(join, 'flow_params.csv')

### 2024-06-28 sept2013_edits.Rmd
2013 flood edits

---
title: "2013 flood edits"
author: "Megan Sears"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: yes
    toc_float: yes
    theme: journal
editor_options:
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = F,
  message = F, 
  warning  = F)

library(tidyverse)
library(plotly)
library(lubridate)
library(knitr)
library(kableExtra)
library(hydroGOF)
library(here)

```

```{r, include = F}

setwd('/Users/megansears/Documents/Repos/fourmile/38HRU_model/sept2013_edits')

kge_edits2013 <- read_csv('cal_KGE.csv')

```

- grid_all25 = grid_all (no years missing) but has 25 cms on 9/12/13<br>
- grid_allNA = grid_all (no years missing) but has NA on 9/12/13<br>
- grid_all = grid_all (no years missing) - original grid all<br>
- statn_all25 = statn_all (no years missing) but has 25 cms on 9/12/13<br>
- statn_allNA = statn_all (no years missing) but has NA on 9/12/13<br>
- statn_all = statn_all (no years missing) - original statn all<br>

# Parameters

## KGE for calibrations

```{r look at kge, echo = F}

kge_plot <- ggplot(kge_edits2013, aes(cal_run, KGE, shape = flood_edits, color = flood_edits)) + geom_point(size = 3) +
  theme_bw()

ggplotly(kge_plot)

```

## Unburned params

```{r, echo = F, message = F, warning = F, include = F}

setwd('/Users/megansears/Documents/Repos/fourmile/38HRU_model/sept2013_edits/params')

#pull in all filenames with composite
filenames <- list.files('.', pattern=".csv", full.names=F)

#read all the csvs
dataframes <- lapply(filenames, read_csv)

#name all the csv
names(dataframes) <- substr(filenames, 1, 12)

#extract csvs from list to global env
lapply(names(dataframes), function(x) assign(x, dataframes[[x]], envir = .GlobalEnv))
rm(dataframes) #remove dataframes list

```

```{r params, echo = FALSE, message = FALSE, warning = FALSE}

# function to read files, remove top rows, paste site name
read_cals <- function(df, name){
    df <- df %>%
      slice(-c(1:9, 146:277)) %>%
      separate(Parameter, c("Parameter", "value"), sep = ",") %>%
      drop_na() %>%
      dplyr::select(-1) %>% 
      mutate(cal = name)

}

grid_all <- read_cals(grid_all_cal, name = 'grid_all')
grid_all25 <- read_cals(grid_all25_c, name = 'grid_all25')
grid_allNA <- read_cals(gril_allNA_c, name = 'grid_allNA')

grid <- bind_rows(grid_all25, grid_allNA,
                  grid_all) %>%
  mutate(input_data = 'grid') %>%
  rename(param = Parameter) %>%
  filter(!param == 'locGrw',
         !param == 'tempRes')

statn_all <- read_cals(statn_all_ca, name = 'statn_all')
statn_all25 <- read_cals(statn_all25_, name = 'statn_all25')
statn_allNA <- read_cals(statn_allNA_, name = 'statn_allNA')

statn <- bind_rows(statn_all25, statn_allNA,
                  statn_all) %>%
  mutate(input_data = 'statn') %>%
  rename(param = Parameter) %>%
  filter(!param == 'locGrw',
         !param == 'tempRes')

params <- bind_rows(statn, grid)

params <- params %>%
  filter(!param %in% c('angstrom_a', 'angstrom_b', 
                      'Beta_min', 
                      'Beta_rsd', "Beta_trans", 'clat', 
                      'delayNitrification',
                      'denitrificationRateCoefficient', 
                      'denitrificationSoilSaturationThreshold',
                      'deposition_factor', 'drrad', 
                      'drspac', 'initLPS', 'initRG1',
                      'initRG2', 'Ksink', 'LExCoef', 
                      'longTZ', 'N_concRG1', 'N_concRG2', 'N_delay_RG1',
                      'N_delay_RG2', 
                      'nitrificationSoilTemperatureThreshold', 
                      'nitrificationSurfaceTemperatureThreshold',
                      'opti', 'piadin', 'rootfactor', 'sceno', 
                      'soilImpGT80', 'soilImpLT80',
                      'soilLinRed', 'soilMaxPerc', 'temp_lag')) %>%
    mutate(value = as.numeric(value),
         param = as.factor(param))

#function to plot all params
plot_params <- function(param_name) {
  params %>%
    filter(param == param_name) %>%
    ggplot(aes(x = cal,
               y = value,
               color = cal)) + 
    geom_point(size = 3) + 
    ggtitle(param_name) +
    theme_bw()
}

name <- levels(params$param)

lapply(name, plot_params)

```

## Burn params

```{r echo = FALSE, message = FALSE, warning = FALSE, include = F}

rm(list = ls())

setwd("/Users/megansears/Documents/Repos/fourmile/38HRU_model/sept2013_edits/params")

#pull in all filenames with composite
filenames <- list.files('.', pattern=".csv", full.names=F)

#read all the csvs
dataframes <- lapply(filenames, read_csv)

#name all the csv
names(dataframes) <- substr(filenames, 1, 10)

#extract csvs from list to global env
lapply(names(dataframes), function(x) assign(x, dataframes[[x]], envir = .GlobalEnv))
rm(dataframes) #remove dataframes list

```

```{r, echo = F}

# read in all the grid burn params
read_cals_burn <- function(df, name){
    df <- df %>%
      slice(-c(1:274)) %>%
      separate_wider_delim(Parameter, 
                       delim = ',',
                       names = c('soilID',
                                 'luca_a_rain',
                                 'luca_a_snow',
                                 'luca_soilMaxInfSummer',
                                 'luca_soilMaxDPS',
                                 'luca_lagSurfaceRunoff',
                                 'luca_soilDistMPSLPS')) %>%
      slice(-1) %>%
      dplyr::select(-1) %>% 
      mutate(cal = name)
}

grid_all_burn <- read_cals_burn(grid_all_c, name = 'grid_all')
grid_all25_burn <- read_cals_burn(grid_all25, name = 'grid_all25')
grid_allNA_burn <- read_cals_burn(gril_allNA, name = 'grid_allNA')

grid_burn <- bind_rows(grid_all25_burn, grid_allNA_burn,
                  grid_all_burn) %>%
  mutate(input_data = 'grid')

# now do statn burn params
statn_all_burn <- read_cals_burn(statn_all_, name = 'statn_all')
statn_all25_burn <- read_cals_burn(statn_all2, name = 'statn_all25')
statn_allNA_burn <- read_cals_burn(statn_allN, name = 'statn_allNA')

statn_burn <- bind_rows(statn_all25_burn, statn_allNA_burn,
                  statn_all_burn) %>%
  mutate(input_data = 'statn')

burn_params <- bind_rows(grid_burn, statn_burn) %>%
  ungroup() %>%
  mutate(across(c(luca_a_rain:luca_soilDistMPSLPS), as.numeric)) %>%
  group_by(cal) %>%
  mutate(across(c(luca_a_rain:luca_soilDistMPSLPS), mean)) %>%
  filter(soilID == 22) %>%
  dplyr::select(-soilID) %>% 
  pivot_longer(!c(cal, input_data), 
               names_to = 'params',
               values_to = 'value') %>% 
  mutate(params = str_remove(params, 'luca_')) %>%
  mutate(params = as.factor(params),
         burn = 'yes')

```

```{r, echo = F}

plot_burnparams <- function(param_name) {
  burn_params %>%
    filter(params == param_name) %>%
    ggplot(aes(y = value,
               x = cal,
               color = cal)) +
    geom_point(size = 3) +
    ggtitle(param_name) +
    theme_bw()
}

name2 <- levels(burn_params$params)

lapply(name2, plot_burnparams)

```

# Outlet

## Hydrographs

```{r, echo = F}

setwd('/Users/megansears/Documents/Repos/fourmile/38HRU_model/sept2013_edits')

flow <- read_csv('streamflow.csv') %>%
  replace(.==-9999, NA) %>%
  rename(date = time) %>%
  mutate(date = mdy(date))

flow_pivot <- flow %>%
  pivot_longer(!date, names_to = 'cal_run', values_to = 'q_m3s') %>%
  mutate(year = as.factor(year(date)))

q <- ggplot(flow_pivot, aes(date, q_m3s, color = cal_run)) +
  geom_line() +
  scale_color_manual(name="cal_run", values=c('obs' = 'black',
                                            "grid_allNA"="seagreen",
                                            'grid_all25' = 'blue',
                                            'grid_all' = 'steelblue3',
                                            "statn_all25"="maroon",
                                            "statn_allNA"='purple',
                                            'statn_all' = 'red'))

ggplotly(q)

```

## Q KGE

```{r, echo = F}

flow_kge_all <- flow %>%
  drop_na() %>%
  summarize(grid_allNA = KGE(grid_allNA, obs),
            grid_all25 = KGE(grid_all25, obs),
            gridall = KGE(grid_all, obs),
            statn_all25 = KGE(statn_all25, obs),
            statn_allNA = KGE(statn_allNA, obs),
            statnall = KGE(statn_all, obs)) %>%
    mutate_if(is.numeric,
            round,
            digits = 2)

flow_kge_all <- flow_kge_all %>%
  pivot_longer(everything()) %>%
  arrange(value)

kable(flow_kge_all) %>%
  kable_styling(full_width = F)

```

## Q percent bias

```{r, echo = F}

flow_pbias_all <- flow %>%
  drop_na() %>%
  summarize(grid_allNA = pbias(grid_allNA, obs),
            grid_all25 = pbias(grid_all25, obs),
            gridall = pbias(grid_all, obs),
            statn_all25 = pbias(statn_all25, obs),
            statn_allNA = pbias(statn_allNA, obs),
            statnall = pbias(statn_all, obs)) %>%
    mutate_if(is.numeric,
            round,
            digits = 2)

flow_pbias_all <- flow_pbias_all %>%
  pivot_longer(everything()) %>%
  arrange(value)

kable(flow_pbias_all) %>%
  kable_styling(full_width = F)

```

### 2024-06-28 sept2013_edits.Rmd
kge and pbias by year

@@
 library(here)
+library(viridis)
 
@@
 
+## Q KGE by year
+
+```{r, echo = F}
+
+flow_year <- flow %>%
+  drop_na() %>%
+  mutate(year = year(date)) %>%
+  group_by(year) %>%
+  summarize(grid_allNA = KGE(grid_allNA, obs),
+            grid_all25 = KGE(grid_all25, obs),
+            gridall = KGE(grid_all, obs),
+            statn_all25 = KGE(statn_all25, obs),
+            statn_allNA = KGE(statn_allNA, obs),
+            statnall = KGE(statn_all, obs)) %>%
+    mutate_if(is.numeric,
+            round,
+            digits = 2)
+
+flow_kge <- flow_year %>%
+  pivot_longer(!year, names_to = 'model_run', values_to = 'kge') %>%
+  pivot_wider(names_from = 'year', values_from = 'kge')
+
+flow_kge %>%
+  kable(.) %>%
+  kable_styling()
+
+data_long <- pivot_longer(flow_kge, cols = -model_run, names_to = "year", values_to = "kge")
+
+ggplot(data_long, aes(x = model_run, y = year, fill = kge)) +
+  geom_tile(color = "white") +
+  scale_fill_viridis_c(option = "viridis", name = "KGE", direction = -1) +
+  geom_text(aes(label = round(kge, 2)), color = "grey", size = 4) +
+  theme_bw() +
+  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
+  labs(y = "Year")
+
+```
+
 ## Q percent bias
@@
 ```
+
+## Pbias by year
+
+```{r, echo = F}
+
+flow_year <- flow %>%
+  drop_na() %>%
+  mutate(year = year(date)) %>%
+  group_by(year) %>%
+  summarize(grid_allNA = pbias(grid_allNA, obs),
+            grid_all25 = pbias(grid_all25, obs),
+            gridall = pbias(grid_all, obs),
+            statn_all25 = pbias(statn_all25, obs),
+            statn_allNA = pbias(statn_allNA, obs),
+            statnall = pbias(statn_all, obs)) %>%
+    mutate_if(is.numeric,
+            round,
+            digits = 2)
+
+flow_pbias <- flow_year %>%
+  pivot_longer(!year, names_to = 'model_run', values_to = 'pbias') %>%
+  pivot_wider(names_from = 'year', values_from = 'pbias')
+
+flow_pbias %>%
+  kable(.) %>%
+  kable_styling()
+
+data_long <- pivot_longer(flow_pbias, cols = -model_run, names_to = "year", values_to = "Pbias")
+
+ggplot(data_long, aes(x = model_run, y = year, fill = Pbias)) +
+  geom_tile(color = "white") +
+ scale_fill_gradient2(low = "blue", mid = "white", high = "red", midpoint = 0, name = "Pbias") +
+  geom_text(aes(label = round(Pbias, 2)), color = "black", size = 4) +
+  theme_bw() +
+  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
+  labs(y = "Year")
+
+```

### 2024-07-16 fourmile_outputs_2013edits.Rmd
updated all 38HRU models for sept2013 (na)

--- 2024-06-14 38HRU_model/fourmile_model_outputs.Rmd
@@
 
-setwd('/Users/megansears/Documents/Repos/fourmile/38HRU_model')
-
-kge <- read_csv('calruns_KGE.csv')
-
-```
-
-# KGE for calibrations
+setwd('/Users/megansears/Documents/Repos/fourmile/38HRU_sept2013_updates')
+
+#kge <- read_csv('calruns_KGE.csv') # skip for now - come back if needed
+
+```
 
@@
 
-kge_plot <- ggplot(kge, aes(year_missing, KGE, shape = input_data, color = input_data)) + geom_point(size = 3) +
-  theme_bw()
-
-ggplotly(kge_plot)
+# kge_plot <- ggplot(kge, aes(year_missing, KGE, shape = input_data, color = input_data)) + geom_point(size = 3) +
+#   theme_bw()
+# 
+# ggplotly(kge_plot)
 
@@
 ```{r read in params, echo = FALSE, message = FALSE, warning = FALSE, include = F}
-setwd("/Users/megansears/Documents/Repos/fourmile/38HRU_model/cals")
+
+setwd("/Users/megansears/Documents/Repos/fourmile/38HRU_sept2013_updates/cals")
 
@@
 
-```{r density plots, echo = F, message = F}
+```{r density plots, echo = FALSE, message = FALSE, warning = FALSE}
 
@@
 
-setwd("/Users/megansears/Documents/Repos/fourmile/38HRU_model/cals")
+setwd("/Users/megansears/Documents/Repos/fourmile/38HRU_sept2013_updates/cals")
 
@@
 
-```{r}
+```{r echo = FALSE, message = FALSE, warning = FALSE}
 
@@
 
-```{r}
+```{r echo = FALSE, message = FALSE, warning = FALSE}
 params2 <- params %>%
@@
 
+## Parameters area weighted
+
+```{r echo = FALSE, message = FALSE, warning = FALSE}
+
+# add area weights to params combo
+params_weighted <- params_combo %>%
+  mutate(area = if_else(burn == 'no', 48243400,
+                        18823000)) %>%
+  group_by(param, cal) %>%
+  summarize(numerator = sum(value * area),
+    denominator = sum(area)) %>%
+  mutate(area_weighted_average = numerator / denominator) %>%
+  dplyr::select(-c(numerator, denominator)) %>%
+  separate(col = cal, into = c("source", "year_missing"), sep = "_")
+
+write_csv(params_weighted, '/Users/megansears/Documents/Repos/fourmile/38HRU_sept2013_updates/params_weighted_sept2013_edits.csv')
+
+#function to plot all params
+plot_params <- function(param_name) {
+  params_weighted %>%
+    filter(param == param_name) %>%
+    ggplot(aes(x = year_missing,
+               y = area_weighted_average,
+               color = source)) + 
+    geom_point(size = 3) + 
+    ggtitle(param_name) +
+    theme_bw()
+}
+
+#name <- levels(params_combo$param)
+
+lapply(name2, plot_params)
+
+```
+
 # Outlet results
@@
 
-```{r hydrographs, echo = F}
-setwd('/Users/megansears/Documents/Repos/fourmile/38HRU_model')
+```{r hydrographs, echo = FALSE, message = FALSE, warning = FALSE}
+setwd('/Users/megansears/Documents/Repos/fourmile/38HRU_sept2013_updates')
 
@@
 
+## Cumulative Q
+
+```{r cumq, echo = FALSE, message = FALSE, warning = FALSE}
+
+flow_cumq <- flow_pivot %>%
+  mutate(month = month(date)) %>%
+  filter(month %in% c(4:9)) %>%
+  dplyr::select(-month) %>%
+  #pivot_longer(!date, names_to = 'cal_run', values_to = 'q_m3s') %>%
+  group_by(cal_run, year(date)) %>%
+  mutate(cumsum = cumsum(replace_na(q_m3s, 0))) %>%
+  #rename(year = 4) %>%
+  mutate(year = as.factor(year)) %>%
+  ungroup()
+
+#plot annual cumulative Q vals for ensembles
+plot_cumulq_yr_ <- function(calyear) {
+  {flow_cumq %>%
+    filter(year == calyear) %>%
+    ggplot(aes(x = date,
+               y = cumsum,
+               color = cal_run)) +
+    geom_line() +
+scale_color_manual(name="cal_run", values=c('obs' = 'black',
+                                            "grid_2011"="seagreen",
+                                            "grid_2012"="seagreen2",
+                                            "grid_2013"="steelblue",
+                                            "grid_2014"='dodgerblue',
+                                            "grid_2015" = "cyan3",
+                                            'grid_2016' = 'blue',
+                                            'grid_2017' = 'blue4',
+                                            'grid_2018' = 'cadetblue',
+                                            'grid_2019' = 'lightgreen',
+                                            'grid_2020' = 'olivedrab',
+                                            'grid_all' = 'steelblue3',
+                                            "statn_2011"="maroon",
+                                            "statn_2012"="deeppink4",
+                                            "statn_2013"="deeppink",
+                                            "statn_2014"='purple',
+                                            "statn_2015" = "mediumorchid1",
+                                            'statn_2016' = 'indianred',
+                                            'statn_2017' = 'sienna',
+                                            'statn_2018' = 'salmon2',
+                                            'statn_2019' = 'mediumpurple1',
+                                            'statn_2020' = 'violetred',
+                                            'statn_all' = 'red')) +
+    ggtitle(calyear) +
+    theme_bw() +
+    labs(y = 'cumulative Q (m3s)')} %>%
+    ggplotly()
+}
+
+name <- levels(flow_cumq$year)
+
+cumulative_plots <- lapply(name, plot_cumulq_yr_)
+
+htmltools::tagList(cumulative_plots)
+
+cumulative_plots
+
+```
+
 ## KGE
@@
 
-```{r kge overall, echo = F}
+```{r kge overall, echo = FALSE, message = FALSE, warning = FALSE}
 
@@
 
-```{r kge by year, echo = F}
+```{r kge by year, echo = FALSE, message = FALSE, warning = FALSE}
 
@@
 
-kge_plot_cy <- ggplot(flow_plot, aes(year, kge, color = model_run)) +
-  geom_point(size = 3) +
-  scale_color_manual(name="model_run", values=c("grid2011"="seagreen",
-                                            "grid2012"="seagreen2",
-                                            "grid2013"="steelblue",
-                                            "grid2014"='dodgerblue',
-                                            "grid2015" = "cyan3",
-                                            'grid2016' = 'blue',
-                                            'grid2017' = 'blue4',
-                                            'grid2018' = 'cadetblue',
-                                            'grid2019' = 'lightgreen',
-                                            'grid2020' = 'olivedrab',
-                                            'gridall' = 'steelblue3',
-                                            "statn2011"="maroon",
-                                            "statn2012"="deeppink4",
-                                            "statn2013"="deeppink",
-                                            "statn2014"='purple',
-                                            "statn2015" = "mediumorchid1",
-                                            'statn2016' = 'indianred',
-                                            'statn2017' = 'sienna',
-                                            'statn2018' = 'salmon2',
-                                            'statn2019' = 'mediumpurple1',
-                                            'statn2020' = 'violetred',
-                                            'statnall' = 'red')) +
-  theme_bw()
-
-ggplotly(kge_plot_cy)
+ggplot(flow_plot, aes(x = model_run, y = year, fill = kge)) +
+  geom_tile(color = "white") +
+  scale_fill_viridis_c(option = "viridis", name = "KGE", direction = -1) +
+  geom_text(aes(label = round(kge, 2)), color = "grey", size = 2.5) +
+  theme_bw() +
+  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
+  labs(y = "Year")
 
@@
 
-```{r wy plots, echo = F}
+```{r wy plots, echo = FALSE, message = FALSE, warning = FALSE}
 
@@
                y = kge)) +
-    geom_col() +
+    geom_point(size=3) +
     ggtitle(calyear) +
@@
 
-# Ensembles
-
-## Hydrograph
-
-```{r ensemble hydrographs, echo = F}
-
-ensem <- flow %>%
-  rowwise() %>%
-  mutate(grid_ensemble = mean(c(grid_2011, grid_2012,
-                                grid_2013, grid_2014,
-                                grid_2015, grid_2016,
-                                grid_2017, grid_2018,
-                                grid_2019, grid_2020)),
-         statn_ensemble = mean(c(statn_2011, statn_2012,
-                                 statn_2013, statn_2014,
-                                 statn_2015, statn_2016,
-                                 statn_2017, statn_2018,
-                                 statn_2019, statn_2020)),
-         all_ensemble = mean(c(grid_2011, grid_2012,
-                               grid_2013, grid_2014,
-                               grid_2015, grid_2016,
-                               grid_2017, grid_2018,
-                               grid_2019, grid_2020,
-                               statn_2011, statn_2012,
-                               statn_2013, statn_2014,
-                               statn_2015, statn_2016,
-                               statn_2017, statn_2018,
-                               statn_2019, statn_2020,
-                               grid_all, statn_all))) %>%
-  dplyr::select(date, grid_ensemble, statn_ensemble,
-         all_ensemble, grid_all,
-         statn_all, obs)
-
-ensem_pivot <- ensem %>%
-  pivot_longer(!date, names_to = 'cal_run', values_to = 'q_m3s') %>%
-  mutate(year = as.factor(year(date)))
-
-q_ensemble <- ggplot(ensem_pivot, aes(date, q_m3s, color = cal_run)) +
-  geom_line() +
-  scale_color_manual(name="cal_run", values=c('obs'='black',
-                                            "grid_ensemble"="maroon",
-                                            "statn_ensemble"="darkturquoise",
-                                            "grid_all"="purple1",
-                                            "statn_all"='springgreen4',
-                                            "all_ensemble" = "orange")) +
-  scale_y_continuous(name = 'Q_m3s') +
-  theme_bw()
-
-q_ensemble
-
-```
-
-## KGE
-
-### KGE for ensembles (entire period)
-
-```{r ensemble kge, echo = F}
-
-ensem_kge_all <- ensem %>%
-  ungroup() %>%
-  summarize(grid_ensemble = KGE(grid_ensemble, obs),
-            statn_ensemble = KGE(statn_ensemble, obs),
-            all_ensemble = KGE(all_ensemble, obs),
-            grid_all = KGE(grid_all, obs),
-            statn_all = KGE(statn_all, obs)) %>%
+## Pbias
+
+### Overall pbias
+
+```{r pbias overall, echo = FALSE, message = FALSE, warning = FALSE}
+
+flow_pbias_all <- flow %>%
+  summarize(grid2011 = pbias(grid_2011, obs),
+            grid2012 = pbias(grid_2012, obs),
+            grid2013 = pbias(grid_2013, obs),
+            grid2014 = pbias(grid_2014, obs),
+            grid2015 = pbias(grid_2015, obs),
+            grid2016 = pbias(grid_2016, obs),
+            grid2017 = pbias(grid_2017, obs),
+            grid2018 = pbias(grid_2018, obs),
+            grid2019 = pbias(grid_2019, obs),
+            grid2020 = pbias(grid_2020, obs),
+            gridall = pbias(grid_all, obs),
+            statn2011 = pbias(statn_2011, obs),
+            statn2012 = pbias(statn_2012, obs),
+            statn2013 = pbias(statn_2013, obs),
+            statn2014 = pbias(statn_2014, obs),
+            statn2015 = pbias(statn_2015, obs),
+            statn2016 = pbias(statn_2016, obs),
+            statn2017 = pbias(statn_2017, obs),
+            statn2018 = pbias(statn_2018, obs),
+            statn2019 = pbias(statn_2019, obs),
+            statn2020 = pbias(statn_2020, obs),
+            statnall = pbias(statn_all, obs)) %>%
     mutate_if(is.numeric,
@@
 
-kable(ensem_kge_all) %>%
+flow_pbias_all <- flow_pbias_all %>%
+  pivot_longer(everything()) %>%
+  arrange(abs(value))
+
+kable(flow_pbias_all) %>%
   kable_styling(full_width = F)
@@
 
-### Annual KGEs for ensembles
-
-```{r annual kge ensemble, echo = F}
-
-yr_kge_ensem <- ensem %>%
-  ungroup() %>%
+### Pbias by year
+
+```{r pbias by year, echo = FALSE, message = FALSE, warning = FALSE}
+
+flow_year <- flow %>%
   mutate(year = year(date)) %>%
   group_by(year) %>%
-  summarize(grid_ensemble = KGE(grid_ensemble, obs),
-            statn_ensemble = KGE(statn_ensemble, obs),
-            all_ensemble = KGE(all_ensemble, obs),
-            grid_all = KGE(grid_all, obs),
-            statn_all = KGE(statn_all, obs)) %>%
+  summarize(grid2011 = pbias(grid_2011, obs),
+            grid2012 = pbias(grid_2012, obs),
+            grid2013 = pbias(grid_2013, obs),
+            grid2014 = pbias(grid_2014, obs),
+            grid2015 = pbias(grid_2015, obs),
+            grid2016 = pbias(grid_2016, obs),
+            grid2017 = pbias(grid_2017, obs),
+            grid2018 = pbias(grid_2018, obs),
+            grid2019 = pbias(grid_2019, obs),
+            grid2020 = pbias(grid_2020, obs),
+            gridall = pbias(grid_all, obs),
+            statn2011 = pbias(statn_2011, obs),
+            statn2012 = pbias(statn_2012, obs),
+            statn2013 = pbias(statn_2013, obs),
+            statn2014 = pbias(statn_2014, obs),
+            statn2015 = pbias(statn_2015, obs),
+            statn2016 = pbias(statn_2016, obs),
+            statn2017 = pbias(statn_2017, obs),
+            statn2018 = pbias(statn_2018, obs),
+            statn2019 = pbias(statn_2019, obs),
+            statn2020 = pbias(statn_2020, obs),
+            statnall = pbias(statn_all, obs)) %>%
     mutate_if(is.numeric,
@@
 
-yr_kge_table <- yr_kge_ensem %>%
-  pivot_longer(!year, names_to = 'model_run', values_to = 'kge') %>%
-  pivot_wider(names_from = 'year', values_from = 'kge')
-
-yr_kge_table %>%
+flow_pbias <- flow_year %>%
+  pivot_longer(!year, names_to = 'model_run', values_to = 'pbias') %>%
+  pivot_wider(names_from = 'year', values_from = 'pbias')
+
+flow_pbias %>%
   kable(.) %>%
@@
 
-yr_kge_plot <- yr_kge_ensem %>%
-  pivot_longer(!year, names_to = 'model_run', values_to = 'kge') %>%
+flow_plot <- flow_year %>%
+  pivot_longer(!year, names_to = 'model_run', values_to = 'pbias') %>%
   mutate(year = as.factor(year))
 
-#plot annual kge vals for ensembles
-plot_kge_yr_ensem <- function(calyear) {
-  yr_kge_plot %>%
+ggplot(flow_plot, aes(x = model_run, y = year, fill = pbias)) +
+  geom_tile(color = "white") +
+   scale_fill_gradient2(low = "blue", mid = "white", high = "red", midpoint = 0, name = "Ppias") +
+  geom_text(aes(label = round(pbias, 2)), color = "black", size = 2.5) +
+  theme_bw() +
+  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
+  labs(y = "Year")
+
+```
+
+### Annual Pbias plots
+
+```{r pbias plots, echo = FALSE, message = FALSE, warning = FALSE}
+
+plot_pbias <- function(calyear) {
+  flow_plot %>%
     filter(year == calyear) %>%
     ggplot(aes(x = model_run,
-               y = kge)) +
-    geom_col() +
+               y = pbias)) +
+    geom_point(size=3) +
     ggtitle(calyear) +
@@
 
-name <- levels(yr_kge_plot$year)
-
-lapply(name, plot_kge_yr_ensem)
-
-```
-
-### Monthly KGEs for ensembles
-
-```{r monthly kge ensemble, echo = F}
-
-mo_kge <- ensem %>%
-  ungroup() %>%
-  drop_na() %>%
-  mutate(month = month(date)) %>%
-  group_by(month) %>%
-  summarize(grid_ensemble = KGE(grid_ensemble, obs),
-            statn_ensemble = KGE(statn_ensemble, obs),
-            all_ensemble = KGE(all_ensemble, obs),
-            grid_all = KGE(grid_all, obs),
-            statn_all = KGE(statn_all, obs)) %>%
-    mutate_if(is.numeric,
-            round,
-            digits = 2)
-
-kable(mo_kge) %>%
-  kable_styling(full_width = F)
-
-mo_pivot <- mo_kge %>%
-  pivot_longer(!month, names_to = 'cal_run', values_to = 'KGE') %>%
-  drop_na()
-
-kge_plot_mo <- ggplot(mo_pivot, aes(month, KGE, color = cal_run)) + geom_point(size = 3) +
-    scale_color_manual(name="cal_run", values=c("grid_ensemble"="maroon",
-                                            "statn_ensemble"="darkturquoise",
-                                            "grid_all"="purple1",
-                                            "statn_all"='springgreen4',
-                                            "all_ensemble" = "orange")) +
-  theme_bw()
-
-ggplotly(kge_plot_mo)
-
-```
-
-## RMSE
-
-### Ensemble RMSE for entire period
-
-```{r ensemble rmse, echo = F}
-
-ensem_rmse_all <- ensem %>%
-  ungroup() %>%
-  summarize(grid_ensemble = rmse(grid_ensemble, obs),
-            statn_ensemble = rmse(statn_ensemble, obs),
-            all_ensemble = rmse(all_ensemble, obs),
-            grid_all = rmse(grid_all, obs),
-            statn_all = rmse(statn_all, obs)) %>%
-    mutate_if(is.numeric,
-            round,
-            digits = 4)
-
-kable(ensem_rmse_all) %>%
-  kable_styling(full_width = F)
-
-```
-
-### Annual RMSE for ensembles
-
-```{r annual rmse ensem, echo = F}
-
-yr_rmse_ensem <- ensem %>%
-  ungroup() %>%
-  mutate(year = year(date)) %>%
-  group_by(year) %>%
-  summarize(grid_ensemble = rmse(grid_ensemble, obs),
-            statn_ensemble = rmse(statn_ensemble, obs),
-            all_ensemble = rmse(all_ensemble, obs),
-            grid_all = rmse(grid_all, obs),
-            statn_all = rmse(statn_all, obs)) %>%
-    mutate_if(is.numeric,
-            round,
-            digits = 4)
-
-yr_rmse_table <- yr_rmse_ensem %>%
-  pivot_longer(!year, names_to = 'model_run', values_to = 'rmse') %>%
-  pivot_wider(names_from = 'year', values_from = 'rmse')
-
-yr_rmse_table %>%
-  kable(.) %>%
-  kable_styling()
-
-yr_rmse_plot <- yr_rmse_ensem %>%
-  pivot_longer(!year, names_to = 'model_run', values_to = 'rmse') %>%
-  mutate(year = as.factor(year))
-
-#plot annual rmse vals for ensembles
-plot_rmse_yr_ensem <- function(calyear) {
-  yr_rmse_plot %>%
-    filter(year == calyear) %>%
-    ggplot(aes(x = model_run,
-               y = rmse)) +
-    geom_col() +
-    ggtitle(calyear) +
-    theme_bw() +
-    theme(axis.text.x = element_text(angle = 45, hjust=1))
-}
-
-name <- levels(yr_rmse_plot$year)
-
-lapply(name, plot_rmse_yr_ensem)
-
-```
-
-### Monthly RMSEs for ensembles
-
-```{r month ensem rmse, echo = F}
-
-mo_rmse <- ensem %>%
-  ungroup() %>%
-  drop_na() %>%
-  mutate(month = month(date)) %>%
-  group_by(month) %>%
-  summarize(grid_ensemble = rmse(grid_ensemble, obs),
-            statn_ensemble = rmse(statn_ensemble, obs),
-            all_ensemble = rmse(all_ensemble, obs),
-            grid_all = rmse(grid_all, obs),
-            statn_all = rmse(statn_all, obs)) %>%
-    mutate_if(is.numeric,
-            round,
-            digits = 4)
-
-kable(mo_rmse) %>%
-  kable_styling(full_width = F)
-
-mo_pivot2 <- mo_rmse %>%
-  pivot_longer(!month, names_to = 'cal_run', values_to = 'RMSE') %>%
-  drop_na()
-
-rmse_plot_mo <- ggplot(mo_pivot2, aes(month, RMSE, color = cal_run)) + geom_point(size = 3) +
-    scale_color_manual(name="cal_run", values=c("grid_ensemble"="maroon",
-                                            "statn_ensemble"="darkturquoise",
-                                            "grid_all"="purple1",
-                                            "statn_all"='springgreen4',
-                                            "all_ensemble" = "orange")) +
-  theme_bw()
-
-ggplotly(rmse_plot_mo)
-
-```
-
-## NSE
-
-### Ensemble NSE for entire period
-
-```{r nse all, echo = F}
-
-ensem_nse_all <- ensem %>%
-  ungroup() %>%
-  summarize(grid_ensemble = NSE(grid_ensemble, obs),
-            statn_ensemble = NSE(statn_ensemble, obs),
-            all_ensemble = NSE(all_ensemble, obs),
-            grid_all = NSE(grid_all, obs),
-            statn_all = NSE(statn_all, obs)) %>%
-    mutate_if(is.numeric,
-            round,
-            digits = 2)
-
-kable(ensem_nse_all) %>%
-  kable_styling(full_width = F)
-
-```
-
-### Annual NSE for ensembles
-
-```{r annual nse, echo = F}
-
-yr_nse_ensem <- ensem %>%
-  ungroup() %>%
-  mutate(year = year(date)) %>%
-  group_by(year) %>%
-  summarize(grid_ensemble = NSE(grid_ensemble, obs),
-            statn_ensemble = NSE(statn_ensemble, obs),
-            all_ensemble = NSE(all_ensemble, obs),
-            grid_all = NSE(grid_all, obs),
-            statn_all = NSE(statn_all, obs)) %>%
-    mutate_if(is.numeric,
-            round,
-            digits = 4)
-
-yr_nse_table <- yr_nse_ensem %>%
-  pivot_longer(!year, names_to = 'model_run', values_to = 'nse') %>%
-  pivot_wider(names_from = 'year', values_from = 'nse')
-
-yr_nse_table %>%
-  kable(.) %>%
-  kable_styling()
-
-yr_nse_plot <- yr_nse_ensem %>%
-  pivot_longer(!year, names_to = 'model_run', values_to = 'nse') %>%
-  mutate(year = as.factor(year))
-
-#plot annual nse vals for ensembles
-plot_nse_yr_ensem <- function(calyear) {
-  yr_nse_plot %>%
-    filter(year == calyear) %>%
-    ggplot(aes(x = model_run,
-               y = nse)) +
-    geom_col() +
-    ggtitle(calyear) +
-    theme_bw() +
-    theme(axis.text.x = element_text(angle = 45, hjust=1))
-}
-
-name <- levels(yr_nse_plot$year)
-
-lapply(name, plot_nse_yr_ensem)
-
-```
-
-### Monthly NSE for ensembles
-
-```{r monthly rmse, echo =F}
-
-mo_nse <- ensem %>%
-  ungroup() %>%
-  drop_na() %>%
-  mutate(month = month(date)) %>%
-  group_by(month) %>%
-  summarize(grid_ensemble = NSE(grid_ensemble, obs),
-            statn_ensemble = NSE(statn_ensemble, obs),
-            all_ensemble = NSE(all_ensemble, obs),
-            grid_all = NSE(grid_all, obs),
-            statn_all = NSE(statn_all, obs)) %>%
-    mutate_if(is.numeric,
-            round,
-            digits = 4)
-
-kable(mo_nse) %>%
-  kable_styling(full_width = F)
-
-mo_pivot2 <- mo_nse %>%
-  pivot_longer(!month, names_to = 'cal_run', values_to = 'nse') %>%
-  drop_na()
-
-nse_plot_mo <- ggplot(mo_pivot2, aes(month, nse, color = cal_run)) + geom_point(size = 3) +
-  theme_bw() +
-  scale_color_manual(name="cal_run", values=c("grid_ensemble"="maroon",
-                                            "statn_ensemble"="darkturquoise",
-                                            "grid_all"="purple1",
-                                            "statn_all"='springgreen4',
-                                            "all_ensemble" = "orange"))
-
-ggplotly(nse_plot_mo)
-
-```
-
-## Cumulative Q
-
-```{r cumq, echo = F}
-
-ensem_cumq <- ensem %>%
-  mutate(month = month(date)) %>%
-  filter(month %in% c(4:9)) %>%
-  dplyr::select(-month) %>%
-  pivot_longer(!date, names_to = 'cal_run', values_to = 'q_m3s') %>%
-  group_by(cal_run, year(date)) %>%
-  mutate(cumsum = cumsum(replace_na(q_m3s, 0))) %>%
-  rename(year = 4) %>%
-  mutate(year = as.factor(year)) %>%
-  ungroup()
-
-#plot annual cumulative Q vals for ensembles
-plot_cumulq_yr_ensem <- function(calyear) {
-  {ensem_cumq %>%
-    filter(year == calyear) %>%
-    ggplot(aes(x = date,
-               y = cumsum,
-               color = cal_run)) +
-    geom_line() +
-    scale_color_manual(name="cal_run", values=c("obs"="black",
-                                             "grid_ensemble"="maroon",
-                                            "statn_ensemble"="darkturquoise",
-                                            "grid_all"="purple1",
-                                            "statn_all"='springgreen4',
-                                            "all_ensemble" = "orange")) +
-    ggtitle(calyear) +
-    theme_bw() +
-    labs(y = 'cumulative Q (m3s)')} %>%
-    ggplotly()
-}
-
-name <- levels(ensem_cumq$year)
-
-cumulative_plots <- lapply(name, plot_cumulq_yr_ensem)
-
-htmltools::tagList(cumulative_plots)
-
-cumulative_plots
-
-```
+name <- levels(flow_plot$year)
+
+lapply(name, plot_pbias)
+
+```
+
+<!-- # Ensembles -->
+
+<!-- ## Hydrograph -->
+
+<!-- ```{r ensemble hydrographs, echo = F} -->
+
+<!-- ensem <- flow %>% -->
+<!--   rowwise() %>% -->
+<!--   mutate(grid_ensemble = mean(c(grid_2011, grid_2012, -->
+<!--                                 grid_2013, grid_2014, -->
+<!--                                 grid_2015, grid_2016, -->
+<!--                                 grid_2017, grid_2018, -->
+<!--                                 grid_2019, grid_2020)), -->
+<!--          statn_ensemble = mean(c(statn_2011, statn_2012, -->
+<!--                                  statn_2013, statn_2014, -->
+<!--                                  statn_2015, statn_2016, -->
+<!--                                  statn_2017, statn_2018, -->
+<!--                                  statn_2019, statn_2020)), -->
+<!--          all_ensemble = mean(c(grid_2011, grid_2012, -->
+<!--                                grid_2013, grid_2014, -->
+<!--                                grid_2015, grid_2016, -->
+<!--                                grid_2017, grid_2018, -->
+<!--                                grid_2019, grid_2020, -->
+<!--                                statn_2011, statn_2012, -->
+<!--                                statn_2013, statn_2014, -->
+<!--                                statn_2015, statn_2016, -->
+<!--                                statn_2017, statn_2018, -->
+<!--                                statn_2019, statn_2020, -->
+<!--                                grid_all, statn_all))) %>% -->
+<!--   dplyr::select(date, grid_ensemble, statn_ensemble, -->
+<!--          all_ensemble, grid_all, -->
+<!--          statn_all, obs) -->
+
+<!-- ensem_pivot <- ensem %>% -->
+<!--   pivot_longer(!date, names_to = 'cal_run', values_to = 'q_m3s') %>% -->
+<!--   mutate(year = as.factor(year(date))) -->
+
+<!-- q_ensemble <- ggplot(ensem_pivot, aes(date, q_m3s, color = cal_run)) + -->
+<!--   geom_line() + -->
+<!--   scale_color_manual(name="cal_run", values=c('obs'='black', -->
+<!--                                             "grid_ensemble"="maroon", -->
+<!--                                             "statn_ensemble"="darkturquoise", -->
+<!--                                             "grid_all"="purple1", -->
+<!--                                             "statn_all"='springgreen4', -->
+<!--                                             "all_ensemble" = "orange")) + -->
+<!--   scale_y_continuous(name = 'Q_m3s') + -->
+<!--   theme_bw() -->
+
+<!-- q_ensemble -->
+
+<!-- ``` -->
+
+<!-- ## KGE -->
+
+<!-- ### KGE for ensembles (entire period) -->
+
+<!-- ```{r ensemble kge, echo = F} -->
+
+<!-- ensem_kge_all <- ensem %>% -->
+<!--   ungroup() %>% -->
+<!--   summarize(grid_ensemble = KGE(grid_ensemble, obs), -->
+<!--             statn_ensemble = KGE(statn_ensemble, obs), -->
+<!--             all_ensemble = KGE(all_ensemble, obs), -->
+<!--             grid_all = KGE(grid_all, obs), -->
+<!--             statn_all = KGE(statn_all, obs)) %>% -->
+<!--     mutate_if(is.numeric, -->
+<!--             round, -->
+<!--             digits = 2) -->
+
+<!-- kable(ensem_kge_all) %>% -->
+<!--   kable_styling(full_width = F) -->
+
+<!-- ``` -->
+
+<!-- ### Annual KGEs for ensembles -->
+
+<!-- ```{r annual kge ensemble, echo = F} -->
+
+<!-- yr_kge_ensem <- ensem %>% -->
+<!--   ungroup() %>% -->
+<!--   mutate(year = year(date)) %>% -->
+<!--   group_by(year) %>% -->
+<!--   summarize(grid_ensemble = KGE(grid_ensemble, obs), -->
+<!--             statn_ensemble = KGE(statn_ensemble, obs), -->
+<!--             all_ensemble = KGE(all_ensemble, obs), -->
+<!--             grid_all = KGE(grid_all, obs), -->
+<!--             statn_all = KGE(statn_all, obs)) %>% -->
+<!--     mutate_if(is.numeric, -->
+<!--             round, -->
+<!--             digits = 2) -->
+
+<!-- yr_kge_table <- yr_kge_ensem %>% -->
+<!--   pivot_longer(!year, names_to = 'model_run', values_to = 'kge') %>% -->
+<!--   pivot_wider(names_from = 'year', values_from = 'kge') -->
+
+<!-- yr_kge_table %>% -->
+<!--   kable(.) %>% -->
+<!--   kable_styling() -->
+
+<!-- yr_kge_plot <- yr_kge_ensem %>% -->
+<!--   pivot_longer(!year, names_to = 'model_run', values_to = 'kge') %>% -->
+<!--   mutate(year = as.factor(year)) -->
+
+<!-- #plot annual kge vals for ensembles -->
+<!-- plot_kge_yr_ensem <- function(calyear) { -->
+<!--   yr_kge_plot %>% -->
+<!--     filter(year == calyear) %>% -->
+<!--     ggplot(aes(x = model_run, -->
+<!--                y = kge)) + -->
+<!--     geom_col() + -->
+<!--     ggtitle(calyear) + -->
+<!--     theme_bw() + -->
+<!--     theme(axis.text.x = element_text(angle = 45, hjust=1)) -->
+<!-- } -->
+
+<!-- name <- levels(yr_kge_plot$year) -->
+
+<!-- lapply(name, plot_kge_yr_ensem) -->
+
+<!-- ``` -->
+
+<!-- ### Monthly KGEs for ensembles -->
+
+<!-- ```{r monthly kge ensemble, echo = F} -->
+
+<!-- mo_kge <- ensem %>% -->
+<!--   ungroup() %>% -->
+<!--   drop_na() %>% -->
+<!--   mutate(month = month(date)) %>% -->
+<!--   group_by(month) %>% -->
+<!--   summarize(grid_ensemble = KGE(grid_ensemble, obs), -->
+<!--             statn_ensemble = KGE(statn_ensemble, obs), -->
+<!--             all_ensemble = KGE(all_ensemble, obs), -->
+<!--             grid_all = KGE(grid_all, obs), -->
+<!--             statn_all = KGE(statn_all, obs)) %>% -->
+<!--     mutate_if(is.numeric, -->
+<!--             round, -->
+<!--             digits = 2) -->
+
+<!-- kable(mo_kge) %>% -->
+<!--   kable_styling(full_width = F) -->
+
+<!-- mo_pivot <- mo_kge %>% -->
+<!--   pivot_longer(!month, names_to = 'cal_run', values_to = 'KGE') %>% -->
+<!--   drop_na() -->
+
+<!-- kge_plot_mo <- ggplot(mo_pivot, aes(month, KGE, color = cal_run)) + geom_point(size = 3) + -->
+<!--     scale_color_manual(name="cal_run", values=c("grid_ensemble"="maroon", -->
+<!--                                             "statn_ensemble"="darkturquoise", -->
+<!--                                             "grid_all"="purple1", -->
+<!--                                             "statn_all"='springgreen4', -->
+<!--                                             "all_ensemble" = "orange")) + -->
+<!--   theme_bw() -->
+
+<!-- ggplotly(kge_plot_mo) -->
+
+<!-- ``` -->
+
+<!-- ## RMSE -->
+
+<!-- ### Ensemble RMSE for entire period -->
+
+<!-- ```{r ensemble rmse, echo = F} -->
+
+<!-- ensem_rmse_all <- ensem %>% -->
+<!--   ungroup() %>% -->
+<!--   summarize(grid_ensemble = rmse(grid_ensemble, obs), -->
+<!--             statn_ensemble = rmse(statn_ensemble, obs), -->
+<!--             all_ensemble = rmse(all_ensemble, obs), -->
+<!--             grid_all = rmse(grid_all, obs), -->
+<!--             statn_all = rmse(statn_all, obs)) %>% -->
+<!--     mutate_if(is.numeric, -->
+<!--             round, -->
+<!--             digits = 4) -->
+
+<!-- kable(ensem_rmse_all) %>% -->
+<!--   kable_styling(full_width = F) -->
+
+<!-- ``` -->
+
+<!-- ### Annual RMSE for ensembles -->
+
+<!-- ```{r annual rmse ensem, echo = F} -->
+
+<!-- yr_rmse_ensem <- ensem %>% -->
+<!--   ungroup() %>% -->
+<!--   mutate(year = year(date)) %>% -->
+<!--   group_by(year) %>% -->
+<!--   summarize(grid_ensemble = rmse(grid_ensemble, obs), -->
+<!--             statn_ensemble = rmse(statn_ensemble, obs), -->
+<!--             all_ensemble = rmse(all_ensemble, obs), -->
+<!--             grid_all = rmse(grid_all, obs), -->
+<!--             statn_all = rmse(statn_all, obs)) %>% -->
+<!--     mutate_if(is.numeric, -->
+<!--             round, -->
+<!--             digits = 4) -->
+
+<!-- yr_rmse_table <- yr_rmse_ensem %>% -->
+<!--   pivot_longer(!year, names_to = 'model_run', values_to = 'rmse') %>% -->
+<!--   pivot_wider(names_from = 'year', values_from = 'rmse') -->
+
+<!-- yr_rmse_table %>% -->
+<!--   kable(.) %>% -->
+<!--   kable_styling() -->
+
+<!-- yr_rmse_plot <- yr_rmse_ensem %>% -->
+<!--   pivot_longer(!year, names_to = 'model_run', values_to = 'rmse') %>% -->
+<!--   mutate(year = as.factor(year)) -->
+
+<!-- #plot annual rmse vals for ensembles -->
+<!-- plot_rmse_yr_ensem <- function(calyear) { -->
+<!--   yr_rmse_plot %>% -->
+<!--     filter(year == calyear) %>% -->
+<!--     ggplot(aes(x = model_run, -->
+<!--                y = rmse)) + -->
+<!--     geom_col() + -->
+<!--     ggtitle(calyear) + -->
+<!--     theme_bw() + -->
+<!--     theme(axis.text.x = element_text(angle = 45, hjust=1)) -->
+<!-- } -->
+
+<!-- name <- levels(yr_rmse_plot$year) -->
+
+<!-- lapply(name, plot_rmse_yr_ensem) -->
+
+<!-- ``` -->
+
+<!-- ### Monthly RMSEs for ensembles -->
+
+<!-- ```{r month ensem rmse, echo = F} -->
+
+<!-- mo_rmse <- ensem %>% -->
+<!--   ungroup() %>% -->
+<!--   drop_na() %>% -->
+<!--   mutate(month = month(date)) %>% -->
+<!--   group_by(month) %>% -->
+<!--   summarize(grid_ensemble = rmse(grid_ensemble, obs), -->
+<!--             statn_ensemble = rmse(statn_ensemble, obs), -->
+<!--             all_ensemble = rmse(all_ensemble, obs), -->
+<!--             grid_all = rmse(grid_all, obs), -->
+<!--             statn_all = rmse(statn_all, obs)) %>% -->
+<!--     mutate_if(is.numeric, -->
+<!--             round, -->
+<!--             digits = 4) -->
+
+<!-- kable(mo_rmse) %>% -->
+<!--   kable_styling(full_width = F) -->
+
+<!-- mo_pivot2 <- mo_rmse %>% -->
+<!--   pivot_longer(!month, names_to = 'cal_run', values_to = 'RMSE') %>% -->
+<!--   drop_na() -->
+
+<!-- rmse_plot_mo <- ggplot(mo_pivot2, aes(month, RMSE, color = cal_run)) + geom_point(size = 3) + -->
+<!--     scale_color_manual(name="cal_run", values=c("grid_ensemble"="maroon", -->
+<!--                                             "statn_ensemble"="darkturquoise", -->
+<!--                                             "grid_all"="purple1", -->
+<!--                                             "statn_all"='springgreen4', -->
+<!--                                             "all_ensemble" = "orange")) + -->
+<!--   theme_bw() -->
+
+<!-- ggplotly(rmse_plot_mo) -->
+
+<!-- ``` -->
+
+<!-- ## NSE -->
+
+<!-- ### Ensemble NSE for entire period -->
+
+<!-- ```{r nse all, echo = F} -->
+
+<!-- ensem_nse_all <- ensem %>% -->
+<!--   ungroup() %>% -->
+<!--   summarize(grid_ensemble = NSE(grid_ensemble, obs), -->
+<!--             statn_ensemble = NSE(statn_ensemble, obs), -->
+<!--             all_ensemble = NSE(all_ensemble, obs), -->
+<!--             grid_all = NSE(grid_all, obs), -->
+<!--             statn_all = NSE(statn_all, obs)) %>% -->
+<!--     mutate_if(is.numeric, -->
+<!--             round, -->
+<!--             digits = 2) -->
+
+<!-- kable(ensem_nse_all) %>% -->
+<!--   kable_styling(full_width = F) -->
+
+<!-- ``` -->
+
+<!-- ### Annual NSE for ensembles -->
+
+<!-- ```{r annual nse, echo = F} -->
+
+<!-- yr_nse_ensem <- ensem %>% -->
+<!--   ungroup() %>% -->
+<!--   mutate(year = year(date)) %>% -->
+<!--   group_by(year) %>% -->
+<!--   summarize(grid_ensemble = NSE(grid_ensemble, obs), -->
+<!--             statn_ensemble = NSE(statn_ensemble, obs), -->
+<!--             all_ensemble = NSE(all_ensemble, obs), -->
+<!--             grid_all = NSE(grid_all, obs), -->
+<!--             statn_all = NSE(statn_all, obs)) %>% -->
+<!--     mutate_if(is.numeric, -->
+<!--             round, -->
+<!--             digits = 4) -->
+
+<!-- yr_nse_table <- yr_nse_ensem %>% -->
+<!--   pivot_longer(!year, names_to = 'model_run', values_to = 'nse') %>% -->
+<!--   pivot_wider(names_from = 'year', values_from = 'nse') -->
+
+<!-- yr_nse_table %>% -->
+<!--   kable(.) %>% -->
+<!--   kable_styling() -->
+
+<!-- yr_nse_plot <- yr_nse_ensem %>% -->
+<!--   pivot_longer(!year, names_to = 'model_run', values_to = 'nse') %>% -->
+<!--   mutate(year = as.factor(year)) -->
+
+<!-- #plot annual nse vals for ensembles -->
+<!-- plot_nse_yr_ensem <- function(calyear) { -->
+<!--   yr_nse_plot %>% -->
+<!--     filter(year == calyear) %>% -->
+<!--     ggplot(aes(x = model_run, -->
+<!--                y = nse)) + -->
+<!--     geom_col() + -->
+<!--     ggtitle(calyear) + -->
+<!--     theme_bw() + -->
+<!--     theme(axis.text.x = element_text(angle = 45, hjust=1)) -->
+<!-- } -->
+
+<!-- name <- levels(yr_nse_plot$year) -->
+
+<!-- lapply(name, plot_nse_yr_ensem) -->
+
+<!-- ``` -->
+
+<!-- ### Monthly NSE for ensembles -->
+
+<!-- ```{r monthly rmse, echo =F} -->
+
+<!-- mo_nse <- ensem %>% -->
+<!--   ungroup() %>% -->
+<!--   drop_na() %>% -->
+<!--   mutate(month = month(date)) %>% -->
+<!--   group_by(month) %>% -->
+<!--   summarize(grid_ensemble = NSE(grid_ensemble, obs), -->
+<!--             statn_ensemble = NSE(statn_ensemble, obs), -->
+<!--             all_ensemble = NSE(all_ensemble, obs), -->
+<!--             grid_all = NSE(grid_all, obs), -->
+<!--             statn_all = NSE(statn_all, obs)) %>% -->
+<!--     mutate_if(is.numeric, -->
+<!--             round, -->
+<!--             digits = 4) -->
+
+<!-- kable(mo_nse) %>% -->
+<!--   kable_styling(full_width = F) -->
+
+<!-- mo_pivot2 <- mo_nse %>% -->
+<!--   pivot_longer(!month, names_to = 'cal_run', values_to = 'nse') %>% -->
+<!--   drop_na() -->
+
+<!-- nse_plot_mo <- ggplot(mo_pivot2, aes(month, nse, color = cal_run)) + geom_point(size = 3) + -->
+<!--   theme_bw() + -->
+<!--   scale_color_manual(name="cal_run", values=c("grid_ensemble"="maroon", -->
+<!--                                             "statn_ensemble"="darkturquoise", -->
+<!--                                             "grid_all"="purple1", -->
+<!--                                             "statn_all"='springgreen4', -->
+<!--                                             "all_ensemble" = "orange")) -->
+
+<!-- ggplotly(nse_plot_mo) -->
+
+<!-- ``` -->
 
@@
 
-```{r rd and rg, echo = F, fig.width = 14, fig.asp = 1, out.width = "100%"}
-
-gw_gridall <- read_csv(here('catchment_output/gridall_outlet.csv')) %>%
+```{r rd and rg, echo = FALSE, message = FALSE, warning = FALSE, fig.width = 14, fig.asp = 1, out.width = "100%"}
+
+gw_gridall <- read_csv(here('38HRU_sept2013_updates/catchment_output/grid_all.csv')) %>%
   dplyr::select(time, catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w) %>%
@@
 
-gw_statnall <- read_csv(here('catchment_output/statnall_outlet.csv')) %>%
+gw_statnall <- read_csv(here('38HRU_sept2013_updates/catchment_output/statn_all.csv')) %>%
   dplyr::select(time, catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w) %>%
@@
 
-gw_grid2011 <- read_csv(here('catchment_output/grid2011_outlet.csv')) %>%
-  dplyr::select(time, catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w) %>%
-  mutate(source = 'grid_2011')
-
-gw_grid2012 <- read_csv(here('catchment_output/grid2012_outlet.csv')) %>%
-  dplyr::select(time, catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w) %>%
-  mutate(source = 'grid_2012')
-
-gw_grid2013 <- read_csv(here('catchment_output/grid2013_outlet.csv')) %>%
-  dplyr::select(time, catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w) %>%
-  mutate(source = 'grid_2013')
-
-gw_grid2014 <- read_csv(here('catchment_output/grid2014_outlet.csv')) %>%
-  dplyr::select(time, catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w) %>%
-  mutate(source = 'grid_2014')
-
-gw_grid2015 <- read_csv(here('catchment_output/grid2015_outlet.csv')) %>%
-  dplyr::select(time, catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w) %>%
-  mutate(source = 'grid_2015')
-
-gw_grid2016 <- read_csv(here('catchment_output/grid2016_outlet.csv')) %>%
-  dplyr::select(time, catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w) %>%
-  mutate(source = 'grid_2016')
-
-gw_grid2017 <- read_csv(here('catchment_output/grid2017_outlet.csv')) %>%
-  dplyr::select(time, catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w) %>%
-  mutate(source = 'grid_2017')
-
-gw_grid2018 <- read_csv(here('catchment_output/grid2018_outlet.csv')) %>%
-  dplyr::select(time, catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w) %>%
-  mutate(source = 'grid_2018')
-
-gw_grid2019 <- read_csv(here('catchment_output/grid2019_outlet.csv')) %>%
-  dplyr::select(time, catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w) %>%
-  mutate(source = 'grid_2019')
-
-gw_grid2020 <- read_csv(here('catchment_output/grid2020_outlet.csv')) %>%
-  dplyr::select(time, catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w) %>%
-  mutate(source = 'grid_2020')
-
-gw_statn2011 <- read_csv(here('catchment_output/statn2011_outlet.csv')) %>%
-  dplyr::select(time, catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w) %>%
-  mutate(source = 'statn_2011')
-
-gw_statn2012 <- read_csv(here('catchment_output/statn2012_outlet.csv')) %>%
-  dplyr::select(time, catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w) %>%
-  mutate(source = 'statn_2012')
-
-gw_statn2013 <- read_csv(here('catchment_output/statn2013_outlet.csv')) %>%
-  dplyr::select(time, catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w) %>%
-  mutate(source = 'statn_2013')
-
-gw_statn2014 <- read_csv(here('catchment_output/statn2014_outlet.csv')) %>%
-  dplyr::select(time, catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w) %>%
-  mutate(source = 'statn_2014')
-
-gw_statn2015 <- read_csv(here('catchment_output/statn2015_outlet.csv')) %>%
-  dplyr::select(time, catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w) %>%
-  mutate(source = 'statn_2015')
-
-gw_statn2016 <- read_csv(here('catchment_output/statn2016_outlet.csv')) %>%
-  dplyr::select(time, catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w) %>%
-  mutate(source = 'statn_2016')
-
-gw_statn2017 <- read_csv(here('catchment_output/statn2017_outlet.csv')) %>%
-  dplyr::select(time, catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w) %>%
-  mutate(source = 'statn_2017')
-
-gw_statn2018 <- read_csv(here('catchment_output/statn2018_outlet.csv')) %>%
-  dplyr::select(time, catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w) %>%
-  mutate(source = 'statn_2018')
-
-gw_statn2019 <- read_csv(here('catchment_output/statn2019_outlet.csv')) %>%
-  dplyr::select(time, catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w) %>%
-  mutate(source = 'statn_2019')
-
-gw_statn2020 <- read_csv(here('catchment_output/statn2020_outlet.csv')) %>%
-  dplyr::select(time, catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w) %>%
-  mutate(source = 'statn_2020')
+# gw_grid2011 <- read_csv(here('38HRU_sept2013_updates/catchment_output/grid_2011.csv')) %>%
+#   dplyr::select(time, catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w) %>%
+#   mutate(source = 'grid_2011')
+# 
+# gw_grid2012 <- read_csv(here('38HRU_sept2013_updates/catchment_output/grid_2012.csv')) %>%
+#   dplyr::select(time, catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w) %>%
+#   mutate(source = 'grid_2012')
+# 
+# gw_grid2013 <- read_csv(here('38HRU_sept2013_updates/catchment_output/grid_2013.csv')) %>%
+#   dplyr::select(time, catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w) %>%
+#   mutate(source = 'grid_2013')
+# 
+# gw_grid2014 <- read_csv(here('38HRU_sept2013_updates/catchment_output/grid_2014.csv')) %>%
+#   dplyr::select(time, catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w) %>%
+#   mutate(source = 'grid_2014')
+# 
+# gw_grid2015 <- read_csv(here('38HRU_sept2013_updates/catchment_output/grid_2015.csv')) %>%
+#   dplyr::select(time, catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w) %>%
+#   mutate(source = 'grid_2015')
+# 
+# gw_grid2016 <- read_csv(here('38HRU_sept2013_updates/catchment_output/grid_2016.csv')) %>%
+#   dplyr::select(time, catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w) %>%
+#   mutate(source = 'grid_2016')
+# 
+# gw_grid2017 <- read_csv(here('38HRU_sept2013_updates/catchment_output/grid_2017.csv')) %>%
+#   dplyr::select(time, catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w) %>%
+#   mutate(source = 'grid_2017')
+# 
+# gw_grid2018 <- read_csv(here('38HRU_sept2013_updates/catchment_output/grid_2018.csv')) %>%
+#   dplyr::select(time, catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w) %>%
+#   mutate(source = 'grid_2018')
+# 
+# gw_grid2019 <- read_csv(here('38HRU_sept2013_updates/catchment_output/grid_2019.csv')) %>%
+#   dplyr::select(time, catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w) %>%
+#   mutate(source = 'grid_2019')
+# 
+# gw_grid2020 <- read_csv(here('38HRU_sept2013_updates/catchment_output/grid_2020.csv')) %>%
+#   dplyr::select(time, catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w) %>%
+#   mutate(source = 'grid_2020')
+# 
+# gw_statn2011 <- read_csv(here('38HRU_sept2013_updates/catchment_output/statn_2011.csv')) %>%
+#   dplyr::select(time, catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w) %>%
+#   mutate(source = 'statn_2011')
+# 
+# gw_statn2012 <- read_csv(here('38HRU_sept2013_updates/catchment_output/statn_2012.csv')) %>%
+#   dplyr::select(time, catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w) %>%
+#   mutate(source = 'statn_2012')
+# 
+# gw_statn2013 <- read_csv(here('38HRU_sept2013_updates/catchment_output/statn_2013.csv')) %>%
+#   dplyr::select(time, catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w) %>%
+#   mutate(source = 'statn_2013')
+# 
+# gw_statn2014 <- read_csv(here('38HRU_sept2013_updates/catchment_output/statn_2014.csv')) %>%
+#   dplyr::select(time, catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w) %>%
+#   mutate(source = 'statn_2014')
+# 
+# gw_statn2015 <- read_csv(here('38HRU_sept2013_updates/catchment_output/statn_2015.csv')) %>%
+#   dplyr::select(time, catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w) %>%
+#   mutate(source = 'statn_2015')
+# 
+# gw_statn2016 <- read_csv(here('38HRU_sept2013_updates/catchment_output/statn_2016.csv')) %>%
+#   dplyr::select(time, catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w) %>%
+#   mutate(source = 'statn_2016')
+# 
+# gw_statn2017 <- read_csv(here('38HRU_sept2013_updates/catchment_output/statn_2017.csv')) %>%
+#   dplyr::select(time, catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w) %>%
+#   mutate(source = 'statn_2017')
+# 
+# gw_statn2018 <- read_csv(here('38HRU_sept2013_updates/catchment_output/statn_2018.csv')) %>%
+#   dplyr::select(time, catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w) %>%
+#   mutate(source = 'statn_2018')
+# 
+# gw_statn2019 <- read_csv(here('38HRU_sept2013_updates/catchment_output/statn_2019.csv')) %>%
+#   dplyr::select(time, catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w) %>%
+#   mutate(source = 'statn_2019')
+# 
+# gw_statn2020 <- read_csv(here('38HRU_sept2013_updates/catchment_output/statn_2020.csv')) %>%
+#   dplyr::select(time, catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w) %>%
+#   mutate(source = 'statn_2020')
 
 gw <- bind_rows(
-  gw_gridall, gw_statnall,
-  gw_grid2011, gw_grid2012,
-  gw_grid2013, gw_grid2014,
-  gw_grid2015, gw_grid2016,
-  gw_grid2017, gw_grid2018,
-  gw_grid2019, gw_grid2020,
-  gw_statn2011, gw_statn2012,
-  gw_statn2013, gw_statn2014,
-  gw_statn2015, gw_statn2016,
-  gw_statn2017, gw_statn2018,
-  gw_statn2019, gw_statn2020
+  gw_gridall, gw_statnall
+  # gw_grid2011, gw_grid2012,
+  # gw_grid2013, gw_grid2014,
+  # gw_grid2015, gw_grid2016,
+  # gw_grid2017, gw_grid2018,
+  # gw_grid2019, gw_grid2020,
+  # gw_statn2011, gw_statn2012,
+  # gw_statn2013, gw_statn2014,
+  # gw_statn2015, gw_statn2016,
+  # gw_statn2017, gw_statn2018,
+  # gw_statn2019, gw_statn2020
 ) %>%
@@
 
-```{r rd and rg sums, echo = F, fig.width = 22, fig.asp = 1.5, out.width = "100%"}
+```{r rd and rg sums, echo = FALSE, message = FALSE, warning = FALSE, fig.width = 22, fig.asp = 1.5, out.width = "100%"}
 
@@
 
-```{r gw boxplot, echo = F}
+```{r gw boxplot, echo = FALSE, message = FALSE, warning = FALSE}
 
@@
 
-```{r flow season, echo = F, fig.width = 12, fig.asp = 0.75, out.width = "100%"}
+```{r flow season, echo = FALSE, message = FALSE, warning = FALSE, fig.width = 12, fig.asp = 0.75, out.width = "100%"}
 
@@
 #grid first
-setwd("/Users/megansears/Documents/Repos/fourmile/38HRU_model/HRU_output/grid_all")
+setwd("/Users/megansears/Documents/Repos/fourmile/38HRU_sept2013_updates/HRU_output/grid")
 
@@
 #statn next
-setwd("/Users/megansears/Documents/Repos/fourmile/38HRU_model/HRU_output/statn_all")
+setwd("/Users/megansears/Documents/Repos/fourmile/38HRU_sept2013_updates/HRU_output/statn")
 
@@
 
-# Join param & RD/RG
-
-```{r}
-
-join <- gw_maxcumsum %>%
-  rename(input_data = source)
-
-params1 <- params %>%
-  dplyr::select(-input_data) %>%
-  rename(input_data = cal) %>%
-  dplyr::select(-c(year_missing))
-
-join <- left_join(join, params1, by = c('input_data')) %>%
-  pivot_wider(., names_from='param', values_from='value') %>%
-  pivot_wider(., names_from = 'flow_type', values_from = 'flow_cms')
-
-write_csv(join, 'flow_params.csv')
-
-```
+<!-- # Join param & RD/RG -->
+
+<!-- ```{r} -->
+
+<!-- join <- gw_maxcumsum %>% -->
+<!--   rename(input_data = source) -->
+
+<!-- params1 <- params %>% -->
+<!--   dplyr::select(-input_data) %>% -->
+<!--   rename(input_data = cal) %>% -->
+<!--   dplyr::select(-c(year_missing)) -->
+
+<!-- # -->
+<!-- params_weighted1 <- params_weighted %>% -->
+<!--   rename(input_data = cal) %>% -->
+<!--   pivot_wider(names_from = 'param', -->
+<!--               values_from = 'area_weighted_average') %>% -->
+<!--   rename_with(~ paste0(., '_weighted'), 2:7) -->
+
+<!-- join <- left_join(join, params1, by = c('input_data')) %>% -->
+<!--   pivot_wider(., names_from='param', values_from='value') %>% -->
+<!--   pivot_wider(., names_from = 'flow_type', values_from = 'flow_cms') -->
+
+<!-- join <- left_join(join, params_weighted1, by = 'input_data') -->
+
+<!-- write_csv(join, 'flow_params.csv') -->
+
+<!-- ``` -->

### 2024-07-16 fourmile_dataprocess.Rmd
reminders

@@
 #look at 2011-2013
-hydro_datelimit <- ggplot(daily_q, aes(x=date, y=q_m3s, color=site)) + geom_line() + 
+hydro_datelimit <- ggplot(daily_q_ds3, aes(x=date, y=q_m3s, color=site)) + geom_point() + 
   theme_bw() + 

### 2024-07-16 fourmile_outputs_2013edits.Rmd
updating sept13 edit html

@@
 
-## Tmean difference
-
-2011-2020 average of daily station-grid Tmean
-
 ```{r cumulative tmean for HRUs, echo = F}
 hrus <- st_read('/Users/megansears/Documents/Repos/fourmile/38HRU_model/hrus_final.shp')
+
+mapview(hrus)
 
@@
 
+# #get rid of a bunch of data
+# hru_grid_tmean <- hru_grids %>%
+#   dplyr::select(c(time, ID, tmean)) %>%
+#   rename(tmean_grid = tmean)  %>%
+#   group_by(ID) %>%
+#   summarize(tmean_all_grid = mean(tmean_grid))
+# 
+# hru_statn_tmean <- hru_statn %>%
+#   dplyr::select(c(time, ID, tmean)) %>%
+#   rename(tmean_statn = tmean) %>%
+#   group_by(ID) %>%
+#   summarize(tmean_all_statn = mean(tmean_statn))
+# 
+# tmean_hrus <- left_join(hru_grid_tmean, hru_statn_tmean, by = c('ID')) %>%
+#   mutate(diff = tmean_all_statn - tmean_all_grid) %>%
+#   rename(value = ID)
+# 
+# hrus_map_tmean <- left_join(hrus, tmean_hrus, by = 'value')
+# 
+# tmap_mode('view')
+# 
+# locations_t <- locations %>%
+#   dplyr::filter(name %in% c('Gordon_South', 'Gordon_North',
+#                         'Betasso', 'Niwot_Snotel',
+#                         'University Camp SNTL'))
+# 
+# tm_shape(hrus_map_tmean) +
+#   tm_polygons('diff', id = 'value',
+#               breaks = c(-6,-4,-2,0,2,4,6)) +
+# tm_shape(locations_t) +
+#   tm_symbols(col='blue', size=4)
+
+```
+
+## Tmean difference
+Station - grid
+
+```{r}
+
 #get rid of a bunch of data
@@
 
-tmap_mode('view')
-
-locations_t <- locations %>%
-  dplyr::filter(name %in% c('Gordon_South', 'Gordon_North',
-                        'Betasso', 'Niwot_Snotel',
-                        'University Camp SNTL'))
-
-tm_shape(hrus_map_tmean) +
-  tm_polygons('diff', id = 'value',
-              breaks = c(-6,-4,-2,0,2,4,6)) +
-tm_shape(locations_t) +
-  tm_symbols(col='blue', size=4)
+tmean <- ggplot() +
+  geom_sf(data = hrus_map_tmean, aes(fill = diff), color = "black", lwd = 0.2) +
+  scale_fill_viridis_c(option = "plasma", name = "Tmean difference (°C)",
+                       limits = c(-5, 2)) +
+  theme_bw(base_size=13.5) +
+  theme_void() +
+  theme(
+    legend.position = "bottom",
+    panel.grid.major = element_blank(),
+    panel.grid.minor = element_blank(),
+    axis.title.x = element_blank(),
+    axis.title.y = element_blank())
+
+tmean
 
@@
 
+# #get rid of a bunch of data
+# hru_grid_tmax <- hru_grids %>%
+#   dplyr::select(c(time, ID, tmax)) %>%
+#   rename(tmax_grid = tmax)  %>%
+#   group_by(ID) %>%
+#   summarize(tmax_all_grid = mean(tmax_grid))
+# 
+# hru_statn_tmax <- hru_statn %>%
+#   dplyr::select(c(time, ID, tmax)) %>%
+#   rename(tmax_statn = tmax) %>%
+#   group_by(ID) %>%
+#   summarize(tmax_all_statn = mean(tmax_statn))
+# 
+# tmax_hrus <- left_join(hru_grid_tmax, hru_statn_tmax, by = c('ID')) %>%
+#   mutate(diff = tmax_all_statn - tmax_all_grid) %>%
+#   rename(value = ID)
+# 
+# hrus_map_tmax <- left_join(hrus, tmax_hrus, by = 'value')
+# 
+# tmap_mode('view')
+# 
+# locations_t <- locations %>%
+#   dplyr::filter(name %in% c('Gordon_South', 'Gordon_North',
+#                         'Betasso', 'Niwot_Snotel',
+#                         'University Camp SNTL'))
+# 
+# tm_shape(hrus_map_tmax) +
+#   tm_polygons('diff', id = 'value',
+#               breaks = c(-6,-4,-2,0,2,4,6)) +
+# tm_shape(locations_t) +
+#   tm_symbols(col='blue', size=4)
+
+# T max
 #get rid of a bunch of data
@@
 
-tmap_mode('view')
-
-locations_t <- locations %>%
-  dplyr::filter(name %in% c('Gordon_South', 'Gordon_North',
-                        'Betasso', 'Niwot_Snotel',
-                        'University Camp SNTL'))
-
-tm_shape(hrus_map_tmax) +
-  tm_polygons('diff', id = 'value',
-              breaks = c(-6,-4,-2,0,2,4,6)) +
-tm_shape(locations_t) +
-  tm_symbols(col='blue', size=4)
+tmax <- ggplot() +
+  geom_sf(data = hrus_map_tmax, aes(fill = diff), color = "black", lwd = 0.2) +
+  scale_fill_viridis_c(option = "plasma", name = "Tmax difference (°C)",
+                       limits = c(-5, 2)) +
+  theme_bw(base_size=13.5) +
+  theme_void() +
+  theme(
+    legend.position = "bottom",
+    panel.grid.major = element_blank(),
+    panel.grid.minor = element_blank(),
+    axis.title.x = element_blank(),
+    axis.title.y = element_blank())
+
+tmax
 
@@
 
+# #get rid of a bunch of data
+# hru_grid_tmin <- hru_grids %>%
+#   dplyr::select(c(time, ID, tmin)) %>%
+#   rename(tmin_grid = tmin)  %>%
+#   group_by(ID) %>%
+#   summarize(tmin_all_grid = mean(tmin_grid))
+# 
+# hru_statn_tmin <- hru_statn %>%
+#   dplyr::select(c(time, ID, tmin)) %>%
+#   rename(tmin_statn = tmin) %>%
+#   group_by(ID) %>%
+#   summarize(tmin_all_statn = mean(tmin_statn))
+# 
+# tmin_hrus <- left_join(hru_grid_tmin, hru_statn_tmin, by = c('ID')) %>%
+#   mutate(diff = tmin_all_statn - tmin_all_grid) %>%
+#   rename(value = ID)
+# 
+# hrus_map_tmin <- left_join(hrus, tmin_hrus, by = 'value')
+# 
+# tmap_mode('view')
+# 
+# locations_t <- locations %>%
+#   dplyr::filter(name %in% c('Gordon_South', 'Gordon_North',
+#                         'Betasso', 'Niwot_Snotel',
+#                         'University Camp SNTL'))
+# 
+# tm_shape(hrus_map_tmin) +
+#   tm_polygons('diff', id = 'value',
+#               breaks = c(-6,-4,-2,0,2,4,6)) +
+# tm_shape(locations_t) +
+#   tm_symbols(col='blue', size=4)
+
+# Tmin
 #get rid of a bunch of data
@@
 
-tmap_mode('view')
-
-locations_t <- locations %>%
-  dplyr::filter(name %in% c('Gordon_South', 'Gordon_North',
-                        'Betasso', 'Niwot_Snotel',
-                        'University Camp SNTL'))
-
-tm_shape(hrus_map_tmin) +
-  tm_polygons('diff', id = 'value',
-              breaks = c(-6,-4,-2,0,2,4,6)) +
-tm_shape(locations_t) +
-  tm_symbols(col='blue', size=4)
+tmin <- ggplot() +
+  geom_sf(data = hrus_map_tmin, aes(fill = diff), color = "black", lwd = 0.2) +
+  scale_fill_viridis_c(option = "plasma", name = "Tmin difference (°C)",
+                       limits = c(-5, 2)) +
+  theme_bw(base_size=13.5) +
+  theme_void() +
+  theme(
+    legend.position = "bottom",
+    panel.grid.major = element_blank(),
+    panel.grid.minor = element_blank(),
+    axis.title.x = element_blank(),
+    axis.title.y = element_blank())
+
+tmin
 
@@
 ```{r cum precip, echo = F}
-#get rid of a bunch of data
+# #get rid of a bunch of data
+# hru_grid_precip <- hru_grids %>%
+#   dplyr::select(c(time, ID, precip)) %>%
+#   rename(precip_grid = precip)
+# 
+# hru_statn_precip <- hru_statn %>%
+#   dplyr::select(c(time, ID, precip)) %>%
+#   rename(precip_statn = precip)
+# 
+# precip_hrus <- left_join(hru_grid_precip, hru_statn_precip, by = c('time', 'ID')) %>%
+#   mutate(diff = precip_statn - precip_grid,
+#          year = year(time)) %>%
+#   group_by(year, ID) %>%
+#   mutate(total_diff = cumsum(diff)) %>%
+#   filter(time == max(time)) %>%
+#   group_by(ID) %>%
+#   summarize(precip_avg_cumdiff = mean(total_diff)) %>%
+#   rename(value = ID)
+# 
+# hrus_map_precip <- left_join(hrus, precip_hrus, by = 'value')
+# 
+# tmap_mode('view')
+# 
+# locations_p <- locations %>%
+#   filter(type == 'precip')
+# 
+# tm_shape(hrus_map_precip) +
+#   tm_polygons('precip_avg_cumdiff', midpoint = NA, palette = 'YlGnBu', id = 'value') +
+# tm_shape(locations_p) +
+#   tm_symbols(col='blue', size=4)
+
+# Cumulative p
 hru_grid_precip <- hru_grids %>%
@@
 
-tmap_mode('view')
-
-locations_p <- locations %>%
-  filter(type == 'precip')
-
-tm_shape(hrus_map_precip) +
-  tm_polygons('precip_avg_cumdiff', midpoint = NA, palette = 'YlGnBu', id = 'value') +
-tm_shape(locations_p) +
-  tm_symbols(col='blue', size=4)
+precip <- ggplot() +
+  geom_sf(data = hrus_map_precip, aes(fill = precip_avg_cumdiff), color = "black", lwd = 0.2) +
+  scale_fill_viridis_c(option = "mako", name = "Cumulative P Difference (mm)") +
+  theme_bw(base_size=13.5) +
+  theme_void() +
+  theme(
+    legend.position = "bottom",
+    panel.grid.major = element_blank(),
+    panel.grid.minor = element_blank(),
+    axis.title.x = element_blank(),
+    axis.title.y = element_blank())
+
+precip
 
@@
 
-#get rid of a bunch of data
+# #get rid of a bunch of data
+# hru_grid_solrad <- hru_grids %>%
+#   dplyr::select(c(time, ID, solRad)) %>%
+#   rename(solrad_grid = solRad)  %>%
+#   group_by(ID) %>%
+#   summarize(solrad_all_grid = mean(solrad_grid))
+# 
+# hru_statn_solrad <- hru_statn %>%
+#   dplyr::select(c(time, ID, solRad)) %>%
+#   rename(solrad_statn = solRad) %>%
+#   group_by(ID) %>%
+#   summarize(solrad_all_statn = mean(solrad_statn))
+# 
+# solrad_hrus <- left_join(hru_grid_solrad, hru_statn_solrad, by = c('ID')) %>%
+#   mutate(diff = solrad_all_statn - solrad_all_grid) %>%
+#   rename(value = ID)
+# 
+# hrus_map_solrad <- left_join(hrus, solrad_hrus, by = 'value')
+# 
+# tmap_mode('view')
+# 
+# locations_solrad <- locations %>%
+#   dplyr::filter(name %in% c('Gordon_South',
+#                         'Betasso', 'Niwot_Snotel'))
+# 
+# tm_shape(hrus_map_solrad) +
+#   tm_polygons('diff', midpoint = NA, palette = 'YlOrRd', id = 'value') +
+# tm_shape(locations_solrad) +
+#   tm_symbols(col='blue', size=4)
+
+# solar rad
 hru_grid_solrad <- hru_grids %>%
@@
 
-tmap_mode('view')
-
-locations_solrad <- locations %>%
-  dplyr::filter(name %in% c('Gordon_South',
-                        'Betasso', 'Niwot_Snotel'))
-
-tm_shape(hrus_map_solrad) +
-  tm_polygons('diff', midpoint = NA, palette = 'YlOrRd', id = 'value') +
-tm_shape(locations_solrad) +
-  tm_symbols(col='blue', size=4)
+sr <- ggplot() +
+  geom_sf(data = hrus_map_solrad, aes(fill = diff), color = "black", lwd = 0.2) +
+  scale_fill_viridis_c(option = "cividis", name = expression("Solar rad difference (MJ/m"^"2" * ")")) +
+  theme_bw(base_size=13.5) +
+  theme_void() +
+  theme(
+    legend.position = "bottom",
+    panel.grid.major = element_blank(),
+    panel.grid.minor = element_blank(),
+    axis.title.x = element_blank(),
+    axis.title.y = element_blank()) +
+  guides(
+    fill = guide_colorbar(
+      label.theme = element_text(size = 10)))
+
+sr
 
@@
 
+# #get rid of a bunch of data
+# hru_grid_rh <- hru_grids %>%
+#   dplyr::select(c(time, ID, rhum)) %>%
+#   rename(rh_grid = rhum)  %>%
+#   group_by(ID) %>%
+#   summarize(rh_all_grid = mean(rh_grid))
+# 
+# hru_statn_rh <- hru_statn %>%
+#   dplyr::select(c(time, ID, rhum)) %>%
+#   rename(rh_statn = rhum) %>%
+#   group_by(ID) %>%
+#   summarize(rh_all_statn = mean(rh_statn))
+# 
+# rh_hrus <- left_join(hru_grid_rh, hru_statn_rh, by = c('ID')) %>%
+#   mutate(diff = rh_all_statn - rh_all_grid) %>%
+#   rename(value = ID)
+# 
+# hrus_map_rh <- left_join(hrus, rh_hrus, by = 'value')
+# 
+# tmap_mode('view')
+# 
+# locations_rh <- locations %>%
+#   dplyr::filter(name %in% c('Gordon_South', 'Gordon_North',
+#                         'Betasso', 'Niwot_Snotel'))
+# 
+# tm_shape(hrus_map_rh) +
+#   tm_polygons('diff', midpoint = NA, id = 'value') +
+# tm_shape(locations_rh) +
+#   tm_symbols(col='blue', size=4)
+
+# RH
 #get rid of a bunch of data
@@
 
-tmap_mode('view')
-
-locations_rh <- locations %>%
-  dplyr::filter(name %in% c('Gordon_South', 'Gordon_North',
-                        'Betasso', 'Niwot_Snotel'))
-
-tm_shape(hrus_map_rh) +
-  tm_polygons('diff', midpoint = NA, id = 'value') +
-tm_shape(locations_rh) +
-  tm_symbols(col='blue', size=4)
+rh <- ggplot() +
+  geom_sf(data = hrus_map_rh, aes(fill = diff), color = "black", lwd = 0.2) +
+  scale_fill_viridis_c(option = "viridis", name = "RH difference (%)") +
+  theme_bw(base_size=13.5) +
+  theme_void() +
+  theme(
+    legend.position = "bottom",
+    panel.grid.major = element_blank(),
+    panel.grid.minor = element_blank(),
+    axis.title.x = element_blank(),
+    axis.title.y = element_blank())
+
+rh
+
+```
+
+```{r}
+
+# lots <- ggarrange(precip,
+#                   sr,
+#                   rh,
+#                   tmean,
+#                   tmax,
+#                   tmin) 
+#           #nrow = 4)
+#           #ncol= 0)
+# lots
 
@@
 
-tmap_mode('view')
+tmap_mode('plot')
 

### 2024-07-16 spatial_figs.Rmd
reminders
updating sept13 edit html
updating

@@
 # update the HRUs
-hru_new <- vect('/Users/megansears/Documents/Repos/fourmile/data/GIS/hrus_final.shp')
+hru_new <- vect('/Users/megansears/Documents/Repos/fourmile/38HRU_model/hrus_final.shp')
 plot(hru_new)
 
-hru_new <- st_read('/Users/megansears/Documents/Repos/fourmile/data/GIS/hrus_final.shp') %>%
+hru_new <- st_read('/Users/megansears/Documents/Repos/fourmile/38HRU_model/hrus_final.shp')
 
-mapview(hru_new)
+mapview(hru_new) + mapview(hru_test)
+mapview(hru_test)
 
@@
 
-# Figure 1b-e -- NEED TO REDO WITH WHOLE CATCHMENT DATA
+# Figure 1b-e -- NEED TO REDO WITH WHOLE CATCHMENT DATA and UPDATED MODELS
 
@@
 
-# difference
+# difference - UPDATE file sources!!
 

### 2024-07-16 fourmile_outputs_2013edits.Rmd
fixed spatial figs

@@
   facet_wrap(~param, scales = 'free_y')
+
+write_csv(params_combo, '/Users/megansears/Documents/Repos/fourmile/38HRU_sept2013_updates/params_burn_unburn.csv')
 
@@
 
-# gw_grid2011 <- read_csv(here('38HRU_sept2013_updates/catchment_output/grid_2011.csv')) %>%
-#   dplyr::select(time, catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w) %>%
-#   mutate(source = 'grid_2011')
-# 
-# gw_grid2012 <- read_csv(here('38HRU_sept2013_updates/catchment_output/grid_2012.csv')) %>%
-#   dplyr::select(time, catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w) %>%
-#   mutate(source = 'grid_2012')
-# 
-# gw_grid2013 <- read_csv(here('38HRU_sept2013_updates/catchment_output/grid_2013.csv')) %>%
-#   dplyr::select(time, catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w) %>%
-#   mutate(source = 'grid_2013')
-# 
-# gw_grid2014 <- read_csv(here('38HRU_sept2013_updates/catchment_output/grid_2014.csv')) %>%
-#   dplyr::select(time, catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w) %>%
-#   mutate(source = 'grid_2014')
-# 
-# gw_grid2015 <- read_csv(here('38HRU_sept2013_updates/catchment_output/grid_2015.csv')) %>%
-#   dplyr::select(time, catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w) %>%
-#   mutate(source = 'grid_2015')
-# 
-# gw_grid2016 <- read_csv(here('38HRU_sept2013_updates/catchment_output/grid_2016.csv')) %>%
-#   dplyr::select(time, catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w) %>%
-#   mutate(source = 'grid_2016')
-# 
-# gw_grid2017 <- read_csv(here('38HRU_sept2013_updates/catchment_output/grid_2017.csv')) %>%
-#   dplyr::select(time, catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w) %>%
-#   mutate(source = 'grid_2017')
-# 
-# gw_grid2018 <- read_csv(here('38HRU_sept2013_updates/catchment_output/grid_2018.csv')) %>%
-#   dplyr::select(time, catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w) %>%
-#   mutate(source = 'grid_2018')
-# 
-# gw_grid2019 <- read_csv(here('38HRU_sept2013_updates/catchment_output/grid_2019.csv')) %>%
-#   dplyr::select(time, catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w) %>%
-#   mutate(source = 'grid_2019')
-# 
-# gw_grid2020 <- read_csv(here('38HRU_sept2013_updates/catchment_output/grid_2020.csv')) %>%
-#   dplyr::select(time, catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w) %>%
-#   mutate(source = 'grid_2020')
-# 
-# gw_statn2011 <- read_csv(here('38HRU_sept2013_updates/catchment_output/statn_2011.csv')) %>%
-#   dplyr::select(time, catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w) %>%
-#   mutate(source = 'statn_2011')
-# 
-# gw_statn2012 <- read_csv(here('38HRU_sept2013_updates/catchment_output/statn_2012.csv')) %>%
-#   dplyr::select(time, catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w) %>%
-#   mutate(source = 'statn_2012')
-# 
-# gw_statn2013 <- read_csv(here('38HRU_sept2013_updates/catchment_output/statn_2013.csv')) %>%
-#   dplyr::select(time, catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w) %>%
-#   mutate(source = 'statn_2013')
-# 
-# gw_statn2014 <- read_csv(here('38HRU_sept2013_updates/catchment_output/statn_2014.csv')) %>%
-#   dplyr::select(time, catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w) %>%
-#   mutate(source = 'statn_2014')
-# 
-# gw_statn2015 <- read_csv(here('38HRU_sept2013_updates/catchment_output/statn_2015.csv')) %>%
-#   dplyr::select(time, catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w) %>%
-#   mutate(source = 'statn_2015')
-# 
-# gw_statn2016 <- read_csv(here('38HRU_sept2013_updates/catchment_output/statn_2016.csv')) %>%
-#   dplyr::select(time, catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w) %>%
-#   mutate(source = 'statn_2016')
-# 
-# gw_statn2017 <- read_csv(here('38HRU_sept2013_updates/catchment_output/statn_2017.csv')) %>%
-#   dplyr::select(time, catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w) %>%
-#   mutate(source = 'statn_2017')
-# 
-# gw_statn2018 <- read_csv(here('38HRU_sept2013_updates/catchment_output/statn_2018.csv')) %>%
-#   dplyr::select(time, catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w) %>%
-#   mutate(source = 'statn_2018')
-# 
-# gw_statn2019 <- read_csv(here('38HRU_sept2013_updates/catchment_output/statn_2019.csv')) %>%
-#   dplyr::select(time, catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w) %>%
-#   mutate(source = 'statn_2019')
-# 
-# gw_statn2020 <- read_csv(here('38HRU_sept2013_updates/catchment_output/statn_2020.csv')) %>%
-#   dplyr::select(time, catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w) %>%
-#   mutate(source = 'statn_2020')
+gw_grid2011 <- read_csv(here('38HRU_sept2013_updates/catchment_output/grid_2011.csv')) %>%
+  dplyr::select(time, catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w) %>%
+  mutate(source = 'grid_2011')
+
+gw_grid2012 <- read_csv(here('38HRU_sept2013_updates/catchment_output/grid_2012.csv')) %>%
+  dplyr::select(time, catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w) %>%
+  mutate(source = 'grid_2012')
+
+gw_grid2013 <- read_csv(here('38HRU_sept2013_updates/catchment_output/grid_2013.csv')) %>%
+  dplyr::select(time, catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w) %>%
+  mutate(source = 'grid_2013')
+
+gw_grid2014 <- read_csv(here('38HRU_sept2013_updates/catchment_output/grid_2014.csv')) %>%
+  dplyr::select(time, catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w) %>%
+  mutate(source = 'grid_2014')
+
+gw_grid2015 <- read_csv(here('38HRU_sept2013_updates/catchment_output/grid_2015.csv')) %>%
+  dplyr::select(time, catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w) %>%
+  mutate(source = 'grid_2015')
+
+gw_grid2016 <- read_csv(here('38HRU_sept2013_updates/catchment_output/grid_2016.csv')) %>%
+  dplyr::select(time, catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w) %>%
+  mutate(source = 'grid_2016')
+
+gw_grid2017 <- read_csv(here('38HRU_sept2013_updates/catchment_output/grid_2017.csv')) %>%
+  dplyr::select(time, catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w) %>%
+  mutate(source = 'grid_2017')
+
+gw_grid2018 <- read_csv(here('38HRU_sept2013_updates/catchment_output/grid_2018.csv')) %>%
+  dplyr::select(time, catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w) %>%
+  mutate(source = 'grid_2018')
+
+gw_grid2019 <- read_csv(here('38HRU_sept2013_updates/catchment_output/grid_2019.csv')) %>%
+  dplyr::select(time, catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w) %>%
+  mutate(source = 'grid_2019')
+
+gw_grid2020 <- read_csv(here('38HRU_sept2013_updates/catchment_output/grid_2020.csv')) %>%
+  dplyr::select(time, catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w) %>%
+  mutate(source = 'grid_2020')
+
+gw_statn2011 <- read_csv(here('38HRU_sept2013_updates/catchment_output/statn_2011.csv')) %>%
+  dplyr::select(time, catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w) %>%
+  mutate(source = 'statn_2011')
+
+gw_statn2012 <- read_csv(here('38HRU_sept2013_updates/catchment_output/statn_2012.csv')) %>%
+  dplyr::select(time, catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w) %>%
+  mutate(source = 'statn_2012')
+
+gw_statn2013 <- read_csv(here('38HRU_sept2013_updates/catchment_output/statn_2013.csv')) %>%
+  dplyr::select(time, catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w) %>%
+  mutate(source = 'statn_2013')
+
+gw_statn2014 <- read_csv(here('38HRU_sept2013_updates/catchment_output/statn_2014.csv')) %>%
+  dplyr::select(time, catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w) %>%
+  mutate(source = 'statn_2014')
+
+gw_statn2015 <- read_csv(here('38HRU_sept2013_updates/catchment_output/statn_2015.csv')) %>%
+  dplyr::select(time, catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w) %>%
+  mutate(source = 'statn_2015')
+
+gw_statn2016 <- read_csv(here('38HRU_sept2013_updates/catchment_output/statn_2016.csv')) %>%
+  dplyr::select(time, catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w) %>%
+  mutate(source = 'statn_2016')
+
+gw_statn2017 <- read_csv(here('38HRU_sept2013_updates/catchment_output/statn_2017.csv')) %>%
+  dplyr::select(time, catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w) %>%
+  mutate(source = 'statn_2017')
+
+gw_statn2018 <- read_csv(here('38HRU_sept2013_updates/catchment_output/statn_2018.csv')) %>%
+  dplyr::select(time, catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w) %>%
+  mutate(source = 'statn_2018')
+
+gw_statn2019 <- read_csv(here('38HRU_sept2013_updates/catchment_output/statn_2019.csv')) %>%
+  dplyr::select(time, catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w) %>%
+  mutate(source = 'statn_2019')
+
+gw_statn2020 <- read_csv(here('38HRU_sept2013_updates/catchment_output/statn_2020.csv')) %>%
+  dplyr::select(time, catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w) %>%
+  mutate(source = 'statn_2020')
 
 gw <- bind_rows(
-  gw_gridall, gw_statnall
-  # gw_grid2011, gw_grid2012,
-  # gw_grid2013, gw_grid2014,
-  # gw_grid2015, gw_grid2016,
-  # gw_grid2017, gw_grid2018,
-  # gw_grid2019, gw_grid2020,
-  # gw_statn2011, gw_statn2012,
-  # gw_statn2013, gw_statn2014,
-  # gw_statn2015, gw_statn2016,
-  # gw_statn2017, gw_statn2018,
-  # gw_statn2019, gw_statn2020
+  gw_gridall, gw_statnall,
+  gw_grid2011, gw_grid2012,
+  gw_grid2013, gw_grid2014,
+  gw_grid2015, gw_grid2016,
+  gw_grid2017, gw_grid2018,
+  gw_grid2019, gw_grid2020,
+  gw_statn2011, gw_statn2012,
+  gw_statn2013, gw_statn2014,
+  gw_statn2015, gw_statn2016,
+  gw_statn2017, gw_statn2018,
+  gw_statn2019, gw_statn2020
 ) %>%
@@
 
-<!-- # Join param & RD/RG -->
-
-<!-- ```{r} -->
-
-<!-- join <- gw_maxcumsum %>% -->
-<!--   rename(input_data = source) -->
-
-<!-- params1 <- params %>% -->
-<!--   dplyr::select(-input_data) %>% -->
-<!--   rename(input_data = cal) %>% -->
-<!--   dplyr::select(-c(year_missing)) -->
-
-<!-- # -->
-<!-- params_weighted1 <- params_weighted %>% -->
-<!--   rename(input_data = cal) %>% -->
-<!--   pivot_wider(names_from = 'param', -->
-<!--               values_from = 'area_weighted_average') %>% -->
-<!--   rename_with(~ paste0(., '_weighted'), 2:7) -->
-
-<!-- join <- left_join(join, params1, by = c('input_data')) %>% -->
-<!--   pivot_wider(., names_from='param', values_from='value') %>% -->
-<!--   pivot_wider(., names_from = 'flow_type', values_from = 'flow_cms') -->
-
-<!-- join <- left_join(join, params_weighted1, by = 'input_data') -->
-
-<!-- write_csv(join, 'flow_params.csv') -->
-
-<!-- ``` -->
+# Join param & RD/RG
+
+```{r}
+
+join <- gw_maxcumsum %>%
+  rename(input_data = source)
+
+params1 <- params %>%
+  dplyr::select(-input_data) %>%
+  rename(input_data = cal) %>%
+  dplyr::select(-c(year_missing))
+
+#
+params_weighted1 <- params_weighted %>%
+  mutate(input_data = paste(source, year_missing, sep = "_")) %>% 
+  pivot_wider(names_from = 'param',
+              values_from = 'area_weighted_average') %>%
+  rename_with(~ paste0(., '_weighted'), 4:9) %>%
+  dplyr::select(-c(year_missing, source))
+
+join <- left_join(join, params1, by = c('input_data')) %>%
+  pivot_wider(., names_from='param', values_from='value') %>%
+  pivot_wider(., names_from = 'flow_type', values_from = 'flow_cms')
+
+join <- left_join(join, params_weighted1, by = 'input_data')
+
+write_csv(join, '/Users/megansears/Documents/Repos/fourmile/38HRU_sept2013_updates/flow_params.csv')
+
+```

### 2024-07-16 fourmile_outputs_2013edits.Rmd
minor update

@@
 
-# Join param & RD/RG
-
-```{r}
-
-join <- gw_maxcumsum %>%
-  rename(input_data = source)
-
-params1 <- params %>%
-  dplyr::select(-input_data) %>%
-  rename(input_data = cal) %>%
-  dplyr::select(-c(year_missing))
-
-#
-params_weighted1 <- params_weighted %>%
-  mutate(input_data = paste(source, year_missing, sep = "_")) %>% 
-  pivot_wider(names_from = 'param',
-              values_from = 'area_weighted_average') %>%
-  rename_with(~ paste0(., '_weighted'), 4:9) %>%
-  dplyr::select(-c(year_missing, source))
-
-join <- left_join(join, params1, by = c('input_data')) %>%
-  pivot_wider(., names_from='param', values_from='value') %>%
-  pivot_wider(., names_from = 'flow_type', values_from = 'flow_cms')
-
-join <- left_join(join, params_weighted1, by = 'input_data')
-
-write_csv(join, '/Users/megansears/Documents/Repos/fourmile/38HRU_sept2013_updates/flow_params.csv')
-
-```
+<!-- # Join param & RD/RG -->
+
+<!-- ```{r} -->
+
+<!-- join <- gw_maxcumsum %>% -->
+<!--   rename(input_data = source) -->
+
+<!-- params1 <- params %>% -->
+<!--   dplyr::select(-input_data) %>% -->
+<!--   rename(input_data = cal) %>% -->
+<!--   dplyr::select(-c(year_missing)) -->
+
+<!-- # -->
+<!-- params_weighted1 <- params_weighted %>% -->
+<!--   mutate(input_data = paste(source, year_missing, sep = "_")) %>%  -->
+<!--   pivot_wider(names_from = 'param', -->
+<!--               values_from = 'area_weighted_average') %>% -->
+<!--   rename_with(~ paste0(., '_weighted'), 4:9) %>% -->
+<!--   dplyr::select(-c(year_missing, source)) -->
+
+<!-- join <- left_join(join, params1, by = c('input_data')) %>% -->
+<!--   pivot_wider(., names_from='param', values_from='value') %>% -->
+<!--   pivot_wider(., names_from = 'flow_type', values_from = 'flow_cms') -->
+
+<!-- join <- left_join(join, params_weighted1, by = 'input_data') -->
+
+<!-- write_csv(join, '/Users/megansears/Documents/Repos/fourmile/38HRU_sept2013_updates/flow_params.csv') -->
+
+<!-- ``` -->

### 2024-07-17 fourmile_outputs_2013edits.Rmd
dont need all RD RG cals in there

--- 2024-07-16 fourmile_outputs_2013edits.Rmd
@@
 <!-- params_weighted1 <- params_weighted %>% -->
-<!--   rename(input_data = cal) %>% -->
+<!--   mutate(input_data = paste(source, year_missing, sep = "_")) %>%  -->
 <!--   pivot_wider(names_from = 'param', -->
 <!--               values_from = 'area_weighted_average') %>% -->
-<!--   rename_with(~ paste0(., '_weighted'), 2:7) -->
+<!--   rename_with(~ paste0(., '_weighted'), 4:9) %>% -->
+<!--   dplyr::select(-c(year_missing, source)) -->
 
@@
 
-<!-- write_csv(join, 'flow_params.csv') -->
+<!-- write_csv(join, '/Users/megansears/Documents/Repos/fourmile/38HRU_sept2013_updates/flow_params.csv') -->
 

### 2024-07-19 fourmile_outputs_2013edits.Rmd
added all row to heatmaps (KGE and pbias). fixed rd/rg seasons

@@
 
-ggplot(flow_plot, aes(x = model_run, y = year, fill = kge)) +
+# add all to the plot below
+kge_all <- flow_kge_all %>%
+  mutate(year = 'all years') %>%
+  rename(model_run = name,
+         kge = value)
+
+flow_plot_updated <- bind_rows(flow_plot, kge_all)
+
+ggplot(flow_plot_updated, aes(x = model_run, y = year, fill = kge)) +
   geom_tile(color = "white") +
@@
 
-ggplot(flow_plot, aes(x = model_run, y = year, fill = pbias)) +
+# add all to the plot below
+pbias_all <- flow_pbias_all %>%
+  mutate(year = 'all years') %>%
+  rename(model_run = name,
+         pbias = value)
+
+flow_plot_updated <- bind_rows(flow_plot, pbias_all)
+
+ggplot(flow_plot_updated, aes(x = model_run, y = year, fill = pbias)) +
   geom_tile(color = "white") +
@@
   geom_point(position=position_jitterdodge(),alpha=0.3) +
-  ggtitle('Max annual cumulative sums')
+  ggtitle('Annual sum') +
+  labs(y = 'Total volume (m3)')
 
@@
   facet_wrap(~flow_type, scales = 'free') +
-  ggtitle('Max annual cumulative sums')
+  ggtitle('Annual sum') +
+  labs(y = 'Total volume (m3)')
 
@@
 ### RD and RG by season
+
+- January-February = baseflow_winter
+- March-June = snowmelt
+- July-August = Monsoon
+- September-December = Baseflow_fall
 
@@
   mutate(season = case_when(month %in% c(3,4,5,6) ~ 'snowmelt',
-                            month %in% c(7,8,9,10) ~ 'monsoon',
-                            month %in% c(11,12,1,2) ~ 'baseflow')) %>%
+                            month %in% c(7,8) ~ 'monsoon',
+                            month %in% c(9,10,11,12) ~ 'baseflow_fall',
+                            month %in% c(1,2) ~ 'baseflow_winter')) %>%
   group_by(source, year, season) %>%
@@
   geom_boxplot(position = position_dodge(1)) +
-  geom_point(position=position_jitterdodge(),alpha=0.3) +
+  #geom_point(position=position_jitterdodge(),alpha=0.3) +
   #geom_point(aes(color = source)) +
-  facet_wrap(~season, scales = 'free') +
-  ggtitle('Max annual season cumulative sums') +
+  facet_wrap(~season) +
+  ggtitle('RD/RG annual sums') +
   theme_bw() +
   theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
-  theme(text = element_text(size = 20))
+  theme(text = element_text(size = 20)) +
+  labs(y = 'Total flow (m3)')
 
@@
   facet_wrap(~season + flow_type, scales = 'free') +
-  ggtitle('Max annual season cumulative sums') +
+  ggtitle('Seasonal sums') +
   theme_bw() +
-  theme(text = element_text(size = 20))
+  theme(text = element_text(size = 20)) +
+  labs(y = 'Total flow (m3)')
 

### 2024-07-19 fourmile_outputs_2013edits.Rmd
updated a spelling error

@@
   geom_tile(color = "white") +
-   scale_fill_gradient2(low = "blue", mid = "white", high = "red", midpoint = 0, name = "Ppias") +
+   scale_fill_gradient2(low = "blue", mid = "white", high = "red", midpoint = 0, name = "Pbias") +
   geom_text(aes(label = round(pbias, 2)), color = "black", size = 2.5) +

### 2024-08-12 compare_luca_runs.Rmd
comparing luca runs

---
title: "Comparing LUCA runs for station all"
author: "Megan Sears"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: yes
    toc_float: yes
    theme: journal
editor_options:
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = F,
  message = F, 
  warning  = F)

library(tidyverse)
library(plotly)
library(lubridate)
library(knitr)
library(kableExtra)
library(dataRetrieval)
library(hydroGOF)
library(sp)
library(raster)
library(sf)
library(mapview)
library(here)
library(scales)
library(dataRetrieval)
library(tmap)
library(ggpubr)
library(gridExtra)
library(stringr)

```

# KGE from calibrations

12 station all runs

- KGE mean is 0.86
- Standard deviation is 0.007

```{r}

kge <- read_csv('/Users/megansears/Documents/Repos/fourmile/38HRU_sept2013_updates/cals/compare_luca_runs/kge_compare.csv')

ggplot(kge, aes(as.character(run), kge)) + geom_point() + labs(x='Station all run')

```

# Parameters

## Scatter plots

```{r read in params, echo = FALSE, message = FALSE, warning = FALSE, include = F}

setwd("/Users/megansears/Documents/Repos/fourmile/38HRU_sept2013_updates/cals/compare_luca_runs")

#pull in all filenames with composite
filenames <- list.files('.', pattern=".csv", full.names=F)

#read all the csvs
dataframes <- lapply(filenames, read_csv)

#name all the csv
names(dataframes) <- substr(filenames, 1, 11)

#extract csvs from list to global env
lapply(names(dataframes), function(x) assign(x, dataframes[[x]], envir = .GlobalEnv))
rm(dataframes) #remove dataframes list

```

```{r, fig.width = 10}

# function to read files, remove top rows, paste site name
read_cals <- function(df, name){
    df <- df %>%
      slice(-c(1:9, 146:277)) %>%
      separate(Parameter, c("Parameter", "value"), sep = ",") %>%
      drop_na() %>%
      dplyr::select(-1) %>% 
      mutate(cal = name)

}

statn_all1 <- read_cals(statn_all1., name = 'statn_all1')
statn_all2 <- read_cals(statn_all2., name = 'statn_all2')
statn_all3 <- read_cals(statn_all3., name = 'statn_all3')
statn_all4 <- read_cals(statn_all4., name = 'statn_all4')
statn_all5 <- read_cals(statn_all5., name = 'statn_all5')
statn_all6 <- read_cals(statn_all6., name = 'statn_all6')
statn_all7 <- read_cals(statn_all7., name = 'statn_all7')
statn_all8 <- read_cals(statn_all8., name = 'statn_all8')
statn_all9 <- read_cals(statn_all9., name = 'statn_all9')
statn_all10 <- read_cals(statn_all10, name = 'statn_all10')
statn_all11 <- read_cals(statn_all11, name = 'statn_all11')
statn_all12 <- read_cals(statn_all12, name = 'statn_all12')

statn <- bind_rows(statn_all1, statn_all2, statn_all3, statn_all4, statn_all5,
                  statn_all6, statn_all7, statn_all8, statn_all9, statn_all10,
                  statn_all11, statn_all12) %>%
  # mutate(input_data = 'grid') %>%
  # mutate(year_missing_almost = gsub('grid_', '', cal)) %>%
  # mutate(year_missing = gsub('all', 'none', year_missing_almost)) %>%
  # dplyr::select(-c(year_missing_almost)) %>%
  rename(param = Parameter) %>%
  filter(!param == 'locGrw',
         !param == 'tempRes')

params <- statn %>%
  filter(!param %in% c('angstrom_a', 'angstrom_b', 
                      'Beta_min', 
                      'Beta_rsd', "Beta_trans", 'clat', 
                      'delayNitrification',
                      'denitrificationRateCoefficient', 
                      'denitrificationSoilSaturationThreshold',
                      'deposition_factor', 'drrad', 
                      'drspac', 'initLPS', 'initRG1',
                      'initRG2', 'Ksink', 'LExCoef', 
                      'longTZ', 'N_concRG1', 'N_concRG2', 'N_delay_RG1',
                      'N_delay_RG2', 
                      'nitrificationSoilTemperatureThreshold', 
                      'nitrificationSurfaceTemperatureThreshold',
                      'opti', 'piadin', 'rootfactor', 'sceno', 
                      'soilImpGT80', 'soilImpLT80',
                      'soilLinRed', 'soilMaxPerc', 'temp_lag')) %>%
    mutate(value = as.numeric(value),
         param = as.factor(param))

#function to plot all params
plot_params <- function(param_name) {
  params %>%
    filter(param == param_name) %>%
    ggplot(aes(x = cal,
               y = value)) + 
    geom_point(size = 3) + 
    ggtitle(param_name) +
    theme_bw()
}

name <- levels(params$param)

lapply(name, plot_params)

# boxplots
plot_params <- function(param_name) {
  # Filter the data for the specific parameter and calculate the standard deviation
  filtered_data <- params %>%
    filter(param == param_name)

  stdev_value <- sd(filtered_data$value, na.rm = TRUE)

  # Create the plot
  ggplot(filtered_data, aes(x = param, y = value)) + 
    geom_boxplot() +
    ggtitle(param_name) +
    theme_bw() +
    # Add standard deviation as text annotation
    geom_text(aes(label = paste("SD =", round(stdev_value, 2)), 
                  x = 1, 
                  y = max(filtered_data$value, na.rm = TRUE)),
              vjust = -0.5, 
              hjust = 2,
              color = "red")
}
name <- levels(params$param)

lapply(name, plot_params)

```

```{r echo = FALSE, message = FALSE, warning = FALSE, include = F}

setwd("/Users/megansears/Documents/Repos/fourmile/38HRU_sept2013_updates/cals/compare_luca_runs")

rm(list = ls())

#pull in all filenames with composite
filenames <- list.files('.', pattern=".csv", full.names=F)

#read all the csvs
dataframes <- lapply(filenames, read_csv)

#name all the csv
names(dataframes) <- substr(filenames, 1, 11)

#extract csvs from list to global env
lapply(names(dataframes), function(x) assign(x, dataframes[[x]], envir = .GlobalEnv))
rm(dataframes) #remove dataframes list

```

```{r echo = FALSE, message = FALSE, warning = FALSE}

# read in all the grid burn params
read_cals_burn <- function(df, name){
    df <- df %>%
      slice(-c(1:274)) %>%
      separate_wider_delim(Parameter, 
                       delim = ',',
                       names = c('soilID',
                                 'luca_a_rain',
                                 'luca_a_snow',
                                 'luca_soilMaxInfSummer',
                                 'luca_soilMaxDPS',
                                 'luca_lagSurfaceRunoff',
                                 'luca_soilDistMPSLPS')) %>%
      slice(-1) %>%
      dplyr::select(-1) %>% 
      mutate(cal = name)
}

statn_all1 <- read_cals_burn(statn_all1., name = 'statn_all1')
statn_all2 <- read_cals_burn(statn_all2., name = 'statn_all2')
statn_all3 <- read_cals_burn(statn_all3., name = 'statn_all3')
statn_all4 <- read_cals_burn(statn_all4., name = 'statn_all4')
statn_all5 <- read_cals_burn(statn_all5., name = 'statn_all5')
statn_all6 <- read_cals_burn(statn_all6., name = 'statn_all6')
statn_all7 <- read_cals_burn(statn_all7., name = 'statn_all7')
statn_all8 <- read_cals_burn(statn_all8., name = 'statn_all8')
statn_all9 <- read_cals_burn(statn_all9., name = 'statn_all9')
statn_all10 <- read_cals_burn(statn_all10, name = 'statn_all10')
statn_all11 <- read_cals_burn(statn_all11, name = 'statn_all11')
statn_all12 <- read_cals_burn(statn_all12, name = 'statn_all12')

burn_params <- bind_rows(statn_all1, statn_all2, statn_all3, statn_all4, statn_all5,
                  statn_all6, statn_all7, statn_all8, statn_all9, statn_all10,
                  statn_all11, statn_all12) %>%
  ungroup() %>%
  mutate(across(c(luca_a_rain:luca_soilDistMPSLPS), as.numeric)) %>%
  group_by(cal) %>%
  mutate(across(c(luca_a_rain:luca_soilDistMPSLPS), mean)) %>%
  filter(soilID == 22) %>%
  dplyr::select(-soilID) %>% 
  pivot_longer(!cal, 
               names_to = 'params',
               values_to = 'value') %>% 
  mutate(params = str_remove(params, 'luca_')) %>%
  mutate(params = as.factor(params),
         burn = 'yes')

```

## Burned scatter plots

```{r echo = FALSE, message = FALSE, warning = FALSE, fig.width = 10}

plot_burnparams <- function(param_name) {
  burn_params %>%
    filter(params == param_name) %>%
    ggplot(aes(y = value,
               x = cal)) +
    geom_point(size = 3) +
    ggtitle(param_name) +
    theme_bw()
}

name2 <- levels(burn_params$params)

lapply(name2, plot_burnparams)

# boxplots
plot_burnparams <- function(param_name) {
  # Filter the data for the specific parameter and calculate the standard deviation
  filtered_data <- burn_params %>%
    filter(params == param_name)

  stdev_value <- sd(filtered_data$value, na.rm = TRUE)

  # Create the plot
  ggplot(filtered_data, aes(x = params, y = value)) + 
    geom_boxplot() +
    ggtitle(param_name) +
    theme_bw() +
    # Add standard deviation as text annotation
    geom_text(aes(label = paste("SD =", round(stdev_value, 2)), 
                  x = 1, 
                  y = max(filtered_data$value, na.rm = TRUE)),
              vjust = -0.5, 
              hjust = 2,
              color = "red")
}

name2 <- levels(burn_params$params)

lapply(name2, plot_burnparams)

```

### 2024-08-12 compare_luca_runs.Rmd
updated total volume of water for annual and fixed rd/rg seasonal sums

@@
 ```{r, fig.width = 10}
-
 # function to read files, remove top rows, paste site name
@@
 lapply(name, plot_params)
+```
 
+## Box plots
+
+```{r, fig.width = 10}
 # boxplots
@@
 ```{r echo = FALSE, message = FALSE, warning = FALSE, fig.width = 10}
-
 plot_burnparams <- function(param_name) {
@@
 lapply(name2, plot_burnparams)
+```
 
+## Burned box plots
+
+```{r echo = FALSE, message = FALSE, warning = FALSE, fig.width = 10}
 # boxplots

### 2024-08-12 fourmile_outputs_2013edits.Rmd
updated total volume of water for annual and fixed rd/rg seasonal sums

@@
 
-## Cumulative Q
+## Cumulative volume
 
@@
   #pivot_longer(!date, names_to = 'cal_run', values_to = 'q_m3s') %>%
+  mutate(vol_m3 = q_m3s * 86400) %>% 
   group_by(cal_run, year(date)) %>%
-  mutate(cumsum = cumsum(replace_na(q_m3s, 0))) %>%
+  mutate(cumsum = cumsum(replace_na(vol_m3, 0))) %>%
   #rename(year = 4) %>%
@@
     theme_bw() +
-    labs(y = 'cumulative Q (m3s)')} %>%
+    labs(y = 'Volume (m^3)')} %>%
     ggplotly()
@@
 
+- **Different units than streamflow (cms) and volume (m3)** 
+- **All in mm**
+
 ```{r rd and rg, echo = FALSE, message = FALSE, warning = FALSE, fig.width = 14, fig.asp = 1, out.width = "100%"}
@@
   ggtitle('RD1') +
-  theme(text = element_text(size = 20))
+  theme(text = element_text(size = 20)) +
+  labs(y = 'RD1 (mm)')
 
@@
   ggtitle('RD2') +
-  theme(text = element_text(size = 20))
+  theme(text = element_text(size = 20))+
+  labs(y = 'RD2 (mm)')
 
@@
   ggtitle('RG1') +
-  theme(text = element_text(size = 20))
+  theme(text = element_text(size = 20)) +
+  labs(y = 'RG1 (mm)')
 
@@
   ggtitle('RG2') +
-  theme(text = element_text(size = 20))
+  theme(text = element_text(size = 20))+
+  labs(y = 'RG2 (mm)')
 
@@
   scale_x_date(labels = date_format("%b")) +
-  ggtitle('Cumulative RD1') +
+  ggtitle('Cumulative RD1 (mm)') +
   theme(text = element_text(size = 20))
@@
   scale_x_date(labels = date_format("%b")) +
-  ggtitle('Cumulative RD2') +
+  ggtitle('Cumulative RD2 (mm)') +
   theme(text = element_text(size = 20))
@@
   scale_x_date(labels = date_format("%b")) +
-  ggtitle('Cumulative RG1') +
+  ggtitle('Cumulative RG1 (mm)') +
   theme(text = element_text(size = 20))
@@
   scale_x_date(labels = date_format("%b")) +
-  ggtitle('Cumulative RG2') +
+  ggtitle('Cumulative RG2 (mm)') +
   theme(text = element_text(size = 20))
@@
   facet_wrap(~year + source, scales = 'free_x', ncol=2) +
-  ggtitle('Cumulative RD and RG') +
+  ggtitle('Cumulative RD and RG (mm)') +
   theme(text = element_text(size = 24))
@@
   ggtitle('Annual sum') +
-  labs(y = 'Total volume (m3)')
+  labs(y = 'mm of water')
 
@@
 flow_season <- gw %>%
-  dplyr::select(RD1cumsum, RD2cumsum, RG1cumsum, RG2cumsum, date, year, source) %>%
+  dplyr::select(catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w, date, year, source) %>%
   mutate(month = month(date)) %>%
@@
   group_by(source, year, season) %>%
-  summarize(yr_season_RD1 = max(RD1cumsum),
-            yr_season_RD2 = max(RD2cumsum),
-            yr_season_RG1 = max(RG1cumsum),
-            yr_season_RG2 = max(RG2cumsum)) %>%
-            pivot_longer(!c(year, source, season), names_to = 'flow_type', values_to = 'flow_cms')
+  mutate(yr_season_RD1 = cumsum(catchmentRD1_w),
+            yr_season_RD2 = cumsum(catchmentRD2_w),
+            yr_season_RG1 = cumsum(catchmentRG1_w),
+            yr_season_RG2 = cumsum(catchmentRG2_w)) %>%
+  summarize(sumRD1 = max(yr_season_RD1),
+            sumRD2 = max(yr_season_RD2),
+            sumRG1 = max(yr_season_RG1),
+            sumRG2 = max(yr_season_RG2)) %>%
+            pivot_longer(!c(year, source, season), names_to = 'flow_type', values_to = 'mm_water')
 
 flow_season %>%
-  ggplot(aes(x = flow_type, y = flow_cms, fill = source)) +
+  ggplot(aes(x = flow_type, y = mm_water, fill = source)) +
   geom_boxplot(position = position_dodge(1)) +
@@
   facet_wrap(~season) +
-  ggtitle('RD/RG annual sums') +
+  ggtitle('RD/RG sums (mm)') +
   theme_bw() +
@@
   theme(text = element_text(size = 20)) +
-  labs(y = 'Total flow (m3)')
+  labs(y = 'RD/RG sums (mm)')
 
 flow_season %>%
-  ggplot(aes(x = flow_type, y = flow_cms, fill = source)) +
+  ggplot(aes(x = flow_type, y = mm_water, fill = source)) +
   geom_boxplot(position = position_dodge(1)) +
@@
   theme(text = element_text(size = 20)) +
-  labs(y = 'Total flow (m3)')
+  labs(y = 'RD/RG seasonal sums (mm)')
 

### 2024-08-19 compare_luca_runs.Rmd
updating luca comparisons

@@
 
-kge <- read_csv('/Users/megansears/Documents/Repos/fourmile/38HRU_sept2013_updates/cals/compare_luca_runs/kge_compare.csv')
+kge <- read_csv('/Users/megansears/Documents/Repos/fourmile/38HRU_sept2013_updates/cals/compare_luca_runs/kge_compare.csv') %>%
+  filter(!cal == 'statn_all1')
 
@@
 
-# Parameters
+# Unburned parameters
 
@@
 
-statn_all1 <- read_cals(statn_all1., name = 'statn_all1')
+#statn_all1 <- read_cals(statn_all1., name = 'statn_all1')
 statn_all2 <- read_cals(statn_all2., name = 'statn_all2')
@@
 
-statn <- bind_rows(statn_all1, statn_all2, statn_all3, statn_all4, statn_all5,
+statn <- bind_rows(#statn_all1, 
+                   statn_all2, statn_all3, statn_all4, statn_all5,
                   statn_all6, statn_all7, statn_all8, statn_all9, statn_all10,
@@
 
+limits <- read_csv('/Users/megansears/Documents/Repos/fourmile/38HRU_sept2013_updates/cals/param_limits.csv')
+
+params_limits <- left_join(params, limits, by = 'param') %>%
+  mutate(param = as.factor(param))
+
 #function to plot all params
 plot_params <- function(param_name) {
-  params %>%
+  params_limits %>%
     filter(param == param_name) %>%
@@
                y = value)) + 
+    geom_hline(aes(yintercept = lower), color = 'red') +
+    geom_hline(aes(yintercept = upper), color = 'red') + 
     geom_point(size = 3) + 
@@
 
-name <- levels(params$param)
+name <- levels(params_limits$param)
 
 lapply(name, plot_params)
+
 ```
@@
 lapply(name, plot_params)
+
+```
+
+## Metrics
+
+```{r}
+
+params_summary <- params %>%
+  group_by(param) %>%
+  summarize(mean = mean(value),
+            sd = sd(value),
+            cv = sd(value)/mean(value),
+            min = min(value),
+            max = max(value))
+
+kable(params_summary, digits = 2) %>%
+  kable_styling(full_width = F)
 
@@
 
-statn_all1 <- read_cals_burn(statn_all1., name = 'statn_all1')
+#statn_all1 <- read_cals_burn(statn_all1., name = 'statn_all1')
 statn_all2 <- read_cals_burn(statn_all2., name = 'statn_all2')
@@
 
-burn_params <- bind_rows(statn_all1, statn_all2, statn_all3, statn_all4, statn_all5,
+burn_params <- bind_rows(#statn_all1, 
+                         statn_all2, statn_all3, statn_all4, statn_all5,
                   statn_all6, statn_all7, statn_all8, statn_all9, statn_all10,
@@
 
+# Burned parameters
+
 ## Burned scatter plots
@@
 ```{r echo = FALSE, message = FALSE, warning = FALSE, fig.width = 10}
+
+burn_limits <- read_csv('/Users/megansears/Documents/Repos/fourmile/38HRU_sept2013_updates/cals/burn_param_limits.csv')
+
+burn_params_limits <- left_join(burn_params, burn_limits, by = 'params') %>%
+  mutate(params = as.factor(params))
+
 plot_burnparams <- function(param_name) {
-  burn_params %>%
+  burn_params_limits %>%
     filter(params == param_name) %>%
@@
                x = cal)) +
+    geom_hline(aes(yintercept = lower), color = 'red') +
+    geom_hline(aes(yintercept = upper), color = 'red') + 
     geom_point(size = 3) +
@@
 
-name2 <- levels(burn_params$params)
+name2 <- levels(burn_params_limits$params)
 
 lapply(name2, plot_burnparams)
+
 ```
@@
 ```
+
+## Burned metrics
+
+```{r}
+
+burn_params_summary <- burn_params %>%
+  group_by(params) %>%
+  summarize(mean = mean(value),
+            sd = sd(value),
+            cv = sd(value)/mean(value),
+            min = min(value),
+            max = max(value))
+
+kable(burn_params_summary, digits = 2) %>%
+  kable_styling(full_width = F)
+
+```

### 2024-08-26 fourmile_outputs_2013edits.Rmd
updated folder structure and added new cals and model runs

@@
 
-The two burned HRU parameters were averaged together.
+The burned HRU parameters were averaged together.
 
@@
 ```{r hydrographs, echo = FALSE, message = FALSE, warning = FALSE}
+
 setwd('/Users/megansears/Documents/Repos/fourmile/38HRU_sept2013_updates')
@@
 
-gw_gridall <- read_csv(here('38HRU_sept2013_updates/catchment_output/grid_all.csv')) %>%
+gw_gridall <- read_csv(here('38HRU_sept2013_updates/catchment_output/grid_all.csv'), skip = 3) %>%
+  slice(-c(1,2)) %>%
   dplyr::select(time, catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w) %>%
-  mutate(source = 'grid_all')
-
-gw_statnall <- read_csv(here('38HRU_sept2013_updates/catchment_output/statn_all.csv')) %>%
+  mutate(source = 'grid_all') %>%
+  mutate(across(c(catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w), as.numeric))
+
+gw_statnall <- read_csv(here('38HRU_sept2013_updates/catchment_output/statn_all.csv'), skip = 3) %>%
+  slice(-c(1,2)) %>%
   dplyr::select(time, catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w) %>%
-  mutate(source = 'statn_all')
-
-# gw_grid2011 <- read_csv(here('38HRU_sept2013_updates/catchment_output/grid_2011.csv')) %>%
+  mutate(source = 'statn_all') %>%
+  mutate(across(c(catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w), as.numeric))
+
+# gw_grid2011 <- read_csv(here('38HRU_sept2013_updates/catchment_output/grid_2011.csv'), skip = 3) %>%
+#   slice(-c(1,2)) %>%
 #   dplyr::select(time, catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w) %>%
-#   mutate(source = 'grid_2011')
-# 
-# gw_grid2012 <- read_csv(here('38HRU_sept2013_updates/catchment_output/grid_2012.csv')) %>%
+#   mutate(source = 'grid_2011')%>%
+#   mutate(across(c(catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w), as.numeric))
+# 
+# gw_grid2012 <- read_csv(here('38HRU_sept2013_updates/catchment_output/grid_2012.csv'), skip = 3) %>%
+#   slice(-c(1,2)) %>%
 #   dplyr::select(time, catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w) %>%
-#   mutate(source = 'grid_2012')
-# 
-# gw_grid2013 <- read_csv(here('38HRU_sept2013_updates/catchment_output/grid_2013.csv')) %>%
+#   mutate(source = 'grid_2012')%>%
+#   mutate(across(c(catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w), as.numeric))
+# 
+# gw_grid2013 <- read_csv(here('38HRU_sept2013_updates/catchment_output/grid_2013.csv'), skip = 3) %>%
+#   slice(-c(1,2)) %>%
 #   dplyr::select(time, catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w) %>%
-#   mutate(source = 'grid_2013')
-# 
-# gw_grid2014 <- read_csv(here('38HRU_sept2013_updates/catchment_output/grid_2014.csv')) %>%
+#   mutate(source = 'grid_2013')%>%
+#   mutate(across(c(catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w), as.numeric))
+# 
+# gw_grid2014 <- read_csv(here('38HRU_sept2013_updates/catchment_output/grid_2014.csv'), skip = 3) %>%
+#   slice(-c(1,2)) %>%
 #   dplyr::select(time, catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w) %>%
-#   mutate(source = 'grid_2014')
-# 
-# gw_grid2015 <- read_csv(here('38HRU_sept2013_updates/catchment_output/grid_2015.csv')) %>%
+#   mutate(source = 'grid_2014')%>%
+#   mutate(across(c(catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w), as.numeric))
+# 
+# gw_grid2015 <- read_csv(here('38HRU_sept2013_updates/catchment_output/grid_2015.csv'), skip = 3) %>%
+#   slice(-c(1,2)) %>%
 #   dplyr::select(time, catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w) %>%
-#   mutate(source = 'grid_2015')
-# 
-# gw_grid2016 <- read_csv(here('38HRU_sept2013_updates/catchment_output/grid_2016.csv')) %>%
+#   mutate(source = 'grid_2015')%>%
+#   mutate(across(c(catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w), as.numeric))
+# 
+# gw_grid2016 <- read_csv(here('38HRU_sept2013_updates/catchment_output/grid_2016.csv'), skip = 3) %>%
+#   slice(-c(1,2)) %>%
 #   dplyr::select(time, catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w) %>%
-#   mutate(source = 'grid_2016')
-# 
-# gw_grid2017 <- read_csv(here('38HRU_sept2013_updates/catchment_output/grid_2017.csv')) %>%
+#   mutate(source = 'grid_2016')%>%
+#   mutate(across(c(catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w), as.numeric))
+# 
+# gw_grid2017 <- read_csv(here('38HRU_sept2013_updates/catchment_output/grid_2017.csv'), skip = 3) %>%
+#   slice(-c(1,2)) %>%
 #   dplyr::select(time, catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w) %>%
-#   mutate(source = 'grid_2017')
-# 
-# gw_grid2018 <- read_csv(here('38HRU_sept2013_updates/catchment_output/grid_2018.csv')) %>%
+#   mutate(source = 'grid_2017')%>%
+#   mutate(across(c(catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w), as.numeric))
+# 
+# gw_grid2018 <- read_csv(here('38HRU_sept2013_updates/catchment_output/grid_2018.csv'), skip = 3) %>%
+#   slice(-c(1,2)) %>%
 #   dplyr::select(time, catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w) %>%
-#   mutate(source = 'grid_2018')
-# 
-# gw_grid2019 <- read_csv(here('38HRU_sept2013_updates/catchment_output/grid_2019.csv')) %>%
+#   mutate(source = 'grid_2018')%>%
+#   mutate(across(c(catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w), as.numeric))
+# 
+# gw_grid2019 <- read_csv(here('38HRU_sept2013_updates/catchment_output/grid_2019.csv'), skip = 3) %>%
+#   slice(-c(1,2)) %>%
 #   dplyr::select(time, catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w) %>%
-#   mutate(source = 'grid_2019')
-# 
-# gw_grid2020 <- read_csv(here('38HRU_sept2013_updates/catchment_output/grid_2020.csv')) %>%
+#   mutate(source = 'grid_2019')%>%
+#   mutate(across(c(catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w), as.numeric))
+# 
+# gw_grid2020 <- read_csv(here('38HRU_sept2013_updates/catchment_output/grid_2020.csv'), skip = 3) %>%
+#   slice(-c(1,2)) %>%
 #   dplyr::select(time, catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w) %>%
-#   mutate(source = 'grid_2020')
-# 
-# gw_statn2011 <- read_csv(here('38HRU_sept2013_updates/catchment_output/statn_2011.csv')) %>%
+#   mutate(source = 'grid_2020')%>%
+#   mutate(across(c(catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w), as.numeric))
+# 
+# gw_statn2011 <- read_csv(here('38HRU_sept2013_updates/catchment_output/statn_2011.csv'), skip = 3) %>%
+#   slice(-c(1,2)) %>%
 #   dplyr::select(time, catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w) %>%
-#   mutate(source = 'statn_2011')
-# 
-# gw_statn2012 <- read_csv(here('38HRU_sept2013_updates/catchment_output/statn_2012.csv')) %>%
+#   mutate(source = 'statn_2011')%>%
+#   mutate(across(c(catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w), as.numeric))
+# 
+# gw_statn2012 <- read_csv(here('38HRU_sept2013_updates/catchment_output/statn_2012.csv'), skip = 3) %>%
+#   slice(-c(1,2)) %>%
 #   dplyr::select(time, catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w) %>%
-#   mutate(source = 'statn_2012')
-# 
-# gw_statn2013 <- read_csv(here('38HRU_sept2013_updates/catchment_output/statn_2013.csv')) %>%
+#   mutate(source = 'statn_2012')%>%
+#   mutate(across(c(catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w), as.numeric))
+# 
+# gw_statn2013 <- read_csv(here('38HRU_sept2013_updates/catchment_output/statn_2013.csv'), skip = 3) %>%
+#   slice(-c(1,2)) %>%
 #   dplyr::select(time, catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w) %>%
-#   mutate(source = 'statn_2013')
-# 
-# gw_statn2014 <- read_csv(here('38HRU_sept2013_updates/catchment_output/statn_2014.csv')) %>%
+#   mutate(source = 'statn_2013')%>%
+#   mutate(across(c(catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w), as.numeric))
+# 
+# gw_statn2014 <- read_csv(here('38HRU_sept2013_updates/catchment_output/statn_2014.csv'), skip = 3) %>%
+#   slice(-c(1,2)) %>%
 #   dplyr::select(time, catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w) %>%
-#   mutate(source = 'statn_2014')
-# 
-# gw_statn2015 <- read_csv(here('38HRU_sept2013_updates/catchment_output/statn_2015.csv')) %>%
+#   mutate(source = 'statn_2014')%>%
+#   mutate(across(c(catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w), as.numeric))
+# 
+# gw_statn2015 <- read_csv(here('38HRU_sept2013_updates/catchment_output/statn_2015.csv'), skip = 3) %>%
+#   slice(-c(1,2)) %>%
 #   dplyr::select(time, catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w) %>%
-#   mutate(source = 'statn_2015')
-# 
-# gw_statn2016 <- read_csv(here('38HRU_sept2013_updates/catchment_output/statn_2016.csv')) %>%
+#   mutate(source = 'statn_2015')%>%
+#   mutate(across(c(catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w), as.numeric))
+# 
+# gw_statn2016 <- read_csv(here('38HRU_sept2013_updates/catchment_output/statn_2016.csv'), skip = 3) %>%
+#   slice(-c(1,2)) %>%
 #   dplyr::select(time, catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w) %>%
-#   mutate(source = 'statn_2016')
-# 
-# gw_statn2017 <- read_csv(here('38HRU_sept2013_updates/catchment_output/statn_2017.csv')) %>%
+#   mutate(source = 'statn_2016')%>%
+#   mutate(across(c(catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w), as.numeric))
+# 
+# gw_statn2017 <- read_csv(here('38HRU_sept2013_updates/catchment_output/statn_2017.csv'), skip = 3) %>%
+#   slice(-c(1,2)) %>%
 #   dplyr::select(time, catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w) %>%
-#   mutate(source = 'statn_2017')
-# 
-# gw_statn2018 <- read_csv(here('38HRU_sept2013_updates/catchment_output/statn_2018.csv')) %>%
+#   mutate(source = 'statn_2017')%>%
+#   mutate(across(c(catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w), as.numeric))
+# 
+# gw_statn2018 <- read_csv(here('38HRU_sept2013_updates/catchment_output/statn_2018.csv'), skip = 3) %>%
+#   slice(-c(1,2)) %>%
 #   dplyr::select(time, catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w) %>%
-#   mutate(source = 'statn_2018')
-# 
-# gw_statn2019 <- read_csv(here('38HRU_sept2013_updates/catchment_output/statn_2019.csv')) %>%
+#   mutate(source = 'statn_2018')%>%
+#   mutate(across(c(catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w), as.numeric))
+# 
+# gw_statn2019 <- read_csv(here('38HRU_sept2013_updates/catchment_output/statn_2019.csv'), skip = 3) %>%
+#   slice(-c(1,2)) %>%
 #   dplyr::select(time, catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w) %>%
-#   mutate(source = 'statn_2019')
-# 
-# gw_statn2020 <- read_csv(here('38HRU_sept2013_updates/catchment_output/statn_2020.csv')) %>%
+#   mutate(source = 'statn_2019')%>%
+#   mutate(across(c(catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w), as.numeric))
+# 
+# gw_statn2020 <- read_csv(here('38HRU_sept2013_updates/catchment_output/statn_2020.csv'), skip = 3) %>%
+#   slice(-c(1,2)) %>%
 #   dplyr::select(time, catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w) %>%
-#   mutate(source = 'statn_2020')
+#   mutate(source = 'statn_2020')%>%
+#   mutate(across(c(catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w), as.numeric))
 
@@
 ) %>%
-  mutate(date = mdy(time),
-         year = year(date))
+  mutate(date = ymd(time),
+         year = year(date)) %>%
+  arrange(date)
 
@@
 ```{r cumulative tmean for HRUs, echo = F}
-hrus <- st_read('/Users/megansears/Documents/Repos/fourmile/38HRU_model/hrus_final.shp')
+hrus <- st_read('/Users/megansears/Documents/Repos/fourmile/38HRU_sept2013_updates/hrus_final.shp')
 
@@
 
-locations <- read_csv('/Users/megansears/Documents/Repos/fourmile/38HRU_model/fourmile_sensors.csv')
+locations <- read_csv('/Users/megansears/Documents/Repos/fourmile/38HRU_sept2013_updates/fourmile_sensors.csv')
 

### 2024-09-24 fourmile_outputs_2013edits.Rmd
adding rd and rg hru outputs

@@
 
+# HRU RD/RG
+
+```{r}
+
+elev <- read_csv('./38HRU_sept2013_updates/hru_elev.csv')
+
+rd1_grid <- hru_grids %>%
+  dplyr::select(time, outRD1, ID) %>%
+  mutate(source = 'grid') %>%
+  left_join(., elev, by = 'ID') %>%
+  arrange(time) %>%
+  mutate(year = year(time)) %>%
+  mutate(elevation_group = ntile(elevation, 4)) %>% 
+  group_by(year, elevation_group) %>%
+  mutate(rd1_summed = cumsum(outRD1))
+
+rd1_statn <- hru_statn %>%
+  dplyr::select(time, outRD1, ID) %>%
+  mutate(source = 'statn') %>% 
+  left_join(., elev, by = 'ID') %>%
+  arrange(time) %>%
+  mutate(year = year(time)) %>%
+  mutate(elevation_group = ntile(elevation, 4)) %>% 
+  group_by(year, elevation_group) %>%
+  mutate(rd1_summed = cumsum(outRD1))
+
+#rd1_hru <- bind_rows(rd1_grid, rd1_statn)
+
+library(viridis)
+
+rd1_grid_plot <- ggplot(rd1_grid, aes(x=time, y=rd1_summed, color=elevation_group)) + 
+  geom_line() +
+  scale_color_viridis_c() +  # Use a continuous viridis color palette
+  theme_bw()
+
+ggplotly(rd1_grid_plot)
+
+rd1_statn_plot <- ggplot(rd1_statn, aes(x=time, y=rd1_summed, color=elevation_group)) + 
+  geom_line() +
+  scale_color_viridis_c() +
+  theme_bw()
+
+ggplotly(rd1_statn_plot)
+
+###########################
+
+rd2_grid <- hru_grids %>%
+  dplyr::select(time, outRD2, ID) %>%
+  mutate(source = 'grid') %>%
+  left_join(., elev, by = 'ID') %>%
+  arrange(time) %>%
+  mutate(year = year(time)) %>%
+  mutate(elevation_group = ntile(elevation, 4)) %>% 
+  group_by(year, elevation_group) %>%
+  mutate(rd2_summed = cumsum(outRD2))
+
+rd2_statn <- hru_statn %>%
+  dplyr::select(time, outRD2, ID) %>%
+  mutate(source = 'statn') %>% 
+  left_join(., elev, by = 'ID') %>%
+  arrange(time) %>%
+  mutate(year = year(time)) %>%
+  mutate(elevation_group = ntile(elevation, 4)) %>% 
+  group_by(year, elevation_group) %>%
+  mutate(rd2_summed = cumsum(outRD2))
+
+rd2_grid_plot <- ggplot(rd2_grid, aes(x=time, y=rd2_summed, color=elevation_group)) + 
+  geom_line() +
+  scale_color_viridis_c() +  # Use a continuous viridis color palette
+  theme_bw()
+
+ggplotly(rd2_grid_plot)
+
+rd2_statn_plot <- ggplot(rd2_statn, aes(x=time, y=rd2_summed, color=elevation)) + 
+  geom_line() +
+  scale_color_viridis_c(option = 'mako') +
+  theme_bw()
+
+ggplotly(rd2_statn_plot)
+
+```
+
 <!-- # Join param & RD/RG -->

### 2024-09-24 spatial_figs.Rmd
minor updates

@@
 ```{r}
-grid <- read_csv("/Users/megansears/Documents/Repos/fourmile/38HRU_model/output/4milecreek38HRUs-gridall_#1/out/Catchment.csv",
+grid <- read_csv("/Users/megansears/Documents/ages-data-fourmile_creek/output/4milecreek38HRUs-gridallNA_#1/out/Catchment.csv",
                  skip=3) %>%
@@
 
-statn <- read_csv('/Users/megansears/Documents/Repos/fourmile/38HRU_model/output/4milecreek38HRUs-statnall_#1/out/Catchment.csv',
+statn <- read_csv('/Users/megansears/Documents/ages-data-fourmile_creek/output/4milecreek38HRUs-statnall_na_#1/out/Catchment.csv',
                  skip=3) %>%
@@
 ```
+
+# Obs hydrograph
+
+```{r}
+
+setwd('/Users/megansears/Documents/Repos/fourmile/38HRU_sept2013_updates')
+
+flow <- read_csv('discharge_all.csv') %>%
+  replace(.==-9999, NA) %>%
+  rename(date = time) %>%
+  mutate(date = mdy(date)) %>%
+  dplyr::select(date, obs) %>%
+  mutate(year = year(date),
+         DOY = yday(date)) %>%
+  drop_na(obs)
+
+library(viridis)
+
+ggplot(flow, aes(x = DOY, y = obs, color = as.factor(year))) + 
+  geom_line(size = 1.1) +
+  theme_bw(base_size = 20) +
+  labs(y = 'Discharge (cms)', color = 'Year') +
+  scale_color_viridis_d(option = "turbo")
+
+ggsave("./figures/flow_obs_plot.png", dpi = 600)
+
+summary(flow)
+
+```

### 2024-10-04 fourmile_outputs_2013edits.Rmd
added hru climate outputs and hru rd/rg

--- 2024-08-26 fourmile_outputs_2013edits.Rmd
@@
 
+############################
+### look at month
+#get rid of a bunch of data
+hru_grid_tmean_jan <- hru_grids %>%
+  dplyr::select(c(time, ID, tmean)) %>%
+  rename(tmean_grid = tmean)  %>%
+  mutate(month = month(time)) %>%
+  filter(month %in% c(12,1,2,3)) %>%
+  group_by(ID) %>%
+  summarize(tmean_all_grid = mean(tmean_grid))
+
+hru_statn_tmean_jan <- hru_statn %>%
+  dplyr::select(c(time, ID, tmean)) %>%
+  rename(tmean_statn = tmean) %>%
+  mutate(month = month(time)) %>%
+  filter(month %in% c(12,1,2,3)) %>%
+  group_by(ID) %>%
+  summarize(tmean_all_statn = mean(tmean_statn))
+
+tmean_hrus_jan <- left_join(hru_grid_tmean_jan, hru_statn_tmean_jan, by = c('ID')) %>%
+  mutate(diff = tmean_all_statn - tmean_all_grid) %>%
+  rename(value = ID)
+
+hrus_map_tmean_jan <- left_join(hrus, tmean_hrus_jan, by = 'value')
+
+tmean_jan <- ggplot() +
+  geom_sf(data = hrus_map_tmean_jan, aes(fill = diff), color = "black", lwd = 0.2) +
+  scale_fill_viridis_c(option = "plasma", name = "Tmean difference (°C)",
+                       limits = c(-5, 3)) +
+  theme_bw(base_size=13.5) +
+  theme_void() +
+  theme(
+    legend.position = "bottom",
+    panel.grid.major = element_blank(),
+    panel.grid.minor = element_blank(),
+    axis.title.x = element_blank(),
+    axis.title.y = element_blank()) +
+  ggtitle('Winter')
+
+#tmean_jan
+
+## 
+hru_grid_tmean_apr <- hru_grids %>%
+  dplyr::select(c(time, ID, tmean)) %>%
+  rename(tmean_grid = tmean)  %>%
+  mutate(month = month(time)) %>%
+  filter(month %in% c(4,5,6)) %>%
+  group_by(ID) %>%
+  summarize(tmean_all_grid = mean(tmean_grid))
+
+hru_statn_tmean_apr <- hru_statn %>%
+  dplyr::select(c(time, ID, tmean)) %>%
+  rename(tmean_statn = tmean) %>%
+  mutate(month = month(time)) %>%
+  filter(month %in% c(4,5,6)) %>%
+  group_by(ID) %>%
+  summarize(tmean_all_statn = mean(tmean_statn))
+
+tmean_hrus_apr <- left_join(hru_grid_tmean_apr, hru_statn_tmean_apr, by = c('ID')) %>%
+  mutate(diff = tmean_all_statn - tmean_all_grid) %>%
+  rename(value = ID)
+
+hrus_map_tmean_apr <- left_join(hrus, tmean_hrus_apr, by = 'value')
+
+tmean_apr <- ggplot() +
+  geom_sf(data = hrus_map_tmean_apr, aes(fill = diff), color = "black", lwd = 0.2) +
+  scale_fill_viridis_c(option = "plasma", name = "Tmean difference (°C)",
+                       limits = c(-5, 3)) +
+  theme_bw(base_size=13.5) +
+  theme_void() +
+  theme(
+    legend.position = "bottom",
+    panel.grid.major = element_blank(),
+    panel.grid.minor = element_blank(),
+    axis.title.x = element_blank(),
+    axis.title.y = element_blank()) +
+  ggtitle('Snowmelt')
+
+#tmean_apr
+
+#### 
+hru_grid_tmean_jul <- hru_grids %>%
+  dplyr::select(c(time, ID, tmean)) %>%
+  rename(tmean_grid = tmean)  %>%
+  mutate(month = month(time)) %>%
+  filter(month %in% c(7,8)) %>%
+  group_by(ID) %>%
+  summarize(tmean_all_grid = mean(tmean_grid))
+
+hru_statn_tmean_jul <- hru_statn %>%
+  dplyr::select(c(time, ID, tmean)) %>%
+  rename(tmean_statn = tmean) %>%
+  mutate(month = month(time)) %>%
+  filter(month %in% c(7,8)) %>%
+  group_by(ID) %>%
+  summarize(tmean_all_statn = mean(tmean_statn))
+
+tmean_hrus_jul <- left_join(hru_grid_tmean_jul, hru_statn_tmean_jul, by = c('ID')) %>%
+  mutate(diff = tmean_all_statn - tmean_all_grid) %>%
+  rename(value = ID)
+
+hrus_map_tmean_jul <- left_join(hrus, tmean_hrus_jul, by = 'value')
+
+tmean_jul <- ggplot() +
+  geom_sf(data = hrus_map_tmean_jul, aes(fill = diff), color = "black", lwd = 0.2) +
+  scale_fill_viridis_c(option = "plasma", name = "Tmean difference (°C)",
+                            limits = c(-5, 3)) +
+  theme_bw(base_size=13.5) +
+  theme_void() +
+  theme(
+    legend.position = "bottom",
+    panel.grid.major = element_blank(),
+    panel.grid.minor = element_blank(),
+    axis.title.x = element_blank(),
+    axis.title.y = element_blank()) +
+  ggtitle('Monsoon')
+
+#tmean_jul
+
+##
+
+hru_grid_tmean_sep <- hru_grids %>%
+  dplyr::select(c(time, ID, tmean)) %>%
+  rename(tmean_grid = tmean)  %>%
+  mutate(month = month(time)) %>%
+  filter(month %in% c(9,10,11)) %>%
+  group_by(ID) %>%
+  summarize(tmean_all_grid = mean(tmean_grid))
+
+hru_statn_tmean_sep <- hru_statn %>%
+  dplyr::select(c(time, ID, tmean)) %>%
+  rename(tmean_statn = tmean) %>%
+  mutate(month = month(time)) %>%
+  filter(month %in% c(9,10,11)) %>%
+  group_by(ID) %>%
+  summarize(tmean_all_statn = mean(tmean_statn))
+
+tmean_hrus_sep <- left_join(hru_grid_tmean_sep, hru_statn_tmean_sep, by = c('ID')) %>%
+  mutate(diff = tmean_all_statn - tmean_all_grid) %>%
+  rename(value = ID)
+
+hrus_map_tmean_sep <- left_join(hrus, tmean_hrus_sep, by = 'value')
+
+tmean_sep <- ggplot() +
+  geom_sf(data = hrus_map_tmean_sep, aes(fill = diff), color = "black", lwd = 0.2) +
+  scale_fill_viridis_c(option = "plasma", name = "Tmean difference (°C)",
+                       limits = c(-5, 3)) +
+  theme_bw(base_size=13.5) +
+  theme_void() +
+  theme(
+    legend.position = "bottom",
+    panel.grid.major = element_blank(),
+    panel.grid.minor = element_blank(),
+    axis.title.x = element_blank(),
+    axis.title.y = element_blank()) +
+  ggtitle('Fall')
+
+#tmean_sep
+###
+
+lots <- ggarrange(tmean_jan,
+                  tmean_apr,
+                  tmean_jul,
+                  tmean_sep) 
+          #nrow = 4)
+          #ncol= 0)
+lots
+
 ```
@@
 precip
+
+#################
+# winter p
+hru_grid_precip <- hru_grids %>%
+  dplyr::select(c(time, ID, precip)) %>%
+  rename(precip_grid = precip)
+
+hru_statn_precip <- hru_statn %>%
+  dplyr::select(c(time, ID, precip)) %>%
+  rename(precip_statn = precip)
+
+precip_hrus_jan <- left_join(hru_grid_precip, hru_statn_precip, by = c('time', 'ID')) %>%
+  mutate(month = month(time)) %>%
+  filter(month %in% c(1,2,3)) %>% 
+  mutate(diff = precip_statn - precip_grid,
+         year = year(time)) %>%
+  group_by(year, ID) %>%
+  mutate(total_diff = cumsum(diff)) %>%
+  filter(time == max(time)) %>%
+  group_by(ID) %>%
+  summarize(precip_avg_cumdiff = mean(total_diff)) %>%
+  rename(value = ID)
+
+hrus_map_precip_jan <- left_join(hrus, precip_hrus_jan, by = 'value')
+
+precip_jan <- ggplot() +
+  geom_sf(data = hrus_map_precip_jan, aes(fill = precip_avg_cumdiff), color = "black", lwd = 0.2) +
+  scale_fill_viridis_c(option = "mako", name = "Cumulative P Difference (mm)",
+                       limits = c(-51, 7.5)) +
+  theme_bw(base_size=13.5) +
+  theme_void() +
+  theme(
+    legend.position = "bottom",
+    panel.grid.major = element_blank(),
+    panel.grid.minor = element_blank(),
+    axis.title.x = element_blank(),
+    axis.title.y = element_blank()) +
+  ggtitle('Winter')
+
+##
+precip_hrus_apr <- left_join(hru_grid_precip, hru_statn_precip, by = c('time', 'ID')) %>%
+  mutate(month = month(time)) %>%
+  filter(month %in% c(4,5,6)) %>% 
+  mutate(diff = precip_statn - precip_grid,
+         year = year(time)) %>%
+  group_by(year, ID) %>%
+  mutate(total_diff = cumsum(diff)) %>%
+  filter(time == max(time)) %>%
+  group_by(ID) %>%
+  summarize(precip_avg_cumdiff = mean(total_diff)) %>%
+  rename(value = ID)
+
+hrus_map_precip_apr <- left_join(hrus, precip_hrus_apr, by = 'value')
+
+precip_apr <- ggplot() +
+  geom_sf(data = hrus_map_precip_apr, aes(fill = precip_avg_cumdiff), color = "black", lwd = 0.2) +
+  scale_fill_viridis_c(option = "mako", name = "Cumulative P Difference (mm)",
+                       limits = c(-51, 7.5)) +
+  theme_bw(base_size=13.5) +
+  theme_void() +
+  theme(
+    legend.position = "bottom",
+    panel.grid.major = element_blank(),
+    panel.grid.minor = element_blank(),
+    axis.title.x = element_blank(),
+    axis.title.y = element_blank()) +
+  ggtitle('Snowmelt')
+##
+
+precip_hrus_jul <- left_join(hru_grid_precip, hru_statn_precip, by = c('time', 'ID')) %>%
+  mutate(month = month(time)) %>%
+  filter(month %in% c(7,8)) %>% 
+  mutate(diff = precip_statn - precip_grid,
+         year = year(time)) %>%
+  group_by(year, ID) %>%
+  mutate(total_diff = cumsum(diff)) %>%
+  filter(time == max(time)) %>%
+  group_by(ID) %>%
+  summarize(precip_avg_cumdiff = mean(total_diff)) %>%
+  rename(value = ID)
+
+hrus_map_precip_jul <- left_join(hrus, precip_hrus_jul, by = 'value')
+
+precip_jul <- ggplot() +
+  geom_sf(data = hrus_map_precip_jul, aes(fill = precip_avg_cumdiff), color = "black", lwd = 0.2) +
+  scale_fill_viridis_c(option = "mako", name = "Cumulative P Difference (mm)",
+                       limits = c(-51, 7.5)) +
+  theme_bw(base_size=13.5) +
+  theme_void() +
+  theme(
+    legend.position = "bottom",
+    panel.grid.major = element_blank(),
+    panel.grid.minor = element_blank(),
+    axis.title.x = element_blank(),
+    axis.title.y = element_blank()) +
+  ggtitle('Monsoon')
+
+## 
+precip_hrus_sep <- left_join(hru_grid_precip, hru_statn_precip, by = c('time', 'ID')) %>%
+  mutate(month = month(time)) %>%
+  filter(month %in% c(9,10,11)) %>% 
+  mutate(diff = precip_statn - precip_grid,
+         year = year(time)) %>%
+  group_by(year, ID) %>%
+  mutate(total_diff = cumsum(diff)) %>%
+  filter(time == max(time)) %>%
+  group_by(ID) %>%
+  summarize(precip_avg_cumdiff = mean(total_diff)) %>%
+  rename(value = ID)
+
+hrus_map_precip_sep <- left_join(hrus, precip_hrus_sep, by = 'value')
+
+precip_sep <- ggplot() +
+  geom_sf(data = hrus_map_precip_sep, aes(fill = precip_avg_cumdiff), color = "black", lwd = 0.2) +
+  scale_fill_viridis_c(option = "mako", name = "Cumulative P Difference (mm)",
+                       limits = c(-51, 7.5)) +
+  theme_bw(base_size=13.5) +
+  theme_void() +
+  theme(
+    legend.position = "bottom",
+    panel.grid.major = element_blank(),
+    panel.grid.minor = element_blank(),
+    axis.title.x = element_blank(),
+    axis.title.y = element_blank()) +
+  ggtitle('Fall')
+
+lots <- ggarrange(precip_jan,
+                  precip_apr,
+                  precip_jul,
+                  precip_sep) 
+          #nrow = 4)
+          #ncol= 0)
+lots
 
@@
 
+##########
+### look at month
+#get rid of a bunch of data
+hru_grid_solrad_jan <- hru_grids %>%
+  dplyr::select(c(time, ID, solrad_grid=solRad)) %>%
+  mutate(month = month(time)) %>%
+  filter(month %in% c(12,1,2,3)) %>%
+  group_by(ID) %>%
+  summarize(solrad_all_grid = mean(solrad_grid))
+
+hru_statn_solrad_jan <- hru_statn %>%
+  dplyr::select(c(time, ID, solrad_statn=solRad)) %>%
+  mutate(month = month(time)) %>%
+  filter(month %in% c(12,1,2,3)) %>%
+  group_by(ID) %>%
+  summarize(solrad_all_statn = mean(solrad_statn))
+
+solrad_hrus_jan <- left_join(hru_grid_solrad_jan, hru_statn_solrad_jan, by = c('ID')) %>%
+  mutate(diff = solrad_all_statn - solrad_all_grid) %>%
+  rename(value = ID)
+
+hrus_map_solrad_jan <- left_join(hrus, solrad_hrus_jan, by = 'value')
+
+solrad_jan <- ggplot() +
+  geom_sf(data = hrus_map_solrad_jan, aes(fill = diff), color = "black", lwd = 0.2) +
+  scale_fill_viridis_c(option = "cividis", name = expression("Solar rad difference (MJ/m"^"2" * ")"),
+                       limits = c(-8.5, 1.5)) +
+  theme_bw(base_size=13.5) +
+  theme_void() +
+  theme(
+    legend.position = "bottom",
+    panel.grid.major = element_blank(),
+    panel.grid.minor = element_blank(),
+    axis.title.x = element_blank(),
+    axis.title.y = element_blank()) +
+  ggtitle('Winter')
+
+#solrad_jan
+
+## 
+hru_grid_solrad_apr <- hru_grids %>%
+  dplyr::select(c(time, ID, solrad_grid=solRad)) %>%
+  mutate(month = month(time)) %>%
+  filter(month %in% c(4,5,6)) %>%
+  group_by(ID) %>%
+  summarize(solrad_all_grid = mean(solrad_grid))
+
+hru_statn_solrad_apr <- hru_statn %>%
+  dplyr::select(c(time, ID, solrad_statn=solRad)) %>%
+  mutate(month = month(time)) %>%
+  filter(month %in% c(4,5,6)) %>%
+  group_by(ID) %>%
+  summarize(solrad_all_statn = mean(solrad_statn))
+
+solrad_hrus_apr <- left_join(hru_grid_solrad_apr, hru_statn_solrad_apr, by = c('ID')) %>%
+  mutate(diff = solrad_all_statn - solrad_all_grid) %>%
+  rename(value = ID)
+
+hrus_map_solrad_apr <- left_join(hrus, solrad_hrus_apr, by = 'value')
+
+solrad_apr <- ggplot() +
+  geom_sf(data = hrus_map_solrad_apr, aes(fill = diff), color = "black", lwd = 0.2) +
+  scale_fill_viridis_c(option = "cividis", name = expression("Solar rad difference (MJ/m"^"2" * ")"),
+                       limits = c(-8.5, 1.5)) +
+  theme_bw(base_size=13.5) +
+  theme_void() +
+  theme(
+    legend.position = "bottom",
+    panel.grid.major = element_blank(),
+    panel.grid.minor = element_blank(),
+    axis.title.x = element_blank(),
+    axis.title.y = element_blank()) +
+  ggtitle('Snowmelt')
+
+#solrad_apr
+
+#### 
+hru_grid_solrad_jul <- hru_grids %>%
+  dplyr::select(c(time, ID, solrad_grid=solRad)) %>%
+  mutate(month = month(time)) %>%
+  filter(month %in% c(7,8)) %>%
+  group_by(ID) %>%
+  summarize(solrad_all_grid = mean(solrad_grid))
+
+hru_statn_solrad_jul <- hru_statn %>%
+  dplyr::select(c(time, ID, solrad_statn=solRad)) %>%
+  mutate(month = month(time)) %>%
+  filter(month %in% c(7,8)) %>%
+  group_by(ID) %>%
+  summarize(solrad_all_statn = mean(solrad_statn))
+
+solrad_hrus_jul <- left_join(hru_grid_solrad_jul, hru_statn_solrad_jul, by = c('ID')) %>%
+  mutate(diff = solrad_all_statn - solrad_all_grid) %>%
+  rename(value = ID)
+
+hrus_map_solrad_jul <- left_join(hrus, solrad_hrus_jul, by = 'value')
+
+solrad_jul <- ggplot() +
+  geom_sf(data = hrus_map_solrad_jul, aes(fill = diff), color = "black", lwd = 0.2) +
+  scale_fill_viridis_c(option = "cividis", name = expression("Solar rad difference (MJ/m"^"2" * ")"),
+                       limits = c(-8.5, 1.5)) +
+  theme_bw(base_size=13.5) +
+  theme_void() +
+  theme(
+    legend.position = "bottom",
+    panel.grid.major = element_blank(),
+    panel.grid.minor = element_blank(),
+    axis.title.x = element_blank(),
+    axis.title.y = element_blank()) +
+  ggtitle('Monsoon')
+
+#solrad_jul
+
+##
+hru_grid_solrad_sep <- hru_grids %>%
+  dplyr::select(c(time, ID, solrad_grid=solRad)) %>%
+  mutate(month = month(time)) %>%
+  filter(month %in% c(9,10,11)) %>%
+  group_by(ID) %>%
+  summarize(solrad_all_grid = mean(solrad_grid))
+
+hru_statn_solrad_sep <- hru_statn %>%
+  dplyr::select(c(time, ID, solrad_statn=solRad)) %>%
+  mutate(month = month(time)) %>%
+  filter(month %in% c(9,10,11)) %>%
+  group_by(ID) %>%
+  summarize(solrad_all_statn = mean(solrad_statn))
+
+solrad_hrus_sep <- left_join(hru_grid_solrad_sep, hru_statn_solrad_sep, by = c('ID')) %>%
+  mutate(diff = solrad_all_statn - solrad_all_grid) %>%
+  rename(value = ID)
+
+hrus_map_solrad_sep <- left_join(hrus, solrad_hrus_sep, by = 'value')
+
+solrad_sep <- ggplot() +
+  geom_sf(data = hrus_map_solrad_sep, aes(fill = diff), color = "black", lwd = 0.2) +
+  scale_fill_viridis_c(option = "cividis", name = expression("Solar rad difference (MJ/m"^"2" * ")"),
+                       limits = c(-8.5, 1.5)) +
+  theme_bw(base_size=13.5) +
+  theme_void() +
+  theme(
+    legend.position = "bottom",
+    panel.grid.major = element_blank(),
+    panel.grid.minor = element_blank(),
+    axis.title.x = element_blank(),
+    axis.title.y = element_blank()) +
+  ggtitle('Fall')
+
+###
+
+lots <- ggarrange(solrad_jan,
+                  solrad_apr,
+                  solrad_jul,
+                  solrad_sep) 
+          #nrow = 4)
+          #ncol= 0)
+lots
+
 ```
@@
 rh
+#####
+
+hru_grid_rh_jan <- hru_grids %>%
+  dplyr::select(c(time, ID, rh_grid=rhum)) %>%
+  mutate(month = month(time)) %>%
+  filter(month %in% c(12,1,2,3)) %>%
+  group_by(ID) %>%
+  summarize(rh_all_grid = mean(rh_grid))
+
+hru_statn_rh_jan <- hru_statn %>%
+  dplyr::select(c(time, ID, rh_statn=rhum)) %>%
+  mutate(month = month(time)) %>%
+  filter(month %in% c(12,1,2,3)) %>%
+  group_by(ID) %>%
+  summarize(rh_all_statn = mean(rh_statn))
+
+rh_hrus_jan <- left_join(hru_grid_rh_jan, hru_statn_rh_jan, by = c('ID')) %>%
+  mutate(diff = rh_all_statn - rh_all_grid) %>%
+  rename(value = ID)
+
+hrus_map_rh_jan <- left_join(hrus, rh_hrus_jan, by = 'value')
+
+rh_jan <- ggplot() +
+  geom_sf(data = hrus_map_rh_jan, aes(fill = diff), color = "black", lwd = 0.2) +
+  scale_fill_viridis_c(option = "viridis", name = "RH difference (%)",
+                       limits = c(-3, 10)) +
+  theme_bw(base_size=13.5) +
+  theme_void() +
+  theme(
+    legend.position = "bottom",
+    panel.grid.major = element_blank(),
+    panel.grid.minor = element_blank(),
+    axis.title.x = element_blank(),
+    axis.title.y = element_blank()) +
+  ggtitle('Winter')
+
+##
+hru_grid_rh_apr <- hru_grids %>%
+  dplyr::select(c(time, ID, rh_grid=rhum)) %>%
+  mutate(month = month(time)) %>%
+  filter(month %in% c(4,5,6)) %>%
+  group_by(ID) %>%
+  summarize(rh_all_grid = mean(rh_grid))
+
+hru_statn_rh_apr <- hru_statn %>%
+  dplyr::select(c(time, ID, rh_statn=rhum)) %>%
+  mutate(month = month(time)) %>%
+  filter(month %in% c(4,5,6)) %>%
+  group_by(ID) %>%
+  summarize(rh_all_statn = mean(rh_statn))
+
+rh_hrus_apr <- left_join(hru_grid_rh_apr, hru_statn_rh_apr, by = c('ID')) %>%
+  mutate(diff = rh_all_statn - rh_all_grid) %>%
+  rename(value = ID)
+
+hrus_map_rh_apr <- left_join(hrus, rh_hrus_apr, by = 'value')
+
+rh_apr <- ggplot() +
+  geom_sf(data = hrus_map_rh_apr, aes(fill = diff), color = "black", lwd = 0.2) +
+  scale_fill_viridis_c(option = "viridis", name = "RH difference (%)",
+                       limits = c(-3, 10)) +
+  theme_bw(base_size=13.5) +
+  theme_void() +
+  theme(
+    legend.position = "bottom",
+    panel.grid.major = element_blank(),
+    panel.grid.minor = element_blank(),
+    axis.title.x = element_blank(),
+    axis.title.y = element_blank()) +
+  ggtitle('Snowmelt')
+
+##
+hru_grid_rh_jul <- hru_grids %>%
+  dplyr::select(c(time, ID, rh_grid=rhum)) %>%
+  mutate(month = month(time)) %>%
+  filter(month %in% c(7,8)) %>%
+  group_by(ID) %>%
+  summarize(rh_all_grid = mean(rh_grid))
+
+hru_statn_rh_jul <- hru_statn %>%
+  dplyr::select(c(time, ID, rh_statn=rhum)) %>%
+  mutate(month = month(time)) %>%
+  filter(month %in% c(7,8)) %>%
+  group_by(ID) %>%
+  summarize(rh_all_statn = mean(rh_statn))
+
+rh_hrus_jul <- left_join(hru_grid_rh_jul, hru_statn_rh_jul, by = c('ID')) %>%
+  mutate(diff = rh_all_statn - rh_all_grid) %>%
+  rename(value = ID)
+
+hrus_map_rh_jul <- left_join(hrus, rh_hrus_jul, by = 'value')
+
+rh_jul <- ggplot() +
+  geom_sf(data = hrus_map_rh_jul, aes(fill = diff), color = "black", lwd = 0.2) +
+  scale_fill_viridis_c(option = "viridis", name = "RH difference (%)",
+                       limits = c(-3,10)) +
+  theme_bw(base_size=13.5) +
+  theme_void() +
+  theme(
+    legend.position = "bottom",
+    panel.grid.major = element_blank(),
+    panel.grid.minor = element_blank(),
+    axis.title.x = element_blank(),
+    axis.title.y = element_blank()) +
+  ggtitle('Monsoon')
+
+##
+hru_grid_rh_sep <- hru_grids %>%
+  dplyr::select(c(time, ID, rh_grid=rhum)) %>%
+  mutate(month = month(time)) %>%
+  filter(month %in% c(9,10,10)) %>%
+  group_by(ID) %>%
+  summarize(rh_all_grid = mean(rh_grid))
+
+hru_statn_rh_sep <- hru_statn %>%
+  dplyr::select(c(time, ID, rh_statn=rhum)) %>%
+  mutate(month = month(time)) %>%
+  filter(month %in% c(9,10,10)) %>%
+  group_by(ID) %>%
+  summarize(rh_all_statn = mean(rh_statn))
+
+rh_hrus_sep <- left_join(hru_grid_rh_sep, hru_statn_rh_sep, by = c('ID')) %>%
+  mutate(diff = rh_all_statn - rh_all_grid) %>%
+  rename(value = ID)
+
+hrus_map_rh_sep <- left_join(hrus, rh_hrus_sep, by = 'value')
+
+rh_sep <- ggplot() +
+  geom_sf(data = hrus_map_rh_sep, aes(fill = diff), color = "black", lwd = 0.2) +
+  scale_fill_viridis_c(option = "viridis", name = "RH difference (%)",
+                       limits = c(-3,10)) +
+  theme_bw(base_size=13.5) +
+  theme_void() +
+  theme(
+    legend.position = "bottom",
+    panel.grid.major = element_blank(),
+    panel.grid.minor = element_blank(),
+    axis.title.x = element_blank(),
+    axis.title.y = element_blank()) +
+  ggtitle('Fall')
+
+lots <- ggarrange(rh_jan,
+                  rh_apr,
+                  rh_jul,
+                  rh_sep) 
+          #nrow = 4)
+          #ncol= 0)
+lots
 
@@
 
+# HRU RD/RG
+
+Group 1 is lowest elevation, 4 is highest elevation
+
+```{r}
+
+setwd("~/Documents/Repos/fourmile")
+
+elev <- read_csv('./38HRU_sept2013_updates/hru_elev.csv') %>%
+  mutate(elevation_group = ntile(elevation, 4))
+
+rd1_grid <- hru_grids %>%
+  dplyr::select(time, outRD1, ID) %>%
+  mutate(source = 'grid') %>%
+  left_join(., elev, by = 'ID') %>%
+  arrange(time) %>%
+  mutate(year = year(time)) %>%
+  group_by(year, elevation_group) %>%
+  mutate(rd1_summed = cumsum(outRD1)) %>%
+  group_by(year, elevation_group) %>%
+  summarise(max_rd1_summed = max(rd1_summed)) %>%
+  mutate(type = 'grid')
+
+rd1_statn <- hru_statn %>%
+  dplyr::select(time, outRD1, ID) %>%
+  mutate(source = 'statn') %>% 
+  left_join(., elev, by = 'ID') %>%
+  arrange(time) %>%
+  mutate(year = year(time)) %>%
+  group_by(year, elevation_group) %>%
+  mutate(rd1_summed = cumsum(outRD1)) %>%
+  group_by(year, elevation_group) %>%
+  summarise(max_rd1_summed = max(rd1_summed)) %>%
+  mutate(type = 'statn')
+
+rd1_hru <- bind_rows(rd1_grid, rd1_statn)
+
+# elevation group area
+elev_area <- elev %>%
+  group_by(elevation_group) %>%
+  summarize(group_area = sum(area))
+
+rd1_hru <- left_join(rd1_hru, elev_area, by = 'elevation_group') %>%
+  mutate(RD1_mm_year = (max_rd1_summed/group_area)*1000)
+
+library(viridis)
+
+rd1_plot <- ggplot(rd1_hru, aes(x=as.factor(year), y=RD1_mm_year, 
+                                      color=as.factor(elevation_group),
+                                      shape = type)) + 
+  geom_point(size = 3) +
+  #scale_color_viridis_d() +
+  theme_bw() +
+  labs(x = 'Year',
+       y = 'Total RD1 (mm/year)')
+
+ggplotly(rd1_plot)
+
+###########################
+
+rd2_grid <- hru_grids %>%
+  dplyr::select(time, outRD2, ID) %>%
+  mutate(source = 'grid') %>%
+  left_join(., elev, by = 'ID') %>%
+  arrange(time) %>%
+  mutate(year = year(time)) %>%
+  group_by(year, elevation_group) %>%
+  mutate(rd2_summed = cumsum(outRD2)) %>%
+  group_by(year, elevation_group) %>%
+  summarise(max_rd2_summed = max(rd2_summed)) %>%
+  mutate(type = 'grid')
+
+rd2_statn <- hru_statn %>%
+  dplyr::select(time, outRD2, ID) %>%
+  mutate(source = 'statn') %>% 
+  left_join(., elev, by = 'ID') %>%
+  arrange(time) %>%
+  mutate(year = year(time)) %>%
+  group_by(year, elevation_group) %>%
+  mutate(rd2_summed = cumsum(outRD2)) %>%
+  group_by(year, elevation_group) %>%
+  summarise(max_rd2_summed = max(rd2_summed)) %>%
+  mutate(type = 'statn')
+
+rd2_hru <- bind_rows(rd2_grid, rd2_statn)
+
+rd2_hru <- left_join(rd2_hru, elev_area, by = 'elevation_group') %>%
+  mutate(rd2_mm_year = (max_rd2_summed/group_area)*1000)
+
+rd2_plot <- ggplot(rd2_hru, aes(x=as.factor(year), y=rd2_mm_year, 
+                                      color=as.factor(elevation_group),
+                                      shape = type)) + 
+  geom_point(size = 3) +
+  #scale_color_viridis_d() +
+  theme_bw() +
+  labs(x = 'Year',
+       y = 'Total RD2 (mm/year)')
+
+ggplotly(rd2_plot)
+
+###########
+
+# RG1
+rg1_grid <- hru_grids %>%
+  dplyr::select(time, outRG1, ID) %>%
+  mutate(source = 'grid') %>%
+  left_join(., elev, by = 'ID') %>%
+  arrange(time) %>%
+  mutate(year = year(time)) %>%
+  group_by(year, elevation_group) %>%
+  mutate(rg1_summed = cumsum(outRG1)) %>%
+  group_by(year, elevation_group) %>%
+  summarise(max_rg1_summed = max(rg1_summed)) %>%
+  mutate(type = 'grid')
+
+rg1_statn <- hru_statn %>%
+  dplyr::select(time, outRG1, ID) %>%
+  mutate(source = 'statn') %>% 
+  left_join(., elev, by = 'ID') %>%
+  arrange(time) %>%
+  mutate(year = year(time)) %>%
+  group_by(year, elevation_group) %>%
+  mutate(rg1_summed = cumsum(outRG1)) %>%
+  group_by(year, elevation_group) %>%
+  summarise(max_rg1_summed = max(rg1_summed)) %>%
+  mutate(type = 'statn')
+
+rg1_hru <- bind_rows(rg1_grid, rg1_statn)
+
+rg1_hru <- left_join(rg1_hru, elev_area, by = 'elevation_group') %>%
+  mutate(rg1_mm_year = (max_rg1_summed/group_area)*1000)
+
+rg1_plot <- ggplot(rg1_hru, aes(x=as.factor(year), y=rg1_mm_year, 
+                                      color=as.factor(elevation_group),
+                                      shape = type)) + 
+  geom_point(size = 3) +
+  #scale_color_viridis_d() +
+  theme_bw() +
+  labs(x = 'Year',
+       y = 'Total RG1 (mm/year)')
+
+ggplotly(rg1_plot)
+
+#######
+
+# rg2
+rg2_grid <- hru_grids %>%
+  dplyr::select(time, outRG2, ID) %>%
+  mutate(source = 'grid') %>%
+  left_join(., elev, by = 'ID') %>%
+  arrange(time) %>%
+  mutate(year = year(time)) %>%
+  group_by(year, elevation_group) %>%
+  mutate(rg2_summed = cumsum(outRG2)) %>%
+  group_by(year, elevation_group) %>%
+  summarise(max_rg2_summed = max(rg2_summed)) %>%
+  mutate(type = 'grid')
+
+rg2_statn <- hru_statn %>%
+  dplyr::select(time, outRG2, ID) %>%
+  mutate(source = 'statn') %>% 
+  left_join(., elev, by = 'ID') %>%
+  arrange(time) %>%
+  mutate(year = year(time)) %>%
+  group_by(year, elevation_group) %>%
+  mutate(rg2_summed = cumsum(outRG2)) %>%
+  group_by(year, elevation_group) %>%
+  summarise(max_rg2_summed = max(rg2_summed)) %>%
+  mutate(type = 'statn')
+
+rg2_hru <- bind_rows(rg2_grid, rg2_statn)
+
+rg2_hru <- left_join(rg2_hru, elev_area, by = 'elevation_group') %>%
+  mutate(rg2_mm_year = (max_rg2_summed/group_area)*1000)
+
+rg2_plot <- ggplot(rg2_hru, aes(x=as.factor(year), y=rg2_mm_year, 
+                                      color=as.factor(elevation_group),
+                                      shape = type)) + 
+  geom_point(size = 3) +
+  #scale_color_viridis_d() +
+  theme_bw() +
+  labs(x = 'Year',
+       y = 'Total RG2 (mm/year)')
+
+ggplotly(rg2_plot)
+
+```
+
 <!-- # Join param & RD/RG -->

### 2024-10-08 fourmile_outputs_2013edits.Rmd
hru updates

@@
 ```{r}
-
 #get rid of a bunch of data
@@
 
+```
+
+### Tmean season
+
+- Dec-Mar: Winter
+- Apr-Jun: Snowmelt/spring
+- Jul-Aug: Monsoon
+- Sep-Nov: Baseflow/fall
+
+```{r}
 ############################
@@
 
+### Tmax season
+
+- Dec-Mar: Winter
+- Apr-Jun: Snowmelt/spring
+- Jul-Aug: Monsoon
+- Sep-Nov: Baseflow/fall
+
+```{r}
+############################
+### look at month
+#get rid of a bunch of data
+hru_grid_tmax_jan <- hru_grids %>%
+  dplyr::select(c(time, ID, tmax)) %>%
+  rename(tmax_grid = tmax)  %>%
+  mutate(month = month(time)) %>%
+  filter(month %in% c(12,1,2,3)) %>%
+  group_by(ID) %>%
+  summarize(tmax_all_grid = mean(tmax_grid))
+
+hru_statn_tmax_jan <- hru_statn %>%
+  dplyr::select(c(time, ID, tmax)) %>%
+  rename(tmax_statn = tmax) %>%
+  mutate(month = month(time)) %>%
+  filter(month %in% c(12,1,2,3)) %>%
+  group_by(ID) %>%
+  summarize(tmax_all_statn = mean(tmax_statn))
+
+tmax_hrus_jan <- left_join(hru_grid_tmax_jan, hru_statn_tmax_jan, by = c('ID')) %>%
+  mutate(diff = tmax_all_statn - tmax_all_grid) %>%
+  rename(value = ID)
+
+hrus_map_tmax_jan <- left_join(hrus, tmax_hrus_jan, by = 'value')
+
+tmax_jan <- ggplot() +
+  geom_sf(data = hrus_map_tmax_jan, aes(fill = diff), color = "black", lwd = 0.2) +
+  scale_fill_viridis_c(option = "plasma", name = "tmax difference (°C)",
+                       limits = c(-5.1, 3)) +
+  theme_bw(base_size=13.5) +
+  theme_void() +
+  theme(
+    legend.position = "bottom",
+    panel.grid.major = element_blank(),
+    panel.grid.minor = element_blank(),
+    axis.title.x = element_blank(),
+    axis.title.y = element_blank()) +
+  ggtitle('Winter')
+
+#tmax_jan
+
+## 
+hru_grid_tmax_apr <- hru_grids %>%
+  dplyr::select(c(time, ID, tmax)) %>%
+  rename(tmax_grid = tmax)  %>%
+  mutate(month = month(time)) %>%
+  filter(month %in% c(4,5,6)) %>%
+  group_by(ID) %>%
+  summarize(tmax_all_grid = mean(tmax_grid))
+
+hru_statn_tmax_apr <- hru_statn %>%
+  dplyr::select(c(time, ID, tmax)) %>%
+  rename(tmax_statn = tmax) %>%
+  mutate(month = month(time)) %>%
+  filter(month %in% c(4,5,6)) %>%
+  group_by(ID) %>%
+  summarize(tmax_all_statn = mean(tmax_statn))
+
+tmax_hrus_apr <- left_join(hru_grid_tmax_apr, hru_statn_tmax_apr, by = c('ID')) %>%
+  mutate(diff = tmax_all_statn - tmax_all_grid) %>%
+  rename(value = ID)
+
+hrus_map_tmax_apr <- left_join(hrus, tmax_hrus_apr, by = 'value')
+
+tmax_apr <- ggplot() +
+  geom_sf(data = hrus_map_tmax_apr, aes(fill = diff), color = "black", lwd = 0.2) +
+  scale_fill_viridis_c(option = "plasma", name = "tmax difference (°C)",
+                       limits = c(-5.1, 3)) +
+  theme_bw(base_size=13.5) +
+  theme_void() +
+  theme(
+    legend.position = "bottom",
+    panel.grid.major = element_blank(),
+    panel.grid.minor = element_blank(),
+    axis.title.x = element_blank(),
+    axis.title.y = element_blank()) +
+  ggtitle('Snowmelt')
+
+#tmax_apr
+
+#### 
+hru_grid_tmax_jul <- hru_grids %>%
+  dplyr::select(c(time, ID, tmax)) %>%
+  rename(tmax_grid = tmax)  %>%
+  mutate(month = month(time)) %>%
+  filter(month %in% c(7,8)) %>%
+  group_by(ID) %>%
+  summarize(tmax_all_grid = mean(tmax_grid))
+
+hru_statn_tmax_jul <- hru_statn %>%
+  dplyr::select(c(time, ID, tmax)) %>%
+  rename(tmax_statn = tmax) %>%
+  mutate(month = month(time)) %>%
+  filter(month %in% c(7,8)) %>%
+  group_by(ID) %>%
+  summarize(tmax_all_statn = mean(tmax_statn))
+
+tmax_hrus_jul <- left_join(hru_grid_tmax_jul, hru_statn_tmax_jul, by = c('ID')) %>%
+  mutate(diff = tmax_all_statn - tmax_all_grid) %>%
+  rename(value = ID)
+
+hrus_map_tmax_jul <- left_join(hrus, tmax_hrus_jul, by = 'value')
+
+tmax_jul <- ggplot() +
+  geom_sf(data = hrus_map_tmax_jul, aes(fill = diff), color = "black", lwd = 0.2) +
+  scale_fill_viridis_c(option = "plasma", name = "tmax difference (°C)",
+                            limits = c(-5.1, 3)) +
+  theme_bw(base_size=13.5) +
+  theme_void() +
+  theme(
+    legend.position = "bottom",
+    panel.grid.major = element_blank(),
+    panel.grid.minor = element_blank(),
+    axis.title.x = element_blank(),
+    axis.title.y = element_blank()) +
+  ggtitle('Monsoon')
+
+#tmax_jul
+
+##
+
+hru_grid_tmax_sep <- hru_grids %>%
+  dplyr::select(c(time, ID, tmax)) %>%
+  rename(tmax_grid = tmax)  %>%
+  mutate(month = month(time)) %>%
+  filter(month %in% c(9,10,11)) %>%
+  group_by(ID) %>%
+  summarize(tmax_all_grid = mean(tmax_grid))
+
+hru_statn_tmax_sep <- hru_statn %>%
+  dplyr::select(c(time, ID, tmax)) %>%
+  rename(tmax_statn = tmax) %>%
+  mutate(month = month(time)) %>%
+  filter(month %in% c(9,10,11)) %>%
+  group_by(ID) %>%
+  summarize(tmax_all_statn = mean(tmax_statn))
+
+tmax_hrus_sep <- left_join(hru_grid_tmax_sep, hru_statn_tmax_sep, by = c('ID')) %>%
+  mutate(diff = tmax_all_statn - tmax_all_grid) %>%
+  rename(value = ID)
+
+hrus_map_tmax_sep <- left_join(hrus, tmax_hrus_sep, by = 'value')
+
+tmax_sep <- ggplot() +
+  geom_sf(data = hrus_map_tmax_sep, aes(fill = diff), color = "black", lwd = 0.2) +
+  scale_fill_viridis_c(option = "plasma", name = "tmax difference (°C)",
+                       limits = c(-5.1, 3)) +
+  theme_bw(base_size=13.5) +
+  theme_void() +
+  theme(
+    legend.position = "bottom",
+    panel.grid.major = element_blank(),
+    panel.grid.minor = element_blank(),
+    axis.title.x = element_blank(),
+    axis.title.y = element_blank()) +
+  ggtitle('Fall')
+
+#tmax_sep
+###
+
+lots <- ggarrange(tmax_jan,
+                  tmax_apr,
+                  tmax_jul,
+                  tmax_sep) 
+          #nrow = 4)
+          #ncol= 0)
+lots
+
+```
+
 ## Tmin difference
@@
 
+### Tmin season
+
+- Dec-Mar: Winter
+- Apr-Jun: Snowmelt/spring
+- Jul-Aug: Monsoon
+- Sep-Nov: Baseflow/fall
+
+```{r}
+############################
+### look at month
+#get rid of a bunch of data
+hru_grid_tmin_jan <- hru_grids %>%
+  dplyr::select(c(time, ID, tmin)) %>%
+  rename(tmin_grid = tmin)  %>%
+  mutate(month = month(time)) %>%
+  filter(month %in% c(12,1,2,3)) %>%
+  group_by(ID) %>%
+  summarize(tmin_all_grid = mean(tmin_grid))
+
+hru_statn_tmin_jan <- hru_statn %>%
+  dplyr::select(c(time, ID, tmin)) %>%
+  rename(tmin_statn = tmin) %>%
+  mutate(month = month(time)) %>%
+  filter(month %in% c(12,1,2,3)) %>%
+  group_by(ID) %>%
+  summarize(tmin_all_statn = mean(tmin_statn))
+
+tmin_hrus_jan <- left_join(hru_grid_tmin_jan, hru_statn_tmin_jan, by = c('ID')) %>%
+  mutate(diff = tmin_all_statn - tmin_all_grid) %>%
+  rename(value = ID)
+
+hrus_map_tmin_jan <- left_join(hrus, tmin_hrus_jan, by = 'value')
+
+tmin_jan <- ggplot() +
+  geom_sf(data = hrus_map_tmin_jan, aes(fill = diff), color = "black", lwd = 0.2) +
+  scale_fill_viridis_c(option = "plasma", name = "tmin difference (°C)",
+                       limits = c(-5, 3)) +
+  theme_bw(base_size=13.5) +
+  theme_void() +
+  theme(
+    legend.position = "bottom",
+    panel.grid.major = element_blank(),
+    panel.grid.minor = element_blank(),
+    axis.title.x = element_blank(),
+    axis.title.y = element_blank()) +
+  ggtitle('Winter')
+
+#tmin_jan
+
+## 
+hru_grid_tmin_apr <- hru_grids %>%
+  dplyr::select(c(time, ID, tmin)) %>%
+  rename(tmin_grid = tmin)  %>%
+  mutate(month = month(time)) %>%
+  filter(month %in% c(4,5,6)) %>%
+  group_by(ID) %>%
+  summarize(tmin_all_grid = mean(tmin_grid))
+
+hru_statn_tmin_apr <- hru_statn %>%
+  dplyr::select(c(time, ID, tmin)) %>%
+  rename(tmin_statn = tmin) %>%
+  mutate(month = month(time)) %>%
+  filter(month %in% c(4,5,6)) %>%
+  group_by(ID) %>%
+  summarize(tmin_all_statn = mean(tmin_statn))
+
+tmin_hrus_apr <- left_join(hru_grid_tmin_apr, hru_statn_tmin_apr, by = c('ID')) %>%
+  mutate(diff = tmin_all_statn - tmin_all_grid) %>%
+  rename(value = ID)
+
+hrus_map_tmin_apr <- left_join(hrus, tmin_hrus_apr, by = 'value')
+
+tmin_apr <- ggplot() +
+  geom_sf(data = hrus_map_tmin_apr, aes(fill = diff), color = "black", lwd = 0.2) +
+  scale_fill_viridis_c(option = "plasma", name = "tmin difference (°C)",
+                       limits = c(-5, 3)) +
+  theme_bw(base_size=13.5) +
+  theme_void() +
+  theme(
+    legend.position = "bottom",
+    panel.grid.major = element_blank(),
+    panel.grid.minor = element_blank(),
+    axis.title.x = element_blank(),
+    axis.title.y = element_blank()) +
+  ggtitle('Snowmelt')
+
+#tmin_apr
+
+#### 
+hru_grid_tmin_jul <- hru_grids %>%
+  dplyr::select(c(time, ID, tmin)) %>%
+  rename(tmin_grid = tmin)  %>%
+  mutate(month = month(time)) %>%
+  filter(month %in% c(7,8)) %>%
+  group_by(ID) %>%
+  summarize(tmin_all_grid = mean(tmin_grid))
+
+hru_statn_tmin_jul <- hru_statn %>%
+  dplyr::select(c(time, ID, tmin)) %>%
+  rename(tmin_statn = tmin) %>%
+  mutate(month = month(time)) %>%
+  filter(month %in% c(7,8)) %>%
+  group_by(ID) %>%
+  summarize(tmin_all_statn = mean(tmin_statn))
+
+tmin_hrus_jul <- left_join(hru_grid_tmin_jul, hru_statn_tmin_jul, by = c('ID')) %>%
+  mutate(diff = tmin_all_statn - tmin_all_grid) %>%
+  rename(value = ID)
+
+hrus_map_tmin_jul <- left_join(hrus, tmin_hrus_jul, by = 'value')
+
+tmin_jul <- ggplot() +
+  geom_sf(data = hrus_map_tmin_jul, aes(fill = diff), color = "black", lwd = 0.2) +
+  scale_fill_viridis_c(option = "plasma", name = "tmin difference (°C)",
+                            limits = c(-5, 3)) +
+  theme_bw(base_size=13.5) +
+  theme_void() +
+  theme(
+    legend.position = "bottom",
+    panel.grid.major = element_blank(),
+    panel.grid.minor = element_blank(),
+    axis.title.x = element_blank(),
+    axis.title.y = element_blank()) +
+  ggtitle('Monsoon')
+
+#tmin_jul
+
+##
+
+hru_grid_tmin_sep <- hru_grids %>%
+  dplyr::select(c(time, ID, tmin)) %>%
+  rename(tmin_grid = tmin)  %>%
+  mutate(month = month(time)) %>%
+  filter(month %in% c(9,10,11)) %>%
+  group_by(ID) %>%
+  summarize(tmin_all_grid = mean(tmin_grid))
+
+hru_statn_tmin_sep <- hru_statn %>%
+  dplyr::select(c(time, ID, tmin)) %>%
+  rename(tmin_statn = tmin) %>%
+  mutate(month = month(time)) %>%
+  filter(month %in% c(9,10,11)) %>%
+  group_by(ID) %>%
+  summarize(tmin_all_statn = mean(tmin_statn))
+
+tmin_hrus_sep <- left_join(hru_grid_tmin_sep, hru_statn_tmin_sep, by = c('ID')) %>%
+  mutate(diff = tmin_all_statn - tmin_all_grid) %>%
+  rename(value = ID)
+
+hrus_map_tmin_sep <- left_join(hrus, tmin_hrus_sep, by = 'value')
+
+tmin_sep <- ggplot() +
+  geom_sf(data = hrus_map_tmin_sep, aes(fill = diff), color = "black", lwd = 0.2) +
+  scale_fill_viridis_c(option = "plasma", name = "tmin difference (°C)",
+                       limits = c(-5, 3)) +
+  theme_bw(base_size=13.5) +
+  theme_void() +
+  theme(
+    legend.position = "bottom",
+    panel.grid.major = element_blank(),
+    panel.grid.minor = element_blank(),
+    axis.title.x = element_blank(),
+    axis.title.y = element_blank()) +
+  ggtitle('Fall')
+
+#tmin_sep
+###
+
+lots <- ggarrange(tmin_jan,
+                  tmin_apr,
+                  tmin_jul,
+                  tmin_sep) 
+          #nrow = 4)
+          #ncol= 0)
+lots
+
+```
+
 ## Cumulative Precip difference
@@
   mutate(month = month(time)) %>%
-  filter(month %in% c(1,2,3)) %>% 
+  filter(month %in% c(12,1,2,3)) %>% 
   mutate(diff = precip_statn - precip_grid,
@@
   scale_fill_viridis_c(option = "viridis", name = "RH difference (%)",
-                       limits = c(-3, 10)) +
+                       limits = c(-3, 10.5)) +
   theme_bw(base_size=13.5) +
@@
   scale_fill_viridis_c(option = "viridis", name = "RH difference (%)",
-                       limits = c(-3,10)) +
+                       limits = c(-3,10.5)) +
   theme_bw(base_size=13.5) +
@@
   mutate(month = month(time)) %>%
-  filter(month %in% c(9,10,10)) %>%
+  filter(month %in% c(9,10,11)) %>%
   group_by(ID) %>%
@@
 rd1_hru <- left_join(rd1_hru, elev_area, by = 'elevation_group') %>%
-  mutate(RD1_mm_year = (max_rd1_summed/group_area)*1000)
+  mutate(RD1_mm_year = ((max_rd1_summed/1000)/group_area)/1000)
 
@@
 rd2_hru <- left_join(rd2_hru, elev_area, by = 'elevation_group') %>%
-  mutate(rd2_mm_year = (max_rd2_summed/group_area)*1000)
+  mutate(rd2_mm_year = ((max_rd2_summed/1000)/group_area)/1000)
 
@@
 rg1_hru <- left_join(rg1_hru, elev_area, by = 'elevation_group') %>%
-  mutate(rg1_mm_year = (max_rg1_summed/group_area)*1000)
+  mutate(rg1_mm_year = ((max_rg1_summed/1000)/group_area)/1000)
 
@@
 rg2_hru <- left_join(rg2_hru, elev_area, by = 'elevation_group') %>%
-  mutate(rg2_mm_year = (max_rg2_summed/group_area)*1000)
+  mutate(rg2_mm_year = ((max_rg2_summed/1000)/group_area)/1000)
 

### 2024-10-08 spatial_figs.Rmd
hru updates

@@
 library(viridis)
+library(ggpubr)
 
@@
 # update the HRUs
-hru_new <- vect('/Users/megansears/Documents/Repos/fourmile/38HRU_model/hrus_final.shp')
+hru_new <- vect('/Users/megansears/Documents/Repos/fourmile/data/GIS/hrus_final.shp')
 plot(hru_new)
 
-hru_new <- st_read('/Users/megansears/Documents/Repos/fourmile/38HRU_model/hrus_final.shp')
+hru_new <- st_read('/Users/megansears/Documents/Repos/fourmile/data/GIS/hrus_final.shp')
 
-mapview(hru_new) + mapview(hru_test)
-mapview(hru_test)
+mapview(hru_new) 
+#mapview(hru_test)
 
@@
 terrain
+ggsave('./figures/fig1a.png', dpi=600)
+##
 
-ggsave('./figures/fig1a.png', dpi=600)
+reference_location <- data.frame(
+  x = -105.2705,  # Longitude for Boulder
+  y = 40.0150,    # Latitude for Boulder
+  name = "Boulder, CO"
+)
+
+# Your existing terrain plot
+terrain2 <- ggplot() +
+  geom_raster(data = dem_df, 
+              aes(x = x, y = y, fill = layer)) +  
+  scale_fill_gradientn(colors = terrain.colors(200),  
+                       name = "Elevation (m)") +
+  geom_sf(data = fire, 
+          aes(color = "Fire"), 
+          fill = NA, 
+          lwd = 0.75) +
+  geom_sf(data = hru_new, 
+          aes(color = "HRU"), 
+          fill = NA, 
+          lwd = 0.5) +
+  geom_sf(data = locations, 
+          aes(shape = factor(display_use)), 
+          size = 4) + 
+  scale_shape_manual(values = custom_shapes) +
+  scale_color_manual(name = NULL,
+                     values = c(Fire = "red", HRU = "black"), 
+                     labels = c(Fire = "Fourmile Canyon fire", HRU = "HRUs")) + 
+  labs(shape = element_blank()) +
+  theme_bw(base_size = 25) +
+  theme(axis.title.x = element_blank(),
+        axis.title.y = element_blank(),
+        legend.spacing.y = unit(0.01, "cm")) +
+  geom_point(data = reference_location, aes(x = x, y = y), color = "blue", size = 4, shape = 21, fill = "yellow") + # Reference marker
+  geom_text(data = reference_location, aes(x = x, y = y, label = name), vjust = -1, color = "blue") # Reference label
+
+terrain2
+``##
 
@@
 ```{r}
-grid <- read_csv("/Users/megansears/Documents/ages-data-fourmile_creek/output/4milecreek38HRUs-gridallNA_#1/out/Catchment.csv",
+grid <- read_csv("/Users/megansears/Documents/Repos/fourmile/38HRU_sept2013_updates/grid_all_Catchment.csv",
                  skip=3) %>%
@@
 
-statn <- read_csv('/Users/megansears/Documents/ages-data-fourmile_creek/output/4milecreek38HRUs-statnall_na_#1/out/Catchment.csv',
+statn <- read_csv('/Users/megansears/Documents/Repos/fourmile/38HRU_sept2013_updates/statn_all_Catchment.csv',
                  skip=3) %>%
@@
           legend = 'bottom',
-          ncol=4) 
+          ncol=2,
+          nrow=2) 
           #nrow = 4)
@@
 ggsave("./figures/quad.png", plot = quad, dpi = 600)
+
+quad_plus <- ggarrange(flow_plot,quad,
+                       nrow=2)
+quad_plus
+
+ggsave("./figures/quad_plus.png", plot = quad_plus, dpi = 600)
 
@@
 
+####
 rh <- ggplot() +
   geom_sf(data = hrus_map_rh, aes(fill = diff), color = "black", lwd = 0.2) +
-  scale_fill_viridis_c(option = "viridis", name = "RH difference (%)") +
-  theme_bw(base_size=13.5) +
-  theme_void() +
-  theme(
-    legend.position = "bottom",
-    panel.grid.major = element_blank(),
-    panel.grid.minor = element_blank(),
-    axis.title.x = element_blank(),
-    axis.title.y = element_blank())
+  scale_fill_viridis_c(option = "viridis", name = "RH (%)") +
+  theme_bw(base_size=15.5) +
+  theme_void() + top_theme
 
@@
   geom_sf(data = hrus_map_solrad, aes(fill = diff), color = "black", lwd = 0.2) +
-  scale_fill_viridis_c(option = "cividis", name = expression("Solar rad difference (MJ/m"^"2" * ")")) +
-  theme_bw(base_size=13.5) +
-  theme_void() +
-  theme(
-    legend.position = "bottom",
-    panel.grid.major = element_blank(),
-    panel.grid.minor = element_blank(),
-    axis.title.x = element_blank(),
-    axis.title.y = element_blank()) +
-  guides(
-    fill = guide_colorbar(
-      label.theme = element_text(size = 10)))
+  scale_fill_viridis_c(option = "cividis", name = expression("Srad (MJ/m"^"2" * ")")) +
+  theme_bw(base_size=15.5) +
+  theme_void() + top_theme
 
@@
   geom_sf(data = hrus_map_precip, aes(fill = precip_avg_cumdiff), color = "black", lwd = 0.2) +
-  scale_fill_viridis_c(option = "mako", name = "Cumulative P Difference (mm)") +
-  theme_bw(base_size=13.5) +
-  theme_void() +
-  theme(
-    legend.position = "bottom",
-    panel.grid.major = element_blank(),
-    panel.grid.minor = element_blank(),
-    axis.title.x = element_blank(),
-    axis.title.y = element_blank())
+  scale_fill_viridis_c(option = "mako", name = "Cumulative P (mm)") +
+  theme_bw(base_size=15.5) +
+  theme_void() + top_theme
 
@@
   geom_sf(data = hrus_map_tmean, aes(fill = diff), color = "black", lwd = 0.2) +
-  scale_fill_viridis_c(option = "plasma", name = "Tmean difference (°C)",
+  scale_fill_viridis_c(option = "plasma", name = "Tmean (°C)",
                        limits = c(-5, 2)) +
-  theme_bw(base_size=13.5) +
-  theme_void() +
-  theme(
-    legend.position = "bottom",
-    panel.grid.major = element_blank(),
-    panel.grid.minor = element_blank(),
-    axis.title.x = element_blank(),
-    axis.title.y = element_blank())
+  theme_bw(base_size=15.5) +
+  theme_void() + bottom_theme
 
@@
   geom_sf(data = hrus_map_tmin, aes(fill = diff), color = "black", lwd = 0.2) +
-  scale_fill_viridis_c(option = "plasma", name = "Tmin difference (°C)",
+  scale_fill_viridis_c(option = "plasma", name = "Tmin (°C)",
                        limits = c(-5, 2)) +
-  theme_bw(base_size=13.5) +
-  theme_void() +
-  theme(
-    legend.position = "bottom",
-    panel.grid.major = element_blank(),
-    panel.grid.minor = element_blank(),
-    axis.title.x = element_blank(),
-    axis.title.y = element_blank())
+  theme_bw(base_size=15.5) +
+  theme_void() + bottom_theme
 
@@
   geom_sf(data = hrus_map_tmax, aes(fill = diff), color = "black", lwd = 0.2) +
-  scale_fill_viridis_c(option = "plasma", name = "Tmax difference (°C)",
+  scale_fill_viridis_c(option = "plasma", name = "Tmax (°C)",
                        limits = c(-5, 2)) +
-  theme_bw(base_size=13.5) +
-  theme_void() +
-  theme(
+  theme_bw(base_size=15.5) +
+  theme_void() + bottom_theme
+
+tmax
+
+bottom_theme <-   theme(
     legend.position = "bottom",
     panel.grid.major = element_blank(),
+    legend.key.width = unit(.75, "cm"),
     panel.grid.minor = element_blank(),
     axis.title.x = element_blank(),
-    axis.title.y = element_blank())
+    axis.title.y = element_blank(),
+    plot.margin = unit(c(-6, 0, 0, 0), "cm"), 
+    panel.spacing = unit(0, "lines"))
 
-tmin
+top_theme <-   theme(
+    legend.position = "bottom",
+    panel.grid.major = element_blank(),
+    legend.key.width = unit(.75, "cm"),
+    panel.grid.minor = element_blank(),
+    axis.title.x = element_blank(),
+    axis.title.y = element_blank(),
+    plot.margin = unit(c(0, 0, -6, 0), "cm"), 
+    panel.spacing = unit(0, "lines"))
 
-lots <- ggarrange(precip,
-                  sr,
-                  rh,
-                  tmean,
-                  tmax,
-                  tmin) 
-          #nrow = 4)
-          #ncol= 0)
+lots <- ggarrange(
+  precip, sr, rh, tmean, tmax, tmin,
+  heights=)
+
 lots
 
-ggsave("./figures/diff.png", plot = lots, dpi = 600)
+ggsave("./figures/diff_update.png", plot = lots, dpi = 600)
 
@@
 
-ggplot(flow, aes(x = DOY, y = obs, color = as.factor(year))) + 
+flow_plot <- ggplot(flow, aes(x = DOY, y = obs, color = as.factor(year))) + 
   geom_line(size = 1.1) +
@@
   scale_color_viridis_d(option = "turbo")
+
+flow_plot
 

### 2024-10-08 fourmile_outputs_2013edits.Rmd
fxied winter cumulative p hru plot

@@
   scale_fill_viridis_c(option = "mako", name = "Cumulative P Difference (mm)",
-                       limits = c(-51, 7.5)) +
+                       limits = c(-51, 9.5)) +
   theme_bw(base_size=13.5) +

### 2024-10-08 fourmile_outputs_2013edits.Rmd
fixed sections

@@
 precip
-
+```
+
+### P season
+
+- Dec-Mar: Winter
+- Apr-Jun: Snowmelt/spring
+- Jul-Aug: Monsoon
+- Sep-Nov: Baseflow/fall
+
+```{r cum precip season, echo = F}
 #################
@@
 ```{r cum sol rad, echo = F}
-
 # #get rid of a bunch of data
@@
 sr
-
+```
+
+### Solar rad season
+
+- Dec-Mar: Winter
+- Apr-Jun: Snowmelt/spring
+- Jul-Aug: Monsoon
+- Sep-Nov: Baseflow/fall
+
+```{r cum sol rad season, echo = F}
 ##########
@@
 ```{r rh, echo = F}
-
 # #get rid of a bunch of data
@@
 #####
-
+```
+
+### RH season
+
+- Dec-Mar: Winter
+- Apr-Jun: Snowmelt/spring
+- Jul-Aug: Monsoon
+- Sep-Nov: Baseflow/fall
+
+```{r rh season, echo = F}
 hru_grid_rh_jan <- hru_grids %>%

### 2024-11-26 state_vars.Rmd
looking at state variables with climate inputs

---
title: "Fourmile state variables"
author: "Megan Sears"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: yes
    toc_float: yes
    theme: journal
editor_options:
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = F,
  message = F, 
  warning  = F)

library(tidyverse)
library(ggplot2); theme_set(theme_bw(base_size = 20))
library(plotly)
library(knitr)
library(kableExtra)

```

```{r, include = F}

statn <- read_csv('./38HRU_sept2013_updates/catchment_output/Catchment_statnall.csv') %>%
  mutate(date = mdy(time),
         source = 'statn') %>%
  select(-time)

grid <- read_csv('./38HRU_sept2013_updates/catchment_output/Catchment_gridall.csv') %>%
  mutate(date = mdy(time),
         source = 'grid') %>%
  select(-time)

both <- bind_rows(statn, grid)

```

# Catchment

## Inputs

```{r}

temp <- ggplot(both, 
               aes(date, 
                   tmean,
                   color = source)) +
  geom_line() +
  scale_color_manual(values = c("orange", "blue"))

ggplotly(temp)

tmean_avg <- both %>%
  mutate(month = month(date),
         year = year(date)) %>% 
  group_by(source, month) %>%
  summarize(mean_tmean = mean(tmean))

ggplot(tmean_avg, aes(x=month, y=mean_tmean,
                 color=source)) +
  geom_point(size=3) +
  scale_color_manual(values = c("orange", "blue")) +
  labs(y= 'Monthly mean tmean (C)')

precip <- ggplot(both, 
               aes(date, 
                   precip,
                   color = source)) +
  geom_line() +
  scale_color_manual(values = c("orange", "blue"))

ggplotly(precip)

precip_avg <- both %>%
  mutate(month = month(date),
         year = year(date)) %>% 
  group_by(source, month, year) %>%
  summarize(sum_mo = sum(precip)) %>%
  ungroup() %>% 
  group_by(source, month) %>%
  summarize(mean_p = mean(sum_mo))

ggplot(precip_avg, aes(x=month, y=mean_p,
                 color=source)) +
  geom_point(size=3) +
  scale_color_manual(values = c("orange", "blue")) +
  labs(y= 'Monthly mean precip (mm)')

solrad_avg <- both %>%
  mutate(month = month(date),
         year = year(date)) %>% 
  group_by(source, month) %>%
  summarize(mean_solrad = mean(solRad))

ggplot(solrad_avg, aes(x=month, y=mean_solrad,
                 color=source)) +
  geom_point(size=3) +
  scale_color_manual(values = c("orange", "blue")) +
  labs(y= 'Monthly mean solrad')

```

## Interception
- Average interception: grid > statn
- Monthly average: Statn > grid 1:4 and 10:12, grid > statn 5:9
- During the summer rain interception is greater from grid
- In the winter snow interception is greater from statn

```{r}
int_avg <- both %>%
  mutate(month = month(date),
         year = year(date)) %>% 
  group_by(source, month) %>%
  summarize(mean_interception = mean(interception))

ggplot(int_avg, aes(x=month, y=mean_interception,
                 color=source)) +
  geom_point(size=3) +
  scale_color_manual(values = c("orange", "blue")) +
  labs(y= 'Monthly mean interception')

interception <- ggplot(both, 
               aes(date, 
                   interception,
                   color = source)) +
  geom_line() +
  scale_color_manual(values = c("orange", "blue"))

ggplotly(interception)

```

## ET

- Average ET: grid > statn
- Monthly average ET: grid > statn 1:6 and 9:12, statn > grid 7:8

```{r}

et_avg <- both %>%
  mutate(month = month(date),
         year = year(date)) %>% 
  group_by(source, month) %>%
  summarize(mean_et = mean(actET...21))

ggplot(et_avg, aes(x=month, y=mean_et,
                 color=source)) +
  geom_point(size=3) +
  scale_color_manual(values = c("orange", "blue")) +
  labs(y= 'Monthly mean ET (mm)')

et <- ggplot(both, 
               aes(date, 
                   actET...21,
                   color = source)) +
  geom_line() +
  scale_color_manual(values = c("orange", "blue")) +
  labs(y='ET (mm)')

ggplotly(et)

```

## SWE

- Grid > Statn
- SWE starts accumulating faster in Sept for statn than grid
- But grid > statn all other months

```{r}

swe_avg <- both %>%
  mutate(month = month(date),
         year = year(date)) %>% 
  group_by(source, month) %>%
  summarize(mean_swe = mean(snowTotSWE))

ggplot(swe_avg, aes(x=month, y=mean_swe,
                 color=source)) +
  geom_point(size=3) +
  scale_color_manual(values = c("orange", "blue")) +
  labs(y= 'Monthly mean SWE (l/day)')

snowTotSWE <- ggplot(both, 
                     aes(date, 
                         snowTotSWE,
                         color = source)) +
  geom_line() +
  scale_color_manual(values = c("orange", "blue")) +
  labs(y='SWE (l/day)')

ggplotly(snowTotSWE)

```

## Soil sat (whole profile)

- Statn > grid all months

```{r}

soil_avg <- both %>%
  mutate(month = month(date),
         year = year(date)) %>% 
  group_by(source, month) %>%
  summarize(mean_soil = mean(soilSat))

ggplot(soil_avg, aes(x=month, y=mean_soil,
                 color=source)) +
  geom_point(size=3) +
  scale_color_manual(values = c("orange", "blue")) +
  labs(y= 'Monthly mean soil sat')

soil <- ggplot(both, 
               aes(date, 
                   soilSat,
                   color = source)) +
  geom_line() +
  scale_color_manual(values = c("orange", "blue"))

ggplotly(soil)

```

## Surface runoff

- RG1: when there is surface runoff, statn is slightly higher
- Except for September (Sep 2013 flood heavily influences this avg)
- Many of the surface runoff events are happening Mar-May and Jul

```{r}

rd1_avg <- both %>%
  mutate(month = month(date),
         year = year(date)) %>% 
  group_by(source, month) %>%
  summarize(mean_rd1 = mean(outRD1))

ggplot(rd1_avg, aes(x=month, y=mean_rd1,
                 color=source)) +
  geom_point(size=3) +
  scale_color_manual(values = c("orange", "blue")) +
  labs(y= 'Monthly mean surface runoff (l)')

rd1 <- ggplot(both, 
               aes(date, 
                   outRD1,
                   color = source)) +
  geom_line() +
  scale_color_manual(values = c("orange", "blue")) +
  labs(y='Surface runoff (l)')

ggplotly(rd1)

```

## Interflow

- Statn > grid Jan to Apr
- Grid > statn May, Jun, Oct
- Other months are similar

```{r}

rd2_avg <- both %>%
  mutate(month = month(date),
         year = year(date)) %>% 
  group_by(source, month) %>%
  summarize(mean_rd2 = mean(outRD2))

ggplot(rd2_avg, aes(x=month, y=mean_rd2,
                 color=source)) +
  geom_point(size=3) +
  scale_color_manual(values = c("orange", "blue")) +
  labs(y= 'Monthly mean interflow (l)')

rd2 <- ggplot(both, 
               aes(date, 
                   outRD2,
                   color = source)) +
  geom_line() +
  scale_color_manual(values = c("orange", "blue")) +
  labs(y='Interflow (l)')

ggplotly(rd2)

```

## Groundwater

- RG1 = shallow groundwater
- RG1: during snowmelt runoff to fall baseflow grid > statn
- RG1: statn > grid during winter

- RG2 = groundwater baseflow
- RG2: Very small relative to RG1
- RG2: Grid > statn

```{r}
gw1_avg <- both %>%
  mutate(month = month(date),
         year = year(date)) %>% 
  group_by(source, month) %>%
  summarize(mean_rg1 = mean(outRG1))

ggplot(gw1_avg, aes(x=month, y=mean_rg1,
                 color=source)) +
  geom_point(size=3) +
  scale_color_manual(values = c("orange", "blue")) +
  labs(y= 'Monthly mean RG1 (unit?)')

gw1 <- ggplot(both, 
               aes(date, 
                   outRG1,
                   color = source)) +
  geom_line() +
  scale_color_manual(values = c("orange", "blue"))

ggplotly(gw1)

################################################################
gw2_avg <- both %>%
  mutate(month = month(date),
         year = year(date)) %>% 
  group_by(source, month) %>%
  summarize(mean_rg2 = mean(outRG2))

ggplot(gw2_avg, aes(x=month, y=mean_rg2,
                 color=source)) +
  geom_point(size=3) +
  scale_color_manual(values = c("orange", "blue")) +
  labs(y= 'Monthly mean RG2 (unit?)')

gw2 <- ggplot(both, 
               aes(date, 
                   outRG2,
                   color = source)) +
  geom_line() +
  scale_color_manual(values = c("orange", "blue"))

ggplotly(gw2)

```

# High elevation HRU

HRU18

```{r}

statn_hi <- read_csv('./38HRU_sept2013_updates/HRU_18_statn.csv') %>% 
  mutate(date = mdy(time),
         source = 'statn') %>%
  select(-time)

grid_hi <- read_csv('./38HRU_sept2013_updates/HRU_18_grid.csv') %>%
  mutate(date = mdy(time),
         source = 'grid') %>%
  select(-time)

both_hi <- bind_rows(statn_hi, grid_hi)

```

## Inputs

```{r}

tmean_avg <- both_hi %>%
  mutate(month = month(date),
         year = year(date)) %>% 
  group_by(source, month) %>%
  summarize(mean_tmean = mean(tmean))

ggplot(tmean_avg, aes(x=month, y=mean_tmean,
                 color=source)) +
  geom_point(size=3) +
  scale_color_manual(values = c("orange", "blue")) +
  labs(y= 'Monthly mean tmean (C)')

temp <- ggplot(both_hi, 
               aes(date, 
                   tmean,
                   color = source)) +
  geom_line() +
  scale_color_manual(values = c("orange", "blue"))

ggplotly(temp)
############
precip_avg <- both_hi %>%
  mutate(month = month(date),
         year = year(date)) %>% 
  group_by(source, month, year) %>%
  summarize(sum_mo = sum(precip)) %>%
  ungroup() %>% 
  group_by(source, month) %>%
  summarize(mean_p = mean(sum_mo))

ggplot(precip_avg, aes(x=month, y=mean_p,
                 color=source)) +
  geom_point(size=3) +
  scale_color_manual(values = c("orange", "blue")) +
  labs(y= 'Monthly mean precip (mm)')

precip <- ggplot(both_hi, 
               aes(date, 
                   precip,
                   color = source)) +
  geom_line() +
  scale_color_manual(values = c("orange", "blue"))

ggplotly(precip)
#################

solrad_avg <- both_hi %>%
  mutate(month = month(date),
         year = year(date)) %>% 
  group_by(source, month) %>%
  summarize(mean_solrad = mean(solRad))

ggplot(solrad_avg, aes(x=month, y=mean_solrad,
                 color=source)) +
  geom_point(size=3) +
  scale_color_manual(values = c("orange", "blue")) +
  labs(y= 'Monthly mean solrad (MJ/m2/day)')

```

## Interception

- Station > grid except for Jul

```{r}
int_avg <- both_hi %>%
  mutate(month = month(date),
         year = year(date)) %>% 
  group_by(source, month) %>%
  summarize(mean_interception = mean(interception))

ggplot(int_avg, aes(x=month, y=mean_interception,
                 color=source)) +
  geom_point(size=3) +
  scale_color_manual(values = c("orange", "blue")) +
  labs(y= 'Monthly mean interception')

interception <- ggplot(both_hi, 
               aes(date, 
                   interception,
                   color = source)) +
  geom_line() +
  scale_color_manual(values = c("orange", "blue"))

ggplotly(interception)

```

## ET

- Grid > statn except for Mar

```{r}

et_avg <- both_hi %>%
  mutate(month = month(date),
         year = year(date)) %>% 
  group_by(source, month) %>%
  summarize(mean_et = mean(actET))

ggplot(et_avg, aes(x=month, y=mean_et,
                 color=source)) +
  geom_point(size=3) +
  scale_color_manual(values = c("orange", "blue")) +
  labs(y= 'Monthly mean ET (mm)')

et <- ggplot(both_hi, 
               aes(date, 
                   actET,
                   color = source)) +
  geom_line() +
  scale_color_manual(values = c("orange", "blue")) +
  labs(y='ET (mm)')

ggplotly(et)

```

## SWE

- Grid > statn

```{r}

swe_avg <- both_hi %>%
  mutate(month = month(date),
         year = year(date)) %>% 
  group_by(source, month) %>%
  summarize(mean_swe = mean(snowTotSWE))

ggplot(swe_avg, aes(x=month, y=mean_swe,
                 color=source)) +
  geom_point(size=3) +
  scale_color_manual(values = c("orange", "blue")) +
  labs(y= 'Monthly mean SWE (l/day)')

snowTotSWE <- ggplot(both_hi, 
                     aes(date, 
                         snowTotSWE,
                         color = source)) +
  geom_line() +
  scale_color_manual(values = c("orange", "blue")) +
  labs(y='SWE (l/day)')

ggplotly(snowTotSWE)

```

## Soil sat (whole profile)

- Statn > grid

```{r}

soil_avg <- both_hi %>%
  mutate(month = month(date),
         year = year(date)) %>% 
  group_by(source, month) %>%
  summarize(mean_soil = mean(soilSat))

ggplot(soil_avg, aes(x=month, y=mean_soil,
                 color=source)) +
  geom_point(size=3) +
  scale_color_manual(values = c("orange", "blue")) +
  labs(y= 'Monthly mean soil sat')

soil <- ggplot(both_hi, 
               aes(date, 
                   soilSat,
                   color = source)) +
  geom_line() +
  scale_color_manual(values = c("orange", "blue"))

ggplotly(soil)

```

## Surface runoff

- No surface runoff

```{r}

rd1_avg <- both_hi %>%
  mutate(month = month(date),
         year = year(date)) %>% 
  group_by(source, month) %>%
  summarize(mean_rd1 = mean(outRD1))

ggplot(rd1_avg, aes(x=month, y=mean_rd1,
                 color=source)) +
  geom_point(size=3) +
  scale_color_manual(values = c("orange", "blue")) +
  labs(y= 'Monthly mean surface runoff (l)')

rd1 <- ggplot(both_hi, 
               aes(date, 
                   outRD1,
                   color = source)) +
  geom_line() +
  scale_color_manual(values = c("orange", "blue")) +
  labs(y='Surface runoff (l)')

ggplotly(rd1)

```

## Interflow

- Statn > grid Jan to Apr
- Grid > statn May to Jun
- Other months are similar

```{r}

rd2_avg <- both_hi %>%
  mutate(month = month(date),
         year = year(date)) %>% 
  group_by(source, month) %>%
  summarize(mean_rd2 = mean(outRD2))

ggplot(rd2_avg, aes(x=month, y=mean_rd2,
                 color=source)) +
  geom_point(size=3) +
  scale_color_manual(values = c("orange", "blue")) +
  labs(y= 'Monthly mean interflow (l)')

rd2 <- ggplot(both_hi, 
               aes(date, 
                   outRD2,
                   color = source)) +
  geom_line() +
  scale_color_manual(values = c("orange", "blue")) +
  labs(y='Interflow (l)')

ggplotly(rd2)

```

## Groundwater

- RG1 = shallow groundwater
- RG1: Jan to May statn > grid
- RG1: grid > statn Jun, Jul, Oct
- RG1: similar rest of year

- RG2 = groundwater baseflow
- RG2: Very small relative to RG1
- RG2: Grid > statn

```{r}
gw1_avg <- both_hi %>%
  mutate(month = month(date),
         year = year(date)) %>% 
  group_by(source, month) %>%
  summarize(mean_rg1 = mean(outRG1))

ggplot(gw1_avg, aes(x=month, y=mean_rg1,
                 color=source)) +
  geom_point(size=3) +
  scale_color_manual(values = c("orange", "blue")) +
  labs(y= 'Monthly mean RG1 (unit?)')

gw1 <- ggplot(both_hi, 
               aes(date, 
                   outRG1,
                   color = source)) +
  geom_line() +
  scale_color_manual(values = c("orange", "blue"))

ggplotly(gw1)

################################################################
gw2_avg <- both_hi %>%
  mutate(month = month(date),
         year = year(date)) %>% 
  group_by(source, month) %>%
  summarize(mean_rg2 = mean(outRG2))

ggplot(gw2_avg, aes(x=month, y=mean_rg2,
                 color=source)) +
  geom_point(size=3) +
  scale_color_manual(values = c("orange", "blue")) +
  labs(y= 'Monthly mean RG2 (unit?)')

gw2 <- ggplot(both_hi, 
               aes(date, 
                   outRG2,
                   color = source)) +
  geom_line() +
  scale_color_manual(values = c("orange", "blue"))

ggplotly(gw2)

```

# Low elevation HRU

HRU19

```{r}

statn_lo <- read_csv('./38HRU_sept2013_updates/HRU_19_statn.csv') %>% 
  mutate(date = mdy(time),
         source = 'statn') %>%
  select(-time)

grid_lo <- read_csv('./38HRU_sept2013_updates/HRU_19_grid.csv') %>%
  mutate(date = mdy(time),
         source = 'grid') %>%
  select(-time)

both_lo <- bind_rows(statn_lo, grid_lo)

```

## Inputs

```{r}

tmean_avg <- both_lo %>%
  mutate(month = month(date),
         year = year(date)) %>% 
  group_by(source, month) %>%
  summarize(mean_tmean = mean(tmean))

ggplot(tmean_avg, aes(x=month, y=mean_tmean,
                 color=source)) +
  geom_point(size=3) +
  scale_color_manual(values = c("orange", "blue")) +
  labs(y= 'Monthly mean tmean (C)')

temp <- ggplot(both_lo, 
               aes(date, 
                   tmean,
                   color = source)) +
  geom_line() +
  scale_color_manual(values = c("orange", "blue"))

ggplotly(temp)
############
precip_avg <- both_lo %>%
  mutate(month = month(date),
         year = year(date)) %>% 
  group_by(source, month, year) %>%
  summarize(sum_mo = sum(precip)) %>%
  ungroup() %>% 
  group_by(source, month) %>%
  summarize(mean_p = mean(sum_mo))

ggplot(precip_avg, aes(x=month, y=mean_p,
                 color=source)) +
  geom_point(size=3) +
  scale_color_manual(values = c("orange", "blue")) +
  labs(y= 'Monthly mean precip (mm)')

precip <- ggplot(both_lo, 
               aes(date, 
                   precip,
                   color = source)) +
  geom_line() +
  scale_color_manual(values = c("orange", "blue"))

ggplotly(precip)
#################

solrad_avg <- both_lo %>%
  mutate(month = month(date),
         year = year(date)) %>% 
  group_by(source, month) %>%
  summarize(mean_solrad = mean(solRad))

ggplot(solrad_avg, aes(x=month, y=mean_solrad,
                 color=source)) +
  geom_point(size=3) +
  scale_color_manual(values = c("orange", "blue")) +
  labs(y= 'Monthly mean solrad (MJ/m2/day)')

```

## Interception

- Statn > grid Oct to Apr
- Grid > statn May to Sep

```{r}
int_avg <- both_lo %>%
  mutate(month = month(date),
         year = year(date)) %>% 
  group_by(source, month) %>%
  summarize(mean_interception = mean(interception))

ggplot(int_avg, aes(x=month, y=mean_interception,
                 color=source)) +
  geom_point(size=3) +
  scale_color_manual(values = c("orange", "blue")) +
  labs(y= 'Monthly mean interception')

interception <- ggplot(both_lo, 
               aes(date, 
                   interception,
                   color = source)) +
  geom_line() +
  scale_color_manual(values = c("orange", "blue"))

ggplotly(interception)

```

## ET

- Grid > statn Sep to May

```{r}

et_avg <- both_lo %>%
  mutate(month = month(date),
         year = year(date)) %>% 
  group_by(source, month) %>%
  summarize(mean_et = mean(actET))

ggplot(et_avg, aes(x=month, y=mean_et,
                 color=source)) +
  geom_point(size=3) +
  scale_color_manual(values = c("orange", "blue")) +
  labs(y= 'Monthly mean ET (mm)')

et <- ggplot(both_lo, 
               aes(date, 
                   actET,
                   color = source)) +
  geom_line() +
  scale_color_manual(values = c("orange", "blue")) +
  labs(y='ET (mm)')

ggplotly(et)

```

## SWE

- Grid > statn Oct to Feb
- Statn > grid Mar to Apr and Sep

```{r}

swe_avg <- both_lo %>%
  mutate(month = month(date),
         year = year(date)) %>% 
  group_by(source, month) %>%
  summarize(mean_swe = mean(snowTotSWE))

ggplot(swe_avg, aes(x=month, y=mean_swe,
                 color=source)) +
  geom_point(size=3) +
  scale_color_manual(values = c("orange", "blue")) +
  labs(y= 'Monthly mean SWE (l/day)')

snowTotSWE <- ggplot(both_lo, 
                     aes(date, 
                         snowTotSWE,
                         color = source)) +
  geom_line() +
  scale_color_manual(values = c("orange", "blue")) +
  labs(y='SWE (l/day)')

ggplotly(snowTotSWE)

```

## Soil sat (whole profile)

- Statn > grid

```{r}

soil_avg <- both_lo %>%
  mutate(month = month(date),
         year = year(date)) %>% 
  group_by(source, month) %>%
  summarize(mean_soil = mean(soilSat))

ggplot(soil_avg, aes(x=month, y=mean_soil,
                 color=source)) +
  geom_point(size=3) +
  scale_color_manual(values = c("orange", "blue")) +
  labs(y= 'Monthly mean soil sat')

soil <- ggplot(both_lo, 
               aes(date, 
                   soilSat,
                   color = source)) +
  geom_line() +
  scale_color_manual(values = c("orange", "blue"))

ggplotly(soil)

```

## Surface runoff

- Very little except for Sep 2013 (grid > statn)

```{r}

rd1_avg <- both_lo %>%
  mutate(month = month(date),
         year = year(date)) %>% 
  group_by(source, month) %>%
  summarize(mean_rd1 = mean(outRD1))

ggplot(rd1_avg, aes(x=month, y=mean_rd1,
                 color=source)) +
  geom_point(size=3) +
  scale_color_manual(values = c("orange", "blue")) +
  labs(y= 'Monthly mean surface runoff (l)')

rd1 <- ggplot(both_lo, 
               aes(date, 
                   outRD1,
                   color = source)) +
  geom_line() +
  scale_color_manual(values = c("orange", "blue")) +
  labs(y='Surface runoff (l)')

ggplotly(rd1)

```

## Interflow

- Statn > grid Jan, May, June, July, Sep

```{r}

rd2_avg <- both_lo %>%
  mutate(month = month(date),
         year = year(date)) %>% 
  group_by(source, month) %>%
  summarize(mean_rd2 = mean(outRD2))

ggplot(rd2_avg, aes(x=month, y=mean_rd2,
                 color=source)) +
  geom_point(size=3) +
  scale_color_manual(values = c("orange", "blue")) +
  labs(y= 'Monthly mean interflow (l)')

rd2 <- ggplot(both_lo, 
               aes(date, 
                   outRD2,
                   color = source)) +
  geom_line() +
  scale_color_manual(values = c("orange", "blue")) +
  labs(y='Interflow (l)')

ggplotly(rd2)

```

## Groundwater

- RG1 = shallow groundwater
- RG1: Jan, Feb, May, Aug, Sep, Dec statn > grid

- RG2 = groundwater baseflow
- RG2: Very small relative to RG1
- RG2: Grid > statn

```{r}
gw1_avg <- both_lo %>%
  mutate(month = month(date),
         year = year(date)) %>% 
  group_by(source, month) %>%
  summarize(mean_rg1 = mean(outRG1))

ggplot(gw1_avg, aes(x=month, y=mean_rg1,
                 color=source)) +
  geom_point(size=3) +
  scale_color_manual(values = c("orange", "blue")) +
  labs(y= 'Monthly mean RG1 (unit?)')

gw1 <- ggplot(both_lo, 
               aes(date, 
                   outRG1,
                   color = source)) +
  geom_line() +
  scale_color_manual(values = c("orange", "blue"))

ggplotly(gw1)

################################################################
gw2_avg <- both_lo %>%
  mutate(month = month(date),
         year = year(date)) %>% 
  group_by(source, month) %>%
  summarize(mean_rg2 = mean(outRG2))

ggplot(gw2_avg, aes(x=month, y=mean_rg2,
                 color=source)) +
  geom_point(size=3) +
  scale_color_manual(values = c("orange", "blue")) +
  labs(y= 'Monthly mean RG2 (unit?)')

gw2 <- ggplot(both_lo, 
               aes(date, 
                   outRG2,
                   color = source)) +
  geom_line() +
  scale_color_manual(values = c("orange", "blue"))

ggplotly(gw2)

```

### 2024-12-16 spatial_figs.Rmd
minor updates

@@
 terrain2
-``##
+##
 
@@
   theme_bw(base_size=15.5) +
-  theme_void() + top_theme
+  theme_void() + bottom_theme
 
@@
 lots <- ggarrange(
-  precip, sr, rh, tmean, tmax, tmin,
-  heights=)
+  precip, sr, rh, tmean,
+  heights = 1)
 
@@
 
-ggsave("./figures/diff_update.png", plot = lots, dpi = 600)
+ggsave("./figures/diff_update2.png", plot = lots, dpi = 600)
 

### 2024-12-17 38HRU_dec2024_updates/fourmile_output_dec2024.Rmd
statn and grid all dec 2024 updates

--- 2024-10-08 fourmile_outputs_2013edits.Rmd
@@
 
-setwd('/Users/megansears/Documents/Repos/fourmile/38HRU_sept2013_updates')
+setwd('/Users/megansears/Documents/Repos/fourmile/38HRU_dec2024_updates')
 
@@
 
-setwd("/Users/megansears/Documents/Repos/fourmile/38HRU_sept2013_updates/cals")
+setwd("/Users/megansears/Documents/Repos/fourmile/38HRU_dec2024_updates/cals")
 
@@
 
-grid_2011 <- read_cals(grid_2011., name = 'grid_2011')
-grid_2012 <- read_cals(grid_2012., name = 'grid_2012')
-grid_2013 <- read_cals(grid_2013., name = 'grid_2013')
-grid_2014 <- read_cals(grid_2014., name = 'grid_2014')
-grid_2015 <- read_cals(grid_2015., name = 'grid_2015')
-grid_2016 <- read_cals(grid_2016., name = 'grid_2016')
-grid_2017 <- read_cals(grid_2017., name = 'grid_2017')
-grid_2018 <- read_cals(grid_2018., name = 'grid_2018')
-grid_2019 <- read_cals(grid_2019., name = 'grid_2019')
-grid_2020 <- read_cals(grid_2020., name = 'grid_2020')
+# grid_2011 <- read_cals(grid_2011., name = 'grid_2011')
+# grid_2012 <- read_cals(grid_2012., name = 'grid_2012')
+# grid_2013 <- read_cals(grid_2013., name = 'grid_2013')
+# grid_2014 <- read_cals(grid_2014., name = 'grid_2014')
+# grid_2015 <- read_cals(grid_2015., name = 'grid_2015')
+# grid_2016 <- read_cals(grid_2016., name = 'grid_2016')
+# grid_2017 <- read_cals(grid_2017., name = 'grid_2017')
+# grid_2018 <- read_cals(grid_2018., name = 'grid_2018')
+# grid_2019 <- read_cals(grid_2019., name = 'grid_2019')
+# grid_2020 <- read_cals(grid_2020., name = 'grid_2020')
 grid_all <- read_cals(grid_all.c, name = 'grid_all')
 
-grid <- bind_rows(grid_2011, grid_2012, grid_2013, grid_2014, grid_2015,
-                  grid_2016, grid_2017, grid_2018, grid_2019, grid_2020,
-                  grid_all) %>%
+# grid <- bind_rows(grid_2011, grid_2012, grid_2013, grid_2014, grid_2015,
+#                   grid_2016, grid_2017, grid_2018, grid_2019, grid_2020,
+#                   grid_all) %>%
+#   mutate(input_data = 'grid') %>%
+#   mutate(year_missing_almost = gsub('grid_', '', cal)) %>%
+#   mutate(year_missing = gsub('all', 'none', year_missing_almost)) %>%
+#   dplyr::select(-c(year_missing_almost)) %>%
+#   rename(param = Parameter) %>%
+#   filter(!param == 'locGrw',
+#          !param == 'tempRes')
+
+grid <- grid_all %>%
   mutate(input_data = 'grid') %>%
@@
 
-statn_2011 <- read_cals(statn_2011, name = 'statn_2011')
-statn_2012 <- read_cals(statn_2012, name = 'statn_2012')
-statn_2013 <- read_cals(statn_2013, name = 'statn_2013')
-statn_2014 <- read_cals(statn_2014, name = 'statn_2014')
-statn_2015 <- read_cals(statn_2015, name = 'statn_2015')
-statn_2016 <- read_cals(statn_2016, name = 'statn_2016')
-statn_2017 <- read_cals(statn_2017, name = 'statn_2017')
-statn_2018 <- read_cals(statn_2018, name = 'statn_2018')
-statn_2019 <- read_cals(statn_2019, name = 'statn_2019')
-statn_2020 <- read_cals(statn_2020, name = 'statn_2020')
+# statn_2011 <- read_cals(statn_2011, name = 'statn_2011')
+# statn_2012 <- read_cals(statn_2012, name = 'statn_2012')
+# statn_2013 <- read_cals(statn_2013, name = 'statn_2013')
+# statn_2014 <- read_cals(statn_2014, name = 'statn_2014')
+# statn_2015 <- read_cals(statn_2015, name = 'statn_2015')
+# statn_2016 <- read_cals(statn_2016, name = 'statn_2016')
+# statn_2017 <- read_cals(statn_2017, name = 'statn_2017')
+# statn_2018 <- read_cals(statn_2018, name = 'statn_2018')
+# statn_2019 <- read_cals(statn_2019, name = 'statn_2019')
+# statn_2020 <- read_cals(statn_2020, name = 'statn_2020')
 statn_all <- read_cals(statn_all., name = 'statn_all')
 
-statn <- bind_rows(statn_2011, statn_2012, statn_2013, statn_2014, statn_2015,
-                  statn_2016, statn_2017, statn_2018, statn_2019, statn_2020,
-                  statn_all) %>%
+# statn <- bind_rows(statn_2011, statn_2012, statn_2013, statn_2014, statn_2015,
+#                   statn_2016, statn_2017, statn_2018, statn_2019, statn_2020,
+#                   statn_all) %>%
+#   mutate(input_data = 'statn') %>%
+#   mutate(year_missing_almost = gsub('statn_', '', cal)) %>%
+#   mutate(year_missing = gsub('all', 'none', year_missing_almost)) %>%
+#   dplyr::select(-c(year_missing_almost)) %>%
+#   rename(param = Parameter) %>%
+#   filter(!param == 'locGrw',
+#          !param == 'tempRes')
+
+statn <- statn_all %>%
   mutate(input_data = 'statn') %>%
@@
 
-mean_params <- params %>%
-  group_by(param, input_data) %>%
-  summarize(mean = mean(value))
-
-plotdens_params <- function(param_name) {
-  params %>%
-    filter(param == param_name) %>%
-    ggplot(aes(x = value,
-               fill = input_data, 
-               color = input_data)) + 
-    geom_density(alpha=0.5) +
-    geom_vline(data=filter(mean_params, param == param_name), 
-               aes(xintercept=mean, color=input_data),
-             linetype="dashed", linewidth=0.75) +
-    ggtitle(param_name) +
-    theme_bw()
-}
-
-name <- levels(params$param)
-
-lapply(name, plotdens_params)
+# mean_params <- params %>%
+#   group_by(param, input_data) %>%
+#   summarize(mean = mean(value))
+# 
+# plotdens_params <- function(param_name) {
+#   params %>%
+#     filter(param == param_name) %>%
+#     ggplot(aes(x = value,
+#                fill = input_data, 
+#                color = input_data)) + 
+#     geom_density(alpha=0.5) +
+#     geom_vline(data=filter(mean_params, param == param_name), 
+#                aes(xintercept=mean, color=input_data),
+#              linetype="dashed", linewidth=0.75) +
+#     ggtitle(param_name) +
+#     theme_bw()
+# }
+# 
+# name <- levels(params$param)
+# 
+# lapply(name, plotdens_params)
 
@@
 
-rm(statn_2011, statn_2012, statn_2013, statn_2014, statn_2015,
-                  statn_2016, statn_2017, statn_2018, statn_2019, statn_2020,
-                  statn_all., statn_all)
-
-setwd("/Users/megansears/Documents/Repos/fourmile/38HRU_sept2013_updates/cals")
+# rm(statn_2011, statn_2012, statn_2013, statn_2014, statn_2015,
+#                   statn_2016, statn_2017, statn_2018, statn_2019, statn_2020,
+#                   statn_all., statn_all)
+
+rm(statn_all)
+
+setwd("/Users/megansears/Documents/Repos/fourmile/38HRU_dec2024_updates/cals")
 
@@
 
-grid_2011_burn <- read_cals_burn(grid_2011., name = 'grid_2011')
-grid_2012_burn <- read_cals_burn(grid_2012., name = 'grid_2012')
-grid_2013_burn <- read_cals_burn(grid_2013., name = 'grid_2013')
-grid_2014_burn <- read_cals_burn(grid_2014., name = 'grid_2014')
-grid_2015_burn <- read_cals_burn(grid_2015., name = 'grid_2015')
-grid_2016_burn <- read_cals_burn(grid_2016., name = 'grid_2016')
-grid_2017_burn <- read_cals_burn(grid_2017., name = 'grid_2017')
-grid_2018_burn <- read_cals_burn(grid_2018., name = 'grid_2018')
-grid_2019_burn <- read_cals_burn(grid_2019., name = 'grid_2019')
-grid_2020_burn <- read_cals_burn(grid_2020., name = 'grid_2020')
+# grid_2011_burn <- read_cals_burn(grid_2011., name = 'grid_2011')
+# grid_2012_burn <- read_cals_burn(grid_2012., name = 'grid_2012')
+# grid_2013_burn <- read_cals_burn(grid_2013., name = 'grid_2013')
+# grid_2014_burn <- read_cals_burn(grid_2014., name = 'grid_2014')
+# grid_2015_burn <- read_cals_burn(grid_2015., name = 'grid_2015')
+# grid_2016_burn <- read_cals_burn(grid_2016., name = 'grid_2016')
+# grid_2017_burn <- read_cals_burn(grid_2017., name = 'grid_2017')
+# grid_2018_burn <- read_cals_burn(grid_2018., name = 'grid_2018')
+# grid_2019_burn <- read_cals_burn(grid_2019., name = 'grid_2019')
+# grid_2020_burn <- read_cals_burn(grid_2020., name = 'grid_2020')
 grid_all_burn <- read_cals_burn(grid_all.c, name = 'grid_all')
 
-grid_burn <- bind_rows(grid_2011_burn, 
-                  grid_2012_burn, 
-                  grid_2013_burn, 
-                  grid_2014_burn, 
-                  grid_2015_burn,
-                  grid_2016_burn, 
-                  grid_2017_burn, 
-                  grid_2018_burn, 
-                  grid_2019_burn, 
-                  grid_2020_burn,
-                  grid_all_burn) %>%
+# grid_burn <- bind_rows(grid_2011_burn, 
+#                   grid_2012_burn, 
+#                   grid_2013_burn, 
+#                   grid_2014_burn, 
+#                   grid_2015_burn,
+#                   grid_2016_burn, 
+#                   grid_2017_burn, 
+#                   grid_2018_burn, 
+#                   grid_2019_burn, 
+#                   grid_2020_burn,
+#                   grid_all_burn) %>%
+#   mutate(input_data = 'grid') %>%
+#   mutate(year_missing_almost = gsub('grid_', '', cal)) %>%
+#   mutate(year_missing = gsub('all', 'none', year_missing_almost)) %>%
+#   dplyr::select(-c(year_missing_almost))
+
+grid_burn <- grid_all_burn %>%
   mutate(input_data = 'grid') %>%
@@
 # now do statn burn params
-statn_2011_burn <- read_cals_burn(statn_2011, name = 'statn_2011')
-statn_2012_burn <- read_cals_burn(statn_2012, name = 'statn_2012')
-statn_2013_burn <- read_cals_burn(statn_2013, name = 'statn_2013')
-statn_2014_burn <- read_cals_burn(statn_2014, name = 'statn_2014')
-statn_2015_burn <- read_cals_burn(statn_2015, name = 'statn_2015')
-statn_2016_burn <- read_cals_burn(statn_2016, name = 'statn_2016')
-statn_2017_burn <- read_cals_burn(statn_2017, name = 'statn_2017')
-statn_2018_burn <- read_cals_burn(statn_2018, name = 'statn_2018')
-statn_2019_burn <- read_cals_burn(statn_2019, name = 'statn_2019')
-statn_2020_burn <- read_cals_burn(statn_2020, name = 'statn_2020')
+# statn_2011_burn <- read_cals_burn(statn_2011, name = 'statn_2011')
+# statn_2012_burn <- read_cals_burn(statn_2012, name = 'statn_2012')
+# statn_2013_burn <- read_cals_burn(statn_2013, name = 'statn_2013')
+# statn_2014_burn <- read_cals_burn(statn_2014, name = 'statn_2014')
+# statn_2015_burn <- read_cals_burn(statn_2015, name = 'statn_2015')
+# statn_2016_burn <- read_cals_burn(statn_2016, name = 'statn_2016')
+# statn_2017_burn <- read_cals_burn(statn_2017, name = 'statn_2017')
+# statn_2018_burn <- read_cals_burn(statn_2018, name = 'statn_2018')
+# statn_2019_burn <- read_cals_burn(statn_2019, name = 'statn_2019')
+# statn_2020_burn <- read_cals_burn(statn_2020, name = 'statn_2020')
 statn_all_burn <- read_cals_burn(statn_all., name = 'statn_all')
 
-statn_burn <- bind_rows(statn_2011_burn, 
-                  statn_2012_burn, 
-                  statn_2013_burn, 
-                  statn_2014_burn, 
-                  statn_2015_burn,
-                  statn_2016_burn, 
-                  statn_2017_burn, 
-                  statn_2018_burn, 
-                  statn_2019_burn, 
-                  statn_2020_burn,
-                  statn_all_burn) %>%
+# statn_burn <- bind_rows(statn_2011_burn, 
+#                   statn_2012_burn, 
+#                   statn_2013_burn, 
+#                   statn_2014_burn, 
+#                   statn_2015_burn,
+#                   statn_2016_burn, 
+#                   statn_2017_burn, 
+#                   statn_2018_burn, 
+#                   statn_2019_burn, 
+#                   statn_2020_burn,
+#                   statn_all_burn) %>%
+#   mutate(input_data = 'statn') %>%
+#   mutate(year_missing_almost = gsub('statn_', '', cal)) %>%
+#   mutate(year_missing = gsub('all', 'none', year_missing_almost)) %>%
+#   dplyr::select(-c(year_missing_almost))
+
+statn_burn <- statn_all_burn %>%
   mutate(input_data = 'statn') %>%
@@
 
-ggplot(params_combo, aes(x=burn, y=value, fill=input_data)) +
-  geom_boxplot() +
-  facet_wrap(~param, scales = 'free_y')
-
-write_csv(params_combo, '/Users/megansears/Documents/Repos/fourmile/38HRU_sept2013_updates/params_burn_unburn.csv')
+# ggplot(params_combo, aes(x=burn, y=value, fill=input_data)) +
+#   geom_boxplot() +
+#   facet_wrap(~param, scales = 'free_y')
+# 
+# write_csv(params_combo, '/Users/megansears/Documents/Repos/fourmile/38HRU_sept2013_updates/params_burn_unburn.csv')
 
@@
 
-write_csv(params_weighted, '/Users/megansears/Documents/Repos/fourmile/38HRU_sept2013_updates/params_weighted_sept2013_edits.csv')
+#write_csv(params_weighted, '/Users/megansears/Documents/Repos/fourmile/38HRU_sept2013_updates/params_weighted_sept2013_edits.csv')
 
@@
 ```
-
-# Outlet results
-
-## Hydrograph
-
-```{r hydrographs, echo = FALSE, message = FALSE, warning = FALSE}
-
-setwd('/Users/megansears/Documents/Repos/fourmile/38HRU_sept2013_updates')
-
-flow <- read_csv('discharge_all.csv') %>%
-  replace(.==-9999, NA) %>%
-  rename(date = time) %>%
-  mutate(date = mdy(date))
-
-flow_pivot <- flow %>%
-  pivot_longer(!date, names_to = 'cal_run', values_to = 'q_m3s') %>%
-  mutate(year = as.factor(year(date)))
-
-q <- ggplot(flow_pivot, aes(date, q_m3s, color = cal_run)) +
-  geom_line() +
-  scale_color_manual(name="cal_run", values=c('obs' = 'black',
-                                            "grid_2011"="seagreen",
-                                            "grid_2012"="seagreen2",
-                                            "grid_2013"="steelblue",
-                                            "grid_2014"='dodgerblue',
-                                            "grid_2015" = "cyan3",
-                                            'grid_2016' = 'blue',
-                                            'grid_2017' = 'blue4',
-                                            'grid_2018' = 'cadetblue',
-                                            'grid_2019' = 'lightgreen',
-                                            'grid_2020' = 'olivedrab',
-                                            'grid_all' = 'steelblue3',
-                                            "statn_2011"="maroon",
-                                            "statn_2012"="deeppink4",
-                                            "statn_2013"="deeppink",
-                                            "statn_2014"='purple',
-                                            "statn_2015" = "mediumorchid1",
-                                            'statn_2016' = 'indianred',
-                                            'statn_2017' = 'sienna',
-                                            'statn_2018' = 'salmon2',
-                                            'statn_2019' = 'mediumpurple1',
-                                            'statn_2020' = 'violetred',
-                                            'statn_all' = 'red'))
-
-ggplotly(q)
-
-```
-
-## Cumulative volume
-
-```{r cumq, echo = FALSE, message = FALSE, warning = FALSE}
-
-flow_cumq <- flow_pivot %>%
-  mutate(month = month(date)) %>%
-  filter(month %in% c(4:9)) %>%
-  dplyr::select(-month) %>%
-  #pivot_longer(!date, names_to = 'cal_run', values_to = 'q_m3s') %>%
-  mutate(vol_m3 = q_m3s * 86400) %>% 
-  group_by(cal_run, year(date)) %>%
-  mutate(cumsum = cumsum(replace_na(vol_m3, 0))) %>%
-  #rename(year = 4) %>%
-  mutate(year = as.factor(year)) %>%
-  ungroup()
-
-#plot annual cumulative Q vals for ensembles
-plot_cumulq_yr_ <- function(calyear) {
-  {flow_cumq %>%
-    filter(year == calyear) %>%
-    ggplot(aes(x = date,
-               y = cumsum,
-               color = cal_run)) +
-    geom_line() +
-scale_color_manual(name="cal_run", values=c('obs' = 'black',
-                                            "grid_2011"="seagreen",
-                                            "grid_2012"="seagreen2",
-                                            "grid_2013"="steelblue",
-                                            "grid_2014"='dodgerblue',
-                                            "grid_2015" = "cyan3",
-                                            'grid_2016' = 'blue',
-                                            'grid_2017' = 'blue4',
-                                            'grid_2018' = 'cadetblue',
-                                            'grid_2019' = 'lightgreen',
-                                            'grid_2020' = 'olivedrab',
-                                            'grid_all' = 'steelblue3',
-                                            "statn_2011"="maroon",
-                                            "statn_2012"="deeppink4",
-                                            "statn_2013"="deeppink",
-                                            "statn_2014"='purple',
-                                            "statn_2015" = "mediumorchid1",
-                                            'statn_2016' = 'indianred',
-                                            'statn_2017' = 'sienna',
-                                            'statn_2018' = 'salmon2',
-                                            'statn_2019' = 'mediumpurple1',
-                                            'statn_2020' = 'violetred',
-                                            'statn_all' = 'red')) +
-    ggtitle(calyear) +
-    theme_bw() +
-    labs(y = 'Volume (m^3)')} %>%
-    ggplotly()
-}
-
-name <- levels(flow_cumq$year)
-
-cumulative_plots <- lapply(name, plot_cumulq_yr_)
-
-htmltools::tagList(cumulative_plots)
-
-cumulative_plots
-
-```
-
-## KGE
-
-### Overall KGE
-
-```{r kge overall, echo = FALSE, message = FALSE, warning = FALSE}
-
-flow_kge_all <- flow %>%
-  summarize(grid2011 = KGE(grid_2011, obs),
-            grid2012 = KGE(grid_2012, obs),
-            grid2013 = KGE(grid_2013, obs),
-            grid2014 = KGE(grid_2014, obs),
-            grid2015 = KGE(grid_2015, obs),
-            grid2016 = KGE(grid_2016, obs),
-            grid2017 = KGE(grid_2017, obs),
-            grid2018 = KGE(grid_2018, obs),
-            grid2019 = KGE(grid_2019, obs),
-            grid2020 = KGE(grid_2020, obs),
-            gridall = KGE(grid_all, obs),
-            statn2011 = KGE(statn_2011, obs),
-            statn2012 = KGE(statn_2012, obs),
-            statn2013 = KGE(statn_2013, obs),
-            statn2014 = KGE(statn_2014, obs),
-            statn2015 = KGE(statn_2015, obs),
-            statn2016 = KGE(statn_2016, obs),
-            statn2017 = KGE(statn_2017, obs),
-            statn2018 = KGE(statn_2018, obs),
-            statn2019 = KGE(statn_2019, obs),
-            statn2020 = KGE(statn_2020, obs),
-            statnall = KGE(statn_all, obs)) %>%
-    mutate_if(is.numeric,
-            round,
-            digits = 2)
-
-flow_kge_all <- flow_kge_all %>%
-  pivot_longer(everything()) %>%
-  arrange(value)
-
-kable(flow_kge_all) %>%
-  kable_styling(full_width = F)
-
-```
-
-### KGE by year
-
-```{r kge by year, echo = FALSE, message = FALSE, warning = FALSE}
-
-flow_year <- flow %>%
-  mutate(year = year(date)) %>%
-  group_by(year) %>%
-  summarize(grid2011 = KGE(grid_2011, obs),
-            grid2012 = KGE(grid_2012, obs),
-            grid2013 = KGE(grid_2013, obs),
-            grid2014 = KGE(grid_2014, obs),
-            grid2015 = KGE(grid_2015, obs),
-            grid2016 = KGE(grid_2016, obs),
-            grid2017 = KGE(grid_2017, obs),
-            grid2018 = KGE(grid_2018, obs),
-            grid2019 = KGE(grid_2019, obs),
-            grid2020 = KGE(grid_2020, obs),
-            gridall = KGE(grid_all, obs),
-            statn2011 = KGE(statn_2011, obs),
-            statn2012 = KGE(statn_2012, obs),
-            statn2013 = KGE(statn_2013, obs),
-            statn2014 = KGE(statn_2014, obs),
-            statn2015 = KGE(statn_2015, obs),
-            statn2016 = KGE(statn_2016, obs),
-            statn2017 = KGE(statn_2017, obs),
-            statn2018 = KGE(statn_2018, obs),
-            statn2019 = KGE(statn_2019, obs),
-            statn2020 = KGE(statn_2020, obs),
-            statnall = KGE(statn_all, obs)) %>%
-    mutate_if(is.numeric,
-            round,
-            digits = 2)
-
-flow_kge <- flow_year %>%
-  pivot_longer(!year, names_to = 'model_run', values_to = 'kge') %>%
-  pivot_wider(names_from = 'year', values_from = 'kge')
-
-flow_kge %>%
-  kable(.) %>%
-  kable_styling()
-
-flow_plot <- flow_year %>%
-  pivot_longer(!year, names_to = 'model_run', values_to = 'kge') %>%
-  mutate(year = as.factor(year))
-
-# add all to the plot below
-kge_all <- flow_kge_all %>%
-  mutate(year = 'all years') %>%
-  rename(model_run = name,
-         kge = value)
-
-flow_plot_updated <- bind_rows(flow_plot, kge_all)
-
-ggplot(flow_plot_updated, aes(x = model_run, y = year, fill = kge)) +
-  geom_tile(color = "white") +
-  scale_fill_viridis_c(option = "viridis", name = "KGE", direction = -1) +
-  geom_text(aes(label = round(kge, 2)), color = "grey", size = 2.5) +
-  theme_bw() +
-  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
-  labs(y = "Year")
-
-```
-
-### Annual KGE plots
-
-```{r wy plots, echo = FALSE, message = FALSE, warning = FALSE}
-
-plot_kge <- function(calyear) {
-  flow_plot %>%
-    filter(year == calyear) %>%
-    ggplot(aes(x = model_run,
-               y = kge)) +
-    geom_point(size=3) +
-    ggtitle(calyear) +
-    theme_bw() +
-    theme(axis.text.x = element_text(angle = 45, hjust=1))
-}
-
-name <- levels(flow_plot$year)
-
-lapply(name, plot_kge)
-
-```
-
-## Pbias
-
-### Overall pbias
-
-```{r pbias overall, echo = FALSE, message = FALSE, warning = FALSE}
-
-flow_pbias_all <- flow %>%
-  summarize(grid2011 = pbias(grid_2011, obs),
-            grid2012 = pbias(grid_2012, obs),
-            grid2013 = pbias(grid_2013, obs),
-            grid2014 = pbias(grid_2014, obs),
-            grid2015 = pbias(grid_2015, obs),
-            grid2016 = pbias(grid_2016, obs),
-            grid2017 = pbias(grid_2017, obs),
-            grid2018 = pbias(grid_2018, obs),
-            grid2019 = pbias(grid_2019, obs),
-            grid2020 = pbias(grid_2020, obs),
-            gridall = pbias(grid_all, obs),
-            statn2011 = pbias(statn_2011, obs),
-            statn2012 = pbias(statn_2012, obs),
-            statn2013 = pbias(statn_2013, obs),
-            statn2014 = pbias(statn_2014, obs),
-            statn2015 = pbias(statn_2015, obs),
-            statn2016 = pbias(statn_2016, obs),
-            statn2017 = pbias(statn_2017, obs),
-            statn2018 = pbias(statn_2018, obs),
-            statn2019 = pbias(statn_2019, obs),
-            statn2020 = pbias(statn_2020, obs),
-            statnall = pbias(statn_all, obs)) %>%
-    mutate_if(is.numeric,
-            round,
-            digits = 2)
-
-flow_pbias_all <- flow_pbias_all %>%
-  pivot_longer(everything()) %>%
-  arrange(abs(value))
-
-kable(flow_pbias_all) %>%
-  kable_styling(full_width = F)
-
-```
-
-### Pbias by year
-
-```{r pbias by year, echo = FALSE, message = FALSE, warning = FALSE}
-
-flow_year <- flow %>%
-  mutate(year = year(date)) %>%
-  group_by(year) %>%
-  summarize(grid2011 = pbias(grid_2011, obs),
-            grid2012 = pbias(grid_2012, obs),
-            grid2013 = pbias(grid_2013, obs),
-            grid2014 = pbias(grid_2014, obs),
-            grid2015 = pbias(grid_2015, obs),
-            grid2016 = pbias(grid_2016, obs),
-            grid2017 = pbias(grid_2017, obs),
-            grid2018 = pbias(grid_2018, obs),
-            grid2019 = pbias(grid_2019, obs),
-            grid2020 = pbias(grid_2020, obs),
-            gridall = pbias(grid_all, obs),
-            statn2011 = pbias(statn_2011, obs),
-            statn2012 = pbias(statn_2012, obs),
-            statn2013 = pbias(statn_2013, obs),
-            statn2014 = pbias(statn_2014, obs),
-            statn2015 = pbias(statn_2015, obs),
-            statn2016 = pbias(statn_2016, obs),
-            statn2017 = pbias(statn_2017, obs),
-            statn2018 = pbias(statn_2018, obs),
-            statn2019 = pbias(statn_2019, obs),
-            statn2020 = pbias(statn_2020, obs),
-            statnall = pbias(statn_all, obs)) %>%
-    mutate_if(is.numeric,
-            round,
-            digits = 2)
-
-flow_pbias <- flow_year %>%
-  pivot_longer(!year, names_to = 'model_run', values_to = 'pbias') %>%
-  pivot_wider(names_from = 'year', values_from = 'pbias')
-
-flow_pbias %>%
-  kable(.) %>%
-  kable_styling()
-
-flow_plot <- flow_year %>%
-  pivot_longer(!year, names_to = 'model_run', values_to = 'pbias') %>%
-  mutate(year = as.factor(year))
-
-# add all to the plot below
-pbias_all <- flow_pbias_all %>%
-  mutate(year = 'all years') %>%
-  rename(model_run = name,
-         pbias = value)
-
-flow_plot_updated <- bind_rows(flow_plot, pbias_all)
-
-ggplot(flow_plot_updated, aes(x = model_run, y = year, fill = pbias)) +
-  geom_tile(color = "white") +
-   scale_fill_gradient2(low = "blue", mid = "white", high = "red", midpoint = 0, name = "Pbias") +
-  geom_text(aes(label = round(pbias, 2)), color = "black", size = 2.5) +
-  theme_bw() +
-  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
-  labs(y = "Year")
-
-```
-
-### Annual Pbias plots
-
-```{r pbias plots, echo = FALSE, message = FALSE, warning = FALSE}
-
-plot_pbias <- function(calyear) {
-  flow_plot %>%
-    filter(year == calyear) %>%
-    ggplot(aes(x = model_run,
-               y = pbias)) +
-    geom_point(size=3) +
-    ggtitle(calyear) +
-    theme_bw() +
-    theme(axis.text.x = element_text(angle = 45, hjust=1))
-}
-
-name <- levels(flow_plot$year)
-
-lapply(name, plot_pbias)
-
-```
-
-<!-- # Ensembles -->
-
-<!-- ## Hydrograph -->
-
-<!-- ```{r ensemble hydrographs, echo = F} -->
-
-<!-- ensem <- flow %>% -->
-<!--   rowwise() %>% -->
-<!--   mutate(grid_ensemble = mean(c(grid_2011, grid_2012, -->
-<!--                                 grid_2013, grid_2014, -->
-<!--                                 grid_2015, grid_2016, -->
-<!--                                 grid_2017, grid_2018, -->
-<!--                                 grid_2019, grid_2020)), -->
-<!--          statn_ensemble = mean(c(statn_2011, statn_2012, -->
-<!--                                  statn_2013, statn_2014, -->
-<!--                                  statn_2015, statn_2016, -->
-<!--                                  statn_2017, statn_2018, -->
-<!--                                  statn_2019, statn_2020)), -->
-<!--          all_ensemble = mean(c(grid_2011, grid_2012, -->
-<!--                                grid_2013, grid_2014, -->
-<!--                                grid_2015, grid_2016, -->
-<!--                                grid_2017, grid_2018, -->
-<!--                                grid_2019, grid_2020, -->
-<!--                                statn_2011, statn_2012, -->
-<!--                                statn_2013, statn_2014, -->
-<!--                                statn_2015, statn_2016, -->
-<!--                                statn_2017, statn_2018, -->
-<!--                                statn_2019, statn_2020, -->
-<!--                                grid_all, statn_all))) %>% -->
-<!--   dplyr::select(date, grid_ensemble, statn_ensemble, -->
-<!--          all_ensemble, grid_all, -->
-<!--          statn_all, obs) -->
-
-<!-- ensem_pivot <- ensem %>% -->
-<!--   pivot_longer(!date, names_to = 'cal_run', values_to = 'q_m3s') %>% -->
-<!--   mutate(year = as.factor(year(date))) -->
-
-<!-- q_ensemble <- ggplot(ensem_pivot, aes(date, q_m3s, color = cal_run)) + -->
-<!--   geom_line() + -->
-<!--   scale_color_manual(name="cal_run", values=c('obs'='black', -->
-<!--                                             "grid_ensemble"="maroon", -->
-<!--                                             "statn_ensemble"="darkturquoise", -->
-<!--                                             "grid_all"="purple1", -->
-<!--                                             "statn_all"='springgreen4', -->
-<!--                                             "all_ensemble" = "orange")) + -->
-<!--   scale_y_continuous(name = 'Q_m3s') + -->
-<!--   theme_bw() -->
-
-<!-- q_ensemble -->
-
-<!-- ``` -->
-
-<!-- ## KGE -->
-
-<!-- ### KGE for ensembles (entire period) -->
-
-<!-- ```{r ensemble kge, echo = F} -->
-
-<!-- ensem_kge_all <- ensem %>% -->
-<!--   ungroup() %>% -->
-<!--   summarize(grid_ensemble = KGE(grid_ensemble, obs), -->
-<!--             statn_ensemble = KGE(statn_ensemble, obs), -->
-<!--             all_ensemble = KGE(all_ensemble, obs), -->
-<!--             grid_all = KGE(grid_all, obs), -->
-<!--             statn_all = KGE(statn_all, obs)) %>% -->
-<!--     mutate_if(is.numeric, -->
-<!--             round, -->
-<!--             digits = 2) -->
-
-<!-- kable(ensem_kge_all) %>% -->
-<!--   kable_styling(full_width = F) -->
-
-<!-- ``` -->
-
-<!-- ### Annual KGEs for ensembles -->
-
-<!-- ```{r annual kge ensemble, echo = F} -->
-
-<!-- yr_kge_ensem <- ensem %>% -->
-<!--   ungroup() %>% -->
-<!--   mutate(year = year(date)) %>% -->
-<!--   group_by(year) %>% -->
-<!--   summarize(grid_ensemble = KGE(grid_ensemble, obs), -->
-<!--             statn_ensemble = KGE(statn_ensemble, obs), -->
-<!--             all_ensemble = KGE(all_ensemble, obs), -->
-<!--             grid_all = KGE(grid_all, obs), -->
-<!--             statn_all = KGE(statn_all, obs)) %>% -->
-<!--     mutate_if(is.numeric, -->
-<!--             round, -->
-<!--             digits = 2) -->
-
-<!-- yr_kge_table <- yr_kge_ensem %>% -->
-<!--   pivot_longer(!year, names_to = 'model_run', values_to = 'kge') %>% -->
-<!--   pivot_wider(names_from = 'year', values_from = 'kge') -->
-
-<!-- yr_kge_table %>% -->
-<!--   kable(.) %>% -->
-<!--   kable_styling() -->
-
-<!-- yr_kge_plot <- yr_kge_ensem %>% -->
-<!--   pivot_longer(!year, names_to = 'model_run', values_to = 'kge') %>% -->
-<!--   mutate(year = as.factor(year)) -->
-
-<!-- #plot annual kge vals for ensembles -->
-<!-- plot_kge_yr_ensem <- function(calyear) { -->
-<!--   yr_kge_plot %>% -->
-<!--     filter(year == calyear) %>% -->
-<!--     ggplot(aes(x = model_run, -->
-<!--                y = kge)) + -->
-<!--     geom_col() + -->
-<!--     ggtitle(calyear) + -->
-<!--     theme_bw() + -->
-<!--     theme(axis.text.x = element_text(angle = 45, hjust=1)) -->
-<!-- } -->
-
-<!-- name <- levels(yr_kge_plot$year) -->
-
-<!-- lapply(name, plot_kge_yr_ensem) -->
-
-<!-- ``` -->
-
-<!-- ### Monthly KGEs for ensembles -->
-
-<!-- ```{r monthly kge ensemble, echo = F} -->
-
-<!-- mo_kge <- ensem %>% -->
-<!--   ungroup() %>% -->
-<!--   drop_na() %>% -->
-<!--   mutate(month = month(date)) %>% -->
-<!--   group_by(month) %>% -->
-<!--   summarize(grid_ensemble = KGE(grid_ensemble, obs), -->
-<!--             statn_ensemble = KGE(statn_ensemble, obs), -->
-<!--             all_ensemble = KGE(all_ensemble, obs), -->
-<!--             grid_all = KGE(grid_all, obs), -->
-<!--             statn_all = KGE(statn_all, obs)) %>% -->
-<!--     mutate_if(is.numeric, -->
-<!--             round, -->
-<!--             digits = 2) -->
-
-<!-- kable(mo_kge) %>% -->
-<!--   kable_styling(full_width = F) -->
-
-<!-- mo_pivot <- mo_kge %>% -->
-<!--   pivot_longer(!month, names_to = 'cal_run', values_to = 'KGE') %>% -->
-<!--   drop_na() -->
-
-<!-- kge_plot_mo <- ggplot(mo_pivot, aes(month, KGE, color = cal_run)) + geom_point(size = 3) + -->
-<!--     scale_color_manual(name="cal_run", values=c("grid_ensemble"="maroon", -->
-<!--                                             "statn_ensemble"="darkturquoise", -->
-<!--                                             "grid_all"="purple1", -->
-<!--                                             "statn_all"='springgreen4', -->
-<!--                                             "all_ensemble" = "orange")) + -->
-<!--   theme_bw() -->
-
-<!-- ggplotly(kge_plot_mo) -->
-
-<!-- ``` -->
-
-<!-- ## RMSE -->
-
-<!-- ### Ensemble RMSE for entire period -->
-
-<!-- ```{r ensemble rmse, echo = F} -->
-
-<!-- ensem_rmse_all <- ensem %>% -->
-<!--   ungroup() %>% -->
-<!--   summarize(grid_ensemble = rmse(grid_ensemble, obs), -->
-<!--             statn_ensemble = rmse(statn_ensemble, obs), -->
-<!--             all_ensemble = rmse(all_ensemble, obs), -->
-<!--             grid_all = rmse(grid_all, obs), -->
-<!--             statn_all = rmse(statn_all, obs)) %>% -->
-<!--     mutate_if(is.numeric, -->
-<!--             round, -->
-<!--             digits = 4) -->
-
-<!-- kable(ensem_rmse_all) %>% -->
-<!--   kable_styling(full_width = F) -->
-
-<!-- ``` -->
-
-<!-- ### Annual RMSE for ensembles -->
-
-<!-- ```{r annual rmse ensem, echo = F} -->
-
-<!-- yr_rmse_ensem <- ensem %>% -->
-<!--   ungroup() %>% -->
-<!--   mutate(year = year(date)) %>% -->
-<!--   group_by(year) %>% -->
-<!--   summarize(grid_ensemble = rmse(grid_ensemble, obs), -->
-<!--             statn_ensemble = rmse(statn_ensemble, obs), -->
-<!--             all_ensemble = rmse(all_ensemble, obs), -->
-<!--             grid_all = rmse(grid_all, obs), -->
-<!--             statn_all = rmse(statn_all, obs)) %>% -->
-<!--     mutate_if(is.numeric, -->
-<!--             round, -->
-<!--             digits = 4) -->
-
-<!-- yr_rmse_table <- yr_rmse_ensem %>% -->
-<!--   pivot_longer(!year, names_to = 'model_run', values_to = 'rmse') %>% -->
-<!--   pivot_wider(names_from = 'year', values_from = 'rmse') -->
-
-<!-- yr_rmse_table %>% -->
-<!--   kable(.) %>% -->
-<!--   kable_styling() -->
-
-<!-- yr_rmse_plot <- yr_rmse_ensem %>% -->
-<!--   pivot_longer(!year, names_to = 'model_run', values_to = 'rmse') %>% -->
-<!--   mutate(year = as.factor(year)) -->
-
-<!-- #plot annual rmse vals for ensembles -->
-<!-- plot_rmse_yr_ensem <- function(calyear) { -->
-<!--   yr_rmse_plot %>% -->
-<!--     filter(year == calyear) %>% -->
-<!--     ggplot(aes(x = model_run, -->
-<!--                y = rmse)) + -->
-<!--     geom_col() + -->
-<!--     ggtitle(calyear) + -->
-<!--     theme_bw() + -->
-<!--     theme(axis.text.x = element_text(angle = 45, hjust=1)) -->
-<!-- } -->
-
-<!-- name <- levels(yr_rmse_plot$year) -->
-
-<!-- lapply(name, plot_rmse_yr_ensem) -->
-
-<!-- ``` -->
-
-<!-- ### Monthly RMSEs for ensembles -->
-
-<!-- ```{r month ensem rmse, echo = F} -->
-
-<!-- mo_rmse <- ensem %>% -->
-<!--   ungroup() %>% -->
-<!--   drop_na() %>% -->
-<!--   mutate(month = month(date)) %>% -->
-<!--   group_by(month) %>% -->
-<!--   summarize(grid_ensemble = rmse(grid_ensemble, obs), -->
-<!--             statn_ensemble = rmse(statn_ensemble, obs), -->
-<!--             all_ensemble = rmse(all_ensemble, obs), -->
-<!--             grid_all = rmse(grid_all, obs), -->
-<!--             statn_all = rmse(statn_all, obs)) %>% -->
-<!--     mutate_if(is.numeric, -->
-<!--             round, -->
-<!--             digits = 4) -->
-
-<!-- kable(mo_rmse) %>% -->
-<!--   kable_styling(full_width = F) -->
-
-<!-- mo_pivot2 <- mo_rmse %>% -->
-<!--   pivot_longer(!month, names_to = 'cal_run', values_to = 'RMSE') %>% -->
-<!--   drop_na() -->
-
-<!-- rmse_plot_mo <- ggplot(mo_pivot2, aes(month, RMSE, color = cal_run)) + geom_point(size = 3) + -->
-<!--     scale_color_manual(name="cal_run", values=c("grid_ensemble"="maroon", -->
-<!--                                             "statn_ensemble"="darkturquoise", -->
-<!--                                             "grid_all"="purple1", -->
-<!--                                             "statn_all"='springgreen4', -->
-<!--                                             "all_ensemble" = "orange")) + -->
-<!--   theme_bw() -->
-
-<!-- ggplotly(rmse_plot_mo) -->
-
-<!-- ``` -->
-
-<!-- ## NSE -->
-
-<!-- ### Ensemble NSE for entire period -->
-
-<!-- ```{r nse all, echo = F} -->
-
-<!-- ensem_nse_all <- ensem %>% -->
-<!--   ungroup() %>% -->
-<!--   summarize(grid_ensemble = NSE(grid_ensemble, obs), -->
-<!--             statn_ensemble = NSE(statn_ensemble, obs), -->
-<!--             all_ensemble = NSE(all_ensemble, obs), -->
-<!--             grid_all = NSE(grid_all, obs), -->
-<!--             statn_all = NSE(statn_all, obs)) %>% -->
-<!--     mutate_if(is.numeric, -->
-<!--             round, -->
-<!--             digits = 2) -->
-
-<!-- kable(ensem_nse_all) %>% -->
-<!--   kable_styling(full_width = F) -->
-
-<!-- ``` -->
-
-<!-- ### Annual NSE for ensembles -->
-
-<!-- ```{r annual nse, echo = F} -->
-
-<!-- yr_nse_ensem <- ensem %>% -->
-<!--   ungroup() %>% -->
-<!--   mutate(year = year(date)) %>% -->
-<!--   group_by(year) %>% -->
-<!--   summarize(grid_ensemble = NSE(grid_ensemble, obs), -->
-<!--             statn_ensemble = NSE(statn_ensemble, obs), -->
-<!--             all_ensemble = NSE(all_ensemble, obs), -->
-<!--             grid_all = NSE(grid_all, obs), -->
-<!--             statn_all = NSE(statn_all, obs)) %>% -->
-<!--     mutate_if(is.numeric, -->
-<!--             round, -->
-<!--             digits = 4) -->
-
-<!-- yr_nse_table <- yr_nse_ensem %>% -->
-<!--   pivot_longer(!year, names_to = 'model_run', values_to = 'nse') %>% -->
-<!--   pivot_wider(names_from = 'year', values_from = 'nse') -->
-
-<!-- yr_nse_table %>% -->
-<!--   kable(.) %>% -->
-<!--   kable_styling() -->
-
-<!-- yr_nse_plot <- yr_nse_ensem %>% -->
-<!--   pivot_longer(!year, names_to = 'model_run', values_to = 'nse') %>% -->
-<!--   mutate(year = as.factor(year)) -->
-
-<!-- #plot annual nse vals for ensembles -->
-<!-- plot_nse_yr_ensem <- function(calyear) { -->
-<!--   yr_nse_plot %>% -->
-<!--     filter(year == calyear) %>% -->
-<!--     ggplot(aes(x = model_run, -->
-<!--                y = nse)) + -->
-<!--     geom_col() + -->
-<!--     ggtitle(calyear) + -->
-<!--     theme_bw() + -->
-<!--     theme(axis.text.x = element_text(angle = 45, hjust=1)) -->
-<!-- } -->
-
-<!-- name <- levels(yr_nse_plot$year) -->
-
-<!-- lapply(name, plot_nse_yr_ensem) -->
-
-<!-- ``` -->
-
-<!-- ### Monthly NSE for ensembles -->
-
-<!-- ```{r monthly rmse, echo =F} -->
-
-<!-- mo_nse <- ensem %>% -->
-<!--   ungroup() %>% -->
-<!--   drop_na() %>% -->
-<!--   mutate(month = month(date)) %>% -->
-<!--   group_by(month) %>% -->
-<!--   summarize(grid_ensemble = NSE(grid_ensemble, obs), -->
-<!--             statn_ensemble = NSE(statn_ensemble, obs), -->
-<!--             all_ensemble = NSE(all_ensemble, obs), -->
-<!--             grid_all = NSE(grid_all, obs), -->
-<!--             statn_all = NSE(statn_all, obs)) %>% -->
-<!--     mutate_if(is.numeric, -->
-<!--             round, -->
-<!--             digits = 4) -->
-
-<!-- kable(mo_nse) %>% -->
-<!--   kable_styling(full_width = F) -->
-
-<!-- mo_pivot2 <- mo_nse %>% -->
-<!--   pivot_longer(!month, names_to = 'cal_run', values_to = 'nse') %>% -->
-<!--   drop_na() -->
-
-<!-- nse_plot_mo <- ggplot(mo_pivot2, aes(month, nse, color = cal_run)) + geom_point(size = 3) + -->
-<!--   theme_bw() + -->
-<!--   scale_color_manual(name="cal_run", values=c("grid_ensemble"="maroon", -->
-<!--                                             "statn_ensemble"="darkturquoise", -->
-<!--                                             "grid_all"="purple1", -->
-<!--                                             "statn_all"='springgreen4', -->
-<!--                                             "all_ensemble" = "orange")) -->
-
-<!-- ggplotly(nse_plot_mo) -->
-
-<!-- ``` -->
-
-<!-- # Catchment results -->
-
-<!-- ## Precip -->
-
-<!-- ```{r catch precip, echo = F} -->
-<!-- setwd("/Users/megansears/Documents/Repos/fourmile/catchment_output") -->
-
-<!-- statn <- read_csv('statnall.csv') -->
-<!-- grid <- read_csv('gridall.csv') -->
-
-<!-- grid <- grid %>% mutate(site = 'grid') -->
-<!-- statn <- statn %>% mutate(site = 'statn') -->
-
-<!-- catchment <- bind_rows(grid, statn) %>% -->
-<!--   mutate(year = as.factor(year(time))) %>% -->
-<!--   group_by(year, site) %>% -->
-<!--   mutate(cumulative_p = cumsum(precip)) -->
-
-<!-- #plot cumulative precip by year -->
-<!-- plot_cumprecip <- function(calyear) { -->
-<!--   {catchment %>% -->
-<!--     filter(year == calyear) %>% -->
-<!--     ggplot(aes(x = time, -->
-<!--                y = cumulative_p, color = site)) + -->
-<!--     geom_line(size=1) + -->
-<!--     ggtitle(calyear) + -->
-<!--     ylab('Cumulative precip (mm)') + -->
-<!--     theme_bw() + -->
-<!--     theme(axis.text.x = element_text(angle = 45, hjust=1))} %>% -->
-<!--     ggplotly() -->
-<!-- } -->
-
-<!-- name <- levels(catchment$year) -->
-
-<!-- precip_plots <- lapply(name, plot_cumprecip) -->
-
-<!-- htmltools::tagList(precip_plots) -->
-
-<!-- precip_plots -->
-
-<!-- ## total P -->
-<!-- max_cumulativep <- catchment %>% -->
-<!--   group_by(year, site) %>% -->
-<!--   summarize(total_cumulativep = max(cumulative_p)) -->
-
-<!-- ggplot(max_cumulativep, aes(x=year, y=total_cumulativep, color=site)) + -->
-<!--   geom_point(size=3) + -->
-<!--   ggtitle('Total cumulative precip (mm) by year') -->
-
-<!-- ``` -->
-
-<!-- ## Tmean -->
-
-<!-- ```{r tmean catch, echo = F} -->
-<!-- ## tmean -->
-<!-- tmean <- catchment %>% -->
-<!--   group_by(year, site) %>% -->
-<!--   summarize(tmean = mean(tmean)) %>% -->
-<!--   ggplot(aes(x = year, y=tmean, color = site)) + -->
-<!--   geom_point(size=3) + -->
-<!--   ggtitle('Average temp by year') -->
-
-<!-- tmean -->
-
-<!-- ``` -->
-
-# RD and RG
-
-- **Different units than streamflow (cms) and volume (m3)** 
-- **All in mm**
-
-```{r rd and rg, echo = FALSE, message = FALSE, warning = FALSE, fig.width = 14, fig.asp = 1, out.width = "100%"}
-
-gw_gridall <- read_csv(here('38HRU_sept2013_updates/catchment_output/grid_all.csv'), skip = 3) %>%
-  slice(-c(1,2)) %>%
-  dplyr::select(time, catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w) %>%
-  mutate(source = 'grid_all') %>%
-  mutate(across(c(catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w), as.numeric))
-
-gw_statnall <- read_csv(here('38HRU_sept2013_updates/catchment_output/statn_all.csv'), skip = 3) %>%
-  slice(-c(1,2)) %>%
-  dplyr::select(time, catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w) %>%
-  mutate(source = 'statn_all') %>%
-  mutate(across(c(catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w), as.numeric))
-
-# gw_grid2011 <- read_csv(here('38HRU_sept2013_updates/catchment_output/grid_2011.csv'), skip = 3) %>%
-#   slice(-c(1,2)) %>%
-#   dplyr::select(time, catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w) %>%
-#   mutate(source = 'grid_2011')%>%
-#   mutate(across(c(catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w), as.numeric))
-# 
-# gw_grid2012 <- read_csv(here('38HRU_sept2013_updates/catchment_output/grid_2012.csv'), skip = 3) %>%
-#   slice(-c(1,2)) %>%
-#   dplyr::select(time, catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w) %>%
-#   mutate(source = 'grid_2012')%>%
-#   mutate(across(c(catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w), as.numeric))
-# 
-# gw_grid2013 <- read_csv(here('38HRU_sept2013_updates/catchment_output/grid_2013.csv'), skip = 3) %>%
-#   slice(-c(1,2)) %>%
-#   dplyr::select(time, catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w) %>%
-#   mutate(source = 'grid_2013')%>%
-#   mutate(across(c(catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w), as.numeric))
-# 
-# gw_grid2014 <- read_csv(here('38HRU_sept2013_updates/catchment_output/grid_2014.csv'), skip = 3) %>%
-#   slice(-c(1,2)) %>%
-#   dplyr::select(time, catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w) %>%
-#   mutate(source = 'grid_2014')%>%
-#   mutate(across(c(catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w), as.numeric))
-# 
-# gw_grid2015 <- read_csv(here('38HRU_sept2013_updates/catchment_output/grid_2015.csv'), skip = 3) %>%
-#   slice(-c(1,2)) %>%
-#   dplyr::select(time, catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w) %>%
-#   mutate(source = 'grid_2015')%>%
-#   mutate(across(c(catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w), as.numeric))
-# 
-# gw_grid2016 <- read_csv(here('38HRU_sept2013_updates/catchment_output/grid_2016.csv'), skip = 3) %>%
-#   slice(-c(1,2)) %>%
-#   dplyr::select(time, catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w) %>%
-#   mutate(source = 'grid_2016')%>%
-#   mutate(across(c(catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w), as.numeric))
-# 
-# gw_grid2017 <- read_csv(here('38HRU_sept2013_updates/catchment_output/grid_2017.csv'), skip = 3) %>%
-#   slice(-c(1,2)) %>%
-#   dplyr::select(time, catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w) %>%
-#   mutate(source = 'grid_2017')%>%
-#   mutate(across(c(catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w), as.numeric))
-# 
-# gw_grid2018 <- read_csv(here('38HRU_sept2013_updates/catchment_output/grid_2018.csv'), skip = 3) %>%
-#   slice(-c(1,2)) %>%
-#   dplyr::select(time, catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w) %>%
-#   mutate(source = 'grid_2018')%>%
-#   mutate(across(c(catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w), as.numeric))
-# 
-# gw_grid2019 <- read_csv(here('38HRU_sept2013_updates/catchment_output/grid_2019.csv'), skip = 3) %>%
-#   slice(-c(1,2)) %>%
-#   dplyr::select(time, catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w) %>%
-#   mutate(source = 'grid_2019')%>%
-#   mutate(across(c(catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w), as.numeric))
-# 
-# gw_grid2020 <- read_csv(here('38HRU_sept2013_updates/catchment_output/grid_2020.csv'), skip = 3) %>%
-#   slice(-c(1,2)) %>%
-#   dplyr::select(time, catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w) %>%
-#   mutate(source = 'grid_2020')%>%
-#   mutate(across(c(catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w), as.numeric))
-# 
-# gw_statn2011 <- read_csv(here('38HRU_sept2013_updates/catchment_output/statn_2011.csv'), skip = 3) %>%
-#   slice(-c(1,2)) %>%
-#   dplyr::select(time, catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w) %>%
-#   mutate(source = 'statn_2011')%>%
-#   mutate(across(c(catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w), as.numeric))
-# 
-# gw_statn2012 <- read_csv(here('38HRU_sept2013_updates/catchment_output/statn_2012.csv'), skip = 3) %>%
-#   slice(-c(1,2)) %>%
-#   dplyr::select(time, catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w) %>%
-#   mutate(source = 'statn_2012')%>%
-#   mutate(across(c(catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w), as.numeric))
-# 
-# gw_statn2013 <- read_csv(here('38HRU_sept2013_updates/catchment_output/statn_2013.csv'), skip = 3) %>%
-#   slice(-c(1,2)) %>%
-#   dplyr::select(time, catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w) %>%
-#   mutate(source = 'statn_2013')%>%
-#   mutate(across(c(catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w), as.numeric))
-# 
-# gw_statn2014 <- read_csv(here('38HRU_sept2013_updates/catchment_output/statn_2014.csv'), skip = 3) %>%
-#   slice(-c(1,2)) %>%
-#   dplyr::select(time, catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w) %>%
-#   mutate(source = 'statn_2014')%>%
-#   mutate(across(c(catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w), as.numeric))
-# 
-# gw_statn2015 <- read_csv(here('38HRU_sept2013_updates/catchment_output/statn_2015.csv'), skip = 3) %>%
-#   slice(-c(1,2)) %>%
-#   dplyr::select(time, catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w) %>%
-#   mutate(source = 'statn_2015')%>%
-#   mutate(across(c(catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w), as.numeric))
-# 
-# gw_statn2016 <- read_csv(here('38HRU_sept2013_updates/catchment_output/statn_2016.csv'), skip = 3) %>%
-#   slice(-c(1,2)) %>%
-#   dplyr::select(time, catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w) %>%
-#   mutate(source = 'statn_2016')%>%
-#   mutate(across(c(catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w), as.numeric))
-# 
-# gw_statn2017 <- read_csv(here('38HRU_sept2013_updates/catchment_output/statn_2017.csv'), skip = 3) %>%
-#   slice(-c(1,2)) %>%
-#   dplyr::select(time, catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w) %>%
-#   mutate(source = 'statn_2017')%>%
-#   mutate(across(c(catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w), as.numeric))
-# 
-# gw_statn2018 <- read_csv(here('38HRU_sept2013_updates/catchment_output/statn_2018.csv'), skip = 3) %>%
-#   slice(-c(1,2)) %>%
-#   dplyr::select(time, catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w) %>%
-#   mutate(source = 'statn_2018')%>%
-#   mutate(across(c(catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w), as.numeric))
-# 
-# gw_statn2019 <- read_csv(here('38HRU_sept2013_updates/catchment_output/statn_2019.csv'), skip = 3) %>%
-#   slice(-c(1,2)) %>%
-#   dplyr::select(time, catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w) %>%
-#   mutate(source = 'statn_2019')%>%
-#   mutate(across(c(catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w), as.numeric))
-# 
-# gw_statn2020 <- read_csv(here('38HRU_sept2013_updates/catchment_output/statn_2020.csv'), skip = 3) %>%
-#   slice(-c(1,2)) %>%
-#   dplyr::select(time, catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w) %>%
-#   mutate(source = 'statn_2020')%>%
-#   mutate(across(c(catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w), as.numeric))
-
-gw <- bind_rows(
-  gw_gridall, gw_statnall
-  # gw_grid2011, gw_grid2012,
-  # gw_grid2013, gw_grid2014,
-  # gw_grid2015, gw_grid2016,
-  # gw_grid2017, gw_grid2018,
-  # gw_grid2019, gw_grid2020,
-  # gw_statn2011, gw_statn2012,
-  # gw_statn2013, gw_statn2014,
-  # gw_statn2015, gw_statn2016,
-  # gw_statn2017, gw_statn2018,
-  # gw_statn2019, gw_statn2020
-) %>%
-  mutate(date = ymd(time),
-         year = year(date)) %>%
-  arrange(date)
-
-ggplot(gw, aes(x=date, color = source)) +
-  geom_line(aes(y=catchmentRD1_w), size =1) +
-  facet_wrap(~year, scales = 'free', ncol = 2) +
-  scale_x_date(labels = date_format("%b")) +
-  ggtitle('RD1') +
-  theme(text = element_text(size = 20)) +
-  labs(y = 'RD1 (mm)')
-
-ggplot(gw, aes(x=date, color = source)) +
-  geom_line(aes(y=catchmentRD2_w), size =1) +
-  facet_wrap(~year, scales = 'free', ncol = 2) +
-  scale_x_date(labels = date_format("%b")) +
-  ggtitle('RD2') +
-  theme(text = element_text(size = 20))+
-  labs(y = 'RD2 (mm)')
-
-ggplot(gw, aes(x=date, color = source)) +
-  geom_line(aes(y=catchmentRG1_w), size =1) +
-  facet_wrap(~year, scales = 'free', ncol = 2) +
-  scale_x_date(labels = date_format("%b")) +
-  ggtitle('RG1') +
-  theme(text = element_text(size = 20)) +
-  labs(y = 'RG1 (mm)')
-
-ggplot(gw, aes(x=date, color = source)) +
-  geom_line(aes(y=catchmentRG2_w), size =1) +
-  facet_wrap(~year, scales = 'free', ncol=2) +
-  scale_x_date(labels = date_format("%b")) +
-  ggtitle('RG2') +
-  theme(text = element_text(size = 20))+
-  labs(y = 'RG2 (mm)')
-
-gw <- gw %>%
-  arrange(date) %>%
-  group_by(year, source) %>%
-  mutate(RD1cumsum = cumsum(catchmentRD1_w),
-         RD2cumsum = cumsum(catchmentRD2_w),
-         RG1cumsum = cumsum(catchmentRG1_w),
-         RG2cumsum = cumsum(catchmentRG2_w))
-
-ggplot(gw, aes(x=date, color = source)) +
-  geom_line(aes(y=RD1cumsum), size =1) +
-  facet_wrap(~year, scales = 'free', ncol=2) +
-  scale_x_date(labels = date_format("%b")) +
-  ggtitle('Cumulative RD1 (mm)') +
-  theme(text = element_text(size = 20))
-
-ggplot(gw, aes(x=date, color = source)) +
-  geom_line(aes(y=RD2cumsum), size = 1) +
-  facet_wrap(~year, scales = 'free', ncol=2) +
-  scale_x_date(labels = date_format("%b")) +
-  ggtitle('Cumulative RD2 (mm)') +
-  theme(text = element_text(size = 20))
-
-ggplot(gw, aes(x=date, color = source)) +
-  geom_line(aes(y=RG1cumsum), size  = 1) +
-  facet_wrap(~year, scales = 'free', ncol = 2) +
-  scale_x_date(labels = date_format("%b")) +
-  ggtitle('Cumulative RG1 (mm)') +
-  theme(text = element_text(size = 20))
-
-ggplot(gw, aes(x=date, color = source)) +
-  geom_line(aes(y=RG2cumsum), size =1) +
-  facet_wrap(~year, scales = 'free', ncol = 2) +
-  scale_x_date(labels = date_format("%b")) +
-  ggtitle('Cumulative RG2 (mm)') +
-  theme(text = element_text(size = 20))
-
-```
-
-```{r rd and rg sums, echo = FALSE, message = FALSE, warning = FALSE, fig.width = 22, fig.asp = 1.5, out.width = "100%"}
-
-##################
-# all 4 with facets
-
-ggplot(gw, aes(x=date)) +
-  geom_line(aes(y=RG2cumsum, color = 'cumulative RG2'), size =1) +
-  geom_line(aes(y=RG1cumsum, color = 'cumulative RG1'), size =1) +
-  geom_line(aes(y=RD1cumsum, color = 'cumulative RD1'), size =1) +
-  geom_line(aes(y=RD2cumsum, color = 'cumulative RD2'), size =1) +
-  scale_x_date(labels = date_format("%b")) +
-  facet_wrap(~year + source, scales = 'free_x', ncol=2) +
-  ggtitle('Cumulative RD and RG (mm)') +
-  theme(text = element_text(size = 24))
-
-```
-
-```{r gw boxplot, echo = FALSE, message = FALSE, warning = FALSE}
-
-gw_maxcumsum <- gw %>%
-  group_by(source, year) %>%
-  summarize(yr_cum_RD1 = max(RD1cumsum),
-            yr_cum_RD2 = max(RD2cumsum),
-            yr_cum_RG1 = max(RG1cumsum),
-            yr_cum_RG2 = max(RG2cumsum)) %>%
-  mutate(year = as.factor(year)) %>%
-  pivot_longer(!c(year, source), names_to = 'flow_type', values_to = 'flow_cms')
-
-ggplot(gw_maxcumsum, aes(x = flow_type, y = flow_cms, fill = source)) +
-  geom_boxplot(position = position_dodge(1)) +
-  geom_point(position=position_jitterdodge(),alpha=0.3) +
-  ggtitle('Annual sum') +
-  labs(y = 'mm of water')
-
-ggplot(gw_maxcumsum, aes(x = flow_type, y = flow_cms, fill = source)) +
-  geom_boxplot(position = position_dodge(1)) +
-  geom_point(position=position_jitterdodge(),alpha=0.3) +
-  #geom_point(aes(color = source)) +
-  facet_wrap(~flow_type, scales = 'free') +
-  ggtitle('Annual sum') +
-  labs(y = 'mm of water')
-
-```
-
-### RD and RG by season
-
-- January-February = baseflow_winter
-- March-June = snowmelt
-- July-August = Monsoon
-- September-December = Baseflow_fall
-
-```{r flow season, echo = FALSE, message = FALSE, warning = FALSE, fig.width = 12, fig.asp = 0.75, out.width = "100%"}
-
-#group by season and get max sums by season
-flow_season <- gw %>%
-  dplyr::select(catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w, date, year, source) %>%
-  mutate(month = month(date)) %>%
-  mutate(season = case_when(month %in% c(3,4,5,6) ~ 'snowmelt',
-                            month %in% c(7,8) ~ 'monsoon',
-                            month %in% c(9,10,11,12) ~ 'baseflow_fall',
-                            month %in% c(1,2) ~ 'baseflow_winter')) %>%
-  group_by(source, year, season) %>%
-  mutate(yr_season_RD1 = cumsum(catchmentRD1_w),
-            yr_season_RD2 = cumsum(catchmentRD2_w),
-            yr_season_RG1 = cumsum(catchmentRG1_w),
-            yr_season_RG2 = cumsum(catchmentRG2_w)) %>%
-  summarize(sumRD1 = max(yr_season_RD1),
-            sumRD2 = max(yr_season_RD2),
-            sumRG1 = max(yr_season_RG1),
-            sumRG2 = max(yr_season_RG2)) %>%
-            pivot_longer(!c(year, source, season), names_to = 'flow_type', values_to = 'mm_water')
-
-flow_season %>%
-  ggplot(aes(x = flow_type, y = mm_water, fill = source)) +
-  geom_boxplot(position = position_dodge(1)) +
-  #geom_point(position=position_jitterdodge(),alpha=0.3) +
-  #geom_point(aes(color = source)) +
-  facet_wrap(~season) +
-  ggtitle('RD/RG sums (mm)') +
-  theme_bw() +
-  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
-  theme(text = element_text(size = 20)) +
-  labs(y = 'RD/RG sums (mm)')
-
-flow_season %>%
-  ggplot(aes(x = flow_type, y = mm_water, fill = source)) +
-  geom_boxplot(position = position_dodge(1)) +
-  geom_point(position=position_jitterdodge(),alpha=0.3) +
-  #geom_point(aes(color = source)) +
-  facet_wrap(~season + flow_type, scales = 'free') +
-  ggtitle('Seasonal sums') +
-  theme_bw() +
-  theme(text = element_text(size = 20)) +
-  labs(y = 'RD/RG seasonal sums (mm)')
-
-```
-
-# HRU results
-
-```{r cumulative tmean for HRUs, echo = F}
-hrus <- st_read('/Users/megansears/Documents/Repos/fourmile/38HRU_sept2013_updates/hrus_final.shp')
-
-mapview(hrus)
-
-locations <- read_csv('/Users/megansears/Documents/Repos/fourmile/38HRU_sept2013_updates/fourmile_sensors.csv')
-
-locations <- locations %>%
-  st_as_sf(., coords=c('y','x'), crs = 4326)
-
-#grid first
-setwd("/Users/megansears/Documents/Repos/fourmile/38HRU_sept2013_updates/HRU_output/grid")
-
-read_ages_grid <- function(dataframe){
-  read_csv(dataframe, skip = 3) %>%
-  slice(3:n()) %>%
-  dplyr::select(-starts_with('@'),
-                -1) %>%
-  mutate(time = ymd(time)) %>%
-  mutate_if(is.character, as.numeric) %>%
-  mutate(source = 'grid')
-
-}
-
-#pull in all filenames with HRU in the name
-filenames <- list.files(".", pattern="HRU", full.names=F)
-
-#read all the csvs using read_ages function
-dataframes <- lapply(filenames, read_ages_grid)
-
-#name all the csvs based on first 6 characters
-names(dataframes) <- substr(filenames, 1, 6)
-
-#bind all and make 1 df
-hru_grids <- dataframes %>%
-  bind_rows()
-
-#statn next
-setwd("/Users/megansears/Documents/Repos/fourmile/38HRU_sept2013_updates/HRU_output/statn")
-
-read_ages_statn <- function(dataframe){
-  read_csv(dataframe, skip = 3) %>%
-  slice(3:n()) %>%
-  dplyr::select(-starts_with('@'),
-                -1) %>%
-  mutate(time = ymd(time)) %>%
-  mutate_if(is.character, as.numeric) %>%
-  mutate(source = 'statn')
-
-}
-
-#pull in all filenames with HRU in the name
-filenames <- list.files(".", pattern="HRU", full.names=F)
-
-#read all the csvs using read_ages function
-dataframes <- lapply(filenames, read_ages_statn)
-
-#name all the csvs based on first 6 characters
-names(dataframes) <- substr(filenames, 1, 6)
-
-#bind all and make 1 df
-hru_statn <- dataframes %>%
-  bind_rows()
-
-# #get rid of a bunch of data
-# hru_grid_tmean <- hru_grids %>%
-#   dplyr::select(c(time, ID, tmean)) %>%
-#   rename(tmean_grid = tmean)  %>%
-#   group_by(ID) %>%
-#   summarize(tmean_all_grid = mean(tmean_grid))
-# 
-# hru_statn_tmean <- hru_statn %>%
-#   dplyr::select(c(time, ID, tmean)) %>%
-#   rename(tmean_statn = tmean) %>%
-#   group_by(ID) %>%
-#   summarize(tmean_all_statn = mean(tmean_statn))
-# 
-# tmean_hrus <- left_join(hru_grid_tmean, hru_statn_tmean, by = c('ID')) %>%
-#   mutate(diff = tmean_all_statn - tmean_all_grid) %>%
-#   rename(value = ID)
-# 
-# hrus_map_tmean <- left_join(hrus, tmean_hrus, by = 'value')
-# 
-# tmap_mode('view')
-# 
-# locations_t <- locations %>%
-#   dplyr::filter(name %in% c('Gordon_South', 'Gordon_North',
-#                         'Betasso', 'Niwot_Snotel',
-#                         'University Camp SNTL'))
-# 
-# tm_shape(hrus_map_tmean) +
-#   tm_polygons('diff', id = 'value',
-#               breaks = c(-6,-4,-2,0,2,4,6)) +
-# tm_shape(locations_t) +
-#   tm_symbols(col='blue', size=4)
-
-```
-
-## Tmean difference
-Station - grid
-
-```{r}
-#get rid of a bunch of data
-hru_grid_tmean <- hru_grids %>%
-  dplyr::select(c(time, ID, tmean)) %>%
-  rename(tmean_grid = tmean)  %>%
-  group_by(ID) %>%
-  summarize(tmean_all_grid = mean(tmean_grid))
-
-hru_statn_tmean <- hru_statn %>%
-  dplyr::select(c(time, ID, tmean)) %>%
-  rename(tmean_statn = tmean) %>%
-  group_by(ID) %>%
-  summarize(tmean_all_statn = mean(tmean_statn))
-
-tmean_hrus <- left_join(hru_grid_tmean, hru_statn_tmean, by = c('ID')) %>%
-  mutate(diff = tmean_all_statn - tmean_all_grid) %>%
-  rename(value = ID)
-
-hrus_map_tmean <- left_join(hrus, tmean_hrus, by = 'value')
-
-tmean <- ggplot() +
-  geom_sf(data = hrus_map_tmean, aes(fill = diff), color = "black", lwd = 0.2) +
-  scale_fill_viridis_c(option = "plasma", name = "Tmean difference (°C)",
-                       limits = c(-5, 2)) +
-  theme_bw(base_size=13.5) +
-  theme_void() +
-  theme(
-    legend.position = "bottom",
-    panel.grid.major = element_blank(),
-    panel.grid.minor = element_blank(),
-    axis.title.x = element_blank(),
-    axis.title.y = element_blank())
-
-tmean
-
-```
-
-### Tmean season
-
-- Dec-Mar: Winter
-- Apr-Jun: Snowmelt/spring
-- Jul-Aug: Monsoon
-- Sep-Nov: Baseflow/fall
-
-```{r}
-############################
-### look at month
-#get rid of a bunch of data
-hru_grid_tmean_jan <- hru_grids %>%
-  dplyr::select(c(time, ID, tmean)) %>%
-  rename(tmean_grid = tmean)  %>%
-  mutate(month = month(time)) %>%
-  filter(month %in% c(12,1,2,3)) %>%
-  group_by(ID) %>%
-  summarize(tmean_all_grid = mean(tmean_grid))
-
-hru_statn_tmean_jan <- hru_statn %>%
-  dplyr::select(c(time, ID, tmean)) %>%
-  rename(tmean_statn = tmean) %>%
-  mutate(month = month(time)) %>%
-  filter(month %in% c(12,1,2,3)) %>%
-  group_by(ID) %>%
-  summarize(tmean_all_statn = mean(tmean_statn))
-
-tmean_hrus_jan <- left_join(hru_grid_tmean_jan, hru_statn_tmean_jan, by = c('ID')) %>%
-  mutate(diff = tmean_all_statn - tmean_all_grid) %>%
-  rename(value = ID)
-
-hrus_map_tmean_jan <- left_join(hrus, tmean_hrus_jan, by = 'value')
-
-tmean_jan <- ggplot() +
-  geom_sf(data = hrus_map_tmean_jan, aes(fill = diff), color = "black", lwd = 0.2) +
-  scale_fill_viridis_c(option = "plasma", name = "Tmean difference (°C)",
-                       limits = c(-5, 3)) +
-  theme_bw(base_size=13.5) +
-  theme_void() +
-  theme(
-    legend.position = "bottom",
-    panel.grid.major = element_blank(),
-    panel.grid.minor = element_blank(),
-    axis.title.x = element_blank(),
-    axis.title.y = element_blank()) +
-  ggtitle('Winter')
-
-#tmean_jan
-
-## 
-hru_grid_tmean_apr <- hru_grids %>%
-  dplyr::select(c(time, ID, tmean)) %>%
-  rename(tmean_grid = tmean)  %>%
-  mutate(month = month(time)) %>%
-  filter(month %in% c(4,5,6)) %>%
-  group_by(ID) %>%
-  summarize(tmean_all_grid = mean(tmean_grid))
-
-hru_statn_tmean_apr <- hru_statn %>%
-  dplyr::select(c(time, ID, tmean)) %>%
-  rename(tmean_statn = tmean) %>%
-  mutate(month = month(time)) %>%
-  filter(month %in% c(4,5,6)) %>%
-  group_by(ID) %>%
-  summarize(tmean_all_statn = mean(tmean_statn))
-
-tmean_hrus_apr <- left_join(hru_grid_tmean_apr, hru_statn_tmean_apr, by = c('ID')) %>%
-  mutate(diff = tmean_all_statn - tmean_all_grid) %>%
-  rename(value = ID)
-
-hrus_map_tmean_apr <- left_join(hrus, tmean_hrus_apr, by = 'value')
-
-tmean_apr <- ggplot() +
-  geom_sf(data = hrus_map_tmean_apr, aes(fill = diff), color = "black", lwd = 0.2) +
-  scale_fill_viridis_c(option = "plasma", name = "Tmean difference (°C)",
-                       limits = c(-5, 3)) +
-  theme_bw(base_size=13.5) +
-  theme_void() +
-  theme(
-    legend.position = "bottom",
-    panel.grid.major = element_blank(),
-    panel.grid.minor = element_blank(),
-    axis.title.x = element_blank(),
-    axis.title.y = element_blank()) +
-  ggtitle('Snowmelt')
-
-#tmean_apr
-
-#### 
-hru_grid_tmean_jul <- hru_grids %>%
-  dplyr::select(c(time, ID, tmean)) %>%
-  rename(tmean_grid = tmean)  %>%
-  mutate(month = month(time)) %>%
-  filter(month %in% c(7,8)) %>%
-  group_by(ID) %>%
-  summarize(tmean_all_grid = mean(tmean_grid))
-
-hru_statn_tmean_jul <- hru_statn %>%
-  dplyr::select(c(time, ID, tmean)) %>%
-  rename(tmean_statn = tmean) %>%
-  mutate(month = month(time)) %>%
-  filter(month %in% c(7,8)) %>%
-  group_by(ID) %>%
-  summarize(tmean_all_statn = mean(tmean_statn))
-
-tmean_hrus_jul <- left_join(hru_grid_tmean_jul, hru_statn_tmean_jul, by = c('ID')) %>%
-  mutate(diff = tmean_all_statn - tmean_all_grid) %>%
-  rename(value = ID)
-
-hrus_map_tmean_jul <- left_join(hrus, tmean_hrus_jul, by = 'value')
-
-tmean_jul <- ggplot() +
-  geom_sf(data = hrus_map_tmean_jul, aes(fill = diff), color = "black", lwd = 0.2) +
-  scale_fill_viridis_c(option = "plasma", name = "Tmean difference (°C)",
-                            limits = c(-5, 3)) +
-  theme_bw(base_size=13.5) +
-  theme_void() +
-  theme(
-    legend.position = "bottom",
-    panel.grid.major = element_blank(),
-    panel.grid.minor = element_blank(),
-    axis.title.x = element_blank(),
-    axis.title.y = element_blank()) +
-  ggtitle('Monsoon')
-
-#tmean_jul
-
-##
-
-hru_grid_tmean_sep <- hru_grids %>%
-  dplyr::select(c(time, ID, tmean)) %>%
-  rename(tmean_grid = tmean)  %>%
-  mutate(month = month(time)) %>%
-  filter(month %in% c(9,10,11)) %>%
-  group_by(ID) %>%
-  summarize(tmean_all_grid = mean(tmean_grid))
-
-hru_statn_tmean_sep <- hru_statn %>%
-  dplyr::select(c(time, ID, tmean)) %>%
-  rename(tmean_statn = tmean) %>%
-  mutate(month = month(time)) %>%
-  filter(month %in% c(9,10,11)) %>%
-  group_by(ID) %>%
-  summarize(tmean_all_statn = mean(tmean_statn))
-
-tmean_hrus_sep <- left_join(hru_grid_tmean_sep, hru_statn_tmean_sep, by = c('ID')) %>%
-  mutate(diff = tmean_all_statn - tmean_all_grid) %>%
-  rename(value = ID)
-
-hrus_map_tmean_sep <- left_join(hrus, tmean_hrus_sep, by = 'value')
-
-tmean_sep <- ggplot() +
-  geom_sf(data = hrus_map_tmean_sep, aes(fill = diff), color = "black", lwd = 0.2) +
-  scale_fill_viridis_c(option = "plasma", name = "Tmean difference (°C)",
-                       limits = c(-5, 3)) +
-  theme_bw(base_size=13.5) +
-  theme_void() +
-  theme(
-    legend.position = "bottom",
-    panel.grid.major = element_blank(),
-    panel.grid.minor = element_blank(),
-    axis.title.x = element_blank(),
-    axis.title.y = element_blank()) +
-  ggtitle('Fall')
-
-#tmean_sep
-###
-
-lots <- ggarrange(tmean_jan,
-                  tmean_apr,
-                  tmean_jul,
-                  tmean_sep) 
-          #nrow = 4)
-          #ncol= 0)
-lots
-
-```
-
-## Tmax difference
-
-```{r tmax, echo = F}
-
-# #get rid of a bunch of data
-# hru_grid_tmax <- hru_grids %>%
-#   dplyr::select(c(time, ID, tmax)) %>%
-#   rename(tmax_grid = tmax)  %>%
-#   group_by(ID) %>%
-#   summarize(tmax_all_grid = mean(tmax_grid))
-# 
-# hru_statn_tmax <- hru_statn %>%
-#   dplyr::select(c(time, ID, tmax)) %>%
-#   rename(tmax_statn = tmax) %>%
-#   group_by(ID) %>%
-#   summarize(tmax_all_statn = mean(tmax_statn))
-# 
-# tmax_hrus <- left_join(hru_grid_tmax, hru_statn_tmax, by = c('ID')) %>%
-#   mutate(diff = tmax_all_statn - tmax_all_grid) %>%
-#   rename(value = ID)
-# 
-# hrus_map_tmax <- left_join(hrus, tmax_hrus, by = 'value')
-# 
-# tmap_mode('view')
-# 
-# locations_t <- locations %>%
-#   dplyr::filter(name %in% c('Gordon_South', 'Gordon_North',
-#                         'Betasso', 'Niwot_Snotel',
-#                         'University Camp SNTL'))
-# 
-# tm_shape(hrus_map_tmax) +
-#   tm_polygons('diff', id = 'value',
-#               breaks = c(-6,-4,-2,0,2,4,6)) +
-# tm_shape(locations_t) +
-#   tm_symbols(col='blue', size=4)
-
-# T max
-#get rid of a bunch of data
-hru_grid_tmax <- hru_grids %>%
-  dplyr::select(c(time, ID, tmax)) %>%
-  rename(tmax_grid = tmax)  %>%
-  group_by(ID) %>%
-  summarize(tmax_all_grid = mean(tmax_grid))
-
-hru_statn_tmax <- hru_statn %>%
-  dplyr::select(c(time, ID, tmax)) %>%
-  rename(tmax_statn = tmax) %>%
-  group_by(ID) %>%
-  summarize(tmax_all_statn = mean(tmax_statn))
-
-tmax_hrus <- left_join(hru_grid_tmax, hru_statn_tmax, by = c('ID')) %>%
-  mutate(diff = tmax_all_statn - tmax_all_grid) %>%
-  rename(value = ID)
-
-hrus_map_tmax <- left_join(hrus, tmax_hrus, by = 'value')
-
-tmax <- ggplot() +
-  geom_sf(data = hrus_map_tmax, aes(fill = diff), color = "black", lwd = 0.2) +
-  scale_fill_viridis_c(option = "plasma", name = "Tmax difference (°C)",
-                       limits = c(-5, 2)) +
-  theme_bw(base_size=13.5) +
-  theme_void() +
-  theme(
-    legend.position = "bottom",
-    panel.grid.major = element_blank(),
-    panel.grid.minor = element_blank(),
-    axis.title.x = element_blank(),
-    axis.title.y = element_blank())
-
-tmax
-
-```
-
-### Tmax season
-
-- Dec-Mar: Winter
-- Apr-Jun: Snowmelt/spring
-- Jul-Aug: Monsoon
-- Sep-Nov: Baseflow/fall
-
-```{r}
-############################
-### look at month
-#get rid of a bunch of data
-hru_grid_tmax_jan <- hru_grids %>%
-  dplyr::select(c(time, ID, tmax)) %>%
-  rename(tmax_grid = tmax)  %>%
-  mutate(month = month(time)) %>%
-  filter(month %in% c(12,1,2,3)) %>%
-  group_by(ID) %>%
-  summarize(tmax_all_grid = mean(tmax_grid))
-
-hru_statn_tmax_jan <- hru_statn %>%
-  dplyr::select(c(time, ID, tmax)) %>%
-  rename(tmax_statn = tmax) %>%
-  mutate(month = month(time)) %>%
-  filter(month %in% c(12,1,2,3)) %>%
-  group_by(ID) %>%
-  summarize(tmax_all_statn = mean(tmax_statn))
-
-tmax_hrus_jan <- left_join(hru_grid_tmax_jan, hru_statn_tmax_jan, by = c('ID')) %>%
-  mutate(diff = tmax_all_statn - tmax_all_grid) %>%
-  rename(value = ID)
-
-hrus_map_tmax_jan <- left_join(hrus, tmax_hrus_jan, by = 'value')
-
-tmax_jan <- ggplot() +
-  geom_sf(data = hrus_map_tmax_jan, aes(fill = diff), color = "black", lwd = 0.2) +
-  scale_fill_viridis_c(option = "plasma", name = "tmax difference (°C)",
-                       limits = c(-5.1, 3)) +
-  theme_bw(base_size=13.5) +
-  theme_void() +
-  theme(
-    legend.position = "bottom",
-    panel.grid.major = element_blank(),
-    panel.grid.minor = element_blank(),
-    axis.title.x = element_blank(),
-    axis.title.y = element_blank()) +
-  ggtitle('Winter')
-
-#tmax_jan
-
-## 
-hru_grid_tmax_apr <- hru_grids %>%
-  dplyr::select(c(time, ID, tmax)) %>%
-  rename(tmax_grid = tmax)  %>%
-  mutate(month = month(time)) %>%
-  filter(month %in% c(4,5,6)) %>%
-  group_by(ID) %>%
-  summarize(tmax_all_grid = mean(tmax_grid))
-
-hru_statn_tmax_apr <- hru_statn %>%
-  dplyr::select(c(time, ID, tmax)) %>%
-  rename(tmax_statn = tmax) %>%
-  mutate(month = month(time)) %>%
-  filter(month %in% c(4,5,6)) %>%
-  group_by(ID) %>%
-  summarize(tmax_all_statn = mean(tmax_statn))
-
-tmax_hrus_apr <- left_join(hru_grid_tmax_apr, hru_statn_tmax_apr, by = c('ID')) %>%
-  mutate(diff = tmax_all_statn - tmax_all_grid) %>%
-  rename(value = ID)
-
-hrus_map_tmax_apr <- left_join(hrus, tmax_hrus_apr, by = 'value')
-
-tmax_apr <- ggplot() +
-  geom_sf(data = hrus_map_tmax_apr, aes(fill = diff), color = "black", lwd = 0.2) +
-  scale_fill_viridis_c(option = "plasma", name = "tmax difference (°C)",
-                       limits = c(-5.1, 3)) +
-  theme_bw(base_size=13.5) +
-  theme_void() +
-  theme(
-    legend.position = "bottom",
-    panel.grid.major = element_blank(),
-    panel.grid.minor = element_blank(),
-    axis.title.x = element_blank(),
-    axis.title.y = element_blank()) +
-  ggtitle('Snowmelt')
-
-#tmax_apr
-
-#### 
-hru_grid_tmax_jul <- hru_grids %>%
-  dplyr::select(c(time, ID, tmax)) %>%
-  rename(tmax_grid = tmax)  %>%
-  mutate(month = month(time)) %>%
-  filter(month %in% c(7,8)) %>%
-  group_by(ID) %>%
-  summarize(tmax_all_grid = mean(tmax_grid))
-
-hru_statn_tmax_jul <- hru_statn %>%
-  dplyr::select(c(time, ID, tmax)) %>%
-  rename(tmax_statn = tmax) %>%
-  mutate(month = month(time)) %>%
-  filter(month %in% c(7,8)) %>%
-  group_by(ID) %>%
-  summarize(tmax_all_statn = mean(tmax_statn))
-
-tmax_hrus_jul <- left_join(hru_grid_tmax_jul, hru_statn_tmax_jul, by = c('ID')) %>%
-  mutate(diff = tmax_all_statn - tmax_all_grid) %>%
-  rename(value = ID)
-
-hrus_map_tmax_jul <- left_join(hrus, tmax_hrus_jul, by = 'value')
-
-tmax_jul <- ggplot() +
-  geom_sf(data = hrus_map_tmax_jul, aes(fill = diff), color = "black", lwd = 0.2) +
-  scale_fill_viridis_c(option = "plasma", name = "tmax difference (°C)",
-                            limits = c(-5.1, 3)) +
-  theme_bw(base_size=13.5) +
-  theme_void() +
-  theme(
-    legend.position = "bottom",
-    panel.grid.major = element_blank(),
-    panel.grid.minor = element_blank(),
-    axis.title.x = element_blank(),
-    axis.title.y = element_blank()) +
-  ggtitle('Monsoon')
-
-#tmax_jul
-
-##
-
-hru_grid_tmax_sep <- hru_grids %>%
-  dplyr::select(c(time, ID, tmax)) %>%
-  rename(tmax_grid = tmax)  %>%
-  mutate(month = month(time)) %>%
-  filter(month %in% c(9,10,11)) %>%
-  group_by(ID) %>%
-  summarize(tmax_all_grid = mean(tmax_grid))
-
-hru_statn_tmax_sep <- hru_statn %>%
-  dplyr::select(c(time, ID, tmax)) %>%
-  rename(tmax_statn = tmax) %>%
-  mutate(month = month(time)) %>%
-  filter(month %in% c(9,10,11)) %>%
-  group_by(ID) %>%
-  summarize(tmax_all_statn = mean(tmax_statn))
-
-tmax_hrus_sep <- left_join(hru_grid_tmax_sep, hru_statn_tmax_sep, by = c('ID')) %>%
-  mutate(diff = tmax_all_statn - tmax_all_grid) %>%
-  rename(value = ID)
-
-hrus_map_tmax_sep <- left_join(hrus, tmax_hrus_sep, by = 'value')
-
-tmax_sep <- ggplot() +
-  geom_sf(data = hrus_map_tmax_sep, aes(fill = diff), color = "black", lwd = 0.2) +
-  scale_fill_viridis_c(option = "plasma", name = "tmax difference (°C)",
-                       limits = c(-5.1, 3)) +
-  theme_bw(base_size=13.5) +
-  theme_void() +
-  theme(
-    legend.position = "bottom",
-    panel.grid.major = element_blank(),
-    panel.grid.minor = element_blank(),
-    axis.title.x = element_blank(),
-    axis.title.y = element_blank()) +
-  ggtitle('Fall')
-
-#tmax_sep
-###
-
-lots <- ggarrange(tmax_jan,
-                  tmax_apr,
-                  tmax_jul,
-                  tmax_sep) 
-          #nrow = 4)
-          #ncol= 0)
-lots
-
-```
-
-## Tmin difference
-
-```{r tmin, echo = F}
-
-# #get rid of a bunch of data
-# hru_grid_tmin <- hru_grids %>%
-#   dplyr::select(c(time, ID, tmin)) %>%
-#   rename(tmin_grid = tmin)  %>%
-#   group_by(ID) %>%
-#   summarize(tmin_all_grid = mean(tmin_grid))
-# 
-# hru_statn_tmin <- hru_statn %>%
-#   dplyr::select(c(time, ID, tmin)) %>%
-#   rename(tmin_statn = tmin) %>%
-#   group_by(ID) %>%
-#   summarize(tmin_all_statn = mean(tmin_statn))
-# 
-# tmin_hrus <- left_join(hru_grid_tmin, hru_statn_tmin, by = c('ID')) %>%
-#   mutate(diff = tmin_all_statn - tmin_all_grid) %>%
-#   rename(value = ID)
-# 
-# hrus_map_tmin <- left_join(hrus, tmin_hrus, by = 'value')
-# 
-# tmap_mode('view')
-# 
-# locations_t <- locations %>%
-#   dplyr::filter(name %in% c('Gordon_South', 'Gordon_North',
-#                         'Betasso', 'Niwot_Snotel',
-#                         'University Camp SNTL'))
-# 
-# tm_shape(hrus_map_tmin) +
-#   tm_polygons('diff', id = 'value',
-#               breaks = c(-6,-4,-2,0,2,4,6)) +
-# tm_shape(locations_t) +
-#   tm_symbols(col='blue', size=4)
-
-# Tmin
-#get rid of a bunch of data
-hru_grid_tmin <- hru_grids %>%
-  dplyr::select(c(time, ID, tmin)) %>%
-  rename(tmin_grid = tmin)  %>%
-  group_by(ID) %>%
-  summarize(tmin_all_grid = mean(tmin_grid))
-
-hru_statn_tmin <- hru_statn %>%
-  dplyr::select(c(time, ID, tmin)) %>%
-  rename(tmin_statn = tmin) %>%
-  group_by(ID) %>%
-  summarize(tmin_all_statn = mean(tmin_statn))
-
-tmin_hrus <- left_join(hru_grid_tmin, hru_statn_tmin, by = c('ID')) %>%
-  mutate(diff = tmin_all_statn - tmin_all_grid) %>%
-  rename(value = ID)
-
-hrus_map_tmin <- left_join(hrus, tmin_hrus, by = 'value')
-
-tmin <- ggplot() +
-  geom_sf(data = hrus_map_tmin, aes(fill = diff), color = "black", lwd = 0.2) +
-  scale_fill_viridis_c(option = "plasma", name = "Tmin difference (°C)",
-                       limits = c(-5, 2)) +
-  theme_bw(base_size=13.5) +
-  theme_void() +
-  theme(
-    legend.position = "bottom",
-    panel.grid.major = element_blank(),
-    panel.grid.minor = element_blank(),
-    axis.title.x = element_blank(),
-    axis.title.y = element_blank())
-
-tmin
-
-```
-
-### Tmin season
-
-- Dec-Mar: Winter
-- Apr-Jun: Snowmelt/spring
-- Jul-Aug: Monsoon
-- Sep-Nov: Baseflow/fall
-
-```{r}
-############################
-### look at month
-#get rid of a bunch of data
-hru_grid_tmin_jan <- hru_grids %>%
-  dplyr::select(c(time, ID, tmin)) %>%
-  rename(tmin_grid = tmin)  %>%
-  mutate(month = month(time)) %>%
-  filter(month %in% c(12,1,2,3)) %>%
-  group_by(ID) %>%
-  summarize(tmin_all_grid = mean(tmin_grid))
-
-hru_statn_tmin_jan <- hru_statn %>%
-  dplyr::select(c(time, ID, tmin)) %>%
-  rename(tmin_statn = tmin) %>%
-  mutate(month = month(time)) %>%
-  filter(month %in% c(12,1,2,3)) %>%
-  group_by(ID) %>%
-  summarize(tmin_all_statn = mean(tmin_statn))
-
-tmin_hrus_jan <- left_join(hru_grid_tmin_jan, hru_statn_tmin_jan, by = c('ID')) %>%
-  mutate(diff = tmin_all_statn - tmin_all_grid) %>%
-  rename(value = ID)
-
-hrus_map_tmin_jan <- left_join(hrus, tmin_hrus_jan, by = 'value')
-
-tmin_jan <- ggplot() +
-  geom_sf(data = hrus_map_tmin_jan, aes(fill = diff), color = "black", lwd = 0.2) +
-  scale_fill_viridis_c(option = "plasma", name = "tmin difference (°C)",
-                       limits = c(-5, 3)) +
-  theme_bw(base_size=13.5) +
-  theme_void() +
-  theme(
-    legend.position = "bottom",
-    panel.grid.major = element_blank(),
-    panel.grid.minor = element_blank(),
-    axis.title.x = element_blank(),
-    axis.title.y = element_blank()) +
-  ggtitle('Winter')
-
-#tmin_jan
-
-## 
-hru_grid_tmin_apr <- hru_grids %>%
-  dplyr::select(c(time, ID, tmin)) %>%
-  rename(tmin_grid = tmin)  %>%
-  mutate(month = month(time)) %>%
-  filter(month %in% c(4,5,6)) %>%
-  group_by(ID) %>%
-  summarize(tmin_all_grid = mean(tmin_grid))
-
-hru_statn_tmin_apr <- hru_statn %>%
-  dplyr::select(c(time, ID, tmin)) %>%
-  rename(tmin_statn = tmin) %>%
-  mutate(month = month(time)) %>%
-  filter(month %in% c(4,5,6)) %>%
-  group_by(ID) %>%
-  summarize(tmin_all_statn = mean(tmin_statn))
-
-tmin_hrus_apr <- left_join(hru_grid_tmin_apr, hru_statn_tmin_apr, by = c('ID')) %>%
-  mutate(diff = tmin_all_statn - tmin_all_grid) %>%
-  rename(value = ID)
-
-hrus_map_tmin_apr <- left_join(hrus, tmin_hrus_apr, by = 'value')
-
-tmin_apr <- ggplot() +
-  geom_sf(data = hrus_map_tmin_apr, aes(fill = diff), color = "black", lwd = 0.2) +
-  scale_fill_viridis_c(option = "plasma", name = "tmin difference (°C)",
-                       limits = c(-5, 3)) +
-  theme_bw(base_size=13.5) +
-  theme_void() +
-  theme(
-    legend.position = "bottom",
-    panel.grid.major = element_blank(),
-    panel.grid.minor = element_blank(),
-    axis.title.x = element_blank(),
-    axis.title.y = element_blank()) +
-  ggtitle('Snowmelt')
-
-#tmin_apr
-
-#### 
-hru_grid_tmin_jul <- hru_grids %>%
-  dplyr::select(c(time, ID, tmin)) %>%
-  rename(tmin_grid = tmin)  %>%
-  mutate(month = month(time)) %>%
-  filter(month %in% c(7,8)) %>%
-  group_by(ID) %>%
-  summarize(tmin_all_grid = mean(tmin_grid))
-
-hru_statn_tmin_jul <- hru_statn %>%
-  dplyr::select(c(time, ID, tmin)) %>%
-  rename(tmin_statn = tmin) %>%
-  mutate(month = month(time)) %>%
-  filter(month %in% c(7,8)) %>%
-  group_by(ID) %>%
-  summarize(tmin_all_statn = mean(tmin_statn))
-
-tmin_hrus_jul <- left_join(hru_grid_tmin_jul, hru_statn_tmin_jul, by = c('ID')) %>%
-  mutate(diff = tmin_all_statn - tmin_all_grid) %>%
-  rename(value = ID)
-
-hrus_map_tmin_jul <- left_join(hrus, tmin_hrus_jul, by = 'value')
-
-tmin_jul <- ggplot() +
-  geom_sf(data = hrus_map_tmin_jul, aes(fill = diff), color = "black", lwd = 0.2) +
-  scale_fill_viridis_c(option = "plasma", name = "tmin difference (°C)",
-                            limits = c(-5, 3)) +
-  theme_bw(base_size=13.5) +
-  theme_void() +
-  theme(
-    legend.position = "bottom",
-    panel.grid.major = element_blank(),
-    panel.grid.minor = element_blank(),
-    axis.title.x = element_blank(),
-    axis.title.y = element_blank()) +
-  ggtitle('Monsoon')
-
-#tmin_jul
-
-##
-
-hru_grid_tmin_sep <- hru_grids %>%
-  dplyr::select(c(time, ID, tmin)) %>%
-  rename(tmin_grid = tmin)  %>%
-  mutate(month = month(time)) %>%
-  filter(month %in% c(9,10,11)) %>%
-  group_by(ID) %>%
-  summarize(tmin_all_grid = mean(tmin_grid))
-
-hru_statn_tmin_sep <- hru_statn %>%
-  dplyr::select(c(time, ID, tmin)) %>%
-  rename(tmin_statn = tmin) %>%
-  mutate(month = month(time)) %>%
-  filter(month %in% c(9,10,11)) %>%
-  group_by(ID) %>%
-  summarize(tmin_all_statn = mean(tmin_statn))
-
-tmin_hrus_sep <- left_join(hru_grid_tmin_sep, hru_statn_tmin_sep, by = c('ID')) %>%
-  mutate(diff = tmin_all_statn - tmin_all_grid) %>%
-  rename(value = ID)
-
-hrus_map_tmin_sep <- left_join(hrus, tmin_hrus_sep, by = 'value')
-
-tmin_sep <- ggplot() +
-  geom_sf(data = hrus_map_tmin_sep, aes(fill = diff), color = "black", lwd = 0.2) +
-  scale_fill_viridis_c(option = "plasma", name = "tmin difference (°C)",
-                       limits = c(-5, 3)) +
-  theme_bw(base_size=13.5) +
-  theme_void() +
-  theme(
-    legend.position = "bottom",
-    panel.grid.major = element_blank(),
-    panel.grid.minor = element_blank(),
-    axis.title.x = element_blank(),
-    axis.title.y = element_blank()) +
-  ggtitle('Fall')
-
-#tmin_sep
-###
-
-lots <- ggarrange(tmin_jan,
-                  tmin_apr,
-                  tmin_jul,
-                  tmin_sep) 
-          #nrow = 4)
-          #ncol= 0)
-lots
-
-```
-
-## Cumulative Precip difference
-
-2011-2020 average of daily station-grid precip for DOY 365 (or 366)
-
-```{r cum precip, echo = F}
-# #get rid of a bunch of data
-# hru_grid_precip <- hru_grids %>%
-#   dplyr::select(c(time, ID, precip)) %>%
-#   rename(precip_grid = precip)
-# 
-# hru_statn_precip <- hru_statn %>%
-#   dplyr::select(c(time, ID, precip)) %>%
-#   rename(precip_statn = precip)
-# 
-# precip_hrus <- left_join(hru_grid_precip, hru_statn_precip, by = c('time', 'ID')) %>%
-#   mutate(diff = precip_statn - precip_grid,
-#          year = year(time)) %>%
-#   group_by(year, ID) %>%
-#   mutate(total_diff = cumsum(diff)) %>%
-#   filter(time == max(time)) %>%
-#   group_by(ID) %>%
-#   summarize(precip_avg_cumdiff = mean(total_diff)) %>%
-#   rename(value = ID)
-# 
-# hrus_map_precip <- left_join(hrus, precip_hrus, by = 'value')
-# 
-# tmap_mode('view')
-# 
-# locations_p <- locations %>%
-#   filter(type == 'precip')
-# 
-# tm_shape(hrus_map_precip) +
-#   tm_polygons('precip_avg_cumdiff', midpoint = NA, palette = 'YlGnBu', id = 'value') +
-# tm_shape(locations_p) +
-#   tm_symbols(col='blue', size=4)
-
-# Cumulative p
-hru_grid_precip <- hru_grids %>%
-  dplyr::select(c(time, ID, precip)) %>%
-  rename(precip_grid = precip)
-
-hru_statn_precip <- hru_statn %>%
-  dplyr::select(c(time, ID, precip)) %>%
-  rename(precip_statn = precip)
-
-precip_hrus <- left_join(hru_grid_precip, hru_statn_precip, by = c('time', 'ID')) %>%
-  mutate(diff = precip_statn - precip_grid,
-         year = year(time)) %>%
-  group_by(year, ID) %>%
-  mutate(total_diff = cumsum(diff)) %>%
-  filter(time == max(time)) %>%
-  group_by(ID) %>%
-  summarize(precip_avg_cumdiff = mean(total_diff)) %>%
-  rename(value = ID)
-
-hrus_map_precip <- left_join(hrus, precip_hrus, by = 'value')
-
-precip <- ggplot() +
-  geom_sf(data = hrus_map_precip, aes(fill = precip_avg_cumdiff), color = "black", lwd = 0.2) +
-  scale_fill_viridis_c(option = "mako", name = "Cumulative P Difference (mm)") +
-  theme_bw(base_size=13.5) +
-  theme_void() +
-  theme(
-    legend.position = "bottom",
-    panel.grid.major = element_blank(),
-    panel.grid.minor = element_blank(),
-    axis.title.x = element_blank(),
-    axis.title.y = element_blank())
-
-precip
-
-#################
-# winter p
-hru_grid_precip <- hru_grids %>%
-  dplyr::select(c(time, ID, precip)) %>%
-  rename(precip_grid = precip)
-
-hru_statn_precip <- hru_statn %>%
-  dplyr::select(c(time, ID, precip)) %>%
-  rename(precip_statn = precip)
-
-precip_hrus_jan <- left_join(hru_grid_precip, hru_statn_precip, by = c('time', 'ID')) %>%
-  mutate(month = month(time)) %>%
-  filter(month %in% c(12,1,2,3)) %>% 
-  mutate(diff = precip_statn - precip_grid,
-         year = year(time)) %>%
-  group_by(year, ID) %>%
-  mutate(total_diff = cumsum(diff)) %>%
-  filter(time == max(time)) %>%
-  group_by(ID) %>%
-  summarize(precip_avg_cumdiff = mean(total_diff)) %>%
-  rename(value = ID)
-
-hrus_map_precip_jan <- left_join(hrus, precip_hrus_jan, by = 'value')
-
-precip_jan <- ggplot() +
-  geom_sf(data = hrus_map_precip_jan, aes(fill = precip_avg_cumdiff), color = "black", lwd = 0.2) +
-  scale_fill_viridis_c(option = "mako", name = "Cumulative P Difference (mm)",
-                       limits = c(-51, 9.5)) +
-  theme_bw(base_size=13.5) +
-  theme_void() +
-  theme(
-    legend.position = "bottom",
-    panel.grid.major = element_blank(),
-    panel.grid.minor = element_blank(),
-    axis.title.x = element_blank(),
-    axis.title.y = element_blank()) +
-  ggtitle('Winter')
-
-##
-precip_hrus_apr <- left_join(hru_grid_precip, hru_statn_precip, by = c('time', 'ID')) %>%
-  mutate(month = month(time)) %>%
-  filter(month %in% c(4,5,6)) %>% 
-  mutate(diff = precip_statn - precip_grid,
-         year = year(time)) %>%
-  group_by(year, ID) %>%
-  mutate(total_diff = cumsum(diff)) %>%
-  filter(time == max(time)) %>%
-  group_by(ID) %>%
-  summarize(precip_avg_cumdiff = mean(total_diff)) %>%
-  rename(value = ID)
-
-hrus_map_precip_apr <- left_join(hrus, precip_hrus_apr, by = 'value')
-
-precip_apr <- ggplot() +
-  geom_sf(data = hrus_map_precip_apr, aes(fill = precip_avg_cumdiff), color = "black", lwd = 0.2) +
-  scale_fill_viridis_c(option = "mako", name = "Cumulative P Difference (mm)",
-                       limits = c(-51, 9.5)) +
-  theme_bw(base_size=13.5) +
-  theme_void() +
-  theme(
-    legend.position = "bottom",
-    panel.grid.major = element_blank(),
-    panel.grid.minor = element_blank(),
-    axis.title.x = element_blank(),
-    axis.title.y = element_blank()) +
-  ggtitle('Snowmelt')
-##
-
-precip_hrus_jul <- left_join(hru_grid_precip, hru_statn_precip, by = c('time', 'ID')) %>%
-  mutate(month = month(time)) %>%
-  filter(month %in% c(7,8)) %>% 
-  mutate(diff = precip_statn - precip_grid,
-         year = year(time)) %>%
-  group_by(year, ID) %>%
-  mutate(total_diff = cumsum(diff)) %>%
-  filter(time == max(time)) %>%
-  group_by(ID) %>%
-  summarize(precip_avg_cumdiff = mean(total_diff)) %>%
-  rename(value = ID)
-
-hrus_map_precip_jul <- left_join(hrus, precip_hrus_jul, by = 'value')
-
-precip_jul <- ggplot() +
-  geom_sf(data = hrus_map_precip_jul, aes(fill = precip_avg_cumdiff), color = "black", lwd = 0.2) +
-  scale_fill_viridis_c(option = "mako", name = "Cumulative P Difference (mm)",
-                       limits = c(-51, 9.5)) +
-  theme_bw(base_size=13.5) +
-  theme_void() +
-  theme(
-    legend.position = "bottom",
-    panel.grid.major = element_blank(),
-    panel.grid.minor = element_blank(),
-    axis.title.x = element_blank(),
-    axis.title.y = element_blank()) +
-  ggtitle('Monsoon')
-
-## 
-precip_hrus_sep <- left_join(hru_grid_precip, hru_statn_precip, by = c('time', 'ID')) %>%
-  mutate(month = month(time)) %>%
-  filter(month %in% c(9,10,11)) %>% 
-  mutate(diff = precip_statn - precip_grid,
-         year = year(time)) %>%
-  group_by(year, ID) %>%
-  mutate(total_diff = cumsum(diff)) %>%
-  filter(time == max(time)) %>%
-  group_by(ID) %>%
-  summarize(precip_avg_cumdiff = mean(total_diff)) %>%
-  rename(value = ID)
-
-hrus_map_precip_sep <- left_join(hrus, precip_hrus_sep, by = 'value')
-
-precip_sep <- ggplot() +
-  geom_sf(data = hrus_map_precip_sep, aes(fill = precip_avg_cumdiff), color = "black", lwd = 0.2) +
-  scale_fill_viridis_c(option = "mako", name = "Cumulative P Difference (mm)",
-                       limits = c(-51, 9.5)) +
-  theme_bw(base_size=13.5) +
-  theme_void() +
-  theme(
-    legend.position = "bottom",
-    panel.grid.major = element_blank(),
-    panel.grid.minor = element_blank(),
-    axis.title.x = element_blank(),
-    axis.title.y = element_blank()) +
-  ggtitle('Fall')
-
-lots <- ggarrange(precip_jan,
-                  precip_apr,
-                  precip_jul,
-                  precip_sep) 
-          #nrow = 4)
-          #ncol= 0)
-lots
-
-```
-
-## Solar radiation difference
-
-2011-2020 average of daily station-grid solar rad
-
-```{r cum sol rad, echo = F}
-
-# #get rid of a bunch of data
-# hru_grid_solrad <- hru_grids %>%
-#   dplyr::select(c(time, ID, solRad)) %>%
-#   rename(solrad_grid = solRad)  %>%
-#   group_by(ID) %>%
-#   summarize(solrad_all_grid = mean(solrad_grid))
-# 
-# hru_statn_solrad <- hru_statn %>%
-#   dplyr::select(c(time, ID, solRad)) %>%
-#   rename(solrad_statn = solRad) %>%
-#   group_by(ID) %>%
-#   summarize(solrad_all_statn = mean(solrad_statn))
-# 
-# solrad_hrus <- left_join(hru_grid_solrad, hru_statn_solrad, by = c('ID')) %>%
-#   mutate(diff = solrad_all_statn - solrad_all_grid) %>%
-#   rename(value = ID)
-# 
-# hrus_map_solrad <- left_join(hrus, solrad_hrus, by = 'value')
-# 
-# tmap_mode('view')
-# 
-# locations_solrad <- locations %>%
-#   dplyr::filter(name %in% c('Gordon_South',
-#                         'Betasso', 'Niwot_Snotel'))
-# 
-# tm_shape(hrus_map_solrad) +
-#   tm_polygons('diff', midpoint = NA, palette = 'YlOrRd', id = 'value') +
-# tm_shape(locations_solrad) +
-#   tm_symbols(col='blue', size=4)
-
-# solar rad
-hru_grid_solrad <- hru_grids %>%
-  dplyr::select(c(time, ID, solRad)) %>%
-  rename(solrad_grid = solRad)  %>%
-  group_by(ID) %>%
-  summarize(solrad_all_grid = mean(solrad_grid))
-
-hru_statn_solrad <- hru_statn %>%
-  dplyr::select(c(time, ID, solRad)) %>%
-  rename(solrad_statn = solRad) %>%
-  group_by(ID) %>%
-  summarize(solrad_all_statn = mean(solrad_statn))
-
-solrad_hrus <- left_join(hru_grid_solrad, hru_statn_solrad, by = c('ID')) %>%
-  mutate(diff = solrad_all_statn - solrad_all_grid) %>%
-  rename(value = ID)
-
-hrus_map_solrad <- left_join(hrus, solrad_hrus, by = 'value')
-
-sr <- ggplot() +
-  geom_sf(data = hrus_map_solrad, aes(fill = diff), color = "black", lwd = 0.2) +
-  scale_fill_viridis_c(option = "cividis", name = expression("Solar rad difference (MJ/m"^"2" * ")")) +
-  theme_bw(base_size=13.5) +
-  theme_void() +
-  theme(
-    legend.position = "bottom",
-    panel.grid.major = element_blank(),
-    panel.grid.minor = element_blank(),
-    axis.title.x = element_blank(),
-    axis.title.y = element_blank()) +
-  guides(
-    fill = guide_colorbar(
-      label.theme = element_text(size = 10)))
-
-sr
-
-##########
-### look at month
-#get rid of a bunch of data
-hru_grid_solrad_jan <- hru_grids %>%
-  dplyr::select(c(time, ID, solrad_grid=solRad)) %>%
-  mutate(month = month(time)) %>%
-  filter(month %in% c(12,1,2,3)) %>%
-  group_by(ID) %>%
-  summarize(solrad_all_grid = mean(solrad_grid))
-
-hru_statn_solrad_jan <- hru_statn %>%
-  dplyr::select(c(time, ID, solrad_statn=solRad)) %>%
-  mutate(month = month(time)) %>%
-  filter(month %in% c(12,1,2,3)) %>%
-  group_by(ID) %>%
-  summarize(solrad_all_statn = mean(solrad_statn))
-
-solrad_hrus_jan <- left_join(hru_grid_solrad_jan, hru_statn_solrad_jan, by = c('ID')) %>%
-  mutate(diff = solrad_all_statn - solrad_all_grid) %>%
-  rename(value = ID)
-
-hrus_map_solrad_jan <- left_join(hrus, solrad_hrus_jan, by = 'value')
-
-solrad_jan <- ggplot() +
-  geom_sf(data = hrus_map_solrad_jan, aes(fill = diff), color = "black", lwd = 0.2) +
-  scale_fill_viridis_c(option = "cividis", name = expression("Solar rad difference (MJ/m"^"2" * ")"),
-                       limits = c(-8.5, 1.5)) +
-  theme_bw(base_size=13.5) +
-  theme_void() +
-  theme(
-    legend.position = "bottom",
-    panel.grid.major = element_blank(),
-    panel.grid.minor = element_blank(),
-    axis.title.x = element_blank(),
-    axis.title.y = element_blank()) +
-  ggtitle('Winter')
-
-#solrad_jan
-
-## 
-hru_grid_solrad_apr <- hru_grids %>%
-  dplyr::select(c(time, ID, solrad_grid=solRad)) %>%
-  mutate(month = month(time)) %>%
-  filter(month %in% c(4,5,6)) %>%
-  group_by(ID) %>%
-  summarize(solrad_all_grid = mean(solrad_grid))
-
-hru_statn_solrad_apr <- hru_statn %>%
-  dplyr::select(c(time, ID, solrad_statn=solRad)) %>%
-  mutate(month = month(time)) %>%
-  filter(month %in% c(4,5,6)) %>%
-  group_by(ID) %>%
-  summarize(solrad_all_statn = mean(solrad_statn))
-
-solrad_hrus_apr <- left_join(hru_grid_solrad_apr, hru_statn_solrad_apr, by = c('ID')) %>%
-  mutate(diff = solrad_all_statn - solrad_all_grid) %>%
-  rename(value = ID)
-
-hrus_map_solrad_apr <- left_join(hrus, solrad_hrus_apr, by = 'value')
-
-solrad_apr <- ggplot() +
-  geom_sf(data = hrus_map_solrad_apr, aes(fill = diff), color = "black", lwd = 0.2) +
-  scale_fill_viridis_c(option = "cividis", name = expression("Solar rad difference (MJ/m"^"2" * ")"),
-                       limits = c(-8.5, 1.5)) +
-  theme_bw(base_size=13.5) +
-  theme_void() +
-  theme(
-    legend.position = "bottom",
-    panel.grid.major = element_blank(),
-    panel.grid.minor = element_blank(),
-    axis.title.x = element_blank(),
-    axis.title.y = element_blank()) +
-  ggtitle('Snowmelt')
-
-#solrad_apr
-
-#### 
-hru_grid_solrad_jul <- hru_grids %>%
-  dplyr::select(c(time, ID, solrad_grid=solRad)) %>%
-  mutate(month = month(time)) %>%
-  filter(month %in% c(7,8)) %>%
-  group_by(ID) %>%
-  summarize(solrad_all_grid = mean(solrad_grid))
-
-hru_statn_solrad_jul <- hru_statn %>%
-  dplyr::select(c(time, ID, solrad_statn=solRad)) %>%
-  mutate(month = month(time)) %>%
-  filter(month %in% c(7,8)) %>%
-  group_by(ID) %>%
-  summarize(solrad_all_statn = mean(solrad_statn))
-
-solrad_hrus_jul <- left_join(hru_grid_solrad_jul, hru_statn_solrad_jul, by = c('ID')) %>%
-  mutate(diff = solrad_all_statn - solrad_all_grid) %>%
-  rename(value = ID)
-
-hrus_map_solrad_jul <- left_join(hrus, solrad_hrus_jul, by = 'value')
-
-solrad_jul <- ggplot() +
-  geom_sf(data = hrus_map_solrad_jul, aes(fill = diff), color = "black", lwd = 0.2) +
-  scale_fill_viridis_c(option = "cividis", name = expression("Solar rad difference (MJ/m"^"2" * ")"),
-                       limits = c(-8.5, 1.5)) +
-  theme_bw(base_size=13.5) +
-  theme_void() +
-  theme(
-    legend.position = "bottom",
-    panel.grid.major = element_blank(),
-    panel.grid.minor = element_blank(),
-    axis.title.x = element_blank(),
-    axis.title.y = element_blank()) +
-  ggtitle('Monsoon')
-
-#solrad_jul
-
-##
-hru_grid_solrad_sep <- hru_grids %>%
-  dplyr::select(c(time, ID, solrad_grid=solRad)) %>%
-  mutate(month = month(time)) %>%
-  filter(month %in% c(9,10,11)) %>%
-  group_by(ID) %>%
-  summarize(solrad_all_grid = mean(solrad_grid))
-
-hru_statn_solrad_sep <- hru_statn %>%
-  dplyr::select(c(time, ID, solrad_statn=solRad)) %>%
-  mutate(month = month(time)) %>%
-  filter(month %in% c(9,10,11)) %>%
-  group_by(ID) %>%
-  summarize(solrad_all_statn = mean(solrad_statn))
-
-solrad_hrus_sep <- left_join(hru_grid_solrad_sep, hru_statn_solrad_sep, by = c('ID')) %>%
-  mutate(diff = solrad_all_statn - solrad_all_grid) %>%
-  rename(value = ID)
-
-hrus_map_solrad_sep <- left_join(hrus, solrad_hrus_sep, by = 'value')
-
-solrad_sep <- ggplot() +
-  geom_sf(data = hrus_map_solrad_sep, aes(fill = diff), color = "black", lwd = 0.2) +
-  scale_fill_viridis_c(option = "cividis", name = expression("Solar rad difference (MJ/m"^"2" * ")"),
-                       limits = c(-8.5, 1.5)) +
-  theme_bw(base_size=13.5) +
-  theme_void() +
-  theme(
-    legend.position = "bottom",
-    panel.grid.major = element_blank(),
-    panel.grid.minor = element_blank(),
-    axis.title.x = element_blank(),
-    axis.title.y = element_blank()) +
-  ggtitle('Fall')
-
-###
-
-lots <- ggarrange(solrad_jan,
-                  solrad_apr,
-                  solrad_jul,
-                  solrad_sep) 
-          #nrow = 4)
-          #ncol= 0)
-lots
-
-```
-
-## RH difference
-
-```{r rh, echo = F}
-
-# #get rid of a bunch of data
-# hru_grid_rh <- hru_grids %>%
-#   dplyr::select(c(time, ID, rhum)) %>%
-#   rename(rh_grid = rhum)  %>%
-#   group_by(ID) %>%
-#   summarize(rh_all_grid = mean(rh_grid))
-# 
-# hru_statn_rh <- hru_statn %>%
-#   dplyr::select(c(time, ID, rhum)) %>%
-#   rename(rh_statn = rhum) %>%
-#   group_by(ID) %>%
-#   summarize(rh_all_statn = mean(rh_statn))
-# 
-# rh_hrus <- left_join(hru_grid_rh, hru_statn_rh, by = c('ID')) %>%
-#   mutate(diff = rh_all_statn - rh_all_grid) %>%
-#   rename(value = ID)
-# 
-# hrus_map_rh <- left_join(hrus, rh_hrus, by = 'value')
-# 
-# tmap_mode('view')
-# 
-# locations_rh <- locations %>%
-#   dplyr::filter(name %in% c('Gordon_South', 'Gordon_North',
-#                         'Betasso', 'Niwot_Snotel'))
-# 
-# tm_shape(hrus_map_rh) +
-#   tm_polygons('diff', midpoint = NA, id = 'value') +
-# tm_shape(locations_rh) +
-#   tm_symbols(col='blue', size=4)
-
-# RH
-#get rid of a bunch of data
-hru_grid_rh <- hru_grids %>%
-  dplyr::select(c(time, ID, rhum)) %>%
-  rename(rh_grid = rhum)  %>%
-  group_by(ID) %>%
-  summarize(rh_all_grid = mean(rh_grid))
-
-hru_statn_rh <- hru_statn %>%
-  dplyr::select(c(time, ID, rhum)) %>%
-  rename(rh_statn = rhum) %>%
-  group_by(ID) %>%
-  summarize(rh_all_statn = mean(rh_statn))
-
-rh_hrus <- left_join(hru_grid_rh, hru_statn_rh, by = c('ID')) %>%
-  mutate(diff = rh_all_statn - rh_all_grid) %>%
-  rename(value = ID)
-
-hrus_map_rh <- left_join(hrus, rh_hrus, by = 'value')
-
-rh <- ggplot() +
-  geom_sf(data = hrus_map_rh, aes(fill = diff), color = "black", lwd = 0.2) +
-  scale_fill_viridis_c(option = "viridis", name = "RH difference (%)") +
-  theme_bw(base_size=13.5) +
-  theme_void() +
-  theme(
-    legend.position = "bottom",
-    panel.grid.major = element_blank(),
-    panel.grid.minor = element_blank(),
-    axis.title.x = element_blank(),
-    axis.title.y = element_blank())
-
-rh
-#####
-
-hru_grid_rh_jan <- hru_grids %>%
-  dplyr::select(c(time, ID, rh_grid=rhum)) %>%
-  mutate(month = month(time)) %>%
-  filter(month %in% c(12,1,2,3)) %>%
-  group_by(ID) %>%
-  summarize(rh_all_grid = mean(rh_grid))
-
-hru_statn_rh_jan <- hru_statn %>%
-  dplyr::select(c(time, ID, rh_statn=rhum)) %>%
-  mutate(month = month(time)) %>%
-  filter(month %in% c(12,1,2,3)) %>%
-  group_by(ID) %>%
-  summarize(rh_all_statn = mean(rh_statn))
-
-rh_hrus_jan <- left_join(hru_grid_rh_jan, hru_statn_rh_jan, by = c('ID')) %>%
-  mutate(diff = rh_all_statn - rh_all_grid) %>%
-  rename(value = ID)
-
-hrus_map_rh_jan <- left_join(hrus, rh_hrus_jan, by = 'value')
-
-rh_jan <- ggplot() +
-  geom_sf(data = hrus_map_rh_jan, aes(fill = diff), color = "black", lwd = 0.2) +
-  scale_fill_viridis_c(option = "viridis", name = "RH difference (%)",
-                       limits = c(-3, 10.5)) +
-  theme_bw(base_size=13.5) +
-  theme_void() +
-  theme(
-    legend.position = "bottom",
-    panel.grid.major = element_blank(),
-    panel.grid.minor = element_blank(),
-    axis.title.x = element_blank(),
-    axis.title.y = element_blank()) +
-  ggtitle('Winter')
-
-##
-hru_grid_rh_apr <- hru_grids %>%
-  dplyr::select(c(time, ID, rh_grid=rhum)) %>%
-  mutate(month = month(time)) %>%
-  filter(month %in% c(4,5,6)) %>%
-  group_by(ID) %>%
-  summarize(rh_all_grid = mean(rh_grid))
-
-hru_statn_rh_apr <- hru_statn %>%
-  dplyr::select(c(time, ID, rh_statn=rhum)) %>%
-  mutate(month = month(time)) %>%
-  filter(month %in% c(4,5,6)) %>%
-  group_by(ID) %>%
-  summarize(rh_all_statn = mean(rh_statn))
-
-rh_hrus_apr <- left_join(hru_grid_rh_apr, hru_statn_rh_apr, by = c('ID')) %>%
-  mutate(diff = rh_all_statn - rh_all_grid) %>%
-  rename(value = ID)
-
-hrus_map_rh_apr <- left_join(hrus, rh_hrus_apr, by = 'value')
-
-rh_apr <- ggplot() +
-  geom_sf(data = hrus_map_rh_apr, aes(fill = diff), color = "black", lwd = 0.2) +
-  scale_fill_viridis_c(option = "viridis", name = "RH difference (%)",
-                       limits = c(-3, 10.5)) +
-  theme_bw(base_size=13.5) +
-  theme_void() +
-  theme(
-    legend.position = "bottom",
-    panel.grid.major = element_blank(),
-    panel.grid.minor = element_blank(),
-    axis.title.x = element_blank(),
-    axis.title.y = element_blank()) +
-  ggtitle('Snowmelt')
-
-##
-hru_grid_rh_jul <- hru_grids %>%
-  dplyr::select(c(time, ID, rh_grid=rhum)) %>%
-  mutate(month = month(time)) %>%
-  filter(month %in% c(7,8)) %>%
-  group_by(ID) %>%
-  summarize(rh_all_grid = mean(rh_grid))
-
-hru_statn_rh_jul <- hru_statn %>%
-  dplyr::select(c(time, ID, rh_statn=rhum)) %>%
-  mutate(month = month(time)) %>%
-  filter(month %in% c(7,8)) %>%
-  group_by(ID) %>%
-  summarize(rh_all_statn = mean(rh_statn))
-
-rh_hrus_jul <- left_join(hru_grid_rh_jul, hru_statn_rh_jul, by = c('ID')) %>%
-  mutate(diff = rh_all_statn - rh_all_grid) %>%
-  rename(value = ID)
-
-hrus_map_rh_jul <- left_join(hrus, rh_hrus_jul, by = 'value')
-
-rh_jul <- ggplot() +
-  geom_sf(data = hrus_map_rh_jul, aes(fill = diff), color = "black", lwd = 0.2) +
-  scale_fill_viridis_c(option = "viridis", name = "RH difference (%)",
-                       limits = c(-3,10.5)) +
-  theme_bw(base_size=13.5) +
-  theme_void() +
-  theme(
-    legend.position = "bottom",
-    panel.grid.major = element_blank(),
-    panel.grid.minor = element_blank(),
-    axis.title.x = element_blank(),
-    axis.title.y = element_blank()) +
-  ggtitle('Monsoon')
-
-##
-hru_grid_rh_sep <- hru_grids %>%
-  dplyr::select(c(time, ID, rh_grid=rhum)) %>%
-  mutate(month = month(time)) %>%
-  filter(month %in% c(9,10,11)) %>%
-  group_by(ID) %>%
-  summarize(rh_all_grid = mean(rh_grid))
-
-hru_statn_rh_sep <- hru_statn %>%
-  dplyr::select(c(time, ID, rh_statn=rhum)) %>%
-  mutate(month = month(time)) %>%
-  filter(month %in% c(9,10,11)) %>%
-  group_by(ID) %>%
-  summarize(rh_all_statn = mean(rh_statn))
-
-rh_hrus_sep <- left_join(hru_grid_rh_sep, hru_statn_rh_sep, by = c('ID')) %>%
-  mutate(diff = rh_all_statn - rh_all_grid) %>%
-  rename(value = ID)
-
-hrus_map_rh_sep <- left_join(hrus, rh_hrus_sep, by = 'value')
-
-rh_sep <- ggplot() +
-  geom_sf(data = hrus_map_rh_sep, aes(fill = diff), color = "black", lwd = 0.2) +
-  scale_fill_viridis_c(option = "viridis", name = "RH difference (%)",
-                       limits = c(-3,10.5)) +
-  theme_bw(base_size=13.5) +
-  theme_void() +
-  theme(
-    legend.position = "bottom",
-    panel.grid.major = element_blank(),
-    panel.grid.minor = element_blank(),
-    axis.title.x = element_blank(),
-    axis.title.y = element_blank()) +
-  ggtitle('Fall')
-
-lots <- ggarrange(rh_jan,
-                  rh_apr,
-                  rh_jul,
-                  rh_sep) 
-          #nrow = 4)
-          #ncol= 0)
-lots
-
-```
-
-```{r}
-
-# lots <- ggarrange(precip,
-#                   sr,
-#                   rh,
-#                   tmean,
-#                   tmax,
-#                   tmin) 
-#           #nrow = 4)
-#           #ncol= 0)
-# lots
-
-```
-
-## Average soil sat comparison
-
-```{r soilsat, echo = F}
-
-#get rid of a bunch of data
-hru_grid_soilsat <- hru_grids %>%
-  dplyr::select(c(time, ID, soilSat)) %>%
-  rename(soilsat_grid = soilSat)  %>%
-  group_by(ID) %>%
-  summarize(soilsat_all_grid = mean(soilsat_grid))
-
-hru_statn_soilsat <- hru_statn %>%
-  dplyr::select(c(time, ID, soilSat)) %>%
-  rename(soilsat_statn = soilSat) %>%
-  group_by(ID) %>%
-  summarize(soilsat_all_statn = mean(soilsat_statn))
-
-soilsat_hrus <- left_join(hru_grid_soilsat, hru_statn_soilsat, by = c('ID')) %>%
-  rename(value = ID)
-
-hrus_map_soilsat <- left_join(hrus, soilsat_hrus, by = 'value')
-
-tmap_mode('plot')
-
-soilavg_grid <- tm_shape(hrus_map_soilsat) +
-  tm_polygons('soilsat_all_grid', midpoint = NA, id = 'value',
-              breaks = c(0.0, 0.05, 0.1, 0.15, 0.2, 0.25, 0.3, 0.35, 0.4)) +
-  tm_legend(legend.outside = T) +
-  tm_layout(main.title = 'Average soil sat')
-
-soilavg_statn <- tm_shape(hrus_map_soilsat) +
-  tm_polygons('soilsat_all_statn', midpoint = NA, id = 'value',
-              breaks = c(0.0, 0.05, 0.1, 0.15, 0.2, 0.25, 0.3, 0.35, 0.4)) +
-  tm_legend(legend.outside = T)
-
-tmap_arrange(soilavg_grid, soilavg_statn)
-
-```
-
-## Average max soil sat comparison
-
-```{r max soilsat, echo = F}
-
-#get rid of a bunch of data
-hru_grid_soilsat_max <- hru_grids %>%
-  dplyr::select(c(time, ID, soilSat)) %>%
-  rename(soilsat_grid = soilSat)  %>%
-  mutate(year = year(time)) %>%
-  group_by(ID, year) %>%
-  summarize(soilsat_yrmax_grid = max(soilsat_grid)) %>%
-  summarize(avg_max_grid = mean(soilsat_yrmax_grid))
-
-hru_statn_soilsat_max <- hru_statn %>%
-  dplyr::select(c(time, ID, soilSat)) %>%
-  rename(soilsat_statn = soilSat) %>%
-  mutate(year = year(time)) %>%
-  group_by(ID, year) %>%
-  summarize(soilsat_yrmax_statn = max(soilsat_statn)) %>%
-  summarize(avg_max_statn = mean(soilsat_yrmax_statn))
-
-soilsat_hrus_max <- left_join(hru_grid_soilsat_max, hru_statn_soilsat_max, by = c('ID')) %>%
-  rename(value = ID)
-
-hrus_map_soilsat_max <- left_join(hrus, soilsat_hrus_max, by = 'value')
-
-tmap_mode('plot')
-
-soilavg_grid_max <- tm_shape(hrus_map_soilsat_max) +
-  tm_polygons('avg_max_grid', midpoint = NA, id = 'value',
-              breaks = c(0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.7, 0.8)) +
-  tm_legend(legend.outside = T) +
-  tm_layout(main.title = 'Average max soil sat',
-            title.position = c('left', 'top'))
-
-soilavg_statn_max <- tm_shape(hrus_map_soilsat_max) +
-  tm_polygons('avg_max_statn', midpoint = NA, id = 'value',
-              breaks = c(0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.7, 0.8)) +
-  tm_legend(legend.outside = T)
-
-tmap_arrange(soilavg_grid_max, soilavg_statn_max)
-
-```
-
-## Average ET comparison
-
-```{r et, echo = F}
-#get rid of a bunch of data
-hru_grid_ET <- hru_grids %>%
-  dplyr::select(c(time, ID, actET)) %>%
-  rename(ET_grid = actET)  %>%
-  group_by(ID) %>%
-  summarize(ET_all_grid = mean(ET_grid))
-
-hru_statn_ET <- hru_statn %>%
-  dplyr::select(c(time, ID, actET)) %>%
-  rename(ET_statn = actET) %>%
-  group_by(ID) %>%
-  summarize(ET_all_statn = mean(ET_statn))
-
-ET_hrus <- left_join(hru_grid_ET, hru_statn_ET, by = c('ID')) %>%
-  rename(value = ID)
-
-hrus_map_ET <- left_join(hrus, ET_hrus, by = 'value')
-
-tmap_mode('plot')
-
-ETavg_grid <- tm_shape(hrus_map_ET) +
-  tm_polygons('ET_all_grid', midpoint = NA, id = 'value',
-              breaks = c(0.0,0.2, 0.4, 0.6, 0.8, 1.0, 1.2)) +
-  tm_legend(legend.outside = T) +
-  tm_layout(main.title = 'Average ET')
-
-ETavg_statn <- tm_shape(hrus_map_ET) +
-  tm_polygons('ET_all_statn', midpoint = NA, id = 'value',
-             breaks = c(0.0, 0.1, 0.2, 0.4, 0.6, 0.8, 1.0, 1.2)) +
-  tm_legend(legend.outside = T)
-
-tmap_arrange(ETavg_grid, ETavg_statn)
-
-```
-
-## Average ET difference
-
-```{r et diff, echo = F}
-
-ET_hrus <- ET_hrus %>%
-  mutate(diff = ET_all_statn - ET_all_grid)
-
-hrus_map_et_diff <- left_join(hrus, ET_hrus, by = 'value')
-
-tmap_mode('plot')
-
-tm_shape(hrus_map_et_diff) +
-  tm_polygons('diff', midpoint = NA, id = 'value')  +
-  tm_legend(legend.outside = T) +
-  tm_layout(main.title = 'Average ET difference')
-
-```
-
-## Average LAI comparison
-
-```{r lai, echo = F}
-
-#get rid of a bunch of data
-hru_grid_LAI <- hru_grids %>%
-  dplyr::select(c(time, ID, LAI)) %>%
-  rename(LAI_grid = LAI)  %>%
-  group_by(ID) %>%
-  summarize(LAI_all_grid = mean(LAI_grid))
-
-hru_statn_LAI <- hru_statn %>%
-  dplyr::select(c(time, ID, LAI)) %>%
-  rename(LAI_statn = LAI) %>%
-  group_by(ID) %>%
-  summarize(LAI_all_statn = mean(LAI_statn))
-
-LAI_hrus <- left_join(hru_grid_LAI, hru_statn_LAI, by = c('ID')) %>%
-  rename(value = ID)
-
-hrus_map_LAI <- left_join(hrus, LAI_hrus, by = 'value')
-
-tmap_mode('plot')
-
-LAIavg_grid <- tm_shape(hrus_map_LAI) +
-  tm_polygons('LAI_all_grid', midpoint = NA, id = 'value',
-              breaks = c(1,2,3,4,5)) +
-  tm_legend(legend.outside = T) +
-  tm_layout(main.title = 'Average LAI')
-
-LAIavg_statn <- tm_shape(hrus_map_LAI) +
-  tm_polygons('LAI_all_statn', midpoint = NA, id = 'value',
-              breaks = c(1,2,3,4,5)) +
-  tm_legend(legend.outside = T)
-
-tmap_arrange(LAIavg_grid, LAIavg_statn)
-
-```
-
-# HRU RD/RG
-
-Group 1 is lowest elevation, 4 is highest elevation
-
-```{r}
-
-setwd("~/Documents/Repos/fourmile")
-
-elev <- read_csv('./38HRU_sept2013_updates/hru_elev.csv') %>%
-  mutate(elevation_group = ntile(elevation, 4))
-
-rd1_grid <- hru_grids %>%
-  dplyr::select(time, outRD1, ID) %>%
-  mutate(source = 'grid') %>%
-  left_join(., elev, by = 'ID') %>%
-  arrange(time) %>%
-  mutate(year = year(time)) %>%
-  group_by(year, elevation_group) %>%
-  mutate(rd1_summed = cumsum(outRD1)) %>%
-  group_by(year, elevation_group) %>%
-  summarise(max_rd1_summed = max(rd1_summed)) %>%
-  mutate(type = 'grid')
-
-rd1_statn <- hru_statn %>%
-  dplyr::select(time, outRD1, ID) %>%
-  mutate(source = 'statn') %>% 
-  left_join(., elev, by = 'ID') %>%
-  arrange(time) %>%
-  mutate(year = year(time)) %>%
-  group_by(year, elevation_group) %>%
-  mutate(rd1_summed = cumsum(outRD1)) %>%
-  group_by(year, elevation_group) %>%
-  summarise(max_rd1_summed = max(rd1_summed)) %>%
-  mutate(type = 'statn')
-
-rd1_hru <- bind_rows(rd1_grid, rd1_statn)
-
-# elevation group area
-elev_area <- elev %>%
-  group_by(elevation_group) %>%
-  summarize(group_area = sum(area))
-
-rd1_hru <- left_join(rd1_hru, elev_area, by = 'elevation_group') %>%
-  mutate(RD1_mm_year = ((max_rd1_summed/1000)/group_area)/1000)
-
-library(viridis)
-
-rd1_plot <- ggplot(rd1_hru, aes(x=as.factor(year), y=RD1_mm_year, 
-                                      color=as.factor(elevation_group),
-                                      shape = type)) + 
-  geom_point(size = 3) +
-  #scale_color_viridis_d() +
-  theme_bw() +
-  labs(x = 'Year',
-       y = 'Total RD1 (mm/year)')
-
-ggplotly(rd1_plot)
-
-###########################
-
-rd2_grid <- hru_grids %>%
-  dplyr::select(time, outRD2, ID) %>%
-  mutate(source = 'grid') %>%
-  left_join(., elev, by = 'ID') %>%
-  arrange(time) %>%
-  mutate(year = year(time)) %>%
-  group_by(year, elevation_group) %>%
-  mutate(rd2_summed = cumsum(outRD2)) %>%
-  group_by(year, elevation_group) %>%
-  summarise(max_rd2_summed = max(rd2_summed)) %>%
-  mutate(type = 'grid')
-
-rd2_statn <- hru_statn %>%
-  dplyr::select(time, outRD2, ID) %>%
-  mutate(source = 'statn') %>% 
-  left_join(., elev, by = 'ID') %>%
-  arrange(time) %>%
-  mutate(year = year(time)) %>%
-  group_by(year, elevation_group) %>%
-  mutate(rd2_summed = cumsum(outRD2)) %>%
-  group_by(year, elevation_group) %>%
-  summarise(max_rd2_summed = max(rd2_summed)) %>%
-  mutate(type = 'statn')
-
-rd2_hru <- bind_rows(rd2_grid, rd2_statn)
-
-rd2_hru <- left_join(rd2_hru, elev_area, by = 'elevation_group') %>%
-  mutate(rd2_mm_year = ((max_rd2_summed/1000)/group_area)/1000)
-
-rd2_plot <- ggplot(rd2_hru, aes(x=as.factor(year), y=rd2_mm_year, 
-                                      color=as.factor(elevation_group),
-                                      shape = type)) + 
-  geom_point(size = 3) +
-  #scale_color_viridis_d() +
-  theme_bw() +
-  labs(x = 'Year',
-       y = 'Total RD2 (mm/year)')
-
-ggplotly(rd2_plot)
-
-###########
-
-# RG1
-rg1_grid <- hru_grids %>%
-  dplyr::select(time, outRG1, ID) %>%
-  mutate(source = 'grid') %>%
-  left_join(., elev, by = 'ID') %>%
-  arrange(time) %>%
-  mutate(year = year(time)) %>%
-  group_by(year, elevation_group) %>%
-  mutate(rg1_summed = cumsum(outRG1)) %>%
-  group_by(year, elevation_group) %>%
-  summarise(max_rg1_summed = max(rg1_summed)) %>%
-  mutate(type = 'grid')
-
-rg1_statn <- hru_statn %>%
-  dplyr::select(time, outRG1, ID) %>%
-  mutate(source = 'statn') %>% 
-  left_join(., elev, by = 'ID') %>%
-  arrange(time) %>%
-  mutate(year = year(time)) %>%
-  group_by(year, elevation_group) %>%
-  mutate(rg1_summed = cumsum(outRG1)) %>%
-  group_by(year, elevation_group) %>%
-  summarise(max_rg1_summed = max(rg1_summed)) %>%
-  mutate(type = 'statn')
-
-rg1_hru <- bind_rows(rg1_grid, rg1_statn)
-
-rg1_hru <- left_join(rg1_hru, elev_area, by = 'elevation_group') %>%
-  mutate(rg1_mm_year = ((max_rg1_summed/1000)/group_area)/1000)
-
-rg1_plot <- ggplot(rg1_hru, aes(x=as.factor(year), y=rg1_mm_year, 
-                                      color=as.factor(elevation_group),
-                                      shape = type)) + 
-  geom_point(size = 3) +
-  #scale_color_viridis_d() +
-  theme_bw() +
-  labs(x = 'Year',
-       y = 'Total RG1 (mm/year)')
-
-ggplotly(rg1_plot)
-
-#######
-
-# rg2
-rg2_grid <- hru_grids %>%
-  dplyr::select(time, outRG2, ID) %>%
-  mutate(source = 'grid') %>%
-  left_join(., elev, by = 'ID') %>%
-  arrange(time) %>%
-  mutate(year = year(time)) %>%
-  group_by(year, elevation_group) %>%
-  mutate(rg2_summed = cumsum(outRG2)) %>%
-  group_by(year, elevation_group) %>%
-  summarise(max_rg2_summed = max(rg2_summed)) %>%
-  mutate(type = 'grid')
-
-rg2_statn <- hru_statn %>%
-  dplyr::select(time, outRG2, ID) %>%
-  mutate(source = 'statn') %>% 
-  left_join(., elev, by = 'ID') %>%
-  arrange(time) %>%
-  mutate(year = year(time)) %>%
-  group_by(year, elevation_group) %>%
-  mutate(rg2_summed = cumsum(outRG2)) %>%
-  group_by(year, elevation_group) %>%
-  summarise(max_rg2_summed = max(rg2_summed)) %>%
-  mutate(type = 'statn')
-
-rg2_hru <- bind_rows(rg2_grid, rg2_statn)
-
-rg2_hru <- left_join(rg2_hru, elev_area, by = 'elevation_group') %>%
-  mutate(rg2_mm_year = ((max_rg2_summed/1000)/group_area)/1000)
-
-rg2_plot <- ggplot(rg2_hru, aes(x=as.factor(year), y=rg2_mm_year, 
-                                      color=as.factor(elevation_group),
-                                      shape = type)) + 
-  geom_point(size = 3) +
-  #scale_color_viridis_d() +
-  theme_bw() +
-  labs(x = 'Year',
-       y = 'Total RG2 (mm/year)')
-
-ggplotly(rg2_plot)
-
-```
-
-<!-- # Join param & RD/RG -->
-
-<!-- ```{r} -->
-
-<!-- join <- gw_maxcumsum %>% -->
-<!--   rename(input_data = source) -->
-
-<!-- params1 <- params %>% -->
-<!--   dplyr::select(-input_data) %>% -->
-<!--   rename(input_data = cal) %>% -->
-<!--   dplyr::select(-c(year_missing)) -->
-
-<!-- # -->
-<!-- params_weighted1 <- params_weighted %>% -->
-<!--   mutate(input_data = paste(source, year_missing, sep = "_")) %>% -->
-<!--   pivot_wider(names_from = 'param', -->
-<!--               values_from = 'area_weighted_average') %>% -->
-<!--   rename_with(~ paste0(., '_weighted'), 4:9) %>% -->
-<!--   dplyr::select(-c(year_missing, source)) -->
-
-<!-- join <- left_join(join, params1, by = c('input_data')) %>% -->
-<!--   pivot_wider(., names_from='param', values_from='value') %>% -->
-<!--   pivot_wider(., names_from = 'flow_type', values_from = 'flow_cms') -->
-
-<!-- join <- left_join(join, params_weighted1, by = 'input_data') -->
-
-<!-- write_csv(join, '/Users/megansears/Documents/Repos/fourmile/38HRU_sept2013_updates/flow_params.csv') -->
-
-<!-- ``` -->

### 2024-12-27 fourmile_output_dec2024.Rmd
cals for dec2024 updates

--- 2024-10-08 fourmile_outputs_2013edits.Rmd
@@
 
-## Density plots
-
 ```{r density plots, echo = FALSE, message = FALSE, warning = FALSE}
 
-mean_params <- params %>%
-  group_by(param, input_data) %>%
-  summarize(mean = mean(value))
-
-plotdens_params <- function(param_name) {
-  params %>%
-    filter(param == param_name) %>%
-    ggplot(aes(x = value,
-               fill = input_data, 
-               color = input_data)) + 
-    geom_density(alpha=0.5) +
-    geom_vline(data=filter(mean_params, param == param_name), 
-               aes(xintercept=mean, color=input_data),
-             linetype="dashed", linewidth=0.75) +
-    ggtitle(param_name) +
-    theme_bw()
-}
-
-name <- levels(params$param)
-
-lapply(name, plotdens_params)
+# mean_params <- params %>%
+#   group_by(param, input_data) %>%
+#   summarize(mean = mean(value))
+# 
+# plotdens_params <- function(param_name) {
+#   params %>%
+#     filter(param == param_name) %>%
+#     ggplot(aes(x = value,
+#                fill = input_data, 
+#                color = input_data)) + 
+#     geom_density(alpha=0.5) +
+#     geom_vline(data=filter(mean_params, param == param_name), 
+#                aes(xintercept=mean, color=input_data),
+#              linetype="dashed", linewidth=0.75) +
+#     ggtitle(param_name) +
+#     theme_bw()
+# }
+# 
+# name <- levels(params$param)
+# 
+# lapply(name, plotdens_params)
 
@@
 
-```{r hydrographs, echo = FALSE, message = FALSE, warning = FALSE}
-
-setwd('/Users/megansears/Documents/Repos/fourmile/38HRU_sept2013_updates')
+```{r hydrographs, echo = FALSE, message = FALSE, warning = FALSE, fig.width=10, fig.height=6}
+
+setwd('/Users/megansears/Documents/Repos/fourmile/38HRU_dec2024_updates')
 
@@
   scale_color_manual(name="cal_run", values=c('obs' = 'black',
-                                            "grid_2011"="seagreen",
-                                            "grid_2012"="seagreen2",
-                                            "grid_2013"="steelblue",
-                                            "grid_2014"='dodgerblue',
-                                            "grid_2015" = "cyan3",
-                                            'grid_2016' = 'blue',
-                                            'grid_2017' = 'blue4',
-                                            'grid_2018' = 'cadetblue',
-                                            'grid_2019' = 'lightgreen',
-                                            'grid_2020' = 'olivedrab',
+                                            # "grid_2011"="seagreen",
+                                            # "grid_2012"="seagreen2",
+                                            # "grid_2013"="steelblue",
+                                            # "grid_2014"='dodgerblue',
+                                            # "grid_2015" = "cyan3",
+                                            # 'grid_2016' = 'blue',
+                                            # 'grid_2017' = 'blue4',
+                                            # 'grid_2018' = 'cadetblue',
+                                            # 'grid_2019' = 'lightgreen',
+                                            # 'grid_2020' = 'olivedrab',
                                             'grid_all' = 'steelblue3',
-                                            "statn_2011"="maroon",
-                                            "statn_2012"="deeppink4",
-                                            "statn_2013"="deeppink",
-                                            "statn_2014"='purple',
-                                            "statn_2015" = "mediumorchid1",
-                                            'statn_2016' = 'indianred',
-                                            'statn_2017' = 'sienna',
-                                            'statn_2018' = 'salmon2',
-                                            'statn_2019' = 'mediumpurple1',
-                                            'statn_2020' = 'violetred',
-                                            'statn_all' = 'red'))
+                                            # "statn_2011"="maroon",
+                                            # "statn_2012"="deeppink4",
+                                            # "statn_2013"="deeppink",
+                                            # "statn_2014"='purple',
+                                            # "statn_2015" = "mediumorchid1",
+                                            # 'statn_2016' = 'indianred',
+                                            # 'statn_2017' = 'sienna',
+                                            # 'statn_2018' = 'salmon2',
+                                            # 'statn_2019' = 'mediumpurple1',
+                                            # 'statn_2020' = 'violetred',
+                                            'statn_all' = 'red')) +
+  theme_bw(base_size=20)
 
@@
 scale_color_manual(name="cal_run", values=c('obs' = 'black',
-                                            "grid_2011"="seagreen",
-                                            "grid_2012"="seagreen2",
-                                            "grid_2013"="steelblue",
-                                            "grid_2014"='dodgerblue',
-                                            "grid_2015" = "cyan3",
-                                            'grid_2016' = 'blue',
-                                            'grid_2017' = 'blue4',
-                                            'grid_2018' = 'cadetblue',
-                                            'grid_2019' = 'lightgreen',
-                                            'grid_2020' = 'olivedrab',
+                                            # "grid_2011"="seagreen",
+                                            # "grid_2012"="seagreen2",
+                                            # "grid_2013"="steelblue",
+                                            # "grid_2014"='dodgerblue',
+                                            # "grid_2015" = "cyan3",
+                                            # 'grid_2016' = 'blue',
+                                            # 'grid_2017' = 'blue4',
+                                            # 'grid_2018' = 'cadetblue',
+                                            # 'grid_2019' = 'lightgreen',
+                                            # 'grid_2020' = 'olivedrab',
                                             'grid_all' = 'steelblue3',
-                                            "statn_2011"="maroon",
-                                            "statn_2012"="deeppink4",
-                                            "statn_2013"="deeppink",
-                                            "statn_2014"='purple',
-                                            "statn_2015" = "mediumorchid1",
-                                            'statn_2016' = 'indianred',
-                                            'statn_2017' = 'sienna',
-                                            'statn_2018' = 'salmon2',
-                                            'statn_2019' = 'mediumpurple1',
-                                            'statn_2020' = 'violetred',
+                                            # "statn_2011"="maroon",
+                                            # "statn_2012"="deeppink4",
+                                            # "statn_2013"="deeppink",
+                                            # "statn_2014"='purple',
+                                            # "statn_2015" = "mediumorchid1",
+                                            # 'statn_2016' = 'indianred',
+                                            # 'statn_2017' = 'sienna',
+                                            # 'statn_2018' = 'salmon2',
+                                            # 'statn_2019' = 'mediumpurple1',
+                                            # 'statn_2020' = 'violetred',
                                             'statn_all' = 'red')) +
@@
 
+# flow_kge_all <- flow %>%
+#   summarize(grid2011 = KGE(grid_2011, obs),
+#             grid2012 = KGE(grid_2012, obs),
+#             grid2013 = KGE(grid_2013, obs),
+#             grid2014 = KGE(grid_2014, obs),
+#             grid2015 = KGE(grid_2015, obs),
+#             grid2016 = KGE(grid_2016, obs),
+#             grid2017 = KGE(grid_2017, obs),
+#             grid2018 = KGE(grid_2018, obs),
+#             grid2019 = KGE(grid_2019, obs),
+#             grid2020 = KGE(grid_2020, obs),
+#             gridall = KGE(grid_all, obs),
+#             statn2011 = KGE(statn_2011, obs),
+#             statn2012 = KGE(statn_2012, obs),
+#             statn2013 = KGE(statn_2013, obs),
+#             statn2014 = KGE(statn_2014, obs),
+#             statn2015 = KGE(statn_2015, obs),
+#             statn2016 = KGE(statn_2016, obs),
+#             statn2017 = KGE(statn_2017, obs),
+#             statn2018 = KGE(statn_2018, obs),
+#             statn2019 = KGE(statn_2019, obs),
+#             statn2020 = KGE(statn_2020, obs),
+#             statnall = KGE(statn_all, obs)) %>%
+#     mutate_if(is.numeric,
+#             round,
+#             digits = 2)
+
 flow_kge_all <- flow %>%
-  summarize(grid2011 = KGE(grid_2011, obs),
-            grid2012 = KGE(grid_2012, obs),
-            grid2013 = KGE(grid_2013, obs),
-            grid2014 = KGE(grid_2014, obs),
-            grid2015 = KGE(grid_2015, obs),
-            grid2016 = KGE(grid_2016, obs),
-            grid2017 = KGE(grid_2017, obs),
-            grid2018 = KGE(grid_2018, obs),
-            grid2019 = KGE(grid_2019, obs),
-            grid2020 = KGE(grid_2020, obs),
-            gridall = KGE(grid_all, obs),
-            statn2011 = KGE(statn_2011, obs),
-            statn2012 = KGE(statn_2012, obs),
-            statn2013 = KGE(statn_2013, obs),
-            statn2014 = KGE(statn_2014, obs),
-            statn2015 = KGE(statn_2015, obs),
-            statn2016 = KGE(statn_2016, obs),
-            statn2017 = KGE(statn_2017, obs),
-            statn2018 = KGE(statn_2018, obs),
-            statn2019 = KGE(statn_2019, obs),
-            statn2020 = KGE(statn_2020, obs),
-            statnall = KGE(statn_all, obs)) %>%
+  summarize(
+            gridall = KGE(grid_all,
+                          obs, 
+                          na.rm=T, 
+                          method='2012'),
+            statnall = KGE(statn_all, 
+                           obs, 
+                           na.rm=T,
+                           method='2012')) %>%
     mutate_if(is.numeric,
@@
   group_by(year) %>%
-  summarize(grid2011 = KGE(grid_2011, obs),
-            grid2012 = KGE(grid_2012, obs),
-            grid2013 = KGE(grid_2013, obs),
-            grid2014 = KGE(grid_2014, obs),
-            grid2015 = KGE(grid_2015, obs),
-            grid2016 = KGE(grid_2016, obs),
-            grid2017 = KGE(grid_2017, obs),
-            grid2018 = KGE(grid_2018, obs),
-            grid2019 = KGE(grid_2019, obs),
-            grid2020 = KGE(grid_2020, obs),
-            gridall = KGE(grid_all, obs),
-            statn2011 = KGE(statn_2011, obs),
-            statn2012 = KGE(statn_2012, obs),
-            statn2013 = KGE(statn_2013, obs),
-            statn2014 = KGE(statn_2014, obs),
-            statn2015 = KGE(statn_2015, obs),
-            statn2016 = KGE(statn_2016, obs),
-            statn2017 = KGE(statn_2017, obs),
-            statn2018 = KGE(statn_2018, obs),
-            statn2019 = KGE(statn_2019, obs),
-            statn2020 = KGE(statn_2020, obs),
-            statnall = KGE(statn_all, obs)) %>%
+  summarize(
+    # grid2011 = KGE(grid_2011, obs),
+    #         grid2012 = KGE(grid_2012, obs),
+    #         grid2013 = KGE(grid_2013, obs),
+    #         grid2014 = KGE(grid_2014, obs),
+    #         grid2015 = KGE(grid_2015, obs),
+    #         grid2016 = KGE(grid_2016, obs),
+    #         grid2017 = KGE(grid_2017, obs),
+    #         grid2018 = KGE(grid_2018, obs),
+    #         grid2019 = KGE(grid_2019, obs),
+    #         grid2020 = KGE(grid_2020, obs),
+            gridall = KGE(grid_all, obs, na.rm = T, method='2012'),
+            # statn2011 = KGE(statn_2011, obs),
+            # statn2012 = KGE(statn_2012, obs),
+            # statn2013 = KGE(statn_2013, obs),
+            # statn2014 = KGE(statn_2014, obs),
+            # statn2015 = KGE(statn_2015, obs),
+            # statn2016 = KGE(statn_2016, obs),
+            # statn2017 = KGE(statn_2017, obs),
+            # statn2018 = KGE(statn_2018, obs),
+            # statn2019 = KGE(statn_2019, obs),
+            # statn2020 = KGE(statn_2020, obs),
+            statnall = KGE(statn_all, obs, na.rm=T, method='2012')) %>%
     mutate_if(is.numeric,
@@
 
-### Annual KGE plots
-
-```{r wy plots, echo = FALSE, message = FALSE, warning = FALSE}
-
-plot_kge <- function(calyear) {
-  flow_plot %>%
-    filter(year == calyear) %>%
-    ggplot(aes(x = model_run,
-               y = kge)) +
-    geom_point(size=3) +
-    ggtitle(calyear) +
-    theme_bw() +
-    theme(axis.text.x = element_text(angle = 45, hjust=1))
-}
-
-name <- levels(flow_plot$year)
-
-lapply(name, plot_kge)
-
-```
+<!-- ### Annual KGE plots -->
+
+<!-- ```{r wy plots, echo = FALSE, message = FALSE, warning = FALSE} -->
+
+<!-- plot_kge <- function(calyear) { -->
+<!--   flow_plot %>% -->
+<!--     filter(year == calyear) %>% -->
+<!--     ggplot(aes(x = model_run, -->
+<!--                y = kge)) + -->
+<!--     geom_point(size=3) + -->
+<!--     ggtitle(calyear) + -->
+<!--     theme_bw() + -->
+<!--     theme(axis.text.x = element_text(angle = 45, hjust=1)) -->
+<!-- } -->
+
+<!-- name <- levels(flow_plot$year) -->
+
+<!-- lapply(name, plot_kge) -->
+
+<!-- ``` -->
 
@@
 flow_pbias_all <- flow %>%
-  summarize(grid2011 = pbias(grid_2011, obs),
-            grid2012 = pbias(grid_2012, obs),
-            grid2013 = pbias(grid_2013, obs),
-            grid2014 = pbias(grid_2014, obs),
-            grid2015 = pbias(grid_2015, obs),
-            grid2016 = pbias(grid_2016, obs),
-            grid2017 = pbias(grid_2017, obs),
-            grid2018 = pbias(grid_2018, obs),
-            grid2019 = pbias(grid_2019, obs),
-            grid2020 = pbias(grid_2020, obs),
+  summarize(
+    # grid2011 = pbias(grid_2011, obs),
+    #         grid2012 = pbias(grid_2012, obs),
+    #         grid2013 = pbias(grid_2013, obs),
+    #         grid2014 = pbias(grid_2014, obs),
+    #         grid2015 = pbias(grid_2015, obs),
+    #         grid2016 = pbias(grid_2016, obs),
+    #         grid2017 = pbias(grid_2017, obs),
+    #         grid2018 = pbias(grid_2018, obs),
+    #         grid2019 = pbias(grid_2019, obs),
+    #         grid2020 = pbias(grid_2020, obs),
             gridall = pbias(grid_all, obs),
-            statn2011 = pbias(statn_2011, obs),
-            statn2012 = pbias(statn_2012, obs),
-            statn2013 = pbias(statn_2013, obs),
-            statn2014 = pbias(statn_2014, obs),
-            statn2015 = pbias(statn_2015, obs),
-            statn2016 = pbias(statn_2016, obs),
-            statn2017 = pbias(statn_2017, obs),
-            statn2018 = pbias(statn_2018, obs),
-            statn2019 = pbias(statn_2019, obs),
-            statn2020 = pbias(statn_2020, obs),
+            # statn2011 = pbias(statn_2011, obs),
+            # statn2012 = pbias(statn_2012, obs),
+            # statn2013 = pbias(statn_2013, obs),
+            # statn2014 = pbias(statn_2014, obs),
+            # statn2015 = pbias(statn_2015, obs),
+            # statn2016 = pbias(statn_2016, obs),
+            # statn2017 = pbias(statn_2017, obs),
+            # statn2018 = pbias(statn_2018, obs),
+            # statn2019 = pbias(statn_2019, obs),
+            # statn2020 = pbias(statn_2020, obs),
             statnall = pbias(statn_all, obs)) %>%
@@
   group_by(year) %>%
-  summarize(grid2011 = pbias(grid_2011, obs),
-            grid2012 = pbias(grid_2012, obs),
-            grid2013 = pbias(grid_2013, obs),
-            grid2014 = pbias(grid_2014, obs),
-            grid2015 = pbias(grid_2015, obs),
-            grid2016 = pbias(grid_2016, obs),
-            grid2017 = pbias(grid_2017, obs),
-            grid2018 = pbias(grid_2018, obs),
-            grid2019 = pbias(grid_2019, obs),
-            grid2020 = pbias(grid_2020, obs),
+  summarize(
+    # grid2011 = pbias(grid_2011, obs),
+    #         grid2012 = pbias(grid_2012, obs),
+    #         grid2013 = pbias(grid_2013, obs),
+    #         grid2014 = pbias(grid_2014, obs),
+    #         grid2015 = pbias(grid_2015, obs),
+    #         grid2016 = pbias(grid_2016, obs),
+    #         grid2017 = pbias(grid_2017, obs),
+    #         grid2018 = pbias(grid_2018, obs),
+    #         grid2019 = pbias(grid_2019, obs),
+    #         grid2020 = pbias(grid_2020, obs),
             gridall = pbias(grid_all, obs),
-            statn2011 = pbias(statn_2011, obs),
-            statn2012 = pbias(statn_2012, obs),
-            statn2013 = pbias(statn_2013, obs),
-            statn2014 = pbias(statn_2014, obs),
-            statn2015 = pbias(statn_2015, obs),
-            statn2016 = pbias(statn_2016, obs),
-            statn2017 = pbias(statn_2017, obs),
-            statn2018 = pbias(statn_2018, obs),
-            statn2019 = pbias(statn_2019, obs),
-            statn2020 = pbias(statn_2020, obs),
+            # statn2011 = pbias(statn_2011, obs),
+            # statn2012 = pbias(statn_2012, obs),
+            # statn2013 = pbias(statn_2013, obs),
+            # statn2014 = pbias(statn_2014, obs),
+            # statn2015 = pbias(statn_2015, obs),
+            # statn2016 = pbias(statn_2016, obs),
+            # statn2017 = pbias(statn_2017, obs),
+            # statn2018 = pbias(statn_2018, obs),
+            # statn2019 = pbias(statn_2019, obs),
+            # statn2020 = pbias(statn_2020, obs),
             statnall = pbias(statn_all, obs)) %>%
@@
 
-### Annual Pbias plots
-
-```{r pbias plots, echo = FALSE, message = FALSE, warning = FALSE}
-
-plot_pbias <- function(calyear) {
-  flow_plot %>%
-    filter(year == calyear) %>%
-    ggplot(aes(x = model_run,
-               y = pbias)) +
-    geom_point(size=3) +
-    ggtitle(calyear) +
-    theme_bw() +
-    theme(axis.text.x = element_text(angle = 45, hjust=1))
-}
-
-name <- levels(flow_plot$year)
-
-lapply(name, plot_pbias)
-
-```
-
-<!-- # Ensembles -->
-
-<!-- ## Hydrograph -->
-
-<!-- ```{r ensemble hydrographs, echo = F} -->
-
-<!-- ensem <- flow %>% -->
-<!--   rowwise() %>% -->
-<!--   mutate(grid_ensemble = mean(c(grid_2011, grid_2012, -->
-<!--                                 grid_2013, grid_2014, -->
-<!--                                 grid_2015, grid_2016, -->
-<!--                                 grid_2017, grid_2018, -->
-<!--                                 grid_2019, grid_2020)), -->
-<!--          statn_ensemble = mean(c(statn_2011, statn_2012, -->
-<!--                                  statn_2013, statn_2014, -->
-<!--                                  statn_2015, statn_2016, -->
-<!--                                  statn_2017, statn_2018, -->
-<!--                                  statn_2019, statn_2020)), -->
-<!--          all_ensemble = mean(c(grid_2011, grid_2012, -->
-<!--                                grid_2013, grid_2014, -->
-<!--                                grid_2015, grid_2016, -->
-<!--                                grid_2017, grid_2018, -->
-<!--                                grid_2019, grid_2020, -->
-<!--                                statn_2011, statn_2012, -->
-<!--                                statn_2013, statn_2014, -->
-<!--                                statn_2015, statn_2016, -->
-<!--                                statn_2017, statn_2018, -->
-<!--                                statn_2019, statn_2020, -->
-<!--                                grid_all, statn_all))) %>% -->
-<!--   dplyr::select(date, grid_ensemble, statn_ensemble, -->
-<!--          all_ensemble, grid_all, -->
-<!--          statn_all, obs) -->
-
-<!-- ensem_pivot <- ensem %>% -->
-<!--   pivot_longer(!date, names_to = 'cal_run', values_to = 'q_m3s') %>% -->
-<!--   mutate(year = as.factor(year(date))) -->
-
-<!-- q_ensemble <- ggplot(ensem_pivot, aes(date, q_m3s, color = cal_run)) + -->
-<!--   geom_line() + -->
-<!--   scale_color_manual(name="cal_run", values=c('obs'='black', -->
-<!--                                             "grid_ensemble"="maroon", -->
-<!--                                             "statn_ensemble"="darkturquoise", -->
-<!--                                             "grid_all"="purple1", -->
-<!--                                             "statn_all"='springgreen4', -->
-<!--                                             "all_ensemble" = "orange")) + -->
-<!--   scale_y_continuous(name = 'Q_m3s') + -->
-<!--   theme_bw() -->
-
-<!-- q_ensemble -->
-
-<!-- ``` -->
-
-<!-- ## KGE -->
-
-<!-- ### KGE for ensembles (entire period) -->
-
-<!-- ```{r ensemble kge, echo = F} -->
-
-<!-- ensem_kge_all <- ensem %>% -->
-<!--   ungroup() %>% -->
-<!--   summarize(grid_ensemble = KGE(grid_ensemble, obs), -->
-<!--             statn_ensemble = KGE(statn_ensemble, obs), -->
-<!--             all_ensemble = KGE(all_ensemble, obs), -->
-<!--             grid_all = KGE(grid_all, obs), -->
-<!--             statn_all = KGE(statn_all, obs)) %>% -->
-<!--     mutate_if(is.numeric, -->
-<!--             round, -->
-<!--             digits = 2) -->
-
-<!-- kable(ensem_kge_all) %>% -->
-<!--   kable_styling(full_width = F) -->
-
-<!-- ``` -->
-
-<!-- ### Annual KGEs for ensembles -->
-
-<!-- ```{r annual kge ensemble, echo = F} -->
-
-<!-- yr_kge_ensem <- ensem %>% -->
-<!--   ungroup() %>% -->
-<!--   mutate(year = year(date)) %>% -->
-<!--   group_by(year) %>% -->
-<!--   summarize(grid_ensemble = KGE(grid_ensemble, obs), -->
-<!--             statn_ensemble = KGE(statn_ensemble, obs), -->
-<!--             all_ensemble = KGE(all_ensemble, obs), -->
-<!--             grid_all = KGE(grid_all, obs), -->
-<!--             statn_all = KGE(statn_all, obs)) %>% -->
-<!--     mutate_if(is.numeric, -->
-<!--             round, -->
-<!--             digits = 2) -->
-
-<!-- yr_kge_table <- yr_kge_ensem %>% -->
-<!--   pivot_longer(!year, names_to = 'model_run', values_to = 'kge') %>% -->
-<!--   pivot_wider(names_from = 'year', values_from = 'kge') -->
-
-<!-- yr_kge_table %>% -->
-<!--   kable(.) %>% -->
-<!--   kable_styling() -->
-
-<!-- yr_kge_plot <- yr_kge_ensem %>% -->
-<!--   pivot_longer(!year, names_to = 'model_run', values_to = 'kge') %>% -->
-<!--   mutate(year = as.factor(year)) -->
-
-<!-- #plot annual kge vals for ensembles -->
-<!-- plot_kge_yr_ensem <- function(calyear) { -->
-<!--   yr_kge_plot %>% -->
+<!-- ### Annual Pbias plots -->
+
+<!-- ```{r pbias plots, echo = FALSE, message = FALSE, warning = FALSE} -->
+
+<!-- plot_pbias <- function(calyear) { -->
+<!--   flow_plot %>% -->
 <!--     filter(year == calyear) %>% -->
 <!--     ggplot(aes(x = model_run, -->
-<!--                y = kge)) + -->
-<!--     geom_col() + -->
+<!--                y = pbias)) + -->
+<!--     geom_point(size=3) + -->
 <!--     ggtitle(calyear) + -->
@@
 
-<!-- name <- levels(yr_kge_plot$year) -->
-
-<!-- lapply(name, plot_kge_yr_ensem) -->
-
-<!-- ``` -->
-
-<!-- ### Monthly KGEs for ensembles -->
-
-<!-- ```{r monthly kge ensemble, echo = F} -->
-
-<!-- mo_kge <- ensem %>% -->
-<!--   ungroup() %>% -->
-<!--   drop_na() %>% -->
-<!--   mutate(month = month(date)) %>% -->
-<!--   group_by(month) %>% -->
-<!--   summarize(grid_ensemble = KGE(grid_ensemble, obs), -->
-<!--             statn_ensemble = KGE(statn_ensemble, obs), -->
-<!--             all_ensemble = KGE(all_ensemble, obs), -->
-<!--             grid_all = KGE(grid_all, obs), -->
-<!--             statn_all = KGE(statn_all, obs)) %>% -->
-<!--     mutate_if(is.numeric, -->
-<!--             round, -->
-<!--             digits = 2) -->
-
-<!-- kable(mo_kge) %>% -->
-<!--   kable_styling(full_width = F) -->
-
-<!-- mo_pivot <- mo_kge %>% -->
-<!--   pivot_longer(!month, names_to = 'cal_run', values_to = 'KGE') %>% -->
-<!--   drop_na() -->
-
-<!-- kge_plot_mo <- ggplot(mo_pivot, aes(month, KGE, color = cal_run)) + geom_point(size = 3) + -->
-<!--     scale_color_manual(name="cal_run", values=c("grid_ensemble"="maroon", -->
-<!--                                             "statn_ensemble"="darkturquoise", -->
-<!--                                             "grid_all"="purple1", -->
-<!--                                             "statn_all"='springgreen4', -->
-<!--                                             "all_ensemble" = "orange")) + -->
-<!--   theme_bw() -->
-
-<!-- ggplotly(kge_plot_mo) -->
-
-<!-- ``` -->
-
-<!-- ## RMSE -->
-
-<!-- ### Ensemble RMSE for entire period -->
-
-<!-- ```{r ensemble rmse, echo = F} -->
-
-<!-- ensem_rmse_all <- ensem %>% -->
-<!--   ungroup() %>% -->
-<!--   summarize(grid_ensemble = rmse(grid_ensemble, obs), -->
-<!--             statn_ensemble = rmse(statn_ensemble, obs), -->
-<!--             all_ensemble = rmse(all_ensemble, obs), -->
-<!--             grid_all = rmse(grid_all, obs), -->
-<!--             statn_all = rmse(statn_all, obs)) %>% -->
-<!--     mutate_if(is.numeric, -->
-<!--             round, -->
-<!--             digits = 4) -->
-
-<!-- kable(ensem_rmse_all) %>% -->
-<!--   kable_styling(full_width = F) -->
-
-<!-- ``` -->
-
-<!-- ### Annual RMSE for ensembles -->
-
-<!-- ```{r annual rmse ensem, echo = F} -->
-
-<!-- yr_rmse_ensem <- ensem %>% -->
-<!--   ungroup() %>% -->
-<!--   mutate(year = year(date)) %>% -->
-<!--   group_by(year) %>% -->
-<!--   summarize(grid_ensemble = rmse(grid_ensemble, obs), -->
-<!--             statn_ensemble = rmse(statn_ensemble, obs), -->
-<!--             all_ensemble = rmse(all_ensemble, obs), -->
-<!--             grid_all = rmse(grid_all, obs), -->
-<!--             statn_all = rmse(statn_all, obs)) %>% -->
-<!--     mutate_if(is.numeric, -->
-<!--             round, -->
-<!--             digits = 4) -->
-
-<!-- yr_rmse_table <- yr_rmse_ensem %>% -->
-<!--   pivot_longer(!year, names_to = 'model_run', values_to = 'rmse') %>% -->
-<!--   pivot_wider(names_from = 'year', values_from = 'rmse') -->
-
-<!-- yr_rmse_table %>% -->
-<!--   kable(.) %>% -->
-<!--   kable_styling() -->
-
-<!-- yr_rmse_plot <- yr_rmse_ensem %>% -->
-<!--   pivot_longer(!year, names_to = 'model_run', values_to = 'rmse') %>% -->
-<!--   mutate(year = as.factor(year)) -->
-
-<!-- #plot annual rmse vals for ensembles -->
-<!-- plot_rmse_yr_ensem <- function(calyear) { -->
-<!--   yr_rmse_plot %>% -->
-<!--     filter(year == calyear) %>% -->
-<!--     ggplot(aes(x = model_run, -->
-<!--                y = rmse)) + -->
-<!--     geom_col() + -->
-<!--     ggtitle(calyear) + -->
-<!--     theme_bw() + -->
-<!--     theme(axis.text.x = element_text(angle = 45, hjust=1)) -->
-<!-- } -->
-
-<!-- name <- levels(yr_rmse_plot$year) -->
-
-<!-- lapply(name, plot_rmse_yr_ensem) -->
-
-<!-- ``` -->
-
-<!-- ### Monthly RMSEs for ensembles -->
-
-<!-- ```{r month ensem rmse, echo = F} -->
-
-<!-- mo_rmse <- ensem %>% -->
-<!--   ungroup() %>% -->
-<!--   drop_na() %>% -->
-<!--   mutate(month = month(date)) %>% -->
-<!--   group_by(month) %>% -->
-<!--   summarize(grid_ensemble = rmse(grid_ensemble, obs), -->
-<!--             statn_ensemble = rmse(statn_ensemble, obs), -->
-<!--             all_ensemble = rmse(all_ensemble, obs), -->
-<!--             grid_all = rmse(grid_all, obs), -->
-<!--             statn_all = rmse(statn_all, obs)) %>% -->
-<!--     mutate_if(is.numeric, -->
-<!--             round, -->
-<!--             digits = 4) -->
-
-<!-- kable(mo_rmse) %>% -->
-<!--   kable_styling(full_width = F) -->
-
-<!-- mo_pivot2 <- mo_rmse %>% -->
-<!--   pivot_longer(!month, names_to = 'cal_run', values_to = 'RMSE') %>% -->
-<!--   drop_na() -->
-
-<!-- rmse_plot_mo <- ggplot(mo_pivot2, aes(month, RMSE, color = cal_run)) + geom_point(size = 3) + -->
-<!--     scale_color_manual(name="cal_run", values=c("grid_ensemble"="maroon", -->
-<!--                                             "statn_ensemble"="darkturquoise", -->
-<!--                                             "grid_all"="purple1", -->
-<!--                                             "statn_all"='springgreen4', -->
-<!--                                             "all_ensemble" = "orange")) + -->
-<!--   theme_bw() -->
-
-<!-- ggplotly(rmse_plot_mo) -->
-
-<!-- ``` -->
-
-<!-- ## NSE -->
-
-<!-- ### Ensemble NSE for entire period -->
-
-<!-- ```{r nse all, echo = F} -->
-
-<!-- ensem_nse_all <- ensem %>% -->
-<!--   ungroup() %>% -->
-<!--   summarize(grid_ensemble = NSE(grid_ensemble, obs), -->
-<!--             statn_ensemble = NSE(statn_ensemble, obs), -->
-<!--             all_ensemble = NSE(all_ensemble, obs), -->
-<!--             grid_all = NSE(grid_all, obs), -->
-<!--             statn_all = NSE(statn_all, obs)) %>% -->
-<!--     mutate_if(is.numeric, -->
-<!--             round, -->
-<!--             digits = 2) -->
-
-<!-- kable(ensem_nse_all) %>% -->
-<!--   kable_styling(full_width = F) -->
-
-<!-- ``` -->
-
-<!-- ### Annual NSE for ensembles -->
-
-<!-- ```{r annual nse, echo = F} -->
-
-<!-- yr_nse_ensem <- ensem %>% -->
-<!--   ungroup() %>% -->
-<!--   mutate(year = year(date)) %>% -->
-<!--   group_by(year) %>% -->
-<!--   summarize(grid_ensemble = NSE(grid_ensemble, obs), -->
-<!--             statn_ensemble = NSE(statn_ensemble, obs), -->
-<!--             all_ensemble = NSE(all_ensemble, obs), -->
-<!--             grid_all = NSE(grid_all, obs), -->
-<!--             statn_all = NSE(statn_all, obs)) %>% -->
-<!--     mutate_if(is.numeric, -->
-<!--             round, -->
-<!--             digits = 4) -->
-
-<!-- yr_nse_table <- yr_nse_ensem %>% -->
-<!--   pivot_longer(!year, names_to = 'model_run', values_to = 'nse') %>% -->
-<!--   pivot_wider(names_from = 'year', values_from = 'nse') -->
-
-<!-- yr_nse_table %>% -->
-<!--   kable(.) %>% -->
-<!--   kable_styling() -->
-
-<!-- yr_nse_plot <- yr_nse_ensem %>% -->
-<!--   pivot_longer(!year, names_to = 'model_run', values_to = 'nse') %>% -->
-<!--   mutate(year = as.factor(year)) -->
-
-<!-- #plot annual nse vals for ensembles -->
-<!-- plot_nse_yr_ensem <- function(calyear) { -->
-<!--   yr_nse_plot %>% -->
-<!--     filter(year == calyear) %>% -->
-<!--     ggplot(aes(x = model_run, -->
-<!--                y = nse)) + -->
-<!--     geom_col() + -->
-<!--     ggtitle(calyear) + -->
-<!--     theme_bw() + -->
-<!--     theme(axis.text.x = element_text(angle = 45, hjust=1)) -->
-<!-- } -->
-
-<!-- name <- levels(yr_nse_plot$year) -->
-
-<!-- lapply(name, plot_nse_yr_ensem) -->
-
-<!-- ``` -->
-
-<!-- ### Monthly NSE for ensembles -->
-
-<!-- ```{r monthly rmse, echo =F} -->
-
-<!-- mo_nse <- ensem %>% -->
-<!--   ungroup() %>% -->
-<!--   drop_na() %>% -->
-<!--   mutate(month = month(date)) %>% -->
-<!--   group_by(month) %>% -->
-<!--   summarize(grid_ensemble = NSE(grid_ensemble, obs), -->
-<!--             statn_ensemble = NSE(statn_ensemble, obs), -->
-<!--             all_ensemble = NSE(all_ensemble, obs), -->
-<!--             grid_all = NSE(grid_all, obs), -->
-<!--             statn_all = NSE(statn_all, obs)) %>% -->
-<!--     mutate_if(is.numeric, -->
-<!--             round, -->
-<!--             digits = 4) -->
-
-<!-- kable(mo_nse) %>% -->
-<!--   kable_styling(full_width = F) -->
-
-<!-- mo_pivot2 <- mo_nse %>% -->
-<!--   pivot_longer(!month, names_to = 'cal_run', values_to = 'nse') %>% -->
-<!--   drop_na() -->
-
-<!-- nse_plot_mo <- ggplot(mo_pivot2, aes(month, nse, color = cal_run)) + geom_point(size = 3) + -->
-<!--   theme_bw() + -->
-<!--   scale_color_manual(name="cal_run", values=c("grid_ensemble"="maroon", -->
-<!--                                             "statn_ensemble"="darkturquoise", -->
-<!--                                             "grid_all"="purple1", -->
-<!--                                             "statn_all"='springgreen4', -->
-<!--                                             "all_ensemble" = "orange")) -->
-
-<!-- ggplotly(nse_plot_mo) -->
-
-<!-- ``` -->
-
-<!-- # Catchment results -->
-
-<!-- ## Precip -->
-
-<!-- ```{r catch precip, echo = F} -->
-<!-- setwd("/Users/megansears/Documents/Repos/fourmile/catchment_output") -->
-
-<!-- statn <- read_csv('statnall.csv') -->
-<!-- grid <- read_csv('gridall.csv') -->
-
-<!-- grid <- grid %>% mutate(site = 'grid') -->
-<!-- statn <- statn %>% mutate(site = 'statn') -->
-
-<!-- catchment <- bind_rows(grid, statn) %>% -->
-<!--   mutate(year = as.factor(year(time))) %>% -->
-<!--   group_by(year, site) %>% -->
-<!--   mutate(cumulative_p = cumsum(precip)) -->
-
-<!-- #plot cumulative precip by year -->
-<!-- plot_cumprecip <- function(calyear) { -->
-<!--   {catchment %>% -->
-<!--     filter(year == calyear) %>% -->
-<!--     ggplot(aes(x = time, -->
-<!--                y = cumulative_p, color = site)) + -->
-<!--     geom_line(size=1) + -->
-<!--     ggtitle(calyear) + -->
-<!--     ylab('Cumulative precip (mm)') + -->
-<!--     theme_bw() + -->
-<!--     theme(axis.text.x = element_text(angle = 45, hjust=1))} %>% -->
-<!--     ggplotly() -->
-<!-- } -->
-
-<!-- name <- levels(catchment$year) -->
-
-<!-- precip_plots <- lapply(name, plot_cumprecip) -->
-
-<!-- htmltools::tagList(precip_plots) -->
-
-<!-- precip_plots -->
-
-<!-- ## total P -->
-<!-- max_cumulativep <- catchment %>% -->
-<!--   group_by(year, site) %>% -->
-<!--   summarize(total_cumulativep = max(cumulative_p)) -->
-
-<!-- ggplot(max_cumulativep, aes(x=year, y=total_cumulativep, color=site)) + -->
-<!--   geom_point(size=3) + -->
-<!--   ggtitle('Total cumulative precip (mm) by year') -->
-
-<!-- ``` -->
-
-<!-- ## Tmean -->
-
-<!-- ```{r tmean catch, echo = F} -->
-<!-- ## tmean -->
-<!-- tmean <- catchment %>% -->
-<!--   group_by(year, site) %>% -->
-<!--   summarize(tmean = mean(tmean)) %>% -->
-<!--   ggplot(aes(x = year, y=tmean, color = site)) + -->
-<!--   geom_point(size=3) + -->
-<!--   ggtitle('Average temp by year') -->
-
-<!-- tmean -->
+<!-- name <- levels(flow_plot$year) -->
+
+<!-- lapply(name, plot_pbias) -->
 
@@
 
-gw_gridall <- read_csv(here('38HRU_sept2013_updates/catchment_output/grid_all.csv'), skip = 3) %>%
+gw_gridall <- read_csv(here('38HRU_dec2024_updates/catchment_output/grid_all.csv'), skip = 3) %>%
   slice(-c(1,2)) %>%
@@
 
-gw_statnall <- read_csv(here('38HRU_sept2013_updates/catchment_output/statn_all.csv'), skip = 3) %>%
+gw_statnall <- read_csv(here('38HRU_dec2024_updates/catchment_output/statn_all.csv'), skip = 3) %>%
   slice(-c(1,2)) %>%
@@
 ) %>%
-  mutate(date = ymd(time),
+  mutate(date = mdy(time),
          year = year(date)) %>%
@@
 ```
-
-# HRU results
-
-```{r cumulative tmean for HRUs, echo = F}
-hrus <- st_read('/Users/megansears/Documents/Repos/fourmile/38HRU_sept2013_updates/hrus_final.shp')
-
-mapview(hrus)
-
-locations <- read_csv('/Users/megansears/Documents/Repos/fourmile/38HRU_sept2013_updates/fourmile_sensors.csv')
-
-locations <- locations %>%
-  st_as_sf(., coords=c('y','x'), crs = 4326)
-
-#grid first
-setwd("/Users/megansears/Documents/Repos/fourmile/38HRU_sept2013_updates/HRU_output/grid")
-
-read_ages_grid <- function(dataframe){
-  read_csv(dataframe, skip = 3) %>%
-  slice(3:n()) %>%
-  dplyr::select(-starts_with('@'),
-                -1) %>%
-  mutate(time = ymd(time)) %>%
-  mutate_if(is.character, as.numeric) %>%
-  mutate(source = 'grid')
-
-}
-
-#pull in all filenames with HRU in the name
-filenames <- list.files(".", pattern="HRU", full.names=F)
-
-#read all the csvs using read_ages function
-dataframes <- lapply(filenames, read_ages_grid)
-
-#name all the csvs based on first 6 characters
-names(dataframes) <- substr(filenames, 1, 6)
-
-#bind all and make 1 df
-hru_grids <- dataframes %>%
-  bind_rows()
-
-#statn next
-setwd("/Users/megansears/Documents/Repos/fourmile/38HRU_sept2013_updates/HRU_output/statn")
-
-read_ages_statn <- function(dataframe){
-  read_csv(dataframe, skip = 3) %>%
-  slice(3:n()) %>%
-  dplyr::select(-starts_with('@'),
-                -1) %>%
-  mutate(time = ymd(time)) %>%
-  mutate_if(is.character, as.numeric) %>%
-  mutate(source = 'statn')
-
-}
-
-#pull in all filenames with HRU in the name
-filenames <- list.files(".", pattern="HRU", full.names=F)
-
-#read all the csvs using read_ages function
-dataframes <- lapply(filenames, read_ages_statn)
-
-#name all the csvs based on first 6 characters
-names(dataframes) <- substr(filenames, 1, 6)
-
-#bind all and make 1 df
-hru_statn <- dataframes %>%
-  bind_rows()
-
-# #get rid of a bunch of data
-# hru_grid_tmean <- hru_grids %>%
-#   dplyr::select(c(time, ID, tmean)) %>%
-#   rename(tmean_grid = tmean)  %>%
-#   group_by(ID) %>%
-#   summarize(tmean_all_grid = mean(tmean_grid))
-# 
-# hru_statn_tmean <- hru_statn %>%
-#   dplyr::select(c(time, ID, tmean)) %>%
-#   rename(tmean_statn = tmean) %>%
-#   group_by(ID) %>%
-#   summarize(tmean_all_statn = mean(tmean_statn))
-# 
-# tmean_hrus <- left_join(hru_grid_tmean, hru_statn_tmean, by = c('ID')) %>%
-#   mutate(diff = tmean_all_statn - tmean_all_grid) %>%
-#   rename(value = ID)
-# 
-# hrus_map_tmean <- left_join(hrus, tmean_hrus, by = 'value')
-# 
-# tmap_mode('view')
-# 
-# locations_t <- locations %>%
-#   dplyr::filter(name %in% c('Gordon_South', 'Gordon_North',
-#                         'Betasso', 'Niwot_Snotel',
-#                         'University Camp SNTL'))
-# 
-# tm_shape(hrus_map_tmean) +
-#   tm_polygons('diff', id = 'value',
-#               breaks = c(-6,-4,-2,0,2,4,6)) +
-# tm_shape(locations_t) +
-#   tm_symbols(col='blue', size=4)
-
-```
-
-## Tmean difference
-Station - grid
-
-```{r}
-#get rid of a bunch of data
-hru_grid_tmean <- hru_grids %>%
-  dplyr::select(c(time, ID, tmean)) %>%
-  rename(tmean_grid = tmean)  %>%
-  group_by(ID) %>%
-  summarize(tmean_all_grid = mean(tmean_grid))
-
-hru_statn_tmean <- hru_statn %>%
-  dplyr::select(c(time, ID, tmean)) %>%
-  rename(tmean_statn = tmean) %>%
-  group_by(ID) %>%
-  summarize(tmean_all_statn = mean(tmean_statn))
-
-tmean_hrus <- left_join(hru_grid_tmean, hru_statn_tmean, by = c('ID')) %>%
-  mutate(diff = tmean_all_statn - tmean_all_grid) %>%
-  rename(value = ID)
-
-hrus_map_tmean <- left_join(hrus, tmean_hrus, by = 'value')
-
-tmean <- ggplot() +
-  geom_sf(data = hrus_map_tmean, aes(fill = diff), color = "black", lwd = 0.2) +
-  scale_fill_viridis_c(option = "plasma", name = "Tmean difference (°C)",
-                       limits = c(-5, 2)) +
-  theme_bw(base_size=13.5) +
-  theme_void() +
-  theme(
-    legend.position = "bottom",
-    panel.grid.major = element_blank(),
-    panel.grid.minor = element_blank(),
-    axis.title.x = element_blank(),
-    axis.title.y = element_blank())
-
-tmean
-
-```
-
-### Tmean season
-
-- Dec-Mar: Winter
-- Apr-Jun: Snowmelt/spring
-- Jul-Aug: Monsoon
-- Sep-Nov: Baseflow/fall
-
-```{r}
-############################
-### look at month
-#get rid of a bunch of data
-hru_grid_tmean_jan <- hru_grids %>%
-  dplyr::select(c(time, ID, tmean)) %>%
-  rename(tmean_grid = tmean)  %>%
-  mutate(month = month(time)) %>%
-  filter(month %in% c(12,1,2,3)) %>%
-  group_by(ID) %>%
-  summarize(tmean_all_grid = mean(tmean_grid))
-
-hru_statn_tmean_jan <- hru_statn %>%
-  dplyr::select(c(time, ID, tmean)) %>%
-  rename(tmean_statn = tmean) %>%
-  mutate(month = month(time)) %>%
-  filter(month %in% c(12,1,2,3)) %>%
-  group_by(ID) %>%
-  summarize(tmean_all_statn = mean(tmean_statn))
-
-tmean_hrus_jan <- left_join(hru_grid_tmean_jan, hru_statn_tmean_jan, by = c('ID')) %>%
-  mutate(diff = tmean_all_statn - tmean_all_grid) %>%
-  rename(value = ID)
-
-hrus_map_tmean_jan <- left_join(hrus, tmean_hrus_jan, by = 'value')
-
-tmean_jan <- ggplot() +
-  geom_sf(data = hrus_map_tmean_jan, aes(fill = diff), color = "black", lwd = 0.2) +
-  scale_fill_viridis_c(option = "plasma", name = "Tmean difference (°C)",
-                       limits = c(-5, 3)) +
-  theme_bw(base_size=13.5) +
-  theme_void() +
-  theme(
-    legend.position = "bottom",
-    panel.grid.major = element_blank(),
-    panel.grid.minor = element_blank(),
-    axis.title.x = element_blank(),
-    axis.title.y = element_blank()) +
-  ggtitle('Winter')
-
-#tmean_jan
-
-## 
-hru_grid_tmean_apr <- hru_grids %>%
-  dplyr::select(c(time, ID, tmean)) %>%
-  rename(tmean_grid = tmean)  %>%
-  mutate(month = month(time)) %>%
-  filter(month %in% c(4,5,6)) %>%
-  group_by(ID) %>%
-  summarize(tmean_all_grid = mean(tmean_grid))
-
-hru_statn_tmean_apr <- hru_statn %>%
-  dplyr::select(c(time, ID, tmean)) %>%
-  rename(tmean_statn = tmean) %>%
-  mutate(month = month(time)) %>%
-  filter(month %in% c(4,5,6)) %>%
-  group_by(ID) %>%
-  summarize(tmean_all_statn = mean(tmean_statn))
-
-tmean_hrus_apr <- left_join(hru_grid_tmean_apr, hru_statn_tmean_apr, by = c('ID')) %>%
-  mutate(diff = tmean_all_statn - tmean_all_grid) %>%
-  rename(value = ID)
-
-hrus_map_tmean_apr <- left_join(hrus, tmean_hrus_apr, by = 'value')
-
-tmean_apr <- ggplot() +
-  geom_sf(data = hrus_map_tmean_apr, aes(fill = diff), color = "black", lwd = 0.2) +
-  scale_fill_viridis_c(option = "plasma", name = "Tmean difference (°C)",
-                       limits = c(-5, 3)) +
-  theme_bw(base_size=13.5) +
-  theme_void() +
-  theme(
-    legend.position = "bottom",
-    panel.grid.major = element_blank(),
-    panel.grid.minor = element_blank(),
-    axis.title.x = element_blank(),
-    axis.title.y = element_blank()) +
-  ggtitle('Snowmelt')
-
-#tmean_apr
-
-#### 
-hru_grid_tmean_jul <- hru_grids %>%
-  dplyr::select(c(time, ID, tmean)) %>%
-  rename(tmean_grid = tmean)  %>%
-  mutate(month = month(time)) %>%
-  filter(month %in% c(7,8)) %>%
-  group_by(ID) %>%
-  summarize(tmean_all_grid = mean(tmean_grid))
-
-hru_statn_tmean_jul <- hru_statn %>%
-  dplyr::select(c(time, ID, tmean)) %>%
-  rename(tmean_statn = tmean) %>%
-  mutate(month = month(time)) %>%
-  filter(month %in% c(7,8)) %>%
-  group_by(ID) %>%
-  summarize(tmean_all_statn = mean(tmean_statn))
-
-tmean_hrus_jul <- left_join(hru_grid_tmean_jul, hru_statn_tmean_jul, by = c('ID')) %>%
-  mutate(diff = tmean_all_statn - tmean_all_grid) %>%
-  rename(value = ID)
-
-hrus_map_tmean_jul <- left_join(hrus, tmean_hrus_jul, by = 'value')
-
-tmean_jul <- ggplot() +
-  geom_sf(data = hrus_map_tmean_jul, aes(fill = diff), color = "black", lwd = 0.2) +
-  scale_fill_viridis_c(option = "plasma", name = "Tmean difference (°C)",
-                            limits = c(-5, 3)) +
-  theme_bw(base_size=13.5) +
-  theme_void() +
-  theme(
-    legend.position = "bottom",
-    panel.grid.major = element_blank(),
-    panel.grid.minor = element_blank(),
-    axis.title.x = element_blank(),
-    axis.title.y = element_blank()) +
-  ggtitle('Monsoon')
-
-#tmean_jul
-
-##
-
-hru_grid_tmean_sep <- hru_grids %>%
-  dplyr::select(c(time, ID, tmean)) %>%
-  rename(tmean_grid = tmean)  %>%
-  mutate(month = month(time)) %>%
-  filter(month %in% c(9,10,11)) %>%
-  group_by(ID) %>%
-  summarize(tmean_all_grid = mean(tmean_grid))
-
-hru_statn_tmean_sep <- hru_statn %>%
-  dplyr::select(c(time, ID, tmean)) %>%
-  rename(tmean_statn = tmean) %>%
-  mutate(month = month(time)) %>%
-  filter(month %in% c(9,10,11)) %>%
-  group_by(ID) %>%
-  summarize(tmean_all_statn = mean(tmean_statn))
-
-tmean_hrus_sep <- left_join(hru_grid_tmean_sep, hru_statn_tmean_sep, by = c('ID')) %>%
-  mutate(diff = tmean_all_statn - tmean_all_grid) %>%
-  rename(value = ID)
-
-hrus_map_tmean_sep <- left_join(hrus, tmean_hrus_sep, by = 'value')
-
-tmean_sep <- ggplot() +
-  geom_sf(data = hrus_map_tmean_sep, aes(fill = diff), color = "black", lwd = 0.2) +
-  scale_fill_viridis_c(option = "plasma", name = "Tmean difference (°C)",
-                       limits = c(-5, 3)) +
-  theme_bw(base_size=13.5) +
-  theme_void() +
-  theme(
-    legend.position = "bottom",
-    panel.grid.major = element_blank(),
-    panel.grid.minor = element_blank(),
-    axis.title.x = element_blank(),
-    axis.title.y = element_blank()) +
-  ggtitle('Fall')
-
-#tmean_sep
-###
-
-lots <- ggarrange(tmean_jan,
-                  tmean_apr,
-                  tmean_jul,
-                  tmean_sep) 
-          #nrow = 4)
-          #ncol= 0)
-lots
-
-```
-
-## Tmax difference
-
-```{r tmax, echo = F}
-
-# #get rid of a bunch of data
-# hru_grid_tmax <- hru_grids %>%
-#   dplyr::select(c(time, ID, tmax)) %>%
-#   rename(tmax_grid = tmax)  %>%
-#   group_by(ID) %>%
-#   summarize(tmax_all_grid = mean(tmax_grid))
-# 
-# hru_statn_tmax <- hru_statn %>%
-#   dplyr::select(c(time, ID, tmax)) %>%
-#   rename(tmax_statn = tmax) %>%
-#   group_by(ID) %>%
-#   summarize(tmax_all_statn = mean(tmax_statn))
-# 
-# tmax_hrus <- left_join(hru_grid_tmax, hru_statn_tmax, by = c('ID')) %>%
-#   mutate(diff = tmax_all_statn - tmax_all_grid) %>%
-#   rename(value = ID)
-# 
-# hrus_map_tmax <- left_join(hrus, tmax_hrus, by = 'value')
-# 
-# tmap_mode('view')
-# 
-# locations_t <- locations %>%
-#   dplyr::filter(name %in% c('Gordon_South', 'Gordon_North',
-#                         'Betasso', 'Niwot_Snotel',
-#                         'University Camp SNTL'))
-# 
-# tm_shape(hrus_map_tmax) +
-#   tm_polygons('diff', id = 'value',
-#               breaks = c(-6,-4,-2,0,2,4,6)) +
-# tm_shape(locations_t) +
-#   tm_symbols(col='blue', size=4)
-
-# T max
-#get rid of a bunch of data
-hru_grid_tmax <- hru_grids %>%
-  dplyr::select(c(time, ID, tmax)) %>%
-  rename(tmax_grid = tmax)  %>%
-  group_by(ID) %>%
-  summarize(tmax_all_grid = mean(tmax_grid))
-
-hru_statn_tmax <- hru_statn %>%
-  dplyr::select(c(time, ID, tmax)) %>%
-  rename(tmax_statn = tmax) %>%
-  group_by(ID) %>%
-  summarize(tmax_all_statn = mean(tmax_statn))
-
-tmax_hrus <- left_join(hru_grid_tmax, hru_statn_tmax, by = c('ID')) %>%
-  mutate(diff = tmax_all_statn - tmax_all_grid) %>%
-  rename(value = ID)
-
-hrus_map_tmax <- left_join(hrus, tmax_hrus, by = 'value')
-
-tmax <- ggplot() +
-  geom_sf(data = hrus_map_tmax, aes(fill = diff), color = "black", lwd = 0.2) +
-  scale_fill_viridis_c(option = "plasma", name = "Tmax difference (°C)",
-                       limits = c(-5, 2)) +
-  theme_bw(base_size=13.5) +
-  theme_void() +
-  theme(
-    legend.position = "bottom",
-    panel.grid.major = element_blank(),
-    panel.grid.minor = element_blank(),
-    axis.title.x = element_blank(),
-    axis.title.y = element_blank())
-
-tmax
-
-```
-
-### Tmax season
-
-- Dec-Mar: Winter
-- Apr-Jun: Snowmelt/spring
-- Jul-Aug: Monsoon
-- Sep-Nov: Baseflow/fall
-
-```{r}
-############################
-### look at month
-#get rid of a bunch of data
-hru_grid_tmax_jan <- hru_grids %>%
-  dplyr::select(c(time, ID, tmax)) %>%
-  rename(tmax_grid = tmax)  %>%
-  mutate(month = month(time)) %>%
-  filter(month %in% c(12,1,2,3)) %>%
-  group_by(ID) %>%
-  summarize(tmax_all_grid = mean(tmax_grid))
-
-hru_statn_tmax_jan <- hru_statn %>%
-  dplyr::select(c(time, ID, tmax)) %>%
-  rename(tmax_statn = tmax) %>%
-  mutate(month = month(time)) %>%
-  filter(month %in% c(12,1,2,3)) %>%
-  group_by(ID) %>%
-  summarize(tmax_all_statn = mean(tmax_statn))
-
-tmax_hrus_jan <- left_join(hru_grid_tmax_jan, hru_statn_tmax_jan, by = c('ID')) %>%
-  mutate(diff = tmax_all_statn - tmax_all_grid) %>%
-  rename(value = ID)
-
-hrus_map_tmax_jan <- left_join(hrus, tmax_hrus_jan, by = 'value')
-
-tmax_jan <- ggplot() +
-  geom_sf(data = hrus_map_tmax_jan, aes(fill = diff), color = "black", lwd = 0.2) +
-  scale_fill_viridis_c(option = "plasma", name = "tmax difference (°C)",
-                       limits = c(-5.1, 3)) +
-  theme_bw(base_size=13.5) +
-  theme_void() +
-  theme(
-    legend.position = "bottom",
-    panel.grid.major = element_blank(),
-    panel.grid.minor = element_blank(),
-    axis.title.x = element_blank(),
-    axis.title.y = element_blank()) +
-  ggtitle('Winter')
-
-#tmax_jan
-
-## 
-hru_grid_tmax_apr <- hru_grids %>%
-  dplyr::select(c(time, ID, tmax)) %>%
-  rename(tmax_grid = tmax)  %>%
-  mutate(month = month(time)) %>%
-  filter(month %in% c(4,5,6)) %>%
-  group_by(ID) %>%
-  summarize(tmax_all_grid = mean(tmax_grid))
-
-hru_statn_tmax_apr <- hru_statn %>%
-  dplyr::select(c(time, ID, tmax)) %>%
-  rename(tmax_statn = tmax) %>%
-  mutate(month = month(time)) %>%
-  filter(month %in% c(4,5,6)) %>%
-  group_by(ID) %>%
-  summarize(tmax_all_statn = mean(tmax_statn))
-
-tmax_hrus_apr <- left_join(hru_grid_tmax_apr, hru_statn_tmax_apr, by = c('ID')) %>%
-  mutate(diff = tmax_all_statn - tmax_all_grid) %>%
-  rename(value = ID)
-
-hrus_map_tmax_apr <- left_join(hrus, tmax_hrus_apr, by = 'value')
-
-tmax_apr <- ggplot() +
-  geom_sf(data = hrus_map_tmax_apr, aes(fill = diff), color = "black", lwd = 0.2) +
-  scale_fill_viridis_c(option = "plasma", name = "tmax difference (°C)",
-                       limits = c(-5.1, 3)) +
-  theme_bw(base_size=13.5) +
-  theme_void() +
-  theme(
-    legend.position = "bottom",
-    panel.grid.major = element_blank(),
-    panel.grid.minor = element_blank(),
-    axis.title.x = element_blank(),
-    axis.title.y = element_blank()) +
-  ggtitle('Snowmelt')
-
-#tmax_apr
-
-#### 
-hru_grid_tmax_jul <- hru_grids %>%
-  dplyr::select(c(time, ID, tmax)) %>%
-  rename(tmax_grid = tmax)  %>%
-  mutate(month = month(time)) %>%
-  filter(month %in% c(7,8)) %>%
-  group_by(ID) %>%
-  summarize(tmax_all_grid = mean(tmax_grid))
-
-hru_statn_tmax_jul <- hru_statn %>%
-  dplyr::select(c(time, ID, tmax)) %>%
-  rename(tmax_statn = tmax) %>%
-  mutate(month = month(time)) %>%
-  filter(month %in% c(7,8)) %>%
-  group_by(ID) %>%
-  summarize(tmax_all_statn = mean(tmax_statn))
-
-tmax_hrus_jul <- left_join(hru_grid_tmax_jul, hru_statn_tmax_jul, by = c('ID')) %>%
-  mutate(diff = tmax_all_statn - tmax_all_grid) %>%
-  rename(value = ID)
-
-hrus_map_tmax_jul <- left_join(hrus, tmax_hrus_jul, by = 'value')
-
-tmax_jul <- ggplot() +
-  geom_sf(data = hrus_map_tmax_jul, aes(fill = diff), color = "black", lwd = 0.2) +
-  scale_fill_viridis_c(option = "plasma", name = "tmax difference (°C)",
-                            limits = c(-5.1, 3)) +
-  theme_bw(base_size=13.5) +
-  theme_void() +
-  theme(
-    legend.position = "bottom",
-    panel.grid.major = element_blank(),
-    panel.grid.minor = element_blank(),
-    axis.title.x = element_blank(),
-    axis.title.y = element_blank()) +
-  ggtitle('Monsoon')
-
-#tmax_jul
-
-##
-
-hru_grid_tmax_sep <- hru_grids %>%
-  dplyr::select(c(time, ID, tmax)) %>%
-  rename(tmax_grid = tmax)  %>%
-  mutate(month = month(time)) %>%
-  filter(month %in% c(9,10,11)) %>%
-  group_by(ID) %>%
-  summarize(tmax_all_grid = mean(tmax_grid))
-
-hru_statn_tmax_sep <- hru_statn %>%
-  dplyr::select(c(time, ID, tmax)) %>%
-  rename(tmax_statn = tmax) %>%
-  mutate(month = month(time)) %>%
-  filter(month %in% c(9,10,11)) %>%
-  group_by(ID) %>%
-  summarize(tmax_all_statn = mean(tmax_statn))
-
-tmax_hrus_sep <- left_join(hru_grid_tmax_sep, hru_statn_tmax_sep, by = c('ID')) %>%
-  mutate(diff = tmax_all_statn - tmax_all_grid) %>%
-  rename(value = ID)
-
-hrus_map_tmax_sep <- left_join(hrus, tmax_hrus_sep, by = 'value')
-
-tmax_sep <- ggplot() +
-  geom_sf(data = hrus_map_tmax_sep, aes(fill = diff), color = "black", lwd = 0.2) +
-  scale_fill_viridis_c(option = "plasma", name = "tmax difference (°C)",
-                       limits = c(-5.1, 3)) +
-  theme_bw(base_size=13.5) +
-  theme_void() +
-  theme(
-    legend.position = "bottom",
-    panel.grid.major = element_blank(),
-    panel.grid.minor = element_blank(),
-    axis.title.x = element_blank(),
-    axis.title.y = element_blank()) +
-  ggtitle('Fall')
-
-#tmax_sep
-###
-
-lots <- ggarrange(tmax_jan,
-                  tmax_apr,
-                  tmax_jul,
-                  tmax_sep) 
-          #nrow = 4)
-          #ncol= 0)
-lots
-
-```
-
-## Tmin difference
-
-```{r tmin, echo = F}
-
-# #get rid of a bunch of data
-# hru_grid_tmin <- hru_grids %>%
-#   dplyr::select(c(time, ID, tmin)) %>%
-#   rename(tmin_grid = tmin)  %>%
-#   group_by(ID) %>%
-#   summarize(tmin_all_grid = mean(tmin_grid))
-# 
-# hru_statn_tmin <- hru_statn %>%
-#   dplyr::select(c(time, ID, tmin)) %>%
-#   rename(tmin_statn = tmin) %>%
-#   group_by(ID) %>%
-#   summarize(tmin_all_statn = mean(tmin_statn))
-# 
-# tmin_hrus <- left_join(hru_grid_tmin, hru_statn_tmin, by = c('ID')) %>%
-#   mutate(diff = tmin_all_statn - tmin_all_grid) %>%
-#   rename(value = ID)
-# 
-# hrus_map_tmin <- left_join(hrus, tmin_hrus, by = 'value')
-# 
-# tmap_mode('view')
-# 
-# locations_t <- locations %>%
-#   dplyr::filter(name %in% c('Gordon_South', 'Gordon_North',
-#                         'Betasso', 'Niwot_Snotel',
-#                         'University Camp SNTL'))
-# 
-# tm_shape(hrus_map_tmin) +
-#   tm_polygons('diff', id = 'value',
-#               breaks = c(-6,-4,-2,0,2,4,6)) +
-# tm_shape(locations_t) +
-#   tm_symbols(col='blue', size=4)
-
-# Tmin
-#get rid of a bunch of data
-hru_grid_tmin <- hru_grids %>%
-  dplyr::select(c(time, ID, tmin)) %>%
-  rename(tmin_grid = tmin)  %>%
-  group_by(ID) %>%
-  summarize(tmin_all_grid = mean(tmin_grid))
-
-hru_statn_tmin <- hru_statn %>%
-  dplyr::select(c(time, ID, tmin)) %>%
-  rename(tmin_statn = tmin) %>%
-  group_by(ID) %>%
-  summarize(tmin_all_statn = mean(tmin_statn))
-
-tmin_hrus <- left_join(hru_grid_tmin, hru_statn_tmin, by = c('ID')) %>%
-  mutate(diff = tmin_all_statn - tmin_all_grid) %>%
-  rename(value = ID)
-
-hrus_map_tmin <- left_join(hrus, tmin_hrus, by = 'value')
-
-tmin <- ggplot() +
-  geom_sf(data = hrus_map_tmin, aes(fill = diff), color = "black", lwd = 0.2) +
-  scale_fill_viridis_c(option = "plasma", name = "Tmin difference (°C)",
-                       limits = c(-5, 2)) +
-  theme_bw(base_size=13.5) +
-  theme_void() +
-  theme(
-    legend.position = "bottom",
-    panel.grid.major = element_blank(),
-    panel.grid.minor = element_blank(),
-    axis.title.x = element_blank(),
-    axis.title.y = element_blank())
-
-tmin
-
-```
-
-### Tmin season
-
-- Dec-Mar: Winter
-- Apr-Jun: Snowmelt/spring
-- Jul-Aug: Monsoon
-- Sep-Nov: Baseflow/fall
-
-```{r}
-############################
-### look at month
-#get rid of a bunch of data
-hru_grid_tmin_jan <- hru_grids %>%
-  dplyr::select(c(time, ID, tmin)) %>%
-  rename(tmin_grid = tmin)  %>%
-  mutate(month = month(time)) %>%
-  filter(month %in% c(12,1,2,3)) %>%
-  group_by(ID) %>%
-  summarize(tmin_all_grid = mean(tmin_grid))
-
-hru_statn_tmin_jan <- hru_statn %>%
-  dplyr::select(c(time, ID, tmin)) %>%
-  rename(tmin_statn = tmin) %>%
-  mutate(month = month(time)) %>%
-  filter(month %in% c(12,1,2,3)) %>%
-  group_by(ID) %>%
-  summarize(tmin_all_statn = mean(tmin_statn))
-
-tmin_hrus_jan <- left_join(hru_grid_tmin_jan, hru_statn_tmin_jan, by = c('ID')) %>%
-  mutate(diff = tmin_all_statn - tmin_all_grid) %>%
-  rename(value = ID)
-
-hrus_map_tmin_jan <- left_join(hrus, tmin_hrus_jan, by = 'value')
-
-tmin_jan <- ggplot() +
-  geom_sf(data = hrus_map_tmin_jan, aes(fill = diff), color = "black", lwd = 0.2) +
-  scale_fill_viridis_c(option = "plasma", name = "tmin difference (°C)",
-                       limits = c(-5, 3)) +
-  theme_bw(base_size=13.5) +
-  theme_void() +
-  theme(
-    legend.position = "bottom",
-    panel.grid.major = element_blank(),
-    panel.grid.minor = element_blank(),
-    axis.title.x = element_blank(),
-    axis.title.y = element_blank()) +
-  ggtitle('Winter')
-
-#tmin_jan
-
-## 
-hru_grid_tmin_apr <- hru_grids %>%
-  dplyr::select(c(time, ID, tmin)) %>%
-  rename(tmin_grid = tmin)  %>%
-  mutate(month = month(time)) %>%
-  filter(month %in% c(4,5,6)) %>%
-  group_by(ID) %>%
-  summarize(tmin_all_grid = mean(tmin_grid))
-
-hru_statn_tmin_apr <- hru_statn %>%
-  dplyr::select(c(time, ID, tmin)) %>%
-  rename(tmin_statn = tmin) %>%
-  mutate(month = month(time)) %>%
-  filter(month %in% c(4,5,6)) %>%
-  group_by(ID) %>%
-  summarize(tmin_all_statn = mean(tmin_statn))
-
-tmin_hrus_apr <- left_join(hru_grid_tmin_apr, hru_statn_tmin_apr, by = c('ID')) %>%
-  mutate(diff = tmin_all_statn - tmin_all_grid) %>%
-  rename(value = ID)
-
-hrus_map_tmin_apr <- left_join(hrus, tmin_hrus_apr, by = 'value')
-
-tmin_apr <- ggplot() +
-  geom_sf(data = hrus_map_tmin_apr, aes(fill = diff), color = "black", lwd = 0.2) +
-  scale_fill_viridis_c(option = "plasma", name = "tmin difference (°C)",
-                       limits = c(-5, 3)) +
-  theme_bw(base_size=13.5) +
-  theme_void() +
-  theme(
-    legend.position = "bottom",
-    panel.grid.major = element_blank(),
-    panel.grid.minor = element_blank(),
-    axis.title.x = element_blank(),
-    axis.title.y = element_blank()) +
-  ggtitle('Snowmelt')
-
-#tmin_apr
-
-#### 
-hru_grid_tmin_jul <- hru_grids %>%
-  dplyr::select(c(time, ID, tmin)) %>%
-  rename(tmin_grid = tmin)  %>%
-  mutate(month = month(time)) %>%
-  filter(month %in% c(7,8)) %>%
-  group_by(ID) %>%
-  summarize(tmin_all_grid = mean(tmin_grid))
-
-hru_statn_tmin_jul <- hru_statn %>%
-  dplyr::select(c(time, ID, tmin)) %>%
-  rename(tmin_statn = tmin) %>%
-  mutate(month = month(time)) %>%
-  filter(month %in% c(7,8)) %>%
-  group_by(ID) %>%
-  summarize(tmin_all_statn = mean(tmin_statn))
-
-tmin_hrus_jul <- left_join(hru_grid_tmin_jul, hru_statn_tmin_jul, by = c('ID')) %>%
-  mutate(diff = tmin_all_statn - tmin_all_grid) %>%
-  rename(value = ID)
-
-hrus_map_tmin_jul <- left_join(hrus, tmin_hrus_jul, by = 'value')
-
-tmin_jul <- ggplot() +
-  geom_sf(data = hrus_map_tmin_jul, aes(fill = diff), color = "black", lwd = 0.2) +
-  scale_fill_viridis_c(option = "plasma", name = "tmin difference (°C)",
-                            limits = c(-5, 3)) +
-  theme_bw(base_size=13.5) +
-  theme_void() +
-  theme(
-    legend.position = "bottom",
-    panel.grid.major = element_blank(),
-    panel.grid.minor = element_blank(),
-    axis.title.x = element_blank(),
-    axis.title.y = element_blank()) +
-  ggtitle('Monsoon')
-
-#tmin_jul
-
-##
-
-hru_grid_tmin_sep <- hru_grids %>%
-  dplyr::select(c(time, ID, tmin)) %>%
-  rename(tmin_grid = tmin)  %>%
-  mutate(month = month(time)) %>%
-  filter(month %in% c(9,10,11)) %>%
-  group_by(ID) %>%
-  summarize(tmin_all_grid = mean(tmin_grid))
-
-hru_statn_tmin_sep <- hru_statn %>%
-  dplyr::select(c(time, ID, tmin)) %>%
-  rename(tmin_statn = tmin) %>%
-  mutate(month = month(time)) %>%
-  filter(month %in% c(9,10,11)) %>%
-  group_by(ID) %>%
-  summarize(tmin_all_statn = mean(tmin_statn))
-
-tmin_hrus_sep <- left_join(hru_grid_tmin_sep, hru_statn_tmin_sep, by = c('ID')) %>%
-  mutate(diff = tmin_all_statn - tmin_all_grid) %>%
-  rename(value = ID)
-
-hrus_map_tmin_sep <- left_join(hrus, tmin_hrus_sep, by = 'value')
-
-tmin_sep <- ggplot() +
-  geom_sf(data = hrus_map_tmin_sep, aes(fill = diff), color = "black", lwd = 0.2) +
-  scale_fill_viridis_c(option = "plasma", name = "tmin difference (°C)",
-                       limits = c(-5, 3)) +
-  theme_bw(base_size=13.5) +
-  theme_void() +
-  theme(
-    legend.position = "bottom",
-    panel.grid.major = element_blank(),
-    panel.grid.minor = element_blank(),
-    axis.title.x = element_blank(),
-    axis.title.y = element_blank()) +
-  ggtitle('Fall')
-
-#tmin_sep
-###
-
-lots <- ggarrange(tmin_jan,
-                  tmin_apr,
-                  tmin_jul,
-                  tmin_sep) 
-          #nrow = 4)
-          #ncol= 0)
-lots
-
-```
-
-## Cumulative Precip difference
-
-2011-2020 average of daily station-grid precip for DOY 365 (or 366)
-
-```{r cum precip, echo = F}
-# #get rid of a bunch of data
-# hru_grid_precip <- hru_grids %>%
-#   dplyr::select(c(time, ID, precip)) %>%
-#   rename(precip_grid = precip)
-# 
-# hru_statn_precip <- hru_statn %>%
-#   dplyr::select(c(time, ID, precip)) %>%
-#   rename(precip_statn = precip)
-# 
-# precip_hrus <- left_join(hru_grid_precip, hru_statn_precip, by = c('time', 'ID')) %>%
-#   mutate(diff = precip_statn - precip_grid,
-#          year = year(time)) %>%
-#   group_by(year, ID) %>%
-#   mutate(total_diff = cumsum(diff)) %>%
-#   filter(time == max(time)) %>%
-#   group_by(ID) %>%
-#   summarize(precip_avg_cumdiff = mean(total_diff)) %>%
-#   rename(value = ID)
-# 
-# hrus_map_precip <- left_join(hrus, precip_hrus, by = 'value')
-# 
-# tmap_mode('view')
-# 
-# locations_p <- locations %>%
-#   filter(type == 'precip')
-# 
-# tm_shape(hrus_map_precip) +
-#   tm_polygons('precip_avg_cumdiff', midpoint = NA, palette = 'YlGnBu', id = 'value') +
-# tm_shape(locations_p) +
-#   tm_symbols(col='blue', size=4)
-
-# Cumulative p
-hru_grid_precip <- hru_grids %>%
-  dplyr::select(c(time, ID, precip)) %>%
-  rename(precip_grid = precip)
-
-hru_statn_precip <- hru_statn %>%
-  dplyr::select(c(time, ID, precip)) %>%
-  rename(precip_statn = precip)
-
-precip_hrus <- left_join(hru_grid_precip, hru_statn_precip, by = c('time', 'ID')) %>%
-  mutate(diff = precip_statn - precip_grid,
-         year = year(time)) %>%
-  group_by(year, ID) %>%
-  mutate(total_diff = cumsum(diff)) %>%
-  filter(time == max(time)) %>%
-  group_by(ID) %>%
-  summarize(precip_avg_cumdiff = mean(total_diff)) %>%
-  rename(value = ID)
-
-hrus_map_precip <- left_join(hrus, precip_hrus, by = 'value')
-
-precip <- ggplot() +
-  geom_sf(data = hrus_map_precip, aes(fill = precip_avg_cumdiff), color = "black", lwd = 0.2) +
-  scale_fill_viridis_c(option = "mako", name = "Cumulative P Difference (mm)") +
-  theme_bw(base_size=13.5) +
-  theme_void() +
-  theme(
-    legend.position = "bottom",
-    panel.grid.major = element_blank(),
-    panel.grid.minor = element_blank(),
-    axis.title.x = element_blank(),
-    axis.title.y = element_blank())
-
-precip
-
-#################
-# winter p
-hru_grid_precip <- hru_grids %>%
-  dplyr::select(c(time, ID, precip)) %>%
-  rename(precip_grid = precip)
-
-hru_statn_precip <- hru_statn %>%
-  dplyr::select(c(time, ID, precip)) %>%
-  rename(precip_statn = precip)
-
-precip_hrus_jan <- left_join(hru_grid_precip, hru_statn_precip, by = c('time', 'ID')) %>%
-  mutate(month = month(time)) %>%
-  filter(month %in% c(12,1,2,3)) %>% 
-  mutate(diff = precip_statn - precip_grid,
-         year = year(time)) %>%
-  group_by(year, ID) %>%
-  mutate(total_diff = cumsum(diff)) %>%
-  filter(time == max(time)) %>%
-  group_by(ID) %>%
-  summarize(precip_avg_cumdiff = mean(total_diff)) %>%
-  rename(value = ID)
-
-hrus_map_precip_jan <- left_join(hrus, precip_hrus_jan, by = 'value')
-
-precip_jan <- ggplot() +
-  geom_sf(data = hrus_map_precip_jan, aes(fill = precip_avg_cumdiff), color = "black", lwd = 0.2) +
-  scale_fill_viridis_c(option = "mako", name = "Cumulative P Difference (mm)",
-                       limits = c(-51, 9.5)) +
-  theme_bw(base_size=13.5) +
-  theme_void() +
-  theme(
-    legend.position = "bottom",
-    panel.grid.major = element_blank(),
-    panel.grid.minor = element_blank(),
-    axis.title.x = element_blank(),
-    axis.title.y = element_blank()) +
-  ggtitle('Winter')
-
-##
-precip_hrus_apr <- left_join(hru_grid_precip, hru_statn_precip, by = c('time', 'ID')) %>%
-  mutate(month = month(time)) %>%
-  filter(month %in% c(4,5,6)) %>% 
-  mutate(diff = precip_statn - precip_grid,
-         year = year(time)) %>%
-  group_by(year, ID) %>%
-  mutate(total_diff = cumsum(diff)) %>%
-  filter(time == max(time)) %>%
-  group_by(ID) %>%
-  summarize(precip_avg_cumdiff = mean(total_diff)) %>%
-  rename(value = ID)
-
-hrus_map_precip_apr <- left_join(hrus, precip_hrus_apr, by = 'value')
-
-precip_apr <- ggplot() +
-  geom_sf(data = hrus_map_precip_apr, aes(fill = precip_avg_cumdiff), color = "black", lwd = 0.2) +
-  scale_fill_viridis_c(option = "mako", name = "Cumulative P Difference (mm)",
-                       limits = c(-51, 9.5)) +
-  theme_bw(base_size=13.5) +
-  theme_void() +
-  theme(
-    legend.position = "bottom",
-    panel.grid.major = element_blank(),
-    panel.grid.minor = element_blank(),
-    axis.title.x = element_blank(),
-    axis.title.y = element_blank()) +
-  ggtitle('Snowmelt')
-##
-
-precip_hrus_jul <- left_join(hru_grid_precip, hru_statn_precip, by = c('time', 'ID')) %>%
-  mutate(month = month(time)) %>%
-  filter(month %in% c(7,8)) %>% 
-  mutate(diff = precip_statn - precip_grid,
-         year = year(time)) %>%
-  group_by(year, ID) %>%
-  mutate(total_diff = cumsum(diff)) %>%
-  filter(time == max(time)) %>%
-  group_by(ID) %>%
-  summarize(precip_avg_cumdiff = mean(total_diff)) %>%
-  rename(value = ID)
-
-hrus_map_precip_jul <- left_join(hrus, precip_hrus_jul, by = 'value')
-
-precip_jul <- ggplot() +
-  geom_sf(data = hrus_map_precip_jul, aes(fill = precip_avg_cumdiff), color = "black", lwd = 0.2) +
-  scale_fill_viridis_c(option = "mako", name = "Cumulative P Difference (mm)",
-                       limits = c(-51, 9.5)) +
-  theme_bw(base_size=13.5) +
-  theme_void() +
-  theme(
-    legend.position = "bottom",
-    panel.grid.major = element_blank(),
-    panel.grid.minor = element_blank(),
-    axis.title.x = element_blank(),
-    axis.title.y = element_blank()) +
-  ggtitle('Monsoon')
-
-## 
-precip_hrus_sep <- left_join(hru_grid_precip, hru_statn_precip, by = c('time', 'ID')) %>%
-  mutate(month = month(time)) %>%
-  filter(month %in% c(9,10,11)) %>% 
-  mutate(diff = precip_statn - precip_grid,
-         year = year(time)) %>%
-  group_by(year, ID) %>%
-  mutate(total_diff = cumsum(diff)) %>%
-  filter(time == max(time)) %>%
-  group_by(ID) %>%
-  summarize(precip_avg_cumdiff = mean(total_diff)) %>%
-  rename(value = ID)
-
-hrus_map_precip_sep <- left_join(hrus, precip_hrus_sep, by = 'value')
-
-precip_sep <- ggplot() +
-  geom_sf(data = hrus_map_precip_sep, aes(fill = precip_avg_cumdiff), color = "black", lwd = 0.2) +
-  scale_fill_viridis_c(option = "mako", name = "Cumulative P Difference (mm)",
-                       limits = c(-51, 9.5)) +
-  theme_bw(base_size=13.5) +
-  theme_void() +
-  theme(
-    legend.position = "bottom",
-    panel.grid.major = element_blank(),
-    panel.grid.minor = element_blank(),
-    axis.title.x = element_blank(),
-    axis.title.y = element_blank()) +
-  ggtitle('Fall')
-
-lots <- ggarrange(precip_jan,
-                  precip_apr,
-                  precip_jul,
-                  precip_sep) 
-          #nrow = 4)
-          #ncol= 0)
-lots
-
-```
-
-## Solar radiation difference
-
-2011-2020 average of daily station-grid solar rad
-
-```{r cum sol rad, echo = F}
-
-# #get rid of a bunch of data
-# hru_grid_solrad <- hru_grids %>%
-#   dplyr::select(c(time, ID, solRad)) %>%
-#   rename(solrad_grid = solRad)  %>%
-#   group_by(ID) %>%
-#   summarize(solrad_all_grid = mean(solrad_grid))
-# 
-# hru_statn_solrad <- hru_statn %>%
-#   dplyr::select(c(time, ID, solRad)) %>%
-#   rename(solrad_statn = solRad) %>%
-#   group_by(ID) %>%
-#   summarize(solrad_all_statn = mean(solrad_statn))
-# 
-# solrad_hrus <- left_join(hru_grid_solrad, hru_statn_solrad, by = c('ID')) %>%
-#   mutate(diff = solrad_all_statn - solrad_all_grid) %>%
-#   rename(value = ID)
-# 
-# hrus_map_solrad <- left_join(hrus, solrad_hrus, by = 'value')
-# 
-# tmap_mode('view')
-# 
-# locations_solrad <- locations %>%
-#   dplyr::filter(name %in% c('Gordon_South',
-#                         'Betasso', 'Niwot_Snotel'))
-# 
-# tm_shape(hrus_map_solrad) +
-#   tm_polygons('diff', midpoint = NA, palette = 'YlOrRd', id = 'value') +
-# tm_shape(locations_solrad) +
-#   tm_symbols(col='blue', size=4)
-
-# solar rad
-hru_grid_solrad <- hru_grids %>%
-  dplyr::select(c(time, ID, solRad)) %>%
-  rename(solrad_grid = solRad)  %>%
-  group_by(ID) %>%
-  summarize(solrad_all_grid = mean(solrad_grid))
-
-hru_statn_solrad <- hru_statn %>%
-  dplyr::select(c(time, ID, solRad)) %>%
-  rename(solrad_statn = solRad) %>%
-  group_by(ID) %>%
-  summarize(solrad_all_statn = mean(solrad_statn))
-
-solrad_hrus <- left_join(hru_grid_solrad, hru_statn_solrad, by = c('ID')) %>%
-  mutate(diff = solrad_all_statn - solrad_all_grid) %>%
-  rename(value = ID)
-
-hrus_map_solrad <- left_join(hrus, solrad_hrus, by = 'value')
-
-sr <- ggplot() +
-  geom_sf(data = hrus_map_solrad, aes(fill = diff), color = "black", lwd = 0.2) +
-  scale_fill_viridis_c(option = "cividis", name = expression("Solar rad difference (MJ/m"^"2" * ")")) +
-  theme_bw(base_size=13.5) +
-  theme_void() +
-  theme(
-    legend.position = "bottom",
-    panel.grid.major = element_blank(),
-    panel.grid.minor = element_blank(),
-    axis.title.x = element_blank(),
-    axis.title.y = element_blank()) +
-  guides(
-    fill = guide_colorbar(
-      label.theme = element_text(size = 10)))
-
-sr
-
-##########
-### look at month
-#get rid of a bunch of data
-hru_grid_solrad_jan <- hru_grids %>%
-  dplyr::select(c(time, ID, solrad_grid=solRad)) %>%
-  mutate(month = month(time)) %>%
-  filter(month %in% c(12,1,2,3)) %>%
-  group_by(ID) %>%
-  summarize(solrad_all_grid = mean(solrad_grid))
-
-hru_statn_solrad_jan <- hru_statn %>%
-  dplyr::select(c(time, ID, solrad_statn=solRad)) %>%
-  mutate(month = month(time)) %>%
-  filter(month %in% c(12,1,2,3)) %>%
-  group_by(ID) %>%
-  summarize(solrad_all_statn = mean(solrad_statn))
-
-solrad_hrus_jan <- left_join(hru_grid_solrad_jan, hru_statn_solrad_jan, by = c('ID')) %>%
-  mutate(diff = solrad_all_statn - solrad_all_grid) %>%
-  rename(value = ID)
-
-hrus_map_solrad_jan <- left_join(hrus, solrad_hrus_jan, by = 'value')
-
-solrad_jan <- ggplot() +
-  geom_sf(data = hrus_map_solrad_jan, aes(fill = diff), color = "black", lwd = 0.2) +
-  scale_fill_viridis_c(option = "cividis", name = expression("Solar rad difference (MJ/m"^"2" * ")"),
-                       limits = c(-8.5, 1.5)) +
-  theme_bw(base_size=13.5) +
-  theme_void() +
-  theme(
-    legend.position = "bottom",
-    panel.grid.major = element_blank(),
-    panel.grid.minor = element_blank(),
-    axis.title.x = element_blank(),
-    axis.title.y = element_blank()) +
-  ggtitle('Winter')
-
-#solrad_jan
-
-## 
-hru_grid_solrad_apr <- hru_grids %>%
-  dplyr::select(c(time, ID, solrad_grid=solRad)) %>%
-  mutate(month = month(time)) %>%
-  filter(month %in% c(4,5,6)) %>%
-  group_by(ID) %>%
-  summarize(solrad_all_grid = mean(solrad_grid))
-
-hru_statn_solrad_apr <- hru_statn %>%
-  dplyr::select(c(time, ID, solrad_statn=solRad)) %>%
-  mutate(month = month(time)) %>%
-  filter(month %in% c(4,5,6)) %>%
-  group_by(ID) %>%
-  summarize(solrad_all_statn = mean(solrad_statn))
-
-solrad_hrus_apr <- left_join(hru_grid_solrad_apr, hru_statn_solrad_apr, by = c('ID')) %>%
-  mutate(diff = solrad_all_statn - solrad_all_grid) %>%
-  rename(value = ID)
-
-hrus_map_solrad_apr <- left_join(hrus, solrad_hrus_apr, by = 'value')
-
-solrad_apr <- ggplot() +
-  geom_sf(data = hrus_map_solrad_apr, aes(fill = diff), color = "black", lwd = 0.2) +
-  scale_fill_viridis_c(option = "cividis", name = expression("Solar rad difference (MJ/m"^"2" * ")"),
-                       limits = c(-8.5, 1.5)) +
-  theme_bw(base_size=13.5) +
-  theme_void() +
-  theme(
-    legend.position = "bottom",
-    panel.grid.major = element_blank(),
-    panel.grid.minor = element_blank(),
-    axis.title.x = element_blank(),
-    axis.title.y = element_blank()) +
-  ggtitle('Snowmelt')
-
-#solrad_apr
-
-#### 
-hru_grid_solrad_jul <- hru_grids %>%
-  dplyr::select(c(time, ID, solrad_grid=solRad)) %>%
-  mutate(month = month(time)) %>%
-  filter(month %in% c(7,8)) %>%
-  group_by(ID) %>%
-  summarize(solrad_all_grid = mean(solrad_grid))
-
-hru_statn_solrad_jul <- hru_statn %>%
-  dplyr::select(c(time, ID, solrad_statn=solRad)) %>%
-  mutate(month = month(time)) %>%
-  filter(month %in% c(7,8)) %>%
-  group_by(ID) %>%
-  summarize(solrad_all_statn = mean(solrad_statn))
-
-solrad_hrus_jul <- left_join(hru_grid_solrad_jul, hru_statn_solrad_jul, by = c('ID')) %>%
-  mutate(diff = solrad_all_statn - solrad_all_grid) %>%
-  rename(value = ID)
-
-hrus_map_solrad_jul <- left_join(hrus, solrad_hrus_jul, by = 'value')
-
-solrad_jul <- ggplot() +
-  geom_sf(data = hrus_map_solrad_jul, aes(fill = diff), color = "black", lwd = 0.2) +
-  scale_fill_viridis_c(option = "cividis", name = expression("Solar rad difference (MJ/m"^"2" * ")"),
-                       limits = c(-8.5, 1.5)) +
-  theme_bw(base_size=13.5) +
-  theme_void() +
-  theme(
-    legend.position = "bottom",
-    panel.grid.major = element_blank(),
-    panel.grid.minor = element_blank(),
-    axis.title.x = element_blank(),
-    axis.title.y = element_blank()) +
-  ggtitle('Monsoon')
-
-#solrad_jul
-
-##
-hru_grid_solrad_sep <- hru_grids %>%
-  dplyr::select(c(time, ID, solrad_grid=solRad)) %>%
-  mutate(month = month(time)) %>%
-  filter(month %in% c(9,10,11)) %>%
-  group_by(ID) %>%
-  summarize(solrad_all_grid = mean(solrad_grid))
-
-hru_statn_solrad_sep <- hru_statn %>%
-  dplyr::select(c(time, ID, solrad_statn=solRad)) %>%
-  mutate(month = month(time)) %>%
-  filter(month %in% c(9,10,11)) %>%
-  group_by(ID) %>%
-  summarize(solrad_all_statn = mean(solrad_statn))
-
-solrad_hrus_sep <- left_join(hru_grid_solrad_sep, hru_statn_solrad_sep, by = c('ID')) %>%
-  mutate(diff = solrad_all_statn - solrad_all_grid) %>%
-  rename(value = ID)
-
-hrus_map_solrad_sep <- left_join(hrus, solrad_hrus_sep, by = 'value')
-
-solrad_sep <- ggplot() +
-  geom_sf(data = hrus_map_solrad_sep, aes(fill = diff), color = "black", lwd = 0.2) +
-  scale_fill_viridis_c(option = "cividis", name = expression("Solar rad difference (MJ/m"^"2" * ")"),
-                       limits = c(-8.5, 1.5)) +
-  theme_bw(base_size=13.5) +
-  theme_void() +
-  theme(
-    legend.position = "bottom",
-    panel.grid.major = element_blank(),
-    panel.grid.minor = element_blank(),
-    axis.title.x = element_blank(),
-    axis.title.y = element_blank()) +
-  ggtitle('Fall')
-
-###
-
-lots <- ggarrange(solrad_jan,
-                  solrad_apr,
-                  solrad_jul,
-                  solrad_sep) 
-          #nrow = 4)
-          #ncol= 0)
-lots
-
-```
-
-## RH difference
-
-```{r rh, echo = F}
-
-# #get rid of a bunch of data
-# hru_grid_rh <- hru_grids %>%
-#   dplyr::select(c(time, ID, rhum)) %>%
-#   rename(rh_grid = rhum)  %>%
-#   group_by(ID) %>%
-#   summarize(rh_all_grid = mean(rh_grid))
-# 
-# hru_statn_rh <- hru_statn %>%
-#   dplyr::select(c(time, ID, rhum)) %>%
-#   rename(rh_statn = rhum) %>%
-#   group_by(ID) %>%
-#   summarize(rh_all_statn = mean(rh_statn))
-# 
-# rh_hrus <- left_join(hru_grid_rh, hru_statn_rh, by = c('ID')) %>%
-#   mutate(diff = rh_all_statn - rh_all_grid) %>%
-#   rename(value = ID)
-# 
-# hrus_map_rh <- left_join(hrus, rh_hrus, by = 'value')
-# 
-# tmap_mode('view')
-# 
-# locations_rh <- locations %>%
-#   dplyr::filter(name %in% c('Gordon_South', 'Gordon_North',
-#                         'Betasso', 'Niwot_Snotel'))
-# 
-# tm_shape(hrus_map_rh) +
-#   tm_polygons('diff', midpoint = NA, id = 'value') +
-# tm_shape(locations_rh) +
-#   tm_symbols(col='blue', size=4)
-
-# RH
-#get rid of a bunch of data
-hru_grid_rh <- hru_grids %>%
-  dplyr::select(c(time, ID, rhum)) %>%
-  rename(rh_grid = rhum)  %>%
-  group_by(ID) %>%
-  summarize(rh_all_grid = mean(rh_grid))
-
-hru_statn_rh <- hru_statn %>%
-  dplyr::select(c(time, ID, rhum)) %>%
-  rename(rh_statn = rhum) %>%
-  group_by(ID) %>%
-  summarize(rh_all_statn = mean(rh_statn))
-
-rh_hrus <- left_join(hru_grid_rh, hru_statn_rh, by = c('ID')) %>%
-  mutate(diff = rh_all_statn - rh_all_grid) %>%
-  rename(value = ID)
-
-hrus_map_rh <- left_join(hrus, rh_hrus, by = 'value')
-
-rh <- ggplot() +
-  geom_sf(data = hrus_map_rh, aes(fill = diff), color = "black", lwd = 0.2) +
-  scale_fill_viridis_c(option = "viridis", name = "RH difference (%)") +
-  theme_bw(base_size=13.5) +
-  theme_void() +
-  theme(
-    legend.position = "bottom",
-    panel.grid.major = element_blank(),
-    panel.grid.minor = element_blank(),
-    axis.title.x = element_blank(),
-    axis.title.y = element_blank())
-
-rh
-#####
-
-hru_grid_rh_jan <- hru_grids %>%
-  dplyr::select(c(time, ID, rh_grid=rhum)) %>%
-  mutate(month = month(time)) %>%
-  filter(month %in% c(12,1,2,3)) %>%
-  group_by(ID) %>%
-  summarize(rh_all_grid = mean(rh_grid))
-
-hru_statn_rh_jan <- hru_statn %>%
-  dplyr::select(c(time, ID, rh_statn=rhum)) %>%
-  mutate(month = month(time)) %>%
-  filter(month %in% c(12,1,2,3)) %>%
-  group_by(ID) %>%
-  summarize(rh_all_statn = mean(rh_statn))
-
-rh_hrus_jan <- left_join(hru_grid_rh_jan, hru_statn_rh_jan, by = c('ID')) %>%
-  mutate(diff = rh_all_statn - rh_all_grid) %>%
-  rename(value = ID)
-
-hrus_map_rh_jan <- left_join(hrus, rh_hrus_jan, by = 'value')
-
-rh_jan <- ggplot() +
-  geom_sf(data = hrus_map_rh_jan, aes(fill = diff), color = "black", lwd = 0.2) +
-  scale_fill_viridis_c(option = "viridis", name = "RH difference (%)",
-                       limits = c(-3, 10.5)) +
-  theme_bw(base_size=13.5) +
-  theme_void() +
-  theme(
-    legend.position = "bottom",
-    panel.grid.major = element_blank(),
-    panel.grid.minor = element_blank(),
-    axis.title.x = element_blank(),
-    axis.title.y = element_blank()) +
-  ggtitle('Winter')
-
-##
-hru_grid_rh_apr <- hru_grids %>%
-  dplyr::select(c(time, ID, rh_grid=rhum)) %>%
-  mutate(month = month(time)) %>%
-  filter(month %in% c(4,5,6)) %>%
-  group_by(ID) %>%
-  summarize(rh_all_grid = mean(rh_grid))
-
-hru_statn_rh_apr <- hru_statn %>%
-  dplyr::select(c(time, ID, rh_statn=rhum)) %>%
-  mutate(month = month(time)) %>%
-  filter(month %in% c(4,5,6)) %>%
-  group_by(ID) %>%
-  summarize(rh_all_statn = mean(rh_statn))
-
-rh_hrus_apr <- left_join(hru_grid_rh_apr, hru_statn_rh_apr, by = c('ID')) %>%
-  mutate(diff = rh_all_statn - rh_all_grid) %>%
-  rename(value = ID)
-
-hrus_map_rh_apr <- left_join(hrus, rh_hrus_apr, by = 'value')
-
-rh_apr <- ggplot() +
-  geom_sf(data = hrus_map_rh_apr, aes(fill = diff), color = "black", lwd = 0.2) +
-  scale_fill_viridis_c(option = "viridis", name = "RH difference (%)",
-                       limits = c(-3, 10.5)) +
-  theme_bw(base_size=13.5) +
-  theme_void() +
-  theme(
-    legend.position = "bottom",
-    panel.grid.major = element_blank(),
-    panel.grid.minor = element_blank(),
-    axis.title.x = element_blank(),
-    axis.title.y = element_blank()) +
-  ggtitle('Snowmelt')
-
-##
-hru_grid_rh_jul <- hru_grids %>%
-  dplyr::select(c(time, ID, rh_grid=rhum)) %>%
-  mutate(month = month(time)) %>%
-  filter(month %in% c(7,8)) %>%
-  group_by(ID) %>%
-  summarize(rh_all_grid = mean(rh_grid))
-
-hru_statn_rh_jul <- hru_statn %>%
-  dplyr::select(c(time, ID, rh_statn=rhum)) %>%
-  mutate(month = month(time)) %>%
-  filter(month %in% c(7,8)) %>%
-  group_by(ID) %>%
-  summarize(rh_all_statn = mean(rh_statn))
-
-rh_hrus_jul <- left_join(hru_grid_rh_jul, hru_statn_rh_jul, by = c('ID')) %>%
-  mutate(diff = rh_all_statn - rh_all_grid) %>%
-  rename(value = ID)
-
-hrus_map_rh_jul <- left_join(hrus, rh_hrus_jul, by = 'value')
-
-rh_jul <- ggplot() +
-  geom_sf(data = hrus_map_rh_jul, aes(fill = diff), color = "black", lwd = 0.2) +
-  scale_fill_viridis_c(option = "viridis", name = "RH difference (%)",
-                       limits = c(-3,10.5)) +
-  theme_bw(base_size=13.5) +
-  theme_void() +
-  theme(
-    legend.position = "bottom",
-    panel.grid.major = element_blank(),
-    panel.grid.minor = element_blank(),
-    axis.title.x = element_blank(),
-    axis.title.y = element_blank()) +
-  ggtitle('Monsoon')
-
-##
-hru_grid_rh_sep <- hru_grids %>%
-  dplyr::select(c(time, ID, rh_grid=rhum)) %>%
-  mutate(month = month(time)) %>%
-  filter(month %in% c(9,10,11)) %>%
-  group_by(ID) %>%
-  summarize(rh_all_grid = mean(rh_grid))
-
-hru_statn_rh_sep <- hru_statn %>%
-  dplyr::select(c(time, ID, rh_statn=rhum)) %>%
-  mutate(month = month(time)) %>%
-  filter(month %in% c(9,10,11)) %>%
-  group_by(ID) %>%
-  summarize(rh_all_statn = mean(rh_statn))
-
-rh_hrus_sep <- left_join(hru_grid_rh_sep, hru_statn_rh_sep, by = c('ID')) %>%
-  mutate(diff = rh_all_statn - rh_all_grid) %>%
-  rename(value = ID)
-
-hrus_map_rh_sep <- left_join(hrus, rh_hrus_sep, by = 'value')
-
-rh_sep <- ggplot() +
-  geom_sf(data = hrus_map_rh_sep, aes(fill = diff), color = "black", lwd = 0.2) +
-  scale_fill_viridis_c(option = "viridis", name = "RH difference (%)",
-                       limits = c(-3,10.5)) +
-  theme_bw(base_size=13.5) +
-  theme_void() +
-  theme(
-    legend.position = "bottom",
-    panel.grid.major = element_blank(),
-    panel.grid.minor = element_blank(),
-    axis.title.x = element_blank(),
-    axis.title.y = element_blank()) +
-  ggtitle('Fall')
-
-lots <- ggarrange(rh_jan,
-                  rh_apr,
-                  rh_jul,
-                  rh_sep) 
-          #nrow = 4)
-          #ncol= 0)
-lots
-
-```
-
-```{r}
-
-# lots <- ggarrange(precip,
-#                   sr,
-#                   rh,
-#                   tmean,
-#                   tmax,
-#                   tmin) 
-#           #nrow = 4)
-#           #ncol= 0)
-# lots
-
-```
-
-## Average soil sat comparison
-
-```{r soilsat, echo = F}
-
-#get rid of a bunch of data
-hru_grid_soilsat <- hru_grids %>%
-  dplyr::select(c(time, ID, soilSat)) %>%
-  rename(soilsat_grid = soilSat)  %>%
-  group_by(ID) %>%
-  summarize(soilsat_all_grid = mean(soilsat_grid))
-
-hru_statn_soilsat <- hru_statn %>%
-  dplyr::select(c(time, ID, soilSat)) %>%
-  rename(soilsat_statn = soilSat) %>%
-  group_by(ID) %>%
-  summarize(soilsat_all_statn = mean(soilsat_statn))
-
-soilsat_hrus <- left_join(hru_grid_soilsat, hru_statn_soilsat, by = c('ID')) %>%
-  rename(value = ID)
-
-hrus_map_soilsat <- left_join(hrus, soilsat_hrus, by = 'value')
-
-tmap_mode('plot')
-
-soilavg_grid <- tm_shape(hrus_map_soilsat) +
-  tm_polygons('soilsat_all_grid', midpoint = NA, id = 'value',
-              breaks = c(0.0, 0.05, 0.1, 0.15, 0.2, 0.25, 0.3, 0.35, 0.4)) +
-  tm_legend(legend.outside = T) +
-  tm_layout(main.title = 'Average soil sat')
-
-soilavg_statn <- tm_shape(hrus_map_soilsat) +
-  tm_polygons('soilsat_all_statn', midpoint = NA, id = 'value',
-              breaks = c(0.0, 0.05, 0.1, 0.15, 0.2, 0.25, 0.3, 0.35, 0.4)) +
-  tm_legend(legend.outside = T)
-
-tmap_arrange(soilavg_grid, soilavg_statn)
-
-```
-
-## Average max soil sat comparison
-
-```{r max soilsat, echo = F}
-
-#get rid of a bunch of data
-hru_grid_soilsat_max <- hru_grids %>%
-  dplyr::select(c(time, ID, soilSat)) %>%
-  rename(soilsat_grid = soilSat)  %>%
-  mutate(year = year(time)) %>%
-  group_by(ID, year) %>%
-  summarize(soilsat_yrmax_grid = max(soilsat_grid)) %>%
-  summarize(avg_max_grid = mean(soilsat_yrmax_grid))
-
-hru_statn_soilsat_max <- hru_statn %>%
-  dplyr::select(c(time, ID, soilSat)) %>%
-  rename(soilsat_statn = soilSat) %>%
-  mutate(year = year(time)) %>%
-  group_by(ID, year) %>%
-  summarize(soilsat_yrmax_statn = max(soilsat_statn)) %>%
-  summarize(avg_max_statn = mean(soilsat_yrmax_statn))
-
-soilsat_hrus_max <- left_join(hru_grid_soilsat_max, hru_statn_soilsat_max, by = c('ID')) %>%
-  rename(value = ID)
-
-hrus_map_soilsat_max <- left_join(hrus, soilsat_hrus_max, by = 'value')
-
-tmap_mode('plot')
-
-soilavg_grid_max <- tm_shape(hrus_map_soilsat_max) +
-  tm_polygons('avg_max_grid', midpoint = NA, id = 'value',
-              breaks = c(0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.7, 0.8)) +
-  tm_legend(legend.outside = T) +
-  tm_layout(main.title = 'Average max soil sat',
-            title.position = c('left', 'top'))
-
-soilavg_statn_max <- tm_shape(hrus_map_soilsat_max) +
-  tm_polygons('avg_max_statn', midpoint = NA, id = 'value',
-              breaks = c(0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.7, 0.8)) +
-  tm_legend(legend.outside = T)
-
-tmap_arrange(soilavg_grid_max, soilavg_statn_max)
-
-```
-
-## Average ET comparison
-
-```{r et, echo = F}
-#get rid of a bunch of data
-hru_grid_ET <- hru_grids %>%
-  dplyr::select(c(time, ID, actET)) %>%
-  rename(ET_grid = actET)  %>%
-  group_by(ID) %>%
-  summarize(ET_all_grid = mean(ET_grid))
-
-hru_statn_ET <- hru_statn %>%
-  dplyr::select(c(time, ID, actET)) %>%
-  rename(ET_statn = actET) %>%
-  group_by(ID) %>%
-  summarize(ET_all_statn = mean(ET_statn))
-
-ET_hrus <- left_join(hru_grid_ET, hru_statn_ET, by = c('ID')) %>%
-  rename(value = ID)
-
-hrus_map_ET <- left_join(hrus, ET_hrus, by = 'value')
-
-tmap_mode('plot')
-
-ETavg_grid <- tm_shape(hrus_map_ET) +
-  tm_polygons('ET_all_grid', midpoint = NA, id = 'value',
-              breaks = c(0.0,0.2, 0.4, 0.6, 0.8, 1.0, 1.2)) +
-  tm_legend(legend.outside = T) +
-  tm_layout(main.title = 'Average ET')
-
-ETavg_statn <- tm_shape(hrus_map_ET) +
-  tm_polygons('ET_all_statn', midpoint = NA, id = 'value',
-             breaks = c(0.0, 0.1, 0.2, 0.4, 0.6, 0.8, 1.0, 1.2)) +
-  tm_legend(legend.outside = T)
-
-tmap_arrange(ETavg_grid, ETavg_statn)
-
-```
-
-## Average ET difference
-
-```{r et diff, echo = F}
-
-ET_hrus <- ET_hrus %>%
-  mutate(diff = ET_all_statn - ET_all_grid)
-
-hrus_map_et_diff <- left_join(hrus, ET_hrus, by = 'value')
-
-tmap_mode('plot')
-
-tm_shape(hrus_map_et_diff) +
-  tm_polygons('diff', midpoint = NA, id = 'value')  +
-  tm_legend(legend.outside = T) +
-  tm_layout(main.title = 'Average ET difference')
-
-```
-
-## Average LAI comparison
-
-```{r lai, echo = F}
-
-#get rid of a bunch of data
-hru_grid_LAI <- hru_grids %>%
-  dplyr::select(c(time, ID, LAI)) %>%
-  rename(LAI_grid = LAI)  %>%
-  group_by(ID) %>%
-  summarize(LAI_all_grid = mean(LAI_grid))
-
-hru_statn_LAI <- hru_statn %>%
-  dplyr::select(c(time, ID, LAI)) %>%
-  rename(LAI_statn = LAI) %>%
-  group_by(ID) %>%
-  summarize(LAI_all_statn = mean(LAI_statn))
-
-LAI_hrus <- left_join(hru_grid_LAI, hru_statn_LAI, by = c('ID')) %>%
-  rename(value = ID)
-
-hrus_map_LAI <- left_join(hrus, LAI_hrus, by = 'value')
-
-tmap_mode('plot')
-
-LAIavg_grid <- tm_shape(hrus_map_LAI) +
-  tm_polygons('LAI_all_grid', midpoint = NA, id = 'value',
-              breaks = c(1,2,3,4,5)) +
-  tm_legend(legend.outside = T) +
-  tm_layout(main.title = 'Average LAI')
-
-LAIavg_statn <- tm_shape(hrus_map_LAI) +
-  tm_polygons('LAI_all_statn', midpoint = NA, id = 'value',
-              breaks = c(1,2,3,4,5)) +
-  tm_legend(legend.outside = T)
-
-tmap_arrange(LAIavg_grid, LAIavg_statn)
-
-```
-
-# HRU RD/RG
-
-Group 1 is lowest elevation, 4 is highest elevation
-
-```{r}
-
-setwd("~/Documents/Repos/fourmile")
-
-elev <- read_csv('./38HRU_sept2013_updates/hru_elev.csv') %>%
-  mutate(elevation_group = ntile(elevation, 4))
-
-rd1_grid <- hru_grids %>%
-  dplyr::select(time, outRD1, ID) %>%
-  mutate(source = 'grid') %>%
-  left_join(., elev, by = 'ID') %>%
-  arrange(time) %>%
-  mutate(year = year(time)) %>%
-  group_by(year, elevation_group) %>%
-  mutate(rd1_summed = cumsum(outRD1)) %>%
-  group_by(year, elevation_group) %>%
-  summarise(max_rd1_summed = max(rd1_summed)) %>%
-  mutate(type = 'grid')
-
-rd1_statn <- hru_statn %>%
-  dplyr::select(time, outRD1, ID) %>%
-  mutate(source = 'statn') %>% 
-  left_join(., elev, by = 'ID') %>%
-  arrange(time) %>%
-  mutate(year = year(time)) %>%
-  group_by(year, elevation_group) %>%
-  mutate(rd1_summed = cumsum(outRD1)) %>%
-  group_by(year, elevation_group) %>%
-  summarise(max_rd1_summed = max(rd1_summed)) %>%
-  mutate(type = 'statn')
-
-rd1_hru <- bind_rows(rd1_grid, rd1_statn)
-
-# elevation group area
-elev_area <- elev %>%
-  group_by(elevation_group) %>%
-  summarize(group_area = sum(area))
-
-rd1_hru <- left_join(rd1_hru, elev_area, by = 'elevation_group') %>%
-  mutate(RD1_mm_year = ((max_rd1_summed/1000)/group_area)/1000)
-
-library(viridis)
-
-rd1_plot <- ggplot(rd1_hru, aes(x=as.factor(year), y=RD1_mm_year, 
-                                      color=as.factor(elevation_group),
-                                      shape = type)) + 
-  geom_point(size = 3) +
-  #scale_color_viridis_d() +
-  theme_bw() +
-  labs(x = 'Year',
-       y = 'Total RD1 (mm/year)')
-
-ggplotly(rd1_plot)
-
-###########################
-
-rd2_grid <- hru_grids %>%
-  dplyr::select(time, outRD2, ID) %>%
-  mutate(source = 'grid') %>%
-  left_join(., elev, by = 'ID') %>%
-  arrange(time) %>%
-  mutate(year = year(time)) %>%
-  group_by(year, elevation_group) %>%
-  mutate(rd2_summed = cumsum(outRD2)) %>%
-  group_by(year, elevation_group) %>%
-  summarise(max_rd2_summed = max(rd2_summed)) %>%
-  mutate(type = 'grid')
-
-rd2_statn <- hru_statn %>%
-  dplyr::select(time, outRD2, ID) %>%
-  mutate(source = 'statn') %>% 
-  left_join(., elev, by = 'ID') %>%
-  arrange(time) %>%
-  mutate(year = year(time)) %>%
-  group_by(year, elevation_group) %>%
-  mutate(rd2_summed = cumsum(outRD2)) %>%
-  group_by(year, elevation_group) %>%
-  summarise(max_rd2_summed = max(rd2_summed)) %>%
-  mutate(type = 'statn')
-
-rd2_hru <- bind_rows(rd2_grid, rd2_statn)
-
-rd2_hru <- left_join(rd2_hru, elev_area, by = 'elevation_group') %>%
-  mutate(rd2_mm_year = ((max_rd2_summed/1000)/group_area)/1000)
-
-rd2_plot <- ggplot(rd2_hru, aes(x=as.factor(year), y=rd2_mm_year, 
-                                      color=as.factor(elevation_group),
-                                      shape = type)) + 
-  geom_point(size = 3) +
-  #scale_color_viridis_d() +
-  theme_bw() +
-  labs(x = 'Year',
-       y = 'Total RD2 (mm/year)')
-
-ggplotly(rd2_plot)
-
-###########
-
-# RG1
-rg1_grid <- hru_grids %>%
-  dplyr::select(time, outRG1, ID) %>%
-  mutate(source = 'grid') %>%
-  left_join(., elev, by = 'ID') %>%
-  arrange(time) %>%
-  mutate(year = year(time)) %>%
-  group_by(year, elevation_group) %>%
-  mutate(rg1_summed = cumsum(outRG1)) %>%
-  group_by(year, elevation_group) %>%
-  summarise(max_rg1_summed = max(rg1_summed)) %>%
-  mutate(type = 'grid')
-
-rg1_statn <- hru_statn %>%
-  dplyr::select(time, outRG1, ID) %>%
-  mutate(source = 'statn') %>% 
-  left_join(., elev, by = 'ID') %>%
-  arrange(time) %>%
-  mutate(year = year(time)) %>%
-  group_by(year, elevation_group) %>%
-  mutate(rg1_summed = cumsum(outRG1)) %>%
-  group_by(year, elevation_group) %>%
-  summarise(max_rg1_summed = max(rg1_summed)) %>%
-  mutate(type = 'statn')
-
-rg1_hru <- bind_rows(rg1_grid, rg1_statn)
-
-rg1_hru <- left_join(rg1_hru, elev_area, by = 'elevation_group') %>%
-  mutate(rg1_mm_year = ((max_rg1_summed/1000)/group_area)/1000)
-
-rg1_plot <- ggplot(rg1_hru, aes(x=as.factor(year), y=rg1_mm_year, 
-                                      color=as.factor(elevation_group),
-                                      shape = type)) + 
-  geom_point(size = 3) +
-  #scale_color_viridis_d() +
-  theme_bw() +
-  labs(x = 'Year',
-       y = 'Total RG1 (mm/year)')
-
-ggplotly(rg1_plot)
-
-#######
-
-# rg2
-rg2_grid <- hru_grids %>%
-  dplyr::select(time, outRG2, ID) %>%
-  mutate(source = 'grid') %>%
-  left_join(., elev, by = 'ID') %>%
-  arrange(time) %>%
-  mutate(year = year(time)) %>%
-  group_by(year, elevation_group) %>%
-  mutate(rg2_summed = cumsum(outRG2)) %>%
-  group_by(year, elevation_group) %>%
-  summarise(max_rg2_summed = max(rg2_summed)) %>%
-  mutate(type = 'grid')
-
-rg2_statn <- hru_statn %>%
-  dplyr::select(time, outRG2, ID) %>%
-  mutate(source = 'statn') %>% 
-  left_join(., elev, by = 'ID') %>%
-  arrange(time) %>%
-  mutate(year = year(time)) %>%
-  group_by(year, elevation_group) %>%
-  mutate(rg2_summed = cumsum(outRG2)) %>%
-  group_by(year, elevation_group) %>%
-  summarise(max_rg2_summed = max(rg2_summed)) %>%
-  mutate(type = 'statn')
-
-rg2_hru <- bind_rows(rg2_grid, rg2_statn)
-
-rg2_hru <- left_join(rg2_hru, elev_area, by = 'elevation_group') %>%
-  mutate(rg2_mm_year = ((max_rg2_summed/1000)/group_area)/1000)
-
-rg2_plot <- ggplot(rg2_hru, aes(x=as.factor(year), y=rg2_mm_year, 
-                                      color=as.factor(elevation_group),
-                                      shape = type)) + 
-  geom_point(size = 3) +
-  #scale_color_viridis_d() +
-  theme_bw() +
-  labs(x = 'Year',
-       y = 'Total RG2 (mm/year)')
-
-ggplotly(rg2_plot)
-
-```
-
-<!-- # Join param & RD/RG -->
-
-<!-- ```{r} -->
-
-<!-- join <- gw_maxcumsum %>% -->
-<!--   rename(input_data = source) -->
-
-<!-- params1 <- params %>% -->
-<!--   dplyr::select(-input_data) %>% -->
-<!--   rename(input_data = cal) %>% -->
-<!--   dplyr::select(-c(year_missing)) -->
-
-<!-- # -->
-<!-- params_weighted1 <- params_weighted %>% -->
-<!--   mutate(input_data = paste(source, year_missing, sep = "_")) %>% -->
-<!--   pivot_wider(names_from = 'param', -->
-<!--               values_from = 'area_weighted_average') %>% -->
-<!--   rename_with(~ paste0(., '_weighted'), 4:9) %>% -->
-<!--   dplyr::select(-c(year_missing, source)) -->
-
-<!-- join <- left_join(join, params1, by = c('input_data')) %>% -->
-<!--   pivot_wider(., names_from='param', values_from='value') %>% -->
-<!--   pivot_wider(., names_from = 'flow_type', values_from = 'flow_cms') -->
-
-<!-- join <- left_join(join, params_weighted1, by = 'input_data') -->
-
-<!-- write_csv(join, '/Users/megansears/Documents/Repos/fourmile/38HRU_sept2013_updates/flow_params.csv') -->
-
-<!-- ``` -->

### 2025-01-17 spatial_figs.Rmd
few minor site map updates

@@
 dem_raster <- merge(dem_raster, dem_raster2)
+
+dem_raster1 <- rast(dem_raster)
+
+# extract min, max
+min <- terra::extract(dem_raster1, hru_new, 'min', touches=T)
+min(min$layer)
+
+max <- terra::extract(dem_raster1, hru_new, 'max', touches=T)
+max(max$layer)
 
@@
                     labels = c("Gridded", "Observed")) +   # Rename fill legend items
-  theme_bw(base_size = 12) +
+  theme_bw(base_size = 20) +
   labs(y = 'Precipitation (mm)',
@@
   guides(color = guide_legend(title = NULL),
-         fill = guide_legend(title = NULL))
+         fill = guide_legend(title = NULL)) +
+    theme(
+    panel.grid = element_blank(),
+    panel.background = element_rect(fill = "white"),
+    text = element_text(color = "black"),
+    axis.title = element_text(color = "black"),
+    axis.text = element_text(color = "black"),
+    strip.text = element_blank()
+  )
 

### 2025-01-17 fourmile_output_dec2024.Rmd
found out what was wrong with grid_all KGE: 9/12/13 Q still included (not in cal but copied from elsewhere when putting together discharge_all.csv)
updated most recent cals (still need grid 2014-2020) and forward runs

@@
 
-```{r look at kge, echo = F}
-
-# kge_plot <- ggplot(kge, aes(year_missing, KGE, shape = input_data, color = input_data)) + geom_point(size = 3) +
-#   theme_bw()
-# 
-# ggplotly(kge_plot)
-
-```
-
 # Parameters
@@
 
-# grid_2011 <- read_cals(grid_2011., name = 'grid_2011')
-# grid_2012 <- read_cals(grid_2012., name = 'grid_2012')
-# grid_2013 <- read_cals(grid_2013., name = 'grid_2013')
+grid_2011 <- read_cals(grid_2011., name = 'grid_2011')
+grid_2012 <- read_cals(grid_2012., name = 'grid_2012')
+grid_2013 <- read_cals(grid_2013., name = 'grid_2013')
 # grid_2014 <- read_cals(grid_2014., name = 'grid_2014')
@@
 
-# grid <- bind_rows(grid_2011, grid_2012, grid_2013, grid_2014, grid_2015,
-#                   grid_2016, grid_2017, grid_2018, grid_2019, grid_2020,
-#                   grid_all) %>%
-#   mutate(input_data = 'grid') %>%
-#   mutate(year_missing_almost = gsub('grid_', '', cal)) %>%
-#   mutate(year_missing = gsub('all', 'none', year_missing_almost)) %>%
-#   dplyr::select(-c(year_missing_almost)) %>%
-#   rename(param = Parameter) %>%
-#   filter(!param == 'locGrw',
-#          !param == 'tempRes')
-
-grid <- grid_all %>%
+grid <- bind_rows(grid_2011, grid_2012, grid_2013, #grid_2014, grid_2015,
+                  #grid_2016, grid_2017, grid_2018, grid_2019, grid_2020,
+                  grid_all) %>%
   mutate(input_data = 'grid') %>%
@@
 
-# statn_2011 <- read_cals(statn_2011, name = 'statn_2011')
-# statn_2012 <- read_cals(statn_2012, name = 'statn_2012')
-# statn_2013 <- read_cals(statn_2013, name = 'statn_2013')
-# statn_2014 <- read_cals(statn_2014, name = 'statn_2014')
-# statn_2015 <- read_cals(statn_2015, name = 'statn_2015')
-# statn_2016 <- read_cals(statn_2016, name = 'statn_2016')
-# statn_2017 <- read_cals(statn_2017, name = 'statn_2017')
-# statn_2018 <- read_cals(statn_2018, name = 'statn_2018')
-# statn_2019 <- read_cals(statn_2019, name = 'statn_2019')
-# statn_2020 <- read_cals(statn_2020, name = 'statn_2020')
+statn_2011 <- read_cals(statn_2011, name = 'statn_2011')
+statn_2012 <- read_cals(statn_2012, name = 'statn_2012')
+statn_2013 <- read_cals(statn_2013, name = 'statn_2013')
+statn_2014 <- read_cals(statn_2014, name = 'statn_2014')
+statn_2015 <- read_cals(statn_2015, name = 'statn_2015')
+statn_2016 <- read_cals(statn_2016, name = 'statn_2016')
+statn_2017 <- read_cals(statn_2017, name = 'statn_2017')
+statn_2018 <- read_cals(statn_2018, name = 'statn_2018')
+statn_2019 <- read_cals(statn_2019, name = 'statn_2019')
+statn_2020 <- read_cals(statn_2020, name = 'statn_2020')
 statn_all <- read_cals(statn_all., name = 'statn_all')
 
-# statn <- bind_rows(statn_2011, statn_2012, statn_2013, statn_2014, statn_2015,
-#                   statn_2016, statn_2017, statn_2018, statn_2019, statn_2020,
-#                   statn_all) %>%
-#   mutate(input_data = 'statn') %>%
-#   mutate(year_missing_almost = gsub('statn_', '', cal)) %>%
-#   mutate(year_missing = gsub('all', 'none', year_missing_almost)) %>%
-#   dplyr::select(-c(year_missing_almost)) %>%
-#   rename(param = Parameter) %>%
-#   filter(!param == 'locGrw',
-#          !param == 'tempRes')
-
-statn <- statn_all %>%
+statn <- bind_rows(statn_2011, statn_2012, statn_2013, statn_2014, statn_2015,
+                  statn_2016, statn_2017, statn_2018, statn_2019, statn_2020,
+                  statn_all) %>%
   mutate(input_data = 'statn') %>%
@@
 
-# mean_params <- params %>%
-#   group_by(param, input_data) %>%
-#   summarize(mean = mean(value))
-# 
-# plotdens_params <- function(param_name) {
-#   params %>%
-#     filter(param == param_name) %>%
-#     ggplot(aes(x = value,
-#                fill = input_data, 
-#                color = input_data)) + 
-#     geom_density(alpha=0.5) +
-#     geom_vline(data=filter(mean_params, param == param_name), 
-#                aes(xintercept=mean, color=input_data),
-#              linetype="dashed", linewidth=0.75) +
-#     ggtitle(param_name) +
-#     theme_bw()
-# }
-# 
-# name <- levels(params$param)
-# 
-# lapply(name, plotdens_params)
+mean_params <- params %>%
+  group_by(param, input_data) %>%
+  summarize(mean = mean(value))
+
+plotdens_params <- function(param_name) {
+  params %>%
+    filter(param == param_name) %>%
+    ggplot(aes(x = value,
+               fill = input_data,
+               color = input_data)) +
+    geom_density(alpha=0.5) +
+    geom_vline(data=filter(mean_params, param == param_name),
+               aes(xintercept=mean, color=input_data),
+             linetype="dashed", linewidth=0.75) +
+    ggtitle(param_name) +
+    theme_bw()
+}
+
+name <- levels(params$param)
+
+lapply(name, plotdens_params)
 
@@
 
-# rm(statn_2011, statn_2012, statn_2013, statn_2014, statn_2015,
-#                   statn_2016, statn_2017, statn_2018, statn_2019, statn_2020,
-#                   statn_all., statn_all)
-
-rm(statn_all)
+rm(statn_2011, statn_2012, statn_2013, statn_2014, statn_2015,
+                  statn_2016, statn_2017, statn_2018, statn_2019, statn_2020,
+                  statn_all., statn_all)
 
@@
 
-# grid_2011_burn <- read_cals_burn(grid_2011., name = 'grid_2011')
-# grid_2012_burn <- read_cals_burn(grid_2012., name = 'grid_2012')
-# grid_2013_burn <- read_cals_burn(grid_2013., name = 'grid_2013')
+grid_2011_burn <- read_cals_burn(grid_2011., name = 'grid_2011')
+grid_2012_burn <- read_cals_burn(grid_2012., name = 'grid_2012')
+grid_2013_burn <- read_cals_burn(grid_2013., name = 'grid_2013')
 # grid_2014_burn <- read_cals_burn(grid_2014., name = 'grid_2014')
@@
 
-# grid_burn <- bind_rows(grid_2011_burn, 
-#                   grid_2012_burn, 
-#                   grid_2013_burn, 
+grid_burn <- bind_rows(grid_2011_burn,
+                  grid_2012_burn,
+                  grid_2013_burn,
                   # grid_2014_burn,
@@
                   # grid_2020_burn,
-#                   grid_all_burn) %>%
-#   mutate(input_data = 'grid') %>%
-#   mutate(year_missing_almost = gsub('grid_', '', cal)) %>%
-#   mutate(year_missing = gsub('all', 'none', year_missing_almost)) %>%
-#   dplyr::select(-c(year_missing_almost))
-
-grid_burn <- grid_all_burn %>%
+                  grid_all_burn) %>%
   mutate(input_data = 'grid') %>%
@@
 # now do statn burn params
-# statn_2011_burn <- read_cals_burn(statn_2011, name = 'statn_2011')
-# statn_2012_burn <- read_cals_burn(statn_2012, name = 'statn_2012')
-# statn_2013_burn <- read_cals_burn(statn_2013, name = 'statn_2013')
-# statn_2014_burn <- read_cals_burn(statn_2014, name = 'statn_2014')
-# statn_2015_burn <- read_cals_burn(statn_2015, name = 'statn_2015')
-# statn_2016_burn <- read_cals_burn(statn_2016, name = 'statn_2016')
-# statn_2017_burn <- read_cals_burn(statn_2017, name = 'statn_2017')
-# statn_2018_burn <- read_cals_burn(statn_2018, name = 'statn_2018')
-# statn_2019_burn <- read_cals_burn(statn_2019, name = 'statn_2019')
-# statn_2020_burn <- read_cals_burn(statn_2020, name = 'statn_2020')
+statn_2011_burn <- read_cals_burn(statn_2011, name = 'statn_2011')
+statn_2012_burn <- read_cals_burn(statn_2012, name = 'statn_2012')
+statn_2013_burn <- read_cals_burn(statn_2013, name = 'statn_2013')
+statn_2014_burn <- read_cals_burn(statn_2014, name = 'statn_2014')
+statn_2015_burn <- read_cals_burn(statn_2015, name = 'statn_2015')
+statn_2016_burn <- read_cals_burn(statn_2016, name = 'statn_2016')
+statn_2017_burn <- read_cals_burn(statn_2017, name = 'statn_2017')
+statn_2018_burn <- read_cals_burn(statn_2018, name = 'statn_2018')
+statn_2019_burn <- read_cals_burn(statn_2019, name = 'statn_2019')
+statn_2020_burn <- read_cals_burn(statn_2020, name = 'statn_2020')
 statn_all_burn <- read_cals_burn(statn_all., name = 'statn_all')
 
-# statn_burn <- bind_rows(statn_2011_burn, 
-#                   statn_2012_burn, 
-#                   statn_2013_burn, 
-#                   statn_2014_burn, 
-#                   statn_2015_burn,
-#                   statn_2016_burn, 
-#                   statn_2017_burn, 
-#                   statn_2018_burn, 
-#                   statn_2019_burn, 
-#                   statn_2020_burn,
-#                   statn_all_burn) %>%
-#   mutate(input_data = 'statn') %>%
-#   mutate(year_missing_almost = gsub('statn_', '', cal)) %>%
-#   mutate(year_missing = gsub('all', 'none', year_missing_almost)) %>%
-#   dplyr::select(-c(year_missing_almost))
-
-statn_burn <- statn_all_burn %>%
+statn_burn <- bind_rows(statn_2011_burn,
+                  statn_2012_burn,
+                  statn_2013_burn,
+                  statn_2014_burn,
+                  statn_2015_burn,
+                  statn_2016_burn,
+                  statn_2017_burn,
+                  statn_2018_burn,
+                  statn_2019_burn,
+                  statn_2020_burn,
+                  statn_all_burn) %>%
   mutate(input_data = 'statn') %>%
@@
 ```{r echo = FALSE, message = FALSE, warning = FALSE}
+
 params2 <- params %>%
@@
 
-# Outlet results
-
-## Hydrograph
-
-```{r hydrographs, echo = FALSE, message = FALSE, warning = FALSE, fig.width=10, fig.height=6}
-
-setwd('/Users/megansears/Documents/Repos/fourmile/38HRU_dec2024_updates')
-
-flow <- read_csv('discharge_all.csv') %>%
-  replace(.==-9999, NA) %>%
-  rename(date = time) %>%
-  mutate(date = mdy(date))
-
-flow_pivot <- flow %>%
-  pivot_longer(!date, names_to = 'cal_run', values_to = 'q_m3s') %>%
-  mutate(year = as.factor(year(date)))
-
-q <- ggplot(flow_pivot, aes(date, q_m3s, color = cal_run)) +
-  geom_line() +
-  scale_color_manual(name="cal_run", values=c('obs' = 'black',
-                                            # "grid_2011"="seagreen",
-                                            # "grid_2012"="seagreen2",
-                                            # "grid_2013"="steelblue",
-                                            # "grid_2014"='dodgerblue',
-                                            # "grid_2015" = "cyan3",
-                                            # 'grid_2016' = 'blue',
-                                            # 'grid_2017' = 'blue4',
-                                            # 'grid_2018' = 'cadetblue',
-                                            # 'grid_2019' = 'lightgreen',
-                                            # 'grid_2020' = 'olivedrab',
-                                            'grid_all' = 'steelblue3',
-                                            # "statn_2011"="maroon",
-                                            # "statn_2012"="deeppink4",
-                                            # "statn_2013"="deeppink",
-                                            # "statn_2014"='purple',
-                                            # "statn_2015" = "mediumorchid1",
-                                            # 'statn_2016' = 'indianred',
-                                            # 'statn_2017' = 'sienna',
-                                            # 'statn_2018' = 'salmon2',
-                                            # 'statn_2019' = 'mediumpurple1',
-                                            # 'statn_2020' = 'violetred',
-                                            'statn_all' = 'red')) +
-  theme_bw(base_size=20)
-
-ggplotly(q)
-
-```
-
-## Cumulative volume
-
-```{r cumq, echo = FALSE, message = FALSE, warning = FALSE}
-
-flow_cumq <- flow_pivot %>%
-  mutate(month = month(date)) %>%
-  filter(month %in% c(4:9)) %>%
-  dplyr::select(-month) %>%
-  #pivot_longer(!date, names_to = 'cal_run', values_to = 'q_m3s') %>%
-  mutate(vol_m3 = q_m3s * 86400) %>%
-  group_by(cal_run, year(date)) %>%
-  mutate(cumsum = cumsum(replace_na(vol_m3, 0))) %>%
-  #rename(year = 4) %>%
-  mutate(year = as.factor(year)) %>%
-  ungroup()
-
-#plot annual cumulative Q vals for ensembles
-plot_cumulq_yr_ <- function(calyear) {
-  {flow_cumq %>%
-    filter(year == calyear) %>%
-    ggplot(aes(x = date,
-               y = cumsum,
-               color = cal_run)) +
-    geom_line() +
-scale_color_manual(name="cal_run", values=c('obs' = 'black',
-                                            # "grid_2011"="seagreen",
-                                            # "grid_2012"="seagreen2",
-                                            # "grid_2013"="steelblue",
-                                            # "grid_2014"='dodgerblue',
-                                            # "grid_2015" = "cyan3",
-                                            # 'grid_2016' = 'blue',
-                                            # 'grid_2017' = 'blue4',
-                                            # 'grid_2018' = 'cadetblue',
-                                            # 'grid_2019' = 'lightgreen',
-                                            # 'grid_2020' = 'olivedrab',
-                                            'grid_all' = 'steelblue3',
-                                            # "statn_2011"="maroon",
-                                            # "statn_2012"="deeppink4",
-                                            # "statn_2013"="deeppink",
-                                            # "statn_2014"='purple',
-                                            # "statn_2015" = "mediumorchid1",
-                                            # 'statn_2016' = 'indianred',
-                                            # 'statn_2017' = 'sienna',
-                                            # 'statn_2018' = 'salmon2',
-                                            # 'statn_2019' = 'mediumpurple1',
-                                            # 'statn_2020' = 'violetred',
-                                            'statn_all' = 'red')) +
-    ggtitle(calyear) +
-    theme_bw() +
-    labs(y = 'Volume (m^3)')} %>%
-    ggplotly()
-}
-
-name <- levels(flow_cumq$year)
-
-cumulative_plots <- lapply(name, plot_cumulq_yr_)
-
-htmltools::tagList(cumulative_plots)
-
-cumulative_plots
-
-```
-
-## KGE
-
-### Overall KGE
-
-```{r kge overall, echo = FALSE, message = FALSE, warning = FALSE}
-
-# flow_kge_all <- flow %>%
-#   summarize(grid2011 = KGE(grid_2011, obs),
-#             grid2012 = KGE(grid_2012, obs),
-#             grid2013 = KGE(grid_2013, obs),
-#             grid2014 = KGE(grid_2014, obs),
-#             grid2015 = KGE(grid_2015, obs),
-#             grid2016 = KGE(grid_2016, obs),
-#             grid2017 = KGE(grid_2017, obs),
-#             grid2018 = KGE(grid_2018, obs),
-#             grid2019 = KGE(grid_2019, obs),
-#             grid2020 = KGE(grid_2020, obs),
-#             gridall = KGE(grid_all, obs),
-#             statn2011 = KGE(statn_2011, obs),
-#             statn2012 = KGE(statn_2012, obs),
-#             statn2013 = KGE(statn_2013, obs),
-#             statn2014 = KGE(statn_2014, obs),
-#             statn2015 = KGE(statn_2015, obs),
-#             statn2016 = KGE(statn_2016, obs),
-#             statn2017 = KGE(statn_2017, obs),
-#             statn2018 = KGE(statn_2018, obs),
-#             statn2019 = KGE(statn_2019, obs),
-#             statn2020 = KGE(statn_2020, obs),
-#             statnall = KGE(statn_all, obs)) %>%
-#     mutate_if(is.numeric,
-#             round,
-#             digits = 2)
-
-flow_kge_all <- flow %>%
-  summarize(
-            gridall = KGE(grid_all,
-                          obs, 
-                          na.rm=T, 
-                          method='2012'),
-            statnall = KGE(statn_all, 
-                           obs, 
-                           na.rm=T,
-                           method='2012')) %>%
-    mutate_if(is.numeric,
-            round,
-            digits = 2)
-
-flow_kge_all <- flow_kge_all %>%
-  pivot_longer(everything()) %>%
-  arrange(value)
-
-kable(flow_kge_all) %>%
-  kable_styling(full_width = F)
-
-```
-
-### KGE by year
-
-```{r kge by year, echo = FALSE, message = FALSE, warning = FALSE}
-
-flow_year <- flow %>%
-  mutate(year = year(date)) %>%
-  group_by(year) %>%
-  summarize(
-    # grid2011 = KGE(grid_2011, obs),
-    #         grid2012 = KGE(grid_2012, obs),
-    #         grid2013 = KGE(grid_2013, obs),
-    #         grid2014 = KGE(grid_2014, obs),
-    #         grid2015 = KGE(grid_2015, obs),
-    #         grid2016 = KGE(grid_2016, obs),
-    #         grid2017 = KGE(grid_2017, obs),
-    #         grid2018 = KGE(grid_2018, obs),
-    #         grid2019 = KGE(grid_2019, obs),
-    #         grid2020 = KGE(grid_2020, obs),
-            gridall = KGE(grid_all, obs, na.rm = T, method='2012'),
-            # statn2011 = KGE(statn_2011, obs),
-            # statn2012 = KGE(statn_2012, obs),
-            # statn2013 = KGE(statn_2013, obs),
-            # statn2014 = KGE(statn_2014, obs),
-            # statn2015 = KGE(statn_2015, obs),
-            # statn2016 = KGE(statn_2016, obs),
-            # statn2017 = KGE(statn_2017, obs),
-            # statn2018 = KGE(statn_2018, obs),
-            # statn2019 = KGE(statn_2019, obs),
-            # statn2020 = KGE(statn_2020, obs),
-            statnall = KGE(statn_all, obs, na.rm=T, method='2012')) %>%
-    mutate_if(is.numeric,
-            round,
-            digits = 2)
-
-flow_kge <- flow_year %>%
-  pivot_longer(!year, names_to = 'model_run', values_to = 'kge') %>%
-  pivot_wider(names_from = 'year', values_from = 'kge')
-
-flow_kge %>%
-  kable(.) %>%
-  kable_styling()
-
-flow_plot <- flow_year %>%
-  pivot_longer(!year, names_to = 'model_run', values_to = 'kge') %>%
-  mutate(year = as.factor(year))
-
-# add all to the plot below
-kge_all <- flow_kge_all %>%
-  mutate(year = 'all years') %>%
-  rename(model_run = name,
-         kge = value)
-
-flow_plot_updated <- bind_rows(flow_plot, kge_all)
-
-ggplot(flow_plot_updated, aes(x = model_run, y = year, fill = kge)) +
-  geom_tile(color = "white") +
-  scale_fill_viridis_c(option = "viridis", name = "KGE", direction = -1) +
-  geom_text(aes(label = round(kge, 2)), color = "grey", size = 2.5) +
-  theme_bw() +
-  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
-  labs(y = "Year")
-
-```
-
-<!-- ### Annual KGE plots -->
-
-<!-- ```{r wy plots, echo = FALSE, message = FALSE, warning = FALSE} -->
-
-<!-- plot_kge <- function(calyear) { -->
-<!--   flow_plot %>% -->
+<!-- # Outlet results -->
+
+<!-- ## Hydrograph -->
+
+<!-- ```{r hydrographs, echo = FALSE, message = FALSE, warning = FALSE, fig.width=10, fig.height=6} -->
+
+<!-- setwd('/Users/megansears/Documents/Repos/fourmile/38HRU_dec2024_updates') -->
+
+<!-- flow <- read_csv('discharge_all.csv') %>% -->
+<!--   replace(.==-9999, NA) %>% -->
+<!--   rename(date = time) %>% -->
+<!--   mutate(date = mdy(date))  -->
+
+<!-- flow_pivot <- flow %>% -->
+<!--   pivot_longer(!date, names_to = 'cal_run', values_to = 'q_m3s') %>% -->
+<!--   mutate(year = as.factor(year(date))) -->
+
+<!-- q <- ggplot(flow_pivot, aes(date, q_m3s, color = cal_run)) + -->
+<!--   geom_line() + -->
+<!--   scale_color_manual(name="cal_run", values=c('obs' = 'black', -->
+<!--                                             # "grid_2011"="seagreen", -->
+<!--                                             # "grid_2012"="seagreen2", -->
+<!--                                             # "grid_2013"="steelblue", -->
+<!--                                             # "grid_2014"='dodgerblue', -->
+<!--                                             # "grid_2015" = "cyan3", -->
+<!--                                             # 'grid_2016' = 'blue', -->
+<!--                                             # 'grid_2017' = 'blue4', -->
+<!--                                             # 'grid_2018' = 'cadetblue', -->
+<!--                                             # 'grid_2019' = 'lightgreen', -->
+<!--                                             # 'grid_2020' = 'olivedrab', -->
+<!--                                             'grid_all' = 'steelblue3', -->
+<!--                                             # "statn_2011"="maroon", -->
+<!--                                             # "statn_2012"="deeppink4", -->
+<!--                                             # "statn_2013"="deeppink", -->
+<!--                                             # "statn_2014"='purple', -->
+<!--                                             # "statn_2015" = "mediumorchid1", -->
+<!--                                             # 'statn_2016' = 'indianred', -->
+<!--                                             # 'statn_2017' = 'sienna', -->
+<!--                                             # 'statn_2018' = 'salmon2', -->
+<!--                                             # 'statn_2019' = 'mediumpurple1', -->
+<!--                                             # 'statn_2020' = 'violetred', -->
+<!--                                             'statn_all' = 'red')) + -->
+<!--   theme_bw(base_size=20) -->
+
+<!-- ggplotly(q) -->
+
+<!-- ``` -->
+
+<!-- ## Cumulative volume -->
+
+<!-- ```{r cumq, echo = FALSE, message = FALSE, warning = FALSE} -->
+
+<!-- flow_cumq <- flow_pivot %>% -->
+<!--   mutate(month = month(date)) %>% -->
+<!--   filter(month %in% c(4:9)) %>% -->
+<!--   dplyr::select(-month) %>% -->
+<!--   #pivot_longer(!date, names_to = 'cal_run', values_to = 'q_m3s') %>% -->
+<!--   mutate(vol_m3 = q_m3s * 86400) %>% -->
+<!--   group_by(cal_run, year(date)) %>% -->
+<!--   mutate(cumsum = cumsum(replace_na(vol_m3, 0))) %>% -->
+<!--   #rename(year = 4) %>% -->
+<!--   mutate(year = as.factor(year)) %>% -->
+<!--   ungroup() -->
+
+<!-- #plot annual cumulative Q vals for ensembles -->
+<!-- plot_cumulq_yr_ <- function(calyear) { -->
+<!--   {flow_cumq %>% -->
 <!--     filter(year == calyear) %>% -->
-<!--     ggplot(aes(x = model_run, -->
-<!--                y = kge)) + -->
-<!--     geom_point(size=3) + -->
+<!--     ggplot(aes(x = date, -->
+<!--                y = cumsum, -->
+<!--                color = cal_run)) + -->
+<!--     geom_line() + -->
+<!-- scale_color_manual(name="cal_run", values=c('obs' = 'black', -->
+<!--                                             # "grid_2011"="seagreen", -->
+<!--                                             # "grid_2012"="seagreen2", -->
+<!--                                             # "grid_2013"="steelblue", -->
+<!--                                             # "grid_2014"='dodgerblue', -->
+<!--                                             # "grid_2015" = "cyan3", -->
+<!--                                             # 'grid_2016' = 'blue', -->
+<!--                                             # 'grid_2017' = 'blue4', -->
+<!--                                             # 'grid_2018' = 'cadetblue', -->
+<!--                                             # 'grid_2019' = 'lightgreen', -->
+<!--                                             # 'grid_2020' = 'olivedrab', -->
+<!--                                             'grid_all' = 'steelblue3', -->
+<!--                                             # "statn_2011"="maroon", -->
+<!--                                             # "statn_2012"="deeppink4", -->
+<!--                                             # "statn_2013"="deeppink", -->
+<!--                                             # "statn_2014"='purple', -->
+<!--                                             # "statn_2015" = "mediumorchid1", -->
+<!--                                             # 'statn_2016' = 'indianred', -->
+<!--                                             # 'statn_2017' = 'sienna', -->
+<!--                                             # 'statn_2018' = 'salmon2', -->
+<!--                                             # 'statn_2019' = 'mediumpurple1', -->
+<!--                                             # 'statn_2020' = 'violetred', -->
+<!--                                             'statn_all' = 'red')) + -->
 <!--     ggtitle(calyear) + -->
 <!--     theme_bw() + -->
-<!--     theme(axis.text.x = element_text(angle = 45, hjust=1)) -->
+<!--     labs(y = 'Volume (m^3)')} %>% -->
+<!--     ggplotly() -->
 <!-- } -->
 
-<!-- name <- levels(flow_plot$year) -->
-
-<!-- lapply(name, plot_kge) -->
+<!-- name <- levels(flow_cumq$year) -->
+
+<!-- cumulative_plots <- lapply(name, plot_cumulq_yr_) -->
+
+<!-- htmltools::tagList(cumulative_plots) -->
+
+<!-- cumulative_plots -->
 
@@
 
-## Pbias
-
-### Overall pbias
-
-```{r pbias overall, echo = FALSE, message = FALSE, warning = FALSE}
-
-flow_pbias_all <- flow %>%
-  summarize(
-    # grid2011 = pbias(grid_2011, obs),
-    #         grid2012 = pbias(grid_2012, obs),
-    #         grid2013 = pbias(grid_2013, obs),
-    #         grid2014 = pbias(grid_2014, obs),
-    #         grid2015 = pbias(grid_2015, obs),
-    #         grid2016 = pbias(grid_2016, obs),
-    #         grid2017 = pbias(grid_2017, obs),
-    #         grid2018 = pbias(grid_2018, obs),
-    #         grid2019 = pbias(grid_2019, obs),
-    #         grid2020 = pbias(grid_2020, obs),
-            gridall = pbias(grid_all, obs),
-            # statn2011 = pbias(statn_2011, obs),
-            # statn2012 = pbias(statn_2012, obs),
-            # statn2013 = pbias(statn_2013, obs),
-            # statn2014 = pbias(statn_2014, obs),
-            # statn2015 = pbias(statn_2015, obs),
-            # statn2016 = pbias(statn_2016, obs),
-            # statn2017 = pbias(statn_2017, obs),
-            # statn2018 = pbias(statn_2018, obs),
-            # statn2019 = pbias(statn_2019, obs),
-            # statn2020 = pbias(statn_2020, obs),
-            statnall = pbias(statn_all, obs)) %>%
-    mutate_if(is.numeric,
-            round,
-            digits = 2)
-
-flow_pbias_all <- flow_pbias_all %>%
-  pivot_longer(everything()) %>%
-  arrange(abs(value))
-
-kable(flow_pbias_all) %>%
-  kable_styling(full_width = F)
-
-```
-
-### Pbias by year
-
-```{r pbias by year, echo = FALSE, message = FALSE, warning = FALSE}
-
-flow_year <- flow %>%
-  mutate(year = year(date)) %>%
-  group_by(year) %>%
-  summarize(
-    # grid2011 = pbias(grid_2011, obs),
-    #         grid2012 = pbias(grid_2012, obs),
-    #         grid2013 = pbias(grid_2013, obs),
-    #         grid2014 = pbias(grid_2014, obs),
-    #         grid2015 = pbias(grid_2015, obs),
-    #         grid2016 = pbias(grid_2016, obs),
-    #         grid2017 = pbias(grid_2017, obs),
-    #         grid2018 = pbias(grid_2018, obs),
-    #         grid2019 = pbias(grid_2019, obs),
-    #         grid2020 = pbias(grid_2020, obs),
-            gridall = pbias(grid_all, obs),
-            # statn2011 = pbias(statn_2011, obs),
-            # statn2012 = pbias(statn_2012, obs),
-            # statn2013 = pbias(statn_2013, obs),
-            # statn2014 = pbias(statn_2014, obs),
-            # statn2015 = pbias(statn_2015, obs),
-            # statn2016 = pbias(statn_2016, obs),
-            # statn2017 = pbias(statn_2017, obs),
-            # statn2018 = pbias(statn_2018, obs),
-            # statn2019 = pbias(statn_2019, obs),
-            # statn2020 = pbias(statn_2020, obs),
-            statnall = pbias(statn_all, obs)) %>%
-    mutate_if(is.numeric,
-            round,
-            digits = 2)
-
-flow_pbias <- flow_year %>%
-  pivot_longer(!year, names_to = 'model_run', values_to = 'pbias') %>%
-  pivot_wider(names_from = 'year', values_from = 'pbias')
-
-flow_pbias %>%
-  kable(.) %>%
-  kable_styling()
-
-flow_plot <- flow_year %>%
-  pivot_longer(!year, names_to = 'model_run', values_to = 'pbias') %>%
-  mutate(year = as.factor(year))
-
-# add all to the plot below
-pbias_all <- flow_pbias_all %>%
-  mutate(year = 'all years') %>%
-  rename(model_run = name,
-         pbias = value)
-
-flow_plot_updated <- bind_rows(flow_plot, pbias_all)
-
-ggplot(flow_plot_updated, aes(x = model_run, y = year, fill = pbias)) +
-  geom_tile(color = "white") +
-   scale_fill_gradient2(low = "blue", mid = "white", high = "red", midpoint = 0, name = "Pbias") +
-  geom_text(aes(label = round(pbias, 2)), color = "black", size = 2.5) +
-  theme_bw() +
-  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
-  labs(y = "Year")
-
-```
-
-<!-- ### Annual Pbias plots -->
-
-<!-- ```{r pbias plots, echo = FALSE, message = FALSE, warning = FALSE} -->
-
-<!-- plot_pbias <- function(calyear) { -->
-<!--   flow_plot %>% -->
-<!--     filter(year == calyear) %>% -->
-<!--     ggplot(aes(x = model_run, -->
-<!--                y = pbias)) + -->
-<!--     geom_point(size=3) + -->
-<!--     ggtitle(calyear) + -->
+<!-- ## KGE -->
+
+<!-- ### Overall KGE -->
+
+<!-- ```{r kge overall, echo = FALSE, message = FALSE, warning = FALSE} -->
+
+<!-- # flow_kge_all <- flow %>% -->
+<!-- #   summarize(grid2011 = KGE(grid_2011, obs), -->
+<!-- #             grid2012 = KGE(grid_2012, obs), -->
+<!-- #             grid2013 = KGE(grid_2013, obs), -->
+<!-- #             grid2014 = KGE(grid_2014, obs), -->
+<!-- #             grid2015 = KGE(grid_2015, obs), -->
+<!-- #             grid2016 = KGE(grid_2016, obs), -->
+<!-- #             grid2017 = KGE(grid_2017, obs), -->
+<!-- #             grid2018 = KGE(grid_2018, obs), -->
+<!-- #             grid2019 = KGE(grid_2019, obs), -->
+<!-- #             grid2020 = KGE(grid_2020, obs), -->
+<!-- #             gridall = KGE(grid_all, obs), -->
+<!-- #             statn2011 = KGE(statn_2011, obs), -->
+<!-- #             statn2012 = KGE(statn_2012, obs), -->
+<!-- #             statn2013 = KGE(statn_2013, obs), -->
+<!-- #             statn2014 = KGE(statn_2014, obs), -->
+<!-- #             statn2015 = KGE(statn_2015, obs), -->
+<!-- #             statn2016 = KGE(statn_2016, obs), -->
+<!-- #             statn2017 = KGE(statn_2017, obs), -->
+<!-- #             statn2018 = KGE(statn_2018, obs), -->
+<!-- #             statn2019 = KGE(statn_2019, obs), -->
+<!-- #             statn2020 = KGE(statn_2020, obs), -->
+<!-- #             statnall = KGE(statn_all, obs)) %>% -->
+<!-- #     mutate_if(is.numeric, -->
+<!-- #             round, -->
+<!-- #             digits = 2) -->
+
+<!-- kge_grid <- flow %>% -->
+<!--   summarize(grid_kge = KGE(grid_all, -->
+<!--                            obs, -->
+<!--                            na.rm=T, -->
+<!--                            method = '2012')) -->
+
+<!-- flow_kge_all <- flow %>% -->
+<!--   summarize( -->
+<!--             gridall = KGE(grid_all, -->
+<!--                           obs,  -->
+<!--                           na.rm=T,  -->
+<!--                           method='2012'), -->
+<!--             statnall = KGE(statn_all,  -->
+<!--                            obs,  -->
+<!--                            na.rm=T, -->
+<!--                            method='2012')) %>% -->
+<!--     mutate_if(is.numeric, -->
+<!--             round, -->
+<!--             digits = 2) -->
+
+<!-- flow_kge_all <- flow_kge_all %>% -->
+<!--   pivot_longer(everything()) %>% -->
+<!--   arrange(value) -->
+
+<!-- kable(flow_kge_all) %>% -->
+<!--   kable_styling(full_width = F) -->
+
+<!-- ``` -->
+
+<!-- ### KGE by year -->
+
+<!-- ```{r kge by year, echo = FALSE, message = FALSE, warning = FALSE} -->
+
+<!-- flow_year <- flow %>% -->
+<!--   mutate(year = year(date)) %>% -->
+<!--   group_by(year) %>% -->
+<!--   summarize( -->
+<!--     # grid2011 = KGE(grid_2011, obs), -->
+<!--     #         grid2012 = KGE(grid_2012, obs), -->
+<!--     #         grid2013 = KGE(grid_2013, obs), -->
+<!--     #         grid2014 = KGE(grid_2014, obs), -->
+<!--     #         grid2015 = KGE(grid_2015, obs), -->
+<!--     #         grid2016 = KGE(grid_2016, obs), -->
+<!--     #         grid2017 = KGE(grid_2017, obs), -->
+<!--     #         grid2018 = KGE(grid_2018, obs), -->
+<!--     #         grid2019 = KGE(grid_2019, obs), -->
+<!--     #         grid2020 = KGE(grid_2020, obs), -->
+<!--             gridall = KGE(grid_all, obs, na.rm = T, method='2012'), -->
+<!--             # statn2011 = KGE(statn_2011, obs), -->
+<!--             # statn2012 = KGE(statn_2012, obs), -->
+<!--             # statn2013 = KGE(statn_2013, obs), -->
+<!--             # statn2014 = KGE(statn_2014, obs), -->
+<!--             # statn2015 = KGE(statn_2015, obs), -->
+<!--             # statn2016 = KGE(statn_2016, obs), -->
+<!--             # statn2017 = KGE(statn_2017, obs), -->
+<!--             # statn2018 = KGE(statn_2018, obs), -->
+<!--             # statn2019 = KGE(statn_2019, obs), -->
+<!--             # statn2020 = KGE(statn_2020, obs), -->
+<!--             statnall = KGE(statn_all, obs, na.rm=T, method='2012')) %>% -->
+<!--     mutate_if(is.numeric, -->
+<!--             round, -->
+<!--             digits = 2) -->
+
+<!-- flow_kge <- flow_year %>% -->
+<!--   pivot_longer(!year, names_to = 'model_run', values_to = 'kge') %>% -->
+<!--   pivot_wider(names_from = 'year', values_from = 'kge') -->
+
+<!-- flow_kge %>% -->
+<!--   kable(.) %>% -->
+<!--   kable_styling() -->
+
+<!-- flow_plot <- flow_year %>% -->
+<!--   pivot_longer(!year, names_to = 'model_run', values_to = 'kge') %>% -->
+<!--   mutate(year = as.factor(year)) -->
+
+<!-- # add all to the plot below -->
+<!-- kge_all <- flow_kge_all %>% -->
+<!--   mutate(year = 'all years') %>% -->
+<!--   rename(model_run = name, -->
+<!--          kge = value) -->
+
+<!-- flow_plot_updated <- bind_rows(flow_plot, kge_all) -->
+
+<!-- ggplot(flow_plot_updated, aes(x = model_run, y = year, fill = kge)) + -->
+<!--   geom_tile(color = "white") + -->
+<!--   scale_fill_viridis_c(option = "viridis", name = "KGE", direction = -1) + -->
+<!--   geom_text(aes(label = round(kge, 2)), color = "grey", size = 2.5) + -->
 <!--   theme_bw() + -->
-<!--     theme(axis.text.x = element_text(angle = 45, hjust=1)) -->
-<!-- } -->
-
-<!-- name <- levels(flow_plot$year) -->
-
-<!-- lapply(name, plot_pbias) -->
+<!--   theme(axis.text.x = element_text(angle = 45, hjust = 1)) + -->
+<!--   labs(y = "Year") -->
 
@@
 
-# RD and RG
-
-- **Different units than streamflow (cms) and volume (m3)**
-- **All in mm**
-
-```{r rd and rg, echo = FALSE, message = FALSE, warning = FALSE, fig.width = 14, fig.asp = 1, out.width = "100%"}
-
-gw_gridall <- read_csv(here('38HRU_dec2024_updates/catchment_output/grid_all.csv'), skip = 3) %>%
-  slice(-c(1,2)) %>%
-  dplyr::select(time, catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w) %>%
-  mutate(source = 'grid_all') %>%
-  mutate(across(c(catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w), as.numeric))
-
-gw_statnall <- read_csv(here('38HRU_dec2024_updates/catchment_output/statn_all.csv'), skip = 3) %>%
-  slice(-c(1,2)) %>%
-  dplyr::select(time, catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w) %>%
-  mutate(source = 'statn_all') %>%
-  mutate(across(c(catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w), as.numeric))
-
-# gw_grid2011 <- read_csv(here('38HRU_sept2013_updates/catchment_output/grid_2011.csv'), skip = 3) %>%
-#   slice(-c(1,2)) %>%
-#   dplyr::select(time, catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w) %>%
-#   mutate(source = 'grid_2011')%>%
-#   mutate(across(c(catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w), as.numeric))
-#
-# gw_grid2012 <- read_csv(here('38HRU_sept2013_updates/catchment_output/grid_2012.csv'), skip = 3) %>%
-#   slice(-c(1,2)) %>%
-#   dplyr::select(time, catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w) %>%
-#   mutate(source = 'grid_2012')%>%
-#   mutate(across(c(catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w), as.numeric))
-#
-# gw_grid2013 <- read_csv(here('38HRU_sept2013_updates/catchment_output/grid_2013.csv'), skip = 3) %>%
-#   slice(-c(1,2)) %>%
-#   dplyr::select(time, catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w) %>%
-#   mutate(source = 'grid_2013')%>%
-#   mutate(across(c(catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w), as.numeric))
-#
-# gw_grid2014 <- read_csv(here('38HRU_sept2013_updates/catchment_output/grid_2014.csv'), skip = 3) %>%
-#   slice(-c(1,2)) %>%
-#   dplyr::select(time, catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w) %>%
-#   mutate(source = 'grid_2014')%>%
-#   mutate(across(c(catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w), as.numeric))
-#
-# gw_grid2015 <- read_csv(here('38HRU_sept2013_updates/catchment_output/grid_2015.csv'), skip = 3) %>%
-#   slice(-c(1,2)) %>%
-#   dplyr::select(time, catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w) %>%
-#   mutate(source = 'grid_2015')%>%
-#   mutate(across(c(catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w), as.numeric))
-#
-# gw_grid2016 <- read_csv(here('38HRU_sept2013_updates/catchment_output/grid_2016.csv'), skip = 3) %>%
-#   slice(-c(1,2)) %>%
-#   dplyr::select(time, catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w) %>%
-#   mutate(source = 'grid_2016')%>%
-#   mutate(across(c(catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w), as.numeric))
-#
-# gw_grid2017 <- read_csv(here('38HRU_sept2013_updates/catchment_output/grid_2017.csv'), skip = 3) %>%
-#   slice(-c(1,2)) %>%
-#   dplyr::select(time, catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w) %>%
-#   mutate(source = 'grid_2017')%>%
-#   mutate(across(c(catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w), as.numeric))
-#
-# gw_grid2018 <- read_csv(here('38HRU_sept2013_updates/catchment_output/grid_2018.csv'), skip = 3) %>%
-#   slice(-c(1,2)) %>%
-#   dplyr::select(time, catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w) %>%
-#   mutate(source = 'grid_2018')%>%
-#   mutate(across(c(catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w), as.numeric))
-#
-# gw_grid2019 <- read_csv(here('38HRU_sept2013_updates/catchment_output/grid_2019.csv'), skip = 3) %>%
-#   slice(-c(1,2)) %>%
-#   dplyr::select(time, catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w) %>%
-#   mutate(source = 'grid_2019')%>%
-#   mutate(across(c(catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w), as.numeric))
-#
-# gw_grid2020 <- read_csv(here('38HRU_sept2013_updates/catchment_output/grid_2020.csv'), skip = 3) %>%
-#   slice(-c(1,2)) %>%
-#   dplyr::select(time, catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w) %>%
-#   mutate(source = 'grid_2020')%>%
-#   mutate(across(c(catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w), as.numeric))
-#
-# gw_statn2011 <- read_csv(here('38HRU_sept2013_updates/catchment_output/statn_2011.csv'), skip = 3) %>%
-#   slice(-c(1,2)) %>%
-#   dplyr::select(time, catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w) %>%
-#   mutate(source = 'statn_2011')%>%
-#   mutate(across(c(catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w), as.numeric))
-#
-# gw_statn2012 <- read_csv(here('38HRU_sept2013_updates/catchment_output/statn_2012.csv'), skip = 3) %>%
-#   slice(-c(1,2)) %>%
-#   dplyr::select(time, catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w) %>%
-#   mutate(source = 'statn_2012')%>%
-#   mutate(across(c(catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w), as.numeric))
-#
-# gw_statn2013 <- read_csv(here('38HRU_sept2013_updates/catchment_output/statn_2013.csv'), skip = 3) %>%
-#   slice(-c(1,2)) %>%
-#   dplyr::select(time, catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w) %>%
-#   mutate(source = 'statn_2013')%>%
-#   mutate(across(c(catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w), as.numeric))
-#
-# gw_statn2014 <- read_csv(here('38HRU_sept2013_updates/catchment_output/statn_2014.csv'), skip = 3) %>%
-#   slice(-c(1,2)) %>%
-#   dplyr::select(time, catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w) %>%
-#   mutate(source = 'statn_2014')%>%
-#   mutate(across(c(catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w), as.numeric))
-#
-# gw_statn2015 <- read_csv(here('38HRU_sept2013_updates/catchment_output/statn_2015.csv'), skip = 3) %>%
-#   slice(-c(1,2)) %>%
-#   dplyr::select(time, catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w) %>%
-#   mutate(source = 'statn_2015')%>%
-#   mutate(across(c(catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w), as.numeric))
-#
-# gw_statn2016 <- read_csv(here('38HRU_sept2013_updates/catchment_output/statn_2016.csv'), skip = 3) %>%
-#   slice(-c(1,2)) %>%
-#   dplyr::select(time, catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w) %>%
-#   mutate(source = 'statn_2016')%>%
-#   mutate(across(c(catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w), as.numeric))
-#
-# gw_statn2017 <- read_csv(here('38HRU_sept2013_updates/catchment_output/statn_2017.csv'), skip = 3) %>%
-#   slice(-c(1,2)) %>%
-#   dplyr::select(time, catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w) %>%
-#   mutate(source = 'statn_2017')%>%
-#   mutate(across(c(catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w), as.numeric))
-#
-# gw_statn2018 <- read_csv(here('38HRU_sept2013_updates/catchment_output/statn_2018.csv'), skip = 3) %>%
-#   slice(-c(1,2)) %>%
-#   dplyr::select(time, catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w) %>%
-#   mutate(source = 'statn_2018')%>%
-#   mutate(across(c(catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w), as.numeric))
-#
-# gw_statn2019 <- read_csv(here('38HRU_sept2013_updates/catchment_output/statn_2019.csv'), skip = 3) %>%
-#   slice(-c(1,2)) %>%
-#   dplyr::select(time, catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w) %>%
-#   mutate(source = 'statn_2019')%>%
-#   mutate(across(c(catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w), as.numeric))
-#
-# gw_statn2020 <- read_csv(here('38HRU_sept2013_updates/catchment_output/statn_2020.csv'), skip = 3) %>%
-#   slice(-c(1,2)) %>%
-#   dplyr::select(time, catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w) %>%
-#   mutate(source = 'statn_2020')%>%
-#   mutate(across(c(catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w), as.numeric))
-
-gw <- bind_rows(
-  gw_gridall, gw_statnall
-  # gw_grid2011, gw_grid2012,
-  # gw_grid2013, gw_grid2014,
-  # gw_grid2015, gw_grid2016,
-  # gw_grid2017, gw_grid2018,
-  # gw_grid2019, gw_grid2020,
-  # gw_statn2011, gw_statn2012,
-  # gw_statn2013, gw_statn2014,
-  # gw_statn2015, gw_statn2016,
-  # gw_statn2017, gw_statn2018,
-  # gw_statn2019, gw_statn2020
-) %>%
-  mutate(date = mdy(time),
-         year = year(date)) %>%
-  arrange(date)
-
-ggplot(gw, aes(x=date, color = source)) +
-  geom_line(aes(y=catchmentRD1_w), size =1) +
-  facet_wrap(~year, scales = 'free', ncol = 2) +
-  scale_x_date(labels = date_format("%b")) +
-  ggtitle('RD1') +
-  theme(text = element_text(size = 20)) +
-  labs(y = 'RD1 (mm)')
-
-ggplot(gw, aes(x=date, color = source)) +
-  geom_line(aes(y=catchmentRD2_w), size =1) +
-  facet_wrap(~year, scales = 'free', ncol = 2) +
-  scale_x_date(labels = date_format("%b")) +
-  ggtitle('RD2') +
-  theme(text = element_text(size = 20))+
-  labs(y = 'RD2 (mm)')
-
-ggplot(gw, aes(x=date, color = source)) +
-  geom_line(aes(y=catchmentRG1_w), size =1) +
-  facet_wrap(~year, scales = 'free', ncol = 2) +
-  scale_x_date(labels = date_format("%b")) +
-  ggtitle('RG1') +
-  theme(text = element_text(size = 20)) +
-  labs(y = 'RG1 (mm)')
-
-ggplot(gw, aes(x=date, color = source)) +
-  geom_line(aes(y=catchmentRG2_w), size =1) +
-  facet_wrap(~year, scales = 'free', ncol=2) +
-  scale_x_date(labels = date_format("%b")) +
-  ggtitle('RG2') +
-  theme(text = element_text(size = 20))+
-  labs(y = 'RG2 (mm)')
-
-gw <- gw %>%
-  arrange(date) %>%
-  group_by(year, source) %>%
-  mutate(RD1cumsum = cumsum(catchmentRD1_w),
-         RD2cumsum = cumsum(catchmentRD2_w),
-         RG1cumsum = cumsum(catchmentRG1_w),
-         RG2cumsum = cumsum(catchmentRG2_w))
-
-ggplot(gw, aes(x=date, color = source)) +
-  geom_line(aes(y=RD1cumsum), size =1) +
-  facet_wrap(~year, scales = 'free', ncol=2) +
-  scale_x_date(labels = date_format("%b")) +
-  ggtitle('Cumulative RD1 (mm)') +
-  theme(text = element_text(size = 20))
-
-ggplot(gw, aes(x=date, color = source)) +
-  geom_line(aes(y=RD2cumsum), size = 1) +
-  facet_wrap(~year, scales = 'free', ncol=2) +
-  scale_x_date(labels = date_format("%b")) +
-  ggtitle('Cumulative RD2 (mm)') +
-  theme(text = element_text(size = 20))
-
-ggplot(gw, aes(x=date, color = source)) +
-  geom_line(aes(y=RG1cumsum), size  = 1) +
-  facet_wrap(~year, scales = 'free', ncol = 2) +
-  scale_x_date(labels = date_format("%b")) +
-  ggtitle('Cumulative RG1 (mm)') +
-  theme(text = element_text(size = 20))
-
-ggplot(gw, aes(x=date, color = source)) +
-  geom_line(aes(y=RG2cumsum), size =1) +
-  facet_wrap(~year, scales = 'free', ncol = 2) +
-  scale_x_date(labels = date_format("%b")) +
-  ggtitle('Cumulative RG2 (mm)') +
-  theme(text = element_text(size = 20))
-
-```
-
-```{r rd and rg sums, echo = FALSE, message = FALSE, warning = FALSE, fig.width = 22, fig.asp = 1.5, out.width = "100%"}
-
-##################
-# all 4 with facets
-
-ggplot(gw, aes(x=date)) +
-  geom_line(aes(y=RG2cumsum, color = 'cumulative RG2'), size =1) +
-  geom_line(aes(y=RG1cumsum, color = 'cumulative RG1'), size =1) +
-  geom_line(aes(y=RD1cumsum, color = 'cumulative RD1'), size =1) +
-  geom_line(aes(y=RD2cumsum, color = 'cumulative RD2'), size =1) +
-  scale_x_date(labels = date_format("%b")) +
-  facet_wrap(~year + source, scales = 'free_x', ncol=2) +
-  ggtitle('Cumulative RD and RG (mm)') +
-  theme(text = element_text(size = 24))
-
-```
-
-```{r gw boxplot, echo = FALSE, message = FALSE, warning = FALSE}
-
-gw_maxcumsum <- gw %>%
-  group_by(source, year) %>%
-  summarize(yr_cum_RD1 = max(RD1cumsum),
-            yr_cum_RD2 = max(RD2cumsum),
-            yr_cum_RG1 = max(RG1cumsum),
-            yr_cum_RG2 = max(RG2cumsum)) %>%
-  mutate(year = as.factor(year)) %>%
-  pivot_longer(!c(year, source), names_to = 'flow_type', values_to = 'flow_cms')
-
-ggplot(gw_maxcumsum, aes(x = flow_type, y = flow_cms, fill = source)) +
-  geom_boxplot(position = position_dodge(1)) +
-  geom_point(position=position_jitterdodge(),alpha=0.3) +
-  ggtitle('Annual sum') +
-  labs(y = 'mm of water')
-
-ggplot(gw_maxcumsum, aes(x = flow_type, y = flow_cms, fill = source)) +
-  geom_boxplot(position = position_dodge(1)) +
-  geom_point(position=position_jitterdodge(),alpha=0.3) +
-  #geom_point(aes(color = source)) +
-  facet_wrap(~flow_type, scales = 'free') +
-  ggtitle('Annual sum') +
-  labs(y = 'mm of water')
-
-```
-
-### RD and RG by season
-
-- January-February = baseflow_winter
-- March-June = snowmelt
-- July-August = Monsoon
-- September-December = Baseflow_fall
-
-```{r flow season, echo = FALSE, message = FALSE, warning = FALSE, fig.width = 12, fig.asp = 0.75, out.width = "100%"}
-
-#group by season and get max sums by season
-flow_season <- gw %>%
-  dplyr::select(catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w, date, year, source) %>%
-  mutate(month = month(date)) %>%
-  mutate(season = case_when(month %in% c(3,4,5,6) ~ 'snowmelt',
-                            month %in% c(7,8) ~ 'monsoon',
-                            month %in% c(9,10,11,12) ~ 'baseflow_fall',
-                            month %in% c(1,2) ~ 'baseflow_winter')) %>%
-  group_by(source, year, season) %>%
-  mutate(yr_season_RD1 = cumsum(catchmentRD1_w),
-            yr_season_RD2 = cumsum(catchmentRD2_w),
-            yr_season_RG1 = cumsum(catchmentRG1_w),
-            yr_season_RG2 = cumsum(catchmentRG2_w)) %>%
-  summarize(sumRD1 = max(yr_season_RD1),
-            sumRD2 = max(yr_season_RD2),
-            sumRG1 = max(yr_season_RG1),
-            sumRG2 = max(yr_season_RG2)) %>%
-            pivot_longer(!c(year, source, season), names_to = 'flow_type', values_to = 'mm_water')
-
-flow_season %>%
-  ggplot(aes(x = flow_type, y = mm_water, fill = source)) +
-  geom_boxplot(position = position_dodge(1)) +
-  #geom_point(position=position_jitterdodge(),alpha=0.3) +
-  #geom_point(aes(color = source)) +
-  facet_wrap(~season) +
-  ggtitle('RD/RG sums (mm)') +
-  theme_bw() +
-  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
-  theme(text = element_text(size = 20)) +
-  labs(y = 'RD/RG sums (mm)')
-
-flow_season %>%
-  ggplot(aes(x = flow_type, y = mm_water, fill = source)) +
-  geom_boxplot(position = position_dodge(1)) +
-  geom_point(position=position_jitterdodge(),alpha=0.3) +
-  #geom_point(aes(color = source)) +
-  facet_wrap(~season + flow_type, scales = 'free') +
-  ggtitle('Seasonal sums') +
-  theme_bw() +
-  theme(text = element_text(size = 20)) +
-  labs(y = 'RD/RG seasonal sums (mm)')
-
-```
+<!-- <!-- ### Annual KGE plots --> -->
+
+<!-- <!-- ```{r wy plots, echo = FALSE, message = FALSE, warning = FALSE} --> -->
+
+<!-- <!-- plot_kge <- function(calyear) { --> -->
+<!-- <!--   flow_plot %>% --> -->
+<!-- <!--     filter(year == calyear) %>% --> -->
+<!-- <!--     ggplot(aes(x = model_run, --> -->
+<!-- <!--                y = kge)) + --> -->
+<!-- <!--     geom_point(size=3) + --> -->
+<!-- <!--     ggtitle(calyear) + --> -->
+<!-- <!--     theme_bw() + --> -->
+<!-- <!--     theme(axis.text.x = element_text(angle = 45, hjust=1)) --> -->
+<!-- <!-- } --> -->
+
+<!-- <!-- name <- levels(flow_plot$year) --> -->
+
+<!-- <!-- lapply(name, plot_kge) --> -->
+
+<!-- <!-- ``` --> -->
+
+<!-- ## Pbias -->
+
+<!-- ### Overall pbias -->
+
+<!-- ```{r pbias overall, echo = FALSE, message = FALSE, warning = FALSE} -->
+
+<!-- flow_pbias_all <- flow %>% -->
+<!--   summarize( -->
+<!--     # grid2011 = pbias(grid_2011, obs), -->
+<!--     #         grid2012 = pbias(grid_2012, obs), -->
+<!--     #         grid2013 = pbias(grid_2013, obs), -->
+<!--     #         grid2014 = pbias(grid_2014, obs), -->
+<!--     #         grid2015 = pbias(grid_2015, obs), -->
+<!--     #         grid2016 = pbias(grid_2016, obs), -->
+<!--     #         grid2017 = pbias(grid_2017, obs), -->
+<!--     #         grid2018 = pbias(grid_2018, obs), -->
+<!--     #         grid2019 = pbias(grid_2019, obs), -->
+<!--     #         grid2020 = pbias(grid_2020, obs), -->
+<!--             gridall = pbias(grid_all, obs), -->
+<!--             # statn2011 = pbias(statn_2011, obs), -->
+<!--             # statn2012 = pbias(statn_2012, obs), -->
+<!--             # statn2013 = pbias(statn_2013, obs), -->
+<!--             # statn2014 = pbias(statn_2014, obs), -->
+<!--             # statn2015 = pbias(statn_2015, obs), -->
+<!--             # statn2016 = pbias(statn_2016, obs), -->
+<!--             # statn2017 = pbias(statn_2017, obs), -->
+<!--             # statn2018 = pbias(statn_2018, obs), -->
+<!--             # statn2019 = pbias(statn_2019, obs), -->
+<!--             # statn2020 = pbias(statn_2020, obs), -->
+<!--             statnall = pbias(statn_all, obs)) %>% -->
+<!--     mutate_if(is.numeric, -->
+<!--             round, -->
+<!--             digits = 2) -->
+
+<!-- flow_pbias_all <- flow_pbias_all %>% -->
+<!--   pivot_longer(everything()) %>% -->
+<!--   arrange(abs(value)) -->
+
+<!-- kable(flow_pbias_all) %>% -->
+<!--   kable_styling(full_width = F) -->
+
+<!-- ``` -->
+
+<!-- ### Pbias by year -->
+
+<!-- ```{r pbias by year, echo = FALSE, message = FALSE, warning = FALSE} -->
+
+<!-- flow_year <- flow %>% -->
+<!--   mutate(year = year(date)) %>% -->
+<!--   group_by(year) %>% -->
+<!--   summarize( -->
+<!--     # grid2011 = pbias(grid_2011, obs), -->
+<!--     #         grid2012 = pbias(grid_2012, obs), -->
+<!--     #         grid2013 = pbias(grid_2013, obs), -->
+<!--     #         grid2014 = pbias(grid_2014, obs), -->
+<!--     #         grid2015 = pbias(grid_2015, obs), -->
+<!--     #         grid2016 = pbias(grid_2016, obs), -->
+<!--     #         grid2017 = pbias(grid_2017, obs), -->
+<!--     #         grid2018 = pbias(grid_2018, obs), -->
+<!--     #         grid2019 = pbias(grid_2019, obs), -->
+<!--     #         grid2020 = pbias(grid_2020, obs), -->
+<!--             gridall = pbias(grid_all, obs), -->
+<!--             # statn2011 = pbias(statn_2011, obs), -->
+<!--             # statn2012 = pbias(statn_2012, obs), -->
+<!--             # statn2013 = pbias(statn_2013, obs), -->
+<!--             # statn2014 = pbias(statn_2014, obs), -->
+<!--             # statn2015 = pbias(statn_2015, obs), -->
+<!--             # statn2016 = pbias(statn_2016, obs), -->
+<!--             # statn2017 = pbias(statn_2017, obs), -->
+<!--             # statn2018 = pbias(statn_2018, obs), -->
+<!--             # statn2019 = pbias(statn_2019, obs), -->
+<!--             # statn2020 = pbias(statn_2020, obs), -->
+<!--             statnall = pbias(statn_all, obs)) %>% -->
+<!--     mutate_if(is.numeric, -->
+<!--             round, -->
+<!--             digits = 2) -->
+
+<!-- flow_pbias <- flow_year %>% -->
+<!--   pivot_longer(!year, names_to = 'model_run', values_to = 'pbias') %>% -->
+<!--   pivot_wider(names_from = 'year', values_from = 'pbias') -->
+
+<!-- flow_pbias %>% -->
+<!--   kable(.) %>% -->
+<!--   kable_styling() -->
+
+<!-- flow_plot <- flow_year %>% -->
+<!--   pivot_longer(!year, names_to = 'model_run', values_to = 'pbias') %>% -->
+<!--   mutate(year = as.factor(year)) -->
+
+<!-- # add all to the plot below -->
+<!-- pbias_all <- flow_pbias_all %>% -->
+<!--   mutate(year = 'all years') %>% -->
+<!--   rename(model_run = name, -->
+<!--          pbias = value) -->
+
+<!-- flow_plot_updated <- bind_rows(flow_plot, pbias_all) -->
+
+<!-- ggplot(flow_plot_updated, aes(x = model_run, y = year, fill = pbias)) + -->
+<!--   geom_tile(color = "white") + -->
+<!--    scale_fill_gradient2(low = "blue", mid = "white", high = "red", midpoint = 0, name = "Pbias") + -->
+<!--   geom_text(aes(label = round(pbias, 2)), color = "black", size = 2.5) + -->
+<!--   theme_bw() + -->
+<!--   theme(axis.text.x = element_text(angle = 45, hjust = 1)) + -->
+<!--   labs(y = "Year") -->
+
+<!-- ``` -->
+
+<!-- <!-- ### Annual Pbias plots --> -->
+
+<!-- <!-- ```{r pbias plots, echo = FALSE, message = FALSE, warning = FALSE} --> -->
+
+<!-- <!-- plot_pbias <- function(calyear) { --> -->
+<!-- <!--   flow_plot %>% --> -->
+<!-- <!--     filter(year == calyear) %>% --> -->
+<!-- <!--     ggplot(aes(x = model_run, --> -->
+<!-- <!--                y = pbias)) + --> -->
+<!-- <!--     geom_point(size=3) + --> -->
+<!-- <!--     ggtitle(calyear) + --> -->
+<!-- <!--     theme_bw() + --> -->
+<!-- <!--     theme(axis.text.x = element_text(angle = 45, hjust=1)) --> -->
+<!-- <!-- } --> -->
+
+<!-- <!-- name <- levels(flow_plot$year) --> -->
+
+<!-- <!-- lapply(name, plot_pbias) --> -->
+
+<!-- <!-- ``` --> -->
+
+<!-- # RD and RG -->
+
+<!-- - **Different units than streamflow (cms) and volume (m3)** -->
+<!-- - **All in mm** -->
+
+<!-- ```{r rd and rg, echo = FALSE, message = FALSE, warning = FALSE, fig.width = 14, fig.asp = 1, out.width = "100%"} -->
+
+<!-- gw_gridall <- read_csv(here('38HRU_dec2024_updates/catchment_output/grid_all.csv'), skip = 3) %>% -->
+<!--   slice(-c(1,2)) %>% -->
+<!--   dplyr::select(time, catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w) %>% -->
+<!--   mutate(source = 'grid_all') %>% -->
+<!--   mutate(across(c(catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w), as.numeric)) -->
+
+<!-- gw_statnall <- read_csv(here('38HRU_dec2024_updates/catchment_output/statn_all.csv'), skip = 3) %>% -->
+<!--   slice(-c(1,2)) %>% -->
+<!--   dplyr::select(time, catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w) %>% -->
+<!--   mutate(source = 'statn_all') %>% -->
+<!--   mutate(across(c(catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w), as.numeric)) -->
+
+<!-- # gw_grid2011 <- read_csv(here('38HRU_sept2013_updates/catchment_output/grid_2011.csv'), skip = 3) %>% -->
+<!-- #   slice(-c(1,2)) %>% -->
+<!-- #   dplyr::select(time, catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w) %>% -->
+<!-- #   mutate(source = 'grid_2011')%>% -->
+<!-- #   mutate(across(c(catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w), as.numeric)) -->
+<!-- # -->
+<!-- # gw_grid2012 <- read_csv(here('38HRU_sept2013_updates/catchment_output/grid_2012.csv'), skip = 3) %>% -->
+<!-- #   slice(-c(1,2)) %>% -->
+<!-- #   dplyr::select(time, catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w) %>% -->
+<!-- #   mutate(source = 'grid_2012')%>% -->
+<!-- #   mutate(across(c(catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w), as.numeric)) -->
+<!-- # -->
+<!-- # gw_grid2013 <- read_csv(here('38HRU_sept2013_updates/catchment_output/grid_2013.csv'), skip = 3) %>% -->
+<!-- #   slice(-c(1,2)) %>% -->
+<!-- #   dplyr::select(time, catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w) %>% -->
+<!-- #   mutate(source = 'grid_2013')%>% -->
+<!-- #   mutate(across(c(catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w), as.numeric)) -->
+<!-- # -->
+<!-- # gw_grid2014 <- read_csv(here('38HRU_sept2013_updates/catchment_output/grid_2014.csv'), skip = 3) %>% -->
+<!-- #   slice(-c(1,2)) %>% -->
+<!-- #   dplyr::select(time, catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w) %>% -->
+<!-- #   mutate(source = 'grid_2014')%>% -->
+<!-- #   mutate(across(c(catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w), as.numeric)) -->
+<!-- # -->
+<!-- # gw_grid2015 <- read_csv(here('38HRU_sept2013_updates/catchment_output/grid_2015.csv'), skip = 3) %>% -->
+<!-- #   slice(-c(1,2)) %>% -->
+<!-- #   dplyr::select(time, catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w) %>% -->
+<!-- #   mutate(source = 'grid_2015')%>% -->
+<!-- #   mutate(across(c(catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w), as.numeric)) -->
+<!-- # -->
+<!-- # gw_grid2016 <- read_csv(here('38HRU_sept2013_updates/catchment_output/grid_2016.csv'), skip = 3) %>% -->
+<!-- #   slice(-c(1,2)) %>% -->
+<!-- #   dplyr::select(time, catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w) %>% -->
+<!-- #   mutate(source = 'grid_2016')%>% -->
+<!-- #   mutate(across(c(catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w), as.numeric)) -->
+<!-- # -->
+<!-- # gw_grid2017 <- read_csv(here('38HRU_sept2013_updates/catchment_output/grid_2017.csv'), skip = 3) %>% -->
+<!-- #   slice(-c(1,2)) %>% -->
+<!-- #   dplyr::select(time, catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w) %>% -->
+<!-- #   mutate(source = 'grid_2017')%>% -->
+<!-- #   mutate(across(c(catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w), as.numeric)) -->
+<!-- # -->
+<!-- # gw_grid2018 <- read_csv(here('38HRU_sept2013_updates/catchment_output/grid_2018.csv'), skip = 3) %>% -->
+<!-- #   slice(-c(1,2)) %>% -->
+<!-- #   dplyr::select(time, catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w) %>% -->
+<!-- #   mutate(source = 'grid_2018')%>% -->
+<!-- #   mutate(across(c(catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w), as.numeric)) -->
+<!-- # -->
+<!-- # gw_grid2019 <- read_csv(here('38HRU_sept2013_updates/catchment_output/grid_2019.csv'), skip = 3) %>% -->
+<!-- #   slice(-c(1,2)) %>% -->
+<!-- #   dplyr::select(time, catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w) %>% -->
+<!-- #   mutate(source = 'grid_2019')%>% -->
+<!-- #   mutate(across(c(catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w), as.numeric)) -->
+<!-- # -->
+<!-- # gw_grid2020 <- read_csv(here('38HRU_sept2013_updates/catchment_output/grid_2020.csv'), skip = 3) %>% -->
+<!-- #   slice(-c(1,2)) %>% -->
+<!-- #   dplyr::select(time, catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w) %>% -->
+<!-- #   mutate(source = 'grid_2020')%>% -->
+<!-- #   mutate(across(c(catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w), as.numeric)) -->
+<!-- # -->
+<!-- # gw_statn2011 <- read_csv(here('38HRU_sept2013_updates/catchment_output/statn_2011.csv'), skip = 3) %>% -->
+<!-- #   slice(-c(1,2)) %>% -->
+<!-- #   dplyr::select(time, catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w) %>% -->
+<!-- #   mutate(source = 'statn_2011')%>% -->
+<!-- #   mutate(across(c(catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w), as.numeric)) -->
+<!-- # -->
+<!-- # gw_statn2012 <- read_csv(here('38HRU_sept2013_updates/catchment_output/statn_2012.csv'), skip = 3) %>% -->
+<!-- #   slice(-c(1,2)) %>% -->
+<!-- #   dplyr::select(time, catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w) %>% -->
+<!-- #   mutate(source = 'statn_2012')%>% -->
+<!-- #   mutate(across(c(catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w), as.numeric)) -->
+<!-- # -->
+<!-- # gw_statn2013 <- read_csv(here('38HRU_sept2013_updates/catchment_output/statn_2013.csv'), skip = 3) %>% -->
+<!-- #   slice(-c(1,2)) %>% -->
+<!-- #   dplyr::select(time, catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w) %>% -->
+<!-- #   mutate(source = 'statn_2013')%>% -->
+<!-- #   mutate(across(c(catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w), as.numeric)) -->
+<!-- # -->
+<!-- # gw_statn2014 <- read_csv(here('38HRU_sept2013_updates/catchment_output/statn_2014.csv'), skip = 3) %>% -->
+<!-- #   slice(-c(1,2)) %>% -->
+<!-- #   dplyr::select(time, catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w) %>% -->
+<!-- #   mutate(source = 'statn_2014')%>% -->
+<!-- #   mutate(across(c(catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w), as.numeric)) -->
+<!-- # -->
+<!-- # gw_statn2015 <- read_csv(here('38HRU_sept2013_updates/catchment_output/statn_2015.csv'), skip = 3) %>% -->
+<!-- #   slice(-c(1,2)) %>% -->
+<!-- #   dplyr::select(time, catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w) %>% -->
+<!-- #   mutate(source = 'statn_2015')%>% -->
+<!-- #   mutate(across(c(catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w), as.numeric)) -->
+<!-- # -->
+<!-- # gw_statn2016 <- read_csv(here('38HRU_sept2013_updates/catchment_output/statn_2016.csv'), skip = 3) %>% -->
+<!-- #   slice(-c(1,2)) %>% -->
+<!-- #   dplyr::select(time, catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w) %>% -->
+<!-- #   mutate(source = 'statn_2016')%>% -->
+<!-- #   mutate(across(c(catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w), as.numeric)) -->
+<!-- # -->
+<!-- # gw_statn2017 <- read_csv(here('38HRU_sept2013_updates/catchment_output/statn_2017.csv'), skip = 3) %>% -->
+<!-- #   slice(-c(1,2)) %>% -->
+<!-- #   dplyr::select(time, catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w) %>% -->
+<!-- #   mutate(source = 'statn_2017')%>% -->
+<!-- #   mutate(across(c(catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w), as.numeric)) -->
+<!-- # -->
+<!-- # gw_statn2018 <- read_csv(here('38HRU_sept2013_updates/catchment_output/statn_2018.csv'), skip = 3) %>% -->
+<!-- #   slice(-c(1,2)) %>% -->
+<!-- #   dplyr::select(time, catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w) %>% -->
+<!-- #   mutate(source = 'statn_2018')%>% -->
+<!-- #   mutate(across(c(catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w), as.numeric)) -->
+<!-- # -->
+<!-- # gw_statn2019 <- read_csv(here('38HRU_sept2013_updates/catchment_output/statn_2019.csv'), skip = 3) %>% -->
+<!-- #   slice(-c(1,2)) %>% -->
+<!-- #   dplyr::select(time, catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w) %>% -->
+<!-- #   mutate(source = 'statn_2019')%>% -->
+<!-- #   mutate(across(c(catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w), as.numeric)) -->
+<!-- # -->
+<!-- # gw_statn2020 <- read_csv(here('38HRU_sept2013_updates/catchment_output/statn_2020.csv'), skip = 3) %>% -->
+<!-- #   slice(-c(1,2)) %>% -->
+<!-- #   dplyr::select(time, catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w) %>% -->
+<!-- #   mutate(source = 'statn_2020')%>% -->
+<!-- #   mutate(across(c(catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w), as.numeric)) -->
+
+<!-- gw <- bind_rows( -->
+<!--   gw_gridall, gw_statnall -->
+<!--   # gw_grid2011, gw_grid2012, -->
+<!--   # gw_grid2013, gw_grid2014, -->
+<!--   # gw_grid2015, gw_grid2016, -->
+<!--   # gw_grid2017, gw_grid2018, -->
+<!--   # gw_grid2019, gw_grid2020, -->
+<!--   # gw_statn2011, gw_statn2012, -->
+<!--   # gw_statn2013, gw_statn2014, -->
+<!--   # gw_statn2015, gw_statn2016, -->
+<!--   # gw_statn2017, gw_statn2018, -->
+<!--   # gw_statn2019, gw_statn2020 -->
+<!-- ) %>% -->
+<!--   mutate(date = mdy(time), -->
+<!--          year = year(date)) %>% -->
+<!--   arrange(date) -->
+
+<!-- ggplot(gw, aes(x=date, color = source)) + -->
+<!--   geom_line(aes(y=catchmentRD1_w), size =1) + -->
+<!--   facet_wrap(~year, scales = 'free', ncol = 2) + -->
+<!--   scale_x_date(labels = date_format("%b")) + -->
+<!--   ggtitle('RD1') + -->
+<!--   theme(text = element_text(size = 20)) + -->
+<!--   labs(y = 'RD1 (mm)') -->
+
+<!-- ggplot(gw, aes(x=date, color = source)) + -->
+<!--   geom_line(aes(y=catchmentRD2_w), size =1) + -->
+<!--   facet_wrap(~year, scales = 'free', ncol = 2) + -->
+<!--   scale_x_date(labels = date_format("%b")) + -->
+<!--   ggtitle('RD2') + -->
+<!--   theme(text = element_text(size = 20))+ -->
+<!--   labs(y = 'RD2 (mm)') -->
+
+<!-- ggplot(gw, aes(x=date, color = source)) + -->
+<!--   geom_line(aes(y=catchmentRG1_w), size =1) + -->
+<!--   facet_wrap(~year, scales = 'free', ncol = 2) + -->
+<!--   scale_x_date(labels = date_format("%b")) + -->
+<!--   ggtitle('RG1') + -->
+<!--   theme(text = element_text(size = 20)) + -->
+<!--   labs(y = 'RG1 (mm)') -->
+
+<!-- ggplot(gw, aes(x=date, color = source)) + -->
+<!--   geom_line(aes(y=catchmentRG2_w), size =1) + -->
+<!--   facet_wrap(~year, scales = 'free', ncol=2) + -->
+<!--   scale_x_date(labels = date_format("%b")) + -->
+<!--   ggtitle('RG2') + -->
+<!--   theme(text = element_text(size = 20))+ -->
+<!--   labs(y = 'RG2 (mm)') -->
+
+<!-- gw <- gw %>% -->
+<!--   arrange(date) %>% -->
+<!--   group_by(year, source) %>% -->
+<!--   mutate(RD1cumsum = cumsum(catchmentRD1_w), -->
+<!--          RD2cumsum = cumsum(catchmentRD2_w), -->
+<!--          RG1cumsum = cumsum(catchmentRG1_w), -->
+<!--          RG2cumsum = cumsum(catchmentRG2_w)) -->
+
+<!-- ggplot(gw, aes(x=date, color = source)) + -->
+<!--   geom_line(aes(y=RD1cumsum), size =1) + -->
+<!--   facet_wrap(~year, scales = 'free', ncol=2) + -->
+<!--   scale_x_date(labels = date_format("%b")) + -->
+<!--   ggtitle('Cumulative RD1 (mm)') + -->
+<!--   theme(text = element_text(size = 20)) -->
+
+<!-- ggplot(gw, aes(x=date, color = source)) + -->
+<!--   geom_line(aes(y=RD2cumsum), size = 1) + -->
+<!--   facet_wrap(~year, scales = 'free', ncol=2) + -->
+<!--   scale_x_date(labels = date_format("%b")) + -->
+<!--   ggtitle('Cumulative RD2 (mm)') + -->
+<!--   theme(text = element_text(size = 20)) -->
+
+<!-- ggplot(gw, aes(x=date, color = source)) + -->
+<!--   geom_line(aes(y=RG1cumsum), size  = 1) + -->
+<!--   facet_wrap(~year, scales = 'free', ncol = 2) + -->
+<!--   scale_x_date(labels = date_format("%b")) + -->
+<!--   ggtitle('Cumulative RG1 (mm)') + -->
+<!--   theme(text = element_text(size = 20)) -->
+
+<!-- ggplot(gw, aes(x=date, color = source)) + -->
+<!--   geom_line(aes(y=RG2cumsum), size =1) + -->
+<!--   facet_wrap(~year, scales = 'free', ncol = 2) + -->
+<!--   scale_x_date(labels = date_format("%b")) + -->
+<!--   ggtitle('Cumulative RG2 (mm)') + -->
+<!--   theme(text = element_text(size = 20)) -->
+
+<!-- ``` -->
+
+<!-- ```{r rd and rg sums, echo = FALSE, message = FALSE, warning = FALSE, fig.width = 22, fig.asp = 1.5, out.width = "100%"} -->
+
+<!-- ################## -->
+<!-- # all 4 with facets -->
+
+<!-- ggplot(gw, aes(x=date)) + -->
+<!--   geom_line(aes(y=RG2cumsum, color = 'cumulative RG2'), size =1) + -->
+<!--   geom_line(aes(y=RG1cumsum, color = 'cumulative RG1'), size =1) + -->
+<!--   geom_line(aes(y=RD1cumsum, color = 'cumulative RD1'), size =1) + -->
+<!--   geom_line(aes(y=RD2cumsum, color = 'cumulative RD2'), size =1) + -->
+<!--   scale_x_date(labels = date_format("%b")) + -->
+<!--   facet_wrap(~year + source, scales = 'free_x', ncol=2) + -->
+<!--   ggtitle('Cumulative RD and RG (mm)') + -->
+<!--   theme(text = element_text(size = 24)) -->
+
+<!-- ``` -->
+
+<!-- ```{r gw boxplot, echo = FALSE, message = FALSE, warning = FALSE} -->
+
+<!-- gw_maxcumsum <- gw %>% -->
+<!--   group_by(source, year) %>% -->
+<!--   summarize(yr_cum_RD1 = max(RD1cumsum), -->
+<!--             yr_cum_RD2 = max(RD2cumsum), -->
+<!--             yr_cum_RG1 = max(RG1cumsum), -->
+<!--             yr_cum_RG2 = max(RG2cumsum)) %>% -->
+<!--   mutate(year = as.factor(year)) %>% -->
+<!--   pivot_longer(!c(year, source), names_to = 'flow_type', values_to = 'flow_cms') -->
+
+<!-- ggplot(gw_maxcumsum, aes(x = flow_type, y = flow_cms, fill = source)) + -->
+<!--   geom_boxplot(position = position_dodge(1)) + -->
+<!--   geom_point(position=position_jitterdodge(),alpha=0.3) + -->
+<!--   ggtitle('Annual sum') + -->
+<!--   labs(y = 'mm of water') -->
+
+<!-- ggplot(gw_maxcumsum, aes(x = flow_type, y = flow_cms, fill = source)) + -->
+<!--   geom_boxplot(position = position_dodge(1)) + -->
+<!--   geom_point(position=position_jitterdodge(),alpha=0.3) + -->
+<!--   #geom_point(aes(color = source)) + -->
+<!--   facet_wrap(~flow_type, scales = 'free') + -->
+<!--   ggtitle('Annual sum') + -->
+<!--   labs(y = 'mm of water') -->
+
+<!-- ``` -->
+
+<!-- ### RD and RG by season -->
+
+<!-- - January-February = baseflow_winter -->
+<!-- - March-June = snowmelt -->
+<!-- - July-August = Monsoon -->
+<!-- - September-December = Baseflow_fall -->
+
+<!-- ```{r flow season, echo = FALSE, message = FALSE, warning = FALSE, fig.width = 12, fig.asp = 0.75, out.width = "100%"} -->
+
+<!-- #group by season and get max sums by season -->
+<!-- flow_season <- gw %>% -->
+<!--   dplyr::select(catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w, date, year, source) %>% -->
+<!--   mutate(month = month(date)) %>% -->
+<!--   mutate(season = case_when(month %in% c(3,4,5,6) ~ 'snowmelt', -->
+<!--                             month %in% c(7,8) ~ 'monsoon', -->
+<!--                             month %in% c(9,10,11,12) ~ 'baseflow_fall', -->
+<!--                             month %in% c(1,2) ~ 'baseflow_winter')) %>% -->
+<!--   group_by(source, year, season) %>% -->
+<!--   mutate(yr_season_RD1 = cumsum(catchmentRD1_w), -->
+<!--             yr_season_RD2 = cumsum(catchmentRD2_w), -->
+<!--             yr_season_RG1 = cumsum(catchmentRG1_w), -->
+<!--             yr_season_RG2 = cumsum(catchmentRG2_w)) %>% -->
+<!--   summarize(sumRD1 = max(yr_season_RD1), -->
+<!--             sumRD2 = max(yr_season_RD2), -->
+<!--             sumRG1 = max(yr_season_RG1), -->
+<!--             sumRG2 = max(yr_season_RG2)) %>% -->
+<!--             pivot_longer(!c(year, source, season), names_to = 'flow_type', values_to = 'mm_water') -->
+
+<!-- flow_season %>% -->
+<!--   ggplot(aes(x = flow_type, y = mm_water, fill = source)) + -->
+<!--   geom_boxplot(position = position_dodge(1)) + -->
+<!--   #geom_point(position=position_jitterdodge(),alpha=0.3) + -->
+<!--   #geom_point(aes(color = source)) + -->
+<!--   facet_wrap(~season) + -->
+<!--   ggtitle('RD/RG sums (mm)') + -->
+<!--   theme_bw() + -->
+<!--   theme(axis.text.x = element_text(angle = 45, hjust = 1)) + -->
+<!--   theme(text = element_text(size = 20)) + -->
+<!--   labs(y = 'RD/RG sums (mm)') -->
+
+<!-- flow_season %>% -->
+<!--   ggplot(aes(x = flow_type, y = mm_water, fill = source)) + -->
+<!--   geom_boxplot(position = position_dodge(1)) + -->
+<!--   geom_point(position=position_jitterdodge(),alpha=0.3) + -->
+<!--   #geom_point(aes(color = source)) + -->
+<!--   facet_wrap(~season + flow_type, scales = 'free') + -->
+<!--   ggtitle('Seasonal sums') + -->
+<!--   theme_bw() + -->
+<!--   theme(text = element_text(size = 20)) + -->
+<!--   labs(y = 'RD/RG seasonal sums (mm)') -->
+
+<!-- ``` -->

### 2025-01-17 spatial_figs.Rmd
updated figure 2

@@
   mutate(year = year(date),
-         DOY = yday(date)) %>%
-  drop_na(obs)
+         DOY = yday(date)) #%>%
+  #drop_na(obs)
 
@@
 
-flow_plot <- ggplot(flow, aes(x = DOY, y = obs, color = as.factor(year))) + 
+flow_plot <- ggplot(flow, aes(x = DOY, y = obs, color = as.factor(year),
+                              linetype = as.factor(year))) + 
   geom_line(size = 1.1) +
@@
   labs(y = 'Discharge (cms)', color = 'Year') +
-  scale_color_viridis_d(option = "turbo")
+  scale_color_viridis_d(option = "mako") +
+     theme(
+    panel.grid = element_blank(),
+    panel.background = element_rect(fill = "white"),
+    strip.background = element_blank(),
+    text = element_text(color = "black"),
+    axis.title = element_text(color = "black"),
+    axis.text = element_text(color = "black"),
+    strip.text = element_text(color = "black"))
 
@@
 
+flow_plot2 <- ggplot(flow, aes(x = date, y = obs)) + 
+  geom_line(size = 1.1) +
+  theme_bw(base_size = 20) +
+  labs(y = 'Discharge (cms)',
+         x = element_blank()) +
+   theme(
+    legend.position = "none",
+    panel.grid = element_blank(),
+    panel.background = element_rect(fill = "white"),
+    strip.background = element_blank(),
+    text = element_text(color = "black"),
+    axis.title = element_text(color = "black"),
+    axis.text = element_text(color = "black"),
+    strip.text = element_text(color = "black"))
+
+flow_plot2
+
+ggsave("/Users/megansears/Documents/Repos/fourmile/figures/flow_obs_plot2.png", dpi = 600, width = 12, height = 4, units = "in")
+
 ```
+
+# statn vs grid met
+
+```{r}
+
+grid <- read_csv("/Users/megansears/Documents/Repos/fourmile/38HRU_sept2013_updates/grid_all_Catchment.csv",
+                 skip=3) %>%
+   slice(3:n()) %>%
+  dplyr::select(-starts_with('@'),
+                -1) %>%
+  mutate(date = ymd(time)) %>%
+  dplyr::select(-time) %>%
+  mutate_if(is.character, as.numeric) %>% 
+  mutate(site = 'grid')
+
+statn <- read_csv('/Users/megansears/Documents/Repos/fourmile/38HRU_sept2013_updates/statn_all_Catchment.csv',
+                 skip=3) %>%
+   slice(3:n()) %>%
+  dplyr::select(-starts_with('@'),
+                -1) %>%
+  mutate(date = ymd(time)) %>%
+  dplyr::select(-time) %>%
+  mutate_if(is.character, as.numeric) %>% 
+  mutate(site = 'statn')
+
+all <- bind_rows(grid, statn) %>%
+  arrange(date)
+
+catchment_mo_mean <- all %>%
+  mutate(month = month(date)) %>%
+  group_by(site, month) %>%
+  summarise(across(tmean:solRad, ~ mean(.x, na.rm = TRUE))) %>%
+  dplyr::select(site, month, tmean_mean = tmean, 
+                solrad_mean = solRad, rh_mean = rhum)
+
+catchment_mo_sum <- all %>%
+  dplyr::select(date, precip, site) %>%
+  mutate(month = month(date),
+         year = year(date)) %>%
+  group_by(month, year, site) %>%
+  summarize(p_sum = sum(precip)) %>%
+  group_by(month, site) %>%
+  summarize(avg_p = mean(p_sum),
+          sd_p = sd(p_sum))
+
+catchment_mo_sd <- all %>%
+  mutate(month = month(date)) %>%
+  group_by(site, month) %>%
+  summarise(across(tmean:solRad, ~ sd(.x, na.rm = TRUE))) %>%
+  dplyr::select(site, month, tmean_sd = tmean, 
+                solrad_sd = solRad, rh_sd = rhum)
+
+catchment_mo <- left_join(catchment_mo_mean, catchment_mo_sd, 
+                          by = c('month', 'site'))
+
+catchment_mo <- left_join(catchment_mo, catchment_mo_sum)
+
+catchment_mo2 <- catchment_mo %>%
+  mutate(month_name = month.abb[month]) %>%
+  mutate(month_name = factor(month_name, 
+                             levels = c('Jan', 'Feb', 'Mar',
+                                        'Apr', 'May', 'Jun',
+                                        'Jul', 'Aug', 'Sep',
+                                        'Oct', 'Nov', 'Dec')))
+
+p_cols <- ggplot(catchment_mo2, aes(x = month_name, y = avg_p,
+                                    color = site, fill = site)) +
+  geom_col(position = 'dodge') +
+  geom_errorbar(aes(ymin = 0, ymax = avg_p + sd_p), 
+                position = position_dodge(width = 0.6), width = 0.2) +
+  scale_color_manual(values = c("blue", "orange"),
+                     labels = c("Gridded", "Observed")) +  # Rename color legend items
+  scale_fill_manual(values = c("blue", "orange"),
+                    labels = c("Gridded", "Observed")) +   # Rename fill legend items
+  theme_bw(base_size = 20) +
+  labs(y = 'Precipitation (mm)',
+       x = element_blank()) +
+  guides(color = guide_legend(title = NULL),
+         fill = guide_legend(title = NULL)) +
+    theme(
+    panel.grid = element_blank(),
+    panel.background = element_rect(fill = "white"),
+    text = element_text(color = "black"),
+    axis.title = element_text(color = "black"),
+    axis.text = element_text(color = "black"),
+    strip.text = element_blank()
+  )
+
+p_cols
+
+ggsave("/Users/megansears/Documents/Repos/fourmile/figures/precip.png", plot = p_cols, width = 8, height = 6, dpi = 300)
+
+# Temperature plot
+t_moplot <- ggplot(catchment_mo2, aes(x = month_name, y = tmean_mean, 
+                                      color = site, group = site)) +
+  geom_ribbon(aes(ymin = tmean_mean - tmean_sd, ymax = tmean_mean + tmean_sd, fill = site), alpha = 0.4) +
+  geom_line() +
+  geom_point() +
+  scale_color_manual(values = c("blue", "orange"),
+                     labels = c("Gridded", "Observed")) +  # Set line color to blue and orange and rename
+  scale_fill_manual(values = c("blue", "orange"),
+                    labels = c("Gridded", "Observed")) +   # Set ribbon fill color to blue and orange and rename
+  theme_bw(base_size=20) +
+  labs(y = expression("Air temperature " ( degree~C)),
+       x = element_blank()) +
+  labs(color = NULL, fill = NULL) +
+      theme(
+    panel.grid = element_blank(),
+    panel.background = element_rect(fill = "white"),
+    text = element_text(color = "black"),
+    axis.title = element_text(color = "black"),
+    axis.text = element_text(color = "black"),
+    strip.text = element_blank())
+
+# Solar radiation plot
+sol_moplot <- ggplot(catchment_mo2, aes(x = month_name, y = solrad_mean, 
+                                         color = site, group = site)) +
+  geom_ribbon(aes(ymin = solrad_mean - solrad_sd, ymax = solrad_mean + solrad_sd, fill = site), alpha = 0.4) +
+  geom_line() +
+  geom_point() +
+  scale_color_manual(values = c("blue", "orange"),
+                     labels = c("Gridded", "Observed")) +  # Set line color to blue and orange and rename
+  scale_fill_manual(values = c("blue", "orange"),
+                    labels = c("Gridded", "Observed")) +   # Set ribbon fill color to blue and orange and rename
+  theme_bw(base_size = 20) +
+  labs(y = expression("Solar radiation (MJ/m"^"2" * ")"),
+       x = element_blank()) +
+  labs(color = NULL, fill = NULL) +
+      theme(
+    panel.grid = element_blank(),
+    panel.background = element_rect(fill = "white"),
+    text = element_text(color = "black"),
+    axis.title = element_text(color = "black"),
+    axis.text = element_text(color = "black"),
+    strip.text = element_blank())
+
+# Relative humidity plot
+rh_moplot <- ggplot(catchment_mo2, aes(x = month_name, y = rh_mean, 
+                                        color = site, group = site)) +
+  geom_ribbon(aes(ymin = rh_mean - rh_sd, ymax = rh_mean + rh_sd, fill = site), alpha = 0.4) +
+  geom_line() +
+  geom_point() +
+  scale_color_manual(values = c("blue", "orange"),
+                     labels = c("Gridded", "Observed")) +  # Set line color to blue and orange and rename
+  scale_fill_manual(values = c("blue", "orange"),
+                    labels = c("Gridded", "Observed")) +   # Set ribbon fill color to blue and orange and rename
+  theme_bw(base_size = 20) +
+  labs(y = 'RH (%)', x= element_blank()) +
+  labs(color = NULL, fill = NULL) +
+      theme(
+    panel.grid = element_blank(),
+    panel.background = element_rect(fill = "white"),
+    text = element_text(color = "black"),
+    axis.title = element_text(color = "black"),
+    axis.text = element_text(color = "black"),
+    strip.text = element_blank())
+
+library(ggpubr)
+
+quad <- ggarrange(p_cols, 
+          t_moplot,
+          sol_moplot,
+          rh_moplot,
+          common.legend = T,
+          legend = 'bottom',
+          ncol=2,
+          nrow=2) 
+          #nrow = 4)
+          #ncol= 0)
+quad
+
+ggsave("/Users/megansears/Documents/Repos/fourmile/figures/quad.png", plot = quad, dpi = 600)
+
+quad_plus <- ggarrange(flow_plot2,quad,
+                       nrow=2)
+quad_plus
+
+ggsave("./figures/quad_plus2.png", plot = quad_plus, dpi = 600)
+
+```

### 2025-01-26 fourmile_output_dec2024.Rmd
added rest of cals and forward runs in for dec2024 model edits

--- 2024-12-27 fourmile_output_dec2024.Rmd
@@
 
-# grid_2011 <- read_cals(grid_2011., name = 'grid_2011')
-# grid_2012 <- read_cals(grid_2012., name = 'grid_2012')
-# grid_2013 <- read_cals(grid_2013., name = 'grid_2013')
-# grid_2014 <- read_cals(grid_2014., name = 'grid_2014')
-# grid_2015 <- read_cals(grid_2015., name = 'grid_2015')
-# grid_2016 <- read_cals(grid_2016., name = 'grid_2016')
-# grid_2017 <- read_cals(grid_2017., name = 'grid_2017')
-# grid_2018 <- read_cals(grid_2018., name = 'grid_2018')
-# grid_2019 <- read_cals(grid_2019., name = 'grid_2019')
-# grid_2020 <- read_cals(grid_2020., name = 'grid_2020')
+grid_2011 <- read_cals(grid_2011., name = 'grid_2011')
+grid_2012 <- read_cals(grid_2012., name = 'grid_2012')
+grid_2013 <- read_cals(grid_2013., name = 'grid_2013')
+grid_2014 <- read_cals(grid_2014., name = 'grid_2014')
+grid_2015 <- read_cals(grid_2015., name = 'grid_2015')
+grid_2016 <- read_cals(grid_2016., name = 'grid_2016')
+grid_2017 <- read_cals(grid_2017., name = 'grid_2017')
+grid_2018 <- read_cals(grid_2018., name = 'grid_2018')
+grid_2019 <- read_cals(grid_2019., name = 'grid_2019')
+grid_2020 <- read_cals(grid_2020., name = 'grid_2020')
 grid_all <- read_cals(grid_all.c, name = 'grid_all')
 
-# grid <- bind_rows(grid_2011, grid_2012, grid_2013, grid_2014, grid_2015,
-#                   grid_2016, grid_2017, grid_2018, grid_2019, grid_2020,
-#                   grid_all) %>%
-#   mutate(input_data = 'grid') %>%
-#   mutate(year_missing_almost = gsub('grid_', '', cal)) %>%
-#   mutate(year_missing = gsub('all', 'none', year_missing_almost)) %>%
-#   dplyr::select(-c(year_missing_almost)) %>%
-#   rename(param = Parameter) %>%
-#   filter(!param == 'locGrw',
-#          !param == 'tempRes')
-
-grid <- grid_all %>%
+grid <- bind_rows(grid_2011, grid_2012, grid_2013, grid_2014, grid_2015,
+                  grid_2016, grid_2017, grid_2018, grid_2019, grid_2020,
+                  grid_all) %>%
   mutate(input_data = 'grid') %>%
@@
 
-# grid_2011_burn <- read_cals_burn(grid_2011., name = 'grid_2011')
-# grid_2012_burn <- read_cals_burn(grid_2012., name = 'grid_2012')
-# grid_2013_burn <- read_cals_burn(grid_2013., name = 'grid_2013')
-# grid_2014_burn <- read_cals_burn(grid_2014., name = 'grid_2014')
-# grid_2015_burn <- read_cals_burn(grid_2015., name = 'grid_2015')
-# grid_2016_burn <- read_cals_burn(grid_2016., name = 'grid_2016')
-# grid_2017_burn <- read_cals_burn(grid_2017., name = 'grid_2017')
-# grid_2018_burn <- read_cals_burn(grid_2018., name = 'grid_2018')
-# grid_2019_burn <- read_cals_burn(grid_2019., name = 'grid_2019')
-# grid_2020_burn <- read_cals_burn(grid_2020., name = 'grid_2020')
+grid_2011_burn <- read_cals_burn(grid_2011., name = 'grid_2011')
+grid_2012_burn <- read_cals_burn(grid_2012., name = 'grid_2012')
+grid_2013_burn <- read_cals_burn(grid_2013., name = 'grid_2013')
+grid_2014_burn <- read_cals_burn(grid_2014., name = 'grid_2014')
+grid_2015_burn <- read_cals_burn(grid_2015., name = 'grid_2015')
+grid_2016_burn <- read_cals_burn(grid_2016., name = 'grid_2016')
+grid_2017_burn <- read_cals_burn(grid_2017., name = 'grid_2017')
+grid_2018_burn <- read_cals_burn(grid_2018., name = 'grid_2018')
+grid_2019_burn <- read_cals_burn(grid_2019., name = 'grid_2019')
+grid_2020_burn <- read_cals_burn(grid_2020., name = 'grid_2020')
 grid_all_burn <- read_cals_burn(grid_all.c, name = 'grid_all')
 
-# grid_burn <- bind_rows(grid_2011_burn, 
-#                   grid_2012_burn, 
-#                   grid_2013_burn, 
-#                   grid_2014_burn, 
-#                   grid_2015_burn,
-#                   grid_2016_burn, 
-#                   grid_2017_burn, 
-#                   grid_2018_burn, 
-#                   grid_2019_burn, 
-#                   grid_2020_burn,
-#                   grid_all_burn) %>%
-#   mutate(input_data = 'grid') %>%
-#   mutate(year_missing_almost = gsub('grid_', '', cal)) %>%
-#   mutate(year_missing = gsub('all', 'none', year_missing_almost)) %>%
-#   dplyr::select(-c(year_missing_almost))
-
-grid_burn <- grid_all_burn %>%
+grid_burn <- bind_rows(grid_2011_burn,
+                  grid_2012_burn,
+                  grid_2013_burn,
+                  grid_2014_burn,
+                  grid_2015_burn,
+                  grid_2016_burn,
+                  grid_2017_burn,
+                  grid_2018_burn,
+                  grid_2019_burn,
+                  grid_2020_burn,
+                  grid_all_burn) %>%
   mutate(input_data = 'grid') %>%
@@
 
-# ggplot(params_combo, aes(x=burn, y=value, fill=input_data)) +
-#   geom_boxplot() +
-#   facet_wrap(~param, scales = 'free_y')
+ggplot(params_combo, aes(x=burn, y=value, fill=input_data)) +
+  geom_boxplot() +
+  facet_wrap(~param, scales = 'free_y')
 # 
@@
   scale_color_manual(name="cal_run", values=c('obs' = 'black',
-                                            # "grid_2011"="seagreen",
-                                            # "grid_2012"="seagreen2",
-                                            # "grid_2013"="steelblue",
-                                            # "grid_2014"='dodgerblue',
-                                            # "grid_2015" = "cyan3",
-                                            # 'grid_2016' = 'blue',
-                                            # 'grid_2017' = 'blue4',
-                                            # 'grid_2018' = 'cadetblue',
-                                            # 'grid_2019' = 'lightgreen',
-                                            # 'grid_2020' = 'olivedrab',
+                                            "grid_2011"="seagreen",
+                                            "grid_2012"="seagreen2",
+                                            "grid_2013"="steelblue",
+                                            "grid_2014"='dodgerblue',
+                                            "grid_2015" = "cyan3",
+                                            'grid_2016' = 'blue',
+                                            'grid_2017' = 'blue4',
+                                            'grid_2018' = 'cadetblue',
+                                            'grid_2019' = 'lightgreen',
+                                            'grid_2020' = 'olivedrab',
                                             'grid_all' = 'steelblue3',
-                                            # "statn_2011"="maroon",
-                                            # "statn_2012"="deeppink4",
-                                            # "statn_2013"="deeppink",
-                                            # "statn_2014"='purple',
-                                            # "statn_2015" = "mediumorchid1",
-                                            # 'statn_2016' = 'indianred',
-                                            # 'statn_2017' = 'sienna',
-                                            # 'statn_2018' = 'salmon2',
-                                            # 'statn_2019' = 'mediumpurple1',
-                                            # 'statn_2020' = 'violetred',
+                                            "statn_2011"="maroon",
+                                            "statn_2012"="deeppink4",
+                                            "statn_2013"="deeppink",
+                                            "statn_2014"='purple',
+                                            "statn_2015" = "mediumorchid1",
+                                            'statn_2016' = 'indianred',
+                                            'statn_2017' = 'sienna',
+                                            'statn_2018' = 'salmon2',
+                                            'statn_2019' = 'mediumpurple1',
+                                            'statn_2020' = 'violetred',
                                             'statn_all' = 'red')) +
@@
 scale_color_manual(name="cal_run", values=c('obs' = 'black',
-                                            # "grid_2011"="seagreen",
-                                            # "grid_2012"="seagreen2",
-                                            # "grid_2013"="steelblue",
-                                            # "grid_2014"='dodgerblue',
-                                            # "grid_2015" = "cyan3",
-                                            # 'grid_2016' = 'blue',
-                                            # 'grid_2017' = 'blue4',
-                                            # 'grid_2018' = 'cadetblue',
-                                            # 'grid_2019' = 'lightgreen',
-                                            # 'grid_2020' = 'olivedrab',
+                                            "grid_2011"="seagreen",
+                                            "grid_2012"="seagreen2",
+                                            "grid_2013"="steelblue",
+                                            "grid_2014"='dodgerblue',
+                                            "grid_2015" = "cyan3",
+                                            'grid_2016' = 'blue',
+                                            'grid_2017' = 'blue4',
+                                            'grid_2018' = 'cadetblue',
+                                            'grid_2019' = 'lightgreen',
+                                            'grid_2020' = 'olivedrab',
                                             'grid_all' = 'steelblue3',
-                                            # "statn_2011"="maroon",
-                                            # "statn_2012"="deeppink4",
-                                            # "statn_2013"="deeppink",
-                                            # "statn_2014"='purple',
-                                            # "statn_2015" = "mediumorchid1",
-                                            # 'statn_2016' = 'indianred',
-                                            # 'statn_2017' = 'sienna',
-                                            # 'statn_2018' = 'salmon2',
-                                            # 'statn_2019' = 'mediumpurple1',
-                                            # 'statn_2020' = 'violetred',
+                                            "statn_2011"="maroon",
+                                            "statn_2012"="deeppink4",
+                                            "statn_2013"="deeppink",
+                                            "statn_2014"='purple',
+                                            "statn_2015" = "mediumorchid1",
+                                            'statn_2016' = 'indianred',
+                                            'statn_2017' = 'sienna',
+                                            'statn_2018' = 'salmon2',
+                                            'statn_2019' = 'mediumpurple1',
+                                            'statn_2020' = 'violetred',
                                             'statn_all' = 'red')) +
@@
 
-# flow_kge_all <- flow %>%
-#   summarize(grid2011 = KGE(grid_2011, obs),
-#             grid2012 = KGE(grid_2012, obs),
-#             grid2013 = KGE(grid_2013, obs),
-#             grid2014 = KGE(grid_2014, obs),
-#             grid2015 = KGE(grid_2015, obs),
-#             grid2016 = KGE(grid_2016, obs),
-#             grid2017 = KGE(grid_2017, obs),
-#             grid2018 = KGE(grid_2018, obs),
-#             grid2019 = KGE(grid_2019, obs),
-#             grid2020 = KGE(grid_2020, obs),
-#             gridall = KGE(grid_all, obs),
-#             statn2011 = KGE(statn_2011, obs),
-#             statn2012 = KGE(statn_2012, obs),
-#             statn2013 = KGE(statn_2013, obs),
-#             statn2014 = KGE(statn_2014, obs),
-#             statn2015 = KGE(statn_2015, obs),
-#             statn2016 = KGE(statn_2016, obs),
-#             statn2017 = KGE(statn_2017, obs),
-#             statn2018 = KGE(statn_2018, obs),
-#             statn2019 = KGE(statn_2019, obs),
-#             statn2020 = KGE(statn_2020, obs),
-#             statnall = KGE(statn_all, obs)) %>%
-#     mutate_if(is.numeric,
-#             round,
-#             digits = 2)
-
 flow_kge_all <- flow %>%
-  summarize(
-            gridall = KGE(grid_all,
-                          obs, 
-                          na.rm=T, 
-                          method='2012'),
-            statnall = KGE(statn_all, 
-                           obs, 
-                           na.rm=T,
-                           method='2012')) %>%
+  summarize(grid2011 = KGE(grid_2011, obs),
+            grid2012 = KGE(grid_2012, obs),
+            grid2013 = KGE(grid_2013, obs),
+            grid2014 = KGE(grid_2014, obs),
+            grid2015 = KGE(grid_2015, obs),
+            grid2016 = KGE(grid_2016, obs),
+            grid2017 = KGE(grid_2017, obs),
+            grid2018 = KGE(grid_2018, obs),
+            grid2019 = KGE(grid_2019, obs),
+            grid2020 = KGE(grid_2020, obs),
+            gridall = KGE(grid_all, obs),
+            statn2011 = KGE(statn_2011, obs),
+            statn2012 = KGE(statn_2012, obs),
+            statn2013 = KGE(statn_2013, obs),
+            statn2014 = KGE(statn_2014, obs),
+            statn2015 = KGE(statn_2015, obs),
+            statn2016 = KGE(statn_2016, obs),
+            statn2017 = KGE(statn_2017, obs),
+            statn2018 = KGE(statn_2018, obs),
+            statn2019 = KGE(statn_2019, obs),
+            statn2020 = KGE(statn_2020, obs),
+            statnall = KGE(statn_all, obs)) %>%
     mutate_if(is.numeric,
@@
   summarize(
-    # grid2011 = KGE(grid_2011, obs),
-    #         grid2012 = KGE(grid_2012, obs),
-    #         grid2013 = KGE(grid_2013, obs),
-    #         grid2014 = KGE(grid_2014, obs),
-    #         grid2015 = KGE(grid_2015, obs),
-    #         grid2016 = KGE(grid_2016, obs),
-    #         grid2017 = KGE(grid_2017, obs),
-    #         grid2018 = KGE(grid_2018, obs),
-    #         grid2019 = KGE(grid_2019, obs),
-    #         grid2020 = KGE(grid_2020, obs),
+    grid2011 = KGE(grid_2011, obs),
+            grid2012 = KGE(grid_2012, obs),
+            grid2013 = KGE(grid_2013, obs),
+            grid2014 = KGE(grid_2014, obs),
+            grid2015 = KGE(grid_2015, obs),
+            grid2016 = KGE(grid_2016, obs),
+            grid2017 = KGE(grid_2017, obs),
+            grid2018 = KGE(grid_2018, obs),
+            grid2019 = KGE(grid_2019, obs),
+            grid2020 = KGE(grid_2020, obs),
             gridall = KGE(grid_all, obs, na.rm = T, method='2012'),
-            # statn2011 = KGE(statn_2011, obs),
-            # statn2012 = KGE(statn_2012, obs),
-            # statn2013 = KGE(statn_2013, obs),
-            # statn2014 = KGE(statn_2014, obs),
-            # statn2015 = KGE(statn_2015, obs),
-            # statn2016 = KGE(statn_2016, obs),
-            # statn2017 = KGE(statn_2017, obs),
-            # statn2018 = KGE(statn_2018, obs),
-            # statn2019 = KGE(statn_2019, obs),
-            # statn2020 = KGE(statn_2020, obs),
+            statn2011 = KGE(statn_2011, obs),
+            statn2012 = KGE(statn_2012, obs),
+            statn2013 = KGE(statn_2013, obs),
+            statn2014 = KGE(statn_2014, obs),
+            statn2015 = KGE(statn_2015, obs),
+            statn2016 = KGE(statn_2016, obs),
+            statn2017 = KGE(statn_2017, obs),
+            statn2018 = KGE(statn_2018, obs),
+            statn2019 = KGE(statn_2019, obs),
+            statn2020 = KGE(statn_2020, obs),
             statnall = KGE(statn_all, obs, na.rm=T, method='2012')) %>%
@@
 
-<!-- ### Annual KGE plots -->
-
-<!-- ```{r wy plots, echo = FALSE, message = FALSE, warning = FALSE} -->
-
-<!-- plot_kge <- function(calyear) { -->
-<!--   flow_plot %>% -->
-<!--     filter(year == calyear) %>% -->
-<!--     ggplot(aes(x = model_run, -->
-<!--                y = kge)) + -->
-<!--     geom_point(size=3) + -->
-<!--     ggtitle(calyear) + -->
-<!--     theme_bw() + -->
-<!--     theme(axis.text.x = element_text(angle = 45, hjust=1)) -->
-<!-- } -->
-
-<!-- name <- levels(flow_plot$year) -->
-
-<!-- lapply(name, plot_kge) -->
-
-<!-- ``` -->
-
 ## Pbias
@@
   summarize(
-    # grid2011 = pbias(grid_2011, obs),
-    #         grid2012 = pbias(grid_2012, obs),
-    #         grid2013 = pbias(grid_2013, obs),
-    #         grid2014 = pbias(grid_2014, obs),
-    #         grid2015 = pbias(grid_2015, obs),
-    #         grid2016 = pbias(grid_2016, obs),
-    #         grid2017 = pbias(grid_2017, obs),
-    #         grid2018 = pbias(grid_2018, obs),
-    #         grid2019 = pbias(grid_2019, obs),
-    #         grid2020 = pbias(grid_2020, obs),
+    grid2011 = pbias(grid_2011, obs),
+            grid2012 = pbias(grid_2012, obs),
+            grid2013 = pbias(grid_2013, obs),
+            grid2014 = pbias(grid_2014, obs),
+            grid2015 = pbias(grid_2015, obs),
+            grid2016 = pbias(grid_2016, obs),
+            grid2017 = pbias(grid_2017, obs),
+            grid2018 = pbias(grid_2018, obs),
+            grid2019 = pbias(grid_2019, obs),
+            grid2020 = pbias(grid_2020, obs),
             gridall = pbias(grid_all, obs),
-            # statn2011 = pbias(statn_2011, obs),
-            # statn2012 = pbias(statn_2012, obs),
-            # statn2013 = pbias(statn_2013, obs),
-            # statn2014 = pbias(statn_2014, obs),
-            # statn2015 = pbias(statn_2015, obs),
-            # statn2016 = pbias(statn_2016, obs),
-            # statn2017 = pbias(statn_2017, obs),
-            # statn2018 = pbias(statn_2018, obs),
-            # statn2019 = pbias(statn_2019, obs),
-            # statn2020 = pbias(statn_2020, obs),
+            statn2011 = pbias(statn_2011, obs),
+            statn2012 = pbias(statn_2012, obs),
+            statn2013 = pbias(statn_2013, obs),
+            statn2014 = pbias(statn_2014, obs),
+            statn2015 = pbias(statn_2015, obs),
+            statn2016 = pbias(statn_2016, obs),
+            statn2017 = pbias(statn_2017, obs),
+            statn2018 = pbias(statn_2018, obs),
+            statn2019 = pbias(statn_2019, obs),
+            statn2020 = pbias(statn_2020, obs),
             statnall = pbias(statn_all, obs)) %>%
@@
 ```
-
-<!-- ### Annual Pbias plots -->
-
-<!-- ```{r pbias plots, echo = FALSE, message = FALSE, warning = FALSE} -->
-
-<!-- plot_pbias <- function(calyear) { -->
-<!--   flow_plot %>% -->
-<!--     filter(year == calyear) %>% -->
-<!--     ggplot(aes(x = model_run, -->
-<!--                y = pbias)) + -->
-<!--     geom_point(size=3) + -->
-<!--     ggtitle(calyear) + -->
-<!--     theme_bw() + -->
-<!--     theme(axis.text.x = element_text(angle = 45, hjust=1)) -->
-<!-- } -->
-
-<!-- name <- levels(flow_plot$year) -->
-
-<!-- lapply(name, plot_pbias) -->
-
-<!-- ``` -->
 

### 2025-01-27 fourmile_output_dec2024.Rmd
exported csvs for params

@@
 # 
-# write_csv(params_combo, '/Users/megansears/Documents/Repos/fourmile/38HRU_sept2013_updates/params_burn_unburn.csv')
+#write_csv(params_combo, '/Users/megansears/Documents/Repos/fourmile/38HRU_dec2024_updates/params_burn_unburn.csv')
 
@@
 
-#write_csv(params_weighted, '/Users/megansears/Documents/Repos/fourmile/38HRU_sept2013_updates/params_weighted_sept2013_edits.csv')
+#write_csv(params_weighted, '/Users/megansears/Documents/Repos/fourmile/38HRU_dec2024_updates/params_weighted_dec2024.csv')
 

### 2025-01-27 params.Rmd
params for dec2024 and sensitivity analysis

---
title: "Fourmile Calibrations and Output"
author: "Megan Sears"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: yes
    toc_float: yes
    theme: journal
editor_options:
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = F,
  message = F, 
  warning  = F)

library(tidyverse)
library(plotly)

```

# 10 most sensitive params

```{r}

statn <- read_csv('./data/sens_analysis/output_rsa_kge_runoff_statn.csv') %>%
  rename(statn_sens = sensitivity)

grid <- read_csv('./data/sens_analysis/output_rsa_kge_runoff_grid.csv') %>%
  rename(grid_sens = sensitivity)

join <- left_join(statn, grid, by ='parameter')

# rank them
join <- join %>%
  mutate(grid_rank = rank(-grid_sens),
         statn_rank = rank(-statn_sens),
         avg_rank = (grid_rank + statn_rank)/2) %>%
  arrange(avg_rank)

special <- join %>%
  slice(1:10)

####

# 10 most sensitive params
params <- read_csv('./38HRU_dec2024_updates/params_weighted_dec2024.csv')

params_filter <- params %>%
  filter(param %in% special$parameter)

```

# Burn and unburn params

```{r}

combo <- read_csv('./38HRU_dec2024_updates/params_burn_unburn.csv') %>%
  mutate(burn = if_else(burn == "yes", "Burned", "Unburned"),
         input_data = if_else(input_data =='grid', 
                              'Gridded',
                              'Station'))

ggplot(combo, aes(x = value, fill = input_data)) +
  geom_density(alpha = 0.6) +
  facet_wrap(burn ~ param, scales = "free") +
  theme_bw(base_size = 20) +
  scale_fill_manual(values = c("#0047AB", "orange")) +
  theme(
    strip.background = element_blank(),
    panel.grid = element_blank(),
    legend.position = "bottom"
  )

ggplot(combo, aes(x=burn, y=value, fill=input_data)) +
  #geom_violin(trim=T, scale='width', alpha=0.6) +
  geom_boxplot(alpha=0.8,
                outlier.colour = "black") +
  # stat_summary(fun.y=median, geom="point", size=2, color="black",
  #              position = position_dodge(width = 0.9)) +
  stat_compare_means(aes(group = input_data),
                     method = "wilcox.test", 
                     label = "p.signif",
                     hide.ns = T,
                     paired = F,
                     #label.y = 0,
                     #label.x = 1.4,
                     size = 7) +
  facet_wrap(~param, scales = 'free_y') +
  labs(y=element_blank(),
       x=element_blank()) +
  theme_bw(base_size=20) +
  scale_fill_manual(values = c("#0047AB", "orange")) +
    theme(
    legend.position = 'bottom',
    #legend.justification = c(0, 1.1), 
    legend.text = element_text(size = 16),
    legend.title = element_blank(), 
    panel.grid = element_blank(),
    panel.background = element_rect(fill = "white"),
    strip.background = element_blank(),
    text = element_text(color = "black"),
    axis.title = element_text(color = "black"),
    axis.text = element_text(color = "black"),
    #strip.text = element_blank()
  ) +
  scale_y_continuous(expand = expansion(mult = c(0.05, 0.15)))

```

### 2025-01-30 params.Rmd
plotted top8 sensitive params between grid and statn, plotted remaining parms for supp

@@
 library(plotly)
+library(ggpubr)
 
@@
 
-# 10 most sensitive params
+# Sensitivity analysis
 
 ```{r}
-
 statn <- read_csv('./data/sens_analysis/output_rsa_kge_runoff_statn.csv') %>%
@@
 
-special <- join %>%
-  slice(1:10)
+# in the average top 10 rank:
+# soilOutLPS, snow_trs, lagSurfaceRunoff, a_rain, lagInterflow,
+# baseTemp, a_snow, t_factor, soilLatVertLPS, r_factor
+# all but the last two are in statn and grids top 10,
+# so show the first 8 in the plot
+# rest of params show in the supp
 
-####
+```
 
-# 10 most sensitive params
-params <- read_csv('./38HRU_dec2024_updates/params_weighted_dec2024.csv')
+# Parameters selected from above
 
-params_filter <- params %>%
-  filter(param %in% special$parameter)
+```{r}
+# params area weighted (only for lagSurfaceRunoff, a_rain, a_snow)
+params <- read_csv('./38HRU_dec2024_updates/params_weighted_dec2024.csv') %>%
+  filter(param %in% c('lagSurfaceRunoff',
+                      'a_rain',
+                      'a_snow')) %>% # select params in the top 8 sens that are area weighted
+  rename(value = area_weighted_average,
+         input_data = source) %>%
+  select(param, input_data, value)
+
+# params unburned (above is params that needed to be area weighted bc burn/unburn)
+params_unburn <- read_csv('./38HRU_dec2024_updates/params_unburn.csv') %>%
+  filter(param %in% c('soilOutLPS',
+                      'snow_trs',
+                      'lagInterflow',
+                      'baseTemp',
+                      't_factor')) %>%
+  select(param, input_data, value)
+
+# join the two to get the top 8 sensitve params
+param_sens <- bind_rows(params, params_unburn) %>% 
+  mutate(input_data = if_else(input_data == 'grid',
+                              'Gridded',
+                              'Station'))
+
+# get distribution for signf. test
+ggplot(param_sens, aes(x = value, fill = input_data)) +
+  geom_density(alpha = 0.6) +
+  facet_wrap(~param, scales = "free") +
+  theme_bw(base_size = 20) +
+  scale_fill_manual(values = c("#0047AB", "orange")) +
+  theme(
+    strip.background = element_blank(),
+    panel.grid = element_blank(),
+    legend.position = "bottom"
+  )
+
+# boxplots of top 8
+ggplot(param_sens, aes(x=input_data, y=value, fill=input_data)) +
+  geom_boxplot(alpha=0.8,
+                outlier.colour = "black") +
+  facet_wrap(~param, scales = 'free_y') +
+  labs(y=element_blank(),
+       x=element_blank()) +
+  theme_bw(base_size=20) +
+  stat_compare_means(aes(group = input_data),
+                     method = "wilcox.test", 
+                     label = "p.signif",
+                     hide.ns = T,
+                     paired = F,
+                     #label.y = 0,
+                     #label.x = 1.4,
+                     size = 7) +
+  scale_fill_manual(values = c("#0047AB", "orange")) +
+    theme(
+    legend.position = 'none',
+    #legend.justification = c(0, 1.1), 
+    legend.text = element_text(size = 16),
+    legend.title = element_blank(), 
+    panel.grid = element_blank(),
+    panel.background = element_rect(fill = "white"),
+    strip.background = element_blank(),
+    text = element_text(color = "black"),
+    axis.title = element_text(color = "black"),
+    axis.text = element_text(color = "black"),
+    #strip.text = element_blank()
+  ) +
+  scale_y_continuous(expand = expansion(mult = c(0.05, 0.15)))
+
+ggsave('./figures/param_sensit_boxplots.png',
+       dpi=600)
+
+# show rest of params for supplemental
+# first take area weighted params (except lagSurfaceRunoff, a_rain, a_snow since that is already shown in main fig)
+otherParamsWeighted <- read_csv('./38HRU_dec2024_updates/params_weighted_dec2024.csv') %>%
+  filter(!param %in% c('lagSurfaceRunoff',
+                       'a_rain',
+                       'a_snow')) %>%
+  rename(value = area_weighted_average,
+         input_data = source) %>%
+  select(param, input_data, value)
+
+# params that were not affected by burn
+otherParams <- read_csv('./38HRU_dec2024_updates/params_unburn.csv') %>%
+  filter(!param %in% c('soilOutLPS',
+                       'snow_trs',
+                       'lagInterflow',
+                       'baseTemp',
+                       't_factor',
+                       'lagSurfaceRunoff',
+                       'a_rain',
+                       'a_snow')) %>% # these are the ones already shown
+  filter(!param %in% otherParamsWeighted$param) %>% # there are the ones that need to be area weighted
+  select(param, input_data, value)
+
+# now join the area weighted other to the other params
+otherParams <- bind_rows(otherParams, otherParamsWeighted)
+
+# plot the remaning params for catchment
+ggplot(otherParams, aes(x=input_data, y=value, fill=input_data)) +
+  geom_boxplot(alpha=0.8,
+                outlier.colour = "black") +
+  facet_wrap(~param, scales = 'free_y',
+             ncol=3) +
+  labs(y=element_blank(),
+       x=element_blank()) +
+  theme_bw(base_size=20) +
+  stat_compare_means(aes(group = input_data),
+                     method = "wilcox.test", 
+                     label = "p.signif",
+                     hide.ns = T,
+                     paired = F,
+                     #label.y = 0,
+                     #label.x = 1.4,
+                     size = 7) +
+  scale_fill_manual(values = c("#0047AB", "orange")) +
+    theme(
+    legend.position = 'none',
+    #legend.justification = c(0, 1.1), 
+    legend.text = element_text(size = 16),
+    legend.title = element_blank(), 
+    panel.grid = element_blank(),
+    panel.background = element_rect(fill = "white"),
+    strip.background = element_blank(),
+    text = element_text(color = "black"),
+    axis.title = element_text(color = "black"),
+    axis.text = element_text(color = "black"),
+    #strip.text = element_blank()
+  ) +
+  scale_y_continuous(expand = expansion(mult = c(0.05, 0.15)))
+
+ggsave('./figures/remainingparams_boxplots.png',
+       dpi=600,
+       height=16,
+       width=10)
 
@@
 
+ggsave('./figures/burn_unburn_params.png',
+       dpi=600)
+
 ```

### 2025-01-30 fourmile_output_dec2024.Rmd
1:1 and residual plots for statn_all & grid_all, updated KGE and pbias all model plots

@@
          param = as.factor(param))
+
+write_csv(params, '/Users/megansears/Documents/Repos/fourmile/38HRU_dec2024_updates/params_unburn.csv')
 
@@
 ggplotly(q)
+
+```
+
+Q 1:1  and residual plots
+
+```{r}
+
+flowComp <- flow %>%
+  dplyr::select(date,obs, statn_all, grid_all) %>%
+  drop_na(obs) %>% 
+  mutate(month = month(date)) %>%
+  mutate(statn_res = obs - statn_all,
+         grid_res = obs - grid_all)
+
+statn_comp <- ggplot(flowComp) +
+  geom_point(aes(x=obs, y = statn_all, color=as.factor(month))) +
+  geom_abline(intercept = 0, slope = 1, linetype = "dashed", color = "red")
+
+ggplotly(statn_comp)
+
+grid_comp <- ggplot(flowComp) +
+  geom_point(aes(x=obs, y = grid_all, color = as.factor(month))) +
+  geom_abline(intercept = 0, slope = 1, linetype = "dashed", color = "red") +
+  ylim(0,5)
+
+ggplotly(grid_comp)
+
+statn_res <- ggplot(flowComp) + geom_point(aes(x=obs, y = statn_res, color = as.factor(month))) +
+  theme_bw(base_size = 20) +
+    geom_hline(yintercept = 0, linetype = "dashed", color = "red")
+
+ggplotly(statn_res)
+
+ggplot(flowComp) + geom_point(aes(x=obs, y = grid_res, color = as.factor(month))) +
+  theme_bw(base_size = 20)+
+    geom_hline(yintercept = 0, linetype = "dashed", color = "red")
+
+grid_res <- ggplot(flowComp) + geom_point(aes(x=obs, y = grid_res, color = as.factor(month))) +
+  theme_bw(base_size = 20) + ylim(-5,6)+
+    geom_hline(yintercept = 0, linetype = "dashed", color = "red")
+
+ggplotly(grid_res)
 
@@
 
-ggplot(flow_plot_updated, aes(x = model_run, y = year, fill = kge)) +
+flow_plot_updated <- flow_plot_updated %>%
+  mutate(kge_revise = if_else(kge < 0, 0, kge))
+
+ggplot(flow_plot_updated, aes(x = model_run, y = year, fill = kge_revise)) +
   geom_tile(color = "white") +
-  scale_fill_viridis_c(option = "viridis", name = "KGE", direction = -1) +
-  geom_text(aes(label = round(kge, 2)), color = "grey", size = 2.5) +
-  theme_bw() +
+  scale_fill_viridis_c(option = "mako", name = "KGE", direction = -1) +
+  geom_text(aes(label = round(kge_revise, 2)), color = "grey", size = 2.5) +
+  theme_bw(base_size=20) +
   theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
@@
   geom_text(aes(label = round(pbias, 2)), color = "black", size = 2.5) +
-  theme_bw() +
+  theme_bw(base_size=20) +
   theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
@@
   geom_line(aes(y=catchmentRD1_w), size =1) +
-  facet_wrap(~year, scales = 'free', ncol = 2) +
+  facet_wrap(~year, scales="free", ncol = 2) +
   scale_x_date(labels = date_format("%b")) +
@@
   theme(text = element_text(size = 20)) +
-  labs(y = 'RD1 (mm)')
+  labs(y = 'RD1 (mm)') +
+  theme_bw(base_size=20)
 
@@
   theme(text = element_text(size = 20))+
-  labs(y = 'RD2 (mm)')
+  labs(y = 'RD2 (mm)')+
+  theme_bw(base_size=20)
 
@@
   theme(text = element_text(size = 20)) +
-  labs(y = 'RG1 (mm)')
+  labs(y = 'RG1 (mm)')+
+  theme_bw(base_size=20)
 
@@
   theme(text = element_text(size = 20))+
-  labs(y = 'RG2 (mm)')
+  labs(y = 'RG2 (mm)')+
+  theme_bw(base_size=20)
 
@@
   ggtitle('Cumulative RD1 (mm)') +
-  theme(text = element_text(size = 20))
+  theme(text = element_text(size = 20)) +
+  theme_bw(base_size=20)
 
@@
   ggtitle('Cumulative RD2 (mm)') +
-  theme(text = element_text(size = 20))
+  theme(text = element_text(size = 20))+
+  theme_bw(base_size=20)
 
@@
   ggtitle('Cumulative RG1 (mm)') +
-  theme(text = element_text(size = 20))
+  theme(text = element_text(size = 20))+
+  theme_bw(base_size=20)
 
@@
   ggtitle('Cumulative RG2 (mm)') +
-  theme(text = element_text(size = 20))
+  theme(text = element_text(size = 20))+
+  theme_bw(base_size=20)
 
@@
 
-ggplot(gw, aes(x=date)) +
+gw %>%
+  filter(source == 'grid_all') %>%
+  ggplot(aes(x=date)) +
   geom_line(aes(y=RG2cumsum, color = 'cumulative RG2'), size =1) +
@@
   scale_x_date(labels = date_format("%b")) +
-  facet_wrap(~year + source, scales = 'free_x', ncol=2) +
-  ggtitle('Cumulative RD and RG (mm)') +
-  theme(text = element_text(size = 24))
+  facet_wrap(~year, scales = 'free_x', ncol=3) +
+  ggtitle('Grid Cumulative RD and RG (mm)') +
+  #theme(text = element_text(size = 24)) +
+  theme_bw(base_size=14) +
+  labs(y='cumulative sum')
+
+gw %>%
+  filter(source == 'statn_all') %>%
+  ggplot(aes(x=date)) +
+  geom_line(aes(y=RG2cumsum, color = 'cumulative RG2'), size =1) +
+  geom_line(aes(y=RG1cumsum, color = 'cumulative RG1'), size =1) +
+  geom_line(aes(y=RD1cumsum, color = 'cumulative RD1'), size =1) +
+  geom_line(aes(y=RD2cumsum, color = 'cumulative RD2'), size =1) +
+  scale_x_date(labels = date_format("%b")) +
+  facet_wrap(~year, scales = 'free_x', ncol=3) +
+  ggtitle('Statn Cumulative RD and RG (mm)') +
+  #theme(text = element_text(size = 24)) +
+  theme_bw(base_size=14) +
+  labs(y='cumulative sum')
 
@@
   geom_boxplot(position = position_dodge(1)) +
-  geom_point(position=position_jitterdodge(),alpha=0.3) +
+  #geom_point(position=position_jitterdodge(),alpha=0.3) +
   ggtitle('Annual sum') +
-  labs(y = 'mm of water')
+  labs(y = 'mm of water') + theme_bw(base_size=20)
 
@@
   geom_boxplot(position = position_dodge(1)) +
-  geom_point(position=position_jitterdodge(),alpha=0.3) +
+  #geom_point(position=position_jitterdodge(),alpha=0.3) +
   #geom_point(aes(color = source)) +
@@
   ggtitle('Annual sum') +
-  labs(y = 'mm of water')
+  labs(y = 'mm of water') + theme_bw(base_size=20)
 

### 2025-01-31 spatial_figs.Rmd
updating colors to match other figs

--- 2025-01-17 spatial_figs.Rmd
@@
 
+flow_plot2 <- ggplot(flow, aes(x = date, y = obs)) + 
+  geom_line(size = 1.1) +
+  theme_bw(base_size = 20) +
+  labs(y = 'Discharge (cms)',
+         x = element_blank()) +
+   theme(
+    legend.position = "none",
+    panel.grid = element_blank(),
+    panel.background = element_rect(fill = "white"),
+    strip.background = element_blank(),
+    text = element_text(color = "black"),
+    axis.title = element_text(color = "black"),
+    axis.text = element_text(color = "black"),
+    strip.text = element_text(color = "black"))
+
+flow_plot2
+
+ggsave("/Users/megansears/Documents/Repos/fourmile/figures/flow_obs_plot2.png", dpi = 600, width = 12, height = 4, units = "in")
+
 ```
+
+# statn vs grid met
+
+```{r}
+
+grid <- read_csv("/Users/megansears/Documents/Repos/fourmile/38HRU_sept2013_updates/grid_all_Catchment.csv",
+                 skip=3) %>%
+   slice(3:n()) %>%
+  dplyr::select(-starts_with('@'),
+                -1) %>%
+  mutate(date = ymd(time)) %>%
+  dplyr::select(-time) %>%
+  mutate_if(is.character, as.numeric) %>% 
+  mutate(site = 'grid')
+
+statn <- read_csv('/Users/megansears/Documents/Repos/fourmile/38HRU_sept2013_updates/statn_all_Catchment.csv',
+                 skip=3) %>%
+   slice(3:n()) %>%
+  dplyr::select(-starts_with('@'),
+                -1) %>%
+  mutate(date = ymd(time)) %>%
+  dplyr::select(-time) %>%
+  mutate_if(is.character, as.numeric) %>% 
+  mutate(site = 'statn')
+
+all <- bind_rows(grid, statn) %>%
+  arrange(date)
+
+catchment_mo_mean <- all %>%
+  mutate(month = month(date)) %>%
+  group_by(site, month) %>%
+  summarise(across(tmean:solRad, ~ mean(.x, na.rm = TRUE))) %>%
+  dplyr::select(site, month, tmean_mean = tmean, 
+                solrad_mean = solRad, rh_mean = rhum)
+
+catchment_mo_sum <- all %>%
+  dplyr::select(date, precip, site) %>%
+  mutate(month = month(date),
+         year = year(date)) %>%
+  group_by(month, year, site) %>%
+  summarize(p_sum = sum(precip)) %>%
+  group_by(month, site) %>%
+  summarize(avg_p = mean(p_sum),
+          sd_p = sd(p_sum))
+
+catchment_mo_sd <- all %>%
+  mutate(month = month(date)) %>%
+  group_by(site, month) %>%
+  summarise(across(tmean:solRad, ~ sd(.x, na.rm = TRUE))) %>%
+  dplyr::select(site, month, tmean_sd = tmean, 
+                solrad_sd = solRad, rh_sd = rhum)
+
+catchment_mo <- left_join(catchment_mo_mean, catchment_mo_sd, 
+                          by = c('month', 'site'))
+
+catchment_mo <- left_join(catchment_mo, catchment_mo_sum)
+
+catchment_mo2 <- catchment_mo %>%
+  mutate(month_name = month.abb[month]) %>%
+  mutate(month_name = factor(month_name, 
+                             levels = c('Jan', 'Feb', 'Mar',
+                                        'Apr', 'May', 'Jun',
+                                        'Jul', 'Aug', 'Sep',
+                                        'Oct', 'Nov', 'Dec')))
+
+p_cols <- ggplot(catchment_mo2, aes(x = month_name, y = avg_p,
+                                    color = site, fill = site)) +
+  geom_col(position = 'dodge') +
+  geom_errorbar(aes(ymin = 0, ymax = avg_p + sd_p), 
+                position = position_dodge(width = 0.6), width = 0.2) +
+  scale_color_manual(values = c("#0047AB", "orange"),
+                     labels = c("Gridded", "Station")) +  # Rename color legend items
+  scale_fill_manual(values = c("#0047AB", "orange"),
+                    labels = c("Gridded", "Station")) +   # Rename fill legend items
+  theme_bw(base_size = 20) +
+  labs(y = 'Precipitation (mm)',
+       x = element_blank()) +
+  guides(color = guide_legend(title = NULL),
+         fill = guide_legend(title = NULL)) +
+    theme(
+    panel.grid = element_blank(),
+    panel.background = element_rect(fill = "white"),
+    text = element_text(color = "black"),
+    axis.title = element_text(color = "black"),
+    axis.text = element_text(color = "black"),
+    strip.text = element_blank()
+  )
+
+p_cols
+
+ggsave("/Users/megansears/Documents/Repos/fourmile/figures/precip.png", plot = p_cols, width = 8, height = 6, dpi = 300)
+
+# Temperature plot
+t_moplot <- ggplot(catchment_mo2, aes(x = month_name, y = tmean_mean, 
+                                      color = site, group = site)) +
+  geom_ribbon(aes(ymin = tmean_mean - tmean_sd, ymax = tmean_mean + tmean_sd, fill = site), alpha = 0.6) +
+  geom_line() +
+  geom_point() +
+  scale_color_manual(values = c("#0047AB", "orange"),
+                     labels = c("Gridded", "Station")) +  # Set line color to #0047AB and orange and rename
+  scale_fill_manual(values = c("#0047AB", "orange"),
+                    labels = c("Gridded", "Station")) +   # Set ribbon fill color to #0047AB and orange and rename
+  theme_bw(base_size=20) +
+  labs(y = expression("Air temperature " ( degree~C)),
+       x = element_blank()) +
+  labs(color = NULL, fill = NULL) +
+      theme(
+    panel.grid = element_blank(),
+    panel.background = element_rect(fill = "white"),
+    text = element_text(color = "black"),
+    axis.title = element_text(color = "black"),
+    axis.text = element_text(color = "black"),
+    strip.text = element_blank())
+
+# Solar radiation plot
+sol_moplot <- ggplot(catchment_mo2, aes(x = month_name, y = solrad_mean, 
+                                         color = site, group = site)) +
+  geom_ribbon(aes(ymin = solrad_mean - solrad_sd, ymax = solrad_mean + solrad_sd, fill = site), alpha = 0.6) +
+  geom_line() +
+  geom_point() +
+  scale_color_manual(values = c("#0047AB", "orange"),
+                     labels = c("Gridded", "Station")) +  # Set line color to #0047AB and orange and rename
+  scale_fill_manual(values = c("#0047AB", "orange"),
+                    labels = c("Gridded", "Station")) +   # Set ribbon fill color to #0047AB and orange and rename
+  theme_bw(base_size = 20) +
+  labs(y = expression("Solar radiation (MJ/m"^"2" * ")"),
+       x = element_blank()) +
+  labs(color = NULL, fill = NULL) +
+      theme(
+    panel.grid = element_blank(),
+    panel.background = element_rect(fill = "white"),
+    text = element_text(color = "black"),
+    axis.title = element_text(color = "black"),
+    axis.text = element_text(color = "black"),
+    strip.text = element_blank())
+
+# Relative humidity plot
+rh_moplot <- ggplot(catchment_mo2, aes(x = month_name, y = rh_mean, 
+                                        color = site, group = site)) +
+  geom_ribbon(aes(ymin = rh_mean - rh_sd, ymax = rh_mean + rh_sd, fill = site), alpha = 0.6) +
+  geom_line() +
+  geom_point() +
+  scale_color_manual(values = c("#0047AB", "orange"),
+                     labels = c("Gridded", "Station")) +  # Set line color to #0047AB and orange and rename
+  scale_fill_manual(values = c("#0047AB", "orange"),
+                    labels = c("Gridded", "Station")) +   # Set ribbon fill color to #0047AB and orange and rename
+  theme_bw(base_size = 20) +
+  labs(y = 'RH (%)', x= element_blank()) +
+  labs(color = NULL, fill = NULL) +
+      theme(
+    panel.grid = element_blank(),
+    panel.background = element_rect(fill = "white"),
+    text = element_text(color = "black"),
+    axis.title = element_text(color = "black"),
+    axis.text = element_text(color = "black"),
+    strip.text = element_blank())
+
+library(ggpubr)
+
+quad <- ggarrange(p_cols, 
+          t_moplot,
+          sol_moplot,
+          rh_moplot,
+          common.legend = T,
+          legend = 'bottom',
+          ncol=2,
+          nrow=2) 
+          #nrow = 4)
+          #ncol= 0)
+quad
+
+ggsave("/Users/megansears/Documents/Repos/fourmile/figures/quad.png", plot = quad, dpi = 600)
+
+```

### 2025-01-31 state_vars.Rmd
look at state vars for dec2024 and started interpret. results

@@
 
-statn <- read_csv('./38HRU_sept2013_updates/catchment_output/Catchment_statnall.csv') %>%
+statn <- read_csv('./38HRU_dec2024_updates/catchment_output/Catchment_statnall.csv') %>%
   mutate(date = mdy(time),
@@
 
-grid <- read_csv('./38HRU_sept2013_updates/catchment_output/Catchment_gridall.csv') %>%
+grid <- read_csv('./38HRU_dec2024_updates/catchment_output/Catchment_gridall.csv') %>%
   mutate(date = mdy(time),
@@
   geom_line() +
-  scale_color_manual(values = c("orange", "blue"))
+  scale_color_manual(values = c("#0047AB", "orange"))
 
@@
   geom_point(size=3) +
-  scale_color_manual(values = c("orange", "blue")) +
+  scale_color_manual(values = c("#0047AB", "orange")) +
   labs(y= 'Monthly mean tmean (C)')
@@
   geom_point(size=3) +
-  scale_color_manual(values = c("orange", "blue")) +
+  scale_color_manual(values = c("#0047AB", "orange")) +
   labs(y= 'Monthly mean precip (mm)')
@@
   geom_point(size=3) +
-  scale_color_manual(values = c("orange", "blue")) +
+  scale_color_manual(values = c("#0047AB", "orange")) +
   labs(y= 'Monthly mean solrad')
@@
 ## Interception
-- Average interception: grid > statn
+
 - Monthly average: Statn > grid 1:4 and 10:12, grid > statn 5:9
@@
   geom_point(size=3) +
-  scale_color_manual(values = c("orange", "blue")) +
+  scale_color_manual(values = c("#0047AB", "orange")) +
   labs(y= 'Monthly mean interception')
@@
 - Average ET: grid > statn
-- Monthly average ET: grid > statn 1:6 and 9:12, statn > grid 7:8
+- Monthly average ET: grid > statn 1:5 and 9:12, statn > grid 6:8
 
@@
   geom_point(size=3) +
-  scale_color_manual(values = c("orange", "blue")) +
+  scale_color_manual(values = c("#0047AB", "orange")) +
   labs(y= 'Monthly mean ET (mm)')
@@
   geom_line() +
-  scale_color_manual(values = c("orange", "blue")) +
+  scale_color_manual(values = c("#0047AB", "orange")) +
   labs(y='ET (mm)')
@@
 
-- Grid > Statn
-- SWE starts accumulating faster in Sept for statn than grid
-- But grid > statn all other months
+- Despite grid being higher all winter, it melts out faster than statn
+- grid generally has higher SWE, but statn starts accumulating earlier & melts slower
 
@@
   geom_point(size=3) +
-  scale_color_manual(values = c("orange", "blue")) +
+  scale_color_manual(values = c("#0047AB", "orange")) +
   labs(y= 'Monthly mean SWE (l/day)')
@@
   geom_line() +
-  scale_color_manual(values = c("orange", "blue")) +
+  scale_color_manual(values = c("#0047AB", "orange")) +
   labs(y='SWE (l/day)')
@@
 
-- Statn > grid all months
+- 4,5,6,10 statn > SM than grid
+- SM higher for statn
 
@@
   geom_point(size=3) +
-  scale_color_manual(values = c("orange", "blue")) +
+  scale_color_manual(values = c("#0047AB", "orange")) +
   labs(y= 'Monthly mean soil sat')
@@
 
-- RG1: when there is surface runoff, statn is slightly higher
-- Except for September (Sep 2013 flood heavily influences this avg)
-- Many of the surface runoff events are happening Mar-May and Jul
+- RG1: very little other than Sept, where grid > statn
 
@@
   geom_point(size=3) +
-  scale_color_manual(values = c("orange", "blue")) +
+  scale_color_manual(values = c("#0047AB", "orange")) +
   labs(y= 'Monthly mean surface runoff (l)')
@@
   geom_line() +
-  scale_color_manual(values = c("orange", "blue")) +
+  scale_color_manual(values = c("#0047AB", "orange")) +
   labs(y='Surface runoff (l)')
@@
 
-- Statn > grid Jan to Apr
-- Grid > statn May, Jun, Oct
-- Other months are similar
+- Statn > grid
+- very little grid
 
@@
   geom_point(size=3) +
-  scale_color_manual(values = c("orange", "blue")) +
+  scale_color_manual(values = c("#0047AB", "orange")) +
   labs(y= 'Monthly mean interflow (l)')
@@
   geom_line() +
-  scale_color_manual(values = c("orange", "blue")) +
+  scale_color_manual(values = c("#0047AB", "orange")) +
   labs(y='Interflow (l)')
@@
 - RG1 = shallow groundwater
-- RG1: during snowmelt runoff to fall baseflow grid > statn
-- RG1: statn > grid during winter
+- RG1: grid > statn
 
@@
   geom_point(size=3) +
-  scale_color_manual(values = c("orange", "blue")) +
+  scale_color_manual(values = c("#0047AB", "orange")) +
   labs(y= 'Monthly mean RG1 (unit?)')
@@
   geom_point(size=3) +
-  scale_color_manual(values = c("orange", "blue")) +
+  scale_color_manual(values = c("#0047AB", "orange")) +
   labs(y= 'Monthly mean RG2 (unit?)')
@@
 ```
+
+NOTHING BELOW HAS BEEN UPDATED WITH DEC2024 UPDATES
 
@@
   geom_point(size=3) +
-  scale_color_manual(values = c("orange", "blue")) +
+  scale_color_manual(values = c("#0047AB", "orange")) +
   labs(y= 'Monthly mean solrad (MJ/m2/day)')

### 2025-02-04 fourmile_output_dec2024.Rmd
made scales on residual plots same

@@
   theme_bw(base_size = 20) +
-    geom_hline(yintercept = 0, linetype = "dashed", color = "red")
+    geom_hline(yintercept = 0, linetype = "dashed", color = "red")+
+  ylim(-5, 6)
 

### 2025-02-04 params.Rmd
added soilLatVertLPS to main param fig, minor fig formatting

@@
          input_data = source) %>%
-  select(param, input_data, value)
+  dplyr::select(param, input_data, value)
 
@@
                       'baseTemp',
-                      't_factor')) %>%
-  select(param, input_data, value)
+                      't_factor',
+                      'soilLatVertLPS')) %>%
+  dplyr::select(param, input_data, value)
 
@@
                        'a_rain',
-                       'a_snow')) %>% # these are the ones already shown
+                       'a_snow',
+                       'soilLatVertLPS')) %>% # these are the ones already shown
   filter(!param %in% otherParamsWeighted$param) %>% # there are the ones that need to be area weighted
-  select(param, input_data, value)
+  dplyr::select(param, input_data, value)
 
@@
   ) +
-  scale_y_continuous(expand = expansion(mult = c(0.05, 0.15)))
+  scale_y_continuous(expand = expansion(mult = c(0.001, 0.3)))
 

### 2025-02-21 params.Rmd
added 2way ANOVA and Tukey to burn/unburn params

@@
 library(ggpubr)
+library(broom)
+library(multcompView)
 
@@
 
+#write_csv(combo, './38HRU_dec2024_updates/params_burn_unburn.csv')
+combo <- read_csv('./38HRU_dec2024_updates/params_burn_unburn.csv')
+
 ggplot(combo, aes(x = value, fill = input_data)) +
@@
 ggplot(combo, aes(x=burn, y=value, fill=input_data)) +
-  #geom_violin(trim=T, scale='width', alpha=0.6) +
   geom_boxplot(alpha=0.8,
                 outlier.colour = "black") +
-  # stat_summary(fun.y=median, geom="point", size=2, color="black",
-  #              position = position_dodge(width = 0.9)) +
-  stat_compare_means(aes(group = input_data),
-                     method = "wilcox.test", 
-                     label = "p.signif",
-                     hide.ns = T,
-                     paired = F,
-                     #label.y = 0,
-                     #label.x = 1.4,
-                     size = 7) +
+  geom_text(aes(label = letter)) +
+  # stat_compare_means(aes(group = input_data),
+  #                    method = "wilcox.test", 
+  #                    label = "p.signif",
+  #                    hide.ns = T,
+  #                    paired = F,
+  #                    #label.y = 0,
+  #                    #label.x = 1.4,
+  #                    size = 7) +
   facet_wrap(~param, scales = 'free_y') +
@@
 
-ggsave('./figures/burn_unburn_params.png',
+ggsave('./figures/burn_unburn_params_tukey.png',
        dpi=600)
 
+# Compute y_text just above the boxplot whiskers
+combo <- combo %>%
+  group_by(param, burn, input_data) %>%
+  mutate(y_text = max(value, na.rm = TRUE) * 1.08) %>%  # Slightly above max value
+  ungroup()
+
+ggplot(combo, aes(x = burn, y = value, fill = input_data)) +
+  geom_boxplot(alpha = 0.8, outlier.colour = "black") +
+  geom_text(aes(label = letter, y = y_text), 
+            position = position_dodge(width = 0.75),  # Align with boxplots
+            size = 6, 
+            vjust = 0) +  # Prevent overlap with whiskers
+  facet_wrap(~param, scales = 'free_y') +
+  labs(y = element_blank(), x = element_blank()) +
+  theme_bw(base_size = 20) +
+  scale_fill_manual(values = c("#0047AB", "orange")) +
+  theme(
+    legend.position = 'bottom',
+    legend.text = element_text(size = 16),
+    legend.title = element_blank(),
+    panel.grid = element_blank(),
+    panel.background = element_rect(fill = "white"),
+    strip.background = element_blank(),
+    text = element_text(color = "black"),
+    axis.title = element_text(color = "black"),
+    axis.text = element_text(color = "black")
+  ) +
+   scale_y_continuous(expand = expansion(mult = c(0.05, 0.1)))
+
+ggsave('./figures/burn_unburn_params_tukey.png',
+       dpi=600,
+       width = 12,
+       height = 8)
+
 ```
+
+# Anova for Burn/Unburn Params
+
+```{r}
+
+tukey_results <- combo %>%
+  rename(burn_status = burn) %>%
+  mutate(burn_status = as.factor(burn_status),
+         input_data = as.factor(input_data)) %>%
+  group_split(param) %>%
+  map(function(df) {
+    # 2 way anova
+    model <- aov(value ~ burn_status * input_data, data = df)
+
+    # Tukey HSD
+    tukey_test <- TukeyHSD(model)
+
+    # Tukey letters based on p val
+    tukey_letters <- multcompLetters4(model, tukey_test)
+
+    list(
+      parameter = unique(df$param),
+      model = model,
+      tukey = tukey_test,
+      letters = tukey_letters
+    )
+  })
+
+# Convert results into a tibble
+tukey_df <- tibble(
+  parameter = map_chr(tukey_results, "parameter"),
+  model = map(tukey_results, "model"),
+  tukey = map(tukey_results, "tukey"),
+  letters = map(tukey_results, "letters")
+)
+
+# added tukey letters to parmas_burn_unburn.csv in dec2024 folder
+
+```

### 2025-02-21 fourmile_output_dec2024.Rmd
finished residual plots

@@
 library(stringr)
+library(cowplot)
 
@@
 
-Q 1:1  and residual plots
+# Q 1:1  and residual plots
 
@@
 ggplotly(grid_res)
+
+################################################################################
+
+# make the actual figures
+compFlip <- flowComp %>%
+  dplyr::select(-month) %>%
+  pivot_longer(!c(date, obs), names_to = 'flow_type',
+               values_to = 'flow_cms')
+
+# residual scatter plot
+plot <- compFlip %>%
+  filter(flow_type %in% c('statn_res', 'grid_res')) %>%
+  ggplot(., aes(x=obs, 
+                     y=flow_cms,
+                color = flow_type)) +
+  geom_hline(yintercept = 0, color = "black") +
+  geom_point(size=3,
+             alpha=0.6) +
+  ylim(-5,6) +
+  theme_bw(base_size = 20) +
+  scale_color_manual(values = c("#0047AB", "orange")) +
+  labs(x='Observed discharge (cms)',
+       y='Residuals (cms)') +
+  facet_wrap(~flow_type,
+             labeller = as_labeller(c("grid_res" = "Gridded", "statn_res" = "Station"))) +
+  theme(
+    legend.position = 'none',
+    legend.text = element_text(size = 16),
+    legend.title = element_blank(),
+    panel.grid = element_blank(),
+    panel.background = element_rect(fill = "white"),
+    strip.background = element_blank(),
+    text = element_text(color = "black"),
+    axis.title = element_text(color = "black"),
+    axis.text = element_text(color = "black")
+  )
+
+plot
+
+# pick select years to show resids over time
+plot_bottom12 <- compFlip %>%
+  filter(flow_type %in% c('statn_res', 'grid_res')) %>%
+  mutate(year = year(date)) %>%
+  filter(year %in% c(2012, 2015, 2017)) %>% 
+  mutate(flow_type = if_else(flow_type == 'grid_res', 
+                             "Gridded",
+                             "Station")) %>%
+  ggplot(aes(x = date, y = flow_cms, color = flow_type)) +  
+  geom_line(size=1, alpha=0.7) + 
+  scale_color_manual(values = c("#0047AB", "orange")) +
+  facet_wrap(~year, scales="free_x") +
+  labs(x=element_blank(),
+       y='Residuals (cms)') +
+  theme(
+   legend.position = c(0.93, 0.85),
+    legend.text = element_text(size = 16),
+    legend.title = element_blank(),
+    panel.grid = element_blank(),
+    panel.background = element_rect(fill = "white"),
+    strip.background = element_blank(),
+    text = element_text(color = "black"),
+    axis.title = element_text(color = "black"),
+    axis.text = element_text(color = "black")
+  )
+
+plot_bottom12
+
+# add 2 above plots together
+plot_grid(plot, plot_bottom12, ncol = 1)
+
+# export
+ggsave('/Users/megansears/Documents/Repos/fourmile/figures/resids.png',
+       dpi=600,
+       width = 12,
+       height = 8)
+
+# OPTION 2 - make the bottom the whole time series
+plot_bottom <- compFlip %>%
+  filter(flow_type %in% c('statn_res', 'grid_res')) %>%
+  complete(date = seq.Date(min(date), max(date), by = "day"), fill = list(flow_cms = NA)) %>%
+  # Create a new group ID that resets at each missing value (only where flow_cms is NA)
+  mutate(group_id = cumsum(is.na(flow_cms))) %>%
+  filter(!is.na(flow_cms)) %>%
+  mutate(flow_type = if_else(flow_type == 'grid_res', 
+                             "Gridded",
+                             "Station")) %>%
+  ggplot(aes(x = date, y = flow_cms, color = flow_type, group = group_id)) +  
+  geom_line(size=1, alpha=0.7) +  
+  ylim(-4,6) +
+  scale_color_manual(values = c("#0047AB", "orange")) +
+  labs(x=element_blank(),
+       y='Residuals (cms)') +
+  theme(
+    legend.position = c(0.9, 0.87),
+    legend.text = element_text(size = 16),
+    legend.title = element_blank(),
+    panel.grid = element_blank(),
+    panel.background = element_rect(fill = "white"),
+    strip.background = element_blank(),
+    text = element_text(color = "black"),
+    axis.title = element_text(color = "black"),
+    axis.text = element_text(color = "black")
+  )
+
+plot_bottom
+
+plot_grid(plot, plot_bottom, ncol = 1)
+
+# export
+ggsave('/Users/megansears/Documents/Repos/fourmile/figures/resids_option2.png',
+       dpi=600,
+       width = 12,
+       height = 8)
 

### 2025-02-21 fourmile_output_dec2024.Rmd
minor
updates to KGE fig (need to fix legend & add boxplot)

@@
 kge_all <- flow_kge_all %>%
-  mutate(year = 'all years') %>%
+  mutate(year = 'All') %>%
   rename(model_run = name,
@@
 
-ggplot(flow_plot_updated, aes(x = model_run, y = year, fill = kge_revise)) +
+flow_plot_updated <- flow_plot_updated %>% 
+  mutate(source = case_when(
+    grepl("grid", model_run) ~ "grid",
+    grepl("statn", model_run) ~ "statn"),
+    year_excluded = str_extract(model_run, "\\d{4}$")) %>%
+  mutate(year_excluded = if_else(model_run %in% c('gridall',
+                                                       'statnall'),
+                                  'None', year_excluded))
+
+ggplot(flow_plot_updated, aes(x = year_excluded, y = year, fill = kge_revise)) +
   geom_tile(color = "white") +
   scale_fill_viridis_c(option = "mako", name = "KGE", direction = -1) +
-  geom_text(aes(label = round(kge_revise, 2)), color = "grey", size = 2.5) +
+  #geom_text(aes(label = round(kge_revise, 2)), color = "grey", size = 2.5) +
+  geom_text(aes(label = sprintf("%.2f", kge_revise)), color = "grey", size = 2.5) +
   theme_bw(base_size=20) +
   theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
-  labs(y = "Year")
+  labs(y = "Year",
+       x='Year Excluded') +
+  facet_wrap(~source,
+             scales = 'free_x',
+             labeller = as_labeller(c("grid" = "Gridded", "statn" = "Station"))) +
+  theme(
+    axis.text.x = element_text(angle = 45, hjust = 1),
+    legend.position = 'bottom',
+    legend.text = element_text(size = 16),
+    legend.title = element_text(size = 16),  # Correct way to adjust legend title text
+    legend.key.width = unit(1, "cm"),
+    panel.grid = element_blank(),
+    panel.background = element_rect(fill = "white"),
+    strip.background = element_blank(),
+    text = element_text(color = "black"),
+    axis.title = element_text(color = "black"),
+    axis.text = element_text(color = "black")
+  )
+
+ggsave('/Users/megansears/Documents/Repos/fourmile/figures/kge_heatmap.png',
+       dpi=600,
+       width = 10,
+       height = 6)
 

### 2025-02-25 fourmile_output_dec2024.Rmd
updated water partition boxplots. need to finish adding tukey letters. added 2015 as example year for cumulative flows

@@
 
+# look at 2015, high snow year 
+example <- gw %>%
+  filter(year == 2015) %>%
+  ungroup() %>% 
+  dplyr::select(date, source,
+         RD1cumsum,
+         RD2cumsum,
+         RG1cumsum,
+         RG2cumsum) %>%
+  pivot_longer(!c(date,source), names_to='flow_type',
+               values_to='flow_cms') %>%
+  mutate(source = if_else(source == 'grid_all',
+                          'Gridded',
+                          'Station'))
+
+facet_labels <- c('RD1cumsum' = 'Surface runoff',
+                  'RD2cumsum' = 'Interflow',
+                  'RG1cumsum' = 'Fast groundwater',
+                  'RG2cumsum' = 'Slow groundwater')
+
+ggplot(example,
+       aes(x=date, y = flow_cms, color=source)) +
+  geom_line() +
+  facet_wrap(~flow_type, 
+             scales = 'free_y',
+             labeller = labeller(flow_type = facet_labels)) +
+   geom_line(size=1, alpha=0.7) +  
+  scale_color_manual(values = c("#0047AB", "orange")) +
+  labs(x=element_blank(),
+       y='Flow (cms)') +
+  theme_bw(base_size = 20) +
+  theme(
+    legend.position = c(0.94, 0.08),
+    legend.text = element_text(size = 12),
+    legend.title = element_blank(),
+    panel.grid = element_blank(),
+    panel.background = element_rect(fill = "white"),
+    strip.background = element_blank(),
+    text = element_text(color = "black"),
+    axis.title = element_text(color = "black"),
+    axis.text = element_text(color = "black")
+  )
+
+ggsave('./figures/2015_flowcumulative.png',
+       dpi=600)
+
 ```
@@
   mutate(year = as.factor(year)) %>%
-  pivot_longer(!c(year, source), names_to = 'flow_type', values_to = 'flow_cms')
+  pivot_longer(!c(year, source), names_to = 'flow_type', values_to = 'flow_cms') %>%
+  mutate(source = if_else(source == 'grid_all',
+                          'Gridded',
+                          'Station'))
 
@@
   #geom_point(position=position_jitterdodge(),alpha=0.3) +
+  scale_y_log10() +
   ggtitle('Annual sum') +
-  labs(y = 'mm of water') + theme_bw(base_size=20)
+  labs(y = 'mm of water') + theme_bw(base_size=20) # this plot doesnt show lower values (eg rd1)
+# i tried with log scale on y and it looks really bad so going with facet below
+
+facet_labels <- c('yr_cum_RD1' = 'Surface runoff',
+                  'yr_cum_RD2' = 'Interflow',
+                  'yr_cum_RG1' = 'Fast groundwater',
+                  'yr_cum_RG2' = 'Slow groundwater')
 
 ggplot(gw_maxcumsum, aes(x = flow_type, y = flow_cms, fill = source)) +
-  geom_boxplot(position = position_dodge(1)) +
-  #geom_point(position=position_jitterdodge(),alpha=0.3) +
-  #geom_point(aes(color = source)) +
-  facet_wrap(~flow_type, scales = 'free') +
-  ggtitle('Annual sum') +
-  labs(y = 'mm of water') + theme_bw(base_size=20)
+  geom_boxplot(position = position_dodge(1),
+               outliers=F) + # need to note 1 outlier is removed from RD1 grid and statn (2013 flood) ****
+  stat_compare_means(data = gw_maxcumsum %>% 
+                       filter(flow_type != "yr_cum_RD1"),
+                     aes(group = source),
+                     method = "wilcox.test",
+                     label = "p.signif",
+                     hide.ns = T,
+                     paired = F,
+                     size = 7) +
+  facet_wrap(~flow_type, 
+             scales = 'free',
+             labeller = labeller(flow_type = facet_labels)) +
+  labs(y = 'mm of water') + 
+  theme_bw(base_size=20) +
+  scale_fill_manual(values = c("#0047AB", "orange")) +
+  theme(
+    legend.position = c(0.9, 0.38),
+    legend.text = element_text(size = 12),
+    legend.title = element_blank(),
+    panel.grid = element_blank(),
+    panel.background = element_rect(fill = "white"),
+    strip.background = element_blank(),
+    text = element_text(color = "black"),
+    axis.title = element_text(color = "black"),
+    axis.text = element_text(color = "black"),
+    axis.title.x = element_blank(),
+    axis.text.x = element_blank(),
+    axis.ticks.x = element_blank()) +
+  scale_y_continuous(expand = expansion(mult = c(0.05, 0.15)))
+
+ggsave('./figures/water_partition_boxplots.png',
+       dpi=600)
+
+# want to see distribution
+ggplot(gw_maxcumsum, aes(x = flow_cms, fill = source)) +
+  geom_density(alpha = 0.6, adjust = 1.2) +  # Adjust smoothness with `adjust`
+  facet_wrap(~flow_type, 
+             scales = 'free', 
+             labeller = labeller(flow_type = facet_labels)) +
+  labs(x = "Flow (cms)", y = "Density") + 
+  theme_bw(base_size = 20) +
+  scale_fill_manual(values = c("#0047AB", "orange")) +
+  theme(
+    legend.position = 'top',
+    legend.text = element_text(size = 16),
+    legend.title = element_blank(),
+    panel.grid = element_blank(),
+    panel.background = element_rect(fill = "white"),
+    strip.background = element_blank(),
+    text = element_text(color = "black"),
+    axis.title = element_text(color = "black"),
+    axis.text = element_text(color = "black")
+  )
+
+```
+
+### RD and RG stats
+
+```{r}
+
+model <-aov(flow_cms ~ source * flow_type, 
+            data = gw_maxcumsum)
+
+# Tukey HSD
+tukey_test <- TukeyHSD(model)
+
+tukey_test
+
+library(multcompView)
+tukey_letters <- multcompLetters4(model, tukey_test)
+
+tukey_letters$`source:flow_type`$Letters
+
+# make a vector of the letters
+letters_vector <- c("a", "b", "b", "c", "c", "c", "c", "c")
+
+gw_maxcumsum <- gw_maxcumsum %>%
+  mutate(letter = case_when(
+    source == "Gridded" & flow_type == "yr_cum_RG1" ~ letters_vector[1],
+    source == "Station" & flow_type == "yr_cum_RG1" ~ letters_vector[2],
+    source == "Station" & flow_type == "yr_cum_RD2" ~ letters_vector[3],
+    source == "Gridded" & flow_type == "yr_cum_RD1" ~ letters_vector[4],
+    source == "Station" & flow_type == "yr_cum_RD1" ~ letters_vector[5],
+    source == "Gridded" & flow_type == "yr_cum_RD2" ~ letters_vector[6],
+    source == "Gridded" & flow_type == "yr_cum_RG2" ~ letters_vector[7],
+    source == "Station" & flow_type == "yr_cum_RG2" ~ letters_vector[8]
+  ))
+
+# now make the same figure as above but with letters
+facet_labels <- c('yr_cum_RD1' = 'Surface runoff',
+                  'yr_cum_RD2' = 'Interflow',
+                  'yr_cum_RG1' = 'Fast groundwater',
+                  'yr_cum_RG2' = 'Slow groundwater')
+
+gw_maxcumsum_letters <- gw_maxcumsum %>%
+  group_by(source, flow_type) %>%
+  mutate(max = max(flow_cms)) %>%
+  distinct(flow_type, source, .keep_all = TRUE) %>%
+    mutate(max = if_else((flow_type == 'yr_cum_RD1' & 
+                           source == 'Gridded'),
+                         3.5, max)) %>%
+    mutate(max = if_else((flow_type == 'yr_cum_RD1' & 
+                           source == 'Station'),
+                         1.3, max))
+
+ggplot(gw_maxcumsum, aes(x = flow_type, y = flow_cms, fill = source)) +
+  geom_boxplot(position = position_dodge(1),
+               outliers=F) + # need to note 1 outlier is removed from RD1 grid and statn (2013 flood) ****
+  geom_text(data = gw_maxcumsum_letters, 
+            aes(label=letter,
+                x=flow_type, 
+                y=max), 
+            position=position_dodge2(0.75), 
+            vjust = -6) + 
+  facet_wrap(~flow_type, 
+             scales = 'free',
+             labeller = labeller(flow_type = facet_labels)) +
+  labs(y = 'mm of water') + 
+  theme_bw(base_size=20) +
+  scale_fill_manual(values = c("#0047AB", "orange")) +
+  theme(
+    legend.position = c(0.9, 0.38),
+    legend.text = element_text(size = 12),
+    legend.title = element_blank(),
+    panel.grid = element_blank(),
+    panel.background = element_rect(fill = "white"),
+    strip.background = element_blank(),
+    text = element_text(color = "black"),
+    axis.title = element_text(color = "black"),
+    axis.text = element_text(color = "black"),
+    axis.title.x = element_blank(),
+    axis.text.x = element_blank(),
+    axis.ticks.x = element_blank())
+
+ggsave('./figures/water_partition_boxplots.png',
+       dpi=600)
 

### 2025-02-25 params.Rmd
minor

@@
 
-# Compute y_text just above the boxplot whiskers
+# text above boxplots
 combo <- combo %>%

### 2025-02-27 fourmile_output_dec2024.Rmd
finished adding letter to boxplots for tukey

@@
                            source == 'Station'),
-                         1.3, max))
+                         1.3, max)) %>%
+  mutate(y_text = max * 1.07)
 
@@
             aes(label=letter,
-                x=flow_type, 
-                y=max), 
-            position=position_dodge2(0.75), 
-            vjust = -6) + 
+                y=y_text),
+            position = position_dodge(width = 0.97),
+            size = 6, 
+            vjust = 0) + 
   facet_wrap(~flow_type, 
@@
     axis.text.x = element_blank(),
-    axis.ticks.x = element_blank())
+    axis.ticks.x = element_blank()) +
+  scale_y_continuous(expand = expansion(mult = c(0.05, 0.1)))
 

### 2025-02-27 params.Rmd
minor

@@
             size = 6, 
-            vjust = 0) +  # Prevent overlap with whiskers
+            vjust = 0) +  
   facet_wrap(~param, scales = 'free_y') +

### 2025-03-13 fourmile_output_dec2024.Rmd
updated kge and pbais heatmaps

@@
 
-ggplot(flow_plot_updated, aes(x = year_excluded, y = year, fill = kge_revise)) +
+# need to make separate plots bc can't put boxplots in margins for facet wrap
+grid_kge_plot <- flow_plot_updated %>%
+  filter(source == 'grid') %>% 
+ggplot(., aes(x = year_excluded, 
+              y = year, fill = 
+                kge_revise)) +
   geom_tile(color = "white") +
-  scale_fill_viridis_c(option = "mako", name = "KGE", direction = -1) +
-  #geom_text(aes(label = round(kge_revise, 2)), color = "grey", size = 2.5) +
-  geom_text(aes(label = sprintf("%.2f", kge_revise)), color = "grey", size = 2.5) +
+  scale_fill_viridis_c(option = "mako", 
+                       name = "KGE", 
+                       direction = -1) +
+  geom_text(aes(label = sprintf("%.2f", 
+                                kge_revise)), 
+            color = "grey", 
+            size = 2.5) +
   theme_bw(base_size=20) +
-  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
+  theme(axis.text.x = element_text(angle = 45, 
+                                   hjust = 1)) +
   labs(y = "Year",
        x='Year Excluded') +
-  facet_wrap(~source,
-             scales = 'free_x',
-             labeller = as_labeller(c("grid" = "Gridded", "statn" = "Station"))) +
+  # facet_wrap(~source,
+  #            scales = 'free_x',
+  #            labeller = as_labeller(c("grid" = "Gridded", 
+  #                                     "statn" = "Station"))) +
   theme(
-    axis.text.x = element_text(angle = 45, hjust = 1),
-    legend.position = 'bottom',
-    legend.text = element_text(size = 16),
-    legend.title = element_text(size = 16),  # Correct way to adjust legend title text
-    legend.key.width = unit(1, "cm"),
+    axis.text.x = element_text(angle = 45, 
+                               hjust = 1),
+    legend.position = 'none',
+    legend.text = element_text(size = 14),
+    legend.title = element_text(size = 14),
+    legend.key.width = unit(.75, "cm"),
     panel.grid = element_blank(),
@@
 
-ggsave('/Users/megansears/Documents/Repos/fourmile/figures/kge_heatmap.png',
+grid_kge_plot
+
+#003f5c
+#58508d
+#bc5090
+#ff6361
+#ffa600
+
+ggsave('/Users/megansears/Documents/Repos/fourmile/figures/kge_heatmap_grid.png',
+       dpi=600,
+       width = 10,
+       height = 6)
+
+```
+
+```{r}
+
+flow_plot_updated <- flow_plot_updated %>%
+  mutate(kge_revise_bins = cut(kge,
+                               breaks = c(-Inf, 0, 0.25, 0.5, 0.75, 1),
+                               include.lowest = TRUE,
+                               labels = c("< 0", "0-0.25", "0.25-0.5", "0.5-0.75", "0.75-1")))
+
+grid_kge_plot <- flow_plot_updated %>%
+  filter(source == 'grid') %>% 
+ggplot(., aes(x = year_excluded, 
+              y = year, 
+              fill = kge_revise_bins)) +
+  geom_tile(color = "white") +
+  # scale_fill_manual(values = color_palette) +
+paletteer::scale_fill_paletteer_d("PNWColors::Anemone") +
+  geom_text(aes(label = sprintf("%.2f", 
+                                kge)), 
+            color = "black", 
+            size = 3) +
+  theme_bw(base_size=20) +
+  theme(axis.text.x = element_text(angle = 45, 
+                                   hjust = 1)) +
+  labs(y = "Year",
+       x='Year Excluded',
+       fill = 'KGE') +
+  theme(
+    axis.text.x = element_text(angle = 45, 
+                               hjust = 1),
+    legend.position = 'bottom',
+    legend.text = element_text(size = 14),
+    legend.title = element_text(size = 14),
+    legend.key.width = unit(.75, "cm"),
+    panel.grid = element_blank(),
+    panel.background = element_rect(fill = "white"),
+    strip.background = element_blank(),
+    text = element_text(color = "black"),
+    axis.title = element_text(color = "black"),
+    axis.text = element_text(color = "black"),
+    plot.margin = margin(t = 0, r = 10, b = 10, l = 10),
+    legend.margin = margin(t = -8, b = -4, unit = "pt")
+  ) + ggtitle('a. Gridded')
+
+grid_kge_plot
+
+ggsave('/Users/megansears/Documents/Repos/fourmile/figures/kge_heatmap_grid_basic.png',
+       dpi=600,
+       width = 10,
+       height = 6)
+
+# mean_kge <- mean(flow_plot_updated$kge, na.rm = TRUE)
+# 
+# # Boxplot with mean line
+# boxplot_x <- flow_plot_updated %>%
+#   filter(source == "grid") %>%
+#   ggplot(aes(x=source, y = kge)) +
+#   geom_hline(yintercept = mean_kge, color = "black", linetype = "dashed", size = 0.5) +
+#   geom_boxplot(outliers=F, fill = "grey", color = "black") +
+#   theme_bw(base_size=16) +
+#   theme(
+#     panel.grid = element_blank(),
+#     panel.background = element_rect(fill = "white"),
+#     strip.background = element_blank(),
+#     text = element_text(color = "black"),
+#     axis.title = element_text(color = "black"),
+#     axis.text = element_text(color = "black"),
+#     axis.title.y = element_blank(),
+#     axis.title.x = element_blank(),
+#     axis.text.x = element_blank(),
+#     axis.ticks.x = element_blank(),
+#     plot.margin = margin(t = 10, r = 5, b = 76, l = 5)  # Adjust margins if necessary
+#   ) +
+#    scale_y_continuous(position = "right") 
+# 
+# boxplot_x
+# 
+# plot_grid(grid_kge_plot,boxplot_x, ncol = 2, 
+#           rel_widths = c(3, 0.75))
+# 
+# 
+# ggsave('/Users/megansears/Documents/Repos/fourmile/figures/kge_heatmap_grid.png',
+#        dpi=600,
+#        width = 10,
+#        height = 6)
+# 
+# ######
+# 
+# boxplot_yrex <- flow_plot_updated %>%
+#   filter(source == "grid") %>%
+#   ggplot(aes(x=year_excluded, y = kge)) +
+#   geom_boxplot(outliers=F, fill = "grey", 
+#                color = "black",
+#                width = 0.5) +
+#   theme_bw(base_size=20) +
+#   labs(y= 'KGE') +
+#   theme(
+#     panel.grid = element_blank(),
+#     panel.background = element_rect(fill = "white"),
+#     strip.background = element_blank(),
+#     text = element_text(color = "black"),
+#     axis.title = element_text(color = "black"),
+#     axis.text = element_text(color = "black"),
+#     #axis.title.y = element_blank(),
+#     axis.title.x = element_blank(),
+#     axis.text.x = element_blank(),
+#     axis.ticks.x = element_blank(),
+#     plot.margin = margin(t = 10, r = 10, b = 0, l = 24)  # Adjust margins if necessary
+#   )
+#   
+# boxplot_yrex
+# 
+# plot_grid(NULL, boxplot_yrex, NULL, grid_kge_plot, ncol = 1,
+#            rel_heights = c(0.1, 1, -0.00005, 2))
+# 
+# ggsave('/Users/megansears/Documents/Repos/fourmile/figures/kge_heatmap_grid_test.png',
+#        dpi=600,
+#        width = 10,
+#        height = 6)
+
+statn_kge_plot <- flow_plot_updated %>%
+  filter(source == 'statn') %>% 
+ggplot(., aes(x = year_excluded, 
+              y = year, 
+              fill = kge_revise_bins)) +
+  geom_tile(color = "white") +
+  facet_wrap(~source) +
+  # scale_fill_manual(values = color_palette) +
+paletteer::scale_fill_paletteer_d("PNWColors::Anemone") +
+  geom_text(aes(label = sprintf("%.2f", 
+                                kge)), 
+            color = "black", 
+            size = 3) +
+  theme_bw(base_size=20) +
+  theme(axis.text.x = element_text(angle = 45, 
+                                   hjust = 1)) +
+  labs(y = "Year",
+       x='Year Excluded',
+       fill = 'KGE') +
+  theme(
+    axis.text.x = element_text(angle = 45, 
+                               hjust = 1),
+    legend.position = 'bottom',
+    legend.text = element_text(size = 14),
+    legend.title = element_text(size = 14),
+    legend.key.width = unit(.75, "cm"),
+    panel.grid = element_blank(),
+    panel.background = element_rect(fill = "white"),
+    strip.background = element_blank(),
+    text = element_text(color = "black"),
+    axis.title = element_text(color = "black"),
+    axis.text = element_text(color = "black"),
+    plot.margin = margin(t = 10, r = 10, b = 10, l = 10),
+    legend.margin = margin(t = -8, b = -4, unit = "pt"),
+    # axis.title.y = element_blank(),
+    # axis.text.y = element_blank(),
+    # axis.ticks.y = element_blank()
+  )
+
+statn_kge_plot
+
+ggsave('/Users/megansears/Documents/Repos/fourmile/figures/kge_heatmap_statn_basic.png',
+       dpi=600,
+       width = 10,
+       height = 6)
+
+# facet wrap the plots
+new_facet_titles <- c(
+  "grid" = "Gridded",
+  "statn" = "Station"
+)
+
+both_kge_plot <- flow_plot_updated %>%
+  ggplot(., aes(x = year_excluded, 
+              y = year, 
+              fill = kge_revise_bins)) +
+  geom_tile(color = "white") +
+  facet_wrap(~source, labeller = labeller(source = new_facet_titles)) +
+paletteer::scale_fill_paletteer_d("PNWColors::Anemone") +
+  geom_text(aes(label = sprintf("%.2f", 
+                                kge)), 
+            color = "black", 
+            size = 3) +
+  theme_bw(base_size=18) +
+  theme(axis.text.x = element_text(angle = 45, 
+                                   hjust = 1)) +
+  labs(y = "Year",
+       x='Year excluded',
+       fill = 'KGE') +
+  theme(
+    axis.text.x = element_text(angle = 45, 
+                               hjust = 1),
+    legend.position = 'bottom',
+    legend.text = element_text(size = 14),
+    legend.title = element_text(size = 14),
+    legend.key.width = unit(.75, "cm"),
+    panel.grid = element_blank(),
+    panel.background = element_rect(fill = "white"),
+    strip.background = element_blank(),
+    text = element_text(color = "black"),
+    axis.title = element_text(color = "black"),
+    axis.text = element_text(color = "black"),
+    plot.margin = margin(t = 10, r = 10, b = 10, l = 10),
+    legend.margin = margin(t = -8, b = -4, unit = "pt"),
+    # axis.title.y = element_blank(),
+    # axis.text.y = element_blank(),
+    # axis.ticks.y = element_blank()
+  )
+
+both_kge_plot
+
+ggsave('/Users/megansears/Documents/Repos/fourmile/figures/kge_heatmap_both_basic.png',
        dpi=600,
@@
 pbias_all <- flow_pbias_all %>%
-  mutate(year = 'all years') %>%
+  mutate(year = 'All') %>%
   rename(model_run = name,
@@
   labs(y = "Year")
+
+####
+# pbias figure
+flow_plot_updated <- flow_plot_updated %>% 
+  mutate(source = case_when(
+    grepl("grid", model_run) ~ "grid",
+    grepl("statn", model_run) ~ "statn"),
+    year_excluded = str_extract(model_run, "\\d{4}$")) %>%
+  mutate(year_excluded = if_else(model_run %in% c('gridall',
+                                                       'statnall'),
+                                  'None', year_excluded))
+
+both_pbias_plot <- flow_plot_updated %>%
+  ggplot(., aes(x = year_excluded, 
+              y = year, 
+              fill = pbias)) +
+  geom_tile(color = "white") +
+  facet_wrap(~source, labeller = labeller(source = new_facet_titles)) +
+  #paletteer::scale_fill_paletteer_c("ggthemes::Gold-Purple Diverging") +
+  #paletteer::scale_fill_paletteer_c("grDevices::Red-Green") +
+  #paletteer::scale_fill_paletteer_c("grDevices::Purple-Green") +
+  paletteer::scale_fill_paletteer_c("grDevices::Green-Brown") +
+  #paletteer::scale_fill_paletteer_c("grDevices::Earth") +
+  geom_text(aes(label = sprintf("%.2f", 
+                                pbias)), 
+            color = "black", 
+            size = 2.75) +
+  theme_bw(base_size=18) +
+  theme(axis.text.x = element_text(angle = 45, 
+                                   hjust = 1)) +
+  labs(y = "Year",
+       x='Year excluded',
+       fill = 'Pbias') +
+  theme(
+    axis.text.x = element_text(angle = 45, 
+                               hjust = 1),
+    legend.position = 'bottom',
+    legend.text = element_text(size = 14),
+    legend.title = element_text(size = 14),
+    legend.key.width = unit(.75, "cm"),
+    panel.grid = element_blank(),
+    panel.background = element_rect(fill = "white"),
+    strip.background = element_blank(),
+    text = element_text(color = "black"),
+    axis.title = element_text(color = "black"),
+    axis.text = element_text(color = "black"),
+    plot.margin = margin(t = 10, r = 10, b = 10, l = 10),
+    legend.margin = margin(t = -8, b = -4, unit = "pt"),
+    # axis.title.y = element_blank(),
+    # axis.text.y = element_blank(),
+    # axis.ticks.y = element_blank()
+  )
+
+both_pbias_plot
+
+ggsave('/Users/megansears/Documents/Repos/fourmile/figures/pbias_heatmap_both_basic.png',
+       dpi=600,
+       width = 10,
+       height = 6)
 
@@
     axis.title = element_text(color = "black"),
-    axis.text = element_text(color = "black")
+    axis.text = element_text(color = "black"),
+    plot.margin = margin(t = 10, r = 20, b = 10, l = 10)
   )
@@
 ggsave('./figures/2015_flowcumulative.png',
-       dpi=600)
+       dpi=600,
+       width=14,
+       height=8)
 

### 2025-03-13 state_vars.Rmd
starting anova for water partition
looking at high and low HRUs

@@
 
-# High elevation HRU
+# High elevation HRU - old
 
@@
 
-statn_hi <- read_csv('./38HRU_sept2013_updates/HRU_18_statn.csv') %>% 
+statn_hi <- read_csv('./38HRU_dec2024_updates/HRU/statn_HRU_18.csv') %>% 
   mutate(date = mdy(time),
          source = 'statn') %>%
-  select(-time)
-
-grid_hi <- read_csv('./38HRU_sept2013_updates/HRU_18_grid.csv') %>%
+  dplyr::select(-time)
+
+grid_hi <- read_csv('./38HRU_dec2024_updates/HRU/grid_HRU_18.csv') %>%
   mutate(date = mdy(time),
          source = 'grid') %>%
-  select(-time)
+  dplyr::select(-time)
 
@@
 
-# Low elevation HRU
+# Low elevation HRU - old
 
@@
 ```
+
+# 2015 for low and high HRU
+
+```{r}
+
+statn_hi <- read_csv('./38HRU_dec2024_updates/HRU/statn_HRU_18.csv') %>% 
+  mutate(date = mdy(time),
+         source = 'statn') %>%
+  dplyr::select(-time)
+
+grid_hi <- read_csv('./38HRU_dec2024_updates/HRU/grid_HRU_18.csv') %>%
+  mutate(date = mdy(time),
+         source = 'grid') %>%
+  dplyr::select(-time)
+
+both_hi <- bind_rows(statn_hi, grid_hi) %>%
+  mutate(year = year(date),
+         month = month(date)) %>%
+  filter(year == 2015,
+         month %in% c(4,5,6))
+
+temp <- ggplot(both_hi, 
+               aes(date, 
+                   tmean,
+                   color = source)) +
+  geom_line() +
+  scale_color_manual(values = c("#0047AB", "orange"))
+
+ggplotly(temp)
+
+swe <- ggplot(both_hi, 
+               aes(date, 
+                   snowTotSWE,
+                   color = source)) +
+  geom_line() +
+  scale_color_manual(values = c("#0047AB", "orange"))
+
+ggplotly(swe)
+
+```
+
+```{r}
+
+statn_hi <- read_csv('./38HRU_dec2024_updates/HRU/statn_HRU_19.csv') %>% 
+  mutate(date = mdy(time),
+         source = 'statn') %>%
+  dplyr::select(-time)
+
+grid_hi <- read_csv('./38HRU_dec2024_updates/HRU/grid_HRU_19.csv') %>%
+  mutate(date = mdy(time),
+         source = 'grid') %>%
+  dplyr::select(-time)
+
+both_hi <- bind_rows(statn_hi, grid_hi) %>%
+  mutate(year = year(date),
+         month = month(date)) %>%
+  filter(year == 2015,
+         month %in% c(4,5,6))
+
+temp <- ggplot(both_hi, 
+               aes(date, 
+                   tmean,
+                   color = source)) +
+  geom_line() +
+  scale_color_manual(values = c("#0047AB", "orange"))
+
+ggplotly(temp)
+
+swe <- ggplot(both_hi, 
+               aes(date, 
+                   snowTotSWE,
+                   color = source)) +
+  geom_line() +
+  scale_color_manual(values = c("#0047AB", "orange"))
+
+ggplotly(swe)
+
+```
+
+# ANOVA for water partition
+
+```{r}
+
+flow <- both %>%
+  select(date, 
+         source, 
+         outRG1,
+         outRG2,
+         outRD1, 
+         outRD2,
+         source)
+
+rd1_model <- aov(outRD2 ~ source, data = flow)
+summary(rd1_model)
+
+```

### 2025-03-18 fourmile_output_dec2024.Rmd
updated flow partition and 2015 example figure

@@
 
-ggplot(example,
+example_yr <- ggplot(example,
        aes(x=date, y = flow_cms, color=source)) +
@@
   scale_color_manual(values = c("#0047AB", "orange")) +
+  scale_x_date(date_labels = "%b") +
   labs(x=element_blank(),
@@
   theme(
-    legend.position = c(0.94, 0.08),
+    legend.position = c(0.94, 0.1),
     legend.text = element_text(size = 12),
@@
   )
+
+example_yr
 
@@
 
-ggplot(gw_maxcumsum, aes(x = flow_type, y = flow_cms, fill = source)) +
+flow_box <- ggplot(gw_maxcumsum, aes(x = flow_type, y = flow_cms, fill = source)) +
   geom_boxplot(position = position_dodge(1),
@@
   theme(
-    legend.position = c(0.9, 0.38),
+    legend.position = c(0.93, 0.36),
     legend.text = element_text(size = 12),
@@
   scale_y_continuous(expand = expansion(mult = c(0.05, 0.15)))
+
+flow_box
 
@@
   theme(
-    legend.position = c(0.9, 0.38),
+    legend.position = c(0.94, 0.36),
     legend.text = element_text(size = 12),
@@
 
-ggsave('./figures/water_partition_boxplots.png',
-       dpi=600)
+flow_box
+
+# ggsave('./figures/water_partition_boxplots.png',
+#        dpi=600)
+
+# cowplot
+plot_grid(
+  flow_box,
+  example_yr,
+  ncol = 1,
+  labels = c("a", "b"),       # Add labels
+  label_size = 18,            # Optional: adjust the label size
+  label_fontface = "bold"     # Optional: make labels bold
+)
+
+ggsave('./figures/water_partition_combine.png',
+       dpi=600,
+       width=12,
+       height=12)
 

### 2025-03-18 state_vars.Rmd
created figure for high and low HRU - tmean & SWE

@@
 library(kableExtra)
+library(cowplot)
 
@@
 
-statn_hi <- read_csv('./38HRU_dec2024_updates/HRU/statn_HRU_19.csv') %>% 
+statn_low <- read_csv('./38HRU_dec2024_updates/HRU/statn_HRU_19.csv') %>% 
   mutate(date = mdy(time),
@@
 
-grid_hi <- read_csv('./38HRU_dec2024_updates/HRU/grid_HRU_19.csv') %>%
+grid_low <- read_csv('./38HRU_dec2024_updates/HRU/grid_HRU_19.csv') %>%
   mutate(date = mdy(time),
@@
 
-both_hi <- bind_rows(statn_hi, grid_hi) %>%
+both_low <- bind_rows(statn_low, grid_low) %>%
   mutate(year = year(date),
@@
 
-temp <- ggplot(both_hi, 
+temp <- ggplot(both_low, 
                aes(date, 
@@
 
-swe <- ggplot(both_hi, 
+swe <- ggplot(both_low, 
                aes(date, 
@@
 ggplotly(swe)
+
+## combine low and high together
+hi <- both_hi %>%
+  dplyr::select(tmean, snowTotSWE, source, date) %>%
+  mutate(elevation = 'High')
+
+low <- both_low %>%
+  dplyr::select(tmean, snowTotSWE, source, date) %>%
+  mutate(elevation = 'Low')
+
+both <- bind_rows(hi, low) %>%
+  mutate(elev_source =
+           case_when(source == 'statn' & elevation == 'High' ~ 'Station - High',
+                     source == 'statn' & elevation == 'Low' ~ 'Station - Low',
+                     source == 'grid' & elevation == 'High' ~ 'Gridded - High',
+                     source == 'grid' & elevation == 'Low' ~ 'Gridded - Low'))
+
+# figure
+tmean <- ggplot(both,
+       aes(x=date, y = tmean, 
+           color = elev_source,
+           linetype=elev_source)) +
+   geom_line(size=1, alpha=0.8) +  
+    scale_color_manual(values = c("Gridded - High" = "#0047AB", 
+                                  "Gridded - Low" = "#0047AB", 
+                                  "Station - High" = "orange",
+                                  "Station - Low" = "orange")) +
+  scale_linetype_manual(values = c("Gridded - High" = "dashed", 
+                                  "Gridded - Low" = "solid", 
+                                  "Station - High" = "dashed",
+                                  "Station - Low" = "solid")) + 
+  scale_x_date(date_labels = "%b") +
+  labs(x = element_blank(),
+       y = 'Mean temperature (°C)') +
+  theme_bw(base_size = 20) +
+  theme(legend.position = "none",
+    panel.grid = element_blank(),
+    panel.background = element_rect(fill = "white"),
+    strip.background = element_blank(),
+    text = element_text(color = "black"),
+    axis.title = element_text(color = "black"),
+    axis.text = element_text(color = "black"),
+    legend.key.width = unit(1, "cm")
+    #plot.margin = margin(t = 10, r = 20, b = 10, l = 10)
+  )
+
+swe <- ggplot(both,
+       aes(x=date, y = snowTotSWE, 
+           color = elev_source,
+           linetype=elev_source)) +
+   geom_line(size=1, alpha=0.8) +  
+    scale_color_manual(values = c("Gridded - High" = "#0047AB", 
+                                  "Gridded - Low" = "#0047AB", 
+                                  "Station - High" = "orange",
+                                  "Station - Low" = "orange")) +
+  scale_linetype_manual(values = c("Gridded - High" = "dashed", 
+                                  "Gridded - Low" = "solid", 
+                                  "Station - High" = "dashed",
+                                  "Station - Low" = "solid")) + 
+  scale_x_date(date_labels = "%b") +
+  #scale_y_log10() +
+  labs(x = element_blank(),
+       y = 'SWE (mm)') +
+  theme_bw(base_size = 20) +
+  theme(
+    legend.position = c(0.74, 0.85),
+    legend.text = element_text(size = 12),
+    legend.title = element_blank(),
+    panel.grid = element_blank(),
+    panel.background = element_rect(fill = "white"),
+    strip.background = element_blank(),
+    text = element_text(color = "black"),
+    axis.title = element_text(color = "black"),
+    axis.text = element_text(color = "black"),
+    legend.key.width = unit(1, "cm")
+    #plot.margin = margin(t = 10, r = 20, b = 10, l = 10)
+  )
+
+swe
+
+plot_grid(tmean, swe)
+
+ggsave('./figures/tmean_swe_2015.png',
+       width = 10,
+       height = 5,
+       dpi=600)
 

### 2025-03-20 fourmile_output_dec2024.Rmd
updated pbias fig so scale is centered on 0

@@
 
+### #### test
+# Compute max absolute value for symmetric limits
+max_abs <- max(abs(flow_plot_updated$pbias), na.rm = TRUE)
+
+both_pbias_plot <- flow_plot_updated %>%
+  ggplot(aes(x = year_excluded, 
+             y = year, 
+             fill = pbias)) +
+  geom_tile(color = "white") +
+  facet_wrap(~source, labeller = labeller(source = new_facet_titles)) +
+  paletteer::scale_fill_paletteer_c(
+    "grDevices::Green-Brown",
+    limits = c(-max_abs, max_abs),
+    oob = scales::squish
+  ) +
+  geom_text(aes(label = sprintf("%.2f", pbias)), 
+            color = "black", 
+            size = 2.75) +
+  theme_bw(base_size=18) +
+  theme(
+    axis.text.x = element_text(angle = 45, hjust = 1),
+    legend.position = 'bottom',
+    legend.text = element_text(size = 14),
+    legend.title = element_text(size = 14),
+    legend.key.width = unit(2, "cm"),
+    panel.grid = element_blank(),
+    panel.background = element_rect(fill = "white"),
+    strip.background = element_blank(),
+    text = element_text(color = "black"),
+    axis.title = element_text(color = "black"),
+    axis.text = element_text(color = "black"),
+    plot.margin = margin(t = 10, r = 10, b = 10, l = 10),
+    legend.margin = margin(t = -8, b = -4, unit = "pt")
+  ) +
+  labs(y = "Year",
+       x = 'Year excluded',
+       fill = 'Pbias')
+
+both_pbias_plot
+
+ggsave('/Users/megansears/Documents/Repos/fourmile/figures/pbias_heatmap_both_basic_0center.png',
+       dpi=600,
+       width = 10,
+       height = 6)
+
 ```

### 2025-03-25 burn_sev.Rmd
burn severity and snow persistence calcs

---
title: "burn_sev"
author: "Megan Sears"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}

library(stars)
library(tidyverse)
library(mapview)

```

```{r}

# for CPF only
dnbr <- read_stars('./data/GIS/co4005110538520100906_20100621_20110624_dnbr.tif')

burn_cat <- st_apply(dnbr, 1:2, function(x) case_when(
  x < -251  ~ 6,
  x > -250 & x < -101 ~ 7,
  x > -100 & x < 99 ~ 1,
  x > 100 & x < 269 ~ 2,
  x > 270 & x < 439 ~ 3,
  x > 440 & x < 659 ~ 4,
  x > 600 ~ 5,
))

sites <- st_read('/Users/megansears/Documents/Repos/fourmile/data/GIS/Fourmile Watershed.shp')

# need to add area to sites (only some sites have it calculated)
sites$area_m2 <- st_area(sites)

sites <- sites %>%  
  mutate(area_km2 = as.numeric(area_m2) / 1e6)

burn_cat <- st_transform(burn_cat, st_crs(sites))

burn_cat_poly <- st_as_sf(burn_cat, as_points = F, merge=F)

mapview(burn_cat_poly)

intersect <- st_intersection(burn_cat_poly, sites)

mapview(intersect)

intersect$area_m2 <- st_area(intersect)

intersect_summ <- intersect %>%
  group_by(co4005110538520100906_20100621_20110624_dnbr.tif) %>%
  summarize(sum_area = sum(area_m2)) %>%
  mutate(area_km2 = as.numeric(sum_area) / 1e6) %>%
  as.data.frame() %>% 
  dplyr::select(-geometry)

percents <- intersect_summ %>%
  mutate(frac_catchment = area_km2/67.2218) %>% 
  mutate(actual_percent = frac_catchment*100)

write_csv(intersect_summ, './data/final_model_inputs/cpf_burncat_percent.csv')

```

# snow persistence

```{r}

sp <- read_stars('/Users/megansears/Documents/Repos/fourmile/data/GIS/SP_mean.tif')

sites <- st_transform(sites, st_crs(sp))

sp <- st_crop(sp, sites)

mapview(sp) + mapview(sites)

sp <- sp %>%
  as.data.frame() %>%
  drop_na()

SP_cats <- sp %>%
  mutate(sp_ct = case_when(
  SP_mean.tif < 50 ~ "Int",
  SP_mean.tif < 75 ~ 'Trans',
  SP_mean.tif >= 75 ~ "Persis"
  )) %>%
  group_by(sp_ct) %>%
  summarize(count = n()) %>%
  mutate(frac = count/316)

```

### 2025-03-29 spatial_figs.Rmd
updated precip fig to only include summer

@@
 ```{r}
-grid <- read_csv("/Users/megansears/Documents/Repos/fourmile/38HRU_sept2013_updates/grid_all_Catchment.csv",
-                 skip=3) %>%
-   slice(3:n()) %>%
-  dplyr::select(-starts_with('@'),
-                -1) %>%
-  mutate(date = ymd(time)) %>%
-  dplyr::select(-time) %>%
-  mutate_if(is.character, as.numeric) %>% 
-  mutate(site = 'grid')
-
-statn <- read_csv('/Users/megansears/Documents/Repos/fourmile/38HRU_sept2013_updates/statn_all_Catchment.csv',
-                 skip=3) %>%
-   slice(3:n()) %>%
-  dplyr::select(-starts_with('@'),
-                -1) %>%
-  mutate(date = ymd(time)) %>%
-  dplyr::select(-time) %>%
-  mutate_if(is.character, as.numeric) %>% 
-  mutate(site = 'statn')
-
-all <- bind_rows(grid, statn) %>%
-  arrange(date)
-
-catchment_mo_mean <- all %>%
-  mutate(month = month(date)) %>%
-  group_by(site, month) %>%
-  summarise(across(precip:solRad, ~ mean(.x, na.rm = TRUE))) %>%
-  dplyr::select(site, month,
-                precip_mean = precip, tmean_mean = tmean, 
-                solrad_mean = solRad, rh_mean = rhum)
-
-catchment_mo_sd <- all %>%
-  mutate(month = month(date)) %>%
-  group_by(site, month) %>%
-  summarise(across(precip:solRad, ~ sd(.x, na.rm = TRUE))) %>%
-  dplyr::select(site, month,
-                precip_sd = precip, tmean_sd = tmean, 
-                solrad_sd = solRad, rh_sd = rhum)
-
-catchment_mo <- left_join(catchment_mo_mean, catchment_mo_sd, 
-                          by = c('month', 'site'))
-
-catchment_mo2 <- catchment_mo %>%
-  mutate(month_name = month.abb[month]) %>%
-  mutate(month_name = factor(month_name, 
-                             levels = c('Jan', 'Feb', 'Mar',
-                                        'Apr', 'May', 'Jun',
-                                        'Jul', 'Aug', 'Sep',
-                                        'Oct', 'Nov', 'Dec')))
-
-p_cols <- ggplot(catchment_mo2, aes(x = month_name, y = precip_mean,
-                                    color = site, fill = site)) +
-  geom_col(position = 'dodge') +
-  geom_errorbar(aes(ymin = 0, ymax = precip_mean + precip_sd), 
-                position = position_dodge(width = 0.6), width = 0.2) +
-  scale_color_manual(values = c("blue", "orange"),
-                     labels = c("Gridded", "Observed")) +  # Rename color legend items
-  scale_fill_manual(values = c("blue", "orange"),
-                    labels = c("Gridded", "Observed")) +   # Rename fill legend items
-  theme_bw(base_size = 20) +
-  labs(y = 'Precipitation (mm)',
-       x = element_blank()) +
-  guides(color = guide_legend(title = NULL),
-         fill = guide_legend(title = NULL)) +
-    theme(
-    panel.grid = element_blank(),
-    panel.background = element_rect(fill = "white"),
-    text = element_text(color = "black"),
-    axis.title = element_text(color = "black"),
-    axis.text = element_text(color = "black"),
-    strip.text = element_blank()
-  )
-
-p_cols
-
-ggsave("P.png", plot = p_cols, width = 8, height = 6, dpi = 300)
-
-# Temperature plot
-t_moplot <- ggplot(catchment_mo2, aes(x = month_name, y = tmean_mean, 
-                                      color = site, group = site)) +
-  geom_ribbon(aes(ymin = tmean_mean - tmean_sd, ymax = tmean_mean + tmean_sd, fill = site), alpha = 0.2) +
-  geom_line() +
-  geom_point() +
-  scale_color_manual(values = c("blue", "orange"),
-                     labels = c("Gridded", "Observed")) +  # Set line color to blue and orange and rename
-  scale_fill_manual(values = c("blue", "orange"),
-                    labels = c("Gridded", "Observed")) +   # Set ribbon fill color to blue and orange and rename
-  theme_bw(base_size=12) +
-  labs(y = expression("Mean temperature " ( degree~C)),
-       x = element_blank()) +
-  labs(color = NULL, fill = NULL)
-
-# Solar radiation plot
-sol_moplot <- ggplot(catchment_mo2, aes(x = month_name, y = solrad_mean, 
-                                         color = site, group = site)) +
-  geom_ribbon(aes(ymin = solrad_mean - solrad_sd, ymax = solrad_mean + solrad_sd, fill = site), alpha = 0.2) +
-  geom_line() +
-  geom_point() +
-  scale_color_manual(values = c("blue", "orange"),
-                     labels = c("Gridded", "Observed")) +  # Set line color to blue and orange and rename
-  scale_fill_manual(values = c("blue", "orange"),
-                    labels = c("Gridded", "Observed")) +   # Set ribbon fill color to blue and orange and rename
-  theme_bw(base_size = 12) +
-  labs(y = expression("Solar radiation (MJ/m"^"2" * ")"),
-       x = element_blank()) +
-  labs(color = NULL, fill = NULL)
-
-# Relative humidity plot
-rh_moplot <- ggplot(catchment_mo2, aes(x = month_name, y = rh_mean, 
-                                        color = site, group = site)) +
-  geom_ribbon(aes(ymin = rh_mean - rh_sd, ymax = rh_mean + rh_sd, fill = site), alpha = 0.2) +
-  geom_line() +
-  geom_point() +
-  scale_color_manual(values = c("blue", "orange"),
-                     labels = c("Gridded", "Observed")) +  # Set line color to blue and orange and rename
-  scale_fill_manual(values = c("blue", "orange"),
-                    labels = c("Gridded", "Observed")) +   # Set ribbon fill color to blue and orange and rename
-  theme_bw(base_size = 12) +
-  labs(y = 'RH (%)', x= element_blank()) +
-  labs(color = NULL, fill = NULL)
-
-# Print the plots
-t_moplot
-sol_moplot
-rh_moplot
-
+# grid <- read_csv("/Users/megansears/Documents/Repos/fourmile/38HRU_sept2013_updates/grid_all_Catchment.csv",
+#                  skip=3) %>%
+#    slice(3:n()) %>%
+#   dplyr::select(-starts_with('@'),
+#                 -1) %>%
+#   mutate(date = ymd(time)) %>%
+#   dplyr::select(-time) %>%
+#   mutate_if(is.character, as.numeric) %>% 
+#   mutate(site = 'grid')
+# 
+# statn <- read_csv('/Users/megansears/Documents/Repos/fourmile/38HRU_sept2013_updates/statn_all_Catchment.csv',
+#                  skip=3) %>%
+#    slice(3:n()) %>%
+#   dplyr::select(-starts_with('@'),
+#                 -1) %>%
+#   mutate(date = ymd(time)) %>%
+#   dplyr::select(-time) %>%
+#   mutate_if(is.character, as.numeric) %>% 
+#   mutate(site = 'statn')
+# 
+# all <- bind_rows(grid, statn) %>%
+#   arrange(date)
+# 
+# catchment_mo_mean <- all %>%
+#   mutate(month = month(date)) %>%
+#   group_by(site, month) %>%
+#   summarise(across(precip:solRad, ~ mean(.x, na.rm = TRUE))) %>%
+#   dplyr::select(site, month,
+#                 precip_mean = precip, tmean_mean = tmean, 
+#                 solrad_mean = solRad, rh_mean = rhum)
+# 
+# catchment_mo_sd <- all %>%
+#   mutate(month = month(date)) %>%
+#   group_by(site, month) %>%
+#   summarise(across(precip:solRad, ~ sd(.x, na.rm = TRUE))) %>%
+#   dplyr::select(site, month,
+#                 precip_sd = precip, tmean_sd = tmean, 
+#                 solrad_sd = solRad, rh_sd = rhum)
+# 
+# 
+# catchment_mo <- left_join(catchment_mo_mean, catchment_mo_sd, 
+#                           by = c('month', 'site'))
+# 
+# catchment_mo2 <- catchment_mo %>%
+#   mutate(month_name = month.abb[month]) %>%
+#   mutate(month_name = factor(month_name, 
+#                              levels = c('Jan', 'Feb', 'Mar',
+#                                         'Apr', 'May', 'Jun',
+#                                         'Jul', 'Aug', 'Sep',
+#                                         'Oct', 'Nov', 'Dec')))
+# 
+# 
+# p_cols <- catchment_mo2 %>% 
+#   filter(month_name %in% c('Jun','Jul','Aug', 'Sep')) %>%
+#   ggplot(., aes(x = month_name, y = precip_mean,
+#                                     color = site, fill = site)) +
+#   geom_col(position = 'dodge') +
+#   geom_errorbar(aes(ymin = 0, ymax = precip_mean + precip_sd), 
+#                 position = position_dodge(width = 0.6), width = 0.2) +
+#   scale_color_manual(values = c("blue", "orange"),
+#                      labels = c("Gridded", "Observed")) +  # Rename color legend items
+#   scale_fill_manual(values = c("blue", "orange"),
+#                     labels = c("Gridded", "Observed")) +   # Rename fill legend items
+#   theme_bw(base_size = 20) +
+#   labs(y = 'Precipitation (mm)',
+#        x = element_blank()) +
+#   guides(color = guide_legend(title = NULL),
+#          fill = guide_legend(title = NULL)) +
+#     theme(
+#     panel.grid = element_blank(),
+#     panel.background = element_rect(fill = "white"),
+#     text = element_text(color = "black"),
+#     axis.title = element_text(color = "black"),
+#     axis.text = element_text(color = "black"),
+#     strip.text = element_blank()
+#   ) 
+# 
+# 
+# p_cols
+# 
+# ggsave("P.png", plot = p_cols, width = 8, height = 6, dpi = 300)
+# 
+# # Temperature plot
 # t_moplot <- ggplot(catchment_mo2, aes(x = month_name, y = tmean_mean, 
@@
 #   geom_point() +
-#   theme_bw(base_size=14) +
+#   scale_color_manual(values = c("blue", "orange"),
+#                      labels = c("Gridded", "Observed")) +  # Set line color to blue and orange and rename
+#   scale_fill_manual(values = c("blue", "orange"),
+#                     labels = c("Gridded", "Observed")) +   # Set ribbon fill color to blue and orange and rename
+#   theme_bw(base_size=20) +
 #   labs(y = expression("Mean temperature " ( degree~C)),
-#        x = element_blank())
+#        x = element_blank()) +
+#    guides(color = guide_legend(title = NULL),
+#          fill = guide_legend(title = NULL)) +
+#     theme(
+#     panel.grid = element_blank(),
+#     panel.background = element_rect(fill = "white"),
+#     text = element_text(color = "black"),
+#     axis.title = element_text(color = "black"),
+#     axis.text = element_text(color = "black"),
+#     strip.text = element_blank()
+#   ) 
 # 
-# t_moplot
-# 
+# # Solar radiation plot
 # sol_moplot <- ggplot(catchment_mo2, aes(x = month_name, y = solrad_mean, 
@@
 #   geom_point() +
-#   theme_bw(base_size = 14) +
+#   scale_color_manual(values = c("blue", "orange"),
+#                      labels = c("Gridded", "Observed")) +  # Set line color to blue and orange and rename
+#   scale_fill_manual(values = c("blue", "orange"),
+#                     labels = c("Gridded", "Observed")) +   # Set ribbon fill color to blue and orange and rename
+#   theme_bw(base_size = 20) +
 #   labs(y = expression("Solar radiation (MJ/m"^"2" * ")"),
-#        x = element_blank()) 
+#        x = element_blank()) +
+#    guides(color = guide_legend(title = NULL),
+#          fill = guide_legend(title = NULL)) +
+#     theme(
+#     panel.grid = element_blank(),
+#     panel.background = element_rect(fill = "white"),
+#     text = element_text(color = "black"),
+#     axis.title = element_text(color = "black"),
+#     axis.text = element_text(color = "black"),
+#     strip.text = element_blank()
+#   ) 
 # 
-# sol_moplot
-# 
-# 
+# # Relative humidity plot
 # rh_moplot <- ggplot(catchment_mo2, aes(x = month_name, y = rh_mean, 
@@
 #   geom_point() +
-#   theme_bw(base_size = 14) +
-#   labs(y = 'RH (%)', x= element_blank()) 
+#   scale_color_manual(values = c("blue", "orange"),
+#                      labels = c("Gridded", "Observed")) +  # Set line color to blue and orange and rename
+#   scale_fill_manual(values = c("blue", "orange"),
+#                     labels = c("Gridded", "Observed")) +   # Set ribbon fill color to blue and orange and rename
+#   theme_bw(base_size = 20) +
+#   labs(y = 'RH (%)', x= element_blank()) +
+#    guides(color = guide_legend(title = NULL),
+#          fill = guide_legend(title = NULL)) +
+#     theme(
+#     panel.grid = element_blank(),
+#     panel.background = element_rect(fill = "white"),
+#     text = element_text(color = "black"),
+#     axis.title = element_text(color = "black"),
+#     axis.text = element_text(color = "black"),
+#     strip.text = element_blank()
+#   ) 
+# 
+# # Print the plots
+# t_moplot
+# sol_moplot
 # rh_moplot
-library(ggpubr)
-
-quad <- ggarrange(p_cols, 
-          t_moplot,
-          sol_moplot,
-          rh_moplot,
-          common.legend = T,
-          legend = 'bottom',
-          ncol=2,
-          nrow=2) 
-          #nrow = 4)
-          #ncol= 0)
-quad
-
-ggsave("./figures/quad.png", plot = quad, dpi = 600)
-
-quad_plus <- ggarrange(flow_plot,quad,
-                       nrow=2)
-quad_plus
-
-ggsave("./figures/quad_plus.png", plot = quad_plus, dpi = 600)
-
-```
-
-# difference - UPDATE file sources!!
-
-```{r}
-
-#grid first
-setwd("/Users/megansears/Documents/Repos/fourmile/38HRU_sept2013_updates/HRU_output/grid")
-
-read_ages_grid <- function(dataframe){
-  read_csv(dataframe, skip = 3) %>%
-  slice(3:n()) %>%
-  dplyr::select(-starts_with('@'),
-                -1) %>%
-  mutate(time = ymd(time)) %>%
-  mutate_if(is.character, as.numeric) %>%
-  mutate(source = 'grid')
-
-}
-
-#pull in all filenames with HRU in the name
-filenames <- list.files(".", pattern="HRU", full.names=F)
-
-#read all the csvs using read_ages function
-dataframes <- lapply(filenames, read_ages_grid)
-
-#name all the csvs based on first 6 characters
-names(dataframes) <- substr(filenames, 1, 6)
-
-#bind all and make 1 df
-hru_grids <- dataframes %>%
-  bind_rows()
-
-#statn next
-setwd("/Users/megansears/Documents/Repos/fourmile/38HRU_sept2013_updates/HRU_output/statn")
-
-read_ages_statn <- function(dataframe){
-  read_csv(dataframe, skip = 3) %>%
-  slice(3:n()) %>%
-  dplyr::select(-starts_with('@'),
-                -1) %>%
-  mutate(time = ymd(time)) %>%
-  mutate_if(is.character, as.numeric) %>%
-  mutate(source = 'statn')
-
-}
-
-#pull in all filenames with HRU in the name
-filenames <- list.files(".", pattern="HRU", full.names=F)
-
-#read all the csvs using read_ages function
-dataframes <- lapply(filenames, read_ages_statn)
-
-#name all the csvs based on first 6 characters
-names(dataframes) <- substr(filenames, 1, 6)
-
-#bind all and make 1 df
-hru_statn <- dataframes %>%
-  bind_rows()
-
-#get rid of a bunch of data
-hru_grid_tmean <- hru_grids %>%
-  dplyr::select(c(time, ID, tmean)) %>%
-  rename(tmean_grid = tmean)  %>%
-  group_by(ID) %>%
-  summarize(tmean_all_grid = mean(tmean_grid))
-
-hru_statn_tmean <- hru_statn %>%
-  dplyr::select(c(time, ID, tmean)) %>%
-  rename(tmean_statn = tmean) %>%
-  group_by(ID) %>%
-  summarize(tmean_all_statn = mean(tmean_statn))
-
-tmean_hrus <- left_join(hru_grid_tmean, hru_statn_tmean, by = c('ID')) %>%
-  mutate(diff = tmean_all_statn - tmean_all_grid) %>%
-  rename(value = ID)
-
-hrus_map_tmean <- left_join(hru_new, tmean_hrus, by = 'value')
-
-# T max
-#get rid of a bunch of data
-hru_grid_tmax <- hru_grids %>%
-  dplyr::select(c(time, ID, tmax)) %>%
-  rename(tmax_grid = tmax)  %>%
-  group_by(ID) %>%
-  summarize(tmax_all_grid = mean(tmax_grid))
-
-hru_statn_tmax <- hru_statn %>%
-  dplyr::select(c(time, ID, tmax)) %>%
-  rename(tmax_statn = tmax) %>%
-  group_by(ID) %>%
-  summarize(tmax_all_statn = mean(tmax_statn))
-
-tmax_hrus <- left_join(hru_grid_tmax, hru_statn_tmax, by = c('ID')) %>%
-  mutate(diff = tmax_all_statn - tmax_all_grid) %>%
-  rename(value = ID)
-
-hrus_map_tmax <- left_join(hru_new, tmax_hrus, by = 'value')
-
-# Tmin
-#get rid of a bunch of data
-hru_grid_tmin <- hru_grids %>%
-  dplyr::select(c(time, ID, tmin)) %>%
-  rename(tmin_grid = tmin)  %>%
-  group_by(ID) %>%
-  summarize(tmin_all_grid = mean(tmin_grid))
-
-hru_statn_tmin <- hru_statn %>%
-  dplyr::select(c(time, ID, tmin)) %>%
-  rename(tmin_statn = tmin) %>%
-  group_by(ID) %>%
-  summarize(tmin_all_statn = mean(tmin_statn))
-
-tmin_hrus <- left_join(hru_grid_tmin, hru_statn_tmin, by = c('ID')) %>%
-  mutate(diff = tmin_all_statn - tmin_all_grid) %>%
-  rename(value = ID)
-
-hrus_map_tmin <- left_join(hru_new, tmin_hrus, by = 'value')
-
-setwd("~/Documents/Repos/fourmile")
-
-# Cumulative p
-hru_grid_precip <- hru_grids %>%
-  dplyr::select(c(time, ID, precip)) %>%
-  rename(precip_grid = precip)
-
-hru_statn_precip <- hru_statn %>%
-  dplyr::select(c(time, ID, precip)) %>%
-  rename(precip_statn = precip)
-
-precip_hrus <- left_join(hru_grid_precip, hru_statn_precip, by = c('time', 'ID')) %>%
-  mutate(diff = precip_statn - precip_grid,
-         year = year(time)) %>%
-  group_by(year, ID) %>%
-  mutate(total_diff = cumsum(diff)) %>%
-  filter(time == max(time)) %>%
-  group_by(ID) %>%
-  summarize(precip_avg_cumdiff = mean(total_diff)) %>%
-  rename(value = ID)
-
-hrus_map_precip <- left_join(hru_new, precip_hrus, by = 'value')
-
-# solar rad
-hru_grid_solrad <- hru_grids %>%
-  dplyr::select(c(time, ID, solRad)) %>%
-  rename(solrad_grid = solRad)  %>%
-  group_by(ID) %>%
-  summarize(solrad_all_grid = mean(solrad_grid))
-
-hru_statn_solrad <- hru_statn %>%
-  dplyr::select(c(time, ID, solRad)) %>%
-  rename(solrad_statn = solRad) %>%
-  group_by(ID) %>%
-  summarize(solrad_all_statn = mean(solrad_statn))
-
-solrad_hrus <- left_join(hru_grid_solrad, hru_statn_solrad, by = c('ID')) %>%
-  mutate(diff = solrad_all_statn - solrad_all_grid) %>%
-  rename(value = ID)
-
-hrus_map_solrad <- left_join(hru_new, solrad_hrus, by = 'value')
-
-# RH
-#get rid of a bunch of data
-hru_grid_rh <- hru_grids %>%
-  dplyr::select(c(time, ID, rhum)) %>%
-  rename(rh_grid = rhum)  %>%
-  group_by(ID) %>%
-  summarize(rh_all_grid = mean(rh_grid))
-
-hru_statn_rh <- hru_statn %>%
-  dplyr::select(c(time, ID, rhum)) %>%
-  rename(rh_statn = rhum) %>%
-  group_by(ID) %>%
-  summarize(rh_all_statn = mean(rh_statn))
-
-rh_hrus <- left_join(hru_grid_rh, hru_statn_rh, by = c('ID')) %>%
-  mutate(diff = rh_all_statn - rh_all_grid) %>%
-  rename(value = ID)
-
-hrus_map_rh <- left_join(hru_new, rh_hrus, by = 'value')
-
-####
-rh <- ggplot() +
-  geom_sf(data = hrus_map_rh, aes(fill = diff), color = "black", lwd = 0.2) +
-  scale_fill_viridis_c(option = "viridis", name = "RH (%)") +
-  theme_bw(base_size=15.5) +
-  theme_void() + bottom_theme
-
-rh
-
-sr <- ggplot() +
-  geom_sf(data = hrus_map_solrad, aes(fill = diff), color = "black", lwd = 0.2) +
-  scale_fill_viridis_c(option = "cividis", name = expression("Srad (MJ/m"^"2" * ")")) +
-  theme_bw(base_size=15.5) +
-  theme_void() + top_theme
-
-sr
-
-precip <- ggplot() +
-  geom_sf(data = hrus_map_precip, aes(fill = precip_avg_cumdiff), color = "black", lwd = 0.2) +
-  scale_fill_viridis_c(option = "mako", name = "Cumulative P (mm)") +
-  theme_bw(base_size=15.5) +
-  theme_void() + top_theme
-
-precip
-
-tmean <- ggplot() +
-  geom_sf(data = hrus_map_tmean, aes(fill = diff), color = "black", lwd = 0.2) +
-  scale_fill_viridis_c(option = "plasma", name = "Tmean (°C)",
-                       limits = c(-5, 2)) +
-  theme_bw(base_size=15.5) +
-  theme_void() + bottom_theme
-
-tmean
-
-tmin <- ggplot() +
-  geom_sf(data = hrus_map_tmin, aes(fill = diff), color = "black", lwd = 0.2) +
-  scale_fill_viridis_c(option = "plasma", name = "Tmin (°C)",
-                       limits = c(-5, 2)) +
-  theme_bw(base_size=15.5) +
-  theme_void() + bottom_theme
-
-tmin
-
-tmax <- ggplot() +
-  geom_sf(data = hrus_map_tmax, aes(fill = diff), color = "black", lwd = 0.2) +
-  scale_fill_viridis_c(option = "plasma", name = "Tmax (°C)",
-                       limits = c(-5, 2)) +
-  theme_bw(base_size=15.5) +
-  theme_void() + bottom_theme
-
-tmax
-
-bottom_theme <-   theme(
-    legend.position = "bottom",
-    panel.grid.major = element_blank(),
-    legend.key.width = unit(.75, "cm"),
-    panel.grid.minor = element_blank(),
-    axis.title.x = element_blank(),
-    axis.title.y = element_blank(),
-    plot.margin = unit(c(-6, 0, 0, 0), "cm"), 
-    panel.spacing = unit(0, "lines"))
-
-top_theme <-   theme(
-    legend.position = "bottom",
-    panel.grid.major = element_blank(),
-    legend.key.width = unit(.75, "cm"),
-    panel.grid.minor = element_blank(),
-    axis.title.x = element_blank(),
-    axis.title.y = element_blank(),
-    plot.margin = unit(c(0, 0, -6, 0), "cm"), 
-    panel.spacing = unit(0, "lines"))
-
-lots <- ggarrange(
-  precip, sr, rh, tmean,
-  heights = 1)
-
-lots
-
-ggsave("./figures/diff_update2.png", plot = lots, dpi = 600)
-
-```
-
-# Pgrid vs Pstatn
-
-```{r}
-
-statn_catch <- read_csv('/Users/megansears/Documents/Repos/fourmile/38HRU_model/output/4milecreek38HRUs-statnall_#1/out/Catchment.csv',
-                        skip=3) %>%
-  slice(3:n()) %>%
-  dplyr::select(-starts_with('@'),
-                -1) %>%
-  mutate(time = ymd(time)) %>%
-  mutate_if(is.character, as.numeric) %>%
-  mutate(source = 'statn')
-
-grid_catch <- read_csv('/Users/megansears/Documents/Repos/fourmile/38HRU_model/output/4milecreek38HRUs-gridall_#1/out/Catchment.csv',
-                       skip=3) %>%
-  slice(3:n()) %>%
-  dplyr::select(-starts_with('@'),
-                -1) %>%
-  mutate(time = ymd(time)) %>%
-  mutate_if(is.character, as.numeric) %>%
-  mutate(source = 'grid')
-
-catchment_p <- bind_rows(statn_catch, grid_catch) %>%
-  dplyr::select(precip, time, source) %>%
-  pivot_wider(., names_from=source, values_from=precip)
-
-p_comp <- ggplot(catchment_p, aes(x=statn, y=grid)) + geom_point(size = 3) +
-  theme_bw(base_size=25) +
-  labs(x = 'Station precip (mm)',
-       y = 'Grid precip (mm)') +
-  geom_abline(slope = 1, intercept = 0, linetype = "dashed", color = "red")
-
-p_comp
-ggsave("./figures/p_compare.png", plot = p_comp, dpi = 600)
+# 
+# 
+# # t_moplot <- ggplot(catchment_mo2, aes(x = month_name, y = tmean_mean, 
+# #                                       color = site, group = site)) +
+# #   geom_ribbon(aes(ymin = tmean_mean - tmean_sd, ymax = tmean_mean + tmean_sd, fill = site), alpha = 0.2) +
+# #   geom_line() +
+# #   geom_point() +
+# #   theme_bw(base_size=14) +
+# #   labs(y = expression("Mean temperature " ( degree~C)),
+# #        x = element_blank())
+# # 
+# # t_moplot
+# # 
+# # sol_moplot <- ggplot(catchment_mo2, aes(x = month_name, y = solrad_mean, 
+# #                                       color = site, group = site)) +
+# #   geom_ribbon(aes(ymin = solrad_mean - solrad_sd, ymax = solrad_mean + solrad_sd, fill = site), alpha = 0.2) +
+# #   geom_line() +
+# #   geom_point() +
+# #   theme_bw(base_size = 14) +
+# #   labs(y = expression("Solar radiation (MJ/m"^"2" * ")"),
+# #        x = element_blank()) 
+# # 
+# # sol_moplot
+# # 
+# # 
+# # rh_moplot <- ggplot(catchment_mo2, aes(x = month_name, y = rh_mean, 
+# #                                       color = site, group = site)) +
+# #   geom_ribbon(aes(ymin = rh_mean - rh_sd, ymax = rh_mean + rh_sd, fill = site), alpha = 0.2) +
+# #   geom_line() +
+# #   geom_point() +
+# #   theme_bw(base_size = 14) +
+# #   labs(y = 'RH (%)', x= element_blank()) 
+# # rh_moplot
+# library(ggpubr)
+# 
+# quad <- ggarrange(p_cols, 
+#           t_moplot,
+#           sol_moplot,
+#           rh_moplot,
+#           common.legend = T,
+#           legend = 'bottom',
+#           ncol=2,
+#           nrow=2) 
+#           #nrow = 4)
+#           #ncol= 0)
+# quad
+# 
+# ggsave("./figures/quad.png", plot = quad, dpi = 600)
+# 
+# quad_plus <- ggarrange(flow_plot2,quad,
+#                        nrow=2)
+# quad_plus
+# 
+# ggsave("/Users/megansears/Documents/Repos/fourmile/figures/quad_plus_20250329.png", plot = quad_plus, dpi = 600)
+# 
+# 
+# ```
+# 
+# # difference - UPDATE file sources!!
+# 
+# ```{r}
+# 
+# #grid first
+# setwd("/Users/megansears/Documents/Repos/fourmile/38HRU_sept2013_updates/HRU_output/grid")
+# 
+# read_ages_grid <- function(dataframe){
+#   read_csv(dataframe, skip = 3) %>%
+#   slice(3:n()) %>%
+#   dplyr::select(-starts_with('@'),
+#                 -1) %>%
+#   mutate(time = ymd(time)) %>%
+#   mutate_if(is.character, as.numeric) %>%
+#   mutate(source = 'grid')
+# 
+# }
+# 
+# #pull in all filenames with HRU in the name
+# filenames <- list.files(".", pattern="HRU", full.names=F)
+# 
+# #read all the csvs using read_ages function
+# dataframes <- lapply(filenames, read_ages_grid)
+# 
+# #name all the csvs based on first 6 characters
+# names(dataframes) <- substr(filenames, 1, 6)
+# 
+# #bind all and make 1 df
+# hru_grids <- dataframes %>%
+#   bind_rows()
+# 
+# #statn next
+# setwd("/Users/megansears/Documents/Repos/fourmile/38HRU_sept2013_updates/HRU_output/statn")
+# 
+# read_ages_statn <- function(dataframe){
+#   read_csv(dataframe, skip = 3) %>%
+#   slice(3:n()) %>%
+#   dplyr::select(-starts_with('@'),
+#                 -1) %>%
+#   mutate(time = ymd(time)) %>%
+#   mutate_if(is.character, as.numeric) %>%
+#   mutate(source = 'statn')
+# 
+# }
+# 
+# #pull in all filenames with HRU in the name
+# filenames <- list.files(".", pattern="HRU", full.names=F)
+# 
+# #read all the csvs using read_ages function
+# dataframes <- lapply(filenames, read_ages_statn)
+# 
+# #name all the csvs based on first 6 characters
+# names(dataframes) <- substr(filenames, 1, 6)
+# 
+# #bind all and make 1 df
+# hru_statn <- dataframes %>%
+#   bind_rows()
+# 
+# #get rid of a bunch of data
+# hru_grid_tmean <- hru_grids %>%
+#   dplyr::select(c(time, ID, tmean)) %>%
+#   rename(tmean_grid = tmean)  %>%
+#   group_by(ID) %>%
+#   summarize(tmean_all_grid = mean(tmean_grid))
+# 
+# hru_statn_tmean <- hru_statn %>%
+#   dplyr::select(c(time, ID, tmean)) %>%
+#   rename(tmean_statn = tmean) %>%
+#   group_by(ID) %>%
+#   summarize(tmean_all_statn = mean(tmean_statn))
+# 
+# tmean_hrus <- left_join(hru_grid_tmean, hru_statn_tmean, by = c('ID')) %>%
+#   mutate(diff = tmean_all_statn - tmean_all_grid) %>%
+#   rename(value = ID)
+# 
+# hrus_map_tmean <- left_join(hru_new, tmean_hrus, by = 'value')
+# 
+# # T max
+# #get rid of a bunch of data
+# hru_grid_tmax <- hru_grids %>%
+#   dplyr::select(c(time, ID, tmax)) %>%
+#   rename(tmax_grid = tmax)  %>%
+#   group_by(ID) %>%
+#   summarize(tmax_all_grid = mean(tmax_grid))
+# 
+# hru_statn_tmax <- hru_statn %>%
+#   dplyr::select(c(time, ID, tmax)) %>%
+#   rename(tmax_statn = tmax) %>%
+#   group_by(ID) %>%
+#   summarize(tmax_all_statn = mean(tmax_statn))
+# 
+# tmax_hrus <- left_join(hru_grid_tmax, hru_statn_tmax, by = c('ID')) %>%
+#   mutate(diff = tmax_all_statn - tmax_all_grid) %>%
+#   rename(value = ID)
+# 
+# hrus_map_tmax <- left_join(hru_new, tmax_hrus, by = 'value')
+# 
+# 
+# # Tmin
+# #get rid of a bunch of data
+# hru_grid_tmin <- hru_grids %>%
+#   dplyr::select(c(time, ID, tmin)) %>%
+#   rename(tmin_grid = tmin)  %>%
+#   group_by(ID) %>%
+#   summarize(tmin_all_grid = mean(tmin_grid))
+# 
+# hru_statn_tmin <- hru_statn %>%
+#   dplyr::select(c(time, ID, tmin)) %>%
+#   rename(tmin_statn = tmin) %>%
+#   group_by(ID) %>%
+#   summarize(tmin_all_statn = mean(tmin_statn))
+# 
+# tmin_hrus <- left_join(hru_grid_tmin, hru_statn_tmin, by = c('ID')) %>%
+#   mutate(diff = tmin_all_statn - tmin_all_grid) %>%
+#   rename(value = ID)
+# 
+# hrus_map_tmin <- left_join(hru_new, tmin_hrus, by = 'value')
+# 
+# setwd("~/Documents/Repos/fourmile")
+# 
+# # Cumulative p
+# hru_grid_precip <- hru_grids %>%
+#   dplyr::select(c(time, ID, precip)) %>%
+#   rename(precip_grid = precip)
+# 
+# hru_statn_precip <- hru_statn %>%
+#   dplyr::select(c(time, ID, precip)) %>%
+#   rename(precip_statn = precip)
+# 
+# precip_hrus <- left_join(hru_grid_precip, hru_statn_precip, by = c('time', 'ID')) %>%
+#   mutate(diff = precip_statn - precip_grid,
+#          year = year(time)) %>%
+#   group_by(year, ID) %>%
+#   mutate(total_diff = cumsum(diff)) %>%
+#   filter(time == max(time)) %>%
+#   group_by(ID) %>%
+#   summarize(precip_avg_cumdiff = mean(total_diff)) %>%
+#   rename(value = ID)
+# 
+# hrus_map_precip <- left_join(hru_new, precip_hrus, by = 'value')
+# 
+# 
+# # solar rad
+# hru_grid_solrad <- hru_grids %>%
+#   dplyr::select(c(time, ID, solRad)) %>%
+#   rename(solrad_grid = solRad)  %>%
+#   group_by(ID) %>%
+#   summarize(solrad_all_grid = mean(solrad_grid))
+# 
+# hru_statn_solrad <- hru_statn %>%
+#   dplyr::select(c(time, ID, solRad)) %>%
+#   rename(solrad_statn = solRad) %>%
+#   group_by(ID) %>%
+#   summarize(solrad_all_statn = mean(solrad_statn))
+# 
+# solrad_hrus <- left_join(hru_grid_solrad, hru_statn_solrad, by = c('ID')) %>%
+#   mutate(diff = solrad_all_statn - solrad_all_grid) %>%
+#   rename(value = ID)
+# 
+# hrus_map_solrad <- left_join(hru_new, solrad_hrus, by = 'value')
+# 
+# 
+# # RH
+# #get rid of a bunch of data
+# hru_grid_rh <- hru_grids %>%
+#   dplyr::select(c(time, ID, rhum)) %>%
+#   rename(rh_grid = rhum)  %>%
+#   group_by(ID) %>%
+#   summarize(rh_all_grid = mean(rh_grid))
+# 
+# hru_statn_rh <- hru_statn %>%
+#   dplyr::select(c(time, ID, rhum)) %>%
+#   rename(rh_statn = rhum) %>%
+#   group_by(ID) %>%
+#   summarize(rh_all_statn = mean(rh_statn))
+# 
+# rh_hrus <- left_join(hru_grid_rh, hru_statn_rh, by = c('ID')) %>%
+#   mutate(diff = rh_all_statn - rh_all_grid) %>%
+#   rename(value = ID)
+# 
+# hrus_map_rh <- left_join(hru_new, rh_hrus, by = 'value')
+# 
+# ####
+# rh <- ggplot() +
+#   geom_sf(data = hrus_map_rh, aes(fill = diff), color = "black", lwd = 0.2) +
+#   scale_fill_viridis_c(option = "viridis", name = "RH (%)") +
+#   theme_bw(base_size=15.5) +
+#   theme_void() + bottom_theme
+# 
+# rh
+# 
+# sr <- ggplot() +
+#   geom_sf(data = hrus_map_solrad, aes(fill = diff), color = "black", lwd = 0.2) +
+#   scale_fill_viridis_c(option = "cividis", name = expression("Srad (MJ/m"^"2" * ")")) +
+#   theme_bw(base_size=15.5) +
+#   theme_void() + top_theme
+# 
+# 
+# sr
+# 
+# precip <- ggplot() +
+#   geom_sf(data = hrus_map_precip, aes(fill = precip_avg_cumdiff), color = "black", lwd = 0.2) +
+#   scale_fill_viridis_c(option = "mako", name = "Cumulative P (mm)") +
+#   theme_bw(base_size=15.5) +
+#   theme_void() + top_theme
+# 
+# precip
+# 
+# tmean <- ggplot() +
+#   geom_sf(data = hrus_map_tmean, aes(fill = diff), color = "black", lwd = 0.2) +
+#   scale_fill_viridis_c(option = "plasma", name = "Tmean (°C)",
+#                        limits = c(-5, 2)) +
+#   theme_bw(base_size=15.5) +
+#   theme_void() + bottom_theme
+# 
+# tmean
+# 
+# 
+# tmin <- ggplot() +
+#   geom_sf(data = hrus_map_tmin, aes(fill = diff), color = "black", lwd = 0.2) +
+#   scale_fill_viridis_c(option = "plasma", name = "Tmin (°C)",
+#                        limits = c(-5, 2)) +
+#   theme_bw(base_size=15.5) +
+#   theme_void() + bottom_theme
+# 
+# tmin
+# 
+# tmax <- ggplot() +
+#   geom_sf(data = hrus_map_tmax, aes(fill = diff), color = "black", lwd = 0.2) +
+#   scale_fill_viridis_c(option = "plasma", name = "Tmax (°C)",
+#                        limits = c(-5, 2)) +
+#   theme_bw(base_size=15.5) +
+#   theme_void() + bottom_theme
+#   
+# tmax
+# 
+# bottom_theme <-   theme(
+#     legend.position = "bottom",
+#     panel.grid.major = element_blank(),
+#     legend.key.width = unit(.75, "cm"),
+#     panel.grid.minor = element_blank(),
+#     axis.title.x = element_blank(),
+#     axis.title.y = element_blank(),
+#     plot.margin = unit(c(-6, 0, 0, 0), "cm"), 
+#     panel.spacing = unit(0, "lines"))
+# 
+# top_theme <-   theme(
+#     legend.position = "bottom",
+#     panel.grid.major = element_blank(),
+#     legend.key.width = unit(.75, "cm"),
+#     panel.grid.minor = element_blank(),
+#     axis.title.x = element_blank(),
+#     axis.title.y = element_blank(),
+#     plot.margin = unit(c(0, 0, -6, 0), "cm"), 
+#     panel.spacing = unit(0, "lines"))
+# 
+# 
+# lots <- ggarrange(
+#   precip, sr, rh, tmean,
+#   heights = 1)
+# 
+# 
+# lots
+# 
+# ggsave("./figures/diff_update2.png", plot = lots, dpi = 600)
+# 
+# ```
+# 
+# # Pgrid vs Pstatn
+# 
+# ```{r}
+# 
+# statn_catch <- read_csv('/Users/megansears/Documents/Repos/fourmile/38HRU_model/output/4milecreek38HRUs-statnall_#1/out/Catchment.csv',
+#                         skip=3) %>%
+#   slice(3:n()) %>%
+#   dplyr::select(-starts_with('@'),
+#                 -1) %>%
+#   mutate(time = ymd(time)) %>%
+#   mutate_if(is.character, as.numeric) %>%
+#   mutate(source = 'statn')
+# 
+# grid_catch <- read_csv('/Users/megansears/Documents/Repos/fourmile/38HRU_model/output/4milecreek38HRUs-gridall_#1/out/Catchment.csv',
+#                        skip=3) %>%
+#   slice(3:n()) %>%
+#   dplyr::select(-starts_with('@'),
+#                 -1) %>%
+#   mutate(time = ymd(time)) %>%
+#   mutate_if(is.character, as.numeric) %>%
+#   mutate(source = 'grid')
+#   
+# catchment_p <- bind_rows(statn_catch, grid_catch) %>%
+#   dplyr::select(precip, time, source) %>%
+#   pivot_wider(., names_from=source, values_from=precip)
+# 
+# p_comp <- ggplot(catchment_p, aes(x=statn, y=grid)) + geom_point(size = 3) +
+#   theme_bw(base_size=25) +
+#   labs(x = 'Station precip (mm)',
+#        y = 'Grid precip (mm)') +
+#   geom_abline(slope = 1, intercept = 0, linetype = "dashed", color = "red") 
+# 
+# p_comp
+# ggsave("./figures/p_compare.png", plot = p_comp, dpi = 600)
 
@@
 
-p_cols <- ggplot(catchment_mo2, aes(x = month_name, y = avg_p,
+p_cols <- catchment_mo2 %>% 
+  filter(month_name %in% c('Jun','Jul','Aug', 'Sep')) %>%
+  ggplot(., aes(x = month_name, y = avg_p,
                                     color = site, fill = site)) +
@@
 
-ggsave("/Users/megansears/Documents/Repos/fourmile/figures/quad.png", plot = quad, dpi = 600)
+ggsave("/Users/megansears/Documents/Repos/fourmile/figures/quad_20250329.png", plot = quad, dpi = 600)
+
+quad_plus <- ggarrange(flow_plot2,quad,
+                       nrow=2)
+quad_plus
+
+ggsave("/Users/megansears/Documents/Repos/fourmile/figures/quad_plus_20250329.png", plot = quad_plus, dpi = 600)
 

### 2025-03-31 spatial_figs.Rmd
climate diff figs

--- 2025-01-31 spatial_figs.Rmd
@@
 #   geom_point() +
-#   theme_bw(base_size = 14) +
-#   labs(y = 'RH (%)', x= element_blank()) 
+#   scale_color_manual(values = c("blue", "orange"),
+#                      labels = c("Gridded", "Observed")) +  # Set line color to blue and orange and rename
+#   scale_fill_manual(values = c("blue", "orange"),
+#                     labels = c("Gridded", "Observed")) +   # Set ribbon fill color to blue and orange and rename
+#   theme_bw(base_size = 20) +
+#   labs(y = 'RH (%)', x= element_blank()) +
+#    guides(color = guide_legend(title = NULL),
+#          fill = guide_legend(title = NULL)) +
+#     theme(
+#     panel.grid = element_blank(),
+#     panel.background = element_rect(fill = "white"),
+#     text = element_text(color = "black"),
+#     axis.title = element_text(color = "black"),
+#     axis.text = element_text(color = "black"),
+#     strip.text = element_blank()
+#   ) 
+# 
+# # Print the plots
+# t_moplot
+# sol_moplot
 # rh_moplot
-library(ggpubr)
-
-quad <- ggarrange(p_cols, 
-          t_moplot,
-          sol_moplot,
-          rh_moplot,
-          common.legend = T,
-          legend = 'bottom',
-          ncol=2,
-          nrow=2) 
-          #nrow = 4)
-          #ncol= 0)
-quad
-
-ggsave("./figures/quad.png", plot = quad, dpi = 600)
-
-quad_plus <- ggarrange(flow_plot,quad,
-                       nrow=2)
-quad_plus
-
-ggsave("./figures/quad_plus.png", plot = quad_plus, dpi = 600)
-
+# 
+# 
+# # t_moplot <- ggplot(catchment_mo2, aes(x = month_name, y = tmean_mean, 
+# #                                       color = site, group = site)) +
+# #   geom_ribbon(aes(ymin = tmean_mean - tmean_sd, ymax = tmean_mean + tmean_sd, fill = site), alpha = 0.2) +
+# #   geom_line() +
+# #   geom_point() +
+# #   theme_bw(base_size=14) +
+# #   labs(y = expression("Mean temperature " ( degree~C)),
+# #        x = element_blank())
+# # 
+# # t_moplot
+# # 
+# # sol_moplot <- ggplot(catchment_mo2, aes(x = month_name, y = solrad_mean, 
+# #                                       color = site, group = site)) +
+# #   geom_ribbon(aes(ymin = solrad_mean - solrad_sd, ymax = solrad_mean + solrad_sd, fill = site), alpha = 0.2) +
+# #   geom_line() +
+# #   geom_point() +
+# #   theme_bw(base_size = 14) +
+# #   labs(y = expression("Solar radiation (MJ/m"^"2" * ")"),
+# #        x = element_blank()) 
+# # 
+# # sol_moplot
+# # 
+# # 
+# # rh_moplot <- ggplot(catchment_mo2, aes(x = month_name, y = rh_mean, 
+# #                                       color = site, group = site)) +
+# #   geom_ribbon(aes(ymin = rh_mean - rh_sd, ymax = rh_mean + rh_sd, fill = site), alpha = 0.2) +
+# #   geom_line() +
+# #   geom_point() +
+# #   theme_bw(base_size = 14) +
+# #   labs(y = 'RH (%)', x= element_blank()) 
+# # rh_moplot
+# library(ggpubr)
+# 
+# quad <- ggarrange(p_cols, 
+#           t_moplot,
+#           sol_moplot,
+#           rh_moplot,
+#           common.legend = T,
+#           legend = 'bottom',
+#           ncol=2,
+#           nrow=2) 
+#           #nrow = 4)
+#           #ncol= 0)
+# quad
+# 
+# ggsave("./figures/quad.png", plot = quad, dpi = 600)
+# 
+# quad_plus <- ggarrange(flow_plot2,quad,
+#                        nrow=2)
+# quad_plus
+# 
+# ggsave("/Users/megansears/Documents/Repos/fourmile/figures/quad_plus_20250329.png", plot = quad_plus, dpi = 600)
+# 
+# 
 ```
 
-# difference - UPDATE file sources!!
+# HRU climate diff
 
@@
 ```{r}
-
-statn_catch <- read_csv('/Users/megansears/Documents/Repos/fourmile/38HRU_model/output/4milecreek38HRUs-statnall_#1/out/Catchment.csv',
-                        skip=3) %>%
-  slice(3:n()) %>%
-  dplyr::select(-starts_with('@'),
-                -1) %>%
-  mutate(time = ymd(time)) %>%
-  mutate_if(is.character, as.numeric) %>%
-  mutate(source = 'statn')
-
-grid_catch <- read_csv('/Users/megansears/Documents/Repos/fourmile/38HRU_model/output/4milecreek38HRUs-gridall_#1/out/Catchment.csv',
-                       skip=3) %>%
-  slice(3:n()) %>%
-  dplyr::select(-starts_with('@'),
-                -1) %>%
-  mutate(time = ymd(time)) %>%
-  mutate_if(is.character, as.numeric) %>%
-  mutate(source = 'grid')
-
-catchment_p <- bind_rows(statn_catch, grid_catch) %>%
-  dplyr::select(precip, time, source) %>%
-  pivot_wider(., names_from=source, values_from=precip)
-
-p_comp <- ggplot(catchment_p, aes(x=statn, y=grid)) + geom_point(size = 3) +
-  theme_bw(base_size=25) +
-  labs(x = 'Station precip (mm)',
-       y = 'Grid precip (mm)') +
-  geom_abline(slope = 1, intercept = 0, linetype = "dashed", color = "red")
-
-p_comp
-ggsave("./figures/p_compare.png", plot = p_comp, dpi = 600)
+#
+# statn_catch <- read_csv('/Users/megansears/Documents/Repos/fourmile/38HRU_model/output/4milecreek38HRUs-statnall_#1/out/Catchment.csv',
+#                         skip=3) %>%
+#   slice(3:n()) %>%
+#   dplyr::select(-starts_with('@'),
+#                 -1) %>%
+#   mutate(time = ymd(time)) %>%
+#   mutate_if(is.character, as.numeric) %>%
+#   mutate(source = 'statn')
+#
+# grid_catch <- read_csv('/Users/megansears/Documents/Repos/fourmile/38HRU_model/output/4milecreek38HRUs-gridall_#1/out/Catchment.csv',
+#                        skip=3) %>%
+#   slice(3:n()) %>%
+#   dplyr::select(-starts_with('@'),
+#                 -1) %>%
+#   mutate(time = ymd(time)) %>%
+#   mutate_if(is.character, as.numeric) %>%
+#   mutate(source = 'grid')
+#
+# catchment_p <- bind_rows(statn_catch, grid_catch) %>%
+#   dplyr::select(precip, time, source) %>%
+#   pivot_wider(., names_from=source, values_from=precip)
+#
+# p_comp <- ggplot(catchment_p, aes(x=statn, y=grid)) + geom_point(size = 3) +
+#   theme_bw(base_size=25) +
+#   labs(x = 'Station precip (mm)',
+#        y = 'Grid precip (mm)') +
+#   geom_abline(slope = 1, intercept = 0, linetype = "dashed", color = "red")
+#
+# p_comp
+# ggsave("./figures/p_compare.png", plot = p_comp, dpi = 600)
 

### 2025-04-04 flow_figs.Rmd
prepping for hydrograph fig

---
title: "hydrograph figures"
author: "Megan Sears"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(plotly)

```

```{r}

flow <- read_csv('./38HRU_dec2024_updates/discharge_all.csv') %>%
  replace(.==-9999, NA) %>%
  rename(date = time) %>%
  mutate(date = mdy(date))

flow_pivot <- flow %>%
  pivot_longer(!date, names_to = 'cal_run', values_to = 'q_m3s') %>%
  mutate(year = as.factor(year(date))) %>%
  filter(cal_run %in% c('grid_all',
                        'statn_all',
                        'obs'))

flowEg <- flow_pivot %>%
  filter(year %in% c(2012, 2016, 2017)) %>%
  ggplot(., aes(x=date,
                y=q_m3s, 
                color = cal_run)) +
  geom_line() +
  facet_wrap(~year,
             scales = 'free_x') +
  theme_bw(base_size=20)

flowEg

```

### 2025-04-04 spatial_figs.Rmd
getting HRU climate diff #s

@@
 ####
+
+bottom_theme <-   theme(
+    legend.position = "bottom",
+    panel.grid.major = element_blank(),
+    legend.key.width = unit(.75, "cm"),
+    panel.grid.minor = element_blank(),
+    axis.title.x = element_blank(),
+    axis.title.y = element_blank(),
+    plot.margin = unit(c(-6, 0, 0, 0), "cm"),
+    panel.spacing = unit(0, "lines"))
+
+top_theme <-   theme(
+    legend.position = "bottom",
+    panel.grid.major = element_blank(),
+    legend.key.width = unit(.75, "cm"),
+    panel.grid.minor = element_blank(),
+    axis.title.x = element_blank(),
+    axis.title.y = element_blank(),
+    plot.margin = unit(c(0, 0, -6, 0), "cm"),
+    panel.spacing = unit(0, "lines"))
+
 rh <- ggplot() +
@@
 tmax
-
-bottom_theme <-   theme(
-    legend.position = "bottom",
-    panel.grid.major = element_blank(),
-    legend.key.width = unit(.75, "cm"),
-    panel.grid.minor = element_blank(),
-    axis.title.x = element_blank(),
-    axis.title.y = element_blank(),
-    plot.margin = unit(c(-6, 0, 0, 0), "cm"),
-    panel.spacing = unit(0, "lines"))
-
-top_theme <-   theme(
-    legend.position = "bottom",
-    panel.grid.major = element_blank(),
-    legend.key.width = unit(.75, "cm"),
-    panel.grid.minor = element_blank(),
-    axis.title.x = element_blank(),
-    axis.title.y = element_blank(),
-    plot.margin = unit(c(0, 0, -6, 0), "cm"),
-    panel.spacing = unit(0, "lines"))
 
@@
 ggsave("/Users/megansears/Documents/Repos/fourmile/figures/flow_obs_plot2.png", dpi = 600, width = 12, height = 4, units = "in")
+
+ggplotly(flow_plot2)
+
+# annual total flow
+flowTotYr <- flow %>%
+  group_by(year) %>%
+  summarize(flow_tot = sum(obs, na.rm=T))
+
+avgAllYr <- mean(flowTotYr$flow_tot)
 

### 2025-04-04 fourmile_output_dec2024.Rmd
changed pbias and kge plots by categories

--- 2025-03-18 fourmile_output_dec2024.Rmd
@@
 
-# need to make separate plots bc can't put boxplots in margins for facet wrap
-grid_kge_plot <- flow_plot_updated %>%
-  filter(source == 'grid') %>% 
-ggplot(., aes(x = year_excluded, 
-              y = year, fill = 
-                kge_revise)) +
-  geom_tile(color = "white") +
-  scale_fill_viridis_c(option = "mako", 
-                       name = "KGE", 
-                       direction = -1) +
-  geom_text(aes(label = sprintf("%.2f", 
-                                kge_revise)), 
-            color = "grey", 
-            size = 2.5) +
-  theme_bw(base_size=20) +
-  theme(axis.text.x = element_text(angle = 45, 
-                                   hjust = 1)) +
-  labs(y = "Year",
-       x='Year Excluded') +
-  # facet_wrap(~source,
-  #            scales = 'free_x',
-  #            labeller = as_labeller(c("grid" = "Gridded", 
-  #                                     "statn" = "Station"))) +
-  theme(
-    axis.text.x = element_text(angle = 45, 
-                               hjust = 1),
-    legend.position = 'none',
-    legend.text = element_text(size = 14),
-    legend.title = element_text(size = 14),
-    legend.key.width = unit(.75, "cm"),
-    panel.grid = element_blank(),
-    panel.background = element_rect(fill = "white"),
-    strip.background = element_blank(),
-    text = element_text(color = "black"),
-    axis.title = element_text(color = "black"),
-    axis.text = element_text(color = "black")
-  )
-
-grid_kge_plot
-
-#003f5c
-#58508d
-#bc5090
-#ff6361
-#ffa600
-
-ggsave('/Users/megansears/Documents/Repos/fourmile/figures/kge_heatmap_grid.png',
-       dpi=600,
-       width = 10,
-       height = 6)
+# # need to make separate plots bc can't put boxplots in margins for facet wrap
+# grid_kge_plot <- flow_plot_updated %>%
+#   filter(source == 'grid') %>% 
+# ggplot(., aes(x = year_excluded, 
+#               y = year, fill = 
+#                 kge_revise)) +
+#   geom_tile(color = "white") +
+#   scale_fill_viridis_c(option = "mako", 
+#                        name = "KGE", 
+#                        direction = -1) +
+#   geom_text(aes(label = sprintf("%.2f", 
+#                                 kge_revise)), 
+#             color = "grey", 
+#             size = 2.5) +
+#   theme_bw(base_size=20) +
+#   theme(axis.text.x = element_text(angle = 45, 
+#                                    hjust = 1)) +
+#   labs(y = "Year",
+#        x='Year Excluded') +
+#   # facet_wrap(~source,
+#   #            scales = 'free_x',
+#   #            labeller = as_labeller(c("grid" = "Gridded", 
+#   #                                     "statn" = "Station"))) +
+#   theme(
+#     axis.text.x = element_text(angle = 45, 
+#                                hjust = 1),
+#     legend.position = 'none',
+#     legend.text = element_text(size = 14),
+#     legend.title = element_text(size = 14),
+#     legend.key.width = unit(.75, "cm"),
+#     panel.grid = element_blank(),
+#     panel.background = element_rect(fill = "white"),
+#     strip.background = element_blank(),
+#     text = element_text(color = "black"),
+#     axis.title = element_text(color = "black"),
+#     axis.text = element_text(color = "black")
+#   ) 
+# 
+# grid_kge_plot
+# 
+# 
+# 
+# #003f5c
+# #58508d
+# #bc5090
+# #ff6361
+# #ffa600
+# 
+# ggsave('/Users/megansears/Documents/Repos/fourmile/figures/kge_heatmap_grid.png',
+#        dpi=600,
+#        width = 10,
+#        height = 6)
 
@@
   mutate(kge_revise_bins = cut(kge,
-                               breaks = c(-Inf, 0, 0.25, 0.5, 0.75, 1),
+                               breaks = c(-Inf, 0.2, 0.4, 0.6, 0.8, 1),
                                include.lowest = TRUE,
-                               labels = c("< 0", "0-0.25", "0.25-0.5", "0.5-0.75", "0.75-1")))
-
-grid_kge_plot <- flow_plot_updated %>%
-  filter(source == 'grid') %>% 
-ggplot(., aes(x = year_excluded, 
-              y = year, 
-              fill = kge_revise_bins)) +
-  geom_tile(color = "white") +
-  # scale_fill_manual(values = color_palette) +
-paletteer::scale_fill_paletteer_d("PNWColors::Anemone") +
-  geom_text(aes(label = sprintf("%.2f", 
-                                kge)), 
-            color = "black", 
-            size = 3) +
-  theme_bw(base_size=20) +
-  theme(axis.text.x = element_text(angle = 45, 
-                                   hjust = 1)) +
-  labs(y = "Year",
-       x='Year Excluded',
-       fill = 'KGE') +
-  theme(
-    axis.text.x = element_text(angle = 45, 
-                               hjust = 1),
-    legend.position = 'bottom',
-    legend.text = element_text(size = 14),
-    legend.title = element_text(size = 14),
-    legend.key.width = unit(.75, "cm"),
-    panel.grid = element_blank(),
-    panel.background = element_rect(fill = "white"),
-    strip.background = element_blank(),
-    text = element_text(color = "black"),
-    axis.title = element_text(color = "black"),
-    axis.text = element_text(color = "black"),
-    plot.margin = margin(t = 0, r = 10, b = 10, l = 10),
-    legend.margin = margin(t = -8, b = -4, unit = "pt")
-  ) + ggtitle('a. Gridded')
-
-grid_kge_plot
-
-ggsave('/Users/megansears/Documents/Repos/fourmile/figures/kge_heatmap_grid_basic.png',
-       dpi=600,
-       width = 10,
-       height = 6)
+                               labels = c("< 0.0", "0.2-0.4", "0.4-0.6", "0.6-0.8", "> 0.8")))
+
+# grid_kge_plot <- flow_plot_updated %>%
+#   filter(source == 'grid') %>% 
+# ggplot(., aes(x = year_excluded, 
+#               y = year, 
+#               fill = kge_revise_bins)) +
+#   geom_tile(color = "white") +
+#   # scale_fill_manual(values = color_palette) +
+# paletteer::scale_fill_paletteer_d("PNWColors::Anemone") +
+#   geom_text(aes(label = sprintf("%.2f", 
+#                                 kge)), 
+#             color = "black", 
+#             size = 3) +
+#   theme_bw(base_size=20) +
+#   theme(axis.text.x = element_text(angle = 45, 
+#                                    hjust = 1)) +
+#   labs(y = "Year",
+#        x='Year Excluded',
+#        fill = 'KGE') +
+#   theme(
+#     axis.text.x = element_text(angle = 45, 
+#                                hjust = 1),
+#     legend.position = 'bottom',
+#     legend.text = element_text(size = 14),
+#     legend.title = element_text(size = 14),
+#     legend.key.width = unit(.75, "cm"),
+#     panel.grid = element_blank(),
+#     panel.background = element_rect(fill = "white"),
+#     strip.background = element_blank(),
+#     text = element_text(color = "black"),
+#     axis.title = element_text(color = "black"),
+#     axis.text = element_text(color = "black"),
+#     plot.margin = margin(t = 0, r = 10, b = 10, l = 10),
+#     legend.margin = margin(t = -8, b = -4, unit = "pt")
+#   ) + ggtitle('a. Gridded')
+# 
+# grid_kge_plot
+# 
+# ggsave('/Users/megansears/Documents/Repos/fourmile/figures/kge_heatmap_grid_basic.png',
+#        dpi=600,
+#        width = 10,
+#        height = 6)
 
@@
 #        height = 6)
-
-statn_kge_plot <- flow_plot_updated %>%
-  filter(source == 'statn') %>% 
-ggplot(., aes(x = year_excluded, 
-              y = year, 
-              fill = kge_revise_bins)) +
-  geom_tile(color = "white") +
-  facet_wrap(~source) +
-  # scale_fill_manual(values = color_palette) +
-paletteer::scale_fill_paletteer_d("PNWColors::Anemone") +
-  geom_text(aes(label = sprintf("%.2f", 
-                                kge)), 
-            color = "black", 
-            size = 3) +
-  theme_bw(base_size=20) +
-  theme(axis.text.x = element_text(angle = 45, 
-                                   hjust = 1)) +
-  labs(y = "Year",
-       x='Year Excluded',
-       fill = 'KGE') +
-  theme(
-    axis.text.x = element_text(angle = 45, 
-                               hjust = 1),
-    legend.position = 'bottom',
-    legend.text = element_text(size = 14),
-    legend.title = element_text(size = 14),
-    legend.key.width = unit(.75, "cm"),
-    panel.grid = element_blank(),
-    panel.background = element_rect(fill = "white"),
-    strip.background = element_blank(),
-    text = element_text(color = "black"),
-    axis.title = element_text(color = "black"),
-    axis.text = element_text(color = "black"),
-    plot.margin = margin(t = 10, r = 10, b = 10, l = 10),
-    legend.margin = margin(t = -8, b = -4, unit = "pt"),
-    # axis.title.y = element_blank(),
-    # axis.text.y = element_blank(),
-    # axis.ticks.y = element_blank()
-  )
-
-statn_kge_plot
-
-ggsave('/Users/megansears/Documents/Repos/fourmile/figures/kge_heatmap_statn_basic.png',
-       dpi=600,
-       width = 10,
-       height = 6)
+# 
+# statn_kge_plot <- flow_plot_updated %>%
+#   filter(source == 'statn') %>% 
+# ggplot(., aes(x = year_excluded, 
+#               y = year, 
+#               fill = kge_revise_bins)) +
+#   geom_tile(color = "white") +
+#   facet_wrap(~source) +
+#   # scale_fill_manual(values = color_palette) +
+# paletteer::scale_fill_paletteer_d("PNWColors::Anemone") +
+#   geom_text(aes(label = sprintf("%.2f", 
+#                                 kge)), 
+#             color = "black", 
+#             size = 3) +
+#   theme_bw(base_size=20) +
+#   theme(axis.text.x = element_text(angle = 45, 
+#                                    hjust = 1)) +
+#   labs(y = "Year",
+#        x='Year Excluded',
+#        fill = 'KGE') +
+#   theme(
+#     axis.text.x = element_text(angle = 45, 
+#                                hjust = 1),
+#     legend.position = 'bottom',
+#     legend.text = element_text(size = 14),
+#     legend.title = element_text(size = 14),
+#     legend.key.width = unit(.75, "cm"),
+#     panel.grid = element_blank(),
+#     panel.background = element_rect(fill = "white"),
+#     strip.background = element_blank(),
+#     text = element_text(color = "black"),
+#     axis.title = element_text(color = "black"),
+#     axis.text = element_text(color = "black"),
+#     plot.margin = margin(t = 10, r = 10, b = 10, l = 10),
+#     legend.margin = margin(t = -8, b = -4, unit = "pt"),
+#     # axis.title.y = element_blank(),
+#     # axis.text.y = element_blank(),
+#     # axis.ticks.y = element_blank()
+#   )
+# 
+# statn_kge_plot
+# 
+# ggsave('/Users/megansears/Documents/Repos/fourmile/figures/kge_heatmap_statn_basic.png',
+#        dpi=600,
+#        width = 10,
+#        height = 6)
 
@@
 
+#####################
+kgeCats <- flow_plot_updated %>%
+  mutate(pbiasCat = case_when(
+    abs(pbias) < 10 ~ 'Very good',
+    abs(pbias) >= 10 & abs(pbias) < 15 ~ 'Good',
+    abs(pbias) >= 15 & abs(pbias) < 25 ~ 'Satisfactory',
+    abs(pbias) >= 25 ~ 'Unsatisfactory'),
+    pbiasCat = factor(pbiasCat, levels = c("Unsatisfactory", 
+                                           "Satisfactory", 
+                                           "Good", 
+                                           "Very good")))
+
+both_pbias_plot <- pbiasCats %>%
+  ggplot(aes(x = year_excluded, 
+             y = year, 
+             fill = pbiasCat)) +
+  geom_tile(color = "white") +
+  facet_wrap(~source, labeller = labeller(source = new_facet_titles)) +
+  # paletteer::scale_fill_paletteer_c(
+  #   "grDevices::Green-Brown",
+  #   limits = c(-max_abs, max_abs),
+  #   oob = scales::squish
+  # ) +
+  paletteer::scale_fill_paletteer_d("calecopal::lupinus") +
+  geom_text(aes(label = sprintf("%.2f", pbias)), 
+            color = "black", 
+            size = 2.75) +
+  theme_bw(base_size=18) +
+  theme(
+    axis.text.x = element_text(angle = 45, hjust = 1),
+    legend.position = 'bottom',
+    legend.text = element_text(size = 14),
+    legend.title = element_text(size = 14),
+    legend.key.width = unit(1, "cm"),
+    panel.grid = element_blank(),
+    panel.background = element_rect(fill = "white"),
+    strip.background = element_blank(),
+    text = element_text(color = "black"),
+    axis.title = element_text(color = "black"),
+    axis.text = element_text(color = "black"),
+    plot.margin = margin(t = 10, r = 10, b = 10, l = 10),
+    legend.margin = margin(t = -8, b = -4, unit = "pt")
+  ) +
+  labs(y = "Year",
+       x = 'Year excluded',
+       fill = '% bias')
+
+both_pbias_plot
+
+ggsave('/Users/megansears/Documents/Repos/fourmile/figures/pbias_heatmap_both_cats.png',
+       dpi=600,
+       width = 10,
+       height = 6)
+
 ```
@@
 
-both_pbias_plot <- flow_plot_updated %>%
-  ggplot(., aes(x = year_excluded, 
+# both_pbias_plot <- flow_plot_updated %>%
+#   ggplot(., aes(x = year_excluded, 
+#               y = year, 
+#               fill = pbias)) +
+#   geom_tile(color = "white") +
+#   facet_wrap(~source, labeller = labeller(source = new_facet_titles)) +
+#   #paletteer::scale_fill_paletteer_c("ggthemes::Gold-Purple Diverging") +
+#   #paletteer::scale_fill_paletteer_c("grDevices::Red-Green") +
+#   #paletteer::scale_fill_paletteer_c("grDevices::Purple-Green") +
+#   paletteer::scale_fill_paletteer_c("grDevices::Green-Brown") +
+#   #paletteer::scale_fill_paletteer_c("grDevices::Earth") +
+#   geom_text(aes(label = sprintf("%.2f", 
+#                                 pbias)), 
+#             color = "black", 
+#             size = 2.75) +
+#   theme_bw(base_size=18) +
+#   theme(axis.text.x = element_text(angle = 45, 
+#                                    hjust = 1)) +
+#   labs(y = "Year",
+#        x='Year excluded',
+#        fill = 'Pbias') +
+#   theme(
+#     axis.text.x = element_text(angle = 45, 
+#                                hjust = 1),
+#     legend.position = 'bottom',
+#     legend.text = element_text(size = 14),
+#     legend.title = element_text(size = 14),
+#     legend.key.width = unit(.75, "cm"),
+#     panel.grid = element_blank(),
+#     panel.background = element_rect(fill = "white"),
+#     strip.background = element_blank(),
+#     text = element_text(color = "black"),
+#     axis.title = element_text(color = "black"),
+#     axis.text = element_text(color = "black"),
+#     plot.margin = margin(t = 10, r = 10, b = 10, l = 10),
+#     legend.margin = margin(t = -8, b = -4, unit = "pt"),
+#     # axis.title.y = element_blank(),
+#     # axis.text.y = element_blank(),
+#     # axis.ticks.y = element_blank()
+#   )
+# 
+# both_pbias_plot
+# 
+# ggsave('/Users/megansears/Documents/Repos/fourmile/figures/pbias_heatmap_both_basic.png',
+#        dpi=600,
+#        width = 10,
+#        height = 6)
+
+# Compute max absolute value for symmetric limits
+# put pbias into categories
+pbiasCats <- flow_plot_updated %>%
+  mutate(pbiasCat = case_when(
+    abs(pbias) < 10 ~ 'Very good',
+    abs(pbias) >= 10 & abs(pbias) < 15 ~ 'Good',
+    abs(pbias) >= 15 & abs(pbias) < 25 ~ 'Satisfactory',
+    abs(pbias) >= 25 ~ 'Unsatisfactory'),
+    pbiasCat = factor(pbiasCat, levels = c("Unsatisfactory", 
+                                           "Satisfactory", 
+                                           "Good", 
+                                           "Very good")))
+
+both_pbias_plot <- pbiasCats %>%
+  ggplot(aes(x = year_excluded, 
              y = year, 
-              fill = pbias)) +
+             fill = pbiasCat)) +
   geom_tile(color = "white") +
   facet_wrap(~source, labeller = labeller(source = new_facet_titles)) +
-  #paletteer::scale_fill_paletteer_c("ggthemes::Gold-Purple Diverging") +
-  #paletteer::scale_fill_paletteer_c("grDevices::Red-Green") +
-  #paletteer::scale_fill_paletteer_c("grDevices::Purple-Green") +
-  paletteer::scale_fill_paletteer_c("grDevices::Green-Brown") +
-  #paletteer::scale_fill_paletteer_c("grDevices::Earth") +
-  geom_text(aes(label = sprintf("%.2f", 
-                                pbias)), 
+  # paletteer::scale_fill_paletteer_c(
+  #   "grDevices::Green-Brown",
+  #   limits = c(-max_abs, max_abs),
+  #   oob = scales::squish
+  # ) +
+  paletteer::scale_fill_paletteer_d("calecopal::lupinus") +
+  #paletteer::scale_fill_paletteer_d("PNWColors::Anemone") +
+  geom_text(aes(label = sprintf("%.2f", pbias)), 
             color = "black", 
@@
   theme_bw(base_size=18) +
-  theme(axis.text.x = element_text(angle = 45, 
-                                   hjust = 1)) +
-  labs(y = "Year",
-       x='Year excluded',
-       fill = 'Pbias') +
   theme(
-    axis.text.x = element_text(angle = 45, 
-                               hjust = 1),
+    axis.text.x = element_text(angle = 45, hjust = 1),
     legend.position = 'bottom',
@@
     legend.title = element_text(size = 14),
-    legend.key.width = unit(.75, "cm"),
+    legend.key.width = unit(1, "cm"),
     panel.grid = element_blank(),
@@
     plot.margin = margin(t = 10, r = 10, b = 10, l = 10),
-    legend.margin = margin(t = -8, b = -4, unit = "pt"),
-    # axis.title.y = element_blank(),
-    # axis.text.y = element_blank(),
-    # axis.ticks.y = element_blank()
-  )
+    legend.margin = margin(t = -8, b = -4, unit = "pt")
+  ) +
+  labs(y = "Year",
+       x = 'Year excluded',
+       fill = '% bias')
 
@@
 
-ggsave('/Users/megansears/Documents/Repos/fourmile/figures/pbias_heatmap_both_basic.png',
+ggsave('/Users/megansears/Documents/Repos/fourmile/figures/pbias_heatmap_both_cats.png',
+       dpi=600,
+       width = 10,
+       height = 6)
+
+# max_abs <- max(abs(flow_plot_updated$pbias), na.rm = TRUE)
+# 
+# both_pbias_plot <- flow_plot_updated %>%
+#   ggplot(aes(x = year_excluded, 
+#              y = year, 
+#              fill = pbias)) +
+#   geom_tile(color = "white") +
+#   facet_wrap(~source, labeller = labeller(source = new_facet_titles)) +
+#   paletteer::scale_fill_paletteer_c(
+#     "grDevices::Green-Brown",
+#     limits = c(-max_abs, max_abs),
+#     oob = scales::squish
+#   ) +
+#   geom_text(aes(label = sprintf("%.2f", pbias)), 
+#             color = "black", 
+#             size = 2.75) +
+#   theme_bw(base_size=18) +
+#   theme(
+#     axis.text.x = element_text(angle = 45, hjust = 1),
+#     legend.position = 'bottom',
+#     legend.text = element_text(size = 14),
+#     legend.title = element_text(size = 14),
+#     legend.key.width = unit(2, "cm"),
+#     panel.grid = element_blank(),
+#     panel.background = element_rect(fill = "white"),
+#     strip.background = element_blank(),
+#     text = element_text(color = "black"),
+#     axis.title = element_text(color = "black"),
+#     axis.text = element_text(color = "black"),
+#     plot.margin = margin(t = 10, r = 10, b = 10, l = 10),
+#     legend.margin = margin(t = -8, b = -4, unit = "pt")
+#   ) +
+#   labs(y = "Year",
+#        x = 'Year excluded',
+#        fill = 'Pbias')
+# 
+# both_pbias_plot
+
+ggsave('/Users/megansears/Documents/Repos/fourmile/figures/pbias_heatmap_both_basic_0center.png',
        dpi=600,

### 2025-04-07 flow_figs.Rmd
added a 2016 hydrograph

@@
   rename(date = time) %>%
-  mutate(date = mdy(date))
+  mutate(date = mdy(date)) %>%
+  drop_na()
 
@@
                         'statn_all',
-                        'obs'))
+                        'obs')) %>%
+  mutate(cal_run = case_match(cal_run,
+                            'grid_all' ~ 'Gridded',
+                            'statn_all' ~ 'Station',
+                            'obs' ~ 'Observed'))
 
 flowEg <- flow_pivot %>%
-  filter(year %in% c(2012, 2016, 2017)) %>%
-  ggplot(., aes(x=date,
-                y=q_m3s, 
-                color = cal_run)) +
-  geom_line() +
-  facet_wrap(~year,
-             scales = 'free_x') +
-  theme_bw(base_size=20)
+  filter(year %in% c(2016)) %>%
+  ggplot(aes(x = date,
+             y = q_m3s, 
+             color = cal_run,
+             linetype = cal_run)) + 
+  geom_line(size = 1, alpha = 1) + 
+  theme_bw(base_size = 20) +
+  scale_color_manual(values = c("Gridded" = "#0047AB", 
+                                "Observed" = "black", 
+                                "Station" = "orange")) +
+  scale_linetype_manual(values = c("Gridded" = "solid",
+                                   "Observed" = "dashed", 
+                                   "Station" = "solid")) +
+  labs(x = element_blank(),
+       y = "Streamflow (cms)") +
+   scale_x_date(date_labels = "%b",
+               date_breaks = "1 month") +
+  theme(
+    legend.position = c(0.9, 0.9),
+    legend.text = element_text(size = 16),
+    legend.key.width = unit(2, "lines"),
+    legend.title = element_blank(),
+    panel.grid = element_blank(),
+    panel.background = element_rect(fill = "white"),
+    strip.background = element_blank(),
+    text = element_text(color = "black"),
+    axis.title = element_text(color = "black"),
+    axis.text = element_text(color = "black")
+  )
 
@@
 
+ggsave('/Users/megansears/Documents/Repos/fourmile/figures/2016_flowEg.png',
+       dpi=600,
+       width = 12,
+       height = 8)
+
 ```

### 2025-04-07 fourmile_output_dec2024.Rmd
changing indiv yr figs to 2016

@@
   mutate(year = year(date)) %>%
-  filter(year %in% c(2012, 2015, 2017)) %>% 
+  filter(year %in% c(2016)) %>% 
   mutate(flow_type = if_else(flow_type == 'grid_res', 
@@
   ggplot(aes(x = date, y = flow_cms, color = flow_type)) +  
-  geom_line(size=1, alpha=0.7) + 
+  geom_hline(yintercept = 0, color = "black") +
+  geom_line(size = 1, alpha = 0.7) + 
   scale_color_manual(values = c("#0047AB", "orange")) +
-  facet_wrap(~year, scales="free_x") +
-  labs(x=element_blank(),
-       y='Residuals (cms)') +
+  scale_x_date(date_labels = "%b %Y", 
+               date_breaks = "1 month") +
+  labs(x = element_blank(),
+       y = 'Residuals (cms)') +
+  theme_bw(base_size = 20) +
   theme(
@@
     panel.grid = element_blank(),
-    panel.background = element_rect(fill = "white"),
-    strip.background = element_blank(),
-    text = element_text(color = "black"),
-    axis.title = element_text(color = "black"),
-    axis.text = element_text(color = "black")
+    panel.background = element_rect(fill = "white")
   )
@@
        height = 8)
+
+```
+
+## add flow 2016 to fig
+
+```{r}
+
+flow <- read_csv('./discharge_all.csv') %>%
+  replace(.==-9999, NA) %>%
+  rename(date = time) %>%
+  mutate(date = mdy(date)) %>%
+  drop_na()
+
+flow_pivot <- flow %>%
+  pivot_longer(!date, names_to = 'cal_run', values_to = 'q_m3s') %>%
+  mutate(year = as.factor(year(date))) %>%
+  filter(cal_run %in% c('grid_all',
+                        'statn_all',
+                        'obs')) %>%
+  mutate(cal_run = case_match(cal_run,
+                            'grid_all' ~ 'Gridded',
+                            'statn_all' ~ 'Station',
+                            'obs' ~ 'Observed'))
+
+flowEg <- flow_pivot %>%
+  filter(year %in% c(2016)) %>%
+  ggplot(aes(x = date,
+             y = q_m3s, 
+             color = cal_run,
+             linetype = cal_run)) + 
+  geom_line(size = 1, alpha = 1) + 
+  theme_bw(base_size = 20) +
+  scale_color_manual(values = c("Gridded" = "#0047AB", 
+                                "Observed" = "black", 
+                                "Station" = "orange")) +
+  scale_linetype_manual(values = c("Gridded" = "solid",
+                                   "Observed" = "dashed", 
+                                   "Station" = "solid")) +
+  labs(x = element_blank(),
+       y = "Streamflow (cms)") +
+   scale_x_date(date_labels = "%b",
+               date_breaks = "1 month") +
+  theme(
+    legend.position = c(0.9, 0.9),
+    legend.text = element_text(size = 16),
+    legend.key.width = unit(2, "lines"),
+    legend.title = element_blank(),
+    panel.grid = element_blank(),
+    panel.background = element_rect(fill = "white"),
+    strip.background = element_blank(),
+    text = element_text(color = "black"),
+    axis.title = element_text(color = "black"),
+    axis.text = element_text(color = "black")
+  )
+
+flowEg
+
+ggsave('/Users/megansears/Documents/Repos/fourmile/figures/2016_flowEg.png',
+       dpi=600,
+       width = 12,
+       height = 8)
+
+plot_grid(plot, flowEg, plot_bottom12, ncol = 1)
 
@@
 
+write_csv(pbiasCats, '/Users/megansears/Documents/Repos/fourmile/38HRU_dec2024_updates/pbiasCats.csv')
+
 both_pbias_plot <- pbiasCats %>%
@@
 example <- gw %>%
-  filter(year == 2015) %>%
+  filter(year == 2016) %>%
   ungroup() %>% 
@@
   scale_color_manual(values = c("#0047AB", "orange")) +
-  scale_x_date(date_labels = "%b") +
+    scale_x_date(date_labels = "%b %Y", 
+               date_breaks = "2 month") +
   labs(x=element_blank(),
        y='Flow (cms)') +
-  theme_bw(base_size = 20) +
+  theme_bw(base_size = 16) +
   theme(
@@
 
-ggsave('./figures/2015_flowcumulative.png',
+ggsave('/Users/megansears/Documents/Repos/fourmile/figures/2016_flowcumulative.png',
        dpi=600,
@@
 
-ggsave('./figures/water_partition_combine.png',
+ggsave('/Users/megansears/Documents/Repos/fourmile/figures/water_partition_combine.png',
        dpi=600,

### 2025-04-07 params.Rmd
started to add pbias cat to param DFs

@@
          input_data = source) %>%
-  dplyr::select(param, input_data, value)
+  dplyr::select(param, input_data, year_missing, value)
 
@@
                       'soilLatVertLPS')) %>%
-  dplyr::select(param, input_data, value)
+  dplyr::select(param, input_data, year_missing, value)
 
@@
                               'Station'))
+
+# read in pbias categories
+pbias <- read_csv('/Users/megansears/Documents/Repos/fourmile/38HRU_dec2024_updates/pbiasCats.csv') %>%
+  filter(year == c('All')) %>%
+  dplyr::select(input_data, year_missing, pbias)
+
+# join pbias to 
+param_sens <- left_join(param_sens, pbias, by = c('input_data', 'year_missing')) %>%
+  mutate(Performance = if_else(abs(pbias) >= 25,
+                               'Unsatisfactory',
+                               'Acceptable'))
 

### 2025-04-07 state_vars.Rmd
changed hru low and high fig to 2016

--- 2025-03-13 state_vars.Rmd
@@
          source = 'statn') %>%
-  select(-time)
+  dplyr::select(-time)
 
@@
          source = 'grid') %>%
-  select(-time)
+  dplyr::select(-time)
 
@@
          month = month(date)) %>%
-  filter(year == 2015,
+  filter(year == 2016,
          month %in% c(4,5,6))
@@
 
-both_hi <- bind_rows(statn_hi, grid_hi) %>%
+both_low <- bind_rows(statn_low, grid_low) %>%
   mutate(year = year(date),
          month = month(date)) %>%
-  filter(year == 2015,
+  filter(year == 2016,
          month %in% c(4,5,6))
 
-temp <- ggplot(both_hi, 
+temp <- ggplot(both_low, 
                aes(date, 
@@
 ggplotly(swe)
+
+## combine low and high together
+hi <- both_hi %>%
+  dplyr::select(tmean, snowTotSWE, precip, source, date) %>%
+  mutate(elevation = 'High')
+
+low <- both_low %>%
+  dplyr::select(tmean, snowTotSWE, precip, source, date) %>%
+  mutate(elevation = 'Low')
+
+both <- bind_rows(hi, low) %>%
+  mutate(elev_source =
+           case_when(source == 'statn' & elevation == 'High' ~ 'Station - High',
+                     source == 'statn' & elevation == 'Low' ~ 'Station - Low',
+                     source == 'grid' & elevation == 'High' ~ 'Gridded - High',
+                     source == 'grid' & elevation == 'Low' ~ 'Gridded - Low'))
+
+# figure
+tmean <- ggplot(both,
+       aes(x=date, y = tmean, 
+           color = elev_source,
+           linetype=elev_source)) +
+   geom_line(size=1, alpha=0.8) +  
+    scale_color_manual(values = c("Gridded - High" = "#0047AB", 
+                                  "Gridded - Low" = "#0047AB", 
+                                  "Station - High" = "orange",
+                                  "Station - Low" = "orange")) +
+  scale_linetype_manual(values = c("Gridded - High" = "dashed", 
+                                  "Gridded - Low" = "solid", 
+                                  "Station - High" = "dashed",
+                                  "Station - Low" = "solid")) + 
+  scale_x_date(date_labels = "%b") +
+  labs(x = element_blank(),
+       y = 'Mean temperature (°C)') +
+  theme_bw(base_size = 20) +
+  theme(#legend.position = 'none',
+    legend.position = c(0.24, 0.852), 
+    legend.text = element_text(size = 10),
+    legend.title = element_blank(),
+    panel.grid = element_blank(),
+    panel.background = element_rect(fill = "white"),
+    strip.background = element_blank(),
+    text = element_text(color = "black"),
+    axis.title = element_text(color = "black"),
+    axis.text = element_text(color = "black"),
+    legend.key.width = unit(1, "cm")
+    #plot.margin = margin(t = 10, r = 20, b = 10, l = 10)
+  )
+
+tmean
+
+swe <- ggplot(both,
+       aes(x=date, y = snowTotSWE, 
+           color = elev_source,
+           linetype=elev_source)) +
+   geom_line(size=1, alpha=0.8) +  
+    scale_color_manual(values = c("Gridded - High" = "#0047AB", 
+                                  "Gridded - Low" = "#0047AB", 
+                                  "Station - High" = "orange",
+                                  "Station - Low" = "orange")) +
+  scale_linetype_manual(values = c("Gridded - High" = "dashed", 
+                                  "Gridded - Low" = "solid", 
+                                  "Station - High" = "dashed",
+                                  "Station - Low" = "solid")) + 
+  scale_x_date(date_labels = "%b") +
+  #scale_y_log10() +
+  labs(x = element_blank(),
+       y = 'SWE (mm)') +
+  theme_bw(base_size = 20) +
+  theme(
+    #legend.position = c(0.89, 0.87),
+    legend.position = 'none',
+    legend.text = element_text(size = 10),
+    legend.title = element_blank(),
+    panel.grid = element_blank(),
+    panel.background = element_rect(fill = "white"),
+    strip.background = element_blank(),
+    text = element_text(color = "black"),
+    axis.title = element_text(color = "black"),
+    axis.text = element_text(color = "black"),
+    legend.key.width = unit(1, "cm")
+    #plot.margin = margin(t = 10, r = 20, b = 10, l = 10)
+  )
+
+swe
+
+p <- both %>%
+  group_by(elev_source) %>%
+  mutate(cumP = cumsum(precip)) %>% 
+  ggplot(.,
+       aes(x=date, y = cumP, 
+           color = elev_source,
+           linetype=elev_source)) +
+   geom_line(size=1, alpha=0.8) +  
+    scale_color_manual(values = c("Gridded - High" = "#0047AB", 
+                                  "Gridded - Low" = "#0047AB", 
+                                  "Station - High" = "orange",
+                                  "Station - Low" = "orange")) +
+  scale_linetype_manual(values = c("Gridded - High" = "dashed", 
+                                  "Gridded - Low" = "solid", 
+                                  "Station - High" = "dashed",
+                                  "Station - Low" = "solid")) + 
+  scale_x_date(date_labels = "%b") +
+  #scale_y_log10() +
+  labs(x = element_blank(),
+       y = 'Precip (mm)') +
+  theme_bw(base_size = 20) +
+  theme(
+    legend.position = 'none',
+    #legend.text = element_text(size = 12),
+    #legend.title = element_blank(),
+    panel.grid = element_blank(),
+    panel.background = element_rect(fill = "white"),
+    strip.background = element_blank(),
+    text = element_text(color = "black"),
+    axis.title = element_text(color = "black"),
+    axis.text = element_text(color = "black"),
+    legend.key.width = unit(1, "cm")
+    #plot.margin = margin(t = 10, r = 20, b = 10, l = 10)
+  )
+
+p
+
+plot_grid(tmean, swe)
+
+ggsave('./figures/tmean_swe_2016.png',
+       width = 10,
+       height = 5,
+       dpi=600)
+
+plot_grid(tmean, p, swe, nrow=1)
+ggsave('./figures/tmean_swe_p_2016.png',
+       width = 10,
+       height = 5,
+       dpi=600)
 

### 2025-04-09 fourmile_output_dec2024.Rmd
redid kge and pbias plot and added nse

@@
 
+## NSE
+
+```{r}
+
+flow_nse_all <- flow %>%
+  drop_na() %>%
+  summarize(grid2011 = NSE(grid_2011, obs),
+            grid2012 = NSE(grid_2012, obs),
+            grid2013 = NSE(grid_2013, obs),
+            grid2014 = NSE(grid_2014, obs),
+            grid2015 = NSE(grid_2015, obs),
+            grid2016 = NSE(grid_2016, obs),
+            grid2017 = NSE(grid_2017, obs),
+            grid2018 = NSE(grid_2018, obs),
+            grid2019 = NSE(grid_2019, obs),
+            grid2020 = NSE(grid_2020, obs),
+            gridall = NSE(grid_all, obs),
+            statn2011 = NSE(statn_2011, obs),
+            statn2012 = NSE(statn_2012, obs),
+            statn2013 = NSE(statn_2013, obs),
+            statn2014 = NSE(statn_2014, obs),
+            statn2015 = NSE(statn_2015, obs),
+            statn2016 = NSE(statn_2016, obs),
+            statn2017 = NSE(statn_2017, obs),
+            statn2018 = NSE(statn_2018, obs),
+            statn2019 = NSE(statn_2019, obs),
+            statn2020 = NSE(statn_2020, obs),
+            statnall = NSE(statn_all, obs)) %>%
+    mutate_if(is.numeric,
+            round,
+            digits = 2)
+
+flow_nse_all <- flow_nse_all %>%
+  pivot_longer(everything()) %>%
+  arrange(value)
+
+# determine nse for each year for every model run
+flow_year <- flow %>%
+  mutate(year = year(date)) %>%
+  group_by(year) %>%
+  summarize(
+    grid2011 = NSE(grid_2011, obs),
+            grid2012 = NSE(grid_2012, obs),
+            grid2013 = NSE(grid_2013, obs),
+            grid2014 = NSE(grid_2014, obs),
+            grid2015 = NSE(grid_2015, obs),
+            grid2016 = NSE(grid_2016, obs),
+            grid2017 = NSE(grid_2017, obs),
+            grid2018 = NSE(grid_2018, obs),
+            grid2019 = NSE(grid_2019, obs),
+            grid2020 = NSE(grid_2020, obs),
+            gridall = NSE(grid_all, obs, na.rm = T, method='2012'),
+            statn2011 = NSE(statn_2011, obs),
+            statn2012 = NSE(statn_2012, obs),
+            statn2013 = NSE(statn_2013, obs),
+            statn2014 = NSE(statn_2014, obs),
+            statn2015 = NSE(statn_2015, obs),
+            statn2016 = NSE(statn_2016, obs),
+            statn2017 = NSE(statn_2017, obs),
+            statn2018 = NSE(statn_2018, obs),
+            statn2019 = NSE(statn_2019, obs),
+            statn2020 = NSE(statn_2020, obs),
+            statnall = NSE(statn_all, obs, na.rm=T, method='2012')) %>%
+    mutate_if(is.numeric,
+            round,
+            digits = 2)
+
+flow_nse <- flow_year %>%
+  pivot_longer(!year, names_to = 'model_run', values_to = 'nse') %>%
+  pivot_wider(names_from = 'year', values_from = 'nse')
+
+flow_plot <- flow_year %>%
+  pivot_longer(!year, names_to = 'model_run', values_to = 'nse') %>%
+  mutate(year = as.factor(year))
+
+# add all to the plot below
+nse_all <- flow_nse_all %>%
+  mutate(year = 'All') %>%
+  rename(model_run = name,
+         nse = value)
+
+flow_plot_updated <- bind_rows(flow_plot, nse_all)
+
+# nse figure
+flow_plot_updated <- flow_plot_updated %>% 
+  mutate(source = case_when(
+    grepl("grid", model_run) ~ "grid",
+    grepl("statn", model_run) ~ "statn"),
+    year_excluded = str_extract(model_run, "\\d{4}$")) %>%
+  mutate(year_excluded = if_else(model_run %in% c('gridall',
+                                                       'statnall'),
+                                  'None', year_excluded))
+
+# put nse into categories
+nseCats <- flow_plot_updated %>%
+  mutate(nseCat = case_when(
+    nse > 0.75 ~ 'Very good',
+    nse > 0.65 & nse <= 0.75 ~ 'Good',
+    nse > 0.5 & nse <= 0.65 ~ 'Satisfactory',
+    nse <= 0.5  ~ 'Unsatisfactory'),
+    nseCat = factor(nseCat, levels = c("Unsatisfactory", 
+                                           "Satisfactory", 
+                                           "Good", 
+                                           "Very good")))
+
+write_csv(nseCats, '/Users/megansears/Documents/Repos/fourmile/38HRU_dec2024_updates/nseCats.csv')
+
+# facet wrap the plots
+new_facet_titles <- c(
+  "grid" = "Gridded",
+  "statn" = "Station"
+)
+
+both_nse_plot <- nseCats %>%
+  ggplot(aes(x = year, 
+             y = year_excluded, 
+             fill = nseCat)) +
+  geom_tile(color = "white") +
+  facet_wrap(~source, labeller = labeller(source = new_facet_titles)) +
+  scale_fill_manual(values = c(
+    "Unsatisfactory" = "#F1F4EEFF", 
+    "Satisfactory" = "#EFDDCFFF",
+    "Good" = "#72E1E1FF",
+    "Very good" = "#009474FF"
+  )) +
+  geom_text(aes(label = sprintf("%.2f", nse)), 
+            color = "black", 
+            size = 2.75) +
+  theme_bw(base_size=18) +
+  theme(
+    axis.text.x = element_text(angle = 45, hjust = 1),
+    legend.position = 'bottom',
+    legend.text = element_text(size = 14),
+    legend.title = element_text(size = 14),
+    legend.key.width = unit(1, "cm"),
+    panel.grid = element_blank(),
+    panel.background = element_rect(fill = "white"),
+    strip.background = element_blank(),
+    text = element_text(color = "black"),
+    axis.title = element_text(color = "black"),
+    axis.text = element_text(color = "black"),
+    plot.margin = margin(t = 10, r = 10, b = 10, l = 10),
+    legend.margin = margin(t = -8, b = -4, unit = "pt")
+  ) +
+  labs(y = "Year excluded",
+       x = 'Year',
+       fill = 'NSE')
+
+both_nse_plot
+
+ggsave('/Users/megansears/Documents/Repos/fourmile/figures/nse_heatmap_both_cats.png',
+       dpi=600,
+       width = 10,
+       height = 6)
+
+```
+
 ## KGE
@@
 
-flow_plot_updated <- flow_plot_updated %>%
-  mutate(kge_revise = if_else(kge < 0, 0, kge))
+# flow_plot_updated <- flow_plot_updated %>%
+#   mutate(kge_revise = if_else(kge < 0, 0, kge))
 
@@
   mutate(kge_revise_bins = cut(kge,
-                               breaks = c(-Inf, 0.2, 0.4, 0.6, 0.8, 1),
+                               breaks = c(-Inf, 0.0, 0.2, 0.4, 0.6, 0.8, 1),
                                include.lowest = TRUE,
-                               labels = c("< 0.0", "0.2-0.4", "0.4-0.6", "0.6-0.8", "> 0.8")))
+                               labels = c("< 0.0","0.0-0.2", "0.2-0.4", "0.4-0.6", "0.6-0.8", "> 0.8")))
 
@@
 both_kge_plot <- flow_plot_updated %>%
-  ggplot(., aes(x = year_excluded, 
-              y = year, 
+  ggplot(., aes(x = year, 
+              y = year_excluded, 
               fill = kge_revise_bins)) +
@@
   facet_wrap(~source, labeller = labeller(source = new_facet_titles)) +
-  paletteer::scale_fill_paletteer_d("PNWColors::Anemone") +
+  #paletteer::scale_fill_paletteer_d("PNWColors::Anemone") +
+  # paletteer::scale_fill_paletteer_d(
+  # "PNWColors::Anemone", 
+  # guide = guide_legend(nrow = 1),
+  # direction = -1) +
+   scale_fill_manual(values = c(
+    "< 0.0" = "#DCBE9BFF", 
+    "0.0-0.2" = "#EFDDCFFF",
+    "0.2-0.4" = "#F1F4EEFF",
+    "0.4-0.6" = "#72E1E1FF",
+    "0.6-0.8" = "#11C2B5FF",
+    "> 0.8" = "#009474FF"),
+    guide = guide_legend(nrow = 1)) +
   geom_text(aes(label = sprintf("%.2f", 
@@
                                    hjust = 1)) +
-  labs(y = "Year",
-       x='Year excluded',
+  labs(y = "Year excluded",
+       x='Year',
        fill = 'KGE') +
@@
     legend.title = element_text(size = 14),
-    legend.key.width = unit(.75, "cm"),
+    legend.key.width = unit(.6, "cm"),
     panel.grid = element_blank(),
@@
     legend.margin = margin(t = -8, b = -4, unit = "pt"),
-    # axis.title.y = element_blank(),
-    # axis.text.y = element_blank(),
-    # axis.ticks.y = element_blank()
   )
@@
 ggsave('/Users/megansears/Documents/Repos/fourmile/figures/kge_heatmap_both_basic.png',
-       dpi=600,
-       width = 10,
-       height = 6)
-
-#####################
-kgeCats <- flow_plot_updated %>%
-  mutate(pbiasCat = case_when(
-    abs(pbias) < 10 ~ 'Very good',
-    abs(pbias) >= 10 & abs(pbias) < 15 ~ 'Good',
-    abs(pbias) >= 15 & abs(pbias) < 25 ~ 'Satisfactory',
-    abs(pbias) >= 25 ~ 'Unsatisfactory'),
-    pbiasCat = factor(pbiasCat, levels = c("Unsatisfactory", 
-                                           "Satisfactory", 
-                                           "Good", 
-                                           "Very good")))
-
-both_pbias_plot <- pbiasCats %>%
-  ggplot(aes(x = year_excluded, 
-             y = year, 
-             fill = pbiasCat)) +
-  geom_tile(color = "white") +
-  facet_wrap(~source, labeller = labeller(source = new_facet_titles)) +
-  # paletteer::scale_fill_paletteer_c(
-  #   "grDevices::Green-Brown",
-  #   limits = c(-max_abs, max_abs),
-  #   oob = scales::squish
-  # ) +
-  paletteer::scale_fill_paletteer_d("calecopal::lupinus") +
-  geom_text(aes(label = sprintf("%.2f", pbias)), 
-            color = "black", 
-            size = 2.75) +
-  theme_bw(base_size=18) +
-  theme(
-    axis.text.x = element_text(angle = 45, hjust = 1),
-    legend.position = 'bottom',
-    legend.text = element_text(size = 14),
-    legend.title = element_text(size = 14),
-    legend.key.width = unit(1, "cm"),
-    panel.grid = element_blank(),
-    panel.background = element_rect(fill = "white"),
-    strip.background = element_blank(),
-    text = element_text(color = "black"),
-    axis.title = element_text(color = "black"),
-    axis.text = element_text(color = "black"),
-    plot.margin = margin(t = 10, r = 10, b = 10, l = 10),
-    legend.margin = margin(t = -8, b = -4, unit = "pt")
-  ) +
-  labs(y = "Year",
-       x = 'Year excluded',
-       fill = '% bias')
-
-both_pbias_plot
-
-ggsave('/Users/megansears/Documents/Repos/fourmile/figures/pbias_heatmap_both_cats.png',
        dpi=600,
@@
 both_pbias_plot <- pbiasCats %>%
-  ggplot(aes(x = year_excluded, 
-             y = year, 
+  ggplot(aes(x = year, 
+             y = year_excluded, 
              fill = pbiasCat)) +
@@
   facet_wrap(~source, labeller = labeller(source = new_facet_titles)) +
-  # paletteer::scale_fill_paletteer_c(
-  #   "grDevices::Green-Brown",
-  #   limits = c(-max_abs, max_abs),
-  #   oob = scales::squish
-  # ) +
-  paletteer::scale_fill_paletteer_d("calecopal::lupinus") +
-  #paletteer::scale_fill_paletteer_d("PNWColors::Anemone") +
+   scale_fill_manual(values = c(
+    "Unsatisfactory" = "#F1F4EEFF", 
+    "Satisfactory" = "#EFDDCFFF",
+    "Good" = "#72E1E1FF",
+    "Very good" = "#009474FF"
+  )) +
   geom_text(aes(label = sprintf("%.2f", pbias)), 
@@
   ) +
-  labs(y = "Year",
-       x = 'Year excluded',
+  labs(y = "Year excluded",
+       x = 'Year',
        fill = '% bias')
@@
 ggsave('/Users/megansears/Documents/Repos/fourmile/figures/pbias_heatmap_both_cats.png',
-       dpi=600,
-       width = 10,
-       height = 6)
-
-# max_abs <- max(abs(flow_plot_updated$pbias), na.rm = TRUE)
-# 
-# both_pbias_plot <- flow_plot_updated %>%
-#   ggplot(aes(x = year_excluded, 
-#              y = year, 
-#              fill = pbias)) +
-#   geom_tile(color = "white") +
-#   facet_wrap(~source, labeller = labeller(source = new_facet_titles)) +
-#   paletteer::scale_fill_paletteer_c(
-#     "grDevices::Green-Brown",
-#     limits = c(-max_abs, max_abs),
-#     oob = scales::squish
-#   ) +
-#   geom_text(aes(label = sprintf("%.2f", pbias)), 
-#             color = "black", 
-#             size = 2.75) +
-#   theme_bw(base_size=18) +
-#   theme(
-#     axis.text.x = element_text(angle = 45, hjust = 1),
-#     legend.position = 'bottom',
-#     legend.text = element_text(size = 14),
-#     legend.title = element_text(size = 14),
-#     legend.key.width = unit(2, "cm"),
-#     panel.grid = element_blank(),
-#     panel.background = element_rect(fill = "white"),
-#     strip.background = element_blank(),
-#     text = element_text(color = "black"),
-#     axis.title = element_text(color = "black"),
-#     axis.text = element_text(color = "black"),
-#     plot.margin = margin(t = 10, r = 10, b = 10, l = 10),
-#     legend.margin = margin(t = -8, b = -4, unit = "pt")
-#   ) +
-#   labs(y = "Year",
-#        x = 'Year excluded',
-#        fill = 'Pbias')
-# 
-# both_pbias_plot
-
-ggsave('/Users/megansears/Documents/Repos/fourmile/figures/pbias_heatmap_both_basic_0center.png',
        dpi=600,

### 2025-04-09 params.Rmd
added model performance to parameters. need to finish formatting

--- 2025-02-27 params.Rmd
@@
 ```{r}
+
 # params area weighted (only for lagSurfaceRunoff, a_rain, a_snow)
@@
                       'soilLatVertLPS')) %>%
-  dplyr::select(param, input_data, value)
+  dplyr::select(param, input_data, year_missing, value) %>%
+  mutate(year_missing = if_else(year_missing == 'none',
+                                'all',
+                                year_missing))
 
@@
 
-# boxplots of top 8
+# read in pbias categories
+pbias <- read_csv('/Users/megansears/Documents/Repos/fourmile/38HRU_dec2024_updates/pbiasCats.csv') %>%
+  filter(year == c('All')) %>%
+  dplyr::select(input_data, year_missing, pbias)
+
+nse <- read_csv('/Users/megansears/Documents/Repos/fourmile/38HRU_dec2024_updates/nseCats.csv') %>%
+  filter(year == c('All')) %>%
+  dplyr::select(input_data, year_missing, nse)
+
+perf <- left_join(nse, pbias, by = c('input_data',
+                                     'year_missing'))
+
+perf <- perf %>%
+  mutate(performance = case_when(
+                                nse < 0.5 & abs(pbias) >= 25 ~ 'Neither',
+                                nse > 0.5 & abs(pbias) >= 25 ~ 'NSE',
+                                nse < 0.5 & abs(pbias) < 25 ~ '% bias',
+                                nse > 0.5 & abs(pbias) < 25 ~ 'NSE + % bias')) %>%
+  mutate(input_data = if_else(input_data == 'grid',
+                              'Gridded', 'Station'),
+         year_missing = if_else(year_missing == 'None',
+                                'all', year_missing))
+
+param_sens <- left_join(param_sens,
+                        perf,
+                        by = c('input_data',
+                               'year_missing'))
+
+# boxplots of top 9
 ggplot(param_sens, aes(x=input_data, y=value, fill=input_data)) +
   geom_boxplot(alpha=0.8,
-                outlier.colour = "black") +
+                outlier.shape=NA) +
   facet_wrap(~param, scales = 'free_y') +
@@
                      size = 7) +
+  geom_jitter(aes(shape = performance),
+            position = position_jitter(width = 0.15), 
+            size = 2.5, 
+            alpha = 0.6,
+            stroke = 1,
+            color = "black") +
+  scale_shape_manual(values = c(
+  "% bias" = 1,
+  "NSE + % bias" = 16
+)) +
   scale_fill_manual(values = c("#0047AB", "orange")) +
@@
 
-ggsave('./figures/param_sensit_boxplots.png',
+ggsave('./figures/param_sensit_boxplots_pts.png',
        dpi=600)

### 2025-04-23 spatial_figs.Rmd
added title to HRU climate fig

@@
     axis.title.y = element_blank(),
-    plot.margin = unit(c(-6, 0, 0, 0), "cm"),
+    plot.margin = unit(c(-4, 0, 0, 0), "cm"),
     panel.spacing = unit(0, "lines"))
@@
     axis.title.y = element_blank(),
-    plot.margin = unit(c(0, 0, -6, 0), "cm"),
+    plot.margin = unit(c(0, 0, -4, 0), "cm"),
     panel.spacing = unit(0, "lines"))
@@
 
-ggsave("./figures/diff_update2.png", plot = lots, dpi = 600)
+#ggsave("./figures/diff_update2.png", plot = lots, dpi = 600)
+
+library(cowplot)
+title <- ggdraw() + 
+  draw_label("Difference = Station - Gridded", 
+             fontface = "bold", 
+             size = 16,
+             x = 0,  # left-aligned
+             hjust = 0) +
+  theme(plot.margin = margin(0, 0, -200,15))  # reduce space between title and plot
+
+# Combine title and the main plot
+final_plot <- plot_grid(title, lots, ncol = 1, rel_heights = c(0.05, 1))
+
+final_plot
+
+ggsave(filename = "./figures/diff_update2_wtitle.png", 
+       plot = final_plot, 
+       dpi = 600)
 

### 2025-04-23 params.Rmd
added circles for NSE and pbias performance on parameter boxplots

@@
                                 nse > 0.5 & abs(pbias) >= 25 ~ 'NSE',
-                                nse < 0.5 & abs(pbias) < 25 ~ '% bias',
-                                nse > 0.5 & abs(pbias) < 25 ~ 'NSE + % bias')) %>%
+                                nse < 0.5 & abs(pbias) < 25 ~ '% bias satisfactory',
+                                nse > 0.5 & abs(pbias) < 25 ~ 'NSE + % bias satisfactory')) %>%
   mutate(input_data = if_else(input_data == 'grid',
@@
   geom_jitter(aes(shape = performance),
-            position = position_jitter(width = 0.15), 
+            position = position_jitter(width = 0.1), 
             size = 2.5, 
@@
   scale_shape_manual(values = c(
-  "% bias" = 1,
-  "NSE + % bias" = 16
+  "% bias satisfactory" = 1,
+  "NSE + % bias satisfactory" = 16
 )) +
-  scale_fill_manual(values = c("#0047AB", "orange")) +
+  scale_fill_manual(values = c("#0047AB", "orange"),
+                    guide='none') +
     theme(
-    legend.position = 'none',
+    legend.position = 'bottom',
     #legend.justification = c(0, 1.1), 
@@
   ) +
-  scale_y_continuous(expand = expansion(mult = c(0.05, 0.15)))
+  scale_y_continuous(expand = expansion(mult = c(0.1, 0.25)))
 
@@
 
-ggplot(combo, aes(x=burn, y=value, fill=input_data)) +
-  geom_boxplot(alpha=0.8,
-                outlier.colour = "black") +
-  geom_text(aes(label = letter)) +
-  # stat_compare_means(aes(group = input_data),
-  #                    method = "wilcox.test", 
-  #                    label = "p.signif",
-  #                    hide.ns = T,
-  #                    paired = F,
-  #                    #label.y = 0,
-  #                    #label.x = 1.4,
-  #                    size = 7) +
-  facet_wrap(~param, scales = 'free_y') +
-  labs(y=element_blank(),
-       x=element_blank()) +
-  theme_bw(base_size=20) +
-  scale_fill_manual(values = c("#0047AB", "orange")) +
-    theme(
-    legend.position = 'bottom',
-    #legend.justification = c(0, 1.1), 
-    legend.text = element_text(size = 16),
-    legend.title = element_blank(), 
-    panel.grid = element_blank(),
-    panel.background = element_rect(fill = "white"),
-    strip.background = element_blank(),
-    text = element_text(color = "black"),
-    axis.title = element_text(color = "black"),
-    axis.text = element_text(color = "black"),
-    #strip.text = element_blank()
-  ) +
-  scale_y_continuous(expand = expansion(mult = c(0.05, 0.15)))
+perf1 <- perf %>%
+  mutate(year_missing = if_else(year_missing == 'all',
+                                'none',
+                                year_missing))
 
-ggsave('./figures/burn_unburn_params_tukey.png',
-       dpi=600)
+combo <- left_join(combo,
+                        perf1,
+                        by = c('input_data',
+                               'year_missing'))
 
-# text above boxplots
+# text above boxplots - this is from Tukey analysis that was already run below then added to params
 combo <- combo %>%
@@
 ggplot(combo, aes(x = burn, y = value, fill = input_data)) +
-  geom_boxplot(alpha = 0.8, outlier.colour = "black") +
+  geom_boxplot(alpha = 0.8, 
+               outliers = F) +
   geom_text(aes(label = letter, y = y_text), 
@@
             vjust = 0) +  
+  geom_jitter(aes(shape = performance),
+            position = position_jitterdodge(
+    jitter.width = 0.1,
+    dodge.width = 0.75),
+            size = 2.5, 
+            alpha = 0.6,
+            stroke = 1,
+            color = "black") +
+  scale_shape_manual(values = c(
+  "% bias satisfactory" = 1,
+  "NSE + % bias satisfactory" = 16)) +
   facet_wrap(~param, scales = 'free_y') +
@@
 
-ggsave('./figures/burn_unburn_params_tukey.png',
+ggsave('./figures/burn_unburn_params_tukey_pts.png',
        dpi=600,

### 2025-04-24 state_vars.Rmd
updated 2016 high and low HRU plots

--- 2025-03-13 state_vars.Rmd
@@
 ggplotly(swe)
+
+## combine low and high together
+hi <- both_hi %>%
+  dplyr::select(tmean, snowTotSWE, precip, source, date) %>%
+  mutate(elevation = 'High')
+
+low <- both_low %>%
+  dplyr::select(tmean, snowTotSWE, precip, source, date) %>%
+  mutate(elevation = 'Low')
+
+both <- bind_rows(hi, low) %>%
+  mutate(elev_source =
+           case_when(source == 'statn' & elevation == 'High' ~ 'Station - High',
+                     source == 'statn' & elevation == 'Low' ~ 'Station - Low',
+                     source == 'grid' & elevation == 'High' ~ 'Gridded - High',
+                     source == 'grid' & elevation == 'Low' ~ 'Gridded - Low'))
+
+# figure
+tmean <- ggplot(both,
+       aes(x=date, y = tmean, 
+           color = elev_source,
+           linetype=elev_source)) +
+   geom_line(size=1, alpha=0.8) +  
+    scale_color_manual(values = c("Gridded - High" = "#0047AB", 
+                                  "Gridded - Low" = "#0047AB", 
+                                  "Station - High" = "orange",
+                                  "Station - Low" = "orange")) +
+  scale_linetype_manual(values = c("Gridded - High" = "dashed", 
+                                  "Gridded - Low" = "solid", 
+                                  "Station - High" = "dashed",
+                                  "Station - Low" = "solid")) + 
+  scale_x_date(date_labels = "%b") +
+  labs(x = element_blank(),
+       y = 'Mean temperature (°C)') +
+  theme_bw(base_size = 20) +
+  theme(legend.position = 'bottom',
+    #legend.position = c(0.24, 0.852), 
+    legend.text = element_text(size = 10),
+    legend.title = element_blank(),
+    panel.grid = element_blank(),
+    panel.background = element_rect(fill = "white"),
+    strip.background = element_blank(),
+    text = element_text(color = "black"),
+    axis.title = element_text(color = "black"),
+    axis.text = element_text(color = "black"),
+    legend.key.width = unit(1, "cm")
+    #plot.margin = margin(t = 10, r = 20, b = 10, l = 10)
+  )
+
+tmean
+
+swe <- ggplot(both,
+       aes(x=date, y = snowTotSWE, 
+           color = elev_source,
+           linetype=elev_source)) +
+   geom_line(size=1, alpha=0.8) +  
+    scale_color_manual(values = c("Gridded - High" = "#0047AB", 
+                                  "Gridded - Low" = "#0047AB", 
+                                  "Station - High" = "orange",
+                                  "Station - Low" = "orange")) +
+  scale_linetype_manual(values = c("Gridded - High" = "dashed", 
+                                  "Gridded - Low" = "solid", 
+                                  "Station - High" = "dashed",
+                                  "Station - Low" = "solid")) + 
+  scale_x_date(date_labels = "%b") +
+  #scale_y_log10() +
+  labs(x = element_blank(),
+       y = 'SWE (mm)') +
+  theme_bw(base_size = 20) +
+  theme(
+    #legend.position = c(0.89, 0.87),
+    legend.position = 'bottom',
+    legend.text = element_text(size = 10),
+    legend.title = element_blank(),
+    panel.grid = element_blank(),
+    panel.background = element_rect(fill = "white"),
+    strip.background = element_blank(),
+    text = element_text(color = "black"),
+    axis.title = element_text(color = "black"),
+    axis.text = element_text(color = "black"),
+    legend.key.width = unit(1, "cm")
+    #plot.margin = margin(t = 10, r = 20, b = 10, l = 10)
+  )
+
+swe
+
+p <- both %>%
+  group_by(elev_source) %>%
+  mutate(cumP = cumsum(precip)) %>% 
+  ggplot(.,
+       aes(x=date, y = cumP, 
+           color = elev_source,
+           linetype=elev_source)) +
+   geom_line(size=1, alpha=0.8) +  
+    scale_color_manual(values = c("Gridded - High" = "#0047AB", 
+                                  "Gridded - Low" = "#0047AB", 
+                                  "Station - High" = "orange",
+                                  "Station - Low" = "orange")) +
+  scale_linetype_manual(values = c("Gridded - High" = "dashed", 
+                                  "Gridded - Low" = "solid", 
+                                  "Station - High" = "dashed",
+                                  "Station - Low" = "solid")) + 
+  scale_x_date(date_labels = "%b") +
+  #scale_y_log10() +
+  labs(x = element_blank(),
+       y = 'Precip (mm)') +
+  theme_bw(base_size = 20) +
+  theme(
+    legend.position = 'bottom',
+    #legend.text = element_text(size = 12),
+    #legend.title = element_blank(),
+    panel.grid = element_blank(),
+    panel.background = element_rect(fill = "white"),
+    strip.background = element_blank(),
+    text = element_text(color = "black"),
+    axis.title = element_text(color = "black"),
+    axis.text = element_text(color = "black"),
+    legend.key.width = unit(1, "cm")
+    #plot.margin = margin(t = 10, r = 20, b = 10, l = 10)
+  )
+
+p
+
+# plot_grid(tmean, swe)
+# 
+# ggsave('./figures/tmean_swe_2016.png',
+#        width = 10,
+#        height = 5,
+#        dpi=600)
+
+plot_grid(tmean, p, swe, nrow=1)
+
+ggsave('./figures/tmean_swe_p_2016.png',
+       width = 10,
+       height = 5,
+       dpi=600)
+
+library(cowplot)
+
+legend <- cowplot::get_plot_component(tmean, "guide-box", return_all = TRUE)[[3]]
+
+tmean_noleg <- tmean + theme(legend.position = "none")
+p_noleg <- p + theme(legend.position = "none")
+swe_noleg <- swe + theme(legend.position = "none")
+
+combined <- plot_grid(tmean_noleg, p_noleg, swe_noleg, nrow = 1)
+final_plot <- plot_grid(combined, legend, ncol = 1, rel_heights = c(1, 0.1))
+final_plot
+
+ggsave('./figures/tmean_swe_p_2016.png',
+       width = 10,
+       height = 5,
+       dpi=600)
+
+# stats for precip, tmean, and swe
+both_avg <- both %>%
+  group_by(elev_source) %>%
+  summarize(mean_temp = mean(tmean),
+            max_swe = max(snowTotSWE),
+            mean_p = mean(precip))
 

### 2025-04-25 fourmile_output_dec2024.Rmd
added pts based on performance to the flow type boxplots

@@
 
-# look at 2015, high snow year 
+# look at 2016, best performing year 
 example <- gw %>%
@@
   labs(x=element_blank(),
-       y='Flow (cms)') +
+       y='mm of water') +
   theme_bw(base_size = 16) +
@@
 
+perf <- read_csv('/Users/megansears/Documents/Repos/fourmile/38HRU_dec2024_updates/nse_pbias_grid_statn_all.csv') %>%
+  mutate(year = as.factor(year))
+
+gw_maxcumsum <- left_join(gw_maxcumsum,
+                          perf,
+                          by = c('source',
+                                 'year'))
+
+gw_maxcumsum <- gw_maxcumsum %>%
+  mutate(flow_cms = if_else(flow_type == 'yr_cum_RD1' &
+                                flow_cms > 48,
+                              NA,
+                              flow_cms))
+
 gw_maxcumsum_letters <- gw_maxcumsum %>%
@@
                          1.3, max)) %>%
-  mutate(y_text = max * 1.07)
-
-flow_box <- ggplot(gw_maxcumsum, aes(x = flow_type, y = flow_cms, fill = source)) +
-  geom_boxplot(position = position_dodge(1),
-               outliers=F) + # need to note 1 outlier is removed from RD1 grid and statn (2013 flood) ****
+  mutate(y_text = max * 1.06)
+
+flow_box <- ggplot(gw_maxcumsum, aes(x = source, y = flow_cms, fill = source)) +
+  geom_boxplot(outliers=F,width=0.7) + # need to note 1 outlier is removed from RD1 grid and statn (2013 flood) ****
+  geom_jitter(
+    aes(shape = both),
+    position = position_jitter(width = 0.25),
+    size = 2.5,
+    alpha = 0.7,
+    stroke = 1,
+    color = "black") +
+  scale_shape_manual(values = c(
+  "NSE + % bias unsatisfactory" = 4,
+  "NSE + % bias satisfactory" = 16,
+  "NSE satisfactory" = 1)) +
   geom_text(data = gw_maxcumsum_letters, 
@@
   theme_bw(base_size=20) +
-  scale_fill_manual(values = c("#0047AB", "orange")) +
+  scale_fill_manual(values = c("#0047AB", "orange"), guide = 'none') +
   theme(
-    legend.position = c(0.94, 0.36),
+    #legend.position = c(0.94, 0.36),
+    legend.position = 'bottom',
     legend.text = element_text(size = 12),
@@
     axis.title.x = element_blank(),
-    axis.text.x = element_blank(),
-    axis.ticks.x = element_blank()) +
-  scale_y_continuous(expand = expansion(mult = c(0.05, 0.1)))
+    legend.spacing = unit(0.1, "lines"),
+    legend.margin = margin(t = -8, r = 0, b = -2, l = 0)) +
+    #axis.text.x = element_blank(),
+    #axis.ticks.x = element_blank()) +
+  scale_y_continuous(expand = expansion(mult = c(0.1, 0.15)))
 
@@
 
-# ggsave('./figures/water_partition_boxplots.png',
+# ggsave('./figures/water_partition_boxplsource()# ggsave('./figures/water_partition_boxplots.png',
 #        dpi=600)
@@
 
-ggsave('/Users/megansears/Documents/Repos/fourmile/figures/water_partition_combine.png',
+ggsave('/Users/megansears/Documents/Repos/fourmile/figures/water_partition_combine_pts.png',
        dpi=600,

### 2025-04-25 highestKGE_models.Rmd
from best calibration scenarios, ran models forward and calculated performance metrics

---
title: "Fourmile-Best Runs"
author: "Megan Sears"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: yes
    toc_float: yes
    theme: journal
editor_options:
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = F,
  message = F, 
  warning  = F)

library(tidyverse)
library(plotly)
library(hydroGOF)

```

# Performance metrics

```{r}

flow <- read_csv('./best_performance/best_perf_flow.csv') %>%
  mutate(date = mdy(date)) %>%
  replace(.==-9999, NA)

kge <- flow %>%
  drop_na() %>% 
  summarize(KGE_grid2012_grid = KGE(grid2012_grid, obs),
            KGE_grid2012_statn = KGE(grid2012_statn, obs),
            KGE_statn2017_grid = KGE(statn2017_grid, obs),
            KGE_statn2017_statn = KGE(statn2017_statn, obs))

nse <- flow %>%
  drop_na() %>% 
  summarize(NSE_grid2012_grid = NSE(grid2012_grid, obs),
            NSE_grid2012_statn = NSE(grid2012_statn, obs),
            NSE_statn2017_grid = NSE(statn2017_grid, obs),
            NSE_statn2017_statn = NSE(statn2017_statn, obs))

pbias <- flow %>%
  drop_na() %>%
  summarize(pbias_grid2012_grid = pbias(grid2012_grid, obs),
            pbias_grid2012_statn = pbias(grid2012_statn, obs),
            pbias_statn2017_grid = pbias(statn2017_grid, obs),
            pbias_statn2017_statn = pbias(statn2017_statn, obs))

kge_yr <- flow %>%
  mutate(year = year(date)) %>%
  group_by(year) %>%
  summarize(KGE_grid2012_grid = KGE(grid2012_grid, obs),
            KGE_grid2012_statn = KGE(grid2012_statn, obs),
            KGE_statn2017_grid = KGE(statn2017_grid, obs),
            KGE_statn2017_statn = KGE(statn2017_statn, obs))

```

# Hydrographs

```{r}

flow_long <- flow %>%
  drop_na() %>%
  pivot_longer(!date,
               names_to = 'run',
               values_to = 'flow_cms')

hydrograph <- ggplot(flow_long,
       aes(x=date,
           y=flow_cms,
           color=run)) +
  geom_line(size = 0.5) +
  theme_bw(base_size=20)

ggplotly(hydrograph)

```

### 2025-05-02 fourmile_output_dec2024.Rmd
combined 2016 hydrograph with 2016 cumulative flows

@@
     legend.position = 'bottom',
-    legend.text = element_text(size = 12),
+    legend.text = element_text(size = 16),
     legend.title = element_blank(),
@@
 
-# ggsave('./figures/water_partition_boxplsource()# ggsave('./figures/water_partition_boxplots.png',
-#        dpi=600)
+ggsave('./figures/water_partition_boxplots.png',
+       dpi=600,
+       width = 12,
+       height = 8)
 
@@
 ```
+
+# Example year
+
+```{r}
+
+# 2016 hydrograph
+flowEg <- flow_pivot %>%
+  filter(year %in% c(2016)) %>%
+  ggplot(aes(x = date,
+             y = q_m3s, 
+             color = cal_run,
+             linetype = cal_run)) + 
+  geom_line(size = 1, alpha = 1) + 
+  theme_bw(base_size = 20) +
+  scale_color_manual(values = c("Gridded" = "#0047AB", 
+                                "Observed" = "black", 
+                                "Station" = "orange")) +
+  scale_linetype_manual(values = c("Gridded" = "solid",
+                                   "Observed" = "dashed", 
+                                   "Station" = "solid")) +
+  labs(x = element_blank(),
+       y = "Streamflow (cms)") +
+   scale_x_date(date_labels = "%b",
+               date_breaks = "1 month") +
+  theme(
+    legend.position = c(0.9, 0.85),
+    legend.text = element_text(size = 14),
+    legend.key.width = unit(2, "lines"),
+    legend.title = element_blank(),
+    panel.grid = element_blank(),
+    panel.background = element_rect(fill = "white"),
+    strip.background = element_blank(),
+    text = element_text(color = "black"),
+    axis.title = element_text(color = "black"),
+    axis.text = element_text(color = "black"),
+    plot.margin = margin(t = 2, r = 20, b = 2, l = 10)
+  )
+
+flowEg
+
+# 2016 flow partition
+example <- gw %>%
+  filter(year == 2016) %>%
+  ungroup() %>% 
+  dplyr::select(date, source,
+         RD1cumsum,
+         RD2cumsum,
+         RG1cumsum,
+         RG2cumsum) %>%
+  pivot_longer(!c(date,source), names_to='flow_type',
+               values_to='flow_cms') %>%
+  mutate(source = if_else(source == 'grid_all',
+                          'Gridded',
+                          'Station'))
+
+facet_labels <- c('yr_cum_RD1' = 'Surface runoff',
+                  'yr_cum_RD2' = 'Interflow',
+                  'yr_cum_RG1' = 'Fast groundwater',
+                  'yr_cum_RG2' = 'Slow groundwater')
+
+example_yr <- ggplot(example,
+       aes(x=date, y = flow_cms, color=source)) +
+  geom_line() +
+  facet_wrap(~flow_type, 
+             scales = 'free_y',
+             labeller = labeller(flow_type = facet_labels)) +
+   geom_line(size=1, alpha=0.7) +  
+  scale_color_manual(values = c("#0047AB", "orange")) +
+    scale_x_date(date_labels = "%b", 
+               date_breaks = "2 month") +
+  labs(x=element_blank(),
+       y='mm of water') +
+  theme_bw(base_size = 16) +
+  theme(
+    legend.position = 'none',
+    legend.text = element_text(size = 12),
+    legend.title = element_blank(),
+    panel.grid = element_blank(),
+    panel.background = element_rect(fill = "white"),
+    strip.background = element_blank(),
+    text = element_text(color = "black"),
+    axis.title = element_text(color = "black"),
+    axis.text = element_text(color = "black"),
+    plot.margin = margin(t = 2, r = 20, b = 10, l = 10)
+  )
+
+example_yr
+
+plot_grid(flowEg,
+          example_yr,
+          ncol=1)
+
+ggsave('/Users/megansears/Documents/Repos/fourmile/figures/2016_all_flow.png',
+       dpi=600,
+       width=10,
+       height=8)
+
+```

### 2025-05-02 state_vars.Rmd
adding burn & unburn HRU examples

@@
 
-# 2015 for low and high HRU
+# 2016 for low and high HRU
 
@@
 
-# ANOVA for water partition
-
-```{r}
-
-flow <- both %>%
-  select(date, 
-         source, 
-         outRG1,
-         outRG2,
-         outRD1, 
-         outRD2,
-         source)
-
-rd1_model <- aov(outRD2 ~ source, data = flow)
-summary(rd1_model)
-
-```
+# Burn vs Unburn HRU
+
+```{r}
+
+unburn <- read_csv('./38HRU_dec2024_updates/HRU/statn_HRU_2_unburn.csv') %>%
+  mutate(date = mdy(time),
+         year = year(date),
+         type = 'unburn') %>%
+  filter(year == 2016)
+
+burn <- read_csv('./38HRU_dec2024_updates/HRU/statn_HRU_5_burn.csv') %>%
+  mutate(date = mdy(time),
+         year = year(date),
+         type = 'burn') %>%
+  filter(year == 2016)
+
+```

### 2025-05-02 state_vars.Rmd
looking at burn and unburn HRU state vars

--- 2025-04-24 state_vars.Rmd
@@
 
-# ANOVA for water partition
-
-```{r}
-
-flow <- both %>%
-  select(date, 
-         source, 
-         outRG1,
-         outRG2,
-         outRD1, 
-         outRD2,
-         source)
-
-rd1_model <- aov(outRD2 ~ source, data = flow)
-summary(rd1_model)
-
-```
+# Burn vs Unburn HRU
+
+```{r}
+
+unburn <- read_csv('./38HRU_dec2024_updates/HRU/statn_HRU_2_unburn.csv') %>%
+  mutate(date = mdy(time),
+         year = year(date),
+         type = 'unburn') %>%
+  filter(year == 2011)
+
+burn <- read_csv('./38HRU_dec2024_updates/HRU/statn_HRU_5_burn.csv') %>%
+  mutate(date = mdy(time),
+         year = year(date),
+         type = 'burn') %>%
+  filter(year == 2011)
+
+both <- bind_rows(unburn, burn)
+
+# interception
+inter <- both %>%
+  dplyr::select(date, type, interception)
+
+ggplot(inter,
+       aes(x=date,,
+           y=interception,
+           color=type)) +
+  geom_line() +
+  theme_bw(base_size=20)
+
+# swe
+swe <- both %>%
+  dplyr::select(date, type, snowTotSWE)
+
+ggplot(swe,
+       aes(x=date,,
+           y=snowTotSWE,
+           color=type)) +
+  geom_line() +
+  theme_bw(base_size=20)
+
+# swe
+p <- both %>%
+  dplyr::select(date, type, precip)
+
+ggplot(p,
+       aes(x=date,,
+           y=precip,
+           color=type)) +
+  geom_line() +
+  theme_bw(base_size=20)
+
+# surface runoff
+runoff <- both %>%
+  dplyr::select(date, type, outRD1)
+
+ggplot(runoff,
+       aes(x=date,,
+           y=outRD1,
+           color=type)) +
+  geom_line() +
+  theme_bw(base_size=20)
+
+# interflow
+interflow <- both %>%
+  dplyr::select(date, type, outRD2)
+
+ggplot(interflow,
+       aes(x=date,,
+           y=outRD2,
+           color=type)) +
+  geom_line() +
+  theme_bw(base_size=20)
+
+gw <- both %>%
+  dplyr::select(date, type, outRG1)
+
+ggplot(gw,
+       aes(x=date,,
+           y=outRG1,
+           color=type)) +
+  geom_line() +
+  theme_bw(base_size=20)
+
+# dps
+dps <- both %>%
+  dplyr::select(date, type, actDPS)
+
+ggplot(dps,
+       aes(x=date,,
+           y=actDPS,
+           color=type)) +
+  geom_line() +
+  theme_bw(base_size=20)
+
+# mps
+mps <- both %>%
+  dplyr::select(date, type, soilSatMPS)
+
+ggplot(mps,
+       aes(x=date,,
+           y=soilSatMPS,
+           color=type)) +
+  geom_line() +
+  theme_bw(base_size=20)
+
+# lps
+lps <- both %>%
+  dplyr::select(date, type, soilSatLPS)
+
+ggplot(lps,
+       aes(x=date,,
+           y=soilSatLPS,
+           color=type)) +
+  geom_line() +
+  theme_bw(base_size=20)
+
+# soil sat
+soilsat <- both %>%
+  dplyr::select(date, type, soilSat)
+
+ggplot(soilsat,
+       aes(x=date,,
+           y=soilSat,
+           color=type)) +
+  geom_line() +
+  theme_bw(base_size=20)
+
+```

### 2025-05-06 params.Rmd
changed order of param boxplots to match order of processes
reorder burn/unburn params to match order of processes

@@
                                'year_missing'))
+
+param_sens$param <- factor(param_sens$param, levels = c("snow_trs", 
+                                                        "baseTemp", 
+                                                        "t_factor",
+                                                        "a_rain",
+                                                        "a_snow",
+                                                        "lagSurfaceRunoff",
+                                                        "soilLatVertLPS",
+                                                        "soilOutLPS",
+                                                        "lagInterflow"))
 
@@
 
+# reorder the params
+combo$param <- factor(combo$param, levels = c("a_snow",
+                                                        "a_rain",
+                                                        "soilMaxInfSummer",
+                                                        "soilMaxDPS",
+                                                        "lagSurfaceRunoff",
+                                                        "soilDistMPSLPS"))
+
 # text above boxplots - this is from Tukey analysis that was already run below then added to params
@@
 
-ggsave('./figures/burn_unburn_params_tukey_pts.png',
+ggsave('./figures/burn_unburn_params_tukey_pts_reoder.png',
        dpi=600,

### 2025-05-06 state_vars.Rmd
looking at physical properties that are impacted by burn params

--- 2025-05-02 state_vars.Rmd
@@
          month = month(date)) %>%
-  filter(year == 2016,
-         month %in% c(4,5,6))
+  filter(year == 2016) #
+         #month %in% c(4,5,6))
 
@@
 
-```
+both <- bind_rows(unburn, burn)
+
+# interception
+inter <- both %>%
+  dplyr::select(date, type, intercStorage)
+
+int_plot <- ggplot(inter,
+       aes(x=date,,
+           y=intercStorage,
+           color=type)) +
+  geom_line() +
+  theme_bw(base_size=20)
+
+ggplotly(int_plot)
+
+# swe
+swe <- both %>%
+  dplyr::select(date, type, snowTotSWE)
+
+ggplot(swe,
+       aes(x=date,,
+           y=snowTotSWE,
+           color=type)) +
+  geom_line() +
+  theme_bw(base_size=20)
+
+# swe
+p <- both %>%
+  dplyr::select(date, type, precip) %>%
+  group_by(type) %>%
+  mutate(p_cumu = cumsum(precip))
+
+ggplot(p,
+       aes(x=date,
+           y=p_cumu,
+           color=type)) +
+  geom_line() +
+  theme_bw(base_size=20)
+
+# soil sat
+soilsat <- both %>%
+  dplyr::select(date, type, soilSat)
+
+ggplot(soilsat,
+       aes(x=date,
+           y=soilSat,
+           color=type)) +
+  geom_line() +
+  theme_bw(base_size=20)
+
+# surface runoff
+runoff <- both %>%
+  dplyr::select(date, type, outRD1)
+
+ggplot(runoff,
+       aes(x=date,,
+           y=outRD1,
+           color=type)) +
+  geom_line() +
+  theme_bw(base_size=20)
+
+# interflow
+interflow <- both %>%
+  dplyr::select(date, type, outRD2) %>%
+  mutate(interflow_cum = cumsum(outRD2))
+
+ggplot(interflow,
+       aes(x=date,,
+           y=interflow_cum,
+           color=type)) +
+  geom_line() +
+  theme_bw(base_size=20)
+
+gw <- both %>%
+  dplyr::select(date, type, outRG1) %>%
+  mutate(gw_cumu = cumsum(outRG1))
+
+ggplot(gw,
+       aes(x=date,,
+           y=gw_cumu,
+           color=type)) +
+  geom_line() +
+  theme_bw(base_size=20)
+
+# dps
+dps <- both %>%
+  dplyr::select(date, type, actDPS)
+
+ggplot(dps,
+       aes(x=date,,
+           y=actDPS,
+           color=type)) +
+  geom_line() +
+  theme_bw(base_size=20)
+
+# mps
+mps <- both %>%
+  dplyr::select(date, type, soilSatMPS)
+
+ggplot(mps,
+       aes(x=date,,
+           y=soilSatMPS,
+           color=type)) +
+  geom_line() +
+  theme_bw(base_size=20)
+
+# lps
+lps <- both %>%
+  dplyr::select(date, type, soilSatLPS)
+
+ggplot(lps,
+       aes(x=date,,
+           y=soilSatLPS,
+           color=type)) +
+  geom_line() +
+  theme_bw(base_size=20)
+
+# soil sat
+soilsat <- both %>%
+  dplyr::select(date, type, soilSat)
+
+ggplot(soilsat,
+       aes(x=date,,
+           y=soilSat,
+           color=type)) +
+  geom_line() +
+  theme_bw(base_size=20)
+
+## make the actual plot
+p_plot <- ggplot(p, aes(x = date,
+                        y = p_cumu, 
+                        color = type)) +
+  geom_line(size=1, alpha=0.8) +
+    scale_color_manual(values = c("burn" = "red", 
+                                  "unburn" = "black")) +
+  scale_x_date(date_labels = "%b") +
+  labs(x = element_blank(),
+       y = 'Cumulative precipitation (mm)') +
+  theme_bw(base_size = 18) +
+  theme(legend.position = 'bottom',
+    #legend.position = c(0.24, 0.852), 
+    legend.text = element_text(size = 10),
+    legend.title = element_blank(),
+    panel.grid = element_blank(),
+    panel.background = element_rect(fill = "white"),
+    strip.background = element_blank(),
+    text = element_text(color = "black"),
+    axis.title = element_text(color = "black"),
+    axis.text = element_text(color = "black"),
+    legend.key.width = unit(1, "cm")
+  )
+
+p_plot
+
+inter <- inter %>%
+  mutate(type = factor(type, levels = c("unburn", "burn")))
+
+int_plot <- ggplot(inter, aes(x = date,
+                        y = intercStorage, 
+                        color = type)) +
+  geom_line(size=1, alpha=0.7) +
+    scale_color_manual(values = c("burn" = "red", 
+                                  "unburn" = "black")) +
+  scale_x_date(date_labels = "%b") +
+  labs(x = element_blank(),
+       y = 'Interception (mm)') +
+  theme_bw(base_size = 20) +
+  theme(legend.position = 'bottom',
+    #legend.position = c(0.24, 0.852), 
+    legend.text = element_text(size = 10),
+    legend.title = element_blank(),
+    panel.grid = element_blank(),
+    panel.background = element_rect(fill = "white"),
+    strip.background = element_blank(),
+    text = element_text(color = "black"),
+    axis.title = element_text(color = "black"),
+    axis.text = element_text(color = "black"),
+    legend.key.width = unit(1, "cm")
+  )
+
+int_plot
+
+soilsat_plot <- ggplot(soilsat, aes(x = date,
+                        y = soilSat, 
+                        color = type)) +
+  geom_line(size=1, alpha=0.7) +
+    scale_color_manual(values = c("burn" = "red", 
+                                  "unburn" = "black")) +
+  scale_x_date(date_labels = "%b") +
+  labs(x = element_blank(),
+       y = 'Soil saturation') +
+  theme_bw(base_size = 20) +
+  theme(legend.position = 'bottom',
+    #legend.position = c(0.24, 0.852), 
+    legend.text = element_text(size = 10),
+    legend.title = element_blank(),
+    panel.grid = element_blank(),
+    panel.background = element_rect(fill = "white"),
+    strip.background = element_blank(),
+    text = element_text(color = "black"),
+    axis.title = element_text(color = "black"),
+    axis.text = element_text(color = "black"),
+    legend.key.width = unit(1, "cm")
+  )
+
+soilsat_plot
+
+interflow_plot <- ggplot(interflow, aes(x = date,
+                        y = interflow_cum, 
+                        color = type)) +
+  geom_line(size=1, alpha=0.7) +
+    scale_color_manual(values = c("burn" = "red", 
+                                  "unburn" = "black")) +
+  scale_x_date(date_labels = "%b") +
+  labs(x = element_blank(),
+       y = 'Interflow (L)') +
+  theme_bw(base_size = 20) +
+  theme(legend.position = 'bottom',
+    #legend.position = c(0.24, 0.852), 
+    legend.text = element_text(size = 10),
+    legend.title = element_blank(),
+    panel.grid = element_blank(),
+    panel.background = element_rect(fill = "white"),
+    strip.background = element_blank(),
+    text = element_text(color = "black"),
+    axis.title = element_text(color = "black"),
+    axis.text = element_text(color = "black"),
+    legend.key.width = unit(1, "cm")
+  )
+
+interflow_plot
+
+gw_plot <- ggplot(gw, aes(x = date,
+                        y = gw_cumu, 
+                        color = type)) +
+  geom_line(size=1, alpha=0.7) +
+    scale_color_manual(values = c("burn" = "red", 
+                                  "unburn" = "black")) +
+  scale_x_date(date_labels = "%b") +
+  labs(x = element_blank(),
+       y = 'Shallow groundwater (L)') +
+  theme_bw(base_size = 20) +
+  theme(legend.position = 'bottom',
+    #legend.position = c(0.24, 0.852), 
+    legend.text = element_text(size = 10),
+    legend.title = element_blank(),
+    panel.grid = element_blank(),
+    panel.background = element_rect(fill = "white"),
+    strip.background = element_blank(),
+    text = element_text(color = "black"),
+    axis.title = element_text(color = "black"),
+    axis.text = element_text(color = "black"),
+    legend.key.width = unit(1, "cm")
+  )
+
+gw_plot
+
+swe_plot <- ggplot(swe, aes(x = date,
+                        y = snowTotSWE, 
+                        color = type)) +
+  geom_line(size=1, alpha=0.7) +
+    scale_color_manual(values = c("burn" = "red", 
+                                  "unburn" = "black")) +
+  scale_x_date(date_labels = "%b") +
+  labs(x = element_blank(),
+       y = 'SWE (mm)') +
+  theme_bw(base_size = 20) +
+  theme(legend.position = 'bottom',
+    #legend.position = c(0.24, 0.852), 
+    legend.text = element_text(size = 10),
+    legend.title = element_blank(),
+    panel.grid = element_blank(),
+    panel.background = element_rect(fill = "white"),
+    strip.background = element_blank(),
+    text = element_text(color = "black"),
+    axis.title = element_text(color = "black"),
+    axis.text = element_text(color = "black"),
+    legend.key.width = unit(1, "cm")
+  )
+
+swe_plot
+
+legend <- cowplot::get_plot_component(p_plot, "guide-box", return_all = TRUE)[[3]]
+
+p_plot <- p_plot + theme(legend.position = "none")
+int_plot <- int_plot + theme(legend.position = "none")
+soilsat_plot <- soilsat_plot + theme(legend.position = "none")
+interflow_plot <- interflow_plot + theme(legend.position = "none")
+gw_plot <- gw_plot + theme(legend.position = "none")
+swe_plot <- swe_plot + theme(legend.position = "none")
+
+plots <- plot_grid(p_plot,
+          int_plot,
+          swe_plot,
+          soilsat_plot,
+          interflow_plot,
+          gw_plot,
+          ncol = 3)
+
+final_plot <- plot_grid(
+  plots,
+  legend,
+  ncol = 1,
+  rel_heights = c(1, 0.07)  # Adjust height of legend
+)
+
+final_plot
+
+ggsave('./figures/burn_unburn_eg.png')
+
+soilsat_mean <- soilsat %>% 
+  group_by(type) %>% 
+  summarize(mean_ss = mean(soilSat))
+
+soilsat_mean
+
+intercep_mean <- inter %>% 
+  group_by(type) %>% 
+  summarize(mean_inter = mean(intercStorage))
+
+intercep_mean
+
+```

### 2025-05-09 fourmile_output_dec2024.Rmd
added flow partition summary

@@
 
-ggplot(gw, aes(x=date, color = source)) +
-  geom_line(aes(y=catchmentRD1_w), size =1) +
-  facet_wrap(~year, scales="free", ncol = 2) +
-  scale_x_date(labels = date_format("%b")) +
-  ggtitle('RD1') +
-  theme(text = element_text(size = 20)) +
-  labs(y = 'RD1 (mm)') +
-  theme_bw(base_size=20)
-
-ggplot(gw, aes(x=date, color = source)) +
-  geom_line(aes(y=catchmentRD2_w), size =1) +
-  facet_wrap(~year, scales = 'free', ncol = 2) +
-  scale_x_date(labels = date_format("%b")) +
-  ggtitle('RD2') +
-  theme(text = element_text(size = 20))+
-  labs(y = 'RD2 (mm)')+
-  theme_bw(base_size=20)
-
-ggplot(gw, aes(x=date, color = source)) +
-  geom_line(aes(y=catchmentRG1_w), size =1) +
-  facet_wrap(~year, scales = 'free', ncol = 2) +
-  scale_x_date(labels = date_format("%b")) +
-  ggtitle('RG1') +
-  theme(text = element_text(size = 20)) +
-  labs(y = 'RG1 (mm)')+
-  theme_bw(base_size=20)
-
-ggplot(gw, aes(x=date, color = source)) +
-  geom_line(aes(y=catchmentRG2_w), size =1) +
-  facet_wrap(~year, scales = 'free', ncol=2) +
-  scale_x_date(labels = date_format("%b")) +
-  ggtitle('RG2') +
-  theme(text = element_text(size = 20))+
-  labs(y = 'RG2 (mm)')+
-  theme_bw(base_size=20)
+# ggplot(gw, aes(x=date, color = source)) +
+#   geom_line(aes(y=catchmentRD1_w), size =1) +
+#   facet_wrap(~year, scales="free", ncol = 2) +
+#   scale_x_date(labels = date_format("%b")) +
+#   ggtitle('RD1') +
+#   theme(text = element_text(size = 20)) +
+#   labs(y = 'RD1 (mm)') +
+#   theme_bw(base_size=20)
+# 
+# ggplot(gw, aes(x=date, color = source)) +
+#   geom_line(aes(y=catchmentRD2_w), size =1) +
+#   facet_wrap(~year, scales = 'free', ncol = 2) +
+#   scale_x_date(labels = date_format("%b")) +
+#   ggtitle('RD2') +
+#   theme(text = element_text(size = 20))+
+#   labs(y = 'RD2 (mm)')+
+#   theme_bw(base_size=20)
+# 
+# ggplot(gw, aes(x=date, color = source)) +
+#   geom_line(aes(y=catchmentRG1_w), size =1) +
+#   facet_wrap(~year, scales = 'free', ncol = 2) +
+#   scale_x_date(labels = date_format("%b")) +
+#   ggtitle('RG1') +
+#   theme(text = element_text(size = 20)) +
+#   labs(y = 'RG1 (mm)')+
+#   theme_bw(base_size=20)
+# 
+# ggplot(gw, aes(x=date, color = source)) +
+#   geom_line(aes(y=catchmentRG2_w), size =1) +
+#   facet_wrap(~year, scales = 'free', ncol=2) +
+#   scale_x_date(labels = date_format("%b")) +
+#   ggtitle('RG2') +
+#   theme(text = element_text(size = 20))+
+#   labs(y = 'RG2 (mm)')+
+#   theme_bw(base_size=20)
 
@@
 
-ggplot(gw, aes(x=date, color = source)) +
-  geom_line(aes(y=RD1cumsum), size =1) +
-  facet_wrap(~year, scales = 'free', ncol=2) +
-  scale_x_date(labels = date_format("%b")) +
-  ggtitle('Cumulative RD1 (mm)') +
-  theme(text = element_text(size = 20)) +
-  theme_bw(base_size=20)
-
-ggplot(gw, aes(x=date, color = source)) +
-  geom_line(aes(y=RD2cumsum), size = 1) +
-  facet_wrap(~year, scales = 'free', ncol=2) +
-  scale_x_date(labels = date_format("%b")) +
-  ggtitle('Cumulative RD2 (mm)') +
-  theme(text = element_text(size = 20))+
-  theme_bw(base_size=20)
-
-ggplot(gw, aes(x=date, color = source)) +
-  geom_line(aes(y=RG1cumsum), size  = 1) +
-  facet_wrap(~year, scales = 'free', ncol = 2) +
-  scale_x_date(labels = date_format("%b")) +
-  ggtitle('Cumulative RG1 (mm)') +
-  theme(text = element_text(size = 20))+
-  theme_bw(base_size=20)
-
-ggplot(gw, aes(x=date, color = source)) +
-  geom_line(aes(y=RG2cumsum), size =1) +
-  facet_wrap(~year, scales = 'free', ncol = 2) +
-  scale_x_date(labels = date_format("%b")) +
-  ggtitle('Cumulative RG2 (mm)') +
-  theme(text = element_text(size = 20))+
-  theme_bw(base_size=20)
+# ggplot(gw, aes(x=date, color = source)) +
+#   geom_line(aes(y=RD1cumsum), size =1) +
+#   facet_wrap(~year, scales = 'free', ncol=2) +
+#   scale_x_date(labels = date_format("%b")) +
+#   ggtitle('Cumulative RD1 (mm)') +
+#   theme(text = element_text(size = 20)) +
+#   theme_bw(base_size=20)
+# 
+# ggplot(gw, aes(x=date, color = source)) +
+#   geom_line(aes(y=RD2cumsum), size = 1) +
+#   facet_wrap(~year, scales = 'free', ncol=2) +
+#   scale_x_date(labels = date_format("%b")) +
+#   ggtitle('Cumulative RD2 (mm)') +
+#   theme(text = element_text(size = 20))+
+#   theme_bw(base_size=20)
+# 
+# ggplot(gw, aes(x=date, color = source)) +
+#   geom_line(aes(y=RG1cumsum), size  = 1) +
+#   facet_wrap(~year, scales = 'free', ncol = 2) +
+#   scale_x_date(labels = date_format("%b")) +
+#   ggtitle('Cumulative RG1 (mm)') +
+#   theme(text = element_text(size = 20))+
+#   theme_bw(base_size=20)
+# 
+# ggplot(gw, aes(x=date, color = source)) +
+#   geom_line(aes(y=RG2cumsum), size =1) +
+#   facet_wrap(~year, scales = 'free', ncol = 2) +
+#   scale_x_date(labels = date_format("%b")) +
+#   ggtitle('Cumulative RG2 (mm)') +
+#   theme(text = element_text(size = 20))+
+#   theme_bw(base_size=20)
 
@@
   )
+
+flow_summ <- gw_maxcumsum %>%
+  #filter(!year == 2013) %>%
+  group_by(source, flow_type) %>%
+  summarize(min = min(flow_cms),
+            max = max(flow_cms))
 

### 2025-05-15 fourmile_output_dec2024.Rmd
added 1:1 of performance metrics

@@
             grid2020 = KGE(grid_2020, obs),
-            gridall = KGE(grid_all, obs, na.rm = T, method='2012'),
+            gridall = KGE(grid_all, obs, na.rm = T),
             statn2011 = KGE(statn_2011, obs),
@@
             statn2020 = KGE(statn_2020, obs),
-            statnall = KGE(statn_all, obs, na.rm=T, method='2012')) %>%
+            statnall = KGE(statn_all, obs, na.rm=T)) %>%
     mutate_if(is.numeric,
@@
   mutate(year = as.factor(year))
+
+write_csv(flow_plot,
+          '/Users/megansears/Documents/Repos/fourmile/38HRU_dec2024_updates/all_kge.csv')
 
@@
 ```
+
+1:1 performance metrics
+
+```{r}
+
+perf <- read_csv('/Users/megansears/Documents/Repos/fourmile/38HRU_dec2024_updates/all_kge.csv') %>%
+  dplyr::select(year, model_run, value, metric)
+
+perf <- perf %>%
+  pivot_wider(names_from=metric,
+               values_from=value)
+
+nse_kge <- ggplot(perf, aes(x=kge, y=nse)) + 
+  geom_point(size=1) +
+  geom_abline(slope = 1, intercept = 0, linetype = "dashed", color = "red") +
+  theme_bw(base_size=20) # +
+  # ylim(-0,1) +
+  # xlim(0,1)
+
+ggplotly(nse_kge)
+
+ggplot(perf, aes(x=kge, y=pbias)) + 
+  geom_point(size=1) +
+  geom_abline(slope = 1, intercept = 0, linetype = "dashed", color = "red")
+
+```

### 2025-05-18 fourmile_output_dec2024.Rmd
added kge vs nse and kge vs pbias plots

@@
   mutate(year = as.factor(year))
+
+# add all to the plot below
+kge_all <- flow_kge_all %>%
+  mutate(year = 'All') %>%
+  rename(model_run = name,
+         kge = value)
+
+flow_plot <- bind_rows(flow_plot, kge_all)
 
@@
 
-1:1 performance metrics
+# 1:1 performance metrics
 
@@
 
-perf <- read_csv('/Users/megansears/Documents/Repos/fourmile/38HRU_dec2024_updates/all_kge.csv') %>%
-  dplyr::select(year, model_run, value, metric)
+perf <- read_csv('/Users/megansears/Documents/Repos/fourmile/38HRU_dec2024_updates/perf_metrics.csv')
 
@@
   pivot_wider(names_from=metric,
-               values_from=value)
-
-nse_kge <- ggplot(perf, aes(x=kge, y=nse)) + 
-  geom_point(size=1) +
-  geom_abline(slope = 1, intercept = 0, linetype = "dashed", color = "red") +
-  theme_bw(base_size=20) # +
-  # ylim(-0,1) +
-  # xlim(0,1)
-
-ggplotly(nse_kge)
-
-ggplot(perf, aes(x=kge, y=pbias)) + 
-  geom_point(size=1) +
-  geom_abline(slope = 1, intercept = 0, linetype = "dashed", color = "red")
-
-```
+               values_from=value) %>%
+  filter(year == 'All')
+
+perf1 <- perf %>%
+  mutate(type = case_when(
+    str_detect(model_run, "grid") ~ "Gridded",
+    str_detect(model_run, "statn") ~ "Station"))
+
+nse_kge <- ggplot(perf1, aes(x=KGE, y=NSE, color=type)) + 
+  geom_point(size=4, alpha=0.8) +
+  theme_bw(base_size=20) +
+  scale_color_manual(values = c("#0047AB", "orange")) +
+  theme(
+    legend.position = 'bottom',
+    legend.text = element_text(size = 16),
+    legend.title = element_blank(),
+    panel.background = element_rect(fill = "white"),
+    strip.background = element_blank(),
+    text = element_text(color = "black"),
+    axis.title = element_text(color = "black"),
+    axis.text = element_text(color = "black"),
+    panel.grid.major.x = element_blank()  # remove vertical major grid lines
+   # panel.grid.minor.x = element_blank(),
+    #panel.grid.minor = element_blank()      # remove all minor grid lines
+
+  )
+
+nse_kge
+
+pbias_kge <- ggplot(perf1, aes(x=KGE, y=pbias, color=type)) + 
+  geom_point(size=4, alpha=0.8) +
+  theme_bw(base_size=20) +
+  scale_color_manual(values = c("#0047AB", "orange")) +
+  labs(y = '% bias') +
+  theme(
+    legend.position = 'bottom',
+    legend.text = element_text(size = 16),
+    legend.title = element_blank(),
+    panel.background = element_rect(fill = "white"),
+    strip.background = element_blank(),
+    text = element_text(color = "black"),
+    axis.title = element_text(color = "black"),
+    axis.text = element_text(color = "black"),
+    panel.grid.major.x = element_blank()  # remove vertical major grid lines
+   # panel.grid.minor.x = element_blank(),
+    #panel.grid.minor = element_blank()      # remove all minor grid lines
+
+  )
+
+pbias_kge
+
+library(patchwork)
+
+combined_plot <- nse_kge + pbias_kge + 
+  plot_layout(ncol = 2, guides = "collect") & 
+  theme(legend.position = 'bottom')
+
+combined_plot
+
+ggsave('/Users/megansears/Documents/Repos/fourmile/figures/kge_nse_pbias.png',
+       dpi=600,
+       width=10,
+       height=6)
+
+```

### 2025-05-21 fourmile_output_dec2024.Rmd
udpated kge vs bias and kge vs nse to add jitter

--- 2025-05-15 fourmile_output_dec2024.Rmd
@@
   pivot_wider(names_from=metric,
-               values_from=value)
-
-nse_kge <- ggplot(perf, aes(x=kge, y=nse)) + 
-  geom_point(size=1) +
-  geom_abline(slope = 1, intercept = 0, linetype = "dashed", color = "red") +
-  theme_bw(base_size=20) # +
-  # ylim(-0,1) +
-  # xlim(0,1)
-
-ggplotly(nse_kge)
-
-ggplot(perf, aes(x=kge, y=pbias)) + 
-  geom_point(size=1) +
-  geom_abline(slope = 1, intercept = 0, linetype = "dashed", color = "red")
-
-```
+               values_from=value) %>%
+  filter(year == 'All')
+
+perf1 <- perf %>%
+  mutate(type = case_when(
+    str_detect(model_run, "grid") ~ "Gridded",
+    str_detect(model_run, "statn") ~ "Station"))
+
+nse_kge <- ggplot(perf1, aes(x=KGE, y=NSE, color=type)) + 
+  #geom_point(size=4, alpha=0.7) +
+   geom_jitter(size = 4, alpha = 0.7, width = 0.05, height = 0.05) +
+  theme_bw(base_size=20) +
+  scale_color_manual(values = c("#0047AB", "orange")) +
+  theme(
+    legend.position = 'bottom',
+    legend.text = element_text(size = 16),
+    legend.title = element_blank(),
+    panel.background = element_rect(fill = "white"),
+    strip.background = element_blank(),
+    text = element_text(color = "black"),
+    axis.title = element_text(color = "black"),
+    axis.text = element_text(color = "black"),
+    panel.grid.major.x = element_blank()  # remove vertical major grid lines
+   # panel.grid.minor.x = element_blank(),
+    #panel.grid.minor = element_blank()      # remove all minor grid lines
+
+  )
+
+nse_kge
+
+pbias_kge <- ggplot(perf1, aes(x=KGE, y=pbias, color=type)) + 
+  #geom_point(size=4, alpha=0.8) +
+  geom_jitter(size = 4, alpha = 0.7, width = 0.001, height = 0.001) +
+  theme_bw(base_size=20) +
+  scale_color_manual(values = c("#0047AB", "orange")) +
+  labs(y = '% bias') +
+  theme(
+    legend.position = 'bottom',
+    legend.text = element_text(size = 16),
+    legend.title = element_blank(),
+    panel.background = element_rect(fill = "white"),
+    strip.background = element_blank(),
+    text = element_text(color = "black"),
+    axis.title = element_text(color = "black"),
+    axis.text = element_text(color = "black"),
+    panel.grid.major.x = element_blank()  # remove vertical major grid lines
+   # panel.grid.minor.x = element_blank(),
+    #panel.grid.minor = element_blank()      # remove all minor grid lines
+
+  )
+
+pbias_kge
+
+library(patchwork)
+
+combined_plot <- nse_kge + pbias_kge + 
+  plot_layout(ncol = 2, guides = "collect") & 
+  theme(legend.position = 'bottom')
+
+combined_plot
+
+ggsave('/Users/megansears/Documents/Repos/fourmile/figures/kge_nse_pbias.png',
+       dpi=600,
+       width=10,
+       height=6)
+
+```

### 2025-08-28 spatial_figs.Rmd
summary stats for obs Q
updated fig 2 and 3 based on reviewer comments

@@
 
+# get the location of the stream gauge
+gauge <- locations %>%
+  filter(display == 'stream')
+
 ####
@@
   geom_sf(data = hrus_map_rh, aes(fill = diff), color = "black", lwd = 0.2) +
+  geom_sf(data=gauge, shape=3, size=2, stroke=2) +
   scale_fill_viridis_c(option = "viridis", name = "RH (%)") +
@@
   geom_sf(data = hrus_map_solrad, aes(fill = diff), color = "black", lwd = 0.2) +
+  geom_sf(data=gauge, shape=3, size=2, stroke=2) +
   scale_fill_viridis_c(option = "cividis", name = expression("Srad (MJ/m"^"2" * ")")) +
@@
   geom_sf(data = hrus_map_precip, aes(fill = precip_avg_cumdiff), color = "black", lwd = 0.2) +
+  geom_sf(data=gauge, shape=3, size=2, stroke=2) +
   scale_fill_viridis_c(option = "mako", name = "Cumulative P (mm)") +
@@
   geom_sf(data = hrus_map_tmean, aes(fill = diff), color = "black", lwd = 0.2) +
+  geom_sf(data=gauge, shape=3, size=2, stroke=2) +
   scale_fill_viridis_c(option = "plasma", name = "Tmean (°C)",
@@
 
-ggsave(filename = "./figures/diff_update2_wtitle.png", 
+ggsave(filename = "./figures/diff_update2_wtitle&gauge.png",
        plot = final_plot,
-       dpi = 600)
+       dpi = 800,
+       bg = 'white',
+       width = 12,
+       height = 8,
+       limitsize = FALSE)
 
@@
          x = element_blank()) +
+    scale_x_date(
+    date_breaks = "1 year",          # one tick per year
+    date_labels = "%Y"               # show only the year
+  ) +
    theme(
@@
 
-ggsave("/Users/megansears/Documents/Repos/fourmile/figures/flow_obs_plot2.png", dpi = 600, width = 12, height = 4, units = "in")
+ggsave("/Users/megansears/Documents/Repos/fourmile/figures/flow_obs_plot2_eachyrlabel.png", dpi = 600, width = 12, height = 4, units = "in")
 
@@
   summarize(flow_tot = sum(obs, na.rm=T))
+
+flowTotYr <- flow %>%
+  group_by(year) %>%
+  summarize(flow_tot = mean(obs, na.rm=T))
+
+flowTotYr <- flow %>%
+  group_by(year) %>%
+  summarize(flow_tot = max(obs, na.rm=T))
 
@@
   group_by(month, year, site) %>%
-  summarize(p_sum = sum(precip)) %>%
-  group_by(month, site) %>%
-  summarize(avg_p = mean(p_sum),
-          sd_p = sd(p_sum))
+  summarize(p_sum = sum(precip)) # %>%
+  # group_by(month, site) %>%
+  # summarize(avg_p = mean(p_sum),
+  #         sd_p = sd(p_sum))
 
@@
 
-p_cols <- catchment_mo2 %>% 
+catchment_mo_sum2 <- catchment_mo_sum %>%
+  mutate(month_name = month.abb[month]) %>%
+  mutate(month_name = factor(month_name, 
+                             levels = c('Jan', 'Feb', 'Mar',
+                                        'Apr', 'May', 'Jun',
+                                        'Jul', 'Aug', 'Sep',
+                                        'Oct', 'Nov', 'Dec')))
+
+p_box <- catchment_mo_sum2 %>% 
   filter(month_name %in% c('Jun','Jul','Aug', 'Sep')) %>%
-  ggplot(., aes(x = month_name, y = avg_p,
-                                    color = site, fill = site)) +
-  geom_col(position = 'dodge') +
-  geom_errorbar(aes(ymin = 0, ymax = avg_p + sd_p), 
-                position = position_dodge(width = 0.6), width = 0.2) +
-  scale_color_manual(values = c("#0047AB", "orange"),
-                     labels = c("Gridded", "Station")) +  # Rename color legend items
+  ggplot(., aes(x = month_name, y = p_sum, fill = site)) +
+  geom_boxplot() +
+  ylim(0,150) +
+  # geom_errorbar(aes(ymin = 0, ymax = avg_p + sd_p), 
+  #               position = position_dodge(width = 0.6), width = 0.2) +
+  # scale_color_manual(values = c("#0047AB", "orange"),
+  #                    labels = c("Gridded", "Station")) +  # Rename color legend items
   scale_fill_manual(values = c("#0047AB", "orange"),
@@
        x = element_blank()) +
-  guides(color = guide_legend(title = NULL),
-         fill = guide_legend(title = NULL)) +
+  # guides(color = guide_legend(title = NULL),
+  #        fill = guide_legend(title = NULL)) +
+    guides(
+    fill = guide_legend(
+      title = NULL,
+      override.aes = list(shape = NA, linetype = 0)  # remove boxplot look
+    )) +
     theme(
@@
 
-p_cols
-
-ggsave("/Users/megansears/Documents/Repos/fourmile/figures/precip.png", plot = p_cols, width = 8, height = 6, dpi = 300)
+p_box
+
+ggsave("/Users/megansears/Documents/Repos/fourmile/figures/precip_box.png", plot = p_cols, width = 8, height = 6, dpi = 300)
 
@@
 
-quad <- ggarrange(p_cols, 
+quad <- ggarrange(p_box, 
           t_moplot,
@@
 
-ggsave("/Users/megansears/Documents/Repos/fourmile/figures/quad_20250329.png", plot = quad, dpi = 600)
-
-quad_plus <- ggarrange(flow_plot2,quad,
-                       nrow=2)
+ggsave("/Users/megansears/Documents/Repos/fourmile/figures/quad_20250329_timEdits.png", plot = quad, dpi = 600)
+
+quad_plus <- ggarrange(
+  flow_plot2, quad,
+  nrow = 2,
+  heights = c(1, 2)   # first row gets 1 part, second gets 2 parts
+)
+
 quad_plus
 
-ggsave("/Users/megansears/Documents/Repos/fourmile/figures/quad_plus_20250329.png", plot = quad_plus, dpi = 600)
+ggsave("/Users/megansears/Documents/Repos/fourmile/figures/quad_plus_timEdits.png", plot = quad_plus, dpi = 600,
+       width = 14,
+       height = 12,
+       bg='white')
 

### 2025-09-02 fourmile_output_dec2024.Rmd
cleaning up fig4 - moved to manuscriptFig Rmd

@@
 
-write_csv(nseCats, '/Users/megansears/Documents/Repos/fourmile/38HRU_dec2024_updates/nseCats.csv')
+#write_csv(nseCats, '/Users/megansears/Documents/Repos/fourmile/38HRU_dec2024_updates/nseCats.csv')
 
@@
 
+both_nse_plot <- nseCats %>%
+  ggplot(aes(x = year, 
+             y = year_excluded, 
+             fill = nseCat)) +
+  geom_tile(color = "white") +
+  facet_wrap(~source, labeller = labeller(source = new_facet_titles)) +
+  scale_fill_manual(values = c(
+    "Unsatisfactory" = "#F1F4EEFF", 
+    "Satisfactory"  = "#EFDDCFFF",
+    "Good"          = "#72E1E1FF",
+    "Very good"     = "#009474FF"
+  )) +
+  geom_text(aes(label = sprintf("%.2f", nse), color = nseCat), 
+            size = 2.75) +
+  scale_color_manual(values = c(
+    "Unsatisfactory" = "black",
+    "Satisfactory"   = "black",
+    "Good"           = "black",
+    "Very good"      = "white"
+  ), guide = "none") +
+  theme_bw(base_size=18) +
+  theme(
+    axis.text.x = element_text(angle = 45, hjust = 1),
+    legend.position = 'bottom',
+    legend.text = element_text(size = 14),
+    legend.title = element_text(size = 14),
+    legend.key.width = unit(1, "cm"),
+    panel.grid = element_blank(),
+    panel.background = element_rect(fill = "white"),
+    strip.background = element_blank(),
+    text = element_text(color = "black"),
+    axis.title = element_text(color = "black"),
+    axis.text = element_text(color = "black"),
+    plot.margin = margin(t = 10, r = 10, b = 10, l = 10),
+    legend.margin = margin(t = -8, b = -4, unit = "pt")
+  ) +
+  labs(y = "Year excluded",
+       x = 'Year',
+       fill = 'NSE')
+
+both_nse_plot
+
+ggsave('/Users/megansears/Documents/Repos/fourmile/figures/nse_heatmap_both_cats_whiteft.png',
+       dpi=600,
+       width = 10,
+       height = 6)
+
 ```
@@
 
-write_csv(flow_plot,
-          '/Users/megansears/Documents/Repos/fourmile/38HRU_dec2024_updates/all_kge.csv')
+# write_csv(flow_plot,
+#           '/Users/megansears/Documents/Repos/fourmile/38HRU_dec2024_updates/all_kge.csv')
 
@@
   facet_wrap(~source, labeller = labeller(source = new_facet_titles)) +
-  #paletteer::scale_fill_paletteer_d("PNWColors::Anemone") +
-  # paletteer::scale_fill_paletteer_d(
-  # "PNWColors::Anemone", 
-  # guide = guide_legend(nrow = 1),
-  # direction = -1) +
    scale_fill_manual(values = c(
@@
     guide = guide_legend(nrow = 1)) +
-  geom_text(aes(label = sprintf("%.2f", 
-                                kge)), 
-            color = "black", 
+  # geom_text(aes(label = sprintf("%.2f", 
+  #                               kge)), 
+  #           color = "black", 
+  #           size = 3) +
+    geom_text(aes(label = sprintf("%.2f", kge), 
+                color = kge_revise_bins), 
             size = 3) +
+  scale_color_manual(values = c(
+    "< 0.0"   = "black",
+    "0.0-0.2" = "black",
+    "0.2-0.4" = "black",
+    "0.4-0.6" = "black",
+    "0.6-0.8" = "black",
+    "> 0.8"   = "white"
+  ), guide = "none") +
   theme_bw(base_size=18) +
@@
 
-ggsave('/Users/megansears/Documents/Repos/fourmile/figures/kge_heatmap_both_basic.png',
-       dpi=600,
+ggsave('/Users/megansears/Documents/Repos/fourmile/figures/kge_heatmap_whiteft.png',
+       dpi=800,
        width = 10,
@@
 
-write_csv(pbiasCats, '/Users/megansears/Documents/Repos/fourmile/38HRU_dec2024_updates/pbiasCats.csv')
+#write_csv(pbiasCats, '/Users/megansears/Documents/Repos/fourmile/38HRU_dec2024_updates/pbiasCats.csv')
 
@@
     "Very good" = "#009474FF"
-  )) +
-  geom_text(aes(label = sprintf("%.2f", pbias)), 
-            color = "black", 
+  ),
+  #guide = guide_legend(ncol = 1)
+  ) +
+  # geom_text(aes(label = sprintf("%.2f", pbias)), 
+  #           color = "black", 
+  #           size = 2.75) +
+  geom_text(aes(label = sprintf("%0.1f", pbias),   # one decimal place
+                color = pbiasCat), 
             size = 2.75) +
+  scale_color_manual(values = c(
+    "Unsatisfactory" = "black",
+    "Satisfactory"   = "black",
+    "Good"           = "black",
+    "Very good"      = "white"
+  ), guide = "none") + 
   theme_bw(base_size=18) +
@@
 
-ggsave('/Users/megansears/Documents/Repos/fourmile/figures/pbias_heatmap_both_cats.png',
-       dpi=600,
+ggsave('/Users/megansears/Documents/Repos/fourmile/figures/pbias_heatmap_whiteft.png',
+       dpi=800,
        width = 10,
        height = 6)
+
+plot_grid(both_kge_plot,
+          both_pbias_plot,
+          both_nse_plot,
+          ncol=1,
+          labels = c("a) KGE", 
+                     "b) Bias", 
+                     "c) NSE"),
+          label_size = 18,
+          label_fontface = "bold",
+          label_x = 0.02,
+          label_y = 0.98
+)
+
+ggsave('/Users/megansears/Documents/Repos/fourmile/figures/heatmap_metrics.png',
+       dpi=800,
+       width = 10,
+       height = 14)
+
+########
+
+# Top plot
+top_plot <- both_kge_plot +
+  theme(
+    axis.title.x = element_blank(),
+    axis.text.x  = element_blank(),
+    axis.ticks.x = element_blank(),
+    legend.position = "none",
+    plot.margin = margin(5, 5, 5, 40)   # add space on the left
+  )
+
+# Middle plot
+middle_plot <- both_pbias_plot +
+  theme(
+    strip.text = element_blank(),
+    axis.title.x = element_blank(),
+    axis.text.x  = element_blank(),
+    axis.ticks.x = element_blank(),
+    legend.position = "none",
+    plot.margin = margin(5, 5, 5, 40)   # add space on the left
+  )
+
+# Bottom plot
+bottom_plot <- both_nse_plot +
+  theme(
+    strip.text = element_blank(),
+    legend.position = "none",
+    plot.margin = margin(5, 5, 5, 40)   # add space on the left
+  )
+
+# Combine plots
+final_grid <- plot_grid(
+  top_plot,
+  middle_plot,
+  bottom_plot,
+  ncol = 1,
+  labels = c("a) KGE", "b) Bias", "c) NSE"),
+  label_size = 16,
+  label_fontface = "bold",
+  label_x = -0.03,
+  label_y = 1.04,
+  rel_heights = c(1.1, 1, 1.2),
+  align = "v",
+  axis = "l"
+)
+
+final_grid_add <- final_grid +
+  theme(plot.margin = margin(20, 5, 5, 5))
+
+ggsave('/Users/megansears/Documents/Repos/fourmile/figures/heatmap_metrics.pdf',
+       dpi=800,
+       width = 10,
+       height = 14,
+       bg='white')
 

### 2025-09-02 manuscriptFigures.Rmd
Code for manuscript figures

---
title: "Manuscript figures"
author: "Megan Sears"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = F,
  message = F, 
  warning  = F)

library(tidyverse)
library(plotly)
library(kableExtra)
library(hydroGOF)
library(here)
library(scales)
library(tmap)
library(ggpubr)
library(gridExtra)
library(stringr)
library(cowplot)

```

# Figure 1

```{r}

# this is a spatial map that was started in R and moved to Arc
# put the paths to files below **

```

# Figure 2

Streamflow and climate overview

4 panel met first

```{r}
# Note, it is OK these are pulling from the sept2013 udpate and not dec2024
# because the climate outputs will not change due to changed  obs streamflow (removed 2013 flood Q)
grid <- read_csv("./38HRU_sept2013_updates/grid_all_Catchment.csv",
                 skip=3) %>%
   slice(3:n()) %>%
  dplyr::select(-starts_with('@'),
                -1) %>%
  mutate(date = ymd(time)) %>%
  dplyr::select(-time) %>%
  mutate_if(is.character, as.numeric) %>% 
  mutate(site = 'grid')

statn <- read_csv('./38HRU_sept2013_updates/statn_all_Catchment.csv',
                 skip=3) %>%
   slice(3:n()) %>%
  dplyr::select(-starts_with('@'),
                -1) %>%
  mutate(date = ymd(time)) %>%
  dplyr::select(-time) %>%
  mutate_if(is.character, as.numeric) %>% 
  mutate(site = 'statn')

all <- bind_rows(grid, statn) %>%
  arrange(date)

catchment_mo_mean <- all %>%
  mutate(month = month(date)) %>%
  group_by(site, month) %>%
  summarise(across(tmean:solRad, ~ mean(.x, na.rm = TRUE))) %>%
  dplyr::select(site, month, tmean_mean = tmean, 
                solrad_mean = solRad, rh_mean = rhum)

# sum is for P only
catchment_mo_sum <- all %>%
  dplyr::select(date, precip, site) %>%
  mutate(month = month(date),
         year = year(date)) %>%
  group_by(month, year, site) %>%
  summarize(p_sum = sum(precip))

catchment_mo_sd <- all %>%
  mutate(month = month(date)) %>%
  group_by(site, month) %>%
  summarise(across(tmean:solRad, ~ sd(.x, na.rm = TRUE))) %>%
  dplyr::select(site, month, tmean_sd = tmean, 
                solrad_sd = solRad, rh_sd = rhum)

catchment_mo <- left_join(catchment_mo_mean, catchment_mo_sd, 
                          by = c('month', 'site'))

catchment_mo <- left_join(catchment_mo, catchment_mo_sum)

catchment_mo2 <- catchment_mo %>%
  mutate(month_name = month.abb[month]) %>%
  mutate(month_name = factor(month_name, 
                             levels = c('Jan', 'Feb', 'Mar',
                                        'Apr', 'May', 'Jun',
                                        'Jul', 'Aug', 'Sep',
                                        'Oct', 'Nov', 'Dec')))
# add month for P
catchment_mo_sum2 <- catchment_mo_sum %>%
  mutate(month_name = month.abb[month]) %>%
  mutate(month_name = factor(month_name, 
                             levels = c('Jan', 'Feb', 'Mar',
                                        'Apr', 'May', 'Jun',
                                        'Jul', 'Aug', 'Sep',
                                        'Oct', 'Nov', 'Dec')))

# changed P to boxplot per TG comment (instead of cols)
p_box <- catchment_mo_sum2 %>% 
  filter(month_name %in% c('Jun','Jul','Aug', 'Sep')) %>%
  ggplot(., aes(x = month_name, y = p_sum, fill = site)) +
  geom_boxplot() +
  ylim(0,150) + # remove the 2013 flood outliers
  scale_fill_manual(values = c("#0047AB", "orange"),
                    labels = c("Gridded", "Station")) +
  theme_bw(base_size = 20) +
  labs(y = 'Precipitation (mm)',
       x = element_blank()) +
    guides(
    fill = guide_legend(
      title = NULL,
      override.aes = list(shape = NA, linetype = 0)  # remove boxplot look on legend
    )) +
    theme(
    panel.grid = element_blank(),
    panel.background = element_rect(fill = "white"),
    text = element_text(color = "black"),
    axis.title = element_text(color = "black"),
    axis.text = element_text(color = "black"),
    strip.text = element_blank())

p_box

# Temperature plot
t_moplot <- ggplot(catchment_mo2, aes(x = month_name, 
                                      y = tmean_mean, 
                                      color = site, 
                                      group = site)) +
  geom_ribbon(aes(ymin = tmean_mean - tmean_sd, 
                  ymax = tmean_mean + tmean_sd, 
                  fill = site), 
              alpha = 0.6) +
  geom_line() +
  geom_point() +
  scale_color_manual(values = c("#0047AB", "orange"),
                     labels = c("Gridded", "Station")) +
  scale_fill_manual(values = c("#0047AB", "orange"),
                    labels = c("Gridded", "Station")) +
  theme_bw(base_size=20) +
  labs(y = expression("Air temperature " ( degree~C)),
       x = element_blank()) +
  labs(color = NULL, fill = NULL) +
      theme(
    panel.grid = element_blank(),
    panel.background = element_rect(fill = "white"),
    text = element_text(color = "black"),
    axis.title = element_text(color = "black"),
    axis.text = element_text(color = "black"),
    strip.text = element_blank())

# Solar radiation plot
sol_moplot <- ggplot(catchment_mo2, 
                     aes(x = month_name, y = solrad_mean, 
                                         color = site, group = site)) +
  geom_ribbon(aes(ymin = solrad_mean - solrad_sd, 
                  ymax = solrad_mean + solrad_sd, 
                  fill = site), 
              alpha = 0.6) +
  geom_line() +
  geom_point() +
  scale_color_manual(values = c("#0047AB", "orange"),
                     labels = c("Gridded", "Station")) +
  scale_fill_manual(values = c("#0047AB", "orange"),
                    labels = c("Gridded", "Station")) +
  theme_bw(base_size = 20) +
  labs(y = expression("Solar radiation (MJ/m"^"2" * ")"),
       x = element_blank()) +
  labs(color = NULL, fill = NULL) +
      theme(
    panel.grid = element_blank(),
    panel.background = element_rect(fill = "white"),
    text = element_text(color = "black"),
    axis.title = element_text(color = "black"),
    axis.text = element_text(color = "black"),
    strip.text = element_blank())

# Relative humidity plot
rh_moplot <- ggplot(catchment_mo2, 
                    aes(x = month_name, 
                        y = rh_mean, 
                        color = site, 
                        group = site)) +
  geom_ribbon(aes(ymin = rh_mean - rh_sd, 
                  ymax = rh_mean + rh_sd, 
                  fill = site), 
              alpha = 0.6) +
  geom_line() +
  geom_point() +
  scale_color_manual(values = c("#0047AB", "orange"),
                     labels = c("Gridded", "Station")) +
  scale_fill_manual(values = c("#0047AB", "orange"),
                    labels = c("Gridded", "Station")) +
  theme_bw(base_size = 20) +
  labs(y = 'RH (%)', x= element_blank()) +
  labs(color = NULL, fill = NULL) +
      theme(
    panel.grid = element_blank(),
    panel.background = element_rect(fill = "white"),
    text = element_text(color = "black"),
    axis.title = element_text(color = "black"),
    axis.text = element_text(color = "black"),
    strip.text = element_blank())

# pull met panels together
quad <- ggarrange(p_box, 
          t_moplot,
          sol_moplot,
          rh_moplot,
          common.legend = T,
          legend = 'bottom',
          ncol=2,
          nrow=2)

quad

ggsave("./figures/quad_20250329_timEdits.png", 
       plot = quad, 
       dpi = 600)

```

Add in streamflow to 4 panel met

```{r}

flow <- read_csv('./38HRU_dec2024_updates/discharge_all.csv') %>%
  replace(.==-9999, NA) %>%
  rename(date = time) %>%
  mutate(date = mdy(date)) %>%
  dplyr::select(date, obs) %>%
  mutate(year = year(date),
         DOY = yday(date)) #%>%
  #drop_na(obs)

flow_plot2 <- ggplot(flow, aes(x = date, y = obs)) + 
  geom_line(size = 1.1) +
  theme_bw(base_size = 20) +
  labs(y = 'Discharge (cms)',
         x = element_blank()) +
    scale_x_date(
    date_breaks = "1 year",          # one tick per year
    date_labels = "%Y"               # show only the year
  ) +
   theme(
    legend.position = "none",
    panel.grid = element_blank(),
    panel.background = element_rect(fill = "white"),
    strip.background = element_blank(),
    text = element_text(color = "black"),
    axis.title = element_text(color = "black"),
    axis.text = element_text(color = "black"),
    strip.text = element_text(color = "black"))

flow_plot2

ggsave("./figures/flow_obs_plot2_eachyrlabel.png", 
       dpi = 600, 
       width = 12, 
       height = 4, 
       units = "in")

# stats for manuscript text
# annual total flow
flowTotYr <- flow %>%
  group_by(year) %>%
  summarize(flow_tot = sum(obs, na.rm=T))

flowTotYr <- flow %>%
  group_by(year) %>%
  summarize(flow_tot = mean(obs, na.rm=T))

flowTotYr <- flow %>%
  group_by(year) %>%
  summarize(flow_tot = max(obs, na.rm=T))

avgAllYr <- mean(flowTotYr$flow_tot)

```

Add together streamflow and 4 panel met

```{r}

# add streamflow to the top of the met 4 panel
quad_plus <- ggarrange(
  flow_plot2, 
  quad,
  nrow = 2,
  heights = c(1, 2)   # first row gets 1 part, second gets 2 parts
)

quad_plus

ggsave("./figures/figure2.png", 
       plot = quad_plus, 
       dpi = 600,
       width = 14,
       height = 12,
       bg='white')

```

# Figure 3

```{r}

# get HRU shp for maps
hru_new <- st_read('./data/GIS/hrus_final.shp')

# grid first
read_ages_grid <- function(filename){
  read_csv(file.path("./38HRU_sept2013_updates/HRU_output/grid/", 
                     filename), skip = 3) %>%
  slice(3:n()) %>%
  dplyr::select(-starts_with('@'),
                -1) %>%
  mutate(time = ymd(time)) %>%
  mutate_if(is.character, as.numeric) %>%
  mutate(source = 'grid')

}

#pull in all filenames with HRU in the name
filenames <- list.files("./38HRU_sept2013_updates/HRU_output/grid/", 
                        pattern="HRU", 
                        full.names=F)

#read all the csvs using read_ages function
dataframes <- lapply(filenames, read_ages_grid)

#name all the csvs based on first 6 characters
names(dataframes) <- substr(filenames, 1, 6)

#bind all and make 1 df
hru_grids <- dataframes %>%
  bind_rows()

# statn next
read_ages_statn <- function(filename){
  read_csv(file.path("./38HRU_sept2013_updates/HRU_output/statn/", 
                     filename), skip = 3) %>%
  slice(3:n()) %>%
  dplyr::select(-starts_with('@'),
                -1) %>%
  mutate(time = ymd(time)) %>%
  mutate_if(is.character, as.numeric) %>%
  mutate(source = 'statn')

}

#pull in all filenames with HRU in the name
filenames <- list.files("./38HRU_sept2013_updates/HRU_output/statn/", 
                        pattern="HRU", 
                        full.names=F)

#read all the csvs using read_ages function
dataframes <- lapply(filenames, read_ages_statn)

#name all the csvs based on first 6 characters
names(dataframes) <- substr(filenames, 1, 6)

#bind all and make 1 df
hru_statn <- dataframes %>%
  bind_rows()

# Tmean
hru_grid_tmean <- hru_grids %>%
  dplyr::select(c(time, ID, tmean)) %>%
  rename(tmean_grid = tmean)  %>%
  group_by(ID) %>%
  summarize(tmean_all_grid = mean(tmean_grid))

hru_statn_tmean <- hru_statn %>%
  dplyr::select(c(time, ID, tmean)) %>%
  rename(tmean_statn = tmean) %>%
  group_by(ID) %>%
  summarize(tmean_all_statn = mean(tmean_statn))

tmean_hrus <- left_join(hru_grid_tmean, hru_statn_tmean, by = c('ID')) %>%
  mutate(diff = tmean_all_statn - tmean_all_grid) %>%
  rename(value = ID)

hrus_map_tmean <- left_join(hru_new, tmean_hrus, by = 'value')

# Cumulative p
hru_grid_precip <- hru_grids %>%
  dplyr::select(c(time, ID, precip)) %>%
  rename(precip_grid = precip)

hru_statn_precip <- hru_statn %>%
  dplyr::select(c(time, ID, precip)) %>%
  rename(precip_statn = precip)

precip_hrus <- left_join(hru_grid_precip, hru_statn_precip, by = c('time', 'ID')) %>%
  mutate(diff = precip_statn - precip_grid,
         year = year(time)) %>%
  group_by(year, ID) %>%
  mutate(total_diff = cumsum(diff)) %>%
  filter(time == max(time)) %>%
  group_by(ID) %>%
  summarize(precip_avg_cumdiff = mean(total_diff)) %>%
  rename(value = ID)

hrus_map_precip <- left_join(hru_new, precip_hrus, by = 'value')

# Solar rad
hru_grid_solrad <- hru_grids %>%
  dplyr::select(c(time, ID, solRad)) %>%
  rename(solrad_grid = solRad)  %>%
  group_by(ID) %>%
  summarize(solrad_all_grid = mean(solrad_grid))

hru_statn_solrad <- hru_statn %>%
  dplyr::select(c(time, ID, solRad)) %>%
  rename(solrad_statn = solRad) %>%
  group_by(ID) %>%
  summarize(solrad_all_statn = mean(solrad_statn))

solrad_hrus <- left_join(hru_grid_solrad, hru_statn_solrad, by = c('ID')) %>%
  mutate(diff = solrad_all_statn - solrad_all_grid) %>%
  rename(value = ID)

hrus_map_solrad <- left_join(hru_new, solrad_hrus, by = 'value')

# RH
hru_grid_rh <- hru_grids %>%
  dplyr::select(c(time, ID, rhum)) %>%
  rename(rh_grid = rhum)  %>%
  group_by(ID) %>%
  summarize(rh_all_grid = mean(rh_grid))

hru_statn_rh <- hru_statn %>%
  dplyr::select(c(time, ID, rhum)) %>%
  rename(rh_statn = rhum) %>%
  group_by(ID) %>%
  summarize(rh_all_statn = mean(rh_statn))

rh_hrus <- left_join(hru_grid_rh, hru_statn_rh, by = c('ID')) %>%
  mutate(diff = rh_all_statn - rh_all_grid) %>%
  rename(value = ID)

hrus_map_rh <- left_join(hru_new, rh_hrus, by = 'value')

# get the location of the stream gauge
locations <- read_csv('/Users/megansears/Documents/Repos/fourmile/data/GIS/locations_all.csv')

locations <- locations %>%
  st_as_sf(., coords=c('lon','lat'), crs = 4326)

gauge <- locations %>%
  filter(display == 'stream')

# bottom theme for panel fig
bottom_theme <-   theme(
    legend.position = "bottom",
    panel.grid.major = element_blank(),
    legend.key.width = unit(.75, "cm"),
    panel.grid.minor = element_blank(),
    axis.title.x = element_blank(),
    axis.title.y = element_blank(),
    plot.margin = unit(c(-4, 0, 0, 0), "cm"),
    panel.spacing = unit(0, "lines"))

# top theme for panel fig
top_theme <-   theme(
    legend.position = "bottom",
    panel.grid.major = element_blank(),
    legend.key.width = unit(.75, "cm"),
    panel.grid.minor = element_blank(),
    axis.title.x = element_blank(),
    axis.title.y = element_blank(),
    plot.margin = unit(c(0, 0, -4, 0), "cm"),
    panel.spacing = unit(0, "lines"))

# RH panel
rh <- ggplot() +
  geom_sf(data = hrus_map_rh, aes(fill = diff), color = "black", lwd = 0.2) +
  geom_sf(data=gauge, shape=3, size=2, stroke=2) +
  scale_fill_viridis_c(option = "viridis", name = "RH (%)") +
  theme_bw(base_size=15.5) +
  theme_void() + bottom_theme

rh

# Solar rad panel
sr <- ggplot() +
  geom_sf(data = hrus_map_solrad, aes(fill = diff), color = "black", lwd = 0.2) +
  geom_sf(data=gauge, shape=3, size=2, stroke=2) +
  scale_fill_viridis_c(option = "cividis", name = expression("Srad (MJ/m"^"2" * ")")) +
  theme_bw(base_size=15.5) +
  theme_void() + top_theme

sr

# P panel
precip <- ggplot() +
  geom_sf(data = hrus_map_precip, aes(fill = precip_avg_cumdiff), color = "black", lwd = 0.2) +
  geom_sf(data=gauge, shape=3, size=2, stroke=2) +
  scale_fill_viridis_c(option = "mako", name = "Cumulative P (mm)") +
  theme_bw(base_size=15.5) +
  theme_void() + top_theme

precip

# Tmean panel
tmean <- ggplot() +
  geom_sf(data = hrus_map_tmean, aes(fill = diff), color = "black", lwd = 0.2) +
  geom_sf(data=gauge, shape=3, size=2, stroke=2) +
  scale_fill_viridis_c(option = "plasma", name = "Tmean (°C)",
                       limits = c(-5, 2)) +
  theme_bw(base_size=15.5) +
  theme_void() + bottom_theme

tmean

# add the 4 panels togther
lots <- ggarrange(
  precip, 
  sr, 
  rh, 
  tmean,
  heights = 1)

lots

# add ttile
title <- ggdraw() + 
  draw_label("Difference = Station - Gridded", 
             fontface = "bold", 
             size = 16,
             x = 0,  # left-aligned
             hjust = 0) +
  theme(plot.margin = margin(0, 0, -200,15))  # reduce space between title and plot

# Combine title and the main plot
final_plot <- plot_grid(title, 
                        lots, 
                        ncol = 1, 
                        rel_heights = c(0.05, 1))

final_plot

ggsave(filename = "./figures/figure3.pdf",
       plot = final_plot,
       dpi = 800,
       bg = 'white',
       width = 12,
       height = 8,
       limitsize = FALSE)

```

# Figure 4

## KGE

```{r}

# read in KGE values (all_kge also has nse and bias even tho name says otherwise)
flow_plot <- read_csv('./38HRU_dec2024_updates/all_kge.csv') %>%
  filter(metric == 'KGE') %>%
  dplyr::select(-metric) %>%
  rename(kge = value)

# split model run to source and year
# create kge bins for fig
flow_plot_updated <- flow_plot %>% 
  mutate(source = case_when(
    grepl("grid", model_run) ~ "grid",
    grepl("statn", model_run) ~ "statn"),
    year_excluded = str_extract(model_run, "\\d{4}$")) %>%
  mutate(year_excluded = if_else(model_run %in% c('gridall',
                                                       'statnall'),
                                  'None', year_excluded)) %>%
  mutate(kge_revise_bins = cut(kge,
                               breaks = c(-Inf, 0.0, 0.2, 0.4, 0.6, 0.8, 1),
                               include.lowest = TRUE,
                               labels = c("< 0.0","0.0-0.2", "0.2-0.4", "0.4-0.6", "0.6-0.8", "> 0.8")))

# facet wrap titles
new_facet_titles <- c(
  "grid" = "Gridded",
  "statn" = "Station"
)

# kge plot
both_kge_plot <- flow_plot_updated %>%
  ggplot(., aes(x = year, 
              y = year_excluded, 
              fill = kge_revise_bins)) +
  geom_tile(color = "white") +
  facet_wrap(~source, labeller = labeller(source = new_facet_titles)) +
   scale_fill_manual(values = c(
    "< 0.0" = "#DCBE9BFF", 
    "0.0-0.2" = "#EFDDCFFF",
    "0.2-0.4" = "#F1F4EEFF",
    "0.4-0.6" = "#72E1E1FF",
    "0.6-0.8" = "#11C2B5FF",
    "> 0.8" = "#009474FF"),
    guide = guide_legend(nrow = 1)) +
    geom_text(aes(label = sprintf("%.2f", kge), 
                color = kge_revise_bins), 
            size = 3) +
  scale_color_manual(values = c(
    "< 0.0"   = "black",
    "0.0-0.2" = "black",
    "0.2-0.4" = "black",
    "0.4-0.6" = "black",
    "0.6-0.8" = "black",
    "> 0.8"   = "white"
  ), 
  guide = "none") +
  theme_bw(base_size=18) +
  theme(axis.text.x = element_text(angle = 45, 
                                   hjust = 1)) +
  labs(y = "Year excluded",
       x='Year',
       fill = 'KGE') +
  theme(
    axis.text.x = element_text(angle = 45, 
                               hjust = 1),
    legend.position = 'bottom',
    legend.text = element_text(size = 14),
    legend.title = element_text(size = 14),
    legend.key.width = unit(.6, "cm"),
    panel.grid = element_blank(),
    panel.background = element_rect(fill = "white"),
    strip.background = element_blank(),
    text = element_text(color = "black"),
    axis.title = element_text(color = "black"),
    axis.text = element_text(color = "black"),
    plot.margin = margin(t = 10, r = 10, b = 10, l = 10),
    legend.margin = margin(t = -8, b = -4, unit = "pt")
  )

both_kge_plot

# ggsave('./figures/kge_heatmap_whiteft.png',
#        dpi=800,
#        width = 10,
#        height = 6)

```

### KGE legend

```{r}

# kge legend
kge_legend <- flow_plot_updated %>%
  ggplot(., aes(x = year, 
              y = year_excluded, 
              fill = kge_revise_bins)) +
  geom_tile(color = "white") +
  facet_wrap(~source, labeller = labeller(source = new_facet_titles)) +
   scale_fill_manual(values = c(
    "< 0.0" = "#DCBE9BFF", 
    "0.0-0.2" = "#EFDDCFFF",
    "0.2-0.4" = "#F1F4EEFF",
    "0.4-0.6" = "#72E1E1FF",
    "0.6-0.8" = "#11C2B5FF",
    "> 0.8" = "#009474FF"),
    guide = guide_legend(ncol = 1)) +
    geom_text(aes(label = sprintf("%.2f", kge), 
                color = kge_revise_bins), 
            size = 3) +
  scale_color_manual(values = c(
    "< 0.0"   = "black",
    "0.0-0.2" = "black",
    "0.2-0.4" = "black",
    "0.4-0.6" = "black",
    "0.6-0.8" = "black",
    "> 0.8"   = "white"
  ), 
  guide = "none") +
  theme_bw(base_size=18) +
  theme(axis.text.x = element_text(angle = 45, 
                                   hjust = 1)) +
  labs(y = "Year excluded",
       x='Year',
       fill = 'KGE') +
  theme(
    axis.text.x = element_text(angle = 45, 
                               hjust = 1),
    legend.position = 'right',
    legend.text = element_text(size = 14),
    legend.title = element_text(size = 14),
    legend.key.width = unit(.6, "cm"),
    panel.grid = element_blank(),
    panel.background = element_rect(fill = "white"),
    strip.background = element_blank(),
    text = element_text(color = "black"),
    axis.title = element_text(color = "black"),
    axis.text = element_text(color = "black"),
    plot.margin = margin(t = 10, r = 10, b = 10, l = 10),
    legend.margin = margin(t = -8, b = -4, unit = "pt")
  )

kge_legend

# Extract the legend
leg <- ggpubr::get_legend(kge_legend)

# Convert to ggplot
leg_gg <- ggpubr::as_ggplot(leg)

# Plot it
print(leg_gg)

ggsave('./figures/figure4_kgeLegend.png',
       dpi=800,
       width = 12,
       height = 8,
       bg = 'white')

```

## Bias

```{r}

pbiasCats <- read_csv('./38HRU_dec2024_updates/pbiasCats.csv') %>%
  rename(source = input_data)

# plot
both_pbias_plot <- pbiasCats %>%
  ggplot(aes(x = year, 
             y = year_missing, 
             fill = pbiasCat)) +
  geom_tile(color = "white") +
  facet_wrap(~source, labeller = labeller(source = new_facet_titles)) +
   scale_fill_manual(values = c(
    "Unsatisfactory" = "#F1F4EEFF", 
    "Satisfactory" = "#EFDDCFFF",
    "Good" = "#72E1E1FF",
    "Very good" = "#009474FF"
  )) +
  geom_text(aes(label = sprintf("%0.1f", pbias),   # one decimal place
                color = pbiasCat), 
            size = 2.75) +
  scale_color_manual(values = c(
    "Unsatisfactory" = "black",
    "Satisfactory"   = "black",
    "Good"           = "black",
    "Very good"      = "white"
  ), guide = "none") + 
  theme_bw(base_size=18) +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1),
    legend.position = 'bottom',
    legend.text = element_text(size = 14),
    legend.title = element_text(size = 14),
    legend.key.width = unit(1, "cm"),
    panel.grid = element_blank(),
    panel.background = element_rect(fill = "white"),
    strip.background = element_blank(),
    text = element_text(color = "black"),
    axis.title = element_text(color = "black"),
    axis.text = element_text(color = "black"),
    plot.margin = margin(t = 10, r = 10, b = 10, l = 10),
    legend.margin = margin(t = -8, b = -4, unit = "pt")
  ) +
  labs(y = "Year excluded",
       x = 'Year',
       fill = '% bias')

both_pbias_plot

# ggsave('./figures/pbias_heatmap_whiteft.png',
#        dpi=800,
#        width = 10,
#        height = 6)

```

### Bias legend

```{r}

# plot
bias_leg <- pbiasCats %>%
  ggplot(aes(x = year, 
             y = year_missing, 
             fill = pbiasCat)) +
  geom_tile(color = "white") +
  facet_wrap(~source, labeller = labeller(source = new_facet_titles)) +
   scale_fill_manual(values = c(
    "Unsatisfactory" = "#F1F4EEFF", 
    "Satisfactory" = "#EFDDCFFF",
    "Good" = "#72E1E1FF",
    "Very good" = "#009474FF"
  )) +
  geom_text(aes(label = sprintf("%0.1f", pbias),   # one decimal place
                color = pbiasCat), 
            size = 2.75) +
  scale_color_manual(values = c(
    "Unsatisfactory" = "black",
    "Satisfactory"   = "black",
    "Good"           = "black",
    "Very good"      = "white"
  ), guide = "none") + 
  theme_bw(base_size=18) +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1),
    legend.position = 'right',
    legend.text = element_text(size = 14),
    legend.title = element_text(size = 14),
    legend.key.width = unit(1, "cm"),
    panel.grid = element_blank(),
    panel.background = element_rect(fill = "white"),
    strip.background = element_blank(),
    text = element_text(color = "black"),
    axis.title = element_text(color = "black"),
    axis.text = element_text(color = "black"),
    plot.margin = margin(t = 10, r = 10, b = 10, l = 10),
    legend.margin = margin(t = -8, b = -4, unit = "pt")
  ) +
  labs(y = "Year excluded",
       x = 'Year',
       fill = 'Bias')

bias_leg

# Extract the legend
leg <- ggpubr::get_legend(bias_leg)

# Convert to ggplot
leg_gg <- ggpubr::as_ggplot(leg)

# Plot it
print(leg_gg)

ggsave('./figures/figure4_biasLegend.png',
       dpi=800,
       width = 12,
       height = 8,
       bg = 'white')

```

## NSE

```{r}

nseCats <- read_csv('./38HRU_dec2024_updates/nseCats.csv') %>%
  rename(source = input_data)

both_nse_plot <- nseCats %>%
  ggplot(aes(x = year, 
             y = year_missing, 
             fill = nseCat)) +
  geom_tile(color = "white") +
  facet_wrap(~source, labeller = labeller(source = new_facet_titles)) +
  scale_fill_manual(values = c(
    "Unsatisfactory" = "#F1F4EEFF", 
    "Satisfactory"  = "#EFDDCFFF",
    "Good"          = "#72E1E1FF",
    "Very good"     = "#009474FF"
  )) +
  geom_text(aes(label = sprintf("%.2f", nse), color = nseCat), 
            size = 2.75) +
  scale_color_manual(values = c(
    "Unsatisfactory" = "black",
    "Satisfactory"   = "black",
    "Good"           = "black",
    "Very good"      = "white"
  ), guide = "none") +
  theme_bw(base_size=18) +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1),
    legend.position = 'bottom',
    legend.text = element_text(size = 14),
    legend.title = element_text(size = 14),
    legend.key.width = unit(1, "cm"),
    panel.grid = element_blank(),
    panel.background = element_rect(fill = "white"),
    strip.background = element_blank(),
    text = element_text(color = "black"),
    axis.title = element_text(color = "black"),
    axis.text = element_text(color = "black"),
    plot.margin = margin(t = 10, r = 10, b = 10, l = 10),
    legend.margin = margin(t = -8, b = -4, unit = "pt")
  ) +
  labs(y = "Year excluded",
       x = 'Year',
       fill = 'NSE')

both_nse_plot

# ggsave('./figures/nse_heatmap_both_cats_whiteft.png',
#        dpi=600,
#        width = 10,
#        height = 6)

```

### NSE legend

```{r}

nse_leg <- nseCats %>%
  ggplot(aes(x = year, 
             y = year_missing, 
             fill = nseCat)) +
  geom_tile(color = "white") +
  facet_wrap(~source, labeller = labeller(source = new_facet_titles)) +
  scale_fill_manual(values = c(
    "Unsatisfactory" = "#F1F4EEFF", 
    "Satisfactory"  = "#EFDDCFFF",
    "Good"          = "#72E1E1FF",
    "Very good"     = "#009474FF"
  )) +
  geom_text(aes(label = sprintf("%.2f", nse), color = nseCat), 
            size = 2.75) +
  scale_color_manual(values = c(
    "Unsatisfactory" = "black",
    "Satisfactory"   = "black",
    "Good"           = "black",
    "Very good"      = "white"
  ), guide = "none") +
  theme_bw(base_size=18) +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1),
    legend.position = 'right',
    legend.text = element_text(size = 14),
    legend.title = element_text(size = 14),
    legend.key.width = unit(1, "cm"),
    panel.grid = element_blank(),
    panel.background = element_rect(fill = "white"),
    strip.background = element_blank(),
    text = element_text(color = "black"),
    axis.title = element_text(color = "black"),
    axis.text = element_text(color = "black"),
    plot.margin = margin(t = 10, r = 10, b = 10, l = 10),
    legend.margin = margin(t = -8, b = -4, unit = "pt")
  ) +
  labs(y = "Year excluded",
       x = 'Year',
       fill = 'NSE')

nse_leg

# Extract the legend
leg <- ggpubr::get_legend(nse_leg)

# Convert to ggplot
leg_gg <- ggpubr::as_ggplot(leg)

# Plot it
print(leg_gg)

ggsave('./figures/figure4_nseLegend.png',
       dpi=800,
       width = 12,
       height = 8,
       bg = 'white')

```

## Combine

```{r}

# Top plot - KGE
top_plot <- both_kge_plot +
  theme(
    axis.title.x = element_blank(),
    axis.text.x  = element_blank(),
    axis.ticks.x = element_blank(),
    legend.position = "none",
    plot.margin = margin(5, 5, 5, 40)   # add space on the left
  )

# Middle plot - Bias
middle_plot <- both_pbias_plot +
  theme(
    strip.text = element_blank(),
    axis.title.x = element_blank(),
    axis.text.x  = element_blank(),
    axis.ticks.x = element_blank(),
    legend.position = "none",
    plot.margin = margin(5, 5, 5, 40)   # add space on the left
  )

# Bottom plot - NSE
bottom_plot <- both_nse_plot +
  theme(
    strip.text = element_blank(),
    legend.position = "none",
    plot.margin = margin(5, 5, 5, 40)   # add space on the left
  )

# Combine plots
final_grid <- plot_grid(
  top_plot,
  middle_plot,
  bottom_plot,
  ncol = 1,
  labels = c("a) KGE", "b) Bias", "c) NSE"),
  label_size = 16,
  label_fontface = "bold",
  label_x = -0.03,
  label_y = 1.04,
  rel_heights = c(1.1, 1, 1.2),
  align = "v",
  axis = "l"
)

final_grid_add <- final_grid +
  theme(plot.margin = margin(20, 5, 5, 5))

# ggsave('./figures/figure4_main.pdf',
#        dpi=800,
#        width = 10,
#        height = 14,
#        bg='white')

```

# Figure 5

```{r}

```

# Figure 6

# Figure 7

# Figure 8

# Figure 9

# Figure 10

# Figure 11

### 2025-09-02 manuscriptFigures.Rmd
edits for fig 5-7

@@
 
+# params area weighted (only for lagSurfaceRunoff, a_rain, a_snow)
+params <- read_csv('./38HRU_dec2024_updates/params_weighted_dec2024.csv') %>%
+  filter(param %in% c('lagSurfaceRunoff',
+                      'a_rain',
+                      'a_snow')) %>% # select params in the top 8 sens that are area weighted
+  rename(value = area_weighted_average,
+         input_data = source) %>%
+  dplyr::select(param, input_data, year_missing, value)
+
+# params unburned (above is params that needed to be area weighted bc burn/unburn)
+params_unburn <- read_csv('./38HRU_dec2024_updates/params_unburn.csv') %>%
+  filter(param %in% c('soilOutLPS',
+                      'snow_trs',
+                      'lagInterflow',
+                      'baseTemp',
+                      't_factor',
+                      'soilLatVertLPS')) %>%
+  dplyr::select(param, input_data, year_missing, value) %>%
+  mutate(year_missing = if_else(year_missing == 'none',
+                                'all',
+                                year_missing))
+
+# join the two to get the top 8 sensitve params
+param_sens <- bind_rows(params, params_unburn) %>% 
+  mutate(input_data = if_else(input_data == 'grid',
+                              'Gridded',
+                              'Station'))
+
+# read in pbias categories
+pbias <- read_csv('./38HRU_dec2024_updates/pbiasCats.csv') %>%
+  filter(year == c('All')) %>%
+  dplyr::select(input_data, year_missing, pbias)
+
+nse <- read_csv('./38HRU_dec2024_updates/nseCats.csv') %>%
+  filter(year == c('All')) %>%
+  dplyr::select(input_data, year_missing, nse)
+
+perf <- left_join(nse, pbias, by = c('input_data',
+                                     'year_missing'))
+
+perf <- perf %>%
+  mutate(performance = case_when(
+                                nse < 0.5 & abs(pbias) >= 25 ~ 'Neither',
+                                nse > 0.5 & abs(pbias) >= 25 ~ 'NSE',
+                                nse < 0.5 & abs(pbias) < 25 ~ '% bias satisfactory',
+                                nse > 0.5 & abs(pbias) < 25 ~ 'NSE + % bias satisfactory')) %>%
+  mutate(input_data = if_else(input_data == 'grid',
+                              'Gridded', 'Station'),
+         year_missing = if_else(year_missing == 'None',
+                                'all', year_missing))
+
+param_sens <- left_join(param_sens,
+                        perf,
+                        by = c('input_data',
+                               'year_missing'))
+
+param_sens$param <- fct_recode(param_sens$param,
+  "snow_trs"        = "snow_trs",
+  "baseTemp (°C)"      = "baseTemp",
+  "t_factor"    = "t_factor",
+  "a_rain (mm)"      = "a_rain",
+  "a_snow (mm)"      = "a_snow",
+  "lagSurfaceRunoff"    = "lagSurfaceRunoff",
+  "soilLatVertLPS"      = "soilLatVertLPS",
+  "soilOutLPS"       = "soilOutLPS",
+  "lagInterflow"         = "lagInterflow"
+)
+
+param_sens$param <- fct_relevel(param_sens$param, 
+                                "snow_trs",
+                                "baseTemp (°C)",
+                                "t_factor",
+                                "a_rain (mm)",
+                                "a_snow (mm)",
+                                "lagSurfaceRunoff",
+                                "soilLatVertLPS",
+                                "soilOutLPS",
+                                "lagInterflow")
+
+# boxplots of top 9
+ggplot(param_sens, aes(x=input_data, y=value, fill=input_data)) +
+  geom_boxplot(alpha=0.8,
+                outlier.shape=NA) +
+  facet_wrap(~param, scales = 'free_y',
+             strip.position = 'left') +
+  labs(y=element_blank(),
+       x=element_blank()) +
+  theme_bw(base_size=20) +
+  stat_compare_means(aes(group = input_data),
+                     method = "wilcox.test", 
+                     label = "p.signif",
+                     hide.ns = T,
+                     paired = F,
+                     #label.y = 0,
+                     #label.x = 1.4,
+                     size = 7) +
+  geom_jitter(aes(shape = performance),
+            position = position_jitter(width = 0.1), 
+            size = 2.5, 
+            alpha = 0.6,
+            stroke = 1,
+            color = "black") +
+  scale_shape_manual(values = c(
+  "% bias satisfactory" = 1,
+  "NSE + % bias satisfactory" = 16
+)) +
+  scale_fill_manual(values = c("#0047AB", "orange"),
+                    guide='none') +
+    theme(
+    legend.position = 'bottom',
+    #legend.justification = c(0, 1.1), 
+    legend.text = element_text(size = 16),
+    legend.title = element_blank(), 
+    panel.grid = element_blank(),
+    panel.background = element_rect(fill = "white"),
+    strip.background = element_blank(),
+    text = element_text(color = "black"),
+    axis.title = element_text(color = "black"),
+    axis.text = element_text(color = "black"),
+    strip.placement = 'outside',
+    #strip.background = element_blank(),
+    axis.title.y = element_blank()) +
+  scale_y_continuous(expand = expansion(mult = c(0.1, 0.25)))
+
+ggsave('./figures/figure5.png',
+       dpi=600,
+       width=12,
+       height=8,
+       bg='white')
+
+## same as above but with param limits added
+param_limits <- data.frame(
+  param = c("snow_trs", "baseTemp (°C)", "t_factor",
+            "a_rain (mm)", "a_snow (mm)", "lagSurfaceRunoff",
+            "soilLatVertLPS", "soilOutLPS", "lagInterflow"),
+  low  = c(-5, -5, 0, 0.1, 0.1, 1, 0.001, 0.01, 1),
+  high = c(5, 5, 5, 10, 10, 1.5, 10, 10, 2)
+)
+
+param_lines <- param_limits %>%
+  pivot_longer(cols = c(low, high),
+               names_to = "type", 
+               values_to = "y")
+
+# Make sure param in param_lines is a factor with the same order
+param_lines$param <- fct_relevel(param_lines$param,
+                                 "snow_trs",
+                                 "baseTemp (°C)",
+                                 "t_factor",
+                                 "a_rain (mm)",
+                                 "a_snow (mm)",
+                                 "lagSurfaceRunoff",
+                                 "soilLatVertLPS",
+                                 "soilOutLPS",
+                                 "lagInterflow")
+
+ggplot(param_sens, aes(x=input_data, y=value, fill=input_data)) +
+  # add horizontal lines for low/high values
+  geom_hline(data = param_lines, aes(yintercept = y),
+             linetype = "dashed", color = "grey70") +
+  geom_boxplot(alpha=0.8,
+                outlier.shape=NA) +
+  facet_wrap(~param, scales = 'free_y',
+             strip.position = 'left') +
+  labs(y=element_blank(),
+       x=element_blank()) +
+  theme_bw(base_size=20) +
+  stat_compare_means(aes(group = input_data),
+                     method = "wilcox.test", 
+                     label = "p.signif",
+                     hide.ns = T,
+                     paired = F,
+                     #label.y = 0,
+                     #label.x = 1.4,
+                     size = 7) +
+  geom_jitter(aes(shape = performance),
+            position = position_jitter(width = 0.1), 
+            size = 2.5, 
+            alpha = 0.6,
+            stroke = 1,
+            color = "black") +
+  scale_shape_manual(values = c(
+  "% bias satisfactory" = 1,
+  "NSE + % bias satisfactory" = 16
+)) +
+  scale_fill_manual(values = c("#0047AB", "orange"),
+                    guide='none') +
+    theme(
+    legend.position = 'bottom',
+    #legend.justification = c(0, 1.1), 
+    legend.text = element_text(size = 16),
+    legend.title = element_blank(), 
+    panel.grid = element_blank(),
+    panel.background = element_rect(fill = "white"),
+    strip.background = element_blank(),
+    text = element_text(color = "black"),
+    axis.title = element_text(color = "black"),
+    axis.text = element_text(color = "black"),
+    strip.placement = 'outside',
+    #strip.background = element_blank(),
+    axis.title.y = element_blank()) +
+  scale_y_continuous(expand = expansion(mult = c(0.1, 0.25)))
+
+ggsave('./figures/figure5_wlimits.png',
+       dpi=600,
+       width=12,
+       height=8,
+       bg='white')
+
 ```
 
+### For Supp
+
+```{r}
+
+# show rest of params for supplemental
+# first take area weighted params (except lagSurfaceRunoff, a_rain, a_snow since that is already shown in main fig)
+otherParamsWeighted <- read_csv('./38HRU_dec2024_updates/params_weighted_dec2024.csv') %>%
+  filter(!param %in% c('lagSurfaceRunoff',
+                       'a_rain',
+                       'a_snow')) %>%
+  rename(value = area_weighted_average,
+         input_data = source) %>%
+  dplyr::select(param, input_data, value)
+
+# params that were not affected by burn
+otherParams <- read_csv('./38HRU_dec2024_updates/params_unburn.csv') %>%
+  filter(!param %in% c('soilOutLPS',
+                       'snow_trs',
+                       'lagInterflow',
+                       'baseTemp',
+                       't_factor',
+                       'lagSurfaceRunoff',
+                       'a_rain',
+                       'a_snow',
+                       'soilLatVertLPS')) %>% # these are the ones already shown
+  filter(!param %in% otherParamsWeighted$param) %>% # there are the ones that need to be area weighted
+  dplyr::select(param, input_data, value)
+
+# now join the area weighted other to the other params
+otherParams <- bind_rows(otherParams, otherParamsWeighted)
+
+# plot the remaning params for catchment
+ggplot(otherParams, aes(x=input_data, y=value, fill=input_data)) +
+  geom_boxplot(alpha=0.8,
+                outlier.colour = "black") +
+  facet_wrap(~param, scales = 'free_y',
+             ncol=3) +
+  labs(y=element_blank(),
+       x=element_blank()) +
+  theme_bw(base_size=20) +
+  stat_compare_means(aes(group = input_data),
+                     method = "wilcox.test", 
+                     label = "p.signif",
+                     hide.ns = T,
+                     paired = F,
+                     #label.y = 0,
+                     #label.x = 1.4,
+                     size = 7) +
+  scale_fill_manual(values = c("#0047AB", "orange")) +
+    theme(
+    legend.position = 'none',
+    #legend.justification = c(0, 1.1), 
+    legend.text = element_text(size = 16),
+    legend.title = element_blank(), 
+    panel.grid = element_blank(),
+    panel.background = element_rect(fill = "white"),
+    strip.background = element_blank(),
+    text = element_text(color = "black"),
+    axis.title = element_text(color = "black"),
+    axis.text = element_text(color = "black"),
+    #strip.text = element_blank()
+  ) +
+  scale_y_continuous(expand = expansion(mult = c(0.001, 0.3)))
+
+ggsave('./figures/remainingparams_boxplots_SUPP.png',
+       dpi=600,
+       height=16,
+       width=10)
+
+```
+
 # Figure 6
 
+```{r}
+
+gw_gridall <- read_csv(here('38HRU_dec2024_updates/catchment_output/grid_all.csv'), skip = 3) %>%
+  slice(-c(1,2)) %>%
+  dplyr::select(time,
+                catchmentRD1_w, 
+                catchmentRD2_w, 
+                catchmentRG1_w, 
+                catchmentRG2_w) %>%
+  mutate(source = 'grid_all') %>%
+  mutate(across(c(catchmentRD1_w, 
+                  catchmentRD2_w, 
+                  catchmentRG1_w, 
+                  catchmentRG2_w), 
+                as.numeric))
+
+gw_statnall <- read_csv(here('38HRU_dec2024_updates/catchment_output/statn_all.csv'), skip = 3) %>%
+  slice(-c(1,2)) %>%
+  dplyr::select(time, 
+                catchmentRD1_w, 
+                catchmentRD2_w, 
+                catchmentRG1_w, 
+                catchmentRG2_w) %>%
+  mutate(source = 'statn_all') %>%
+  mutate(across(c(catchmentRD1_w, 
+                  catchmentRD2_w, 
+                  catchmentRG1_w, 
+                  catchmentRG2_w), 
+                as.numeric))
+
+# combine the two above
+gw <- bind_rows(
+  gw_gridall, gw_statnall) %>%
+  mutate(date = mdy(time),
+         year = year(date)) %>%
+  arrange(date) %>%
+  group_by(year, source) %>%
+  mutate(RD1cumsum = cumsum(catchmentRD1_w),
+         RD2cumsum = cumsum(catchmentRD2_w),
+         RG1cumsum = cumsum(catchmentRG1_w),
+         RG2cumsum = cumsum(catchmentRG2_w))
+
+gw_maxcumsum <- gw %>%
+  group_by(source, year) %>%
+  summarize(yr_cum_RD1 = max(RD1cumsum),
+            yr_cum_RD2 = max(RD2cumsum),
+            yr_cum_RG1 = max(RG1cumsum),
+            yr_cum_RG2 = max(RG2cumsum)) %>%
+  mutate(year = as.factor(year)) %>%
+  pivot_longer(!c(year, source), names_to = 'flow_type', values_to = 'flow_cms') %>%
+  mutate(source = if_else(source == 'grid_all',
+                          'Gridded',
+                          'Station'))
+
+# make a vector of the letters - this is from the ANOVA+Tukey results in fourmile_output_dec2024
+letters_vector <- c("a", "b", "b", "c", "c", "c", "c", "c")
+
+gw_maxcumsum <- gw_maxcumsum %>%
+  mutate(letter = case_when(
+    source == "Gridded" & flow_type == "yr_cum_RG1" ~ letters_vector[1],
+    source == "Station" & flow_type == "yr_cum_RG1" ~ letters_vector[2],
+    source == "Station" & flow_type == "yr_cum_RD2" ~ letters_vector[3],
+    source == "Gridded" & flow_type == "yr_cum_RD1" ~ letters_vector[4],
+    source == "Station" & flow_type == "yr_cum_RD1" ~ letters_vector[5],
+    source == "Gridded" & flow_type == "yr_cum_RD2" ~ letters_vector[6],
+    source == "Gridded" & flow_type == "yr_cum_RG2" ~ letters_vector[7],
+    source == "Station" & flow_type == "yr_cum_RG2" ~ letters_vector[8]
+  ))
+
+# now make the same figure as above but with letters
+facet_labels <- c('yr_cum_RD1' = 'Surface runoff',
+                  'yr_cum_RD2' = 'Interflow',
+                  'yr_cum_RG1' = 'Fast groundwater',
+                  'yr_cum_RG2' = 'Slow groundwater')
+
+perf <- read_csv('./38HRU_dec2024_updates/nse_pbias_grid_statn_all.csv') %>%
+  mutate(year = as.factor(year))
+
+gw_maxcumsum <- left_join(gw_maxcumsum,
+                          perf,
+                          by = c('source',
+                                 'year'))
+
+gw_maxcumsum <- gw_maxcumsum %>%
+  mutate(flow_cms = if_else(flow_type == 'yr_cum_RD1' &
+                                flow_cms > 48,
+                              NA,
+                              flow_cms))
+
+gw_maxcumsum_letters <- gw_maxcumsum %>%
+  group_by(source, flow_type) %>%
+  mutate(max = max(flow_cms)) %>%
+  distinct(flow_type, source, .keep_all = TRUE) %>%
+    mutate(max = if_else((flow_type == 'yr_cum_RD1' & 
+                           source == 'Gridded'),
+                         3.5, max)) %>%
+    mutate(max = if_else((flow_type == 'yr_cum_RD1' & 
+                           source == 'Station'),
+                         1.3, max)) %>%
+  mutate(y_text = max * 1.06)
+
+flow_box <- ggplot(gw_maxcumsum, aes(x = source, y = flow_cms, fill = source)) +
+  geom_boxplot(outliers=F,width=0.7) + # need to note 1 outlier is removed from RD1 grid and statn (2013 flood) ****
+  geom_jitter(
+    aes(shape = both),
+    position = position_jitter(width = 0.25),
+    size = 2.5,
+    alpha = 0.7,
+    stroke = 1,
+    color = "black") +
+  scale_shape_manual(values = c(
+  "NSE + % bias unsatisfactory" = 4,
+  "NSE + % bias satisfactory" = 16,
+  "NSE satisfactory" = 1)) +
+  geom_text(data = gw_maxcumsum_letters, 
+            aes(label=letter,
+                y=y_text),
+            position = position_dodge(width = 0.97),
+            size = 6, 
+            vjust = 0) + 
+  facet_wrap(~flow_type, 
+             scales = 'free',
+             labeller = labeller(flow_type = facet_labels)) +
+  labs(y = 'mm of water') + 
+  theme_bw(base_size=20) +
+  scale_fill_manual(values = c("#0047AB", "orange"), guide = 'none') +
+  theme(
+    #legend.position = c(0.94, 0.36),
+    legend.position = 'bottom',
+    legend.text = element_text(size = 16),
+    legend.title = element_blank(),
+    panel.grid = element_blank(),
+    panel.background = element_rect(fill = "white"),
+    strip.background = element_blank(),
+    text = element_text(color = "black"),
+    axis.title = element_text(color = "black"),
+    axis.text = element_text(color = "black"),
+    axis.title.x = element_blank(),
+    legend.spacing = unit(0.1, "lines"),
+    legend.margin = margin(t = -8, r = 0, b = -2, l = 0)) +
+    #axis.text.x = element_blank(),
+    #axis.ticks.x = element_blank()) +
+  scale_y_continuous(expand = expansion(mult = c(0.1, 0.15)))
+
+flow_box
+
+ggsave('./figures/figure6.png',
+       dpi=600,
+       width = 12,
+       height = 8)
+
+# get some stats for manuscript
+stats <- gw %>%
+  group_by(source, year) %>%
+  summarize(yr_cum_RD1 = max(RD1cumsum),
+            yr_cum_RD2 = max(RD2cumsum),
+            yr_cum_RG1 = max(RG1cumsum),
+            yr_cum_RG2 = max(RG2cumsum)) %>%
+  mutate(year = as.factor(year)) %>%
+  pivot_longer(!c(year, source), names_to = 'flow_type', values_to = 'flow_cms') %>%
+  mutate(source = if_else(source == 'grid_all',
+                          'Gridded',
+                          'Station')) %>% 
+  group_by(source, year) %>%
+  mutate(totFlow = sum(flow_cms)) %>%
+  group_by(source, year) %>%
+  mutate(fracFlow = (flow_cms/totFlow)*100) #%>%
+  group_by(source, flow_type) %>% 
+  summarize(meanPercFlow = mean(fracFlow))
+
+```
+
 # Figure 7
 
+```{r}
+
+statn_hi <- read_csv('./38HRU_dec2024_updates/HRU/statn_HRU_18.csv') %>% 
+  mutate(date = mdy(time),
+         source = 'statn') %>%
+  dplyr::select(-time)
+
+grid_hi <- read_csv('./38HRU_dec2024_updates/HRU/grid_HRU_18.csv') %>%
+  mutate(date = mdy(time),
+         source = 'grid') %>%
+  dplyr::select(-time)
+
+both_hi <- bind_rows(statn_hi, grid_hi) %>%
+  mutate(year = year(date),
+         month = month(date)) %>%
+  filter(year == 2016,
+         month %in% c(4,5,6))
+
+statn_low <- read_csv('./38HRU_dec2024_updates/HRU/statn_HRU_19.csv') %>% 
+  mutate(date = mdy(time),
+         source = 'statn') %>%
+  dplyr::select(-time)
+
+grid_low <- read_csv('./38HRU_dec2024_updates/HRU/grid_HRU_19.csv') %>%
+  mutate(date = mdy(time),
+         source = 'grid') %>%
+  dplyr::select(-time)
+
+both_low <- bind_rows(statn_low, grid_low) %>%
+  mutate(year = year(date),
+         month = month(date)) %>%
+  filter(year == 2016,
+         month %in% c(4,5,6))
+
+## combine low and high together
+hi <- both_hi %>%
+  dplyr::select(tmean, snowTotSWE, precip, source, date) %>%
+  mutate(elevation = 'High')
+
+low <- both_low %>%
+  dplyr::select(tmean, snowTotSWE, precip, source, date) %>%
+  mutate(elevation = 'Low')
+
+both <- bind_rows(hi, low) %>%
+  mutate(elev_source =
+           case_when(source == 'statn' & elevation == 'High' ~ 'Station - High',
+                     source == 'statn' & elevation == 'Low' ~ 'Station - Low',
+                     source == 'grid' & elevation == 'High' ~ 'Gridded - High',
+                     source == 'grid' & elevation == 'Low' ~ 'Gridded - Low'))
+
+# figure
+tmean <- ggplot(both,
+       aes(x=date, y = tmean, 
+           color = elev_source,
+           linetype=elev_source)) +
+   geom_line(size=1, alpha=0.8) +  
+    scale_color_manual(values = c("Gridded - High" = "#0047AB", 
+                                  "Gridded - Low" = "#0047AB", 
+                                  "Station - High" = "orange",
+                                  "Station - Low" = "orange")) +
+  scale_linetype_manual(values = c("Gridded - High" = "dashed", 
+                                  "Gridded - Low" = "solid", 
+                                  "Station - High" = "dashed",
+                                  "Station - Low" = "solid")) + 
+  scale_x_date(date_labels = "%b") +
+  labs(x = element_blank(),
+       y = 'Mean temperature (°C)') +
+  theme_bw(base_size = 20) +
+  theme(legend.position = 'bottom',
+    #legend.position = c(0.24, 0.852), 
+    legend.text = element_text(size = 10),
+    legend.title = element_blank(),
+    panel.grid = element_blank(),
+    panel.background = element_rect(fill = "white"),
+    strip.background = element_blank(),
+    text = element_text(color = "black"),
+    axis.title = element_text(color = "black"),
+    axis.text = element_text(color = "black"),
+    legend.key.width = unit(1, "cm")
+    #plot.margin = margin(t = 10, r = 20, b = 10, l = 10)
+  )
+
+tmean
+
+swe <- ggplot(both,
+       aes(x=date, y = snowTotSWE, 
+           color = elev_source,
+           linetype=elev_source)) +
+   geom_line(size=1, alpha=0.8) +  
+    scale_color_manual(values = c("Gridded - High" = "#0047AB", 
+                                  "Gridded - Low" = "#0047AB", 
+                                  "Station - High" = "orange",
+                                  "Station - Low" = "orange")) +
+  scale_linetype_manual(values = c("Gridded - High" = "dashed", 
+                                  "Gridded - Low" = "solid", 
+                                  "Station - High" = "dashed",
+                                  "Station - Low" = "solid")) + 
+  scale_x_date(date_labels = "%b") +
+  #scale_y_log10() +
+  labs(x = element_blank(),
+       y = 'SWE (mm)') +
+  theme_bw(base_size = 20) +
+  theme(
+    #legend.position = c(0.89, 0.87),
+    legend.position = 'bottom',
+    legend.text = element_text(size = 10),
+    legend.title = element_blank(),
+    panel.grid = element_blank(),
+    panel.background = element_rect(fill = "white"),
+    strip.background = element_blank(),
+    text = element_text(color = "black"),
+    axis.title = element_text(color = "black"),
+    axis.text = element_text(color = "black"),
+    legend.key.width = unit(1, "cm")
+    #plot.margin = margin(t = 10, r = 20, b = 10, l = 10)
+  )
+
+swe
+
+p <- both %>%
+  group_by(elev_source) %>%
+  mutate(cumP = cumsum(precip)) %>% 
+  ggplot(.,
+       aes(x=date, y = cumP, 
+           color = elev_source,
+           linetype=elev_source)) +
+   geom_line(size=1, alpha=0.8) +  
+    scale_color_manual(values = c("Gridded - High" = "#0047AB", 
+                                  "Gridded - Low" = "#0047AB", 
+                                  "Station - High" = "orange",
+                                  "Station - Low" = "orange")) +
+  scale_linetype_manual(values = c("Gridded - High" = "dashed", 
+                                  "Gridded - Low" = "solid", 
+                                  "Station - High" = "dashed",
+                                  "Station - Low" = "solid")) + 
+  scale_x_date(date_labels = "%b") +
+  #scale_y_log10() +
+  labs(x = element_blank(),
+       y = 'Precip (mm)') +
+  theme_bw(base_size = 20) +
+  theme(
+    legend.position = 'bottom',
+    #legend.text = element_text(size = 12),
+    #legend.title = element_blank(),
+    panel.grid = element_blank(),
+    panel.background = element_rect(fill = "white"),
+    strip.background = element_blank(),
+    text = element_text(color = "black"),
+    axis.title = element_text(color = "black"),
+    axis.text = element_text(color = "black"),
+    legend.key.width = unit(1, "cm")
+    #plot.margin = margin(t = 10, r = 20, b = 10, l = 10)
+  )
+
+p
+
+legend <- cowplot::get_plot_component(tmean, "guide-box", return_all = TRUE)[[3]]
+
+tmean_noleg <- tmean + theme(legend.position = "none")
+p_noleg <- p + theme(legend.position = "none")
+swe_noleg <- swe + theme(legend.position = "none")
+
+combined <- plot_grid(tmean_noleg, p_noleg, swe_noleg, nrow = 1)
+final_plot <- plot_grid(combined, legend, ncol = 1, rel_heights = c(1, 0.1))
+final_plot
+
+ggsave('./figures/figure7.png',
+       width = 10,
+       height = 5,
+       dpi=800,
+       bg='white')
+
+```
+
 # Figure 8

### 2025-09-04 manuscriptFigures.Rmd
added figs 8-10

@@
 
+HRU low and high for 2016
+HRU high = 18
+HRU low = 19
+
 ```{r}
@@
 
+```{r}
+
+flow <- read_csv('./38HRU_dec2024_updates/discharge_all.csv') %>%
+  replace(.==-9999, NA) %>%
+  rename(date = time) %>%
+  mutate(date = mdy(date)) %>%
+  drop_na()
+
+flow_pivot <- flow %>%
+  pivot_longer(!date, names_to = 'cal_run', values_to = 'q_m3s') %>%
+  mutate(year = as.factor(year(date))) %>%
+  filter(cal_run %in% c('grid_all',
+                        'statn_all',
+                        'obs'
+                        #'statn_2016',
+                        #'grid_2016'
+                        )) %>%
+  mutate(cal_run = case_match(cal_run,
+                            'grid_all' ~ 'Gridded',
+                            'statn_all' ~ 'Station',
+                            'obs' ~ 'Observed'
+                          # 'statn_2016' ~ 'statn_2016',
+                          #  'grid_2016' ~ 'grid_2016'
+  ))
+
+# 2016 hydrograph
+flowEg <- flow_pivot %>%
+  filter(year %in% c(2016)) %>%
+  ggplot(aes(x = date,
+             y = q_m3s, 
+             color = cal_run,
+             linetype = cal_run)) + 
+  geom_line(size = 1, alpha = 1) + 
+  theme_bw(base_size = 20) +
+  scale_color_manual(values = c("Gridded" = "#0047AB", 
+                                "Observed" = "black", 
+                                "Station" = "orange"
+                               # 'statn_2016' = 'orange',
+                              #  'grid_2016' = '#0047AB'
+                                )) +
+  scale_linetype_manual(values = c("Gridded" = "solid",
+                                   "Observed" = "dashed", 
+                                   "Station" = "solid"
+                                   #'statn_2016' = 'twodash',
+                               #'grid_2016' = 'twodash'
+)) +
+  labs(x = element_blank(),
+       y = "Streamflow (cms)") +
+   scale_x_date(date_labels = "%b",
+               date_breaks = "1 month") +
+  theme(
+    legend.position = c(0.9, 0.85),
+    legend.text = element_text(size = 14),
+    legend.key.width = unit(2, "lines"),
+    legend.title = element_blank(),
+    panel.grid = element_blank(),
+    panel.background = element_rect(fill = "white"),
+    strip.background = element_blank(),
+    text = element_text(color = "black"),
+    axis.title = element_text(color = "black"),
+    axis.text = element_text(color = "black"),
+    plot.margin = margin(t = 2, r = 20, b = 2, l = 10)
+  )
+
+flowEg
+
+# 2016 flow partition
+gw_gridall <- read_csv(here('38HRU_dec2024_updates/catchment_output/grid_all.csv'), skip = 3) %>%
+  slice(-c(1,2)) %>%
+  dplyr::select(time,
+                catchmentRD1_w, 
+                catchmentRD2_w, 
+                catchmentRG1_w, 
+                catchmentRG2_w) %>%
+  mutate(source = 'grid_all') %>%
+  mutate(across(c(catchmentRD1_w, 
+                  catchmentRD2_w, 
+                  catchmentRG1_w, 
+                  catchmentRG2_w), 
+                as.numeric))
+
+gw_statnall <- read_csv(here('38HRU_dec2024_updates/catchment_output/statn_all.csv'), skip = 3) %>%
+  slice(-c(1,2)) %>%
+  dplyr::select(time, 
+                catchmentRD1_w, 
+                catchmentRD2_w, 
+                catchmentRG1_w, 
+                catchmentRG2_w) %>%
+  mutate(source = 'statn_all') %>%
+  mutate(across(c(catchmentRD1_w, 
+                  catchmentRD2_w, 
+                  catchmentRG1_w, 
+                  catchmentRG2_w), 
+                as.numeric))
+
+# combine the two above
+gw <- bind_rows(
+  gw_gridall, gw_statnall) %>%
+  mutate(date = mdy(time),
+         year = year(date)) %>%
+  arrange(date) %>%
+  group_by(year, source) %>%
+  mutate(RD1cumsum = cumsum(catchmentRD1_w),
+         RD2cumsum = cumsum(catchmentRD2_w),
+         RG1cumsum = cumsum(catchmentRG1_w),
+         RG2cumsum = cumsum(catchmentRG2_w))
+
+example <- gw %>%
+  filter(year == 2016) %>%
+  ungroup() %>% 
+  dplyr::select(date, source,
+         RD1cumsum,
+         RD2cumsum,
+         RG1cumsum,
+         RG2cumsum) %>%
+  pivot_longer(!c(date,source), names_to='flow_type',
+               values_to='flow_cms') %>%
+  mutate(source = if_else(source == 'grid_all',
+                          'Gridded',
+                          'Station'))
+
+# some 2016 stats
+flow16Stats <- example %>%
+  filter(date == '2016-12-31') %>%
+  group_by(source) %>%
+  mutate(sum = sum(flow_cms)) %>%
+  mutate(percTot = (flow_cms/sum)*100) %>%
+  mutate(percTot = round(percTot, 2))
+
+facet_labels <- c('yr_cum_RD1' = 'Surface runoff',
+                  'yr_cum_RD2' = 'Interflow',
+                  'yr_cum_RG1' = 'Fast groundwater',
+                  'yr_cum_RG2' = 'Slow groundwater')
+
+example_yr <- ggplot(example,
+       aes(x=date, y = flow_cms, color=source)) +
+  geom_line() +
+  facet_wrap(~flow_type, 
+             scales = 'free_y',
+             labeller = labeller(flow_type = facet_labels)) +
+   geom_line(size=1, alpha=0.7) +  
+  scale_color_manual(values = c("#0047AB", "orange")) +
+    scale_x_date(date_labels = "%b", 
+               date_breaks = "2 month") +
+  labs(x=element_blank(),
+       y='mm of water') +
+  theme_bw(base_size = 16) +
+  theme(
+    legend.position = 'none',
+    legend.text = element_text(size = 12),
+    legend.title = element_blank(),
+    panel.grid = element_blank(),
+    panel.background = element_rect(fill = "white"),
+    strip.background = element_blank(),
+    text = element_text(color = "black"),
+    axis.title = element_text(color = "black"),
+    axis.text = element_text(color = "black"),
+    plot.margin = margin(t = 2, r = 20, b = 10, l = 10)
+  )
+
+example_yr
+
+plot_grid(flowEg,
+          example_yr,
+          ncol=1)
+
+ggsave('./figures/figure8.png',
+       dpi=800,
+       width=10,
+       height=8)
+
+```
+
 # Figure 9
 
+```{r}
+
+# params that were cal w/ burned areas
+combo <- read_csv('./38HRU_dec2024_updates/params_burn_unburn.csv')
+
+# read in pbias and nse cats
+pbias <- read_csv('./38HRU_dec2024_updates/pbiasCats.csv') %>%
+  filter(year == c('All')) %>%
+  dplyr::select(input_data, year_missing, pbias)
+
+nse <- read_csv('./38HRU_dec2024_updates/nseCats.csv') %>%
+  filter(year == c('All')) %>%
+  dplyr::select(input_data, year_missing, nse)
+
+perf <- left_join(nse, pbias, by = c('input_data',
+                                     'year_missing'))
+
+# assign categories
+perf <- perf %>%
+  mutate(performance = case_when(
+                                nse < 0.5 & abs(pbias) >= 25 ~ 'Neither',
+                                nse > 0.5 & abs(pbias) >= 25 ~ 'NSE',
+                                nse < 0.5 & abs(pbias) < 25 ~ '% bias satisfactory',
+                                nse > 0.5 & abs(pbias) < 25 ~ 'NSE + % bias satisfactory')) %>%
+  mutate(input_data = if_else(input_data == 'grid',
+                              'Gridded', 'Station'),
+         year_missing = if_else(year_missing == 'None',
+                                'all', year_missing))
+perf1 <- perf %>%
+  mutate(year_missing = if_else(year_missing == 'all',
+                                'none',
+                                year_missing))
+
+combo <- left_join(combo,
+                        perf1,
+                        by = c('input_data',
+                               'year_missing'))
+
+# reorder the params
+# combo$param <- factor(combo$param, levels = c("a_snow",
+#                                                         "a_rain",
+#                                                         "soilMaxInfSummer",
+#                                                         "soilMaxDPS",
+#                                                         "lagSurfaceRunoff",
+#                                                         "soilDistMPSLPS"))
+combo <- combo %>%
+  mutate(param = fct_recode(param,
+    "a_rain (mm)" = "a_rain",
+    "a_snow (mm)" = "a_snow",
+    "soilMaxInfSummer (mm/day)" = "soilMaxInfSummer",
+    "soilMaxDPS (mm)" = "soilMaxDPS",
+    "lagSurfaceRunoff" = "lagSurfaceRunoff",
+    "soilDistMPSLPS" = "soilDistMPSLPS"
+  ))
+
+# text above boxplots - this is from Tukey analysis that was already run below then added to params
+combo <- combo %>%
+  group_by(param, burn, input_data) %>%
+  mutate(y_text = max(value, na.rm = TRUE) * 1.08) %>%  # Slightly above max value
+  ungroup()
+
+ggplot(combo, aes(x = burn, y = value, fill = input_data)) +
+  geom_boxplot(alpha = 0.8, 
+               outliers = F) +
+  geom_text(aes(label = letter, y = y_text), 
+            position = position_dodge(width = 0.75),  # Align with boxplots
+            size = 6, 
+            vjust = 0) +  
+  geom_jitter(aes(shape = performance),
+            position = position_jitterdodge(
+    jitter.width = 0.1,
+    dodge.width = 0.75),
+            size = 2.5, 
+            alpha = 0.6,
+            stroke = 1,
+            color = "black") +
+  scale_shape_manual(values = c(
+  "% bias satisfactory" = 1,
+  "NSE + % bias satisfactory" = 16)) +
+  facet_wrap(~param, 
+             scales = 'free_y',
+             strip.position = 'left') +
+  labs(y = element_blank(), x = element_blank()) +
+  theme_bw(base_size = 20) +
+  scale_fill_manual(values = c("#0047AB", "orange")) +
+  theme(
+    legend.position = 'bottom',
+    legend.text = element_text(size = 16),
+    legend.title = element_blank(),
+    panel.grid = element_blank(),
+    panel.background = element_rect(fill = "white"),
+    strip.background = element_blank(),
+    text = element_text(color = "black"),
+    axis.title = element_text(color = "black"),
+    axis.text = element_text(color = "black"),
+    strip.placement = 'outside',
+    axis.title.y = element_blank()
+  ) +
+   scale_y_continuous(expand = expansion(mult = c(0.05, 0.1)))
+
+ggsave('./figures/figure9.png',
+       dpi=800,
+       width = 12,
+       height = 8)
+
+```
+
 # Figure 10
 
-# Figure 11
+```{r}
+
+unburn <- read_csv('./38HRU_dec2024_updates/HRU/statn_HRU_2_unburn.csv') %>%
+  mutate(date = mdy(time),
+         year = year(date),
+         type = 'unburn') %>%
+  filter(year == 2016)
+
+burn <- read_csv('./38HRU_dec2024_updates/HRU/statn_HRU_5_burn.csv') %>%
+  mutate(date = mdy(time),
+         year = year(date),
+         type = 'burn') %>%
+  filter(year == 2016)
+
+both <- bind_rows(unburn, burn)
+
+# interception
+inter <- both %>%
+  dplyr::select(date, type, intercStorage)
+
+# swe
+swe <- both %>%
+  dplyr::select(date, type, snowTotSWE)
+
+p <- both %>%
+  dplyr::select(date, type, precip) %>%
+  group_by(type) %>%
+  mutate(p_cumu = cumsum(precip))
+
+# soil sat
+soilsat <- both %>%
+  dplyr::select(date, type, soilSat)
+
+# surface runoff
+runoff <- both %>%
+  dplyr::select(date, type, outRD1)
+
+# interflow
+interflow <- both %>%
+  dplyr::select(date, type, outRD2) %>%
+  mutate(interflow_cum = cumsum(outRD2))
+
+gw <- both %>%
+  dplyr::select(date, type, outRG1) %>%
+  mutate(gw_cumu = cumsum(outRG1))
+
+# dps
+dps <- both %>%
+  dplyr::select(date, type, actDPS)
+
+# mps
+mps <- both %>%
+  dplyr::select(date, type, soilSatMPS)
+
+# lps
+lps <- both %>%
+  dplyr::select(date, type, soilSatLPS)
+
+# soil sat
+soilsat <- both %>%
+  dplyr::select(date, type, soilSat)
+
+## make the actual plot
+p_plot <- ggplot(p, aes(x = date,
+                        y = p_cumu, 
+                        color = type)) +
+  geom_line(size=1, alpha=0.8) +
+    scale_color_manual(values = c("burn" = "red", 
+                                  "unburn" = "black")) +
+  scale_x_date(date_labels = "%b") +
+  labs(x = element_blank(),
+       y = 'Precipitation (mm)') +
+  theme_bw(base_size = 18) +
+  theme(legend.position = 'bottom',
+    #legend.position = c(0.24, 0.852), 
+    legend.text = element_text(size = 12),
+    legend.title = element_blank(),
+    panel.grid = element_blank(),
+    panel.background = element_rect(fill = "white"),
+    strip.background = element_blank(),
+    text = element_text(color = "black"),
+    axis.title = element_text(color = "black"),
+    axis.text = element_text(color = "black"),
+    legend.key.width = unit(1, "cm")
+  )
+
+p_plot
+
+inter <- inter %>%
+  mutate(type = factor(type, levels = c("unburn", "burn")))
+
+int_plot <- ggplot(inter, aes(x = date,
+                        y = intercStorage, 
+                        color = type)) +
+  geom_line(size=1, alpha=0.7) +
+    scale_color_manual(values = c("burn" = "red", 
+                                  "unburn" = "black")) +
+  scale_x_date(date_labels = "%b") +
+  labs(x = element_blank(),
+       y = 'Interception (mm)') +
+  theme_bw(base_size = 20) +
+  theme(legend.position = 'bottom',
+    #legend.position = c(0.24, 0.852), 
+    legend.text = element_text(size = 10),
+    legend.title = element_blank(),
+    panel.grid = element_blank(),
+    panel.background = element_rect(fill = "white"),
+    strip.background = element_blank(),
+    text = element_text(color = "black"),
+    axis.title = element_text(color = "black"),
+    axis.text = element_text(color = "black"),
+    legend.key.width = unit(1, "cm")
+  )
+
+int_plot
+
+soilsat_plot <- ggplot(soilsat, aes(x = date,
+                        y = soilSat, 
+                        color = type)) +
+  geom_line(size=1, alpha=0.7) +
+    scale_color_manual(values = c("burn" = "red", 
+                                  "unburn" = "black")) +
+  scale_x_date(date_labels = "%b") +
+  labs(x = element_blank(),
+       y = 'Soil saturation') +
+  theme_bw(base_size = 20) +
+  theme(legend.position = 'bottom',
+    #legend.position = c(0.24, 0.852), 
+    legend.text = element_text(size = 10),
+    legend.title = element_blank(),
+    panel.grid = element_blank(),
+    panel.background = element_rect(fill = "white"),
+    strip.background = element_blank(),
+    text = element_text(color = "black"),
+    axis.title = element_text(color = "black"),
+    axis.text = element_text(color = "black"),
+    legend.key.width = unit(1, "cm")
+  )
+
+soilsat_plot
+
+interflow_plot <- ggplot(interflow, aes(x = date,
+                        y = interflow_cum, 
+                        color = type)) +
+  geom_line(size=1, alpha=0.7) +
+    scale_color_manual(values = c("burn" = "red", 
+                                  "unburn" = "black")) +
+  scale_x_date(date_labels = "%b") +
+  labs(x = element_blank(),
+       y = 'Interflow (L)') +
+  theme_bw(base_size = 20) +
+  theme(legend.position = 'bottom',
+    #legend.position = c(0.24, 0.852), 
+    legend.text = element_text(size = 10),
+    legend.title = element_blank(),
+    panel.grid = element_blank(),
+    panel.background = element_rect(fill = "white"),
+    strip.background = element_blank(),
+    text = element_text(color = "black"),
+    axis.title = element_text(color = "black"),
+    axis.text = element_text(color = "black"),
+    legend.key.width = unit(1, "cm")
+  )
+
+interflow_plot
+
+gw_plot <- ggplot(gw, aes(x = date,
+                        y = gw_cumu, 
+                        color = type)) +
+  geom_line(size=1, alpha=0.7) +
+    scale_color_manual(values = c("burn" = "red", 
+                                  "unburn" = "black")) +
+  scale_x_date(date_labels = "%b") +
+  labs(x = element_blank(),
+       y = 'Shallow groundwater (L)') +
+  theme_bw(base_size = 20) +
+  theme(legend.position = 'bottom',
+    #legend.position = c(0.24, 0.852), 
+    legend.text = element_text(size = 10),
+    legend.title = element_blank(),
+    panel.grid = element_blank(),
+    panel.background = element_rect(fill = "white"),
+    strip.background = element_blank(),
+    text = element_text(color = "black"),
+    axis.title = element_text(color = "black"),
+    axis.text = element_text(color = "black"),
+    legend.key.width = unit(1, "cm")
+  )
+
+gw_plot
+
+swe_plot <- ggplot(swe, aes(x = date,
+                        y = snowTotSWE, 
+                        color = type)) +
+  geom_line(size=1, alpha=0.7) +
+    scale_color_manual(values = c("burn" = "red", 
+                                  "unburn" = "black")) +
+  scale_x_date(date_labels = "%b") +
+  labs(x = element_blank(),
+       y = 'SWE (mm)') +
+  theme_bw(base_size = 20) +
+  theme(legend.position = 'bottom',
+    #legend.position = c(0.24, 0.852), 
+    legend.text = element_text(size = 10),
+    legend.title = element_blank(),
+    panel.grid = element_blank(),
+    panel.background = element_rect(fill = "white"),
+    strip.background = element_blank(),
+    text = element_text(color = "black"),
+    axis.title = element_text(color = "black"),
+    axis.text = element_text(color = "black"),
+    legend.key.width = unit(1, "cm")
+  )
+
+swe_plot
+
+legend <- cowplot::get_plot_component(p_plot, "guide-box", return_all = TRUE)[[3]]
+
+p_plot <- p_plot + theme(legend.position = "none")
+int_plot <- int_plot + theme(legend.position = "none")
+soilsat_plot <- soilsat_plot + theme(legend.position = "none")
+interflow_plot <- interflow_plot + theme(legend.position = "none")
+gw_plot <- gw_plot + theme(legend.position = "none")
+swe_plot <- swe_plot + theme(legend.position = "none")
+
+plots <- plot_grid(p_plot,
+          int_plot,
+          swe_plot,
+          soilsat_plot,
+          interflow_plot,
+          gw_plot,
+          ncol = 3)
+
+final_plot <- plot_grid(
+  plots,
+  legend,
+  ncol = 1,
+  rel_heights = c(1, 0.07)  # Adjust height of legend
+)
+
+final_plot
+
+ggsave('./figures/figure10.png',
+       dpi=800,
+       bg='white',
+       height=8,
+       width=12)
+
+```

### 2025-10-15 manuscriptFigures.Rmd
added figure 11. updated supp figure to include param min and max

@@
 # first take area weighted params (except lagSurfaceRunoff, a_rain, a_snow since that is already shown in main fig)
-otherParamsWeighted <- read_csv('./38HRU_dec2024_updates/params_weighted_dec2024.csv') %>%
+otherParamsWeighted <- read_csv('./38HRU_dec2024_updates/updated_wranges/params_weighted_dec2024_ranges.csv') %>%
   filter(!param %in% c('lagSurfaceRunoff',
@@
          input_data = source) %>%
-  dplyr::select(param, input_data, value)
+  dplyr::select(param, input_data, value, min, max)
 
 # params that were not affected by burn
-otherParams <- read_csv('./38HRU_dec2024_updates/params_unburn.csv') %>%
+otherParams <- read_csv('./38HRU_dec2024_updates/updated_wranges/params_unburn_ranges.csv') %>%
   filter(!param %in% c('soilOutLPS',
@@
   filter(!param %in% otherParamsWeighted$param) %>% # there are the ones that need to be area weighted
-  dplyr::select(param, input_data, value)
+  dplyr::select(param, input_data, value, min, max)
 
@@
 
-# plot the remaning params for catchment
-ggplot(otherParams, aes(x=input_data, y=value, fill=input_data)) +
+# Create a summary dataframe for hlines
+lines_df <- otherParams %>%
+  dplyr::group_by(param) %>%
+  dplyr::summarize(min_val = min(value, na.rm = TRUE),
+                   max_val = max(value, na.rm = TRUE))
+
+# supp info plot
+ggplot(otherParams, aes(x = input_data, y = value, fill = input_data)) +
+  geom_hline(data = lines_df, aes(yintercept = min_val), 
+             linetype = "dashed", color = "grey70") +
+  geom_hline(data = lines_df, aes(yintercept = max_val), 
+             linetype = "dashed", color = "grey70") +
   geom_boxplot(alpha=0.8,
@@
   ) +
-  scale_y_continuous(expand = expansion(mult = c(0.001, 0.3)))
+  scale_y_continuous(expand = expansion(mult = c(0.1, 0.2)))
 
@@
 ```
+
+# Figure 11
+
+```{r}
+
+perf <- read_csv('/Users/megansears/Documents/Repos/fourmile/38HRU_dec2024_updates/perf_metrics.csv')
+
+perf <- perf %>%
+  pivot_wider(names_from=metric,
+               values_from=value) %>%
+  filter(year == 'All')
+
+perf1 <- perf %>%
+  mutate(type = case_when(
+    str_detect(model_run, "grid") ~ "Gridded",
+    str_detect(model_run, "statn") ~ "Station"))
+
+nse_kge <- ggplot(perf1, aes(x=KGE, y=NSE, color=type)) + 
+  #geom_point(size=4, alpha=0.7) +
+   geom_jitter(size = 4, alpha = 0.7, width = 0.05, height = 0.05) +
+  theme_bw(base_size=20) +
+  scale_color_manual(values = c("#0047AB", "orange")) +
+  theme(
+    legend.position = 'bottom',
+    legend.text = element_text(size = 16),
+    legend.title = element_blank(),
+    panel.background = element_rect(fill = "white"),
+    strip.background = element_blank(),
+    text = element_text(color = "black"),
+    axis.title = element_text(color = "black"),
+    axis.text = element_text(color = "black"),
+    panel.grid.major.x = element_blank()  # remove vertical major grid lines
+   # panel.grid.minor.x = element_blank(),
+    #panel.grid.minor = element_blank()      # remove all minor grid lines
+
+  )
+
+nse_kge
+
+pbias_kge <- ggplot(perf1, aes(x=KGE, y=pbias, color=type)) + 
+  #geom_point(size=4, alpha=0.8) +
+  geom_jitter(size = 4, alpha = 0.7, width = 0.001, height = 0.001) +
+  theme_bw(base_size=20) +
+  scale_color_manual(values = c("#0047AB", "orange")) +
+  labs(y = '% bias') +
+  theme(
+    legend.position = 'bottom',
+    legend.text = element_text(size = 16),
+    legend.title = element_blank(),
+    panel.background = element_rect(fill = "white"),
+    strip.background = element_blank(),
+    text = element_text(color = "black"),
+    axis.title = element_text(color = "black"),
+    axis.text = element_text(color = "black"),
+    panel.grid.major.x = element_blank()  # remove vertical major grid lines
+   # panel.grid.minor.x = element_blank(),
+    #panel.grid.minor = element_blank()      # remove all minor grid lines
+
+  )
+
+pbias_kge
+
+library(patchwork)
+
+combined_plot <- nse_kge + pbias_kge + 
+  plot_layout(ncol = 2, guides = "collect") & 
+  theme(legend.position = 'bottom')
+
+combined_plot
+
+# ggsave('/Users/megansears/Documents/Repos/fourmile/figures/kge_nse_pbias.png',
+#        dpi=600,
+#        width=10,
+#        height=6)
+
+```

### 2025-10-22 StatnPrecip.Rmd
edited statn precip: no TB !6:9, proper prism shift for !6:9, updated TBs for 2016-2020 to be proper sum

---
title: "precip_statn"
author: "Megan Sears"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}

library(tidyverse)

```

# Precip gauges
GH, LM, SE, SP, ST were missing 2016-2020 so that is in next chunk

```{r}

prec <- read_csv('/Users/megansears/Documents/Repos/fourmile/data/Archive/files_to_edit/precipAll_statn.csv')

#daily precip
precall <- prec %>%
  mutate(date = dmy(date),
         doy = yday(date)) %>%
  mutate(year = year(date),
         month = month(date)) %>%
  filter(year > 2009) %>% 
  mutate_at(c('Gordon_South', 'Gordon_North',
              'GH', 'LM', 'SE', 'SP', 'ST', 'NADP_SL'),
            ~(ifelse(!month %in% c(6:9),
                               NA, .))) # make NA if not in 6:9 month

# need to add betasso
bet_rain <- bet_met %>%
  dplyr::select(c(5,6)) %>%
  rename(Betasso_rain = 1) %>%
  mutate(date = as.Date(DATE_TIME)) %>%
  group_by(date) %>%
  summarize(Betasso = sum(Betasso_rain)) %>%
  filter(date > '2009-12-31') %>%
  mutate(month = month(date)) %>%
  mutate(Betasso = if_else(!month %in% 6:9, NA_real_, Betasso)) # make NA if not in 6:9 month

precall <- full_join(precall, bet_rain, by = 'date')
# precall includes all the precip gauges now
# it also has filtered the TBs out for months !6:9
# but the TBs are missing 2016 - 2020 data which is in updated_precip_2016to2020.xlsx

# formatting to get ready for Ages
precallFormat <- precall %>%
  select(-c(doy, year, month.x, month.y)) %>%
  mutate(across(everything(), ~ replace_na(., as.integer(-9999)))) %>%
  mutate(date = format(date, '%d.%m.%Y'))

write.csv(precallFormat, 
          '/Users/megansears/Documents/Repos/fourmile/data/Archive/files_to_edit/precipStatn_noWinterTB_TBmissing16&20.csv')

```

# TBs that were missing 2016-2020

```{r}

missingP <- read_csv('./data/Archive/files_to_edit/updated_precip_2016to20_mm.csv')

# for TBs: "(two records a day if no precipitation, but additional data if there was precipitation- one record for each tip of the tipping bucket)"
# above is from Sheila Murphy in the UCFCD directions (saved in this folder)

gh <- missingP %>%
  select(date = GH_date, GH) %>%
  mutate(date = mdy(date)) %>%
  arrange(date) %>%
  group_by(date) %>% # group by date since several tips per day can happen
  summarize(GH = sum(GH)) %>% # sum by day
  filter(date < '2021-01-01') %>% # filter anything later than 1 Jan 2021
  complete(date =
             seq.Date(min(date), 
                      max(ymd('2020-12-31')), 
                      by = "day")) # fill in missing dates

lm <- missingP %>%
  select(date = LM_date, LM) %>%
  mutate(date = mdy(date)) %>%
  arrange(date) %>%
  group_by(date) %>%
  summarize(LM = sum(LM)) %>%
  filter(date < '2021-01-01') %>%
  complete(date =
             seq.Date(min(date), 
                      max(ymd('2020-12-31')), 
                      by = "day"))

se <- missingP %>%
  select(date = SE_date, SE) %>%
  mutate(date = mdy(date)) %>%
  arrange(date) %>%
  group_by(date) %>%
  summarize(SE = sum(SE)) %>%
  filter(date < '2021-01-01') %>%
  complete(date =
             seq.Date(min(date), 
                      max(ymd('2020-12-31')), 
                      by = "day"))

sp <- missingP %>%
  select(date = SP_date, SP) %>%
  mutate(date = mdy(date)) %>%
  arrange(date) %>%
  group_by(date) %>%
  summarize(SP = sum(SP)) %>%
  filter(date < '2021-01-01') %>%
  complete(date =
             seq.Date(min(date), 
                      max(ymd('2020-12-31')), 
                      by = "day"))

st <- missingP %>%
  select(date = ST_date, ST) %>%
  mutate(date = mdy(date)) %>%
  arrange(date) %>%
  group_by(date) %>%
  summarize(ST = sum(ST)) %>%
  filter(date < '2021-01-01') %>%
  complete(date =
             seq.Date(min(date), 
                      max(ymd('2020-12-31')), 
                      by = "day"))

# combine as all TBs as 1 df
dfs <- list(gh,
            lm,
            se,
            sp,
            st)

# Perform left joins in sequence
tbAll <- reduce(dfs, 
                left_join, 
                by = "date")

# tbAll is GH,LM,SE,SP,ST tipping buckets for 2016-2020
# after looking at a summary of tbAll the following TBs have too high readings randomly
# GH, SP ST
# LM and and SE maxes were 26 and 27 mm per day
# GH had two readings at 949 and 403 - the next smallest max was 29.5 so filtered it by 30
# SP had one reading at 1208, next smallest max was 25.4 so filtered by 26
# ST had many readings greater than 30 (some very large), if there was no precip at any of the other gauges
# and it was larger than ~25 then I assumed it was not real so used 24.5 as filter 
# since the next max that also occurred when other gauges had readings

tbAllFormat <- tbAll %>%
  mutate(GH = if_else(GH > 30.0, NA, GH),
         SP = if_else(SP > 26.0, NA, SP),
         ST = if_else(ST > 24.5, NA, ST))

# now start to format for Ages inputs
# -9999 for NA
# date should be dd.mm.yyyy
tbAllFormat <- tbAllFormat %>%
  mutate(across(everything(), ~ replace_na(., as.integer(-9999)))) %>%
  mutate(month = month(date)) %>%
  mutate(
    across(2:6, ~ if_else(!month %in% 6:9, -9999, .))) %>%
  select(-month) %>% 
  mutate(date = format(date, '%d.%m.%Y'))

write.csv(tbAllFormat,
          '/Users/megansears/Documents/Repos/fourmile/data/Archive/files_to_edit/tb16to20_formatted.csv')

```

# Prism supplement

```{r}

prismSupp <- read_csv('/Users/megansears/Documents/Repos/fourmile/data/Archive/files_to_edit/prismForStatn.csv') %>%
  mutate(date = dmy(date)) %>%
  mutate(month = month(date)) %>%
  mutate(
    across(2:8, ~ if_else(month %in% 6:9, -9999, .))) %>%
  select(-month) %>%
  mutate(date = format(date, '%d.%m.%Y'))

write.csv(prismSupp,
          '/Users/megansears/Documents/Repos/fourmile/data/Archive/files_to_edit/prismForStatn_formatted.csv')

```

### 2025-12-14 fourmile_output_dec2024.Rmd
met shifts

@@
 
-setwd('/Users/megansears/Documents/Repos/fourmile/38HRU_dec2024_updates')
+setwd('/Users/megansears/Documents/Repos/fourmile/38HRU_oct2025_updates')
 
@@
 
-setwd("/Users/megansears/Documents/Repos/fourmile/38HRU_dec2024_updates/cals")
+setwd("/Users/megansears/Documents/Repos/fourmile/38HRU_oct2025_updates/cals")
 
@@
 
-write_csv(params, '/Users/megansears/Documents/Repos/fourmile/38HRU_dec2024_updates/params_unburn.csv')
+write_csv(params, '/Users/megansears/Documents/Repos/fourmile/38HRU_oct2025_updates/params_unburn.csv')
 
@@
 # 
-#write_csv(params_combo, '/Users/megansears/Documents/Repos/fourmile/38HRU_dec2024_updates/params_burn_unburn.csv')
+write_csv(params_combo, '/Users/megansears/Documents/Repos/fourmile/38HRU_oct2025_updates/params_burn_unburn.csv')
 
@@
 
-#write_csv(params_weighted, '/Users/megansears/Documents/Repos/fourmile/38HRU_dec2024_updates/params_weighted_dec2024.csv')
+write_csv(params_weighted, '/Users/megansears/Documents/Repos/fourmile/38HRU_oct2025_updates/params_weighted_oct2025.csv')
 
@@
 
-#write_csv(nseCats, '/Users/megansears/Documents/Repos/fourmile/38HRU_dec2024_updates/nseCats.csv')
+write_csv(nseCats, '/Users/megansears/Documents/Repos/fourmile/38HRU_oct2025_updates/nseCats.csv')
 
@@
 
-# write_csv(flow_plot,
-#           '/Users/megansears/Documents/Repos/fourmile/38HRU_dec2024_updates/all_kge.csv')
+write_csv(flow_plot,
+          '/Users/megansears/Documents/Repos/fourmile/38HRU_oct2025_updates/all_kge.csv')
 
@@
 
-#write_csv(pbiasCats, '/Users/megansears/Documents/Repos/fourmile/38HRU_dec2024_updates/pbiasCats.csv')
+write_csv(pbiasCats, '/Users/megansears/Documents/Repos/fourmile/38HRU_oct2025_updates/pbiasCats.csv')
 
@@
 
-gw_gridall <- read_csv(here('38HRU_dec2024_updates/catchment_output/grid_all.csv'), skip = 3) %>%
+gw_gridall <- read_csv(here('38HRU_oct2025_updates/catchment_output/grid_all.csv'), skip = 3) %>%
   slice(-c(1,2)) %>%
@@
 
-gw_statnall <- read_csv(here('38HRU_dec2024_updates/catchment_output/statn_all.csv'), skip = 3) %>%
+gw_statnall <- read_csv(here('38HRU_oct2025_updates/catchment_output/statn_all.csv'), skip = 3) %>%
   slice(-c(1,2)) %>%
@@
 ) %>%
-  mutate(date = mdy(time),
+  mutate(date = ymd(time),
          year = year(date)) %>%

### 2025-12-14 highestKGE_models.Rmd
met shifts

@@
 ```
+
+# Performance
+Above is old
+
+```{r}
+
+flow <- read_csv('/Users/megansears/Documents/Repos/fourmile/38HRU_oct2025_updates/discharge_table2.csv') %>%
+  filter(!obs == -9999) %>%
+  summarize(KGE_grid19_statnin = KGE(obs, grid2019_statninput),
+            KGE_statnall_gridin = KGE(obs, statnall_gridinput),
+            pbias_grid19_statnin = pbias(obs, grid2019_statninput),
+            pbias_statnall_gridin = pbias(obs, statnall_gridinput),
+            NSE_grid19_statnin = NSE(obs, grid2019_statninput),
+            NSE_statnall_gridin = NSE(obs, statnall_gridinput),
+            )
+
+flow
+
+```

### 2025-12-14 manuscriptFigures.Rmd
met shifts

@@
 library(here)
+library(sf)
 library(scales)
@@
 # because the climate outputs will not change due to changed  obs streamflow (removed 2013 flood Q)
-grid <- read_csv("./38HRU_sept2013_updates/grid_all_Catchment.csv",
+grid <- read_csv("./38HRU_oct2025_updates/grid_all_Catchment.csv",
                  skip=3) %>%
@@
 
-statn <- read_csv('./38HRU_sept2013_updates/statn_all_Catchment.csv',
+statn <- read_csv('./38HRU_oct2025_updates/statn_all_Catchment.csv',
                  skip=3) %>%
@@
 
-flow <- read_csv('./38HRU_dec2024_updates/discharge_all.csv') %>%
+flow <- read_csv('./38HRU_oct2025_updates/discharge_all.csv') %>%
   replace(.==-9999, NA) %>%
@@
 read_ages_grid <- function(filename){
-  read_csv(file.path("./38HRU_sept2013_updates/HRU_output/grid/", 
+  read_csv(file.path("./38HRU_oct2025_updates/HRU_output/grid/", 
                      filename), skip = 3) %>%
@@
 #pull in all filenames with HRU in the name
-filenames <- list.files("./38HRU_sept2013_updates/HRU_output/grid/", 
+filenames <- list.files("./38HRU_oct2025_updates/HRU_output/grid/", 
                         pattern="HRU", 
@@
 read_ages_statn <- function(filename){
-  read_csv(file.path("./38HRU_sept2013_updates/HRU_output/statn/", 
+  read_csv(file.path("./38HRU_oct2025_updates/HRU_output/statn/", 
                      filename), skip = 3) %>%
@@
 #pull in all filenames with HRU in the name
-filenames <- list.files("./38HRU_sept2013_updates/HRU_output/statn/", 
+filenames <- list.files("./38HRU_oct2025_updates/HRU_output/statn/", 
                         pattern="HRU", 
@@
 
-ggsave(filename = "./figures/figure3.pdf",
+ggsave(filename = "./figures/figure3_oct25.pdf",
        plot = final_plot,
@@
 # read in KGE values (all_kge also has nse and bias even tho name says otherwise)
-flow_plot <- read_csv('./38HRU_dec2024_updates/all_kge.csv') %>%
+flow_plot <- read_csv('./all_kge.csv') %>%
   filter(metric == 'KGE') %>%
@@
 
-pbiasCats <- read_csv('./38HRU_dec2024_updates/pbiasCats.csv') %>%
-  rename(source = input_data)
+pbiasCats <- read_csv('./pbiasCats.csv') #%>%
+  #rename(source = input_data)
 
@@
   facet_wrap(~source, labeller = labeller(source = new_facet_titles)) +
-   scale_fill_manual(values = c(
+scale_fill_manual(
+  breaks = c("Very good", "Good", "Satisfactory", "Unsatisfactory"),
+  values = c(
     "Unsatisfactory" = "#F1F4EEFF", 
@@
     "Very good"     = "#009474FF"
-  )) +
+  )
+)+
   geom_text(aes(label = sprintf("%0.1f", pbias),   # one decimal place
@@
 
-ggsave('./figures/figure4_biasLegend.png',
+ggsave('/Users/megansears/Documents/Repos/fourmile/figures/figure4_biasLegend.png',
        dpi=800,
@@
 
-nseCats <- read_csv('./38HRU_dec2024_updates/nseCats.csv') %>%
-  rename(source = input_data)
+nseCats <- read_csv('./nseCats.csv') #%>%
+  #rename(source = input_data)
 
@@
   facet_wrap(~source, labeller = labeller(source = new_facet_titles)) +
-  scale_fill_manual(values = c(
+scale_fill_manual(
+  breaks = c("Very good", "Good", "Satisfactory", "Unsatisfactory"),
+  values = c(
     "Unsatisfactory" = "#F1F4EEFF", 
@@
     "Very good"     = "#009474FF"
-  )) +
+  )
+)+
   geom_text(aes(label = sprintf("%.2f", nse), color = nseCat), 
@@
 
-ggsave('./figures/figure4_nseLegend.png',
+ggsave('/Users/megansears/Documents/Repos/fourmile/figures/figure4_nseLegend.png',
        dpi=800,
@@
 
-# ggsave('./figures/figure4_main.pdf',
-#        dpi=800,
-#        width = 10,
-#        height = 14,
-#        bg='white')
+final_grid_add
+
+ggsave('/Users/megansears/Documents/Repos/fourmile/figures/figure4_main_oct2025.pdf',
+       dpi=800,
+       width = 10,
+       height = 14,
+       bg='white')
 
@@
 # params area weighted (only for lagSurfaceRunoff, a_rain, a_snow)
-params <- read_csv('./38HRU_dec2024_updates/params_weighted_dec2024.csv') %>%
+params <- read_csv('./38HRU_oct2025_updates/params_weighted_oct2025.csv') %>%
   filter(param %in% c('lagSurfaceRunoff',
@@
 # params unburned (above is params that needed to be area weighted bc burn/unburn)
-params_unburn <- read_csv('./38HRU_dec2024_updates/params_unburn.csv') %>%
+params_unburn <- read_csv('./38HRU_oct2025_updates/params_unburn.csv') %>%
   filter(param %in% c('soilOutLPS',
@@
 # read in pbias categories
-pbias <- read_csv('./38HRU_dec2024_updates/pbiasCats.csv') %>%
+pbias <- read_csv('./38HRU_oct2025_updates/pbiasCats.csv') %>%
   filter(year == c('All')) %>%
-  dplyr::select(input_data, year_missing, pbias)
-
-nse <- read_csv('./38HRU_dec2024_updates/nseCats.csv') %>%
+  dplyr::select(source, year_missing, pbias)
+
+nse <- read_csv('./38HRU_oct2025_updates/nseCats.csv') %>%
   filter(year == c('All')) %>%
-  dplyr::select(input_data, year_missing, nse)
-
-perf <- left_join(nse, pbias, by = c('input_data',
+  dplyr::select(source, year_missing, nse)
+
+perf <- left_join(nse, pbias, by = c('source',
                                      'year_missing'))
@@
                                 nse > 0.5 & abs(pbias) < 25 ~ 'NSE + % bias satisfactory')) %>%
-  mutate(input_data = if_else(input_data == 'grid',
+  mutate(input_data = if_else(source == 'grid',
                               'Gridded', 'Station'),
@@
 
-ggsave('./figures/figure5.png',
+ggsave('./figures/figure5_oct2025.png',
        dpi=600,
@@
 
-ggsave('./figures/figure5_wlimits.png',
+ggsave('./figures/figure5_wlimits_oct2025.png',
        dpi=600,
@@
 # first take area weighted params (except lagSurfaceRunoff, a_rain, a_snow since that is already shown in main fig)
-otherParamsWeighted <- read_csv('./38HRU_dec2024_updates/updated_wranges/params_weighted_dec2024_ranges.csv') %>%
+otherParamsWeighted <- read_csv('./38HRU_oct2025_updates/updated_wranges/params_weighted_oct2025_ranges.csv') %>%
   filter(!param %in% c('lagSurfaceRunoff',
@@
          input_data = source) %>%
-  dplyr::select(param, input_data, value, min, max)
+  dplyr::select(param, input_data, value)
 
 # params that were not affected by burn
-otherParams <- read_csv('./38HRU_dec2024_updates/updated_wranges/params_unburn_ranges.csv') %>%
+otherParams <- read_csv('./38HRU_oct2025_updates/updated_wranges/params_unburn_ranges.csv') %>%
   filter(!param %in% c('soilOutLPS',
@@
 
-ggsave('./figures/remainingparams_boxplots_SUPP.png',
+ggsave('./figures/remainingparams_boxplots_SUPP_oct2025.png',
        dpi=600,
@@
   gw_gridall, gw_statnall) %>%
-  mutate(date = mdy(time),
+  mutate(date = ymd(time),
          year = year(date)) %>%
@@
 
-perf <- read_csv('./38HRU_dec2024_updates/nse_pbias_grid_statn_all.csv') %>%
+perf <- read_csv('./38HRU_oct2025_updates/nse_pbias_grid_statn_all.csv') %>%
   mutate(year = as.factor(year))
@@
   mutate(flow_cms = if_else(flow_type == 'yr_cum_RD1' &
-                                flow_cms > 48,
+                                flow_cms > 25,
                               NA,
@@
     #axis.ticks.x = element_blank()) +
-  scale_y_continuous(expand = expansion(mult = c(0.1, 0.15)))
+  scale_y_continuous(expand = expansion(mult = c(0.1, 0.2)))
 
@@
 
-ggsave('./figures/figure6.png',
+ggsave('./figures/figure6_oct2025.png',
        dpi=600,
@@
   group_by(source, year) %>%
-  mutate(fracFlow = (flow_cms/totFlow)*100) #%>%
+  mutate(fracFlow = (flow_cms/totFlow)*100) %>%
   group_by(source, flow_type) %>% 
@@
 
-statn_hi <- read_csv('./38HRU_dec2024_updates/HRU/statn_HRU_18.csv') %>% 
+statn_hi <- read_csv('./38HRU_oct2025_updates/HRU/statn_HRU_18.csv') %>% 
   mutate(date = mdy(time),
@@
 
-grid_hi <- read_csv('./38HRU_dec2024_updates/HRU/grid_HRU_18.csv') %>%
+grid_hi <- read_csv('./38HRU_oct2025_updates/HRU/grid_HRU_18.csv') %>%
   mutate(date = mdy(time),
@@
 
-statn_low <- read_csv('./38HRU_dec2024_updates/HRU/statn_HRU_19.csv') %>% 
+statn_low <- read_csv('./38HRU_oct2025_updates/HRU/statn_HRU_19.csv') %>% 
   mutate(date = mdy(time),
@@
 
-grid_low <- read_csv('./38HRU_dec2024_updates/HRU/grid_HRU_19.csv') %>%
+grid_low <- read_csv('./38HRU_oct2025_updates/HRU/grid_HRU_19.csv') %>%
   mutate(date = mdy(time),
@@
 
-ggsave('./figures/figure7.png',
+ggsave('./figures/figure7_oct2025.png',
        width = 10,
@@
 # 2016 flow partition
-gw_gridall <- read_csv(here('38HRU_dec2024_updates/catchment_output/grid_all.csv'), skip = 3) %>%
+gw_gridall <- read_csv(here('38HRU_oct2025_updates/catchment_output/grid_all.csv'), skip = 3) %>%
   slice(-c(1,2)) %>%
@@
 
-facet_labels <- c('yr_cum_RD1' = 'Surface runoff',
-                  'yr_cum_RD2' = 'Interflow',
-                  'yr_cum_RG1' = 'Fast groundwater',
-                  'yr_cum_RG2' = 'Slow groundwater')
+facet_labels <- c('RD1cumsum' = 'Surface runoff',
+                  'RD2cumsum' = 'Interflow',
+                  'RG1cumsum' = 'Fast groundwater',
+                  'RG2cumsum' = 'Slow groundwater')
 
@@
 
-ggsave('./figures/figure8.png',
+ggsave('./figures/figure8_oct2025.png',
        dpi=800,
@@
 # params that were cal w/ burned areas
-combo <- read_csv('./38HRU_dec2024_updates/params_burn_unburn.csv')
+combo <- read_csv('./38HRU_oct2025_updates/params_burn_unburn.csv')
 
 # read in pbias and nse cats
-pbias <- read_csv('./38HRU_dec2024_updates/pbiasCats.csv') %>%
+pbias <- read_csv('./38HRU_oct2025_updates/pbiasCats.csv') %>%
   filter(year == c('All')) %>%
-  dplyr::select(input_data, year_missing, pbias)
-
-nse <- read_csv('./38HRU_dec2024_updates/nseCats.csv') %>%
+  dplyr::select(source, year_missing, pbias)
+
+nse <- read_csv('./38HRU_oct2025_updates/nseCats.csv') %>%
   filter(year == c('All')) %>%
   dplyr::select(input_data, year_missing, nse)
-
 perf <- left_join(nse, pbias, by = c('input_data',
@@
 
-ggsave('./figures/figure9.png',
+ggsave('./figures/figure9_oct2025.png',
        dpi=800,

### 2025-12-14 fourmile_output_dec2024.Rmd
updating filepaths

@@
 # export
-ggsave('/Users/megansears/Documents/Repos/fourmile/figures/resids.png',
+ggsave('/Users/megansears/Documents/Repos/fourmile/figures/resids_oct2025.png',
        dpi=600,
@@
 
-flow <- read_csv('./discharge_all.csv') %>%
+flow <- read_csv('/Users/megansears/Documents/Repos/fourmile/38HRU_oct2025_updates/discharge_all.csv') %>%
   replace(.==-9999, NA) %>%

### 2025-12-14 manuscriptFigures.Rmd
added et plot to burn v unburn, updating filepaths

@@
   filter(year == c('All')) %>%
-  dplyr::select(input_data, year_missing, nse)
-perf <- left_join(nse, pbias, by = c('input_data',
+  dplyr::select(source, year_missing, nse)
+
+perf <- left_join(nse, pbias, by = c('source',
                                      'year_missing'))
@@
 
-unburn <- read_csv('./38HRU_dec2024_updates/HRU/statn_HRU_2_unburn.csv') %>%
+unburn <- read_csv('./38HRU_oct2025_updates/HRU/statn_HRU_2_unburn.csv') %>%
   mutate(date = mdy(time),
@@
 
-burn <- read_csv('./38HRU_dec2024_updates/HRU/statn_HRU_5_burn.csv') %>%
+burn <- read_csv('./38HRU_oct2025_updates/HRU/statn_HRU_5_burn.csv') %>%
   mutate(date = mdy(time),
@@
   dplyr::select(date, type, soilSat)
+
+et <- both %>%
+  dplyr::select(date, type, actET)
 
@@
 
+et_plot <- ggplot(et, aes(x = date,
+                        y = actET, 
+                        color = type)) +
+  geom_line(size=1, alpha=0.7) +
+    scale_color_manual(values = c("burn" = "red", 
+                                  "unburn" = "black")) +
+  scale_x_date(date_labels = "%b") +
+  labs(x = element_blank(),
+       y = 'ET (mm)') +
+  theme_bw(base_size = 20) +
+  theme(legend.position = 'bottom',
+    #legend.position = c(0.24, 0.852), 
+    legend.text = element_text(size = 10),
+    legend.title = element_blank(),
+    panel.grid = element_blank(),
+    panel.background = element_rect(fill = "white"),
+    strip.background = element_blank(),
+    text = element_text(color = "black"),
+    axis.title = element_text(color = "black"),
+    axis.text = element_text(color = "black"),
+    legend.key.width = unit(1, "cm")
+  )
+
+et_plot
+
 interflow_plot <- ggplot(interflow, aes(x = date,
@@
 swe_plot <- swe_plot + theme(legend.position = "none")
-
-plots <- plot_grid(p_plot,
+et_plot <- et_plot + theme(legend.position = "none")
+
+plots <- plot_grid( #p_plot,
           int_plot,
@@
           soilsat_plot,
+          et_plot,
           interflow_plot,
@@
 
-ggsave('./figures/figure10.png',
+ggsave('./figures/figure10_oct2025.png',
        dpi=800,
@@
 
-perf <- read_csv('/Users/megansears/Documents/Repos/fourmile/38HRU_dec2024_updates/perf_metrics.csv')
+perf <- read_csv('/Users/megansears/Documents/Repos/fourmile/38HRU_oct2025_updates/perf_metrics.csv')
 
@@
 
-pbias_kge <- ggplot(perf1, aes(x=KGE, y=pbias, color=type)) + 
+pbias_kge <- ggplot(perf1, aes(x=KGE, y=Bias, color=type)) + 
   #geom_point(size=4, alpha=0.8) +
@@
   scale_color_manual(values = c("#0047AB", "orange")) +
-  labs(y = '% bias') +
+  labs(y = 'Bias') +
   theme(
@@
 
-# ggsave('/Users/megansears/Documents/Repos/fourmile/figures/kge_nse_pbias.png',
-#        dpi=600,
-#        width=10,
-#        height=6)
+ggsave('/Users/megansears/Documents/Repos/fourmile/figures/figure11_oct2025.png',
+       dpi=600,
+       width=10,
+       height=6)
 

### 2025-12-14 params.Rmd
updating filepaths

@@
 
-combo <- read_csv('./38HRU_dec2024_updates/params_burn_unburn.csv') %>%
+combo <- read_csv('./38HRU_oct2025_updates/params_burn_unburn.csv') %>%
   mutate(burn = if_else(burn == "yes", "Burned", "Unburned"),
@@
 
-#write_csv(combo, './38HRU_dec2024_updates/params_burn_unburn.csv')
-combo <- read_csv('./38HRU_dec2024_updates/params_burn_unburn.csv')
+#write_csv(combo, './38HRU_oct2025_updates/params_burn_unburn.csv')
+combo <- read_csv('./38HRU_oct2025_updates/params_burn_unburn.csv')
 
